### 2023-11-08 GHI_enh_02_process.tex
Commit 2023-11-08 14:14

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  a4paper,oneside]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{placeins}
\captionsetup{font=small}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Enhancement of SDR in Thessaloniki},
  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2023-11-08}

\begin{document}
\maketitle
\begin{abstract}
Study of GHI enchantment.
\end{abstract}

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
Alpha * HAU is CS\_ref

\hypertarget{plot-some-days-with-strong-enhancement-cases}{%
\subsection{Plot some days with strong enhancement cases}\label{plot-some-days-with-strong-enhancement-cases}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-30} \end{center}

\textbf{END}

\begin{verbatim}
2023-11-08 09:12:54.0 athan@tyler GHI_enh_02_process.R 0.296492 mins
\end{verbatim}

\end{document}

### 2023-11-21 GHI_enh_02_process.tex
Commit 2023-11-21 12:14

@@
 \usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{longtable,booktabs,array}
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2023-11-08}
+\date{2023-11-21}
 
@@
 Alpha * HAU is CS\_ref
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/unnamed-chunk-6-1} \end{center}
 
@@
 
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/enchtrendyear-1}
+
+}
+
+\caption{Trend of the total of enhancement cases per year.}\label{fig:enchtrendyear}
+\end{figure}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\DocumentationTok{\#\# \_ Cases per month  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
+
+\FunctionTok{plot}\NormalTok{(Enh\_monthly}\SpecialCharTok{$}\NormalTok{Date, Enh\_monthly}\SpecialCharTok{$}\NormalTok{N\_att ,}
+     \AttributeTok{ylab =} \FunctionTok{bquote}\NormalTok{(}\StringTok{"Difference from mean [\%]"}\NormalTok{ )}
+\NormalTok{)}
+\CommentTok{\# title("Number of enchantments incidences", cex = 0.7)}
+\NormalTok{lm1        }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{( Enh\_monthly}\SpecialCharTok{$}\NormalTok{N\_att }\SpecialCharTok{\textasciitilde{}}\NormalTok{ Enh\_monthly}\SpecialCharTok{$}\NormalTok{Date )}
+\FunctionTok{abline}\NormalTok{(lm1, }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
+\NormalTok{fit }\OtherTok{\textless{}{-}}\NormalTok{ lm1[[}\DecValTok{1}\NormalTok{]]}
+\FunctionTok{legend}\NormalTok{(}\StringTok{\textquotesingle{}topleft\textquotesingle{}}\NormalTok{, }\AttributeTok{lty =} \DecValTok{1}\NormalTok{, }\AttributeTok{bty =} \StringTok{"n"}\NormalTok{,}
+       \FunctionTok{paste}\NormalTok{(}\StringTok{\textquotesingle{}Y =\textquotesingle{}}\NormalTok{, }\FunctionTok{signif}\NormalTok{(fit[}\DecValTok{1}\NormalTok{],}\DecValTok{2}\NormalTok{),}\ControlFlowTok{if}\NormalTok{(fit[}\DecValTok{2}\NormalTok{]}\SpecialCharTok{\textgreater{}}\DecValTok{0}\NormalTok{)}\StringTok{\textquotesingle{}+\textquotesingle{}}\NormalTok{else}\StringTok{\textquotesingle{}{-}\textquotesingle{}}\NormalTok{,}\FunctionTok{signif}\NormalTok{(}\FunctionTok{abs}\NormalTok{(fit[}\DecValTok{2}\NormalTok{]}\SpecialCharTok{*}\NormalTok{Days\_of\_year),}\DecValTok{3}\NormalTok{),}\StringTok{\textquotesingle{}* year\textquotesingle{}}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/unnamed-chunk-9-1} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\DocumentationTok{\#\# \_ Cases per day  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/enchtrendday-1}
+
+}
+
+\caption{Trend of the total of enhancement cases per year.}\label{fig:enchtrendday}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/enchNtrendday-1}
+
+}
+
+\caption{Trend of the total of enhancement cases per year.}\label{fig:enchNtrendday}
+\end{figure}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\DocumentationTok{\#\# ignore extreme cases for now}
+\CommentTok{\# plot(Enh\_sza$SZA, Enh\_sza$N\_ex)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/szacases-1}
+
+}
+
+\caption{Enhancement cases percentage in total GHI data per SZA ($1^\circ$ bin).}\label{fig:szacases}
+\end{figure}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\DocumentationTok{\#\# consecutive data id}
+\CommentTok{\# test \textless{}{-} c(F,T,F, rep(T,5),F,F,T,F,F,F, rep(T,5))}
+\CommentTok{\#}
+\CommentTok{\# DT \textless{}{-} data.table(test)}
+\CommentTok{\# DT[, cnF := cumsum(test == FALSE)]}
+\CommentTok{\# DT[, cnT := cumsum(test == TRUE) ]}
+\CommentTok{\# \# the realation of diff may be a general solution}
+\CommentTok{\# DT[, ddF := c(0, diff(cnF))]}
+\CommentTok{\# DT[, ddT := c(0, diff(cnT))]}
+\CommentTok{\#}
+\CommentTok{\# DT[, G1  := test]}
+\CommentTok{\# DT[, G0  := test]}
+\CommentTok{\#}
+\CommentTok{\#}
+\CommentTok{\# allow \textless{}{-} 1}
+\CommentTok{\# for (i in 1:nrow(DT)) \{}
+\CommentTok{\#     p1 \textless{}{-} i {-} 1}
+\CommentTok{\#     n1 \textless{}{-} i + 1}
+\CommentTok{\#     if (p1 \textgreater{} 0 \& n1 \textless{}= nrow(DT)) \{}
+\CommentTok{\#         if (DT$G1[p1] == TRUE  \&}
+\CommentTok{\#             DT$G1[i]  == FALSE \&}
+\CommentTok{\#             DT$G1[n1] == TRUE  ) \{}
+\CommentTok{\#             DT$G1[i]  \textless{}{-} TRUE}
+\CommentTok{\#         \}}
+\CommentTok{\#     \}}
+\CommentTok{\# \}}
+\CommentTok{\#}
+\CommentTok{\# DT[, Grp1 := rleid(c(NA,diff(cumsum(G1))))]}
+\CommentTok{\# DT[G1 == FALSE, Grp1 := NA]}
+\CommentTok{\#}
+\CommentTok{\# DT[, Grp0 := rleid(c(NA,diff(cumsum(G0))))]}
+\CommentTok{\# DT[G0 == FALSE, Grp0 := NA]}
+\CommentTok{\#}
+\CommentTok{\# DT}
+\end{Highlighting}
+\end{Shaded}
+
 \textbf{END}
@@
 \begin{verbatim}
-2023-11-08 09:12:54.0 athan@tyler GHI_enh_02_process.R 0.296492 mins
+2023-11-21 10:00:59.8 athan@sagan GHI_enh_02_process.R 0.429637 mins
 \end{verbatim}

### 2023-11-23 GHI_enh_01_raw_data.R
Commit 2023-11-23 20:14

@@ -54,7 +54,6 @@
 
 ## __ Document options ---------------------------------------------------------
 
-#+ ch01, echo=F, include=T
 knitr::opts_chunk$set(comment    = ""       )
 knitr::opts_chunk$set(echo       = FALSE    )
 knitr::opts_chunk$set(dev        = c("pdf", "png"))
@@ -62,7 +61,6 @@ knitr::opts_chunk$set(out.width  = "100%"   )
 knitr::opts_chunk$set(fig.align  = "center" )
 
 
-#+ ch02, include=T, echo=F
 ## __ Set environment ----------------------------------------------------------
 Sys.setenv(TZ = "UTC")
 Script.Name <- "./GHI_enh_02_process.R"
@@ -73,7 +71,7 @@ if (!interactive()) {
     sink(file = paste0("./runtime/",  basename(sub("\\.R$",".out", Script.Name))), split = TRUE)
 }
 
-#+ ch03, echo=F, include=T
+
 library(data.table, quietly = TRUE, warn.conflicts = FALSE)
 require(zoo       , quietly = TRUE, warn.conflicts = FALSE)
 library(pander    , quietly = TRUE, warn.conflicts = FALSE)
@@ -130,7 +128,6 @@ havetorun <- !file.exists(raw_input_data)                              |
     file.mtime(variables_fl)              > file.mtime(raw_input_data) |
     file.mtime("./GHI_enh_01_raw_data.R") > file.mtime(raw_input_data)
 
-#+ ch04, include=T, echo=F, results="asis"
 if (havetorun) {
     cat(paste("\n !! Create raw input data ->", raw_input_data), "\n")
 

### 2023-11-23 GHI_enh_01_raw_data.tex
Commit 2023-11-23 20:14

--- 2023-11-08 GHI_enh_02_process.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2023-11-08}
+\date{2023-11-23}
 
@@
 }
-Alpha * HAU is CS\_ref
+\#\# Prepare raw data for use in the paper
 
-\hypertarget{plot-some-days-with-strong-enhancement-cases}{%
-\subsection{Plot some days with strong enhancement cases}\label{plot-some-days-with-strong-enhancement-cases}}
+This collects raw data and prepare it mainly SDR analysis.
+It uses the data output of one of the ClearSky algorithms.
+It caches the raw data in order to reuse it in next states of analyses.
+Creates:
+- Raw\_Input.Rds
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-1} \end{center}
+\begin{verbatim}
+## 
+##  !! Create raw input data -> ./data/Raw_Input.Rds 
+## 
+##     Will read 31 input files
+## 
+##     Load data from Clear Sky process from original
+## 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1993.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1994.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1995.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1996.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1997.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1998.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1999.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2000.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2001.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2002.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2003.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2004.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2005.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2006.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2007.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2008.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2009.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2010.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2011.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2012.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2013.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2014.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2015.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2016.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2017.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2018.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2019.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2020.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2021.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2022.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2023.Rds 
+## 
+##   There are  0  duplicate dates remaining!
+## 
+##   Extra SKIP of CM-21 data!
+## 
+##   Select quality data only
+\end{verbatim}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-3} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-8} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-9} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-10} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-11} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-12} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-13} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-14} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-15} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-16} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-17} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-18} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-19} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-20} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-21} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-22} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-23} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-24} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-25} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-26} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-27} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-28} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-29} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-30} \end{center}
+\begin{verbatim}
+## Written:  ./figures/tbl_tsi_info.dat 
+## 
+## 
+##   Sun Earth distance correction
+## 
+##   Saved raw input data: ./data/Raw_Input.Rds
+\end{verbatim}
 
@@
 \begin{verbatim}
-2023-11-08 09:12:54.0 athan@tyler GHI_enh_02_process.R 0.296492 mins
+2023-11-23 16:53:58.9 athan@sagan GHI_enh_02_process.R 7.216420 mins
 \end{verbatim}

### 2023-11-23 GHI_enh_00_variables.R

@@ -52,6 +52,7 @@ common_data_14_2         <- "./data/common_data_14_2.Rda"
 variables_fl             <- "./GHI_enh_0_variables.R"
 data_procsess_fl         <- "./GHI_enh_00_raw_data.R"
 raw_input_data           <- "./data/Raw_Input.Rds"
+Input_data_ID            <- "./data/CE_ID_Input.Rds"
 I1_longterm              <- "./data/Input_1_longterm_trends.Rda"
 I2_szatrend              <- "./data/Input_2_sza_trends.Rda"
 I3_trendsconsist         <- "./data/Input_3_trends_consist.Rda"

### 2023-11-24 GHI_enh_01_raw_data.tex
Commit 2023-11-24 12:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2023-11-23}
+\date{2023-11-24}
 
@@
 ## 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1993.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1994.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1995.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1996.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1997.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1998.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1999.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2000.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2001.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2002.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2003.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2004.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2005.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2006.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2007.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2008.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2009.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2010.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2011.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2012.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2013.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2014.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2015.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2016.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2017.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2018.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2019.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2020.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2021.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2022.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2023.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1993.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1994.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1995.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1996.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1997.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1998.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1999.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2000.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2001.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2002.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2003.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2004.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2005.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2006.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2007.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2008.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2009.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2010.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2011.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2012.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2013.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2014.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2015.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2016.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2017.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2018.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2019.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2020.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2021.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2022.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2023.Rds 
 ## 
@@
 ##   Select quality data only
+## 
+## 
+## DROP DIRECT DATA POINTS: 0 !!
+## 
+## 
+## DROP GLOBAL DATA POINTS: 0 !!
 \end{verbatim}
@@
 \begin{verbatim}
-2023-11-23 16:53:58.9 athan@sagan GHI_enh_02_process.R 7.216420 mins
+2023-11-24 08:30:24.9 athan@sagan GHI_enh_02_process.R 6.690100 mins
 \end{verbatim}

### 2023-11-24 GHI_enh_03_process.tex
Commit 2023-11-24 22:14

--- 2023-11-21 GHI_enh_02_process.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2023-11-21}
+\date{2023-11-24}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/unnamed-chunk-6-1} \end{center}
-
-\hypertarget{plot-some-days-with-strong-enhancement-cases}{%
-\subsection{Plot some days with strong enhancement cases}\label{plot-some-days-with-strong-enhancement-cases}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-3} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-8} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-9} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-10} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-11} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-12} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-13} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-14} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-15} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-16} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-17} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-18} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-19} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-20} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-21} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-22} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-23} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-24} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-25} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-26} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-27} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-28} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-29} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-30} \end{center}
-
 \begin{figure}
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/enchtrendyear-1}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/enchtrendyear-1}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/unnamed-chunk-9-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-7-1} \end{center}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/enchtrendday-1}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/enchtrendday-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/enchNtrendday-1}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/enchNtrendday-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/szacases-1}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/szacases-1}
 
@@
 \begin{verbatim}
-2023-11-21 10:00:59.8 athan@sagan GHI_enh_02_process.R 0.429637 mins
+2023-11-24 16:31:40.1 athan@tyler GHI_enh_03_process.R 0.225677 mins
 \end{verbatim}

### 2023-11-25 GHI_enh_02_ID_CE.R
Commit 2023-11-25 12:14

@@ -47,8 +47,8 @@
 
 #+ echo=F, include=F
 knitr::opts_chunk$set(comment    = ""       )
-knitr::opts_chunk$set(dev        = c("pdf", "png"))
-# knitr::opts_chunk$set(dev        = "png"    )
+knitr::opts_chunk$set(dev        = c("pdf", "png")) ## expected option
+knitr::opts_chunk$set(dev        = "png"    )       ## too much data
 knitr::opts_chunk$set(out.width  = "100%"   )
 knitr::opts_chunk$set(fig.align  = "center" )
 knitr::opts_chunk$set(cache      =  FALSE   )  ## !! breaks calculations
@@ -196,10 +196,6 @@ SelEnhanc <- "Enhanc_C_1"
 # SelEnhanc <- "Enhanc_C_2"
 # SelEnhanc <- "Enhanc_C_3"
 
-# DATA[ , GLB_diff :=   wattGLB - CS_ref            ]  ## enhancement
-# DATA[ , GLB_ench := ( wattGLB - CS_ref ) / CS_ref ]  ## relative enhancement
-# DATA[ , GLB_rati :=   wattGLB / CS_ref            ]
-
 
 ## __ My criteria  ---------------------------------------------------------
 GLB_ench_THRES     <-  1.12 ## enchantment relative to HAU
@@ -216,8 +212,6 @@ DATA[, Enhanc_C_1 := FALSE]
 #          ClearnessIndex_kt > Clearness_Kt_THRES,
 #      Enhanc_C_1 := TRUE]
 
-# DATA[ ClearnessIndex_kt > Clearness_Kt_THRES,
-#      Enhanc_C_1 := TRUE]
 
 DATA[, Enhanc_C_1_ref := ETH * Clearness_Kt_THRES + GLB_diff_THRES]
 DATA[wattGLB > Enhanc_C_1_ref,
@@ -229,11 +223,6 @@ if (SelEnhanc == "Enhanc_C_1") {
     DATA[ , GLB_rati :=   wattGLB / Enhanc_C_1_ref                    ]
 }
 
-
-# DATA[CS_ref * GLB_ench_THRES + GLB_diff_THRES > ETH * Clearness_Kt_THRES, ]
-
-# DATA[wattGLB           > CS_ref * GLB_ench_THRES + GLB_diff_THRES,
-#      Enhanc_C_1 := TRUE]
 
 
 

### 2023-11-25 GHI_enh_02_ID_CE.R
Commit 2023-11-25 14:14

@@ -45,17 +45,16 @@
 
 ## __ Document options ---------------------------------------------------------
 
-#+ echo=F, include=F
+#+ echo=FALSE, include=TRUE
 knitr::opts_chunk$set(comment    = ""       )
-knitr::opts_chunk$set(dev        = c("pdf", "png")) ## expected option
-knitr::opts_chunk$set(dev        = "png"    )       ## too much data
+# knitr::opts_chunk$set(dev        = c("pdf", "png")) ## expected option
+knitr::opts_chunk$set(dev        = "png"    )       ## for too much data
 knitr::opts_chunk$set(out.width  = "100%"   )
 knitr::opts_chunk$set(fig.align  = "center" )
 knitr::opts_chunk$set(cache      =  FALSE   )  ## !! breaks calculations
-# knitr::opts_chunk$set(fig.pos    = '!h'    )
 
 
-#+ include=F, echo=F
+#+ echo=FALSE, include=TRUE
 ## __ Set environment ----------------------------------------------------------
 Sys.setenv(TZ = "UTC")
 Script.Name <- "./GHI_enh_02_ID_CE.R"
@@ -66,7 +65,7 @@ if (!interactive()) {
 }
 
 
-#+ echo=F, include=T
+#+ echo=FALSE, include=TRUE
 library(data.table, quietly = TRUE, warn.conflicts = FALSE)
 require(zoo       , quietly = TRUE, warn.conflicts = FALSE)
 library(pander    , quietly = TRUE, warn.conflicts = FALSE)
@@ -166,6 +165,7 @@ theme_set(theme_paper())
 
 
 
+alpha <- 0.9653023236718680788471
 
 
 
@@ -186,19 +186,15 @@ tic  <- Sys.time()
 #'
 #'  Alpha * HAU is CS_ref
 #'
-#+ include=FALSE, echo=FALSE
-alpha <- 0.9653023236718680788471
+#+ echo=TRUE, include=TRUE
 
-
-
-## __ Enhancement criteria  ------------------------------------------------
+## __ Enhancement criteria  ----------------------------------------------------
 SelEnhanc <- "Enhanc_C_1"
 # SelEnhanc <- "Enhanc_C_2"
 # SelEnhanc <- "Enhanc_C_3"
 
-
[…]

### 2023-11-25 GHI_enh_02_ID_CE.R
Commit 2023-11-25 20:14

@@ -314,7 +314,8 @@ enh_days <- DATA[get(SelEnhanc) == TRUE,
                  .(Enh_sum      = sum(GLB_ench, na.rm = TRUE),
                    Enh_max      = max(GLB_ench, na.rm = TRUE),
                    Enh_diff_sum = sum(GLB_diff, na.rm = TRUE),
-                   Enh_diff_max = max(GLB_diff, na.rm = TRUE)),
+                   Enh_diff_max = max(GLB_diff, na.rm = TRUE),
+                   Enh_N        = sum(get(SelEnhanc))),
                  Day]
 
 hist(enh_days$Enh_sum)
@@ -323,7 +324,7 @@ hist(enh_days$Enh_diff_max)
 hist(enh_days$Enh_diff_sum)
 
 
-sunny_days <- DATA[, .(Sunshine = sum(TYPE == "Clear")/max(DayLength, na.rm = TRUE),
+sunny_days <- DATA[, .(Sunshine = sum(TYPE == "Clear") / max(DayLength, na.rm = TRUE),
                        Energy   = sum(ClearnessIndex_kt, na.rm = TRUE)/sum(TYPE == "Clear"),
                        EC       = sum(get(SelEnhanc)),
                        Cloud    = sum(TYPE == "Cloud")),
@@ -351,14 +352,20 @@ sunnyd  <- sunny_days[Sunshine > 0.79 & Energy > 0.74]
 sunnyd  <- sunnyd[!Day %in% maxenhd$Day & !Day %in% enhsnd$Day]
 sunnyd  <- sunnyd[sample(1:nrow(sunnyd), 20)]
 
+
+## sunny with enhancements
+sunnyenh <- sunny_days[Sunshine > 0.77 & Energy > 0.73 & EC > 0]
+sunnyenh <- sunnyenh[!Day %in% maxenhd$Day & !Day %in% enhsnd$Day & !Day %in% sunnyd$Day]
+
+
 ## cloudy days
 clouds <- sunny_days[Sunshine > 0.6 & Energy > 0.6 & EC > 2 & Cloud > 5]
-clouds <- clouds[!Day %in% maxenhd$Day & !Day %in% enhsnd$Day & !Day %in% sunnyd$Day]
+clouds <- clouds[!Day %in% sunnyenh$Day & !Day %in% maxenhd$Day & !Day %in% enhsnd$Day & !Day %in% sunnyd$Day]
 clouds <- clouds[sample(1:nrow(clouds), 20)]
 
 ## some random days
[…]

### 2023-11-26 GHI_enh_02_ID_CE.R
Commit 2023-11-26 04:14

@@ -52,7 +52,7 @@ knitr::opts_chunk$set(dev        = "png"    )       ## for too much data
 knitr::opts_chunk$set(out.width  = "100%"   )
 knitr::opts_chunk$set(fig.align  = "center" )
 knitr::opts_chunk$set(cache      =  FALSE   )  ## !! breaks calculations
-
+knitr::opts_chunk$set(fig.pos    = '!h'     )
 
 #+ echo=FALSE, include=TRUE
 ## __ Set environment ----------------------------------------------------------
@@ -448,8 +448,9 @@ for (ii in 1:length(vecData)) {
 #+ echo=F, include=T
 
 
+##  Yearly plots  --------------------------------------------------------------
 
-#'
+#' \newpage
 #' \FloatBarrier
 #' # Plot years with enhancement cases
 #'

### 2023-11-27 article/article.qmd
Commit 2023-11-27 18:14

---
title:    SDR enhancement by clouds
subtitle: A Short Subtitle
author:

  - name:  Athanasios Natsis
    email: natsisphysicist@gmail.com
    affiliations: 
        - id:          auth
          name:        Aristotle University of Thessaloniki
          department:  Laboratory of Atmospheric Physics
          address:     Campus Box 149 
          city:        Thessaloniki
          state:       Greece
          postal-code: 54124
    attributes:
        corresponding: true
    note: This is the first author footnote.

  - name:  Alkiviadis Bais
    email: abais@auth.gr
    affiliations:
        - id: another-u
          name: Another University
          department: Department Name
          address: Street Address
          city: City
          state: State
          postal-code: Postal Code
    note: |
      Another author footnote, this is a very long footnote and it should be a really long footnote. But this footnote is not yet sufficiently long enough to make two lines of footnote text.

  - name:  Charikleia Meleti
    email: meleti@auth.gr
    affiliations:
        - ref: auth
    note: Yet another author footnote.

abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - keyword1
  - keyword2
date: last-modified
bibliography:  [bibliography.bib, Mainreferences.bib]
format:
  elsevier-pdf:
    keep-tex:     true
    journal:
      name:       Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
  docx: default
  html: default

editor_options: 
  chunk_output_type: console
---

# Intro

# Data and methodology

# Results

# Discussion and conclusions

------------------------------------------------------------------------

::: callout-important
## gcff

This is nice
:::

<!--# check this out -->

# Bibliography styles

Here are two sample references: @Feynman1963118 @Dirac1953888.

By default, natbib will be used with the `authoryear` style, set in `classoption` variable in YAML. You can sets extra options with `natbiboptions` variable in YAML header. Example

```         
natbiboptions: longnamesfirst,angle,semicolon
```

There are various more specific bibliography styles available at <https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files>. To use one of these, add it in the header using, for example, `biblio-style: model1-num-names`.

## Using CSL

If `cite-method` is set to `citeproc` in `elsevier_article()`, then pandoc is used for citations instead of `natbib`. In this case, the `csl` option is used to format the references. By default, this template will provide an appropriate style, but alternative `csl` files are available from <https://www.zotero.org/styles?q=elsevier>. These can be downloaded and stored locally, or the url can be used as in the example header.

@eq-lowbap

[@Bais1997]

[@Bais2013; @Bennie2008]

# Equations

Here is an equation: $$ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
$$ {#eq-lowbap}

Inline equations work as well: $\sum_{i = 2}^\infty\{\alpha_i^\beta\}$

# Figures and tables

@fig-meaningless is generated using an R chunk.

```{r}
#| label: fig-meaningless
#| fig-cap: A meaningless scatterplot
#| fig-width: 5
#| fig-height: 5
#| fig-align: center
#| out-width: 50%
#| echo: false
plot(runif(25), runif(25))
```

# Tables coming from R

Tables can also be generated using R chunks, as shown in @tbl-simple example.

```{r}
#| label: tbl-simple
#| tbl-cap: Caption centered above table
#| echo: true
knitr::kable(head(mtcars)[,1:4])
```

# References {.unnumbered}

### 2023-11-27 article/article.tex
Commit 2023-11-27 18:14

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  super,
  preprint,
  3p]{elsarticle}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={SDR enhancement by clouds},
  pdfauthor={Athanasios Natsis; Alkiviadis Bais; Charikleia Meleti},
  pdfkeywords={keyword1, keyword2},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\setlength{\parindent}{6pt}
\begin{document}

\begin{frontmatter}
\title{SDR enhancement by clouds \\\large{A Short Subtitle} }
\author[1]{Athanasios Natsis%
\corref{cor1}%
\fnref{fn1}}
 \ead{natsisphysicist@gmail.com} 
\author[2]{Alkiviadis Bais%
%
\fnref{fn2}}
 \ead{abais@auth.gr} 
\author[1]{Charikleia Meleti%
%
\fnref{fn3}}
 \ead{meleti@auth.gr}

\affiliation[1]{organization={Aristotle University of
Thessaloniki, Laboratory of Atmospheric Physics},addressline={Campus Box
149},city={Thessaloniki},postcode={54124},postcodesep={}}
\affiliation[2]{organization={Another University, Department
Name},addressline={Street Address},city={City},postcode={Postal
Code},postcodesep={}}

\cortext[cor1]{Corresponding author}
\fntext[fn1]{This is the first author footnote.}
\fntext[fn2]{Another author footnote, this is a very long footnote and
it should be a really long footnote. But this footnote is not yet
sufficiently long enough to make two lines of footnote text.}
\fntext[fn3]{Yet another author footnote.}

\begin{abstract}
This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo
rutrum at. Sed at tempus elit.
\end{abstract}

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, sharp corners]}{\end{tcolorbox}}\fi

\hypertarget{intro}{%
\section{Intro}\label{intro}}

\hypertarget{data-and-methodology}{%
\section{Data and methodology}\label{data-and-methodology}}

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion-and-conclusions}{%
\section{Discussion and conclusions}\label{discussion-and-conclusions}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, colframe=quarto-callout-important-color-frame, colbacktitle=quarto-callout-important-color!10!white, toptitle=1mm, bottomtitle=1mm, rightrule=.15mm, bottomrule=.15mm, opacitybacktitle=0.6, breakable, coltitle=black, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, titlerule=0mm, opacityback=0, left=2mm, arc=.35mm, toprule=.15mm, colback=white]

This is nice

\end{tcolorbox}

\hypertarget{bibliography-styles}{%
\section{Bibliography styles}\label{bibliography-styles}}

Here are two sample references: \citet{Feynman1963118}
\citet{Dirac1953888}.

By default, natbib will be used with the \texttt{authoryear} style, set
in \texttt{classoption} variable in YAML. You can sets extra options
with \texttt{natbiboptions} variable in YAML header. Example

\begin{verbatim}
natbiboptions: longnamesfirst,angle,semicolon
\end{verbatim}

There are various more specific bibliography styles available at
\url{https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files}.
To use one of these, add it in the header using, for example,
\texttt{biblio-style:\ model1-num-names}.

\hypertarget{using-csl}{%
\subsection{Using CSL}\label{using-csl}}

If \texttt{cite-method} is set to \texttt{citeproc} in
\texttt{elsevier\_article()}, then pandoc is used for citations instead
of \texttt{natbib}. In this case, the \texttt{csl} option is used to
format the references. By default, this template will provide an
appropriate style, but alternative \texttt{csl} files are available from
\url{https://www.zotero.org/styles?q=elsevier}. These can be downloaded
and stored locally, or the url can be used as in the example header.

Equation~\ref{eq-lowbap}

\citep{Bais1997}

\citep{Bais2013, Bennie2008}

\hypertarget{equations}{%
\section{Equations}\label{equations}}

Here is an equation: \begin{equation}\protect\hypertarget{eq-lowbap}{}{ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
}\label{eq-lowbap}\end{equation}

Inline equations work as well: \(\sum_{i = 2}^\infty\{\alpha_i^\beta\}\)

\hypertarget{figures-and-tables}{%
\section{Figures and tables}\label{figures-and-tables}}

Figure~\ref{fig-meaningless} is generated using an R chunk.

\begin{figure}

{\centering \includegraphics[width=0.5\textwidth,height=\textheight]{article_files/figure-pdf/fig-meaningless-1.pdf}

}

\caption{\label{fig-meaningless}A meaningless scatterplot}

\end{figure}

\hypertarget{tables-coming-from-r}{%
\section{Tables coming from R}\label{tables-coming-from-r}}

Tables can also be generated using R chunks, as shown in
Table~\ref{tbl-simple} example.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}\FunctionTok{head}\NormalTok{(mtcars)[,}\DecValTok{1}\SpecialCharTok{:}\DecValTok{4}\NormalTok{])}
\end{Highlighting}
\end{Shaded}

\hypertarget{tbl-simple}{}
\begin{longtable}[]{@{}lrrrr@{}}
\caption{\label{tbl-simple}Caption centered above table}\tabularnewline
\toprule\noalign{}
& mpg & cyl & disp & hp \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
& mpg & cyl & disp & hp \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Mazda RX4 & 21.0 & 6 & 160 & 110 \\
Mazda RX4 Wag & 21.0 & 6 & 160 & 110 \\
Datsun 710 & 22.8 & 4 & 108 & 93 \\
Hornet 4 Drive & 21.4 & 6 & 258 & 110 \\
Hornet Sportabout & 18.7 & 8 & 360 & 175 \\
Valiant & 18.1 & 6 & 225 & 105 \\
\end{longtable}

\renewcommand\refname{References}
  \bibliography{bibliography.bib,Mainreferences.bib}

\end{document}

### 2023-11-27 article/article.qmd
Commit 2023-11-27 20:14

@@
 date:          last-modified
-bibliography:  [bibliography.bib, Mainreferences.bib]
+bibliography:  [bibliography.bib]
 format:
@@
 
-[@Bais2013; @Bennie2008]
-
 # Equations

### 2023-11-27 article/article.tex
Commit 2023-11-27 20:14

@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, sharp corners]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, interior hidden, breakable, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi
 
@@
 
-\begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, colframe=quarto-callout-important-color-frame, colbacktitle=quarto-callout-important-color!10!white, toptitle=1mm, bottomtitle=1mm, rightrule=.15mm, bottomrule=.15mm, opacitybacktitle=0.6, breakable, coltitle=black, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, titlerule=0mm, opacityback=0, left=2mm, arc=.35mm, toprule=.15mm, colback=white]
+\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-important-color!10!white, opacityback=0, titlerule=0mm, arc=.35mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, toprule=.15mm, coltitle=black, breakable, bottomtitle=1mm, rightrule=.15mm, colframe=quarto-callout-important-color-frame, opacitybacktitle=0.6, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, left=2mm, colback=white]
 
@@
 \citep{Bais1997}
-
-\citep{Bais2013, Bennie2008}
 
@@
 \renewcommand\refname{References}
-  \bibliography{bibliography.bib,Mainreferences.bib}
+  \bibliography{bibliography.bib}
 

### 2023-11-27 GHI_enh_01_raw_data.tex
Commit 2023-11-25 12:14
Commit 2023-11-25 14:14
Commit 2023-11-25 16:14
Commit 2023-11-27 20:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2023-11-24}
+\date{2023-11-27}
 
@@
 ## 
-##  !! Create raw input data -> ./data/Raw_Input.Rds 
+##  !! Create raw input data -> ./data/CE_ID_Input.Rds 
 ## 
@@
 ## 
-##   Saved raw input data: ./data/Raw_Input.Rds
+##   Saved raw input data: ./data/CE_ID_Input.Rds
 \end{verbatim}
@@
 \begin{verbatim}
-2023-11-24 08:30:24.9 athan@sagan GHI_enh_02_process.R 6.690100 mins
+2023-11-27 16:57:17.7 athan@sagan GHI_enh_01_raw_data.R 5.129633 mins
 \end{verbatim}

### 2023-11-27 article/article.qmd
Commit 2023-11-27 22:14

@@
     note: This is the first author footnote.
-
   - name:  Alkiviadis Bais
@@
       Another author footnote, this is a very long footnote and it should be a really long footnote. But this footnote is not yet sufficiently long enough to make two lines of footnote text.
-
   - name:  Charikleia Meleti
@@
     note: Yet another author footnote.
-
 abstract: |
@@
       model:      3p
-      cite-style: super
+      cite-style: authoryear
   docx: default
   html: default
-
 editor_options: 
@@
 
+Data with quality control
+
+Clear sky identification
+- helps on determining thresholds
+
+Criteria for enhancement based on TSI
+- some other were tested
+
+Thresholds by inspecting a selection of days with some specs
+
 # Results
+
+- max
+- seasonal
+- trends
+- duration
+- occurrence
+- SZA
 

### 2023-11-27 article/article.tex
Commit 2023-11-27 22:14

@@
 \documentclass[
-  super,
+  authoryear,
   preprint,
@@
 \usepackage[]{natbib}
-\bibliographystyle{elsarticle-num}
+\bibliographystyle{elsarticle-harv}
 \IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, interior hidden, breakable, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, interior hidden, enhanced, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
 
@@
 \section{Data and methodology}\label{data-and-methodology}}
+
+Data with quality control
+
+Clear sky identification
+
+Criteria for enhancement based on TSI
+
+Thresholds by inspecting a selection of days with some specs
 
@@
 
-\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-important-color!10!white, opacityback=0, titlerule=0mm, arc=.35mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, toprule=.15mm, coltitle=black, breakable, bottomtitle=1mm, rightrule=.15mm, colframe=quarto-callout-important-color-frame, opacitybacktitle=0.6, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, left=2mm, colback=white]
+\begin{tcolorbox}[enhanced jigsaw, left=2mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, toptitle=1mm, leftrule=.75mm, colframe=quarto-callout-important-color-frame, rightrule=.15mm, opacitybacktitle=0.6, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, opacityback=0, bottomrule=.15mm, toprule=.15mm, colbacktitle=quarto-callout-important-color!10!white, coltitle=black, colback=white]
 

### 2023-11-28 article/article.tex
Commit 2023-11-28 08:14

@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, interior hidden, enhanced, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, boxrule=0pt, frame hidden, interior hidden, enhanced, sharp corners]}{\end{tcolorbox}}\fi
 
@@
 
-Clear sky identification
+Clear sky identification - helps on determining thresholds
 
-Criteria for enhancement based on TSI
+Criteria for enhancement based on TSI - some other were tested
 
@@
 
+\begin{itemize}
+\tightlist
+\item
+  max
+\item
+  seasonal
+\item
+  trends
+\item
+  duration
+\item
+  occurrence
+\item
+  SZA
+\end{itemize}
+
 \hypertarget{discussion-and-conclusions}{%
@@
 
-\begin{tcolorbox}[enhanced jigsaw, left=2mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, toptitle=1mm, leftrule=.75mm, colframe=quarto-callout-important-color-frame, rightrule=.15mm, opacitybacktitle=0.6, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, opacityback=0, bottomrule=.15mm, toprule=.15mm, colbacktitle=quarto-callout-important-color!10!white, coltitle=black, colback=white]
+\begin{tcolorbox}[enhanced jigsaw, colback=white, coltitle=black, left=2mm, colframe=quarto-callout-important-color-frame, rightrule=.15mm, toprule=.15mm, colbacktitle=quarto-callout-important-color!10!white, titlerule=0mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, leftrule=.75mm, opacityback=0, breakable, bottomtitle=1mm, opacitybacktitle=0.6, toptitle=1mm, arc=.35mm, bottomrule=.15mm]
 

### 2023-11-28 article/article.qmd
Commit 2023-11-28 12:14

@@
 
+### Data selection
+
+To preserve an unbiased representation of the data we applied a constrain similar the one used by @CastillejoCuberos2020.
+Where, for each valid hour of day, there must exist at list 45 minutes of valid measurements, including night time near sunrise and sunset.
+Days with less than 5 valid hours are rejected completely.
+
+<!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7), otherwise all data for this day is flagged as invalid.
+There must be at least This work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid, otherwise all minute data for this hour is flagged as invalid.
+-->
+
+-   CastillejoCuberos2020
+-   valid data 45min /h and 5h / day
+-   SZA above biology
+
 Clear sky identification
+
 -   helps on determining thresholds
@@
 Criteria for enhancement based on TSI
+
 -   some other were tested

### 2023-11-28 article/article.tex
Commit 2023-11-28 12:14

--- 2023-11-27 article/article.tex
@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, interior hidden, enhanced, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, sharp corners, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi
 
@@
 
+\hypertarget{data-selection}{%
+\subsubsection{Data selection}\label{data-selection}}
+
+To preserve an unbiased representation of the data we applied a
+constrain similar the one used by \citet{CastillejoCuberos2020}. Where,
+for each valid hour of day, there must exist at list 45 minutes of valid
+measurements, including night time, near dusk and dawn. Days with less
+than 5 complete hours are rejected completely.
+
+\begin{itemize}
+\tightlist
+\item
+  CastillejoCuberos2020
+\item
+  valid data 45min /h and 5h / day
+\item
+  SZA above biology
+\end{itemize}
+
 Clear sky identification
 
+\begin{itemize}
+\tightlist
+\item
+  helps on determining thresholds
+\end{itemize}
+
 Criteria for enhancement based on TSI
+
+\begin{itemize}
+\tightlist
+\item
+  some other were tested
+\end{itemize}
 
@@
 
-\begin{tcolorbox}[enhanced jigsaw, left=2mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, toptitle=1mm, leftrule=.75mm, colframe=quarto-callout-important-color-frame, rightrule=.15mm, opacitybacktitle=0.6, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, opacityback=0, bottomrule=.15mm, toprule=.15mm, colbacktitle=quarto-callout-important-color!10!white, coltitle=black, colback=white]
+\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, breakable, left=2mm, rightrule=.15mm, bottomrule=.15mm, colframe=quarto-callout-important-color-frame, colback=white, toprule=.15mm, colbacktitle=quarto-callout-important-color!10!white, bottomtitle=1mm, toptitle=1mm, coltitle=black, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, titlerule=0mm, arc=.35mm, opacityback=0, leftrule=.75mm]
 

### 2023-11-28 article/article.qmd
Commit 2023-11-28 14:14

@@
 ---
+
+```{r setup, echo=F, include=T, warning=FALSE, message=FALSE}
+suppressMessages(
+    res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
+)
+## document configurations
+knitr::opts_chunk$set(comment    = ""      )
+# knitr::opts_chunk$set(dev        = "pdf"   )
+knitr::opts_chunk$set(out.width  = "70%"   )
+knitr::opts_chunk$set(fig.align  = "center")
+knitr::opts_chunk$set(fig.pos    = 'h!'    )
+options(knitr.graphics.auto_pdf = FALSE)
+library(pander)
+library(data.table)
+library(kableExtra)
+library(dplyr)
+## load data from trends analysis
+source("../GHI_enh_00_variables.R")
+# load(common_data)
+# load("./data/Input_1_longterm_trends.Rda")
+## TSI data span info
+TSIinfo <- data.table(read.csv("../figures/tbl_tsi_info.dat",
+                    strip.white = TRUE,
+                    sep = ";",
+                    header = TRUE))
+
+# ## create local citations file and links here
+# source("~/CODE/FUNCTIONS/R/gather_citations.R")
+# suppressMessages(
+#     gather_citations(
+#         sourcefile   = "./Article.Rmd",
+#         mainreposit  = "./Mainreferences.bib",
+#         localreposit = "./references.bib",
+#         folderlink   = "./References_links",
+#         workingdir   = "./"
+#     )
+# )
+
+```
 

### 2023-11-28 article/article.tex
Commit 2023-11-28 14:14

@@
 
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 \makeatletter
@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, sharp corners, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, frame hidden, borderline west={3pt}{0pt}{shadecolor}, interior hidden, breakable, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi
 
@@
 for each valid hour of day, there must exist at list 45 minutes of valid
-measurements, including night time, near dusk and dawn. Days with less
-than 5 complete hours are rejected completely.
+measurements, including night time near sunrise and sunset. Days with
+less than 5 valid hours are rejected completely.
 
@@
 
-\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, breakable, left=2mm, rightrule=.15mm, bottomrule=.15mm, colframe=quarto-callout-important-color-frame, colback=white, toprule=.15mm, colbacktitle=quarto-callout-important-color!10!white, bottomtitle=1mm, toptitle=1mm, coltitle=black, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, titlerule=0mm, arc=.35mm, opacityback=0, leftrule=.75mm]
+\begin{tcolorbox}[enhanced jigsaw, colback=white, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, toptitle=1mm, titlerule=0mm, colbacktitle=quarto-callout-important-color!10!white, rightrule=.15mm, left=2mm, opacityback=0, bottomtitle=1mm, coltitle=black, leftrule=.75mm, breakable, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-important-color-frame, opacitybacktitle=0.6, toprule=.15mm]
 
@@
 
-\begin{figure}
+\begin{figure}[h!]
 
@@
 \hypertarget{tbl-simple}{}
-\begin{longtable}[]{@{}lrrrr@{}}
-\caption{\label{tbl-simple}Caption centered above table}\tabularnewline
-\toprule\noalign{}
-& mpg & cyl & disp & hp \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-& mpg & cyl & disp & hp \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Mazda RX4 & 21.0 & 6 & 160 & 110 \\
-Mazda RX4 Wag & 21.0 & 6 & 160 & 110 \\
-Datsun 710 & 22.8 & 4 & 108 & 93 \\
-Hornet 4 Drive & 21.4 & 6 & 258 & 110 \\
-Hornet Sportabout & 18.7 & 8 & 360 & 175 \\
-Valiant & 18.1 & 6 & 225 & 105 \\
-\end{longtable}
+\begin{table}
+\caption{\label{tbl-simple}Caption centered above table }\tabularnewline
+
+\centering
+\begin{tabular}{l|r|r|r|r}
+\hline
+  & mpg & cyl & disp & hp\\
+\hline
+Mazda RX4 & 21.0 & 6 & 160 & 110\\
+\hline
+Mazda RX4 Wag & 21.0 & 6 & 160 & 110\\
+\hline
+Datsun 710 & 22.8 & 4 & 108 & 93\\
+\hline
+Hornet 4 Drive & 21.4 & 6 & 258 & 110\\
+\hline
+Hornet Sportabout & 18.7 & 8 & 360 & 175\\
+\hline
+Valiant & 18.1 & 6 & 225 & 105\\
+\hline
+\end{tabular}
+\end{table}
 

### 2023-11-28 article/article.qmd
Commit 2023-11-28 15:09

@@
 
-Data with quality control
+## Data quality control
 
-### Data selection
+## Data selection
 
@@
 Days with less than 5 valid hours are rejected completely.
-
 <!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7), otherwise all data for this day is flagged as invalid.
 There must be at least This work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid, otherwise all minute data for this hour is flagged as invalid.
--->
+--> Furthermore, due to a systematic obstruction of the horizon and the significant measurement uncertainty on large SZAs, we excluded all data with $SZA > `r 90 - BIO_ELEVA`^\circ$.
 
--   CastillejoCuberos2020
--   valid data 45min /h and 5h / day
--   SZA above biology
+## Clear sky identification
 
-Clear sky identification
+Use it to find some interesting days to manual check the CE thresholds. No other usage of clear/cloud characterization in CE.
 
--   helps on determining thresholds
+## Criteria for enhancement based on TSI
 
-Criteria for enhancement based on TSI
+Many have used models or some statistical method to determine then CE thresholds.
+
+....... cite ...... Descriptions
+
+We used as reference the .... extraterrestrial horizontal irradiance .....
+
+ETH := cosde(SZA) * \text{TSI}
 

### 2023-11-28 article/article.tex
Commit 2023-11-28 15:09

@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, frame hidden, borderline west={3pt}{0pt}{shadecolor}, interior hidden, breakable, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced]}{\end{tcolorbox}}\fi
 
@@
 
-Data with quality control
+\hypertarget{data-quality-control}{%
+\subsection{Data quality control}\label{data-quality-control}}
 
 \hypertarget{data-selection}{%
-\subsubsection{Data selection}\label{data-selection}}
+\subsection{Data selection}\label{data-selection}}
 
@@
 measurements, including night time near sunrise and sunset. Days with
-less than 5 valid hours are rejected completely.
-
-\begin{itemize}
-\tightlist
-\item
-  CastillejoCuberos2020
-\item
-  valid data 45min /h and 5h / day
-\item
-  SZA above biology
-\end{itemize}
+less than 5 valid hours are rejected completely. Furthermore, due to a
+systematic obstruction of the horizon and the significant measurement
+uncertainty on large SZAs, we excluded all data with \(SZA > 78^\circ\).
 
@@
 
-\begin{tcolorbox}[enhanced jigsaw, colback=white, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, toptitle=1mm, titlerule=0mm, colbacktitle=quarto-callout-important-color!10!white, rightrule=.15mm, left=2mm, opacityback=0, bottomtitle=1mm, coltitle=black, leftrule=.75mm, breakable, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-important-color-frame, opacitybacktitle=0.6, toprule=.15mm]
+\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, left=2mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, leftrule=.75mm, toprule=.15mm, coltitle=black, titlerule=0mm, arc=.35mm, opacitybacktitle=0.6, bottomtitle=1mm, breakable, colframe=quarto-callout-important-color-frame, opacityback=0, bottomrule=.15mm, colbacktitle=quarto-callout-important-color!10!white, colback=white, toptitle=1mm]
 

### 2023-11-28 article/article.tex
Commit 2023-11-28 19:13

@@
 \begin{frontmatter}
-\title{SDR enhancement by clouds \\\large{A Short Subtitle} }
+\title{SDR enhancement by clouds \\\large{An analysis} }
 \author[1]{Athanasios Natsis%
@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, sharp corners, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden]}{\end{tcolorbox}}\fi
 
@@
 
-Clear sky identification
+\hypertarget{clear-sky-identification}{%
+\subsection{Clear sky identification}\label{clear-sky-identification}}
+
+Use it to find some interesting days to manual check the CE thresholds.
+No other usage of clear/cloud characterization in CE.
+
+\hypertarget{criteria-for-enhancement-based-on-tsi}{%
+\subsection{Criteria for enhancement based on
+TSI}\label{criteria-for-enhancement-based-on-tsi}}
+
+Many have used models or some statistical method to determine then CE
+thresholds.
+
+\ldots\ldots. cite \ldots\ldots{} Descriptions
+
+We used as reference the \ldots. extraterrestrial horizontal irradiance
+\ldots..
+
+\[
+\text{ETH} = \cos(\theta) \times \text{TSI}_\text{TOA}
+\]
+
+\begin{equation}\protect\hypertarget{eq-CEcrit1}{}{
+\text{GHI} > 0.8 \times \text{ETH} + 20\,Wm^{-2}
+}\label{eq-CEcrit1}\end{equation}
+
+Where GHI sddsfa
 
@@
 \item
-  helps on determining thresholds
-\end{itemize}
-
-Criteria for enhancement based on TSI
-
-\begin{itemize}
-\tightlist
-\item
-  some other were tested
+  some other were tested Equation~\ref{eq-CEcrit1}
 \end{itemize}
@@
 
-\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, left=2mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, leftrule=.75mm, toprule=.15mm, coltitle=black, titlerule=0mm, arc=.35mm, opacitybacktitle=0.6, bottomtitle=1mm, breakable, colframe=quarto-callout-important-color-frame, opacityback=0, bottomrule=.15mm, colbacktitle=quarto-callout-important-color!10!white, colback=white, toptitle=1mm]
+\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, leftrule=.75mm, colframe=quarto-callout-important-color-frame, breakable, coltitle=black, rightrule=.15mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, colbacktitle=quarto-callout-important-color!10!white, arc=.35mm, toptitle=1mm, left=2mm, bottomtitle=1mm, bottomrule=.15mm, titlerule=0mm, opacitybacktitle=0.6, opacityback=0, colback=white]
 
@@
 \end{tcolorbox}
-
-\hypertarget{bibliography-styles}{%
-\section{Bibliography styles}\label{bibliography-styles}}
-
-Here are two sample references: \citet{Feynman1963118}
-\citet{Dirac1953888}.
-
-By default, natbib will be used with the \texttt{authoryear} style, set
-in \texttt{classoption} variable in YAML. You can sets extra options
-with \texttt{natbiboptions} variable in YAML header. Example
-
-\begin{verbatim}
-natbiboptions: longnamesfirst,angle,semicolon
-\end{verbatim}
-
-There are various more specific bibliography styles available at
-\url{https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files}.
-To use one of these, add it in the header using, for example,
-\texttt{biblio-style:\ model1-num-names}.
-
-\hypertarget{using-csl}{%
-\subsection{Using CSL}\label{using-csl}}
-
-If \texttt{cite-method} is set to \texttt{citeproc} in
-\texttt{elsevier\_article()}, then pandoc is used for citations instead
-of \texttt{natbib}. In this case, the \texttt{csl} option is used to
-format the references. By default, this template will provide an
-appropriate style, but alternative \texttt{csl} files are available from
-\url{https://www.zotero.org/styles?q=elsevier}. These can be downloaded
-and stored locally, or the url can be used as in the example header.
-
-Equation~\ref{eq-lowbap}
-
-\citep{Bais1997}
-
-\hypertarget{equations}{%
-\section{Equations}\label{equations}}
-
-Here is an equation: \begin{equation}\protect\hypertarget{eq-lowbap}{}{ 
-  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
-  \left(\frac{x}{\beta}\right)^{\alpha-1}
-  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
-  \alpha,\beta,x > 0 .
-}\label{eq-lowbap}\end{equation}
-
-Inline equations work as well: \(\sum_{i = 2}^\infty\{\alpha_i^\beta\}\)
 

### 2023-11-28 GHI_enh_03_process.R

@@ -303,6 +303,43 @@ for (avar in grep("^month$", names(ST_E_monthly_seas), value = T, invert = T) ) 
 }
 
 
+# _ Yearly stats  --------------------------------------------------------------
+
+
+ST_yearly <- DATA[, unlist(lapply(.SD, data.summary, na.rm = FALSE),
+                            recursive = FALSE),
+                   .SDcols = my.cols,
+                   by = .(year(Date))]
+ST_yearly$Date <- as.POSIXct(strptime(paste(ST_yearly$year, "01", "1"),"%Y %m %d"))
+
+
+ST_extreme_yearly <- DATA[wattGLB > ETH,
+                           unlist(lapply(.SD, data.summary, na.rm = TRUE),
+                                  recursive = FALSE),
+                           .SDcols = my.cols,
+                           by = .(year(Date))]
+ST_extreme_yearly$Date <- as.POSIXct(strptime(paste(ST_extreme_yearly$year, "01", "1"),"%Y %m %d"))
+
+
+
+ST_E_yearly <- DATA[get(SelEnhanc) == TRUE,
+                     unlist(lapply(.SD, enhanc.summary, na.rm = FALSE),
+                            recursive = FALSE),
+                     .SDcols = my.cols,
+                     by = .(year(Date), month(Date))]
+ST_E_yearly <- as.POSIXct(strptime(paste(ST_E_yearly$year, "01", "1"),"%Y %m %d"))
+
+
+
+ST_E_yearly_seas <- DATA[get(SelEnhanc) == TRUE,
+                     unlist(lapply(.SD, enhanc.summary, na.rm = FALSE),
+                            recursive = FALSE),
+                     .SDcols = my.cols,
+                     by = .(month(Date))]
+
+
+
+
 
 # _ SZA stats  -----------------------------------------------------------------
 

### 2023-11-28 GHI_enh_01_raw_data.tex
Commit 2023-11-28 12:14
Commit 2023-11-28 20:14

--- 2023-11-23 GHI_enh_01_raw_data.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2023-11-23}
+\date{2023-11-28}
 
@@
 ## 
-##  !! Create raw input data -> ./data/Raw_Input.Rds 
-## 
-##     Will read 31 input files
-## 
-##     Load data from Clear Sky process from original
-## 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1993.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1994.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1995.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1996.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1997.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1998.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_1999.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2000.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2001.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2002.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2003.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2004.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2005.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2006.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2007.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2008.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2009.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2010.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2011.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2012.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2013.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2014.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2015.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2016.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2017.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2018.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2019.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2020.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2021.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2022.Rds 
-## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v14_2_2023.Rds 
-## 
-##   There are  0  duplicate dates remaining!
-## 
-##   Extra SKIP of CM-21 data!
-## 
-##   Select quality data only
-\end{verbatim}
-
-\begin{verbatim}
-## Written:  ./figures/tbl_tsi_info.dat 
-## 
-## 
-##   Sun Earth distance correction
-## 
-##   Saved raw input data: ./data/Raw_Input.Rds
+##  Raw input data are ready in  ./data/CE_ID_Input.Rds
 \end{verbatim}
@@
 \begin{verbatim}
-2023-11-23 16:53:58.9 athan@sagan GHI_enh_02_process.R 7.216420 mins
+2023-11-28 17:38:39.4 athan@sagan GHI_enh_01_raw_data.R 0.006276 mins
 \end{verbatim}

### 2024-01-10 GHI_enh_03_process.R
Commit 2024-01-10 11:17

@@ -297,7 +297,7 @@ ST_E_monthly <- DATA[get(SelEnhanc) == TRUE,
 ST_E_monthly <- as.POSIXct(strptime(paste(ST_E_monthly$year, ST_E_monthly$month, "1"),"%Y %m %d"))
 
 
-## mothly climatology
+## monthly climatology
 ST_E_monthly_seas <- DATA[get(SelEnhanc) == TRUE,
                      unlist(lapply(.SD, enhanc.summary, na.rm = FALSE),
                             recursive = FALSE),
@@ -342,13 +342,6 @@ ST_E_yearly <- DATA[get(SelEnhanc) == TRUE,
 ST_E_yearly <- as.POSIXct(strptime(paste(ST_E_yearly$year, "01", "1"),"%Y %m %d"))
 
 
-## seasonal stats on enhancement cases
-ST_E_yearly_seas <- DATA[get(SelEnhanc) == TRUE,
-                     unlist(lapply(.SD, enhanc.summary, na.rm = FALSE),
-                            recursive = FALSE),
-                     .SDcols = my.cols,
-                     by = .(month(Date))]
-
 
 
 
@@ -388,7 +381,7 @@ ST_E_sza <- DATA[get(SelEnhanc) == TRUE,
 
 
 ## Quarter of year with one month shift to include December in the next years winter
-DATA[,   season_Yqrt := as.yearqtr(as.yearmon(paste(year(Date), month(Date), sep = "-")) + 1/12)]
+DATA[,       season_Yqrt := as.yearqtr(as.yearmon(paste(year(Date), month(Date), sep = "-")) + 1/12)]
 ST_daily[,   season_Yqrt := as.yearqtr(as.yearmon(paste(year(Date), month(Date), sep = "-")) + 1/12)]
 ST_monthly[, season_Yqrt := as.yearqtr(as.yearmon(paste(year(Date), month(Date), sep = "-")) + 1/12)]
 
@@ -410,7 +403,7 @@ ST_monthly[season_Yqrt %% 1 == 0.75, Season := "Autumn"]
 # - by season
 # - by season_yqrt
 
-
+##TODO create deseasonal data
 
 #
 #

### 2024-01-15 GHI_enh_03_process.tex
Commit 2023-11-27 20:14
Commit 2024-01-15 12:16

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2023-11-24}
+\date{2024-01-15}
 
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/enchtrendyear-1}
-
-}
-
-\caption{Trend of the total of enhancement cases per year.}\label{fig:enchtrendyear}
-\end{figure}
+\hypertarget{time-series-decomposition-tests}{%
+\subsection{Time series decomposition tests}\label{time-series-decomposition-tests}}
 
@@
 \begin{Highlighting}[]
-\DocumentationTok{\#\# \_ Cases per month  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-
-\FunctionTok{plot}\NormalTok{(Enh\_monthly}\SpecialCharTok{$}\NormalTok{Date, Enh\_monthly}\SpecialCharTok{$}\NormalTok{N\_att ,}
-     \AttributeTok{ylab =} \FunctionTok{bquote}\NormalTok{(}\StringTok{"Difference from mean [\%]"}\NormalTok{ )}
-\NormalTok{)}
-\CommentTok{\# title("Number of enchantments incidences", cex = 0.7)}
-\NormalTok{lm1        }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{( Enh\_monthly}\SpecialCharTok{$}\NormalTok{N\_att }\SpecialCharTok{\textasciitilde{}}\NormalTok{ Enh\_monthly}\SpecialCharTok{$}\NormalTok{Date )}
-\FunctionTok{abline}\NormalTok{(lm1, }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
-\NormalTok{fit }\OtherTok{\textless{}{-}}\NormalTok{ lm1[[}\DecValTok{1}\NormalTok{]]}
-\FunctionTok{legend}\NormalTok{(}\StringTok{\textquotesingle{}topleft\textquotesingle{}}\NormalTok{, }\AttributeTok{lty =} \DecValTok{1}\NormalTok{, }\AttributeTok{bty =} \StringTok{"n"}\NormalTok{,}
-       \FunctionTok{paste}\NormalTok{(}\StringTok{\textquotesingle{}Y =\textquotesingle{}}\NormalTok{, }\FunctionTok{signif}\NormalTok{(fit[}\DecValTok{1}\NormalTok{],}\DecValTok{2}\NormalTok{),}\ControlFlowTok{if}\NormalTok{(fit[}\DecValTok{2}\NormalTok{]}\SpecialCharTok{\textgreater{}}\DecValTok{0}\NormalTok{)}\StringTok{\textquotesingle{}+\textquotesingle{}}\NormalTok{else}\StringTok{\textquotesingle{}{-}\textquotesingle{}}\NormalTok{,}\FunctionTok{signif}\NormalTok{(}\FunctionTok{abs}\NormalTok{(fit[}\DecValTok{2}\NormalTok{]}\SpecialCharTok{*}\NormalTok{Days\_of\_year),}\DecValTok{3}\NormalTok{),}\StringTok{\textquotesingle{}* year\textquotesingle{}}\NormalTok{))}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.mean)}
 \end{Highlighting}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-7-1} \end{center}
+\begin{verbatim}
+TypeError: Attempting to change the setter of an unconfigurable property.
+TypeError: Attempting to change the setter of an unconfigurable property.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-1} \end{center}
 
@@
 \begin{Highlighting}[]
-\DocumentationTok{\#\# \_ Cases per day  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.sum)}
 \end{Highlighting}
@@
 
-\begin{figure}
+\begin{verbatim}
+TypeError: Attempting to change the setter of an unconfigurable property.
+TypeError: Attempting to change the setter of an unconfigurable property.
+\end{verbatim}
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/enchtrendday-1}
-
-}
-
-\caption{Trend of the total of enhancement cases per year.}\label{fig:enchtrendday}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/enchNtrendday-1}
-
-}
-
-\caption{Trend of the total of enhancement cases per year.}\label{fig:enchNtrendday}
-\end{figure}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-2} \end{center}
 
@@
 \begin{Highlighting}[]
-\DocumentationTok{\#\# ignore extreme cases for now}
-\CommentTok{\# plot(Enh\_sza$SZA, Enh\_sza$N\_ex)}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.max)}
 \end{Highlighting}
@@
 
-\begin{figure}
+\begin{verbatim}
+TypeError: Attempting to change the setter of an unconfigurable property.
+TypeError: Attempting to change the setter of an unconfigurable property.
+\end{verbatim}
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/szacases-1}
-
-}
-
-\caption{Enhancement cases percentage in total GHI data per SZA ($1^\circ$ bin).}\label{fig:szacases}
-\end{figure}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-3} \end{center}
 
@@
 \begin{Highlighting}[]
-\DocumentationTok{\#\# consecutive data id}
-\CommentTok{\# test \textless{}{-} c(F,T,F, rep(T,5),F,F,T,F,F,F, rep(T,5))}
-\CommentTok{\#}
-\CommentTok{\# DT \textless{}{-} data.table(test)}
-\CommentTok{\# DT[, cnF := cumsum(test == FALSE)]}
-\CommentTok{\# DT[, cnT := cumsum(test == TRUE) ]}
-\CommentTok{\# \# the realation of diff may be a general solution}
-\CommentTok{\# DT[, ddF := c(0, diff(cnF))]}
-\CommentTok{\# DT[, ddT := c(0, diff(cnT))]}
-\CommentTok{\#}
-\CommentTok{\# DT[, G1  := test]}
-\CommentTok{\# DT[, G0  := test]}
-\CommentTok{\#}
-\CommentTok{\#}
-\CommentTok{\# allow \textless{}{-} 1}
-\CommentTok{\# for (i in 1:nrow(DT)) \{}
-\CommentTok{\#     p1 \textless{}{-} i {-} 1}
-\CommentTok{\#     n1 \textless{}{-} i + 1}
-\CommentTok{\#     if (p1 \textgreater{} 0 \& n1 \textless{}= nrow(DT)) \{}
-\CommentTok{\#         if (DT$G1[p1] == TRUE  \&}
-\CommentTok{\#             DT$G1[i]  == FALSE \&}
-\CommentTok{\#             DT$G1[n1] == TRUE  ) \{}
-\CommentTok{\#             DT$G1[i]  \textless{}{-} TRUE}
-\CommentTok{\#         \}}
-\CommentTok{\#     \}}
-\CommentTok{\# \}}
-\CommentTok{\#}
-\CommentTok{\# DT[, Grp1 := rleid(c(NA,diff(cumsum(G1))))]}
-\CommentTok{\# DT[G1 == FALSE, Grp1 := NA]}
-\CommentTok{\#}
-\CommentTok{\# DT[, Grp0 := rleid(c(NA,diff(cumsum(G0))))]}
-\CommentTok{\# DT[G0 == FALSE, Grp0 := NA]}
-\CommentTok{\#}
-\CommentTok{\# DT}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.N)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+TypeError: Attempting to change the setter of an unconfigurable property.
+TypeError: Attempting to change the setter of an unconfigurable property.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-4} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.mean)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+TypeError: Attempting to change the setter of an unconfigurable property.
+TypeError: Attempting to change the setter of an unconfigurable property.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-5} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.sum)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+TypeError: Attempting to change the setter of an unconfigurable property.
+TypeError: Attempting to change the setter of an unconfigurable property.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-6} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.max)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+TypeError: Attempting to change the setter of an unconfigurable property.
+TypeError: Attempting to change the setter of an unconfigurable property.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-7} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.N)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+TypeError: Attempting to change the setter of an unconfigurable property.
+TypeError: Attempting to change the setter of an unconfigurable property.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-8} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.mean)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+TypeError: Attempting to change the setter of an unconfigurable property.
+TypeError: Attempting to change the setter of an unconfigurable property.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-9} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.sum )}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+TypeError: Attempting to change the setter of an unconfigurable property.
+TypeError: Attempting to change the setter of an unconfigurable property.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-10} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.max )}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+TypeError: Attempting to change the setter of an unconfigurable property.
+TypeError: Attempting to change the setter of an unconfigurable property.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-11} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N   )}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+TypeError: Attempting to change the setter of an unconfigurable property.
+TypeError: Attempting to change the setter of an unconfigurable property.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-12} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N   ,}\AttributeTok{.smooth=}\NormalTok{T, }\AttributeTok{.smooth\_span =} \FloatTok{0.3}\NormalTok{, }\AttributeTok{.interactive =}\NormalTok{ F)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-13} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_acf\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{F, }\AttributeTok{.lags =}\DecValTok{1}\SpecialCharTok{:}\DecValTok{60}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-14} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_stl\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N,}
+                     \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"observed"}\NormalTok{,}\StringTok{"season"}\NormalTok{, }\StringTok{"trend"}\NormalTok{, }\StringTok{"remainder"}\NormalTok{),}
+                     \AttributeTok{.trend =} \DecValTok{180}\NormalTok{,}
+                     \AttributeTok{.frequency =} \DecValTok{30}\NormalTok{,}
+                     \AttributeTok{.interactive =}\NormalTok{ F}
+\NormalTok{                     )}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+frequency = 30 observations
+\end{verbatim}
+
+\begin{verbatim}
+trend = 180 observations
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-15} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_stl\_diagnostics}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N,}
+                     \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"observed"}\NormalTok{,}\StringTok{"season"}\NormalTok{, }\StringTok{"trend"}\NormalTok{, }\StringTok{"remainder"}\NormalTok{),}
+                     \AttributeTok{.trend =} \DecValTok{180}\NormalTok{,}
+                     \AttributeTok{.frequency =} \DecValTok{30}\NormalTok{,}
+                     \AttributeTok{.interactive =}\NormalTok{ F}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+frequency = 30 observations
+trend = 180 observations
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-16} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_seasonal\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{ F,}
+                          \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"week"}\NormalTok{, }\StringTok{"month.lbl"}\NormalTok{, }\StringTok{"quarter"}\NormalTok{, }\StringTok{"year"}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-17} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_seasonal\_diagnostics}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{ F)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-18} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# https://business{-}science.github.io/timetk/articles/TK08\_Automatic\_Anomaly\_Detection.html}
+
+\FunctionTok{plot\_time\_series\_regression}\NormalTok{(}
+    \AttributeTok{.data         =}\NormalTok{ ST\_E\_monthly,}
+    \AttributeTok{.date\_var     =}\NormalTok{ Date,}
+    \AttributeTok{.formula      =}\NormalTok{ wattGLB.N }\SpecialCharTok{\textasciitilde{}} \FunctionTok{as.numeric}\NormalTok{(Date)  ,}
+    \AttributeTok{.facet\_ncol   =} \DecValTok{2}\NormalTok{,}
+    \CommentTok{\# .interactive  = FALSE,}
+    \AttributeTok{.show\_summary =} \ConstantTok{TRUE}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+
+Call:
+stats::lm(formula = .formula, data = df)
+
+Residuals:
+   Min     1Q Median     3Q    Max 
+-404.5 -198.5  -82.3  139.7 1090.3
+
+Coefficients:
+                   Estimate Std. Error t value Pr(>|t|)    
+(Intercept)      -7.444e+01  6.622e+01  -1.124    0.262    
+as.numeric(Date)  3.317e-07  5.344e-08   6.207 1.51e-09 ***
+---
+Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+
+Residual standard error: 276.5 on 353 degrees of freedom
+Multiple R-squared:  0.09841,   Adjusted R-squared:  0.09585 
+F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09
+\end{verbatim}
+
+\begin{verbatim}
+TypeError: Attempting to change the setter of an unconfigurable property.
+TypeError: Attempting to change the setter of an unconfigurable property.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-19} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{lm1 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(ST\_E\_monthly}\SpecialCharTok{$}\NormalTok{wattGLB.N }\SpecialCharTok{\textasciitilde{}}\NormalTok{ ST\_E\_monthly}\SpecialCharTok{$}\NormalTok{Date)}
+\FunctionTok{summary}\NormalTok{(lm1)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+
+Call:
+lm(formula = ST_E_monthly$wattGLB.N ~ ST_E_monthly$Date)
+
+Residuals:
+   Min     1Q Median     3Q    Max 
+-404.5 -198.5  -82.3  139.7 1090.3
+
+Coefficients:
+                    Estimate Std. Error t value Pr(>|t|)    
+(Intercept)       -7.444e+01  6.622e+01  -1.124    0.262    
+ST_E_monthly$Date  3.317e-07  5.344e-08   6.207 1.51e-09 ***
+---
+Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+
+Residual standard error: 276.5 on 353 degrees of freedom
+Multiple R-squared:  0.09841,   Adjusted R-squared:  0.09585 
+F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot\_time\_series\_regression}\NormalTok{(}
+    \AttributeTok{.data         =}\NormalTok{ ST\_E\_daily,}
+    \AttributeTok{.date\_var     =}\NormalTok{ Date,}
+    \AttributeTok{.formula      =}\NormalTok{ wattGLB.N }\SpecialCharTok{\textasciitilde{}} \FunctionTok{as.numeric}\NormalTok{(Date)  ,}
+    \AttributeTok{.facet\_ncol   =} \DecValTok{2}\NormalTok{,}
+    \CommentTok{\# .interactive  = FALSE,}
+    \AttributeTok{.show\_summary =} \ConstantTok{FALSE}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+TypeError: Attempting to change the setter of an unconfigurable property.
+TypeError: Attempting to change the setter of an unconfigurable property.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-20} \end{center}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\#  Save from environment  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
+\DocumentationTok{\#\# Variables}
+\NormalTok{objects }\OtherTok{\textless{}{-}} \FunctionTok{grep}\NormalTok{(}\StringTok{"\^{}tic$|\^{}tac$|\^{}Script.Name$|\^{}tag$"}\NormalTok{, }\FunctionTok{ls}\NormalTok{(), }\AttributeTok{value =}\NormalTok{ T, }\AttributeTok{invert =}\NormalTok{ T)}
+\NormalTok{objects }\OtherTok{\textless{}{-}}\NormalTok{ objects[}\FunctionTok{sapply}\NormalTok{(objects, }\ControlFlowTok{function}\NormalTok{(x)}
+    \FunctionTok{is.numeric}\NormalTok{(}\FunctionTok{get}\NormalTok{(x)) }\SpecialCharTok{|}
+        \FunctionTok{is.character}\NormalTok{(}\FunctionTok{get}\NormalTok{(x)) }\SpecialCharTok{\&}
+        \FunctionTok{object.size}\NormalTok{(}\FunctionTok{get}\NormalTok{(x)) }\SpecialCharTok{\textless{}} \DecValTok{1009} \SpecialCharTok{\&}
+\NormalTok{        (}\SpecialCharTok{!}\FunctionTok{is.vector}\NormalTok{(}\FunctionTok{get}\NormalTok{(x)) }\SpecialCharTok{|}
+             \SpecialCharTok{!}\FunctionTok{is.function}\NormalTok{(}\FunctionTok{get}\NormalTok{(x))), }\AttributeTok{simplify =}\NormalTok{ T)]}
+\DocumentationTok{\#\# Data}
+\NormalTok{objects }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}
+\NormalTok{    objects,}
+    \FunctionTok{grep}\NormalTok{(}\StringTok{"\^{}ST\_"}\NormalTok{, }\FunctionTok{ls}\NormalTok{(), }\AttributeTok{value =} \ConstantTok{TRUE}\NormalTok{)}
+\NormalTok{)}
+
+\FunctionTok{save}\NormalTok{(}\AttributeTok{file =} \FunctionTok{paste0}\NormalTok{(}\StringTok{"./data/"}\NormalTok{, }\FunctionTok{basename}\NormalTok{(}\FunctionTok{sub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{.R"}\NormalTok{, }\StringTok{".Rda"}\NormalTok{, Script.Name))),}
+     \AttributeTok{list =}\NormalTok{ objects,}
+     \AttributeTok{compress =} \StringTok{"xz"}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{verbatim}
-2023-11-24 16:31:40.1 athan@tyler GHI_enh_03_process.R 0.225677 mins
+2024-01-15 09:05:38.4 athan@sagan GHI_enh_03_process.R 1.420055 mins
 \end{verbatim}

### 2024-01-15 GHI_enh_03_process.tex
Commit 2024-01-15 13:17

@@
 
+interactive FALSE
+
 \begin{Shaded}
 \begin{Highlighting}[]
-\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.mean)}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.mean, }\AttributeTok{.interactive =}\NormalTok{ isinter)}
 \end{Highlighting}
@@
 \begin{verbatim}
-TypeError: Attempting to change the setter of an unconfigurable property.
-TypeError: Attempting to change the setter of an unconfigurable property.
+Warning: Removed 2 rows containing missing values (`geom_line()`).
+Removed 2 rows containing missing values (`geom_line()`).
 \end{verbatim}
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.sum)}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.sum , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.max)}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.max , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.N)}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.N   , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
 \end{Highlighting}
 \end{Shaded}
-
-\begin{verbatim}
-TypeError: Attempting to change the setter of an unconfigurable property.
-TypeError: Attempting to change the setter of an unconfigurable property.
-\end{verbatim}
 
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N   ,}\AttributeTok{.smooth=}\NormalTok{T, }\AttributeTok{.smooth\_span =} \FloatTok{0.3}\NormalTok{, }\AttributeTok{.interactive =}\NormalTok{ F)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-13} \end{center}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{plot\_acf\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{F, }\AttributeTok{.lags =}\DecValTok{1}\SpecialCharTok{:}\DecValTok{60}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-14} \end{center}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{plot\_stl\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N,}
-                     \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"observed"}\NormalTok{,}\StringTok{"season"}\NormalTok{, }\StringTok{"trend"}\NormalTok{, }\StringTok{"remainder"}\NormalTok{),}
-                     \AttributeTok{.trend =} \DecValTok{180}\NormalTok{,}
-                     \AttributeTok{.frequency =} \DecValTok{30}\NormalTok{,}
-                     \AttributeTok{.interactive =}\NormalTok{ F}
-\NormalTok{                     )}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-frequency = 30 observations
-\end{verbatim}
-
-\begin{verbatim}
-trend = 180 observations
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-15} \end{center}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{plot\_stl\_diagnostics}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N,}
-                     \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"observed"}\NormalTok{,}\StringTok{"season"}\NormalTok{, }\StringTok{"trend"}\NormalTok{, }\StringTok{"remainder"}\NormalTok{),}
-                     \AttributeTok{.trend =} \DecValTok{180}\NormalTok{,}
-                     \AttributeTok{.frequency =} \DecValTok{30}\NormalTok{,}
-                     \AttributeTok{.interactive =}\NormalTok{ F}
-\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-frequency = 30 observations
-trend = 180 observations
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-16} \end{center}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{plot\_seasonal\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{ F,}
-                          \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"week"}\NormalTok{, }\StringTok{"month.lbl"}\NormalTok{, }\StringTok{"quarter"}\NormalTok{, }\StringTok{"year"}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-17} \end{center}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{plot\_seasonal\_diagnostics}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{ F)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-18} \end{center}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# https://business{-}science.github.io/timetk/articles/TK08\_Automatic\_Anomaly\_Detection.html}
-
-\FunctionTok{plot\_time\_series\_regression}\NormalTok{(}
-    \AttributeTok{.data         =}\NormalTok{ ST\_E\_monthly,}
-    \AttributeTok{.date\_var     =}\NormalTok{ Date,}
-    \AttributeTok{.formula      =}\NormalTok{ wattGLB.N }\SpecialCharTok{\textasciitilde{}} \FunctionTok{as.numeric}\NormalTok{(Date)  ,}
-    \AttributeTok{.facet\_ncol   =} \DecValTok{2}\NormalTok{,}
-    \CommentTok{\# .interactive  = FALSE,}
-    \AttributeTok{.show\_summary =} \ConstantTok{TRUE}
-\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-
-Call:
-stats::lm(formula = .formula, data = df)
-
-Residuals:
-   Min     1Q Median     3Q    Max 
--404.5 -198.5  -82.3  139.7 1090.3
-
-Coefficients:
-                   Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      -7.444e+01  6.622e+01  -1.124    0.262    
-as.numeric(Date)  3.317e-07  5.344e-08   6.207 1.51e-09 ***
----
-Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-
-Residual standard error: 276.5 on 353 degrees of freedom
-Multiple R-squared:  0.09841,   Adjusted R-squared:  0.09585 
-F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09
-\end{verbatim}
-
-\begin{verbatim}
-TypeError: Attempting to change the setter of an unconfigurable property.
-TypeError: Attempting to change the setter of an unconfigurable property.
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-19} \end{center}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{lm1 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(ST\_E\_monthly}\SpecialCharTok{$}\NormalTok{wattGLB.N }\SpecialCharTok{\textasciitilde{}}\NormalTok{ ST\_E\_monthly}\SpecialCharTok{$}\NormalTok{Date)}
-\FunctionTok{summary}\NormalTok{(lm1)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-
-Call:
-lm(formula = ST_E_monthly$wattGLB.N ~ ST_E_monthly$Date)
-
-Residuals:
-   Min     1Q Median     3Q    Max 
--404.5 -198.5  -82.3  139.7 1090.3
-
-Coefficients:
-                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       -7.444e+01  6.622e+01  -1.124    0.262    
-ST_E_monthly$Date  3.317e-07  5.344e-08   6.207 1.51e-09 ***
----
-Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-
-Residual standard error: 276.5 on 353 degrees of freedom
-Multiple R-squared:  0.09841,   Adjusted R-squared:  0.09585 
-F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{plot\_time\_series\_regression}\NormalTok{(}
-    \AttributeTok{.data         =}\NormalTok{ ST\_E\_daily,}
-    \AttributeTok{.date\_var     =}\NormalTok{ Date,}
-    \AttributeTok{.formula      =}\NormalTok{ wattGLB.N }\SpecialCharTok{\textasciitilde{}} \FunctionTok{as.numeric}\NormalTok{(Date)  ,}
-    \AttributeTok{.facet\_ncol   =} \DecValTok{2}\NormalTok{,}
-    \CommentTok{\# .interactive  = FALSE,}
-    \AttributeTok{.show\_summary =} \ConstantTok{FALSE}
-\NormalTok{)}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N   , }\AttributeTok{.smooth =}\NormalTok{ T, }\AttributeTok{.smooth\_span =} \FloatTok{0.3}\NormalTok{ )}
 \end{Highlighting}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-20} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-13} \end{center}
 
@@
 \begin{Highlighting}[]
+\CommentTok{\#}
+\CommentTok{\#}
+\CommentTok{\# plot\_acf\_diagnostics(ST\_E\_daily, Date, wattGLB.N, .interactive = F, .lags = 1:60)}
+\CommentTok{\#}
+\CommentTok{\#}
+\CommentTok{\#}
+\CommentTok{\# plot\_stl\_diagnostics(ST\_E\_daily, Date, wattGLB.N,}
+\CommentTok{\#                      .feature\_set = c("observed","season", "trend", "remainder"),}
+\CommentTok{\#                      .trend = 180,}
+\CommentTok{\#                      .frequency = 30,}
+\CommentTok{\#                      .interactive = F}
+\CommentTok{\#                      )}
+\CommentTok{\#}
+\CommentTok{\# plot\_stl\_diagnostics(ST\_E\_monthly, Date, wattGLB.N,}
+\CommentTok{\#                      .feature\_set = c("observed","season", "trend", "remainder"),}
+\CommentTok{\#                      .trend = 180,}
+\CommentTok{\#                      .frequency = 30,}
+\CommentTok{\#                      .interactive = F}
+\CommentTok{\# )}
+\CommentTok{\#}
+\CommentTok{\#}
+\CommentTok{\# plot\_seasonal\_diagnostics(ST\_E\_daily, Date, wattGLB.N, .interactive = F,}
+\CommentTok{\#                           .feature\_set = c("week", "month.lbl", "quarter", "year"))}
+\CommentTok{\#}
+\CommentTok{\# plot\_seasonal\_diagnostics(ST\_E\_monthly, Date, wattGLB.N, .interactive = F)}
+\CommentTok{\#}
+\CommentTok{\# \# https://business{-}science.github.io/timetk/articles/TK08\_Automatic\_Anomaly\_Detection.html}
+\CommentTok{\#}
+\CommentTok{\# plot\_time\_series\_regression(}
+\CommentTok{\#     .data         = ST\_E\_monthly,}
+\CommentTok{\#     .date\_var     = Date,}
+\CommentTok{\#     .formula      = wattGLB.N \textasciitilde{} as.numeric(Date)  ,}
+\CommentTok{\#     .facet\_ncol   = 2,}
+\CommentTok{\#     \# .interactive  = FALSE,}
+\CommentTok{\#     .show\_summary = TRUE}
+\CommentTok{\# )}
+\CommentTok{\# lm1 \textless{}{-} lm(ST\_E\_monthly$wattGLB.N \textasciitilde{} ST\_E\_monthly$Date)}
+\CommentTok{\# summary(lm1)}
+\CommentTok{\#}
+\CommentTok{\# plot\_time\_series\_regression(}
+\CommentTok{\#     .data         = ST\_E\_daily,}
+\CommentTok{\#     .date\_var     = Date,}
+\CommentTok{\#     .formula      = wattGLB.N \textasciitilde{} as.numeric(Date)  ,}
+\CommentTok{\#     .facet\_ncol   = 2,}
+\CommentTok{\#     \# .interactive  = FALSE,}
+\CommentTok{\#     .show\_summary = FALSE}
+\CommentTok{\# )}
+
 \CommentTok{\#  Save from environment  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
@@
 \begin{verbatim}
-2024-01-15 09:05:38.4 athan@sagan GHI_enh_03_process.R 1.420055 mins
+2024-01-15 10:23:12.5 athan@sagan GHI_enh_03_process.R 1.167804 mins
 \end{verbatim}

### 2024-01-16 GHI_enh_00_variables.R
Commit 2024-01-16 12:15

@@ -1,25 +1,5 @@
 
-## Variables for project
-
-#### dictionary ####
-dict <- list(DIR_att    = 'Dir. Beam Irrad.',
-             HOR_att    = 'Dir. Irrad. horizontal plane',
-             DIR_transp = 'Transp. for Dir. Irrad.',
-             GLB_att    = "SDR",
-             tsi1au_att = "TSI at 1au",
-             CLOUD      = "Cloudy sky cond.")
-## function to translate objects names
-translate <- function(x) {
-    res <- c()
-    for (ax in x) {
-        res <- c(res,
-                 as.vector(unlist(
-                     dict[stringr::str_detect(ax, names(dict))]
-                 ))
-        )
-    }
-    return(res)
-}
+## Project Variables
 
 
 #### Data range ####

### 2024-01-16 GHI_enh_03_process.tex
Commit 2024-01-16 12:15

--- 2024-01-15 GHI_enh_03_process.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-01-15}
+\date{2024-01-16}
 
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.mean)}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.mean, }\AttributeTok{.interactive =}\NormalTok{ isinter)}
 \end{Highlighting}
 \end{Shaded}
-
-\begin{verbatim}
-TypeError: Attempting to change the setter of an unconfigurable property.
-TypeError: Attempting to change the setter of an unconfigurable property.
-\end{verbatim}
 
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.sum)}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.sum , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
 \end{Highlighting}
 \end{Shaded}
-
-\begin{verbatim}
-TypeError: Attempting to change the setter of an unconfigurable property.
-TypeError: Attempting to change the setter of an unconfigurable property.
-\end{verbatim}
 
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.max)}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.max , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
 \end{Highlighting}
 \end{Shaded}
-
-\begin{verbatim}
-TypeError: Attempting to change the setter of an unconfigurable property.
-TypeError: Attempting to change the setter of an unconfigurable property.
-\end{verbatim}
 
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.N)}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_daily, Date, wattGLB.N   , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
 \end{Highlighting}
 \end{Shaded}
-
-\begin{verbatim}
-TypeError: Attempting to change the setter of an unconfigurable property.
-TypeError: Attempting to change the setter of an unconfigurable property.
-\end{verbatim}
 
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.mean)}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.mean, }\AttributeTok{.interactive =}\NormalTok{ isinter)}
 \end{Highlighting}
 \end{Shaded}
-
-\begin{verbatim}
-TypeError: Attempting to change the setter of an unconfigurable property.
-TypeError: Attempting to change the setter of an unconfigurable property.
-\end{verbatim}
 
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.sum )}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.sum , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
 \end{Highlighting}
 \end{Shaded}
-
-\begin{verbatim}
-TypeError: Attempting to change the setter of an unconfigurable property.
-TypeError: Attempting to change the setter of an unconfigurable property.
-\end{verbatim}
 
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.max )}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.max , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
 \end{Highlighting}
 \end{Shaded}
-
-\begin{verbatim}
-TypeError: Attempting to change the setter of an unconfigurable property.
-TypeError: Attempting to change the setter of an unconfigurable property.
-\end{verbatim}
 
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N   )}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N   , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
 \end{Highlighting}
 \end{Shaded}
-
-\begin{verbatim}
-TypeError: Attempting to change the setter of an unconfigurable property.
-TypeError: Attempting to change the setter of an unconfigurable property.
-\end{verbatim}
 
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N   ,}\AttributeTok{.smooth=}\NormalTok{T, }\AttributeTok{.smooth\_span =} \FloatTok{0.3}\NormalTok{, }\AttributeTok{.interactive =}\NormalTok{ F)}
+\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N   , }\AttributeTok{.interactive =}\NormalTok{ isinter, }\AttributeTok{.smooth =}\NormalTok{ T, }\AttributeTok{.smooth\_span =} \FloatTok{0.3}\NormalTok{ )}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_acf\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{F, }\AttributeTok{.lags =}\DecValTok{1}\SpecialCharTok{:}\DecValTok{60}\NormalTok{)}
+\FunctionTok{plot\_acf\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N, }\AttributeTok{.lags =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{60}\NormalTok{, }\AttributeTok{.interactive =}\NormalTok{ isinter)}
 \end{Highlighting}
@@
                      \AttributeTok{.frequency =} \DecValTok{30}\NormalTok{,}
-                     \AttributeTok{.interactive =}\NormalTok{ F}
+                     \AttributeTok{.interactive =}\NormalTok{ isinter}
 \NormalTok{                     )}
@@
                      \AttributeTok{.frequency =} \DecValTok{30}\NormalTok{,}
-                     \AttributeTok{.interactive =}\NormalTok{ F}
-\NormalTok{)}
+                     \AttributeTok{.interactive =}\NormalTok{ isinter}
+\NormalTok{                     )}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_seasonal\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{ F,}
+\FunctionTok{plot\_seasonal\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{ isinter,}
                           \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"week"}\NormalTok{, }\StringTok{"month.lbl"}\NormalTok{, }\StringTok{"quarter"}\NormalTok{, }\StringTok{"year"}\NormalTok{))}
@@
 \begin{Highlighting}[]
-\FunctionTok{plot\_seasonal\_diagnostics}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{ F)}
+\FunctionTok{plot\_seasonal\_diagnostics}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{ isinter)}
 \end{Highlighting}
@@
     \AttributeTok{.facet\_ncol   =} \DecValTok{2}\NormalTok{,}
-    \CommentTok{\# .interactive  = FALSE,}
+    \AttributeTok{.interactive  =}\NormalTok{ isinter,}
     \AttributeTok{.show\_summary =} \ConstantTok{TRUE}
@@
 F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09
-\end{verbatim}
-
-\begin{verbatim}
-TypeError: Attempting to change the setter of an unconfigurable property.
-TypeError: Attempting to change the setter of an unconfigurable property.
 \end{verbatim}
@@
     \AttributeTok{.facet\_ncol   =} \DecValTok{2}\NormalTok{,}
-    \CommentTok{\# .interactive  = FALSE,}
+    \AttributeTok{.interactive  =}\NormalTok{ isinter,}
     \AttributeTok{.show\_summary =} \ConstantTok{FALSE}
@@
 \end{Shaded}
-
-\begin{verbatim}
-TypeError: Attempting to change the setter of an unconfigurable property.
-TypeError: Attempting to change the setter of an unconfigurable property.
-\end{verbatim}
 
@@
 \begin{verbatim}
-2024-01-15 09:05:38.4 athan@sagan GHI_enh_03_process.R 1.420055 mins
+2024-01-16 09:31:56.9 athan@sagan GHI_enh_03_process.R 0.865834 mins
 \end{verbatim}

### 2024-01-16 GHI_enh_04_investigate.tex
Commit 2024-01-16 12:15

--- 2023-11-28 GHI_enh_01_raw_data.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2023-11-28}
+\date{2024-01-16}
 
@@
 }
-\#\# Prepare raw data for use in the paper
-
-This collects raw data and prepare it mainly SDR analysis.
-It uses the data output of one of the ClearSky algorithms.
-It caches the raw data in order to reuse it in next states of analyses.
-Creates:
-- Raw\_Input.Rds
-
 \begin{verbatim}
-## 
-##  Raw input data are ready in  ./data/CE_ID_Input.Rds
+ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
 \end{verbatim}
@@
 \begin{verbatim}
-2023-11-28 17:38:39.4 athan@sagan GHI_enh_01_raw_data.R 0.006276 mins
+2024-01-16 09:48:38.4 athan@sagan GHI_enh_04_investigate.R 0.000095 mins
 \end{verbatim}

### 2024-01-16 GHI_enh_00_dictionary.R
Commit 2024-01-16 13:14

@@ -1,12 +1,12 @@
 
-#### dictionary ####
+#### dictionary  ---------------------------------------------------------------
 dictionay <- list(
-    # Name        Short                             Long
-    ST_daily         = c("Daily",                       "Daily statistics",                       ),
-    ST_E_daily       = c("Daily Enhancements",           "Daily Enhancements",           ),
-    ST_E_daily_seas  = c("Seasonal Daily Enhancements", "Seasonal Daily Enhancements", ),
-    ST_extreme_daily = c("Daily Extreme Enhancements",   "Daily Extreme Enhancements",   ),
-    empty            = c(" --- empty --- ",             " --- empty --- "              )
+    # Name        Short                                 Long
+    ST_daily         = c("Daily",                       "Daily statistics"                      ),
+    ST_E_daily       = c("Daily Enhancements",          "Daily Enhancements statistics"         ),
+    ST_E_daily_seas  = c("Seasonal Daily Enhancements", "Seasonal Daily Enhancements"           ),
+    ST_extreme_daily = c("Daily Extreme Enhancements",  "Daily Extreme Enhancements statistics" ),
+    empty            = c(" --- empty --- ",             " --- empty --- "                       )
 )
 
 
@@ -41,4 +41,63 @@ tr_var <- function(x, type = "short") {
 
 
 tr_var(x = "DIR_att")
+
+
+
+## __ Set ggplot global theme  -------------------------------------------------
+
+theme_paper <- function(){
+    # font <- "Georgia"   #assign font family up front
+
+    theme_bw() %+replace%    #replace elements we want to change
+        theme(
+            # panel.grid.major = element_blank(),    #strip major gridlines
+            # panel.grid.minor = element_blank(),    #strip minor gridlines
+            panel.background   = element_rect(fill = 'transparent'), #transparent panel bg
+
+            # axis.ticks = element_blank(),          #strip axis ticks
+
+            #text elements
+            # plot.title = element_text(             #title
+            #     family = font,            #set font family
+            #     size = 20,                #set font size
+            #     face = 'bold',            #bold typeface
+            #     hjust = 0,                #left align
+            #     vjust = 2),               #raise slightly
+            #
+            # plot.subtitle = element_text(          #subtitle
+            #     family = font,            #font family
+            #     size = 14),               #font size
+            #
+            # plot.caption = element_text(           #caption
+            #     family = font,            #font family
+            #     size = 9,                 #font size
+            #     hjust = 1),               #right align
+            #
+            # axis.title = element_text(             #axis titles
[…]

### 2024-01-16 GHI_enh_04_investigate.tex
Commit 2024-01-16 13:14

@@
 \begin{verbatim}
+Loading required package: stringr
+\end{verbatim}
+
+\begin{verbatim}
+Run previous step: ./GHI_enh_03_process.R
+\end{verbatim}
+
+\begin{verbatim}
+
+Attaching package: 'timetk'
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:data.table':
+
+    :=
+\end{verbatim}
+
+\begin{verbatim}
+frequency = 30 observations
+\end{verbatim}
+
+\begin{verbatim}
+trend = 180 observations
+\end{verbatim}
+
+\begin{verbatim}
+frequency = 30 observations
+\end{verbatim}
+
+\begin{verbatim}
+trend = 180 observations
+\end{verbatim}
+
+\begin{verbatim}
+
+Call:
+stats::lm(formula = .formula, data = df)
+
+Residuals:
+   Min     1Q Median     3Q    Max 
+-404.5 -198.5  -82.3  139.7 1090.3
+
+Coefficients:
+                   Estimate Std. Error t value Pr(>|t|)    
+(Intercept)      -7.444e+01  6.622e+01  -1.124    0.262    
+as.numeric(Date)  3.317e-07  5.344e-08   6.207 1.51e-09 ***
+---
+Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+
+Residual standard error: 276.5 on 353 degrees of freedom
+Multiple R-squared:  0.09841,   Adjusted R-squared:  0.09585 
+F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09
+
+2024-01-16 10:20:53.2 athan@sagan GHI_enh_03_process.R 0.513138 mins
+\end{verbatim}
+
+\begin{verbatim}
 ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
@@
 \begin{verbatim}
-2024-01-16 09:48:38.4 athan@sagan GHI_enh_04_investigate.R 0.000095 mins
+2024-01-16 10:20:53.5 athan@sagan GHI_enh_03_process.R 0.000111 mins
 \end{verbatim}

### 2024-01-16 GHI_enh_01_raw_data.R

@@ -410,7 +410,6 @@ if (havetorun) {
     ## remove unused columns
     rm.cols.DT(DATA, "CSflag_*", quiet = TRUE)
 
-
     #  Save raw input data  ----------------------------------------------------
     saveRDS(DATA, file = raw_input_data, compress = "xz")
     cat("\n  Saved raw input data:", raw_input_data, "\n\n")

### 2024-01-16 GHI_enh_03_process.R

@@ -84,6 +84,7 @@ source("~/CODE/FUNCTIONS/R/trig_deg.R")
 ## __ Source initial scripts ---------------------------------------------------
 # source("./DHI_GHI_0_data_input.R")
 source("./GHI_enh_00_variables.R")
+source("./GHI_enh_00_dictionary.R")
 
 
 ## Overide notification function
@@ -97,9 +98,9 @@ options(error = function() {
 
 ##  Prepare raw data if needed  ------------------------------------------------
 if (
-    file.exists(Input_data_ID) == FALSE |
-    file.mtime(Input_data_ID) < file.mtime("./GHI_enh_00_variables.R") |
-    file.mtime(Input_data_ID) < file.mtime("./GHI_enh_02_ID_CE.R")
+    file.exists("data/GHI_enh_02_ID_CE.Rda") == FALSE |
+    file.mtime("data/GHI_enh_02_ID_CE.Rda") < file.mtime("./GHI_enh_00_variables.R") |
+    file.mtime("data/GHI_enh_02_ID_CE.Rda") < file.mtime("./GHI_enh_02_ID_CE.R")
 ) {
     source("./GHI_enh_02_ID_CE.R")
     dummy <- gc()
@@ -107,7 +108,7 @@ if (
 
 
 ##  Load Enhancement data  -----------------------------------------------------
-DATA <- readRDS(Input_data_ID)
+load("data/GHI_enh_02_ID_CE.Rda")
 DATA[, DOY := yday(Date)]
 tic  <- Sys.time()
 

### 2024-01-17 GHI_enh_04_investigate.tex
Commit 2024-01-17 12:16

--- 2024-01-16 GHI_enh_04_investigate.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-01-16}
+\date{2024-01-17}
 
@@
 \begin{verbatim}
+Loading required package: stringr
+\end{verbatim}
+
+\begin{verbatim}
 ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
 \end{verbatim}
+
+\newpage
+\FloatBarrier
+
+\hypertarget{trends-daily}{%
+\subsubsection{Trends daily}\label{trends-daily}}
+
+\newpage
+
+\hypertarget{trends-on-daily-observations-data}{%
+\paragraph{Trends on Daily Observations data}\label{trends-on-daily-observations-data}}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-3} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-8} \end{center}
+
+\newpage
+
+\hypertarget{trends-on-daily-enhancements-data}{%
+\paragraph{Trends on Daily Enhancements data}\label{trends-on-daily-enhancements-data}}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-9} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-10} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-11} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-12} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-13} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-14} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-15} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-16} \end{center}
 
@@
 \begin{verbatim}
-2024-01-16 09:48:38.4 athan@sagan GHI_enh_04_investigate.R 0.000095 mins
+2024-01-17 09:44:55.0 athan@sagan GHI_enh_04_investigate.R 0.066815 mins
 \end{verbatim}

### 2024-01-17 GHI_enh_04_investigate.tex
Commit 2024-01-17 13:17

@@
 
+\newpage
+
+\hypertarget{trends-on-daily-extreme-enhancements-data}{%
+\paragraph{Trends on Daily Extreme Enhancements data}\label{trends-on-daily-extreme-enhancements-data}}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-17} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-18} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-19} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-20} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-21} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-22} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-23} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-24} \end{center}
+
 \textbf{END}
@@
 \begin{verbatim}
-2024-01-17 09:44:55.0 athan@sagan GHI_enh_04_investigate.R 0.066815 mins
+2024-01-17 10:06:09.7 athan@sagan GHI_enh_04_investigate.R 0.091749 mins
 \end{verbatim}

### 2024-01-18 GHI_enh_04_investigate.tex
Commit 2024-01-18 18:18

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-01-17}
+\date{2024-01-18}
 
@@
 \begin{verbatim}
-Loading required package: stringr
-\end{verbatim}
-
-\begin{verbatim}
 ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
@@
 
-\hypertarget{trends-daily}{%
-\subsubsection{Trends daily}\label{trends-daily}}
+\hypertarget{daily-trends}{%
+\subsubsection{Daily Trends}\label{daily-trends}}
 
 \newpage
+
+\begin{verbatim}
+Loading required package: stringr
+\end{verbatim}
 
@@
 
+lmD: 1.71458 +/- 0.1322584
+
+lmY: 1.714601 +/- 0.1322612
+
+Tourpali: 1.7152 0.1817 9.4404 0
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-1} \end{center}
+
+lmD: 1.015311 +/- 0.173386
+
+lmY: 1.015342 +/- 0.1733898
+
+Tourpali: 1.1004 0.255 4.3146 0
+
+lmD: -0.1672102 +/- 0.1436958
+
+lmY: -0.1672003 +/- 0.1436989
+
+\begin{verbatim}
+Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
+possible convergence problem: optim gave code = 1
+\end{verbatim}
+
+\begin{verbatim}
+Warning in sqrt(diag(se)): NaNs produced
+
+Warning in sqrt(diag(se)): NaNs produced
+\end{verbatim}
 
@@
 
+Tourpali: -0.1679 3.8757 -0.0433 0.9654
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-3} \end{center}
+
+lmD: 605.1187 +/- 96.27827
+
+lmY: 605.1308 +/- 96.28033
+
+Tourpali: 605.7835 145.2351 4.1711 0
 
@@
 
+lmD: 0.002984713 +/- 0.0002850018
+
+lmY: 0.00298475 +/- 0.0002850079
+
+Tourpali: 0.003 4e-04 7.7371 0
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-5} \end{center}
+
+lmD: 0.001565283 +/- 0.0003220401
+
+lmY: 0.001565348 +/- 0.000322047
+
+Tourpali: 0.0018 5e-04 3.3956 7e-04
+
+lmD: -0.1672102 +/- 0.1436958
+
+lmY: -0.1672003 +/- 0.1436989
+
+\begin{verbatim}
+Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
+possible convergence problem: optim gave code = 1
+
+Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
+NaNs produced
+
+Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
+NaNs produced
+\end{verbatim}
 
@@
 
+Tourpali: -0.1679 3.8757 -0.0433 0.9654
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-7} \end{center}
+
+lmD: 0.9735636 +/- 0.1446246
+
+lmY: 0.9735884 +/- 0.1446277
+
+Tourpali: 1.0386 0.2143 4.8455 0
 
@@
 
+lmD: 0.7131394 +/- 0.1236589
+
+lmY: 0.7131522 +/- 0.1236614
+
+Tourpali: 0.7132 0.1476 4.8325 0
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-9} \end{center}
+
+lmD: 0.1205603 +/- 0.04472432
+
+lmY: 0.1205635 +/- 0.04472525
+
+Tourpali: 0.1206 0.0487 2.4752 0.0133
 
@@
 
+lmD: 0.5126011 +/- 0.05584138
+
+lmY: 0.5126089 +/- 0.05584254
+
+Tourpali: 0.5126 0.0703 7.2901 0
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-11} \end{center}
+
+lmD: 28.03241 +/- 3.452126
+
+lmY: 28.0328 +/- 3.452198
+
+Tourpali: 28.0362 4.3653 6.4225 0
 
@@
 
+lmD: 0.001091243 +/- 0.0001452364
+
+lmY: 0.001091258 +/- 0.0001452394
+
+Tourpali: 0.0011 2e-04 6.6404 0
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-13} \end{center}
+
+lmD: 0.0002586606 +/- 6.142941e-05
+
+lmY: 0.0002586644 +/- 6.143069e-05
+
+Tourpali: 3e-04 1e-04 3.7461 2e-04
 
@@
 
+lmD: 0.5126011 +/- 0.05584138
+
+lmY: 0.5126089 +/- 0.05584254
+
+Tourpali: 0.5126 0.0703 7.2901 0
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-15} \end{center}
+
+lmD: 0.03561979 +/- 0.004001997
+
+lmY: 0.03562032 +/- 0.004002081
+
+Tourpali: 0.0356 0.0048 7.3697 0
 
@@
 
+lmD: -0.1184401 +/- 0.3426654
+
+lmY: -0.1183983 +/- 0.3426728
+
+Tourpali: -0.1021 0.5303 -0.1925 0.8473
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-17} \end{center}
+
+lmD: -0.2498159 +/- 0.2873017
+
+lmY: -0.2497925 +/- 0.287308
+
+Tourpali: -0.249 0.4778 -0.5212 0.6022
 
@@
 
+lmD: 0.02397815 +/- 0.02221734
+
+lmY: 0.02397998 +/- 0.02221782
+
+Tourpali: 0.024 0.0229 1.0454 0.2959
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-19} \end{center}
+
+lmD: 4.678815 +/- 4.938622
+
+lmY: 4.679265 +/- 4.938728
+
+Tourpali: 4.6804 5.0982 0.9181 0.3586
 
@@
 
+lmD: 0.0002750923 +/- 0.0002421161
+
+lmY: 0.0002751196 +/- 0.0002421213
+
+Tourpali: 3e-04 3e-04 1.0722 0.2836
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-21} \end{center}
+
+lmD: 0.0001464247 +/- 0.0001495252
+
+lmY: 0.0001464348 +/- 0.0001495284
+
+Tourpali: 1e-04 2e-04 0.8844 0.3765
 
@@
 
+lmD: 0.02397815 +/- 0.02221734
+
+lmY: 0.02397998 +/- 0.02221782
+
+Tourpali: 0.024 0.0229 1.0454 0.2959
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-23} \end{center}
+
+lmD: 0.007036274 +/- 0.006116865
+
+lmY: 0.007036819 +/- 0.006116997
+
+Tourpali: 0.007 0.0063 1.1208 0.2624
 
@@
 \begin{verbatim}
-2024-01-17 10:06:09.7 athan@sagan GHI_enh_04_investigate.R 0.091749 mins
+2024-01-18 15:45:20.0 athan@sagan GHI_enh_04_investigate.R 0.179315 mins
 \end{verbatim}

### 2024-01-19 GHI_enh_05_distributions.R
Commit 2024-01-19 13:11

@@ -126,24 +126,20 @@ DRAFT <- TRUE
 ##  Daily  ---------------------------------------------------------------------
 
 
-names(DATA)
-
 #'
-#' \newpage
 #' \FloatBarrier
 #'
-#' ### Distributions
+#' ### Frequency Distributions
 #'
-#+ distributions, echo=F, include=T, results="asis"
+#+ freqdistributions, echo=F, include=T, results="asis"
 
 
 breaks <- 50
 hist(DATA[get(unique(CEC)) == TRUE, GLB_ench],
      breaks = breaks,
-     col  = varcol("GLB_ench"),
+     col  = varcol( "GLB_ench"),
      xlab = varname("GLB_ench"),
      main = varname("GLB_ench"))
-
 
 hist(DATA[get(unique(CEC)) == TRUE, GLB_diff],
      breaks = breaks,
@@ -151,19 +147,51 @@ hist(DATA[get(unique(CEC)) == TRUE, GLB_diff],
      xlab = bquote(.(varname("GLB_diff")) ~ group("[", W/m^2,"]")),
      main = bquote(.(varname("GLB_diff")) ~ group("[", W/m^2,"]")))
 
-
 hist(DATA[get(unique(CEC)) == TRUE, GLB_rati],
      breaks = breaks,
-     col  = varcol("GLB_rati"),
+     col  = varcol( "GLB_rati"),
+     xlab = varname("GLB_rati"),
+     main = varname("GLB_rati"))
+
+
+## test for one year
+ayear <- 2020
+
+hist(DATA[get(unique(CEC)) == TRUE & year(Date) == ayear, GLB_ench],
+     breaks = breaks,
+     col  = varcol( "GLB_ench"),
+     xlab = varname("GLB_ench"),
+     main = paste(varname("GLB_ench"), ayear))
+
+
+hist(DATA[get(unique(CEC)) == TRUE & year(Date) == ayear, GLB_diff],
+     breaks = breaks,
+     col  = varcol("GLB_diff"),
+     xlab = bquote(.(varname("GLB_diff")) ~ group("[", W/m^2,"]")),
+     main = bquote(.(varname("GLB_diff")) ~ group("[", W/m^2,"]")))
+
+hist(DATA[get(unique(CEC)) == TRUE & year(Date) == ayear, GLB_rati],
+     breaks = breaks,
+     col  = varcol( "GLB_rati"),
[…]

### 2024-01-21 GHI_enh_04_investigate.tex
Commit 2024-01-21 16:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-01-18}
+\date{2024-01-21}
 
@@
 }
+\begin{verbatim}
+
+Attaching package: 'zoo'
+\end{verbatim}
+
+\begin{verbatim}
+The following objects are masked from 'package:base':
+
+    as.Date, as.Date.numeric
+\end{verbatim}
+
 \begin{verbatim}
@@
 
-Tourpali: 1.7152 0.1817 9.4404 0
+Arima: 1.7152 0.1817 9.4404 0
 
@@
 
-Tourpali: 1.1004 0.255 4.3146 0
+Arima: 1.1004 0.255 4.3146 0
 
@@
 
-Tourpali: -0.1679 3.8757 -0.0433 0.9654
+Arima: -0.1679 3.8751 -0.0433 0.9654
 
@@
 
-Tourpali: 605.7835 145.2351 4.1711 0
+Arima: 605.7835 145.2351 4.1711 0
 
@@
 
-Tourpali: 0.003 4e-04 7.7371 0
+Arima: 0.003 4e-04 7.7371 0
 
@@
 
-Tourpali: 0.0018 5e-04 3.3956 7e-04
+Arima: 0.0018 5e-04 3.3956 7e-04
 
@@
 
-Tourpali: 1.0386 0.2143 4.8455 0
+Arima: 1.0386 0.2143 4.8455 0
 
@@
 
-Tourpali: 0.7132 0.1476 4.8325 0
+Arima: 0.7132 0.1476 4.8325 0
 
@@
 
-Tourpali: 0.1206 0.0487 2.4752 0.0133
+Arima: 0.1206 0.0487 2.4752 0.0133
 
@@
 
-Tourpali: 0.5126 0.0703 7.2901 0
+Arima: 0.5126 0.0703 7.2901 0
 
@@
 
-Tourpali: 28.0362 4.3653 6.4225 0
+Arima: 28.0362 4.3654 6.4224 0
 
@@
 
-Tourpali: 0.0011 2e-04 6.6404 0
+Arima: 0.0011 2e-04 6.6404 0
 
@@
 
-Tourpali: 3e-04 1e-04 3.7461 2e-04
+Arima: 3e-04 1e-04 3.7461 2e-04
 
@@
 
-Tourpali: 0.0356 0.0048 7.3697 0
+Arima: 0.0356 0.0048 7.3697 0
 
@@
 
-Tourpali: -0.1021 0.5303 -0.1925 0.8473
+Arima: -0.1021 0.5303 -0.1925 0.8473
 
@@
 
-Tourpali: -0.249 0.4778 -0.5212 0.6022
+Arima: -0.249 0.4778 -0.5212 0.6022
 
@@
 
-Tourpali: 0.024 0.0229 1.0454 0.2959
+Arima: 0.024 0.0229 1.0454 0.2959
 
@@
 
-Tourpali: 4.6804 5.0982 0.9181 0.3586
+Arima: 4.6804 5.0982 0.9181 0.3586
 
@@
 
-Tourpali: 3e-04 3e-04 1.0722 0.2836
+Arima: 3e-04 3e-04 1.0722 0.2836
 
@@
 
-Tourpali: 1e-04 2e-04 0.8844 0.3765
+Arima: 1e-04 2e-04 0.8844 0.3765
 
@@
 
-Tourpali: 0.007 0.0063 1.1208 0.2624
+Arima: 0.007 0.0063 1.1208 0.2624
 
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-24} \end{center}
+
+\newpage
+\FloatBarrier
+
+\hypertarget{group-stats}{%
+\subsubsection{Group stats}\label{group-stats}}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3} \end{center}
+
+\newpage
+\FloatBarrier
+
+\hypertarget{energy-contribution-of-enhancements}{%
+\subsubsection{Energy contribution of enhancements}\label{energy-contribution-of-enhancements}}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-3} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-4} \end{center}
+
+\newpage
+\FloatBarrier
+
+\hypertarget{sza-enhancements}{%
+\subsubsection{SZA enhancements}\label{sza-enhancements}}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-3} \end{center}
 
@@
 \begin{verbatim}
-2024-01-18 15:45:20.0 athan@sagan GHI_enh_04_investigate.R 0.179315 mins
+2024-01-21 11:10:50.8 athan@tyler GHI_enh_04_investigate.R 1.035152 mins
 \end{verbatim}

### 2024-01-21 GHI_enh_00_dictionary.R

@@ -67,6 +67,26 @@ varname <- function(avar) {
     )
 }
 
+## Stats name
+staname <- function(avar) {
+    switch(gsub(".*\\.", "", avar),
+           sum    = "totals",
+           min    = "minimum",
+           max    = "maximun",
+           median = "median",
+           sumPOS = "total of positives",
+           sumNEG = "total of negatives",
+           N_pos  = "number of positive cases",
+           N_neg  = "number of negative cases",
+           N      = "number of cases",
+           TotalN = "number of observations",
+           avar
+    )
+
+}
+
+
+
 # varcol("GLB_rati")
 # varcol("GLB_rati.max")
 

### 2024-01-22 GHI_enh_00_dictionary.R
Commit 2024-01-22 10:14

@@ -60,12 +60,15 @@ varcol <- function(avar) {
 ## Name for each variable
 varname <- function(avar) {
     switch(gsub("\\..*$", "", gsub(".*_", "", avar)),
-           diff = "Irradiance above reference",
-           ench = "Relative Enchancement",
-           rati = "Enchancement ratio",
+           diff    = "Irradiance above reference",
+           ench    = "Relative Enchancement",
+           rati    = "Enchancement ratio",
+           wattGLB = "GHI",
            avar
     )
 }
+
+
 
 ## Stats name
 staname <- function(avar) {

### 2024-01-22 GHI_enh_04_investigate.tex
Commit 2024-01-21 22:14
Commit 2024-01-22 10:14
Commit 2024-01-22 12:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-01-21}
+\date{2024-01-22}
 
@@
 
-Arima: -0.1679 3.8751 -0.0433 0.9654
+Arima: -0.1679 3.8757 -0.0433 0.9654
 
@@
 
-Arima: 28.0362 4.3654 6.4224 0
+Arima: 28.0362 4.3653 6.4225 0
 
@@
 
+@Zhang2018
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4} \end{center}
 
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-4} \end{center}
+
+@Martins2022
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-5} \end{center}
 
@@
 \begin{verbatim}
-2024-01-21 11:10:50.8 athan@tyler GHI_enh_04_investigate.R 1.035152 mins
+2024-01-22 08:48:56.1 athan@sagan GHI_enh_04_investigate.R 0.252639 mins
 \end{verbatim}

### 2024-01-22 GHI_enh_04_investigate.R

@@ -312,14 +312,23 @@ write.csv(x = dailytrendsY,
 #+ groups, echo=F, include=T, results="asis"
 
 
+
 hist(ST_G0$GLB_ench.N,
+     breaks = 50,
      xlab = "Minutes of enhacement",
      main = "Duration of enhancement cases")
+
 
 
 plot(ST_G0$GLB_ench.N, ST_G0$GLB_diff.sum/ST_G0$GLB_ench.N,
      xlab = "Duration of enhancemnt",
      ylab = "Extra Irradiance per mimute")
+
+
+cat( "@Zhang2018" )
+plot(ST_G0[, GLB_diff.max, GLB_diff.N ],
+     xlab = "Duration of enhancemnt",
+     ylab = "Maximun Over Irradiance")
 
 
 plot(ST_E_daily[, sum(GLB_ench.N), by = yday(Date)],

### 2024-01-26 GHI_enh_01_raw_data.tex
Commit 2023-11-30 19:12
Commit 2024-01-16 14:15
Commit 2024-01-26 12:14

--- 2023-11-27 GHI_enh_01_raw_data.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2023-11-27}
+\date{2024-01-26}
 
@@
 ## 
-##   Sun Earth distance correction
-## 
 ##   Saved raw input data: ./data/CE_ID_Input.Rds
@@
 \begin{verbatim}
-2023-11-27 16:57:17.7 athan@sagan GHI_enh_01_raw_data.R 5.129633 mins
+
+2024-01-26 09:51:48.2 athan@sagan GHI_enh_01_raw_data.R 5.347763 mins
 \end{verbatim}

### 2024-01-26 GHI_enh_01_raw_data.R

@@ -348,11 +348,11 @@ if (havetorun) {
     DATA[, ETH := cosde(SZA) * TSIextEARTH_comb ]  ## TSI at ground
     DATA[, ClearnessIndex_kt := wattGLB / ETH ]
 
-    ## _ Move measurements to mean earth distance  -----------------------------
-    cat("\n  Sun Earth distance correction\n")
-    DATA[, wattDIR_1au := wattDIR * (sun_dist ^ 2)]
-    DATA[, wattGLB_1au := wattGLB * (sun_dist ^ 2)]
-    DATA[, wattHOR_1au := wattHOR * (sun_dist ^ 2)]
+    # ## _ Move measurements to mean earth distance  -----------------------------
+    # cat("\n  Sun Earth distance correction\n")
+    # DATA[, wattDIR_1au := wattDIR * (sun_dist ^ 2)]
+    # DATA[, wattGLB_1au := wattGLB * (sun_dist ^ 2)]
+    # DATA[, wattHOR_1au := wattHOR * (sun_dist ^ 2)]
 
     ## fix noon just in case
     DATA[Azimuth <= 180 , preNoon := TRUE ]

### 2024-01-30 GHI_enh_01_raw_data.tex
Commit 2024-01-27 20:14
Commit 2024-01-30 09:09

--- 2023-11-28 GHI_enh_01_raw_data.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2023-11-28}
+\date{2024-01-30}
 
@@
 ## 
-##  Raw input data are ready in  ./data/CE_ID_Input.Rds
+##  !! Create raw input data -> ./data/CE_ID_Input.Rds 
+## 
+##     Will read 32 input files
+## 
+##     Load data from Clear Sky process from original
+## 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1993.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1994.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1995.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1996.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1997.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1998.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_1999.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2000.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2001.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2002.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2003.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2004.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2005.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2006.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2007.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2008.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2009.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2010.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2011.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2012.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2013.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2014.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2015.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2016.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2017.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2018.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2019.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2020.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2021.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2022.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2023.Rds 
+## READING: /home/athan/DATA/Broad_Band/CS_id/Clear_sky_id_Reno-Hansen_apply_v15_2024.Rds 
+## 
+##   There are  0  duplicate dates remaining!
+## 
+##   Extra SKIP of CM-21 data!
+## 
+##   Select quality data only
+## 
+## 
+## DROP DIRECT DATA POINTS: 0 !!
+## 
+## 
+## DROP GLOBAL DATA POINTS: 0 !!
+\end{verbatim}
+
+\begin{verbatim}
+## Written:  ./figures/tbl_tsi_info.dat 
+## 
+## 
+##   Saved raw input data: ./data/CE_ID_Input.Rds
 \end{verbatim}
@@
 \begin{verbatim}
-2023-11-28 17:38:39.4 athan@sagan GHI_enh_01_raw_data.R 0.006276 mins
+
+2024-01-30 06:18:12.9 athan@sagan GHI_enh_01_raw_data.R 5.010160 mins
 \end{verbatim}

### 2024-01-30 GHI_enh_03_process.tex
Commit 2024-01-16 14:15
Commit 2024-01-17 12:16
Commit 2024-01-18 12:18
Commit 2024-01-19 10:14
Commit 2024-01-20 20:15
Commit 2024-01-21 00:14
Commit 2024-01-21 16:14
Commit 2024-01-30 13:15

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-01-16}
+\date{2024-01-30}
 
@@
     Min      1Q  Median      3Q     Max 
--404.5 -198.5  -82.3  139.7 1090.3
+-414.28 -204.05  -79.81  138.47 1080.23
 
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      -7.444e+01  6.622e+01  -1.124    0.262    
-as.numeric(Date)  3.317e-07  5.344e-08   6.207 1.51e-09 ***
+(Intercept)      -9.272e+01  6.658e+01  -1.393    0.165    
+as.numeric(Date)  3.492e-07  5.341e-08   6.537 2.17e-10 ***
 ---
@@
 
-Residual standard error: 276.5 on 353 degrees of freedom
-Multiple R-squared:  0.09841,   Adjusted R-squared:  0.09585 
-F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09
+Residual standard error: 282.2 on 358 degrees of freedom
+Multiple R-squared:  0.1066,    Adjusted R-squared:  0.1041 
+F-statistic: 42.73 on 1 and 358 DF,  p-value: 2.168e-10
 \end{verbatim}
@@
                     Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       -7.444e+01  6.622e+01  -1.124    0.262    
-ST_E_monthly$Date  3.317e-07  5.344e-08   6.207 1.51e-09 ***
+(Intercept)       -9.272e+01  6.658e+01  -1.393    0.165    
+ST_E_monthly$Date  3.492e-07  5.341e-08   6.537 2.17e-10 ***
 ---
@@
 \begin{verbatim}
-2024-01-16 09:31:56.9 athan@sagan GHI_enh_03_process.R 0.865834 mins
+2024-01-30 10:54:28.8 athan@sagan GHI_enh_03_process.R 1.047631 mins
 \end{verbatim}

### 2024-02-09 Article.Rmd
Commit 2024-02-09 09:10

---
title:         "Trends of SDR in Thessaloniki"
# header-includes:
author:
  - name:         Athanasios N. Natsis 
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
#    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  Campus Box 149
    city:         Thessaloniki
    # state:        State
    postcode:     54124
    country:      Greece
#  - code:         Another University
#    organization: Department
#    addressline:  A street 29
#    postcode:     2054 NX
#    city:         Manchester,
#    country:      The Netherlands
# footnote:
#   - code:         1
#     text:         "This is the first author footnote."
#   - code:         2
#     text:         "Another author footnote."

abstract: |
  The shortwave downward solar irradiance (SDR) is an important factor that drives climate processes, production and can affect all living organisms.
  Observations of SDR at different locations around the world with different environmental

# back matter
keywords: |
  GHI; SDR; solar radiation; Solar Brigthening/Dimming; aerosols; clouds.

# acknowledgement: |
#   All sources of funding of the study should be disclosed. Please clearly
#   indicate grants that you have received in support of your research work.
#   Clearly state if you received funds for covering the costs to publish in open
#   access.

# authorcontributions: |
#   For research articles with several authors, a short paragraph specifying their
#   individual contributions must be provided. The following statements should be
#   used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the
#   experiments; X.X. and Y.Y. analyzed the data; W.W. contributed
#   reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
#   limited to those who have contributed substantially to the work reported.

funding: |
  This research received no external funding.

journal:         "An awesome journal"
date:            "`r Sys.Date()`"
classoption:     preprint, 3p, authoryear
bibliography:    Mainreferences.bib
linenumbers:     false
numbersections:  true
abbreviations:
  - short: DNI
    long: Direct beam/normal irradiance
  - short: CSid
    long: Clear sky identification algorithm
  - short: CUSUM
    long: Cumulative sum
  - short: SDR
    long: Solar downward radiation
  - short: SZA
    long: Solar zenith angle

header-includes:
   # - \usepackage{subfig}
   - \usepackage{subcaption}
   - \captionsetup[sub]{position=bottom, labelfont={bf, small, stretch=1.17}, labelsep=space, textfont={small, stretch=1.17}, aboveskip=6pt,  belowskip=-6pt, singlelinecheck=off, justification=justified}
   - \usepackage{placeins}

output: 
  rticles::mdpi_article:
    extra_dependencies:  longtable
    keep_tex:            yes
  bookdown::word_document2: default
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              no
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
---

```{r echo=F, include=T, warning=FALSE, message=FALSE}
suppressMessages(
    res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
)
## document configurations
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
library(kableExtra)
library(dplyr)
## load data from trends analysis
source("./DHI_GHI_00_raw_data.R")
load(common_data)
load("./data/Input_1_longterm_trends.Rda")
## number of measurements for each dataset
SDR_N_All   <- sum(  ALL_1_daily_DESEAS[,GLB_att_N])
SDR_N_Clear <- sum(CLEAR_1_daily_DESEAS[,GLB_att_N])
SDR_N_Cloud <- sum(CLOUD_1_daily_DESEAS[,GLB_att_N])
## TSI data span info
TSIinfo <- data.table(read.csv("./figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
## variables we use in the analysis
source("./DHI_GHI_0_variables.R")

## create local citations file and links here
source("~/CODE/FUNCTIONS/R/gather_citations.R")
suppressMessages(
    gather_citations(
        sourcefile   = "./Article.Rmd",
        mainreposit  = "./Mainreferences.bib",
        localreposit = "./references.bib",
        folderlink   = "./References_links",
        workingdir   = "./"
    )
)
```

# Introduction.

# Observational data and methodology.

# Results

# Conclusions

# References {-}

<div id="refs"></div>

# Appendix {-}

### 2024-02-09 GHI_enh_02_ID_CE.R
Commit 2024-02-09 11:09

@@ -114,7 +114,7 @@ if (
 
 ## __ Execution control  -------------------------------------------------------
 TEST <- FALSE
-# TEST <- TRUE
+TEST <- TRUE
 
 if (TEST) {
     warning("\n\n ** Test is active!! ** \n\n")
@@ -266,7 +266,7 @@ if (SelEnhanc == "Enhanc_C_3") {
 ## __ 4. my  Criteria  ---------------------------------------------------------
 
 ## set values base
-csmodel <- "Low_2_B.Low_2_W"
+csmodel <- "Low_B.Low_W"
 
 #'
 #' ## 4. Use libradtran **`r csmodel`** as reference for Clear sky.
@@ -277,10 +277,11 @@ csmodel <- "Low_2_B.Low_2_W"
 cat("\n USING CSMODE:", csmodel, "\n\n")
 
 switch(csmodel,
-       Low_B.Exact_W   = { C4_cs_ref_ratio <- 1.04 ; C4_GLB_diff_THRES <- 20 },
        Exact_B.Exact_W = { C4_cs_ref_ratio <- 1.02 ; C4_GLB_diff_THRES <- 55 },
-       Low_B.High_W    = { C4_cs_ref_ratio <- 1.05 ; C4_GLB_diff_THRES <- 20 },
        Low_2_B.Low_2_W = { C4_cs_ref_ratio <- 1.03 ; C4_GLB_diff_THRES <-  5 },
+       Low_B.Exact_W   = { C4_cs_ref_ratio <- 1.04 ; C4_GLB_diff_THRES <- 20 },
+       Low_B.High_W    = { C4_cs_ref_ratio <- 1.05 ; C4_GLB_diff_THRES <- 20 },
+       Low_B.Low_W     = { C4_cs_ref_ratio <- 1.07 ; C4_GLB_diff_THRES <-  0 },
                          { C4_cs_ref_ratio <- 1    ; C4_GLB_diff_THRES <-  0 })
 
 DATA[, Enhanc_C_4 := FALSE]

### 2024-02-19 GHI_enh_03_process.tex
Commit 2024-01-31 14:13
Commit 2024-02-01 14:14
Commit 2024-02-08 13:10
Commit 2024-02-19 13:11

--- 2024-01-16 GHI_enh_03_process.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-01-16}
+\date{2024-02-19}
 
@@
     Min      1Q  Median      3Q     Max 
--404.5 -198.5  -82.3  139.7 1090.3
+-448.24 -172.37  -59.22  113.90  892.70
 
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      -7.444e+01  6.622e+01  -1.124    0.262    
-as.numeric(Date)  3.317e-07  5.344e-08   6.207 1.51e-09 ***
+(Intercept)      -1.126e+02  5.761e+01  -1.955   0.0514 .  
+as.numeric(Date)  4.155e-07  4.624e-08   8.985   <2e-16 ***
 ---
@@
 
-Residual standard error: 276.5 on 353 degrees of freedom
-Multiple R-squared:  0.09841,   Adjusted R-squared:  0.09585 
-F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09
+Residual standard error: 244.7 on 359 degrees of freedom
+Multiple R-squared:  0.1836,    Adjusted R-squared:  0.1813 
+F-statistic: 80.72 on 1 and 359 DF,  p-value: < 2.2e-16
 \end{verbatim}
@@
                     Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       -7.444e+01  6.622e+01  -1.124    0.262    
-ST_E_monthly$Date  3.317e-07  5.344e-08   6.207 1.51e-09 ***
+(Intercept)       -1.126e+02  5.761e+01  -1.955   0.0514 .  
+ST_E_monthly$Date  4.155e-07  4.624e-08   8.985   <2e-16 ***
 ---
@@
 \begin{verbatim}
-2024-01-16 09:31:56.9 athan@sagan GHI_enh_03_process.R 0.865834 mins
+2024-02-19 10:09:06.3 athan@tyler GHI_enh_03_process.R 2.125423 mins
 \end{verbatim}

### 2024-02-19 GHI_enh_04_investigate.tex
Commit 2024-01-30 13:15
Commit 2024-01-31 14:13
Commit 2024-02-01 14:14
Commit 2024-02-08 13:10
Commit 2024-02-19 14:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-01-22}
+\date{2024-02-19}
 
@@
 Attaching package: 'zoo'
+\end{verbatim}
+
+\begin{verbatim}
+The following objects are masked from 'package:data.table':
+
+    yearmon, yearqtr
 \end{verbatim}
@@
 
-lmD: 1.71458 +/- 0.1322584
+lmD: 1.539332 +/- 0.1014749
 
-lmY: 1.714601 +/- 0.1322612
+lmY: 1.539352 +/- 0.1014768
 
-Arima: 1.7152 0.1817 9.4404 0
+Arima: 1.5397 0.1354 11.3752 0
 
@@
 
-lmD: 1.015311 +/- 0.173386
+lmD: 1.077113 +/- 0.1694257
 
-lmY: 1.015342 +/- 0.1733898
+lmY: 1.077139 +/- 0.1694289
 
-Arima: 1.1004 0.255 4.3146 0
+Arima: 1.1517 0.2512 4.5849 0
 
-lmD: -0.1672102 +/- 0.1436958
+lmD: 0.2020422 +/- 0.1403033
 
-lmY: -0.1672003 +/- 0.1436989
+lmY: 0.2020754 +/- 0.140306
 
@@
 
-Arima: -0.1679 3.8757 -0.0433 0.9654
+Arima: 0.2014 5.4204 0.0371 0.9704
 
@@
 
-lmD: 605.1187 +/- 96.27827
+lmD: 499.2985 +/- 96.76248
 
-lmY: 605.1308 +/- 96.28033
+lmY: 499.3033 +/- 96.76432
 
-Arima: 605.7835 145.2351 4.1711 0
+Arima: 500.4495 151.9546 3.2934 0.001
 
@@
 
-lmD: 0.002984713 +/- 0.0002850018
+lmD: 0.003568686 +/- 0.0002801799
 
-lmY: 0.00298475 +/- 0.0002850079
+lmY: 0.003568727 +/- 0.0002801853
 
-Arima: 0.003 4e-04 7.7371 0
+Arima: 0.0036 4e-04 9.731 0
 
@@
 
-lmD: 0.001565283 +/- 0.0003220401
+lmD: 0.001823537 +/- 0.0003202326
 
-lmY: 0.001565348 +/- 0.000322047
+lmY: 0.00182361 +/- 0.0003202387
 
-Arima: 0.0018 5e-04 3.3956 7e-04
+Arima: 0.002 5e-04 3.8775 1e-04
 
-lmD: -0.1672102 +/- 0.1436958
+lmD: 0.2020422 +/- 0.1403033
 
-lmY: -0.1672003 +/- 0.1436989
+lmY: 0.2020754 +/- 0.140306
 
@@
 
-lmD: 0.9735636 +/- 0.1446246
+lmD: 0.9626897 +/- 0.1495875
 
-lmY: 0.9735884 +/- 0.1446277
+lmY: 0.9627106 +/- 0.1495904
 
-Arima: 1.0386 0.2143 4.8455 0
+Arima: 1.0336 0.2275 4.5431 0
 
@@
 
-lmD: 0.7131394 +/- 0.1236589
+lmD: 0.8351144 +/- 0.09713712
 
-lmY: 0.7131522 +/- 0.1236614
+lmY: 0.8351303 +/- 0.09713899
 
-Arima: 0.7132 0.1476 4.8325 0
+Arima: 0.8351 0.1135 7.3608 0
 
@@
 
-lmD: 0.1205603 +/- 0.04472432
+lmD: 0.163156 +/- 0.03446857
 
-lmY: 0.1205635 +/- 0.04472525
+lmY: 0.1631591 +/- 0.03446923
 
-Arima: 0.1206 0.0487 2.4752 0.0133
+Arima: 0.1632 0.0372 4.3911 0
 
@@
 
-lmD: 0.5126011 +/- 0.05584138
+lmD: 0.5453637 +/- 0.04850372
 
-lmY: 0.5126089 +/- 0.05584254
+lmY: 0.5453737 +/- 0.04850466
 
-Arima: 0.5126 0.0703 7.2901 0
+Arima: 0.5454 0.0575 9.4902 0
 
@@
 
-lmD: 28.03241 +/- 3.452126
+lmD: 26.14448 +/- 2.49671
 
-lmY: 28.0328 +/- 3.452198
+lmY: 26.145 +/- 2.496759
 
-Arima: 28.0362 4.3653 6.4225 0
+Arima: 26.1448 3.0029 8.7066 0
 
@@
 
-lmD: 0.001091243 +/- 0.0001452364
+lmD: 0.001478147 +/- 0.0001452906
 
-lmY: 0.001091258 +/- 0.0001452394
+lmY: 0.001478168 +/- 0.0001452934
 
-Arima: 0.0011 2e-04 6.6404 0
+Arima: 0.0015 2e-04 8.804 0
 
@@
 
-lmD: 0.0002586606 +/- 6.142941e-05
+lmD: 0.0003397602 +/- 6.739233e-05
 
-lmY: 0.0002586644 +/- 6.143069e-05
+lmY: 0.0003397619 +/- 6.739364e-05
 
-Arima: 3e-04 1e-04 3.7461 2e-04
+Arima: 3e-04 1e-04 4.6072 0
 
@@
 
-lmD: 0.03561979 +/- 0.004001997
+lmD: 0.04427476 +/- 0.004265004
 
-lmY: 0.03562032 +/- 0.004002081
+lmY: 0.04427565 +/- 0.004265086
 
-Arima: 0.0356 0.0048 7.3697 0
+Arima: 0.0443 0.0049 9.0734 0
 
@@
 
-lmD: -0.1184401 +/- 0.3426654
+lmD: 0.239157 +/- 0.23526
 
-lmY: -0.1183983 +/- 0.3426728
+lmY: 0.239194 +/- 0.235264
 
-Arima: -0.1021 0.5303 -0.1925 0.8473
+Arima: 0.2304 0.3281 0.7023 0.4825
 
@@
 
-lmD: -0.2498159 +/- 0.2873017
+lmD: 0.1370797 +/- 0.1721383
 
-lmY: -0.2497925 +/- 0.287308
+lmY: 0.1371014 +/- 0.1721412
 
-Arima: -0.249 0.4778 -0.5212 0.6022
+Arima: 0.1135 0.2908 0.3902 0.6964
 
@@
 
-lmD: 0.02397815 +/- 0.02221734
+lmD: 0.02925782 +/- 0.02144818
 
-lmY: 0.02397998 +/- 0.02221782
+lmY: 0.02925974 +/- 0.02144855
 
-Arima: 0.024 0.0229 1.0454 0.2959
+Arima: 0.0293 0.0223 1.3139 0.1889
 
@@
 
-lmD: 4.678815 +/- 4.938622
+lmD: 6.254578 +/- 4.293245
 
-lmY: 4.679265 +/- 4.938728
+lmY: 6.255019 +/- 4.293318
 
-Arima: 4.6804 5.0982 0.9181 0.3586
+Arima: 6.2546 4.3752 1.4296 0.1528
 
@@
 
-lmD: 0.0002750923 +/- 0.0002421161
+lmD: 0.0006000764 +/- 0.0003458892
 
-lmY: 0.0002751196 +/- 0.0002421213
+lmY: 0.0006000719 +/- 0.0003458953
 
-Arima: 3e-04 3e-04 1.0722 0.2836
+Arima: 6e-04 4e-04 1.5164 0.1294
 
@@
 
-lmD: 0.0001464247 +/- 0.0001495252
+lmD: 0.0004422727 +/- 0.0002935454
 
-lmY: 0.0001464348 +/- 0.0001495284
+lmY: 0.0004422599 +/- 0.0002935506
 
-Arima: 1e-04 2e-04 0.8844 0.3765
+Arima: 4e-04 4e-04 1.2377 0.2158
 
@@
 
-lmD: 0.007036274 +/- 0.006116865
+lmD: 0.008932077 +/- 0.005813607
 
-lmY: 0.007036819 +/- 0.006116997
+lmY: 0.008932528 +/- 0.005813706
 
-Arima: 0.007 0.0063 1.1208 0.2624
+Arima: 0.0089 0.0061 1.4624 0.1436
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-8} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-9} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-10} \end{center}
+
+\begin{verbatim}
+ Group0 wattGLB.mean wattGLB.SD wattGLB.max wattGLB.min wattGLB.median
+  <int>        <num>      <num>       <num>       <num>          <num>
+\end{verbatim}
+
+1: 13 225.5281 12.544463 242.3534 203.6571 227.4027
+2: 315 183.2380 14.021218 205.7494 161.2362 183.4280
+3: 393 211.4853 26.002452 254.6444 169.0380 210.8473
+4: 501 259.8284 9.591647 272.2979 242.1095 260.8614
+5: 591 227.3434 9.025312 240.3322 214.5732 225.0337
+---\\
+253: 65381 186.9246 8.529287 197.1196 173.4441 187.0577
+254: 65423 194.8850 10.569185 207.5506 179.9910 196.8111
+255: 65519 181.8946 11.823089 200.5545 165.3543 182.3613
+256: 65529 178.3845 4.546207 186.4354 173.1996 176.4594
+257: 65533 217.2415 16.147690 236.0007 182.0452 222.7584
+wattGLB.sum wattGLB.N GLB\_ench.mean GLB\_ench.SD GLB\_ench.max GLB\_ench.min
+1: 2706.337 12 0.01659718 0.007597084 0.02543323 0.0041557214
+2: 2931.808 16 0.01163209 0.008450614 0.02498250 0.0005249866
+3: 6133.073 29 0.03494054 0.021369070 0.07259215 0.0044677582
+4: 2598.284 10 0.01406600 0.008869984 0.02725920 0.0007449344
+5: 3410.151 15 0.03288980 0.018031095 0.06712790 0.0011333915
+---\\
+253: 1682.321 9 0.03425477 0.010915540 0.05378668 0.0118438957
+254: 2143.735 11 0.03947032 0.018939813 0.07284705 0.0123456804
+255: 2364.630 13 0.01785069 0.010225149 0.04054656 0.0055296019
+256: 1605.460 9 0.04394266 0.035577012 0.11668555 0.0112579853
+257: 3693.105 17 0.04877689 0.033134593 0.09685661 0.0045080034
+GLB\_ench.median GLB\_ench.sum GLB\_ench.N GLB\_diff.mean GLB\_diff.SD
+1: 0.01721937 0.1991661 12 3.660370 1.651727
+2: 0.01278289 0.1861135 16 1.988442 1.350952
+3: 0.03071007 1.0132755 29 6.568530 3.245441
+4: 0.01192006 0.1406600 10 3.555058 2.194372
+5: 0.02545803 0.4933469 15 7.052047 3.532240
+---\\
+253: 0.03470823 0.3082929 9 6.159514 1.935746
+254: 0.04550629 0.4341735 11 7.343593 3.465457
+255: 0.01677883 0.2320589 13 3.108486 1.622229
+256: 0.03000519 0.3954839 9 7.259927 5.518687
+257: 0.04859240 0.8292071 17 9.892759 6.595347
+GLB\_diff.max GLB\_diff.min GLB\_diff.median GLB\_diff.sum GLB\_diff.N SZA.mean
+1: 5.649198 1.0029849 3.774258 43.92444 12 75.40653
+2: 3.940819 0.1079590 2.312200 31.81508 16 76.61730
+3: 11.440352 1.1326292 6.282210 190.48737 29 75.33588
+4: 6.842022 0.2026931 3.093025 35.55058 10 74.03057
+5: 13.497769 0.2712624 5.748451 105.78070 15 77.05677
+---\\
+253: 9.547676 2.2941778 6.272625 55.43563 9 77.12742
+254: 13.894581 2.1950124 8.002303 80.77952 11 76.73931
+255: 6.456701 1.0612959 2.882533 40.41032 13 76.78463
+256: 18.438732 2.0755204 5.133219 65.33934 9 77.17689
+257: 19.080014 1.0591174 10.403814 168.17691 17 75.18167
+SZA.SD SZA.max SZA.min SZA.median SZA.sum SZA.N Date
+1: 0.6667310 76.42244 74.38838 75.40725 904.8784 12 1993-05-13 04:33:30
+2: 0.8567238 77.96388 75.26476 76.61909 1225.8768 16 1993-07-13 04:22:30
+3: 1.5939261 77.95091 72.71007 75.33887 2184.7406 29 1993-08-12 04:45:30
+4: 0.5362886 74.82883 73.23468 74.02978 740.3057 10 1993-10-04 14:30:30
+5: 0.5907621 77.98809 76.13886 77.05264 1155.8515 15 1993-12-06 07:01:30
+---\\
+253: 0.4856759 77.83591 76.41717 77.12805 694.1468 9 2023-06-18 16:37:30
+254: 0.5905545 77.62822 75.84766 76.74023 844.1324 11 2023-06-30 04:17:30
+255: 0.7131983 77.88183 75.68429 76.78564 998.2002 13 2023-07-28 04:33:30
+256: 0.5066369 77.91629 76.43632 77.17730 694.5920 9 2023-08-06 04:40:30
+257: 0.9419447 76.67187 73.68745 75.18288 1278.0885 17 2023-08-06 16:04:30
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-11} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-12} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-13} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-14} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-15} \end{center}
+
+Group0 wattGLB.mean wattGLB.SD wattGLB.max wattGLB.min wattGLB.median
+1: 16423 249.6246 39.53847 315.8996 185.1393 248.8458
+wattGLB.sum wattGLB.N GLB\_ench.mean GLB\_ench.SD GLB\_ench.max GLB\_ench.min
+1: 10484.23 42 0.03013706 0.02002665 0.07315483 0.000646732
+GLB\_ench.median GLB\_ench.sum GLB\_ench.N GLB\_diff.mean GLB\_diff.SD
+1: 0.02576315 1.265756 42 6.504293 3.430543
+GLB\_diff.max GLB\_diff.min GLB\_diff.median GLB\_diff.sum GLB\_diff.N SZA.mean
+1: 12.62058 0.2041703 6.416318 273.1803 42 74.25137
+SZA.SD SZA.max SZA.min SZA.median SZA.sum SZA.N Date
+1: 2.245081 77.98308 70.48178 74.26151 3118.558 42 2004-05-25 04:16:30
+Group0 wattGLB.mean wattGLB.SD wattGLB.max wattGLB.min wattGLB.median
+1: 15087 228.4206 30.98628 279.3502 177.6686 229.0747
+wattGLB.sum wattGLB.N GLB\_ench.mean GLB\_ench.SD GLB\_ench.max GLB\_ench.min
+1: 7081.037 31 0.01717012 0.01012086 0.03564823 0.0002394964
+GLB\_ench.median GLB\_ench.sum GLB\_ench.N GLB\_diff.mean GLB\_diff.SD
+1: 0.01952886 0.5322736 31 3.550457 1.75638
+GLB\_diff.max GLB\_diff.min GLB\_diff.median GLB\_diff.sum GLB\_diff.N SZA.mean
+1: 6.235319 0.065965 4.201192 110.0642 31 75.0963
+SZA.SD SZA.max SZA.min SZA.median SZA.sum SZA.N Date
+1: 1.712864 77.9228 72.27203 75.09567 2327.985 31 2003-09-05 05:06:30
+{[}1{]} 3.550457
+
 \textbf{END}
@@
 \begin{verbatim}
-2024-01-22 08:48:56.1 athan@sagan GHI_enh_04_investigate.R 0.252639 mins
+2024-02-19 11:13:55.4 athan@tyler GHI_enh_04_investigate.R 0.693826 mins
 \end{verbatim}

### 2024-02-19 GHI_enh_02_ID_CE.R
Commit 2024-02-19 16:14

@@ -114,7 +114,7 @@ if (
 
 ## __ Execution control  -------------------------------------------------------
 TEST <- FALSE
-# TEST <- TRUE
+TEST <- TRUE
 
 if (TEST) {
     warning("\n\n ** Test is active!! ** \n\n")

### 2024-02-20 GHI_enh_02_ID_CE.R
Commit 2024-02-20 17:13

@@ -266,25 +266,24 @@ csmodel <- "Low_B.Low_W"
 #' ## 4. Use libradtran **`r csmodel`** as reference for Clear sky.
 #'
 #+ echo=TRUE, include=TRUE
-
-
 cat("\n USING CSMODE:", csmodel, "\n\n")
-
 
 switch(csmodel,
        Exact_B.Exact_W = { C4_cs_ref_ratio <- 1.02; C4_GLB_diff_THRES <- 55; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
        Low_2_B.Low_2_W = { C4_cs_ref_ratio <- 1.03; C4_GLB_diff_THRES <-  5; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
        Low_B.Exact_W   = { C4_cs_ref_ratio <- 1.04; C4_GLB_diff_THRES <- 20; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
        Low_B.High_W    = { C4_cs_ref_ratio <- 1.05; C4_GLB_diff_THRES <- 20; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
-       Low_B.Low_W     = { C4_cs_ref_ratio <- 1.05; C4_GLB_diff_THRES <-  0; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.15},
+       Low_B.Low_W     = { C4_cs_ref_ratio <- 1.05; C4_GLB_diff_THRES <-  0; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.10},
                          { C4_cs_ref_ratio <- 1   ; C4_GLB_diff_THRES <-  0; C4_lowcut_sza <-  0; C4_lowcut_ratio <- 1   })
-
+## init flag
 DATA[, Enhanc_C_4 := FALSE]
 
-DATA[, max(SZA)]
+# DATA[, max(SZA)]
 
-smo <- approxfun(x = c(DATA[, max(SZA)], C4_lowcut_sza),
-                 y = c(C4_lowcut_ratio, C4_cs_ref_ratio))
+smo <- approxfun(
+    x = c(DATA[, max(SZA)], C4_lowcut_sza  ),
+    y = c(C4_lowcut_ratio,  C4_cs_ref_ratio)
+    )
 
 smo(80:70) * (1/cosd(80:70) / max(1/cosd(80:70)))
 
[…]

### 2024-02-22 article/article.qmd
Commit 2023-11-28 16:14
Commit 2023-11-28 17:11
Commit 2024-02-22 11:14

--- 2023-11-28 article/article.qmd
@@
 
-  - name:  Athanasios Natsis
+  - name:  Athanasios N. Natsis
     email: natsisphysicist@gmail.com
@@
 
+```{r setup, echo=F, include=T, warning=FALSE, message=FALSE}
+suppressMessages(
+    res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
+)
+## document configurations
+knitr::opts_chunk$set(comment    = ""      )
+# knitr::opts_chunk$set(dev        = "pdf"   )
+knitr::opts_chunk$set(out.width  = "70%"   )
+knitr::opts_chunk$set(fig.align  = "center")
+knitr::opts_chunk$set(fig.pos    = 'h!'    )
+options(knitr.graphics.auto_pdf = FALSE)
+library(pander)
+library(data.table)
+library(kableExtra)
+library(dplyr)
+## load data from trends analysis
+source("~/MANUSCRIPTS/02_enhancement/GHI_enh_00_variables.R")
+TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/02_enhancement/figures/tbl_tsi_info.dat",
+                    strip.white = TRUE,
+                    sep = ";",
+                    header = TRUE))
+# ## create local citations file and links here
+# source("~/CODE/FUNCTIONS/R/gather_citations.R")
+# suppressMessages(
+#     gather_citations(
+#         sourcefile   = "./Article.Rmd",
+#         mainreposit  = "./Mainreferences.bib",
+#         localreposit = "./references.bib",
+#         folderlink   = "./References_links",
+#         workingdir   = "./"
+#     )
+# )
+```
+
+CE: cloud enhancement cases one minute
+
+CEG: continuous group of cloud enhancement cases
+
 # Intro
@@
 
-Data with quality control
+The recording of the signal is the one minute average.
+Thus we will refer to this time scale as a cloud enhancement event (CE).
+Due to the instruments response time.
 
-### Data selection
+## Data quality control
+
+## Data selection
 
@@
 Days with less than 5 valid hours are rejected completely.
-
 <!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7), otherwise all data for this day is flagged as invalid.
 There must be at least This work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid, otherwise all minute data for this hour is flagged as invalid.
--->
+--> Furthermore, due to a systematic obstruction of the horizon and the significant measurement uncertainty on large SZAs, we excluded all data with $SZA > `r 90 - BIO_ELEVA`^\circ$.
 
--   CastillejoCuberos2020
--   valid data 45min /h and 5h / day
--   SZA above biology
+## Clear sky identification
 
-Clear sky identification
+Use it to find some interesting days to manual check the CE thresholds. No other usage of clear/cloud characterization in CE.
 
--   helps on determining thresholds
+## Criteria for enhancement based on TSI
 
-Criteria for enhancement based on TSI
+Many have used models or some statistical method to determine then CE thresholds.
+
+....... cite ...... Descriptions
+
+We used as reference the .... extraterrestrial horizontal irradiance .....
+
+$$
+\text{ETH} = \cos(\theta) \times \text{TSI}_\text{TOA}
+$$
+
+$$
+\text{GHI} > 999 \text{ETH}
+$$
+
+$$
+f(x)=\begin{cases}
+1, & \text{if $x<0$}.\\
+0, & \text{otherwise}.
+\end{cases}
+$$
 

### 2024-02-22 article/article.tex
Commit 2024-02-22 11:14

--- 2023-11-28 article/article.tex
@@
   pdftitle={SDR enhancement by clouds},
-  pdfauthor={Athanasios Natsis; Alkiviadis Bais; Charikleia Meleti},
+  pdfauthor={Athanasios N. Natsis; Alkiviadis Bais; Charikleia Meleti},
   pdfkeywords={keyword1, keyword2},
@@
 \title{SDR enhancement by clouds \\\large{A Short Subtitle} }
-\author[1]{Athanasios Natsis%
+\author[1]{Athanasios N. Natsis%
 \corref{cor1}%
@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, breakable, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi
+
+CE: cloud enhancement cases one minute
+
+CEG: continuous group of cloud enhancement cases
 
@@
 \section{Data and methodology}\label{data-and-methodology}}
+
+The recording of the signal is the one minute average. Thus we will
+refer to this time scale as a cloud enhancement event (CE). Due to the
+instruments response time.
 
@@
 
-Clear sky identification
+\hypertarget{clear-sky-identification}{%
+\subsection{Clear sky identification}\label{clear-sky-identification}}
 
-\begin{itemize}
-\tightlist
-\item
-  helps on determining thresholds
-\end{itemize}
+Use it to find some interesting days to manual check the CE thresholds.
+No other usage of clear/cloud characterization in CE.
 
-Criteria for enhancement based on TSI
+\hypertarget{criteria-for-enhancement-based-on-tsi}{%
+\subsection{Criteria for enhancement based on
+TSI}\label{criteria-for-enhancement-based-on-tsi}}
+
+Many have used models or some statistical method to determine then CE
+thresholds.
+
+\ldots\ldots. cite \ldots\ldots{} Descriptions
+
+We used as reference the \ldots. extraterrestrial horizontal irradiance
+\ldots..
+
+\[
+\text{ETH} = \cos(\theta) \times \text{TSI}_\text{TOA}
+\]
+
+\[
+\text{GHI} > 999 \text{ETH}
+\]
+
+\[
+f(x)=\begin{cases}
+1, & \text{if $x<0$}.\\
+0, & \text{otherwise}.
+\end{cases}
+\]
 
@@
 
-\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, left=2mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, leftrule=.75mm, toprule=.15mm, coltitle=black, titlerule=0mm, arc=.35mm, opacitybacktitle=0.6, bottomtitle=1mm, breakable, colframe=quarto-callout-important-color-frame, opacityback=0, bottomrule=.15mm, colbacktitle=quarto-callout-important-color!10!white, colback=white, toptitle=1mm]
+\begin{tcolorbox}[enhanced jigsaw, bottomrule=.15mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, bottomtitle=1mm, colback=white, rightrule=.15mm, breakable, toptitle=1mm, toprule=.15mm, colframe=quarto-callout-important-color-frame, opacityback=0, leftrule=.75mm, opacitybacktitle=0.6, coltitle=black, left=2mm, titlerule=0mm, arc=.35mm, colbacktitle=quarto-callout-important-color!10!white]
 
@@
 \hypertarget{tbl-simple}{}
-\begin{table}
-\caption{\label{tbl-simple}Caption centered above table }\tabularnewline
-
-\centering
-\begin{tabular}{l|r|r|r|r}
-\hline
-  & mpg & cyl & disp & hp\\
-\hline
-Mazda RX4 & 21.0 & 6 & 160 & 110\\
-\hline
-Mazda RX4 Wag & 21.0 & 6 & 160 & 110\\
-\hline
-Datsun 710 & 22.8 & 4 & 108 & 93\\
-\hline
-Hornet 4 Drive & 21.4 & 6 & 258 & 110\\
-\hline
-Hornet Sportabout & 18.7 & 8 & 360 & 175\\
-\hline
-Valiant & 18.1 & 6 & 225 & 105\\
-\hline
-\end{tabular}
-\end{table}
+\begin{longtable}[]{@{}lrrrr@{}}
+\caption{\label{tbl-simple}Caption centered above table}\tabularnewline
+\toprule\noalign{}
+& mpg & cyl & disp & hp \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+& mpg & cyl & disp & hp \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Mazda RX4 & 21.0 & 6 & 160 & 110 \\
+Mazda RX4 Wag & 21.0 & 6 & 160 & 110 \\
+Datsun 710 & 22.8 & 4 & 108 & 93 \\
+Hornet 4 Drive & 21.4 & 6 & 258 & 110 \\
+Hornet Sportabout & 18.7 & 8 & 360 & 175 \\
+Valiant & 18.1 & 6 & 225 & 105 \\
+\end{longtable}
 

### 2024-02-22 article/article.qmd
Commit 2024-02-22 12:14

@@
 source("~/MANUSCRIPTS/02_enhancement/GHI_enh_00_variables.R")
+load("~/MANUSCRIPTS/02_enhancement/data/GHI_enh_03_process.Rda")
 TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/02_enhancement/figures/tbl_tsi_info.dat",
@@
 $$
-f(x)=\begin{cases}
-1, & \text{if $x<0$}.\\
-0, & \text{otherwise}.
+\text{CE}_\text{Threshold} = \begin{cases}
+`r C4_cs_ref_ratio`, & \text{if $\theta \leq `r C4_lowcut_sza`^\circ$}.\\
+\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{if $ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}.
 \end{cases}
-$$
+$${#eq-test}
 

### 2024-02-22 article/article.tex
Commit 2024-02-22 12:14

@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, breakable, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, frame hidden, boxrule=0pt, breakable, borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced]}{\end{tcolorbox}}\fi
 
@@
 
-\[
-f(x)=\begin{cases}
-1, & \text{if $x<0$}.\\
-0, & \text{otherwise}.
+\begin{equation}\protect\hypertarget{eq-test}{}{
+\text{CE: GHI} > \begin{cases}
+1.05, & \text{if $\theta \leq 60^\circ$}.\\
+1.18, & \text{if $ 80^\circ > \theta > 60^\circ$}.
 \end{cases}
-\]
+}\label{eq-test}\end{equation}
 
@@
 
-\begin{tcolorbox}[enhanced jigsaw, bottomrule=.15mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, bottomtitle=1mm, colback=white, rightrule=.15mm, breakable, toptitle=1mm, toprule=.15mm, colframe=quarto-callout-important-color-frame, opacityback=0, leftrule=.75mm, opacitybacktitle=0.6, coltitle=black, left=2mm, titlerule=0mm, arc=.35mm, colbacktitle=quarto-callout-important-color!10!white]
+\begin{tcolorbox}[enhanced jigsaw, opacityback=0, leftrule=.75mm, coltitle=black, breakable, bottomrule=.15mm, colbacktitle=quarto-callout-important-color!10!white, colframe=quarto-callout-important-color-frame, left=2mm, titlerule=0mm, bottomtitle=1mm, colback=white, arc=.35mm, toptitle=1mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, rightrule=.15mm, toprule=.15mm, opacitybacktitle=0.6]
 

### 2024-02-22 GHI_enh_03_process.tex
Commit 2024-02-22 14:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-02-19}
+\date{2024-02-22}
 
@@
     Min      1Q  Median      3Q     Max 
--448.24 -172.37  -59.22  113.90  892.70
+-382.05 -149.78  -46.64   98.42  770.22
 
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      -1.126e+02  5.761e+01  -1.955   0.0514 .  
-as.numeric(Date)  4.155e-07  4.624e-08   8.985   <2e-16 ***
+(Intercept)      -1.067e+02  5.109e+01  -2.088   0.0375 *  
+as.numeric(Date)  3.393e-07  4.098e-08   8.279  2.5e-15 ***
 ---
@@
 
-Residual standard error: 244.7 on 359 degrees of freedom
-Multiple R-squared:  0.1836,    Adjusted R-squared:  0.1813 
-F-statistic: 80.72 on 1 and 359 DF,  p-value: < 2.2e-16
+Residual standard error: 216.2 on 358 degrees of freedom
+Multiple R-squared:  0.1607,    Adjusted R-squared:  0.1583 
+F-statistic: 68.54 on 1 and 358 DF,  p-value: 2.498e-15
 \end{verbatim}
@@
                     Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       -1.126e+02  5.761e+01  -1.955   0.0514 .  
-ST_E_monthly$Date  4.155e-07  4.624e-08   8.985   <2e-16 ***
+(Intercept)       -1.067e+02  5.109e+01  -2.088   0.0375 *  
+ST_E_monthly$Date  3.393e-07  4.098e-08   8.279  2.5e-15 ***
 ---
@@
 
+\FunctionTok{cat}\NormalTok{(objects, }\AttributeTok{sep =} \StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+aa
+aday
+All_daily_ratio_lim
+alpha
+ampl
+avar
+BIO_ELEVA
+C1_Clearness_Kt_THRES
+C1_GLB_diff_THRES
+C2_Clearness_Kt_THRES
+C3_cs_ref_ratio
+C4_cs_ref_ratio
+C4_GLB_diff_THRES
+C4_lowcut_ratio
+C4_lowcut_sza
+Clear_daily_ratio_lim
+CLEARdir
+Cloud_daily_ratio_lim
+cols
+common_data_13
+common_data_14
+common_data_14_2
+CS_file_13
+CS_file_14
+CS_file_14_2
+csmodel
+Daily_aggregation_N_lim
+Daily_confidence_limit
+daylist
+Days_of_year
+I1_longterm
+I2_szatrend
+I3_trendsconsist
+ii
+Input_data_ID
+Kurudz_SC
+MIN_ELEVA
+MIN_N
+Monthly_aggegation_N_lim
+Monthly_confidence_limit
+my.cols
+my.cols.gr
+pyear
+R_COMPILE_PKGS
+raw_input_data
+running_mean_window_days
+running_mean_window_years
+SEAS_MIN_N
+SelEnhanc
+SZA_aggregation_N_lim
+SZA_BIN
+SZA_confidence_limit
+variables_fl
+yearstodo
+ylim
+ST_daily
+ST_E_daily
+ST_E_daily_seas
+ST_E_monthly
+ST_E_monthly_seas
+ST_E_sza
+ST_E_yearly
+ST_extreme_daily
+ST_extreme_monthly
+ST_extreme_SZA
+ST_extreme_yearly
+ST_G0
+ST_G1
+ST_monthly
+ST_sza
+ST_total
+ST_yearly
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
 \FunctionTok{save}\NormalTok{(}\AttributeTok{file =} \FunctionTok{paste0}\NormalTok{(}\StringTok{"./data/"}\NormalTok{, }\FunctionTok{basename}\NormalTok{(}\FunctionTok{sub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{.R"}\NormalTok{, }\StringTok{".Rda"}\NormalTok{, Script.Name))),}
@@
 \begin{verbatim}
-2024-02-19 10:09:06.3 athan@tyler GHI_enh_03_process.R 2.125423 mins
+2024-02-22 12:05:59.3 athan@tyler GHI_enh_03_process.R 2.189978 mins
 \end{verbatim}

### 2024-02-22 GHI_enh_04_investigate.tex
Commit 2024-02-22 12:14
Commit 2024-02-22 14:14

--- 2024-01-22 GHI_enh_04_investigate.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-01-22}
+\date{2024-02-22}
 
@@
 
-lmD: 1.71458 +/- 0.1322584
+lmD: 1.608404 +/- 0.1098661
 
-lmY: 1.714601 +/- 0.1322612
+lmY: 1.608426 +/- 0.1098682
 
-Arima: 1.7152 0.1817 9.4404 0
+Arima: 1.6087 0.1487 10.8185 0
 
@@
 
-lmD: 1.015311 +/- 0.173386
+lmD: 1.06616 +/- 0.1703576
 
-lmY: 1.015342 +/- 0.1733898
+lmY: 1.066188 +/- 0.1703608
 
-Arima: 1.1004 0.255 4.3146 0
+Arima: 1.1439 0.255 4.4864 0
 
-lmD: -0.1672102 +/- 0.1436958
+lmD: 0.2020422 +/- 0.1403033
 
-lmY: -0.1672003 +/- 0.1436989
+lmY: 0.2020754 +/- 0.140306
 
@@
 
-lmD: 605.1187 +/- 96.27827
+lmD: 499.5958 +/- 96.35149
 
-lmY: 605.1308 +/- 96.28033
+lmY: 499.601 +/- 96.35332
 
-Arima: 605.7835 145.2351 4.1711 0
+Arima: 500.7839 150.1232 3.3358 9e-04
 
@@
 
-lmD: 0.002984713 +/- 0.0002850018
+lmD: 0.003319458 +/- 0.0002745369
 
-lmY: 0.00298475 +/- 0.0002850079
+lmY: 0.003319501 +/- 0.0002745421
 
-Arima: 0.003 4e-04 7.7371 0
+Arima: 0.0033 4e-04 9.0564 0
 
@@
 
-lmD: 0.001565283 +/- 0.0003220401
+lmD: 0.001746196 +/- 0.0003178251
 
-lmY: 0.001565348 +/- 0.000322047
+lmY: 0.001746269 +/- 0.0003178311
 
-Arima: 0.0018 5e-04 3.3956 7e-04
+Arima: 0.0019 5e-04 3.7071 2e-04
 
-lmD: -0.1672102 +/- 0.1436958
+lmD: 0.2020422 +/- 0.1403033
 
-lmY: -0.1672003 +/- 0.1436989
+lmY: 0.2020754 +/- 0.140306
 
@@
 
-lmD: 0.9735636 +/- 0.1446246
+lmD: 0.9305909 +/- 0.1460762
 
-lmY: 0.9735884 +/- 0.1446277
+lmY: 0.9306112 +/- 0.146079
 
-Arima: 1.0386 0.2143 4.8455 0
+Arima: 1.0003 0.2219 4.5077 0
 
@@
 
-lmD: 0.7131394 +/- 0.1236589
+lmD: 0.8634408 +/- 0.1045511
 
-lmY: 0.7131522 +/- 0.1236614
+lmY: 0.8634567 +/- 0.1045531
 
-Arima: 0.7132 0.1476 4.8325 0
+Arima: 0.8634 0.1212 7.1257 0
 
@@
 
-lmD: 0.1205603 +/- 0.04472432
+lmD: 0.1926088 +/- 0.038164
 
-lmY: 0.1205635 +/- 0.04472525
+lmY: 0.1926139 +/- 0.03816473
 
-Arima: 0.1206 0.0487 2.4752 0.0133
+Arima: 0.1926 0.0403 4.7782 0
 
@@
 
-lmD: 0.5126011 +/- 0.05584138
+lmD: 0.5100905 +/- 0.04695669
 
-lmY: 0.5126089 +/- 0.05584254
+lmY: 0.5100995 +/- 0.04695759
 
-Arima: 0.5126 0.0703 7.2901 0
+Arima: 0.5101 0.0557 9.1553 0
 
@@
 
-lmD: 28.03241 +/- 3.452126
+lmD: 25.65919 +/- 2.576134
 
-lmY: 28.0328 +/- 3.452198
+lmY: 25.65971 +/- 2.576183
 
-Arima: 28.0362 4.3653 6.4225 0
+Arima: 25.6594 3.1045 8.2652 0
 
@@
 
-lmD: 0.001091243 +/- 0.0001452364
+lmD: 0.001358275 +/- 0.0001381135
 
-lmY: 0.001091258 +/- 0.0001452394
+lmY: 0.001358294 +/- 0.0001381161
 
-Arima: 0.0011 2e-04 6.6404 0
+Arima: 0.0014 2e-04 8.5635 0
 
@@
 
-lmD: 0.0002586606 +/- 6.142941e-05
+lmD: 0.0003544276 +/- 6.15321e-05
 
-lmY: 0.0002586644 +/- 6.143069e-05
+lmY: 0.0003544331 +/- 6.153328e-05
 
-Arima: 3e-04 1e-04 3.7461 2e-04
+Arima: 4e-04 1e-04 5.1881 0
 
@@
 
-lmD: 0.03561979 +/- 0.004001997
+lmD: 0.03803985 +/- 0.003667512
 
-lmY: 0.03562032 +/- 0.004002081
+lmY: 0.03804065 +/- 0.003667582
 
-Arima: 0.0356 0.0048 7.3697 0
+Arima: 0.038 0.0043 8.9476 0
 
@@
 
-lmD: -0.1184401 +/- 0.3426654
+lmD: 0.2175113 +/- 0.2519978
 
-lmY: -0.1183983 +/- 0.3426728
+lmY: 0.217552 +/- 0.2520021
 
-Arima: -0.1021 0.5303 -0.1925 0.8473
+Arima: 0.2071 0.368 0.5628 0.5736
 
@@
 
-lmD: -0.2498159 +/- 0.2873017
+lmD: 0.1126483 +/- 0.193195
 
-lmY: -0.2497925 +/- 0.287308
+lmY: 0.112674 +/- 0.1931983
 
-Arima: -0.249 0.4778 -0.5212 0.6022
+Arima: 0.0865 0.3384 0.2558 0.7981
 
@@
 
-lmD: 4.678815 +/- 4.938622
+lmD: 6.106963 +/- 4.268209
 
-lmY: 4.679265 +/- 4.938728
+lmY: 6.107414 +/- 4.268282
 
-Arima: 4.6804 5.0982 0.9181 0.3586
+Arima: 6.107 4.3537 1.4027 0.1607
 
@@
 
-lmD: 0.0002750923 +/- 0.0002421161
+lmD: 0.0004829553 +/- 0.0002839705
 
-lmY: 0.0002751196 +/- 0.0002421213
+lmY: 0.0004829612 +/- 0.0002839754
 
-Arima: 3e-04 3e-04 1.0722 0.2836
+Arima: 5e-04 3e-04 1.492 0.1357
 
@@
 
-lmD: 0.0001464247 +/- 0.0001495252
+lmD: 0.000372236 +/- 0.0002233382
 
-lmY: 0.0001464348 +/- 0.0001495284
+lmY: 0.0003722343 +/- 0.0002233421
 
-Arima: 1e-04 2e-04 0.8844 0.3765
+Arima: 4e-04 3e-04 1.3298 0.1836
 
@@
 
-lmD: 0.007036274 +/- 0.006116865
+lmD: 0.008401207 +/- 0.005558251
 
-lmY: 0.007036819 +/- 0.006116997
+lmY: 0.008401691 +/- 0.005558346
 
-Arima: 0.007 0.0063 1.1208 0.2624
+Arima: 0.0084 0.0058 1.453 0.1462
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-8} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-9} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-10} \end{center}
+
+\begin{verbatim}
+Group0 wattGLB.mean wattGLB.SD wattGLB.max wattGLB.min wattGLB.median
+ <int>        <num>      <num>       <num>       <num>          <num>
+\end{verbatim}
+
+1: 481 257.3195 8.350655 267.7489 242.6236 260.3138
+2: 971 216.5679 16.495293 235.1144 193.4734 217.7960
+3: 2241 227.5736 20.457901 258.0261 193.1068 229.0391
+4: 4773 271.5252 11.060322 283.9255 252.6598 271.0824
+5: 5117 262.1138 11.248980 274.8783 238.8148 264.6210
+6: 6541 253.6101 10.607348 267.7551 234.0414 257.8234
+7: 6845 258.8941 14.521709 279.3143 236.2212 259.3578
+8: 7467 242.4683 10.808965 255.5432 223.2814 245.7159
+9: 9457 241.5889 17.780983 262.0485 217.5930 241.8318
+10: 9969 252.6750 12.743428 268.5044 227.0751 256.7234
+11: 10165 234.4787 24.636237 272.8474 192.0395 234.9695
+12: 11649 240.6856 13.273652 256.0748 217.2753 242.5054
+13: 13153 226.7698 13.156939 245.9949 205.9152 227.1448
+14: 13443 267.3652 17.692463 297.1763 242.8280 265.7668
+15: 15895 249.5382 8.105678 260.5660 235.4649 251.6262
+16: 16137 296.0602 11.066762 309.3942 275.7864 297.5333
+17: 16171 269.2776 29.202926 309.5713 219.8781 268.9006
+18: 16895 254.6044 15.235006 274.4095 225.2859 258.0783
+19: 17643 253.1900 13.469979 268.8240 229.1515 252.6631
+20: 20345 226.6557 15.490955 243.2169 201.2967 230.7191
+21: 21735 284.9456 11.383299 294.4455 266.5703 290.7959
+22: 21817 290.7313 11.694535 302.3524 269.8491 293.7271
+23: 22165 197.8942 8.745153 210.3744 187.2505 195.5802
+24: 22413 271.7703 11.120987 287.8414 254.3186 272.3344
+25: 23611 228.9324 11.456181 244.7993 211.1329 229.0438
+26: 23891 199.6014 7.185312 210.5290 190.3904 197.4787
+27: 25719 214.0681 12.946659 234.4364 194.3404 213.3949
+28: 25997 238.5985 13.424769 258.7934 212.3301 238.1350
+29: 26285 227.0978 13.456321 248.0932 206.5112 230.1962
+30: 26801 253.3993 10.784431 269.0709 235.7569 253.5561
+31: 30515 240.4971 13.310081 260.6187 220.6540 242.2806
+32: 32341 272.3105 11.410122 283.1927 253.4763 278.5194
+33: 32401 305.1635 12.743889 323.8292 284.4144 304.5790
+34: 32773 309.3578 10.040387 321.8635 289.3885 311.7055
+35: 32961 232.4638 11.267541 245.9080 211.7075 232.6364
+36: 33451 225.2788 13.751736 241.9490 201.3797 228.0213
+37: 34245 207.9986 16.032702 234.4686 182.6589 210.3605
+38: 34523 234.0512 9.322204 246.0256 216.5182 236.1390
+39: 36351 218.4261 13.432350 235.0774 197.6608 219.5851
+40: 38177 266.8840 13.588883 287.9246 247.9963 265.6052
+41: 39591 228.1790 17.191522 247.5159 198.1167 231.1033
+42: 40373 311.4466 14.864073 326.7722 286.0813 314.2091
+43: 42061 248.7708 20.245299 276.4848 212.5114 253.7164
+44: 42973 252.3753 14.880182 271.7679 228.6148 254.1153
+45: 44053 244.8663 10.681053 254.4108 224.9672 250.5007
+46: 44557 216.6079 18.711766 246.4339 189.0774 214.8244
+47: 45027 265.2793 13.305152 278.2774 242.9361 268.8201
+48: 46959 246.3336 13.453849 262.4803 222.0861 247.0723
+49: 49635 211.1405 12.624785 227.5580 185.0832 213.3587
+50: 50495 262.2053 13.934278 277.6889 234.1425 269.4443
+51: 50605 249.1680 14.188662 267.4369 224.7586 254.9338
+52: 52523 227.7282 20.116051 253.4785 199.4729 226.2721
+53: 53139 344.2763 7.339423 354.4374 333.1648 345.1473
+54: 56531 275.6256 11.625398 293.1797 258.6227 279.5499
+Group0 wattGLB.mean wattGLB.SD wattGLB.max wattGLB.min wattGLB.median
+wattGLB.sum wattGLB.N GLB\_ench.mean GLB\_ench.SD GLB\_ench.max GLB\_ench.min
+1: 2315.875 9 0.012658526 0.007336238 0.02424117 3.618639e-03
+2: 2815.383 13 0.047619711 0.021833954 0.08294003 2.255959e-02
+3: 3868.751 17 0.039832241 0.017813047 0.06850870 9.280731e-03
+4: 2986.777 11 0.020651085 0.008641277 0.03082640 8.954612e-04
+5: 2883.252 11 0.038727945 0.016111091 0.05646997 5.673899e-03
+6: 3804.152 15 0.024133423 0.015218137 0.04713257 2.270427e-03
+7: 3106.729 12 0.024471454 0.005111052 0.03085490 1.271853e-02
+8: 2424.683 10 0.037730781 0.010797752 0.05477434 2.295391e-02
+9: 3140.655 13 0.026700651 0.017716174 0.05521067 3.520107e-03
+10: 3284.775 13 0.021796120 0.016940071 0.04437075 9.246931e-04
+11: 5627.489 24 0.010556456 0.004473778 0.01870079 1.562197e-04
+12: 2647.541 11 0.029061085 0.011690478 0.04044334 5.334540e-03
+13: 2267.698 10 0.020102389 0.009460425 0.03143787 1.302508e-03
+14: 3475.748 13 0.034180747 0.029177954 0.08087082 5.747693e-03
+15: 2245.844 9 0.031944825 0.015093392 0.05579390 1.868089e-03
+16: 2960.602 10 0.024513994 0.011193488 0.03640057 7.469758e-04
+17: 7001.218 26 0.019012780 0.010888190 0.03634797 2.224907e-04
+18: 4073.670 16 0.031447300 0.015400785 0.05138621 5.572228e-03
+19: 3291.470 13 0.018391577 0.009547554 0.03248679 4.422927e-05
+20: 2493.212 11 0.037911399 0.024767963 0.06725911 1.875988e-04
+21: 2849.456 10 0.023801910 0.015583707 0.04685870 2.065899e-03
+22: 2907.313 10 0.033181155 0.012452456 0.05072824 1.471443e-02
+23: 1781.048 9 0.041713910 0.010811978 0.06207495 2.938039e-02
+24: 2717.703 10 0.007545367 0.003968287 0.01339272 1.924395e-03
+25: 2289.324 10 0.026299708 0.005504021 0.03510600 1.631896e-02
+26: 1996.014 10 0.038398619 0.024925074 0.07789760 1.072219e-02
+27: 3211.022 15 0.024096160 0.013027169 0.04707513 3.168538e-03
+28: 2624.583 11 0.043034541 0.016692047 0.05948743 2.531670e-03
+29: 2270.978 10 0.028007669 0.015535227 0.04761875 3.593981e-04
+30: 3800.990 15 0.031491054 0.018805811 0.05927515 2.584543e-04
+31: 2404.971 10 0.038589789 0.010968345 0.05515072 1.995441e-02
+32: 2450.794 9 0.018450798 0.013828299 0.04170371 1.879353e-03
+33: 3661.962 12 0.010887983 0.004505853 0.01949511 2.646608e-03
+34: 3402.936 11 0.030439037 0.011510021 0.04467660 6.627475e-03
+35: 2557.102 11 0.028062706 0.013370819 0.05219082 1.580210e-03
+36: 2703.345 12 0.036161296 0.013891987 0.05672386 8.752650e-03
+37: 3535.976 17 0.022004659 0.010721158 0.04355565 1.232982e-03
+38: 2106.460 9 0.029267500 0.012383610 0.05493501 1.369300e-02
+39: 2402.687 11 0.019759475 0.012609945 0.03856265 1.773580e-03
+40: 2401.956 9 0.016632251 0.013926082 0.03925770 9.912776e-04
+41: 3422.686 15 0.029600589 0.014457621 0.04591226 2.056735e-03
+42: 4360.252 14 0.019192384 0.012672902 0.04222100 1.143358e-03
+43: 4726.645 19 0.022230155 0.011242035 0.04245011 5.084744e-04
+44: 2523.753 10 0.040388316 0.012871856 0.05338784 1.545235e-02
+45: 2203.796 9 0.037599517 0.024501144 0.07546839 3.286317e-03
+46: 4332.159 20 0.025563708 0.018461184 0.06292646 1.748176e-04
+47: 2918.073 11 0.029903082 0.014946483 0.05388691 1.126394e-02
+48: 2956.003 12 0.026969021 0.009248109 0.03677788 5.856216e-03
+49: 2744.826 13 0.038178239 0.020137012 0.07843259 1.235585e-02
+50: 3408.669 13 0.034775401 0.020270629 0.06542295 8.675716e-04
+51: 2491.680 10 0.040929889 0.025743183 0.07423877 3.238012e-03
+52: 3415.924 15 0.033089620 0.022677872 0.07868768 1.837827e-03
+53: 5164.145 15 0.023156220 0.011315598 0.04155787 4.477347e-03
+54: 3031.882 11 0.033064675 0.009660209 0.04996016 1.510975e-02
+wattGLB.sum wattGLB.N GLB\_ench.mean GLB\_ench.SD GLB\_ench.max GLB\_ench.min
+GLB\_ench.median GLB\_ench.sum GLB\_ench.N GLB\_diff.mean GLB\_diff.SD
+1: 0.015258046 0.11392673 9 3.199036 1.8480448
+2: 0.039096006 0.61905624 13 9.966257 4.8884446
+3: 0.043623325 0.67714809 17 8.883353 4.3646547
+4: 0.022923458 0.22716194 11 5.454028 2.2964250
+5: 0.038872608 0.42600739 11 9.720812 3.9778306
+6: 0.026109729 0.36200134 15 5.863463 3.6771214
+7: 0.026478712 0.29365744 12 6.198542 1.3979056
+8: 0.039026838 0.37730781 10 8.789569 2.4734154
+9: 0.028149166 0.34710846 13 6.393541 4.3927825
+10: 0.025010146 0.28334956 13 5.325565 4.1401913
+11: 0.011501331 0.25335495 24 2.385627 0.9033321
+12: 0.035082242 0.31967194 11 6.842998 2.8138916
+13: 0.021310344 0.20102389 10 4.546239 2.2560872
+14: 0.015261181 0.44434972 13 9.049197 7.9546905
+15: 0.028532127 0.28750343 9 7.616027 3.4449100
+16: 0.026141419 0.24513994 10 7.072265 3.2745393
+17: 0.017372697 0.49433229 26 5.177275 3.2101952
+18: 0.036315304 0.50315680 16 7.653078 3.7272740
+19: 0.021240929 0.23909050 13 4.597832 2.4288289
+20: 0.039578716 0.41702539 11 8.430668 5.5901279
+21: 0.021613611 0.23801910 10 6.622547 4.3609825
+22: 0.033304814 0.33181155 10 9.354052 3.5886059
+23: 0.037862781 0.37542519 9 7.871330 1.8081641
+24: 0.007193847 0.07545367 10 2.045319 1.0756519
+25: 0.026281327 0.26299708 10 5.901763 1.4188436
+26: 0.030018550 0.38398619 10 7.177111 4.3189650
+27: 0.021968899 0.36144240 15 4.866735 2.3725309
+28: 0.050770058 0.47337995 11 9.902114 3.8759116
+29: 0.029454867 0.28007669 10 6.263638 3.5362813
+30: 0.031495092 0.47236580 15 7.487870 4.2009478
+31: 0.039377360 0.38589789 10 8.984041 2.7993517
+32: 0.014690505 0.16605718 9 4.963055 3.7497745
+33: 0.011258487 0.13065580 12 3.282424 1.3951637
+34: 0.030019287 0.33482940 11 9.089175 3.3620941
+35: 0.028369249 0.30868976 11 6.244589 2.8426525
+36: 0.037457676 0.43393555 12 7.859623 3.0925107
+37: 0.020304850 0.37407920 17 4.373601 1.9308509
+38: 0.029622972 0.26340750 9 6.627341 2.6671677
+39: 0.024055070 0.21735423 11 4.320715 2.7985120
+40: 0.012158590 0.14969026 9 4.475643 3.8461418
+41: 0.031475748 0.44400884 15 6.595177 3.3311668
+42: 0.017107832 0.26869337 14 5.895968 3.9687884
+43: 0.021184023 0.42237294 19 5.390649 2.7084635
+44: 0.046369850 0.40388316 10 9.911890 3.4559727
+45: 0.037114103 0.33839565 9 8.854696 5.7971486
+46: 0.020396835 0.51127416 20 5.116160 3.2912175
+47: 0.034581387 0.32893390 11 7.742948 3.9356336
+48: 0.028914602 0.32362825 12 6.493560 2.2810668
+49: 0.040038173 0.49631711 13 7.640835 3.7885766
+50: 0.035518569 0.45208022 13 8.732851 5.0956093
+51: 0.037655078 0.40929889 10 9.832733 6.3377317
+52: 0.026555134 0.49634430 15 7.477650 5.3627709
+53: 0.024525322 0.34734329 15 7.689821 3.5802888
+54: 0.033550143 0.36371142 11 8.781796 2.4711802
+GLB\_ench.median GLB\_ench.sum GLB\_ench.N GLB\_diff.mean GLB\_diff.SD
+GLB\_diff.max GLB\_diff.min GLB\_diff.median GLB\_diff.sum GLB\_diff.N SZA.mean
+1: 6.160961 0.95393626 3.732131 28.79133 9 76.31201
+2: 17.875093 4.42961403 7.645469 129.56134 13 76.90457
+3: 16.393935 1.77569262 9.238884 151.01700 17 76.27771
+4: 8.419473 0.25401677 6.006594 59.99431 11 73.20135
+5: 14.008714 1.53057138 10.082840 106.92893 11 75.55524
+6: 11.550150 0.60022134 5.955268 87.95195 15 77.03026
+7: 8.093370 3.14079477 6.554798 74.38251 12 75.58466
+8: 12.701306 5.72706736 8.699920 87.89569 10 74.99706
+9: 13.415155 0.78688284 6.620988 83.11603 13 76.83387
+10: 11.034378 0.20978078 5.844482 69.23234 13 74.74039
+11: 3.712330 0.04261748 2.578156 57.25504 24 75.03040
+12: 9.744155 1.15291380 8.043454 75.27298 11 74.93893
+13: 7.391575 0.26785722 4.692944 45.46239 10 76.44427
+14: 22.234745 1.38772473 3.857838 117.63956 13 76.49536
+15: 12.860788 0.48035878 7.228265 68.54425 9 76.02615
+16: 10.584420 0.22778327 7.720153 70.72265 10 73.10869
+17: 10.565255 0.04890994 4.814865 134.60916 26 74.37201
+18: 12.601320 1.48118995 8.964507 122.44924 16 74.22174
+19: 8.391113 0.01013476 5.350149 59.77182 13 77.00104
+20: 15.035396 0.03775594 8.501772 92.73735 11 75.74552
+21: 13.123121 0.60704073 6.036769 66.22547 10 73.15433
+22: 14.535052 3.91309767 9.143830 93.54052 10 72.96694
+23: 10.944203 5.58221547 7.454849 70.84197 9 77.22327
+24: 3.683893 0.49514869 2.007895 20.45319 10 74.61690
+25: 8.247916 3.39014619 5.856710 59.01763 10 76.00182
+26: 13.759151 2.23338608 5.886701 71.77111 10 77.14195
+27: 8.737290 0.72729942 4.669355 73.00103 15 76.73547
+28: 13.201156 0.53619218 11.641778 108.92325 11 75.18558
+29: 10.690524 0.07473518 6.306326 62.63638 10 76.51308
+30: 13.192533 0.06952456 7.851910 112.31806 15 76.89333
+31: 13.084696 4.81038628 9.002430 89.84041 10 77.07601
+32: 11.150283 0.47547802 3.875148 44.66750 9 74.25991
+33: 6.192366 0.84981708 3.460090 39.38908 12 72.97619
+34: 13.124351 2.09778460 8.620152 99.98092 11 74.32935
+35: 11.203243 0.38790970 6.417657 68.69048 11 76.91713
+36: 12.228722 2.07816265 8.223374 94.31548 12 76.85870
+37: 7.995524 0.26755568 4.026333 74.35122 17 76.52836
+38: 11.923298 2.92473441 6.531802 59.64607 9 75.28093
+39: 8.517587 0.35569821 5.068282 47.52786 11 76.47527
+40: 10.876280 0.24558977 3.190591 40.28079 9 74.58380
+41: 10.502950 0.50748250 7.492738 98.92766 15 75.66150
+42: 13.107754 0.37304609 5.063451 82.54355 14 74.07967
+43: 10.331708 0.14002949 5.300350 102.42234 19 74.44621
+44: 13.662964 3.47887935 11.598532 99.11890 10 76.50848
+45: 17.810858 0.82052822 8.998589 79.69227 9 74.80061
+46: 11.193598 0.04225977 4.197251 102.32320 20 76.14464
+47: 14.066980 2.74402614 8.666315 85.17243 11 75.29915
+48: 9.266976 1.29301233 6.787583 77.92272 12 74.61536
+49: 14.575181 2.75979485 7.672405 99.33086 13 76.56101
+50: 16.345143 0.23581784 8.914622 113.52706 13 76.09532
+51: 18.482095 0.83094177 8.743070 98.32733 10 76.66623
+52: 18.490645 0.37093385 5.889783 112.16475 15 76.51321
+53: 13.293183 1.57986595 8.373120 115.34731 15 72.87559
+54: 13.332046 4.25076472 9.074488 96.59975 11 74.32984
+GLB\_diff.max GLB\_diff.min GLB\_diff.median GLB\_diff.sum GLB\_diff.N SZA.mean
+SZA.SD SZA.max SZA.min SZA.median SZA.sum SZA.N Date
+1: 0.4126326 76.91638 75.71103 76.31079 686.8081 9 1993-11-09 13:44:30
+2: 0.6959464 77.97477 75.83039 76.90583 999.7594 13 1994-06-06 04:12:30
+3: 0.9063386 77.71007 74.83847 76.27978 1296.7211 17 1995-06-04 16:22:30
+4: 0.6229631 74.13993 72.26164 73.20172 805.2148 11 1997-08-08 15:54:30
+5: 0.5673775 76.41237 74.70170 75.55404 831.1076 11 1997-10-15 05:58:30
+6: 0.5740839 77.93570 76.13869 77.02600 1155.4539 15 1998-12-26 07:16:30
+7: 0.6803507 76.62240 74.54679 75.58471 907.0160 12 1999-04-11 15:36:30
+8: 0.5720907 75.84711 74.14653 74.99722 749.9706 10 1999-08-23 15:46:30
+9: 0.7245096 77.95086 75.71848 76.83336 998.8403 13 2001-03-23 05:34:30
+10: 0.6996295 75.81644 73.66070 74.74155 971.6251 13 2001-06-19 04:24:30
+11: 1.3259361 77.18335 72.87084 75.03227 1800.7297 24 2001-08-13 04:50:30
+12: 0.6225850 75.87690 73.99976 74.93933 824.3282 11 2002-08-12 15:59:30
+13: 0.5686156 77.28956 75.59932 76.44415 764.4427 10 2003-09-11 05:15:30
+14: 0.5040005 77.27684 75.72395 76.49215 994.4397 13 2003-12-08 07:08:30
+15: 0.5157706 76.77922 75.27257 76.02634 684.2354 9 2005-04-20 15:49:30
+16: 0.5586641 73.93830 72.27763 73.10918 731.0869 10 2005-05-22 04:40:30
+17: 1.3982814 76.64999 72.07998 74.37593 1933.6722 26 2005-05-26 04:23:30
+18: 0.8703323 75.59030 72.84829 74.22321 1187.5479 16 2005-07-16 16:15:30
+19: 0.5772728 77.89445 76.11577 76.99845 1001.0135 13 2006-01-28 07:00:30
+20: 0.6006058 76.64976 74.83889 75.74631 833.2007 11 2007-07-14 16:27:30
+21: 0.5525135 73.97468 72.33230 73.15488 731.5433 10 2008-06-01 16:07:30
+22: 0.5507165 73.78460 72.14755 72.96751 729.6694 10 2008-06-08 04:35:30
+23: 0.5041615 77.95901 76.48627 77.22373 695.0095 9 2008-08-02 04:37:30
+24: 0.5335595 75.41114 73.82510 74.61609 746.1690 10 2008-10-06 14:29:30
+25: 0.5408238 76.80458 75.19694 76.00253 760.0182 10 2009-06-28 04:21:30
+26: 0.5675200 77.98491 76.29791 77.14231 771.4195 10 2009-08-16 16:06:30
+27: 0.7946317 77.97640 75.48888 76.73720 1151.0320 15 2010-06-24 04:13:30
+28: 0.5979557 76.08580 74.28292 75.18639 827.0413 11 2010-07-07 04:29:30
+29: 0.5684890 77.35819 75.66832 76.51296 765.1308 10 2010-09-11 05:15:30
+30: 0.6890233 77.97693 75.82008 76.89015 1153.4000 15 2011-02-04 06:51:30
+31: 0.5503702 77.89480 76.25879 77.07548 770.7601 10 2013-03-12 05:53:30
+32: 0.4981402 74.98817 73.53302 74.25942 668.3392 9 2013-09-26 14:46:30
+33: 0.6382201 73.95156 72.00449 72.97502 875.7143 12 2013-10-02 05:56:30
+34: 0.5115414 75.10319 73.56088 74.32757 817.6229 11 2014-02-10 14:14:30
+35: 0.6246035 77.85876 75.97554 76.91712 846.0884 11 2014-04-05 15:38:30
+36: 0.6662228 77.87379 75.84129 76.85944 922.3044 12 2014-05-08 16:08:30
+37: 0.9027478 77.95489 75.09468 76.53050 1300.9821 17 2014-07-04 16:31:30
+38: 0.5035338 76.01576 74.54485 75.28137 677.5283 9 2014-07-25 16:19:30
+39: 0.5904427 77.36402 75.58379 76.47619 841.2280 11 2015-06-26 04:17:30
+40: 0.5121475 75.33141 73.83534 74.58411 671.2542 9 2016-05-05 04:46:30
+41: 0.8456150 76.98480 74.33769 75.66166 1134.9226 15 2016-08-29 15:37:30
+42: 0.6353117 75.07161 73.09742 74.07669 1037.1154 14 2017-02-08 14:08:30
+43: 1.0604087 76.14075 72.74900 74.44699 1414.4779 19 2017-08-18 05:00:30
+44: 0.5565998 77.33637 75.68185 76.50806 765.0848 10 2018-03-18 15:17:30
+45: 0.4979635 75.52724 74.07260 74.80111 673.2055 9 2018-07-13 16:23:30
+46: 1.1128487 77.92971 74.35592 76.14570 1522.8929 20 2018-08-20 04:52:30
+47: 0.5668083 76.15546 74.44651 75.29792 828.2906 11 2018-10-15 14:17:30
+48: 0.6646320 75.62803 73.60037 74.61609 895.3843 12 2019-07-25 16:14:30
+49: 0.7312688 77.68680 75.43358 76.56153 995.2931 13 2020-08-18 04:52:30
+50: 0.6785496 77.14303 75.05228 76.09383 989.2391 13 2021-03-01 06:16:30
+51: 0.5560203 77.49328 75.84048 76.66580 766.6623 10 2021-03-17 15:17:30
+52: 0.8424561 77.83192 75.19470 76.51315 1147.6982 15 2021-09-06 05:08:30
+53: 0.5012419 73.66846 72.09949 72.87043 1093.1338 15 2021-12-30 07:51:30
+54: 0.6155061 75.25692 73.40112 74.33039 817.6283 11 2023-05-12 15:58:30
+SZA.SD SZA.max SZA.min SZA.median SZA.sum SZA.N Date
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-11} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-12} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-13} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-14} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-15} \end{center}
+
+Empty data.table (0 rows and 30 cols): Group0,wattGLB.mean,wattGLB.SD,wattGLB.max,wattGLB.min,wattGLB.median\ldots{}
+Empty data.table (0 rows and 30 cols): Group0,wattGLB.mean,wattGLB.SD,wattGLB.max,wattGLB.min,wattGLB.median\ldots{}
+numeric(0)
+
 \textbf{END}
@@
 \begin{verbatim}
-2024-01-22 08:48:56.1 athan@sagan GHI_enh_04_investigate.R 0.252639 mins
+2024-02-22 12:06:37.3 athan@tyler GHI_enh_04_investigate.R 0.439034 mins
 \end{verbatim}

### 2024-02-26 GHI_enh_04_investigate.tex
Commit 2024-02-26 12:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-02-22}
+\date{2024-02-26}
 
@@
 
-@Zhang2018
+\hypertarget{zhang2018}{%
+\subsection{@Zhang2018}\label{zhang2018}}
 
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCEmonth-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-1} \end{center}
 
@@
 \begin{verbatim}
-2024-02-22 12:06:37.3 athan@tyler GHI_enh_04_investigate.R 0.439034 mins
+2024-02-26 09:17:11.1 athan@tyler GHI_enh_04_investigate.R 0.584574 mins
 \end{verbatim}

### 2024-02-26 article/article.Rmd
Commit 2024-02-26 13:11

--- 2024-02-22 article/article.qmd
@@
 author:
-
   - name:         Athanasios N. Natsis 
     email:        natsisphysicist@gmail.com
-    affiliations: 
-        - id:          auth
-          name:        Aristotle University of Thessaloniki
-          department:  Laboratory of Atmospheric Physics
-          address:     Campus Box 149 
-          city:        Thessaloniki
-          state:       Greece
-          postal-code: 54124
-    attributes:
-        corresponding: true
-    note: This is the first author footnote.
+    affiliation:  Laboratory of Atmospheric Physics
+    footnote:     footnote one
+    correspondingauthor: true
   - name:         Alkiviadis Bais
     email:        abais@auth.gr 
-    affiliations:
-        - id: another-u
-          name: Another University
-          department: Department Name
-          address: Street Address
-          city: City
-          state: State
-          postal-code: Postal Code
-    note: |
-      Another author footnote, this is a very long footnote and it should be a really long footnote. But this footnote is not yet sufficiently long enough to make two lines of footnote text.
+    affiliation:  Laboratory of Atmospheric Physics
+    correspondingauthor: false
   - name:         Charikleia Meleti
     email:        meleti@auth.gr
-    affiliations:
-        - ref: auth
-    note: Yet another author footnote.
+    affiliation:  Laboratory of Atmospheric Physics
 abstract: |
@@
 bibliography:  [bibliography.bib]
-format:
-  elsevier-pdf:
-    keep-tex:     true
-    journal:
-      name:       Journal Name
-      formatting: preprint
-      model:      3p
-      cite-style: authoryear
-  docx: default
-  html: default
-editor_options: 
-  chunk_output_type: console
+
+output: 
+ #  rticles::mdpi_article:
+ #    extra_dependencies:  longtable
+ #    keep_tex:            yes
+  bookdown::word_document2: default
+  bookdown::pdf_document2:
+    number_sections:  no
+    fig_caption:      yes
+    keep_tex:         no
+    latex_engine:     xelatex
+    toc:              no
+    toc_depth:        4
+    fig_width:        7
+    fig_height:       4.5
+    documentclass:    article
+    classoption:      a4paper,oneside
+    fontsize:         12pt
+    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
+    link-citations:   yes
+    colorlinks:       yes
+    urlcolor:         blue
+    biblio-style:     apalike
 ---
@@
 )
+suppressMessages({
+renv::load("~/MANUSCRIPTS/02_enhancement/", quiet = TRUE)
+})
 ## document configurations
@@
 
+ \ref{eq:test}
+
 $$
@@
 
-$$
+\begin{equation}
 \text{CE}_\text{Threshold} = \begin{cases}
@@
 \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{if $ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}.
-\end{cases}
-$${#eq-test}
+\end{cases}\label{eq:test}
+\end{equation}
 
--   some other were tested
+```{r echo=FALSE, fig.cap="", out.width = '100%'}
+knitr::include_graphics("../images/climCEmonth-1.png")
+```
+
+-   some others were tested
 
@@
 
-::: callout-important
-## gcff
-
-This is nice
-:::
-
-<!--# check this out -->
-
-# Bibliography styles
-
-Here are two sample references: @Feynman1963118 @Dirac1953888.
-
-By default, natbib will be used with the `authoryear` style, set in `classoption` variable in YAML. You can sets extra options with `natbiboptions` variable in YAML header. Example
-
-```         
-natbiboptions: longnamesfirst,angle,semicolon
-```
-
-There are various more specific bibliography styles available at <https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files>.
-To use one of these, add it in the header using, for example, `biblio-style: model1-num-names`.
-
-## Using CSL
-
-If `cite-method` is set to `citeproc` in `elsevier_article()`, then pandoc is used for citations instead of `natbib`.
-In this case, the `csl` option is used to format the references.
-By default, this template will provide an appropriate style, but alternative `csl` files are available from <https://www.zotero.org/styles?q=elsevier>.
-These can be downloaded and stored locally, or the url can be used as in the example header.
-
-@eq-lowbap
+## render test
 
@@
 
-# Equations
-
-Here is an equation: $$ 
-  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
-  \left(\frac{x}{\beta}\right)^{\alpha-1}
-  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
-  \alpha,\beta,x > 0 .
-$$ {#eq-lowbap}
-
-Inline equations work as well: $\sum_{i = 2}^\infty\{\alpha_i^\beta\}$
-
-# Figures and tables
-
-@fig-meaningless is generated using an R chunk.
-
-```{r}
-#| label: fig-meaningless
-#| fig-cap: A meaningless scatterplot
-#| fig-width: 5
-#| fig-height: 5
-#| fig-align: center
-#| out-width: 50%
-#| echo: false
-plot(runif(25), runif(25))
-```
-
-# Tables coming from R
-
-Tables can also be generated using R chunks, as shown in @tbl-simple example.
-
-```{r}
-#| label: tbl-simple
-#| tbl-cap: Caption centered above table
-#| echo: true
-knitr::kable(head(mtcars)[,1:4])
-```
-
 # References {.unnumbered}

### 2024-02-26 article/article.Rmd
Commit 2024-02-26 15:09

@@
 
-```{r setup, echo=F, include=T, warning=FALSE, message=FALSE}
-suppressMessages(
-    res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
-)
-suppressMessages({
+```{r setup, echo=F, include=FALSE}
+rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
 renv::load("~/MANUSCRIPTS/02_enhancement/", quiet = TRUE)
-})
 ## document configurations

### 2024-02-27 GHI_enh_04_investigate.tex
Commit 2024-02-26 13:11
Commit 2024-02-27 13:09

--- 2024-02-19 GHI_enh_04_investigate.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-02-19}
+\date{2024-02-27}
 
@@
 
-lmD: 1.539332 +/- 0.1014749
+lmD: 1.608404 +/- 0.1098661
 
-lmY: 1.539352 +/- 0.1014768
+lmY: 1.608426 +/- 0.1098682
 
-Arima: 1.5397 0.1354 11.3752 0
+Arima: 1.6087 0.1487 10.8185 0
 
@@
 
-lmD: 1.077113 +/- 0.1694257
+lmD: 1.06616 +/- 0.1703576
 
-lmY: 1.077139 +/- 0.1694289
+lmY: 1.066188 +/- 0.1703608
 
-Arima: 1.1517 0.2512 4.5849 0
+Arima: 1.1439 0.255 4.4864 0
 
@@
 
-lmD: 499.2985 +/- 96.76248
+lmD: 499.5958 +/- 96.35149
 
-lmY: 499.3033 +/- 96.76432
+lmY: 499.601 +/- 96.35332
 
-Arima: 500.4495 151.9546 3.2934 0.001
+Arima: 500.7839 150.1232 3.3358 9e-04
 
@@
 
-lmD: 0.003568686 +/- 0.0002801799
+lmD: 0.003319458 +/- 0.0002745369
 
-lmY: 0.003568727 +/- 0.0002801853
+lmY: 0.003319501 +/- 0.0002745421
 
-Arima: 0.0036 4e-04 9.731 0
+Arima: 0.0033 4e-04 9.0564 0
 
@@
 
-lmD: 0.001823537 +/- 0.0003202326
+lmD: 0.001746196 +/- 0.0003178251
 
-lmY: 0.00182361 +/- 0.0003202387
+lmY: 0.001746269 +/- 0.0003178311
 
-Arima: 0.002 5e-04 3.8775 1e-04
+Arima: 0.0019 5e-04 3.7071 2e-04
 
@@
 
-lmD: 0.9626897 +/- 0.1495875
+lmD: 0.9305909 +/- 0.1460762
 
-lmY: 0.9627106 +/- 0.1495904
+lmY: 0.9306112 +/- 0.146079
 
-Arima: 1.0336 0.2275 4.5431 0
+Arima: 1.0003 0.2219 4.5077 0
 
@@
 
-lmD: 0.8351144 +/- 0.09713712
+lmD: 0.8634408 +/- 0.1045511
 
-lmY: 0.8351303 +/- 0.09713899
+lmY: 0.8634567 +/- 0.1045531
 
-Arima: 0.8351 0.1135 7.3608 0
+Arima: 0.8634 0.1212 7.1257 0
 
@@
 
-lmD: 0.163156 +/- 0.03446857
+lmD: 0.1926088 +/- 0.038164
 
-lmY: 0.1631591 +/- 0.03446923
+lmY: 0.1926139 +/- 0.03816473
 
-Arima: 0.1632 0.0372 4.3911 0
+Arima: 0.1926 0.0403 4.7782 0
 
@@
 
-lmD: 0.5453637 +/- 0.04850372
+lmD: 0.5100905 +/- 0.04695669
 
-lmY: 0.5453737 +/- 0.04850466
+lmY: 0.5100995 +/- 0.04695759
 
-Arima: 0.5454 0.0575 9.4902 0
+Arima: 0.5101 0.0557 9.1553 0
 
@@
 
-lmD: 26.14448 +/- 2.49671
+lmD: 25.65919 +/- 2.576134
 
-lmY: 26.145 +/- 2.496759
+lmY: 25.65971 +/- 2.576183
 
-Arima: 26.1448 3.0029 8.7066 0
+Arima: 25.6594 3.1045 8.2652 0
 
@@
 
-lmD: 0.001478147 +/- 0.0001452906
+lmD: 0.001358275 +/- 0.0001381135
 
-lmY: 0.001478168 +/- 0.0001452934
+lmY: 0.001358294 +/- 0.0001381161
 
-Arima: 0.0015 2e-04 8.804 0
+Arima: 0.0014 2e-04 8.5635 0
 
@@
 
-lmD: 0.0003397602 +/- 6.739233e-05
+lmD: 0.0003544276 +/- 6.15321e-05
 
-lmY: 0.0003397619 +/- 6.739364e-05
+lmY: 0.0003544331 +/- 6.153328e-05
 
-Arima: 3e-04 1e-04 4.6072 0
+Arima: 4e-04 1e-04 5.1881 0
 
@@
 
-lmD: 0.04427476 +/- 0.004265004
+lmD: 0.03803985 +/- 0.003667512
 
-lmY: 0.04427565 +/- 0.004265086
+lmY: 0.03804065 +/- 0.003667582
 
-Arima: 0.0443 0.0049 9.0734 0
+Arima: 0.038 0.0043 8.9476 0
 
@@
 
-lmD: 0.239157 +/- 0.23526
+lmD: 0.2175113 +/- 0.2519978
 
-lmY: 0.239194 +/- 0.235264
+lmY: 0.217552 +/- 0.2520021
 
-Arima: 0.2304 0.3281 0.7023 0.4825
+Arima: 0.2071 0.368 0.5628 0.5736
 
@@
 
-lmD: 0.1370797 +/- 0.1721383
+lmD: 0.1126483 +/- 0.193195
 
-lmY: 0.1371014 +/- 0.1721412
+lmY: 0.112674 +/- 0.1931983
 
-Arima: 0.1135 0.2908 0.3902 0.6964
+Arima: 0.0865 0.3384 0.2558 0.7981
 
@@
 
-lmD: 6.254578 +/- 4.293245
+lmD: 6.106963 +/- 4.268209
 
-lmY: 6.255019 +/- 4.293318
+lmY: 6.107414 +/- 4.268282
 
-Arima: 6.2546 4.3752 1.4296 0.1528
+Arima: 6.107 4.3537 1.4027 0.1607
 
@@
 
-lmD: 0.0006000764 +/- 0.0003458892
+lmD: 0.0004829553 +/- 0.0002839705
 
-lmY: 0.0006000719 +/- 0.0003458953
+lmY: 0.0004829612 +/- 0.0002839754
 
-Arima: 6e-04 4e-04 1.5164 0.1294
+Arima: 5e-04 3e-04 1.492 0.1357
 
@@
 
-lmD: 0.0004422727 +/- 0.0002935454
+lmD: 0.000372236 +/- 0.0002233382
 
-lmY: 0.0004422599 +/- 0.0002935506
+lmY: 0.0003722343 +/- 0.0002233421
 
-Arima: 4e-04 4e-04 1.2377 0.2158
+Arima: 4e-04 3e-04 1.3298 0.1836
 
@@
 
-lmD: 0.008932077 +/- 0.005813607
+lmD: 0.008401207 +/- 0.005558251
 
-lmY: 0.008932528 +/- 0.005813706
+lmY: 0.008401691 +/- 0.005558346
 
-Arima: 0.0089 0.0061 1.4624 0.1436
+Arima: 0.0084 0.0058 1.453 0.1462
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-7} \end{center}
+
 @Martins2022
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-5} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-8} \end{center}
 
@@
 
-\begin{verbatim}
- Group0 wattGLB.mean wattGLB.SD wattGLB.max wattGLB.min wattGLB.median
-  <int>        <num>      <num>       <num>       <num>          <num>
-\end{verbatim}
-
-1: 13 225.5281 12.544463 242.3534 203.6571 227.4027
-2: 315 183.2380 14.021218 205.7494 161.2362 183.4280
-3: 393 211.4853 26.002452 254.6444 169.0380 210.8473
-4: 501 259.8284 9.591647 272.2979 242.1095 260.8614
-5: 591 227.3434 9.025312 240.3322 214.5732 225.0337
----\\
-253: 65381 186.9246 8.529287 197.1196 173.4441 187.0577
-254: 65423 194.8850 10.569185 207.5506 179.9910 196.8111
-255: 65519 181.8946 11.823089 200.5545 165.3543 182.3613
-256: 65529 178.3845 4.546207 186.4354 173.1996 176.4594
-257: 65533 217.2415 16.147690 236.0007 182.0452 222.7584
-wattGLB.sum wattGLB.N GLB\_ench.mean GLB\_ench.SD GLB\_ench.max GLB\_ench.min
-1: 2706.337 12 0.01659718 0.007597084 0.02543323 0.0041557214
-2: 2931.808 16 0.01163209 0.008450614 0.02498250 0.0005249866
-3: 6133.073 29 0.03494054 0.021369070 0.07259215 0.0044677582
-4: 2598.284 10 0.01406600 0.008869984 0.02725920 0.0007449344
-5: 3410.151 15 0.03288980 0.018031095 0.06712790 0.0011333915
----\\
-253: 1682.321 9 0.03425477 0.010915540 0.05378668 0.0118438957
-254: 2143.735 11 0.03947032 0.018939813 0.07284705 0.0123456804
-255: 2364.630 13 0.01785069 0.010225149 0.04054656 0.0055296019
-256: 1605.460 9 0.04394266 0.035577012 0.11668555 0.0112579853
-257: 3693.105 17 0.04877689 0.033134593 0.09685661 0.0045080034
-GLB\_ench.median GLB\_ench.sum GLB\_ench.N GLB\_diff.mean GLB\_diff.SD
-1: 0.01721937 0.1991661 12 3.660370 1.651727
-2: 0.01278289 0.1861135 16 1.988442 1.350952
-3: 0.03071007 1.0132755 29 6.568530 3.245441
-4: 0.01192006 0.1406600 10 3.555058 2.194372
-5: 0.02545803 0.4933469 15 7.052047 3.532240
----\\
-253: 0.03470823 0.3082929 9 6.159514 1.935746
-254: 0.04550629 0.4341735 11 7.343593 3.465457
-255: 0.01677883 0.2320589 13 3.108486 1.622229
-256: 0.03000519 0.3954839 9 7.259927 5.518687
-257: 0.04859240 0.8292071 17 9.892759 6.595347
-GLB\_diff.max GLB\_diff.min GLB\_diff.median GLB\_diff.sum GLB\_diff.N SZA.mean
-1: 5.649198 1.0029849 3.774258 43.92444 12 75.40653
-2: 3.940819 0.1079590 2.312200 31.81508 16 76.61730
-3: 11.440352 1.1326292 6.282210 190.48737 29 75.33588
-4: 6.842022 0.2026931 3.093025 35.55058 10 74.03057
-5: 13.497769 0.2712624 5.748451 105.78070 15 77.05677
----\\
-253: 9.547676 2.2941778 6.272625 55.43563 9 77.12742
-254: 13.894581 2.1950124 8.002303 80.77952 11 76.73931
-255: 6.456701 1.0612959 2.882533 40.41032 13 76.78463
-256: 18.438732 2.0755204 5.133219 65.33934 9 77.17689
-257: 19.080014 1.0591174 10.403814 168.17691 17 75.18167
-SZA.SD SZA.max SZA.min SZA.median SZA.sum SZA.N Date
-1: 0.6667310 76.42244 74.38838 75.40725 904.8784 12 1993-05-13 04:33:30
-2: 0.8567238 77.96388 75.26476 76.61909 1225.8768 16 1993-07-13 04:22:30
-3: 1.5939261 77.95091 72.71007 75.33887 2184.7406 29 1993-08-12 04:45:30
-4: 0.5362886 74.82883 73.23468 74.02978 740.3057 10 1993-10-04 14:30:30
-5: 0.5907621 77.98809 76.13886 77.05264 1155.8515 15 1993-12-06 07:01:30
----\\
-253: 0.4856759 77.83591 76.41717 77.12805 694.1468 9 2023-06-18 16:37:30
-254: 0.5905545 77.62822 75.84766 76.74023 844.1324 11 2023-06-30 04:17:30
-255: 0.7131983 77.88183 75.68429 76.78564 998.2002 13 2023-07-28 04:33:30
-256: 0.5066369 77.91629 76.43632 77.17730 694.5920 9 2023-08-06 04:40:30
-257: 0.9419447 76.67187 73.68745 75.18288 1278.0885 17 2023-08-06 16:04:30
-
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-11} \end{center}
@@
 
-Group0 wattGLB.mean wattGLB.SD wattGLB.max wattGLB.min wattGLB.median
-1: 16423 249.6246 39.53847 315.8996 185.1393 248.8458
-wattGLB.sum wattGLB.N GLB\_ench.mean GLB\_ench.SD GLB\_ench.max GLB\_ench.min
-1: 10484.23 42 0.03013706 0.02002665 0.07315483 0.000646732
-GLB\_ench.median GLB\_ench.sum GLB\_ench.N GLB\_diff.mean GLB\_diff.SD
-1: 0.02576315 1.265756 42 6.504293 3.430543
-GLB\_diff.max GLB\_diff.min GLB\_diff.median GLB\_diff.sum GLB\_diff.N SZA.mean
-1: 12.62058 0.2041703 6.416318 273.1803 42 74.25137
-SZA.SD SZA.max SZA.min SZA.median SZA.sum SZA.N Date
-1: 2.245081 77.98308 70.48178 74.26151 3118.558 42 2004-05-25 04:16:30
-Group0 wattGLB.mean wattGLB.SD wattGLB.max wattGLB.min wattGLB.median
-1: 15087 228.4206 30.98628 279.3502 177.6686 229.0747
-wattGLB.sum wattGLB.N GLB\_ench.mean GLB\_ench.SD GLB\_ench.max GLB\_ench.min
-1: 7081.037 31 0.01717012 0.01012086 0.03564823 0.0002394964
-GLB\_ench.median GLB\_ench.sum GLB\_ench.N GLB\_diff.mean GLB\_diff.SD
-1: 0.01952886 0.5322736 31 3.550457 1.75638
-GLB\_diff.max GLB\_diff.min GLB\_diff.median GLB\_diff.sum GLB\_diff.N SZA.mean
-1: 6.235319 0.065965 4.201192 110.0642 31 75.0963
-SZA.SD SZA.max SZA.min SZA.median SZA.sum SZA.N Date
-1: 1.712864 77.9228 72.27203 75.09567 2327.985 31 2003-09-05 05:06:30
-{[}1{]} 3.550457
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-16} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-17} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-18} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-19} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-20} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-21} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-22} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-23} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-24} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-25} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-26} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-27} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-28} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-29} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-30} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-31} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-32} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-33} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-34} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-35} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-36} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-37} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-38} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-39} \end{center}
 
@@
 \begin{verbatim}
-2024-02-19 11:13:55.4 athan@tyler GHI_enh_04_investigate.R 0.693826 mins
+2024-02-27 10:55:58.9 athan@tyler GHI_enh_04_investigate.R 0.609646 mins
 \end{verbatim}

### 2024-02-27 GHI_enh_03_process.tex
Commit 2024-02-27 14:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-02-22}
+\date{2024-02-27}
 
@@
 \begin{verbatim}
-Warning: Removed 2 rows containing missing values (`geom_line()`).
-Removed 2 rows containing missing values (`geom_line()`).
+Warning: Removed 2 rows containing missing values or values
+outside the scale range (`geom_line()`).
+Removed 2 rows containing missing values or values
+outside the scale range (`geom_line()`).
 \end{verbatim}
@@
 ST_E_sza
+ST_E_sza_monthly
 ST_E_yearly
@@
 ST_extreme_SZA
+ST_extreme_SZA_monthly
 ST_extreme_yearly
@@
 ST_sza
+ST_sza_monthly
 ST_total
@@
 \begin{verbatim}
-2024-02-22 12:05:59.3 athan@tyler GHI_enh_03_process.R 2.189978 mins
+2024-02-27 11:14:26.8 athan@sagan GHI_enh_03_process.R 1.108372 mins
 \end{verbatim}

### 2024-02-28 GHI_enh_03_process.tex
Commit 2024-02-28 16:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-02-27}
+\date{2024-02-28}
 
@@
 \begin{verbatim}
-Warning: Removed 2 rows containing missing values or values
-outside the scale range (`geom_line()`).
-Removed 2 rows containing missing values or values
-outside the scale range (`geom_line()`).
+Warning: Removed 2 rows containing missing values or values outside the scale range (`geom_line()`).
+Removed 2 rows containing missing values or values outside the scale range (`geom_line()`).
 \end{verbatim}
@@
     Min      1Q  Median      3Q     Max 
--382.05 -149.78  -46.64   98.42  770.22
+-372.77 -150.51  -49.67   99.05  778.55
 
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      -1.067e+02  5.109e+01  -2.088   0.0375 *  
-as.numeric(Date)  3.393e-07  4.098e-08   8.279  2.5e-15 ***
+(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
+as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
 ---
@@
 
-Residual standard error: 216.2 on 358 degrees of freedom
-Multiple R-squared:  0.1607,    Adjusted R-squared:  0.1583 
-F-statistic: 68.54 on 1 and 358 DF,  p-value: 2.498e-15
+Residual standard error: 217 on 361 degrees of freedom
+Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
+F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
 \end{verbatim}
@@
                     Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       -1.067e+02  5.109e+01  -2.088   0.0375 *  
-ST_E_monthly$Date  3.393e-07  4.098e-08   8.279  2.5e-15 ***
+(Intercept)       -9.118e+01  5.082e+01  -1.794   0.0736 .  
+ST_E_monthly$Date  3.246e-07  4.062e-08   7.991 1.82e-14 ***
 ---
@@
 \begin{verbatim}
-2024-02-27 11:14:26.8 athan@sagan GHI_enh_03_process.R 1.108372 mins
+2024-02-28 13:08:22.6 athan@sagan GHI_enh_03_process.R 1.133646 mins
 \end{verbatim}

### 2024-02-28 GHI_enh_04_investigate.tex
Commit 2024-02-28 16:14

@@
 
-lmD: 1.608404 +/- 0.1098661
+lmD: 1.566022 +/- 0.1083205
 
-lmY: 1.608426 +/- 0.1098682
+lmY: 1.566038 +/- 0.1083224
 
-Arima: 1.6087 0.1487 10.8185 0
+Arima: 1.5664 0.1467 10.6787 0
 
@@
 
-lmD: 1.06616 +/- 0.1703576
+lmD: 1.087008 +/- 0.1678713
 
-lmY: 1.066188 +/- 0.1703608
+lmY: 1.087035 +/- 0.1678742
 
-Arima: 1.1439 0.255 4.4864 0
+Arima: 1.16 0.2511 4.6199 0
 
-lmD: 0.2020422 +/- 0.1403033
+lmD: -0.01234536 +/- 0.1388793
 
-lmY: 0.2020754 +/- 0.140306
+lmY: -0.01233011 +/- 0.1388818
 
@@
 
-Arima: 0.2014 5.4204 0.0371 0.9704
+Arima: -0.0132 6.8981 -0.0019 0.9985
 
@@
 
-lmD: 499.5958 +/- 96.35149
+lmD: 561.0124 +/- 94.87888
 
-lmY: 499.601 +/- 96.35332
+lmY: 561.0217 +/- 94.88053
 
-Arima: 500.7839 150.1232 3.3358 9e-04
+Arima: 562.031 148.2404 3.7913 1e-04
 
@@
 
-lmD: 0.003319458 +/- 0.0002745369
+lmD: 0.003266094 +/- 0.0002706818
 
-lmY: 0.003319501 +/- 0.0002745421
+lmY: 0.003266127 +/- 0.0002706866
 
-Arima: 0.0033 4e-04 9.0564 0
+Arima: 0.0033 4e-04 9.0498 0
 
@@
 
-lmD: 0.001746196 +/- 0.0003178251
+lmD: 0.001677055 +/- 0.00031363
 
-lmY: 0.001746269 +/- 0.0003178311
+lmY: 0.001677118 +/- 0.0003136354
 
-Arima: 0.0019 5e-04 3.7071 2e-04
+Arima: 0.0018 5e-04 3.6151 3e-04
 
-lmD: 0.2020422 +/- 0.1403033
+lmD: -0.01234536 +/- 0.1388793
 
-lmY: 0.2020754 +/- 0.140306
+lmY: -0.01233011 +/- 0.1388818
 
@@
 
-lmD: 0.9305909 +/- 0.1460762
+lmD: 0.9770213 +/- 0.1439346
 
-lmY: 0.9306112 +/- 0.146079
+lmY: 0.9770437 +/- 0.1439371
 
-Arima: 1.0003 0.2219 4.5077 0
+Arima: 1.041 0.2186 4.7612 0
 
@@
 
-lmD: 0.8634408 +/- 0.1045511
+lmD: 0.8175146 +/- 0.1034317
 
-lmY: 0.8634567 +/- 0.1045531
+lmY: 0.8175255 +/- 0.1034336
 
-Arima: 0.8634 0.1212 7.1257 0
+Arima: 0.8175 0.12 6.8104 0
 
@@
 
-lmD: 0.1926088 +/- 0.038164
+lmD: 0.1909484 +/- 0.03787569
 
-lmY: 0.1926139 +/- 0.03816473
+lmY: 0.190953 +/- 0.03787636
 
-Arima: 0.1926 0.0403 4.7782 0
+Arima: 0.191 0.0401 4.7635 0
 
@@
 
-lmD: 0.5100905 +/- 0.04695669
+lmD: 0.4856759 +/- 0.04638817
 
-lmY: 0.5100995 +/- 0.04695759
+lmY: 0.4856822 +/- 0.046389
 
-Arima: 0.5101 0.0557 9.1553 0
+Arima: 0.4857 0.0552 8.802 0
 
@@
 
-lmD: 25.65919 +/- 2.576134
+lmD: 24.46426 +/- 2.544261
 
-lmY: 25.65971 +/- 2.576183
+lmY: 24.46465 +/- 2.544306
 
-Arima: 25.6594 3.1045 8.2652 0
+Arima: 24.4646 3.0718 7.9642 0
 
@@
 
-lmD: 0.001358275 +/- 0.0001381135
+lmD: 0.001335923 +/- 0.0001367163
 
-lmY: 0.001358294 +/- 0.0001381161
+lmY: 0.001335939 +/- 0.0001367188
 
-Arima: 0.0014 2e-04 8.5635 0
+Arima: 0.0013 2e-04 8.5092 0
 
@@
 
-lmD: 0.0003544276 +/- 6.15321e-05
+lmD: 0.000372438 +/- 6.132797e-05
 
-lmY: 0.0003544331 +/- 6.153328e-05
+lmY: 0.0003724446 +/- 6.132906e-05
 
-Arima: 4e-04 1e-04 5.1881 0
+Arima: 4e-04 1e-04 5.4467 0
 
@@
 
-lmD: 0.03803985 +/- 0.003667512
+lmD: 0.03656094 +/- 0.003621568
 
-lmY: 0.03804065 +/- 0.003667582
+lmY: 0.03656157 +/- 0.003621632
 
-Arima: 0.038 0.0043 8.9476 0
+Arima: 0.0366 0.0042 8.6966 0
 
@@
 
-lmD: 0.2175113 +/- 0.2519978
+lmD: 0.1872432 +/- 0.2494753
 
-lmY: 0.217552 +/- 0.2520021
+lmY: 0.1872803 +/- 0.2494792
 
-Arima: 0.2071 0.368 0.5628 0.5736
+Arima: 0.1718 0.3646 0.4712 0.6375
 
@@
 
-lmD: 0.1126483 +/- 0.193195
+lmD: 0.0912832 +/- 0.1914519
 
-lmY: 0.112674 +/- 0.1931983
+lmY: 0.09130632 +/- 0.191455
 
-Arima: 0.0865 0.3384 0.2558 0.7981
+Arima: 0.05 0.3354 0.1491 0.8815
 
@@
 
-lmD: 0.02925782 +/- 0.02144818
+lmD: 0.03034705 +/- 0.02124537
 
-lmY: 0.02925974 +/- 0.02144855
+lmY: 0.03034902 +/- 0.02124571
 
-Arima: 0.0293 0.0223 1.3139 0.1889
+Arima: 0.0304 0.022 1.3788 0.1679
 
@@
 
-lmD: 6.106963 +/- 4.268209
+lmD: 6.13936 +/- 4.224962
 
-lmY: 6.107414 +/- 4.268282
+lmY: 6.139801 +/- 4.22503
 
-Arima: 6.107 4.3537 1.4027 0.1607
+Arima: 6.1407 4.3045 1.4266 0.1537
 
@@
 
-lmD: 0.0004829553 +/- 0.0002839705
+lmD: 0.0005085756 +/- 0.0002811408
 
-lmY: 0.0004829612 +/- 0.0002839754
+lmY: 0.0005085833 +/- 0.0002811453
 
-Arima: 5e-04 3e-04 1.492 0.1357
+Arima: 5e-04 3e-04 1.598 0.11
 
@@
 
-lmD: 0.000372236 +/- 0.0002233382
+lmD: 0.000398809 +/- 0.0002210804
 
-lmY: 0.0003722343 +/- 0.0002233421
+lmY: 0.0003988093 +/- 0.0002210839
 
-Arima: 4e-04 3e-04 1.3298 0.1836
+Arima: 4e-04 3e-04 1.4507 0.1469
 
@@
 
-lmD: 0.008401207 +/- 0.005558251
+lmD: 0.008776506 +/- 0.00550671
 
-lmY: 0.008401691 +/- 0.005558346
+lmY: 0.008777009 +/- 0.005506798
 
-Arima: 0.0084 0.0058 1.453 0.1462
+Arima: 0.0088 0.0057 1.5378 0.1241
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-8} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-9} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-10} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-11} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-12} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-13} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-14} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-15} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-16} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-17} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-18} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-19} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-20} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-21} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-22} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-23} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-24} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-25} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-26} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-27} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-28} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-29} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-30} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-31} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-32} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-33} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-34} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-35} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-36} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-37} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-38} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-39} \end{center}
-
 \textbf{END}
@@
 \begin{verbatim}
-2024-02-27 10:55:58.9 athan@tyler GHI_enh_04_investigate.R 0.609646 mins
+2024-02-28 13:08:49.0 athan@sagan GHI_enh_04_investigate.R 0.269881 mins
 \end{verbatim}

### 2024-02-29 GHI_enh_04_investigate.tex
Commit 2024-02-29 12:14
Commit 2024-02-29 13:12

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-02-28}
+\date{2024-02-29}
 
@@
 
-Arima: -0.0132 6.8981 -0.0019 0.9985
+Arima: -0.0132 6.9042 -0.0019 0.9985
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3} \end{center}
+
 \hypertarget{zhang2018}{%
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-5} \end{center}
 
@@
 
+\newpage
+\FloatBarrier
+
+\hypertarget{sza-enhancements-by-month}{%
+\subsubsection{SZA enhancements by month}\label{sza-enhancements-by-month}}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-3} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-8} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-9} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-10} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-11} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-12} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-13} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-14} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-15} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-16} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-17} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-18} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-19} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-20} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-21} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-22} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-23} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-24} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-25} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-26} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-27} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-28} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-29} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-30} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-31} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-32} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-33} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-34} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-35} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-36} \end{center}
+
 \textbf{END}
@@
 \begin{verbatim}
-2024-02-28 13:08:49.0 athan@sagan GHI_enh_04_investigate.R 0.269881 mins
+2024-02-29 11:01:18.2 athan@tyler GHI_enh_04_investigate.R 1.255829 mins
 \end{verbatim}

### 2024-02-29 article/article.Rmd
Commit 2024-02-29 13:12

@@
 
-```{r echo=FALSE, fig.cap="", out.width = '100%'}
+```{r echo=FALSE, fig.cap="Trend of the daily excess energy due to CE", out.width = '100%'}
+knitr::include_graphics("../images/daily-12.png")
+```
+
+```{r echo=FALSE, fig.cap="Distribution of the number of CE cases", out.width = '100%'}
 knitr::include_graphics("../images/climCEmonth-1.png")
 ```
+
+```{r echo=FALSE, fig.cap="Trend of the yearly excess energy", out.width = '100%'}
+knitr::include_graphics("../images/energy-1.png")
+```
+
+```{r echo=FALSE, fig.cap="Trend of the excess energy per CE", out.width = '100%'}
+knitr::include_graphics("../images/energy-3.png")
+```
+
+## Groups stats
+
+```{r echo=FALSE, fig.cap="Distribution of CE groups", out.width = '100%'}
+knitr::include_graphics("../images/groups-1.png")
+```
+
+```{r echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration", out.width = '100%'}
+knitr::include_graphics("../images/groups-2.png")
+```
+
+```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration", out.width = '100%'}
+knitr::include_graphics("../images/groups-2.png")
+```
+
+## CE above TSI
 

### 2024-02-29 GHI_enh_04_investigate.tex
Commit 2024-02-29 15:11

@@
 
+\begin{verbatim}
+
+Attaching package: 'dplyr'
+\end{verbatim}
+
+\begin{verbatim}
+The following objects are masked from 'package:data.table':
+
+    between, first, last
+\end{verbatim}
+
+\begin{verbatim}
+The following objects are masked from 'package:stats':
+
+    filter, lag
+\end{verbatim}
+
+\begin{verbatim}
+The following objects are masked from 'package:base':
+
+    intersect, setdiff, setequal, union
+\end{verbatim}
+
+\begin{verbatim}
+Loading required package: viridisLite
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-6} \end{center}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCEmonth-1} \end{center}
@@
 \begin{verbatim}
-2024-02-29 11:01:18.2 athan@tyler GHI_enh_04_investigate.R 1.255829 mins
+2024-02-29 13:02:09.3 athan@tyler GHI_enh_04_investigate.R 0.985446 mins
 \end{verbatim}

### 2024-02-29 GHI_enh_04_investigate.R
Commit 2024-02-29 17:11

@@ -68,10 +68,12 @@ if (!interactive()) {
 
 
 #+ echo=F, include=T
-library(data.table, quietly = TRUE, warn.conflicts = FALSE)
-library(pander    , quietly = TRUE, warn.conflicts = FALSE)
-library(ggplot2   , quietly = TRUE, warn.conflicts = FALSE)
-library(lmtest    , quietly = TRUE, warn.conflicts = FALSE)
+library(data.table    , quietly = TRUE, warn.conflicts = FALSE)
+library(pander        , quietly = TRUE, warn.conflicts = FALSE)
+library(ggplot2       , quietly = TRUE, warn.conflicts = FALSE)
+library(lmtest        , quietly = TRUE, warn.conflicts = FALSE)
+library(viridis       , quietly = TRUE, warn.conflicts = FALSE)
+library(ggpointdensity, quietly = TRUE, warn.conflicts = FALSE)
 
 panderOptions("table.alignment.default", "right")
 panderOptions("table.split.table",        120   )
@@ -323,10 +325,26 @@ plot(ST_G0$GLB_ench.N, ST_G0$GLB_diff.sum/ST_G0$GLB_ench.N,
      xlab = "Duration of enhancemnt",
      ylab = "Extra mean Irradiance per mimute")
 
+ggplot(data    = ST_G0,
+       mapping = aes(x = GLB_ench.N, y = ST_G0$GLB_diff.sum/ST_G0$GLB_ench.N)) +
+  xlab("Duration of CE group [minutes]") +
+  ylab("Extra mean Irradiance per mimute [W/m^2]") +
+  geom_pointdensity(adjust = 10) +
+  scale_color_viridis()
+
+
 
 plot(ST_G0$GLB_ench.N, ST_G0$GLB_diff.mean,
      xlab = "Duration of enhancemnt",
      ylab = "Extra mean Irradiance per mimute")
+
+
+ggplot(data    = ST_G0,
+       mapping = aes(x = GLB_diff.N, y = GLB_diff.mean)) +
+  xlab("Duration of CE group [minutes]") +
+  ylab("Mean Over Irradiance [W/m^2]") +
+  geom_pointdensity(adjust = 5) +
+  scale_color_viridis()
 
 
 
@@ -338,6 +356,16 @@ plot(ST_G0[, GLB_diff.max, GLB_diff.N ],
      ylab = "Maximun Over Irradiance")
 
 
[…]

### 2024-02-29 GHI_enh_04_investigate.tex
Commit 2024-02-29 17:11

--- 2024-02-29 GHI_enh_04_investigate.tex
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-5} \end{center}
+
 \hypertarget{zhang2018}{%
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-6} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-5} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8} \end{center}
 
@@
 \begin{verbatim}
-2024-02-29 11:01:18.2 athan@tyler GHI_enh_04_investigate.R 1.255829 mins
+2024-02-29 14:29:51.0 athan@tyler GHI_enh_04_investigate.R 1.085176 mins
 \end{verbatim}

### 2024-02-29 GHI_enh_04_investigate.tex
Commit 2024-02-29 18:11

@@
 
+\begin{verbatim}
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
+i Please use the `legend.position.inside` argument of `theme()` instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3} \end{center}
@@
 
+\begin{verbatim}
+Warning: The S3 guide system was deprecated in ggplot2 3.5.0.
+i It has been replaced by a ggproto system that can be extended.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-6} \end{center}
+
 \hypertarget{zhang2018}{%
 \subsection{@Zhang2018}\label{zhang2018}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-6} \end{center}
 
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9} \end{center}
 
@@
 \begin{verbatim}
-2024-02-29 14:29:51.0 athan@tyler GHI_enh_04_investigate.R 1.085176 mins
+2024-02-29 16:10:43.9 athan@tyler GHI_enh_04_investigate.R 1.399842 mins
 \end{verbatim}

### 2024-02-29 article/article.Rmd
Commit 2024-02-29 19:12

--- 2024-02-26 article/article.Rmd
@@
 author:
-  - name:         Athanasios N. Natsis 
-    email:        natsisphysicist@gmail.com
-    affiliation:  Laboratory of Atmospheric Physics
-    footnote:     footnote one
-    correspondingauthor: true
+  - Athanasios N. Natsis^[Laboratory of Atmospheric Physics natsisphysicist@gmail.com] 
   - name:         Alkiviadis Bais
@@
   - keyword2
-date:          last-modified
+
 bibliography:  [bibliography.bib]
+
+date: "`r format(Sys.time(), '%F')`"
+
+header-includes:
+  - \usepackage{caption}
+  - \usepackage{placeins}
+  - \captionsetup{font=small}
 
@@
  #    keep_tex:            yes
-  bookdown::word_document2: default
   bookdown::pdf_document2:
@@
     biblio-style:     apalike
+    bookdown::word_document2: default
 ---
@@
 
-CEG: continuous group of cloud enhancement cases
+ECE: extreme cloud enhancement cases one minute over TSI on horizontal plane
+
+CEG: cloud enhancement groups, cases events with consecutive CE
 
@@
 Thus we will refer to this time scale as a cloud enhancement event (CE).
-Due to the instruments response time.
+Due to the instruments response time.....
 
 ## Data quality control
+
+.......
 
@@
 
-## Clear sky identification
+## Criteria for enhancement identification
 
-Use it to find some interesting days to manual check the CE thresholds. No other usage of clear/cloud characterization in CE.
-
-## Criteria for enhancement based on TSI
+-   some others were tested
 
@@
 
-We used as reference the .... extraterrestrial horizontal irradiance .....
+We used as reference a modelled clear sky approximation,
 
-\ref{eq:test}
-
-$$
-\text{ETH} = \cos(\theta) \times \text{TSI}_\text{TOA}
-$$
-
-$$
-\text{GHI} > 999 \text{ETH}
-$$
+criteria for cloud enhancement identification are set acording the Equation \ref{eq:CE4}
 
@@
 \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{if $ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}.
-\end{cases}\label{eq:test}
+\end{cases}\label{eq:CE4}
+\end{equation}
+where: ..........
+
+expand: libradtran calculations and modeling
+
+A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane Equation \ref{eq:ECE}
+
+\begin{equation}
+\text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
+\label{eq:ECE}
 \end{equation}
 
-```{r echo=FALSE, fig.cap="", out.width = '100%'}
+## Thresholds
+
+Thresholds by inspecting a selection of days with some specs
+
+Reasoning for the selection
+
+Objectivity
+
+Describe set of referce days we used to evalutate
+
+Example of days plot?
+
+... this is more clear to understand and describe ....
+
+\FloatBarrier
+
+# Results
+
+## Trend
+
+```{r echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"}
+knitr::include_graphics("../images/daily-12.png")
+```
+
+```{r echo=FALSE, fig.cap="Trend of the yearly excess energy"}
+knitr::include_graphics("../images/energy-1.png")
+```
+
+```{r echo=FALSE, fig.cap="Trend of the excess energy per CE"}
+knitr::include_graphics("../images/energy-3.png")
+```
+
+\FloatBarrier
+
+## Climatology
+
+```{r echo=FALSE, fig.cap="Distribution of the number of CE cases"}
 knitr::include_graphics("../images/climCEmonth-1.png")
@@
 
--   some others were tested
+```{r echo=FALSE, fig.cap="Distribution of CE above reference"}
+knitr::include_graphics("../images/distributions-5.png")
+```
 
-Thresholds by inspecting a selection of days with some specs
+\FloatBarrier
 
-# Results
+## Groups stats
+
+```{r echo=FALSE, fig.cap="Distribution of CE groups"}
+knitr::include_graphics("../images/groups-1.png")
+```
+
+```{r echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"}
+knitr::include_graphics("../images/groups-4.png")
+```
+
+```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"}
+knitr::include_graphics("../images/groups-6.png")
+```
+
+```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"}
+knitr::include_graphics("../images/groups-8.png")
+```
+
+\FloatBarrier
+
+## Extrene CE above TSI
+
+```{r echo=FALSE, fig.cap="Distribution of the number of ECE cases"}
+knitr::include_graphics("../images/climECEmonth-1.png")
+```
+
+```{r echo=FALSE, fig.cap="Distribution of ECE above 'clear sky' reference"}
+knitr::include_graphics("../images/extremedistributions-2.png")
+```
+
+```{r echo=FALSE, fig.cap="Distribution of ECE Irradiance above 'TSI'"}
+knitr::include_graphics("../images/extremedistributions-4.png")
+```
 
@@
 
+\FloatBarrier
+
 # Discussion and conclusions
 
-------------------------------------------------------------------------
+Compare to other location stats.
+max, ECE, distributions ....
 
-## render test
-
-[@Bais1997]
+Climatology results
 

### 2024-02-29 GHI_enh_04_investigate.R

@@ -126,8 +126,6 @@ DRAFT <- TRUE
 
 
 
-
-
 ##  Daily  ---------------------------------------------------------------------
 cat(ls(pattern = "^ST.*daily"))
 
@@ -319,17 +317,17 @@ write.csv(x = dailytrendsY,
 hist(ST_G0$GLB_ench.N,
      breaks = 50,
      xlab = "Minutes of enhacement per CE group",
-     main = "Duration of enhancement cases")
+     main = "Duration of enhancement cases groups")
 
 
 plot(ST_G0$GLB_ench.N, ST_G0$GLB_diff.sum/ST_G0$GLB_ench.N,
-     xlab = "Duration of enhancemnt",
+     xlab = "Duration of enhancemnt cases groups",
      ylab = "Extra mean Irradiance per mimute")
 
 
 ggplot(data    = ST_G0,
        mapping = aes(x = GLB_ench.N, y = ST_G0$GLB_diff.sum/ST_G0$GLB_ench.N)) +
-  xlab("Duration of CE group [minutes]") +
+  xlab("Duration of CE groups [minutes]") +
   ylab("Extra mean Irradiance per mimute [W/m^2]") +
   geom_pointdensity(aes(color = after_stat(log(n_neighbors))),
                     adjust = 1,
@@ -349,7 +347,7 @@ ggplot(data    = ST_G0,
 
 ggplot(data    = ST_G0,
        mapping = aes(x = GLB_ench.N, y = ST_G0$GLB_diff.sum/ST_G0$GLB_ench.N)) +
-  xlab("Duration of CE group [minutes]") +
+  xlab("Duration of CE groups [minutes]") +
   ylab("Extra mean Irradiance per mimute [W/m^2]") +
   geom_pointdensity(adjust = 10,
                     size = 1) +
@@ -367,12 +365,12 @@ ggplot(data    = ST_G0,
 
 
 plot(ST_G0$GLB_ench.N, ST_G0$GLB_diff.mean,
-     xlab = "Duration of enhancemnt",
+     xlab = "Duration of enhancemnt cases groups",
      ylab = "Extra mean Irradiance per mimute")
 
 ggplot(data    = ST_G0,
        mapping = aes(x = GLB_diff.N, y = GLB_diff.mean)) +
-  xlab("Duration of CE group [minutes]") +
+  xlab("Duration of CE groups [minutes]") +
[…]

### 2024-02-29 article/article.Rmd
Commit 2024-02-29 20:15

@@
 title:    SDR enhancement by clouds
+
 subtitle: A Short Subtitle
+
 author:
-  - Athanasios N. Natsis^[Laboratory of Atmospheric Physics natsisphysicist@gmail.com] 
-  - name:         Alkiviadis Bais
-    email:        abais@auth.gr 
-    affiliation:  Laboratory of Atmospheric Physics
-    correspondingauthor: false
-  - name:         Charikleia Meleti
-    email:        meleti@auth.gr
-    affiliation:  Laboratory of Atmospheric Physics
+  - Athanasios N. Natsis^[Laboratory of Atmospheric Physics _natsisphysicist@gmail.com_] 
+  - Alkiviadis Bais^[Laboratory of Atmospheric Physics _abais@auth.gr_] 
+  - Charikleia Meleti^[Laboratory of Atmospheric Physics _meleti@auth.gr_]
+
 abstract: |
   This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
+
 keywords: 
@@
 ```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"}
-knitr::include_graphics("../images/groups-6.png")
-```
-
-```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"}
 knitr::include_graphics("../images/groups-8.png")
@@
 
--   max
+-   max value ECE
 -   seasonal

### 2024-03-01 GHI_enh_04_investigate.tex
Commit 2024-02-29 19:12
Commit 2024-02-29 20:15
Commit 2024-03-01 19:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-02-29}
+\date{2024-03-01}
 
@@
 
+\begin{verbatim}
+Warning in ans * length(l) + if1: longer object length is not a multiple of
+shorter object length
+\end{verbatim}
+
 \newpage
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-1} \end{center}
+
+lmD: 0.9508227 +/- 0.1552488
+
+lmY: 0.9508465 +/- 0.1552515
+
+Arima: 1.0223 0.2369 4.315 0
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-2} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-2} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-3} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-3} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-4} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-4} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-5} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-5} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-6} \end{center}
+
+lmD: 0.001714795 +/- 0.0002777698
+
+lmY: 0.001714851 +/- 0.0002777746
+
+Arima: 0.0019 5e-04 4.0604 0
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-7} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-6} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-8} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-7} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-9} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-8} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-10} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-9} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-11} \end{center}
+
+lmD: 0.2160878 +/- 0.03807227
+
+lmY: 0.2160919 +/- 0.03807295
+
+Arima: 0.2161 0.0414 5.2173 0
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-12} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-10} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-13} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-11} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-14} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-12} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-15} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-13} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-16} \end{center}
+
+lmD: 0.000422753 +/- 5.903214e-05
+
+lmY: 0.0004227591 +/- 5.903319e-05
+
+Arima: 4e-04 1e-04 6.291 0
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-17} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-14} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-18} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-15} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-19} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-16} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-20} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-17} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-21} \end{center}
+
+lmD: 0.0498083 +/- 0.192504
+
+lmY: 0.04983275 +/- 0.1925071
+
+Arima: 0.0086 0.3464 0.0248 0.9802
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-22} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-18} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-23} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-19} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-24} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-20} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-25} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-21} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-26} \end{center}
+
+lmD: 0.0003565528 +/- 0.0002141263
+
+lmY: 0.0003565519 +/- 0.0002141297
+
+Arima: 3e-04 3e-04 1.3206 0.1866
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-27} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-22} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-28} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-23} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-29} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-24} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-30} \end{center}
 
@@
 \begin{verbatim}
-Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2
+3.5.0.
 i Please use the `legend.position.inside` argument of `theme()` instead.
 This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
+generated.
+\end{verbatim}
+
+\begin{verbatim}
+Warning: The S3 guide system was deprecated in ggplot2 3.5.0.
+i It has been replaced by a ggproto system that can be extended.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
+generated.
 \end{verbatim}
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-5} \end{center}
-
-\begin{verbatim}
-Warning: The S3 guide system was deprecated in ggplot2 3.5.0.
-i It has been replaced by a ggproto system that can be extended.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
 
@@
 \begin{verbatim}
-2024-02-29 16:10:43.9 athan@tyler GHI_enh_04_investigate.R 1.399842 mins
+2024-03-01 16:24:25.3 athan@tyler GHI_enh_04_investigate.R 1.012841 mins
 \end{verbatim}

### 2024-03-01 GHI_enh_00_dictionary.R
Commit 2024-03-01 19:14

@@ -77,6 +77,7 @@ staname <- function(avar) {
            min    = "minimum",
            max    = "maximun",
            median = "median",
+           meαn   = "mean",
            sumPOS = "total of positives",
            sumNEG = "total of negatives",
            N_pos  = "number of positive cases",

### 2024-03-01 GHI_enh_03_process.tex
Commit 2024-03-01 20:13

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-02-28}
+\date{2024-03-01}
 
@@
 \begin{Highlighting}[]
-\CommentTok{\#  Save from environment  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
+\CommentTok{\#  Save environment  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
+
 \DocumentationTok{\#\# Variables}
@@
 \NormalTok{)}
-
+\DocumentationTok{\#\# list saved}
 \FunctionTok{cat}\NormalTok{(objects, }\AttributeTok{sep =} \StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{)}
@@
 R_COMPILE_PKGS
+RANDOM_SEED
 raw_input_data
@@
 \begin{Highlighting}[]
+\DocumentationTok{\#\# Save}
 \FunctionTok{save}\NormalTok{(}\AttributeTok{file =} \FunctionTok{paste0}\NormalTok{(}\StringTok{"./data/"}\NormalTok{, }\FunctionTok{basename}\NormalTok{(}\FunctionTok{sub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{.R"}\NormalTok{, }\StringTok{".Rda"}\NormalTok{, Script.Name))),}
@@
 \begin{verbatim}
-2024-02-28 13:08:22.6 athan@sagan GHI_enh_03_process.R 1.133646 mins
+2024-03-01 17:32:55.6 athan@tyler GHI_enh_03_process.R 2.076944 mins
 \end{verbatim}

### 2024-03-01 GHI_enh_04_investigate.tex
Commit 2024-03-01 21:11

@@
 
-lmD: 1.566022 +/- 0.1083205
+Units for GLB\_diff.max : / Watt m\^{}2lmD: 1.566022 +/- 0.1083205
 
@@
 
-lmD: 0.9508227 +/- 0.1552488
+Units for GLB\_diff.mean : / Watt m\^{}2lmD: 0.9508227 +/- 0.1552488
 
@@
 
-lmD: 1.087008 +/- 0.1678713
+Units for GLB\_diff.median : / Watt m\^{}2lmD: 1.087008 +/- 0.1678713
 
@@
 
-lmD: -0.01234536 +/- 0.1388793
+Units for GLB\_diff.N : lmD: -0.01234536 +/- 0.1388793
 
@@
 
-lmD: 561.0124 +/- 94.87888
+Units for GLB\_diff.sum : / J m\^{}2lmD: 33660.74 +/- 5692.733
 
-lmY: 561.0217 +/- 94.88053
+lmY: 33661.3 +/- 5692.832
 
-Arima: 562.031 148.2404 3.7913 1e-04
+Arima: 33699.7541 8650.717 3.8956 1e-04
 
@@
 
-lmD: 0.003266094 +/- 0.0002706818
+Units for GLB\_ench.max : / Watt m\^{}2lmD: 0.003266094 +/- 0.0002706818
 
@@
 
-lmD: 0.001714795 +/- 0.0002777698
+Units for GLB\_ench.mean : / Watt m\^{}2lmD: 0.001714795 +/- 0.0002777698
 
@@
 
-lmD: 0.001677055 +/- 0.00031363
+Units for GLB\_ench.median : / Watt m\^{}2lmD: 0.001677055 +/- 0.00031363
 
@@
 
-lmD: -0.01234536 +/- 0.1388793
+Units for GLB\_ench.N : lmD: -0.01234536 +/- 0.1388793
 
@@
 
-lmD: 0.9770213 +/- 0.1439346
+Units for GLB\_ench.sum : / Watt m\^{}2lmD: 0.9770213 +/- 0.1439346
 
@@
 
-lmD: 0.8175146 +/- 0.1034317
+Units for GLB\_diff.max : / Watt m\^{}2lmD: 0.8175146 +/- 0.1034317
 
@@
 
-lmD: 0.2160878 +/- 0.03807227
+Units for GLB\_diff.mean : / Watt m\^{}2lmD: 0.2160878 +/- 0.03807227
 
@@
 
-lmD: 0.1909484 +/- 0.03787569
+Units for GLB\_diff.median : / Watt m\^{}2lmD: 0.1909484 +/- 0.03787569
 
@@
 
-lmD: 0.4856759 +/- 0.04638817
+Units for GLB\_diff.N : lmD: 0.4856759 +/- 0.04638817
 
@@
 
-lmD: 24.46426 +/- 2.544261
+Units for GLB\_diff.sum : / J m\^{}2lmD: 1467.856 +/- 152.6556
 
-lmY: 24.46465 +/- 2.544306
+lmY: 1467.879 +/- 152.6584
 
-Arima: 24.4646 3.0718 7.9642 0
+Arima: 1467.8755 184.369 7.9616 0
 
@@
 
-lmD: 0.001335923 +/- 0.0001367163
+Units for GLB\_ench.max : / Watt m\^{}2lmD: 0.001335923 +/- 0.0001367163
 
@@
 
-lmD: 0.000422753 +/- 5.903214e-05
+Units for GLB\_ench.mean : / Watt m\^{}2lmD: 0.000422753 +/- 5.903214e-05
 
@@
 
-lmD: 0.000372438 +/- 6.132797e-05
+Units for GLB\_ench.median : / Watt m\^{}2lmD: 0.000372438 +/- 6.132797e-05
 
@@
 
-lmD: 0.4856759 +/- 0.04638817
+Units for GLB\_ench.N : lmD: 0.4856759 +/- 0.04638817
 
@@
 
-lmD: 0.03656094 +/- 0.003621568
+Units for GLB\_ench.sum : / Watt m\^{}2lmD: 0.03656094 +/- 0.003621568
 
@@
 
-lmD: 0.1872432 +/- 0.2494753
+Units for GLB\_diff.max : / Watt m\^{}2lmD: 0.1872432 +/- 0.2494753
 
@@
 
-lmD: 0.0498083 +/- 0.192504
+Units for GLB\_diff.mean : / Watt m\^{}2lmD: 0.0498083 +/- 0.192504
 
@@
 
-lmD: 0.0912832 +/- 0.1914519
+Units for GLB\_diff.median : / Watt m\^{}2lmD: 0.0912832 +/- 0.1914519
 
@@
 
-lmD: 0.03034705 +/- 0.02124537
+Units for GLB\_diff.N : lmD: 0.03034705 +/- 0.02124537
 
@@
 
-lmD: 6.13936 +/- 4.224962
+Units for GLB\_diff.sum : / J m\^{}2lmD: 368.3616 +/- 253.4977
 
-lmY: 6.139801 +/- 4.22503
+lmY: 368.3881 +/- 253.5018
 
-Arima: 6.1407 4.3045 1.4266 0.1537
+Arima: 368.4448 258.2729 1.4266 0.1537
 
@@
 
-lmD: 0.0005085756 +/- 0.0002811408
+Units for GLB\_ench.max : / Watt m\^{}2lmD: 0.0005085756 +/- 0.0002811408
 
@@
 
-lmD: 0.0003565528 +/- 0.0002141263
+Units for GLB\_ench.mean : / Watt m\^{}2lmD: 0.0003565528 +/- 0.0002141263
 
@@
 
-lmD: 0.000398809 +/- 0.0002210804
+Units for GLB\_ench.median : / Watt m\^{}2lmD: 0.000398809 +/- 0.0002210804
 
@@
 
-lmD: 0.03034705 +/- 0.02124537
+Units for GLB\_ench.N : lmD: 0.03034705 +/- 0.02124537
 
@@
 
-lmD: 0.008776506 +/- 0.00550671
+Units for GLB\_ench.sum : / Watt m\^{}2lmD: 0.008776506 +/- 0.00550671
 
@@
 \begin{verbatim}
-2024-03-01 16:24:25.3 athan@tyler GHI_enh_04_investigate.R 1.012841 mins
+2024-03-01 18:32:55.2 athan@tyler GHI_enh_04_investigate.R 1.018020 mins
 \end{verbatim}

### 2024-03-02 GHI_enh_04_investigate.tex
Commit 2024-03-02 11:17

--- 2024-03-01 GHI_enh_04_investigate.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-01}
+\date{2024-03-02}
 
@@
 
-lmD: 1.566022 +/- 0.1083205
+Units for GLB\_diff.max : Watt/m\^{}2lmD: 1.566022 +/- 0.1083205
 
@@
 
-lmD: 0.9508227 +/- 0.1552488
+Units for GLB\_diff.mean : Watt/m\^{}2lmD: 0.9508227 +/- 0.1552488
 
@@
 
-lmD: 1.087008 +/- 0.1678713
+Units for GLB\_diff.median : Watt/m\^{}2lmD: 1.087008 +/- 0.1678713
 
@@
 
-lmD: 561.0124 +/- 94.87888
+Units for GLB\_diff.sum : J/m\^{}2lmD: 33660.74 +/- 5692.733
 
-lmY: 561.0217 +/- 94.88053
+lmY: 33661.3 +/- 5692.832
 
-Arima: 562.031 148.2404 3.7913 1e-04
+Arima: 33699.7541 8650.717 3.8956 1e-04
 
@@
 
-lmD: 0.003266094 +/- 0.0002706818
+Units for GLB\_ench.max : Watt/m\^{}2lmD: 0.003266094 +/- 0.0002706818
 
@@
 
-lmD: 0.001714795 +/- 0.0002777698
+Units for GLB\_ench.mean : Watt/m\^{}2lmD: 0.001714795 +/- 0.0002777698
 
@@
 
-lmD: 0.001677055 +/- 0.00031363
+Units for GLB\_ench.median : Watt/m\^{}2lmD: 0.001677055 +/- 0.00031363
 
@@
 
-lmD: 0.9770213 +/- 0.1439346
+Units for GLB\_ench.sum : Watt/m\^{}2lmD: 0.9770213 +/- 0.1439346
 
@@
 
-lmD: 0.8175146 +/- 0.1034317
+Units for GLB\_diff.max : Watt/m\^{}2lmD: 0.8175146 +/- 0.1034317
 
@@
 
-lmD: 0.2160878 +/- 0.03807227
+Units for GLB\_diff.mean : Watt/m\^{}2lmD: 0.2160878 +/- 0.03807227
 
@@
 
-lmD: 0.1909484 +/- 0.03787569
+Units for GLB\_diff.median : Watt/m\^{}2lmD: 0.1909484 +/- 0.03787569
 
@@
 
-lmD: 24.46426 +/- 2.544261
+Units for GLB\_diff.sum : J/m\^{}2lmD: 1467.856 +/- 152.6556
 
-lmY: 24.46465 +/- 2.544306
+lmY: 1467.879 +/- 152.6584
 
-Arima: 24.4646 3.0718 7.9642 0
+Arima: 1467.8755 184.369 7.9616 0
 
@@
 
-lmD: 0.001335923 +/- 0.0001367163
+Units for GLB\_ench.max : Watt/m\^{}2lmD: 0.001335923 +/- 0.0001367163
 
@@
 
-lmD: 0.000422753 +/- 5.903214e-05
+Units for GLB\_ench.mean : Watt/m\^{}2lmD: 0.000422753 +/- 5.903214e-05
 
@@
 
-lmD: 0.000372438 +/- 6.132797e-05
+Units for GLB\_ench.median : Watt/m\^{}2lmD: 0.000372438 +/- 6.132797e-05
 
@@
 
-lmD: 0.03656094 +/- 0.003621568
+Units for GLB\_ench.sum : Watt/m\^{}2lmD: 0.03656094 +/- 0.003621568
 
@@
 
-lmD: 0.1872432 +/- 0.2494753
+Units for GLB\_diff.max : Watt/m\^{}2lmD: 0.1872432 +/- 0.2494753
 
@@
 
-lmD: 0.0498083 +/- 0.192504
+Units for GLB\_diff.mean : Watt/m\^{}2lmD: 0.0498083 +/- 0.192504
 
@@
 
-lmD: 0.0912832 +/- 0.1914519
+Units for GLB\_diff.median : Watt/m\^{}2lmD: 0.0912832 +/- 0.1914519
 
@@
 
-lmD: 6.13936 +/- 4.224962
+Units for GLB\_diff.sum : J/m\^{}2lmD: 368.3616 +/- 253.4977
 
-lmY: 6.139801 +/- 4.22503
+lmY: 368.3881 +/- 253.5018
 
-Arima: 6.1407 4.3045 1.4266 0.1537
+Arima: 368.4448 258.2729 1.4266 0.1537
 
@@
 
-lmD: 0.0005085756 +/- 0.0002811408
+Units for GLB\_ench.max : Watt/m\^{}2lmD: 0.0005085756 +/- 0.0002811408
 
@@
 
-lmD: 0.0003565528 +/- 0.0002141263
+Units for GLB\_ench.mean : Watt/m\^{}2lmD: 0.0003565528 +/- 0.0002141263
 
@@
 
-lmD: 0.000398809 +/- 0.0002210804
+Units for GLB\_ench.median : Watt/m\^{}2lmD: 0.000398809 +/- 0.0002210804
 
@@
 
-lmD: 0.008776506 +/- 0.00550671
+Units for GLB\_ench.sum : Watt/m\^{}2lmD: 0.008776506 +/- 0.00550671
 
@@
 \begin{verbatim}
-Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2
-3.5.0.
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
 i Please use the `legend.position.inside` argument of `theme()` instead.
 This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
-generated.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
 \end{verbatim}
@@
 This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
-generated.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
 \end{verbatim}
@@
 \begin{verbatim}
-2024-03-01 16:24:25.3 athan@tyler GHI_enh_04_investigate.R 1.012841 mins
+2024-03-02 09:11:28.2 athan@tyler GHI_enh_04_investigate.R 1.451215 mins
 \end{verbatim}

### 2024-03-02 GHI_enh_03_process.tex
Commit 2024-03-02 12:11

@@
 Days_of_year
+Energy_Div
 I1_longterm
@@
 \begin{verbatim}
-2024-03-01 17:32:55.6 athan@tyler GHI_enh_03_process.R 2.076944 mins
+2024-03-02 09:45:10.6 athan@tyler GHI_enh_03_process.R 2.001386 mins
 \end{verbatim}

### 2024-03-02 GHI_enh_04_investigate.tex
Commit 2024-03-02 12:11

@@
 
-Units for GLB\_diff.sum : J/m\^{}2lmD: 33660.74 +/- 5692.733
+Units for GLB\_diff.sum : kJ/m\^{}2lmD: 33.66074 +/- 5.692733
 
-lmY: 33661.3 +/- 5692.832
+lmY: 33.6613 +/- 5.692832
 
-Arima: 33699.7541 8650.717 3.8956 1e-04
+Arima: 33.7219 8.8826 3.7964 1e-04
 
@@
 
-Units for GLB\_diff.sum : J/m\^{}2lmD: 1467.856 +/- 152.6556
+Units for GLB\_diff.sum : kJ/m\^{}2lmD: 1467.856 +/- 152.6556
 
@@
 
-Units for GLB\_diff.sum : J/m\^{}2lmD: 368.3616 +/- 253.4977
+Units for GLB\_diff.sum : kJ/m\^{}2lmD: 0.3683616 +/- 0.2534977
 
-lmY: 368.3881 +/- 253.5018
+lmY: 0.3683881 +/- 0.2535018
 
-Arima: 368.4448 258.2729 1.4266 0.1537
+Arima: 0.3684 0.2583 1.4266 0.1537
 
@@
 \begin{verbatim}
-2024-03-02 09:11:28.2 athan@tyler GHI_enh_04_investigate.R 1.451215 mins
+2024-03-02 09:46:24.0 athan@tyler GHI_enh_04_investigate.R 0.976988 mins
 \end{verbatim}

### 2024-03-02 GHI_enh_03_process.R

@@ -135,6 +135,7 @@ alpha <- 0.9653023236718680788471
 ## __ Enhancement criteria  ------------------------------------------------
 SelEnhanc <- unique(DATA[, CEC])[1]
 
+Energy_Div <- 1000
 
 ##;  #
 ##;  # Note from editor
@@ -236,9 +237,9 @@ ST_daily[, yts := (year(Date) - min(year(Date))) + ( yday(Date) - 1 ) / Hmisc::y
 
 ## convert sum Irradiance to energy
 ## Σ(W/m^2) * 60 s = J/m^2
-ST_daily[, GLB_diff.sum    := GLB_diff.sum    * 60 ]
-ST_daily[, GLB_diff.sumPOS := GLB_diff.sumPOS * 60 ]
-ST_daily[, GLB_diff.sumNEG := GLB_diff.sumNEG * 60 ]
+ST_daily[, GLB_diff.sum    := GLB_diff.sum    * 60 / Energy_Div]
+ST_daily[, GLB_diff.sumPOS := GLB_diff.sumPOS * 60 / Energy_Div]
+ST_daily[, GLB_diff.sumNEG := GLB_diff.sumNEG * 60 / Energy_Div]
 
 
 ## stats on extreme enhancement cases
@@ -251,9 +252,9 @@ ST_extreme_daily[, yts := (year(Date) - min(year(Date))) + ( yday(Date) - 1 ) / 
 
 ## convert sum Irradiance to energy
 ## Σ(W/m^2) * 60 s = J/m^2
-ST_extreme_daily[, GLB_diff.sum    := GLB_diff.sum    * 60]
-ST_extreme_daily[, GLB_diff.sumPOS := GLB_diff.sumPOS * 60]
-ST_extreme_daily[, GLB_diff.sumNEG := GLB_diff.sumNEG * 60]
+ST_extreme_daily[, GLB_diff.sum    := GLB_diff.sum    * 60 / Energy_Div]
+ST_extreme_daily[, GLB_diff.sumPOS := GLB_diff.sumPOS * 60 / Energy_Div]
+ST_extreme_daily[, GLB_diff.sumNEG := GLB_diff.sumNEG * 60 / Energy_Div]
 
 
 
@@ -282,7 +283,7 @@ ST_E_daily_seas[, yts := DOY ] ## just for convenient of programming
 
[…]

### 2024-03-02 GHI_enh_04_investigate.tex
Commit 2024-03-02 15:11

@@
 
-Units for GLB\_diff.max : Watt/m\^{}2lmD: 1.566022 +/- 0.1083205
+Units for GLB\_diff.max : Watt/m\^{}2
+
+lmD: 1.566022 +/- 0.1083205
 
@@
 
-Units for GLB\_diff.mean : Watt/m\^{}2lmD: 0.9508227 +/- 0.1552488
+Units for GLB\_diff.mean : Watt/m\^{}2
+
+lmD: 0.9508227 +/- 0.1552488
 
@@
 
-Units for GLB\_diff.median : Watt/m\^{}2lmD: 1.087008 +/- 0.1678713
+Units for GLB\_diff.median : Watt/m\^{}2
+
+lmD: 1.087008 +/- 0.1678713
 
@@
 
-Units for GLB\_diff.N : lmD: -0.01234536 +/- 0.1388793
+Units for GLB\_diff.N :
+
+lmD: -0.01234536 +/- 0.1388793
 
@@
 
-Units for GLB\_diff.sum : kJ/m\^{}2lmD: 33.66074 +/- 5.692733
+Units for GLB\_diff.sum : kJ/m\^{}2
+
+lmD: 33.66074 +/- 5.692733
 
@@
 
-Units for GLB\_ench.max : Watt/m\^{}2lmD: 0.003266094 +/- 0.0002706818
+Units for GLB\_ench.max : Watt/m\^{}2
+
+lmD: 0.003266094 +/- 0.0002706818
 
@@
 
-Units for GLB\_ench.mean : Watt/m\^{}2lmD: 0.001714795 +/- 0.0002777698
+Units for GLB\_ench.mean : Watt/m\^{}2
+
+lmD: 0.001714795 +/- 0.0002777698
 
@@
 
-Units for GLB\_ench.median : Watt/m\^{}2lmD: 0.001677055 +/- 0.00031363
+Units for GLB\_ench.median : Watt/m\^{}2
+
+lmD: 0.001677055 +/- 0.00031363
 
@@
 
-Units for GLB\_ench.N : lmD: -0.01234536 +/- 0.1388793
+Units for GLB\_ench.N :
+
+lmD: -0.01234536 +/- 0.1388793
 
@@
 
-Units for GLB\_ench.sum : Watt/m\^{}2lmD: 0.9770213 +/- 0.1439346
+Units for GLB\_ench.sum : Watt/m\^{}2
+
+lmD: 0.9770213 +/- 0.1439346
 
@@
 
-Units for GLB\_diff.max : Watt/m\^{}2lmD: 0.8175146 +/- 0.1034317
+Units for GLB\_diff.max : Watt/m\^{}2
+
+lmD: 0.8175146 +/- 0.1034317
 
@@
 
-Units for GLB\_diff.mean : Watt/m\^{}2lmD: 0.2160878 +/- 0.03807227
+Units for GLB\_diff.mean : Watt/m\^{}2
+
+lmD: 0.2160878 +/- 0.03807227
 
@@
 
-Units for GLB\_diff.median : Watt/m\^{}2lmD: 0.1909484 +/- 0.03787569
+Units for GLB\_diff.median : Watt/m\^{}2
+
+lmD: 0.1909484 +/- 0.03787569
 
@@
 
-Units for GLB\_diff.N : lmD: 0.4856759 +/- 0.04638817
+Units for GLB\_diff.N :
+
+lmD: 0.4856759 +/- 0.04638817
 
@@
 
-Units for GLB\_diff.sum : kJ/m\^{}2lmD: 1467.856 +/- 152.6556
+Units for GLB\_diff.sum : kJ/m\^{}2
+
+lmD: 1467.856 +/- 152.6556
 
@@
 
-Units for GLB\_ench.max : Watt/m\^{}2lmD: 0.001335923 +/- 0.0001367163
+Units for GLB\_ench.max : Watt/m\^{}2
+
+lmD: 0.001335923 +/- 0.0001367163
 
@@
 
-Units for GLB\_ench.mean : Watt/m\^{}2lmD: 0.000422753 +/- 5.903214e-05
+Units for GLB\_ench.mean : Watt/m\^{}2
+
+lmD: 0.000422753 +/- 5.903214e-05
 
@@
 
-Units for GLB\_ench.median : Watt/m\^{}2lmD: 0.000372438 +/- 6.132797e-05
+Units for GLB\_ench.median : Watt/m\^{}2
+
+lmD: 0.000372438 +/- 6.132797e-05
 
@@
 
-Units for GLB\_ench.N : lmD: 0.4856759 +/- 0.04638817
+Units for GLB\_ench.N :
+
+lmD: 0.4856759 +/- 0.04638817
 
@@
 
-Units for GLB\_ench.sum : Watt/m\^{}2lmD: 0.03656094 +/- 0.003621568
+Units for GLB\_ench.sum : Watt/m\^{}2
+
+lmD: 0.03656094 +/- 0.003621568
 
@@
 
-Units for GLB\_diff.max : Watt/m\^{}2lmD: 0.1872432 +/- 0.2494753
+Units for GLB\_diff.max : Watt/m\^{}2
+
+lmD: 0.1872432 +/- 0.2494753
 
@@
 
-Units for GLB\_diff.mean : Watt/m\^{}2lmD: 0.0498083 +/- 0.192504
+Units for GLB\_diff.mean : Watt/m\^{}2
+
+lmD: 0.0498083 +/- 0.192504
 
@@
 
-Units for GLB\_diff.median : Watt/m\^{}2lmD: 0.0912832 +/- 0.1914519
+Units for GLB\_diff.median : Watt/m\^{}2
+
+lmD: 0.0912832 +/- 0.1914519
 
@@
 
-Units for GLB\_diff.N : lmD: 0.03034705 +/- 0.02124537
+Units for GLB\_diff.N :
+
+lmD: 0.03034705 +/- 0.02124537
 
@@
 
-Units for GLB\_diff.sum : kJ/m\^{}2lmD: 0.3683616 +/- 0.2534977
+Units for GLB\_diff.sum : kJ/m\^{}2
+
+lmD: 0.3683616 +/- 0.2534977
 
@@
 
-Units for GLB\_ench.max : Watt/m\^{}2lmD: 0.0005085756 +/- 0.0002811408
+Units for GLB\_ench.max : Watt/m\^{}2
+
+lmD: 0.0005085756 +/- 0.0002811408
 
@@
 
-Units for GLB\_ench.mean : Watt/m\^{}2lmD: 0.0003565528 +/- 0.0002141263
+Units for GLB\_ench.mean : Watt/m\^{}2
+
+lmD: 0.0003565528 +/- 0.0002141263
 
@@
 
-Units for GLB\_ench.median : Watt/m\^{}2lmD: 0.000398809 +/- 0.0002210804
+Units for GLB\_ench.median : Watt/m\^{}2
+
+lmD: 0.000398809 +/- 0.0002210804
 
@@
 
-Units for GLB\_ench.N : lmD: 0.03034705 +/- 0.02124537
+Units for GLB\_ench.N :
+
+lmD: 0.03034705 +/- 0.02124537
 
@@
 
-Units for GLB\_ench.sum : Watt/m\^{}2lmD: 0.008776506 +/- 0.00550671
+Units for GLB\_ench.sum : Watt/m\^{}2
+
+lmD: 0.008776506 +/- 0.00550671
 
@@
 \begin{verbatim}
-Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2
+3.5.0.
 i Please use the `legend.position.inside` argument of `theme()` instead.
 This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
+generated.
 \end{verbatim}
@@
 This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
+generated.
 \end{verbatim}
@@
 \begin{verbatim}
-2024-03-02 09:46:24.0 athan@tyler GHI_enh_04_investigate.R 0.976988 mins
+2024-03-02 12:29:58.0 athan@tyler GHI_enh_04_investigate.R 1.354976 mins
 \end{verbatim}

### 2024-03-05 article/article.Rmd
Commit 2024-03-05 11:13

@@
 
-criteria for cloud enhancement identification are set acording the Equation \ref{eq:CE4}
+criteria for cloud enhancement identification are set according the Equation \ref{eq:CE4}
 
@@
 
-A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane Equation \ref{eq:ECE}
+A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})
 
@@
 
+Sky Camera for some cases
+
 Objectivity
 
-Describe set of referce days we used to evalutate
+Describe set of reference days we used to evaluate
 

### 2024-03-05 article/article.Rmd
Commit 2024-03-05 12:14

@@
 
-We used as reference a modelled clear sky approximation,
+We used as reference a modeled clear sky approximation,
 
@@
 
-A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})
+A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane Equation \ref{eq:ECE}
 

### 2024-03-05 GHI_enh_04_investigate.tex
Commit 2024-03-05 11:13
Commit 2024-03-05 12:14
Commit 2024-03-05 13:12

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-02}
+\date{2024-03-05}
 
@@
 
-lmD: 1.566022 +/- 0.1083205
+lmD: 1.566006 +/- 0.1083205
 
-lmY: 1.566038 +/- 0.1083224
+lmY: 1.566022 +/- 0.1083224
 
-Arima: 1.5664 0.1467 10.6787 0
+Arima: 1.5664 0.1467 10.6786 0
 
@@
 
-lmD: 0.9508227 +/- 0.1552488
+lmD: 0.9508037 +/- 0.1552487
 
-lmY: 0.9508465 +/- 0.1552515
+lmY: 0.9508275 +/- 0.1552514
 
-Arima: 1.0223 0.2369 4.315 0
+Arima: 1.0223 0.2369 4.3149 0
 
@@
 
-lmD: 1.087008 +/- 0.1678713
+lmD: 1.086985 +/- 0.1678711
 
-lmY: 1.087035 +/- 0.1678742
+lmY: 1.087013 +/- 0.1678741
 
-Arima: 1.16 0.2511 4.6199 0
+Arima: 1.16 0.2511 4.6198 0
 
@@
 
-lmD: 33.66074 +/- 5.692733
+lmD: 33.66024 +/- 5.69273
 
-lmY: 33.6613 +/- 5.692832
+lmY: 33.6608 +/- 5.692829
 
-Arima: 33.7219 8.8826 3.7964 1e-04
+Arima: 33.7214 8.8815 3.7968 1e-04
 
@@
 
-lmD: 0.003266094 +/- 0.0002706818
+lmD: 0.003266044 +/- 0.0002706817
 
-lmY: 0.003266127 +/- 0.0002706866
+lmY: 0.003266077 +/- 0.0002706865
 
-Arima: 0.0033 4e-04 9.0498 0
+Arima: 0.0033 4e-04 9.0497 0
 
@@
 
-lmD: 0.001714795 +/- 0.0002777698
+lmD: 0.001714761 +/- 0.0002777697
 
-lmY: 0.001714851 +/- 0.0002777746
+lmY: 0.001714817 +/- 0.0002777745
 
@@
 
-lmD: 0.001677055 +/- 0.00031363
+lmD: 0.001677019 +/- 0.0003136298
 
-lmY: 0.001677118 +/- 0.0003136354
+lmY: 0.001677082 +/- 0.0003136353
 
-Arima: 0.0018 5e-04 3.6151 3e-04
+Arima: 0.0018 5e-04 3.615 3e-04
 
@@
 
-lmD: 0.9770213 +/- 0.1439346
+lmD: 0.9770065 +/- 0.1439346
 
-lmY: 0.9770437 +/- 0.1439371
+lmY: 0.9770288 +/- 0.1439371
 
-Arima: 1.041 0.2186 4.7612 0
+Arima: 1.041 0.2186 4.7611 0
 
@@
 
-lmD: 0.8175146 +/- 0.1034317
+lmD: 0.8175029 +/- 0.1034317
 
-lmY: 0.8175255 +/- 0.1034336
+lmY: 0.8175138 +/- 0.1034336
 
-Arima: 0.8175 0.12 6.8104 0
+Arima: 0.8175 0.12 6.8102 0
 
@@
 
-lmD: 0.2160878 +/- 0.03807227
+lmD: 0.216071 +/- 0.03807207
 
-lmY: 0.2160919 +/- 0.03807295
+lmY: 0.2160751 +/- 0.03807275
 
-Arima: 0.2161 0.0414 5.2173 0
+Arima: 0.2161 0.0414 5.2169 0
 
@@
 
-lmD: 0.1909484 +/- 0.03787569
+lmD: 0.190931 +/- 0.03787542
 
-lmY: 0.190953 +/- 0.03787636
+lmY: 0.1909357 +/- 0.03787609
 
-Arima: 0.191 0.0401 4.7635 0
+Arima: 0.1909 0.0401 4.7631 0
 
@@
 
-lmD: 1467.856 +/- 152.6556
+lmD: 1467.857 +/- 152.6559
 
-lmY: 1467.879 +/- 152.6584
+lmY: 1467.88 +/- 152.6586
 
-Arima: 1467.8755 184.369 7.9616 0
+Arima: 1467.8769 184.2435 7.967 0
 
@@
 
-lmD: 0.001335923 +/- 0.0001367163
+lmD: 0.00133588 +/- 0.0001367161
 
-lmY: 0.001335939 +/- 0.0001367188
+lmY: 0.001335895 +/- 0.0001367186
 
-Arima: 0.0013 2e-04 8.5092 0
+Arima: 0.0013 2e-04 8.5089 0
 
@@
 
-lmD: 0.000422753 +/- 5.903214e-05
+lmD: 0.0004227125 +/- 5.903165e-05
 
-lmY: 0.0004227591 +/- 5.903319e-05
+lmY: 0.0004227187 +/- 5.90327e-05
 
-Arima: 4e-04 1e-04 6.291 0
+Arima: 4e-04 1e-04 6.2905 0
 
@@
 
-lmD: 0.000372438 +/- 6.132797e-05
+lmD: 0.0003723972 +/- 6.132751e-05
 
-lmY: 0.0003724446 +/- 6.132906e-05
+lmY: 0.0003724038 +/- 6.13286e-05
 
-Arima: 4e-04 1e-04 5.4467 0
+Arima: 4e-04 1e-04 5.4462 0
 
@@
 
-lmD: 0.03656094 +/- 0.003621568
+lmD: 0.03656091 +/- 0.003621574
 
-lmY: 0.03656157 +/- 0.003621632
+lmY: 0.03656153 +/- 0.003621638
 
@@
 
-lmD: 0.1872432 +/- 0.2494753
+lmD: 0.1872084 +/- 0.2494764
 
-lmY: 0.1872803 +/- 0.2494792
+lmY: 0.1872455 +/- 0.2494804
 
-Arima: 0.1718 0.3646 0.4712 0.6375
+Arima: 0.1718 0.3646 0.4711 0.6376
 
@@
 
-lmD: 0.0498083 +/- 0.192504
+lmD: 0.04977389 +/- 0.1925048
 
-lmY: 0.04983275 +/- 0.1925071
+lmY: 0.04979834 +/- 0.1925079
 
-Arima: 0.0086 0.3464 0.0248 0.9802
+Arima: 0.0085 0.3464 0.0247 0.9803
 
@@
 
-lmD: 0.0912832 +/- 0.1914519
+lmD: 0.0912485 +/- 0.1914527
 
-lmY: 0.09130632 +/- 0.191455
+lmY: 0.09127162 +/- 0.1914558
 
-Arima: 0.05 0.3354 0.1491 0.8815
+Arima: 0.05 0.3354 0.149 0.8816
 
@@
 
-lmD: 0.3683616 +/- 0.2534977
+lmD: 0.368357 +/- 0.2534977
 
-lmY: 0.3683881 +/- 0.2535018
+lmY: 0.3683834 +/- 0.2535018
 
@@
 
-lmD: 0.0005085756 +/- 0.0002811408
+lmD: 0.0005084984 +/- 0.0002811406
 
-lmY: 0.0005085833 +/- 0.0002811453
+lmY: 0.0005085061 +/- 0.0002811451
 
-Arima: 5e-04 3e-04 1.598 0.11
+Arima: 5e-04 3e-04 1.5978 0.1101
 
@@
 
-lmD: 0.0003565528 +/- 0.0002141263
+lmD: 0.000356478 +/- 0.0002141255
 
-lmY: 0.0003565519 +/- 0.0002141297
+lmY: 0.0003564771 +/- 0.0002141289
 
-Arima: 3e-04 3e-04 1.3206 0.1866
+Arima: 3e-04 3e-04 1.3203 0.1867
 
@@
 
-lmD: 0.000398809 +/- 0.0002210804
+lmD: 0.0003987357 +/- 0.0002210796
 
-lmY: 0.0003988093 +/- 0.0002210839
+lmY: 0.0003987361 +/- 0.0002210831
 
-Arima: 4e-04 3e-04 1.4507 0.1469
+Arima: 4e-04 3e-04 1.4505 0.1469
 
@@
 
-lmD: 0.008776506 +/- 0.00550671
+lmD: 0.008776338 +/- 0.005506711
 
-lmY: 0.008777009 +/- 0.005506798
+lmY: 0.00877684 +/- 0.005506799
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_N_doy-1} \end{center}
 
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCE_daily-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCE_week-1} \end{center}
 
@@
 \begin{verbatim}
-2024-03-02 12:29:58.0 athan@tyler GHI_enh_04_investigate.R 1.354976 mins
+2024-03-05 09:51:07.3 athan@tyler GHI_enh_04_investigate.R 1.319722 mins
 \end{verbatim}

### 2024-03-05 article/article.Rmd
Commit 2024-03-05 13:12

--- 2024-03-05 article/article.Rmd
@@
 
+## New plots for discusion
+
+### Climatology
+
+```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per week"}
+knitr::include_graphics("../images/climCE_week-1.png")
+```
+
+```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per doy"}
+knitr::include_graphics("../images/climCE_daily-1.png")
+```
+
+```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per doy"}
+knitr::include_graphics("../images/clim_CE_N_doy-1.png")
+```
+
+\FloatBarrier
+
 # Discussion and conclusions

### 2024-03-05 GHI_enh_05_distributions.R
Commit 2024-03-05 13:12

@@ -172,28 +172,69 @@ hist(DATA[GLB_diff > 0, GLB_rati],
 #      xlab   = varname("GLB_ench"),
 #      main   = varname("GLB_ench"))
 
-hist(DATA[GLB_diff > 0, GLB_ench],
+h <- hist(DATA[GLB_diff > 0, GLB_ench],
      breaks = breaks,
      freq   = FALSE,
      col    = varcol( "GLB_ench"),
      xlab   = varname("GLB_ench"),
+     main   = varname("GLB_ench"),
+     plot = FALSE)
+
+h$density = h$counts/sum(h$counts)*100
+plot(h,
+     freq   = FALSE,
+     col    = varcol( "GLB_ench"),
+     xlab   = varname("GLB_ench"),
+     ylab   = "Density in %",
      main   = varname("GLB_ench"))
 
 
-hist(DATA[GLB_diff > 0, GLB_diff],
+
+
+
+
+h <- hist(DATA[GLB_diff > 0, GLB_diff],
      breaks = breaks,
      freq   = FALSE,
      col    = varcol("GLB_diff"),
      xlab   = bquote(.(varname("GLB_diff")) ~ group("[", W/m^2,"]")),
-     main   = bquote(.(varname("GLB_diff")) ~ group("[", W/m^2,"]")))
+     main   = bquote(.(varname("GLB_diff")) ~ group("[", W/m^2,"]")),
+     plot = FALSE)
+
+h$density = h$counts/sum(h$counts)*100
+plot(h,
+     freq   = FALSE,
+     col    = varcol("GLB_diff"),
+     xlab   = bquote(.(varname("GLB_diff")) ~ group("[", W/m^2,"]")),
+     ylab   = "Density in %",
+     main   = bquote(.(varname("GLB_diff")) ~ group("[", W/m^2,"]")),
+     )
 
 
-hist(DATA[GLB_diff > 0, GLB_rati],
+
+
+
+h <- hist(DATA[GLB_diff > 0, GLB_rati],
      breaks = breaks,
      freq   = FALSE,
      col    = varcol( "GLB_rati"),
      xlab   = varname("GLB_rati"),
-     main   = varname("GLB_rati"))
+     main   = varname("GLB_rati"),
+     plot = FALSE)
+
+h$density = h$counts/sum(h$counts)*100
+
+plot(h,
+     freq   = FALSE,
+     col    = varcol( "GLB_rati"),
[…]

### 2024-03-05 article/article.Rmd
Commit 2024-03-05 18:24

@@
 
+<!-- ```{r echo=FALSE, fig.cap="Distribution of CE above reference"} -->
+<!-- knitr::include_graphics("../images/relative_distributions-2.png") -->
+<!-- ``` -->
+
 ```{r echo=FALSE, fig.cap="Distribution of CE above reference"}
-knitr::include_graphics("../images/distributions-5.png")
+knitr::include_graphics("../images/relative_distributions-4.png")
 ```

### 2024-03-05 GHI_enh_04_investigate.tex
Commit 2024-03-05 19:12

@@
 
+\begin{verbatim}
+Warning: The dot-dot notation (`..count..`) was deprecated in ggplot2 3.4.0.
+i Please use `after_stat(count)` instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-1} \end{center}
@@
 \begin{verbatim}
-2024-03-05 09:51:07.3 athan@tyler GHI_enh_04_investigate.R 1.319722 mins
+2024-03-05 16:54:52.8 athan@tyler GHI_enh_04_investigate.R 1.097087 mins
 \end{verbatim}

### 2024-03-05 GHI_enh_04_investigate.R
Commit 2024-03-05 19:12

@@ -330,21 +330,34 @@ write.csv(x = dailytrendsY,
 #+ groups, echo=F, include=T, results="asis"
 
 
-hist(ST_G0$GLB_ench.N,
-     breaks = 50,
-     xlab = "Minutes of enhacement of each CE group",
-     main = "Duration of enhancement cases groups")
+# hist(ST_G0$GLB_ench.N,
+#      breaks = 50,
+#      xlab = "Duration of enhancement [min]",
+#      main = "Duration of enhancement of CE groups cases groups")
+
+
+ggplot(data = ST_G0, aes(x = GLB_ench.N)) +
+  geom_histogram(aes(y = (..count..)/sum(..count..) * 100),
+                 binwidth = 5,
+                 color    = "black") +
+  # xlab(bquote(.(varname("GLB_diff")) ~ group("[", W/m^2,"]"))) +
+  xlab("Duration of enhancement [min]") +
+  ylab("Density [%]")
+# +
+#   theme_bw(base_size = 14) +
+#   theme(axis.text = element_text(face="bold"))
+
 
 
 plot(ST_G0$GLB_ench.N, ST_G0$GLB_diff.sum/ST_G0$GLB_ench.N,
-     xlab = "Duration of enhancemnt cases groups",
+     xlab = "Duration of enhancement [min]",
      ylab = "Extra mean Irradiance per mimute")
 
 
 ggplot(data    = ST_G0,
        mapping = aes(x = GLB_ench.N, y = ST_G0$GLB_diff.sum/ST_G0$GLB_ench.N)) +
-  xlab("Duration of CE groups [minutes]") +
-  ylab("Extra mean Irradiance per mimute [W/m^2]") +
+  xlab("Duration of enhancement [min]") +
+  ylab("Mean Over Irradiance per mimute [W/m^2]") +
   geom_pointdensity(aes(color = after_stat(log(n_neighbors))),
                     adjust = 1,
                     size = 1) +
@@ -363,8 +376,8 @@ ggplot(data    = ST_G0,
 
 ggplot(data    = ST_G0,
        mapping = aes(x = GLB_ench.N, y = ST_G0$GLB_diff.sum/ST_G0$GLB_ench.N)) +
-  xlab("Duration of CE groups [minutes]") +
-  ylab("Extra mean Irradiance per mimute [W/m^2]") +
+  xlab("Duration of enhancement [min]") +
[…]

### 2024-03-06 article/article.Rmd
Commit 2024-03-05 20:14
Commit 2024-03-06 11:10

@@
 
+## Clear Sky Irradiance
+
+In order to set a threshold for the CE we had to create a "clear sky" radiation approximation.
+For that reason we decided to use the Libradtran model with climatological data from AERONET, Sun's total solar irradiance from NOAA and Earth - Sun distance calculated by Astropy.
+We simulated radiation on multiple SZA's, for AOD at 500nm +/- 1 and 2 sigma, for watter column +/1 1 and 2 sigma, and for
+
 ## Thresholds
@@
 
-### Climatology
-
 ```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per week"}
@@
 
+```{r echo=FALSE, fig.cap="Trend of the excess energy per CE"}
+knitr::include_graphics("../images/energy-2.png")
+```
+
 \FloatBarrier

### 2024-03-06 article/article.Rmd
Commit 2024-03-06 12:27

--- 2024-03-05 article/article.Rmd
@@
 
+## Clear Sky Irradiance
+
+In order to set a threshold for the CE we had to create a "clear sky" radiation approximation.
+For that reason, we decided to use the Libradtran model with monthly climatological data from AERONET, as our site is part of this network and operates a Cimel photometer since 2003.
+We also use the Sun's total solar irradiance from NOAA and Earth - Sun distance calculated by Astropy.
+We simulated radiation on multiple SZA's, for AOD at $500\,\text{nm}$ +/- 1 and 2 $\sigma$, for water column +/- 1 and 2 $\sigma$, and for two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer (afglms)" and "AFGL atmospheric constituent profile, midlatitude winter (afglmw)".
+
 ## Thresholds

### 2024-03-06 article/article.Rmd
Commit 2024-03-06 13:09

--- 2024-03-05 article/article.Rmd
@@
 
+## Clear Sky Irradiance
+
+In order to set a threshold for the CE we had to create an approximation of "clear sky" radiation for the whole period.
+For this reason, we decided to use the Libradtran....cite..... model with monthly climatological data from AERONET, as our site is part of this network and operates a Cimel photometer since 2003.
+We also use the Sun's total solar irradiance from NOAA ....cite..... and Earth - Sun distance calculated by Astropy....cite......
+We simulated the solar radiation on $0.2^\circ$ SZA's step, for AOD at $500\,\text{nm}$ and offsets of $\pm1$ and $\pm2\sigma$, for water column $\pm1$ and $\pm2\sigma$, and for two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer (afglms)" and "AFGL atmospheric constituent profile, midlatitude winter (afglmw)"....cite......
+.
+
+- Kurudz wavelength
+- solver
+
+After some evaluation of the modelled conditions, in relation to the GHI data, we choose as more representative of the clear sky radiation, the case with $t_{500} - 1\sigma$ and $wc - 1\sigma$.
+
+Lookup table creation ......
+
 ## Thresholds
+
+To select the exact values of the threshold used (Equation \ref{eq:CE4}), we implemented manual inspection of the CE indemnification, on specially selected days from the whole dataset. 
+We used seven sets of random selected days, with characteristics relevant to the efficiency of the threshold.
+
+six criteria in order to evaluate random multiples of 25 days with some characteristics
+
+- 20 days with the largest over irradiance CE events
+- 30 days with largest total over irradiance
+- 20 days without clouds (CSid)
+- days without clouds and EC events
+- days with    clouds and EC events
+- random days
+- manual selected days
 
@@
 ... this is more clear to understand and describe ....
+
+## Other method used and rejected
 

### 2024-03-06 article/article.Rmd
Commit 2024-03-06 14:14

@@
 - 20 days without clouds (CSid)
-- days without clouds and EC events
-- days with    clouds and EC events
-- random days
-- manual selected days
+- any day without clouds and EC events
+- 20 days with at least 60% of day length without clouds and some EC events
+- 30 random days
+- some manual selected days that were included during the manual inspection
+
+For some of this edge cases we further use images from a skycam, in order to evaluate our selection of the thresholds.
 
@@
 
-Sky Camera for some cases
-
-Objectivity
-
-Describe set of reference days we used to evaluate
-
-Example of days plot?
+Include Example of days plot?
 

### 2024-03-07 GHI_enh_04_investigate.tex
Commit 2024-03-05 20:14
Commit 2024-03-07 12:17

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-05}
+\date{2024-03-07}
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-3} \end{center}
+
 \newpage
@@
 \begin{verbatim}
-2024-03-05 16:54:52.8 athan@tyler GHI_enh_04_investigate.R 1.097087 mins
+2024-03-07 09:37:46.8 athan@tyler GHI_enh_04_investigate.R 1.373684 mins
 \end{verbatim}

### 2024-03-07 article/article.Rmd
Commit 2024-03-07 12:17
Commit 2024-03-07 13:13

@@
 - 30 days with largest total over irradiance
-- 20 days without clouds (CSid)
+- 20 days without clouds (CSid) @Natsis2023
 - any day without clouds and EC events
@@
 
+### Yearly plots relative to all GHI data.
+
+```{r echo=FALSE, fig.cap=""}
+knitr::include_graphics("../images/rel_energy-1.png")
+```
+
+```{r echo=FALSE, fig.cap=""}
+knitr::include_graphics("../images/rel_energy-2.png")
+```
+
+```{r echo=FALSE, fig.cap=""}
+knitr::include_graphics("../images/rel_energy-3.png")
+```
+
+\FloatBarrier
+
 # Discussion and conclusions

### 2024-03-07 GHI_enh_04_investigate.R

@@ -550,7 +550,7 @@ title("Climatology of CE cases per weak")
   lmD <- lm( ST_yearly[, year, GLB_diff.sumPOS/GLB_diff.N_pos])
   abline(lmD)
 
-  title("Annual mean Energy excess per CE")
+  title("Mean Energy of over irradiance per CE")
 
   ## display trend on graph
   fit <- lmD[[1]]

### 2024-03-07 article/article.Rmd
Commit 2024-03-07 18:13

@@
 In order to set a threshold for the CE we had to create an approximation of "clear sky" radiation for the whole period.
-For this reason, we decided to use the Libradtran....cite..... model with monthly climatological data from AERONET, as our site is part of this network and operates a Cimel photometer since 2003.
+For this reason, we decided to use the Libradtran model [@Emde2016], with monthly climatological data from AERONET, as our site is part of this network and operates a Cimel photometer since 2003.
 We also use the Sun's total solar irradiance from NOAA ....cite..... and Earth - Sun distance calculated by Astropy....cite......

### 2024-03-07 article/article.Rmd
Commit 2024-03-07 19:17

--- 2024-03-07 article/article.Rmd
@@
 In order to set a threshold for the CE we had to create an approximation of "clear sky" radiation for the whole period.
-For this reason, we decided to use the Libradtran....cite..... model with monthly climatological data from AERONET, as our site is part of this network and operates a Cimel photometer since 2003.
-We also use the Sun's total solar irradiance from NOAA ....cite..... and Earth - Sun distance calculated by Astropy....cite......
-We simulated the solar radiation on $0.2^\circ$ SZA's step, for AOD at $500\,\text{nm}$ and offsets of $\pm1$ and $\pm2\sigma$, for water column $\pm1$ and $\pm2\sigma$, and for two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer (afglms)" and "AFGL atmospheric constituent profile, midlatitude winter (afglmw)"....cite......
-.
+For this reason, we decided to use the Libradtran model [@Emde2016], with monthly climatological data for AOD and water column from AERONET [@Giles2019; @Buis1998].
+Our site is part of AERONET monitoring network and operates a Cimel photometer since 2003.
+We also use the Sun's total solar irradiance from NOAA [@Coddington2005] and Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].
+We have simulated the solar radiation on $0.2^\circ$ SZA's step, for AOD at $500\,\text{nm}$ and offsets of $\pm1$ and $\pm2\sigma$, for water column $\pm1$ and $\pm2\sigma$, and for two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and "AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
+We used the solar spectra of
 

### 2024-03-07 article/article.Rmd
Commit 2024-03-07 20:18

@@
                                header = TRUE))
-# ## create local citations file and links here
-# source("~/CODE/FUNCTIONS/R/gather_citations.R")
-# suppressMessages(
-#     gather_citations(
-#         sourcefile   = "./Article.Rmd",
-#         mainreposit  = "./Mainreferences.bib",
-#         localreposit = "./references.bib",
-#         folderlink   = "./References_links",
-#         workingdir   = "./"
-#     )
-# )
 ```
@@
 
+CE and ECE usefulness
+
+Identify CE cases
+
+Characteristics of CE
+
+Climatology and impact on the GHI
+
+Effects of clouds
+
+- enhancement physics
+- conditions
+- other interferences
+
+....identification methods from bib....
+
+- clearness index
+- modeled approaches
+- algorithmic id
+- AI
+- Visual
+
+.....constrains of the site.....
+
+- data
+- instrument
+- location
+
 # Data and methodology
+
+- measured data
+- available data
+  - sky cam
+  - chp1
+  - cm21
+  - cimel
+- CSid tool
 
@@
 
-.......
+..  todo ...
 
@@
 
-## Criteria for enhancement identification
-
--   some others were tested
-
-Many have used models or some statistical method to determine then CE thresholds.
-
-....... cite ...... Descriptions
-
-We used as reference a modelled clear sky approximation,
-
-criteria for cloud enhancement identification are set according the Equation \ref{eq:CE4}
-
-\begin{equation}
-\text{CE}_\text{Threshold} = \begin{cases}
-`r C4_cs_ref_ratio`, & \text{if $\theta \leq `r C4_lowcut_sza`^\circ$}.\\
-\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{if $ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}.
-\end{cases}\label{eq:CE4}
-\end{equation}
-where: ..........
-
-expand: libradtran calculations and modeling
-
-A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})
-
-\begin{equation}
-\text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
-\label{eq:ECE}
-\end{equation}
-
 ## Clear Sky Irradiance
@@
 We also use the Sun's total solar irradiance from NOAA [@Coddington2005] and Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].
-We have simulated the solar radiation on $0.2^\circ$ SZA's step, for AOD at $500\,\text{nm}$ and offsets of $\pm1$ and $\pm2\sigma$, for water column $\pm1$ and $\pm2\sigma$, and for two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and "AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
-We used the solar spectra of
+We have simulated the solar radiation spectrum of @Kurucz1994 in the range $280$ to $2500\,\text{nm}$, on $0.2^\circ$ SZA's step. 
+With combinations of AOD at $500\,\text{nm}$ ($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column ($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and for two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and "AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
 
-- Kurudz wavelength
-- solver
+<!-- - rte_solver  disort -->
+<!-- - geometry   pseudospherical -->
+<!-- - mol_abs LOWTRAN -->
 
-After some evaluation of the modelled conditions, in relation to the GHI data, we choose as more representative of the clear sky radiation, the case with $t_{500} - 1\sigma$ and $wc - 1\sigma$.
+After some evaluation of the modelled radiation in different atmospheric conditions, in relation to the GHI data, we choose as representative of the clear sky radiation, the case with $t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$.
 
-Lookup table creation ......
+For each GHI measurement in our data we calculated a reference clear sky value, by adjusting the integral of the Kurudz spectrum to the interpolated TSI from NOAA.
+We applied the effect of Sun - Earth distance, and calculated it's value to the horizontal plane by using the cosine of the corresponding interpolated SZA.
+For each period of the year, we used the appropriate atmospheric profile (afglms or afglmw).
+Thus, we can directly compare each measured one minute value of GHI, with the expected clear sky radiation.
 
-## Thresholds
+## Thresholds investigation
 
@@
 
-For some of this edge cases we further use images from a skycam, in order to evaluate our selection of the thresholds.
+For some of this edge cases we further use images from a sky-cam, in order to evaluate our selection of the thresholds.
 
-Thresholds by inspecting a selection of days with some specs
+Thresholds by inspecting a selection of days with some specs......
 
-Reasoning for the selection
+Reasoning for the selection...........
 
-Include Example of days plot?
+## Criteria for enhancement identification
+
+Many have used models or some statistical method to determine then CE thresholds.
+
+....... cite ...... Descriptions
+
+We used as reference a modeled clear sky approximation,
+
+Criteria for cloud enhancement identification are set according the Equation \ref{eq:CE4}
+
+\begin{equation}
+\text{CE}_\text{Threshold} = \begin{cases}
+`r C4_cs_ref_ratio`, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
+\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
+\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
+\end{cases}\label{eq:CE4}
+\end{equation}
+where: $\theta$ solar zenith angle.
+
+A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})
+
+\begin{equation}
+\text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
+\label{eq:ECE}
+\end{equation}
+
+Include Example of days plot? Appendix?
 
@@
 ## Other method used and rejected
+
+-   some other criteria were tested
 
@@
 
-## Extrene CE above TSI
+## Extreme CE above TSI
 
@@
 
-## New plots for discusion
+## New plots for discussion
 

### 2024-03-08 GHI_enh_03_process.tex
Commit 2024-03-03 12:14
Commit 2024-03-07 13:13
Commit 2024-03-08 10:14

--- 2024-03-01 GHI_enh_03_process.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-01}
+\date{2024-03-08}
 
@@
 ST_E_sza
+ST_E_sza_doy
 ST_E_sza_monthly
@@
 ST_extreme_SZA
+ST_extreme_SZA_doy
 ST_extreme_SZA_monthly
@@
 ST_sza
+ST_sza_doy
 ST_sza_monthly
@@
 \begin{verbatim}
-2024-03-01 17:32:55.6 athan@tyler GHI_enh_03_process.R 2.076944 mins
+2024-03-08 07:58:43.3 athan@tyler GHI_enh_03_process.R 2.261788 mins
 \end{verbatim}

### 2024-03-08 GHI_enh_04_investigate.tex
Commit 2024-03-07 13:13
Commit 2024-03-08 12:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-07}
+\date{2024-03-08}
 
@@
 
-lmD: 1467.857 +/- 152.6559
+lmD: 1.467857 +/- 0.1526559
 
-lmY: 1467.88 +/- 152.6586
+lmY: 1.46788 +/- 0.1526586
 
-Arima: 1467.8769 184.2435 7.967 0
+Arima: 1.4679 0.1843 7.9642 0
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-37} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-38} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-39} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-40} \end{center}
+
 \textbf{END}
@@
 \begin{verbatim}
-2024-03-07 09:37:46.8 athan@tyler GHI_enh_04_investigate.R 1.373684 mins
+2024-03-08 08:30:44.9 athan@tyler GHI_enh_04_investigate.R 1.934441 mins
 \end{verbatim}

### 2024-03-08 article/article.Rmd
Commit 2024-03-08 14:14

@@
   bookdown::pdf_document2:
-    number_sections:  no
+    number_sections:  yes
     fig_caption:      yes
@@
     latex_engine:     xelatex
-    toc:              no
+    toc:              yes
     toc_depth:        4
@@
 
+<!-- todo stop long tails on hist -->
+<!-- hist retative frequency label -->
+
+<!-- Whisky plot relative between months -->
+<!-- weight (Nmonth / Nmaxmonth) -->
+
+<!-- whisky plots relative to GLB -->
+
+<!-- set of yearly plots -->
+
 \FloatBarrier
@@
 
+# Appendix {.unnumbered}
+
 # References {.unnumbered}

### 2024-03-12 article/article.Rmd
Commit 2024-03-12 11:11

@@
 
-```{r echo=FALSE, fig.cap="Trend of the yearly excess energy"}
-knitr::include_graphics("../images/energy-1.png")
+```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"}
+knitr::include_graphics("../images/energy-3.png")
 ```
 
-```{r echo=FALSE, fig.cap="Trend of the excess energy per CE"}
-knitr::include_graphics("../images/energy-3.png")
+```{r echo=FALSE, fig.cap="Trend of number of CE cases"}
+knitr::include_graphics("../images/energy-2.png")
+```
+
+```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
+knitr::include_graphics("../images/energy-1.png")
 ```
@@
 
-```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per week"}
-knitr::include_graphics("../images/climCE_week-1.png")
-```
+<!-- ```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per week"} -->
+<!-- knitr::include_graphics("../images/climCE_week-1.png") -->
+<!-- ``` -->
 
-```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per doy"}
-knitr::include_graphics("../images/climCE_daily-1.png")
-```
+<!-- ```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per doy"} -->
+<!-- knitr::include_graphics("../images/climCE_daily-1.png") -->
+<!-- ``` -->
 
-```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per doy"}
-knitr::include_graphics("../images/clim_CE_N_doy-1.png")
-```
+<!-- ```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per doy"} -->
+<!-- knitr::include_graphics("../images/clim_CE_N_doy-1.png") -->
+<!-- ``` -->
 
-```{r echo=FALSE, fig.cap="Trend of the excess energy per CE"}
-knitr::include_graphics("../images/energy-2.png")
-```
+<!-- ### Yearly plots relative to all GHI data. -->
 
-\FloatBarrier
+<!-- ```{r echo=FALSE, fig.cap=""} -->
+<!-- knitr::include_graphics("../images/rel_energy-1.png") -->
+<!-- ``` -->
 
-### Yearly plots relative to all GHI data.
+<!-- ```{r echo=FALSE, fig.cap=""} -->
+<!-- knitr::include_graphics("../images/rel_energy-2.png") -->
+<!-- ``` -->
 
-```{r echo=FALSE, fig.cap=""}
-knitr::include_graphics("../images/rel_energy-1.png")
-```
-
-```{r echo=FALSE, fig.cap=""}
-knitr::include_graphics("../images/rel_energy-2.png")
-```
-
-```{r echo=FALSE, fig.cap=""}
-knitr::include_graphics("../images/rel_energy-3.png")
-```
+<!-- ```{r echo=FALSE, fig.cap=""} -->
+<!-- knitr::include_graphics("../images/rel_energy-3.png") -->
+<!-- ``` -->
 

### 2024-03-12 GHI_enh_04_investigate.tex
Commit 2024-03-12 11:11
Commit 2024-03-12 12:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-08}
+\date{2024-03-12}
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_N-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N-1} \end{center}
+
+\begin{verbatim}
+Warning: Continuous x aesthetic
+i did you forget `aes(group = ...)`?
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N-2} \end{center}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-1} \end{center}
@@
 \begin{verbatim}
-2024-03-08 08:30:44.9 athan@tyler GHI_enh_04_investigate.R 1.934441 mins
+2024-03-12 09:57:38.0 athan@tyler GHI_enh_04_investigate.R 1.109494 mins
 \end{verbatim}

### 2024-03-12 GHI_enh_04_investigate.tex
Commit 2024-03-12 13:11

@@
 \begin{verbatim}
-Warning: Continuous x aesthetic
-i did you forget `aes(group = ...)`?
+Warning: The `fun.y` argument of `stat_summary()` is deprecated as of ggplot2 3.3.0.
+i Please use the `fun` argument instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
 \end{verbatim}
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N-2} \end{center}
 
@@
 \begin{verbatim}
-2024-03-12 09:57:38.0 athan@tyler GHI_enh_04_investigate.R 1.109494 mins
+2024-03-12 10:27:22.9 athan@tyler GHI_enh_04_investigate.R 1.200812 mins
 \end{verbatim}

### 2024-03-12 GHI_enh_04_investigate.tex
Commit 2024-03-12 17:11

@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-1} \end{center}
+
 \begin{verbatim}
-Warning: The dot-dot notation (`..count..`) was deprecated in ggplot2 3.4.0.
-i Please use `after_stat(count)` instead.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+Warning in scale_y_log10(): log-10 transformation introduced infinite values.
 \end{verbatim}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-1} \end{center}
+\begin{verbatim}
+Warning: Removed 25 rows containing missing values or values outside the scale
+range (`geom_bar()`).
+\end{verbatim}
 
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8} \end{center}
+
+\begin{verbatim}
+Scale for x is already present.
+Adding another scale for x, which will replace the existing scale.
+\end{verbatim}
+
+\begin{verbatim}
+Warning: Removed 5 rows containing non-finite outside the scale range
+(`stat_bin2d()`).
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9} \end{center}
+
+\begin{verbatim}
+Scale for x is already present.
+Adding another scale for x, which will replace the existing scale.
+\end{verbatim}
+
+\begin{verbatim}
+Warning: Removed 5 rows containing non-finite outside the scale range
+(`stat_bin2d()`).
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-10} \end{center}
 
@@
 \begin{verbatim}
-2024-03-12 10:27:22.9 athan@tyler GHI_enh_04_investigate.R 1.200812 mins
+2024-03-12 15:10:56.3 athan@tyler GHI_enh_04_investigate.R 2.333127 mins
 \end{verbatim}

### 2024-03-12 article/article.tex
Commit 2024-03-12 17:11

--- 2023-11-28 article/article.tex
@@
 \PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
 %
 \documentclass[
-  authoryear,
-  preprint,
-  3p]{elsarticle}
-
+]{article}
 \usepackage{amsmath,amssymb}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
@@
 \usepackage{xcolor}
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{5}
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{241,243,245}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
-\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
-
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage[margin=1in]{geometry}
+\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 \makeatother
-
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{5}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\usepackage{caption}
+\usepackage{placeins}
+\captionsetup{font=small}
 \usepackage{booktabs}
@@
 \usepackage{xcolor}
-\makeatletter
-\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
-\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
-\definecolor{quarto-callout-color}{HTML}{909090}
-\definecolor{quarto-callout-note-color}{HTML}{0758E5}
-\definecolor{quarto-callout-important-color}{HTML}{CC1914}
-\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
-\definecolor{quarto-callout-tip-color}{HTML}{00A047}
-\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
-\definecolor{quarto-callout-color-frame}{HTML}{acacac}
-\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
-\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
-\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
-\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
-\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
-\makeatother
-\makeatletter
-\makeatother
-\makeatletter
-\makeatother
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\AtBeginDocument{%
-\ifdefined\contentsname
-  \renewcommand*\contentsname{Table of contents}
-\else
-  \newcommand\contentsname{Table of contents}
-\fi
-\ifdefined\listfigurename
-  \renewcommand*\listfigurename{List of Figures}
-\else
-  \newcommand\listfigurename{List of Figures}
-\fi
-\ifdefined\listtablename
-  \renewcommand*\listtablename{List of Tables}
-\else
-  \newcommand\listtablename{List of Tables}
-\fi
-\ifdefined\figurename
-  \renewcommand*\figurename{Figure}
-\else
-  \newcommand\figurename{Figure}
-\fi
-\ifdefined\tablename
-  \renewcommand*\tablename{Table}
-\else
-  \newcommand\tablename{Table}
-\fi
-}
-\@ifpackageloaded{float}{}{\usepackage{float}}
-\floatstyle{ruled}
-\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
-\floatname{codelisting}{Listing}
-\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
-\makeatother
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
-\makeatother
-\makeatletter
-\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
-\makeatother
-\makeatletter
-\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
-\makeatother
-\makeatletter
-\makeatother
-\makeatletter
-\makeatother
-\journal{Journal Name}
 \ifLuaTeX
@@
 \fi
-\usepackage[]{natbib}
-\bibliographystyle{elsarticle-harv}
 \IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
   pdftitle={SDR enhancement by clouds},
-  pdfauthor={Athanasios Natsis; Alkiviadis Bais; Charikleia Meleti},
+  pdfauthor={Athanasios N. Natsis; Alkiviadis Bais; Charikleia Meleti},
   pdfkeywords={keyword1, keyword2},
-  colorlinks=true,
-  linkcolor={blue},
-  filecolor={Maroon},
-  citecolor={Blue},
-  urlcolor={Blue},
+  hidelinks,
   pdfcreator={LaTeX via pandoc}}
 
-\setlength{\parindent}{6pt}
+\title{SDR enhancement by clouds}
+\usepackage{etoolbox}
+\makeatletter
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+}
+\makeatother
+\subtitle{A Short Subtitle}
+\author{Athanasios N.
+Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
+\date{2024-03-12}
+
 \begin{document}
-
-\begin{frontmatter}
-\title{SDR enhancement by clouds \\\large{An analysis} }
-\author[1]{Athanasios Natsis%
-\corref{cor1}%
-\fnref{fn1}}
- \ead{natsisphysicist@gmail.com} 
-\author[2]{Alkiviadis Bais%
-%
-\fnref{fn2}}
- \ead{abais@auth.gr} 
-\author[1]{Charikleia Meleti%
-%
-\fnref{fn3}}
- \ead{meleti@auth.gr}
-
-\affiliation[1]{organization={Aristotle University of
-Thessaloniki, Laboratory of Atmospheric Physics},addressline={Campus Box
-149},city={Thessaloniki},postcode={54124},postcodesep={}}
-\affiliation[2]{organization={Another University, Department
-Name},addressline={Street Address},city={City},postcode={Postal
-Code},postcodesep={}}
-
-\cortext[cor1]{Corresponding author}
-\fntext[fn1]{This is the first author footnote.}
-\fntext[fn2]{Another author footnote, this is a very long footnote and
-it should be a really long footnote. But this footnote is not yet
-sufficiently long enough to make two lines of footnote text.}
-\fntext[fn3]{Yet another author footnote.}
-
+\maketitle
 \begin{abstract}
-This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo
-rutrum at. Sed at tempus elit.
+This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
 \end{abstract}
 
-\begin{keyword}
-    keyword1 \sep 
-    keyword2
-\end{keyword}
-\end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, sharp corners, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden]}{\end{tcolorbox}}\fi
+{
+\setcounter{tocdepth}{4}
+\tableofcontents
+}
+CE: cloud enhancement cases one minute
+
+ECE: extreme cloud enhancement cases one minute over TSI on horizontal plane
+
+CEG: cloud enhancement groups, cases events with consecutive CE
 
@@
 
+CE and ECE usefulness
+
+Identify CE cases
+
+Characteristics of CE
+
+Climatology and impact on the GHI
+
+Effects of clouds
+
+\begin{itemize}
+\tightlist
+\item
+  enhancement physics
+\item
+  conditions
+\item
+  other interferences
+\end{itemize}
+
+\ldots.identification methods from bib\ldots.
+
+\begin{itemize}
+\tightlist
+\item
+  clearness index
+\item
+  modeled approaches
+\item
+  algorithmic id
+\item
+  AI
+\item
+  Visual
+\end{itemize}
+
+\ldots..constrains of the site\ldots..
+
+\begin{itemize}
+\tightlist
+\item
+  data
+\item
+  instrument
+\item
+  location
+\end{itemize}
+
 \hypertarget{data-and-methodology}{%
 \section{Data and methodology}\label{data-and-methodology}}
+
+\begin{itemize}
+\tightlist
+\item
+  measured data
+\item
+  available data
+
+  \begin{itemize}
+  \tightlist
+  \item
+    sky cam
+  \item
+    chp1
+  \item
+    cm21
+  \item
+    cimel
+  \end{itemize}
+\item
+  CSid tool
+\end{itemize}
+
+The recording of the signal is the one minute average.
+Thus we will refer to this time scale as a cloud enhancement event (CE).
+Due to the instruments response time\ldots..
 
@@
 
+.. todo \ldots{}
+
 \hypertarget{data-selection}{%
@@
 
-To preserve an unbiased representation of the data we applied a
-constrain similar the one used by \citet{CastillejoCuberos2020}. Where,
-for each valid hour of day, there must exist at list 45 minutes of valid
-measurements, including night time near sunrise and sunset. Days with
-less than 5 valid hours are rejected completely. Furthermore, due to a
-systematic obstruction of the horizon and the significant measurement
-uncertainty on large SZAs, we excluded all data with \(SZA > 78^\circ\).
+To preserve an unbiased representation of the data we applied a constrain similar the one used by Castillejo-Cuberos and Escobar (2020).
+Where, for each valid hour of day, there must exist at list 45 minutes of valid measurements, including night time near sunrise and sunset.
+Days with less than 5 valid hours are rejected completely.
+Furthermore, due to a systematic obstruction of the horizon and the significant measurement uncertainty on large SZAs, we excluded all data with \(SZA > 78^\circ\).
 
-\hypertarget{clear-sky-identification}{%
-\subsection{Clear sky identification}\label{clear-sky-identification}}
+\hypertarget{clear-sky-irradiance}{%
+\subsection{Clear Sky Irradiance}\label{clear-sky-irradiance}}
 
-Use it to find some interesting days to manual check the CE thresholds.
-No other usage of clear/cloud characterization in CE.
+In order to set a threshold for the CE we had to create an approximation of ``clear sky'' radiation for the whole period.
+For this reason, we decided to use the Libradtran model (Emde et al.
+2016), with monthly climatological data for AOD and water column from AERONET (Giles et al.
+2019; Buis et al.
+1998).
+Our site is part of AERONET monitoring network and operates a Cimel photometer since 2003.
+We also use the Sun's total solar irradiance from NOAA (Coddington et al. 2005) and Earth - Sun distance calculated by Astropy (Astropy Collaboration et al. 2022).
+We have simulated the solar radiation spectrum of Kurucz (1994) in the range \(280\) to \(2500\,\text{nm}\), on \(0.2^\circ\) SZA's step.
+With combinations of AOD at \(500\,\text{nm}\) (\(t_{500\text{nm}}\)) and additional offsets of \(\pm1\) and \(\pm2\sigma\), water column (\(w_h\)) with offsets of \(\pm1\) and \(\pm2\sigma\), and for two atmospheric profiles ``AFGL atmospheric constituent profile, midlatitude summer'' (afglms) and ``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw) (Anderson et al.
+1986).
 
-\hypertarget{criteria-for-enhancement-based-on-tsi}{%
-\subsection{Criteria for enhancement based on
-TSI}\label{criteria-for-enhancement-based-on-tsi}}
+After some evaluation of the modelled radiation in different atmospheric conditions, in relation to the GHI data, we choose as representative of the clear sky radiation, the case with \(t_{\text{cs}} = t_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\).
 
-Many have used models or some statistical method to determine then CE
-thresholds.
+For each GHI measurement in our data we calculated a reference clear sky value, by adjusting the integral of the Kurudz spectrum to the interpolated TSI from NOAA.
+We applied the effect of Sun - Earth distance, and calculated it's value to the horizontal plane by using the cosine of the corresponding interpolated SZA.
+For each period of the year, we used the appropriate atmospheric profile (afglms or afglmw).
+Thus, we can directly compare each measured one minute value of GHI, with the expected clear sky radiation.
 
-\ldots\ldots. cite \ldots\ldots{} Descriptions
+\hypertarget{thresholds-investigation}{%
+\subsection{Thresholds investigation}\label{thresholds-investigation}}
 
-We used as reference the \ldots. extraterrestrial horizontal irradiance
-\ldots..
+To select the exact values of the threshold used (Equation \ref{eq:CE4}), we implemented manual inspection of the CE indemnification, on specially selected days from the whole dataset.
+We used seven sets of random selected days, with characteristics relevant to the efficiency of the threshold.
 
-\[
-\text{ETH} = \cos(\theta) \times \text{TSI}_\text{TOA}
-\]
-
-\begin{equation}\protect\hypertarget{eq-CEcrit1}{}{
-\text{GHI} > 0.8 \times \text{ETH} + 20\,Wm^{-2}
-}\label{eq-CEcrit1}\end{equation}
-
-Where GHI sddsfa
+six criteria in order to evaluate random multiples of 25 days with some characteristics
 
@@
 \item
-  some other were tested Equation~\ref{eq-CEcrit1}
+  20 days with the largest over irradiance CE events
+\item
+  30 days with largest total over irradiance
+\item
+  20 days without clouds (CSid) Natsis, Bais, and Meleti (2023)
+\item
+  any day without clouds and EC events
+\item
+  20 days with at least 60\% of day length without clouds and some EC events
+\item
+  30 random days
+\item
+  some manual selected days that were included during the manual inspection
 \end{itemize}
 
-Thresholds by inspecting a selection of days with some specs
+For some of this edge cases we further use images from a sky-cam, in order to evaluate our selection of the thresholds.
+
+Thresholds by inspecting a selection of days with some specs\ldots\ldots{}
+
+Reasoning for the selection\ldots\ldots\ldots..
+
+\hypertarget{criteria-for-enhancement-identification}{%
+\subsection{Criteria for enhancement identification}\label{criteria-for-enhancement-identification}}
+
+Many have used models or some statistical method to determine then CE thresholds.
+
+\ldots\ldots. cite \ldots\ldots{} Descriptions
+
+We used as reference a modeled clear sky approximation,
+
+Criteria for cloud enhancement identification are set according the Equation \ref{eq:CE4}
+
+\begin{equation}
+\text{CE}_\text{Threshold} = \begin{cases}
+1.05, & \text{$\theta \leq 60^\circ$}\\
+\frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) + 1.18 , & \text{$ 78^\circ > \theta > 60^\circ$}\\
+\text{Excluded measurements}, & \theta > 78^\circ
+\end{cases}\label{eq:CE4}
+\end{equation}
+where: \(\theta\) solar zenith angle.
+
+A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})
+
+\begin{equation}
+\text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
+\label{eq:ECE}
+\end{equation}
+
+Include Example of days plot? Appendix?
+
+\ldots{} this is more clear to understand and describe \ldots.
+
+\hypertarget{other-method-used-and-rejected}{%
+\subsection{Other method used and rejected}\label{other-method-used-and-rejected}}
+
+\begin{itemize}
+\tightlist
+\item
+  some other criteria were tested
+\end{itemize}
+
+\FloatBarrier
 
@@
 
+\hypertarget{trend}{%
+\subsection{Trend}\label{trend}}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/daily-12}
+
+}
+
+\caption{Trend of the daily excess energy due to CE}(\#fig:unnamed-chunk-1)
+\end{figure}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/energy-3}
+
+}
+
+\caption{Treds of the mean over irradiance per CE}(\#fig:unnamed-chunk-2)
+\end{figure}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/energy-2}
+
+}
+
+\caption{Trend of number of CE cases}(\#fig:unnamed-chunk-3)
+\end{figure}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/energy-1}
+
+}
+
+\caption{Trend of the yearly excess energy due to CE over irradiance}(\#fig:unnamed-chunk-4)
+\end{figure}
+
+\FloatBarrier
+
+\hypertarget{climatology}{%
+\subsection{Climatology}\label{climatology}}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/climCEmonth-1}
+
+}
+
+\caption{Distribution of the number of CE cases}(\#fig:unnamed-chunk-5)
+\end{figure}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/relative_distributions-4}
+
+}
+
+\caption{Distribution of CE above reference}(\#fig:unnamed-chunk-6)
+\end{figure}
+
+\FloatBarrier
+
+\hypertarget{groups-stats}{%
+\subsection{Groups stats}\label{groups-stats}}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/groups-1}
+
+}
+
+\caption{Distribution of CE groups}(\#fig:unnamed-chunk-7)
+\end{figure}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/groups-4}
+
+}
+
+\caption{Relation of mean over irradiance and CE group duration}(\#fig:unnamed-chunk-8)
+\end{figure}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/groups-8}
+
+}
+
+\caption{Relation of maximun over irradiance and CE group duration}(\#fig:unnamed-chunk-9)
+\end{figure}
+
+\FloatBarrier
+
+\hypertarget{extreme-ce-above-tsi}{%
+\subsection{Extreme CE above TSI}\label{extreme-ce-above-tsi}}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/climECEmonth-1}
+
+}
+
+\caption{Distribution of the number of ECE cases}(\#fig:unnamed-chunk-10)
+\end{figure}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/extremedistributions-2}
+
+}
+
+\caption{Distribution of ECE above 'clear sky' reference}(\#fig:unnamed-chunk-11)
+\end{figure}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/extremedistributions-4}
+
+}
+
+\caption{Distribution of ECE Irradiance above 'TSI'}(\#fig:unnamed-chunk-12)
+\end{figure}
+
 \begin{itemize}
@@
 \item
-  max
+  max value ECE
 \item
@@
 
+\FloatBarrier
+
+\hypertarget{new-plots-for-discussion}{%
+\subsection{New plots for discussion}\label{new-plots-for-discussion}}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/clim_CE_month_norm_MAX_median_N-2}
+
+}
+
+\caption{Distribution of }(\#fig:unnamed-chunk-13)
+\end{figure}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}
+
+}
+
+\caption{Distribution of }(\#fig:unnamed-chunk-14)
+\end{figure}
+
+\FloatBarrier
+
 \hypertarget{discussion-and-conclusions}{%
@@
 
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+Compare to other location stats.
+max, ECE, distributions \ldots.
 
-\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, leftrule=.75mm, colframe=quarto-callout-important-color-frame, breakable, coltitle=black, rightrule=.15mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, colbacktitle=quarto-callout-important-color!10!white, arc=.35mm, toptitle=1mm, left=2mm, bottomtitle=1mm, bottomrule=.15mm, titlerule=0mm, opacitybacktitle=0.6, opacityback=0, colback=white]
+Climatology results
 
-This is nice
+\hypertarget{appendix}{%
+\section*{Appendix}\label{appendix}}
+\addcontentsline{toc}{section}{Appendix}
 
-\end{tcolorbox}
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
 
-\hypertarget{figures-and-tables}{%
-\section{Figures and tables}\label{figures-and-tables}}
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-Anderson1986}{}}%
+Anderson, G.
+P., J.
+H.
+Chetwynd, S.
+A.
+Clough, E.
+P.
+Shettle, and F.
+X.
+Kneizys.
+1986.
+{``{AFGL} Atmospheric Constituent Profiles (0-120km).''} Air Force Geophysics Laboratory, Optical Physics Division.
 
-Figure~\ref{fig-meaningless} is generated using an R chunk.
+\leavevmode\vadjust pre{\hypertarget{ref-AstropyCollaboration2022}{}}%
+Astropy Collaboration, Adrian M.
+Price-Whelan, Pey Lian Lim, Nicholas Earl, Nathaniel Starkman, Larry Bradley, David L.
+Shupe, et al.
+2022.
+{``{The Astropy Project: Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package}''} 935 (2): 167.
+\url{https://doi.org/10.3847/1538-4357/ac7c74}.
 
-\begin{figure}[h!]
+\leavevmode\vadjust pre{\hypertarget{ref-Buis1998}{}}%
+Buis, J.
+P.
+P., A.
+Setzer, B.
+N.
+N.
+Holben, T.
+F.
+F.
+Eck, I.
+Slutsker, D.
+Tanre, E.
+Vermote, et al.
+1998.
+{``AERONET---a Federated Instrument Network and Data Archive for Aerosol Characterization.''} \emph{Remote Sensing of Environment} 66 (1): 1--16.
 
-{\centering \includegraphics[width=0.5\textwidth,height=\textheight]{article_files/figure-pdf/fig-meaningless-1.pdf}
+\leavevmode\vadjust pre{\hypertarget{ref-CastillejoCuberos2020}{}}%
+Castillejo-Cuberos, Armando, and Rodrigo Escobar.
+2020.
+{``Detection and Characterization of Cloud Enhancement Events for Solar Irradiance Using a Model-Independent, Statistically-Driven Approach.''} \emph{Solar Energy} 209 (October): 547--67.
+\url{https://doi.org/10.1016/j.solener.2020.09.046}.
 
-}
+\leavevmode\vadjust pre{\hypertarget{ref-Coddington2005}{}}%
+Coddington, Odele, Judith L.
+Lean, Doug Lindholm, Peter Pilewskie, Martin Snow, and NOAA CDR Program.
+2005.
+{``{NOAA} Climate Data Record ({CDR}) of Total Solar Irradiance ({TSI}), {NRLTSI} Version 2.
+{D}aily.''} \url{https://doi.org/10.7289/V55B00C1}.
 
-\caption{\label{fig-meaningless}A meaningless scatterplot}
+\leavevmode\vadjust pre{\hypertarget{ref-Emde2016}{}}%
+Emde, Claudia, Robert Buras-Schnell, Arve Kylling, Bernhard Mayer, Josef Gasteiger, Ulrich Hamann, Jonas Kylling, et al.
+2016.
+{``The {libRadtran} Software Package for Radiative Transfer Calculations (Version 2.0.1).''} \emph{Geoscientific Model Development} 9 (5): 1647--72.
+\url{https://doi.org/10.5194/gmd-9-1647-2016}.
 
-\end{figure}
+\leavevmode\vadjust pre{\hypertarget{ref-Giles2019}{}}%
+Giles, David M., Alexander Sinyuk, Mikhail G.
+Sorokin, Joel S.
+Schafer, Alexander Smirnov, Ilya Slutsker, Thomas F.
+Eck, et al.
+2019.
+{``Advancements in the Aerosol Robotic Network ({AERONET}) Version 3 Database -- Automated Near-Real-Time Quality Control Algorithm with Improved Cloud Screening for Sun Photometer Aerosol Optical Depth ({AOD}) Measurements.''} \emph{Atmospheric Measurement Techniques} 12 (1): 169--209.
+\url{https://doi.org/10.5194/amt-12-169-2019}.
 
-\hypertarget{tables-coming-from-r}{%
-\section{Tables coming from R}\label{tables-coming-from-r}}
+\leavevmode\vadjust pre{\hypertarget{ref-Kurucz1994}{}}%
+Kurucz, Robert L. 1994. {``Synthetic Infrared Spectra.''} In \emph{Infrared Solar Physics}, edited by D. M. Rabin, J. T. Jefferies, and C. Lindsey, 523--31. Dordrecht: Springer Netherlands.
 
-Tables can also be generated using R chunks, as shown in
-Table~\ref{tbl-simple} example.
+\leavevmode\vadjust pre{\hypertarget{ref-Natsis2023}{}}%
+Natsis, Athanasios, Alkiviadis Bais, and Charikleia Meleti.
+2023.
+{``Trends from 30-Year Observations of Downward Solar Irradiance in Thessaloniki, Greece.''} \emph{Applied Sciences} 14 (1): 252.
+\url{https://doi.org/10.3390/app14010252}.
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}\FunctionTok{head}\NormalTok{(mtcars)[,}\DecValTok{1}\SpecialCharTok{:}\DecValTok{4}\NormalTok{])}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{tbl-simple}{}
-\begin{table}
-\caption{\label{tbl-simple}Caption centered above table }\tabularnewline
-
-\centering
-\begin{tabular}{l|r|r|r|r}
-\hline
-  & mpg & cyl & disp & hp\\
-\hline
-Mazda RX4 & 21.0 & 6 & 160 & 110\\
-\hline
-Mazda RX4 Wag & 21.0 & 6 & 160 & 110\\
-\hline
-Datsun 710 & 22.8 & 4 & 108 & 93\\
-\hline
-Hornet 4 Drive & 21.4 & 6 & 258 & 110\\
-\hline
-Hornet Sportabout & 18.7 & 8 & 360 & 175\\
-\hline
-Valiant & 18.1 & 6 & 225 & 105\\
-\hline
-\end{tabular}
-\end{table}
-
-\renewcommand\refname{References}
-  \bibliography{bibliography.bib}
+\end{CSLReferences}
 

### 2024-03-12 GHI_enh_04_investigate.tex
Commit 2024-03-12 18:14

@@
 \begin{verbatim}
-2024-03-12 15:10:56.3 athan@tyler GHI_enh_04_investigate.R 2.333127 mins
+2024-03-12 14:56:39.8 athan@tyler GHI_enh_04_investigate.R 1.467140 mins
 \end{verbatim}

### 2024-03-12 article/article.Rmd
Commit 2024-03-12 15:13
Commit 2024-03-12 19:22

@@
 
+$\text{GHI}_\text{i}$: measured one minute global horizontal irradiance
+
+$\text{GHI}_\text{CSi}$: modelled clear sky one minute global horizontal irradiance
+
+$\text{GHI}_\text{CSi}$: modelled clear sky one minute global horizontal irradiance
+
 # Intro
@@
 
-In order to set a threshold for the CE we had to create an approximation of "clear sky" radiation for the whole period.
-For this reason, we decided to use the Libradtran model [@Emde2016], with monthly climatological data for AOD and water column from AERONET [@Giles2019; @Buis1998].
-Our site is part of AERONET monitoring network and operates a Cimel photometer since 2003.
-We also use the Sun's total solar irradiance from NOAA [@Coddington2005] and Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].
-We have simulated the solar radiation spectrum of @Kurucz1994 in the range $280$ to $2500\,\text{nm}$, on $0.2^\circ$ SZA's step. 
-With combinations of AOD at $500\,\text{nm}$ ($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column ($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and for two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and "AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
+In order to set a threshold for the CE we had to create an approximation of "clear sky" radiation for the whole period, to be used as reference.
+For this reason, we decided to use the Libradtran model [@Emde2016], with monthly climatological data of AOD and water column from the AERONET monitoring network [@Giles2019; @Buis1998].
+Our site participate in AERONET, where we operate a Cimel photometer since 2003.
+We also used the Sun's total solar irradiance from NOAA [@Coddington2005] and the Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].
+We simulated the clear sky radiation, using the solar radiation spectrum of @Kurucz1994 in the range $280$ to $2500\,\text{nm}$, with a SZA step of $0.2^\circ$.
+For the atmospheric characteristics, we used combinations of AOD at $500\,\text{nm}$ ($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column ($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and applied it to two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and "AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
+Thus, we were able to emulate different atmospheric condition and level of atmospheric clearness for the climatological conditions of the site.
+
+Furthermore, to account for the Sun's variability in our one-minute GHI measurements, we adjusted the model's input spectrum integral to the one of the the TSI provided by NOAA.
+Finally, we adjusted for the effect of Sun - Earth distance, and calculated the clear sky irradiance value at the horizontal plane by using the cosine of the corresponding interpolated SZA. 
+For each period of the year, we used the appropriate atmospheric profile (afglms or afglmw).
+Thus, the modeled GHI_modeld we can directly compare each measured one minute value of GHI, with the expected clear sky radiation.
 
@@
 
-For each GHI measurement in our data we calculated a reference clear sky value, by adjusting the integral of the Kurudz spectrum to the interpolated TSI from NOAA.
-We applied the effect of Sun - Earth distance, and calculated it's value to the horizontal plane by using the cosine of the corresponding interpolated SZA.
-For each period of the year, we used the appropriate atmospheric profile (afglms or afglmw).
-Thus, we can directly compare each measured one minute value of GHI, with the expected clear sky radiation.
+ We applied the effect of
 
@@
 
-six criteria in order to evaluate random multiples of 25 days with some characteristics
+six criteria 
+in order to evaluate random groups of about 20 to 30 days with some characteristics
 
@@
 
+```{r echo=FALSE, fig.cap="Distribution of "}
+knitr::include_graphics("../images/clim_CE_month_norm_MAX_median_N-2.png")
+```
+
+```{r echo=FALSE, fig.cap="Distribution of "}
+knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")
+```
+
 <!-- ### Yearly plots relative to all GHI data. -->

### 2024-03-13 article/article.Rmd
Commit 2024-03-13 12:10

@@
 
-$\text{GHI}_\text{CSi}$: modelled clear sky one minute global horizontal irradiance
-
-$\text{GHI}_\text{CSi}$: modelled clear sky one minute global horizontal irradiance
+$\text{GHI}_\text{mCSi}$: modelled clear sky one minute global horizontal irradiance
 
@@
 Furthermore, to account for the Sun's variability in our one-minute GHI measurements, we adjusted the model's input spectrum integral to the one of the the TSI provided by NOAA.
-Finally, we adjusted for the effect of Sun - Earth distance, and calculated the clear sky irradiance value at the horizontal plane by using the cosine of the corresponding interpolated SZA. 
+Finally, we adjusted for the effect of the Sun - Earth distance, and calculated the clear sky irradiance value at the horizontal plane by using the cosine of the corresponding interpolated SZA. 
 For each period of the year, we used the appropriate atmospheric profile (afglms or afglmw).
-Thus, the modeled GHI_modeld we can directly compare each measured one minute value of GHI, with the expected clear sky radiation.
+Thus, the modelled GHI_modeld we can directly compare each measured one minute value of GHI, with the expected clear sky radiation.
 
@@
 
+Of course, have to choose which atmospheric conditions qualify as a good clear sky analogous radiation.
+
 After some evaluation of the modelled radiation in different atmospheric conditions, in relation to the GHI data, we choose as representative of the clear sky radiation, the case with $t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$.
 
- We applied the effect of
+Which is an expected result as these values represent an typical atmosphere in Thessaloniki with low load of aerosols and humidity, which are the main factor that atternuate the GHI, execluding clouds.
 

### 2024-03-13 article/article.Rmd
Commit 2024-03-13 17:10

@@
 
+Our monitoring site is operated by the Laboratory of Atmospheric Physics of the Aristotle University of Thessaloniki ()
+
 - measured data
@@
 
-Which is an expected result as these values represent an typical atmosphere in Thessaloniki with low load of aerosols and humidity, which are the main factor that atternuate the GHI, execluding clouds.
+Which is an expected result as these values represent an typical atmosphere in Thessaloniki with low load of aerosols and humidity, which are the main factor that attenuate the GHI, excluding clouds.
 

### 2024-03-13 article/article.Rmd
Commit 2024-03-13 18:14

@@
 
-....identification methods from bib....
+Identification methods from bib
 
@@
 
-.....constrains of the site.....
+Constrains of the site
 
@@
 
-Our monitoring site is operated by the Laboratory of Atmospheric Physics of the Aristotle University of Thessaloniki ()
+Our monitoring site is operating in the Laboratory of Atmospheric Physics of the
+Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
+\(22^\circ\,57'\,\)E, \(80\,\)m~a.s.l.).
+In this study we present data from the period
+`r strftime(min(ST_daily$Date), "%d\\ %B %Y")` to
+`r strftime(max(ST_daily$Date), "%d\\ %B %Y")`.
+
+The GHI data were measured with a Kipp\ & Zonen CM-21 pyranometer.
+During the study period, the pyranometer was independently calibrated three times at
+the Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of
+the instrument’s sensitivity was better than $0.7\%$ relative to the initial
+calibration by the manufacturer.
+
+For the acquisition of radiometric data, the signal of the pyranometer was sampled
+at a rate of $1\,\text{Hz}$.
+The mean and the standard deviation of these samples were calculated and recorded
+every minute.
+The measurements were corrected for the zero offset ("dark signal" in volts), which
+was calculated by averaging all measurements recorded for a period of $3\,\text{h}$,
+before (morning) or after (evening) the Sun reaches an elevation angle of $-10^\circ$.
+The signal was converted to irradiance using a ramped value of the instrument’s
+sensitivity between subsequent calibrations.
+
+<!-- Radiation data quality check -->
+To  further improve the quality of the irradiance data, a manual screening was
+performed to remove inconsistent and erroneous recordings that can occur
+stochastically or systematically during the continuous operation of the instruments.
+The manual screening was aided by a radiation data quality assurance procedure,
+adjusted for the site, which was based on the methods of Long and Shi\ [@Long2006; @Long2008a].
+Thus, problematic recordings have been excluded from further processing.
+Although it is impossible to detect all false data, the large number of available
+data, and the aggregation scheme we used, ensures the quality of the radiation
+measurements used in this study.
+
+<!-- Data selection -->
+Due to the significant measurement uncertainty when the Sun is near the horizon, we
+have excluded all measurements with solar zenith angle (SZA) greater than $`r 90-MIN_ELEVA`^\circ$.
+Moreover, due to obstructions around the site (hills and buildings) that block the direct irradiance, we excluded data with azimuth angle in the range
+$`r FIBais_Az_1`^{\circ}$--$`r FIBais_Az_2`^{\circ}$ and with SZA greater than $`r 90 - FIBais_Elev`^{\circ}$.
 

### 2024-03-13 article/article.Rmd
Commit 2024-03-13 19:12

@@
 
-$\text{GHI}_\text{mCSi}$: modelled clear sky one minute global horizontal irradiance
+$\text{GHI}_\text{mCSi}$: modeled clear sky one minute global horizontal irradiance
 
@@
 
+<!-- Instrument -->
 The GHI data were measured with a Kipp\ & Zonen CM-21 pyranometer.
@@
 
+<!-- Measurements -->
 For the acquisition of radiometric data, the signal of the pyranometer was sampled
@@
 <!-- Data selection -->
-Due to the significant measurement uncertainty when the Sun is near the horizon, we
-have excluded all measurements with solar zenith angle (SZA) greater than $`r 90-MIN_ELEVA`^\circ$.
-Moreover, due to obstructions around the site (hills and buildings) that block the direct irradiance, we excluded data with azimuth angle in the range
-$`r FIBais_Az_1`^{\circ}$--$`r FIBais_Az_2`^{\circ}$ and with SZA greater than $`r 90 - FIBais_Elev`^{\circ}$.
+To preserve an unbiased representation of the data we applied a constrain similar
+the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there
+must exist at list 45 minutes of valid measurements, including night time near
+sunrise and sunset. Days with less than 5 valid hours are rejected completely.
+<!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7),
+otherwise all data for this day is flagged as invalid. There must be at least This
+work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid,
+otherwise all minute data for this hour is flagged as invalid. -->
+Furthermore, due to the significant measurement uncertainty when the Sun is near the
+horizon, and to some systematic obstructions by nearby buildings, we have excluded
+all measurements with solar zenith angle (SZA) greater than $`r 90-BIO_ELEVA`^\circ$.
 
@@
 ## Data selection
-
-To preserve an unbiased representation of the data we applied a constrain similar the one used by @CastillejoCuberos2020.
-Where, for each valid hour of day, there must exist at list 45 minutes of valid measurements, including night time near sunrise and sunset.
-Days with less than 5 valid hours are rejected completely.
-<!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7), otherwise all data for this day is flagged as invalid.
-There must be at least This work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid, otherwise all minute data for this hour is flagged as invalid.
---> Furthermore, due to a systematic obstruction of the horizon and the significant measurement uncertainty on large SZAs, we excluded all data with $SZA > `r 90 - BIO_ELEVA`^\circ$.
 

### 2024-03-13 article/article.Rmd
Commit 2024-03-13 20:15

@@
 
+<!-- Define CE and ECE -->
+In this study, we define as cloud enhancement events (CE) the cases when the measured
+global horizontal irradiance (GHI) at ground level exceeds the expected value under
+sky, unobscured by clouds.
+Similar, we define the extreme cloud enhancement events (ECE), the cases when GHI,
+exceeds the Total Solar Irradiance on horizontal plane at ground level.
+
 Identify CE cases
@@
 # Data and methodology
+
+## GHI data
 
@@
 
-- measured data
+In this study, we evaluate the effects
+
 - available data
@@
 Thus we will refer to this time scale as a cloud enhancement event (CE).
-Due to the instruments response time.....
-
-## Data quality control
-
-..  todo ...
-
-## Data selection
 

### 2024-03-13 article/article.Rmd
Commit 2024-03-13 21:12

@@
 Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
-\(22^\circ\,57'\,\)E, \(80\,\)m~a.s.l.).
+\(22^\circ\,57'\,\)E, \(80\,\)m\ a.s.l.).
 In this study we present data from the period
@@
 
-In this study, we evaluate the effects
+In this study, we evaluated the effects of the clouds on th
 
@@
 
-In order to set a threshold for the CE we had to create an approximation of "clear sky" radiation for the whole period, to be used as reference.
-For this reason, we decided to use the Libradtran model [@Emde2016], with monthly climatological data of AOD and water column from the AERONET monitoring network [@Giles2019; @Buis1998].
-Our site participate in AERONET, where we operate a Cimel photometer since 2003.
-We also used the Sun's total solar irradiance from NOAA [@Coddington2005] and the Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].
-We simulated the clear sky radiation, using the solar radiation spectrum of @Kurucz1994 in the range $280$ to $2500\,\text{nm}$, with a SZA step of $0.2^\circ$.
-For the atmospheric characteristics, we used combinations of AOD at $500\,\text{nm}$ ($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column ($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and applied it to two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and "AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
-Thus, we were able to emulate different atmospheric condition and level of atmospheric clearness for the climatological conditions of the site.
+In order to identify CE cases, we need an approximation of the expected clear sky GHI
+for the whole period of the study, with a temporal resolution of one minute.  Because
+of the lack of exact data about atmospheric factors, responsible for the attenuation
+of the solar radiation in the atmosphere, we can not recreate a minute by minute
+representation of the reference radiation. Thus, we used some climatological data
+with a radiation transfer model.
 
-Furthermore, to account for the Sun's variability in our one-minute GHI measurements, we adjusted the model's input spectrum integral to the one of the the TSI provided by NOAA.
-Finally, we adjusted for the effect of the Sun - Earth distance, and calculated the clear sky irradiance value at the horizontal plane by using the cosine of the corresponding interpolated SZA. 
-For each period of the year, we used the appropriate atmospheric profile (afglms or afglmw).
-Thus, the modelled GHI_modeld we can directly compare each measured one minute value of GHI, with the expected clear sky radiation.
+We decided to use the Libradtran [@Emde2016] radiation transfer model, to modeled
+the clear sky equivalent of GHI, with monthly climatological data of AOD and water
+column from the AERONET monitoring network [@Giles2019; @Buis1998].  Our site
+participates in AERONET, where we operate a Cimel photometer, colocated to
+the CM-21 pyranometer, since 2003
 
-<!-- - rte_solver  disort -->
-<!-- - geometry   pseudospherical -->
-<!-- - mol_abs LOWTRAN -->
+For the production of .....
+
+We also used the Sun's total solar irradiance from NOAA [@Coddington2005] and the
+Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].  We simulated
+the clear sky radiation, using the solar radiation spectrum of @Kurucz1994 in the
+range $280$ to $2500\,\text{nm}$, with a SZA step of $0.2^\circ$.  For the
+atmospheric characteristics, we used combinations of AOD at $500\,\text{nm}$
+($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column
+($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and applied it to two atmospheric
+profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and
+"AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
+Thus, we were able to emulate different atmospheric condition and level of
+atmospheric clearness for the climatological conditions of the site.
+
+Furthermore, to account for the Sun's variability in our one-minute GHI measurements,
+we adjusted the model's input spectrum integral to the one of the the TSI provided by
+NOAA.  Finally, we adjusted for the effect of the Sun - Earth distance, and
+calculated the clear sky irradiance value at the horizontal plane by using the cosine
+of the corresponding interpolated SZA.  For each period of the year, we used the
+appropriate atmospheric profile (afglms or afglmw).  Thus, the modelled GHI_modeld we
+can directly compare each measured one minute value of GHI, with the expected clear
+sky radiation.
+
+- rte_solver  disort
+- geometry   pseudospherical
+- mol_abs LOWTRAN
 
@@
 ## Thresholds investigation
+
+The use of the actual modeled values of clear sky GHI can not provide us with a
+robust method to distinguish the CE cases.
 

### 2024-03-13 article/article.Rmd
Commit 2024-03-13 22:14

@@
 
-abstract: |
-  This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
+# abstract: |
+#   This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
 
@@
 
+# Abstract {.unnumbered}
+
+- Phenomenon
+- Effects
+- bibliography
+- our approach
+- our results
+
 CE: cloud enhancement cases one minute
@@
 CE and ECE usefulness 
+importance
+problems
+
+reported trends
+
+CE mechanism
 
@@
 The use of the actual modeled values of clear sky GHI can not provide us with a
-robust method to distinguish the CE cases.
+robust method to distinguish the CE cases, due to the limited accuracy of the input
+data. Our main focus was to positively identify over irradiance events from CEs,
+thus we used a relative factor, to create an upper envelope of the clear sky
+irradiance, above which, any GHI value can safely attributed to CE.
 
-To select the exact values of the threshold used (Equation \ref{eq:CE4}), we implemented manual inspection of the CE indemnification, on specially selected days from the whole dataset. 
-We used seven sets of random selected days, with characteristics relevant to the efficiency of the threshold.
+To select the exact values of the thresholds (Equation \ref{eq:CE4}), we implemented
+manual inspection of the CE identification, on specially selected days from the whole
+dataset.  We used seven sets of selected days, with characteristics relevant to the
+efficiency of the identification threshold.  These sets were  random groups of about
+20 to 30 days with the following characteristics:
+(a) the largest over irradiance CE events,
+(b) the largest daily total over irradiance,
+(c) without clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
+(d) without clouds and without EC events,
+(e) with at least $60\%$ of the day length without clouds and some EC events,
+(h) random days and
+(i) some manual selected days that were included during the manual inspection.
 
-six criteria 
-in order to evaluate random groups of about 20 to 30 days with some characteristics
+<!-- - some manual selected days that were included during the manual inspection -->
+<!-- - 20 days with the largest over irradiance CE events -->
+<!-- - 30 days with largest total over irradiance -->
+<!-- - 20 days without clouds (CSid) @Natsis2023 -->
+<!-- - any day without clouds and EC events -->
+<!-- - 20 days with at least 60% of day length without clouds and some EC events -->
+<!-- - 30 random days -->
+<!-- - some manual selected days that were included during the manual inspection -->
 
-- 20 days with the largest over irradiance CE events
-- 30 days with largest total over irradiance
-- 20 days without clouds (CSid) @Natsis2023
-- any day without clouds and EC events
-- 20 days with at least 60% of day length without clouds and some EC events
-- 30 random days
-- some manual selected days that were included during the manual inspection
+Where it was needed, for some of edge cases, we also used images from a sky-cam,
+along with the manual inspection.
 
-For some of this edge cases we further use images from a sky-cam, in order to evaluate our selection of the thresholds.
-
-Thresholds by inspecting a selection of days with some specs......
-
-Reasoning for the selection...........
+Reasoning for the  final selection...........
 

### 2024-03-14 GHI_enh_04_investigate.tex
Commit 2024-03-12 19:22
Commit 2024-03-13 14:14
Commit 2024-03-14 11:11

--- 2024-03-12 GHI_enh_04_investigate.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-12}
+\date{2024-03-14}
 
@@
 
-\newpage
-\FloatBarrier
-
-\hypertarget{sza-enhancements}{%
-\subsubsection{SZA enhancements}\label{sza-enhancements}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-3} \end{center}
-
-\newpage
-\FloatBarrier
-
-\hypertarget{sza-enhancements-by-month}{%
-\subsubsection{SZA enhancements by month}\label{sza-enhancements-by-month}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-3} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-8} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-9} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-10} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-11} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-12} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-13} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-14} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-15} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-16} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-17} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-18} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-19} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-20} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-21} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-22} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-23} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-24} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-25} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-26} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-27} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-28} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-29} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-30} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-31} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-32} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-33} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-34} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-35} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-36} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-37} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-38} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-39} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-40} \end{center}
-
 \textbf{END}
@@
 \begin{verbatim}
-2024-03-12 15:10:56.3 athan@tyler GHI_enh_04_investigate.R 2.333127 mins
+2024-03-14 09:06:31.8 athan@tyler GHI_enh_04_investigate.R 1.124109 mins
 \end{verbatim}

### 2024-03-14 GHI_enh_06_sza.tex
Commit 2024-03-14 11:11

--- 2024-03-14 GHI_enh_04_investigate.tex
@@
 
-\begin{verbatim}
-ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
-\end{verbatim}
+\newpage
+\FloatBarrier
+
+\hypertarget{sza-enhancements}{%
+\subsubsection{SZA enhancements}\label{sza-enhancements}}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-3} \end{center}
 
@@
 
-\hypertarget{daily-trends}{%
-\subsubsection{Daily Trends}\label{daily-trends}}
+\hypertarget{sza-enhancements-by-month}{%
+\subsubsection{SZA enhancements by month}\label{sza-enhancements-by-month}}
 
-\begin{verbatim}
-Warning in ans * length(l) + if1: longer object length is not a multiple of
-shorter object length
-\end{verbatim}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-1} \end{center}
 
-\newpage
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-2} \end{center}
 
-\begin{verbatim}
-Loading required package: stringr
-\end{verbatim}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-3} \end{center}
 
-\hypertarget{trends-on-daily-observations-data}{%
-\paragraph{Trends on Daily Observations data}\label{trends-on-daily-observations-data}}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-4} \end{center}
 
-Units for GLB\_diff.max : Watt/m\^{}2
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-5} \end{center}
 
-lmD: 1.566006 +/- 0.1083205
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-6} \end{center}
 
-lmY: 1.566022 +/- 0.1083224
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-7} \end{center}
 
-Arima: 1.5664 0.1467 10.6786 0
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-8} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-9} \end{center}
 
-Units for GLB\_diff.mean : Watt/m\^{}2
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-10} \end{center}
 
-lmD: 0.9508037 +/- 0.1552487
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-11} \end{center}
 
-lmY: 0.9508275 +/- 0.1552514
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-12} \end{center}
 
-Arima: 1.0223 0.2369 4.3149 0
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-13} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-2} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-14} \end{center}
 
-Units for GLB\_diff.median : Watt/m\^{}2
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-15} \end{center}
 
-lmD: 1.086985 +/- 0.1678711
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-16} \end{center}
 
-lmY: 1.087013 +/- 0.1678741
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-17} \end{center}
 
-Arima: 1.16 0.2511 4.6198 0
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-18} \end{center}
 
-Units for GLB\_diff.N :
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-19} \end{center}
 
-lmD: -0.01234536 +/- 0.1388793
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-20} \end{center}
 
-lmY: -0.01233011 +/- 0.1388818
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-21} \end{center}
 
-\begin{verbatim}
-Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
-possible convergence problem: optim gave code = 1
-\end{verbatim}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-22} \end{center}
 
-\begin{verbatim}
-Warning in sqrt(diag(se)): NaNs produced
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-23} \end{center}
 
-Warning in sqrt(diag(se)): NaNs produced
-\end{verbatim}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-24} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-3} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-25} \end{center}
 
-Arima: -0.0132 6.9042 -0.0019 0.9985
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-26} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-4} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-27} \end{center}
 
-Units for GLB\_diff.sum : kJ/m\^{}2
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-28} \end{center}
 
-lmD: 33.66024 +/- 5.69273
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-29} \end{center}
 
-lmY: 33.6608 +/- 5.692829
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-30} \end{center}
 
-Arima: 33.7214 8.8815 3.7968 1e-04
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-31} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-5} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-32} \end{center}
 
-Units for GLB\_ench.max : Watt/m\^{}2
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-33} \end{center}
 
-lmD: 0.003266044 +/- 0.0002706817
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-34} \end{center}
 
-lmY: 0.003266077 +/- 0.0002706865
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-35} \end{center}
 
-Arima: 0.0033 4e-04 9.0497 0
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-6} \end{center}
-
-Units for GLB\_ench.mean : Watt/m\^{}2
-
-lmD: 0.001714761 +/- 0.0002777697
-
-lmY: 0.001714817 +/- 0.0002777745
-
-Arima: 0.0019 5e-04 4.0604 0
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-7} \end{center}
-
-Units for GLB\_ench.median : Watt/m\^{}2
-
-lmD: 0.001677019 +/- 0.0003136298
-
-lmY: 0.001677082 +/- 0.0003136353
-
-Arima: 0.0018 5e-04 3.615 3e-04
-
-Units for GLB\_ench.N :
-
-lmD: -0.01234536 +/- 0.1388793
-
-lmY: -0.01233011 +/- 0.1388818
-
-\begin{verbatim}
-Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
-possible convergence problem: optim gave code = 1
-
-Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
-NaNs produced
-
-Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
-NaNs produced
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-8} \end{center}
-
-Arima: -0.0132 6.9042 -0.0019 0.9985
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-9} \end{center}
-
-Units for GLB\_ench.sum : Watt/m\^{}2
-
-lmD: 0.9770065 +/- 0.1439346
-
-lmY: 0.9770288 +/- 0.1439371
-
-Arima: 1.041 0.2186 4.7611 0
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-10} \end{center}
-
-\newpage
-
-\hypertarget{trends-on-daily-enhancements-data}{%
-\paragraph{Trends on Daily Enhancements data}\label{trends-on-daily-enhancements-data}}
-
-Units for GLB\_diff.max : Watt/m\^{}2
-
-lmD: 0.8175029 +/- 0.1034317
-
-lmY: 0.8175138 +/- 0.1034336
-
-Arima: 0.8175 0.12 6.8102 0
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-11} \end{center}
-
-Units for GLB\_diff.mean : Watt/m\^{}2
-
-lmD: 0.216071 +/- 0.03807207
-
-lmY: 0.2160751 +/- 0.03807275
-
-Arima: 0.2161 0.0414 5.2169 0
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-12} \end{center}
-
-Units for GLB\_diff.median : Watt/m\^{}2
-
-lmD: 0.190931 +/- 0.03787542
-
-lmY: 0.1909357 +/- 0.03787609
-
-Arima: 0.1909 0.0401 4.7631 0
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-13} \end{center}
-
-Units for GLB\_diff.N :
-
-lmD: 0.4856759 +/- 0.04638817
-
-lmY: 0.4856822 +/- 0.046389
-
-Arima: 0.4857 0.0552 8.802 0
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-14} \end{center}
-
-Units for GLB\_diff.sum : kJ/m\^{}2
-
-lmD: 1.467857 +/- 0.1526559
-
-lmY: 1.46788 +/- 0.1526586
-
-Arima: 1.4679 0.1843 7.9642 0
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-15} \end{center}
-
-Units for GLB\_ench.max : Watt/m\^{}2
-
-lmD: 0.00133588 +/- 0.0001367161
-
-lmY: 0.001335895 +/- 0.0001367186
-
-Arima: 0.0013 2e-04 8.5089 0
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-16} \end{center}
-
-Units for GLB\_ench.mean : Watt/m\^{}2
-
-lmD: 0.0004227125 +/- 5.903165e-05
-
-lmY: 0.0004227187 +/- 5.90327e-05
-
-Arima: 4e-04 1e-04 6.2905 0
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-17} \end{center}
-
-Units for GLB\_ench.median : Watt/m\^{}2
-
-lmD: 0.0003723972 +/- 6.132751e-05
-
-lmY: 0.0003724038 +/- 6.13286e-05
-
-Arima: 4e-04 1e-04 5.4462 0
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-18} \end{center}
-
-Units for GLB\_ench.N :
-
-lmD: 0.4856759 +/- 0.04638817
-
-lmY: 0.4856822 +/- 0.046389
-
-Arima: 0.4857 0.0552 8.802 0
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-19} \end{center}
-
-Units for GLB\_ench.sum : Watt/m\^{}2
-
-lmD: 0.03656091 +/- 0.003621574
-
-lmY: 0.03656153 +/- 0.003621638
-
-Arima: 0.0366 0.0042 8.6966 0
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-20} \end{center}
-
-\newpage
-
-\hypertarget{trends-on-daily-extreme-enhancements-data}{%
-\paragraph{Trends on Daily Extreme Enhancements data}\label{trends-on-daily-extreme-enhancements-data}}
-
-Units for GLB\_diff.max : Watt/m\^{}2
-
-lmD: 0.1872084 +/- 0.2494764
-
-lmY: 0.1872455 +/- 0.2494804
-
-Arima: 0.1718 0.3646 0.4711 0.6376
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-21} \end{center}
-
-Units for GLB\_diff.mean : Watt/m\^{}2
-
-lmD: 0.04977389 +/- 0.1925048
-
-lmY: 0.04979834 +/- 0.1925079
-
-Arima: 0.0085 0.3464 0.0247 0.9803
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-22} \end{center}
-
-Units for GLB\_diff.median : Watt/m\^{}2
-
-lmD: 0.0912485 +/- 0.1914527
-
-lmY: 0.09127162 +/- 0.1914558
-
-Arima: 0.05 0.3354 0.149 0.8816
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-23} \end{center}
-
-Units for GLB\_diff.N :
-
-lmD: 0.03034705 +/- 0.02124537
-
-lmY: 0.03034902 +/- 0.02124571
-
-Arima: 0.0304 0.022 1.3788 0.1679
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-24} \end{center}
-
-Units for GLB\_diff.sum : kJ/m\^{}2
-
-lmD: 0.368357 +/- 0.2534977
-
-lmY: 0.3683834 +/- 0.2535018
-
-Arima: 0.3684 0.2583 1.4266 0.1537
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-25} \end{center}
-
-Units for GLB\_ench.max : Watt/m\^{}2
-
-lmD: 0.0005084984 +/- 0.0002811406
-
-lmY: 0.0005085061 +/- 0.0002811451
-
-Arima: 5e-04 3e-04 1.5978 0.1101
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-26} \end{center}
-
-Units for GLB\_ench.mean : Watt/m\^{}2
-
-lmD: 0.000356478 +/- 0.0002141255
-
-lmY: 0.0003564771 +/- 0.0002141289
-
-Arima: 3e-04 3e-04 1.3203 0.1867
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-27} \end{center}
-
-Units for GLB\_ench.median : Watt/m\^{}2
-
-lmD: 0.0003987357 +/- 0.0002210796
-
-lmY: 0.0003987361 +/- 0.0002210831
-
-Arima: 4e-04 3e-04 1.4505 0.1469
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-28} \end{center}
-
-Units for GLB\_ench.N :
-
-lmD: 0.03034705 +/- 0.02124537
-
-lmY: 0.03034902 +/- 0.02124571
-
-Arima: 0.0304 0.022 1.3788 0.1679
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-29} \end{center}
-
-Units for GLB\_ench.sum : Watt/m\^{}2
-
-lmD: 0.008776338 +/- 0.005506711
-
-lmY: 0.00877684 +/- 0.005506799
-
-Arima: 0.0088 0.0057 1.5378 0.1241
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-30} \end{center}
-
-\newpage
-\FloatBarrier
-
-\hypertarget{group-stats}{%
-\subsubsection{Group stats}\label{group-stats}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-1} \end{center}
-
-\begin{verbatim}
-Warning in scale_y_log10(): log-10 transformation introduced infinite values.
-\end{verbatim}
-
-\begin{verbatim}
-Warning: Removed 25 rows containing missing values or values outside the scale
-range (`geom_bar()`).
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-2} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-36} \end{center}
 
@@
 
-\begin{verbatim}
-Warning: The S3 guide system was deprecated in ggplot2 3.5.0.
-i It has been replaced by a ggproto system that can be extended.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-37} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-38} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-39} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-6} \end{center}
-
-\hypertarget{zhang2018}{%
-\subsection{@Zhang2018}\label{zhang2018}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8} \end{center}
-
-\begin{verbatim}
-Scale for x is already present.
-Adding another scale for x, which will replace the existing scale.
-\end{verbatim}
-
-\begin{verbatim}
-Warning: Removed 5 rows containing non-finite outside the scale range
-(`stat_bin2d()`).
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9} \end{center}
-
-\begin{verbatim}
-Scale for x is already present.
-Adding another scale for x, which will replace the existing scale.
-\end{verbatim}
-
-\begin{verbatim}
-Warning: Removed 5 rows containing non-finite outside the scale range
-(`stat_bin2d()`).
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-10} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_N_doy-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCEmonth-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_N-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N-1} \end{center}
-
-\begin{verbatim}
-Warning: The `fun.y` argument of `stat_summary()` is deprecated as of ggplot2 3.3.0.
-i Please use the `fun` argument instead.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCE_daily-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCE_week-1} \end{center}
-
-\newpage
-\FloatBarrier
-
-\hypertarget{energy-contribution-of-enhancements}{%
-\subsubsection{Energy contribution of enhancements}\label{energy-contribution-of-enhancements}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-3} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-7} \end{center}
-
-@Martins2022
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-8} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-3} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-40} \end{center}
 
@@
 \begin{verbatim}
-2024-03-14 09:06:31.8 athan@tyler GHI_enh_04_investigate.R 1.124109 mins
+2024-03-14 09:10:56.9 athan@tyler GHI_enh_06_sza.R 0.671435 mins
 \end{verbatim}

### 2024-03-14 GHI_enh_06_sza.R
Commit 2024-03-14 11:11

@@ -1,0 +1,314 @@
+# /* #!/usr/bin/env Rscript */
+# /* Copyright (C) 2022 Athanasios Natsis <natsisphysicist@gmail.com> */
+#' ---
+#' title:         "Enhancement of SDR in Thessaloniki "
+#' author:
+#'   - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisphysicist@gmail.com]
+#'   - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
+#' abstract:
+#'   "Study of GHI enchantment."
+#'
+#' documentclass:  article
+#' classoption:    a4paper,oneside
+#' fontsize:       10pt
+#' geometry:       "left=0.5in,right=0.5in,top=0.5in,bottom=0.5in"
+#' link-citations: yes
+#' colorlinks:     yes
+#'
+#' header-includes:
+#' - \usepackage{caption}
+#' - \usepackage{placeins}
+#' - \captionsetup{font=small}
+#'
+#' output:
+#'   bookdown::pdf_document2:
+#'     number_sections: no
+#'     fig_caption:     no
+#'     keep_tex:        yes
+#'     latex_engine:    xelatex
+#'     toc:             yes
+#'     toc_depth:       4
+#'     fig_width:       7
+#'     fig_height:      4.5
+#'   html_document:
+#'     toc:             true
+#'     keep_md:         yes
+#'     fig_width:       7
+#'     fig_height:      4.5
+#'
+#' date: "`r format(Sys.time(), '%F')`"
+#'
+#' ---
+
+#+ echo=F, include=T
+
+
+## __ Document options ---------------------------------------------------------
+
+#+ echo=F, include=F
+knitr::opts_chunk$set(comment    = ""       )
+knitr::opts_chunk$set(dev        = c("pdf", "png"))
+# knitr::opts_chunk$set(dev        = "png"    )
+knitr::opts_chunk$set(out.width  = "100%"   )
+knitr::opts_chunk$set(fig.align  = "center" )
+knitr::opts_chunk$set(cache      =  FALSE   )  ## !! breaks calculations
+# knitr::opts_chunk$set(fig.pos    = '!h'    )
+
+
+#+ include=F, echo=F
[…]

### 2024-03-14 GHI_enh_06_sza.tex
Commit 2024-03-14 12:14

@@
 
+\begin{verbatim}
+Not changed:  ./GHI_enh_06_sza.R 
+Not changed:  ./GHI_enh_00_variables.R 
+Not changed:  ./GHI_enh_03_process.R 
+Not changed:  ./data/GHI_enh_03_process.Rda 
+\end{verbatim}
+
+\begin{verbatim}
+[1] FALSE
+\end{verbatim}
+
+\begin{verbatim}
+Written `R_make_` file: .//.R_make.mk 
+\end{verbatim}
+
 \newpage
@@
 
+\newpage
+\FloatBarrier
+
+\hypertarget{sza-heatmaps-of-doy-and-sza}{%
+\subsubsection{SZA heatmaps of DOY and SZA}\label{sza-heatmaps-of-doy-and-sza}}
+
 \begin{verbatim}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-37} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-1} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-38} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-2} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-39} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-3} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-40} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-4} \end{center}
 
@@
 \begin{verbatim}
-2024-03-14 09:10:56.9 athan@tyler GHI_enh_06_sza.R 0.671435 mins
+2024-03-14 09:41:49.6 athan@tyler GHI_enh_06_sza.R 0.259163 mins
 \end{verbatim}

### 2024-03-14 article/article.Rmd
Commit 2024-03-14 12:14

@@
 In this study, we define as cloud enhancement events (CE) the cases when the measured
-global horizontal irradiance (GHI) at ground level exceeds the expected value under
-sky, unobscured by clouds.
+global horizontal irradiance (GHI) at ground level, exceeds the expected value under
+clear-sky conditions.
 Similar, we define the extreme cloud enhancement events (ECE), the cases when GHI,
 exceeds the Total Solar Irradiance on horizontal plane at ground level.
+Although the duration of these bursts varies form instantaneous to several minutes,
+here we are constrained by the recorded data, to one-minute steps.
 
@@
 the clear sky equivalent of GHI, with monthly climatological data of AOD and water
-column from the AERONET monitoring network [@Giles2019; @Buis1998].  Our site
+column from the Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998].  Our site
 participates in AERONET, where we operate a Cimel photometer, colocated to

### 2024-03-14 GHI_enh_03_process.R
Commit 2024-03-14 13:12

@@ -220,9 +220,35 @@ my.cols <- c("wattGLB",
              "GLB_ench",
              "GLB_diff")
 
+
+
+# _ All data stats  ------------------------------------------------------------
 ST_total <- DATA[, unlist(lapply(.SD, data.summary, na.rm = TRUE),
-                        recursive = FALSE),
-               .SDcols = my.cols]
+                          recursive = FALSE),
+                 .SDcols = my.cols]
+
+ST_extreme_total <- DATA[wattGLB > ETH,
+                         unlist(lapply(.SD, data.summary, na.rm = TRUE),
+                                recursive = FALSE),
+                         .SDcols = my.cols]
+
+## convert sum Irradiance to energy
+## Σ(W/m^2) * 60 s = J/m^2
+ST_total[, GLB_diff.sum    := GLB_diff.sum    * 60 / Energy_Div]
+ST_total[, GLB_diff.sumPOS := GLB_diff.sumPOS * 60 / Energy_Div]
+ST_total[, GLB_diff.sumNEG := GLB_diff.sumNEG * 60 / Energy_Div]
+ST_total[, wattGLB.sum     := wattGLB.sum     * 60 / Energy_Div]
+ST_total[, wattGLB.sumPOS  := wattGLB.sumPOS  * 60 / Energy_Div]
+ST_total[, wattGLB.sumNEG  := wattGLB.sumNEG  * 60 / Energy_Div]
+
+ST_extreme_total[, GLB_diff.sum    := GLB_diff.sum    * 60 / Energy_Div]
+ST_extreme_total[, GLB_diff.sumPOS := GLB_diff.sumPOS * 60 / Energy_Div]
+ST_extreme_total[, GLB_diff.sumNEG := GLB_diff.sumNEG * 60 / Energy_Div]
+ST_extreme_total[, wattGLB.sum     := wattGLB.sum     * 60 / Energy_Div]
+ST_extreme_total[, wattGLB.sumPOS  := wattGLB.sumPOS  * 60 / Energy_Div]
+ST_extreme_total[, wattGLB.sumNEG  := wattGLB.sumNEG  * 60 / Energy_Div]
+
+
 
 
 # _ Daily stats  ---------------------------------------------------------------
@@ -331,9 +357,9 @@ ST_G1[, wattGLB.sum   := wattGLB.sum  * 60 / Energy_Div]
 
 
[…]

### 2024-03-14 article/article.Rmd
Commit 2024-03-14 13:12

@@
 
+Our dataset after the proccesing consists of
+
+total data points `r ST_total$wattGLB.N`
+of which CE are `r ST_total$GLB_diff.N_pos`
+and `r ST_total$GLB_diff.N_pos`
+
 \FloatBarrier
@@
 
+```{r loadtrends, echo=F, include=T, warning=FALSE, message=FALSE}
+dailytrends <- data.table(
+  read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear.csv"))
+dailytrends[DATA == "ST_E_daily"]
+
+```
+
+By computing the mean daily over irradiance for all the CE case, we were able to dirive a trend on the mean CE intensity of .....
+
+Figures\ \ref{fig:CEmeanDaily}
+
 ## Trend
 
-```{r echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"}
+```{r CEmeanDaily, echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"}
 knitr::include_graphics("../images/daily-12.png")

### 2024-03-14 GHI_enh_03_process.tex
Commit 2024-03-14 13:12
Commit 2024-03-14 14:16

--- 2024-03-01 GHI_enh_03_process.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-01}
+\date{2024-03-14}
 
@@
 ST_extreme_SZA
+ST_extreme_SZA_doy
 ST_extreme_SZA_monthly
+ST_extreme_total
 ST_extreme_yearly
@@
 \begin{verbatim}
-2024-03-01 17:32:55.6 athan@tyler GHI_enh_03_process.R 2.076944 mins
+2024-03-14 11:20:40.3 athan@tyler GHI_enh_03_process.R 3.214359 mins
 \end{verbatim}

### 2024-03-14 article/article.Rmd
Commit 2024-03-14 17:10

@@
 total data points `r ST_total$wattGLB.N`
+
 of which CE are `r ST_total$GLB_diff.N_pos`
-and `r ST_total$GLB_diff.N_pos`
+
+and `r ST_extreme_total$GLB_diff.N_pos` are ECE
+
+```{r echo=F, include=T, warning=FALSE, message=FALSE}
+ST_total
+
+cat("\n - - - \n")
+
+ST_extreme_total
+
+```
 

### 2024-03-14 GHI_enh_06_sza.tex
Commit 2024-03-14 21:11

@@
 \begin{verbatim}
-
-Attaching package: 'zoo'
-\end{verbatim}
-
-\begin{verbatim}
-The following objects are masked from 'package:data.table':
-
-    yearmon, yearqtr
-\end{verbatim}
-
-\begin{verbatim}
-The following objects are masked from 'package:base':
-
-    as.Date, as.Date.numeric
-\end{verbatim}
-
-\begin{verbatim}
 Not changed:  ./GHI_enh_06_sza.R 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza-1} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-2} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza-2} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-3} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza-3} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-1} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-2} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-2} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-3} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-3} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-4} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-4} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-5} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-5} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-6} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-6} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-7} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-7} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-8} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-8} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-9} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-9} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-10} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-10} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-11} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-11} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-12} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-12} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-13} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-13} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-14} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-14} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-15} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-15} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-16} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-16} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-17} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-17} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-18} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-18} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-19} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-19} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-20} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-20} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-21} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-21} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-22} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-22} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-23} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-23} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-24} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-24} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-25} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-25} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-26} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-26} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-27} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-27} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-28} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-28} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-29} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-29} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-30} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-30} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-31} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-31} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-32} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-32} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-33} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-33} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-34} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-34} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-35} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-35} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-36} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-36} \end{center}
 
@@
 
-\begin{verbatim}
-Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
-i Please use the `legend.position.inside` argument of `theme()` instead.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_doy-1} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_doy-2} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-2} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_doy-3} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-3} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-4} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_doy-4} \end{center}
 
@@
 \begin{verbatim}
-2024-03-14 09:41:49.6 athan@tyler GHI_enh_06_sza.R 0.259163 mins
+2024-03-14 19:08:05.8 athan@tyler GHI_enh_06_sza.R 0.401094 mins
 \end{verbatim}

### 2024-03-15 article/article.Rmd
Commit 2024-03-15 09:10

@@
 
-Our dataset after the proccesing consists of
-
-total data points `r ST_total$wattGLB.N`
-
-of which CE are `r ST_total$GLB_diff.N_pos`
-
-and `r ST_extreme_total$GLB_diff.N_pos` are ECE
+Our dataset, after the data selection processing, consists of
+`r ST_total$wattGLB.N` records of GHI, of which  
+$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\%$ are CE and
+$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\%$ are ECE.
+The stronger highest
 
@@
 
-ST_extreme_total
+ST_daily[max(wattGLB.max,na.rm = T), ]
+
+ST_daily[max(GLB_diff.max,na.rm = T), ]
 

### 2024-03-15 article/article.Rmd
Commit 2024-03-15 10:14

--- 2024-03-14 article/article.Rmd
@@
 
-Our dataset after the proccesing consists of
-
-total data points `r ST_total$wattGLB.N`
-of which CE are `r ST_total$GLB_diff.N_pos`
-and `r ST_total$GLB_diff.N_pos`
+<!-- ```{r echo=F, include=T, warning=FALSE, message=FALSE} -->
+<!-- ST_total -->
+<!-- cat("\n - - - \n") -->
+<!-- ST_daily[which.max(wattGLB.max), wattGLB.max] -->
+<!-- round(ST_E_daily[which.max(GLB_diff.max), GLB_diff.max], 2) -->
+<!-- round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1) -->
+<!-- plot(ST_daily$Date, ST_daily$GLB_diff.max) -->
+<!-- ``` -->
 
@@
 # Results
+
+Our dataset, after the data selection processing, consists of
+`r ST_total$wattGLB.N` records of GHI, of which
+$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are CE and
+$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are ECE events.
+The highest GHI recorder was 
+$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,W/m^2$
+on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`.
+The absolute stronger CE event had an over irradiance of 
+$`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,W/m^2$ on
+`r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`.
+The relative stronger CE event was 
+$`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 
+clear sky threshold, on 
+`r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.
 

### 2024-03-15 article/article.Rmd
Commit 2024-03-15 12:14

@@
 
-```{r CEmeanDaily, echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"}
-knitr::include_graphics("../images/daily-12.png")
+```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean trend of CE over irradiance."}
+knitr::include_graphics("../images/P_daily_trend-1.png")
 ```
+
+# ```{r CEmeanDaily2, echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"}
+# knitr::include_graphics("../images/daily-12.png")
+# ```
 

### 2024-03-15 GHI_enh_04_investigate.tex
Commit 2024-03-15 12:14
Commit 2024-03-15 13:12

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-14}
+\date{2024-03-15}
 
@@
 
-lmD: 1.566006 +/- 0.1083205
+lmD: 1.566006 +/- 0.108321
 
-lmY: 1.566022 +/- 0.1083224
+lmY: 1.566022 +/- 0.108322
 
-Arima: 1.5664 0.1467 10.6786 0
+Arima: 1.566405 +/- 0.146687
 
@@
 
-lmD: 0.9508037 +/- 0.1552487
+lmD: 0.950804 +/- 0.155249
 
-lmY: 0.9508275 +/- 0.1552514
+lmY: 0.950827 +/- 0.155251
 
-Arima: 1.0223 0.2369 4.3149 0
+Arima: 1.022268 +/- 0.236917
 
@@
 
-lmD: 1.086985 +/- 0.1678711
+lmD: 1.086985 +/- 0.167871
 
-lmY: 1.087013 +/- 0.1678741
+lmY: 1.087013 +/- 0.167874
 
-Arima: 1.16 0.2511 4.6198 0
+Arima: 1.159971 +/- 0.251086
 
@@
 
-lmD: -0.01234536 +/- 0.1388793
+lmD: -0.012345 +/- 0.138879
 
-lmY: -0.01233011 +/- 0.1388818
+lmY: -0.01233 +/- 0.138882
 
@@
 
-Arima: -0.0132 6.9042 -0.0019 0.9985
+Arima: -0.013183 +/- 6.904159
 
@@
 
-Arima: 33.7214 8.8815 3.7968 1e-04
+Arima: 33.721354 +/- 8.881459
 
@@
 
-lmD: 0.003266044 +/- 0.0002706817
+lmD: 0.003266 +/- 0.000271
 
-lmY: 0.003266077 +/- 0.0002706865
+lmY: 0.003266 +/- 0.000271
 
-Arima: 0.0033 4e-04 9.0497 0
+Arima: 0.003291 +/- 0.000364
 
@@
 
-lmD: 0.001714761 +/- 0.0002777697
+lmD: 0.001715 +/- 0.000278
 
-lmY: 0.001714817 +/- 0.0002777745
+lmY: 0.001715 +/- 0.000278
 
-Arima: 0.0019 5e-04 4.0604 0
+Arima: 0.001886 +/- 0.000465
 
@@
 
-lmD: 0.001677019 +/- 0.0003136298
+lmD: 0.001677 +/- 0.000314
 
-lmY: 0.001677082 +/- 0.0003136353
+lmY: 0.001677 +/- 0.000314
 
-Arima: 0.0018 5e-04 3.615 3e-04
+Arima: 0.001849 +/- 0.000512
 
@@
 
-lmD: 0.9770065 +/- 0.1439346
+lmD: 0.977006 +/- 0.143935
 
-lmY: 0.9770288 +/- 0.1439371
+lmY: 0.977029 +/- 0.143937
 
-Arima: 1.041 0.2186 4.7611 0
+Arima: 1.040956 +/- 0.218636
 
@@
 
-lmD: 0.8175029 +/- 0.1034317
+lmD: 0.817503 +/- 0.103432
 
-lmY: 0.8175138 +/- 0.1034336
+lmY: 0.817514 +/- 0.103434
 
-Arima: 0.8175 0.12 6.8102 0
+Arima: 0.817505 +/- 0.120041
 
@@
 
-lmD: 0.216071 +/- 0.03807207
+lmD: 0.216071 +/- 0.038072
 
-lmY: 0.2160751 +/- 0.03807275
+lmY: 0.216075 +/- 0.038073
 
-Arima: 0.2161 0.0414 5.2169 0
+Arima: 0.216075 +/- 0.041418
 
@@
 
-lmD: 0.190931 +/- 0.03787542
+lmD: 0.190931 +/- 0.037875
 
-lmY: 0.1909357 +/- 0.03787609
+lmY: 0.190936 +/- 0.037876
 
-Arima: 0.1909 0.0401 4.7631 0
+Arima: 0.190936 +/- 0.040087
 
@@
 
-lmD: 0.4856759 +/- 0.04638817
+lmD: 0.485676 +/- 0.046388
 
-lmY: 0.4856822 +/- 0.046389
+lmY: 0.485682 +/- 0.046389
 
-Arima: 0.4857 0.0552 8.802 0
+Arima: 0.485682 +/- 0.055179
 
@@
 
-lmD: 1.467857 +/- 0.1526559
+lmD: 1.467857 +/- 0.152656
 
-lmY: 1.46788 +/- 0.1526586
+lmY: 1.46788 +/- 0.152659
 
-Arima: 1.4679 0.1843 7.9642 0
+Arima: 1.467877 +/- 0.18431
 
@@
 
-lmD: 0.00133588 +/- 0.0001367161
+lmD: 0.001336 +/- 0.000137
 
-lmY: 0.001335895 +/- 0.0001367186
+lmY: 0.001336 +/- 0.000137
 
-Arima: 0.0013 2e-04 8.5089 0
+Arima: 0.001336 +/- 0.000157
 
@@
 
-lmD: 0.0004227125 +/- 5.903165e-05
+lmD: 0.000423 +/- 5.9e-05
 
-lmY: 0.0004227187 +/- 5.90327e-05
+lmY: 0.000423 +/- 5.9e-05
 
-Arima: 4e-04 1e-04 6.2905 0
+Arima: 0.000423 +/- 6.7e-05
 
@@
 
-lmD: 0.0003723972 +/- 6.132751e-05
+lmD: 0.000372 +/- 6.1e-05
 
-lmY: 0.0003724038 +/- 6.13286e-05
+lmY: 0.000372 +/- 6.1e-05
 
-Arima: 4e-04 1e-04 5.4462 0
+Arima: 0.000372 +/- 6.8e-05
 
@@
 
-lmD: 0.03656091 +/- 0.003621574
+lmD: 0.036561 +/- 0.003622
 
-lmY: 0.03656153 +/- 0.003621638
+lmY: 0.036562 +/- 0.003622
 
-Arima: 0.0366 0.0042 8.6966 0
+Arima: 0.036562 +/- 0.004204
 
@@
 
-lmD: 0.1872084 +/- 0.2494764
+lmD: 0.187208 +/- 0.249476
 
-lmY: 0.1872455 +/- 0.2494804
+lmY: 0.187246 +/- 0.24948
 
-Arima: 0.1718 0.3646 0.4711 0.6376
+Arima: 0.171775 +/- 0.364628
 
@@
 
-lmD: 0.04977389 +/- 0.1925048
+lmD: 0.049774 +/- 0.192505
 
-lmY: 0.04979834 +/- 0.1925079
+lmY: 0.049798 +/- 0.192508
 
-Arima: 0.0085 0.3464 0.0247 0.9803
+Arima: 0.008548 +/- 0.346363
 
@@
 
-lmD: 0.0912485 +/- 0.1914527
+lmD: 0.091248 +/- 0.191453
 
-lmY: 0.09127162 +/- 0.1914558
+lmY: 0.091272 +/- 0.191456
 
-Arima: 0.05 0.3354 0.149 0.8816
+Arima: 0.049975 +/- 0.33542
 
@@
 
-lmD: 0.03034705 +/- 0.02124537
+lmD: 0.030347 +/- 0.021245
 
-lmY: 0.03034902 +/- 0.02124571
+lmY: 0.030349 +/- 0.021246
 
-Arima: 0.0304 0.022 1.3788 0.1679
+Arima: 0.030378 +/- 0.022031
 
@@
 
-lmD: 0.368357 +/- 0.2534977
+lmD: 0.368357 +/- 0.253498
 
-lmY: 0.3683834 +/- 0.2535018
+lmY: 0.368383 +/- 0.253502
 
-Arima: 0.3684 0.2583 1.4266 0.1537
+Arima: 0.36844 +/- 0.258271
 
@@
 
-lmD: 0.0005084984 +/- 0.0002811406
+lmD: 0.000508 +/- 0.000281
 
-lmY: 0.0005085061 +/- 0.0002811451
+lmY: 0.000509 +/- 0.000281
 
-Arima: 5e-04 3e-04 1.5978 0.1101
+Arima: 0.000508 +/- 0.000318
 
@@
 
-lmD: 0.000356478 +/- 0.0002141255
+lmD: 0.000356 +/- 0.000214
 
-lmY: 0.0003564771 +/- 0.0002141289
+lmY: 0.000356 +/- 0.000214
 
-Arima: 3e-04 3e-04 1.3203 0.1867
+Arima: 0.000349 +/- 0.000265
 
@@
 
-lmD: 0.0003987357 +/- 0.0002210796
+lmD: 0.000399 +/- 0.000221
 
-lmY: 0.0003987361 +/- 0.0002210831
+lmY: 0.000399 +/- 0.000221
 
-Arima: 4e-04 3e-04 1.4505 0.1469
+Arima: 0.000392 +/- 0.00027
 
@@
 
-lmD: 0.008776338 +/- 0.005506711
+lmD: 0.008776 +/- 0.005507
 
-lmY: 0.00877684 +/- 0.005506799
+lmY: 0.008777 +/- 0.005507
 
-Arima: 0.0088 0.0057 1.5378 0.1241
+Arima: 0.008799 +/- 0.005722
 
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-30} \end{center}
+
+Arima: 0.216075 +/- 0.041418
+
+\begin{verbatim}
+Warning: The S3 guide system was deprecated in ggplot2 3.5.0.
+i It has been replaced by a ggproto system that can be extended.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_daily_trend-1} \end{center}
 
@@
 i Please use the `legend.position.inside` argument of `theme()` instead.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
-
-\begin{verbatim}
-Warning: The S3 guide system was deprecated in ggplot2 3.5.0.
-i It has been replaced by a ggproto system that can be extended.
 This warning is displayed once every 8 hours.
@@
 
+Arima: 354.314467 +/- 35.576408
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-1} \end{center}
+
+Arima: 127.193673 +/- 11.405953
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-2} \end{center}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-1} \end{center}
@@
 \begin{verbatim}
-2024-03-14 09:06:31.8 athan@tyler GHI_enh_04_investigate.R 1.124109 mins
+2024-03-15 10:49:24.4 athan@tyler GHI_enh_04_investigate.R 1.189463 mins
 \end{verbatim}

### 2024-03-15 article/article.Rmd
Commit 2024-03-15 13:12

--- 2024-03-15 article/article.Rmd
@@
 
+## Trends
+
 ```{r loadtrends, echo=F, include=T, warning=FALSE, message=FALSE}
@@
   read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear.csv"))
-dailytrends[DATA == "ST_E_daily"]
+dailyCE <- dailytrends[DATA == "ST_E_daily"]
 
 ```
+
+We have computed the daily trend of the mean over irradiance of CE (Figure\ \ref{fig:CEmeanDaily}), using
+
+.... cite arima lag ....
+
+```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."}
+knitr::include_graphics("../images/P_daily_trend-1.png")
+```
+
+We observe an increase of
+$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate],3)`\pm
+`r round(dailyCE[var == "GLB_diff.mean", Tmod_Std..Error],3)`\,W/m^2$
+on the mean over irradiance.
 
@@
 
-```{r CEmeanDaily, echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"}
-knitr::include_graphics("../images/daily-12.png")
-```
+<!-- ```{r CEmeanDaily2, echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"} -->
+<!-- knitr::include_graphics("../images/daily-12.png") -->
+<!-- ``` -->
 

### 2024-03-15 GHI_enh_04_investigate.R

@@ -339,7 +339,7 @@ grob <- grobTree(
     label = TeX(
       paste("Trend: $", round(Tres[1], 2),
             "\\pm",     round(Tres[2], 2),
-            "\\,W/m^2$")),
+            "\\,W/m^2/day$")),
     x = 0.5,  y = 0.95, hjust = 0.5,
     gp = gpar(col = "black", fontsize = 13, fontface= "bold")
   ))
@@ -688,7 +688,7 @@ title("Climatology of CE cases per weak")
 
 
 
-##  Energy contribution of enhancements  ---------------------------------------
+## Yearly Energy contribution of enhancements  ---------------------------------------
 
 #'
 #' \newpage
@@ -699,11 +699,11 @@ title("Climatology of CE cases per weak")
 #+ energy, echo=F, include=T, results="asis"
 
 {
-  plot(ST_yearly[, GLB_diff.sumPOS, year],
-       col = varcol("GLB_diff.sumPOS"),
+  plot(ST_E_yearly[, GLB_diff.sum, year],
+       col = varcol("GLB_diff.sum"),
        ylab = "W/m^2")
 
-  lmD <- lm( ST_yearly[, year, GLB_diff.sumPOS])
+  lmD <- lm( ST_E_yearly[, year, GLB_diff.sum])
   abline(lmD)
 
   title("Over Irradiance each year due to CE")
@@ -721,9 +721,9 @@ title("Climatology of CE cases per weak")
 
 
 {
-  plot(ST_yearly[, GLB_diff.N_pos, year],
-       col = varcol("GLB_diff.sumPOS"),
-       ylab = "Total of enhancements")
+  plot(ST_E_yearly[, GLB_diff.N, year],
+       col = varcol("GLB_diff.N"),
+       ylab = "Number of enhancements")
   title("Number of CE each year")
 
   lmD <- lm( ST_yearly[, year, GLB_diff.N_pos])
@@ -760,7 +760,7 @@ title("Climatology of CE cases per weak")
 
 
 
-plot(ST_yearly[, GLB_diff.TotalN, year],
+plot(ST_yearly[, GLB_diff.mean, year],
      ylab = "Total of enhancement minutes")
 
 
@@ -788,6 +788,108 @@ plot(ST_yearly[, GLB_diff.sumPOS/wattGLB.sumPOS, year],
                   staname("wattGLB.sumPOS")
      )
 )
+
+
+
+
+
+
+
[…]

### 2024-03-15 GHI_enh_04_investigate.R
Commit 2024-03-15 14:14

@@ -718,7 +718,7 @@ title("Climatology of CE cases per weak")
 }
 
 
-
+stop()
 
 {
   plot(ST_E_yearly[, GLB_diff.N, year],
@@ -973,18 +973,18 @@ dataset |>
 #'
 #+ energy_monthly, echo=F, include=T, results="asis"
 
-viridis()
+mcol <- viridis(n = 12)
+
 
 {
   plot(ST_E_monthly[, GLB_diff.sum, Date],
        # col = varcol("GLB_diff.sum"),
-       col = ST_E_monthly$month,
+       col = mcol[ST_E_monthly$month],
        ylab = "W/m^2")
+  title("Over Irradiance Energy to CE")
 
   lmD <- lm( ST_E_monthly[, Date, GLB_diff.sum])
   abline(lmD)
-
-  title("Over Irradiance due to CE")
 
   ## display trend on graph
   fit <- lmD[[1]]
@@ -999,12 +999,13 @@ viridis()
 
 
 {
-  plot(ST_E_yearly[, GLB_diff.N, year],
-       col = varcol("GLB_diff.N"),
+  plot(ST_E_monthly[, GLB_diff.N, Date],
+       # col = varcol("GLB_diff.sum"),
+       col = mcol[ST_E_monthly$month],
        ylab = "Number of enhancements")
   title("Number of CE each year")
 
-  lmD <- lm( ST_yearly[, year, GLB_diff.N_pos])
+  lmD <- lm( ST_E_monthly[, Date, GLB_diff.N])
   abline(lmD)
 
   ## display trend on graph
@@ -1018,8 +1019,8 @@ viridis()
 
 
 {
-  plot(ST_yearly[, GLB_diff.sumPOS/GLB_diff.N_pos, year],
-       col = varcol("GLB_diff.sumPOS"),
+  plot(ST_E_monthly[, GLB_diff.sum/GLB_diff.N, Date],
+       col = mcol[ST_E_monthly$month],
        ylab = "W/m^2")
   lmD <- lm( ST_yearly[, year, GLB_diff.sumPOS/GLB_diff.N_pos])
   abline(lmD)
@@ -1038,26 +1039,26 @@ viridis()
 
 
 
-plot(ST_yearly[, GLB_diff.mean, year],
+plot(ST_E_monthly[, GLB_diff.mean, year],
      ylab = "Total of enhancement minutes")
 
 
 
-plot(ST_yearly[, GLB_ench.N, year],
[…]

### 2024-03-15 article/article.tex
Commit 2024-03-15 15:12

@@
 Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
-\date{2024-03-12}
+\date{2024-03-15}
 
@@
 \maketitle
-\begin{abstract}
-This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
-\end{abstract}
 
@@
 }
+\hypertarget{abstract}{%
+\section*{Abstract}\label{abstract}}
+\addcontentsline{toc}{section}{Abstract}
+
+\begin{itemize}
+\tightlist
+\item
+  Phenomenon
+\item
+  Effects
+\item
+  bibliography
+\item
+  our approach
+\item
+  our results
+\end{itemize}
+
 CE: cloud enhancement cases one minute
@@
 
+\(\text{GHI}_\text{i}\): measured one minute global horizontal irradiance
+
+\(\text{GHI}_\text{mCSi}\): modeled clear sky one minute global horizontal irradiance
+
 \hypertarget{intro}{%
@@
 CE and ECE usefulness
+importance
+problems
+
+reported trends
+
+CE mechanism
+
+In this study, we define as cloud enhancement events (CE) the cases when the measured
+global horizontal irradiance (GHI) at ground level, exceeds the expected value under
+clear-sky conditions.
+Similar, we define the extreme cloud enhancement events (ECE), the cases when GHI,
+exceeds the Total Solar Irradiance on horizontal plane at ground level.
+Although the duration of these bursts varies form instantaneous to several minutes,
+here we are constrained by the recorded data, to one-minute steps.
 
@@
 
-\ldots.identification methods from bib\ldots.
+Identification methods from bib
 
@@
 
-\ldots..constrains of the site\ldots..
+Constrains of the site
 
@@
 
+\hypertarget{ghi-data}{%
+\subsection{GHI data}\label{ghi-data}}
+
+Our monitoring site is operating in the Laboratory of Atmospheric Physics of the
+Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
+\(22^\circ\,57'\,\)E, \(80\,\)m~a.s.l.).
+In this study we present data from the period
+13~April 1993 to
+31~December 2023.
+
+The GHI data were measured with a Kipp~\& Zonen CM-21 pyranometer.
+During the study period, the pyranometer was independently calibrated three times at
+the Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of
+the instrument's sensitivity was better than \(0.7\%\) relative to the initial
+calibration by the manufacturer.
+
+For the acquisition of radiometric data, the signal of the pyranometer was sampled
+at a rate of \(1\,\text{Hz}\).
+The mean and the standard deviation of these samples were calculated and recorded
+every minute.
+The measurements were corrected for the zero offset (``dark signal'' in volts), which
+was calculated by averaging all measurements recorded for a period of \(3\,\text{h}\),
+before (morning) or after (evening) the Sun reaches an elevation angle of \(-10^\circ\).
+The signal was converted to irradiance using a ramped value of the instrument's
+sensitivity between subsequent calibrations.
+
+To further improve the quality of the irradiance data, a manual screening was
+performed to remove inconsistent and erroneous recordings that can occur
+stochastically or systematically during the continuous operation of the instruments.
+The manual screening was aided by a radiation data quality assurance procedure,
+adjusted for the site, which was based on the methods of Long and Shi~(Long and Shi 2006, 2008).
+Thus, problematic recordings have been excluded from further processing.
+Although it is impossible to detect all false data, the large number of available
+data, and the aggregation scheme we used, ensures the quality of the radiation
+measurements used in this study.
+
+To preserve an unbiased representation of the data we applied a constrain similar
+the one used by Castillejo-Cuberos and Escobar (2020). Where, for each valid hour of day, there
+must exist at list 45 minutes of valid measurements, including night time near
+sunrise and sunset. Days with less than 5 valid hours are rejected completely.
+Furthermore, due to the significant measurement uncertainty when the Sun is near the
+horizon, and to some systematic obstructions by nearby buildings, we have excluded
+all measurements with solar zenith angle (SZA) greater than \(78^\circ\).
+
+In this study, we evaluated the effects of the clouds on th
+
 \begin{itemize}
 \tightlist
-\item
-  measured data
 \item
@@
 Thus we will refer to this time scale as a cloud enhancement event (CE).
-Due to the instruments response time\ldots..
-
-\hypertarget{data-quality-control}{%
-\subsection{Data quality control}\label{data-quality-control}}
-
-.. todo \ldots{}
-
-\hypertarget{data-selection}{%
-\subsection{Data selection}\label{data-selection}}
-
-To preserve an unbiased representation of the data we applied a constrain similar the one used by Castillejo-Cuberos and Escobar (2020).
-Where, for each valid hour of day, there must exist at list 45 minutes of valid measurements, including night time near sunrise and sunset.
-Days with less than 5 valid hours are rejected completely.
-Furthermore, due to a systematic obstruction of the horizon and the significant measurement uncertainty on large SZAs, we excluded all data with \(SZA > 78^\circ\).
 
@@
 
-In order to set a threshold for the CE we had to create an approximation of ``clear sky'' radiation for the whole period.
-For this reason, we decided to use the Libradtran model (Emde et al.
-2016), with monthly climatological data for AOD and water column from AERONET (Giles et al.
-2019; Buis et al.
-1998).
-Our site is part of AERONET monitoring network and operates a Cimel photometer since 2003.
-We also use the Sun's total solar irradiance from NOAA (Coddington et al. 2005) and Earth - Sun distance calculated by Astropy (Astropy Collaboration et al. 2022).
-We have simulated the solar radiation spectrum of Kurucz (1994) in the range \(280\) to \(2500\,\text{nm}\), on \(0.2^\circ\) SZA's step.
-With combinations of AOD at \(500\,\text{nm}\) (\(t_{500\text{nm}}\)) and additional offsets of \(\pm1\) and \(\pm2\sigma\), water column (\(w_h\)) with offsets of \(\pm1\) and \(\pm2\sigma\), and for two atmospheric profiles ``AFGL atmospheric constituent profile, midlatitude summer'' (afglms) and ``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw) (Anderson et al.
-1986).
+In order to identify CE cases, we need an approximation of the expected clear sky GHI
+for the whole period of the study, with a temporal resolution of one minute. Because
+of the lack of exact data about atmospheric factors, responsible for the attenuation
+of the solar radiation in the atmosphere, we can not recreate a minute by minute
+representation of the reference radiation. Thus, we used some climatological data
+with a radiation transfer model.
+
+We decided to use the Libradtran (Emde et al. 2016) radiation transfer model, to modeled
+the clear sky equivalent of GHI, with monthly climatological data of AOD and water
+column from the Aerosol Robotic Network (AERONET) (Giles et al. 2019; Buis et al. 1998). Our site
+participates in AERONET, where we operate a Cimel photometer, colocated to
+the CM-21 pyranometer, since 2003
+
+For the production of \ldots..
+
+We also used the Sun's total solar irradiance from NOAA (Coddington et al. 2005) and the
+Earth - Sun distance calculated by Astropy (Astropy Collaboration et al. 2022). We simulated
+the clear sky radiation, using the solar radiation spectrum of Kurucz (1994) in the
+range \(280\) to \(2500\,\text{nm}\), with a SZA step of \(0.2^\circ\). For the
+atmospheric characteristics, we used combinations of AOD at \(500\,\text{nm}\)
+(\(t_{500\text{nm}}\)) and additional offsets of \(\pm1\) and \(\pm2\sigma\), water column
+(\(w_h\)) with offsets of \(\pm1\) and \(\pm2\sigma\), and applied it to two atmospheric
+profiles ``AFGL atmospheric constituent profile, midlatitude summer'' (afglms) and
+``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw) (Anderson et al. 1986).
+Thus, we were able to emulate different atmospheric condition and level of
+atmospheric clearness for the climatological conditions of the site.
+
+Furthermore, to account for the Sun's variability in our one-minute GHI measurements,
+we adjusted the model's input spectrum integral to the one of the the TSI provided by
+NOAA. Finally, we adjusted for the effect of the Sun - Earth distance, and
+calculated the clear sky irradiance value at the horizontal plane by using the cosine
+of the corresponding interpolated SZA. For each period of the year, we used the
+appropriate atmospheric profile (afglms or afglmw). Thus, the modelled GHI\_modeld we
+can directly compare each measured one minute value of GHI, with the expected clear
+sky radiation.
+
+\begin{itemize}
+\tightlist
+\item
+  rte\_solver disort
+\item
+  geometry pseudospherical
+\item
+  mol\_abs LOWTRAN
+\end{itemize}
+
+Of course, have to choose which atmospheric conditions qualify as a good clear sky analogous radiation.
 
@@
 
-For each GHI measurement in our data we calculated a reference clear sky value, by adjusting the integral of the Kurudz spectrum to the interpolated TSI from NOAA.
-We applied the effect of Sun - Earth distance, and calculated it's value to the horizontal plane by using the cosine of the corresponding interpolated SZA.
-For each period of the year, we used the appropriate atmospheric profile (afglms or afglmw).
-Thus, we can directly compare each measured one minute value of GHI, with the expected clear sky radiation.
+Which is an expected result as these values represent an typical atmosphere in Thessaloniki with low load of aerosols and humidity, which are the main factor that attenuate the GHI, excluding clouds.
 
@@
 
-To select the exact values of the threshold used (Equation \ref{eq:CE4}), we implemented manual inspection of the CE indemnification, on specially selected days from the whole dataset.
-We used seven sets of random selected days, with characteristics relevant to the efficiency of the threshold.
+The use of the actual modeled values of clear sky GHI can not provide us with a
+robust method to distinguish the CE cases, due to the limited accuracy of the input
+data. Our main focus was to positively identify over irradiance events from CEs,
+thus we used a relative factor, to create an upper envelope of the clear sky
+irradiance, above which, any GHI value can safely attributed to CE.
 
-six criteria in order to evaluate random multiples of 25 days with some characteristics
+To select the exact values of the thresholds (Equation \ref{eq:CE4}), we implemented
+manual inspection of the CE identification, on specially selected days from the whole
+dataset. We used seven sets of selected days, with characteristics relevant to the
+efficiency of the identification threshold. These sets were random groups of about
+20 to 30 days with the following characteristics:
+(a) the largest over irradiance CE events,
+(b) the largest daily total over irradiance,
+(c) without clouds (by implementing a clear sky identification algorithm as discussed in Natsis, Bais, and Meleti (2023)),
+(d) without clouds and without EC events,
+(e) with at least \(60\%\) of the day length without clouds and some EC events,
+(h) random days and
+(i) some manual selected days that were included during the manual inspection.
 
-\begin{itemize}
-\tightlist
-\item
-  20 days with the largest over irradiance CE events
-\item
-  30 days with largest total over irradiance
-\item
-  20 days without clouds (CSid) Natsis, Bais, and Meleti (2023)
-\item
-  any day without clouds and EC events
-\item
-  20 days with at least 60\% of day length without clouds and some EC events
-\item
-  30 random days
-\item
-  some manual selected days that were included during the manual inspection
-\end{itemize}
+Where it was needed, for some of edge cases, we also used images from a sky-cam,
+along with the manual inspection.
 
-For some of this edge cases we further use images from a sky-cam, in order to evaluate our selection of the thresholds.
-
-Thresholds by inspecting a selection of days with some specs\ldots\ldots{}
-
-Reasoning for the selection\ldots\ldots\ldots..
+Reasoning for the final selection\ldots\ldots\ldots..
 
@@
 
-\hypertarget{trend}{%
-\subsection{Trend}\label{trend}}
+Our dataset, after the data selection processing, consists of
+6144534 records of GHI, of which
+\(1.799\,\%\) are CE and
+\(0.036\,\%\) are ECE events.
+The highest GHI recorder was
+\(1416.6\,W/m^2\)
+on 24~May 2007.
+The absolute stronger CE event had an over irradiance of
+\(341.79\,W/m^2\) on
+15~May 2014.
+The relative stronger CE event was
+\(54\,\%\) above the
+clear sky threshold, on
+28~October 2016.
+
+\hypertarget{trends}{%
+\subsection{Trends}\label{trends}}
+
+We have computed the daily trend of the mean over irradiance of CE (Figure~\ref{fig:CEmeanDaily}), using
+
+\ldots. cite arima lag \ldots.
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/daily-12}
+{\centering \includegraphics[width=0.7\linewidth]{../images/P_daily_trend-1}
 
@@
 
-\caption{Trend of the daily excess energy due to CE}(\#fig:unnamed-chunk-1)
+\caption{Daily mean values and trend of the CE over irradiance.}(\#fig:CEmeanDaily)
 \end{figure}
+
+We observe an increase of
+\(0.216\pm 0.041\,W/m^2\)
+on the mean over irradiance.
+
+By computing the mean daily over irradiance for all the CE case, we were able to dirive a trend on the mean CE intensity of \ldots..
+
+Figures~\ref{fig:CEmeanDaily}
+
+\hypertarget{trend}{%
+\subsection{Trend}\label{trend}}
 
@@
 
-\caption{Treds of the mean over irradiance per CE}(\#fig:unnamed-chunk-2)
+\caption{Treds of the mean over irradiance per CE}(\#fig:unnamed-chunk-1)
 \end{figure}
@@
 
-\caption{Trend of number of CE cases}(\#fig:unnamed-chunk-3)
+\caption{Trend of number of CE cases}(\#fig:unnamed-chunk-2)
 \end{figure}
@@
 
-\caption{Trend of the yearly excess energy due to CE over irradiance}(\#fig:unnamed-chunk-4)
+\caption{Trend of the yearly excess energy due to CE over irradiance}(\#fig:unnamed-chunk-3)
 \end{figure}
@@
 
-\caption{Distribution of the number of CE cases}(\#fig:unnamed-chunk-5)
+\caption{Distribution of the number of CE cases}(\#fig:unnamed-chunk-4)
 \end{figure}
@@
 
-\caption{Distribution of CE above reference}(\#fig:unnamed-chunk-6)
+\caption{Distribution of CE above reference}(\#fig:unnamed-chunk-5)
 \end{figure}
@@
 
-\caption{Distribution of CE groups}(\#fig:unnamed-chunk-7)
+\caption{Distribution of CE groups}(\#fig:unnamed-chunk-6)
 \end{figure}
@@
 
-\caption{Relation of mean over irradiance and CE group duration}(\#fig:unnamed-chunk-8)
+\caption{Relation of mean over irradiance and CE group duration}(\#fig:unnamed-chunk-7)
 \end{figure}
@@
 
-\caption{Relation of maximun over irradiance and CE group duration}(\#fig:unnamed-chunk-9)
+\caption{Relation of maximun over irradiance and CE group duration}(\#fig:unnamed-chunk-8)
 \end{figure}
@@
 
-\caption{Distribution of the number of ECE cases}(\#fig:unnamed-chunk-10)
+\caption{Distribution of the number of ECE cases}(\#fig:unnamed-chunk-9)
 \end{figure}
@@
 
-\caption{Distribution of ECE above 'clear sky' reference}(\#fig:unnamed-chunk-11)
+\caption{Distribution of ECE above 'clear sky' reference}(\#fig:unnamed-chunk-10)
 \end{figure}
@@
 
-\caption{Distribution of ECE Irradiance above 'TSI'}(\#fig:unnamed-chunk-12)
+\caption{Distribution of ECE Irradiance above 'TSI'}(\#fig:unnamed-chunk-11)
 \end{figure}
@@
 
-\caption{Distribution of }(\#fig:unnamed-chunk-13)
+\caption{Distribution of }(\#fig:unnamed-chunk-12)
 \end{figure}
@@
 
-\caption{Distribution of }(\#fig:unnamed-chunk-14)
+\caption{Distribution of }(\#fig:unnamed-chunk-13)
 \end{figure}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Long2006}{}}%
+Long, Charles N., and Y.
+Shi.
+2006.
+{``The QCRad Value Added Product: Surface Radiation Measurement Quality Control Testing, Including Climatology Configurable Limits.''} DOE/SC-ARM/TR-074.
+Office of Science, Office of Biological; Environmental Research, U.S.
+Department of Energy.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Long2008a}{}}%
+---------. 2008. {``An Automated Quality Assessment and Control Algorithm for Surface Radiation Measurements.''} \emph{The Open Atmospheric Science Journal}, 23--37.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Natsis2023}{}}%

### 2024-03-15 GHI_enh_04_investigate.tex
Commit 2024-03-15 19:11

@@
     as.Date, as.Date.numeric
+\end{verbatim}
+
+\begin{verbatim}
+Registered S3 methods overwritten by 'ggpp':
+  method                  from   
+  heightDetails.titleGrob ggplot2
+  widthDetails.titleGrob  ggplot2
+\end{verbatim}
+
+\begin{verbatim}
+
+Attaching package: 'ggpp'
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:ggh4x':
+
+    stat_centroid
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:ggplot2':
+
+    annotate
+\end{verbatim}
+
+\begin{verbatim}
+Registered S3 method overwritten by 'ggpmisc':
+  method                  from   
+  as.character.polynomial polynom
 \end{verbatim}
@@
 
-Arima: 354.314467 +/- 35.576408
+lmY: 8.781482 +/- 0.831715
+
+{[}1{]} -17410.99
+{[}1{]} 8.781482
+(Intercept) dataset\$year
+-17410.988738 8.781482
+
+\begin{verbatim}
+`geom_smooth()` using formula = 'y ~ x'
+\end{verbatim}
 
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-1} \end{center}
-
-Arima: 127.193673 +/- 11.405953
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-2} \end{center}
 
@@
 
+\newpage
+\FloatBarrier
+
+\hypertarget{monthly-energy-contribution-of-enhancements}{%
+\subsubsection{Monthly Energy contribution of enhancements}\label{monthly-energy-contribution-of-enhancements}}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-3} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-6} \end{center}
+
+@Martins2022
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-7} \end{center}
+
 \textbf{END}
@@
 \begin{verbatim}
-2024-03-15 10:49:24.4 athan@tyler GHI_enh_04_investigate.R 1.189463 mins
+2024-03-15 17:07:40.1 athan@tyler GHI_enh_04_investigate.R 1.283610 mins
 \end{verbatim}

### 2024-03-15 article/article.Rmd
Commit 2024-03-15 19:11

@@
     fig_caption:      yes
-    keep_tex:         no
+    keep_tex:         yes
     latex_engine:     xelatex

### 2024-03-15 article/article.tex
Commit 2024-03-15 19:11

@@
 
-\caption{Daily mean values and trend of the CE over irradiance.}(\#fig:CEmeanDaily)
+\caption{Daily mean values and trend of the CE over irradiance.}\label{fig:CEmeanDaily}
 \end{figure}
@@
 
-\caption{Treds of the mean over irradiance per CE}(\#fig:unnamed-chunk-1)
+\caption{Treds of the mean over irradiance per CE}\label{fig:unnamed-chunk-1}
 \end{figure}
@@
 
-\caption{Trend of number of CE cases}(\#fig:unnamed-chunk-2)
+\caption{Trend of number of CE cases}\label{fig:unnamed-chunk-2}
 \end{figure}
@@
 
-\caption{Trend of the yearly excess energy due to CE over irradiance}(\#fig:unnamed-chunk-3)
+\caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 
-\caption{Distribution of the number of CE cases}(\#fig:unnamed-chunk-4)
+\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 
-\caption{Distribution of CE above reference}(\#fig:unnamed-chunk-5)
+\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 
-\caption{Distribution of CE groups}(\#fig:unnamed-chunk-6)
+\caption{Distribution of CE groups}\label{fig:unnamed-chunk-6}
 \end{figure}
@@
 
-\caption{Relation of mean over irradiance and CE group duration}(\#fig:unnamed-chunk-7)
+\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-7}
 \end{figure}
@@
 
-\caption{Relation of maximun over irradiance and CE group duration}(\#fig:unnamed-chunk-8)
+\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-8}
 \end{figure}
@@
 
-\caption{Distribution of the number of ECE cases}(\#fig:unnamed-chunk-9)
+\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-9}
 \end{figure}
@@
 
-\caption{Distribution of ECE above 'clear sky' reference}(\#fig:unnamed-chunk-10)
+\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-10}
 \end{figure}
@@
 
-\caption{Distribution of ECE Irradiance above 'TSI'}(\#fig:unnamed-chunk-11)
+\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-11}
 \end{figure}
@@
 
-\caption{Distribution of }(\#fig:unnamed-chunk-12)
+\caption{Distribution of }\label{fig:unnamed-chunk-12}
 \end{figure}
@@
 
-\caption{Distribution of }(\#fig:unnamed-chunk-13)
+\caption{Distribution of }\label{fig:unnamed-chunk-13}
 \end{figure}

### 2024-03-15 GHI_enh_04_investigate.tex
Commit 2024-03-15 20:14
Commit 2024-03-15 21:12

@@
 
-lmY: 8.781482 +/- 0.831715
-
-{[}1{]} -17410.99
-{[}1{]} 8.781482
-(Intercept) dataset\$year
--17410.988738 8.781482
-
-\begin{verbatim}
-`geom_smooth()` using formula = 'y ~ x'
-\end{verbatim}
+lmY: 341.6364 +/- 36.57038
 
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-1} \end{center}
+
+lmY: 122.2229 +/- 11.42113
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-2} \end{center}
+
+lmY: 0.232986 +/- 0.055703
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-3} \end{center}
 
@@
 \begin{verbatim}
-2024-03-15 17:07:40.1 athan@tyler GHI_enh_04_investigate.R 1.283610 mins
+2024-03-15 18:54:55.8 athan@tyler GHI_enh_04_investigate.R 1.392723 mins
 \end{verbatim}

### 2024-03-15 article/article.Rmd
Commit 2024-03-15 21:12

@@
 
+```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"}
+knitr::include_graphics("../images/P_energy-3.pdf")
+```
+
 ```{r echo=FALSE, fig.cap="Trend of number of CE cases"}
@@
 
+```{r echo=FALSE, fig.cap="Trend of number of CE cases"}
+knitr::include_graphics("../images/P_energy-2.pdf")
+```
+
 ```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
 knitr::include_graphics("../images/energy-1.png")
+```
+
+```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
+knitr::include_graphics("../images/P_energy-1.png")
 ```

### 2024-03-15 article/article.tex
Commit 2024-03-15 21:12

@@
 
+{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-3}
+
+}
+
+\caption{Treds of the mean over irradiance per CE}\label{fig:unnamed-chunk-2}
+\end{figure}
+
+\begin{figure}[h!]
+
 {\centering \includegraphics[width=0.7\linewidth]{../images/energy-2}
@@
 
-\caption{Trend of number of CE cases}\label{fig:unnamed-chunk-2}
+\caption{Trend of number of CE cases}\label{fig:unnamed-chunk-3}
+\end{figure}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-2}
+
+}
+
+\caption{Trend of number of CE cases}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 
-\caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:unnamed-chunk-3}
+\caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:unnamed-chunk-5}
+\end{figure}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-1}
+
+}
+
+\caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:unnamed-chunk-6}
 \end{figure}
@@
 
-\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-4}
+\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-7}
 \end{figure}
@@
 
-\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-5}
+\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-8}
 \end{figure}
@@
 
-\caption{Distribution of CE groups}\label{fig:unnamed-chunk-6}
+\caption{Distribution of CE groups}\label{fig:unnamed-chunk-9}
 \end{figure}
@@
 
-\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-7}
+\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-10}
 \end{figure}
@@
 
-\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-8}
+\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-11}
 \end{figure}
@@
 
-\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-9}
+\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-12}
 \end{figure}
@@
 
-\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-10}
+\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-13}
 \end{figure}
@@
 
-\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-11}
+\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-14}
 \end{figure}
@@
 
-\caption{Distribution of }\label{fig:unnamed-chunk-12}
+\caption{Distribution of }\label{fig:unnamed-chunk-15}
 \end{figure}
@@
 
-\caption{Distribution of }\label{fig:unnamed-chunk-13}
+\caption{Distribution of }\label{fig:unnamed-chunk-16}
 \end{figure}

### 2024-03-17 GHI_enh_04_investigate.tex
Commit 2024-03-16 16:14
Commit 2024-03-16 17:10
Commit 2024-03-17 22:10

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-15}
+\date{2024-03-17}
 
@@
 \begin{verbatim}
-Warning: Removed 25 rows containing missing values or values outside the scale
-range (`geom_bar()`).
+Warning: Removed 25 rows containing missing values or values outside the scale range
+(`geom_bar()`).
 \end{verbatim}
@@
 
+lmY: 0.183685 +/- 0.040872
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-8} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_multi-1} \end{center}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-1} \end{center}
@@
 \begin{verbatim}
-2024-03-15 18:54:55.8 athan@tyler GHI_enh_04_investigate.R 1.392723 mins
+2024-03-17 20:07:26.4 athan@tyler GHI_enh_04_investigate.R 1.254163 mins
 \end{verbatim}

### 2024-03-17 article/article.Rmd
Commit 2024-03-17 22:10

@@
 column from the Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998].  Our site
-participates in AERONET, where we operate a Cimel photometer, colocated to
+participates in AERONET, where we operate a Cimel photometer, collocated to
 the CM-21 pyranometer, since 2003
@@
 
-```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"}
-knitr::include_graphics("../images/energy-3.png")
-```
+<!-- ```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"} -->
+<!-- knitr::include_graphics("../images/energy-3.png") -->
+<!-- ``` -->
 
 ```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"}
-knitr::include_graphics("../images/P_energy-3.pdf")
+knitr::include_graphics("../images/P_energy-7.png")
 ```

### 2024-03-17 article/article.tex
Commit 2024-03-16 16:14
Commit 2024-03-17 22:10
Commit 2024-03-17 23:19

--- 2024-03-15 article/article.tex
@@
 Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
-\date{2024-03-15}
+\date{2024-03-17}
 
@@
 column from the Aerosol Robotic Network (AERONET) (Giles et al. 2019; Buis et al. 1998). Our site
-participates in AERONET, where we operate a Cimel photometer, colocated to
+participates in AERONET, where we operate a Cimel photometer, collocated to
 the CM-21 pyranometer, since 2003
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/energy-3}
+{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-7}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/energy-2}
+{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-6}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/energy-1}
+{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-5}
 
@@
 \caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:unnamed-chunk-3}
+\end{figure}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-8}
+
+}
+
+\caption{Trend of the yearly median over irradiance due to CE over irradiance}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 
-\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-4}
+\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 
-\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-5}
+\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-6}
 \end{figure}
@@
 
-\caption{Distribution of CE groups}\label{fig:unnamed-chunk-6}
+\caption{Distribution of CE groups}\label{fig:unnamed-chunk-7}
 \end{figure}
@@
 
-\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-7}
+\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-8}
 \end{figure}
@@
 
-\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-8}
+\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-9}
 \end{figure}
@@
 
-\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-9}
+\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-10}
 \end{figure}
@@
 
-\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-10}
+\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-11}
 \end{figure}
@@
 
-\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-11}
+\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-12}
 \end{figure}
@@
 
-\caption{Distribution of }\label{fig:unnamed-chunk-12}
+\caption{Distribution of }\label{fig:unnamed-chunk-13}
 \end{figure}
@@
 
-\caption{Distribution of }\label{fig:unnamed-chunk-13}
+\caption{Distribution of }\label{fig:unnamed-chunk-14}
 \end{figure}

### 2024-03-17 article/article.Rmd
Commit 2024-03-17 23:19

@@
 
+<!-- ```{r echo=FALSE, fig.cap="Trend of number of CE cases"} -->
+<!-- knitr::include_graphics("../images/energy-2.png") -->
+<!-- ``` -->
+
 ```{r echo=FALSE, fig.cap="Trend of number of CE cases"}
-knitr::include_graphics("../images/energy-2.png")
+knitr::include_graphics("../images/P_energy-6.png")
 ```
 
-```{r echo=FALSE, fig.cap="Trend of number of CE cases"}
-knitr::include_graphics("../images/P_energy-2.pdf")
+<!-- ```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"} -->
+<!-- knitr::include_graphics("../images/energy-1.png") -->
+<!-- ``` -->
+
+```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
+knitr::include_graphics("../images/P_energy-5.png")
 ```
 
-```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
-knitr::include_graphics("../images/energy-1.png")
-```
-
-```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
-knitr::include_graphics("../images/P_energy-1.png")
+```{r echo=FALSE, fig.cap="Trend of the yearly median over irradiance due to CE over irradiance"}
+knitr::include_graphics("../images/P_energy-8.png")
 ```

### 2024-03-19 article/article.Rmd
Commit 2024-03-19 09:11

@@
 
-We have computed the daily trend of the mean over irradiance of CE (Figure\ \ref{fig:CEmeanDaily}), using
-
-.... cite arima lag ....
+We computed the daily trend of the mean over irradiance of CE (Figure\
+\ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
+using the 'maximum likelihood' fitting method [@Gardner1980; @Jones1980] by
+implementing the function 'arima' from the library 'stats' of the R programming
+language [@RCT2023]. The trends were reported together with the $2\sigma$ error.
+We observe an increase of
+$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate],3)`\pm
+`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error],3)`\,W/m^2$
+on the mean over irradiance.
 
@@
 
-We observe an increase of
-$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate],3)`\pm
-`r round(dailyCE[var == "GLB_diff.mean", Tmod_Std..Error],3)`\,W/m^2$
-on the mean over irradiance.
+Although, the previous result is closer to the raw data, we preferred to present the
+annual statistics, that give a more clear picture about the long term CE trends.
+Hence, we calculated the annual values from the one minute measurements.
 

### 2024-03-19 article/article.tex
Commit 2024-03-19 09:11

@@
 Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
-\date{2024-03-17}
+\date{2024-03-19}
 
@@
 
-We have computed the daily trend of the mean over irradiance of CE (Figure~\ref{fig:CEmeanDaily}), using
-
-\ldots. cite arima lag \ldots.
+We computed the daily trend of the mean over irradiance of CE (Figure\\
+\ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
+using the `maximum likelihood' fitting method (Gardner, Harvey, and Phillips 1980; Jones 1980) by
+implementing the function `arima' from the library `stats' of the R programming
+language (R Core Team 2023). The trends were reported together with the \(2\sigma\) error.
+We observe an increase of
+\(0.216\pm 0.083\,W/m^2\)
+on the mean over irradiance.
 
@@
 
-We observe an increase of
-\(0.216\pm 0.041\,W/m^2\)
-on the mean over irradiance.
+Although, the previous result is closer to the raw data, we preferred to present the
+annual statistics, that give a more clear picture about the long term CE trends.
+Hence, we calculated the annual values from the one minute measurements.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Gardner1980}{}}%
+Gardner, G., A.
+C.
+Harvey, and G.
+D.
+A.
+Phillips.
+1980.
+{``Algorithm {AS} 154: An Algorithm for Exact Maximum Likelihood Estimation of Autoregressive-Moving Average Models by Means of Kalman Filtering.''} \emph{Applied Statistics} 29 (3): 311.
+\url{https://doi.org/10.2307/2346910}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Giles2019}{}}%
@@
 \url{https://doi.org/10.5194/amt-12-169-2019}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Jones1980}{}}%
+Jones, Richard H.
+1980.
+{``Maximum Likelihood Fitting of {ARMA} Models to Time Series with Missing Observations.''} \emph{Technometrics} 22 (3): 389--95.
+\url{https://doi.org/10.1080/00401706.1980.10486171}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-RCT2023}{}}%
+R Core Team. 2023. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
+
 \end{CSLReferences}

### 2024-03-19 GHI_enh_04_investigate.R

@@ -342,7 +342,7 @@ grob <- grobTree(
   textGrob(
     label = TeX(
       paste("Trend: $", round(Tres[1], 2),
-            "\\pm",     round(Tres[2], 2),
+            "\\pm",     round(2 * Tres[2], 2),   ## showing 2 sigma!
             "\\,W/m^2/day$")),
     x = 0.5,  y = 0.95, hjust = 0.5,
     gp = gpar(col = "black", fontsize = 13, fontface= "bold")
@@ -831,7 +831,7 @@ grob <- grobTree(
   textGrob(
     label = TeX(
       paste("Trend:  $", round(lmY1$coefficients[2], 1),
-            "\\pm",     round(d2[2,2], 1),
+            "\\pm",      round(2 * d2[2,2], 1),       ## show 2 sigma
             "\\,kJ/m^2/year$")),
     x = 0.95,  y = 0.05, hjust = 1,
     gp = gpar(col = "black", fontsize = 13, fontface = "bold")
@@ -886,7 +886,7 @@ grob <- grobTree(
   textGrob(
     label = TeX(
       paste("Trend:  $", round(lmY2$coefficients[2], 1),
-            "\\pm",     round(d2[2,2], 1),
+            "\\pm",      round(2 * d2[2,2], 1),          ## show 2 sigma
             "\\,/year$")),
     x = 0.95,  y = 0.05, hjust = 1,
     gp = gpar(col = "black", fontsize = 13, fontface= "bold")
@@ -939,7 +939,7 @@ grob <- grobTree(
   textGrob(
     label = TeX(
       paste("Trend:  $", round(lmY3$coefficients[2], 1),
-            "\\pm",     round(d2[2,2], 1),
+            "\\pm",      round(2 * d2[2,2], 1),          ## show 2 sigma
             "\\,W/m^2/year$")),
     x = 0.95,  y = 0.05, hjust = 1,
     gp = gpar(col = "black", fontsize = 13, fontface= "bold")
@@ -994,7 +994,7 @@ grob <- grobTree(
   textGrob(
     label = TeX(
       paste("Trend:  $", round(lmY4$coefficients[2], 1),
-            "\\pm",     round(d2[2,2], 1),
+            "\\pm",      round(2 * d2[2,2], 1),          ## show 2 sigma
             "\\,W/m^2/year$")),
     x = 0.95,  y = 0.05, hjust = 1,
     gp = gpar(col = "black", fontsize = 13, fontface= "bold")

### 2024-03-19 article/article.Rmd
Commit 2024-03-19 11:12

@@
 dailyCE <- dailytrends[DATA == "ST_E_daily"]
+yearlytrends <- data.table(
+  read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear_Proper.csv"))
+yearlyCE <- yearlytrends[DATA == "ST_E_yearly"]
 
@@
 We observe an increase of
-$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate],3)`\pm
-`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error],3)`\,W/m^2$
+$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
+`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2$
 on the mean over irradiance.
@@
 Hence, we calculated the annual values from the one minute measurements.
-
-By computing the mean daily over irradiance for all the CE case, we were able to dirive a trend on the mean CE intensity of .....
-
-Figures\ \ref{fig:CEmeanDaily}
-
-## Trend
+The annual mean over irradiance is
+$`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm
+`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2$
+(Figure\ \ref{fig:P-energy-mean}),
+but this value is not very useful due the high
+variability of this metric.
 
@@
 
-```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"}
+```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean over irradiance per CE."}
 knitr::include_graphics("../images/P_energy-7.png")
 ```
+
+A better indicator of changes on the characteristic of CE would be the number of CE
+occurrences and the total energy of the CE over irradiance. The annual number of CE
+occurrences, shows a steady increase of
+$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
+`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,/y$
+(Figure\ \ref{fig:P-energy-N}).
 
@@
 
-```{r echo=FALSE, fig.cap="Trend of number of CE cases"}
+```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly CE number of occurancies."}
 knitr::include_graphics("../images/P_energy-6.png")
 ```
+Subsequently, the annual energy observed during CE events shows a annual increase of
+$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
+`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
+(Figure\ \ref{fig:P-energy-sum}).
 
@@
 
-```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
+```{r P-energy-sum, echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
 knitr::include_graphics("../images/P_energy-5.png")
@@
 
-```{r echo=FALSE, fig.cap="Trend of the yearly median over irradiance due to CE over irradiance"}
+```{r P-energy-median, echo=FALSE, fig.cap="Trend of the yearly median over irradiance due to CE over irradiance"}
 knitr::include_graphics("../images/P_energy-8.png")

### 2024-03-19 article/article.tex
Commit 2024-03-19 11:12

@@
 
-We computed the daily trend of the mean over irradiance of CE (Figure\\
+We computed the daily trend of the mean over irradiance of CE (Figure~
 \ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
@@
 Hence, we calculated the annual values from the one minute measurements.
-
-By computing the mean daily over irradiance for all the CE case, we were able to dirive a trend on the mean CE intensity of \ldots..
-
-Figures~\ref{fig:CEmeanDaily}
-
-\hypertarget{trend}{%
-\subsection{Trend}\label{trend}}
+The annual mean over irradiance is
+\(0.23\pm 0.11\,W/m^2\)
+(Figure~\ref{fig:P-energy-mean}),
+but this value is not very useful due the high
+variability of this metric.
 
@@
 
-\caption{Treds of the mean over irradiance per CE}\label{fig:unnamed-chunk-1}
+\caption{Trends of the mean over irradiance per CE.}\label{fig:P-energy-mean}
 \end{figure}
+
+A better indicator of changes on the characteristic of CE would be the number of CE
+occurrences and the total energy of the CE over irradiance. The annual number of CE
+occurrences, shows a steady increase of
+\(122.2\pm 22.8\,/y\)
+(Figure~\ref{fig:P-energy-N}).
 
@@
 
-\caption{Trend of number of CE cases}\label{fig:unnamed-chunk-2}
+\caption{Trend of yearly CE number of occurancies.}\label{fig:P-energy-N}
 \end{figure}
+
+Subsequently, the annual energy observed during CE events shows a annual increase of
+\(341.6\pm 73.1\,kJ/y\)
+(Figure~\ref{fig:P-energy-sum}).
 
@@
 
-\caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:unnamed-chunk-3}
+\caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:P-energy-sum}
 \end{figure}
@@
 
-\caption{Trend of the yearly median over irradiance due to CE over irradiance}\label{fig:unnamed-chunk-4}
+\caption{Trend of the yearly median over irradiance due to CE over irradiance}\label{fig:P-energy-median}
 \end{figure}
@@
 
-\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-5}
+\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-1}
 \end{figure}
@@
 
-\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-6}
+\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-2}
 \end{figure}
@@
 
-\caption{Distribution of CE groups}\label{fig:unnamed-chunk-7}
+\caption{Distribution of CE groups}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 
-\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-8}
+\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 
-\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-9}
+\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 
-\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-10}
+\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-6}
 \end{figure}
@@
 
-\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-11}
+\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-7}
 \end{figure}
@@
 
-\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-12}
+\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-8}
 \end{figure}
@@
 
-\caption{Distribution of }\label{fig:unnamed-chunk-13}
+\caption{Distribution of }\label{fig:unnamed-chunk-9}
 \end{figure}
@@
 
-\caption{Distribution of }\label{fig:unnamed-chunk-14}
+\caption{Distribution of }\label{fig:unnamed-chunk-10}
 \end{figure}

### 2024-03-19 GHI_enh_04_investigate.R
Commit 2024-03-19 11:12

@@ -822,7 +822,7 @@ yeartrends <- rbind(yeartrends,
                       linear_fit_stats(lmY1, confidence_interval = 0.99),
                       cor_test_stats(corY),
                       DATA       = "ST_E_yearly",
-                      var        = pvar,
+                      var        = pvar1,
                       N          = sum(!is.na(dataset[[pvar1]]))
                     )
 )
@@ -878,7 +878,7 @@ yeartrends <- rbind(yeartrends,
                       cor_test_stats(corY),
                       DATA       = "ST_E_yearly",
                       var        = pvar2,
-                      N          = sum(!is.na(dataset[[pvar]]))
+                      N          = sum(!is.na(dataset[[pvar2]]))
                     )
 )
 

### 2024-03-19 article/article.Rmd
Commit 2024-03-19 12:14

@@
 
-The recording of the signal is the one minute average.
+The recording of the signal is the one-minute average.
 Thus we will refer to this time scale as a cloud enhancement event (CE).
@@
 of the corresponding interpolated SZA.  For each period of the year, we used the
-appropriate atmospheric profile (afglms or afglmw).  Thus, the modelled GHI_modeld we
+appropriate atmospheric profile (afglms or afglmw).  Thus, the modeled GHI_modeled we
 can directly compare each measured one minute value of GHI, with the expected clear
@@
 
-After some evaluation of the modelled radiation in different atmospheric conditions, in relation to the GHI data, we choose as representative of the clear sky radiation, the case with $t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$.
+After some evaluation of the modeled radiation in different atmospheric conditions,
+in relation to the GHI data, we choose as representative of the clear sky radiation,
+the case with
+$t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$.
 
-Which is an expected result as these values represent an typical atmosphere in Thessaloniki with low load of aerosols and humidity, which are the main factor that attenuate the GHI, excluding clouds.
+Which is an expected result as these values represent an typical atmosphere in
+Thessaloniki with low load of aerosols and humidity, which are the main factor that
+attenuate the GHI, excluding clouds.
 
@@
 `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
-(Figure\ \ref{fig:P-energy-sum}).
+(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
+occurrences.
 
@@
 
+Another interesting aspect of the CE cases, is the seasonal cycle. In Figure\ 
+\ref{fig:relative-month-occurancies}, we have the box plot (whisker plot), where the
+values have been normalized by the highest median value, that occurs in May.
+Although the number of occurrences has a wide spread throughout the study period,
+the most active period of CE occurrences is during May and June. During the Winter
+(December -- February) the CE cases are about 25% of the maximum. The rest of the
+months the occurrences seems to ramp between the maximum and minimum.
+
+```{r relative-month-occurancies, echo=FALSE, fig.cap="Statistics of the number of CE occurancies for each month.
+The box represents the values of the low 25% percentile to 75% percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
+knitr::include_graphics("../images/clim_CE_month_norm_MAX_median_N-2.png")
+```
+
+mean rhombus
+
+<!--
 ```{r echo=FALSE, fig.cap="Distribution of the number of CE cases"}
@@
 ```
+--->
 
@@
 ```{r echo=FALSE, fig.cap="Distribution of "}
-knitr::include_graphics("../images/clim_CE_month_norm_MAX_median_N-2.png")
-```
-
-```{r echo=FALSE, fig.cap="Distribution of "}
 knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")

### 2024-03-19 article/article.Rmd
Commit 2024-03-19 13:12

@@
 ```
-
-mean rhombus
-
 <!--
@@
 
+<!-- Change color -->
+
 ```{r echo=FALSE, fig.cap="Distribution of the number of ECE cases"}
@@
 
-<!-- ```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per week"} -->
-<!-- knitr::include_graphics("../images/climCE_week-1.png") -->
-<!-- ``` -->
-
-<!-- ```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per doy"} -->
-<!-- knitr::include_graphics("../images/climCE_daily-1.png") -->
-<!-- ``` -->
-
-<!-- ```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per doy"} -->
-<!-- knitr::include_graphics("../images/clim_CE_N_doy-1.png") -->
-<!-- ``` -->
-
 ```{r echo=FALSE, fig.cap="Distribution of "}
@@
 <!-- ### Yearly plots relative to all GHI data. -->
-
 <!-- ```{r echo=FALSE, fig.cap=""} -->
@@
 <!-- ``` -->
-
 <!-- ```{r echo=FALSE, fig.cap=""} -->

### 2024-03-19 article/article.tex
Commit 2024-03-19 13:12

@@
 of the corresponding interpolated SZA. For each period of the year, we used the
-appropriate atmospheric profile (afglms or afglmw). Thus, the modelled GHI\_modeld we
+appropriate atmospheric profile (afglms or afglmw). Thus, the modeled GHI\_modeled we
 can directly compare each measured one minute value of GHI, with the expected clear
@@
 
-After some evaluation of the modelled radiation in different atmospheric conditions, in relation to the GHI data, we choose as representative of the clear sky radiation, the case with \(t_{\text{cs}} = t_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\).
+After some evaluation of the modeled radiation in different atmospheric conditions,
+in relation to the GHI data, we choose as representative of the clear sky radiation,
+the case with
+\(t_{\text{cs}} = t_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\).
 
-Which is an expected result as these values represent an typical atmosphere in Thessaloniki with low load of aerosols and humidity, which are the main factor that attenuate the GHI, excluding clouds.
+Which is an expected result as these values represent an typical atmosphere in
+Thessaloniki with low load of aerosols and humidity, which are the main factor that
+attenuate the GHI, excluding clouds.
 
@@
 \(341.6\pm 73.1\,kJ/y\)
-(Figure~\ref{fig:P-energy-sum}).
+(Figure~\ref{fig:P-energy-sum}), witch follows the trend of the number of
+occurrences.
 
@@
 
+Another interesting aspect of the CE cases, is the seasonal cycle. In Figure~
+\ref{fig:relative-month-occurancies}, we have the box plot (whisker plot), where the
+values have been normalized by the highest median value, that occurs in May.
+Although the number of occurrences has a wide spread throughout the study period,
+the most active period of CE occurrences is during May and June. During the Winter
+(December -- February) the CE cases are about 25\% of the maximum. The rest of the
+months the occurrences seems to ramp between the maximum and minimum.
+
 \begin{figure}[h!]
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/climCEmonth-1}
+{\centering \includegraphics[width=0.7\linewidth]{../images/clim_CE_month_norm_MAX_median_N-2}
 
@@
 
-\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-1}
+\caption{Statistics of the number of CE occurancies for each month.
+The box represents the values of the low 25\% percentile to 75\% percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/clim_CE_month_norm_MAX_median_N-2}
+{\centering \includegraphics[width=0.7\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}
 
@@
 \caption{Distribution of }\label{fig:unnamed-chunk-9}
-\end{figure}
-
-\begin{figure}[h!]
-
-{\centering \includegraphics[width=0.7\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}
-
-}
-
-\caption{Distribution of }\label{fig:unnamed-chunk-10}
 \end{figure}

### 2024-03-19 article/article.Rmd
Commit 2024-03-19 17:16
Commit 2024-03-19 18:16

@@
 exceeds the Total Solar Irradiance on horizontal plane at ground level.
-Although the duration of these bursts varies form instantaneous to several minutes,
+Although the duration of these bursts varies from instantaneous to several minutes,
 here we are constrained by the recorded data, to one-minute steps.
@@
 <!-- Data selection -->
-To preserve an unbiased representation of the data we applied a constrain similar
+To preserve an unbiased representation of the data we applied a constraint similar
 the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there
-must exist at list 45 minutes of valid measurements, including night time near
+must exist at list 45 minutes of valid measurements, including nighttime near
 sunrise and sunset. Days with less than 5 valid hours are rejected completely.
@@
 The recording of the signal is the one-minute average.
-Thus we will refer to this time scale as a cloud enhancement event (CE).
+Thus, we will refer to this timescale as a cloud enhancement event (CE).
 
@@
 
-We decided to use the Libradtran [@Emde2016] radiation transfer model, to modeled
+We decided to use the Libradtran [@Emde2016] radiation transfer model, to model
 the clear sky equivalent of GHI, with monthly climatological data of AOD and water
@@
 Furthermore, to account for the Sun's variability in our one-minute GHI measurements,
-we adjusted the model's input spectrum integral to the one of the the TSI provided by
+we adjusted the model's input spectrum integral to the one of the TSI provided by
 NOAA.  Finally, we adjusted for the effect of the Sun - Earth distance, and
@@
 
-Which is an expected result as these values represent an typical atmosphere in
+Which is an expected result as these values represent a typical atmosphere in
 Thessaloniki with low load of aerosols and humidity, which are the main factor that
@@
 
-Where it was needed, for some of edge cases, we also used images from a sky-cam,
+Where it was needed, for some of the edge cases, we also used images from a sky-cam,
 along with the manual inspection.
@@
 
-A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})
+A secondary criterion was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})
 
@@
 annual statistics, that give a more clear picture about the long term CE trends.
-Hence, we calculated the annual values from the one minute measurements.
+Hence, we calculated the annual values from the one-minute measurements.
 The annual mean over irradiance is

### 2024-03-19 article/article.Rmd
Commit 2024-03-19 19:27

@@
 <!-- ``` -->
-
+<!--
 ```{r echo=FALSE, fig.cap="Distribution of CE above reference"}
 knitr::include_graphics("../images/relative_distributions-4.png")
+```
+-->
+
+```{r echo=FALSE, fig.cap="Distribution of CE over irradiance"}
+knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
 ```

### 2024-03-19 article/article.tex
Commit 2024-03-19 17:16
Commit 2024-03-19 19:27

@@
 
-To preserve an unbiased representation of the data we applied a constrain similar
+To preserve an unbiased representation of the data we applied a constraint similar
 the one used by Castillejo-Cuberos and Escobar (2020). Where, for each valid hour of day, there
-must exist at list 45 minutes of valid measurements, including night time near
+must exist at list 45 minutes of valid measurements, including nighttime near
 sunrise and sunset. Days with less than 5 valid hours are rejected completely.
@@
 
-We decided to use the Libradtran (Emde et al. 2016) radiation transfer model, to modeled
+We decided to use the Libradtran (Emde et al. 2016) radiation transfer model, to model
 the clear sky equivalent of GHI, with monthly climatological data of AOD and water
@@
 Furthermore, to account for the Sun's variability in our one-minute GHI measurements,
-we adjusted the model's input spectrum integral to the one of the the TSI provided by
+we adjusted the model's input spectrum integral to the one of the TSI provided by
 NOAA. Finally, we adjusted for the effect of the Sun - Earth distance, and
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/relative_distributions-4}
+{\centering \includegraphics[width=0.7\linewidth]{../images/P-relative-distribution-diff-1}
 
@@
 
-\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-2}
+\caption{Distribution of CE over irradiance}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 
-\caption{Distribution of CE groups}\label{fig:unnamed-chunk-3}
+\caption{Distribution of CE groups}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 
-\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-4}
+\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 
-\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-5}
+\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-6}
 \end{figure}
@@
 
-\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-6}
+\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-7}
 \end{figure}
@@
 
-\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-7}
+\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-8}
 \end{figure}
@@
 
-\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-8}
+\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-9}
 \end{figure}
@@
 
-\caption{Distribution of }\label{fig:unnamed-chunk-9}
+\caption{Distribution of }\label{fig:unnamed-chunk-10}
 \end{figure}

### 2024-03-20 GHI_enh_04_investigate.tex
Commit 2024-03-17 23:19
Commit 2024-03-19 09:11
Commit 2024-03-19 10:14
Commit 2024-03-19 11:12
Commit 2024-03-20 11:12

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-17}
+\date{2024-03-20}
 
@@
 \begin{verbatim}
-Warning: Removed 25 rows containing missing values or values outside the scale range
-(`geom_bar()`).
+Warning: Removed 25 rows containing missing values or values outside the scale
+range (`geom_bar()`).
 \end{verbatim}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-10} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-2} \end{center}
 
@@
 \begin{verbatim}
-2024-03-17 20:07:26.4 athan@tyler GHI_enh_04_investigate.R 1.254163 mins
+2024-03-20 09:08:51.3 athan@tyler GHI_enh_04_investigate.R 1.076711 mins
 \end{verbatim}

### 2024-03-20 article/article.tex
Commit 2024-03-20 10:14
Commit 2024-03-20 11:12

@@
 Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
-\date{2024-03-19}
+\date{2024-03-20}
 
@@
 
-We computed the daily trend of the mean over irradiance of CE (Figure~
-\ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
-using the `maximum likelihood' fitting method (Gardner, Harvey, and Phillips 1980; Jones 1980) by
-implementing the function `arima' from the library `stats' of the R programming
-language (R Core Team 2023). The trends were reported together with the \(2\sigma\) error.
-We observe an increase of
+We computed the daily trend of the mean over irradiance of CE
+(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order autoregressive
+model with lag of 1 day, using the `maximum likelihood' fitting method (Gardner, Harvey, and Phillips 1980; Jones 1980) by implementing the function `arima' from the library `stats' of the R
+programming language (R Core Team 2023). The trends were reported together with the \(2\sigma\)
+error. We observe an increase of
 \(0.216\pm 0.083\,W/m^2\)
@@
 \(0.23\pm 0.11\,W/m^2\)
-(Figure~\ref{fig:P-energy-mean}),
+(Figure\nobreakspace{}\ref{fig:P-energy-mean}),
 but this value is not very useful due the high
@@
 \(122.2\pm 22.8\,/y\)
-(Figure~\ref{fig:P-energy-N}).
+(Figure\nobreakspace{}\ref{fig:P-energy-N}).
+We have to note that the energy related to the CE events can not be directly linked
+with the total energy balance on the atmosphere. The net sun radiation of the region
+is not increased, but rather redistributed through the CE.
 
@@
 
-Another interesting aspect of the CE cases, is the seasonal cycle. In Figure~
-\ref{fig:relative-month-occurancies}, we have the box plot (whisker plot), where the
-values have been normalized by the highest median value, that occurs in May.
-Although the number of occurrences has a wide spread throughout the study period,
-the most active period of CE occurrences is during May and June. During the Winter
-(December -- February) the CE cases are about 25\% of the maximum. The rest of the
-months the occurrences seems to ramp between the maximum and minimum.
+Another interesting aspect of the CE cases, is the seasonal cycle. In
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the box plot
+(whisker plot), where the values have been normalized by the highest median value,
+that occurs in May. Although the number of occurrences has a wide spread throughout
+the study period, the most active period of CE occurrences is during May and June.
+During the Winter (December -- February) the CE cases are about 25\% of the maximum.
+The rest of the months the occurrences seems to ramp between the maximum and minimum.
 
@@
 
+The distribution of the CE over irradiance spreads uniformly
+Figure\nobreakspace{}\ref{fig:ovir-distribution}. Where there is an inverse relation
+between the events frequency and events intensity. This is expected as, the stronger
+the CE events become, the more rare are the particular atmospheric and sun conditions
+to occur.
+
 \begin{figure}[h!]
@@
 
-\caption{Distribution of CE over irradiance}\label{fig:unnamed-chunk-3}
+\caption{Distribution of CE over irradiance}\label{fig:ovir-distribution}
 \end{figure}
@@
 
+In order to further study the characteristics of the CE events, we grouped the singe
+minute CE events, to continuous CE groups (CEG). Thus, a CEG consists of one or more
+successive CE cases, and can have a duration of multiple of minutes. We have
+identified 29009 groups, where the group with the longest duration lasted
+140 minutes on
+07~July 2013.
+By examining the frequency distribution of the CEG durations
+(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), is evident that durations above
+10 minutes are very rare.
+
 \begin{figure}[h!]
@@
 
-\caption{Distribution of CE groups}\label{fig:unnamed-chunk-4}
+\caption{Distribution of CE groups}\label{fig:ceg-duration-distribution}
 \end{figure}
+
+\ldots{} (\textbf{Zhang2018?}) \ldots.
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/groups-4}
+{\centering \includegraphics[width=0.7\linewidth]{../images/P-groups-bin2d-1}
 
@@
 
-\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-5}
-\end{figure}
-
-\begin{figure}[h!]
-
-{\centering \includegraphics[width=0.7\linewidth]{../images/groups-8}
-
-}
-
-\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-6}
+\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 
-\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-7}
+\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 
-\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-8}
-\end{figure}
-
-\begin{figure}[h!]
-
-{\centering \includegraphics[width=0.7\linewidth]{../images/extremedistributions-4}
-
-}
-
-\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-9}
+\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 
-\caption{Distribution of }\label{fig:unnamed-chunk-10}
+\caption{Distribution of }\label{fig:unnamed-chunk-6}
 \end{figure}

### 2024-03-20 GHI_enh_05_distributions.R

@@ -360,7 +360,7 @@ ggplot(data = DATA[GLB_diff > 0], aes(x = GLB_diff)) +
                  color    = "black") +
   xlab(bquote("Over Irradiance" ~ group("[", W/m^2,"]"))) +
   ylab("Relative frequency [%]") +
-  labs(caption = paste("Bin width:", binwidth, "W/m^2"))  +
+  # labs(caption = paste("Bin width:", binwidth, "W/m^2"))  +
   inset_element(p1, left = 0.4, bottom = 0.4, right = 1, top = 1,
                 align_to = "plot")
 

### 2024-03-20 article/article.Rmd
Commit 2024-03-20 10:14
Commit 2024-03-20 11:12

@@
 
-We computed the daily trend of the mean over irradiance of CE (Figure\ 
-\ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
-using the 'maximum likelihood' fitting method [@Gardner1980; @Jones1980] by
-implementing the function 'arima' from the library 'stats' of the R programming
-language [@RCT2023]. The trends were reported together with the $2\sigma$ error.
-We observe an increase of
+We computed the daily trend of the mean over irradiance of CE
+(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order autoregressive
+model with lag of 1 day, using the 'maximum likelihood' fitting method [@Gardner1980;
+@Jones1980] by implementing the function 'arima' from the library 'stats' of the R
+programming language [@RCT2023]. The trends were reported together with the $2\sigma$
+error.  We observe an increase of
 $`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
@@
 `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2$
-(Figure\ \ref{fig:P-energy-mean}),
+(Figure\nobreakspace{}\ref{fig:P-energy-mean}),
 but this value is not very useful due the high
@@
 `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,/y$
-(Figure\ \ref{fig:P-energy-N}).
+(Figure\nobreakspace{}\ref{fig:P-energy-N}).
+We have to note that the energy related to the CE events can not be directly linked
+with the total energy balance on the atmosphere. The net sun radiation of the region
+is not increased, but rather redistributed through the CE.
 
@@
 
-Another interesting aspect of the CE cases, is the seasonal cycle. In Figure\ 
-\ref{fig:relative-month-occurancies}, we have the box plot (whisker plot), where the
-values have been normalized by the highest median value, that occurs in May.
-Although the number of occurrences has a wide spread throughout the study period,
-the most active period of CE occurrences is during May and June. During the Winter
-(December -- February) the CE cases are about 25% of the maximum. The rest of the
-months the occurrences seems to ramp between the maximum and minimum.
+Another interesting aspect of the CE cases, is the seasonal cycle. In
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the box plot
+(whisker plot), where the values have been normalized by the highest median value,
+that occurs in May.  Although the number of occurrences has a wide spread throughout
+the study period, the most active period of CE occurrences is during May and June.
+During the Winter (December -- February) the CE cases are about 25% of the maximum.
+The rest of the months the occurrences seems to ramp between the maximum and minimum.
 
@@
 
-```{r echo=FALSE, fig.cap="Distribution of CE over irradiance"}
+The distribution of the CE over irradiance spreads uniformly
+Figure\nobreakspace{}\ref{fig:ovir-distribution}. Where there is an inverse relation
+between the events frequency and events intensity. This is expected as, the stronger
+the CE events become, the more rare are the particular atmospheric and sun conditions
+to occur.
+
+```{r ovir-distribution, echo=FALSE, fig.cap="Distribution of CE over irradiance"}
 knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
@@
 
-```{r echo=FALSE, fig.cap="Distribution of CE groups"}
+In order to further study the characteristics of the CE events, we grouped the singe
+minute CE events, to continuous CE groups (CEG). Thus, a CEG consists of one or more
+successive CE cases, and can have a duration of multiple of minutes.  We have
+identified `r ST_G0[, .N]` groups, where the group with the longest duration lasted
+`r ST_G0[, max(GLB_diff.N)]` minutes on 
+`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")`.
+By examining the frequency distribution of the CEG durations
+(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), is evident that durations above
+10 minutes are very rare.
+
+```{r ceg-duration-distribution, echo=FALSE, fig.cap="Distribution of CE groups"}
 knitr::include_graphics("../images/groups-1.png")
@@
 
+... @Zhang2018 ....
+
 ```{r echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"}
-knitr::include_graphics("../images/groups-4.png")
+knitr::include_graphics("../images/P-groups-bin2d-1.png")
 ```
 
-```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"}
-knitr::include_graphics("../images/groups-8.png")
-```
+<!-- ```{r echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"} -->
+<!-- knitr::include_graphics("../images/groups-4.png") -->
+<!-- ``` -->
+
+<!-- ```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"} -->
+<!-- knitr::include_graphics("../images/groups-8.png") -->
+<!-- ``` -->
 
@@
 
-```{r echo=FALSE, fig.cap="Distribution of ECE Irradiance above 'TSI'"}
-knitr::include_graphics("../images/extremedistributions-4.png")
-```
+<!-- ```{r echo=FALSE, fig.cap="Distribution of ECE Irradiance above 'TSI'"} -->
+<!-- knitr::include_graphics("../images/extremedistributions-4.png") -->
+<!-- ``` -->
 

### 2024-03-20 GHI_enh_04_investigate.R

@@ -423,7 +423,7 @@ ggplot(data = ST_G0, aes(x = GLB_ench.N)) +
                  boundary = 0,
                  color    = "black") +
   # xlab(bquote(.(varname("GLB_diff")) ~ group("[", W/m^2,"]"))) +
-  xlab("Duration of enhancement [min]") +
+  xlab("Duration of enhancement group [min]") +
   ylab("Relative frequency [%]") +
   labs(caption = paste("Bin width:", binwidth, "min")) +
   inset_element(p1, left = 0.3, bottom = 0.3, right = 1, top = 1,
@@ -437,7 +437,7 @@ ggplot(data = ST_G0, aes(x = GLB_ench.N)) +
                  color    = "black") +
   scale_y_log10() +
   # xlab(bquote(.(varname("GLB_diff")) ~ group("[", W/m^2,"]"))) +
-  xlab("Duration of enhancement [min]") +
+  xlab("Duration of enhancement group [min]") +
   ylab("Frequency") +
   labs(caption = paste("Bin width:", binwidth, "min"))
 
@@ -465,10 +465,6 @@ ggplot(data    = ST_G0,
                      minor_breaks = seq(0, 500, by = 25)) +
   scale_x_continuous(guide        = "axis_minor",
                      minor_breaks = seq(0, 500, by = 10))
-
-
-
-
 
 
 
@@ -541,23 +537,23 @@ ggplot(data    = ST_G0,
 
 
 ## _ Use bin2d -------------
+
+#+ P-groups-bin2d, echo=F, include=T, results="asis"
 my_breaks <- c(2, 10, 50, 250, 1250, 6000)
 my_breaks <- 1 * 2^seq(0, 20, by = 2)
-
-
-lim_dur <- 80
+lim_dur   <- 80
 
 ggplot(data    = ST_G0,
        mapping = aes(x = GLB_ench.N, y = ST_G0$GLB_diff.sum/ST_G0$GLB_ench.N)) +
-  xlab("Duration of enhancement [min]") +
-  ylab(bquote("Mean Over Irradiance per minute" ~ group("[", W/m^2,"]"))) +
+  xlab("Duration of enhancement group [min]") +
+  ylab(bquote("Mean group over irradiance" ~ group("[", kJ/m^2,"]"))) +
   geom_bin_2d(bins = 80) +
   scale_fill_continuous(type = "viridis", transform = "log",
                         breaks = my_breaks, labels = my_breaks) +
[…]

### 2024-03-20 article/article.Rmd
Commit 2024-03-20 12:14

--- 2024-03-19 article/article.Rmd
@@
 
-We computed the daily trend of the mean over irradiance of CE (Figure\ 
+We computed the daily trend of the mean over irradiance of CE (Figure\nobreakspace{}
 \ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
@@
 
-Another interesting aspect of the CE cases, is the seasonal cycle. In Figure\ 
-\ref{fig:relative-month-occurancies}, we have the box plot (whisker plot), where the
-values have been normalized by the highest median value, that occurs in May.
-Although the number of occurrences has a wide spread throughout the study period,
-the most active period of CE occurrences is during May and June. During the Winter
-(December -- February) the CE cases are about 25% of the maximum. The rest of the
-months the occurrences seems to ramp between the maximum and minimum.
+Another interesting aspect of the CE cases, is the seasonal cycle. In
+Figure\nobreakspace{} \ref{fig:relative-month-occurancies}, we have the box plot
+(whisker plot), where the values have been normalized by the highest median value,
+that occurs in May.  Although the number of occurrences has a wide spread throughout
+the study period, the most active period of CE occurrences is during May and June.
+During the Winter (December -- February) the CE cases are about 25% of the maximum.
+The rest of the months the occurrences seems to ramp between the maximum and minimum.
 
@@
 
-```{r echo=FALSE, fig.cap="Distribution of CE over irradiance"}
+The distribution of the CE over irradiance spreads uniformly Figure\nobreakspace{}
+\ref{fig:ovir-distribution}. Where there is an inverse relation  between the events
+frequency and events intensity . This is expected as, the stronger the CE events
+become, the more rare is the atmospheric and sun conditions to occur.
+
+```{r ovir-distribution, echo=FALSE, fig.cap="Distribution of CE over irradiance"}
 knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
@@
 ## Groups stats
+
+In order to further study the characteristics of the CE events, we grouped the singe
+minute CE events, to continuous CE.
 

### 2024-03-20 article/article.tex
Commit 2024-03-20 12:14

@@
 
-\ldots{} (\textbf{Zhang2018?}) \ldots.
-
 \begin{figure}[h!]
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/P-groups-bin2d-1}
+{\centering \includegraphics[width=0.7\linewidth]{../images/groups-4}
 
@@
 \caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-3}
+\end{figure}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/groups-8}
+
+}
+
+\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 
-\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-4}
+\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 
-\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-5}
+\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-6}
+\end{figure}
+
+\begin{figure}[h!]
+
+{\centering \includegraphics[width=0.7\linewidth]{../images/extremedistributions-4}
+
+}
+
+\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-7}
 \end{figure}
@@
 
-\caption{Distribution of }\label{fig:unnamed-chunk-6}
+\caption{Distribution of }\label{fig:unnamed-chunk-8}
 \end{figure}

### 2024-03-20 GHI_enh_04_investigate.R
Commit 2024-03-20 13:12

@@ -537,23 +537,24 @@ ggplot(data    = ST_G0,
 
 
 ## _ Use bin2d -------------
+
+#+ P-groups-bin2d, echo=F, include=T, results="asis"
 my_breaks <- c(2, 10, 50, 250, 1250, 6000)
 my_breaks <- 1 * 2^seq(0, 20, by = 2)
-
-
-lim_dur <- 80
+lim_dur   <- 60
+bins      <- 60
 
 ggplot(data    = ST_G0,
-       mapping = aes(x = GLB_ench.N, y = ST_G0$GLB_diff.sum/ST_G0$GLB_ench.N)) +
-  xlab("Duration of enhancement [min]") +
-  ylab(bquote("Mean Over Irradiance per minute" ~ group("[", W/m^2,"]"))) +
-  geom_bin_2d(bins = 80) +
+       mapping = aes(x = GLB_ench.N, y = GLB_diff.sum/GLB_ench.N)) +
+  xlab("Duration of enhancement group [min]") +
+  ylab(bquote("Mean group over irradiance" ~ group("[", kJ/m^2,"]"))) +
+  geom_bin_2d(bins = bins) +
   scale_fill_continuous(type = "viridis", transform = "log",
                         breaks = my_breaks, labels = my_breaks) +
   theme(legend.position      = c(0.99, 0.99),
         legend.justification = c(1, 1)) +
   theme(legend.background    = element_rect(fill = "white", colour = NA)) +
-  labs(color = 'Count') +
+  labs(fill = 'Count\n(log scale)') +
   scale_y_continuous(guide        = "axis_minor",
                      minor_breaks = seq(0, 500, by = 25)) +
   scale_x_continuous(guide        = "axis_minor",
@@ -564,9 +565,9 @@ ggplot(data    = ST_G0,
 
 
 ggplot(data    = ST_G0,
-       mapping = aes(x = GLB_ench.N, y = ST_G0$GLB_diff.sum/ST_G0$GLB_ench.N)) +
-  xlab("Duration of enhancement [min]") +
-  ylab(bquote("Mean Over Irradiance per minute" ~ group("[", W/m^2,"]"))) +
+       mapping = aes(x = GLB_ench.N, y = GLB_diff.sum/GLB_ench.N)) +
+  xlab("Duration of enhancement group [min]") +
+  ylab(bquote("Mean group over irradiance" ~ group("[", kJ/m^2,"]"))) +
[…]

### 2024-03-20 GHI_enh_04_investigate.tex
Commit 2024-03-20 12:14
Commit 2024-03-20 13:12

@@
 \begin{verbatim}
-Warning: Removed 5 rows containing non-finite outside the scale range
+Warning: Removed 12 rows containing non-finite outside the scale range
 (`stat_bin2d()`).
+\end{verbatim}
+
+\begin{verbatim}
+Warning: Removed 2 rows containing missing values or values outside the scale
+range (`geom_tile()`).
 \end{verbatim}
@@
 \begin{verbatim}
-Warning: Removed 5 rows containing non-finite outside the scale range
-(`stat_bin2d()`).
+Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
+Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
 \end{verbatim}
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-2} \end{center}
+
+\begin{verbatim}
+Scale for x is already present.
+Adding another scale for x, which will replace the existing scale.
+\end{verbatim}
+
+\begin{verbatim}
+Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
+Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-3} \end{center}
 
@@
 \begin{verbatim}
-2024-03-20 09:08:51.3 athan@tyler GHI_enh_04_investigate.R 1.076711 mins
+2024-03-20 09:43:30.5 athan@tyler GHI_enh_04_investigate.R 1.065564 mins
 \end{verbatim}

### 2024-03-20 article/article.Rmd
Commit 2024-03-20 13:12

--- 2024-03-20 article/article.Rmd
@@
 By examining the frequency distribution of the CEG durations
-(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), is evident that durations above
-10 minutes are very rare.
+(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can conclude that longer durations are getting increasingly rare, with durations above 10 minutes very rare.
 
@@
 
-<!-- Change color -->
+Another aspect of the CE events are the cases where the irradiance is above the expected irradiance on top of the atmosphere, we have defined this
 
-```{r echo=FALSE, fig.cap="Distribution of the number of ECE cases"}
-knitr::include_graphics("../images/climECEmonth-1.png")
+```{r echo=FALSE, fig.cap="Distribution of "}
+knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")
 ```
+
+<!-- ```{r echo=FALSE, fig.cap="Distribution of the number of ECE cases"} -->
+<!-- knitr::include_graphics("../images/climECEmonth-1.png") -->
+<!-- ``` -->
 
@@
 ## New plots for discussion
-
-```{r echo=FALSE, fig.cap="Distribution of "}
-knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")
-```
 

### 2024-03-20 article/article.tex
Commit 2024-03-20 13:12

--- 2024-03-20 article/article.tex
@@
 
+Another aspect of the CE events are the cases where the irradiance is above the expected irradiance on top of the atmosphere, we have defined this
+
 \begin{figure}[h!]
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/climECEmonth-1}
+{\centering \includegraphics[width=0.7\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}
 
@@
 
-\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-4}
+\caption{Distribution of }\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 \subsection{New plots for discussion}\label{new-plots-for-discussion}}
-
-\begin{figure}[h!]
-
-{\centering \includegraphics[width=0.7\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}
-
-}
-
-\caption{Distribution of }\label{fig:unnamed-chunk-6}
-\end{figure}
 

### 2024-03-20 article/article.Rmd
Commit 2024-03-20 15:12

@@
 output: 
+  # redoc::redoc: default
  #  rticles::mdpi_article:

### 2024-03-20 article/article.tex
Commit 2024-03-20 17:12

@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/P_daily_trend-1}
+{\centering \includegraphics[width=0.6\linewidth]{../images/P_daily_trend-1}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-7}
+{\centering \includegraphics[width=0.6\linewidth]{../images/P_energy-7}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-6}
+{\centering \includegraphics[width=0.6\linewidth]{../images/P_energy-6}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-5}
+{\centering \includegraphics[width=0.6\linewidth]{../images/P_energy-5}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-8}
+{\centering \includegraphics[width=0.6\linewidth]{../images/P_energy-8}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/clim_CE_month_norm_MAX_median_N-2}
+{\centering \includegraphics[width=0.6\linewidth]{../images/clim_CE_month_norm_MAX_median_N-2}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/P-relative-distribution-diff-1}
+{\centering \includegraphics[width=0.6\linewidth]{../images/P-relative-distribution-diff-1}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/groups-1}
+{\centering \includegraphics[width=0.6\linewidth]{../images/groups-1}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/P-groups-bin2d-1}
+{\centering \includegraphics[width=0.6\linewidth]{../images/P-groups-bin2d-1}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}
+{\centering \includegraphics[width=0.6\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{../images/extremedistributions-2}
+{\centering \includegraphics[width=0.6\linewidth]{../images/extremedistributions-2}
 

### 2024-03-20 article/article.Rmd
Commit 2024-03-20 17:12

@@
 # knitr::opts_chunk$set(dev        = "pdf"   )
-knitr::opts_chunk$set(out.width  = "70%"   )
+knitr::opts_chunk$set(out.width  = "60%"   )
 knitr::opts_chunk$set(fig.align  = "center")

### 2024-03-20 article/article.Rmd
Commit 2024-03-20 23:09

@@
 
-In this study, we evaluated the effects of the clouds on th
+In this study, we evaluated the effects of the clouds on the total downward radiation
+by studding the occurrences of the cloud enhancement cases, their intensity and their
+duration.  The recording of the radiation signal is the one-minute average.  Thus, we
+will refer to this time step as a cloud enhancement event (CE).
 
@@
 - CSid tool
-
-The recording of the signal is the one-minute average.
-Thus, we will refer to this timescale as a cloud enhancement event (CE).
 
@@
 After some evaluation of the modeled radiation in different atmospheric conditions,
-in relation to the GHI data, we choose as representative of the clear sky radiation,
+in relation to the GHI data, we choose as a representative of the clear sky radiation,
 the case with
@@
 
-Which is an expected result as these values represent a typical atmosphere in
+These values will represent a typical atmosphere in
 Thessaloniki with low load of aerosols and humidity, which are the main factor that
 attenuate the GHI, excluding clouds.
+We will refer to this irradiance as $\text{GHI}_\text{mCSi}$.
 
@@
 
-Criteria for cloud enhancement identification are set according the Equation \ref{eq:CE4}
+Criteria for cloud enhancement identification are set according the Equation\nobreakspace\ref{eq:CE4}
 
+<!--
 \begin{equation}
@@
 where: $\theta$ solar zenith angle.
-
-A secondary criterion was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})
+-->
 
 \begin{equation}
-\text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
+\text{CE} : \begin{cases}
+ \text{GHI}_\text{i} > `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
+\text{GHI}_\text{i} > \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
+\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
+\end{cases}\label{eq:CE4b}
+\end{equation}
+where: $\theta$ solar zenith angle.
+
+A secondary criterion was used for extreme cloud enhancement cases (ECE)
+identification, relative to the TSI at horizontal plane
+(Equation\nobreakspace{}\ref{eq:ECE})
+
+\begin{equation}
+\text{ECE}: \text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
 \label{eq:ECE}
@@
 
-<!-- todo stop long tails on hist -->
-<!-- hist retative frequency label -->
-
-<!-- Whisky plot relative between months -->
-<!-- weight (Nmonth / Nmaxmonth) -->
-
 <!-- whisky plots relative to GLB -->
@@
 
-Another aspect of the CE events are the cases where the irradiance is above the expected irradiance on top of the atmosphere, we have defined this
+Another aspect of the CE events are the cases when the irradiance is above the
+expected irradiance on top of the atmosphere, we have defined this as ECE
+(Equation\nobreakspace{}\ref{eq:ECE}).
 
-```{r echo=FALSE, fig.cap="Distribution of "}
+-  max value ECE
+  relative to other works max values
+
+Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies} we have
+computed the distribution of the number of occurrences of ECE events by month in
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the most active
+period is in the spring (March -- May), followed by the months of June, September and
+October.
+
+.......
+
+```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Distribution of "}
 knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")
@@
 
--   max value ECE
--   seasonal
--   trends
--   duration
--   occurrence
 -   SZA
-
-\FloatBarrier
-
-## New plots for discussion
 

### 2024-03-20 article/article.tex
Commit 2024-03-20 23:09

@@
 
-In this study, we evaluated the effects of the clouds on th
+In this study, we evaluated the effects of the clouds on the total downward radiation
+by studding the occurrences of the cloud enhancement cases, their intensity and their
+duration. The recording of the radiation signal is the one-minute average. Thus, we
+will refer to this time step as a cloud enhancement event (CE).
 
@@
 \end{itemize}
-
-The recording of the signal is the one-minute average.
-Thus, we will refer to this timescale as a cloud enhancement event (CE).
 
@@
 
-Which is an expected result as these values represent a typical atmosphere in
+These values will represent a typical atmosphere in
 Thessaloniki with low load of aerosols and humidity, which are the main factor that
 attenuate the GHI, excluding clouds.
+We will refer to this irradiance as \(\text{GHI}_\text{mCSi}\).
 
@@
 
-Criteria for cloud enhancement identification are set according the Equation \ref{eq:CE4}
+Criteria for cloud enhancement identification are set according the Equation\nobreakspace\ref{eq:CE4}
 
 \begin{equation}
-\text{CE}_\text{Threshold} = \begin{cases}
-1.05, & \text{$\theta \leq 60^\circ$}\\
-\frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) + 1.18 , & \text{$ 78^\circ > \theta > 60^\circ$}\\
+\text{CE} : \begin{cases}
+ \text{GHI}_\text{i} > 1.05 \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq 60^\circ$}\\
+\text{GHI}_\text{i} > \left ({ 1.18 + \frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ 78^\circ > \theta > 60^\circ$}\\
 \text{Excluded measurements}, & \theta > 78^\circ
-\end{cases}\label{eq:CE4}
+\end{cases}\label{eq:CE4b}
 \end{equation}
@@
 
-A secondary criterion was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})
+A secondary criterion was used for extreme cloud enhancement cases (ECE)
+identification, relative to the TSI at horizontal plane
+(Equation\nobreakspace{}\ref{eq:ECE})
 
 \begin{equation}
-\text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
+\text{ECE}: \text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
 \label{eq:ECE}
@@
 
-Another aspect of the CE events are the cases where the irradiance is above the expected irradiance on top of the atmosphere, we have defined this
+Another aspect of the CE events are the cases when the irradiance is above the
+expected irradiance on top of the atmosphere, we have defined this as ECE
+(Equation\nobreakspace{}\ref{eq:ECE}).
+
+\begin{itemize}
+\tightlist
+\item
+  max value ECE
+  relative to other works max values
+\end{itemize}
+
+Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies} we have
+computed the distribution of the number of occurrences of ECE events by month in
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the most active
+period is in the spring (March -- May), followed by the months of June, September and
+October.
+
+\ldots\ldots.
 
@@
 
-\caption{Distribution of }\label{fig:unnamed-chunk-4}
+\caption{Distribution of }\label{fig:relative-month-occurancies-ECE}
 \end{figure}
@@
 
-\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-5}
+\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 \item
-  max value ECE
-\item
-  seasonal
-\item
-  trends
-\item
-  duration
-\item
-  occurrence
-\item
   SZA
 \end{itemize}
-
-\FloatBarrier
-
-\hypertarget{new-plots-for-discussion}{%
-\subsection{New plots for discussion}\label{new-plots-for-discussion}}
 

### 2024-03-21 article/article.Rmd
Commit 2024-03-21 08:11

@@
 In this study, we evaluated the effects of the clouds on the total downward radiation
-by studding the occurrences of the cloud enhancement cases, their intensity and their
-duration.  The recording of the radiation signal is the one-minute average.  Thus, we
+by studding the occurrences of the cloud enhancement cases, their intensity, and their
+duration.  The recording of the radiation signal is the mean of one-minute. Thus, we
 will refer to this time step as a cloud enhancement event (CE).
 
+<!--
 - available data
@@
 - CSid tool
+-->
 

### 2024-03-21 article/article.tex
Commit 2024-03-21 08:11

@@
 In this study, we evaluated the effects of the clouds on the total downward radiation
-by studding the occurrences of the cloud enhancement cases, their intensity and their
-duration. The recording of the radiation signal is the one-minute average. Thus, we
+by studding the occurrences of the cloud enhancement cases, their intensity, and their
+duration. The recording of the radiation signal is the mean of one-minute. Thus, we
 will refer to this time step as a cloud enhancement event (CE).
-
-\begin{itemize}
-\tightlist
-\item
-  available data
-
-  \begin{itemize}
-  \tightlist
-  \item
-    sky cam
-  \item
-    chp1
-  \item
-    cm21
-  \item
-    cimel
-  \end{itemize}
-\item
-  CSid tool
-\end{itemize}
 

### 2024-03-21 article/article.Rmd
Commit 2024-03-21 12:16
Commit 2024-03-21 13:31

@@
 
+In this study, we evaluated the effects of the clouds on the total downward radiation
+by studding the occurrences of the cloud enhancement cases, their intensity, and their
+duration.  The recording of the radiation signal is the mean of one-minute. Thus, we
+will refer to this time step as a cloud enhancement event (CE).
+
 # Data and methodology
@@
 
-Our monitoring site is operating in the Laboratory of Atmospheric Physics of the
+The monitoring site is operating in the Laboratory of Atmospheric Physics of the
 Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
@@
 `r strftime(max(ST_daily$Date), "%d\\ %B %Y")`.
-
 <!-- Instrument -->
-The GHI data were measured with a Kipp\ & Zonen CM-21 pyranometer.
-During the study period, the pyranometer was independently calibrated three times at
-the Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of
-the instrument’s sensitivity was better than $0.7\%$ relative to the initial
-calibration by the manufacturer.
-
+The GHI data were measured with a Kipp\ & Zonen CM-21 pyranometer.  During the study
+period, the pyranometer was independently calibrated three times at the
+Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of the
+instrument’s sensitivity was better than $0.7\%$ relative to the initial calibration
+by the manufacturer.
 <!-- Measurements -->
-For the acquisition of radiometric data, the signal of the pyranometer was sampled
-at a rate of $1\,\text{Hz}$.
-The mean and the standard deviation of these samples were calculated and recorded
-every minute.
-The measurements were corrected for the zero offset ("dark signal" in volts), which
-was calculated by averaging all measurements recorded for a period of $3\,\text{h}$,
-before (morning) or after (evening) the Sun reaches an elevation angle of $-10^\circ$.
-The signal was converted to irradiance using a ramped value of the instrument’s
-sensitivity between subsequent calibrations.
+For the acquisition of radiometric data, the signal of the pyranometer was sampled at
+a rate of $1\,\text{Hz}$.  The mean and the standard deviation of these samples were
+calculated and recorded every minute.  The measurements were corrected for the zero
+offset ("dark signal" in volts), which was calculated by averaging all measurements
+recorded for a period of $3\,\text{h}$, before (morning) or after (evening) the Sun
+reaches an elevation angle of $-10^\circ$.  The signal was converted to irradiance
+using the ramped value of the instrument’s sensitivity between subsequent
+calibrations.
 
@@
 The manual screening was aided by a radiation data quality assurance procedure,
-adjusted for the site, which was based on the methods of Long and Shi\ [@Long2006; @Long2008a].
-Thus, problematic recordings have been excluded from further processing.
-Although it is impossible to detect all false data, the large number of available
-data, and the aggregation scheme we used, ensures the quality of the radiation
-measurements used in this study.
-
+adjusted for the site, which was based on the methods of Long and Shi\ [@Long2006;
+@Long2008a].  Thus, problematic recordings have been excluded from further
+processing.  Although it is impossible to detect all false data, the large number of
+available data, and the aggregation scheme we used, ensures the quality of the
+radiation measurements used in this study.
 <!-- Data selection -->
@@
 
-In this study, we evaluated the effects of the clouds on the total downward radiation
-by studding the occurrences of the cloud enhancement cases, their intensity, and their
-duration.  The recording of the radiation signal is the mean of one-minute. Thus, we
-will refer to this time step as a cloud enhancement event (CE).
-
-<!--
-- available data
-  - sky cam
-  - chp1
-  - cm21
-  - cimel
-- CSid tool
--->
-
 ## Clear Sky Irradiance
 
-In order to identify CE cases, we need an approximation of the expected clear sky GHI
-for the whole period of the study, with a temporal resolution of one minute.  Because
-of the lack of exact data about atmospheric factors, responsible for the attenuation
-of the solar radiation in the atmosphere, we can not recreate a minute by minute
-representation of the reference radiation. Thus, we used some climatological data
-with a radiation transfer model.
+In order to identify CE cases, we used a modeled approximation of the expected clear
+sky GHI.  Because of the lack of observational data for the whole period, we used
+some long term climatological data for the main factors responsible for the
+attenuation of the broadband downward solar radiation in the atmosphere, which are
+mainly the aerosols and the water vapors. Fortunately, our site participates in the
+Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998], as we operate a Cimel
+photometer since 2003, collocated with the CM-21 pyranometer.  The mean monthly
+aerosol optical depth (AOD) on different wavelengths is provided by AERONET along
+with the equivalent water column height in the atmosphere.  The simulation of the
+clear sky radiation was performed by the well established radiation transfer model
+Libradtran [@Emde2016].
 
-We decided to use the Libradtran [@Emde2016] radiation transfer model, to model
-the clear sky equivalent of GHI, with monthly climatological data of AOD and water
-column from the Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998].  Our site
-participates in AERONET, where we operate a Cimel photometer, collocated to
-the CM-21 pyranometer, since 2003
-
-For the production of .....
+For completeness we will describe the main points of the radiation simulation
+procedure here.  We used as input the spectrum of @Kurucz1994 in the range $280$ to
+$2500\,\text{nm}$.
 
 We also used the Sun's total solar irradiance from NOAA [@Coddington2005] and the
-Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].  We simulated
-the clear sky radiation, using the solar radiation spectrum of @Kurucz1994 in the
-range $280$ to $2500\,\text{nm}$, with a SZA step of $0.2^\circ$.  For the
+Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].
+
+We simulated
+the clear sky radiation, using the solar radiation , with a SZA step of $0.2^\circ$.
+For the
 atmospheric characteristics, we used combinations of AOD at $500\,\text{nm}$

### 2024-03-21 article/article.tex
Commit 2024-03-21 12:16
Commit 2024-03-21 13:31

@@
 Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
-\date{2024-03-20}
+\date{2024-03-21}
 
@@
 
+In this study, we evaluated the effects of the clouds on the total downward radiation
+by studding the occurrences of the cloud enhancement cases, their intensity, and their
+duration. The recording of the radiation signal is the mean of one-minute. Thus, we
+will refer to this time step as a cloud enhancement event (CE).
+
 \hypertarget{data-and-methodology}{%
@@
 31~December 2023.
-
-The GHI data were measured with a Kipp~\& Zonen CM-21 pyranometer.
-During the study period, the pyranometer was independently calibrated three times at
-the Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of
-the instrument's sensitivity was better than \(0.7\%\) relative to the initial
-calibration by the manufacturer.
-
-For the acquisition of radiometric data, the signal of the pyranometer was sampled
-at a rate of \(1\,\text{Hz}\).
-The mean and the standard deviation of these samples were calculated and recorded
-every minute.
-The measurements were corrected for the zero offset (``dark signal'' in volts), which
-was calculated by averaging all measurements recorded for a period of \(3\,\text{h}\),
-before (morning) or after (evening) the Sun reaches an elevation angle of \(-10^\circ\).
-The signal was converted to irradiance using a ramped value of the instrument's
-sensitivity between subsequent calibrations.
+The GHI data were measured with a Kipp~\& Zonen CM-21 pyranometer. During the study
+period, the pyranometer was independently calibrated three times at the
+Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of the
+instrument's sensitivity was better than \(0.7\%\) relative to the initial calibration
+by the manufacturer.
+For the acquisition of radiometric data, the signal of the pyranometer was sampled at
+a rate of \(1\,\text{Hz}\). The mean and the standard deviation of these samples were
+calculated and recorded every minute. The measurements were corrected for the zero
+offset (``dark signal'' in volts), which was calculated by averaging all measurements
+recorded for a period of \(3\,\text{h}\), before (morning) or after (evening) the Sun
+reaches an elevation angle of \(-10^\circ\). The signal was converted to irradiance
+using the ramped value of the instrument's sensitivity between subsequent
+calibrations.
 
@@
 The manual screening was aided by a radiation data quality assurance procedure,
-adjusted for the site, which was based on the methods of Long and Shi~(Long and Shi 2006, 2008).
-Thus, problematic recordings have been excluded from further processing.
-Although it is impossible to detect all false data, the large number of available
-data, and the aggregation scheme we used, ensures the quality of the radiation
-measurements used in this study.
-
+adjusted for the site, which was based on the methods of Long and Shi~(Long and Shi 2006, 2008). Thus, problematic recordings have been excluded from further
+processing. Although it is impossible to detect all false data, the large number of
+available data, and the aggregation scheme we used, ensures the quality of the
+radiation measurements used in this study.
 To preserve an unbiased representation of the data we applied a constraint similar
@@
 
-In this study, we evaluated the effects of the clouds on the total downward radiation
-by studding the occurrences of the cloud enhancement cases, their intensity, and their
-duration. The recording of the radiation signal is the mean of one-minute. Thus, we
-will refer to this time step as a cloud enhancement event (CE).
-
 \hypertarget{clear-sky-irradiance}{%
@@
 
-In order to identify CE cases, we need an approximation of the expected clear sky GHI
-for the whole period of the study, with a temporal resolution of one minute. Because
-of the lack of exact data about atmospheric factors, responsible for the attenuation
-of the solar radiation in the atmosphere, we can not recreate a minute by minute
-representation of the reference radiation. Thus, we used some climatological data
-with a radiation transfer model.
+In order to identify CE cases, we used a modeled approximation of the expected clear
+sky GHI. Because of the lack of observational data for the whole period, we used
+some long term climatological data for the main factors responsible for the
+attenuation of the broadband downward solar radiation in the atmosphere, which are
+mainly the aerosols and the water vapors. Fortunately, our site participates in the
+Aerosol Robotic Network (AERONET) (Giles et al. 2019; Buis et al. 1998), as we operate a Cimel
+photometer since 2003, collocated with the CM-21 pyranometer. The mean monthly
+aerosol optical depth (AOD) on different wavelengths is provided by AERONET along
+with the equivalent water column height in the atmosphere. The simulation of the
+clear sky radiation was performed by the well established radiation transfer model
+Libradtran (Emde et al. 2016).
 
-We decided to use the Libradtran (Emde et al. 2016) radiation transfer model, to model
-the clear sky equivalent of GHI, with monthly climatological data of AOD and water
-column from the Aerosol Robotic Network (AERONET) (Giles et al. 2019; Buis et al. 1998). Our site
-participates in AERONET, where we operate a Cimel photometer, collocated to
-the CM-21 pyranometer, since 2003
-
-For the production of \ldots..
+For completeness we will describe the main points of the radiation simulation
+procedure here. We used as input the spectrum of Kurucz (1994) in the range \(280\) to
+\(2500\,\text{nm}\).
 
 We also used the Sun's total solar irradiance from NOAA (Coddington et al. 2005) and the
-Earth - Sun distance calculated by Astropy (Astropy Collaboration et al. 2022). We simulated
-the clear sky radiation, using the solar radiation spectrum of Kurucz (1994) in the
-range \(280\) to \(2500\,\text{nm}\), with a SZA step of \(0.2^\circ\). For the
+Earth - Sun distance calculated by Astropy (Astropy Collaboration et al. 2022).
+
+We simulated
+the clear sky radiation, using the solar radiation , with a SZA step of \(0.2^\circ\).
+For the
 atmospheric characteristics, we used combinations of AOD at \(500\,\text{nm}\)

### 2024-03-21 article/article.Rmd
Commit 2024-03-21 14:14

@@
 
-For completeness we will describe the main points of the radiation simulation
-procedure here.  We used as input the spectrum of @Kurucz1994 in the range $280$ to
-$2500\,\text{nm}$.
+For completeness, we will describe here the main points of the radiation simulation
+procedure. We used as input the spectrum of @Kurucz1994 in the range $280$ to
+$2500\,\text{nm}$, with the radiation transfer solver "disort" on a "pseudospherical"
+geometry and the "LOWTRAN" gas parameterization.
 
@@
 the clear sky radiation, using the solar radiation , with a SZA step of $0.2^\circ$.
+
 For the
-atmospheric characteristics, we used combinations of AOD at $500\,\text{nm}$
-($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column
+atmospheric characteristics, we iterated combinations of AOD at $500\,\text{nm}$
+($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, and water column
 ($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and applied it to two atmospheric
@@
 "AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
+
 Thus, we were able to emulate different atmospheric condition and level of
@@
 sky radiation.
-
-- rte_solver  disort
-- geometry   pseudospherical
-- mol_abs LOWTRAN
 

### 2024-03-21 article/article.tex
Commit 2024-03-21 14:14

@@
 
-For completeness we will describe the main points of the radiation simulation
-procedure here. We used as input the spectrum of Kurucz (1994) in the range \(280\) to
-\(2500\,\text{nm}\).
+For completeness, we will describe here the main points of the radiation simulation
+procedure. We used as input the spectrum of Kurucz (1994) in the range \(280\) to
+\(2500\,\text{nm}\), with the radiation transfer solver ``disort'' on a ``pseudospherical''
+geometry and the ``LOWTRAN'' gas parameterization.
 
@@
 the clear sky radiation, using the solar radiation , with a SZA step of \(0.2^\circ\).
+
 For the
-atmospheric characteristics, we used combinations of AOD at \(500\,\text{nm}\)
-(\(t_{500\text{nm}}\)) and additional offsets of \(\pm1\) and \(\pm2\sigma\), water column
+atmospheric characteristics, we iterated combinations of AOD at \(500\,\text{nm}\)
+(\(t_{500\text{nm}}\)) and additional offsets of \(\pm1\) and \(\pm2\sigma\), and water column
 (\(w_h\)) with offsets of \(\pm1\) and \(\pm2\sigma\), and applied it to two atmospheric
@@
 ``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw) (Anderson et al. 1986).
+
 Thus, we were able to emulate different atmospheric condition and level of
@@
 sky radiation.
-
-\begin{itemize}
-\tightlist
-\item
-  rte\_solver disort
-\item
-  geometry pseudospherical
-\item
-  mol\_abs LOWTRAN
-\end{itemize}
 

### 2024-03-21 article/article.Rmd
Commit 2024-03-21 19:14

--- 2024-03-21 article/article.Rmd
@@
 clear sky radiation was performed by the well established radiation transfer model
-Libradtran [@Emde2016].
+Libradtran [@Emde2016], a similar modeling approach was also used by @Vamvakas2020.
 
-For completeness we will describe the main points of the radiation simulation
-procedure here.  We used as input the spectrum of @Kurucz1994 in the range $280$ to
-$2500\,\text{nm}$.
+<!-- Libradtran options -->
+For completeness, we will describe here the main points of the radiation simulation
+procedure. We used as input the spectrum of @Kurucz1994 in the range $280$ to
+$2500\,\text{nm}$, with the Libradtran radiation transfer solver "disort" on a "pseudospherical"
+geometry and the "LOWTRAN" gas parameterization. For each combination of conditions
+we use a SZA step of $0.2^\circ$.
+<!-- Atmospheric options -->
+For the atmospheric characteristics, we iterated for combinations of AOD at
+$500\,\text{nm}$ ($t_{500\text{nm}}$) with additional offsets of $\pm1$ and
+$\pm2\sigma$, and water column ($w_h$), also with offsets of $\pm1$ and $\pm2\sigma$.
+We applied them on two atmospheric profiles, from the Air Force Geophysics
+Laboratory (AFGL). The "AFGL atmospheric constituent profile, midlatitude summer"
+(afglms) and the "AFG Latmospheric constituent profile, midlatitude winter" (afglmw)
+[@Anderson1986].
 
-We also used the Sun's total solar irradiance from NOAA [@Coddington2005] and the
-Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].
-
-We simulated
-the clear sky radiation, using the solar radiation , with a SZA step of $0.2^\circ$.
-For the
-atmospheric characteristics, we used combinations of AOD at $500\,\text{nm}$
-($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column
-($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and applied it to two atmospheric
-profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and
-"AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
-Thus, we were able to emulate different atmospheric condition and level of
-atmospheric clearness for the climatological conditions of the site.
-
-Furthermore, to account for the Sun's variability in our one-minute GHI measurements,
-we adjusted the model's input spectrum integral to the one of the TSI provided by
-NOAA.  Finally, we adjusted for the effect of the Sun - Earth distance, and
-calculated the clear sky irradiance value at the horizontal plane by using the cosine
-of the corresponding interpolated SZA.  For each period of the year, we used the
-appropriate atmospheric profile (afglms or afglmw).  Thus, the modeled GHI_modeled we
-can directly compare each measured one minute value of GHI, with the expected clear
-sky radiation.
-
-- rte_solver  disort
-- geometry   pseudospherical
-- mol_abs LOWTRAN
+<!-- Lookup table -->
+To create a look up table that aligns with our dataset we applied some adjustments.
+To account for the Sun's variability in our one-minute GHI measurements, we corrected
+the model's input spectrum integral to the one of the value of total solar irradiance
+(TSI) provided by NOAA [@Coddington2005].  Also, we applied the effect of the Earth
+-- Sun distance on the irradiance, by using the distance calculated by the Astropy
+[@AstropyCollaboration2022] software library. As needed, we interpolate the
+irradiances to the exact SZA of our measurements.  For each period of the year, we
+used the appropriate atmospheric profile (afglms or afglmw).  Finally, we calculated
+the clear sky irradiance value at the horizontal plane.  Thus, we were able to
+emulate different atmospheric condition and level of atmospheric clearness for the
+climatological conditions of the site.  Thus, the modeled clear sky irradiances,
+based on the climatological conditions of the site, can be directly compared to each
+measured one-minute value of GHI, for different conditions of atmospheric clearness.
 
@@
 ## Criteria for enhancement identification
+
+Initially, we try to implement criteria of CE identification similar to  .
 

### 2024-03-21 article/article.tex
Commit 2024-03-21 19:14

@@
 clear sky radiation was performed by the well established radiation transfer model
-Libradtran (Emde et al. 2016).
+Libradtran (Emde et al. 2016), a similar modeling approach was also used by Vamvakas, Salamalikis, and Kazantzidis (2020).
 
@@
 procedure. We used as input the spectrum of Kurucz (1994) in the range \(280\) to
-\(2500\,\text{nm}\), with the radiation transfer solver ``disort'' on a ``pseudospherical''
-geometry and the ``LOWTRAN'' gas parameterization.
+\(2500\,\text{nm}\), with the Libradtran radiation transfer solver ``disort'' on a ``pseudospherical''
+geometry and the ``LOWTRAN'' gas parameterization. For each combination of conditions
+we use a SZA step of \(0.2^\circ\).
+For the atmospheric characteristics, we iterated for combinations of AOD at
+\(500\,\text{nm}\) (\(t_{500\text{nm}}\)) with additional offsets of \(\pm1\) and
+\(\pm2\sigma\), and water column (\(w_h\)), also with offsets of \(\pm1\) and \(\pm2\sigma\).
+We applied them on two atmospheric profiles, from the Air Force Geophysics
+Laboratory (AFGL). The ``AFGL atmospheric constituent profile, midlatitude summer''
+(afglms) and the ``AFG Latmospheric constituent profile, midlatitude winter'' (afglmw)
+(Anderson et al. 1986).
 
-We also used the Sun's total solar irradiance from NOAA (Coddington et al. 2005) and the
-Earth - Sun distance calculated by Astropy (Astropy Collaboration et al. 2022).
-
-We simulated
-the clear sky radiation, using the solar radiation , with a SZA step of \(0.2^\circ\).
-
-For the
-atmospheric characteristics, we iterated combinations of AOD at \(500\,\text{nm}\)
-(\(t_{500\text{nm}}\)) and additional offsets of \(\pm1\) and \(\pm2\sigma\), and water column
-(\(w_h\)) with offsets of \(\pm1\) and \(\pm2\sigma\), and applied it to two atmospheric
-profiles ``AFGL atmospheric constituent profile, midlatitude summer'' (afglms) and
-``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw) (Anderson et al. 1986).
-
-Thus, we were able to emulate different atmospheric condition and level of
-atmospheric clearness for the climatological conditions of the site.
-
-Furthermore, to account for the Sun's variability in our one-minute GHI measurements,
-we adjusted the model's input spectrum integral to the one of the TSI provided by
-NOAA. Finally, we adjusted for the effect of the Sun - Earth distance, and
-calculated the clear sky irradiance value at the horizontal plane by using the cosine
-of the corresponding interpolated SZA. For each period of the year, we used the
-appropriate atmospheric profile (afglms or afglmw). Thus, the modeled GHI\_modeled we
-can directly compare each measured one minute value of GHI, with the expected clear
-sky radiation.
+To create a look up table that aligns with our dataset we applied some adjustments.
+To account for the Sun's variability in our one-minute GHI measurements, we corrected
+the model's input spectrum integral to the one of the value of total solar irradiance
+(TSI) provided by NOAA (Coddington et al. 2005). Also, we applied the effect of the Earth
+-- Sun distance on the irradiance, by using the distance calculated by the Astropy
+(Astropy Collaboration et al. 2022) software library. As needed, we interpolate the
+irradiances to the exact SZA of our measurements. For each period of the year, we
+used the appropriate atmospheric profile (afglms or afglmw). Finally, we calculated
+the clear sky irradiance value at the horizontal plane. Thus, we were able to
+emulate different atmospheric condition and level of atmospheric clearness for the
+climatological conditions of the site. Thus, the modeled clear sky irradiances,
+based on the climatological conditions of the site, can be directly compared to each
+measured one-minute value of GHI, for different conditions of atmospheric clearness.
 
@@
 \subsection{Criteria for enhancement identification}\label{criteria-for-enhancement-identification}}
+
+Initially, we try to implement criteria of CE identification similar to .
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Vamvakas2020}{}}%
+Vamvakas, Ioannis, Vasileios Salamalikis, and Andreas Kazantzidis.
+2020.
+{``Evaluation of Enhancement Events of Global Horizontal Irradiance Due to Clouds at Patras, South-West Greece.''} \emph{Renewable Energy} 151 (xxxx): 764--71.
+\url{https://doi.org/gq3sbh}.
+
 \end{CSLReferences}

### 2024-03-21 article/article.Rmd
Commit 2024-03-21 20:16

@@
 
+## Cloud enhancement detection
+
+To be able to detect the CE cases, we had establish a baseline, above which we can
+characterize each data point as enhancement event, by estimating the occurring over
+irradiance.  To have an estimation and a first insight on the phenomenon, we
+experimented with two simpler approaches as the reference.  The Haurwitz's model
+[@Haurwitz1945], which is as simple clear sky we have previous adjusted and had good
+fit with our data [@Natsis2023], and the TSI at the top of the atmosphere.  For both
+cases we tested using an appropriate relative threshold and/or an constant offset.
+The initial results, showed that we can detect a big portion of the CE events. But it
+was evident, by inspecting the daily plot of irradiance, that changes on the
+atmospheric conditions introduced numerous false positive and false negative results.
+
+Initially, we try to implement a simpler approach for the clear sky reference,
+without the use of a radiation transfer model. We experimented with a
+
 ## Clear Sky Irradiance
@@
 clear sky radiation was performed by the well established radiation transfer model
-Libradtran [@Emde2016], a similar modeling approach was also used by @Vamvakas2020.
+Libradtran [@Emde2016], a similar modeling approach, was also used by @Vamvakas2020.
 
@@
 
+## Criteria for cloud enhancement identification
+
 Reasoning for the  final selection...........
-
-## Criteria for enhancement identification
-
-Initially, we try to implement criteria of CE identification similar to  .
 

### 2024-03-21 article/article.tex
Commit 2024-03-21 20:16

@@
 
+\hypertarget{cloud-enhancement-detection}{%
+\subsection{Cloud enhancement detection}\label{cloud-enhancement-detection}}
+
+To be able to detect the CE cases, we had establish a baseline, above which we can
+characterize each data point as enhancement event, by estimating the occurring over
+irradiance. To have an estimation and a first insight on the phenomenon, we
+experimented with two simpler approaches as the reference. The Haurwitz's model
+(Haurwitz 1945), which is as simple clear sky we have previous adjusted and had good
+fit with our data (Natsis, Bais, and Meleti 2023), and the TSI at the top of the atmosphere. For both
+cases we tested using an appropriate relative threshold and/or an constant offset.
+The initial results, showed that we can detect a big portion of the CE events. But it
+was evident, by inspecting the daily plot of irradiance, that changes on the
+atmospheric conditions introduced numerous false positive and false negative results.
+
+Initially, we try to implement a simpler approach for the clear sky reference,
+without the use of a radiation transfer model. We experimented with a
+
 \hypertarget{clear-sky-irradiance}{%
@@
 clear sky radiation was performed by the well established radiation transfer model
-Libradtran (Emde et al. 2016), a similar modeling approach was also used by Vamvakas, Salamalikis, and Kazantzidis (2020).
+Libradtran (Emde et al. 2016), a similar modeling approach, was also used by Vamvakas, Salamalikis, and Kazantzidis (2020).
 
@@
 
+\hypertarget{criteria-for-cloud-enhancement-identification}{%
+\subsection{Criteria for cloud enhancement identification}\label{criteria-for-cloud-enhancement-identification}}
+
 Reasoning for the final selection\ldots\ldots\ldots..
-
-\hypertarget{criteria-for-enhancement-identification}{%
-\subsection{Criteria for enhancement identification}\label{criteria-for-enhancement-identification}}
-
-Initially, we try to implement criteria of CE identification similar to .
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Haurwitz1945}{}}%
+Haurwitz, Bernhard. 1945. {``Insolation in {Relation} to {Cloudiness} and {Cloud} {Density}.''} \emph{Journal of Meteorology} 2 (September): 154--66.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Jones1980}{}}%

### 2024-03-21 article/article.Rmd
Commit 2024-03-21 21:13

@@
 irradiance.  To have an estimation and a first insight on the phenomenon, we
-experimented with two simpler approaches as the reference.  The Haurwitz's model
+experimented with two simple approaches as reference.  The Haurwitz's model
 [@Haurwitz1945], which is as simple clear sky we have previous adjusted and had good
@@
 was evident, by inspecting the daily plot of irradiance, that changes on the
-atmospheric conditions introduced numerous false positive and false negative results.
+atmospheric conditions introduced numerous false positive and false negative
+results.  To produce a more accurate reference, we had to take into account more
+factors that effect the clear sky radiation and used a radiation transfer model.
 
-Initially, we try to implement a simpler approach for the clear sky reference,
-without the use of a radiation transfer model. We experimented with a
+## Modeled clear Sky Irradiance
 
-## Clear Sky Irradiance
-
-In order to identify CE cases, we used a modeled approximation of the expected clear
-sky GHI.  Because of the lack of observational data for the whole period, we used
-some long term climatological data for the main factors responsible for the
-attenuation of the broadband downward solar radiation in the atmosphere, which are
-mainly the aerosols and the water vapors. Fortunately, our site participates in the
-Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998], as we operate a Cimel
-photometer since 2003, collocated with the CM-21 pyranometer.  The mean monthly
-aerosol optical depth (AOD) on different wavelengths is provided by AERONET along
-with the equivalent water column height in the atmosphere.  The simulation of the
-clear sky radiation was performed by the well established radiation transfer model
-Libradtran [@Emde2016], a similar modeling approach, was also used by @Vamvakas2020.
+We approximated the expected clear sky GHI by using a model.  Because of the lack of
+observational data for the whole period, we used some long term climatological data
+for the main factors responsible for the attenuation of the broadband downward solar
+radiation in the atmosphere. Which are mainly the aerosols and the water vapors.
+Fortunately, our site participates in the Aerosol Robotic Network (AERONET)
+[@Giles2019; @Buis1998], as we operate a Cimel photometer since 2003, collocated with
+the CM-21 pyranometer.  The mean monthly aerosol optical depth (AOD) on different
+wavelengths is provided by AERONET, along with the equivalent water column height in
+the atmosphere.  The simulation of the clear sky radiation was performed by the well
+established radiation transfer model Libradtran [@Emde2016], a similar
+approach, was also used by @Vamvakas2020.
 
@@
 
+## CE Criteria investigation
+
 Of course, have to choose which atmospheric conditions qualify as a good clear sky analogous radiation.
@@
 
-## Thresholds investigation
+<!---
+Many have used models or some statistical method to determine then CE thresholds.
+-->
 
@@
 
-## Criteria for cloud enhancement identification
-
-Reasoning for the  final selection...........
-
-Many have used models or some statistical method to determine then CE thresholds.
-
-....... cite ...... Descriptions
-
-We used as reference a modeled clear sky approximation,
-
 Criteria for cloud enhancement identification are set according the Equation\nobreakspace\ref{eq:CE4}
@@
 \text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
-\end{cases}\label{eq:CE4b}
+\end{cases}\label{eq:CE4}
 \end{equation}
@@
 
-Include Example of days plot? Appendix?
+- Include Example of days plot? Appendix?
 
 ... this is more clear to understand and describe ....
-
-## Other method used and rejected
-
--   some other criteria were tested
 

### 2024-03-21 article/article.tex
Commit 2024-03-21 21:13

@@
 irradiance. To have an estimation and a first insight on the phenomenon, we
-experimented with two simpler approaches as the reference. The Haurwitz's model
+experimented with two simple approaches as reference. The Haurwitz's model
 (Haurwitz 1945), which is as simple clear sky we have previous adjusted and had good
@@
 was evident, by inspecting the daily plot of irradiance, that changes on the
-atmospheric conditions introduced numerous false positive and false negative results.
+atmospheric conditions introduced numerous false positive and false negative
+results. To produce a more accurate reference, we had to take into account more
+factors that effect the clear sky radiation and used a radiation transfer model.
 
-Initially, we try to implement a simpler approach for the clear sky reference,
-without the use of a radiation transfer model. We experimented with a
+\hypertarget{modeled-clear-sky-irradiance}{%
+\subsection{Modeled clear Sky Irradiance}\label{modeled-clear-sky-irradiance}}
 
-\hypertarget{clear-sky-irradiance}{%
-\subsection{Clear Sky Irradiance}\label{clear-sky-irradiance}}
-
-In order to identify CE cases, we used a modeled approximation of the expected clear
-sky GHI. Because of the lack of observational data for the whole period, we used
-some long term climatological data for the main factors responsible for the
-attenuation of the broadband downward solar radiation in the atmosphere, which are
-mainly the aerosols and the water vapors. Fortunately, our site participates in the
-Aerosol Robotic Network (AERONET) (Giles et al. 2019; Buis et al. 1998), as we operate a Cimel
-photometer since 2003, collocated with the CM-21 pyranometer. The mean monthly
-aerosol optical depth (AOD) on different wavelengths is provided by AERONET along
-with the equivalent water column height in the atmosphere. The simulation of the
-clear sky radiation was performed by the well established radiation transfer model
-Libradtran (Emde et al. 2016), a similar modeling approach, was also used by Vamvakas, Salamalikis, and Kazantzidis (2020).
+We approximated the expected clear sky GHI by using a model. Because of the lack of
+observational data for the whole period, we used some long term climatological data
+for the main factors responsible for the attenuation of the broadband downward solar
+radiation in the atmosphere. Which are mainly the aerosols and the water vapors.
+Fortunately, our site participates in the Aerosol Robotic Network (AERONET)
+(Giles et al. 2019; Buis et al. 1998), as we operate a Cimel photometer since 2003, collocated with
+the CM-21 pyranometer. The mean monthly aerosol optical depth (AOD) on different
+wavelengths is provided by AERONET, along with the equivalent water column height in
+the atmosphere. The simulation of the clear sky radiation was performed by the well
+established radiation transfer model Libradtran (Emde et al. 2016), a similar
+approach, was also used by Vamvakas, Salamalikis, and Kazantzidis (2020).
 
@@
 
+\hypertarget{ce-criteria-investigation}{%
+\subsection{CE Criteria investigation}\label{ce-criteria-investigation}}
+
 Of course, have to choose which atmospheric conditions qualify as a good clear sky analogous radiation.
@@
 We will refer to this irradiance as \(\text{GHI}_\text{mCSi}\).
-
-\hypertarget{thresholds-investigation}{%
-\subsection{Thresholds investigation}\label{thresholds-investigation}}
 
@@
 
-\hypertarget{criteria-for-cloud-enhancement-identification}{%
-\subsection{Criteria for cloud enhancement identification}\label{criteria-for-cloud-enhancement-identification}}
-
-Reasoning for the final selection\ldots\ldots\ldots..
-
-Many have used models or some statistical method to determine then CE thresholds.
-
-\ldots\ldots. cite \ldots\ldots{} Descriptions
-
-We used as reference a modeled clear sky approximation,
-
 Criteria for cloud enhancement identification are set according the Equation\nobreakspace\ref{eq:CE4}
@@
 \text{Excluded measurements}, & \theta > 78^\circ
-\end{cases}\label{eq:CE4b}
+\end{cases}\label{eq:CE4}
 \end{equation}
@@
 
-Include Example of days plot? Appendix?
-
-\ldots{} this is more clear to understand and describe \ldots.
-
-\hypertarget{other-method-used-and-rejected}{%
-\subsection{Other method used and rejected}\label{other-method-used-and-rejected}}
-
 \begin{itemize}
@@
 \item
-  some other criteria were tested
+  Include Example of days plot? Appendix?
 \end{itemize}
+
+\ldots{} this is more clear to understand and describe \ldots.
 

### 2024-03-23 article/article.Rmd
Commit 2024-03-23 21:12

@@
 a rate of $1\,\text{Hz}$.  The mean and the standard deviation of these samples were
-calculated and recorded every minute.  The measurements were corrected for the zero
-offset ("dark signal" in volts), which was calculated by averaging all measurements
-recorded for a period of $3\,\text{h}$, before (morning) or after (evening) the Sun
-reaches an elevation angle of $-10^\circ$.  The signal was converted to irradiance
-using the ramped value of the instrument’s sensitivity between subsequent
-calibrations.
+calculated and recorded for every minute.  The measurements were corrected for the
+zero offset ("dark signal" in volts), which was calculated by averaging all
+measurements recorded for a period of $3\,\text{h}$, before (morning) or after
+(evening) the Sun reaches an elevation angle of $-10^\circ$.  The signal was
+converted to irradiance using the ramped value of the instrument’s sensitivity
+between subsequent calibrations.
 
@@
 <!-- Data selection -->
-To preserve an unbiased representation of the data we applied a constraint similar
-the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there
-must exist at list 45 minutes of valid measurements, including nighttime near
-sunrise and sunset. Days with less than 5 valid hours are rejected completely.
+To preserve an unbiased representation of the data we applied a constraint, similar
+the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there must
+exist at least 45 minutes of valid measurements, including nighttime near sunrise and
+sunset. Days with less than 5 valid hours are rejected completely.
 <!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7),
@@
 Furthermore, due to the significant measurement uncertainty when the Sun is near the
-horizon, and to some systematic obstructions by nearby buildings, we have excluded
-all measurements with solar zenith angle (SZA) greater than $`r 90-BIO_ELEVA`^\circ$.
+horizon, and due to some systematic obstructions by nearby buildings, we have
+excluded all measurements with solar zenith angle (SZA) greater than 
+$`r 90 - BIO_ELEVA`^\circ$.
 
@@
 
-To be able to detect the CE cases, we had establish a baseline, above which we can
-characterize each data point as enhancement event, by estimating the occurring over
-irradiance.  To have an estimation and a first insight on the phenomenon, we
-experimented with two simple approaches as reference.  The Haurwitz's model
-[@Haurwitz1945], which is as simple clear sky we have previous adjusted and had good
-fit with our data [@Natsis2023], and the TSI at the top of the atmosphere.  For both
-cases we tested using an appropriate relative threshold and/or an constant offset.
-The initial results, showed that we can detect a big portion of the CE events. But it
-was evident, by inspecting the daily plot of irradiance, that changes on the
-atmospheric conditions introduced numerous false positive and false negative
-results.  To produce a more accurate reference, we had to take into account more
-factors that effect the clear sky radiation and used a radiation transfer model.
+To be able to detect the CE cases, we had to establish a baseline, above which we can
+characterize each data point as an enhancement event, by estimating the occurring
+over irradiance (OI).  To have an estimation and a first insight on the phenomenon,
+we experimented with two simple approaches for the reference.  The Haurwitz's model
+[@Haurwitz1945], which is as simple clear sky model, and we had already adjusted and
+had good fit with our data [@Natsis2023], and the TSI at the top of the atmosphere.
+We have tested both cases by using an appropriate relative threshold and/or an
+additional constant offset.  The initial results, showed that we can detect a big
+portion of the CE events. These results were helpful, and helped to establish some
+criteria to further improve the CE identification. It was evident, by inspecting the
+daily plot of irradiance, that changes on the atmospheric conditions introduced
+numerous false positive and false negative results.  To produce a more accurate
+reference, we had to take into account more factors that effect the clear sky
+radiation. So we used a radiation transfer model.
 
@@
 for the main factors responsible for the attenuation of the broadband downward solar
-radiation in the atmosphere. Which are mainly the aerosols and the water vapors.
+radiation in the atmosphere. Which are mainly, the aerosols and the water vapors.
 Fortunately, our site participates in the Aerosol Robotic Network (AERONET)
@@
 established radiation transfer model Libradtran [@Emde2016], a similar
-approach, was also used by @Vamvakas2020.
+approach, was also used by @Vamvakas2020 for creating a clear sky reference.
 
@@
 procedure. We used as input the spectrum of @Kurucz1994 in the range $280$ to
-$2500\,\text{nm}$, with the Libradtran radiation transfer solver "disort" on a "pseudospherical"
-geometry and the "LOWTRAN" gas parameterization. For each combination of conditions
-we use a SZA step of $0.2^\circ$.
+$2500\,\text{nm}$, with the Libradtran radiation transfer solver "disort" on a
+"pseudospherical" geometry and the "LOWTRAN" gas parameterization. For each
+combination of conditions we use a SZA step of $0.2^\circ$.
 <!-- Atmospheric options -->
@@
 <!-- Lookup table -->
-To create a look up table that aligns with our dataset we applied some adjustments.
+To create a look up table that aligns with our dataset, we applied some adjustments.
 To account for the Sun's variability in our one-minute GHI measurements, we corrected
-the model's input spectrum integral to the one of the value of total solar irradiance
-(TSI) provided by NOAA [@Coddington2005].  Also, we applied the effect of the Earth
--- Sun distance on the irradiance, by using the distance calculated by the Astropy
-[@AstropyCollaboration2022] software library. As needed, we interpolate the
+the model's input spectrum integral, to the one of the total solar irradiance (TSI)
+provided by NOAA [@Coddington2005].  Also, we applied the effect of the Earth -- Sun
+distance on the irradiance, by using the distance calculated by the Astropy
+[@AstropyCollaboration2022] software library. As needed, we interpolate the resulting
 irradiances to the exact SZA of our measurements.  For each period of the year, we
@@
 the clear sky irradiance value at the horizontal plane.  Thus, we were able to
-emulate different atmospheric condition and level of atmospheric clearness for the
-climatological conditions of the site.  Thus, the modeled clear sky irradiances,
-based on the climatological conditions of the site, can be directly compared to each
-measured one-minute value of GHI, for different conditions of atmospheric clearness.
+emulate different atmospheric condition and levels of atmospheric clearness for the
+climatological conditions of the site.  With this method, the modeled clear sky
+irradiances can be directly compared to each measured one-minute value of GHI, for
+different conditions of atmospheric clearness.
 
 ## CE Criteria investigation
+
+.......here.....
 

### 2024-03-23 article/article.tex
Commit 2024-03-23 21:12

@@
 Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
-\date{2024-03-21}
+\date{2024-03-23}
 
@@
 a rate of \(1\,\text{Hz}\). The mean and the standard deviation of these samples were
-calculated and recorded every minute. The measurements were corrected for the zero
-offset (``dark signal'' in volts), which was calculated by averaging all measurements
-recorded for a period of \(3\,\text{h}\), before (morning) or after (evening) the Sun
-reaches an elevation angle of \(-10^\circ\). The signal was converted to irradiance
-using the ramped value of the instrument's sensitivity between subsequent
-calibrations.
+calculated and recorded for every minute. The measurements were corrected for the
+zero offset (``dark signal'' in volts), which was calculated by averaging all
+measurements recorded for a period of \(3\,\text{h}\), before (morning) or after
+(evening) the Sun reaches an elevation angle of \(-10^\circ\). The signal was
+converted to irradiance using the ramped value of the instrument's sensitivity
+between subsequent calibrations.
 
@@
 radiation measurements used in this study.
-To preserve an unbiased representation of the data we applied a constraint similar
-the one used by Castillejo-Cuberos and Escobar (2020). Where, for each valid hour of day, there
-must exist at list 45 minutes of valid measurements, including nighttime near
-sunrise and sunset. Days with less than 5 valid hours are rejected completely.
+To preserve an unbiased representation of the data we applied a constraint, similar
+the one used by Castillejo-Cuberos and Escobar (2020). Where, for each valid hour of day, there must
+exist at least 45 minutes of valid measurements, including nighttime near sunrise and
+sunset. Days with less than 5 valid hours are rejected completely.
 Furthermore, due to the significant measurement uncertainty when the Sun is near the
-horizon, and to some systematic obstructions by nearby buildings, we have excluded
-all measurements with solar zenith angle (SZA) greater than \(78^\circ\).
+horizon, and due to some systematic obstructions by nearby buildings, we have
+excluded all measurements with solar zenith angle (SZA) greater than
+\(78^\circ\).
 
@@
 
-To be able to detect the CE cases, we had establish a baseline, above which we can
-characterize each data point as enhancement event, by estimating the occurring over
-irradiance. To have an estimation and a first insight on the phenomenon, we
-experimented with two simple approaches as reference. The Haurwitz's model
-(Haurwitz 1945), which is as simple clear sky we have previous adjusted and had good
-fit with our data (Natsis, Bais, and Meleti 2023), and the TSI at the top of the atmosphere. For both
-cases we tested using an appropriate relative threshold and/or an constant offset.
-The initial results, showed that we can detect a big portion of the CE events. But it
-was evident, by inspecting the daily plot of irradiance, that changes on the
-atmospheric conditions introduced numerous false positive and false negative
-results. To produce a more accurate reference, we had to take into account more
-factors that effect the clear sky radiation and used a radiation transfer model.
+To be able to detect the CE cases, we had to establish a baseline, above which we can
+characterize each data point as an enhancement event, by estimating the occurring
+over irradiance (OI). To have an estimation and a first insight on the phenomenon,
+we experimented with two simple approaches for the reference. The Haurwitz's model
+(Haurwitz 1945), which is as simple clear sky model, and we had already adjusted and
+had good fit with our data (Natsis, Bais, and Meleti 2023), and the TSI at the top of the atmosphere.
+We have tested both cases by using an appropriate relative threshold and/or an
+additional constant offset. The initial results, showed that we can detect a big
+portion of the CE events. These results were helpful, and helped to establish some
+criteria to further improve the CE identification. It was evident, by inspecting the
+daily plot of irradiance, that changes on the atmospheric conditions introduced
+numerous false positive and false negative results. To produce a more accurate
+reference, we had to take into account more factors that effect the clear sky
+radiation. So we used a radiation transfer model.
 
@@
 established radiation transfer model Libradtran (Emde et al. 2016), a similar
-approach, was also used by Vamvakas, Salamalikis, and Kazantzidis (2020).
+approach, was also used by Vamvakas, Salamalikis, and Kazantzidis (2020) for creating a clear sky reference.
 
@@
 procedure. We used as input the spectrum of Kurucz (1994) in the range \(280\) to
-\(2500\,\text{nm}\), with the Libradtran radiation transfer solver ``disort'' on a ``pseudospherical''
-geometry and the ``LOWTRAN'' gas parameterization. For each combination of conditions
-we use a SZA step of \(0.2^\circ\).
+\(2500\,\text{nm}\), with the Libradtran radiation transfer solver ``disort'' on a
+``pseudospherical'' geometry and the ``LOWTRAN'' gas parameterization. For each
+combination of conditions we use a SZA step of \(0.2^\circ\).
 For the atmospheric characteristics, we iterated for combinations of AOD at
@@
 
-To create a look up table that aligns with our dataset we applied some adjustments.
+To create a look up table that aligns with our dataset, we applied some adjustments.
 To account for the Sun's variability in our one-minute GHI measurements, we corrected
-the model's input spectrum integral to the one of the value of total solar irradiance
-(TSI) provided by NOAA (Coddington et al. 2005). Also, we applied the effect of the Earth
--- Sun distance on the irradiance, by using the distance calculated by the Astropy
-(Astropy Collaboration et al. 2022) software library. As needed, we interpolate the
+the model's input spectrum integral, to the one of the total solar irradiance (TSI)
+provided by NOAA (Coddington et al. 2005). Also, we applied the effect of the Earth -- Sun
+distance on the irradiance, by using the distance calculated by the Astropy
+(Astropy Collaboration et al. 2022) software library. As needed, we interpolate the resulting
 irradiances to the exact SZA of our measurements. For each period of the year, we
@@
 the clear sky irradiance value at the horizontal plane. Thus, we were able to
-emulate different atmospheric condition and level of atmospheric clearness for the
-climatological conditions of the site. Thus, the modeled clear sky irradiances,
-based on the climatological conditions of the site, can be directly compared to each
-measured one-minute value of GHI, for different conditions of atmospheric clearness.
+emulate different atmospheric condition and levels of atmospheric clearness for the
+climatological conditions of the site. With this method, the modeled clear sky
+irradiances can be directly compared to each measured one-minute value of GHI, for
+different conditions of atmospheric clearness.
 
@@
 \subsection{CE Criteria investigation}\label{ce-criteria-investigation}}
+
+\ldots\ldots.here\ldots..
 

### 2024-03-23 article/article.tex
Commit 2024-03-23 23:12

@@
 
+Many have used models or some statistical method to determine then CE thresholds.
+
 In this study, we evaluated the effects of the clouds on the total downward radiation
@@
 
-\ldots\ldots.here\ldots..
+We evaluasted the performanse of the modeled clear radiation for the different atmospheric conditions,
+as reference.
+by an empirica approach by inspecting a set of chosen days.
+
+we adjusted teh threshold for each and chek then results
+
+After evaluating the modeled clear radiation for the different atmospheric conditions,
+in relation to the measured GHI data, we choose as a representative of the clear sky radiation,
+the case with
+\(t_{\text{cs}} = t_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\).
+
+\begin{itemize}
+\tightlist
+\item
+  can folleo for clear days
+\item
+  this selection has some subjectivity
+\item
+  the most importand are the thresholds
+\end{itemize}
 
 Of course, have to choose which atmospheric conditions qualify as a good clear sky analogous radiation.
+This selection has some subjectivity, as the definition of clear sky, is in relation
+of the intended usage. Our main focus is to be able to identify the OI created by the
+clouds. Although, the aerosols and water vapor are always present and can not be
+completely removed. The effect of the different clearness lavels
 
-After some evaluation of the modeled radiation in different atmospheric conditions,
-in relation to the GHI data, we choose as a representative of the clear sky radiation,
-the case with
-\(t_{\text{cs}} = t_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\).
+model have to be uniform on clear days
+
+the level is adjusted by the threshold
+
+the effect of the sza uniform
 

### 2024-03-23 article/article.Rmd
Commit 2024-03-23 23:12

@@
 
-.......here.....
+We evaluasted the performanse of the modeled clear radiation for the different atmospheric conditions,
+as reference. 
+by an empirica approach by inspecting a set of chosen days.
+
+we adjusted teh threshold for each and chek then results
+
+After evaluating the modeled clear radiation for the different atmospheric conditions,
+in relation to the measured GHI data, we choose as a representative of the clear sky radiation,
+the case with
+$t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$.
+
+- can folleo for clear days
+- this selection has some subjectivity
+- the most importand are the thresholds
 
 Of course, have to choose which atmospheric conditions qualify as a good clear sky analogous radiation.
+This selection has some subjectivity, as the definition of clear sky, is in relation
+of the intended usage. Our main focus is to be able to identify the OI created by the
+clouds. Although, the aerosols and water vapor are always present and can not be
+completely removed. The effect of the different clearness lavels
 
-After some evaluation of the modeled radiation in different atmospheric conditions,
-in relation to the GHI data, we choose as a representative of the clear sky radiation,
-the case with
-$t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$.
+model have to be uniform on clear days
+
+the level is adjusted by the threshold
+
+the effect of the sza uniform
 
@@
 We will refer to this irradiance as $\text{GHI}_\text{mCSi}$.
-
-<!---
-Many have used models or some statistical method to determine then CE thresholds.
--->
 

### 2024-03-24 article/article.Rmd
Commit 2024-03-24 18:14

@@
 
-We evaluasted the performanse of the modeled clear radiation for the different atmospheric conditions,
-as reference. 
-by an empirica approach by inspecting a set of chosen days.
+The use of the actual modeled values of clear sky GHI alone, can not provide us with
+a robust method to distinguish the CE cases, due to the limited accuracy of the input
+data. Our main focus was to positively identify over irradiance events from CEs, thus
+we used a relative factor, to create an upper envelope of the clear sky irradiance,
+above which, any GHI value can safely attributed to CE.  We evaluated the performance
+of the modeled clear radiation for each of atmospheric level of clearness, as
+reference, in order to conclude which is the most appropriate.
 
-we adjusted teh threshold for each and chek then results
+To select the exact values of these thresholds factors (Equation \ref{eq:CE4}), we
+implemented an empirical method, by manual inspection of the CE identification, on
+specially selected days from the whole dataset.  We used seven sets of selected days,
+with characteristics relevant to the efficiency of the identification threshold.
+These sets were random groups of about 20 to 30 days with the following
+characteristics:
+(a) the largest over irradiance CE events,
+(b) the largest daily total over irradiance,
+(c) without clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
+(d) without clouds and without EC events,
+(e) with at least $60\%$ of the day length without clouds and some EC events,
+(h) random days and
+(i) some manual selected days that were included during the manual inspection.
 
@@
 We will refer to this irradiance as $\text{GHI}_\text{mCSi}$.
-
-The use of the actual modeled values of clear sky GHI can not provide us with a
-robust method to distinguish the CE cases, due to the limited accuracy of the input
-data. Our main focus was to positively identify over irradiance events from CEs,
-thus we used a relative factor, to create an upper envelope of the clear sky
-irradiance, above which, any GHI value can safely attributed to CE.
-
-To select the exact values of the thresholds (Equation \ref{eq:CE4}), we implemented
-manual inspection of the CE identification, on specially selected days from the whole
-dataset.  We used seven sets of selected days, with characteristics relevant to the
-efficiency of the identification threshold.  These sets were random groups of about
-20 to 30 days with the following characteristics:
-(a) the largest over irradiance CE events,
-(b) the largest daily total over irradiance,
-(c) without clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
-(d) without clouds and without EC events,
-(e) with at least $60\%$ of the day length without clouds and some EC events,
-(h) random days and
-(i) some manual selected days that were included during the manual inspection.
-
-<!-- - some manual selected days that were included during the manual inspection -->
-<!-- - 20 days with the largest over irradiance CE events -->
-<!-- - 30 days with largest total over irradiance -->
-<!-- - 20 days without clouds (CSid) @Natsis2023 -->
-<!-- - any day without clouds and EC events -->
-<!-- - 20 days with at least 60% of day length without clouds and some EC events -->
-<!-- - 30 random days -->
-<!-- - some manual selected days that were included during the manual inspection -->
 

### 2024-03-24 article/article.tex
Commit 2024-03-24 18:14

@@
 Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
-\date{2024-03-23}
+\date{2024-03-24}
 
@@
 
-We evaluasted the performanse of the modeled clear radiation for the different atmospheric conditions,
-as reference.
-by an empirica approach by inspecting a set of chosen days.
+The use of the actual modeled values of clear sky GHI alone, can not provide us with
+a robust method to distinguish the CE cases, due to the limited accuracy of the input
+data. Our main focus was to positively identify over irradiance events from CEs, thus
+we used a relative factor, to create an upper envelope of the clear sky irradiance,
+above which, any GHI value can safely attributed to CE. We evaluated the performance
+of the modeled clear radiation for each of atmospheric level of clearness, as
+reference, in order to conclude which is the most appropriate.
 
-we adjusted teh threshold for each and chek then results
+To select the exact values of these thresholds factors (Equation \ref{eq:CE4}), we
+implemented an empirical method, by manual inspection of the CE identification, on
+specially selected days from the whole dataset. We used seven sets of selected days,
+with characteristics relevant to the efficiency of the identification threshold.
+These sets were random groups of about 20 to 30 days with the following
+characteristics:
+(a) the largest over irradiance CE events,
+(b) the largest daily total over irradiance,
+(c) without clouds (by implementing a clear sky identification algorithm as discussed in Natsis, Bais, and Meleti (2023)),
+(d) without clouds and without EC events,
+(e) with at least \(60\%\) of the day length without clouds and some EC events,
+(h) random days and
+(i) some manual selected days that were included during the manual inspection.
 
@@
 We will refer to this irradiance as \(\text{GHI}_\text{mCSi}\).
-
-The use of the actual modeled values of clear sky GHI can not provide us with a
-robust method to distinguish the CE cases, due to the limited accuracy of the input
-data. Our main focus was to positively identify over irradiance events from CEs,
-thus we used a relative factor, to create an upper envelope of the clear sky
-irradiance, above which, any GHI value can safely attributed to CE.
-
-To select the exact values of the thresholds (Equation \ref{eq:CE4}), we implemented
-manual inspection of the CE identification, on specially selected days from the whole
-dataset. We used seven sets of selected days, with characteristics relevant to the
-efficiency of the identification threshold. These sets were random groups of about
-20 to 30 days with the following characteristics:
-(a) the largest over irradiance CE events,
-(b) the largest daily total over irradiance,
-(c) without clouds (by implementing a clear sky identification algorithm as discussed in Natsis, Bais, and Meleti (2023)),
-(d) without clouds and without EC events,
-(e) with at least \(60\%\) of the day length without clouds and some EC events,
-(h) random days and
-(i) some manual selected days that were included during the manual inspection.
 

### 2024-03-24 article/article.tex
Commit 2024-03-24 19:10

@@
 (i) some manual selected days that were included during the manual inspection.
+Where it was needed, for some of the edge cases, we also used images from a sky-cam,
+to further aid the decisions of the manual inspection.
 
-After evaluating the modeled clear radiation for the different atmospheric conditions,
-in relation to the measured GHI data, we choose as a representative of the clear sky radiation,
-the case with
-\(t_{\text{cs}} = t_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\).
+After evaluating the modeled clear radiation for the different atmospheric
+conditions, in relation to the measured GHI data, we choose as a representative of
+the clear sky radiation, the case where
+\(t_{\text{cs}} = t_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\)
+(\(\text{GHI}_\text{mCSi}\)).
 
-\begin{itemize}
-\tightlist
-\item
-  can folleo for clear days
-\item
-  this selection has some subjectivity
-\item
-  the most importand are the thresholds
-\end{itemize}
+With a two branched threshold, as a function of SZA. A constant factor for low SZAs,
+and a higher ramped factor for higher SZAs (Equation\nobreakspace\ref{eq:CE4}).
 
-Of course, have to choose which atmospheric conditions qualify as a good clear sky analogous radiation.
-This selection has some subjectivity, as the definition of clear sky, is in relation
-of the intended usage. Our main focus is to be able to identify the OI created by the
-clouds. Although, the aerosols and water vapor are always present and can not be
-completely removed. The effect of the different clearness lavels
-
-model have to be uniform on clear days
-
-the level is adjusted by the threshold
-
-the effect of the sza uniform
-
-These values will represent a typical atmosphere in
-Thessaloniki with low load of aerosols and humidity, which are the main factor that
-attenuate the GHI, excluding clouds.
-We will refer to this irradiance as \(\text{GHI}_\text{mCSi}\).
-
-Where it was needed, for some of the edge cases, we also used images from a sky-cam,
-along with the manual inspection.
-
-Criteria for cloud enhancement identification are set according the Equation\nobreakspace\ref{eq:CE4}
-
+This is the criterion of our CE identification.
 \begin{equation}
@@
 \end{equation}
-where: \(\theta\) solar zenith angle.
+where: \(\theta\) is the solar zenith angle, \(\text{GHI}_\text{i}\) the measured
+irradiance, and \(\text{GHI}_\text{mCSi}\) the selected modeled clear sky irradiance.
+
+We have to note, that the differentiation of the threshold factor was needed, because
+of the high irradiance values we observed, early in the morning and late on the
+afternoon. We have confirmed, by inspecting images from the sky cam, that we have
+duration of elevated irradiance, either due the clearness of the atmosphere, or some
+interferences by reflections on nearby bright surfaces. Although, these cases may
+mask some of the CE events. The actual CE events, produce higher irradiance and thus
+are identified as such. As a side effect, the reported OI will be slight
+underestimated for those SZAs, but the overall contribution of those cases to the
+total daily energy, is minimal due the low occurrences and the lower irradiances.
+
+These selections has some subjectivity, as the definition of clear sky, is in relation
+of the intended usage. Our main focus is to be able to identify the OI created by the
+clouds. Although, the aerosols and water vapor are always present and can not be
+completely removed. The effect of the different clearness levels
+
+These values will represent a typical atmosphere in
+Thessaloniki with low load of aerosols and humidity, which are the main factor that
+attenuate the GHI, excluding clouds.
 

### 2024-03-24 article/article.Rmd
Commit 2024-03-24 19:10

@@
 (i) some manual selected days that were included during the manual inspection.
+Where it was needed, for some of the edge cases, we also used images from a sky-cam,
+to further aid the decisions of the manual inspection.
 
-After evaluating the modeled clear radiation for the different atmospheric conditions,
-in relation to the measured GHI data, we choose as a representative of the clear sky radiation,
-the case with
-$t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$.
+After evaluating the modeled clear radiation for the different atmospheric
+conditions, in relation to the measured GHI data, we choose as a representative of
+the clear sky radiation, the case where
+$t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
+($\text{GHI}_\text{mCSi}$).
 
-- can folleo for clear days
-- this selection has some subjectivity
-- the most importand are the thresholds
+With a two branched threshold, as a function of SZA. A constant factor for low SZAs,
+and a higher ramped factor for higher SZAs (Equation\nobreakspace\ref{eq:CE4}).
 
-Of course, have to choose which atmospheric conditions qualify as a good clear sky analogous radiation.
-This selection has some subjectivity, as the definition of clear sky, is in relation
-of the intended usage. Our main focus is to be able to identify the OI created by the
-clouds. Although, the aerosols and water vapor are always present and can not be
-completely removed. The effect of the different clearness lavels
-
-model have to be uniform on clear days
-
-the level is adjusted by the threshold
-
-the effect of the sza uniform
-
-These values will represent a typical atmosphere in
-Thessaloniki with low load of aerosols and humidity, which are the main factor that
-attenuate the GHI, excluding clouds.
-We will refer to this irradiance as $\text{GHI}_\text{mCSi}$.
-
-Where it was needed, for some of the edge cases, we also used images from a sky-cam,
-along with the manual inspection.
-
-Criteria for cloud enhancement identification are set according the Equation\nobreakspace\ref{eq:CE4}
-
+This is the criterion of our CE identification.
 <!--
@@
 -->
-
 \begin{equation}
@@
 \end{equation}
-where: $\theta$ solar zenith angle.
+where: $\theta$ is the solar zenith angle, $\text{GHI}_\text{i}$ the measured
+irradiance, and $\text{GHI}_\text{mCSi}$ the selected modeled clear sky irradiance.
+
+<!-- reasoning for cretria -->
+We have to note, that the differentiation of the threshold factor was needed, because
+of the high irradiance values we observed, early in the morning and late on the
+afternoon. We have confirmed, by inspecting images from the sky cam, that we have
+duration of elevated irradiance, either due the clearness of the atmosphere, or some
+interferences by reflections on nearby bright surfaces. Although, these cases may
+mask some of the CE events. The actual CE events, produce higher irradiance and thus
+are identified as such. As a side effect, the reported OI will be slight
+underestimated for those SZAs, but the overall contribution of those cases to the
+total daily energy, is minimal due the low occurrences and the lower irradiances.
+
+<!--
+- can follow for clear days
+- this selection has some subjectivity
+- the most important are the thresholds
+- model have to be uniform on clear days
+- the level is adjusted by the threshold 
+- the effect of the sza uniform
+-->
+
+These selections has some subjectivity, as the definition of clear sky, is in relation
+of the intended usage. Our main focus is to be able to identify the OI created by the
+clouds. Although, the aerosols and water vapor are always present and can not be
+completely removed. The effect of the different clearness levels
+
+These values will represent a typical atmosphere in
+Thessaloniki with low load of aerosols and humidity, which are the main factor that
+attenuate the GHI, excluding clouds.
 

### 2024-03-24 article/article.tex
Commit 2024-03-24 20:11

@@
 (\(\text{GHI}_\text{mCSi}\)).
-
-With a two branched threshold, as a function of SZA. A constant factor for low SZAs,
-and a higher ramped factor for higher SZAs (Equation\nobreakspace\ref{eq:CE4}).
-
+These values represent a typical atmosphere in Thessaloniki with low load of aerosols
+and humidity, which are the main factor that attenuate the GHI, excluding clouds. To
+create the limit of CE identification, we created a two branched threshold, as a
+function of SZA. A constant factor for low SZAs, and a higher ramped factor for
+higher SZAs (Equation\nobreakspace\ref{eq:CE4}).
 This is the criterion of our CE identification.
@@
 
-These selections has some subjectivity, as the definition of clear sky, is in relation
-of the intended usage. Our main focus is to be able to identify the OI created by the
+\ldots\ldots\ldots\ldots.
+
+These selections has some subjectivity, as the definition of clear sky, is depended
+on the intended usage. Our main focus is to be able to identify the OI created by the
 clouds. Although, the aerosols and water vapor are always present and can not be
-completely removed. The effect of the different clearness levels
+completely removed.
+The effect of the different clearness levels
 
-These values will represent a typical atmosphere in
-Thessaloniki with low load of aerosols and humidity, which are the main factor that
-attenuate the GHI, excluding clouds.
+\ldots\ldots\ldots\ldots.
 
-A secondary criterion was used for extreme cloud enhancement cases (ECE)
-identification, relative to the TSI at horizontal plane
-(Equation\nobreakspace{}\ref{eq:ECE})
-
+Another aspect of the CE events, that is often reported in the relative bibliography,
+are cases of extreme cloud enhancement (ECE). These are cases of CE where the
+measured intensity of the irradiance, exceeds the equivalent TSI on the top of the
+atmosphere, and satisfy the Equation\nobreakspace{}\ref{eq:ECE}.
 \begin{equation}
-\text{ECE}: \text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
+\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times \text{TSI}_\text{iTOA}
 \label{eq:ECE}
 \end{equation}
+
+\ldots\ldots.
 
@@
 \item
-  Include Example of days plot? Appendix?
+  Include Example of days plot in the Appendix?
+  \ldots{} this is more clear to understand and describe \ldots.
 \end{itemize}
 
-\ldots{} this is more clear to understand and describe \ldots.
+\ldots\ldots.
 
@@
 model with lag of 1 day, using the `maximum likelihood' fitting method (Gardner, Harvey, and Phillips 1980; Jones 1980) by implementing the function `arima' from the library `stats' of the R
-programming language (R Core Team 2023). The trends were reported together with the \(2\sigma\)
+programming language (R Core Team 2023). The trends are reported together with the \(2\sigma\)
 error. We observe an increase of
@@
 annual statistics, that give a more clear picture about the long term CE trends.
-Hence, we calculated the annual values from the one-minute measurements.
-The annual mean over irradiance is
+Hence, we calculated the annual values from the one-minute measurements. The annual
+mean over irradiance is
 \(0.23\pm 0.11\,W/m^2\)
 (Figure\nobreakspace{}\ref{fig:P-energy-mean}),
-but this value is not very useful due the high
-variability of this metric.
+but this value alone is not very useful due the intrinsic high variability of this
+metric.
 
@@
 with the total energy balance on the atmosphere. The net sun radiation of the region
-is not increased, but rather redistributed through the CE.
+is not increased, but rather redistributed through the CE. Although, the
+instantaneous values, can exceed the equivalent clear sky irradiance to a
+considerable level.
 
@@
 
-Subsequently, the annual energy observed during CE events shows a annual increase of
+Subsequently, the total annual energy observed during CE events shows an increase of
 \(341.6\pm 73.1\,kJ/y\)
@@
 
-Another interesting aspect of the CE cases, is the seasonal cycle. In
+Another interesting aspect of the CE cases, is their seasonal cycle. In
 Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the box plot
@@
 During the Winter (December -- February) the CE cases are about 25\% of the maximum.
-The rest of the months the occurrences seems to ramp between the maximum and minimum.
+The rest of the months the occurrences ramp between the maximum and minimum.
 

### 2024-03-24 article/article.Rmd
Commit 2024-03-24 20:11

@@
 ($\text{GHI}_\text{mCSi}$).
-
-With a two branched threshold, as a function of SZA. A constant factor for low SZAs,
-and a higher ramped factor for higher SZAs (Equation\nobreakspace\ref{eq:CE4}).
-
+These values represent a typical atmosphere in Thessaloniki with low load of aerosols
+and humidity, which are the main factor that attenuate the GHI, excluding clouds.  To
+create the limit of CE identification, we created a two branched threshold, as a
+function of SZA. A constant factor for low SZAs, and a higher ramped factor for
+higher SZAs (Equation\nobreakspace\ref{eq:CE4}).
 This is the criterion of our CE identification.
@@
 
-These selections has some subjectivity, as the definition of clear sky, is in relation
-of the intended usage. Our main focus is to be able to identify the OI created by the
+.............
+
+These selections has some subjectivity, as the definition of clear sky, is depended
+on the intended usage. Our main focus is to be able to identify the OI created by the
 clouds. Although, the aerosols and water vapor are always present and can not be
-completely removed. The effect of the different clearness levels
+completely removed. 
+The effect of the different clearness levels
 
-These values will represent a typical atmosphere in
-Thessaloniki with low load of aerosols and humidity, which are the main factor that
-attenuate the GHI, excluding clouds.
+.............
 
-A secondary criterion was used for extreme cloud enhancement cases (ECE)
-identification, relative to the TSI at horizontal plane
-(Equation\nobreakspace{}\ref{eq:ECE})
-
+<!-- extreme cases criterion -->
+Another aspect of the CE events, that is often reported in the relative bibliography,
+are cases of extreme cloud enhancement (ECE). These are cases of CE where the
+measured intensity of the irradiance, exceeds the equivalent TSI on the top of the
+atmosphere, and satisfy the Equation\nobreakspace{}\ref{eq:ECE}.
 \begin{equation}
-\text{ECE}: \text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
+\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times \text{TSI}_\text{iTOA}
 \label{eq:ECE}
@@
 
-- Include Example of days plot? Appendix?
+.......
 
+- Include Example of days plot in the Appendix?
 ... this is more clear to understand and describe ....
+
+.......
 
@@
 @Jones1980] by implementing the function 'arima' from the library 'stats' of the R
-programming language [@RCT2023]. The trends were reported together with the $2\sigma$
+programming language [@RCT2023]. The trends are reported together with the $2\sigma$
 error.  We observe an increase of
@@
 annual statistics, that give a more clear picture about the long term CE trends.
-Hence, we calculated the annual values from the one-minute measurements.
-The annual mean over irradiance is
+Hence, we calculated the annual values from the one-minute measurements.  The annual
+mean over irradiance is
 $`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm
@@
 (Figure\nobreakspace{}\ref{fig:P-energy-mean}),
-but this value is not very useful due the high
-variability of this metric.
+but this value alone is not very useful due the intrinsic high variability of this
+metric.
 
@@
 ```
-Subsequently, the annual energy observed during CE events shows a annual increase of
+Subsequently, the total annual energy observed during CE events shows an increase of
 $`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
@@
 During the Winter (December -- February) the CE cases are about 25% of the maximum.
-The rest of the months the occurrences seems to ramp between the maximum and minimum.
+The rest of the months the occurrences ramp between the maximum and minimum.
 

### 2024-03-24 GHI_enh_04_investigate.tex
Commit 2024-03-24 21:12

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-20}
+\date{2024-03-24}
 
@@
 
+\begin{verbatim}
+Scale for x is already present.
+Adding another scale for x, which will replace the existing scale.
+\end{verbatim}
+
+\begin{verbatim}
+Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
+Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-4} \end{center}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_N_doy-1} \end{center}
@@
 \begin{verbatim}
-2024-03-20 09:43:30.5 athan@tyler GHI_enh_04_investigate.R 1.065564 mins
+2024-03-24 18:26:30.5 athan@tyler GHI_enh_04_investigate.R 2.229609 mins
 \end{verbatim}

### 2024-03-26 article/article.Rmd
Commit 2024-03-24 21:12
Commit 2024-03-26 11:10

@@
 # Intro
+
+The shortwave solar irradiance, reaches the Earth's surface, is the main energy
+source of the planet. It drives and governs the climate.
+It has direct practical application, in different energy production method.  The
+variability of its intensity, can cause difficulties in predicting the yield and
+designing the appropriate equipment. An aspect of this variability are the
+interaction
 
@@
 characterize each data point as an enhancement event, by estimating the occurring
-over irradiance (OI).  To have an estimation and a first insight on the phenomenon,
+over irradiance (OIR).  To have an estimation and a first insight on the phenomenon,
 we experimented with two simple approaches for the reference.  The Haurwitz's model
@@
 mask some of the CE events. The actual CE events, produce higher irradiance and thus
-are identified as such. As a side effect, the reported OI will be slight
+are identified as such. As a side effect, the reported OIR will be slight
 underestimated for those SZAs, but the overall contribution of those cases to the
@@
 These selections has some subjectivity, as the definition of clear sky, is depended
-on the intended usage. Our main focus is to be able to identify the OI created by the
+on the intended usage. Our main focus is to be able to identify the OIR created by the
 clouds. Although, the aerosols and water vapor are always present and can not be
@@
 on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`.
-The absolute stronger CE event had an over irradiance of 
+The absolute stronger CE event had an OIR of 
 $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,W/m^2$ on
@@
 
-We computed the daily trend of the mean over irradiance of CE
+We computed the daily trend of the mean OIR of CE
 (Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order autoregressive
@@
 `r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2$
-on the mean over irradiance.
+on the mean OIR.
 
@@
 Hence, we calculated the annual values from the one-minute measurements.  The annual
-mean over irradiance is
+mean OIR is
 $`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm
@@
 
-```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean over irradiance per CE."}
+```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean OIR per CE."}
 knitr::include_graphics("../images/P_energy-7.png")
@@
 
-In order to further study the characteristics of the CE events, we grouped the singe
+In order to further study the characteristics of the CE events, we grouped the single
 minute CE events, to continuous CE groups (CEG). Thus, a CEG consists of one or more
@@
 By examining the frequency distribution of the CEG durations
-(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can conclude that longer durations are getting increasingly rare, with durations above 10 minutes very rare.
+(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can conclude that
+longer durations are getting increasingly rare, with durations above 10 minutes very
+rare.
 

### 2024-03-26 article/article.Rmd
Commit 2024-03-26 18:14

@@
 source of the planet. It drives and governs the climate.
-It has direct practical application, in different energy production method.  The
-variability of its intensity, can cause difficulties in predicting the yield and
-designing the appropriate equipment. An aspect of this variability are the
-interaction
+It has direct practical application, in different energy production method.
+.... cite ....
+The variability of its intensity, can cause difficulties in predicting the yield and
+designing the appropriate equipment.
+.... cite ....
+An aspect of this variability are the interaction with the clouds, where locally, under some
+conditions the total shortwave irradiance reaching the ground can be higher than the
+expected clear sky irradiance.
+.... cite ....
+Those enhancements have been reported to be able to exceed .... and duration.
+.... cite ....
 
-CE and ECE usefulness 
-importance
-problems
+The underling mechanism of those events have been studied, with the main factor to be
+.... cite ....
 
-reported trends
+Methods of identification used
+.... cite ....
 
-CE mechanism
+...  reported trends ?...
+.... cite ....
+
+<!-- our work -->
+In this study, we used modeled clear sky irradiance, in order to identify cloud
+enhancement. We studied their occurrences, intensity and duration, in a thirty year
+period at the city of Thessaloniki. We were able to determine some trends of the
+phenomenon, it's Climatology, and some other statistical characteristics.
 
 <!-- Define CE and ECE -->
-In this study, we define as cloud enhancement events (CE) the cases when the measured
+here, we defined as cloud enhancement events (CE) the cases when the measured
 global horizontal irradiance (GHI) at ground level, exceeds the expected value under
 clear-sky conditions.
-Similar, we define the extreme cloud enhancement events (ECE), the cases when GHI,
+Similar, we defined as extreme cloud enhancement events (ECE), the cases when GHI,
 exceeds the Total Solar Irradiance on horizontal plane at ground level.
-Although the duration of these bursts varies from instantaneous to several minutes,
+Although the duration of these bursts varies, from instantaneous to several minutes,
 here we are constrained by the recorded data, to one-minute steps.
 
-Identify CE cases
-
 Characteristics of CE
-
-Climatology and impact on the GHI
 

### 2024-03-26 article/article.tex
Commit 2024-03-24 21:12
Commit 2024-03-26 19:09

@@
 Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
-\date{2024-03-24}
+\date{2024-03-26}
 
@@
 
-CE and ECE usefulness
-importance
-problems
+The shortwave solar irradiance, reaches the Earth's surface, is the main energy
+source of the planet. It drives and governs the climate.
+It has direct practical application, in different energy production method.
+\ldots. cite \ldots.
+The variability of its intensity, can cause difficulties in predicting the yield and
+designing the appropriate equipment.
+\ldots. cite \ldots.
+An aspect of this variability are the interaction with the clouds, where locally, under some
+conditions the total shortwave irradiance reaching the ground can be higher than the
+expected clear sky irradiance.
+\ldots. cite \ldots.
+Those enhancements have been reported to be able to exceed \ldots. and duration.
+\ldots. cite \ldots.
 
-reported trends
+The underling mechanism of those events have been studied, with the main factor to be
+\ldots. cite \ldots{}
+The forward scattering of clouds near the sun has been observed to produce cases of
+extreme enhancement irradiances (Yordanov, Saetre, and Midtgård 2015).
 
-CE mechanism
+Gueymard, 2017; Veerman et al., 2022)
+Methods of identification in the literature include the use of a clear sky radiation
+modelel
 
-In this study, we define as cloud enhancement events (CE) the cases when the measured
+\ldots. cite \ldots.
+
+\ldots{} reported trends ?\ldots{}
+\ldots. cite \ldots.
+
+In this study, we used modeled clear sky irradiance, in order to identify cloud
+enhancement. We studied their occurrences, intensity and duration, in a thirty year
+period at the city of Thessaloniki. We were able to determine some trends of the
+phenomenon, it's Climatology, and some other statistical characteristics.
+
+In the relative bibliography different definition have been used for these events, some of
+the are summarized by (\textbf{Gueymard2017?}).
+Here, we defined as cloud enhancement events (CE) the cases when the measured
 global horizontal irradiance (GHI) at ground level, exceeds the expected value under
 clear-sky conditions.
-Similar, we define the extreme cloud enhancement events (ECE), the cases when GHI,
+Similar, we defined as extreme cloud enhancement events (ECE), the cases when GHI,
 exceeds the Total Solar Irradiance on horizontal plane at ground level.
-Although the duration of these bursts varies from instantaneous to several minutes,
+Although the duration of these bursts varies, from instantaneous to several minutes,
 here we are constrained by the recorded data, to one-minute steps.
 
-Identify CE cases
-
 Characteristics of CE
-
-Climatology and impact on the GHI
 
@@
 characterize each data point as an enhancement event, by estimating the occurring
-over irradiance (OI). To have an estimation and a first insight on the phenomenon,
-we experimented with two simple approaches for the reference. The Haurwitz's model
-(Haurwitz 1945), which is as simple clear sky model, and we had already adjusted and
-had good fit with our data (Natsis, Bais, and Meleti 2023), and the TSI at the top of the atmosphere.
-We have tested both cases by using an appropriate relative threshold and/or an
-additional constant offset. The initial results, showed that we can detect a big
-portion of the CE events. These results were helpful, and helped to establish some
-criteria to further improve the CE identification. It was evident, by inspecting the
-daily plot of irradiance, that changes on the atmospheric conditions introduced
-numerous false positive and false negative results. To produce a more accurate
-reference, we had to take into account more factors that effect the clear sky
-radiation. So we used a radiation transfer model.
+over irradiance (OIR). The OIR, here is defined as the irradiance difference of the
+measured one-minute \(\text{GHI}_i\) from the CE identification criterion in
+Equation\nobreakspace\ref{eq:CE4}
+(\(\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}\)).
+To have an estimation and a first insight on the phenomenon, we experimented with two
+simple approaches for the reference. The Haurwitz's model (Haurwitz 1945), which is
+as simple clear sky model, and we had already adjusted and had good fit with our data
+(Natsis, Bais, and Meleti 2023), and the TSI at the top of the atmosphere. We have tested both cases
+by using an appropriate relative threshold and/or an additional constant offset. The
+initial results, showed that we can detect a big portion of the CE events. These
+results were helpful, and helped to establish some criteria to further improve the CE
+identification. It was evident, by inspecting the daily plot of irradiance, that
+changes on the atmospheric conditions introduced numerous false positive and false
+negative results. To produce a more accurate reference, we had to take into account
+more factors that effect the clear sky radiation. So we used a radiation transfer
+model.
 
@@
 \begin{equation}
-\text{CE} : \begin{cases}
- \text{GHI}_\text{i} > 1.05 \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq 60^\circ$}\\
-\text{GHI}_\text{i} > \left ({ 1.18 + \frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ 78^\circ > \theta > 60^\circ$}\\
+\text{CE} : \text{GHI}_\text{i} > \text{GHI}_\text{CSlim,i}, \text{where} \begin{cases}
+ \text{GHI}_\text{CSlim,i} = 1.05 \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq 60^\circ$}\\
+\text{GHI}_\text{CSlim,i} = \left ({ 1.18 + \frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ 78^\circ > \theta > 60^\circ$}\\
 \text{Excluded measurements}, & \theta > 78^\circ
@@
 on 24~May 2007.
-The absolute stronger CE event had an over irradiance of
+The absolute stronger CE event had an OIR of
 \(341.79\,W/m^2\) on
@@
 \(0.216\pm 0.083\,W/m^2\)
-on the mean over irradiance.
+on the mean OIR.
 
@@
 Hence, we calculated the annual values from the one-minute measurements. The annual
-mean over irradiance is
+mean OIR is
 \(0.23\pm 0.11\,W/m^2\)
@@
 
-\caption{Trends of the mean over irradiance per CE.}\label{fig:P-energy-mean}
+\caption{Trends of the mean OIR per CE.}\label{fig:P-energy-mean}
 \end{figure}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Yordanov2015}{}}%
+Yordanov, Georgi Hristov, Tor Oskar Saetre, and Ole-Morten Midtgård.
+2015.
+{``Extreme Overirradiance Events in Norway: 1.6 Suns Measured Close to 60°n.''} \emph{Solar Energy} 115 (May): 68--73.
+\url{https://doi.org/10.1016/j.solener.2015.02.020}.
+
 \end{CSLReferences}

### 2024-03-26 article/article.Rmd
Commit 2024-03-26 19:09

@@
 The underling mechanism of those events have been studied, with the main factor to be
-.... cite ....
+.... cite ...
+The forward scattering of clouds near the sun has been observed to produce cases of
+extreme enhancement irradiances [@Yordanov2015].
 
-Methods of identification used
+Gueymard, 2017; Veerman et al., 2022)
+Methods of identification in the literature include the use of a clear sky radiation
+modelel
+
 .... cite ....
@@
 <!-- Define CE and ECE -->
-here, we defined as cloud enhancement events (CE) the cases when the measured
+In the relative bibliography different definition have been used for these events, some of
+the are summarized by @Gueymard2017.
+Here, we defined as cloud enhancement events (CE) the cases when the measured
 global horizontal irradiance (GHI) at ground level, exceeds the expected value under
@@
 characterize each data point as an enhancement event, by estimating the occurring
-over irradiance (OIR).  To have an estimation and a first insight on the phenomenon,
-we experimented with two simple approaches for the reference.  The Haurwitz's model
-[@Haurwitz1945], which is as simple clear sky model, and we had already adjusted and
-had good fit with our data [@Natsis2023], and the TSI at the top of the atmosphere.
-We have tested both cases by using an appropriate relative threshold and/or an
-additional constant offset.  The initial results, showed that we can detect a big
-portion of the CE events. These results were helpful, and helped to establish some
-criteria to further improve the CE identification. It was evident, by inspecting the
-daily plot of irradiance, that changes on the atmospheric conditions introduced
-numerous false positive and false negative results.  To produce a more accurate
-reference, we had to take into account more factors that effect the clear sky
-radiation. So we used a radiation transfer model.
+over irradiance (OIR). The OIR, here is defined as the irradiance difference of the
+measured one-minute $\text{GHI}_i$ from the CE identification criterion in
+Equation\nobreakspace\ref{eq:CE4}
+($\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}$).
+To have an estimation and a first insight on the phenomenon, we experimented with two
+simple approaches for the reference.  The Haurwitz's model [@Haurwitz1945], which is
+as simple clear sky model, and we had already adjusted and had good fit with our data
+[@Natsis2023], and the TSI at the top of the atmosphere.  We have tested both cases
+by using an appropriate relative threshold and/or an additional constant offset.  The
+initial results, showed that we can detect a big portion of the CE events. These
+results were helpful, and helped to establish some criteria to further improve the CE
+identification. It was evident, by inspecting the daily plot of irradiance, that
+changes on the atmospheric conditions introduced numerous false positive and false
+negative results.  To produce a more accurate reference, we had to take into account
+more factors that effect the clear sky radiation. So we used a radiation transfer
+model.
 
@@
 \text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
-\end{cases}\label{eq:CE4}
+\end{cases}\label{eq:CE4a}
 \end{equation}
@@
 -->
+<!--
 \begin{equation}
@@
 \text{GHI}_\text{i} > \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
+\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
+\end{cases}\label{eq:CE4b}
+\end{equation}
+where: $\theta$ is the solar zenith angle, $\text{GHI}_\text{i}$ the measured
+irradiance, and $\text{GHI}_\text{mCSi}$ the selected modeled clear sky irradiance.
+-->
+\begin{equation}
+\text{CE} : \text{GHI}_\text{i} > \text{GHI}_\text{CSlim,i}, \text{where} \begin{cases}
+ \text{GHI}_\text{CSlim,i} = `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
+\text{GHI}_\text{CSlim,i} = \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
 \text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ

### 2024-03-26 article/article.Rmd
Commit 2024-03-26 20:14

@@
 
-The underling mechanism of those events have been studied, with the main factor to be
-.... cite ...
+There are some propositions of the underling mechanism of those events as summarized
+by @Gueymard2017, and include scattering on the edge of cumulus clouds or through
+thin cirrus.  Further investigation with radiation transfer modeling methods and
+observations have pointed as the prevailing explanation, the forward Mie scattering
+[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015].
+The overall phenomenon can depend on different interactive factors, that include cloud
+thickness and constitution, and the relative position of the sun, the clouds and the observer.
+As such, th
+
 The forward scattering of clouds near the sun has been observed to produce cases of

### 2024-03-26 article/article.tex
Commit 2024-03-26 20:14

@@
 
-The underling mechanism of those events have been studied, with the main factor to be
-\ldots. cite \ldots{}
+There are some propositions of the underling mechanism of those events as summarized
+by (\textbf{Gueymard2017?}), and include scattering on the edge of cumulus clouds or through
+thin cirrus. Further investigation with radiation transfer modeling methods and
+observations have pointed as the prevailing explanation, the forward Mie scattering
+(\textbf{Pecenak2016?}; \textbf{Thuillier2013?}; \textbf{Yordanov2013?}; Yordanov, Saetre, and Midtgård 2015).
+The overall phenomenon can depend on different interactive factors, that include cloud
+thickness and constitution, and the relative position of the sun, the clouds and the observer.
+As such, th
+
 The forward scattering of clouds near the sun has been observed to produce cases of

### 2024-03-27 article/article.Rmd
Commit 2024-03-27 11:12

@@
 [@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015].
-The overall phenomenon can depend on different interactive factors, that include cloud
-thickness and constitution, and the relative position of the sun, the clouds and the observer.
-As such, th
+The overall phenomenon depends on different interactive factors, that include cloud
+thickness and constitution, and the relative position of the sun, the clouds and the
+observer.  As such, there can be multiple contributing mechanism that create the
+observed enhancements.
 
@@
 period at the city of Thessaloniki. We were able to determine some trends of the
-phenomenon, it's Climatology, and some other statistical characteristics.
+phenomenon, it's Climatology, and some of its general characteristics.
 

### 2024-03-27 article/article.tex
Commit 2024-03-27 11:12

--- 2024-03-26 article/article.tex
@@
 Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
-\date{2024-03-26}
+\date{2024-03-27}
 
@@
 
-The underling mechanism of those events have been studied, with the main factor to be
-\ldots. cite \ldots{}
+There are some propositions of the underling mechanism of those events as summarized
+by Gueymard (2017), and include scattering on the edge of cumulus clouds or through
+thin cirrus. Further investigation with radiation transfer modeling methods and
+observations have pointed as the prevailing explanation, the forward Mie scattering
+(Pecenak et al. 2016; Thuillier et al. 2013; G. H. Yordanov et al. 2013; Georgi Hristov Yordanov, Saetre, and Midtgård 2015).
+The overall phenomenon depends on different interactive factors, that include cloud
+thickness and constitution, and the relative position of the sun, the clouds and the
+observer. As such, there can be multiple contributing mechanism that create the
+observed enhancements.
+
 The forward scattering of clouds near the sun has been observed to produce cases of
-extreme enhancement irradiances (Yordanov, Saetre, and Midtgård 2015).
+extreme enhancement irradiances (Georgi Hristov Yordanov, Saetre, and Midtgård 2015).
 
@@
 period at the city of Thessaloniki. We were able to determine some trends of the
-phenomenon, it's Climatology, and some other statistical characteristics.
+phenomenon, it's Climatology, and some of its general characteristics.
 
 In the relative bibliography different definition have been used for these events, some of
-the are summarized by (\textbf{Gueymard2017?}).
+the are summarized by Gueymard (2017).
 Here, we defined as cloud enhancement events (CE) the cases when the measured
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Gueymard2017}{}}%
+Gueymard, Christian A.
+2017.
+{``Cloud and Albedo Enhancement Impacts on Solar Irradiance Using High-Frequency Measurements from Thermopile and Photodiode Radiometers.
+Part 1: Impacts on Global Horizontal Irradiance.''} \emph{Solar Energy} 153: 755--65.
+\url{https://doi.org/gb283c}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Haurwitz1945}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Pecenak2016}{}}%
+Pecenak, Zachary K., Felipe A.
+Mejia, Ben Kurtz, Amato Evan, and Jan Kleissl.
+2016.
+{``Simulating Irradiance Enhancement Dependence on Cloud Optical Depth and Solar Zenith Angle.''} \emph{Solar Energy} 136 (October): 675--81.
+\url{https://doi.org/10.1016/j.solener.2016.07.045}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-RCT2023}{}}%
 R Core Team. 2023. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Thuillier2013}{}}%
+Thuillier, Gérard, Jean-Marie Perrin, Philippe Keckhut, and François Huppert.
+2013.
+{``Local Enhanced Solar Irradiance on the Ground Generated by Cirrus: Measurements and Interpretation.''} \emph{Journal of Applied Remote Sensing} 7 (1): 073543.
+\url{https://doi.org/10.1117/1.JRS.7.073543}.
 
@@
 \url{https://doi.org/gq3sbh}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Yordanov2013}{}}%
+Yordanov, G.
+H., O.-M.
+Midtgård, T.
+O.
+Saetre, H.
+K.
+Nielsen, and L.
+E.
+Norum.
+2013.
+{``Overirradiance (Cloud Enhancement) Events at High Latitudes.''} \emph{{IEEE} Journal of Photovoltaics} 3 (1): 271--77.
+\url{https://doi.org/10.1109/JPHOTOV.2012.2213581}.
 

### 2024-03-27 article/article.tex
Commit 2024-03-27 12:12

@@
 \ldots. cite \ldots.
-An aspect of this variability are the interaction with the clouds, where locally, under some
-conditions the total shortwave irradiance reaching the ground can be higher than the
-expected clear sky irradiance.
+A big aspect of this variability are the interaction with the clouds. In general
+clouds, absorb part of the solar irradiance, but under certain conditions, can
+enhance the total shortwave irradiance reaching the ground. This effect can locally
+increase the observed total shortwave irradiance higher than the expected clear sky
+irradiance {[}see references therein{]}.
 \ldots. cite \ldots.
@@
 \ldots. cite \ldots.
+Martins, Mantelli, and Rüther (2022)
 
-There are some propositions of the underling mechanism of those events as summarized
+Some of the proposed underling mechanisms of those events have been summarized
 by Gueymard (2017), and include scattering on the edge of cumulus clouds or through
 thin cirrus. Further investigation with radiation transfer modeling methods and
-observations have pointed as the prevailing explanation, the forward Mie scattering
-(Pecenak et al. 2016; Thuillier et al. 2013; G. H. Yordanov et al. 2013; Georgi Hristov Yordanov, Saetre, and Midtgård 2015).
+observations have pointed as the prevailing mechanism, the forward Mie scattering
+(Pecenak et al. 2016; Thuillier et al. 2013; G. H. Yordanov et al. 2013; Georgi Hristov Yordanov, Saetre, and Midtgård 2015), through the clouds.
 The overall phenomenon depends on different interactive factors, that include cloud
-thickness and constitution, and the relative position of the sun, the clouds and the
-observer. As such, there can be multiple contributing mechanism that create the
-observed enhancements.
+thickness and constitution, and the relative position of the sun, the clouds, and the
+observer. As such, there multiple contributing mechanism can create the
+observed irradiance enhancements.
 
@@
 
-Gueymard, 2017; Veerman et al., 2022)
-Methods of identification in the literature include the use of a clear sky radiation
-modelel
+It has been reported than enhancements events can interfere in the comparison of
+ground data and satellite observe ovations (Damiani et al. 2018)
+
+Instruments respose \ldots.
+Martins, Mantelli, and Rüther (2022)
+
+Study of the mechanism has also been done with modeling of different cloud types and
+atmospheric conditions.
+Gueymard (2017); Veerman, Van Stratum, and Van Heerwaarden (2022)
+
+Methods of identification in the literature usually include the use of a simulated clear sky radiation
+Vamvakas, Salamalikis, and Kazantzidis (2020); Mol, Knap, and Van Heerwaarden (2023);
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Damiani2018}{}}%
+Damiani, Alessandro, Hitoshi Irie, Takashi Horio, Tamio Takamura, Pradeep Khatri, Hideaki Takenaka, Takashi Nagao, Takashi Y.
+Nakajima, and Raul R.
+Cordero.
+2018.
+{``Evaluation of Himawari-8 Surface Downwelling Solar Radiation by Ground-Based Measurements.''} \emph{Atmos.
+Meas.
+Tech.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Emde2016}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Martins2022}{}}%
+Martins, G.
+L., S.
+L.
+Mantelli, and R.
+Rüther.
+2022.
+{``Evaluating the Performance of Radiometers for Solar Overirradiance Events.''} \emph{Solar Energy} 231 (January): 47--56.
+\url{https://doi.org/10.1016/j.solener.2021.11.050}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Mol2023}{}}%
+Mol, Wouter B., Wouter H.
+Knap, and Chiel C.
+Van Heerwaarden.
+2023.
+{``Ten Years of 1 Hz Solar Irradiance Observations at Cabauw, the Netherlands, with Cloud Observations, Variability Classifications, and Statistics.''} \emph{Earth System Science Data} 15 (5): 2139--51.
+\url{https://doi.org/10.5194/essd-15-2139-2023}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Natsis2023}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Veerman2022}{}}%
+Veerman, M.
+A., B.
+J.
+H.
+Van Stratum, and C.
+C.
+Van Heerwaarden.
+2022.
+{``A Case Study of Cumulus Convection over Land in Cloud‐resolving Simulations with a Coupled Ray Tracer.''} \emph{Geophysical Research Letters} 49 (23).
+\url{https://doi.org/10.1029/2022GL100808}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Yordanov2013}{}}%

### 2024-03-27 article/article.Rmd
Commit 2024-03-27 12:12

--- 2024-03-26 article/article.Rmd
@@
 .... cite ....
-An aspect of this variability are the interaction with the clouds, where locally, under some
-conditions the total shortwave irradiance reaching the ground can be higher than the
-expected clear sky irradiance.
+A big aspect of this variability are the interaction with the clouds. In general
+clouds, absorb part of the solar irradiance, but under certain conditions, can
+enhance the total shortwave irradiance reaching the ground. This effect can locally
+increase the observed total shortwave irradiance higher than the expected clear sky
+irradiance [see references therein].
 .... cite ....
@@
 .... cite ....
+@Martins2022
 
-The underling mechanism of those events have been studied, with the main factor to be
-.... cite ...
+Some of the proposed underling mechanisms of those events have been summarized
+by @Gueymard2017, and include scattering on the edge of cumulus clouds or through
+thin cirrus.  Further investigation with radiation transfer modeling methods and
+observations have pointed as the prevailing mechanism, the forward Mie scattering
+[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015], through the clouds.
+The overall phenomenon depends on different interactive factors, that include cloud
+thickness and constitution, and the relative position of the sun, the clouds, and the
+observer.  As such, there multiple contributing mechanism can  create the
+observed irradiance enhancements.
+
 The forward scattering of clouds near the sun has been observed to produce cases of
@@
 
-Gueymard, 2017; Veerman et al., 2022)
-Methods of identification in the literature include the use of a clear sky radiation
-modelel
+It has been reported than enhancements events can interfere in the comparison of
+ground data and satellite observe ovations [@Damiani2018]
+
+Instruments respose ....
+@Martins2022
+
+Study of the mechanism has also been done with modeling of different cloud types and
+atmospheric conditions.
+@Gueymard2017; @Veerman2022
+
+Methods of identification in the literature usually include the use of a simulated clear sky radiation
+@Vamvakas2020; @Mol2023;
 

### 2024-03-28 GHI_enh_04_investigate.tex
Commit 2024-03-28 11:10

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-24}
+\date{2024-03-28}
 
@@
 
-Arima: -0.013183 +/- 6.904159
+Arima: -0.013183 +/- 6.898051
 
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-4} \end{center}
+
+Units for GLB\_diff.p\_10 : Watt/m\^{}2
+
+lmD: 1.034078 +/- 0.239285
+
+lmY: 1.034088 +/- 0.23929
+
+Arima: 1.03413 +/- 0.363494
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-5} \end{center}
+
+Units for GLB\_diff.p\_5 : Watt/m\^{}2
+
+lmD: 0.944568 +/- 0.252832
+
+lmY: 0.944578 +/- 0.252837
+
+Arima: 0.944623 +/- 0.38704
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-6} \end{center}
+
+Units for GLB\_diff.p\_90 : Watt/m\^{}2
+
+lmD: 1.109672 +/- 0.07725
+
+lmY: 1.109686 +/- 0.077252
+
+Arima: 1.109689 +/- 0.115906
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-7} \end{center}
+
+Units for GLB\_diff.p\_95 : Watt/m\^{}2
+
+lmD: 1.167512 +/- 0.073583
+
+lmY: 1.167525 +/- 0.073584
+
+Arima: 1.167532 +/- 0.106265
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-8} \end{center}
 
@@
 
-Arima: 33.721354 +/- 8.881459
+Arima: 33.721354 +/- 8.881986
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-5} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-9} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-6} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-10} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-7} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-11} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-8} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-12} \end{center}
 
-Arima: -0.013183 +/- 6.904159
+Arima: -0.013183 +/- 6.898051
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-9} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-13} \end{center}
+
+Units for GLB\_ench.p\_10 : Watt/m\^{}2
+
+lmD: 0.00184 +/- 0.000301
+
+lmY: 0.00184 +/- 0.000301
+
+Arima: 0.00184 +/- 0.000473
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-14} \end{center}
+
+Units for GLB\_ench.p\_5 : Watt/m\^{}2
+
+lmD: 0.001768 +/- 0.000292
+
+lmY: 0.001768 +/- 0.000292
+
+Arima: 0.001768 +/- 0.000451
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-15} \end{center}
+
+Units for GLB\_ench.p\_90 : Watt/m\^{}2
+
+lmD: 0.002432 +/- 0.000235
+
+lmY: 0.002432 +/- 0.000235
+
+Arima: 0.002432 +/- 0.000369
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-16} \end{center}
+
+Units for GLB\_ench.p\_95 : Watt/m\^{}2
+
+lmD: 0.002624 +/- 0.000229
+
+lmY: 0.002624 +/- 0.000229
+
+Arima: 0.002624 +/- 0.000346
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-17} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-10} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-18} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-11} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-19} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-12} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-20} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-13} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-21} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-14} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-22} \end{center}
+
+Units for GLB\_diff.p\_10 : Watt/m\^{}2
+
+lmD: -0.00734 +/- 0.019077
+
+lmY: -0.007339 +/- 0.019077
+
+Arima: -0.007339 +/- 0.019267
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-23} \end{center}
+
+Units for GLB\_diff.p\_5 : Watt/m\^{}2
+
+lmD: -0.027816 +/- 0.017696
+
+lmY: -0.027816 +/- 0.017696
+
+Arima: -0.027816 +/- 0.017858
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-24} \end{center}
+
+Units for GLB\_diff.p\_90 : Watt/m\^{}2
+
+lmD: 0.49203 +/- 0.073274
+
+lmY: 0.492037 +/- 0.073275
+
+Arima: 0.492032 +/- 0.081403
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-25} \end{center}
+
+Units for GLB\_diff.p\_95 : Watt/m\^{}2
+
+lmD: 0.595557 +/- 0.083417
+
+lmY: 0.595566 +/- 0.083419
+
+Arima: 0.59556 +/- 0.094857
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-26} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-15} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-27} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-16} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-28} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-17} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-29} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-18} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-30} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-19} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-31} \end{center}
+
+Units for GLB\_ench.p\_10 : Watt/m\^{}2
+
+lmD: 2.1e-05 +/- 3.2e-05
+
+lmY: 2.1e-05 +/- 3.2e-05
+
+Arima: 2.1e-05 +/- 3.6e-05
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-32} \end{center}
+
+Units for GLB\_ench.p\_5 : Watt/m\^{}2
+
+lmD: -1.2e-05 +/- 2.9e-05
+
+lmY: -1.2e-05 +/- 2.9e-05
+
+Arima: -1.2e-05 +/- 3.4e-05
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-33} \end{center}
+
+Units for GLB\_ench.p\_90 : Watt/m\^{}2
+
+lmD: 0.000922 +/- 0.000106
+
+lmY: 0.000922 +/- 0.000106
+
+Arima: 0.000922 +/- 0.00012
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-34} \end{center}
+
+Units for GLB\_ench.p\_95 : Watt/m\^{}2
+
+lmD: 0.001074 +/- 0.000117
+
+lmY: 0.001074 +/- 0.000117
+
+Arima: 0.001074 +/- 0.000134
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-35} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-20} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-36} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-21} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-37} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-22} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-38} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-23} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-39} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-24} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-40} \end{center}
+
+Units for GLB\_diff.p\_10 : Watt/m\^{}2
+
+lmD: -0.069532 +/- 0.179279
+
+lmY: -0.06952 +/- 0.179282
+
+Arima: -0.124647 +/- 0.339466
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-41} \end{center}
+
+Units for GLB\_diff.p\_5 : Watt/m\^{}2
+
+lmD: -0.089703 +/- 0.178956
+
+lmY: -0.089692 +/- 0.178959
+
+Arima: -0.144328 +/- 0.338161
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-42} \end{center}
+
+Units for GLB\_diff.p\_90 : Watt/m\^{}2
+
+lmD: 0.16704 +/- 0.22968
+
+lmY: 0.167077 +/- 0.229683
+
+Arima: 0.146398 +/- 0.353614
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-43} \end{center}
+
+Units for GLB\_diff.p\_95 : Watt/m\^{}2
+
+lmD: 0.17703 +/- 0.238162
+
+lmY: 0.177067 +/- 0.238165
+
+Arima: 0.158966 +/- 0.358093
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-44} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-25} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-45} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-26} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-46} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-27} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-47} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-28} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-48} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-29} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-49} \end{center}
+
+Units for GLB\_ench.p\_10 : Watt/m\^{}2
+
+lmD: 0.000168 +/- 0.000199
+
+lmY: 0.000168 +/- 0.000199
+
+Arima: 0.000157 +/- 0.000257
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-50} \end{center}
+
+Units for GLB\_ench.p\_5 : Watt/m\^{}2
+
+lmD: 0.000155 +/- 0.000199
+
+lmY: 0.000155 +/- 0.000199
+
+Arima: 0.000144 +/- 0.000256
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-51} \end{center}
+
+Units for GLB\_ench.p\_90 : Watt/m\^{}2
+
+lmD: 0.000509 +/- 0.000261
+
+lmY: 0.000509 +/- 0.000261
+
+Arima: 0.000508 +/- 3e-04
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-52} \end{center}
+
+Units for GLB\_ench.p\_95 : Watt/m\^{}2
+
+lmD: 0.00051 +/- 0.00027
+
+lmY: 0.00051 +/- 0.00027
+
+Arima: 0.000509 +/- 0.000307
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-53} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-30} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-54} \end{center}
 
@@
 \begin{verbatim}
-2024-03-24 18:26:30.5 athan@tyler GHI_enh_04_investigate.R 2.229609 mins
+2024-03-28 08:59:32.3 athan@sagan GHI_enh_04_investigate.R 0.815632 mins
 \end{verbatim}

### 2024-04-01 article/article.Rmd
Commit 2024-03-28 10:14
Commit 2024-04-01 12:14

@@
 The shortwave solar irradiance, reaches the Earth's surface, is the main energy
-source of the planet. It drives and governs the climate.
-It has direct practical application, in different energy production method.
-.... cite ....
-The variability of its intensity, can cause difficulties in predicting the yield and
-designing the appropriate equipment.
-.... cite ....
-A big aspect of this variability are the interaction with the clouds. In general
-clouds, absorb part of the solar irradiance, but under certain conditions, can
+source of the atmosphere and biosphere. It drives and governs the climate
+[@Gray2010].  It has direct practical application, in different industries, like
+energy production and agriculture method.  The variability of its intensity, can
+cause difficulties in predicting the yield and designing the appropriate equipment.
+A lot of research focus on predicting the renewable energy production in a  very fine
+timescale and in near real-time (for a review see @Inman2013; @Graabak2016).
+
+A big aspect of this variability are the interaction with the clouds. In general,
+clouds absorb part of the solar irradiance, but under certain conditions, can
 enhance the total shortwave irradiance reaching the ground. This effect can locally
@@
 Those enhancements have been reported to be able to exceed .... and duration.
+And in extreme cases can compromise the integrity of the infrastructure.
 .... cite ....
@@
 In this study, we used modeled clear sky irradiance, in order to identify cloud
-enhancement. We studied their occurrences, intensity and duration, in a thirty year
+enhancement. We studied their occurrences, intensity and duration, in a thirty-year
 period at the city of Thessaloniki. We were able to determine some trends of the
@@
 Laboratory (AFGL). The "AFGL atmospheric constituent profile, midlatitude summer"
-(afglms) and the "AFG Latmospheric constituent profile, midlatitude winter" (afglmw)
+(afglms) and the "AFGL atmospheric constituent profile, midlatitude winter" (afglmw)
 [@Anderson1986].
@@
 <!-- Lookup table -->
-To create a look up table that aligns with our dataset, we applied some adjustments.
+To create a look-up table that aligns with our dataset, we applied some adjustments.
 To account for the Sun's variability in our one-minute GHI measurements, we corrected
@@
 We have to note, that the differentiation of the threshold factor was needed, because
-of the high irradiance values we observed, early in the morning and late on the
+of the high irradiance values we observed, early in the morning and late in the
 afternoon. We have confirmed, by inspecting images from the sky cam, that we have
-duration of elevated irradiance, either due the clearness of the atmosphere, or some
+duration of elevated irradiance, either due to the clearness of the atmosphere, or some
 interferences by reflections on nearby bright surfaces. Although, these cases may
@@
 
-These selections has some subjectivity, as the definition of clear sky, is depended
+These selections have some subjectivity, as the definition of clear sky, is depended
 on the intended usage. Our main focus is to be able to identify the OIR created by the
@@
 - Include Example of days plot in the Appendix?
-... this is more clear to understand and describe ....
+... this is clearer to understand and describe ....
 
@@
 between the events frequency and events intensity. This is expected as, the stronger
-the CE events become, the more rare are the particular atmospheric and sun conditions
-to occur.
+the CE events become, the rarer the particular atmospheric and sun conditions
+occur.
 

### 2024-04-01 article/article.tex
Commit 2024-03-28 10:14
Commit 2024-04-01 12:14

@@
 Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
-\date{2024-03-27}
+\date{2024-04-01}
 
@@
 The shortwave solar irradiance, reaches the Earth's surface, is the main energy
-source of the planet. It drives and governs the climate.
-It has direct practical application, in different energy production method.
-\ldots. cite \ldots.
-The variability of its intensity, can cause difficulties in predicting the yield and
-designing the appropriate equipment.
-\ldots. cite \ldots.
-A big aspect of this variability are the interaction with the clouds. In general
-clouds, absorb part of the solar irradiance, but under certain conditions, can
+source of the atmosphere and biosphere. It drives and governs the climate
+(Gray et al. 2010). It has direct practical application, in different industries, like
+energy production and agriculture method. The variability of its intensity, can
+cause difficulties in predicting the yield and designing the appropriate equipment.
+A lot of research focus on predicting the renewable energy production in a very fine
+timescale and in near real-time (for a review see Inman, Pedro, and Coimbra (2013); Graabak and Korpås (2016)).
+
+A big aspect of this variability are the interaction with the clouds. In general,
+clouds absorb part of the solar irradiance, but under certain conditions, can
 enhance the total shortwave irradiance reaching the ground. This effect can locally
@@
 Those enhancements have been reported to be able to exceed \ldots. and duration.
+And in extreme cases can compromise the integrity of the infrastructure.
 \ldots. cite \ldots.
@@
 Laboratory (AFGL). The ``AFGL atmospheric constituent profile, midlatitude summer''
-(afglms) and the ``AFG Latmospheric constituent profile, midlatitude winter'' (afglmw)
+(afglms) and the ``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw)
 (Anderson et al. 1986).
 
-To create a look up table that aligns with our dataset, we applied some adjustments.
+To create a look-up table that aligns with our dataset, we applied some adjustments.
 To account for the Sun's variability in our one-minute GHI measurements, we corrected
@@
   Include Example of days plot in the Appendix?
-  \ldots{} this is more clear to understand and describe \ldots.
+  \ldots{} this is clearer to understand and describe \ldots.
 \end{itemize}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Graabak2016}{}}%
+Graabak, Ingeborg, and Magnus Korpås.
+2016.
+{``Variability Characteristics of European Wind and Solar Power Resources---a Review.''} \emph{Energies} 9 (6): 449.
+\url{https://doi.org/10.3390/en9060449}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Gray2010}{}}%
+Gray, L.
+J., J.
+Beer, M.
+Geller, J.
+D.
+Haigh, M.
+Lockwood, K.
+Matthes, U.
+Cubasch, et al.
+2010.
+{``{SOLAR} {INFLUENCES} {ON} {CLIMATE}.''} \emph{Reviews of Geophysics} 48 (4): RG4001.
+\url{https://doi.org/10.1029/2009RG000282}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Gueymard2017}{}}%
@@
 Haurwitz, Bernhard. 1945. {``Insolation in {Relation} to {Cloudiness} and {Cloud} {Density}.''} \emph{Journal of Meteorology} 2 (September): 154--66.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Inman2013}{}}%
+Inman, Rich H., Hugo T.
+C.
+Pedro, and Carlos F.
+M.
+Coimbra.
+2013.
+{``Solar Forecasting Methods for Renewable Energy Integration.''} \emph{Progress in Energy and Combustion Science} 39 (6): 535--76.
+\url{https://doi.org/10.1016/j.pecs.2013.06.002}.
 

### 2024-04-01 article/article.Rmd
Commit 2024-04-01 13:13

@@
 cause difficulties in predicting the yield and designing the appropriate equipment.
-A lot of research focus on predicting the renewable energy production in a  very fine
+A lot of research has been focuces on predicting the renewable energy production in a fine
 timescale and in near real-time (for a review see @Inman2013; @Graabak2016).
@@
 irradiance [see references therein].
-.... cite ....
+
+The enhancements can effect the efficiency and stability of photovoltaic power
+production [@Lappalainen2020; @Jaervelae2020].
+
+And extreme enhancements cases have the potential to  compromise the integrity of the
+infrastructure  [@DoNascimento2019].
+
 Those enhancements have been reported to be able to exceed .... and duration.
-And in extreme cases can compromise the integrity of the infrastructure.
-.... cite ....
+For a list of recorded extreme cases
 @Martins2022

### 2024-04-01 article/article.tex
Commit 2024-04-01 13:13

@@
 cause difficulties in predicting the yield and designing the appropriate equipment.
-A lot of research focus on predicting the renewable energy production in a very fine
+A lot of research has been focuces on predicting the renewable energy production in a fine
 timescale and in near real-time (for a review see Inman, Pedro, and Coimbra (2013); Graabak and Korpås (2016)).
@@
 irradiance {[}see references therein{]}.
-\ldots. cite \ldots.
+
+The enhancements can effect the efficiency and stability of photovoltaic power
+production (Lappalainen and Kleissl 2020; Järvelä and Valkealahti 2020).
+
+And extreme enhancements cases have the potential to compromise the integrity of the
+infrastructure (Do Nascimento et al. 2019).
+
 Those enhancements have been reported to be able to exceed \ldots. and duration.
-And in extreme cases can compromise the integrity of the infrastructure.
-\ldots. cite \ldots.
+For a list of recorded extreme cases
 Martins, Mantelli, and Rüther (2022)
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-DoNascimento2019}{}}%
+Do Nascimento, Lucas Rafael, Trajano De Souza Viana, Rafael Antunes Campos, and Ricardo Rüther.
+2019.
+{``Extreme Solar Overirradiance Events: Occurrence and Impacts on Utility-Scale Photovoltaic Power Plants in Brazil.''} \emph{Solar Energy} 186 (July): 370--81.
+\url{https://doi.org/10.1016/j.solener.2019.05.008}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Emde2016}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Jaervelae2020}{}}%
+Järvelä, Markku, and Seppo Valkealahti.
+2020.
+{``Operation of a {PV} Power Plant During Overpower Events Caused by the Cloud Enhancement Phenomenon.''} \emph{Energies} 13 (9): 2185.
+\url{https://doi.org/10.3390/en13092185}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Jones1980}{}}%
@@
 Kurucz, Robert L. 1994. {``Synthetic Infrared Spectra.''} In \emph{Infrared Solar Physics}, edited by D. M. Rabin, J. T. Jefferies, and C. Lindsey, 523--31. Dordrecht: Springer Netherlands.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lappalainen2020}{}}%
+Lappalainen, Kari, and Jan Kleissl.
+2020.
+{``Analysis of the Cloud Enhancement Phenomenon and Its Effects on Photovoltaic Generators Based on Cloud Speed Sensor Measurements.''} \emph{Journal of Renewable and Sustainable Energy} 12 (4): 043502.
+\url{https://doi.org/10.1063/5.0007550}.
 

### 2024-04-02 article/article.Rmd
Commit 2024-04-02 11:11

@@
 cause difficulties in predicting the yield and designing the appropriate equipment.
-A lot of research has been focuces on predicting the renewable energy production in a fine
-timescale and in near real-time (for a review see @Inman2013; @Graabak2016).
+A lot of research has been focuces on predicting the renewable energy production in a
+fine timescale and in near real-time (for a review see @Inman2013; @Graabak2016).
 
 A big aspect of this variability are the interaction with the clouds. In general,
-clouds absorb part of the solar irradiance, but under certain conditions, can
-enhance the total shortwave irradiance reaching the ground. This effect can locally
-increase the observed total shortwave irradiance higher than the expected clear sky
-irradiance [see references therein].
+clouds absorb part of the solar irradiance, but under certain conditions, can enhance
+the total shortwave irradiance reaching the ground. This effect can locally increase
+the observed total shortwave irradiance higher than the expected clear sky irradiance
+[see references therein].
+
+Some of the proposed underling mechanisms of those events have been summarized by
+@Gueymard2017, and include scattering on the edge of cumulus clouds or through thin
+cirrus.  Further investigation with radiation transfer modeling methods and
+observations have pointed as the prevailing mechanism, the forward Mie scattering
+[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015], through the clouds.
+The overall phenomenon depends on different interactive factors, that include cloud
+thickness, constitution and type, and the relative position of the sun, the clouds,
+and the observer [@Gueymard2017; @Veerman2022].  As such, there are multiple contributing mechanism that can create
+the observed irradiance enhancements.
+
+<!--
+Study of the mechanism has also been done with modeling of different cloud types and
+atmospheric conditions.  @Gueymard2017; @Veerman2022
+-->
 
@@
 
-Some of the proposed underling mechanisms of those events have been summarized
-by @Gueymard2017, and include scattering on the edge of cumulus clouds or through
-thin cirrus.  Further investigation with radiation transfer modeling methods and
-observations have pointed as the prevailing mechanism, the forward Mie scattering
-[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015], through the clouds.
-The overall phenomenon depends on different interactive factors, that include cloud
-thickness and constitution, and the relative position of the sun, the clouds, and the
-observer.  As such, there multiple contributing mechanism can create the
-observed irradiance enhancements.
-
 The forward scattering of clouds near the sun has been observed to produce cases of
@@
 @Martins2022
-
-Study of the mechanism has also been done with modeling of different cloud types and
-atmospheric conditions.
-@Gueymard2017; @Veerman2022
 

### 2024-04-02 article/article.tex
Commit 2024-04-02 11:11

@@
 Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
-\date{2024-04-01}
+\date{2024-04-02}
 
@@
 cause difficulties in predicting the yield and designing the appropriate equipment.
-A lot of research has been focuces on predicting the renewable energy production in a fine
-timescale and in near real-time (for a review see Inman, Pedro, and Coimbra (2013); Graabak and Korpås (2016)).
+A lot of research has been focuces on predicting the renewable energy production in a
+fine timescale and in near real-time (for a review see Inman, Pedro, and Coimbra (2013); Graabak and Korpås (2016)).
 
 A big aspect of this variability are the interaction with the clouds. In general,
-clouds absorb part of the solar irradiance, but under certain conditions, can
-enhance the total shortwave irradiance reaching the ground. This effect can locally
-increase the observed total shortwave irradiance higher than the expected clear sky
-irradiance {[}see references therein{]}.
+clouds absorb part of the solar irradiance, but under certain conditions, can enhance
+the total shortwave irradiance reaching the ground. This effect can locally increase
+the observed total shortwave irradiance higher than the expected clear sky irradiance
+{[}see references therein{]}.
+
+Some of the proposed underling mechanisms of those events have been summarized by
+Gueymard (2017), and include scattering on the edge of cumulus clouds or through thin
+cirrus. Further investigation with radiation transfer modeling methods and
+observations have pointed as the prevailing mechanism, the forward Mie scattering
+(Pecenak et al. 2016; Thuillier et al. 2013; G. H. Yordanov et al. 2013; Georgi Hristov Yordanov, Saetre, and Midtgård 2015), through the clouds.
+The overall phenomenon depends on different interactive factors, that include cloud
+thickness, constitution and type, and the relative position of the sun, the clouds,
+and the observer (Gueymard 2017; Veerman, Van Stratum, and Van Heerwaarden 2022). As such, there are multiple contributing mechanism that can create
+the observed irradiance enhancements.
 
@@
 
-Some of the proposed underling mechanisms of those events have been summarized
-by Gueymard (2017), and include scattering on the edge of cumulus clouds or through
-thin cirrus. Further investigation with radiation transfer modeling methods and
-observations have pointed as the prevailing mechanism, the forward Mie scattering
-(Pecenak et al. 2016; Thuillier et al. 2013; G. H. Yordanov et al. 2013; Georgi Hristov Yordanov, Saetre, and Midtgård 2015), through the clouds.
-The overall phenomenon depends on different interactive factors, that include cloud
-thickness and constitution, and the relative position of the sun, the clouds, and the
-observer. As such, there multiple contributing mechanism can create the
-observed irradiance enhancements.
-
 The forward scattering of clouds near the sun has been observed to produce cases of
@@
 Martins, Mantelli, and Rüther (2022)
-
-Study of the mechanism has also been done with modeling of different cloud types and
-atmospheric conditions.
-Gueymard (2017); Veerman, Van Stratum, and Van Heerwaarden (2022)
 

### 2024-04-02 article/article.Rmd
Commit 2024-04-02 12:14

@@
 
-The shortwave solar irradiance, reaches the Earth's surface, is the main energy
-source of the atmosphere and biosphere. It drives and governs the climate
-[@Gray2010].  It has direct practical application, in different industries, like
-energy production and agriculture method.  The variability of its intensity, can
-cause difficulties in predicting the yield and designing the appropriate equipment.
-A lot of research has been focuces on predicting the renewable energy production in a
+The shortwave solar irradiance, reaching Earth's surface, is the main energy source
+of the atmosphere and biosphere and drives and governs the climate [@Gray2010].  It
+has direct practical application, in different industries, like energy production and
+agriculture method.  The variability of its intensity, can cause difficulties in
+predicting the yield, and designing the specifications of the appropriate equipment.
+A lot of research has been focused on predicting the renewable energy production in a
 fine timescale and in near real-time (for a review see @Inman2013; @Graabak2016).
 
-A big aspect of this variability are the interaction with the clouds. In general,
+A big aspect of this variability is the interaction with the clouds. In general,
 clouds absorb part of the solar irradiance, but under certain conditions, can enhance
-the total shortwave irradiance reaching the ground. This effect can locally increase
+the total shortwave irradiance reaching the ground. This effect, can locally increase
 the observed total shortwave irradiance higher than the expected clear sky irradiance
@@
 
-Some of the proposed underling mechanisms of those events have been summarized by
+Some of the proposed underling mechanisms of those events, have been summarized by
 @Gueymard2017, and include scattering on the edge of cumulus clouds or through thin
@@
 The overall phenomenon depends on different interactive factors, that include cloud
-thickness, constitution and type, and the relative position of the sun, the clouds,
-and the observer [@Gueymard2017; @Veerman2022].  As such, there are multiple contributing mechanism that can create
-the observed irradiance enhancements.
+thickness, constitution and type; and the relative position of the sun, the clouds,
+and the observer [@Gueymard2017; @Veerman2022].  As such, there are multiple
+contributing mechanism that are responsible for the observed irradiance enhancements.
+
+Cloud enhancements have been reported, to be able to exceed in intensity even the
+value of the solar constant, resulting of clear indexes above unit. A summary of
+extreme enchantment cases have been compiled by @Martins2022. There are also some
+practical implication of the cloud enchantments.  The intensity and duration of
+enhancements can effect the efficiency and stability of photovoltaic power production
+[@Lappalainen2020; @Jaervelae2020], and extreme enhancements cases, have the
+potential to compromise the integrity of photovoltaic plants infrastructure
+[@DoNascimento2019].  It has also been demonstrated, that these events can interfere
+in the comparison of ground data and satellite observations [@Damiani2018]
 
@@
 
-The enhancements can effect the efficiency and stability of photovoltaic power
-production [@Lappalainen2020; @Jaervelae2020].
-
-And extreme enhancements cases have the potential to  compromise the integrity of the
-infrastructure  [@DoNascimento2019].
-
-Those enhancements have been reported to be able to exceed .... and duration.
-For a list of recorded extreme cases
-@Martins2022
-
-The forward scattering of clouds near the sun has been observed to produce cases of
-extreme enhancement irradiances [@Yordanov2015].
-
-It has been reported than enhancements events can interfere in the comparison of
-ground data and satellite observe ovations [@Damiani2018]
-
+<!--
 Instruments respose ....
 @Martins2022
+-->
 
-Methods of identification in the literature usually include the use of a simulated clear sky radiation
-@Vamvakas2020; @Mol2023;
-
-.... cite ....
-
-...  reported trends ?...
-.... cite ....
+Methods of identification cloud enchantment events in the literature, usually include
+the use of a simulated clear sky radiation as baseline, that is combined with an
+appropriate threshold or some other statistical characteristics, and in some cases,
+with visual methods with a sky cam [@Vamvakas2020; @Mol2023 and references therein].
 
 <!-- our work -->
-In this study, we used modeled clear sky irradiance, in order to identify cloud
-enhancement. We studied their occurrences, intensity and duration, in a thirty-year
-period at the city of Thessaloniki. We were able to determine some trends of the
-phenomenon, it's Climatology, and some of its general characteristics.
+In this study, we evaluated the effects cloud enhancements on the total downward
+radiation by studding the occurrences, their intensity, and their duration in a
+thirty-year period at the city of Thessaloniki.  We used modeled clear sky
+irradiance, as a baseline to identify cloud enhancements.  We were able to determine
+some trends of the phenomenon, it's Climatology, and some of their  general
+characteristics. We weren't able to find a comparable study that provides trends for
+similar long term dataset, as ours.  The recording of the radiation signal is the
+mean of one-minute. Thus, the minimum resolution of cloud enhancement events (CE), in
+this study is one minute.
 
 <!-- Define CE and ECE -->
-In the relative bibliography different definition have been used for these events, some of
-the are summarized by @Gueymard2017.
-Here, we defined as cloud enhancement events (CE) the cases when the measured
-global horizontal irradiance (GHI) at ground level, exceeds the expected value under
-clear-sky conditions.
-Similar, we defined as extreme cloud enhancement events (ECE), the cases when GHI,
-exceeds the Total Solar Irradiance on horizontal plane at ground level.
-Although the duration of these bursts varies, from instantaneous to several minutes,
-here we are constrained by the recorded data, to one-minute steps.
+In the relative bibliography different definition have been used for these events,
+some of the are summarized by @Gueymard2017.  Here, we defined as cloud enhancement
+events (CE) the cases when the measured global horizontal irradiance (GHI) at ground
+level, exceeds the expected value under clear-sky conditions.  Similar, we define as
+extreme cloud enhancement events (ECE), the cases when GHI, exceeds the Total Solar
+Irradiance on horizontal plane at ground level.  Although the duration of these
+bursts varies, from instantaneous to several minutes, here we are constrained by the
+recorded data, to one-minute steps.
 
-Characteristics of CE
-
-Effects of clouds
-
-- enhancement physics
-- conditions
-- other interferences
-
+<!--
 Identification methods from bib
@@
 - location
-
-Many have used models or some statistical method to determine then CE thresholds.
-
-In this study, we evaluated the effects of the clouds on the total downward radiation
-by studding the occurrences of the cloud enhancement cases, their intensity, and their
-duration.  The recording of the radiation signal is the mean of one-minute. Thus, we
-will refer to this time step as a cloud enhancement event (CE).
+-->
 

### 2024-04-02 article/article.tex
Commit 2024-04-02 12:14

@@
 
-The shortwave solar irradiance, reaches the Earth's surface, is the main energy
-source of the atmosphere and biosphere. It drives and governs the climate
-(Gray et al. 2010). It has direct practical application, in different industries, like
-energy production and agriculture method. The variability of its intensity, can
-cause difficulties in predicting the yield and designing the appropriate equipment.
-A lot of research has been focuces on predicting the renewable energy production in a
+The shortwave solar irradiance, reaching Earth's surface, is the main energy source
+of the atmosphere and biosphere and drives and governs the climate (Gray et al. 2010). It
+has direct practical application, in different industries, like energy production and
+agriculture method. The variability of its intensity, can cause difficulties in
+predicting the yield, and designing the specifications of the appropriate equipment.
+A lot of research has been focused on predicting the renewable energy production in a
 fine timescale and in near real-time (for a review see Inman, Pedro, and Coimbra (2013); Graabak and Korpås (2016)).
 
-A big aspect of this variability are the interaction with the clouds. In general,
+A big aspect of this variability is the interaction with the clouds. In general,
 clouds absorb part of the solar irradiance, but under certain conditions, can enhance
-the total shortwave irradiance reaching the ground. This effect can locally increase
+the total shortwave irradiance reaching the ground. This effect, can locally increase
 the observed total shortwave irradiance higher than the expected clear sky irradiance
@@
 
-Some of the proposed underling mechanisms of those events have been summarized by
+Some of the proposed underling mechanisms of those events, have been summarized by
 Gueymard (2017), and include scattering on the edge of cumulus clouds or through thin
@@
 The overall phenomenon depends on different interactive factors, that include cloud
-thickness, constitution and type, and the relative position of the sun, the clouds,
-and the observer (Gueymard 2017; Veerman, Van Stratum, and Van Heerwaarden 2022). As such, there are multiple contributing mechanism that can create
-the observed irradiance enhancements.
+thickness, constitution and type; and the relative position of the sun, the clouds,
+and the observer (Gueymard 2017; Veerman, Van Stratum, and Van Heerwaarden 2022). As such, there are multiple
+contributing mechanism that are responsible for the observed irradiance enhancements.
 
-The enhancements can effect the efficiency and stability of photovoltaic power
-production (Lappalainen and Kleissl 2020; Järvelä and Valkealahti 2020).
+Cloud enhancements have been reported, to be able to exceed in intensity even the
+value of the solar constant, resulting of clear indexes above unit. A summary of
+extreme enchantment cases have been compiled by Martins, Mantelli, and Rüther (2022). There are also some
+practical implication of the cloud enchantments. The intensity and duration of
+enhancements can effect the efficiency and stability of photovoltaic power production
+(Lappalainen and Kleissl 2020; Järvelä and Valkealahti 2020), and extreme enhancements cases, have the
+potential to compromise the integrity of photovoltaic plants infrastructure
+(Do Nascimento et al. 2019). It has also been demonstrated, that these events can interfere
+in the comparison of ground data and satellite observations (Damiani et al. 2018)
 
-And extreme enhancements cases have the potential to compromise the integrity of the
-infrastructure (Do Nascimento et al. 2019).
+Methods of identification cloud enchantment events in the literature, usually include
+the use of a simulated clear sky radiation as baseline, that is combined with an
+appropriate threshold or some other statistical characteristics, and in some cases,
+with visual methods with a sky cam (Vamvakas, Salamalikis, and Kazantzidis 2020; Mol, Knap, and Van Heerwaarden 2023 and references therein).
 
-Those enhancements have been reported to be able to exceed \ldots. and duration.
-For a list of recorded extreme cases
-Martins, Mantelli, and Rüther (2022)
+In this study, we evaluated the effects cloud enhancements on the total downward
+radiation by studding the occurrences, their intensity, and their duration in a
+thirty-year period at the city of Thessaloniki. We used modeled clear sky
+irradiance, as a baseline to identify cloud enhancements. We were able to determine
+some trends of the phenomenon, it's Climatology, and some of their general
+characteristics. We weren't able to find a comparable study that provides trends for
+similar long term dataset, as ours. The recording of the radiation signal is the
+mean of one-minute. Thus, the minimum resolution of cloud enhancement events (CE), in
+this study is one minute.
 
-The forward scattering of clouds near the sun has been observed to produce cases of
-extreme enhancement irradiances (Georgi Hristov Yordanov, Saetre, and Midtgård 2015).
-
-It has been reported than enhancements events can interfere in the comparison of
-ground data and satellite observe ovations (Damiani et al. 2018)
-
-Instruments respose \ldots.
-Martins, Mantelli, and Rüther (2022)
-
-Methods of identification in the literature usually include the use of a simulated clear sky radiation
-Vamvakas, Salamalikis, and Kazantzidis (2020); Mol, Knap, and Van Heerwaarden (2023);
-
-\ldots. cite \ldots.
-
-\ldots{} reported trends ?\ldots{}
-\ldots. cite \ldots.
-
-In this study, we used modeled clear sky irradiance, in order to identify cloud
-enhancement. We studied their occurrences, intensity and duration, in a thirty-year
-period at the city of Thessaloniki. We were able to determine some trends of the
-phenomenon, it's Climatology, and some of its general characteristics.
-
-In the relative bibliography different definition have been used for these events, some of
-the are summarized by Gueymard (2017).
-Here, we defined as cloud enhancement events (CE) the cases when the measured
-global horizontal irradiance (GHI) at ground level, exceeds the expected value under
-clear-sky conditions.
-Similar, we defined as extreme cloud enhancement events (ECE), the cases when GHI,
-exceeds the Total Solar Irradiance on horizontal plane at ground level.
-Although the duration of these bursts varies, from instantaneous to several minutes,
-here we are constrained by the recorded data, to one-minute steps.
-
-Characteristics of CE
-
-Effects of clouds
-
-\begin{itemize}
-\tightlist
-\item
-  enhancement physics
-\item
-  conditions
-\item
-  other interferences
-\end{itemize}
-
-Identification methods from bib
-
-\begin{itemize}
-\tightlist
-\item
-  clearness index
-\item
-  modeled approaches
-\item
-  algorithmic id
-\item
-  AI
-\item
-  Visual
-\end{itemize}
-
-Constrains of the site
-
-\begin{itemize}
-\tightlist
-\item
-  data
-\item
-  instrument
-\item
-  location
-\end{itemize}
-
-Many have used models or some statistical method to determine then CE thresholds.
-
-In this study, we evaluated the effects of the clouds on the total downward radiation
-by studding the occurrences of the cloud enhancement cases, their intensity, and their
-duration. The recording of the radiation signal is the mean of one-minute. Thus, we
-will refer to this time step as a cloud enhancement event (CE).
+In the relative bibliography different definition have been used for these events,
+some of the are summarized by Gueymard (2017). Here, we defined as cloud enhancement
+events (CE) the cases when the measured global horizontal irradiance (GHI) at ground
+level, exceeds the expected value under clear-sky conditions. Similar, we define as
+extreme cloud enhancement events (ECE), the cases when GHI, exceeds the Total Solar
+Irradiance on horizontal plane at ground level. Although the duration of these
+bursts varies, from instantaneous to several minutes, here we are constrained by the
+recorded data, to one-minute steps.
 

### 2024-04-02 Article_B4/Article_B4.Rmd
Commit 2024-04-02 13:13

--- 2024-04-02 article/article.Rmd
@@
 Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of the
-instrument’s sensitivity was better than $0.7\%$ relative to the initial calibration
-by the manufacturer.
+instrument’s sensitivity was better than $0.7\,\%$ relative to the initial
+calibration by the manufacturer.
 <!-- Measurements -->
@@
 ($\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}$).
-To have an estimation and a first insight on the phenomenon, we experimented with two
+To have an estimation, and a first insight on the phenomenon, we experimented with two
 simple approaches for the reference.  The Haurwitz's model [@Haurwitz1945], which is
@@
 (d) without clouds and without EC events,
-(e) with at least $60\%$ of the day length without clouds and some EC events,
+(e) with at least $60\,\%$ of the day length without clouds and some EC events,
 (h) random days and
@@
 the study period, the most active period of CE occurrences is during May and June.
-During the Winter (December -- February) the CE cases are about 25% of the maximum.
+During the Winter (December -- February) the CE cases are about $25\,\%$ of the maximum.
 The rest of the months the occurrences ramp between the maximum and minimum.
@@
 ```{r relative-month-occurancies, echo=FALSE, fig.cap="Statistics of the number of CE occurancies for each month.
-The box represents the values of the low 25% percentile to 75% percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
+The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
 knitr::include_graphics("../images/clim_CE_month_norm_MAX_median_N-2.png")

### 2024-04-02 Article_B4/Article_B4_plain.tex
Commit 2024-04-02 13:13

--- 2024-04-02 article/article.tex
@@
 Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of the
-instrument's sensitivity was better than \(0.7\%\) relative to the initial calibration
-by the manufacturer.
+instrument's sensitivity was better than \(0.7\,\%\) relative to the initial
+calibration by the manufacturer.
 For the acquisition of radiometric data, the signal of the pyranometer was sampled at
@@
 (\(\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}\)).
-To have an estimation and a first insight on the phenomenon, we experimented with two
+To have an estimation, and a first insight on the phenomenon, we experimented with two
 simple approaches for the reference. The Haurwitz's model (Haurwitz 1945), which is
@@
 (d) without clouds and without EC events,
-(e) with at least \(60\%\) of the day length without clouds and some EC events,
+(e) with at least \(60\,\%\) of the day length without clouds and some EC events,
 (h) random days and
@@
 the study period, the most active period of CE occurrences is during May and June.
-During the Winter (December -- February) the CE cases are about 25\% of the maximum.
+During the Winter (December -- February) the CE cases are about \(25\,\%\) of the maximum.
 The rest of the months the occurrences ramp between the maximum and minimum.
@@
 \caption{Statistics of the number of CE occurancies for each month.
-The box represents the values of the low 25\% percentile to 75\% percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies}
+The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies}
 \end{figure}

### 2024-04-06 article/article.Rmd
Commit 2024-04-06 17:15

@@
 
-We approximated the expected clear sky GHI by using a model.  Because of the lack of
-observational data for the whole period, we used some long term climatological data
-for the main factors responsible for the attenuation of the broadband downward solar
-radiation in the atmosphere. Which are mainly, the aerosols and the water vapors.
-Fortunately, our site participates in the Aerosol Robotic Network (AERONET)
-[@Giles2019; @Buis1998], as we operate a Cimel photometer since 2003, collocated with
-the CM-21 pyranometer.  The mean monthly aerosol optical depth (AOD) on different
-wavelengths is provided by AERONET, along with the equivalent water column height in
-the atmosphere.  The simulation of the clear sky radiation was performed by the well
-established radiation transfer model Libradtran [@Emde2016], a similar
-approach, was also used by @Vamvakas2020 for creating a clear sky reference.
+We approximated the expected clear sky GHI by using a radiation transfer model.  The
+simulations was performed by the well established model Libradtran [@Emde2016], a
+similar approach, was also used by @Vamvakas2020 for creating a clear sky reference.
+Because of the lack of observational data for the whole period, we used some long
+term climatological data for the main factors responsible for the attenuation of the
+broadband downward solar radiation in the atmosphere. Which are mainly, the aerosols
+and the water vapors.  Fortunately, our site participates in the Aerosol Robotic
+Network (AERONET) [@Giles2019; @Buis1998], as we operate a Cimel photometer since
+2003, collocated with the CM-21 pyranometer.  The mean monthly aerosol optical depth
+(AOD) on different wavelengths is provided by AERONET, along with the equivalent
+water column height in the atmosphere.
 
@@
 For the atmospheric characteristics, we iterated for combinations of AOD at
-$500\,\text{nm}$ ($t_{500\text{nm}}$) with additional offsets of $\pm1$ and
+$500\,\text{nm}$ ($\tau_{500\text{nm}}$) with additional offsets of $\pm1$ and
 $\pm2\sigma$, and water column ($w_h$), also with offsets of $\pm1$ and $\pm2\sigma$.
@@
 the clear sky radiation, the case where
-$t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
+$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
 ($\text{GHI}_\text{mCSi}$).
@@
 \begin{equation}
-\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times \text{TSI}_\text{iTOA}
+\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
 \label{eq:ECE}
 \end{equation}
+where: $\theta$ the solar zenith angle, $E_{\odot}$ the solar constant, $r$ the Sun -- Earth distance, $i$ each of the one-minute observation
 
@@
 $`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
-`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2$
+`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2/y$
 on the mean OIR.
@@
 $`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2$
+`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2/y$
 (Figure\nobreakspace{}\ref{fig:P-energy-mean}),
@@
 $`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,/y$
+`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/y$
 (Figure\nobreakspace{}\ref{fig:P-energy-N}).

### 2024-04-06 article/article.tex
Commit 2024-04-06 17:15

@@
 Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
-\date{2024-04-02}
+\date{2024-04-06}
 
@@
 
-We approximated the expected clear sky GHI by using a model. Because of the lack of
-observational data for the whole period, we used some long term climatological data
-for the main factors responsible for the attenuation of the broadband downward solar
-radiation in the atmosphere. Which are mainly, the aerosols and the water vapors.
-Fortunately, our site participates in the Aerosol Robotic Network (AERONET)
-(Giles et al. 2019; Buis et al. 1998), as we operate a Cimel photometer since 2003, collocated with
-the CM-21 pyranometer. The mean monthly aerosol optical depth (AOD) on different
-wavelengths is provided by AERONET, along with the equivalent water column height in
-the atmosphere. The simulation of the clear sky radiation was performed by the well
-established radiation transfer model Libradtran (Emde et al. 2016), a similar
-approach, was also used by Vamvakas, Salamalikis, and Kazantzidis (2020) for creating a clear sky reference.
+We approximated the expected clear sky GHI by using a radiation transfer model. The
+simulations was performed by the well established model Libradtran (Emde et al. 2016), a
+similar approach, was also used by Vamvakas, Salamalikis, and Kazantzidis (2020) for creating a clear sky reference.
+Because of the lack of observational data for the whole period, we used some long
+term climatological data for the main factors responsible for the attenuation of the
+broadband downward solar radiation in the atmosphere. Which are mainly, the aerosols
+and the water vapors. Fortunately, our site participates in the Aerosol Robotic
+Network (AERONET) (Giles et al. 2019; Buis et al. 1998), as we operate a Cimel photometer since
+2003, collocated with the CM-21 pyranometer. The mean monthly aerosol optical depth
+(AOD) on different wavelengths is provided by AERONET, along with the equivalent
+water column height in the atmosphere.
 
@@
 For the atmospheric characteristics, we iterated for combinations of AOD at
-\(500\,\text{nm}\) (\(t_{500\text{nm}}\)) with additional offsets of \(\pm1\) and
+\(500\,\text{nm}\) (\(\tau_{500\text{nm}}\)) with additional offsets of \(\pm1\) and
 \(\pm2\sigma\), and water column (\(w_h\)), also with offsets of \(\pm1\) and \(\pm2\sigma\).
@@
 the clear sky radiation, the case where
-\(t_{\text{cs}} = t_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\)
+\(\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\)
 (\(\text{GHI}_\text{mCSi}\)).
@@
 \begin{equation}
-\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times \text{TSI}_\text{iTOA}
+\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
 \label{eq:ECE}
 \end{equation}
+where: \(\theta\) the solar zenith angle, \(E_{\odot}\) the solar constant, \(r\) the Sun -- Earth distance, \(i\) each of the one-minute observation
 
@@
 error. We observe an increase of
-\(0.216\pm 0.083\,W/m^2\)
+\(0.216\pm 0.083\,W/m^2/y\)
 on the mean OIR.
@@
 mean OIR is
-\(0.23\pm 0.11\,W/m^2\)
+\(0.23\pm 0.11\,W/m^2/y\)
 (Figure\nobreakspace{}\ref{fig:P-energy-mean}),
@@
 occurrences, shows a steady increase of
-\(122.2\pm 22.8\,/y\)
+\(122.2\pm 22.8\,\text{cases}/y\)
 (Figure\nobreakspace{}\ref{fig:P-energy-N}).

### 2024-04-06 article/article.Rmd
Commit 2024-04-06 18:14

@@
 ```
-Subsequently, the total annual energy observed during CE events shows an increase of
+
+Subsequently, the mean annual increase of energy due to CE events is
 $`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm

### 2024-04-07 article/article.Rmd
Commit 2024-04-07 20:14

@@
 
-$\text{GHI}_\text{mCSi}$: modeled clear sky one minute global horizontal irradiance
+$\text{GHI}_\text{CSm}$: modeled clear sky one minute global horizontal irradiance
 
@@
 To create a look-up table that aligns with our dataset, we applied some adjustments.
-To account for the Sun's variability in our one-minute GHI measurements, we corrected
+To account for the Sun's variability in our one-minute GHI measurements,
+
+we corrected each modeled value 
 the model's input spectrum integral, to the one of the total solar irradiance (TSI)
-provided by NOAA [@Coddington2005].  Also, we applied the effect of the Earth -- Sun
+provided by NOAA [@Coddington2005].
+
+Also, we applied the effect of the Earth -- Sun
 distance on the irradiance, by using the distance calculated by the Astropy
@@
 $\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
-($\text{GHI}_\text{mCSi}$).
+($\text{GHI}_\text{CSm}$).
 These values represent a typical atmosphere in Thessaloniki with low load of aerosols
@@
 \text{CE} : \text{GHI}_\text{i} > \text{GHI}_\text{CSlim,i}, \text{where} \begin{cases}
- \text{GHI}_\text{CSlim,i} = `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
-\text{GHI}_\text{CSlim,i} = \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
+ \text{GHI}_\text{CSlim,i} = `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{CSm,i}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
+\text{GHI}_\text{CSlim,i} = \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{CSm,i}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
 \text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
@@
 where: $\theta$ is the solar zenith angle, $\text{GHI}_\text{i}$ the measured
-irradiance, and $\text{GHI}_\text{mCSi}$ the selected modeled clear sky irradiance.
+irradiance, and $\text{GHI}_\text{CSm}$ the selected modeled clear sky irradiance, and $i$ each of the one-minute observation.
 
@@
 \end{equation}
-where: $\theta$ the solar zenith angle, $E_{\odot}$ the solar constant, $r$ the Sun -- Earth distance, $i$ each of the one-minute observation
+where: $\theta$ the solar zenith angle, $E_{\odot}$ the solar constant, $r$ the Sun -- Earth distance, and $i$ each of the one-minute observation.
 
@@
 annual statistics, that give a more clear picture about the long term CE trends.
-Hence, we calculated the annual values from the one-minute measurements.  The annual
-mean OIR is
+Hence, we calculated the annual values from the one-minute measurements.  The trend of
+OIR is
 $`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm

### 2024-04-07 article/article.tex
Commit 2024-04-06 18:14
Commit 2024-04-07 21:13

@@
 Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
-\date{2024-04-06}
+\date{2024-04-07}
 
@@
 
-\(\text{GHI}_\text{mCSi}\): modeled clear sky one minute global horizontal irradiance
+\(\text{GHI}_\text{CSm}\): modeled clear sky one minute global horizontal irradiance
 
@@
 \(500\,\text{nm}\) (\(\tau_{500\text{nm}}\)) with additional offsets of \(\pm1\) and
-\(\pm2\sigma\), and water column (\(w_h\)), also with offsets of \(\pm1\) and \(\pm2\sigma\).
+\(\pm2\sigma\), and water column (\(wc\)), also with offsets of \(\pm1\) and \(\pm2\sigma\).
 We applied them on two atmospheric profiles, from the Air Force Geophysics
@@
 To create a look-up table that aligns with our dataset, we applied some adjustments.
-To account for the Sun's variability in our one-minute GHI measurements, we corrected
-the model's input spectrum integral, to the one of the total solar irradiance (TSI)
-provided by NOAA (Coddington et al. 2005). Also, we applied the effect of the Earth -- Sun
+To account for the Sun's variability, in our one-minute GHI measurements,
+we adapted each modeled value by scaling the\\
+model's input spectrum integral, to the corresponding total solar irradiance (TSI)
+provided by NOAA (Coddington et al. 2005).\\
+Also, we applied the effect of the Earth -- Sun
 distance on the irradiance, by using the distance calculated by the Astropy
@@
 \(\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\)
-(\(\text{GHI}_\text{mCSi}\)).
+(\(\text{GHI}_\text{CSm}\)).
 These values represent a typical atmosphere in Thessaloniki with low load of aerosols
@@
 \begin{equation}
-\text{CE} : \text{GHI}_\text{i} > \text{GHI}_\text{CSlim,i}, \text{where} \begin{cases}
- \text{GHI}_\text{CSlim,i} = 1.05 \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq 60^\circ$}\\
-\text{GHI}_\text{CSlim,i} = \left ({ 1.18 + \frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ 78^\circ > \theta > 60^\circ$}\\
+\text{CE} : \text{E}_\text{i} > \text{E}_\text{CSlim,i}, \text{where} \begin{cases}
+ \text{E}_\text{CSlim,i} = 1.05 \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq 60^\circ$}\\
+\text{E}_\text{CSlim,i} = \left ({ 1.18 + \frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ 78^\circ > \theta > 60^\circ$}\\
 \text{Excluded measurements}, & \theta > 78^\circ
@@
 \end{equation}
-where: \(\theta\) is the solar zenith angle, \(\text{GHI}_\text{i}\) the measured
-irradiance, and \(\text{GHI}_\text{mCSi}\) the selected modeled clear sky irradiance.
+where: \(\theta\) is the solar zenith angle, \(\text{E}\) the measured
+irradiance, \(\text{E}_\text{CSm}\) the selected modeled clear sky irradiance, and \(i\) each of the one-minute observation.
 
@@
 \end{equation}
-where: \(\theta\) the solar zenith angle, \(E_{\odot}\) the solar constant, \(r\) the Sun -- Earth distance, \(i\) each of the one-minute observation
+where: \(\theta\) the solar zenith angle, \(E_{\odot}\) the solar constant, \(r\) the Sun -- Earth distance, and \(i\) each of the one-minute observation.
 
@@
 \item
-  Include Example of days plot in the Appendix?
+  Include Example of days plot in the Appendix!
   \ldots{} this is clearer to understand and describe \ldots.
@@
 annual statistics, that give a more clear picture about the long term CE trends.
-Hence, we calculated the annual values from the one-minute measurements. The annual
-mean OIR is
+Hence, we calculated the annual values from the one-minute measurements. The trend of
+OIR is
 \(0.23\pm 0.11\,W/m^2/y\)
@@
 
-Subsequently, the total annual energy observed during CE events shows an increase of
+Subsequently, the mean annual increase of energy due to CE events is
 \(341.6\pm 73.1\,kJ/y\)

### 2024-04-07 article/article.Rmd
Commit 2024-04-07 21:13

@@
 $500\,\text{nm}$ ($\tau_{500\text{nm}}$) with additional offsets of $\pm1$ and
-$\pm2\sigma$, and water column ($w_h$), also with offsets of $\pm1$ and $\pm2\sigma$.
+$\pm2\sigma$, and water column ($wc$), also with offsets of $\pm1$ and $\pm2\sigma$.
 We applied them on two atmospheric profiles, from the Air Force Geophysics
@@
 To create a look-up table that aligns with our dataset, we applied some adjustments.
-To account for the Sun's variability in our one-minute GHI measurements,
-
-we corrected each modeled value 
-the model's input spectrum integral, to the one of the total solar irradiance (TSI)
+To account for the Sun's variability, in our one-minute GHI measurements, 
+we adapted each modeled value by scaling the  
+model's input spectrum integral, to the corresponding total solar irradiance (TSI)
 provided by NOAA [@Coddington2005].  
-
 Also, we applied the effect of the Earth -- Sun
@@
 \begin{equation}
-\text{CE} : \text{GHI}_\text{i} > \text{GHI}_\text{CSlim,i}, \text{where} \begin{cases}
- \text{GHI}_\text{CSlim,i} = `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{CSm,i}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
-\text{GHI}_\text{CSlim,i} = \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{CSm,i}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
+\text{CE} : \text{E}_\text{i} > \text{E}_\text{CSlim,i}, \text{where} \begin{cases}
+ \text{E}_\text{CSlim,i} = `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
+\text{E}_\text{CSlim,i} = \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
 \text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
@@
 \end{equation}
-where: $\theta$ is the solar zenith angle, $\text{GHI}_\text{i}$ the measured
-irradiance, and $\text{GHI}_\text{CSm}$ the selected modeled clear sky irradiance, and $i$ each of the one-minute observation.
+where: $\theta$ is the solar zenith angle, $\text{E}$ the measured
+irradiance, $\text{E}_\text{CSm}$ the selected modeled clear sky irradiance, and $i$ each of the one-minute observation.
 
@@
 
-- Include Example of days plot in the Appendix?
+- Include Example of days plot in the Appendix!
 ... this is clearer to understand and describe ....

### 2024-04-08 GHI_enh_03_process.tex
Commit 2024-03-15 14:14
Commit 2024-03-15 21:12
Commit 2024-03-28 11:10
Commit 2024-04-08 20:14

--- 2024-03-02 GHI_enh_03_process.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-02}
+\date{2024-04-08}
 
@@
 }
+\begin{verbatim}
+
+ USING CSMODE: Low_B.Low_W
+
+C4 factor: 1.05 
+C4 offset: 0 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with extreme cases day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with strong enhancement day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with sunny day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with sunny enhancement day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with cloudy day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with random day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with manual test days 
+\end{verbatim}
+
+\begin{verbatim}
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
+i Please use the `legend.position.inside` argument of `theme()` instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
+\begin{verbatim}
+2024-04-08 15:48:57.0 athan@sagan GHI_enh_02_ID_CE.R 29.123272 mins
+\end{verbatim}
+
 Alpha * HAU is CS\_ref
@@
 Days_of_year
+dummy
 Energy_Div
@@
 \begin{verbatim}
-2024-03-02 09:45:10.6 athan@tyler GHI_enh_03_process.R 2.001386 mins
+2024-04-08 15:55:25.5 athan@sagan GHI_enh_02_ID_CE.R 3.671820 mins
 \end{verbatim}

### 2024-04-09 GHI_enh_04_investigate.tex
Commit 2024-03-28 12:14
Commit 2024-04-07 21:13
Commit 2024-04-09 16:18

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-28}
+\date{2024-04-09}
 
@@
 \begin{verbatim}
+Run previous step: ./GHI_enh_03_process.R
+\end{verbatim}
+
+\begin{verbatim}
+
+Attaching package: 'timetk'
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:data.table':
+
+    :=
+\end{verbatim}
+
+\begin{verbatim}
+frequency = 30 observations
+\end{verbatim}
+
+\begin{verbatim}
+trend = 180 observations
+\end{verbatim}
+
+\begin{verbatim}
+frequency = 30 observations
+\end{verbatim}
+
+\begin{verbatim}
+trend = 180 observations
+\end{verbatim}
+
+\begin{verbatim}
+
+Call:
+stats::lm(formula = .formula, data = df)
+
+Residuals:
+    Min      1Q  Median      3Q     Max 
+-372.77 -150.51  -49.67   99.05  778.55
+
+Coefficients:
+                   Estimate Std. Error t value Pr(>|t|)    
+(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
+as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
+---
+Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+
+Residual standard error: 217 on 361 degrees of freedom
+Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
+F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
+
+aa
+aday
+All_daily_ratio_lim
+alpha
+ampl
+avar
+BIO_ELEVA
+C1_Clearness_Kt_THRES
+C1_GLB_diff_THRES
+C2_Clearness_Kt_THRES
+C3_cs_ref_ratio
+C4_cs_ref_ratio
+C4_GLB_diff_THRES
+C4_lowcut_ratio
+C4_lowcut_sza
+Clear_daily_ratio_lim
+CLEARdir
+Cloud_daily_ratio_lim
+cols
+common_data_13
+common_data_14
+common_data_14_2
+CS_file_13
+CS_file_14
+CS_file_14_2
+csmodel
+Daily_aggregation_N_lim
+Daily_confidence_limit
+daylist
+Days_of_year
+Energy_Div
+I1_longterm
+I2_szatrend
+I3_trendsconsist
+ii
+inpatern
+Input_data_ID
+Kurudz_SC
+MIN_ELEVA
+MIN_N
+Monthly_aggegation_N_lim
+Monthly_confidence_limit
+my.cols
+my.cols.gr
+pyear
+R_COMPILE_PKGS
+RANDOM_SEED
+raw_input_data
+running_mean_window_days
+running_mean_window_years
+SEAS_MIN_N
+SelEnhanc
+SZA_aggregation_N_lim
+SZA_BIN
+SZA_confidence_limit
+torun
+variables_fl
+yearstodo
+ylim
+ST_daily
+ST_E_daily
+ST_E_daily_seas
+ST_E_monthly
+ST_E_monthly_seas
+ST_E_sza
+ST_E_sza_doy
+ST_E_sza_monthly
+ST_E_yearly
+ST_extreme_daily
+ST_extreme_monthly
+ST_extreme_SZA
+ST_extreme_SZA_doy
+ST_extreme_SZA_monthly
+ST_extreme_total
+ST_extreme_yearly
+ST_G0
+ST_G1
+ST_monthly
+ST_sza
+ST_sza_doy
+ST_sza_monthly
+ST_total
+ST_yearly
+2024-04-09 13:15:00.5 athan@tyler GHI_enh_03_process.R 22.842565 mins
+\end{verbatim}
+
+\begin{verbatim}
 ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
@@
 
-Arima: -0.013183 +/- 6.898051
+Arima: -0.013183 +/- 6.904159
 
@@
 
-Arima: 1.03413 +/- 0.363494
+Arima: 1.03413 +/- 0.363491
 
@@
 
-Arima: 0.944623 +/- 0.38704
+Arima: 0.944623 +/- 0.387039
 
@@
 
-Arima: 33.721354 +/- 8.881986
+Arima: 33.721354 +/- 8.881459
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-8} \end{center}
+
 @Martins2022
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-8} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-9} \end{center}
 
@@
 \begin{verbatim}
-2024-03-28 08:59:32.3 athan@sagan GHI_enh_04_investigate.R 0.815632 mins
+2024-04-09 13:17:00.8 athan@tyler GHI_enh_03_process.R 1.962400 mins
 \end{verbatim}

### 2024-04-09 GHI_enh_02_ID_CE.Rmd
Commit 2024-04-09 19:12

---
title:         "Enhancement of SDR in Thessaloniki "
author:
  - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisphysicist@gmail.com]
  - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
abstract:
  "Study of GHI enchantment."

documentclass:  article
classoption:    a4paper,oneside
fontsize:       10pt
geometry:       "left=0.5in,right=0.5in,top=0.5in,bottom=0.5in"
link-citations: yes
colorlinks:     yes

header-includes:
- \usepackage{caption}
- \usepackage{placeins}
- \captionsetup{font=small}

output:
  bookdown::pdf_document2:
    number_sections: no
    fig_caption:     no
    keep_tex:        yes
    latex_engine:    xelatex
    toc:             yes
    toc_depth:       4
    fig_width:       7
    fig_height:      4.5
  html_document:
    toc:             true
    keep_md:         yes
    fig_width:       7
    fig_height:      4.5

date: "`r format(Sys.time(), '%F')`"

---

```{r echo=F, include=T}

## __ Document options ---------------------------------------------------------

knitr::opts_chunk$set(comment    = ""       )
knitr::opts_chunk$set(dev        = c("pdf", "png")) ## expected option
# knitr::opts_chunk$set(dev        = "png"    )       ## for too much data
knitr::opts_chunk$set(out.width  = "100%"   )
knitr::opts_chunk$set(fig.align  = "center" )
knitr::opts_chunk$set(cache      =  FALSE   )  ## !! breaks calculations
knitr::opts_chunk$set(fig.pos    = '!h'     )

## __ Set environment  ---------------------------------------------------------
Sys.setenv(TZ = "UTC")
Script.Name <- "./GHI_enh_02_ID_CE.R"
tic <- Sys.time()

if (!interactive()) {
    pdf( file = paste0("./runtime/", basename(sub("\\.R$",".pdf", Script.Name))))
    sink(file = paste0("./runtime/", basename(sub("\\.R$",".out", Script.Name))), split = TRUE)
}

```
```{r echo=F, include=T}
library(data.table  , quietly = TRUE, warn.conflicts = FALSE)
require(zoo         , quietly = TRUE, warn.conflicts = FALSE)
library(pander      , quietly = TRUE, warn.conflicts = FALSE)
library(ggplot2     , quietly = TRUE, warn.conflicts = FALSE)
library(RColorBrewer, quietly = TRUE, warn.conflicts = FALSE)
library(pracma      , quietly = TRUE, warn.conflicts = FALSE)

panderOptions("table.alignment.default", "right")
panderOptions("table.split.table",        120   )

## __ Load external functions --------------------------------------------------
## Functions from `https://github.com/thanasisn/IStillBreakStuff/tree/main/FUNCTIONS/R`
source("~/CODE/FUNCTIONS/R/data.R")
source("~/CODE/FUNCTIONS/R/trig_deg.R")

## __ Source initial scripts  --------------------------------------------------
source("./GHI_enh_00_variables.R")
source("./GHI_enh_00_dictionary.R")

## Override notification function
options(error = function() {
    if (interactive()) {
        system("mplayer /usr/share/sounds/freedesktop/stereo/dialog-warning.oga", ignore.stdout = T, ignore.stderr = T)
        system(paste("notify-send -u normal -t 30000 ", Script.Name, " 'An error occurred!'"))
    }
})

##  Prepare raw data if needed  ------------------------------------------------
if (
    file.exists(raw_input_data) == FALSE |
    file.mtime(raw_input_data) < file.mtime("./GHI_enh_00_variables.R") |
    file.mtime(raw_input_data) < file.mtime("./GHI_enh_01_raw_data.R")
) {
    source("./GHI_enh_01_raw_data.R")
    dummy <- gc()
}

## __ Execution control  -------------------------------------------------------
TEST <- FALSE
# TEST <- TRUE

if (TEST) {
    warning("\n\n ** Test is active!! ** \n\n")
}

##  Load Enhancement data  -----------------------------------------------------
DATA <- readRDS(raw_input_data)
tic  <- Sys.time()

##  Add CS data from Libradtran  -----------------------------------------------
DATA <- merge(DATA, readRDS("./data/lookuptable_datatable.Rds"))

##  Reset Randomness  ----------------------------------------------------------
RANDOM_SEED <- 333
set.seed(RANDOM_SEED)
## may need to reset seed in each randomness generation below

##  Choose CS data to use ------------------------------------------------------
DATA$TYPE |> unique()
grep("Exact_B", names(DATA), value = T)

##  Get Kurudz Solar constant  -------------------------------------------------

Kurudz <- read.table("~/LibRadTranG/libRadtran-2.0.5/data/solar_flux/kurudz_0.1nm.dat")
Kurudz <- data.table(Kurudz)

# currently we only on set to run Libradtran
spectrum  <- Kurudz[ V1 >= 280 & V1 <= 2500]
Kurudz_SC <- trapz(x = spectrum$V1, y = spectrum$V2) / 1000

summary(DATA[, tsi_1au_comb / Kurudz_SC ])
# plot(DATA[, tsi_1au_comb / Kurudz_SC ])

DATA[, TSI_Kurudz_factor := tsi_1au_comb / Kurudz_SC ]
```

 Alpha * HAU is CS_ref

```{r echo=F, include=TRUE}

## __ Enhancement criteria  ----------------------------------------------------
# SelEnhanc <- "Enhanc_C_1"
# SelEnhanc <- "Enhanc_C_2"
# SelEnhanc <- "Enhanc_C_3"

SelEnhanc <- "Enhanc_C_4"

## Mark used criteria for diff rati ench
DATA[, CEC := SelEnhanc ]
```

## Using criteria **`r SelEnhanc`** for final application

```{r echo=FALSE, include=TRUE}
```

## 1. Use TSI as reference for Clear sky.

```{r echo=TRUE, include=TRUE}

## __ 1. My criteria  ----------------------------------------------------------
# C1_GLB_ench_THRES     <-  1.10 ## enchantment relative to HAU
C1_GLB_diff_THRES     <- 20    ## enchantment absolute diff to HAU
C1_Clearness_Kt_THRES <-  0.8  ## enchantment threshold
# C1_wattGLB_THRES      <- 20    ## minimum value to consider

DATA[, Enhanc_C_1 := FALSE]
# DATA[wattGLB           > CS_ref * C1_GLB_ench_THRES + C1_GLB_diff_THRES &
#      ClearnessIndex_kt > C1_Clearness_Kt_THRES,
#      Enhanc_C_1 := TRUE]

DATA[, Enhanc_C_1_ref := ETH * C1_Clearness_Kt_THRES + C1_GLB_diff_THRES]
DATA[wattGLB > Enhanc_C_1_ref,
     Enhanc_C_1 := TRUE]

if (SelEnhanc == "Enhanc_C_1") {
    DATA[ , GLB_diff :=   wattGLB - Enhanc_C_1_ref                    ] ## enhancement
    DATA[ , GLB_ench := ( wattGLB - Enhanc_C_1_ref ) / Enhanc_C_1_ref ] ## relative enhancement
    DATA[ , GLB_rati :=   wattGLB / Enhanc_C_1_ref                    ]
}
```

## 2. Use TSI as reference for Clear sky.

```{r echo=TRUE, include=TRUE}

## __ 2. Gueymard2017 Criteria  ------------------------------------------------
## Clearness index > 0.8 / 1
C2_Clearness_Kt_THRES <- 0.8
DATA[, Enhanc_C_2 := FALSE]
DATA[, Enhanc_C_2_ref := ETH * C2_Clearness_Kt_THRES]
# DATA[ClearnessIndex_kt > C1_Clearness_Kt_THRES,
#      Enhanc_C_2 := TRUE]
DATA[wattGLB > Enhanc_C_2_ref,
     Enhanc_C_2 := TRUE]

if (SelEnhanc == "Enhanc_C_2") {
    DATA[ , GLB_diff :=   wattGLB - Enhanc_C_2_ref                    ] ## enhancement
    DATA[ , GLB_ench := ( wattGLB - Enhanc_C_2_ref ) / Enhanc_C_2_ref ] ## relative enhancement
    DATA[ , GLB_rati :=   wattGLB / Enhanc_C_2_ref                    ]
}
```

## 3. Use Haurwitz as reference for Clear sky.

```{r echo=TRUE, include=TRUE}

## __ 3. Vamvakas2020  Criteria  -----------------------------------------------
## +5% from model => enhancements above 15 Wm^2 the instrument uncertainty
C3_cs_ref_ratio <- 1.05
DATA[, Enhanc_C_3 := FALSE]
DATA[, Enhanc_C_3_ref := CS_ref * C3_cs_ref_ratio]
DATA[wattGLB > Enhanc_C_3_ref,
     Enhanc_C_3 := TRUE]

if (SelEnhanc == "Enhanc_C_3") {
    DATA[ , GLB_diff :=   wattGLB - Enhanc_C_3_ref                    ] ## enhancement
    DATA[ , GLB_ench := ( wattGLB - Enhanc_C_3_ref ) / Enhanc_C_3_ref ] ## relative enhancement
    DATA[ , GLB_rati :=   wattGLB / Enhanc_C_3_ref                    ]
}

## __ 4. my Criteria  ----------------------------------------------------------

## set values base
csmodel <- "Low_B.Low_W"
```

## 4. Use libradtran **`r csmodel`** as reference for Clear sky.

```{r echo=TRUE, include=TRUE}
cat("\n USING CSMODE:", csmodel, "\n\n")

switch(csmodel,
       Exact_B.Exact_W = { C4_cs_ref_ratio <- 1.02; C4_GLB_diff_THRES <- 55; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
       Low_2_B.Low_2_W = { C4_cs_ref_ratio <- 1.03; C4_GLB_diff_THRES <-  5; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
       Low_B.Exact_W   = { C4_cs_ref_ratio <- 1.04; C4_GLB_diff_THRES <- 20; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
       Low_B.High_W    = { C4_cs_ref_ratio <- 1.05; C4_GLB_diff_THRES <- 20; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
       Low_B.Low_W     = { C4_cs_ref_ratio <- 1.05; C4_GLB_diff_THRES <-  0; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.18},
                         { C4_cs_ref_ratio <- 1   ; C4_GLB_diff_THRES <-  0; C4_lowcut_sza <-  0; C4_lowcut_ratio <- 1   })
## init flag
DATA[, Enhanc_C_4 := FALSE]

# DATA[, max(SZA)]

smo <- approxfun(
    x = c(90 - BIO_ELEVA, C4_lowcut_sza  ),
    y = c(C4_lowcut_ratio,  C4_cs_ref_ratio)
    )

smo(80:70) * (1/cosd(80:70) / max(1/cosd(80:70)))

cat("C4 factor:", C4_cs_ref_ratio,   "\n")
cat("C4 offset:", C4_GLB_diff_THRES, "\n")

## ____ Create global irradiance W/m^2  ----------------------------------------
DATA[, paste0(csmodel,".glo") := (get(paste0(csmodel,".edir")) + get(paste0(csmodel,".edn"))) / 1000 ]

## ____ Apply sun-earth distance correction  -----------------------------------
DATA[, paste0(csmodel,".glo") := get(paste0(csmodel,".glo")) / sun_dist^2 ]

## ____ Apply adjustment to Kurudz spectrum  -----------------------------------
DATA[, paste0(csmodel,".glo") := get(paste0(csmodel,".glo")) * TSI_Kurudz_factor ]

## ____ Calculate clearness index  ---------------------------------------------
DATA[, ClearnessIndex_C_4 := wattGLB / get(paste0(csmodel,".glo")) ]

hist(DATA$ClearnessIndex_C_4, breaks = 100)
abline(v = C4_cs_ref_ratio, col = "red" )

## ____ Calculate reference and mark data  -------------------------------------
## for most of the data
DATA[SZA < C4_lowcut_sza, Enhanc_C_4_ref := (get(paste0(csmodel,".glo")) * C4_cs_ref_ratio) + C4_GLB_diff_THRES ]
## fol low sun angles
# DATA[SZA > C4_lowcut_sza, Enhanc_C_4_ref := (get(paste0(csmodel,".glo")) * C4_lowcut_ratio) ]
DATA[SZA > C4_lowcut_sza, Enhanc_C_4_ref := (get(paste0(csmodel,".glo")) * smo(SZA)) ]

DATA[wattGLB > Enhanc_C_4_ref ,
     Enhanc_C_4 := TRUE]
## use threshold to compute values
if (SelEnhanc == "Enhanc_C_4") {
    DATA[ , GLB_diff :=   wattGLB - Enhanc_C_4_ref                    ] ## enhancement
    DATA[ , GLB_ench := ( wattGLB - Enhanc_C_4_ref ) / Enhanc_C_4_ref ] ## relative enhancement
    DATA[ , GLB_rati :=   wattGLB / Enhanc_C_4_ref                    ]
}

```
```{r echo=F, include=T}

# pyear <- c(1994, 2010, 2022 )
# pyear <- c(2018 )
# p <-
#     ggplot(DATA[year(Date) %in% pyear],
#            aes(get(paste0(SelEnhanc,"_ref")), wattGLB)) +
#     geom_point(data   = DATA[year(Date) %in% pyear & get(SelEnhanc) == FALSE,],
#                colour = "black",
#                na.rm  = TRUE,
#                size   = 0.2) +
#     geom_point(data   = DATA[year(Date) %in% pyear & get(SelEnhanc) == TRUE,],
#                na.rm  = TRUE,
#                size   = 0.2,
#                aes(color = GLB_diff)) +
#     scale_colour_gradient(low      = "blue",
#                           high     = "red",
#                           na.value = NA) +
#     xlab(paste0(SelEnhanc, "_ref")) +
#     labs(color = "Over\nreference") +
#     theme(
#         legend.position      = c(.03, .97),
#         legend.justification = c("left", "top"),
#         legend.box.just      = "right",
#         legend.margin        = margin(6, 6, 6, 6)
#     ) +
#     scale_x_continuous(expand = expansion(mult = c(0.03, 0.03))) +
#     scale_y_continuous(breaks = scales::breaks_extended(n = 6),
#                        expand = expansion(mult = c(0.03, 0.03)))
# print(p)

```
```{r include=TRUE, echo=FALSE}
```

\FloatBarrier

# Using creteria: `r SelEnhanc`

# Distribution of different metrics

```{r echo=FALSE, include=TRUE}

# hist(DATA[GLB_ench > 0, GLB_ench])
# hist(DATA[GLB_diff > 0, GLB_diff])
# hist(DATA[GLB_rati > 1, GLB_rati])

hist(DATA[, GLB_ench], breaks = 100,
     main = varname("GLB_ench"))
abline(v = 0, col = "red")

hist(DATA[, GLB_diff], breaks = 100,
     main = varname("GLB_diff"))
abline(v = 0, col = "red")

hist(DATA[, GLB_rati], breaks = 100,
     main = varname("GLB_rati"))
abline(v = 1, col = "red")

## Mol2023
## activate when +1% and 10w/m from model reference
## near by values with +0.1 are also accepted

pander(table(DATA$Enhanc_C_1),
       caption = "Enhanc_C_1")

pander(table(DATA$Enhanc_C_2),
       caption = "Enhanc_C_2")

pander(table(DATA$Enhanc_C_3),
       caption = "Enhanc_C_3")

pander(table(DATA$Enhanc_C_4),
       caption = "Enhanc_C_4")

##  Test for low elevation angles  ---------------------------------------------

# DATA[get(SelEnhanc) == TRUE , min(GLB_diff) , by = SZA %/% 1]

testsza <- DATA[GLB_diff > 0,
                .(
                    min    = min   (GLB_diff, na.rm = T),
                    max    = max   (GLB_diff, na.rm = T),
                    mean   = mean  (GLB_diff, na.rm = T),
                    median = median(GLB_diff, na.rm = T)

                ) , by = SZA %/% 1]

plot(testsza[ , median, SZA ] )
plot(testsza[ , min,    SZA ] )
plot(testsza[ , max,    SZA ] )
plot(testsza[ , mean,   SZA ] )

for (aa in 77:60) {
    hist(DATA[(SZA %/% 1) == aa & GLB_diff > -300, GLB_diff],
         breaks = 30,
         main = aa)
}

##  Estimate enhancement daily magnitude  --------------------------------------
enh_days <- DATA[get(SelEnhanc) == TRUE,
                 .(Enh_sum      = sum(GLB_ench, na.rm = TRUE),
                   Enh_max      = max(GLB_ench, na.rm = TRUE),
                   Enh_diff_sum = sum(GLB_diff, na.rm = TRUE),
                   Enh_diff_max = max(GLB_diff, na.rm = TRUE),
                   Enh_N        = sum(get(SelEnhanc))),
                 Day]

hist(enh_days$Enh_sum,      breaks = 100)
hist(enh_days$Enh_max,      breaks = 100)
hist(enh_days$Enh_diff_max, breaks = 100)
hist(enh_days$Enh_diff_sum, breaks = 100)

sunny_days <- DATA[, .(Sunshine = sum(TYPE == "Clear") / max(DayLength, na.rm = TRUE),
                       Energy   = sum(ClearnessIndex_kt, na.rm = TRUE)/sum(TYPE == "Clear"),
                       EC       = sum(get(SelEnhanc)),
                       Cloud    = sum(TYPE == "Cloud")),
                   by = Day]

hist(sunny_days$Sunshine, breaks = 100)
hist(sunny_days$Energy,   breaks = 100)
hist(sunny_days$EC,       breaks = 100)
hist(sunny_days$Cloud,    breaks = 100)

## days with maximum values
setorder(enh_days, -Enh_diff_max)
maxenhd <- enh_days[1:20]

## strong total enhancement days
setorder(enh_days, -Enh_sum)
daylist <- enh_days[1:200]
daylist <- daylist[!Day %in% maxenhd$Day]
enhsnd  <- daylist[sample(1:nrow(daylist), 30)]

## select some sunny days
sunnyd  <- sunny_days[Sunshine > 0.79 & Energy > 0.74]
sunnyd  <- sunnyd[!Day %in% maxenhd$Day & !Day %in% enhsnd$Day]
sunnyd  <- sunnyd[sample(1:nrow(sunnyd), 20)]

## sunny with enhancements
sunnyenh <- sunny_days[Sunshine > 0.77 & Energy > 0.73 & EC > 0]
sunnyenh <- sunnyenh[!Day %in% maxenhd$Day & !Day %in% enhsnd$Day & !Day %in% sunnyd$Day]

## cloudy days
clouds <- sunny_days[Sunshine > 0.6 & Energy > 0.6 & EC > 2 & Cloud > 5]
clouds <- clouds[!Day %in% sunnyenh$Day & !Day %in% maxenhd$Day & !Day %in% enhsnd$Day & !Day %in% sunnyd$Day]
clouds <- clouds[sample(1:nrow(clouds), 20)]

## some random days
all_days <- data.table(Day = unique(DATA[, Day]))
all_days <- all_days[!Day %in% sunnyenh$Day & !Day %in% maxenhd$Day & !Day %in% enhsnd$Day & !Day %in% sunnyd$Day & !Day %in% clouds]
all_days <- all_days[sample(1:nrow(all_days), 30)]

## manual selection
testdays <- data.table(Day = c(
    "2000-07-14",
    "2007-07-06",
    "2013-05-27",
    "2016-08-29"
))

## __  Days with strong enhancement cases  -------------------------------------
```

\FloatBarrier

# Plot some days with strong enhancement cases

```{r example_days, echo=F, include=T, results="asis"}

vec_days <- matrix(
    ##   Data      Description
    c("maxenhd",  "extreme cases day",
      "enhsnd",   "strong enhancement day",
      "sunnyd",   "sunny day",
      "sunnyenh", "sunny enhancement day",
      "clouds",   "cloudy day",
      "all_days", "random day",
      "testdays", "manual test days",
      NULL),
    byrow = TRUE,
    ncol  = 2)

## Format to data frame
vec_days <- data.frame(Data        = vec_days[,1],
                       Descriprion = vec_days[,2])

for (ii in 1:nrow(vec_days)) {
    cat("\n\\FloatBarrier\n\n")
    cat("\n## Days with", vec_days$Descriprion[ii], "\n\n")
    temp    <- get(vec_days$Data[ii])
    daylist <- sort(temp$Day)

    for (aday in daylist) {
        temp <- DATA[Day == aday]
        par(mar = c(4, 4, 1, 1))
        ylim <- range(0, temp$ETH, temp$wattGLB, na.rm = TRUE)

        plot(temp$Date, temp$wattGLB, col = "green",
             pch  = ".", cex = 2,
             ylim = ylim,
             ylab = expression(Watt/m^2), xlab = "Time (UTC)")
        ## Global
        lines(temp$Date, temp$wattGLB, col = "green")
        ## Direct
        lines(temp$Date, temp$wattHOR, col = "blue")
        ## TSI on ground
        lines(temp$Date, temp$ETH)

        ## Active model reference
        lines(temp[, get(paste0(SelEnhanc,"_ref")), Date], col = "red" )

        ## CS libradtran reference
        lines(temp[, get(paste0(csmodel, ".glo")), Date], col = "magenta" )
        ## CS libradtran reference
        # lines(temp[, CS_low * TSI_Kurudz_factor , Date], col = "pink" )

        ## add sza axis
        aaa <- temp[Date %in% c(min(Date), (pretty(Date, 10) + 30), max(Date))  , ]
        axis(1, at = aaa$Date, labels = round(aaa$SZA,1),
             line = 1.2, lwd = 0, lwd.ticks = 0, cex.axis = 0.8)

        ## Enchantment cases
        points(temp[get(SelEnhanc) == TRUE, wattGLB, Date], col = "red")
        ## Cloud cases
        points(temp[TYPE == "Cloud", wattGLB, Date], col = "blue", pch = 3, cex = 0.3)

        title(main = paste(as.Date(aday, origin = "1970-01-01"), temp[get(SelEnhanc) == TRUE, .N], temp[TYPE == "Cloud", .N], vec_days$Descriprion[ii]))

        legend("topleft",
                     c(  "GHI", "DNI","GHI threshold","TSI on horizontal level","GHI Enhancement event",paste0(csmodel, ".glo"),"CloudsID"),
               col = c("green","blue",          "red",                  "black",                  "red",              "magenta",    "blue"),
               pch = c(     NA,    NA,             NA,                       NA,                     1 ,                     NA,         3),
               lty = c(      1,     1,              1,                        1,                    NA ,                      1,        NA),
               bty = "n",
               cex = 0.8
        )

        cols <- brewer.pal(n = 9, name = 'Set1')
        #  display.brewer.pal(n = 9, name = 'Set1')

        temp[TYPE == "Clouds", ]

        mark <- temp[get(SelEnhanc) == TRUE, wattGLB, Date]

        # p <- ggplot(temp, aes(x = Date)) +
        #     geom_point(aes(y = wattGLB,                       color = "wattGLB" ),size = .3 ) +
        #     geom_point(data = mark ,
        #                aes(x = Date, y = wattGLB ),           color = "red", shape = 1 )  +
        #     geom_line( aes(y = CS_low ,                       color = "CS_low"  ))     +
        #     # geom_line( aes(y = CS_2_low,                      color = "CS_2_low"))    +
        #     geom_line( aes(y = CS_exact,                      color = "CS_exact")) +
        #     geom_line( aes(y = get(paste0(SelEnhanc,"_ref")), color = "ref_main")) +
        #     geom_line( aes(y = ETH,                           color = "TSI")) +
        #     labs( title = as.Date(aday)) +
        #     scale_color_manual(
        #         values = c(
        #               cols[3],
        #               "red",
        #               cols[4],
        #               # cols[5],
        #               cols[6],
        #               cols[1],
        #               cols[9]
        #             ),
        #         breaks = c(
        #             "wattGLB" ,
        #             "wattGLB" ,
        #             'CS_low'  ,
        #             # "CS_2_low",
        #             "CS_exact",
        #             "ref_main",
        #             "TSI"
        #         ),
        #         labels = c(
        #             'GLB',
        #             "Enhancement",
        #             'CS -1σ',
        #             # "CS -2σ",
        #             "CS",
        #             "Current ref",
        #             "TSI"),
        #         guide = guide_legend(override.aes = list(
        #             linetype = c(NA, rep( 1, 4)),
        #             shape    = c( 1, rep(NA, 4))))
        #         ) +
        #     theme_bw() +
        #     theme(
        #           # legend.position = c(0.1, .9),
        #           legend.position = "right",
        #           legend.title          = element_blank(),
        #           legend.background     = element_rect(fill = 'transparent'),
        #           legend.box.background = element_rect(fill = 'transparent', color = NA))
        # print(p)
        # plotly::ggplotly(p)

        # overplot clearnesindex
        # par(new = T)
        # plot(temp$Date, temp$ClearnessIndex_kt, "l")
        # abline(h = C1_Clearness_Kt_THRES)

        # plot(temp$Date, temp$Clearness_Kt)
        # abline(h=.8,col="red")
        # plot(temp$Date, temp$DiffuseFraction_Kd)
        # plot(temp$Date, temp$GLB_ench)
        # plot(temp$Date, temp$GLB_diff)
        cat(' \n \n')

    }
}
```
```{r echo=F, include=T}

##  Yearly plots  --------------------------------------------------------------
```

\newpage
\FloatBarrier
# Plot years with enhancement cases

```{r example_years, echo=F, include=T, results="asis"}

## TODO plot only enhancement cases
## DO it with base plot
##
yearstodo <- unique(year(DATA$Date))

if (TEST) {
    yearstodo <- sample(yearstodo, 3)
}

pyear <- 2018
for (pyear in yearstodo) {
    p <-
        ggplot(DATA[year(Date) == pyear],
               aes(get(paste0(SelEnhanc,"_ref")), wattGLB)) +
        geom_point(data   = DATA[year(Date) == pyear & get(SelEnhanc) == FALSE,],
                   colour = "black",
                   na.rm  = TRUE,
                   size   = 0.2) +
        geom_point(data   = DATA[year(Date) == pyear & get(SelEnhanc) == TRUE,],
                   na.rm  = TRUE,
                   size   = 0.2,
                   aes(color = GLB_diff)) +
        scale_colour_gradient(low      = "blue",
                              high     = "red",
                              na.value = NA) +
        labs(title = pyear) +
        xlab(paste0(SelEnhanc, "_ref")) +
        labs(color = "Over\nreference") +
        theme(
            legend.position      = c(.03, .97),
            legend.justification = c("left", "top"),
            legend.box.just      = "right",
            legend.margin        = margin(6, 6, 6, 6)
        ) +
        scale_x_continuous(expand = expansion(mult = c(0.03, 0.03))) +
        scale_y_continuous(breaks = scales::breaks_extended(n = 6),
                           expand = expansion(mult = c(0.03, 0.03)))
    print(p)

    # ggplot(DATA, aes(CS_ref, wattGLB)) +
    #     geom_point(data = DATA[GLB_diff < 0], colour = "black", size = 0.5) +
    #     geom_point(data = DATA[GLB_diff > 0], size = 0.5, aes(color = GLB_diff)) +
    #     scale_colour_gradient(low = "blue", high = "red", na.value = NA)

    # ggplot(DATA[year(Date) == 2018], aes(CS_ref, wattGLB)) +
    #     geom_point(data = DATA[year(Date) == 2018 & GLB_diff < 0], colour = "black", size = 0.5) +
    #     geom_point(data = DATA[year(Date) == 2018 & GLB_diff > 0], size = 0.5, aes(color = GLB_diff)) +
    #     scale_colour_gradient2(low = "black", mid = "yellow", high = "red", na.value = NA)

}

if (TEST == TRUE) {
    warning("  TEST IS ACTIVE  !! ")
    cat("\n  TEST IS ACTIVE  !! \n\n")
}

if (TEST == FALSE) {

##  Group continuous values  ---------------------------------------------------

## Init groups logical
DATA[, C1G1 := get(SelEnhanc)]
DATA[, C1G0 := get(SelEnhanc)]

## __ No gap group  ------------------------------------------------------------
DATA[, C1Grp0 := rleid(c(NA,diff(cumsum(C1G0))))]
DATA[C1G0 == FALSE, C1Grp0 := NA]

## __ Allow one gap group  -----------------------------------------------------
DATA[shift(C1G1, n = +1)[[1L]] == TRUE &
     shift(C1G1, n = -1)[[1L]] == TRUE &
     C1G1 == FALSE,
     C1G1 := TRUE]
DATA[, C1Grp1 := rleid(c(NA,diff(cumsum(C1G1))))]
DATA[C1G1 == FALSE, C1Grp1 := NA]

## For bigger gaps should use a similar method with the one gap
## for the pattern TTFFTT -> TTTTTT
## and may need these
DATA[, C1G0 := NULL]
DATA[, C1G1 := NULL]

## Slow implementation
# DATA[, cnF := cumsum(Enhanc_C_1 == FALSE)]
# DATA[, cnT := cumsum(Enhanc_C_1 == TRUE) ]
# ## Init groups logical
# DATA[, C1G1  := Enhanc_C_1]
# DATA[, C1G0  := Enhanc_C_1]
# ## Find groups with one gap
# for (i in 1:nrow(DATA)) {
#     p1 <- i - 1
#     n1 <- i + 1
#     if (p1 > 0 & n1 <= nrow(DATA)) {
#         if (DATA$C1G1[p1] == TRUE  &
#             DATA$C1G1[i]  == FALSE &
#             DATA$C1G1[n1] == TRUE  ) {
#             DATA$C1G1[i]  <- TRUE
#         }
#     }
# }
# ## Allow one gap group
# DATA[, C1Grp1 := rleid(c(NA,diff(cumsum(G1))))]
# DATA[C1G1 == FALSE, C1Grp1 := NA]

#  Save processed data  --------------------------------------------------------
# saveRDS(DATA, file = Input_data_ID, compress = "xz")
# cat("\n  Saved raw input data:", Input_data_ID, "\n\n")

#  Save variables from environment  --------------------------------------------
objects <- grep("^tic$|^tac$|^Script.Name$|^tag$", ls(), value = T, invert = T)
objects <- objects[sapply(objects, function(x)
    is.numeric(get(x)) |
        is.character(get(x)) &
        object.size(get(x)) < 1009 &
        (!is.vector(get(x)) |
             !is.function(get(x))), simplify = T)]
## Data
objects <- c(
    objects, "DATA"
)

save(file = paste0("./data/", basename(sub("\\.R", ".Rda", Script.Name))),
     list = objects,
     compress = "xz")
}
```

**END**

```{r include=T, echo=F}
tac <- Sys.time()
cat(sprintf("%s %s@%s %s %f mins\n\n", Sys.time(), Sys.info()["login"],
            Sys.info()["nodename"], basename(Script.Name), difftime(tac,tic,units = "mins")))
if (difftime(tac,tic,units = "sec") > 30) {
    system("mplayer /usr/share/sounds/freedesktop/stereo/dialog-warning.oga", ignore.stdout = T, ignore.stderr = T)
    system(paste("notify-send -u normal -t 30000 ", Script.Name, " 'R script ended'"))
}
```

### 2024-04-10 high_aod/GHI_enh_02_ID_CE.tex
Commit 2024-04-10 12:14

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  a4paper,oneside]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{placeins}
\captionsetup{font=small}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Enhancement of SDR in Thessaloniki},
  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-09}

\begin{document}
\maketitle
\begin{abstract}
Study of GHI enchantment.
\end{abstract}

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
[1] "/home/athan/MANUSCRIPTS/02_enhancement/high_aod"
\end{verbatim}

\begin{verbatim}
[1] "Cloud" "Clear"
\end{verbatim}

\begin{verbatim}
 [1] "Exact_B.High_W.edir"  "Exact_B.High_W.edn"   "Exact_B.High_W.eup"  
 [4] "Exact_B.Low_2_W.edir" "Exact_B.Low_2_W.edn"  "Exact_B.Low_2_W.eup" 
 [7] "Exact_B.Exact_W.edir" "Exact_B.Exact_W.edn"  "Exact_B.Exact_W.eup" 
[10] "Exact_B.Low_W.edir"   "Exact_B.Low_W.edn"    "Exact_B.Low_W.eup"   
\end{verbatim}

\begin{verbatim}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  1.031   1.034   1.035   1.035   1.035   1.036 
\end{verbatim}

Alpha * HAU is CS\_ref

\hypertarget{using-criteria-enhanc_c_4-for-final-application}{%
\subsection{\texorpdfstring{Using criteria \textbf{Enhanc\_C\_4} for final application}{Using criteria Enhanc\_C\_4 for final application}}\label{using-criteria-enhanc_c_4-for-final-application}}

\hypertarget{use-tsi-as-reference-for-clear-sky.}{%
\subsection{1. Use TSI as reference for Clear sky.}\label{use-tsi-as-reference-for-clear-sky.}}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# \_\_ 1. My criteria  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\CommentTok{\# C1\_GLB\_ench\_THRES     \textless{}{-}  1.10 \#\# enchantment relative to HAU}
\NormalTok{C1\_GLB\_diff\_THRES     }\OtherTok{\textless{}{-}} \DecValTok{20}    \DocumentationTok{\#\# enchantment absolute diff to HAU}
\NormalTok{C1\_Clearness\_Kt\_THRES }\OtherTok{\textless{}{-}}  \FloatTok{0.8}  \DocumentationTok{\#\# enchantment threshold}
\CommentTok{\# C1\_wattGLB\_THRES      \textless{}{-} 20    \#\# minimum value to consider}

\NormalTok{DATA[, Enhanc\_C\_1 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}
\CommentTok{\# DATA[wattGLB           \textgreater{} CS\_ref * C1\_GLB\_ench\_THRES + C1\_GLB\_diff\_THRES \&}
\CommentTok{\#      ClearnessIndex\_kt \textgreater{} C1\_Clearness\_Kt\_THRES,}
\CommentTok{\#      Enhanc\_C\_1 := TRUE]}

\NormalTok{DATA[, Enhanc\_C\_1\_ref }\SpecialCharTok{:=}\NormalTok{ ETH }\SpecialCharTok{*}\NormalTok{ C1\_Clearness\_Kt\_THRES }\SpecialCharTok{+}\NormalTok{ C1\_GLB\_diff\_THRES]}
\NormalTok{DATA[wattGLB }\SpecialCharTok{\textgreater{}}\NormalTok{ Enhanc\_C\_1\_ref,}
\NormalTok{     Enhanc\_C\_1 }\SpecialCharTok{:=} \ConstantTok{TRUE}\NormalTok{]}

\ControlFlowTok{if}\NormalTok{ (SelEnhanc }\SpecialCharTok{==} \StringTok{"Enhanc\_C\_1"}\NormalTok{) \{}
\NormalTok{    DATA[ , GLB\_diff }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_1\_ref                    ] }\DocumentationTok{\#\# enhancement}
\NormalTok{    DATA[ , GLB\_ench }\SpecialCharTok{:=}\NormalTok{ ( wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_1\_ref ) }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_1\_ref ] }\DocumentationTok{\#\# relative enhancement}
\NormalTok{    DATA[ , GLB\_rati }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_1\_ref                    ]}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{use-tsi-as-reference-for-clear-sky.-1}{%
\subsection{2. Use TSI as reference for Clear sky.}\label{use-tsi-as-reference-for-clear-sky.-1}}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# \_\_ 2. Gueymard2017 Criteria  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\DocumentationTok{\#\# Clearness index \textgreater{} 0.8 / 1}
\NormalTok{C2\_Clearness\_Kt\_THRES }\OtherTok{\textless{}{-}} \FloatTok{0.8}
\NormalTok{DATA[, Enhanc\_C\_2 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}
\NormalTok{DATA[, Enhanc\_C\_2\_ref }\SpecialCharTok{:=}\NormalTok{ ETH }\SpecialCharTok{*}\NormalTok{ C2\_Clearness\_Kt\_THRES]}
\CommentTok{\# DATA[ClearnessIndex\_kt \textgreater{} C1\_Clearness\_Kt\_THRES,}
\CommentTok{\#      Enhanc\_C\_2 := TRUE]}
\NormalTok{DATA[wattGLB }\SpecialCharTok{\textgreater{}}\NormalTok{ Enhanc\_C\_2\_ref,}
\NormalTok{     Enhanc\_C\_2 }\SpecialCharTok{:=} \ConstantTok{TRUE}\NormalTok{]}

\ControlFlowTok{if}\NormalTok{ (SelEnhanc }\SpecialCharTok{==} \StringTok{"Enhanc\_C\_2"}\NormalTok{) \{}
\NormalTok{    DATA[ , GLB\_diff }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_2\_ref                    ] }\DocumentationTok{\#\# enhancement}
\NormalTok{    DATA[ , GLB\_ench }\SpecialCharTok{:=}\NormalTok{ ( wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_2\_ref ) }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_2\_ref ] }\DocumentationTok{\#\# relative enhancement}
\NormalTok{    DATA[ , GLB\_rati }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_2\_ref                    ]}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{use-haurwitz-as-reference-for-clear-sky.}{%
\subsection{3. Use Haurwitz as reference for Clear sky.}\label{use-haurwitz-as-reference-for-clear-sky.}}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# \_\_ 3. Vamvakas2020  Criteria  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\DocumentationTok{\#\# +5\% from model =\textgreater{} enhancements above 15 Wm\^{}2 the instrument uncertainty}
\NormalTok{C3\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}
\NormalTok{DATA[, Enhanc\_C\_3 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}
\NormalTok{DATA[, Enhanc\_C\_3\_ref }\SpecialCharTok{:=}\NormalTok{ CS\_ref }\SpecialCharTok{*}\NormalTok{ C3\_cs\_ref\_ratio]}
\NormalTok{DATA[wattGLB }\SpecialCharTok{\textgreater{}}\NormalTok{ Enhanc\_C\_3\_ref,}
\NormalTok{     Enhanc\_C\_3 }\SpecialCharTok{:=} \ConstantTok{TRUE}\NormalTok{]}

\ControlFlowTok{if}\NormalTok{ (SelEnhanc }\SpecialCharTok{==} \StringTok{"Enhanc\_C\_3"}\NormalTok{) \{}
\NormalTok{    DATA[ , GLB\_diff }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_3\_ref                    ] }\DocumentationTok{\#\# enhancement}
\NormalTok{    DATA[ , GLB\_ench }\SpecialCharTok{:=}\NormalTok{ ( wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_3\_ref ) }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_3\_ref ] }\DocumentationTok{\#\# relative enhancement}
\NormalTok{    DATA[ , GLB\_rati }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_3\_ref                    ]}
\NormalTok{\}}

\DocumentationTok{\#\# \_\_ 4. my Criteria  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}

\DocumentationTok{\#\# set values base}
\NormalTok{csmodel }\OtherTok{\textless{}{-}} \StringTok{"High\_B.Low\_W"}
\end{Highlighting}
\end{Shaded}

\hypertarget{use-libradtran-high_b.low_w-as-reference-for-clear-sky.}{%
\subsection{\texorpdfstring{4. Use libradtran \textbf{High\_B.Low\_W} as reference for Clear sky.}{4. Use libradtran High\_B.Low\_W as reference for Clear sky.}}\label{use-libradtran-high_b.low_w-as-reference-for-clear-sky.}}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{cat}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{ USING CSMODE:"}\NormalTok{, csmodel, }\StringTok{"}\SpecialCharTok{\textbackslash{}n\textbackslash{}n}\StringTok{"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}

 USING CSMODE: High_B.Low_W 
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{switch}\NormalTok{(csmodel,}
       \AttributeTok{Exact\_B.Exact\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.02}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{55}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_2\_B.Low\_2\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.03}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{5}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Exact\_W   =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.04}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.High\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
\NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
\DocumentationTok{\#\# init flag}
\NormalTok{DATA[, Enhanc\_C\_4 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}

\CommentTok{\# DATA[, max(SZA)]}

\NormalTok{smo }\OtherTok{\textless{}{-}} \FunctionTok{approxfun}\NormalTok{(}
    \AttributeTok{x =} \FunctionTok{c}\NormalTok{(}\DecValTok{90} \SpecialCharTok{{-}}\NormalTok{ BIO\_ELEVA, C4\_lowcut\_sza  ),}
    \AttributeTok{y =} \FunctionTok{c}\NormalTok{(C4\_lowcut\_ratio,  C4\_cs\_ref\_ratio)}
\NormalTok{    )}

\FunctionTok{smo}\NormalTok{(}\DecValTok{80}\SpecialCharTok{:}\DecValTok{70}\NormalTok{) }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{/}\FunctionTok{cosd}\NormalTok{(}\DecValTok{80}\SpecialCharTok{:}\DecValTok{70}\NormalTok{) }\SpecialCharTok{/} \FunctionTok{max}\NormalTok{(}\DecValTok{1}\SpecialCharTok{/}\FunctionTok{cosd}\NormalTok{(}\DecValTok{80}\SpecialCharTok{:}\DecValTok{70}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
 [1]        NA        NA 0.9855379 0.9053113 0.8366196 0.7771548 0.7251860 0.6793893
 [9] 0.6387354 0.6024114 0.5697672
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{cat}\NormalTok{(}\StringTok{"C4 factor:"}\NormalTok{, C4\_cs\_ref\_ratio,   }\StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
C4 factor: 1.05 
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{cat}\NormalTok{(}\StringTok{"C4 offset:"}\NormalTok{, C4\_GLB\_diff\_THRES, }\StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
C4 offset: 0 
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# \_\_\_\_ Create global irradiance W/m\^{}2  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\NormalTok{DATA[, }\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{) }\SpecialCharTok{:=}\NormalTok{ (}\FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".edir"}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".edn"}\NormalTok{))) }\SpecialCharTok{/} \DecValTok{1000}\NormalTok{ ]}

\DocumentationTok{\#\# \_\_\_\_ Apply sun{-}earth distance correction  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\NormalTok{DATA[, }\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{) }\SpecialCharTok{:=} \FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) }\SpecialCharTok{/}\NormalTok{ sun\_dist}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{ ]}

\DocumentationTok{\#\# \_\_\_\_ Apply adjustment to Kurudz spectrum  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\NormalTok{DATA[, }\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{) }\SpecialCharTok{:=} \FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) }\SpecialCharTok{*}\NormalTok{ TSI\_Kurudz\_factor ]}

\DocumentationTok{\#\# \_\_\_\_ Calculate clearness index  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\NormalTok{DATA[, ClearnessIndex\_C\_4 }\SpecialCharTok{:=}\NormalTok{ wattGLB }\SpecialCharTok{/} \FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) ]}

\FunctionTok{hist}\NormalTok{(DATA}\SpecialCharTok{$}\NormalTok{ClearnessIndex\_C\_4, }\AttributeTok{breaks =} \DecValTok{100}\NormalTok{)}
\FunctionTok{abline}\NormalTok{(}\AttributeTok{v =}\NormalTok{ C4\_cs\_ref\_ratio, }\AttributeTok{col =} \StringTok{"red"}\NormalTok{ )}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-10-1} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# \_\_\_\_ Calculate reference and mark data  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\DocumentationTok{\#\# for most of the data}
\NormalTok{DATA[SZA }\SpecialCharTok{\textless{}}\NormalTok{ C4\_lowcut\_sza, Enhanc\_C\_4\_ref }\SpecialCharTok{:=}\NormalTok{ (}\FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) }\SpecialCharTok{*}\NormalTok{ C4\_cs\_ref\_ratio) }\SpecialCharTok{+}\NormalTok{ C4\_GLB\_diff\_THRES ]}
\DocumentationTok{\#\# fol low sun angles}
\CommentTok{\# DATA[SZA \textgreater{} C4\_lowcut\_sza, Enhanc\_C\_4\_ref := (get(paste0(csmodel,".glo")) * C4\_lowcut\_ratio) ]}
\NormalTok{DATA[SZA }\SpecialCharTok{\textgreater{}}\NormalTok{ C4\_lowcut\_sza, Enhanc\_C\_4\_ref }\SpecialCharTok{:=}\NormalTok{ (}\FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) }\SpecialCharTok{*} \FunctionTok{smo}\NormalTok{(SZA)) ]}

\NormalTok{DATA[wattGLB }\SpecialCharTok{\textgreater{}}\NormalTok{ Enhanc\_C\_4\_ref ,}
\NormalTok{     Enhanc\_C\_4 }\SpecialCharTok{:=} \ConstantTok{TRUE}\NormalTok{]}
\DocumentationTok{\#\# use threshold to compute values}
\ControlFlowTok{if}\NormalTok{ (SelEnhanc }\SpecialCharTok{==} \StringTok{"Enhanc\_C\_4"}\NormalTok{) \{}
\NormalTok{    DATA[ , GLB\_diff }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_4\_ref                    ] }\DocumentationTok{\#\# enhancement}
\NormalTok{    DATA[ , GLB\_ench }\SpecialCharTok{:=}\NormalTok{ ( wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_4\_ref ) }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_4\_ref ] }\DocumentationTok{\#\# relative enhancement}
\NormalTok{    DATA[ , GLB\_rati }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_4\_ref                    ]}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\FloatBarrier

\hypertarget{using-creteria-enhanc_c_4}{%
\section{Using creteria: Enhanc\_C\_4}\label{using-creteria-enhanc_c_4}}

\hypertarget{distribution-of-different-metrics}{%
\section{Distribution of different metrics}\label{distribution-of-different-metrics}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-3} \end{center}

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_1}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
6082440 & 119727 \\
\end{longtable}

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_2}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
6012875 & 189292 \\
\end{longtable}

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_3}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
5455724 & 746443 \\
\end{longtable}

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_4}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
5785494 & 416673 \\
\end{longtable}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-33} \end{center}

\FloatBarrier

\hypertarget{plot-some-days-with-strong-enhancement-cases}{%
\section{Plot some days with strong enhancement cases}\label{plot-some-days-with-strong-enhancement-cases}}

\FloatBarrier

\hypertarget{days-with-extreme-cases-day}{%
\subsection{Days with extreme cases day}\label{days-with-extreme-cases-day}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-20} \end{center}

\FloatBarrier

\hypertarget{days-with-strong-enhancement-day}{%
\subsection{Days with strong enhancement day}\label{days-with-strong-enhancement-day}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-33} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-34} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-35} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-36} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-37} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-38} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-39} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-40} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-41} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-42} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-43} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-44} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-45} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-46} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-47} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-48} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-49} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-50} \end{center}

\FloatBarrier

\hypertarget{days-with-sunny-day}{%
\subsection{Days with sunny day}\label{days-with-sunny-day}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-51} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-52} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-53} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-54} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-55} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-56} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-57} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-58} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-59} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-60} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-61} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-62} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-63} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-64} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-65} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-66} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-67} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-68} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-69} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-70} \end{center}

\FloatBarrier

\hypertarget{days-with-sunny-enhancement-day}{%
\subsection{Days with sunny enhancement day}\label{days-with-sunny-enhancement-day}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-71} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-72} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-73} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-74} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-75} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-76} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-77} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-78} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-79} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-80} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-81} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-82} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-83} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-84} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-85} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-86} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-87} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-88} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-89} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-90} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-91} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-92} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-93} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-94} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-95} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-96} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-97} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-98} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-99} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-100} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-101} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-102} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-103} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-104} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-105} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-106} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-107} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-108} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-109} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-110} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-111} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-112} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-113} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-114} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-115} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-116} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-117} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-118} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-119} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-120} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-121} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-122} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-123} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-124} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-125} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-126} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-127} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-128} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-129} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-130} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-131} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-132} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-133} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-134} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-135} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-136} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-137} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-138} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-139} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-140} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-141} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-142} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-143} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-144} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-145} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-146} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-147} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-148} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-149} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-150} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-151} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-152} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-153} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-154} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-155} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-156} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-157} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-158} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-159} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-160} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-161} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-162} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-163} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-164} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-165} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-166} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-167} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-168} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-169} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-170} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-171} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-172} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-173} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-174} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-175} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-176} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-177} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-178} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-179} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-180} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-181} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-182} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-183} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-184} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-185} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-186} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-187} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-188} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-189} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-190} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-191} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-192} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-193} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-194} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-195} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-196} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-197} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-198} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-199} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-200} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-201} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-202} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-203} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-204} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-205} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-206} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-207} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-208} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-209} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-210} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-211} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-212} \end{center}

\FloatBarrier

\hypertarget{days-with-cloudy-day}{%
\subsection{Days with cloudy day}\label{days-with-cloudy-day}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-213} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-214} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-215} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-216} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-217} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-218} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-219} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-220} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-221} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-222} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-223} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-224} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-225} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-226} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-227} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-228} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-229} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-230} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-231} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-232} \end{center}

\FloatBarrier

\hypertarget{days-with-random-day}{%
\subsection{Days with random day}\label{days-with-random-day}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-233} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-234} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-235} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-236} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-237} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-238} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-239} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-240} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-241} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-242} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-243} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-244} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-245} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-246} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-247} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-248} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-249} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-250} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-251} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-252} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-253} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-254} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-255} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-256} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-257} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-258} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-259} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-260} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-261} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-262} \end{center}

\FloatBarrier

\hypertarget{days-with-manual-test-days}{%
\subsection{Days with manual test days}\label{days-with-manual-test-days}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-263} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-264} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-265} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-266} \end{center}

\newpage
\FloatBarrier

\hypertarget{plot-years-with-enhancement-cases}{%
\section{Plot years with enhancement cases}\label{plot-years-with-enhancement-cases}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-31} \end{center}

\textbf{END}

\begin{verbatim}
2024-04-09 19:11:13.0 athan@tyler GHI_enh_02_ID_CE.R 62.482203 mins
\end{verbatim}

\end{document}

### 2024-04-10 high_aod/GHI_enh_03_process.tex
Commit 2024-04-10 12:14

--- 2024-03-14 GHI_enh_03_process.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-14}
+\date{2024-04-09}
 
@@
 \begin{verbatim}
-Warning: Removed 2 rows containing missing values or values outside the scale range (`geom_line()`).
-Removed 2 rows containing missing values or values outside the scale range (`geom_line()`).
+Warning: Removed 2 rows containing missing values or values outside the scale range
+(`geom_line()`).
+Removed 2 rows containing missing values or values outside the scale range
+(`geom_line()`).
 \end{verbatim}
@@
     Min      1Q  Median      3Q     Max 
--372.77 -150.51  -49.67   99.05  778.55
+-1440.3  -533.0  -125.8   463.6  2804.6
 
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
-as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
+(Intercept)      -2.647e+02  1.691e+02  -1.565    0.118    
+as.numeric(Date)  1.153e-06  1.354e-07   8.517 4.38e-16 ***
 ---
@@
 
-Residual standard error: 217 on 361 degrees of freedom
-Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
-F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
+Residual standard error: 728.2 on 364 degrees of freedom
+Multiple R-squared:  0.1662,    Adjusted R-squared:  0.1639 
+F-statistic: 72.54 on 1 and 364 DF,  p-value: 4.375e-16
 \end{verbatim}
@@
                     Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       -9.118e+01  5.082e+01  -1.794   0.0736 .  
-ST_E_monthly$Date  3.246e-07  4.062e-08   7.991 1.82e-14 ***
+(Intercept)       -2.647e+02  1.691e+02  -1.565    0.118    
+ST_E_monthly$Date  1.153e-06  1.354e-07   8.517 4.38e-16 ***
 ---
@@
 \begin{verbatim}
-2024-03-14 11:20:40.3 athan@tyler GHI_enh_03_process.R 3.214359 mins
+2024-04-09 20:39:01 athan@tyler GHI_enh_03_process.R 13.754702 mins
 \end{verbatim}

### 2024-04-10 high_aod/GHI_enh_06_sza.tex
Commit 2024-04-10 12:14

--- 2024-03-14 GHI_enh_06_sza.tex
@@
 }
-\begin{verbatim}
-Not changed:  ./GHI_enh_06_sza.R 
-Not changed:  ./GHI_enh_00_variables.R 
-Not changed:  ./GHI_enh_03_process.R 
-Not changed:  ./data/GHI_enh_03_process.Rda 
-\end{verbatim}
-
-\begin{verbatim}
-[1] FALSE
-\end{verbatim}
-
-\begin{verbatim}
-Written `R_make_` file: .//.R_make.mk 
-\end{verbatim}
-
 \newpage
@@
 \begin{verbatim}
-2024-03-14 19:08:05.8 athan@tyler GHI_enh_06_sza.R 0.401094 mins
+2024-03-14 19:41:18.5 athan@tyler GHI_enh_06_sza.R 0.846766 mins
 \end{verbatim}

### 2024-04-10 high_aod/GHI_enh_03_process.R

@@ -1,0 +1,1030 @@
+# /* #!/usr/bin/env Rscript */
+# /* Copyright (C) 2022 Athanasios Natsis <natsisphysicist@gmail.com> */
+#' ---
+#' title:         "Enhancement of SDR in Thessaloniki "
+#' author:
+#'   - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisphysicist@gmail.com]
+#'   - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
+#' abstract:
+#'   "Study of GHI enchantment."
+#'
+#' documentclass:  article
+#' classoption:    a4paper,oneside
+#' fontsize:       10pt
+#' geometry:       "left=0.5in,right=0.5in,top=0.5in,bottom=0.5in"
+#' link-citations: yes
+#' colorlinks:     yes
+#'
+#' header-includes:
+#' - \usepackage{caption}
+#' - \usepackage{placeins}
+#' - \captionsetup{font=small}
+#'
+#' output:
+#'   bookdown::pdf_document2:
+#'     number_sections: no
+#'     fig_caption:     no
+#'     keep_tex:        yes
+#'     latex_engine:    xelatex
+#'     toc:             yes
+#'     toc_depth:       4
+#'     fig_width:       7
+#'     fig_height:      4.5
+#'   html_document:
+#'     toc:             true
+#'     keep_md:         yes
+#'     fig_width:       7
+#'     fig_height:      4.5
+#'
+#' date: "`r format(Sys.time(), '%F')`"
+#'
+#' ---
+
+#+ echo=F, include=T
+
+
+## __ Document options  --------------------------------------------------------
+
+#+ echo=F, include=F
+knitr::opts_chunk$set(comment    = ""       )
+knitr::opts_chunk$set(dev        = c("pdf", "png"))
+# knitr::opts_chunk$set(dev        = "png"    )
+knitr::opts_chunk$set(out.width  = "100%"   )
+knitr::opts_chunk$set(fig.align  = "center" )
+knitr::opts_chunk$set(cache      =  FALSE   )  ## !! breaks calculations
+# knitr::opts_chunk$set(fig.pos    = '!h'    )
+
+
+#+ include=F, echo=F
+## __ Set environment  ---------------------------------------------------------
+Sys.setenv(TZ = "UTC")
+Script.Name <- "./GHI_enh_03_process.R"
+
+if (!interactive()) {
[…]

### 2024-04-10 high_aod/GHI_enh_05_distributions.R

@@ -1,0 +1,389 @@
+# /* #!/usr/bin/env Rscript */
+# /* Copyright (C) 2022 Athanasios Natsis <natsisphysicist@gmail.com> */
+#' ---
+#' title:         "Enhancement of SDR in Thessaloniki "
+#' author:
+#'   - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisphysicist@gmail.com]
+#'   - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
+#' abstract:
+#'   "Study of GHI enchantment."
+#'
+#' documentclass:  article
+#' classoption:    a4paper,oneside
+#' fontsize:       10pt
+#' geometry:       "left=0.5in,right=0.5in,top=0.5in,bottom=0.5in"
+#' link-citations: yes
+#' colorlinks:     yes
+#'
+#' header-includes:
+#' - \usepackage{caption}
+#' - \usepackage{placeins}
+#' - \captionsetup{font=small}
+#'
+#' output:
+#'   bookdown::pdf_document2:
+#'     number_sections: no
+#'     fig_caption:     no
+#'     keep_tex:        yes
+#'     latex_engine:    xelatex
+#'     toc:             yes
+#'     toc_depth:       4
+#'     fig_width:       7
+#'     fig_height:      4.5
+#'   html_document:
+#'     toc:             true
+#'     keep_md:         yes
+#'     fig_width:       7
+#'     fig_height:      4.5
+#'
+#' date: "`r format(Sys.time(), '%F')`"
+#'
+#' ---
+
+#+ echo=F, include=T
+
+
+## __ Document options ---------------------------------------------------------
+
+#+ echo=F, include=F
+knitr::opts_chunk$set(comment    = ""       )
+knitr::opts_chunk$set(dev        = c("pdf", "png"))
+# knitr::opts_chunk$set(dev        = "png"    )
+knitr::opts_chunk$set(out.width  = "100%"   )
+knitr::opts_chunk$set(fig.align  = "center" )
+knitr::opts_chunk$set(cache      =  FALSE   )  ## !! breaks calculations
+# knitr::opts_chunk$set(fig.pos    = '!h'    )
+
+
+#+ include=F, echo=F
+## __ Set environment ----------------------------------------------------------
+Sys.setenv(TZ = "UTC")
[…]

### 2024-04-10 high_aod/GHI_enh_06_sza.R

@@ -1,0 +1,275 @@
+# /* #!/usr/bin/env Rscript */
+# /* Copyright (C) 2022 Athanasios Natsis <natsisphysicist@gmail.com> */
+#' ---
+#' title:         "Enhancement of SDR in Thessaloniki "
+#' author:
+#'   - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisphysicist@gmail.com]
+#'   - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
+#' abstract:
+#'   "Study of GHI enchantment."
+#'
+#' documentclass:  article
+#' classoption:    a4paper,oneside
+#' fontsize:       10pt
+#' geometry:       "left=0.5in,right=0.5in,top=0.5in,bottom=0.5in"
+#' link-citations: yes
+#' colorlinks:     yes
+#'
+#' header-includes:
+#' - \usepackage{caption}
+#' - \usepackage{placeins}
+#' - \captionsetup{font=small}
+#'
+#' output:
+#'   bookdown::pdf_document2:
+#'     number_sections: no
+#'     fig_caption:     no
+#'     keep_tex:        yes
+#'     latex_engine:    xelatex
+#'     toc:             yes
+#'     toc_depth:       4
+#'     fig_width:       7
+#'     fig_height:      4.5
+#'   html_document:
+#'     toc:             true
+#'     keep_md:         yes
+#'     fig_width:       7
+#'     fig_height:      4.5
+#'
+#' date: "`r format(Sys.time(), '%F')`"
+#'
+#' ---
+
+#+ echo=F, include=T
+
+
+## __ Document options ---------------------------------------------------------
+
+#+ echo=F, include=F
+knitr::opts_chunk$set(comment    = ""       )
+knitr::opts_chunk$set(dev        = c("pdf", "png"))
+# knitr::opts_chunk$set(dev        = "png"    )
+knitr::opts_chunk$set(out.width  = "100%"   )
+knitr::opts_chunk$set(fig.align  = "center" )
+knitr::opts_chunk$set(cache      =  FALSE   )  ## !! breaks calculations
+# knitr::opts_chunk$set(fig.pos    = '!h'    )
+
+
+#+ include=F, echo=F
+## __ Set environment ----------------------------------------------------------
+Sys.setenv(TZ = "UTC")
+Script.Name <- "./GHI_enh_06_sza.R"
+
[…]

### 2024-04-10 high_aod/GHI_enh_04_investigate.R
Commit 2024-04-10 12:14

@@ -1,0 +1,1418 @@
+# /* #!/usr/bin/env Rscript */
+# /* Copyright (C) 2022 Athanasios Natsis <natsisphysicist@gmail.com> */
+#' ---
+#' title:         "Enhancement of SDR in Thessaloniki "
+#' author:
+#'   - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisphysicist@gmail.com]
+#'   - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
+#' abstract:
+#'   "Study of GHI enchantment."
+#'
+#' documentclass:  article
+#' classoption:    a4paper,oneside
+#' fontsize:       10pt
+#' geometry:       "left=0.5in,right=0.5in,top=0.5in,bottom=0.5in"
+#' link-citations: yes
+#' colorlinks:     yes
+#'
+#' header-includes:
+#' - \usepackage{caption}
+#' - \usepackage{placeins}
+#' - \captionsetup{font=small}
+#'
+#' output:
+#'   bookdown::pdf_document2:
+#'     number_sections: no
+#'     fig_caption:     no
+#'     keep_tex:        yes
+#'     latex_engine:    xelatex
+#'     toc:             yes
+#'     toc_depth:       4
+#'     fig_width:       7
+#'     fig_height:      4.5
+#'   html_document:
+#'     toc:             true
+#'     keep_md:         yes
+#'     fig_width:       7
+#'     fig_height:      4.5
+#'
+#' date: "`r format(Sys.time(), '%F')`"
+#'
+#' ---
+
+#+ echo=F, include=T
+
+
+## __ Document options ---------------------------------------------------------
+
+#+ echo=F, include=F
+knitr::opts_chunk$set(comment    = ""       )
+knitr::opts_chunk$set(dev        = c("pdf", "png"))
+# knitr::opts_chunk$set(dev        = "png"    )
+knitr::opts_chunk$set(out.width  = "100%"   )
+knitr::opts_chunk$set(fig.align  = "center" )
+knitr::opts_chunk$set(cache      =  FALSE   )  ## !! breaks calculations
+# knitr::opts_chunk$set(fig.pos    = '!h'    )
+
+
+#+ include=F, echo=F
+## __ Set environment ----------------------------------------------------------
+Sys.setenv(TZ = "UTC")
+Script.Name <- "./GHI_enh_04_investigate.R"
+
+if (!interactive()) {
[…]

### 2024-04-10 high_aod/article/test/test.tex
Commit 2024-04-10 20:14

\documentclass[preprint, 3p,
authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%

\usepackage[hyphens]{url}

  \journal{An awesome journal} % Sets Journal name

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
% TODO: Currently lineno needs to be loaded after amsmath because of conflict
% https://github.com/latex-lineno/lineno/issues/5
\usepackage{lineno} % add
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Short Paper},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)

% Pandoc syntax highlighting
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

\begin{document}

\begin{frontmatter}

  \title{Short Paper}
    \author[Some Institute of Technology]{Alice Anonymous%
  \corref{cor1}%
  \fnref{1}}
   \ead{alice@example.com} 
    \author[Another University]{Bob Security%
  %
  }
   \ead{bob@example.com} 
    \author[Another University]{Cat Memes%
  %
  \fnref{2}}
   \ead{cat@example.com} 
    \author[Some Institute of Technology]{Derek Zoolander%
  %
  \fnref{2}}
   \ead{derek@example.com} 
      \affiliation[Some Institute of Technology]{
    organization={Big Wig University},addressline={1 main
street},city={Gotham},postcode={123456},state={State},country={United
States},}
    \affiliation[Another University]{
    organization={Department},addressline={A street
29},city={Manchester,},postcode={2054 NX},country={The Netherlands},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{This is the first author footnote.}
    \fntext[2]{Another author footnote.}

  \begin{abstract}
  This is the abstract.

  It consists of two paragraphs.
  \end{abstract}
    \begin{keyword}
    keyword1 \sep 
    keyword2
  \end{keyword}

 \end{frontmatter}

Please make sure that your manuscript follows the guidelines in the
Guide for Authors of the relevant journal. It is not necessary to
typeset your manuscript in exactly the same way as an article, unless
you are submitting to a camera-ready copy (CRC) journal.

For detailed instructions regarding the elsevier article class, see
\url{https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions}

\hypertarget{bibliography-styles}{%
\section{Bibliography styles}\label{bibliography-styles}}

Here are two sample references: \citeauthor{Feynman1963118}
\citetext{\citeyear{Feynman1963118}; \citealp{Dirac1953888}}.

By default, natbib will be used with the \texttt{authoryear} style, set
in \texttt{classoption} variable in YAML and with
\texttt{elsearticle-harv.bst} which is among provided style by
\texttt{elsarticle} documentclass. Other available style are
\texttt{elsarticle-num.bst} and \texttt{elsarticle-num-names.bst} ---
the first one can be used for the numbered scheme, second one for
numbered with new options of natbib.sty.

You can sets extra options with \texttt{natbiboptions} variable in YAML
header. Example

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{natbiboptions}\KeywordTok{:}\AttributeTok{ longnamesfirst,angle,semicolon}
\end{Highlighting}
\end{Shaded}

There are various more specific bibliography styles available at
\url{https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files}.
To use one of these, add it in the header using, for example,
\texttt{biblio-style:\ model1-num-names}.

\hypertarget{using-csl}{%
\subsection{Using CSL}\label{using-csl}}

If \texttt{citation\_package} is set to \texttt{default} in
\texttt{elsevier\_article()}, then pandoc is used for citations instead
of \texttt{natbib}. In this case, the \texttt{csl} option is used to
format the references. Alternative \texttt{csl} files are available from
\url{https://www.zotero.org/styles?q=elsevier}. These can be downloaded
and stored locally, or the url can be used as in the example header.

\hypertarget{equations}{%
\section{Equations}\label{equations}}

Here is an equation: \[ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
\]

Here is another: \begin{align}
  a^2+b^2=c^2.
\end{align}

Inline equations: \(\sum_{i = 2}^\infty\{\alpha_i^\beta\}\)

\hypertarget{figures-and-tables}{%
\section{Figures and tables}\label{figures-and-tables}}

Figure \ref{fig2} is generated using an R chunk.

\begin{figure}

{\centering \includegraphics[width=0.5\linewidth]{test_files/figure-latex/fig2-1}

}

\caption{\label{fig2}A meaningless scatterplot.}\label{fig:fig2}
\end{figure}

\hypertarget{tables-coming-from-r}{%
\section{Tables coming from R}\label{tables-coming-from-r}}

Tables can also be generated using R chunks, as shown in Table
\ref{tab1} for example.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}\FunctionTok{head}\NormalTok{(mtcars)[,}\DecValTok{1}\SpecialCharTok{:}\DecValTok{4}\NormalTok{], }
    \AttributeTok{caption =} \StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{label\{tab1\}Caption centered above table"}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}lrrrr@{}}
\caption{\label{tab1}Caption centered above table}\tabularnewline
\toprule\noalign{}
& mpg & cyl & disp & hp \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
& mpg & cyl & disp & hp \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Mazda RX4 & 21.0 & 6 & 160 & 110 \\
Mazda RX4 Wag & 21.0 & 6 & 160 & 110 \\
Datsun 710 & 22.8 & 4 & 108 & 93 \\
Hornet 4 Drive & 21.4 & 6 & 258 & 110 \\
Hornet Sportabout & 18.7 & 8 & 360 & 175 \\
Valiant & 18.1 & 6 & 225 & 105 \\
\end{longtable}

\renewcommand\refname{References}
\bibliography{mybibfile.bib}

\end{document}

### 2024-04-11 high_aod/GHI_enh_02_ID_CE.R
Commit 2024-04-11 03:12

@@ -118,7 +118,7 @@ getwd()
 
 ## __ Execution control  -------------------------------------------------------
 TEST <- FALSE
-# TEST <- TRUE
+TEST <- TRUE
 
 if (TEST) {
     warning("\n\n ** Test is active!! ** \n\n")
@@ -281,7 +281,7 @@ switch(csmodel,
        Low_B.Exact_W   = { C4_cs_ref_ratio <- 1.04; C4_GLB_diff_THRES <- 20; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
        Low_B.High_W    = { C4_cs_ref_ratio <- 1.05; C4_GLB_diff_THRES <- 20; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
        Low_B.Low_W     = { C4_cs_ref_ratio <- 1.05; C4_GLB_diff_THRES <-  0; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.18},
-       High_B.Low_W    = { C4_cs_ref_ratio <- 1.08; C4_GLB_diff_THRES <-  0; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.18}, ## same as the used criterio
+       High_B.Low_W    = { C4_cs_ref_ratio <- 1.10; C4_GLB_diff_THRES <-  0; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.25}, ## same as the used criterio
                          { C4_cs_ref_ratio <- 1   ; C4_GLB_diff_THRES <-  0; C4_lowcut_sza <-  0; C4_lowcut_ratio <- 1   })
 ## init flag
 DATA[, Enhanc_C_4 := FALSE]

### 2024-04-11 high_aod/GHI_enh_02_ID_CE.tex
Commit 2024-04-11 03:12

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-09}
+\date{2024-04-10}
 
@@
 \begin{verbatim}
+Warning:
+
+ ** Test is active!! ** 
+\end{verbatim}
+
+\begin{verbatim}
 [1] "Cloud" "Clear"
@@
 \begin{verbatim}
- [1] "Exact_B.High_W.edir"  "Exact_B.High_W.edn"   "Exact_B.High_W.eup"  
- [4] "Exact_B.Low_2_W.edir" "Exact_B.Low_2_W.edn"  "Exact_B.Low_2_W.eup" 
- [7] "Exact_B.Exact_W.edir" "Exact_B.Exact_W.edn"  "Exact_B.Exact_W.eup" 
-[10] "Exact_B.Low_W.edir"   "Exact_B.Low_W.edn"    "Exact_B.Low_W.eup"   
+ [1] "Exact_B.High_W.edir"  "Exact_B.High_W.edn"   "Exact_B.High_W.eup"   "Exact_B.Low_2_W.edir"
+ [5] "Exact_B.Low_2_W.edn"  "Exact_B.Low_2_W.eup"  "Exact_B.Exact_W.edir" "Exact_B.Exact_W.edn" 
+ [9] "Exact_B.Exact_W.eup"  "Exact_B.Low_W.edir"   "Exact_B.Low_W.edn"    "Exact_B.Low_W.eup"   
 \end{verbatim}
@@
        \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
-       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
+       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.10}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.25}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
 \NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
@@
 \begin{verbatim}
- [1]        NA        NA 0.9855379 0.9053113 0.8366196 0.7771548 0.7251860 0.6793893
- [9] 0.6387354 0.6024114 0.5697672
+ [1]        NA        NA 1.0440020 0.9584892 0.8852695 0.8218832 0.7664852 0.7176648 0.6743248
+[10] 0.6355989 0.6007941
 \end{verbatim}
@@
 \begin{verbatim}
-C4 factor: 1.05 
+C4 factor: 1.1 
 \end{verbatim}
@@
 \endlastfoot
-5785494 & 416673 \\
+6031301 & 170866 \\
 \end{longtable}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-169} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-170} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-171} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-172} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-173} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-174} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-175} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-176} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-177} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-178} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-179} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-180} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-181} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-182} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-183} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-184} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-185} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-186} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-187} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-188} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-189} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-190} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-191} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-192} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-193} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-194} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-195} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-196} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-197} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-198} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-199} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-200} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-201} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-202} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-203} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-204} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-205} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-206} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-207} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-208} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-209} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-210} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-211} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-212} \end{center}
-
 \FloatBarrier
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-213} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-214} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-215} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-216} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-217} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-218} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-219} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-220} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-221} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-222} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-223} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-224} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-225} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-226} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-227} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-228} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-229} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-230} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-231} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-232} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-169} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-170} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-171} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-172} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-173} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-174} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-175} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-176} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-177} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-178} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-179} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-180} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-181} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-182} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-183} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-184} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-185} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-186} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-187} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-188} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-233} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-234} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-235} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-236} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-237} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-238} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-239} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-240} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-241} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-242} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-243} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-244} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-245} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-246} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-247} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-248} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-249} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-250} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-251} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-252} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-253} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-254} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-255} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-256} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-257} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-258} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-259} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-260} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-261} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-262} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-189} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-190} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-191} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-192} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-193} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-194} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-195} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-196} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-197} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-198} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-199} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-200} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-201} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-202} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-203} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-204} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-205} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-206} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-207} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-208} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-209} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-210} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-211} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-212} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-213} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-214} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-215} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-216} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-217} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-218} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-263} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-264} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-265} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-266} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-219} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-220} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-221} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-222} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-8} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-9} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-10} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-11} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-12} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-13} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-14} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-15} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-16} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-17} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-18} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-19} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-20} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-21} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-22} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-23} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-24} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-25} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-26} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-27} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-28} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-29} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-30} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-31} \end{center}
+\begin{verbatim}
+Warning: TEST IS ACTIVE !!
+\end{verbatim}
+
+TEST IS ACTIVE !!
 
@@
 \begin{verbatim}
-2024-04-09 19:11:13.0 athan@tyler GHI_enh_02_ID_CE.R 62.482203 mins
+2024-04-10 14:41:06.4 athan@tyler GHI_enh_02_ID_CE.R 8.094902 mins
 \end{verbatim}

### 2024-04-11 high_aod/GHI_enh_03_process.tex
Commit 2024-04-11 03:12

--- 2024-04-08 GHI_enh_03_process.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-08}
+\date{2024-04-10}
 
@@
 \begin{verbatim}
+Warning in eval(ei, envir):
 
- USING CSMODE: Low_B.Low_W
+ ** Test is active!! ** 
+\end{verbatim}
 
-C4 factor: 1.05 
+\begin{verbatim}
+
+ USING CSMODE: High_B.Low_W
+
+C4 factor: 1.1 
 C4 offset: 0 
@@
 \begin{verbatim}
-2024-04-08 15:48:57.0 athan@sagan GHI_enh_02_ID_CE.R 29.123272 mins
+Warning in eval(ei, envir): TEST IS ACTIVE !!
+\end{verbatim}
+
+\begin{verbatim}
+
+  TEST IS ACTIVE  !!
+
+2024-04-10 14:55:07 athan@tyler GHI_enh_02_ID_CE.R 6.972880 mins
 \end{verbatim}
@@
     Min      1Q  Median      3Q     Max 
--372.77 -150.51  -49.67   99.05  778.55
+-922.49 -337.13  -68.82  261.22 1657.04
 
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
-as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
+(Intercept)      -1.886e+02  1.075e+02  -1.754   0.0802 .  
+as.numeric(Date)  7.871e-07  8.610e-08   9.141   <2e-16 ***
 ---
@@
 
-Residual standard error: 217 on 361 degrees of freedom
-Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
-F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
+Residual standard error: 463.1 on 364 degrees of freedom
+Multiple R-squared:  0.1867,    Adjusted R-squared:  0.1845 
+F-statistic: 83.56 on 1 and 364 DF,  p-value: < 2.2e-16
 \end{verbatim}
@@
                     Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       -9.118e+01  5.082e+01  -1.794   0.0736 .  
-ST_E_monthly$Date  3.246e-07  4.062e-08   7.991 1.82e-14 ***
+(Intercept)       -1.886e+02  1.075e+02  -1.754   0.0802 .  
+ST_E_monthly$Date  7.871e-07  8.610e-08   9.141   <2e-16 ***
 ---
@@
 \begin{verbatim}
-2024-04-08 15:55:25.5 athan@sagan GHI_enh_02_ID_CE.R 3.671820 mins
+2024-04-10 15:18:08 athan@tyler GHI_enh_02_ID_CE.R 17.930279 mins
 \end{verbatim}

### 2024-04-11 high_aod/GHI_enh_02_ID_CE_.tex
Commit 2024-04-11 12:14

--- 2024-04-11 high_aod/GHI_enh_02_ID_CE.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-10}
+\date{2024-04-11}
 
@@
 }
-\begin{verbatim}
-[1] "/home/athan/MANUSCRIPTS/02_enhancement/high_aod"
-\end{verbatim}
+\begin{Shaded}
+\begin{Highlighting}[]
+\DocumentationTok{\#\# \_\_ Document options {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
+\end{Highlighting}
+\end{Shaded}
 
@@
 \begin{verbatim}
- [1] "Exact_B.High_W.edir"  "Exact_B.High_W.edn"   "Exact_B.High_W.eup"   "Exact_B.Low_2_W.edir"
- [5] "Exact_B.Low_2_W.edn"  "Exact_B.Low_2_W.eup"  "Exact_B.Exact_W.edir" "Exact_B.Exact_W.edn" 
- [9] "Exact_B.Exact_W.eup"  "Exact_B.Low_W.edir"   "Exact_B.Low_W.edn"    "Exact_B.Low_W.eup"   
+ [1] "Exact_B.High_W.edir"  "Exact_B.High_W.edn"   "Exact_B.High_W.eup"  
+ [4] "Exact_B.Low_2_W.edir" "Exact_B.Low_2_W.edn"  "Exact_B.Low_2_W.eup" 
+ [7] "Exact_B.Exact_W.edir" "Exact_B.Exact_W.edn"  "Exact_B.Exact_W.eup" 
+[10] "Exact_B.Low_W.edir"   "Exact_B.Low_W.edn"    "Exact_B.Low_W.eup"   
 \end{verbatim}
@@
        \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
-       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.10}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.25}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
+       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.10}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.30}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
 \NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
@@
 \begin{verbatim}
- [1]        NA        NA 1.0440020 0.9584892 0.8852695 0.8218832 0.7664852 0.7176648 0.6743248
-[10] 0.6355989 0.6007941
+ [1]        NA        NA 1.0857621 0.9949418 0.9171711 0.8498384 0.7909847
+ [8] 0.7391123 0.6930560 0.6518963 0.6148972
 \end{verbatim}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-10-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-10-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-3} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-3} \end{center}
 
@@
 \endlastfoot
-6031301 & 170866 \\
+6054123 & 148044 \\
 \end{longtable}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-8} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-9} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-10} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-11} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-12} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-13} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-14} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-15} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-16} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-17} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-18} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-19} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-20} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-21} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-22} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-23} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-24} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-25} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-26} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-27} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-28} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-29} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-30} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-31} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-32} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-33} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-8} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-9} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-10} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-11} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-12} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-13} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-14} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-15} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-16} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-17} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-18} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-19} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-20} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-21} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-22} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-23} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-24} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-25} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-26} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-27} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-28} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-29} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-30} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-31} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-32} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-33} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-3} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-8} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-9} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-10} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-11} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-12} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-13} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-14} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-15} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-16} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-17} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-18} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-19} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-20} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-3} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-8} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-9} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-10} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-11} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-12} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-13} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-14} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-15} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-16} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-17} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-18} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-19} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-20} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-21} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-22} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-23} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-24} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-25} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-26} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-27} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-28} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-29} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-30} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-31} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-32} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-33} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-34} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-35} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-36} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-37} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-38} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-39} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-40} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-41} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-42} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-43} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-44} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-45} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-46} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-47} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-48} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-49} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-50} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-21} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-22} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-23} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-24} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-25} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-26} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-27} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-28} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-29} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-30} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-31} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-32} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-33} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-34} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-35} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-36} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-37} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-38} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-39} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-40} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-41} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-42} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-43} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-44} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-45} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-46} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-47} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-48} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-49} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-50} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-51} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-52} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-53} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-54} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-55} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-56} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-57} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-58} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-59} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-60} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-61} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-62} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-63} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-64} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-65} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-66} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-67} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-68} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-69} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-70} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-51} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-52} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-53} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-54} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-55} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-56} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-57} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-58} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-59} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-60} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-61} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-62} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-63} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-64} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-65} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-66} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-67} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-68} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-69} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-70} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-71} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-72} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-73} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-74} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-75} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-76} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-77} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-78} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-79} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-80} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-81} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-82} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-83} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-84} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-85} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-86} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-87} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-88} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-89} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-90} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-91} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-92} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-93} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-94} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-95} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-96} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-97} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-98} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-99} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-100} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-101} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-102} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-103} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-104} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-105} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-106} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-107} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-108} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-109} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-110} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-111} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-112} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-113} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-114} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-115} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-116} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-117} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-118} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-119} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-120} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-121} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-122} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-123} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-124} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-125} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-126} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-127} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-128} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-129} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-130} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-131} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-132} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-133} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-134} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-135} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-136} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-137} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-138} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-139} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-140} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-141} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-142} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-143} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-144} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-145} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-146} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-147} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-148} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-149} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-150} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-151} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-152} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-153} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-154} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-155} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-156} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-157} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-158} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-159} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-160} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-161} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-162} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-163} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-164} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-165} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-166} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-167} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-168} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-71} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-72} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-73} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-74} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-75} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-76} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-77} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-78} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-79} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-80} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-81} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-82} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-83} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-84} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-85} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-86} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-87} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-88} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-89} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-90} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-91} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-92} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-93} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-94} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-95} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-96} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-97} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-98} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-99} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-100} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-101} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-102} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-103} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-104} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-105} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-106} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-107} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-108} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-109} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-110} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-111} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-112} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-113} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-114} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-115} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-116} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-117} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-118} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-119} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-120} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-121} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-122} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-123} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-124} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-125} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-126} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-127} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-128} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-129} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-130} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-131} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-132} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-133} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-134} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-135} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-136} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-137} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-138} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-139} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-140} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-141} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-169} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-170} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-171} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-172} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-173} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-174} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-175} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-176} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-177} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-178} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-179} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-180} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-181} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-182} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-183} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-184} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-185} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-186} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-187} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-188} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-142} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-143} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-144} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-145} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-146} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-147} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-148} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-149} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-150} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-151} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-152} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-153} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-154} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-155} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-156} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-157} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-158} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-159} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-160} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-161} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-189} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-190} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-191} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-192} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-193} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-194} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-195} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-196} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-197} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-198} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-199} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-200} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-201} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-202} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-203} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-204} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-205} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-206} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-207} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-208} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-209} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-210} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-211} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-212} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-213} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-214} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-215} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-216} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-217} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-218} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-162} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-163} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-164} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-165} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-166} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-167} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-168} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-169} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-170} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-171} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-172} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-173} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-174} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-175} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-176} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-177} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-178} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-179} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-180} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-181} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-182} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-183} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-184} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-185} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-186} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-187} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-188} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-189} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-190} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-191} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-219} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-220} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-221} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-222} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-192} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-193} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-194} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-195} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-3} \end{center}
+\begin{verbatim}
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2
+3.5.0.
+i Please use the `legend.position.inside` argument of `theme()` instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
+generated.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-3} \end{center}
 
@@
 \begin{verbatim}
-2024-04-10 14:41:06.4 athan@tyler GHI_enh_02_ID_CE.R 8.094902 mins
+2024-04-11 09:13:59.5 athan@sagan GHI_enh_02_ID_CE_highAOD.R 0.935513 mins
 \end{verbatim}

### 2024-04-11 high_aod/GHI_enh_02_ID_CE_.tex
Commit 2024-04-11 14:14

@@
 \begin{verbatim}
-Warning:
-
- ** Test is active!! ** 
-\end{verbatim}
-
-\begin{verbatim}
 [1] "Cloud" "Clear"
@@
        \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
-       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.10}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.30}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
+       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.11}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.31}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
 \NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
@@
 \begin{verbatim}
- [1]        NA        NA 1.0857621 0.9949418 0.9171711 0.8498384 0.7909847
- [8] 0.7391123 0.6930560 0.6518963 0.6148972
+ [1]        NA        NA 1.0941141 1.0026612 0.9243490 0.8565476 0.7972846
+ [8] 0.7450515 0.6986754 0.6572300 0.6199744
 \end{verbatim}
@@
 \begin{verbatim}
-C4 factor: 1.1 
+C4 factor: 1.11 
 \end{verbatim}
@@
 \endlastfoot
-6054123 & 148044 \\
+6072539 & 129628 \\
 \end{longtable}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-137} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-138} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-139} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-140} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-141} \end{center}
-
 \FloatBarrier
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-137} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-138} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-139} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-140} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-141} \end{center}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-142} \end{center}
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-156} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-157} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-158} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-159} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-160} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-161} \end{center}
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-157} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-158} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-159} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-160} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-161} \end{center}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-162} \end{center}
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-186} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-187} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-188} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-189} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-190} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-191} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-192} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-193} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-194} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-195} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-187} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-188} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-189} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-190} \end{center}
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-8} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-9} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-10} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-11} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-12} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-13} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-14} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-15} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-16} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-17} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-18} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-19} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-20} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-21} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-22} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-23} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-24} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-25} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-26} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-27} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-28} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-29} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-30} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-31} \end{center}
+
+\textbf{END}
+
 \begin{verbatim}
-Warning: TEST IS ACTIVE !!
+2024-04-11 09:51:15.2 athan@sagan GHI_enh_02_ID_CE_highAOD.R 32.426616 mins
 \end{verbatim}
 
-TEST IS ACTIVE !!
-
-\textbf{END}
-
-\begin{verbatim}
-2024-04-11 09:13:59.5 athan@sagan GHI_enh_02_ID_CE_highAOD.R 0.935513 mins
-\end{verbatim}
-
 \end{document}

### 2024-04-12 high_aod/GHI_enh_02_ID_CE.tex
Commit 2024-04-12 11:11

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-10}
+\date{2024-04-12}
 
@@
 }
-\begin{verbatim}
-[1] "/home/athan/MANUSCRIPTS/02_enhancement/high_aod"
-\end{verbatim}
-
-\begin{verbatim}
-Warning:
-
- ** Test is active!! ** 
-\end{verbatim}
+\begin{Shaded}
+\begin{Highlighting}[]
+\DocumentationTok{\#\# \_\_ Document options {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
+\end{Highlighting}
+\end{Shaded}
 
@@
        \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
-       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.10}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.25}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
+       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.11}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.31}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
 \NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
@@
 \begin{verbatim}
- [1]        NA        NA 1.0440020 0.9584892 0.8852695 0.8218832 0.7664852 0.7176648 0.6743248
-[10] 0.6355989 0.6007941
+ [1]        NA        NA 1.0941141 1.0026612 0.9243490 0.8565476 0.7972846
+ [8] 0.7450515 0.6986754 0.6572300 0.6199744
 \end{verbatim}
@@
 \endlastfoot
-6031301 & 170866 \\
+6072539 & 129628 \\
 \end{longtable}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-137} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-138} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-139} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-140} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-141} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-142} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-143} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-144} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-145} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-146} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-147} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-148} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-149} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-150} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-151} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-152} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-153} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-154} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-155} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-156} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-157} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-158} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-159} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-160} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-161} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-162} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-163} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-164} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-165} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-166} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-167} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-168} \end{center}
-
 \FloatBarrier
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-169} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-170} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-171} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-172} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-173} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-174} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-175} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-176} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-177} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-178} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-179} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-180} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-181} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-182} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-183} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-184} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-185} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-186} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-187} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-188} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-137} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-138} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-139} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-140} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-141} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-142} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-143} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-144} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-145} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-146} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-147} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-148} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-149} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-150} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-151} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-152} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-153} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-154} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-155} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-156} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-189} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-190} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-191} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-192} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-193} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-194} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-195} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-196} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-197} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-198} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-199} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-200} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-201} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-202} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-203} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-204} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-205} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-206} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-207} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-208} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-209} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-210} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-211} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-212} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-213} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-214} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-215} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-216} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-217} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-218} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-157} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-158} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-159} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-160} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-161} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-162} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-163} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-164} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-165} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-166} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-167} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-168} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-169} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-170} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-171} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-172} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-173} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-174} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-175} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-176} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-177} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-178} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-179} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-180} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-181} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-182} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-183} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-184} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-185} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-186} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-219} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-220} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-221} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-222} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-187} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-188} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-189} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-190} \end{center}
 
@@
 
+\begin{verbatim}
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
+i Please use the `legend.position.inside` argument of `theme()` instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-1} \end{center}
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-8} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-9} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-10} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-11} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-12} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-13} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-14} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-15} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-16} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-17} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-18} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-19} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-20} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-21} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-22} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-23} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-24} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-25} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-26} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-27} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-28} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-29} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-30} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-31} \end{center}
+
+\textbf{END}
+
 \begin{verbatim}
-Warning: TEST IS ACTIVE !!
+2024-04-12 07:30:18.5 athan@sagan GHI_enh_02_ID_CE_highAOD.R 31.981997 mins
 \end{verbatim}
 
-TEST IS ACTIVE !!
-
-\textbf{END}
-
-\begin{verbatim}
-2024-04-10 14:41:06.4 athan@tyler GHI_enh_02_ID_CE.R 8.094902 mins
-\end{verbatim}
-
 \end{document}

### 2024-04-12 high_aod/GHI_enh_03_process.tex
Commit 2024-04-12 12:14

--- 2024-04-08 GHI_enh_03_process.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-08}
+\date{2024-04-12}
 
@@
 
- USING CSMODE: Low_B.Low_W
+ USING CSMODE: High_B.Low_W
 
-C4 factor: 1.05 
+C4 factor: 1.11 
 C4 offset: 0 
 \end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-3} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-8} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-9} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-10} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-11} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-12} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-13} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-14} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-15} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-16} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-17} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-18} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-19} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-20} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-21} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-22} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-23} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-24} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-25} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-26} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-27} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-28} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-29} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-30} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-31} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-32} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-33} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-34} \end{center}
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-35} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-36} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-37} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-38} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-39} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-40} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-41} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-42} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-43} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-44} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-45} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-46} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-47} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-48} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-49} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-50} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-51} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-52} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-53} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-54} \end{center}
+
 \begin{verbatim}
@@
 \end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-55} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-56} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-57} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-58} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-59} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-60} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-61} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-62} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-63} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-64} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-65} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-66} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-67} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-68} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-69} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-70} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-71} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-72} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-73} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-74} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-75} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-76} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-77} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-78} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-79} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-80} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-81} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-82} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-83} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-84} \end{center}
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-85} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-86} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-87} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-88} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-89} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-90} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-91} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-92} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-93} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-94} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-95} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-96} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-97} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-98} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-99} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-100} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-101} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-102} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-103} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-104} \end{center}
+
 \begin{verbatim}
@@
 \end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-105} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-106} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-107} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-108} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-109} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-110} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-111} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-112} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-113} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-114} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-115} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-116} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-117} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-118} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-119} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-120} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-121} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-122} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-123} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-124} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-125} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-126} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-127} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-128} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-129} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-130} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-131} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-132} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-133} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-134} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-135} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-136} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-137} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-138} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-139} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-140} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-141} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-142} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-143} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-144} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-145} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-146} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-147} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-148} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-149} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-150} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-151} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-152} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-153} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-154} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-155} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-156} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-157} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-158} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-159} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-160} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-161} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-162} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-163} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-164} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-165} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-166} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-167} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-168} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-169} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-170} \end{center}
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-171} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-172} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-173} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-174} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-175} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-176} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-177} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-178} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-179} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-180} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-181} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-182} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-183} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-184} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-185} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-186} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-187} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-188} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-189} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-190} \end{center}
+
 \begin{verbatim}
@@
 \end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-191} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-192} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-193} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-194} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-195} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-196} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-197} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-198} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-199} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-200} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-201} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-202} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-203} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-204} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-205} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-206} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-207} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-208} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-209} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-210} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-211} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-212} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-213} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-214} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-215} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-216} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-217} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-218} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-219} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-220} \end{center}
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-221} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-222} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-223} \end{center}
+
 \begin{verbatim}
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-224} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-225} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-226} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-227} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-228} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-229} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-230} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-231} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-232} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-233} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-234} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-235} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-236} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-237} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-238} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-239} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-240} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-241} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-242} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-243} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-244} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-245} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-246} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-247} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-248} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-249} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-250} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-251} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-252} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-253} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-254} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-255} \end{center}
+
 \begin{verbatim}
-2024-04-08 15:48:57.0 athan@sagan GHI_enh_02_ID_CE.R 29.123272 mins
+2024-04-12 08:04:20.8 athan@sagan GHI_enh_02_ID_CE_highAOD.R 30.143398 mins
 \end{verbatim}
@@
     Min      1Q  Median      3Q     Max 
--372.77 -150.51  -49.67   99.05  778.55
+-403.26 -146.68  -25.16  113.64  654.68
 
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
-as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
+(Intercept)      -8.280e+01  4.915e+01  -1.685   0.0929 .  
+as.numeric(Date)  3.608e-07  3.928e-08   9.184   <2e-16 ***
 ---
@@
 
-Residual standard error: 217 on 361 degrees of freedom
-Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
-F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
+Residual standard error: 209.8 on 361 degrees of freedom
+Multiple R-squared:  0.1894,    Adjusted R-squared:  0.1871 
+F-statistic: 84.35 on 1 and 361 DF,  p-value: < 2.2e-16
 \end{verbatim}
@@
                     Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       -9.118e+01  5.082e+01  -1.794   0.0736 .  
-ST_E_monthly$Date  3.246e-07  4.062e-08   7.991 1.82e-14 ***
+(Intercept)       -8.280e+01  4.915e+01  -1.685   0.0929 .  
+ST_E_monthly$Date  3.608e-07  3.928e-08   9.184   <2e-16 ***
 ---
@@
 R_COMPILE_PKGS
+R_LIB_USER
 RANDOM_SEED
 raw_input_data
+RENV_PATHS_CACHE
 running_mean_window_days
@@
 SZA_confidence_limit
+TMPDIR
+user_libs_path
 variables_fl
@@
 \begin{verbatim}
-2024-04-08 15:55:25.5 athan@sagan GHI_enh_02_ID_CE.R 3.671820 mins
+2024-04-12 08:14:12.9 athan@sagan GHI_enh_02_ID_CE_highAOD.R 9.818640 mins
 \end{verbatim}

### 2024-04-12 high_aod/GHI_enh_03_process.R
Commit 2024-04-12 12:14

@@ -62,8 +62,8 @@ Script.Name <- "./GHI_enh_03_process.R"
 setwd("~/MANUSCRIPTS/02_enhancement/high_aod/")
 
 if (!interactive()) {
-    pdf( file = paste0("./runtime/", basename(sub("\\.R$",".pdf", Script.Name))))
-    sink(file = paste0("./runtime/", basename(sub("\\.R$",".out", Script.Name))), split = TRUE)
+  pdf( file = paste0("./runtime/", basename(sub("\\.R$", ".pdf", Script.Name))))
+  sink(file = paste0("./runtime/", basename(sub("\\.R$", ".out", Script.Name))), split = TRUE)
 }
 
 
@@ -1025,6 +1025,6 @@ tac <- Sys.time()
 cat(sprintf("%s %s@%s %s %f mins\n\n", Sys.time(), Sys.info()["login"],
             Sys.info()["nodename"], basename(Script.Name), difftime(tac,tic,units = "mins")))
 if (difftime(tac,tic,units = "sec") > 30) {
-    system("mplayer /usr/share/sounds/freedesktop/stereo/dialog-warning.oga", ignore.stdout = T, ignore.stderr = T)
-    system(paste("notify-send -u normal -t 30000 ", Script.Name, " 'R script ended'"))
+  system("mplayer /usr/share/sounds/freedesktop/stereo/dialog-warning.oga", ignore.stdout = T, ignore.stderr = T)
+  system(paste("notify-send -u normal -t 30000 ", Script.Name, " 'R script ended'"))
 }

### 2024-04-12 high_aod/GHI_enh_04_investigate.R

@@ -42,29 +42,29 @@
 
 #+ echo=F, include=T
 
+## __ Document options  --------------------------------------------------------
 
-## __ Document options ---------------------------------------------------------
-
-#+ echo=F, include=F
+#+ echo=FALSE, include=TRUE
 knitr::opts_chunk$set(comment    = ""       )
 knitr::opts_chunk$set(dev        = c("pdf", "png"))
 # knitr::opts_chunk$set(dev        = "png"    )
 knitr::opts_chunk$set(out.width  = "100%"   )
 knitr::opts_chunk$set(fig.align  = "center" )
 knitr::opts_chunk$set(cache      =  FALSE   )  ## !! breaks calculations
-# knitr::opts_chunk$set(fig.pos    = '!h'    )
+knitr::opts_chunk$set(fig.pos    = '!h'     )
 
-
-#+ include=F, echo=F
-## __ Set environment ----------------------------------------------------------
+#+ echo=FALSE, include=TRUE
+## __ Set environment  ---------------------------------------------------------
 Sys.setenv(TZ = "UTC")
 Script.Name <- "./GHI_enh_04_investigate.R"
 
-if (!interactive()) {
-  pdf( file = paste0("./runtime/",  basename(sub("\\.R$", ".pdf", Script.Name))))
-  sink(file = paste0("./runtime/",  basename(sub("\\.R$", ".out", Script.Name))), split = TRUE)
-}
+## use worktree
+setwd("~/MANUSCRIPTS/02_enhancement/high_aod/")
 
+if (!interactive()) {
+  pdf( file = paste0("./runtime/", basename(sub("\\.R$", ".pdf", Script.Name))))
+  sink(file = paste0("./runtime/", basename(sub("\\.R$", ".out", Script.Name))), split = TRUE)
+}
 
 
 #+ echo=F, include=T
@@ -93,7 +93,7 @@ source("~/CODE/FUNCTIONS/R/data.R")
 source("~/CODE/FUNCTIONS/R/trig_deg.R")
 
 
-## __ Source initial scripts ---------------------------------------------------
+## __ Source initial scripts  --------------------------------------------------
 source("./GHI_enh_00_variables.R")
 source("./GHI_enh_00_dictionary.R")
 source("~/CODE/FUNCTIONS/R/linear_fit_stats.R")
@@ -104,7 +104,7 @@ source("~/CODE/FUNCTIONS/R/cor_test_stats.R")
[…]

### 2024-04-12 high_aod/GHI_enh_03_process.tex
Commit 2024-04-12 16:14

--- 2024-04-11 high_aod/GHI_enh_03_process.tex
@@
 \begin{verbatim}
-Warning in eval(ei, envir):
-
- ** Test is active!! ** 
-\end{verbatim}
-
-\begin{verbatim}
 
@@
 
-C4 factor: 1.1 
+C4 factor: 1.11 
 C4 offset: 0 
@@
 \begin{verbatim}
-Warning in eval(ei, envir): TEST IS ACTIVE !!
-\end{verbatim}
-
-\begin{verbatim}
-
-  TEST IS ACTIVE  !!
-
-2024-04-10 14:55:07 athan@tyler GHI_enh_02_ID_CE.R 6.972880 mins
+2024-04-12 11:43:50.1 athan@sagan GHI_enh_02_ID_CE.R 33.135529 mins
 \end{verbatim}
@@
     Min      1Q  Median      3Q     Max 
--922.49 -337.13  -68.82  261.22 1657.04
+-403.26 -146.68  -25.16  113.64  654.68
 
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      -1.886e+02  1.075e+02  -1.754   0.0802 .  
-as.numeric(Date)  7.871e-07  8.610e-08   9.141   <2e-16 ***
+(Intercept)      -8.280e+01  4.915e+01  -1.685   0.0929 .  
+as.numeric(Date)  3.608e-07  3.928e-08   9.184   <2e-16 ***
 ---
@@
 
-Residual standard error: 463.1 on 364 degrees of freedom
-Multiple R-squared:  0.1867,    Adjusted R-squared:  0.1845 
-F-statistic: 83.56 on 1 and 364 DF,  p-value: < 2.2e-16
+Residual standard error: 209.8 on 361 degrees of freedom
+Multiple R-squared:  0.1894,    Adjusted R-squared:  0.1871 
+F-statistic: 84.35 on 1 and 361 DF,  p-value: < 2.2e-16
 \end{verbatim}
@@
                     Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       -1.886e+02  1.075e+02  -1.754   0.0802 .  
-ST_E_monthly$Date  7.871e-07  8.610e-08   9.141   <2e-16 ***
+(Intercept)       -8.280e+01  4.915e+01  -1.685   0.0929 .  
+ST_E_monthly$Date  3.608e-07  3.928e-08   9.184   <2e-16 ***
 ---
@@
 \begin{verbatim}
-2024-04-10 15:18:08 athan@tyler GHI_enh_02_ID_CE.R 17.930279 mins
+2024-04-12 11:51:07.2 athan@sagan GHI_enh_02_ID_CE.R 4.499965 mins
 \end{verbatim}

### 2024-04-13 article/article.Rmd
Commit 2024-04-13 14:14

@@
 ---
-title:    SDR enhancement by clouds
-
-subtitle: A Short Subtitle
+title: Downward shortwave solar irradiance enhancement by clouds.
 
 author:
-  - Athanasios N. Natsis^[Laboratory of Atmospheric Physics _natsisphysicist@gmail.com_] 
-  - Alkiviadis Bais^[Laboratory of Atmospheric Physics _abais@auth.gr_] 
-  - Charikleia Meleti^[Laboratory of Atmospheric Physics _meleti@auth.gr_]
+  - name:        Athanasios N. Natsis
+    email:       natsisphysicist@gmail.com
+    affiliation: LAP
+    correspondingauthor: true
+    footnote: 1
+  - name:        Alkiviadis Bais
+    email:       abais@auth.gr
+    affiliation: LAP
+  - name:        Charikleia Meleti
+    email:       meleti@auth.gr
+    affiliation: LAP
+    footnote: 2
+address:
+  - code:         LAP
+    organization: Laboratory of Atmospheric Physics, A.U.Th.
+    addressline:  1 main street
+    city:         Thessaloniki
+    postcode:     123456
+    country:      Greece
+  - code:         Another University
+    organization: Department
+    addressline:  A street 29
+    postcode:     2054 NX
+    city:         Manchester,
+    state:        State
+    country:      The Netherlands
+footnote:
+  - code: 1
+    text: "This is the first author footnote."
+  - code: 2
+    text: "Another author footnote."
+abstract: |
+  Here wii be the abstract.
 
-# abstract: |
-#   This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
+  It consists of two paragraphs.
 
@@
 
-bibliography:  [bibliography.bib]
+journal:        "An awesome journal"
+date:           "`r Sys.Date()`"
+linenumbers:    false
+numbersections: true
+bibliography:   bibliography.bib
 
-date: "`r format(Sys.time(), '%F')`"
+biblio-style:   elsarticle-harv # author year style for natbib - use 'elsarticle-num' or 'elsarticle-num-names' for numbered scheme
 
-header-includes:
-  - \usepackage{caption}
-  - \usepackage{placeins}
-  - \captionsetup{font=small}
+classoption:    preprint, 3p, authoryear # remove authoryear is not using `elsarticle-harv`
+# Use a CSL with `citation_package = "default"`
+# csl: https://www.zotero.org/styles/elsevier-harvard
 
 output: 
-  # redoc::redoc: default
- #  rticles::mdpi_article:
- #    extra_dependencies:  longtable
- #    keep_tex:            yes
+  rticles::elsevier_article:
+    keep_tex:         true
+    citation_package: natbib
   bookdown::pdf_document2:
@@
 # knitr::opts_chunk$set(dev        = "pdf"   )
-knitr::opts_chunk$set(out.width  = "60%"   )
-knitr::opts_chunk$set(fig.align  = "center")
-knitr::opts_chunk$set(fig.pos    = 'h!'    )
+knitr::opts_chunk$set(out.width  = "50%"   )
+# knitr::opts_chunk$set(fig.align  = "center")
+# knitr::opts_chunk$set(fig.pos    = 'h!'    )
 options(knitr.graphics.auto_pdf = FALSE)
@@
 
-\FloatBarrier
+<!-- \FloatBarrier -->
 
@@
 
-# References {.unnumbered}
+<!-- # References {.unnumbered} -->
+
+<!--
+Elsevier template
+
+Please make sure that your manuscript follows the guidelines in the 
+Guide for Authors of the relevant journal. It is not necessary to 
+typeset your manuscript in exactly the same way as an article, 
+unless you are submitting to a camera-ready copy (CRC) journal.
+
+For detailed instructions regarding the elsevier article class, see   <https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions>
+
+# Bibliography styles
+
+Here are two sample references: @Feynman1963118 [@Dirac1953888].
+
+By default, natbib will be used with the `authoryear` style, set in `classoption` variable in YAML and with `elsearticle-harv.bst` which is among provided style by `elsarticle` documentclass.
+Other available style are `elsarticle-num.bst` and `elsarticle-num-names.bst` — the first one can be used for the numbered scheme, second one for numbered with new options of natbib.sty.
+
+You can sets extra options with `natbiboptions` variable in YAML header. Example 
+```yaml
+natbiboptions: longnamesfirst,angle,semicolon
+```
+
+There are various more specific bibliography styles available at
+<https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files>. 
+To use one of these, add it in the header using, for example, `biblio-style: model1-num-names`.
+
+## Using CSL
+
+If `citation_package` is set to `default` in `elsevier_article()`, then pandoc is used for citations instead of `natbib`.
+In this case, the `csl` option is used to format the references.
+Alternative `csl` files are available from <https://www.zotero.org/styles?q=elsevier>.
+These can be downloaded
+and stored locally, or the url can be used as in the example header.
+
+# Equations
+
+Here is an equation:
+$$ 
+  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
+  \left(\frac{x}{\beta}\right)^{\alpha-1}
+  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
+  \alpha,\beta,x > 0 .
+$$
+
+Here is another:
+\begin{align}
+  a^2+b^2=c^2.
+\end{align}
+
+Inline equations: $\sum_{i = 2}^\infty\{\alpha_i^\beta\}$
+
+# Figures and tables
+
+Figure \ref{fig2} is generated using an R chunk.
+
+```{r fig2, fig.width = 5, fig.height = 5, fig.align='center', out.width="50%", fig.cap = "\\label{fig2}A meaningless scatterplot.", echo = FALSE}
+plot(runif(25), runif(25))
+```
+
+# Tables coming from R
+
+Tables can also be generated using R chunks, as shown in Table \ref{tab1} for example.
+
+```{r tab1, echo = TRUE}
+knitr::kable(head(mtcars)[,1:4], 
+    caption = "\\label{tab1}Caption centered above table"
+)
+```
+
+-->

### 2024-04-13 GHI_enh_00_dictionary.R

@@ -50,7 +50,8 @@ tr_var <- function(x, type = "short") {
 varcol <- function(avar) {
   # switch(gsub("\\..*$", "", gsub(".*_", "", avar)),
   switch(gsub("^.*_", "", gsub("\\..*", "", "GLB_diff.p_95")),
-         diff = "green",
+         # diff = "green",
+         diff = "#317529",
          ench = "blue",
          rati = "magenta",
          "black"

### 2024-04-13 high_aod/GHI_enh_04_investigate.tex
Commit 2024-04-13 14:14

--- 2024-03-28 GHI_enh_04_investigate.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-28}
+\date{2024-04-13}
 
@@
 
-lmD: 1.566006 +/- 0.108321
+lmD: 1.517841 +/- 0.099133
 
-lmY: 1.566022 +/- 0.108322
+lmY: 1.517857 +/- 0.099134
 
-Arima: 1.566405 +/- 0.146687
+Arima: 1.518153 +/- 0.131133
 
@@
 
-lmD: 0.950804 +/- 0.155249
+lmD: 0.986143 +/- 0.155127
 
-lmY: 0.950827 +/- 0.155251
+lmY: 0.986168 +/- 0.155129
 
-Arima: 1.022268 +/- 0.236917
+Arima: 1.050369 +/- 0.236468
 
@@
 
-lmD: 1.086985 +/- 0.167871
+lmD: 1.152913 +/- 0.165733
 
-lmY: 1.087013 +/- 0.167874
+lmY: 1.152941 +/- 0.165736
 
-Arima: 1.159971 +/- 0.251086
+Arima: 1.217146 +/- 0.245786
 
@@
 Warning in sqrt(diag(se)): NaNs produced
-
 Warning in sqrt(diag(se)): NaNs produced
@@
 
-lmD: 1.034078 +/- 0.239285
+lmD: 1.06442 +/- 0.24189
 
-lmY: 1.034088 +/- 0.23929
+lmY: 1.06443 +/- 0.241895
 
-Arima: 1.03413 +/- 0.363494
+Arima: 1.064477 +/- 0.369173
 
@@
 
-lmD: 0.944568 +/- 0.252832
+lmD: 0.965697 +/- 0.257186
 
-lmY: 0.944578 +/- 0.252837
+lmY: 0.965706 +/- 0.25719
 
-Arima: 0.944623 +/- 0.38704
+Arima: 0.965757 +/- 0.397302
 
@@
 
-lmD: 1.109672 +/- 0.07725
+lmD: 1.086689 +/- 0.074568
 
-lmY: 1.109686 +/- 0.077252
+lmY: 1.086704 +/- 0.07457
 
-Arima: 1.109689 +/- 0.115906
+Arima: 1.086709 +/- 0.111711
 
@@
 
-lmD: 1.167512 +/- 0.073583
+lmD: 1.121477 +/- 0.069651
 
-lmY: 1.167525 +/- 0.073584
+lmY: 1.121491 +/- 0.069652
 
-Arima: 1.167532 +/- 0.106265
+Arima: 1.1215 +/- 0.100263
 
@@
 
-lmD: 33.66024 +/- 5.69273
+lmD: 34.75674 +/- 5.785425
 
-lmY: 33.6608 +/- 5.692829
+lmY: 34.75733 +/- 5.785525
 
-Arima: 33.721354 +/- 8.881986
+Arima: 34.809263 +/- 9.232706
 
@@
 
-lmD: 0.003266 +/- 0.000271
+lmD: 0.00359 +/- 0.000275
 
-lmY: 0.003266 +/- 0.000271
+lmY: 0.00359 +/- 0.000275
 
-Arima: 0.003291 +/- 0.000364
+Arima: 0.003611 +/- 0.000363
 
@@
 
-lmD: 0.001715 +/- 0.000278
+lmD: 0.001821 +/- 0.000281
 
-lmY: 0.001715 +/- 0.000278
+lmY: 0.001821 +/- 0.000281
 
-Arima: 0.001886 +/- 0.000465
+Arima: 0.001976 +/- 0.000461
 
@@
 
-lmD: 0.001677 +/- 0.000314
+lmD: 0.001769 +/- 0.000314
 
-lmY: 0.001677 +/- 0.000314
+lmY: 0.00177 +/- 0.000314
 
-Arima: 0.001849 +/- 0.000512
+Arima: 0.001923 +/- 0.000501
 
@@
 possible convergence problem: optim gave code = 1
-
 Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
 NaNs produced
-
 Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
@@
 
-lmD: 0.00184 +/- 0.000301
+lmD: 0.001905 +/- 0.000317
 
-lmY: 0.00184 +/- 0.000301
+lmY: 0.001905 +/- 0.000317
 
-Arima: 0.00184 +/- 0.000473
+Arima: 0.001905 +/- 0.000497
 
@@
 
-lmD: 0.001768 +/- 0.000292
+lmD: 0.001871 +/- 0.000311
 
-lmY: 0.001768 +/- 0.000292
+lmY: 0.001871 +/- 0.000311
 
-Arima: 0.001768 +/- 0.000451
+Arima: 0.001871 +/- 0.00048
 
@@
 
-lmD: 0.002432 +/- 0.000235
+lmD: 0.002627 +/- 0.000234
 
-lmY: 0.002432 +/- 0.000235
+lmY: 0.002627 +/- 0.000234
 
-Arima: 0.002432 +/- 0.000369
+Arima: 0.002627 +/- 0.000357
 
@@
 
-lmD: 0.002624 +/- 0.000229
+lmD: 0.002857 +/- 0.00023
 
-lmY: 0.002624 +/- 0.000229
+lmY: 0.002857 +/- 0.00023
 
-Arima: 0.002624 +/- 0.000346
+Arima: 0.002857 +/- 0.000337
 
@@
 
-lmD: 0.977006 +/- 0.143935
+lmD: 1.027493 +/- 0.146835
 
-lmY: 0.977029 +/- 0.143937
+lmY: 1.027517 +/- 0.146837
 
-Arima: 1.040956 +/- 0.218636
+Arima: 1.088887 +/- 0.223551
 
@@
 
-lmD: 0.817503 +/- 0.103432
+lmD: 0.821483 +/- 0.093059
 
-lmY: 0.817514 +/- 0.103434
+lmY: 0.821496 +/- 0.093061
 
-Arima: 0.817505 +/- 0.120041
+Arima: 0.821491 +/- 0.106018
 
@@
 
-lmD: 0.216071 +/- 0.038072
+lmD: 0.231635 +/- 0.035413
 
-lmY: 0.216075 +/- 0.038073
+lmY: 0.231639 +/- 0.035414
 
-Arima: 0.216075 +/- 0.041418
+Arima: 0.231639 +/- 0.038541
 
@@
 
-lmD: 0.190931 +/- 0.037875
+lmD: 0.185627 +/- 0.035397
 
-lmY: 0.190936 +/- 0.037876
+lmY: 0.18563 +/- 0.035398
 
-Arima: 0.190936 +/- 0.040087
+Arima: 0.185631 +/- 0.037388
 
@@
 
-lmD: 0.485676 +/- 0.046388
+lmD: 0.484056 +/- 0.045622
 
-lmY: 0.485682 +/- 0.046389
+lmY: 0.484065 +/- 0.045623
 
-Arima: 0.485682 +/- 0.055179
+Arima: 0.484067 +/- 0.052795
 
@@
 
-lmD: -0.00734 +/- 0.019077
+lmD: 0.004522 +/- 0.01809
 
-lmY: -0.007339 +/- 0.019077
+lmY: 0.004522 +/- 0.018091
 
-Arima: -0.007339 +/- 0.019267
+Arima: 0.004522 +/- 0.018546
 
@@
 
-lmD: -0.027816 +/- 0.017696
+lmD: -0.01638 +/- 0.016701
 
-lmY: -0.027816 +/- 0.017696
+lmY: -0.01638 +/- 0.016702
 
-Arima: -0.027816 +/- 0.017858
+Arima: -0.01638 +/- 0.016967
 
@@
 
-lmD: 0.49203 +/- 0.073274
+lmD: 0.513947 +/- 0.066925
 
-lmY: 0.492037 +/- 0.073275
+lmY: 0.513956 +/- 0.066926
 
-Arima: 0.492032 +/- 0.081403
+Arima: 0.513955 +/- 0.073889
 
@@
 
-lmD: 0.595557 +/- 0.083417
+lmD: 0.62079 +/- 0.075699
 
-lmY: 0.595566 +/- 0.083419
+lmY: 0.620801 +/- 0.075701
 
-Arima: 0.59556 +/- 0.094857
+Arima: 0.620798 +/- 0.084973
 
@@
 
-lmD: 1.467857 +/- 0.152656
+lmD: 1.376585 +/- 0.138013
 
-lmY: 1.46788 +/- 0.152659
+lmY: 1.376613 +/- 0.138016
 
-Arima: 1.467877 +/- 0.18431
+Arima: 1.376617 +/- 0.159843
 
@@
 
-lmD: 0.001336 +/- 0.000137
+lmD: 0.00152 +/- 0.000147
 
-lmY: 0.001336 +/- 0.000137
+lmY: 0.00152 +/- 0.000147
 
-Arima: 0.001336 +/- 0.000157
+Arima: 0.00152 +/- 0.000172
 
@@
 
-lmD: 0.000423 +/- 5.9e-05
+lmD: 0.00047 +/- 6.5e-05
 
-lmY: 0.000423 +/- 5.9e-05
+lmY: 0.00047 +/- 6.5e-05
 
-Arima: 0.000423 +/- 6.7e-05
+Arima: 0.00047 +/- 7.4e-05
 
@@
 
-lmD: 0.000372 +/- 6.1e-05
+lmD: 0.000371 +/- 6.8e-05
 
-lmY: 0.000372 +/- 6.1e-05
+lmY: 0.000371 +/- 6.8e-05
 
-Arima: 0.000372 +/- 6.8e-05
+Arima: 0.000371 +/- 7.5e-05
 
@@
 
-lmD: 2.1e-05 +/- 3.2e-05
+lmD: 2.4e-05 +/- 3.2e-05
 
-lmY: 2.1e-05 +/- 3.2e-05
+lmY: 2.4e-05 +/- 3.2e-05
 
-Arima: 2.1e-05 +/- 3.6e-05
+Arima: 2.4e-05 +/- 3.6e-05
 
@@
 
-lmD: -1.2e-05 +/- 2.9e-05
+lmD: -9e-06 +/- 2.8e-05
 
-lmY: -1.2e-05 +/- 2.9e-05
+lmY: -9e-06 +/- 2.8e-05
 
-Arima: -1.2e-05 +/- 3.4e-05
+Arima: -9e-06 +/- 3.3e-05
 
@@
 
-lmD: 0.000922 +/- 0.000106
+lmD: 0.001043 +/- 0.000117
 
-lmY: 0.000922 +/- 0.000106
+lmY: 0.001043 +/- 0.000117
 
-Arima: 0.000922 +/- 0.00012
+Arima: 0.001043 +/- 0.000134
 
@@
 
-lmD: 0.001074 +/- 0.000117
+lmD: 0.00124 +/- 0.000128
 
-lmY: 0.001074 +/- 0.000117
+lmY: 0.00124 +/- 0.000128
 
-Arima: 0.001074 +/- 0.000134
+Arima: 0.00124 +/- 0.000149
 
@@
 
-lmD: 0.036561 +/- 0.003622
+lmD: 0.040357 +/- 0.004191
 
-lmY: 0.036562 +/- 0.003622
+lmY: 0.040358 +/- 0.004191
 
-Arima: 0.036562 +/- 0.004204
+Arima: 0.040358 +/- 0.004746
 
@@
 
-lmD: 0.187208 +/- 0.249476
+lmD: 0.194018 +/- 0.214287
 
-lmY: 0.187246 +/- 0.24948
+lmY: 0.194046 +/- 0.21429
 
-Arima: 0.171775 +/- 0.364628
+Arima: 0.186379 +/- 0.278973
 
@@
 
-lmD: 0.049774 +/- 0.192505
+lmD: 0.05596 +/- 0.153614
 
-lmY: 0.049798 +/- 0.192508
+lmY: 0.055976 +/- 0.153616
 
-Arima: 0.008548 +/- 0.346363
+Arima: 0.03062 +/- 0.246509
 
@@
 
-lmD: 0.091248 +/- 0.191453
+lmD: 0.096383 +/- 0.153736
 
-lmY: 0.091272 +/- 0.191456
+lmY: 0.096398 +/- 0.153738
 
-Arima: 0.049975 +/- 0.33542
+Arima: 0.071517 +/- 0.241036
 
@@
 
-lmD: -0.069532 +/- 0.179279
+lmD: -0.06688 +/- 0.139832
 
-lmY: -0.06952 +/- 0.179282
+lmY: -0.066875 +/- 0.139835
 
-Arima: -0.124647 +/- 0.339466
+Arima: -0.104892 +/- 0.240811
 
@@
 
-lmD: -0.089703 +/- 0.178956
+lmD: -0.088196 +/- 0.139661
 
-lmY: -0.089692 +/- 0.178959
+lmY: -0.088192 +/- 0.139663
 
-Arima: -0.144328 +/- 0.338161
+Arima: -0.125787 +/- 0.23978
 
@@
 
-lmD: 0.16704 +/- 0.22968
+lmD: 0.176855 +/- 0.193744
 
-lmY: 0.167077 +/- 0.229683
+lmY: 0.176884 +/- 0.193747
 
-Arima: 0.146398 +/- 0.353614
+Arima: 0.166242 +/- 0.263579
 
@@
 
-lmD: 0.17703 +/- 0.238162
+lmD: 0.185582 +/- 0.202704
 
-lmY: 0.177067 +/- 0.238165
+lmY: 0.18561 +/- 0.202708
 
-Arima: 0.158966 +/- 0.358093
+Arima: 0.17647 +/- 0.269872
 
@@
 
-lmD: 0.368357 +/- 0.253498
+lmD: 0.354016 +/- 0.243235
 
-lmY: 0.368383 +/- 0.253502
+lmY: 0.35404 +/- 0.243239
 
-Arima: 0.36844 +/- 0.258271
+Arima: 0.354135 +/- 0.247045
 
@@
 
-lmD: 0.000508 +/- 0.000281
+lmD: 0.000568 +/- 0.000406
 
-lmY: 0.000509 +/- 0.000281
+lmY: 0.000568 +/- 0.000406
 
-Arima: 0.000508 +/- 0.000318
+Arima: 0.000566 +/- 0.000539
 
@@
 
-lmD: 0.000356 +/- 0.000214
+lmD: 0.000409 +/- 0.00035
 
-lmY: 0.000356 +/- 0.000214
+lmY: 0.000409 +/- 0.00035
 
-Arima: 0.000349 +/- 0.000265
+Arima: 4e-04 +/- 0.000503
 
@@
 
-lmD: 0.000399 +/- 0.000221
+lmD: 0.000433 +/- 0.000359
 
-lmY: 0.000399 +/- 0.000221
+lmY: 0.000433 +/- 0.000359
 
-Arima: 0.000392 +/- 0.00027
+Arima: 0.000424 +/- 0.000507
 
@@
 
-lmD: 0.000168 +/- 0.000199
+lmD: 0.000213 +/- 0.000334
 
-lmY: 0.000168 +/- 0.000199
+lmY: 0.000213 +/- 0.000334
 
-Arima: 0.000157 +/- 0.000257
+Arima: 0.000198 +/- 0.000495
 
@@
 
-lmD: 0.000155 +/- 0.000199
+lmD: 2e-04 +/- 0.000333
 
-lmY: 0.000155 +/- 0.000199
+lmY: 2e-04 +/- 0.000333
 
-Arima: 0.000144 +/- 0.000256
+Arima: 0.000184 +/- 0.000494
 
@@
 
-lmD: 0.000509 +/- 0.000261
+lmD: 0.000567 +/- 0.000389
 
-lmY: 0.000509 +/- 0.000261
+lmY: 0.000567 +/- 0.000389
 
-Arima: 0.000508 +/- 3e-04
+Arima: 0.000564 +/- 0.000526
 
@@
 
-lmD: 0.00051 +/- 0.00027
+lmD: 0.000568 +/- 0.000396
 
-lmY: 0.00051 +/- 0.00027
+lmY: 0.000568 +/- 0.000397
 
-Arima: 0.000509 +/- 0.000307
+Arima: 0.000565 +/- 0.000532
 
@@
 
-lmD: 0.008776 +/- 0.005507
+lmD: 0.008854 +/- 0.005655
 
-lmY: 0.008777 +/- 0.005507
+lmY: 0.008855 +/- 0.005655
 
-Arima: 0.008799 +/- 0.005722
+Arima: 0.008895 +/- 0.005992
 
@@
 
-Arima: 0.216075 +/- 0.041418
+Arima: 0.231639 +/- 0.038541
 
@@
 \begin{verbatim}
-Warning: Removed 25 rows containing missing values or values outside the scale
+Warning: Removed 15 rows containing missing values or values outside the scale
 range (`geom_bar()`).
@@
 \begin{verbatim}
-Warning: Removed 12 rows containing non-finite outside the scale range
+Warning: Removed 36 rows containing non-finite outside the scale range
 (`stat_bin2d()`).
@@
 \begin{verbatim}
-Warning: Removed 2 rows containing missing values or values outside the scale
+Warning: Removed 3 rows containing missing values or values outside the scale
 range (`geom_tile()`).
@@
 \begin{verbatim}
-Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
-Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
+Warning: Removed 36 rows containing non-finite outside the scale range
+(`stat_bin2d()`).
+\end{verbatim}
+
+\begin{verbatim}
+Warning: Removed 4 rows containing missing values or values outside the scale
+range (`geom_tile()`).
 \end{verbatim}
@@
 \begin{verbatim}
-Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
-Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
+Warning: Removed 36 rows containing non-finite outside the scale range
+(`stat_bin2d()`).
+\end{verbatim}
+
+\begin{verbatim}
+Warning: Removed 3 rows containing missing values or values outside the scale
+range (`geom_tile()`).
 \end{verbatim}
@@
 \begin{verbatim}
-Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
-Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
+Warning: Removed 36 rows containing non-finite outside the scale range (`stat_bin2d()`).
+Removed 3 rows containing missing values or values outside the scale range (`geom_tile()`).
 \end{verbatim}
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-8} \end{center}
+
 @Martins2022
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-8} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-9} \end{center}
 
-lmY: 341.6364 +/- 36.57038
+lmY: 346.8852 +/- 33.74613
 
@@
 
-lmY: 122.2229 +/- 11.42113
+lmY: 133.6263 +/- 11.25784
 
@@
 
-lmY: 0.232986 +/- 0.055703
+lmY: 0.232888 +/- 0.050234
 
@@
 
-lmY: 0.183685 +/- 0.040872
+lmY: 0.202917 +/- 0.037683
 
@@
 \begin{verbatim}
-2024-03-28 08:59:32.3 athan@sagan GHI_enh_04_investigate.R 0.815632 mins
+2024-04-13 09:28:09.9 athan@tyler GHI_enh_04_investigate.R 3.383829 mins
 \end{verbatim}

### 2024-04-13 high_aod/GHI_enh_05_distributions.tex
Commit 2024-04-13 14:14

--- 2024-04-11 high_aod/GHI_enh_02_ID_CE_.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-11}
+\date{2024-04-13}
 
@@
 }
-\begin{Shaded}
-\begin{Highlighting}[]
-\DocumentationTok{\#\# \_\_ Document options {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\end{Highlighting}
-\end{Shaded}
-
 \begin{verbatim}
-Warning:
-
- ** Test is active!! ** 
+Reference mode:       High_B.Low_W 
 \end{verbatim}
@@
 \begin{verbatim}
-[1] "Cloud" "Clear"
+Enhancemnet criteria: Enhanc_C_4 
 \end{verbatim}
 
+\FloatBarrier
+
+\hypertarget{frequency-distributions}{%
+\subsubsection{Frequency Distributions}\label{frequency-distributions}}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/freqdistributions-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/freqdistributions-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/freqdistributions-3} \end{center}
+
+\FloatBarrier
+
+\hypertarget{distributions}{%
+\subsubsection{Distributions}\label{distributions}}
+
 \begin{verbatim}
- [1] "Exact_B.High_W.edir"  "Exact_B.High_W.edn"   "Exact_B.High_W.eup"  
- [4] "Exact_B.Low_2_W.edir" "Exact_B.Low_2_W.edn"  "Exact_B.Low_2_W.eup" 
- [7] "Exact_B.Exact_W.edir" "Exact_B.Exact_W.edn"  "Exact_B.Exact_W.eup" 
-[10] "Exact_B.Low_W.edir"   "Exact_B.Low_W.edn"    "Exact_B.Low_W.eup"   
+Warning in hist.default(DATA[GLB_diff > 0, GLB_ench], breaks = breaks, freq =
+FALSE, : arguments 'freq', 'col', 'main', 'xlab' are not made use of
 \end{verbatim}
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/relative_distributions-1} \end{center}
+
 \begin{verbatim}
-   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
-  1.031   1.034   1.035   1.035   1.035   1.036 
+Warning in hist.default(DATA[GLB_diff > 0, GLB_diff], breaks = breaks, freq =
+FALSE, : arguments 'freq', 'col', 'main', 'xlab' are not made use of
 \end{verbatim}
 
-Alpha * HAU is CS\_ref
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/relative_distributions-2} \end{center}
 
-\hypertarget{using-criteria-enhanc_c_4-for-final-application}{%
-\subsection{\texorpdfstring{Using criteria \textbf{Enhanc\_C\_4} for final application}{Using criteria Enhanc\_C\_4 for final application}}\label{using-criteria-enhanc_c_4-for-final-application}}
+\begin{verbatim}
+Warning in hist.default(DATA[GLB_diff > 0, GLB_rati], breaks = breaks, freq =
+FALSE, : arguments 'freq', 'col', 'main', 'xlab' are not made use of
+\end{verbatim}
 
-\hypertarget{use-tsi-as-reference-for-clear-sky.}{%
-\subsection{1. Use TSI as reference for Clear sky.}\label{use-tsi-as-reference-for-clear-sky.}}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/relative_distributions-3} \end{center}
+
+\begin{verbatim}
+Warning: The dot-dot notation (`..count..`) was deprecated in ggplot2 3.4.0.
+i Please use `after_stat(count)` instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/relative_distributions-4} \end{center}
 
@@
 \begin{Highlighting}[]
-\DocumentationTok{\#\# \_\_ 1.
-My criteria  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\CommentTok{\# C1\_GLB\_ench\_THRES     \textless{}{-}  1.10 \#\# enchantment relative to HAU}
-\NormalTok{C1\_GLB\_diff\_THRES     }\OtherTok{\textless{}{-}} \DecValTok{20}    \DocumentationTok{\#\# enchantment absolute diff to HAU}
-\NormalTok{C1\_Clearness\_Kt\_THRES }\OtherTok{\textless{}{-}}  \FloatTok{0.8}  \DocumentationTok{\#\# enchantment threshold}
-\CommentTok{\# C1\_wattGLB\_THRES      \textless{}{-} 20    \#\# minimum value to consider}
+  \CommentTok{\# scale\_y\_continuous(labels = function(x) paste0(x, "\%"))}
 
-\NormalTok{DATA[, Enhanc\_C\_1 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}
-\CommentTok{\# DATA[wattGLB           \textgreater{} CS\_ref * C1\_GLB\_ench\_THRES + C1\_GLB\_diff\_THRES \&}
-\CommentTok{\#      ClearnessIndex\_kt \textgreater{} C1\_Clearness\_Kt\_THRES,}
-\CommentTok{\#      Enhanc\_C\_1 := TRUE]}
+\CommentTok{\# print(p, vp = grid::viewport(gp=grid::gpar(cex=1.5)))}
+\CommentTok{\# theme\_gray(base\_size = 18)}
 
-\NormalTok{DATA[, Enhanc\_C\_1\_ref }\SpecialCharTok{:=}\NormalTok{ ETH }\SpecialCharTok{*}\NormalTok{ C1\_Clearness\_Kt\_THRES }\SpecialCharTok{+}\NormalTok{ C1\_GLB\_diff\_THRES]}
-\NormalTok{DATA[wattGLB }\SpecialCharTok{\textgreater{}}\NormalTok{ Enhanc\_C\_1\_ref,}
-\NormalTok{     Enhanc\_C\_1 }\SpecialCharTok{:=} \ConstantTok{TRUE}\NormalTok{]}
-
-\ControlFlowTok{if}\NormalTok{ (SelEnhanc }\SpecialCharTok{==} \StringTok{"Enhanc\_C\_1"}\NormalTok{) \{}
-\NormalTok{    DATA[ , GLB\_diff }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_1\_ref                    ] }\DocumentationTok{\#\# enhancement}
-\NormalTok{    DATA[ , GLB\_ench }\SpecialCharTok{:=}\NormalTok{ ( wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_1\_ref ) }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_1\_ref ] }\DocumentationTok{\#\# relative enhancement}
-\NormalTok{    DATA[ , GLB\_rati }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_1\_ref                    ]}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{use-tsi-as-reference-for-clear-sky.-1}{%
-\subsection{2. Use TSI as reference for Clear sky.}\label{use-tsi-as-reference-for-clear-sky.-1}}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\DocumentationTok{\#\# \_\_ 2. Gueymard2017 Criteria  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\DocumentationTok{\#\# Clearness index \textgreater{} 0.8 / 1}
-\NormalTok{C2\_Clearness\_Kt\_THRES }\OtherTok{\textless{}{-}} \FloatTok{0.8}
-\NormalTok{DATA[, Enhanc\_C\_2 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}
-\NormalTok{DATA[, Enhanc\_C\_2\_ref }\SpecialCharTok{:=}\NormalTok{ ETH }\SpecialCharTok{*}\NormalTok{ C2\_Clearness\_Kt\_THRES]}
-\CommentTok{\# DATA[ClearnessIndex\_kt \textgreater{} C1\_Clearness\_Kt\_THRES,}
-\CommentTok{\#      Enhanc\_C\_2 := TRUE]}
-\NormalTok{DATA[wattGLB }\SpecialCharTok{\textgreater{}}\NormalTok{ Enhanc\_C\_2\_ref,}
-\NormalTok{     Enhanc\_C\_2 }\SpecialCharTok{:=} \ConstantTok{TRUE}\NormalTok{]}
-
-\ControlFlowTok{if}\NormalTok{ (SelEnhanc }\SpecialCharTok{==} \StringTok{"Enhanc\_C\_2"}\NormalTok{) \{}
-\NormalTok{    DATA[ , GLB\_diff }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_2\_ref                    ] }\DocumentationTok{\#\# enhancement}
-\NormalTok{    DATA[ , GLB\_ench }\SpecialCharTok{:=}\NormalTok{ ( wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_2\_ref ) }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_2\_ref ] }\DocumentationTok{\#\# relative enhancement}
-\NormalTok{    DATA[ , GLB\_rati }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_2\_ref                    ]}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{use-haurwitz-as-reference-for-clear-sky.}{%
-\subsection{3. Use Haurwitz as reference for Clear sky.}\label{use-haurwitz-as-reference-for-clear-sky.}}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\DocumentationTok{\#\# \_\_ 3. Vamvakas2020  Criteria  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\DocumentationTok{\#\# +5\% from model =\textgreater{} enhancements above 15 Wm\^{}2 the instrument uncertainty}
-\NormalTok{C3\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}
-\NormalTok{DATA[, Enhanc\_C\_3 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}
-\NormalTok{DATA[, Enhanc\_C\_3\_ref }\SpecialCharTok{:=}\NormalTok{ CS\_ref }\SpecialCharTok{*}\NormalTok{ C3\_cs\_ref\_ratio]}
-\NormalTok{DATA[wattGLB }\SpecialCharTok{\textgreater{}}\NormalTok{ Enhanc\_C\_3\_ref,}
-\NormalTok{     Enhanc\_C\_3 }\SpecialCharTok{:=} \ConstantTok{TRUE}\NormalTok{]}
-
-\ControlFlowTok{if}\NormalTok{ (SelEnhanc }\SpecialCharTok{==} \StringTok{"Enhanc\_C\_3"}\NormalTok{) \{}
-\NormalTok{    DATA[ , GLB\_diff }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_3\_ref                    ] }\DocumentationTok{\#\# enhancement}
-\NormalTok{    DATA[ , GLB\_ench }\SpecialCharTok{:=}\NormalTok{ ( wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_3\_ref ) }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_3\_ref ] }\DocumentationTok{\#\# relative enhancement}
-\NormalTok{    DATA[ , GLB\_rati }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_3\_ref                    ]}
-\NormalTok{\}}
-
-\DocumentationTok{\#\# \_\_ 4.
-my Criteria  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-
-\DocumentationTok{\#\# set values base}
-\NormalTok{csmodel }\OtherTok{\textless{}{-}} \StringTok{"High\_B.Low\_W"}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{use-libradtran-high_b.low_w-as-reference-for-clear-sky.}{%
-\subsection{\texorpdfstring{4.
-Use libradtran \textbf{High\_B.Low\_W} as reference for Clear sky.}{4.
-Use libradtran High\_B.Low\_W as reference for Clear sky.}}\label{use-libradtran-high_b.low_w-as-reference-for-clear-sky.}}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{cat}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{ USING CSMODE:"}\NormalTok{, csmodel, }\StringTok{"}\SpecialCharTok{\textbackslash{}n\textbackslash{}n}\StringTok{"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-
- USING CSMODE: High_B.Low_W 
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\ControlFlowTok{switch}\NormalTok{(csmodel,}
-       \AttributeTok{Exact\_B.Exact\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.02}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{55}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
-       \AttributeTok{Low\_2\_B.Low\_2\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.03}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{5}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
-       \AttributeTok{Low\_B.Exact\_W   =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.04}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
-       \AttributeTok{Low\_B.High\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
-       \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
-       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.10}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.30}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
-\NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
-\DocumentationTok{\#\# init flag}
-\NormalTok{DATA[, Enhanc\_C\_4 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}
-
-\CommentTok{\# DATA[, max(SZA)]}
-
-\NormalTok{smo }\OtherTok{\textless{}{-}} \FunctionTok{approxfun}\NormalTok{(}
-    \AttributeTok{x =} \FunctionTok{c}\NormalTok{(}\DecValTok{90} \SpecialCharTok{{-}}\NormalTok{ BIO\_ELEVA, C4\_lowcut\_sza  ),}
-    \AttributeTok{y =} \FunctionTok{c}\NormalTok{(C4\_lowcut\_ratio,  C4\_cs\_ref\_ratio)}
-\NormalTok{    )}
-
-\FunctionTok{smo}\NormalTok{(}\DecValTok{80}\SpecialCharTok{:}\DecValTok{70}\NormalTok{) }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{/}\FunctionTok{cosd}\NormalTok{(}\DecValTok{80}\SpecialCharTok{:}\DecValTok{70}\NormalTok{) }\SpecialCharTok{/} \FunctionTok{max}\NormalTok{(}\DecValTok{1}\SpecialCharTok{/}\FunctionTok{cosd}\NormalTok{(}\DecValTok{80}\SpecialCharTok{:}\DecValTok{70}\NormalTok{)))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
- [1]        NA        NA 1.0857621 0.9949418 0.9171711 0.8498384 0.7909847
- [8] 0.7391123 0.6930560 0.6518963 0.6148972
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{cat}\NormalTok{(}\StringTok{"C4 factor:"}\NormalTok{, C4\_cs\_ref\_ratio,   }\StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-C4 factor: 1.1 
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{cat}\NormalTok{(}\StringTok{"C4 offset:"}\NormalTok{, C4\_GLB\_diff\_THRES, }\StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-C4 offset: 0 
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\DocumentationTok{\#\# \_\_\_\_ Create global irradiance W/m\^{}2  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\NormalTok{DATA[, }\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{) }\SpecialCharTok{:=}\NormalTok{ (}\FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".edir"}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".edn"}\NormalTok{))) }\SpecialCharTok{/} \DecValTok{1000}\NormalTok{ ]}
-
-\DocumentationTok{\#\# \_\_\_\_ Apply sun{-}earth distance correction  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\NormalTok{DATA[, }\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{) }\SpecialCharTok{:=} \FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) }\SpecialCharTok{/}\NormalTok{ sun\_dist}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{ ]}
-
-\DocumentationTok{\#\# \_\_\_\_ Apply adjustment to Kurudz spectrum  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\NormalTok{DATA[, }\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{) }\SpecialCharTok{:=} \FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) }\SpecialCharTok{*}\NormalTok{ TSI\_Kurudz\_factor ]}
-
-\DocumentationTok{\#\# \_\_\_\_ Calculate clearness index  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\NormalTok{DATA[, ClearnessIndex\_C\_4 }\SpecialCharTok{:=}\NormalTok{ wattGLB }\SpecialCharTok{/} \FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) ]}
-
-\FunctionTok{hist}\NormalTok{(DATA}\SpecialCharTok{$}\NormalTok{ClearnessIndex\_C\_4, }\AttributeTok{breaks =} \DecValTok{100}\NormalTok{)}
-\FunctionTok{abline}\NormalTok{(}\AttributeTok{v =}\NormalTok{ C4\_cs\_ref\_ratio, }\AttributeTok{col =} \StringTok{"red"}\NormalTok{ )}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-10-1} \end{center}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\DocumentationTok{\#\# \_\_\_\_ Calculate reference and mark data  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
-\DocumentationTok{\#\# for most of the data}
-\NormalTok{DATA[SZA }\SpecialCharTok{\textless{}}\NormalTok{ C4\_lowcut\_sza, Enhanc\_C\_4\_ref }\SpecialCharTok{:=}\NormalTok{ (}\FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) }\SpecialCharTok{*}\NormalTok{ C4\_cs\_ref\_ratio) }\SpecialCharTok{+}\NormalTok{ C4\_GLB\_diff\_THRES ]}
-\DocumentationTok{\#\# fol low sun angles}
-\CommentTok{\# DATA[SZA \textgreater{} C4\_lowcut\_sza, Enhanc\_C\_4\_ref := (get(paste0(csmodel,".glo")) * C4\_lowcut\_ratio) ]}
-\NormalTok{DATA[SZA }\SpecialCharTok{\textgreater{}}\NormalTok{ C4\_lowcut\_sza, Enhanc\_C\_4\_ref }\SpecialCharTok{:=}\NormalTok{ (}\FunctionTok{get}\NormalTok{(}\FunctionTok{paste0}\NormalTok{(csmodel,}\StringTok{".glo"}\NormalTok{)) }\SpecialCharTok{*} \FunctionTok{smo}\NormalTok{(SZA)) ]}
-
-\NormalTok{DATA[wattGLB }\SpecialCharTok{\textgreater{}}\NormalTok{ Enhanc\_C\_4\_ref ,}
-\NormalTok{     Enhanc\_C\_4 }\SpecialCharTok{:=} \ConstantTok{TRUE}\NormalTok{]}
-\DocumentationTok{\#\# use threshold to compute values}
-\ControlFlowTok{if}\NormalTok{ (SelEnhanc }\SpecialCharTok{==} \StringTok{"Enhanc\_C\_4"}\NormalTok{) \{}
-\NormalTok{    DATA[ , GLB\_diff }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_4\_ref                    ] }\DocumentationTok{\#\# enhancement}
-\NormalTok{    DATA[ , GLB\_ench }\SpecialCharTok{:=}\NormalTok{ ( wattGLB }\SpecialCharTok{{-}}\NormalTok{ Enhanc\_C\_4\_ref ) }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_4\_ref ] }\DocumentationTok{\#\# relative enhancement}
-\NormalTok{    DATA[ , GLB\_rati }\SpecialCharTok{:=}\NormalTok{   wattGLB }\SpecialCharTok{/}\NormalTok{ Enhanc\_C\_4\_ref                    ]}
-\NormalTok{\}}
+\DocumentationTok{\#\#  Extreme cases Distributions  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
 \end{Highlighting}
@@
 
-\hypertarget{using-creteria-enhanc_c_4}{%
-\section{Using creteria: Enhanc\_C\_4}\label{using-creteria-enhanc_c_4}}
+\hypertarget{extreme-cases-distributions}{%
+\subsubsection{Extreme cases Distributions}\label{extreme-cases-distributions}}
 
-\hypertarget{distribution-of-different-metrics}{%
-\section{Distribution of different metrics}\label{distribution-of-different-metrics}}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/extremedistributions-1} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/extremedistributions-2} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-2} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/extremedistributions-3} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-3} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/extremedistributions-4} \end{center}
 
-\begin{longtable}[]{@{}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
-\caption{Enhanc\_C\_1}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedleft
-FALSE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-TRUE
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedleft
-FALSE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-TRUE
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-6082440 & 119727 \\
-\end{longtable}
+Enhanc\_C\_4
+6202167
 
-\begin{longtable}[]{@{}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
-\caption{Enhanc\_C\_2}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedleft
-FALSE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-TRUE
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedleft
-FALSE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-TRUE
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-6012875 & 189292 \\
-\end{longtable}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/extremedistributions-5} \end{center}
 
-\begin{longtable}[]{@{}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
-\caption{Enhanc\_C\_3}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedleft
-FALSE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-TRUE
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedleft
-FALSE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-TRUE
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-5455724 & 746443 \\
-\end{longtable}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/extremedistributions-6} \end{center}
 
-\begin{longtable}[]{@{}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
-\caption{Enhanc\_C\_4}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedleft
-FALSE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-TRUE
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedleft
-FALSE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-TRUE
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-6054123 & 148044 \\
-\end{longtable}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/extremedistributions-7} \end{center}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-8} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-9} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-10} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-11} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-12} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-13} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-14} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-15} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-16} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-17} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-18} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-19} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-20} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-21} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-22} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-23} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-24} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-25} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-26} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-27} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-28} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-29} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-30} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-31} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-32} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-33} \end{center}
-
-\FloatBarrier
-
-\hypertarget{plot-some-days-with-strong-enhancement-cases}{%
-\section{Plot some days with strong enhancement cases}\label{plot-some-days-with-strong-enhancement-cases}}
-
-\FloatBarrier
-
-\hypertarget{days-with-extreme-cases-day}{%
-\subsection{Days with extreme cases day}\label{days-with-extreme-cases-day}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-3} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-8} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-9} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-10} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-11} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-12} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-13} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-14} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-15} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-16} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-17} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-18} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-19} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-20} \end{center}
-
-\FloatBarrier
-
-\hypertarget{days-with-strong-enhancement-day}{%
-\subsection{Days with strong enhancement day}\label{days-with-strong-enhancement-day}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-21} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-22} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-23} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-24} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-25} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-26} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-27} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-28} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-29} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-30} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-31} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-32} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-33} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-34} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-35} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-36} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-37} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-38} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-39} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-40} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-41} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-42} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-43} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-44} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-45} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-46} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-47} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-48} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-49} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-50} \end{center}
-
-\FloatBarrier
-
-\hypertarget{days-with-sunny-day}{%
-\subsection{Days with sunny day}\label{days-with-sunny-day}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-51} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-52} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-53} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-54} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-55} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-56} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-57} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-58} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-59} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-60} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-61} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-62} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-63} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-64} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-65} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-66} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-67} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-68} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-69} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-70} \end{center}
-
-\FloatBarrier
-
-\hypertarget{days-with-sunny-enhancement-day}{%
-\subsection{Days with sunny enhancement day}\label{days-with-sunny-enhancement-day}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-71} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-72} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-73} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-74} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-75} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-76} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-77} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-78} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-79} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-80} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-81} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-82} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-83} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-84} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-85} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-86} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-87} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-88} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-89} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-90} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-91} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-92} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-93} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-94} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-95} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-96} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-97} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-98} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-99} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-100} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-101} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-102} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-103} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-104} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-105} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-106} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-107} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-108} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-109} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-110} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-111} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-112} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-113} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-114} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-115} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-116} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-117} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-118} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-119} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-120} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-121} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-122} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-123} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-124} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-125} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-126} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-127} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-128} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-129} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-130} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-131} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-132} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-133} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-134} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-135} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-136} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-137} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-138} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-139} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-140} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-141} \end{center}
-
-\FloatBarrier
-
-\hypertarget{days-with-cloudy-day}{%
-\subsection{Days with cloudy day}\label{days-with-cloudy-day}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-142} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-143} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-144} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-145} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-146} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-147} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-148} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-149} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-150} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-151} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-152} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-153} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-154} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-155} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-156} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-157} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-158} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-159} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-160} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-161} \end{center}
-
-\FloatBarrier
-
-\hypertarget{days-with-random-day}{%
-\subsection{Days with random day}\label{days-with-random-day}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-162} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-163} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-164} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-165} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-166} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-167} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-168} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-169} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-170} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-171} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-172} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-173} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-174} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-175} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-176} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-177} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-178} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-179} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-180} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-181} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-182} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-183} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-184} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-185} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-186} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-187} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-188} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-189} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-190} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-191} \end{center}
-
-\FloatBarrier
-
-\hypertarget{days-with-manual-test-days}{%
-\subsection{Days with manual test days}\label{days-with-manual-test-days}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-192} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-193} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-194} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-195} \end{center}
-
-\newpage
-\FloatBarrier
-
-\hypertarget{plot-years-with-enhancement-cases}{%
-\section{Plot years with enhancement cases}\label{plot-years-with-enhancement-cases}}
-
-\begin{verbatim}
-Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2
-3.5.0.
-i Please use the `legend.position.inside` argument of `theme()` instead.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was
-generated.
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_years-3} \end{center}
-
-\begin{verbatim}
-Warning: TEST IS ACTIVE !!
-\end{verbatim}
-
-TEST IS ACTIVE !!
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_05_distributions_files/figure-latex/P-relative-distribution-diff-1} \end{center}
 
@@
 \begin{verbatim}
-2024-04-11 09:13:59.5 athan@sagan GHI_enh_02_ID_CE_highAOD.R 0.935513 mins
+2024-04-13 09:47:42.0 athan@tyler GHI_enh_05_distributions.R 2.970822 mins
 \end{verbatim}

### 2024-04-13 article/article.Rmd
Commit 2024-04-13 22:14

@@
 knitr::opts_chunk$set(out.width  = "50%"   )
-# knitr::opts_chunk$set(fig.align  = "center")
+knitr::opts_chunk$set(fig.align  = "center")
 # knitr::opts_chunk$set(fig.pos    = 'h!'    )

### 2024-04-13 high_aod/GHI_enh_02_ID_CE.R
Commit 2024-04-14 00:14

@@ -57,13 +57,13 @@ knitr::opts_chunk$set(fig.pos    = '!h'     )
 ## __ Set environment  ---------------------------------------------------------
 Sys.setenv(TZ = "UTC")
 Script.Name <- "./GHI_enh_02_ID_CE.R"
+tic <- Sys.time()
 
 ## use worktree
 setwd("~/MANUSCRIPTS/02_enhancement/high_aod/")
 
 if (!interactive()) {
-    pdf( file = paste0("./runtime/", basename(sub("\\.R$",".pdf", Script.Name))))
-    sink(file = paste0("./runtime/", basename(sub("\\.R$",".out", Script.Name))), split = TRUE)
+  pdf( file = paste0("./runtime/", basename(sub("\\.R$",".pdf", Script.Name))))
 }
 
 
@@ -158,7 +158,6 @@ summary(DATA[, tsi_1au_comb / Kurudz_SC ])
 # plot(DATA[, tsi_1au_comb / Kurudz_SC ])
 
 DATA[, TSI_Kurudz_factor := tsi_1au_comb / Kurudz_SC ]
-
 
 
 

### 2024-04-13 high_aod/GHI_enh_05_distributions.R

@@ -42,27 +42,28 @@
 
 #+ echo=F, include=T
 
+## __ Document options  --------------------------------------------------------
 
-## __ Document options ---------------------------------------------------------
-
-#+ echo=F, include=F
+#+ echo=FALSE, include=TRUE
 knitr::opts_chunk$set(comment    = ""       )
 knitr::opts_chunk$set(dev        = c("pdf", "png"))
 # knitr::opts_chunk$set(dev        = "png"    )
 knitr::opts_chunk$set(out.width  = "100%"   )
 knitr::opts_chunk$set(fig.align  = "center" )
 knitr::opts_chunk$set(cache      =  FALSE   )  ## !! breaks calculations
-# knitr::opts_chunk$set(fig.pos    = '!h'    )
+knitr::opts_chunk$set(fig.pos    = '!h'     )
 
 
-#+ include=F, echo=F
-## __ Set environment ----------------------------------------------------------
+#+ echo=FALSE, include=TRUE
+## __ Set environment  ---------------------------------------------------------
 Sys.setenv(TZ = "UTC")
 Script.Name <- "./GHI_enh_05_distributions.R"
 
+## use worktree
+setwd("~/MANUSCRIPTS/02_enhancement/high_aod/")
+
 if (!interactive()) {
-    pdf( file = paste0("./runtime/",  basename(sub("\\.R$",".pdf", Script.Name))))
-    sink(file = paste0("./runtime/",  basename(sub("\\.R$",".out", Script.Name))), split = TRUE)
+  pdf( file = paste0("./runtime/", basename(sub("\\.R$", ".pdf", Script.Name))))
 }
 
 
@@ -91,23 +92,23 @@ source("~/CODE/FUNCTIONS/R/cor_test_stats.R")
 
 ## Override notification function
 options(error = function() {
-    if (interactive()) {
-        system("mplayer /usr/share/sounds/freedesktop/stereo/dialog-warning.oga", ignore.stdout = T, ignore.stderr = T)
-        system("notify-send -u normal -t 30000 'R session' 'An error occurred!'")
-    }
+  if (interactive()) {
+    system("mplayer /usr/share/sounds/freedesktop/stereo/dialog-warning.oga", ignore.stdout = T, ignore.stderr = T)
[…]

### 2024-04-13 GHI_enh_04_investigate.tex
Commit 2024-04-14 02:14

--- 2024-03-28 GHI_enh_04_investigate.tex
@@
 \begin{verbatim}
+Run previous step: ./GHI_enh_03_process.R
+\end{verbatim}
+
+\begin{verbatim}
+
+Attaching package: 'timetk'
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:data.table':
+
+    :=
+\end{verbatim}
+
+\begin{verbatim}
+frequency = 30 observations
+\end{verbatim}
+
+\begin{verbatim}
+trend = 180 observations
+\end{verbatim}
+
+\begin{verbatim}
+frequency = 30 observations
+\end{verbatim}
+
+\begin{verbatim}
+trend = 180 observations
+\end{verbatim}
+
+\begin{verbatim}
+
+Call:
+stats::lm(formula = .formula, data = df)
+
+Residuals:
+    Min      1Q  Median      3Q     Max 
+-372.77 -150.51  -49.67   99.05  778.55
+
+Coefficients:
+                   Estimate Std. Error t value Pr(>|t|)    
+(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
+as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
+---
+Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+
+Residual standard error: 217 on 361 degrees of freedom
+Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
+F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
+
+aa
+aday
+All_daily_ratio_lim
+alpha
+ampl
+avar
+BIO_ELEVA
+C1_Clearness_Kt_THRES
+C1_GLB_diff_THRES
+C2_Clearness_Kt_THRES
+C3_cs_ref_ratio
+C4_cs_ref_ratio
+C4_GLB_diff_THRES
+C4_lowcut_ratio
+C4_lowcut_sza
+Clear_daily_ratio_lim
+CLEARdir
+Cloud_daily_ratio_lim
+cols
+common_data_13
+common_data_14
+common_data_14_2
+CS_file_13
+CS_file_14
+CS_file_14_2
+csmodel
+Daily_aggregation_N_lim
+Daily_confidence_limit
+daylist
+Days_of_year
+Energy_Div
+I1_longterm
+I2_szatrend
+I3_trendsconsist
+ii
+Input_data_ID
+Kurudz_SC
+MIN_ELEVA
+MIN_N
+Monthly_aggegation_N_lim
+Monthly_confidence_limit
+my.cols
+my.cols.gr
+pyear
+R_COMPILE_PKGS
+RANDOM_SEED
+raw_input_data
+running_mean_window_days
+running_mean_window_years
+SEAS_MIN_N
+SelEnhanc
+SZA_aggregation_N_lim
+SZA_BIN
+SZA_confidence_limit
+torun
+variables_fl
+yearstodo
+ylim
+ST_daily
+ST_E_daily
+ST_E_daily_seas
+ST_E_monthly
+ST_E_monthly_seas
+ST_E_sza
+ST_E_sza_doy
+ST_E_sza_monthly
+ST_E_yearly
+ST_extreme_daily
+ST_extreme_monthly
+ST_extreme_SZA
+ST_extreme_SZA_doy
+ST_extreme_SZA_monthly
+ST_extreme_total
+ST_extreme_yearly
+ST_G0
+ST_G1
+ST_monthly
+ST_sza
+ST_sza_doy
+ST_sza_monthly
+ST_total
+ST_yearly
+2024-04-13 11:49:40.5 athan@tyler GHI_enh_03_process.R 8.015370 mins
+\end{verbatim}
+
+\begin{verbatim}
 ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
@@
 \begin{verbatim}
-2024-03-28 08:59:32.3 athan@sagan GHI_enh_04_investigate.R 0.815632 mins
+2024-04-13 11:51:44.2 athan@tyler GHI_enh_03_process.R 2.025699 mins
 \end{verbatim}

### 2024-04-14 GHI_enh_04_investigate.tex
Commit 2024-04-14 06:14

--- 2024-03-28 GHI_enh_04_investigate.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-28}
+\date{2024-04-14}
 
@@
 \begin{verbatim}
-2024-03-28 08:59:32.3 athan@sagan GHI_enh_04_investigate.R 0.815632 mins
+2024-04-14 00:48:00.3 athan@tyler GHI_enh_04_investigate.R 1.346105 mins
 \end{verbatim}

### 2024-04-14 article/article.tex
Commit 2024-04-08 18:14
Commit 2024-04-09 19:12
Commit 2024-04-12 14:14
Commit 2024-04-14 06:14

@@
 \documentclass[
-]{article}
+  preprint, 3p, authoryear]{article}
 \usepackage{amsmath,amssymb}
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\usepackage{caption}
-\usepackage{placeins}
-\captionsetup{font=small}
 \usepackage{booktabs}
@@
 \hypersetup{
-  pdftitle={SDR enhancement by clouds},
-  pdfauthor={Athanasios N. Natsis; Alkiviadis Bais; Charikleia Meleti},
+  pdftitle={Downward shortwave solar irradiance enhancement by clouds.},
   pdfkeywords={keyword1, keyword2},
@@
 
-\title{SDR enhancement by clouds}
-\usepackage{etoolbox}
-\makeatletter
-\providecommand{\subtitle}[1]{% add subtitle to \maketitle
-  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
-}
-\makeatother
-\subtitle{A Short Subtitle}
-\author{Athanasios N.
-Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
-\date{2024-04-07}
+\title{Downward shortwave solar irradiance enhancement by clouds.}
+\author{true \and true \and true}
+\date{2024-04-14}
 
@@
 \maketitle
+\begin{abstract}
+Here wii be the abstract.
+
+It consists of two paragraphs.
+\end{abstract}
 
@@
 
-\FloatBarrier
-
 \hypertarget{results}{%
@@
 
-\begin{figure}[h!]
+\begin{figure}
 
-{\centering \includegraphics[width=0.6\linewidth]{../images/P_daily_trend-1}
+{\centering \includegraphics[width=0.5\linewidth]{../images/P_daily_trend-1}
 
@@
 
-\begin{figure}[h!]
+\begin{figure}
 
-{\centering \includegraphics[width=0.6\linewidth]{../images/P_energy-7}
+{\centering \includegraphics[width=0.5\linewidth]{../images/P_energy-7}
 
@@
 
-\begin{figure}[h!]
+\begin{figure}
 
-{\centering \includegraphics[width=0.6\linewidth]{../images/P_energy-6}
+{\centering \includegraphics[width=0.5\linewidth]{../images/P_energy-6}
 
@@
 
-\begin{figure}[h!]
+\begin{figure}
 
-{\centering \includegraphics[width=0.6\linewidth]{../images/P_energy-5}
+{\centering \includegraphics[width=0.5\linewidth]{../images/P_energy-5}
 
@@
 
-\begin{figure}[h!]
+\begin{figure}
 
-{\centering \includegraphics[width=0.6\linewidth]{../images/P_energy-8}
+{\centering \includegraphics[width=0.5\linewidth]{../images/P_energy-8}
 
@@
 \end{figure}
-
-\FloatBarrier
 
@@
 
-\begin{figure}[h!]
+\begin{figure}
 
-{\centering \includegraphics[width=0.6\linewidth]{../images/clim_CE_month_norm_MAX_median_N-2}
+{\centering \includegraphics[width=0.5\linewidth]{../images/clim_CE_month_norm_MAX_median_N-2}
 
@@
 
-\begin{figure}[h!]
+\begin{figure}
 
-{\centering \includegraphics[width=0.6\linewidth]{../images/P-relative-distribution-diff-1}
+{\centering \includegraphics[width=0.5\linewidth]{../images/P-relative-distribution-diff-1}
 
@@
 
-\begin{figure}[h!]
+\begin{figure}
 
-{\centering \includegraphics[width=0.6\linewidth]{../images/groups-1}
+{\centering \includegraphics[width=0.5\linewidth]{../images/groups-1}
 
@@
 
-\begin{figure}[h!]
+\begin{figure}
 
-{\centering \includegraphics[width=0.6\linewidth]{../images/P-groups-bin2d-1}
+{\centering \includegraphics[width=0.5\linewidth]{../images/P-groups-bin2d-1}
 
@@
 
-\begin{figure}[h!]
+\begin{figure}
 
-{\centering \includegraphics[width=0.6\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}
+{\centering \includegraphics[width=0.5\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}
 
@@
 
-\begin{figure}[h!]
+\begin{figure}
 
-{\centering \includegraphics[width=0.6\linewidth]{../images/extremedistributions-2}
+{\centering \includegraphics[width=0.5\linewidth]{../images/extremedistributions-2}
 
@@
 
-\FloatBarrier
-
 \hypertarget{discussion-and-conclusions}{%
@@
 \addcontentsline{toc}{section}{Appendix}
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
 
@@
 2022.
-{``{The Astropy Project: Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package}''} 935 (2): 167.
+{``{The Astropy Project: Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package}.''} \emph{Astrophysical Journal} 935 (2): 167.
 \url{https://doi.org/10.3847/1538-4357/ac7c74}.

### 2024-04-14 high_aod/GHI_enh_03_process.tex
Commit 2024-04-14 06:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-12}
+\date{2024-04-13}
 
@@
 }
-\begin{verbatim}
-
- USING CSMODE: High_B.Low_W
-
-C4 factor: 1.11 
-C4 offset: 0 
-\end{verbatim}
-
-\begin{verbatim}
-
-\FloatBarrier
-
-## Days with extreme cases day 
-\end{verbatim}
-
-\begin{verbatim}
-
-\FloatBarrier
-
-## Days with strong enhancement day 
-\end{verbatim}
-
-\begin{verbatim}
-
-\FloatBarrier
-
-## Days with sunny day 
-\end{verbatim}
-
-\begin{verbatim}
-
-\FloatBarrier
-
-## Days with sunny enhancement day 
-\end{verbatim}
-
-\begin{verbatim}
-
-\FloatBarrier
-
-## Days with cloudy day 
-\end{verbatim}
-
-\begin{verbatim}
-
-\FloatBarrier
-
-## Days with random day 
-\end{verbatim}
-
-\begin{verbatim}
-
-\FloatBarrier
-
-## Days with manual test days 
-\end{verbatim}
-
-\begin{verbatim}
-Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
-i Please use the `legend.position.inside` argument of `theme()` instead.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
-
-\begin{verbatim}
-2024-04-12 11:43:50.1 athan@sagan GHI_enh_02_ID_CE.R 33.135529 mins
-\end{verbatim}
-
 Alpha * HAU is CS\_ref
@@
 Days_of_year
-dummy
 Energy_Div
@@
 \begin{verbatim}
-2024-04-12 11:51:07.2 athan@sagan GHI_enh_02_ID_CE.R 4.499965 mins
+2024-04-13 18:12:11.2 athan@tyler GHI_enh_03_process.R 12.412597 mins
 \end{verbatim}

### 2024-04-14 high_aod/GHI_enh_06_sza.tex
Commit 2024-04-14 06:14

--- 2024-03-14 GHI_enh_06_sza.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-14}
+\date{2024-04-13}
 
@@
     as.Date, as.Date.numeric
-\end{verbatim}
-
-\begin{verbatim}
-Not changed:  ./GHI_enh_06_sza.R 
-Not changed:  ./GHI_enh_00_variables.R 
-Not changed:  ./GHI_enh_03_process.R 
-Not changed:  ./data/GHI_enh_03_process.Rda 
-\end{verbatim}
-
-\begin{verbatim}
-[1] FALSE
-\end{verbatim}
-
-\begin{verbatim}
-Written `R_make_` file: .//.R_make.mk 
 \end{verbatim}
@@
 \begin{verbatim}
-2024-03-14 09:41:49.6 athan@tyler GHI_enh_06_sza.R 0.259163 mins
+2024-04-13 18:20:39.7 athan@tyler GHI_enh_06_sza.R 0.320738 mins
 \end{verbatim}

### 2024-04-14 GHI_enh_06_sza.tex
Commit 2024-04-14 16:14

--- 2024-03-14 GHI_enh_06_sza.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-14}
+\date{2024-04-14}
 
@@
 \begin{verbatim}
-2024-03-14 09:41:49.6 athan@tyler GHI_enh_06_sza.R 0.259163 mins
+2024-04-14 00:55:04.2 athan@tyler GHI_enh_06_sza.R 0.288979 mins
 \end{verbatim}

### 2024-04-15 article/article.tex
Commit 2024-04-16 02:14

@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  preprint, 3p, authoryear]{article}
-\usepackage{amsmath,amssymb}
-\usepackage{iftex}
-\ifPDFTeX
+\documentclass[preprint, 3p,
+authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
+%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
+
+\usepackage[hyphens]{url}
+
+  \journal{An awesome journal} % Sets Journal name
+
+\usepackage{graphicx}
+%%%%%%%%%%%%%%%% end my additions to header
+
 \usepackage[T1]{fontenc}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+% TODO: Currently lineno needs to be loaded after amsmath because of conflict
+% https://github.com/latex-lineno/lineno/issues/5
+\usepackage{lineno} % add
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\else % if luatex or xelatex
+  \usepackage{fontspec}
+  \ifxetex
+    \usepackage{xltxtra,xunicode}
   \fi
-\usepackage{lmodern}
-\ifPDFTeX\else
-  % xetex/luatex font selection
+  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
+  \newcommand{\euro}{€}
 \fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
+% use microtype if available
+\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+\usepackage[]{natbib}
+\bibliographystyle{elsarticle-harv}
+
+\ifxetex
+  \usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \usepackage[unicode=true]{hyperref}
+\fi
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={},
+            pdftitle={Downward shortwave solar irradiance enhancement by clouds.},
+            colorlinks=false,
+            urlcolor=blue,
+            linkcolor=magenta,
+            pdfborder={0 0 0}}
+
+\setcounter{secnumdepth}{5}
+% Pandoc toggle for numbering sections (defaults to be off)
+
+% tightlist command for lists without linebreak
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
 \usepackage{booktabs}
@@
 \usepackage{xcolor}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
-\hypersetup{
-  pdftitle={Downward shortwave solar irradiance enhancement by clouds.},
-  pdfkeywords={keyword1, keyword2},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
+
+\begin{document}
+
+\begin{frontmatter}
 
   \title{Downward shortwave solar irradiance enhancement by clouds.}
-\author{true \and true \and true}
-\date{2024-04-14}
+    \author[LAP]{Athanasios N. Natsis%
+  \corref{cor1}%
+  \fnref{1}}
+   \ead{natsisphysicist@gmail.com} 
+    \author[LAP]{Alkiviadis Bais%
+  %
+  }
+   \ead{abais@auth.gr} 
+    \author[LAP]{Charikleia Meleti%
+  %
+  \fnref{2}}
+   \ead{meleti@auth.gr} 
+      \affiliation[LAP]{
+    organization={Laboratory of Atmospheric Physics,
+A.U.Th.},addressline={1 main
+street},city={Thessaloniki},postcode={123456},country={Greece},}
+    \affiliation[Another University]{
+    organization={Department},addressline={A street
+29},city={Manchester,},postcode={2054 NX},state={State},country={The
+Netherlands},}
+    \cortext[cor1]{Corresponding author}
+    \fntext[1]{This is the first author footnote.}
+    \fntext[2]{Another author footnote.}
 
-\begin{document}
-\maketitle
   \begin{abstract}
@@
   \end{abstract}
+    \begin{keyword}
+    keyword1 \sep 
+    keyword2
+  \end{keyword}
 
-{
-\setcounter{tocdepth}{4}
-\tableofcontents
-}
+ \end{frontmatter}
+
 \hypertarget{abstract}{%
@@
 
-ECE: extreme cloud enhancement cases one minute over TSI on horizontal plane
+ECE: extreme cloud enhancement cases one minute over TSI on horizontal
+plane
 
@@
 
-\(\text{GHI}_\text{i}\): measured one minute global horizontal irradiance
+\(\text{GHI}_\text{i}\): measured one minute global horizontal
+irradiance
 
-\(\text{GHI}_\text{CSm}\): modeled clear sky one minute global horizontal irradiance
+\(\text{GHI}_\text{CSm}\): modeled clear sky one minute global
+horizontal irradiance
 
@@
 
-The shortwave solar irradiance, reaching Earth's surface, is the main energy source
-of the atmosphere and biosphere and drives and governs the climate (Gray et al. 2010). It
-has direct practical application, in different industries, like energy production and
-agriculture method. The variability of its intensity, can cause difficulties in
-predicting the yield, and designing the specifications of the appropriate equipment.
-A lot of research has been focused on predicting the renewable energy production in a
-fine timescale and in near real-time (for a review see Inman, Pedro, and Coimbra (2013); Graabak and Korpås (2016)).
+The shortwave solar irradiance, reaching Earth's surface, is the main
+energy source of the atmosphere and biosphere and drives and governs the
+climate \citep{Gray2010}. It has direct practical application, in
+different industries, like energy production and agriculture method. The
+variability of its intensity, can cause difficulties in predicting the
+yield, and designing the specifications of the appropriate equipment. A
+lot of research has been focused on predicting the renewable energy
+production in a fine timescale and in near real-time (for a review see
+\citet{Inman2013}; \citet{Graabak2016}).
 
-A big aspect of this variability is the interaction with the clouds. In general,
-clouds absorb part of the solar irradiance, but under certain conditions, can enhance
-the total shortwave irradiance reaching the ground. This effect, can locally increase
-the observed total shortwave irradiance higher than the expected clear sky irradiance
-{[}see references therein{]}.
+A big aspect of this variability is the interaction with the clouds. In
+general, clouds absorb part of the solar irradiance, but under certain
+conditions, can enhance the total shortwave irradiance reaching the
+ground. This effect, can locally increase the observed total shortwave
+irradiance higher than the expected clear sky irradiance {[}see
+references therein{]}.
 
-Some of the proposed underling mechanisms of those events, have been summarized by
-Gueymard (2017), and include scattering on the edge of cumulus clouds or through thin
-cirrus. Further investigation with radiation transfer modeling methods and
-observations have pointed as the prevailing mechanism, the forward Mie scattering
-(Pecenak et al. 2016; Thuillier et al. 2013; G. H. Yordanov et al. 2013; Georgi Hristov Yordanov, Saetre, and Midtgård 2015), through the clouds.
-The overall phenomenon depends on different interactive factors, that include cloud
-thickness, constitution and type; and the relative position of the sun, the clouds,
-and the observer (Gueymard 2017; Veerman, Van Stratum, and Van Heerwaarden 2022). As such, there are multiple
-contributing mechanism that are responsible for the observed irradiance enhancements.
+Some of the proposed underling mechanisms of those events, have been
+summarized by \citet{Gueymard2017}, and include scattering on the edge
+of cumulus clouds or through thin cirrus. Further investigation with
+radiation transfer modeling methods and observations have pointed as the
+prevailing mechanism, the forward Mie scattering
+\citep{Pecenak2016, Thuillier2013, Yordanov2013, Yordanov2015}, through
+the clouds. The overall phenomenon depends on different interactive
+factors, that include cloud thickness, constitution and type; and the
+relative position of the sun, the clouds, and the observer
+\citep{Gueymard2017, Veerman2022}. As such, there are multiple
+contributing mechanism that are responsible for the observed irradiance
+enhancements.
 
-Cloud enhancements have been reported, to be able to exceed in intensity even the
-value of the solar constant, resulting of clear indexes above unit. A summary of
-extreme enchantment cases have been compiled by Martins, Mantelli, and Rüther (2022). There are also some
-practical implication of the cloud enchantments. The intensity and duration of
-enhancements can effect the efficiency and stability of photovoltaic power production
-(Lappalainen and Kleissl 2020; Järvelä and Valkealahti 2020), and extreme enhancements cases, have the
-potential to compromise the integrity of photovoltaic plants infrastructure
-(Do Nascimento et al. 2019). It has also been demonstrated, that these events can interfere
-in the comparison of ground data and satellite observations (Damiani et al. 2018)
+Cloud enhancements have been reported, to be able to exceed in intensity
+even the value of the solar constant, resulting of clear indexes above
+unit. A summary of extreme enchantment cases have been compiled by
+\citet{Martins2022}. There are also some practical implication of the
+cloud enchantments. The intensity and duration of enhancements can
+effect the efficiency and stability of photovoltaic power production
+\citep{Lappalainen2020, Jaervelae2020}, and extreme enhancements cases,
+have the potential to compromise the integrity of photovoltaic plants
+infrastructure \citep{DoNascimento2019}. It has also been demonstrated,
+that these events can interfere in the comparison of ground data and
+satellite observations \citep{Damiani2018}
 
-Methods of identification cloud enchantment events in the literature, usually include
-the use of a simulated clear sky radiation as baseline, that is combined with an
-appropriate threshold or some other statistical characteristics, and in some cases,
-with visual methods with a sky cam (Vamvakas, Salamalikis, and Kazantzidis 2020; Mol, Knap, and Van Heerwaarden 2023 and references therein).
+Methods of identification cloud enchantment events in the literature,
+usually include the use of a simulated clear sky radiation as baseline,
+that is combined with an appropriate threshold or some other statistical
+characteristics, and in some cases, with visual methods with a sky cam
+\citep[ and references therein]{Vamvakas2020, Mol2023}.
 
-In this study, we evaluated the effects cloud enhancements on the total downward
-radiation by studding the occurrences, their intensity, and their duration in a
-thirty-year period at the city of Thessaloniki. We used modeled clear sky
-irradiance, as a baseline to identify cloud enhancements. We were able to determine
-some trends of the phenomenon, it's Climatology, and some of their general
-characteristics. We weren't able to find a comparable study that provides trends for
-similar long term dataset, as ours. The recording of the radiation signal is the
-mean of one-minute. Thus, the minimum resolution of cloud enhancement events (CE), in
-this study is one minute.
+In this study, we evaluated the effects cloud enhancements on the total
+downward radiation by studding the occurrences, their intensity, and
+their duration in a thirty-year period at the city of Thessaloniki. We
+used modeled clear sky irradiance, as a baseline to identify cloud
+enhancements. We were able to determine some trends of the phenomenon,
+it's Climatology, and some of their general characteristics. We weren't
+able to find a comparable study that provides trends for similar long
+term dataset, as ours. The recording of the radiation signal is the mean
+of one-minute. Thus, the minimum resolution of cloud enhancement events
+(CE), in this study is one minute.
 
-In the relative bibliography different definition have been used for these events,
-some of the are summarized by Gueymard (2017). Here, we defined as cloud enhancement
-events (CE) the cases when the measured global horizontal irradiance (GHI) at ground
-level, exceeds the expected value under clear-sky conditions. Similar, we define as
-extreme cloud enhancement events (ECE), the cases when GHI, exceeds the Total Solar
-Irradiance on horizontal plane at ground level. Although the duration of these
-bursts varies, from instantaneous to several minutes, here we are constrained by the
-recorded data, to one-minute steps.
+In the relative bibliography different definition have been used for
+these events, some of the are summarized by \citet{Gueymard2017}. Here,
+we defined as cloud enhancement events (CE) the cases when the measured
+global horizontal irradiance (GHI) at ground level, exceeds the expected
+value under clear-sky conditions. Similar, we define as extreme cloud
+enhancement events (ECE), the cases when GHI, exceeds the Total Solar
+Irradiance on horizontal plane at ground level. Although the duration of
+these bursts varies, from instantaneous to several minutes, here we are
+constrained by the recorded data, to one-minute steps.
 
@@
 
-The monitoring site is operating in the Laboratory of Atmospheric Physics of the
-Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
-\(22^\circ\,57'\,\)E, \(80\,\)m~a.s.l.).
-In this study we present data from the period
-13~April 1993 to
-31~December 2023.
-The GHI data were measured with a Kipp~\& Zonen CM-21 pyranometer. During the study
-period, the pyranometer was independently calibrated three times at the
-Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of the
-instrument's sensitivity was better than \(0.7\,\%\) relative to the initial
-calibration by the manufacturer.
-For the acquisition of radiometric data, the signal of the pyranometer was sampled at
-a rate of \(1\,\text{Hz}\). The mean and the standard deviation of these samples were
-calculated and recorded for every minute. The measurements were corrected for the
-zero offset (``dark signal'' in volts), which was calculated by averaging all
-measurements recorded for a period of \(3\,\text{h}\), before (morning) or after
-(evening) the Sun reaches an elevation angle of \(-10^\circ\). The signal was
-converted to irradiance using the ramped value of the instrument's sensitivity
-between subsequent calibrations.
+The monitoring site is operating in the Laboratory of Atmospheric
+Physics of the Aristotle University of Thessaloniki
+(\(40^\circ\,38'\,\)N, \(22^\circ\,57'\,\)E, \(80\,\)m~a.s.l.). In this
+study we present data from the period 13~April 1993 to 31~December 2023.
+The GHI data were measured with a Kipp~\& Zonen CM-21 pyranometer.
+During the study period, the pyranometer was independently calibrated
+three times at the Meteorologisches Observatorium Lindenberg, DWD,
+verifying that the stability of the instrument's sensitivity was better
+than \(0.7\,\%\) relative to the initial calibration by the
+manufacturer. For the acquisition of radiometric data, the signal of the
+pyranometer was sampled at a rate of \(1\,\text{Hz}\). The mean and the
+standard deviation of these samples were calculated and recorded for
+every minute. The measurements were corrected for the zero offset
+(``dark signal'' in volts), which was calculated by averaging all
+measurements recorded for a period of \(3\,\text{h}\), before (morning)
+or after (evening) the Sun reaches an elevation angle of \(-10^\circ\).
+The signal was converted to irradiance using the ramped value of the
+instrument's sensitivity between subsequent calibrations.
 
-To further improve the quality of the irradiance data, a manual screening was
-performed to remove inconsistent and erroneous recordings that can occur
-stochastically or systematically during the continuous operation of the instruments.
-The manual screening was aided by a radiation data quality assurance procedure,
-adjusted for the site, which was based on the methods of Long and Shi~(Long and Shi 2006, 2008). Thus, problematic recordings have been excluded from further
-processing. Although it is impossible to detect all false data, the large number of
-available data, and the aggregation scheme we used, ensures the quality of the
-radiation measurements used in this study.
-To preserve an unbiased representation of the data we applied a constraint, similar
-the one used by Castillejo-Cuberos and Escobar (2020). Where, for each valid hour of day, there must
-exist at least 45 minutes of valid measurements, including nighttime near sunrise and
-sunset. Days with less than 5 valid hours are rejected completely.
-Furthermore, due to the significant measurement uncertainty when the Sun is near the
-horizon, and due to some systematic obstructions by nearby buildings, we have
-excluded all measurements with solar zenith angle (SZA) greater than
-\(78^\circ\).
+To further improve the quality of the irradiance data, a manual
+screening was performed to remove inconsistent and erroneous recordings
+that can occur stochastically or systematically during the continuous
+operation of the instruments. The manual screening was aided by a
+radiation data quality assurance procedure, adjusted for the site, which
+was based on the methods of Long and Shi~\citep{Long2006, Long2008a}.
+Thus, problematic recordings have been excluded from further processing.
+Although it is impossible to detect all false data, the large number of
+available data, and the aggregation scheme we used, ensures the quality
+of the radiation measurements used in this study. To preserve an
+unbiased representation of the data we applied a constraint, similar the
+one used by \citet{CastillejoCuberos2020}. Where, for each valid hour of
+day, there must exist at least 45 minutes of valid measurements,
+including nighttime near sunrise and sunset. Days with less than 5 valid
+hours are rejected completely. Furthermore, due to the significant
+measurement uncertainty when the Sun is near the horizon, and due to
+some systematic obstructions by nearby buildings, we have excluded all
+measurements with solar zenith angle (SZA) greater than \(78^\circ\).
 
 \hypertarget{cloud-enhancement-detection}{%
-\subsection{Cloud enhancement detection}\label{cloud-enhancement-detection}}
+\subsection{Cloud enhancement
+detection}\label{cloud-enhancement-detection}}
 
-To be able to detect the CE cases, we had to establish a baseline, above which we can
-characterize each data point as an enhancement event, by estimating the occurring
-over irradiance (OIR). The OIR, here is defined as the irradiance difference of the
-measured one-minute \(\text{GHI}_i\) from the CE identification criterion in
+To be able to detect the CE cases, we had to establish a baseline, above
+which we can characterize each data point as an enhancement event, by
+estimating the occurring over irradiance (OIR). The OIR, here is defined
+as the irradiance difference of the measured one-minute \(\text{GHI}_i\)
+from the CE identification criterion in
 Equation\nobreakspace\ref{eq:CE4}
-(\(\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}\)).
-To have an estimation, and a first insight on the phenomenon, we experimented with two
-simple approaches for the reference. The Haurwitz's model (Haurwitz 1945), which is
-as simple clear sky model, and we had already adjusted and had good fit with our data
-(Natsis, Bais, and Meleti 2023), and the TSI at the top of the atmosphere. We have tested both cases
-by using an appropriate relative threshold and/or an additional constant offset. The
-initial results, showed that we can detect a big portion of the CE events. These
-results were helpful, and helped to establish some criteria to further improve the CE
-identification. It was evident, by inspecting the daily plot of irradiance, that
-changes on the atmospheric conditions introduced numerous false positive and false
-negative results. To produce a more accurate reference, we had to take into account
-more factors that effect the clear sky radiation. So we used a radiation transfer
-model.
+(\(\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}\)). To have an
+estimation, and a first insight on the phenomenon, we experimented with
+two simple approaches for the reference. The Haurwitz's model
+\citep{Haurwitz1945}, which is as simple clear sky model, and we had
+already adjusted and had good fit with our data \citep{Natsis2023}, and
+the TSI at the top of the atmosphere. We have tested both cases by using
+an appropriate relative threshold and/or an additional constant offset.
+The initial results, showed that we can detect a big portion of the CE
+events. These results were helpful, and helped to establish some
+criteria to further improve the CE identification. It was evident, by
+inspecting the daily plot of irradiance, that changes on the atmospheric
+conditions introduced numerous false positive and false negative
+results. To produce a more accurate reference, we had to take into
+account more factors that effect the clear sky radiation. So we used a
+radiation transfer model.
 
 \hypertarget{modeled-clear-sky-irradiance}{%
-\subsection{Modeled clear Sky Irradiance}\label{modeled-clear-sky-irradiance}}
+\subsection{Modeled clear Sky
+Irradiance}\label{modeled-clear-sky-irradiance}}
 
-We approximated the expected clear sky GHI by using a radiation transfer model. The
-simulations was performed by the well established model Libradtran (Emde et al. 2016), a
-similar approach, was also used by Vamvakas, Salamalikis, and Kazantzidis (2020) for creating a clear sky reference.
-Because of the lack of observational data for the whole period, we used some long
-term climatological data for the main factors responsible for the attenuation of the
-broadband downward solar radiation in the atmosphere. Which are mainly, the aerosols
-and the water vapors. Fortunately, our site participates in the Aerosol Robotic
-Network (AERONET) (Giles et al. 2019; Buis et al. 1998), as we operate a Cimel photometer since
-2003, collocated with the CM-21 pyranometer. The mean monthly aerosol optical depth
-(AOD) on different wavelengths is provided by AERONET, along with the equivalent
-water column height in the atmosphere.
+We approximated the expected clear sky GHI by using a radiation transfer
+model. The simulations was performed by the well established model
+Libradtran \citep{Emde2016}, a similar approach, was also used by
+\citet{Vamvakas2020} for creating a clear sky reference. Because of the
+lack of observational data for the whole period, we used some long term
+climatological data for the main factors responsible for the attenuation
+of the broadband downward solar radiation in the atmosphere. Which are
+mainly, the aerosols and the water vapors. Fortunately, our site
+participates in the Aerosol Robotic Network (AERONET)
+\citep{Giles2019, Buis1998}, as we operate a Cimel photometer since
+2003, collocated with the CM-21 pyranometer. The mean monthly aerosol
+optical depth (AOD) on different wavelengths is provided by AERONET,
+along with the equivalent water column height in the atmosphere.
 
-For completeness, we will describe here the main points of the radiation simulation
-procedure. We used as input the spectrum of Kurucz (1994) in the range \(280\) to
-\(2500\,\text{nm}\), with the Libradtran radiation transfer solver ``disort'' on a
-``pseudospherical'' geometry and the ``LOWTRAN'' gas parameterization. For each
-combination of conditions we use a SZA step of \(0.2^\circ\).
-For the atmospheric characteristics, we iterated for combinations of AOD at
-\(500\,\text{nm}\) (\(\tau_{500\text{nm}}\)) with additional offsets of \(\pm1\) and
-\(\pm2\sigma\), and water column (\(wc\)), also with offsets of \(\pm1\) and \(\pm2\sigma\).
-We applied them on two atmospheric profiles, from the Air Force Geophysics
-Laboratory (AFGL). The ``AFGL atmospheric constituent profile, midlatitude summer''
-(afglms) and the ``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw)
-(Anderson et al. 1986).
+For completeness, we will describe here the main points of the radiation
+simulation procedure. We used as input the spectrum of
+\citet{Kurucz1994} in the range \(280\) to \(2500\,\text{nm}\), with the
+Libradtran radiation transfer solver ``disort'' on a ``pseudospherical''
+geometry and the ``LOWTRAN'' gas parameterization. For each combination
+of conditions we use a SZA step of \(0.2^\circ\). For the atmospheric
+characteristics, we iterated for combinations of AOD at
+\(500\,\text{nm}\) (\(\tau_{500\text{nm}}\)) with additional offsets of
+\(\pm1\) and \(\pm2\sigma\), and water column (\(wc\)), also with
+offsets of \(\pm1\) and \(\pm2\sigma\). We applied them on two
+atmospheric profiles, from the Air Force Geophysics Laboratory (AFGL).
+The ``AFGL atmospheric constituent profile, midlatitude summer''
+(afglms) and the ``AFGL atmospheric constituent profile, midlatitude
+winter'' (afglmw) \citep{Anderson1986}.
 
-To create a look-up table that aligns with our dataset, we applied some adjustments.
-To account for the Sun's variability, in our one-minute GHI measurements,
-we adapted each modeled value by scaling the\\
-model's input spectrum integral, to the corresponding total solar irradiance (TSI)
-provided by NOAA (Coddington et al. 2005).\\
-Also, we applied the effect of the Earth -- Sun
-distance on the irradiance, by using the distance calculated by the Astropy
-(Astropy Collaboration et al. 2022) software library. As needed, we interpolate the resulting
-irradiances to the exact SZA of our measurements. For each period of the year, we
-used the appropriate atmospheric profile (afglms or afglmw). Finally, we calculated
-the clear sky irradiance value at the horizontal plane. Thus, we were able to
-emulate different atmospheric condition and levels of atmospheric clearness for the
-climatological conditions of the site. With this method, the modeled clear sky
-irradiances can be directly compared to each measured one-minute value of GHI, for
-different conditions of atmospheric clearness.
+To create a look-up table that aligns with our dataset, we applied some
+adjustments. To account for the Sun's variability, in our one-minute GHI
+measurements, we adapted each modeled value by scaling the\\
+model's input spectrum integral, to the corresponding total solar
+irradiance (TSI) provided by NOAA \citep{Coddington2005}.\\
+Also, we applied the effect of the Earth -- Sun distance on the
+irradiance, by using the distance calculated by the Astropy
+\citep{AstropyCollaboration2022} software library. As needed, we
+interpolate the resulting irradiances to the exact SZA of our
+measurements. For each period of the year, we used the appropriate
+atmospheric profile (afglms or afglmw). Finally, we calculated the clear
+sky irradiance value at the horizontal plane. Thus, we were able to
+emulate different atmospheric condition and levels of atmospheric
+clearness for the climatological conditions of the site. With this
+method, the modeled clear sky irradiances can be directly compared to
+each measured one-minute value of GHI, for different conditions of
+atmospheric clearness.
 
@@
 
-The use of the actual modeled values of clear sky GHI alone, can not provide us with
-a robust method to distinguish the CE cases, due to the limited accuracy of the input
-data. Our main focus was to positively identify over irradiance events from CEs, thus
-we used a relative factor, to create an upper envelope of the clear sky irradiance,
-above which, any GHI value can safely attributed to CE. We evaluated the performance
-of the modeled clear radiation for each of atmospheric level of clearness, as
-reference, in order to conclude which is the most appropriate.
+The use of the actual modeled values of clear sky GHI alone, can not
+provide us with a robust method to distinguish the CE cases, due to the
+limited accuracy of the input data. Our main focus was to positively
+identify over irradiance events from CEs, thus we used a relative
+factor, to create an upper envelope of the clear sky irradiance, above
+which, any GHI value can safely attributed to CE. We evaluated the
+performance of the modeled clear radiation for each of atmospheric level
+of clearness, as reference, in order to conclude which is the most
+appropriate.
 
-To select the exact values of these thresholds factors (Equation \ref{eq:CE4}), we
-implemented an empirical method, by manual inspection of the CE identification, on
-specially selected days from the whole dataset. We used seven sets of selected days,
-with characteristics relevant to the efficiency of the identification threshold.
-These sets were random groups of about 20 to 30 days with the following
-characteristics:
-(a) the largest over irradiance CE events,
-(b) the largest daily total over irradiance,
-(c) without clouds (by implementing a clear sky identification algorithm as discussed in Natsis, Bais, and Meleti (2023)),
-(d) without clouds and without EC events,
-(e) with at least \(60\,\%\) of the day length without clouds and some EC events,
-(h) random days and
-(i) some manual selected days that were included during the manual inspection.
-Where it was needed, for some of the edge cases, we also used images from a sky-cam,
-to further aid the decisions of the manual inspection.
+To select the exact values of these thresholds factors (Equation
+\ref{eq:CE4}), we implemented an empirical method, by manual inspection
+of the CE identification, on specially selected days from the whole
+dataset. We used seven sets of selected days, with characteristics
+relevant to the efficiency of the identification threshold. These sets
+were random groups of about 20 to 30 days with the following
+characteristics: (a) the largest over irradiance CE events, (b) the
+largest daily total over irradiance, (c) without clouds (by implementing
+a clear sky identification algorithm as discussed in
+\citet{Natsis2023}), (d) without clouds and without EC events, (e) with
+at least \(60\,\%\) of the day length without clouds and some EC events,
+(h) random days and (i) some manual selected days that were included
+during the manual inspection. Where it was needed, for some of the edge
+cases, we also used images from a sky-cam, to further aid the decisions
+of the manual inspection.
 
-After evaluating the modeled clear radiation for the different atmospheric
-conditions, in relation to the measured GHI data, we choose as a representative of
-the clear sky radiation, the case where
-\(\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\)
-(\(\text{GHI}_\text{CSm}\)).
-These values represent a typical atmosphere in Thessaloniki with low load of aerosols
-and humidity, which are the main factor that attenuate the GHI, excluding clouds. To
-create the limit of CE identification, we created a two branched threshold, as a
-function of SZA. A constant factor for low SZAs, and a higher ramped factor for
-higher SZAs (Equation\nobreakspace\ref{eq:CE4}).
-This is the criterion of our CE identification.
-\begin{equation}
+After evaluating the modeled clear radiation for the different
+atmospheric conditions, in relation to the measured GHI data, we choose
+as a representative of the clear sky radiation, the case where
+\(\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma\) and
+\(w_{h\text{cs}} = w_h - 1\sigma\) (\(\text{GHI}_\text{CSm}\)). These
+values represent a typical atmosphere in Thessaloniki with low load of
+aerosols and humidity, which are the main factor that attenuate the GHI,
+excluding clouds. To create the limit of CE identification, we created a
+two branched threshold, as a function of SZA. A constant factor for low
+SZAs, and a higher ramped factor for higher SZAs
+(Equation\nobreakspace\ref{eq:CE4}). This is the criterion of our CE
+identification. \begin{equation}
 \text{CE} : \text{E}_\text{i} > \text{E}_\text{CSlim,i}, \text{where} \begin{cases}
@@
 \end{cases}\label{eq:CE4}
-\end{equation}
-where: \(\theta\) is the solar zenith angle, \(\text{E}\) the measured
-irradiance, \(\text{E}_\text{CSm}\) the selected modeled clear sky irradiance, and \(i\) each of the one-minute observation.
+\end{equation} where: \(\theta\) is the solar zenith angle, \(\text{E}\)
+the measured irradiance, \(\text{E}_\text{CSm}\) the selected modeled
+clear sky irradiance, and \(i\) each of the one-minute observation.
 
-We have to note, that the differentiation of the threshold factor was needed, because
-of the high irradiance values we observed, early in the morning and late in the
-afternoon. We have confirmed, by inspecting images from the sky cam, that we have
-duration of elevated irradiance, either due to the clearness of the atmosphere, or some
-interferences by reflections on nearby bright surfaces. Although, these cases may
-mask some of the CE events. The actual CE events, produce higher irradiance and thus
-are identified as such. As a side effect, the reported OIR will be slight
-underestimated for those SZAs, but the overall contribution of those cases to the
-total daily energy, is minimal due the low occurrences and the lower irradiances.
+We have to note, that the differentiation of the threshold factor was
+needed, because of the high irradiance values we observed, early in the
+morning and late in the afternoon. We have confirmed, by inspecting
+images from the sky cam, that we have duration of elevated irradiance,
+either due to the clearness of the atmosphere, or some interferences by
+reflections on nearby bright surfaces. Although, these cases may mask
+some of the CE events. The actual CE events, produce higher irradiance
+and thus are identified as such. As a side effect, the reported OIR will
+be slight underestimated for those SZAs, but the overall contribution of
+those cases to the total daily energy, is minimal due the low
+occurrences and the lower irradiances.
 
@@
 
-These selections have some subjectivity, as the definition of clear sky, is depended
-on the intended usage. Our main focus is to be able to identify the OIR created by the
-clouds. Although, the aerosols and water vapor are always present and can not be
-completely removed.
-The effect of the different clearness levels
+These selections have some subjectivity, as the definition of clear sky,
+is depended on the intended usage. Our main focus is to be able to
+identify the OIR created by the clouds. Although, the aerosols and water
+vapor are always present and can not be completely removed. The effect
+of the different clearness levels
 
@@
 
-Another aspect of the CE events, that is often reported in the relative bibliography,
-are cases of extreme cloud enhancement (ECE). These are cases of CE where the
-measured intensity of the irradiance, exceeds the equivalent TSI on the top of the
-atmosphere, and satisfy the Equation\nobreakspace{}\ref{eq:ECE}.
-\begin{equation}
+Another aspect of the CE events, that is often reported in the relative
+bibliography, are cases of extreme cloud enhancement (ECE). These are
+cases of CE where the measured intensity of the irradiance, exceeds the
+equivalent TSI on the top of the atmosphere, and satisfy the
+Equation\nobreakspace{}\ref{eq:ECE}. \begin{equation}
 \text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
 \label{eq:ECE}
-\end{equation}
-where: \(\theta\) the solar zenith angle, \(E_{\odot}\) the solar constant, \(r\) the Sun -- Earth distance, and \(i\) each of the one-minute observation.
+\end{equation} where: \(\theta\) the solar zenith angle, \(E_{\odot}\)
+the solar constant, \(r\) the Sun -- Earth distance, and \(i\) each of
+the one-minute observation.
 
@@
 \item
-  Include Example of days plot in the Appendix!
-  \ldots{} this is clearer to understand and describe \ldots.
+  Include Example of days plot in the Appendix! \ldots{} this is clearer
+  to understand and describe \ldots.
 \end{itemize}
@@
 
-Our dataset, after the data selection processing, consists of
-6144534 records of GHI, of which
-\(1.799\,\%\) are CE and
-\(0.036\,\%\) are ECE events.
-The highest GHI recorder was
-\(1416.6\,W/m^2\)
-on 24~May 2007.
-The absolute stronger CE event had an OIR of
-\(341.79\,W/m^2\) on
-15~May 2014.
-The relative stronger CE event was
-\(54\,\%\) above the
-clear sky threshold, on
-28~October 2016.
+Our dataset, after the data selection processing, consists of 6144534
+records of GHI, of which \(1.799\,\%\) are CE and \(0.036\,\%\) are ECE
+events. The highest GHI recorder was \(1416.6\,W/m^2\) on 24~May 2007.
+The absolute stronger CE event had an OIR of \(341.79\,W/m^2\) on 15~May
+2014. The relative stronger CE event was \(54\,\%\) above the clear sky
+threshold, on 28~October 2016.
 
@@
 We computed the daily trend of the mean OIR of CE
-(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order autoregressive
-model with lag of 1 day, using the `maximum likelihood' fitting method (Gardner, Harvey, and Phillips 1980; Jones 1980) by implementing the function `arima' from the library `stats' of the R
-programming language (R Core Team 2023). The trends are reported together with the \(2\sigma\)
-error. We observe an increase of
-\(0.216\pm 0.083\,W/m^2/y\)
-on the mean OIR.
+(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order
+autoregressive model with lag of 1 day, using the `maximum likelihood'
+fitting method \citep{Gardner1980, Jones1980} by implementing the
+function `arima' from the library `stats' of the R programming language
+\citep{RCT2023}. The trends are reported together with the \(2\sigma\)
+error. We observe an increase of \(0.216\pm 0.083\,W/m^2/y\) on the mean
+OIR.
 
@@
 
-Although, the previous result is closer to the raw data, we preferred to present the
-annual statistics, that give a more clear picture about the long term CE trends.
-Hence, we calculated the annual values from the one-minute measurements. The trend of
-OIR is
-\(0.23\pm 0.11\,W/m^2/y\)
-(Figure\nobreakspace{}\ref{fig:P-energy-mean}),
-but this value alone is not very useful due the intrinsic high variability of this
-metric.
+Although, the previous result is closer to the raw data, we preferred to
+present the annual statistics, that give a more clear picture about the
+long term CE trends. Hence, we calculated the annual values from the
+one-minute measurements. The trend of OIR is \(0.23\pm 0.11\,W/m^2/y\)
+(Figure\nobreakspace{}\ref{fig:P-energy-mean}), but this value alone is
+not very useful due the intrinsic high variability of this metric.
 
@@
 
-A better indicator of changes on the characteristic of CE would be the number of CE
-occurrences and the total energy of the CE over irradiance. The annual number of CE
-occurrences, shows a steady increase of
+A better indicator of changes on the characteristic of CE would be the
+number of CE occurrences and the total energy of the CE over irradiance.
+The annual number of CE occurrences, shows a steady increase of
 \(122.2\pm 22.8\,\text{cases}/y\)
-(Figure\nobreakspace{}\ref{fig:P-energy-N}).
-We have to note that the energy related to the CE events can not be directly linked
-with the total energy balance on the atmosphere. The net sun radiation of the region
-is not increased, but rather redistributed through the CE. Although, the
-instantaneous values, can exceed the equivalent clear sky irradiance to a
-considerable level.
+(Figure\nobreakspace{}\ref{fig:P-energy-N}). We have to note that the
+energy related to the CE events can not be directly linked with the
+total energy balance on the atmosphere. The net sun radiation of the
+region is not increased, but rather redistributed through the CE.
+Although, the instantaneous values, can exceed the equivalent clear sky
+irradiance to a considerable level.
 
@@
 Subsequently, the mean annual increase of energy due to CE events is
-\(341.6\pm 73.1\,kJ/y\)
-(Figure~\ref{fig:P-energy-sum}), witch follows the trend of the number of
-occurrences.
+\(341.6\pm 73.1\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
+the trend of the number of occurrences.
 
@@
 Another interesting aspect of the CE cases, is their seasonal cycle. In
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the box plot
-(whisker plot), where the values have been normalized by the highest median value,
-that occurs in May. Although the number of occurrences has a wide spread throughout
-the study period, the most active period of CE occurrences is during May and June.
-During the Winter (December -- February) the CE cases are about \(25\,\%\) of the maximum.
-The rest of the months the occurrences ramp between the maximum and minimum.
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the
+box plot (whisker plot), where the values have been normalized by the
+highest median value, that occurs in May. Although the number of
+occurrences has a wide spread throughout the study period, the most
+active period of CE occurrences is during May and June. During the
+Winter (December -- February) the CE cases are about \(25\,\%\) of the
+maximum. The rest of the months the occurrences ramp between the maximum
+and minimum.
 
@@
 The distribution of the CE over irradiance spreads uniformly
-Figure\nobreakspace{}\ref{fig:ovir-distribution}. Where there is an inverse relation
-between the events frequency and events intensity. This is expected as, the stronger
-the CE events become, the rarer the particular atmospheric and sun conditions
-occur.
+Figure\nobreakspace{}\ref{fig:ovir-distribution}. Where there is an
+inverse relation between the events frequency and events intensity. This
+is expected as, the stronger the CE events become, the rarer the
+particular atmospheric and sun conditions occur.
 
@@
 
-In order to further study the characteristics of the CE events, we grouped the single
-minute CE events, to continuous CE groups (CEG). Thus, a CEG consists of one or more
-successive CE cases, and can have a duration of multiple of minutes. We have
-identified 29009 groups, where the group with the longest duration lasted
-140 minutes on
-07~July 2013.
+In order to further study the characteristics of the CE events, we
+grouped the single minute CE events, to continuous CE groups (CEG).
+Thus, a CEG consists of one or more successive CE cases, and can have a
+duration of multiple of minutes. We have identified 29009 groups, where
+the group with the longest duration lasted 140 minutes on 07~July 2013.
 By examining the frequency distribution of the CEG durations
-(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can conclude that
-longer durations are getting increasingly rare, with durations above 10 minutes very
-rare.
+(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can
+conclude that longer durations are getting increasingly rare, with
+durations above 10 minutes very rare.
 
@@
 
-\ldots{} (\textbf{Zhang2018?}) \ldots.
+\ldots{} \citet{Zhang2018} \ldots.
 
@@
 
-Another aspect of the CE events are the cases when the irradiance is above the
-expected irradiance on top of the atmosphere, we have defined this as ECE
-(Equation\nobreakspace{}\ref{eq:ECE}).
+Another aspect of the CE events are the cases when the irradiance is
+above the expected irradiance on top of the atmosphere, we have defined
+this as ECE (Equation\nobreakspace{}\ref{eq:ECE}).
 
@@
 \item
-  max value ECE
-  relative to other works max values
+  max value ECE relative to other works max values
 \end{itemize}
 
-Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies} we have
-computed the distribution of the number of occurrences of ECE events by month in
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the most active
-period is in the spring (March -- May), followed by the months of June, September and
-October.
+Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies}
+we have computed the distribution of the number of occurrences of ECE
+events by month in
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the
+most active period is in the spring (March -- May), followed by the
+months of June, September and October.
 
@@
 
-Compare to other location stats.
-max, ECE, distributions \ldots.
+Compare to other location stats. max, ECE, distributions \ldots.
 
@@
 
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Anderson1986}{}}%
-Anderson, G.
-P., J.
-H.
-Chetwynd, S.
-A.
-Clough, E.
-P.
-Shettle, and F.
-X.
-Kneizys.
-1986.
-{``{AFGL} Atmospheric Constituent Profiles (0-120km).''} Air Force Geophysics Laboratory, Optical Physics Division.
-
-\leavevmode\vadjust pre{\hypertarget{ref-AstropyCollaboration2022}{}}%
-Astropy Collaboration, Adrian M.
-Price-Whelan, Pey Lian Lim, Nicholas Earl, Nathaniel Starkman, Larry Bradley, David L.
-Shupe, et al.
-2022.
-{``{The Astropy Project: Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package}.''} \emph{Astrophysical Journal} 935 (2): 167.
-\url{https://doi.org/10.3847/1538-4357/ac7c74}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Buis1998}{}}%
-Buis, J.
-P.
-P., A.
-Setzer, B.
-N.
-N.
-Holben, T.
-F.
-F.
-Eck, I.
-Slutsker, D.
-Tanre, E.
-Vermote, et al.
-1998.
-{``AERONET---a Federated Instrument Network and Data Archive for Aerosol Characterization.''} \emph{Remote Sensing of Environment} 66 (1): 1--16.
-
-\leavevmode\vadjust pre{\hypertarget{ref-CastillejoCuberos2020}{}}%
-Castillejo-Cuberos, Armando, and Rodrigo Escobar.
-2020.
-{``Detection and Characterization of Cloud Enhancement Events for Solar Irradiance Using a Model-Independent, Statistically-Driven Approach.''} \emph{Solar Energy} 209 (October): 547--67.
-\url{https://doi.org/10.1016/j.solener.2020.09.046}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Coddington2005}{}}%
-Coddington, Odele, Judith L.
-Lean, Doug Lindholm, Peter Pilewskie, Martin Snow, and NOAA CDR Program.
-2005.
-{``{NOAA} Climate Data Record ({CDR}) of Total Solar Irradiance ({TSI}), {NRLTSI} Version 2.
-{D}aily.''} \url{https://doi.org/10.7289/V55B00C1}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Damiani2018}{}}%
-Damiani, Alessandro, Hitoshi Irie, Takashi Horio, Tamio Takamura, Pradeep Khatri, Hideaki Takenaka, Takashi Nagao, Takashi Y.
-Nakajima, and Raul R.
-Cordero.
-2018.
-{``Evaluation of Himawari-8 Surface Downwelling Solar Radiation by Ground-Based Measurements.''} \emph{Atmos.
-Meas.
-Tech.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-DoNascimento2019}{}}%
-Do Nascimento, Lucas Rafael, Trajano De Souza Viana, Rafael Antunes Campos, and Ricardo Rüther.
-2019.
-{``Extreme Solar Overirradiance Events: Occurrence and Impacts on Utility-Scale Photovoltaic Power Plants in Brazil.''} \emph{Solar Energy} 186 (July): 370--81.
-\url{https://doi.org/10.1016/j.solener.2019.05.008}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Emde2016}{}}%
-Emde, Claudia, Robert Buras-Schnell, Arve Kylling, Bernhard Mayer, Josef Gasteiger, Ulrich Hamann, Jonas Kylling, et al.
-2016.
-{``The {libRadtran} Software Package for Radiative Transfer Calculations (Version 2.0.1).''} \emph{Geoscientific Model Development} 9 (5): 1647--72.
-\url{https://doi.org/10.5194/gmd-9-1647-2016}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gardner1980}{}}%
-Gardner, G., A.
-C.
-Harvey, and G.
-D.
-A.
-Phillips.
-1980.
-{``Algorithm {AS} 154: An Algorithm for Exact Maximum Likelihood Estimation of Autoregressive-Moving Average Models by Means of Kalman Filtering.''} \emph{Applied Statistics} 29 (3): 311.
-\url{https://doi.org/10.2307/2346910}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Giles2019}{}}%
-Giles, David M., Alexander Sinyuk, Mikhail G.
-Sorokin, Joel S.
-Schafer, Alexander Smirnov, Ilya Slutsker, Thomas F.
-Eck, et al.
-2019.
-{``Advancements in the Aerosol Robotic Network ({AERONET}) Version 3 Database -- Automated Near-Real-Time Quality Control Algorithm with Improved Cloud Screening for Sun Photometer Aerosol Optical Depth ({AOD}) Measurements.''} \emph{Atmospheric Measurement Techniques} 12 (1): 169--209.
-\url{https://doi.org/10.5194/amt-12-169-2019}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Graabak2016}{}}%
-Graabak, Ingeborg, and Magnus Korpås.
-2016.
-{``Variability Characteristics of European Wind and Solar Power Resources---a Review.''} \emph{Energies} 9 (6): 449.
-\url{https://doi.org/10.3390/en9060449}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gray2010}{}}%
-Gray, L.
-J., J.
-Beer, M.
-Geller, J.
-D.
-Haigh, M.
-Lockwood, K.
-Matthes, U.
-Cubasch, et al.
-2010.
-{``{SOLAR} {INFLUENCES} {ON} {CLIMATE}.''} \emph{Reviews of Geophysics} 48 (4): RG4001.
-\url{https://doi.org/10.1029/2009RG000282}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gueymard2017}{}}%
-Gueymard, Christian A.
-2017.
-{``Cloud and Albedo Enhancement Impacts on Solar Irradiance Using High-Frequency Measurements from Thermopile and Photodiode Radiometers.
-Part 1: Impacts on Global Horizontal Irradiance.''} \emph{Solar Energy} 153: 755--65.
-\url{https://doi.org/gb283c}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Haurwitz1945}{}}%
-Haurwitz, Bernhard. 1945. {``Insolation in {Relation} to {Cloudiness} and {Cloud} {Density}.''} \emph{Journal of Meteorology} 2 (September): 154--66.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Inman2013}{}}%
-Inman, Rich H., Hugo T.
-C.
-Pedro, and Carlos F.
-M.
-Coimbra.
-2013.
-{``Solar Forecasting Methods for Renewable Energy Integration.''} \emph{Progress in Energy and Combustion Science} 39 (6): 535--76.
-\url{https://doi.org/10.1016/j.pecs.2013.06.002}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jaervelae2020}{}}%
-Järvelä, Markku, and Seppo Valkealahti.
-2020.
-{``Operation of a {PV} Power Plant During Overpower Events Caused by the Cloud Enhancement Phenomenon.''} \emph{Energies} 13 (9): 2185.
-\url{https://doi.org/10.3390/en13092185}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jones1980}{}}%
-Jones, Richard H.
-1980.
-{``Maximum Likelihood Fitting of {ARMA} Models to Time Series with Missing Observations.''} \emph{Technometrics} 22 (3): 389--95.
-\url{https://doi.org/10.1080/00401706.1980.10486171}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kurucz1994}{}}%
-Kurucz, Robert L. 1994. {``Synthetic Infrared Spectra.''} In \emph{Infrared Solar Physics}, edited by D. M. Rabin, J. T. Jefferies, and C. Lindsey, 523--31. Dordrecht: Springer Netherlands.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lappalainen2020}{}}%
-Lappalainen, Kari, and Jan Kleissl.
-2020.
-{``Analysis of the Cloud Enhancement Phenomenon and Its Effects on Photovoltaic Generators Based on Cloud Speed Sensor Measurements.''} \emph{Journal of Renewable and Sustainable Energy} 12 (4): 043502.
-\url{https://doi.org/10.1063/5.0007550}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Long2006}{}}%
-Long, Charles N., and Y.
-Shi.
-2006.
-{``The QCRad Value Added Product: Surface Radiation Measurement Quality Control Testing, Including Climatology Configurable Limits.''} DOE/SC-ARM/TR-074.
-Office of Science, Office of Biological; Environmental Research, U.S.
-Department of Energy.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Long2008a}{}}%
----------. 2008. {``An Automated Quality Assessment and Control Algorithm for Surface Radiation Measurements.''} \emph{The Open Atmospheric Science Journal}, 23--37.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Martins2022}{}}%
-Martins, G.
-L., S.
-L.
-Mantelli, and R.
-Rüther.
-2022.
-{``Evaluating the Performance of Radiometers for Solar Overirradiance Events.''} \emph{Solar Energy} 231 (January): 47--56.
-\url{https://doi.org/10.1016/j.solener.2021.11.050}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Mol2023}{}}%
-Mol, Wouter B., Wouter H.
-Knap, and Chiel C.
-Van Heerwaarden.
-2023.
-{``Ten Years of 1 Hz Solar Irradiance Observations at Cabauw, the Netherlands, with Cloud Observations, Variability Classifications, and Statistics.''} \emph{Earth System Science Data} 15 (5): 2139--51.
-\url{https://doi.org/10.5194/essd-15-2139-2023}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Natsis2023}{}}%
-Natsis, Athanasios, Alkiviadis Bais, and Charikleia Meleti.
-2023.
-{``Trends from 30-Year Observations of Downward Solar Irradiance in Thessaloniki, Greece.''} \emph{Applied Sciences} 14 (1): 252.
-\url{https://doi.org/10.3390/app14010252}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pecenak2016}{}}%
-Pecenak, Zachary K., Felipe A.
-Mejia, Ben Kurtz, Amato Evan, and Jan Kleissl.
-2016.
-{``Simulating Irradiance Enhancement Dependence on Cloud Optical Depth and Solar Zenith Angle.''} \emph{Solar Energy} 136 (October): 675--81.
-\url{https://doi.org/10.1016/j.solener.2016.07.045}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-RCT2023}{}}%
-R Core Team. 2023. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Thuillier2013}{}}%
-Thuillier, Gérard, Jean-Marie Perrin, Philippe Keckhut, and François Huppert.
-2013.
-{``Local Enhanced Solar Irradiance on the Ground Generated by Cirrus: Measurements and Interpretation.''} \emph{Journal of Applied Remote Sensing} 7 (1): 073543.
-\url{https://doi.org/10.1117/1.JRS.7.073543}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Vamvakas2020}{}}%
-Vamvakas, Ioannis, Vasileios Salamalikis, and Andreas Kazantzidis.
-2020.
-{``Evaluation of Enhancement Events of Global Horizontal Irradiance Due to Clouds at Patras, South-West Greece.''} \emph{Renewable Energy} 151 (xxxx): 764--71.
-\url{https://doi.org/gq3sbh}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Veerman2022}{}}%
-Veerman, M.
-A., B.
-J.
-H.
-Van Stratum, and C.
-C.
-Van Heerwaarden.
-2022.
-{``A Case Study of Cumulus Convection over Land in Cloud‐resolving Simulations with a Coupled Ray Tracer.''} \emph{Geophysical Research Letters} 49 (23).
-\url{https://doi.org/10.1029/2022GL100808}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Yordanov2013}{}}%
-Yordanov, G.
-H., O.-M.
-Midtgård, T.
-O.
-Saetre, H.
-K.
-Nielsen, and L.
-E.
-Norum.
-2013.
-{``Overirradiance (Cloud Enhancement) Events at High Latitudes.''} \emph{{IEEE} Journal of Photovoltaics} 3 (1): 271--77.
-\url{https://doi.org/10.1109/JPHOTOV.2012.2213581}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Yordanov2015}{}}%
-Yordanov, Georgi Hristov, Tor Oskar Saetre, and Ole-Morten Midtgård.
-2015.
-{``Extreme Overirradiance Events in Norway: 1.6 Suns Measured Close to 60°n.''} \emph{Solar Energy} 115 (May): 68--73.
-\url{https://doi.org/10.1016/j.solener.2015.02.020}.
-
-\end{CSLReferences}
+\bibliography{bibliography.bib}
 

### 2024-04-16 GHI_enh_Aeronet.tex
Commit 2024-04-16 18:12

--- 2024-03-28 GHI_enh_04_investigate.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-03-28}
+\date{2024-04-16}
 
@@
 \begin{verbatim}
-
-Attaching package: 'zoo'
+Warning: Invalid .internal.selfref detected and fixed by taking a (shallow)
+copy of the data.table so that := can add this new column by reference. At an
+earlier point, this data.table has been copied by R (or was created manually
+using structure() or similar). Avoid names<- and attr<- which in R currently
+(and oddly) may copy the whole data.table. Use set* syntax instead to avoid
+copying: ?set, ?setnames and ?setattr. If this message doesn't help, please
+report your use case to the data.table issue tracker so the root cause can be
+fixed or this message improved.
 \end{verbatim}
@@
 \begin{verbatim}
-The following objects are masked from 'package:data.table':
-
-    yearmon, yearqtr
+Cross over point: 2014.75 
 \end{verbatim}
 
-\begin{verbatim}
-The following objects are masked from 'package:base':
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-1} \end{center}
 
-    as.Date, as.Date.numeric
-\end{verbatim}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-3} \end{center}
 
 \begin{verbatim}
-Registered S3 methods overwritten by 'ggpp':
-  method                  from   
-  heightDetails.titleGrob ggplot2
-  widthDetails.titleGrob  ggplot2
+pdf 
+  3 
 \end{verbatim}
-
-\begin{verbatim}
-
-Attaching package: 'ggpp'
-\end{verbatim}
-
-\begin{verbatim}
-The following object is masked from 'package:ggh4x':
-
-    stat_centroid
-\end{verbatim}
-
-\begin{verbatim}
-The following object is masked from 'package:ggplot2':
-
-    annotate
-\end{verbatim}
-
-\begin{verbatim}
-Registered S3 method overwritten by 'ggpmisc':
-  method                  from   
-  as.character.polynomial polynom
-\end{verbatim}
-
-\begin{verbatim}
-ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
-\end{verbatim}
-
-\newpage
-\FloatBarrier
-
-\hypertarget{daily-trends}{%
-\subsubsection{Daily Trends}\label{daily-trends}}
-
-\begin{verbatim}
-Warning in ans * length(l) + if1: longer object length is not a multiple of
-shorter object length
-\end{verbatim}
-
-\newpage
-
-\begin{verbatim}
-Loading required package: stringr
-\end{verbatim}
-
-\hypertarget{trends-on-daily-observations-data}{%
-\paragraph{Trends on Daily Observations data}\label{trends-on-daily-observations-data}}
-
-Units for GLB\_diff.max : Watt/m\^{}2
-
-lmD: 1.566006 +/- 0.108321
-
-lmY: 1.566022 +/- 0.108322
-
-Arima: 1.566405 +/- 0.146687
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-1} \end{center}
-
-Units for GLB\_diff.mean : Watt/m\^{}2
-
-lmD: 0.950804 +/- 0.155249
-
-lmY: 0.950827 +/- 0.155251
-
-Arima: 1.022268 +/- 0.236917
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-2} \end{center}
-
-Units for GLB\_diff.median : Watt/m\^{}2
-
-lmD: 1.086985 +/- 0.167871
-
-lmY: 1.087013 +/- 0.167874
-
-Arima: 1.159971 +/- 0.251086
-
-Units for GLB\_diff.N :
-
-lmD: -0.012345 +/- 0.138879
-
-lmY: -0.01233 +/- 0.138882
-
-\begin{verbatim}
-Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
-possible convergence problem: optim gave code = 1
-\end{verbatim}
-
-\begin{verbatim}
-Warning in sqrt(diag(se)): NaNs produced
-
-Warning in sqrt(diag(se)): NaNs produced
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-3} \end{center}
-
-Arima: -0.013183 +/- 6.898051
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-4} \end{center}
-
-Units for GLB\_diff.p\_10 : Watt/m\^{}2
-
-lmD: 1.034078 +/- 0.239285
-
-lmY: 1.034088 +/- 0.23929
-
-Arima: 1.03413 +/- 0.363494
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-5} \end{center}
-
-Units for GLB\_diff.p\_5 : Watt/m\^{}2
-
-lmD: 0.944568 +/- 0.252832
-
-lmY: 0.944578 +/- 0.252837
-
-Arima: 0.944623 +/- 0.38704
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-6} \end{center}
-
-Units for GLB\_diff.p\_90 : Watt/m\^{}2
-
-lmD: 1.109672 +/- 0.07725
-
-lmY: 1.109686 +/- 0.077252
-
-Arima: 1.109689 +/- 0.115906
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-7} \end{center}
-
-Units for GLB\_diff.p\_95 : Watt/m\^{}2
-
-lmD: 1.167512 +/- 0.073583
-
-lmY: 1.167525 +/- 0.073584
-
-Arima: 1.167532 +/- 0.106265
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-8} \end{center}
-
-Units for GLB\_diff.sum : kJ/m\^{}2
-
-lmD: 33.66024 +/- 5.69273
-
-lmY: 33.6608 +/- 5.692829
-
-Arima: 33.721354 +/- 8.881986
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-9} \end{center}
-
-Units for GLB\_ench.max : Watt/m\^{}2
-
-lmD: 0.003266 +/- 0.000271
-
-lmY: 0.003266 +/- 0.000271
-
-Arima: 0.003291 +/- 0.000364
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-10} \end{center}
-
-Units for GLB\_ench.mean : Watt/m\^{}2
-
-lmD: 0.001715 +/- 0.000278
-
-lmY: 0.001715 +/- 0.000278
-
-Arima: 0.001886 +/- 0.000465
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-11} \end{center}
-
-Units for GLB\_ench.median : Watt/m\^{}2
-
-lmD: 0.001677 +/- 0.000314
-
-lmY: 0.001677 +/- 0.000314
-
-Arima: 0.001849 +/- 0.000512
-
-Units for GLB\_ench.N :
-
-lmD: -0.012345 +/- 0.138879
-
-lmY: -0.01233 +/- 0.138882
-
-\begin{verbatim}
-Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
-possible convergence problem: optim gave code = 1
-
-Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
-NaNs produced
-
-Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
-NaNs produced
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-12} \end{center}
-
-Arima: -0.013183 +/- 6.898051
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-13} \end{center}
-
-Units for GLB\_ench.p\_10 : Watt/m\^{}2
-
-lmD: 0.00184 +/- 0.000301
-
-lmY: 0.00184 +/- 0.000301
-
-Arima: 0.00184 +/- 0.000473
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-14} \end{center}
-
-Units for GLB\_ench.p\_5 : Watt/m\^{}2
-
-lmD: 0.001768 +/- 0.000292
-
-lmY: 0.001768 +/- 0.000292
-
-Arima: 0.001768 +/- 0.000451
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-15} \end{center}
-
-Units for GLB\_ench.p\_90 : Watt/m\^{}2
-
-lmD: 0.002432 +/- 0.000235
-
-lmY: 0.002432 +/- 0.000235
-
-Arima: 0.002432 +/- 0.000369
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-16} \end{center}
-
-Units for GLB\_ench.p\_95 : Watt/m\^{}2
-
-lmD: 0.002624 +/- 0.000229
-
-lmY: 0.002624 +/- 0.000229
-
-Arima: 0.002624 +/- 0.000346
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-17} \end{center}
-
-Units for GLB\_ench.sum : Watt/m\^{}2
-
-lmD: 0.977006 +/- 0.143935
-
-lmY: 0.977029 +/- 0.143937
-
-Arima: 1.040956 +/- 0.218636
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-18} \end{center}
-
-\newpage
-
-\hypertarget{trends-on-daily-enhancements-data}{%
-\paragraph{Trends on Daily Enhancements data}\label{trends-on-daily-enhancements-data}}
-
-Units for GLB\_diff.max : Watt/m\^{}2
-
-lmD: 0.817503 +/- 0.103432
-
-lmY: 0.817514 +/- 0.103434
-
-Arima: 0.817505 +/- 0.120041
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-19} \end{center}
-
-Units for GLB\_diff.mean : Watt/m\^{}2
-
-lmD: 0.216071 +/- 0.038072
-
-lmY: 0.216075 +/- 0.038073
-
-Arima: 0.216075 +/- 0.041418
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-20} \end{center}
-
-Units for GLB\_diff.median : Watt/m\^{}2
-
-lmD: 0.190931 +/- 0.037875
-
-lmY: 0.190936 +/- 0.037876
-
-Arima: 0.190936 +/- 0.040087
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-21} \end{center}
-
-Units for GLB\_diff.N :
-
-lmD: 0.485676 +/- 0.046388
-
-lmY: 0.485682 +/- 0.046389
-
-Arima: 0.485682 +/- 0.055179
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-22} \end{center}
-
-Units for GLB\_diff.p\_10 : Watt/m\^{}2
-
-lmD: -0.00734 +/- 0.019077
-
-lmY: -0.007339 +/- 0.019077
-
-Arima: -0.007339 +/- 0.019267
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-23} \end{center}
-
-Units for GLB\_diff.p\_5 : Watt/m\^{}2
-
-lmD: -0.027816 +/- 0.017696
-
-lmY: -0.027816 +/- 0.017696
-
-Arima: -0.027816 +/- 0.017858
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-24} \end{center}
-
-Units for GLB\_diff.p\_90 : Watt/m\^{}2
-
-lmD: 0.49203 +/- 0.073274
-
-lmY: 0.492037 +/- 0.073275
-
-Arima: 0.492032 +/- 0.081403
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-25} \end{center}
-
-Units for GLB\_diff.p\_95 : Watt/m\^{}2
-
-lmD: 0.595557 +/- 0.083417
-
-lmY: 0.595566 +/- 0.083419
-
-Arima: 0.59556 +/- 0.094857
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-26} \end{center}
-
-Units for GLB\_diff.sum : kJ/m\^{}2
-
-lmD: 1.467857 +/- 0.152656
-
-lmY: 1.46788 +/- 0.152659
-
-Arima: 1.467877 +/- 0.18431
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-27} \end{center}
-
-Units for GLB\_ench.max : Watt/m\^{}2
-
-lmD: 0.001336 +/- 0.000137
-
-lmY: 0.001336 +/- 0.000137
-
-Arima: 0.001336 +/- 0.000157
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-28} \end{center}
-
-Units for GLB\_ench.mean : Watt/m\^{}2
-
-lmD: 0.000423 +/- 5.9e-05
-
-lmY: 0.000423 +/- 5.9e-05
-
-Arima: 0.000423 +/- 6.7e-05
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-29} \end{center}
-
-Units for GLB\_ench.median : Watt/m\^{}2
-
-lmD: 0.000372 +/- 6.1e-05
-
-lmY: 0.000372 +/- 6.1e-05
-
-Arima: 0.000372 +/- 6.8e-05
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-30} \end{center}
-
-Units for GLB\_ench.N :
-
-lmD: 0.485676 +/- 0.046388
-
-lmY: 0.485682 +/- 0.046389
-
-Arima: 0.485682 +/- 0.055179
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-31} \end{center}
-
-Units for GLB\_ench.p\_10 : Watt/m\^{}2
-
-lmD: 2.1e-05 +/- 3.2e-05
-
-lmY: 2.1e-05 +/- 3.2e-05
-
-Arima: 2.1e-05 +/- 3.6e-05
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-32} \end{center}
-
-Units for GLB\_ench.p\_5 : Watt/m\^{}2
-
-lmD: -1.2e-05 +/- 2.9e-05
-
-lmY: -1.2e-05 +/- 2.9e-05
-
-Arima: -1.2e-05 +/- 3.4e-05
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-33} \end{center}
-
-Units for GLB\_ench.p\_90 : Watt/m\^{}2
-
-lmD: 0.000922 +/- 0.000106
-
-lmY: 0.000922 +/- 0.000106
-
-Arima: 0.000922 +/- 0.00012
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-34} \end{center}
-
-Units for GLB\_ench.p\_95 : Watt/m\^{}2
-
-lmD: 0.001074 +/- 0.000117
-
-lmY: 0.001074 +/- 0.000117
-
-Arima: 0.001074 +/- 0.000134
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-35} \end{center}
-
-Units for GLB\_ench.sum : Watt/m\^{}2
-
-lmD: 0.036561 +/- 0.003622
-
-lmY: 0.036562 +/- 0.003622
-
-Arima: 0.036562 +/- 0.004204
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-36} \end{center}
-
-\newpage
-
-\hypertarget{trends-on-daily-extreme-enhancements-data}{%
-\paragraph{Trends on Daily Extreme Enhancements data}\label{trends-on-daily-extreme-enhancements-data}}
-
-Units for GLB\_diff.max : Watt/m\^{}2
-
-lmD: 0.187208 +/- 0.249476
-
-lmY: 0.187246 +/- 0.24948
-
-Arima: 0.171775 +/- 0.364628
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-37} \end{center}
-
-Units for GLB\_diff.mean : Watt/m\^{}2
-
-lmD: 0.049774 +/- 0.192505
-
-lmY: 0.049798 +/- 0.192508
-
-Arima: 0.008548 +/- 0.346363
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-38} \end{center}
-
-Units for GLB\_diff.median : Watt/m\^{}2
-
-lmD: 0.091248 +/- 0.191453
-
-lmY: 0.091272 +/- 0.191456
-
-Arima: 0.049975 +/- 0.33542
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-39} \end{center}
-
-Units for GLB\_diff.N :
-
-lmD: 0.030347 +/- 0.021245
-
-lmY: 0.030349 +/- 0.021246
-
-Arima: 0.030378 +/- 0.022031
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-40} \end{center}
-
-Units for GLB\_diff.p\_10 : Watt/m\^{}2
-
-lmD: -0.069532 +/- 0.179279
-
-lmY: -0.06952 +/- 0.179282
-
-Arima: -0.124647 +/- 0.339466
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-41} \end{center}
-
-Units for GLB\_diff.p\_5 : Watt/m\^{}2
-
-lmD: -0.089703 +/- 0.178956
-
-lmY: -0.089692 +/- 0.178959
-
-Arima: -0.144328 +/- 0.338161
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-42} \end{center}
-
-Units for GLB\_diff.p\_90 : Watt/m\^{}2
-
-lmD: 0.16704 +/- 0.22968
-
-lmY: 0.167077 +/- 0.229683
-
-Arima: 0.146398 +/- 0.353614
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-43} \end{center}
-
-Units for GLB\_diff.p\_95 : Watt/m\^{}2
-
-lmD: 0.17703 +/- 0.238162
-
-lmY: 0.177067 +/- 0.238165
-
-Arima: 0.158966 +/- 0.358093
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-44} \end{center}
-
-Units for GLB\_diff.sum : kJ/m\^{}2
-
-lmD: 0.368357 +/- 0.253498
-
-lmY: 0.368383 +/- 0.253502
-
-Arima: 0.36844 +/- 0.258271
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-45} \end{center}
-
-Units for GLB\_ench.max : Watt/m\^{}2
-
-lmD: 0.000508 +/- 0.000281
-
-lmY: 0.000509 +/- 0.000281
-
-Arima: 0.000508 +/- 0.000318
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-46} \end{center}
-
-Units for GLB\_ench.mean : Watt/m\^{}2
-
-lmD: 0.000356 +/- 0.000214
-
-lmY: 0.000356 +/- 0.000214
-
-Arima: 0.000349 +/- 0.000265
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-47} \end{center}
-
-Units for GLB\_ench.median : Watt/m\^{}2
-
-lmD: 0.000399 +/- 0.000221
-
-lmY: 0.000399 +/- 0.000221
-
-Arima: 0.000392 +/- 0.00027
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-48} \end{center}
-
-Units for GLB\_ench.N :
-
-lmD: 0.030347 +/- 0.021245
-
-lmY: 0.030349 +/- 0.021246
-
-Arima: 0.030378 +/- 0.022031
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-49} \end{center}
-
-Units for GLB\_ench.p\_10 : Watt/m\^{}2
-
-lmD: 0.000168 +/- 0.000199
-
-lmY: 0.000168 +/- 0.000199
-
-Arima: 0.000157 +/- 0.000257
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-50} \end{center}
-
-Units for GLB\_ench.p\_5 : Watt/m\^{}2
-
-lmD: 0.000155 +/- 0.000199
-
-lmY: 0.000155 +/- 0.000199
-
-Arima: 0.000144 +/- 0.000256
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-51} \end{center}
-
-Units for GLB\_ench.p\_90 : Watt/m\^{}2
-
-lmD: 0.000509 +/- 0.000261
-
-lmY: 0.000509 +/- 0.000261
-
-Arima: 0.000508 +/- 3e-04
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-52} \end{center}
-
-Units for GLB\_ench.p\_95 : Watt/m\^{}2
-
-lmD: 0.00051 +/- 0.00027
-
-lmY: 0.00051 +/- 0.00027
-
-Arima: 0.000509 +/- 0.000307
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-53} \end{center}
-
-Units for GLB\_ench.sum : Watt/m\^{}2
-
-lmD: 0.008776 +/- 0.005507
-
-lmY: 0.008777 +/- 0.005507
-
-Arima: 0.008799 +/- 0.005722
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-54} \end{center}
-
-Arima: 0.216075 +/- 0.041418
-
-\begin{verbatim}
-Warning: The S3 guide system was deprecated in ggplot2 3.5.0.
-i It has been replaced by a ggproto system that can be extended.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_daily_trend-1} \end{center}
-
-\newpage
-\FloatBarrier
-
-\hypertarget{group-stats}{%
-\subsubsection{Group stats}\label{group-stats}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-1} \end{center}
-
-\begin{verbatim}
-Warning in scale_y_log10(): log-10 transformation introduced infinite values.
-\end{verbatim}
-
-\begin{verbatim}
-Warning: Removed 25 rows containing missing values or values outside the scale
-range (`geom_bar()`).
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-2} \end{center}
-
-\begin{verbatim}
-Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
-i Please use the `legend.position.inside` argument of `theme()` instead.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-6} \end{center}
-
-\hypertarget{zhang2018}{%
-\subsection{@Zhang2018}\label{zhang2018}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8} \end{center}
-
-\begin{verbatim}
-Scale for x is already present.
-Adding another scale for x, which will replace the existing scale.
-\end{verbatim}
-
-\begin{verbatim}
-Warning: Removed 12 rows containing non-finite outside the scale range
-(`stat_bin2d()`).
-\end{verbatim}
-
-\begin{verbatim}
-Warning: Removed 2 rows containing missing values or values outside the scale
-range (`geom_tile()`).
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-1} \end{center}
-
-\begin{verbatim}
-Scale for x is already present.
-Adding another scale for x, which will replace the existing scale.
-\end{verbatim}
-
-\begin{verbatim}
-Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
-Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-2} \end{center}
-
-\begin{verbatim}
-Scale for x is already present.
-Adding another scale for x, which will replace the existing scale.
-\end{verbatim}
-
-\begin{verbatim}
-Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
-Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-3} \end{center}
-
-\begin{verbatim}
-Scale for x is already present.
-Adding another scale for x, which will replace the existing scale.
-\end{verbatim}
-
-\begin{verbatim}
-Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
-Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_N_doy-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCEmonth-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_N-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N-1} \end{center}
-
-\begin{verbatim}
-Warning: The `fun.y` argument of `stat_summary()` is deprecated as of ggplot2 3.3.0.
-i Please use the `fun` argument instead.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCE_daily-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCE_week-1} \end{center}
-
-\newpage
-\FloatBarrier
-
-\hypertarget{energy-contribution-of-enhancements}{%
-\subsubsection{Energy contribution of enhancements}\label{energy-contribution-of-enhancements}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-3} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-7} \end{center}
-
-@Martins2022
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-8} \end{center}
-
-lmY: 341.6364 +/- 36.57038
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-1} \end{center}
-
-lmY: 122.2229 +/- 11.42113
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-2} \end{center}
-
-lmY: 0.232986 +/- 0.055703
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-3} \end{center}
-
-lmY: 0.183685 +/- 0.040872
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-8} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_multi-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-3} \end{center}
-
-\newpage
-\FloatBarrier
-
-\hypertarget{monthly-energy-contribution-of-enhancements}{%
-\subsubsection{Monthly Energy contribution of enhancements}\label{monthly-energy-contribution-of-enhancements}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-3} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-6} \end{center}
-
-@Martins2022
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-7} \end{center}
 
@@
 \begin{verbatim}
-2024-03-28 08:59:32.3 athan@sagan GHI_enh_04_investigate.R 0.815632 mins
+2024-04-16 14:12:41.9 athan@tyler GHI_enh_Aeronet.R 0.120263 mins
 \end{verbatim}

### 2024-04-16 GHI_enh_04_investigate.tex
Commit 2024-04-16 19:25

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-14}
+\date{2024-04-16}
 
@@
   as.character.polynomial polynom
+\end{verbatim}
+
+\begin{verbatim}
+Run previous step: ./GHI_enh_03_process.R
+\end{verbatim}
+
+\begin{verbatim}
+Warning in eval(ei, envir):
+
+ ** Test is active!! ** 
+\end{verbatim}
+
+\begin{verbatim}
+Warning: Invalid .internal.selfref detected and fixed by taking a (shallow)
+copy of the data.table so that := can add this new column by reference. At an
+earlier point, this data.table has been copied by R (or was created manually
+using structure() or similar). Avoid names<- and attr<- which in R currently
+(and oddly) may copy the whole data.table. Use set* syntax instead to avoid
+copying: ?set, ?setnames and ?setattr. If this message doesn't help, please
+report your use case to the data.table issue tracker so the root cause can be
+fixed or this message improved.
+\end{verbatim}
+
+\begin{verbatim}
+Cross over point: 2014.75 
+\end{verbatim}
+
+\begin{verbatim}
+2024-04-16 15:32:36.8 athan@tyler GHI_enh_Aeronet.R 0.003239 mins
+
+USING TRASPARENCY TREND
+
+ USING CSMODE: Low_B.Low_W
+
+C4 factor: 1.09 
+C4 offset: 0 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with extreme cases day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with strong enhancement day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with sunny day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with sunny enhancement day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with cloudy day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with random day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with manual test days 
+\end{verbatim}
+
+\begin{verbatim}
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
+i Please use the `legend.position.inside` argument of `theme()` instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
+\begin{verbatim}
+Warning in eval(ei, envir): TEST IS ACTIVE !!
+\end{verbatim}
+
+\begin{verbatim}
+
+  TEST IS ACTIVE  !!
+
+2024-04-16 15:36:05.5 athan@tyler GHI_enh_Aeronet.R 3.481589 mins
+\end{verbatim}
+
+\begin{verbatim}
+
+Attaching package: 'timetk'
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:data.table':
+
+    :=
+\end{verbatim}
+
+\begin{verbatim}
+frequency = 30 observations
+\end{verbatim}
+
+\begin{verbatim}
+trend = 180 observations
+\end{verbatim}
+
+\begin{verbatim}
+frequency = 30 observations
+\end{verbatim}
+
+\begin{verbatim}
+trend = 180 observations
+\end{verbatim}
+
+\begin{verbatim}
+
+Call:
+stats::lm(formula = .formula, data = df)
+
+Residuals:
+    Min      1Q  Median      3Q     Max 
+-372.77 -150.51  -49.67   99.05  778.55
+
+Coefficients:
+                   Estimate Std. Error t value Pr(>|t|)    
+(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
+as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
+---
+Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+
+Residual standard error: 217 on 361 degrees of freedom
+Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
+F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
+
+aa
+aday
+AEin1
+All_daily_ratio_lim
+alpha
+ampl
+avar
+b
+BIO_ELEVA
+C1_Clearness_Kt_THRES
+C1_GLB_diff_THRES
+C2_Clearness_Kt_THRES
+C3_cs_ref_ratio
+C4_cs_ref_ratio
+C4_GLB_diff_THRES
+C4_lowcut_ratio
+C4_lowcut_sza
+C4_test_cs_ref_ratio
+C4_test_GLB_diff_THRES
+C4_test_lowcut_ratio
+C4_test_lowcut_sza
+Clear_daily_ratio_lim
+CLEARdir
+Cloud_daily_ratio_lim
+cols
+common_data_13
+common_data_14
+common_data_14_2
+CS_file_13
+CS_file_14
+CS_file_14_2
+csmodel
+Daily_aggregation_N_lim
+Daily_confidence_limit
+daylist
+Days_of_year
+dummy
+Energy_Div
+I1_longterm
+I2_szatrend
+I3_trendsconsist
+ii
+Input_data_ID
+Kurudz_SC
+mid
+MIN_ELEVA
+MIN_N
+Monthly_aggegation_N_lim
+Monthly_confidence_limit
+my.cols
+my.cols.gr
+pyear
+R_COMPILE_PKGS
+RANDOM_SEED
+raw_input_data
+running_mean_window_days
+running_mean_window_years
+SEAS_MIN_N
+SelEnhanc
+SZA_aggregation_N_lim
+SZA_BIN
+SZA_confidence_limit
+torun
+variables_fl
+yearstodo
+ylim
+zeropoint
+ST_daily
+ST_E_daily
+ST_E_daily_seas
+ST_E_monthly
+ST_E_monthly_seas
+ST_E_sza
+ST_E_sza_doy
+ST_E_sza_monthly
+ST_E_yearly
+ST_extreme_daily
+ST_extreme_monthly
+ST_extreme_SZA
+ST_extreme_SZA_doy
+ST_extreme_SZA_monthly
+ST_extreme_total
+ST_extreme_yearly
+ST_G0
+ST_G1
+ST_monthly
+ST_sza
+ST_sza_doy
+ST_sza_monthly
+ST_total
+ST_yearly
+2024-04-16 15:47:52.8 athan@tyler GHI_enh_Aeronet.R 7.735972 mins
 \end{verbatim}
@@
 
-\begin{verbatim}
-Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
-i Please use the `legend.position.inside` argument of `theme()` instead.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
-
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3} \end{center}
@@
 \begin{verbatim}
-2024-04-14 00:48:00.3 athan@tyler GHI_enh_04_investigate.R 1.346105 mins
+2024-04-16 15:49:17.4 athan@tyler GHI_enh_Aeronet.R 1.356321 mins
 \end{verbatim}

### 2024-04-17 GHI_enh_03_process.tex
Commit 2024-04-11 12:14
Commit 2024-04-17 00:14
Commit 2024-04-17 09:13

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-08}
+\date{2024-04-16}
 
@@
 \begin{verbatim}
+Warning in eval(ei, envir):
+
+ ** Test is active!! ** 
+\end{verbatim}
+
+\begin{verbatim}
+Warning: Invalid .internal.selfref detected and fixed by taking a (shallow)
+copy of the data.table so that := can add this new column by reference. At an
+earlier point, this data.table has been copied by R (or was created manually
+using structure() or similar). Avoid names<- and attr<- which in R currently
+(and oddly) may copy the whole data.table. Use set* syntax instead to avoid
+copying: ?set, ?setnames and ?setattr. If this message doesn't help, please
+report your use case to the data.table issue tracker so the root cause can be
+fixed or this message improved.
+\end{verbatim}
+
+\begin{verbatim}
+Cross over point: 2014.75 
+\end{verbatim}
+
+\begin{verbatim}
+2024-04-16 15:13:21.3 athan@tyler GHI_enh_Aeronet.R 0.022648 mins
+
+USING TRASPARENCY TREND
 
@@
 
-C4 factor: 1.05 
+C4 factor: 1.09 
 C4 offset: 0 
 \end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-3} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-8} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-9} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-10} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-11} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-12} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-13} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-14} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-15} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-16} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-17} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-18} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-19} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-20} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-21} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-22} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-23} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-24} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-25} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-26} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-27} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-28} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-29} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-30} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-31} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-32} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-33} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-34} \end{center}
 
@@
 \end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-105} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-106} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-107} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-108} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-109} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-110} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-111} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-112} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-113} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-114} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-115} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-116} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-117} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-118} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-119} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-120} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-121} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-122} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-123} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-124} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-125} \end{center}
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-126} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-127} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-128} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-129} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-130} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-131} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-132} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-133} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-134} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-135} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-136} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-137} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-138} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-139} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-140} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-141} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-142} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-143} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-144} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-145} \end{center}
+
 \begin{verbatim}
@@
 \end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-146} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-147} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-148} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-149} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-150} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-151} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-152} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-153} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-154} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-155} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-156} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-157} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-158} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-159} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-160} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-161} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-162} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-163} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-164} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-165} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-166} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-167} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-168} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-169} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-170} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-171} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-172} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-173} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-174} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-175} \end{center}
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-176} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-177} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-178} \end{center}
+
 \begin{verbatim}
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-179} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-180} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-181} \end{center}
+
 \begin{verbatim}
-2024-04-08 15:48:57.0 athan@sagan GHI_enh_02_ID_CE.R 29.123272 mins
+Warning in eval(ei, envir): TEST IS ACTIVE !!
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-182} \end{center}
+
+\begin{verbatim}
+
+  TEST IS ACTIVE  !!
+
+2024-04-16 15:16:07.1 athan@tyler GHI_enh_Aeronet.R 2.786622 mins
 \end{verbatim}
@@
 aday
+AEin1
 All_daily_ratio_lim
@@
 avar
+b
 BIO_ELEVA
@@
 C4_lowcut_sza
+C4_test_cs_ref_ratio
+C4_test_GLB_diff_THRES
+C4_test_lowcut_ratio
+C4_test_lowcut_sza
 Clear_daily_ratio_lim
@@
 Kurudz_SC
+mid
 MIN_ELEVA
@@
 ylim
+zeropoint
 ST_daily
@@
 \begin{verbatim}
-2024-04-08 15:55:25.5 athan@sagan GHI_enh_02_ID_CE.R 3.671820 mins
+2024-04-16 15:30:24.9 athan@tyler GHI_enh_Aeronet.R 10.090148 mins
 \end{verbatim}

### 2024-04-17 GHI_enh_03_process.tex
Commit 2024-04-17 11:18

--- 2024-04-08 GHI_enh_03_process.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-08}
+\date{2024-04-17}
 
@@
 \begin{verbatim}
+Warning: Invalid .internal.selfref detected and fixed by taking a (shallow)
+copy of the data.table so that := can add this new column by reference. At an
+earlier point, this data.table has been copied by R (or was created manually
+using structure() or similar). Avoid names<- and attr<- which in R currently
+(and oddly) may copy the whole data.table. Use set* syntax instead to avoid
+copying: ?set, ?setnames and ?setattr. If this message doesn't help, please
+report your use case to the data.table issue tracker so the root cause can be
+fixed or this message improved.
+\end{verbatim}
+
+\begin{verbatim}
+Cross over point: 2014.75 
+\end{verbatim}
+
+\begin{verbatim}
+2024-04-17 05:42:42.7 athan@tyler GHI_enh_Aeronet.R 0.011558 mins
+
+USING TRASPARENCY TREND
 
@@
 
-C4 factor: 1.05 
+C4 factor: 1.09 
 C4 offset: 0 
@@
 \begin{verbatim}
-2024-04-08 15:48:57.0 athan@sagan GHI_enh_02_ID_CE.R 29.123272 mins
+2024-04-17 07:14:42.3 athan@tyler GHI_enh_Aeronet.R 92.002896 mins
 \end{verbatim}
@@
 \begin{verbatim}
-2024-04-08 15:55:25.5 athan@sagan GHI_enh_02_ID_CE.R 3.671820 mins
+2024-04-17 07:39:43.8 athan@tyler GHI_enh_Aeronet.R 14.179698 mins
 \end{verbatim}

### 2024-04-17 GHI_enh_04_investigate.tex
Commit 2024-04-17 13:28

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-16}
+\date{2024-04-17}
 
@@
 Run previous step: ./GHI_enh_03_process.R
-\end{verbatim}
-
-\begin{verbatim}
-Warning in eval(ei, envir):
-
- ** Test is active!! ** 
 \end{verbatim}
@@
 \begin{verbatim}
-2024-04-16 15:32:36.8 athan@tyler GHI_enh_Aeronet.R 0.003239 mins
+2024-04-17 07:44:01.2 athan@tyler GHI_enh_Aeronet.R 0.004314 mins
 
@@
 \begin{verbatim}
-Warning in eval(ei, envir): TEST IS ACTIVE !!
-\end{verbatim}
-
-\begin{verbatim}
-
-  TEST IS ACTIVE  !!
-
-2024-04-16 15:36:05.5 athan@tyler GHI_enh_Aeronet.R 3.481589 mins
+2024-04-17 09:21:27.9 athan@tyler GHI_enh_Aeronet.R 97.447730 mins
 \end{verbatim}
@@
 ST_yearly
-2024-04-16 15:47:52.8 athan@tyler GHI_enh_Aeronet.R 7.735972 mins
+2024-04-17 09:47:34.9 athan@tyler GHI_enh_Aeronet.R 19.406323 mins
 \end{verbatim}
@@
 \begin{verbatim}
-2024-04-16 15:49:17.4 athan@tyler GHI_enh_Aeronet.R 1.356321 mins
+2024-04-17 09:50:38.0 athan@tyler GHI_enh_Aeronet.R 2.951092 mins
 \end{verbatim}

### 2024-04-17 GHI_enh_06_sza.tex
Commit 2024-04-17 16:12

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-14}
+\date{2024-04-17}
 
@@
     as.Date, as.Date.numeric
+\end{verbatim}
+
+\begin{verbatim}
+Run previous step: ./GHI_enh_03_process.R
+\end{verbatim}
+
+\begin{verbatim}
+Warning: Invalid .internal.selfref detected and fixed by taking a (shallow)
+copy of the data.table so that := can add this new column by reference. At an
+earlier point, this data.table has been copied by R (or was created manually
+using structure() or similar). Avoid names<- and attr<- which in R currently
+(and oddly) may copy the whole data.table. Use set* syntax instead to avoid
+copying: ?set, ?setnames and ?setattr. If this message doesn't help, please
+report your use case to the data.table issue tracker so the root cause can be
+fixed or this message improved.
+\end{verbatim}
+
+\begin{verbatim}
+Cross over point: 2014.75 
+\end{verbatim}
+
+\begin{verbatim}
+2024-04-17 11:15:44.6 athan@tyler GHI_enh_Aeronet.R 0.004042 mins
+
+USING TRASPARENCY TREND
+
+ USING CSMODE: Low_B.Low_W
+
+C4 factor: 1.09 
+C4 offset: 0 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with extreme cases day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with strong enhancement day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with sunny day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with sunny enhancement day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with cloudy day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with random day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with manual test days 
+\end{verbatim}
+
+\begin{verbatim}
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
+i Please use the `legend.position.inside` argument of `theme()` instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
+\begin{verbatim}
+2024-04-17 12:37:20.0 athan@tyler GHI_enh_Aeronet.R 81.594176 mins
+\end{verbatim}
+
+\begin{verbatim}
+
+Attaching package: 'timetk'
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:data.table':
+
+    :=
+\end{verbatim}
+
+\begin{verbatim}
+frequency = 30 observations
+\end{verbatim}
+
+\begin{verbatim}
+trend = 180 observations
+\end{verbatim}
+
+\begin{verbatim}
+frequency = 30 observations
+\end{verbatim}
+
+\begin{verbatim}
+trend = 180 observations
+\end{verbatim}
+
+\begin{verbatim}
+
+Call:
+stats::lm(formula = .formula, data = df)
+
+Residuals:
+    Min      1Q  Median      3Q     Max 
+-372.77 -150.51  -49.67   99.05  778.55
+
+Coefficients:
+                   Estimate Std. Error t value Pr(>|t|)    
+(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
+as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
+---
+Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+
+Residual standard error: 217 on 361 degrees of freedom
+Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
+F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
+
+aa
+aday
+AEin1
+All_daily_ratio_lim
+alpha
+ampl
+avar
+b
+BIO_ELEVA
+C1_Clearness_Kt_THRES
+C1_GLB_diff_THRES
+C2_Clearness_Kt_THRES
+C3_cs_ref_ratio
+C4_cs_ref_ratio
+C4_GLB_diff_THRES
+C4_lowcut_ratio
+C4_lowcut_sza
+C4_test_cs_ref_ratio
+C4_test_GLB_diff_THRES
+C4_test_lowcut_ratio
+C4_test_lowcut_sza
+Clear_daily_ratio_lim
+CLEARdir
+Cloud_daily_ratio_lim
+cols
+common_data_13
+common_data_14
+common_data_14_2
+CS_file_13
+CS_file_14
+CS_file_14_2
+csmodel
+Daily_aggregation_N_lim
+Daily_confidence_limit
+daylist
+Days_of_year
+dummy
+Energy_Div
+I1_longterm
+I2_szatrend
+I3_trendsconsist
+ii
+Input_data_ID
+Kurudz_SC
+mid
+MIN_ELEVA
+MIN_N
+Monthly_aggegation_N_lim
+Monthly_confidence_limit
+my.cols
+my.cols.gr
+pyear
+R_COMPILE_PKGS
+RANDOM_SEED
+raw_input_data
+running_mean_window_days
+running_mean_window_years
+SEAS_MIN_N
+SelEnhanc
+SZA_aggregation_N_lim
+SZA_BIN
+SZA_confidence_limit
+torun
+variables_fl
+yearstodo
+ylim
+zeropoint
+ST_daily
+ST_E_daily
+ST_E_daily_seas
+ST_E_monthly
+ST_E_monthly_seas
+ST_E_sza
+ST_E_sza_doy
+ST_E_sza_monthly
+ST_E_yearly
+ST_extreme_daily
+ST_extreme_monthly
+ST_extreme_SZA
+ST_extreme_SZA_doy
+ST_extreme_SZA_monthly
+ST_extreme_total
+ST_extreme_yearly
+ST_G0
+ST_G1
+ST_monthly
+ST_sza
+ST_sza_doy
+ST_sza_monthly
+ST_total
+ST_yearly
+2024-04-17 13:02:58.4 athan@tyler GHI_enh_Aeronet.R 17.504209 mins
 \end{verbatim}
@@
 
-\begin{verbatim}
-Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
-i Please use the `legend.position.inside` argument of `theme()` instead.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
-
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-1} \end{center}
@@
 \begin{verbatim}
-2024-04-14 00:55:04.2 athan@tyler GHI_enh_06_sza.R 0.288979 mins
+2024-04-17 13:03:40.0 athan@tyler GHI_enh_Aeronet.R 0.565343 mins
 \end{verbatim}

### 2024-04-17 article/article.Rmd
Commit 2024-04-17 23:14

@@
 rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
-renv::load("~/MANUSCRIPTS/02_enhancement/", quiet = TRUE)
+# renv::load("~/MANUSCRIPTS/02_enhancement/", quiet = TRUE)
 ## document configurations

### 2024-04-19 GHI_enh_02_ID_CE.R
Commit 2024-04-19 12:14

@@ -274,14 +274,14 @@ if (APPLY_TRANS) {
 cat("\n USING CSMODE:", csmodel, "\n\n")
 
 switch(csmodel,
-       Exact_B.Exact_W = { C4_cs_ref_ratio <- 1.02; C4_GLB_diff_THRES <- 55; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
-       Low_2_B.Low_2_W = { C4_cs_ref_ratio <- 1.03; C4_GLB_diff_THRES <-  5; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
-       Low_B.Exact_W   = { C4_cs_ref_ratio <- 1.04; C4_GLB_diff_THRES <- 20; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
-       Low_B.High_W    = { C4_cs_ref_ratio <- 1.05; C4_GLB_diff_THRES <- 20; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
+       Exact_B.Exact_W = { C4_cs_ref_ratio <- 1.02; C4_GLB_diff_THRES <- 55; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12; C4_GLB_offset_THRES <- 0},
+       Low_2_B.Low_2_W = { C4_cs_ref_ratio <- 1.03; C4_GLB_diff_THRES <-  5; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12; C4_GLB_offset_THRES <- 0},
+       Low_B.Exact_W   = { C4_cs_ref_ratio <- 1.04; C4_GLB_diff_THRES <- 20; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12; C4_GLB_offset_THRES <- 0},
+       Low_B.High_W    = { C4_cs_ref_ratio <- 1.05; C4_GLB_diff_THRES <- 20; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12; C4_GLB_offset_THRES <- 0},
        # Low_B.Low_W     = { C4_cs_ref_ratio <- 1.05; C4_GLB_diff_THRES <-  0; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.18}, ## without transparency
[…]

### 2024-04-19 GHI_enh_03_process.tex
Commit 2024-04-19 14:14

--- 2024-04-08 GHI_enh_03_process.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-08}
+\date{2024-04-19}
 
@@
 }
-\begin{verbatim}
-
- USING CSMODE: Low_B.Low_W
-
-C4 factor: 1.05 
-C4 offset: 0 
-\end{verbatim}
-
-\begin{verbatim}
-
-\FloatBarrier
-
-## Days with extreme cases day 
-\end{verbatim}
-
-\begin{verbatim}
-
-\FloatBarrier
-
-## Days with strong enhancement day 
-\end{verbatim}
-
-\begin{verbatim}
-
-\FloatBarrier
-
-## Days with sunny day 
-\end{verbatim}
-
-\begin{verbatim}
-
-\FloatBarrier
-
-## Days with sunny enhancement day 
-\end{verbatim}
-
-\begin{verbatim}
-
-\FloatBarrier
-
-## Days with cloudy day 
-\end{verbatim}
-
-\begin{verbatim}
-
-\FloatBarrier
-
-## Days with random day 
-\end{verbatim}
-
-\begin{verbatim}
-
-\FloatBarrier
-
-## Days with manual test days 
-\end{verbatim}
-
-\begin{verbatim}
-Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
-i Please use the `legend.position.inside` argument of `theme()` instead.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
-
-\begin{verbatim}
-2024-04-08 15:48:57.0 athan@sagan GHI_enh_02_ID_CE.R 29.123272 mins
-\end{verbatim}
-
 Alpha * HAU is CS\_ref
@@
     Min      1Q  Median      3Q     Max 
--372.77 -150.51  -49.67   99.05  778.55
+-384.81 -144.57  -53.50   96.68  768.76
 
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
-as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
+(Intercept)      -9.187e+01  4.952e+01  -1.855   0.0644 .  
+as.numeric(Date)  3.286e-07  3.958e-08   8.302 2.08e-15 ***
 ---
@@
 
-Residual standard error: 217 on 361 degrees of freedom
-Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
-F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
+Residual standard error: 211.4 on 361 degrees of freedom
+Multiple R-squared:  0.1603,    Adjusted R-squared:  0.158 
+F-statistic: 68.92 on 1 and 361 DF,  p-value: 2.077e-15
 \end{verbatim}
@@
                     Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       -9.118e+01  5.082e+01  -1.794   0.0736 .  
-ST_E_monthly$Date  3.246e-07  4.062e-08   7.991 1.82e-14 ***
+(Intercept)       -9.187e+01  4.952e+01  -1.855   0.0644 .  
+ST_E_monthly$Date  3.286e-07  3.958e-08   8.302 2.08e-15 ***
 ---
@@
 Cloud_daily_ratio_lim
-cols
 common_data_13
@@
 R_COMPILE_PKGS
-RANDOM_SEED
 raw_input_data
@@
 \begin{verbatim}
-2024-04-08 15:55:25.5 athan@sagan GHI_enh_02_ID_CE.R 3.671820 mins
+2024-04-19 10:26:46.8 athan@sagan GHI_enh_03_process.R 3.634787 mins
 \end{verbatim}

### 2024-04-19 GHI_enh_04_investigate.tex
Commit 2024-04-19 14:14

--- 2024-04-14 GHI_enh_04_investigate.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-14}
+\date{2024-04-19}
 
@@
 
-lmD: 1.566006 +/- 0.108321
+lmD: 1.552161 +/- 0.104876
 
-lmY: 1.566022 +/- 0.108322
+lmY: 1.552176 +/- 0.104878
 
-Arima: 1.566405 +/- 0.146687
+Arima: 1.552549 +/- 0.14034
 
@@
 
-lmD: 0.950804 +/- 0.155249
+lmD: 0.954836 +/- 0.154734
 
-lmY: 0.950827 +/- 0.155251
+lmY: 0.954859 +/- 0.154736
 
-Arima: 1.022268 +/- 0.236917
+Arima: 1.024507 +/- 0.23503
 
@@
 
-lmD: 1.086985 +/- 0.167871
+lmD: 1.088987 +/- 0.16743
 
-lmY: 1.087013 +/- 0.167874
+lmY: 1.089013 +/- 0.167433
 
-Arima: 1.159971 +/- 0.251086
+Arima: 1.160151 +/- 0.24838
 
@@
 
-Arima: -0.013183 +/- 6.904159
+Arima: -0.013183 +/- 6.898051
 
@@
 
-lmD: 1.034078 +/- 0.239285
+lmD: 1.050842 +/- 0.240164
 
-lmY: 1.034088 +/- 0.23929
+lmY: 1.050851 +/- 0.240168
 
-Arima: 1.03413 +/- 0.363491
+Arima: 1.050895 +/- 0.364666
 
@@
 
-lmD: 0.944568 +/- 0.252832
+lmD: 0.958299 +/- 0.253655
 
-lmY: 0.944578 +/- 0.252837
+lmY: 0.958309 +/- 0.25366
 
-Arima: 0.944623 +/- 0.387039
+Arima: 0.958355 +/- 0.388216
 
@@
 
-lmD: 1.109672 +/- 0.07725
+lmD: 1.089066 +/- 0.07424
 
-lmY: 1.109686 +/- 0.077252
+lmY: 1.089079 +/- 0.074241
 
-Arima: 1.109689 +/- 0.115906
+Arima: 1.089082 +/- 0.109498
 
@@
 
-lmD: 1.167512 +/- 0.073583
+lmD: 1.136243 +/- 0.070602
 
-lmY: 1.167525 +/- 0.073584
+lmY: 1.136256 +/- 0.070603
 
-Arima: 1.167532 +/- 0.106265
+Arima: 1.136263 +/- 0.100583
 
@@
 
-lmD: 33.66024 +/- 5.69273
+lmD: 33.75698 +/- 5.702807
 
-lmY: 33.6608 +/- 5.692829
+lmY: 33.75752 +/- 5.702906
 
-Arima: 33.721354 +/- 8.881459
+Arima: 33.816428 +/- 8.918367
 
@@
 
-lmD: 0.003266 +/- 0.000271
+lmD: 0.003302 +/- 0.00027
 
-lmY: 0.003266 +/- 0.000271
+lmY: 0.003302 +/- 0.00027
 
-Arima: 0.003291 +/- 0.000364
+Arima: 0.003326 +/- 0.000357
 
@@
 
-lmD: 0.001715 +/- 0.000278
+lmD: 0.001743 +/- 0.000278
 
-lmY: 0.001715 +/- 0.000278
+lmY: 0.001743 +/- 0.000278
 
-Arima: 0.001886 +/- 0.000465
+Arima: 0.001906 +/- 0.000459
 
@@
 
-lmD: 0.001677 +/- 0.000314
+lmD: 0.001718 +/- 0.000312
 
-lmY: 0.001677 +/- 0.000314
+lmY: 0.001718 +/- 0.000312
 
-Arima: 0.001849 +/- 0.000512
+Arima: 0.001883 +/- 0.000503
 
@@
 
-lmD: 0.00184 +/- 0.000301
+lmD: 0.001896 +/- 0.000307
 
-lmY: 0.00184 +/- 0.000301
+lmY: 0.001896 +/- 0.000307
 
-Arima: 0.00184 +/- 0.000473
+Arima: 0.001896 +/- 0.000479
 
@@
 
-lmD: 0.001768 +/- 0.000292
+lmD: 0.001823 +/- 0.000299
 
-lmY: 0.001768 +/- 0.000292
+lmY: 0.001823 +/- 0.000299
 
-Arima: 0.001768 +/- 0.000451
+Arima: 0.001823 +/- 0.00046
 
@@
 
-lmD: 0.002432 +/- 0.000235
+lmD: 0.002414 +/- 0.000233
 
-lmY: 0.002432 +/- 0.000235
+lmY: 0.002414 +/- 0.000233
 
-Arima: 0.002432 +/- 0.000369
+Arima: 0.002414 +/- 0.000362
 
@@
 
-lmD: 0.002624 +/- 0.000229
+lmD: 0.002624 +/- 0.000228
 
-lmY: 0.002624 +/- 0.000229
+lmY: 0.002624 +/- 0.000228
 
-Arima: 0.002624 +/- 0.000346
+Arima: 0.002624 +/- 0.000339
 
@@
 
-lmD: 0.977006 +/- 0.143935
+lmD: 0.988112 +/- 0.144355
 
-lmY: 0.977029 +/- 0.143937
+lmY: 0.988134 +/- 0.144358
 
-Arima: 1.040956 +/- 0.218636
+Arima: 1.051184 +/- 0.218585
 
@@
 
-lmD: 0.817503 +/- 0.103432
+lmD: 0.816129 +/- 0.101923
 
-lmY: 0.817514 +/- 0.103434
+lmY: 0.816139 +/- 0.101925
 
-Arima: 0.817505 +/- 0.120041
+Arima: 0.816132 +/- 0.119665
 
@@
 
-lmD: 0.216071 +/- 0.038072
+lmD: 0.215792 +/- 0.037414
 
-lmY: 0.216075 +/- 0.038073
+lmY: 0.215795 +/- 0.037415
 
-Arima: 0.216075 +/- 0.041418
+Arima: 0.215796 +/- 0.040986
 
@@
 
-lmD: 0.190931 +/- 0.037875
+lmD: 0.181869 +/- 0.03711
 
-lmY: 0.190936 +/- 0.037876
+lmY: 0.181874 +/- 0.037111
 
-Arima: 0.190936 +/- 0.040087
+Arima: 0.181874 +/- 0.039209
 
@@
 
-lmD: 0.485676 +/- 0.046388
+lmD: 0.481659 +/- 0.045723
 
-lmY: 0.485682 +/- 0.046389
+lmY: 0.481664 +/- 0.045724
 
-Arima: 0.485682 +/- 0.055179
+Arima: 0.481665 +/- 0.054201
 
@@
 
-lmD: -0.00734 +/- 0.019077
+lmD: 0.001364 +/- 0.01878
 
-lmY: -0.007339 +/- 0.019077
+lmY: 0.001365 +/- 0.018781
 
-Arima: -0.007339 +/- 0.019267
+Arima: 0.001365 +/- 0.01932
 
@@
 
-lmD: -0.027816 +/- 0.017696
+lmD: -0.018679 +/- 0.017374
 
-lmY: -0.027816 +/- 0.017696
+lmY: -0.018679 +/- 0.017374
 
-Arima: -0.027816 +/- 0.017858
+Arima: -0.018679 +/- 0.017837
 
@@
 
-lmD: 0.49203 +/- 0.073274
+lmD: 0.496018 +/- 0.071855
 
-lmY: 0.492037 +/- 0.073275
+lmY: 0.496024 +/- 0.071857
 
-Arima: 0.492032 +/- 0.081403
+Arima: 0.496022 +/- 0.080622
 
@@
 
-lmD: 0.595557 +/- 0.083417
+lmD: 0.597354 +/- 0.08202
 
-lmY: 0.595566 +/- 0.083419
+lmY: 0.597361 +/- 0.082022
 
-Arima: 0.59556 +/- 0.094857
+Arima: 0.597357 +/- 0.094227
 
@@
 
-lmD: 1.467857 +/- 0.152656
+lmD: 1.432631 +/- 0.148944
 
-lmY: 1.46788 +/- 0.152659
+lmY: 1.432652 +/- 0.148947
 
-Arima: 1.467877 +/- 0.18431
+Arima: 1.432652 +/- 0.180994
 
@@
 
-lmD: 0.001336 +/- 0.000137
+lmD: 0.001383 +/- 0.000137
 
-lmY: 0.001336 +/- 0.000137
+lmY: 0.001383 +/- 0.000137
 
-Arima: 0.001336 +/- 0.000157
+Arima: 0.001383 +/- 0.00016
 
@@
 
-lmD: 0.000423 +/- 5.9e-05
+lmD: 0.00044 +/- 6.1e-05
 
-lmY: 0.000423 +/- 5.9e-05
+lmY: 0.00044 +/- 6.1e-05
 
-Arima: 0.000423 +/- 6.7e-05
+Arima: 0.00044 +/- 7e-05
 
@@
 
-lmD: 0.000372 +/- 6.1e-05
+lmD: 0.000363 +/- 6.4e-05
 
-lmY: 0.000372 +/- 6.1e-05
+lmY: 0.000363 +/- 6.4e-05
 
-Arima: 0.000372 +/- 6.8e-05
+Arima: 0.000363 +/- 7.2e-05
 
@@
 
-lmD: 2.1e-05 +/- 3.2e-05
+lmD: 4e-05 +/- 3.3e-05
 
-lmY: 2.1e-05 +/- 3.2e-05
+lmY: 4e-05 +/- 3.3e-05
 
-Arima: 2.1e-05 +/- 3.6e-05
+Arima: 4e-05 +/- 3.8e-05
 
@@
 
-lmD: -1.2e-05 +/- 2.9e-05
+lmD: 5e-06 +/- 2.9e-05
 
-lmY: -1.2e-05 +/- 2.9e-05
+lmY: 5e-06 +/- 2.9e-05
 
-Arima: -1.2e-05 +/- 3.4e-05
+Arima: 5e-06 +/- 3.4e-05
 
@@
 
-lmD: 0.000922 +/- 0.000106
+lmD: 0.000968 +/- 0.000108
 
-lmY: 0.000922 +/- 0.000106
+lmY: 0.000968 +/- 0.000108
 
-Arima: 0.000922 +/- 0.00012
+Arima: 0.000968 +/- 0.000125
 
@@
 
-lmD: 0.001074 +/- 0.000117
+lmD: 0.001126 +/- 0.000119
 
-lmY: 0.001074 +/- 0.000117
+lmY: 0.001126 +/- 0.000119
 
-Arima: 0.001074 +/- 0.000134
+Arima: 0.001126 +/- 0.000138
 
@@
 
-lmD: 0.036561 +/- 0.003622
+lmD: 0.036713 +/- 0.003659
 
-lmY: 0.036562 +/- 0.003622
+lmY: 0.036714 +/- 0.003659
 
-Arima: 0.036562 +/- 0.004204
+Arima: 0.036714 +/- 0.00425
 
@@
 
-lmD: 0.187208 +/- 0.249476
+lmD: 0.203753 +/- 0.246152
 
-lmY: 0.187246 +/- 0.24948
+lmY: 0.20379 +/- 0.246156
 
-Arima: 0.171775 +/- 0.364628
+Arima: 0.191314 +/- 0.355242
 
@@
 
-lmD: 0.049774 +/- 0.192505
+lmD: 0.066924 +/- 0.186933
 
-lmY: 0.049798 +/- 0.192508
+lmY: 0.066947 +/- 0.186936
 
-Arima: 0.008548 +/- 0.346363
+Arima: 0.031787 +/- 0.332858
 
@@
 
-lmD: 0.091248 +/- 0.191453
+lmD: 0.108038 +/- 0.185587
 
-lmY: 0.091272 +/- 0.191456
+lmY: 0.10806 +/- 0.18559
 
-Arima: 0.049975 +/- 0.33542
+Arima: 0.07227 +/- 0.320898
 
@@
 
-lmD: -0.069532 +/- 0.179279
+lmD: -0.047504 +/- 0.172428
 
-lmY: -0.06952 +/- 0.179282
+lmY: -0.047493 +/- 0.17243
 
-Arima: -0.124647 +/- 0.339466
+Arima: -0.093727 +/- 0.32618
 
@@
 
-lmD: -0.089703 +/- 0.178956
+lmD: -0.06805 +/- 0.171992
 
-lmY: -0.089692 +/- 0.178959
+lmY: -0.068039 +/- 0.171995
 
-Arima: -0.144328 +/- 0.338161
+Arima: -0.113836 +/- 0.324815
 
@@
 
-lmD: 0.16704 +/- 0.22968
+lmD: 0.1818 +/- 0.225799
 
-lmY: 0.167077 +/- 0.229683
+lmY: 0.181836 +/- 0.225802
 
-Arima: 0.146398 +/- 0.353614
+Arima: 0.164846 +/- 0.343081
 
@@
 
-lmD: 0.17703 +/- 0.238162
+lmD: 0.192758 +/- 0.234509
 
-lmY: 0.177067 +/- 0.238165
+lmY: 0.192794 +/- 0.234513
 
-Arima: 0.158966 +/- 0.358093
+Arima: 0.178049 +/- 0.348128
 
@@
 
-lmD: 0.368357 +/- 0.253498
+lmD: 0.372906 +/- 0.252445
 
-lmY: 0.368383 +/- 0.253502
+lmY: 0.372932 +/- 0.252449
 
-Arima: 0.36844 +/- 0.258271
+Arima: 0.373033 +/- 0.257109
 
@@
 
-lmD: 0.000508 +/- 0.000281
+lmD: 0.000567 +/- 0.000291
 
-lmY: 0.000509 +/- 0.000281
+lmY: 0.000567 +/- 0.000291
 
-Arima: 0.000508 +/- 0.000318
+Arima: 0.000567 +/- 0.000322
 
@@
 
-lmD: 0.000356 +/- 0.000214
+lmD: 0.000397 +/- 0.000226
 
-lmY: 0.000356 +/- 0.000214
+lmY: 0.000397 +/- 0.000226
 
-Arima: 0.000349 +/- 0.000265
+Arima: 0.000393 +/- 0.000269
 
@@
 
-lmD: 0.000399 +/- 0.000221
+lmD: 0.000416 +/- 0.000234
 
-lmY: 0.000399 +/- 0.000221
+lmY: 0.000416 +/- 0.000234
 
-Arima: 0.000392 +/- 0.00027
+Arima: 0.000413 +/- 0.000274
 
@@
 
-lmD: 0.000168 +/- 0.000199
+lmD: 0.000209 +/- 0.000208
 
-lmY: 0.000168 +/- 0.000199
+lmY: 0.000209 +/- 0.000208
 
-Arima: 0.000157 +/- 0.000257
+Arima: 0.000203 +/- 0.000261
 
@@
 
-lmD: 0.000155 +/- 0.000199
+lmD: 0.000194 +/- 0.000208
 
-lmY: 0.000155 +/- 0.000199
+lmY: 0.000194 +/- 0.000208
 
-Arima: 0.000144 +/- 0.000256
+Arima: 0.000187 +/- 0.000261
 
@@
 
-lmD: 0.000509 +/- 0.000261
+lmD: 0.000565 +/- 0.000272
 
-lmY: 0.000509 +/- 0.000261
+lmY: 0.000565 +/- 0.000272
 
-Arima: 0.000508 +/- 3e-04
+Arima: 0.000565 +/- 0.000304
 
@@
 
-lmD: 0.00051 +/- 0.00027
+lmD: 0.000571 +/- 0.00028
 
-lmY: 0.00051 +/- 0.00027
+lmY: 0.000571 +/- 0.00028
 
-Arima: 0.000509 +/- 0.000307
+Arima: 0.000571 +/- 0.000312
 
@@
 
-lmD: 0.008776 +/- 0.005507
+lmD: 0.008989 +/- 0.005522
 
-lmY: 0.008777 +/- 0.005507
+lmY: 0.008989 +/- 0.005522
 
-Arima: 0.008799 +/- 0.005722
+Arima: 0.009015 +/- 0.00575
 
@@
 
-Arima: 0.216075 +/- 0.041418
+Arima: 0.215796 +/- 0.040986
 
@@
 \begin{verbatim}
-Warning: Removed 12 rows containing non-finite outside the scale range
+Warning: Removed 16 rows containing non-finite outside the scale range
 (`stat_bin2d()`).
-\end{verbatim}
-
-\begin{verbatim}
-Warning: Removed 2 rows containing missing values or values outside the scale
-range (`geom_tile()`).
 \end{verbatim}
@@
 \begin{verbatim}
-Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
-Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
+Warning: Removed 16 rows containing non-finite outside the scale range
+(`stat_bin2d()`).
+\end{verbatim}
+
+\begin{verbatim}
+Warning: Removed 1 row containing missing values or values outside the scale
+range (`geom_tile()`).
 \end{verbatim}
@@
 \begin{verbatim}
-Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
-Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
+Warning: Removed 16 rows containing non-finite outside the scale range
+(`stat_bin2d()`).
 \end{verbatim}
@@
 
-lmY: 341.6364 +/- 36.57038
+lmY: 339.1753 +/- 35.87673
 
@@
 
-lmY: 122.2229 +/- 11.42113
+lmY: 123.4768 +/- 11.47021
 
@@
 
-lmY: 0.232986 +/- 0.055703
+lmY: 0.228163 +/- 0.054288
 
@@
 
-lmY: 0.183685 +/- 0.040872
+lmY: 0.174806 +/- 0.039192
 
@@
 \begin{verbatim}
-2024-04-14 00:48:00.3 athan@tyler GHI_enh_04_investigate.R 1.346105 mins
+2024-04-19 10:28:33.6 athan@sagan GHI_enh_04_investigate.R 0.788870 mins
 \end{verbatim}

### 2024-04-19 article/article.tex
Commit 2024-04-19 14:14

@@
 \text{CE} : \text{E}_\text{i} > \text{E}_\text{CSlim,i}, \text{where} \begin{cases}
- \text{E}_\text{CSlim,i} = 1.05 \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq 60^\circ$}\\
-\text{E}_\text{CSlim,i} = \left ({ 1.18 + \frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ 78^\circ > \theta > 60^\circ$}\\
+ \text{E}_\text{CSlim,i} = 1.03 \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq 90^\circ$}\\
+\text{E}_\text{CSlim,i} = \left ({ 1.05 + \frac{1.03 - 1.05}{90 - 78} \cdot (\theta- 78) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ 78^\circ > \theta > 90^\circ$}\\
 \text{Excluded measurements}, & \theta > 78^\circ
@@
 Our dataset, after the data selection processing, consists of 6144534
-records of GHI, of which \(1.799\,\%\) are CE and \(0.036\,\%\) are ECE
+records of GHI, of which \(1.824\,\%\) are CE and \(0.036\,\%\) are ECE
 events. The highest GHI recorder was \(1416.6\,W/m^2\) on 24~May 2007.
-The absolute stronger CE event had an OIR of \(341.79\,W/m^2\) on 15~May
-2014. The relative stronger CE event was \(54\,\%\) above the clear sky
-threshold, on 28~October 2016.
+The absolute stronger CE event had an OIR of \(345.53\,W/m^2\) on 24~May
+2007. The relative stronger CE event was \(51.6\,\%\) above the clear
+sky threshold, on 28~October 2016.
 
@@
 \citep{RCT2023}. The trends are reported together with the \(2\sigma\)
-error. We observe an increase of \(0.216\pm 0.083\,W/m^2/y\) on the mean
+error. We observe an increase of \(0.216\pm 0.082\,W/m^2/y\) on the mean
 OIR.
@@
 The annual number of CE occurrences, shows a steady increase of
-\(122.2\pm 22.8\,\text{cases}/y\)
+\(123.5\pm 22.9\,\text{cases}/y\)
 (Figure\nobreakspace{}\ref{fig:P-energy-N}). We have to note that the
@@
 Subsequently, the mean annual increase of energy due to CE events is
-\(341.6\pm 73.1\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
+\(339.2\pm 71.8\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
 the trend of the number of occurrences.
@@
 Thus, a CEG consists of one or more successive CE cases, and can have a
-duration of multiple of minutes. We have identified 29009 groups, where
+duration of multiple of minutes. We have identified 28939 groups, where
 the group with the longest duration lasted 140 minutes on 07~July 2013.

### 2024-04-21 GHI_enh_03_process.tex
Commit 2024-04-21 18:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-19}
+\date{2024-04-21}
 
@@
 }
+\begin{verbatim}
+
+ USING CSMODE: Low_B.Low_W
+
+C4 factor: 1.03 
+C4 offset: 15 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with extreme cases day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with strong enhancement day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with sunny day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with sunny enhancement day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with cloudy day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with random day 
+\end{verbatim}
+
+\begin{verbatim}
+
+\FloatBarrier
+
+## Days with manual test days 
+\end{verbatim}
+
+\begin{verbatim}
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
+i Please use the `legend.position.inside` argument of `theme()` instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
+\begin{verbatim}
+2024-04-21 13:51:37.8 athan@sagan GHI_enh_02_ID_CE.R 14.833272 mins
+\end{verbatim}
+
 Alpha * HAU is CS\_ref
@@
 \begin{verbatim}
-2024-04-19 10:26:46.8 athan@sagan GHI_enh_03_process.R 3.634787 mins
+2024-04-21 13:57:31.4 athan@sagan GHI_enh_02_ID_CE.R 3.765186 mins
 \end{verbatim}

### 2024-04-21 GHI_enh_03_process.tex
Commit 2024-04-21 22:14

@@
 
-C4 factor: 1.03 
+C4 factor: 1.04 
 C4 offset: 15 
@@
 \begin{verbatim}
-2024-04-21 13:51:37.8 athan@sagan GHI_enh_02_ID_CE.R 14.833272 mins
+2024-04-21 16:10:56.4 athan@tyler GHI_enh_02_ID_CE.R 27.296893 mins
 \end{verbatim}
@@
     Min      1Q  Median      3Q     Max 
--384.81 -144.57  -53.50   96.68  768.76
+-349.43 -124.67  -47.48   83.61  668.69
 
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      -9.187e+01  4.952e+01  -1.855   0.0644 .  
-as.numeric(Date)  3.286e-07  3.958e-08   8.302 2.08e-15 ***
+(Intercept)      -8.500e+01  4.348e+01  -1.955   0.0514 .  
+as.numeric(Date)  2.911e-07  3.473e-08   8.383 1.18e-15 ***
 ---
@@
 
-Residual standard error: 211.4 on 361 degrees of freedom
-Multiple R-squared:  0.1603,    Adjusted R-squared:  0.158 
-F-statistic: 68.92 on 1 and 361 DF,  p-value: 2.077e-15
+Residual standard error: 185 on 360 degrees of freedom
+Multiple R-squared:  0.1633,    Adjusted R-squared:  0.161 
+F-statistic: 70.27 on 1 and 360 DF,  p-value: 1.182e-15
 \end{verbatim}
@@
                     Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       -9.187e+01  4.952e+01  -1.855   0.0644 .  
-ST_E_monthly$Date  3.286e-07  3.958e-08   8.302 2.08e-15 ***
+(Intercept)       -8.500e+01  4.348e+01  -1.955   0.0514 .  
+ST_E_monthly$Date  2.911e-07  3.473e-08   8.383 1.18e-15 ***
 ---
@@
 \begin{verbatim}
-2024-04-21 13:57:31.4 athan@sagan GHI_enh_02_ID_CE.R 3.765186 mins
+2024-04-21 16:22:21.3 athan@tyler GHI_enh_02_ID_CE.R 8.808619 mins
 \end{verbatim}

### 2024-04-22 article/article.tex
Commit 2024-04-22 06:14

--- 2024-04-15 article/article.tex
@@
 \text{CE} : \text{E}_\text{i} > \text{E}_\text{CSlim,i}, \text{where} \begin{cases}
- \text{E}_\text{CSlim,i} = 1.05 \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq 60^\circ$}\\
-\text{E}_\text{CSlim,i} = \left ({ 1.18 + \frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ 78^\circ > \theta > 60^\circ$}\\
+ \text{E}_\text{CSlim,i} = 1.04 \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq 90^\circ$}\\
+\text{E}_\text{CSlim,i} = \left ({ 1.04 + \frac{1.04 - 1.04}{90 - 78} \cdot (\theta- 78) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ 78^\circ > \theta > 90^\circ$}\\
 \text{Excluded measurements}, & \theta > 78^\circ
@@
 Our dataset, after the data selection processing, consists of 6144534
-records of GHI, of which \(1.799\,\%\) are CE and \(0.036\,\%\) are ECE
+records of GHI, of which \(1.592\,\%\) are CE and \(0.036\,\%\) are ECE
 events. The highest GHI recorder was \(1416.6\,W/m^2\) on 24~May 2007.
-The absolute stronger CE event had an OIR of \(341.79\,W/m^2\) on 15~May
-2014. The relative stronger CE event was \(54\,\%\) above the clear sky
-threshold, on 28~October 2016.
+The absolute stronger CE event had an OIR of \(335.28\,W/m^2\) on 24~May
+2007. The relative stronger CE event was \(50.2\,\%\) above the clear
+sky threshold, on 28~October 2016.
 
@@
 \citep{RCT2023}. The trends are reported together with the \(2\sigma\)
-error. We observe an increase of \(0.216\pm 0.083\,W/m^2/y\) on the mean
+error. We observe an increase of \(0.202\pm 0.083\,W/m^2/y\) on the mean
 OIR.
@@
 long term CE trends. Hence, we calculated the annual values from the
-one-minute measurements. The trend of OIR is \(0.23\pm 0.11\,W/m^2/y\)
+one-minute measurements. The trend of OIR is \(0.22\pm 0.11\,W/m^2/y\)
 (Figure\nobreakspace{}\ref{fig:P-energy-mean}), but this value alone is
@@
 The annual number of CE occurrences, shows a steady increase of
-\(122.2\pm 22.8\,\text{cases}/y\)
+\(110.1\pm 20.3\,\text{cases}/y\)
 (Figure\nobreakspace{}\ref{fig:P-energy-N}). We have to note that the
@@
 Subsequently, the mean annual increase of energy due to CE events is
-\(341.6\pm 73.1\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
+\(293.3\pm 63.1\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
 the trend of the number of occurrences.
@@
 Thus, a CEG consists of one or more successive CE cases, and can have a
-duration of multiple of minutes. We have identified 29009 groups, where
+duration of multiple of minutes. We have identified 26042 groups, where
 the group with the longest duration lasted 140 minutes on 07~July 2013.

### 2024-04-22 GHI_enh_04_investigate.tex
Commit 2024-04-22 06:14

@@
 
-lmD: 1.552161 +/- 0.104876
+lmD: 1.534136 +/- 0.10269
 
-lmY: 1.552176 +/- 0.104878
+lmY: 1.534151 +/- 0.102692
 
-Arima: 1.552549 +/- 0.14034
+Arima: 1.534524 +/- 0.137014
 
@@
 
-lmD: 0.954836 +/- 0.154734
+lmD: 0.957882 +/- 0.154677
 
-lmY: 0.954859 +/- 0.154736
+lmY: 0.957905 +/- 0.15468
 
-Arima: 1.024507 +/- 0.23503
+Arima: 1.026834 +/- 0.234823
 
@@
 
-lmD: 1.088987 +/- 0.16743
+lmD: 1.097965 +/- 0.167082
 
-lmY: 1.089013 +/- 0.167433
+lmY: 1.097991 +/- 0.167085
 
-Arima: 1.160151 +/- 0.24838
+Arima: 1.168104 +/- 0.247425
 
@@
 
-lmD: 1.050842 +/- 0.240164
+lmD: 1.054627 +/- 0.240574
 
-lmY: 1.050851 +/- 0.240168
+lmY: 1.054636 +/- 0.240578
 
-Arima: 1.050895 +/- 0.364666
+Arima: 1.054681 +/- 0.36529
 
@@
 
-lmD: 0.958299 +/- 0.253655
+lmD: 0.96011 +/- 0.254278
 
-lmY: 0.958309 +/- 0.25366
+lmY: 0.96012 +/- 0.254282
 
-Arima: 0.958355 +/- 0.388216
+Arima: 0.960167 +/- 0.389374
 
@@
 
-lmD: 1.089066 +/- 0.07424
+lmD: 1.084083 +/- 0.073658
 
-lmY: 1.089079 +/- 0.074241
+lmY: 1.084096 +/- 0.073659
 
-Arima: 1.089082 +/- 0.109498
+Arima: 1.0841 +/- 0.108761
 
@@
 
-lmD: 1.136243 +/- 0.070602
+lmD: 1.123441 +/- 0.069672
 
-lmY: 1.136256 +/- 0.070603
+lmY: 1.123454 +/- 0.069673
 
-Arima: 1.136263 +/- 0.100583
+Arima: 1.123462 +/- 0.099367
 
@@
 
-lmD: 33.75698 +/- 5.702807
+lmD: 33.98221 +/- 5.725078
 
-lmY: 33.75752 +/- 5.702906
+lmY: 33.98275 +/- 5.725178
 
-Arima: 33.816428 +/- 8.918367
+Arima: 34.039551 +/- 9.00373
 
@@
 
-lmD: 0.003302 +/- 0.00027
+lmD: 0.003272 +/- 0.000268
 
-lmY: 0.003302 +/- 0.00027
+lmY: 0.003272 +/- 0.000268
 
-Arima: 0.003326 +/- 0.000357
+Arima: 0.003296 +/- 0.000354
 
@@
 
-lmD: 0.001743 +/- 0.000278
+lmD: 0.001727 +/- 0.000275
 
-lmY: 0.001743 +/- 0.000278
+lmY: 0.001727 +/- 0.000275
 
-Arima: 0.001906 +/- 0.000459
+Arima: 0.001888 +/- 0.000454
 
@@
 
-lmD: 0.001718 +/- 0.000312
+lmD: 0.001702 +/- 0.000309
 
-lmY: 0.001718 +/- 0.000312
+lmY: 0.001702 +/- 0.000309
 
-Arima: 0.001883 +/- 0.000503
+Arima: 0.001865 +/- 0.000498
 
@@
 
-lmD: 0.001896 +/- 0.000307
+lmD: 0.001878 +/- 0.000305
 
-lmY: 0.001896 +/- 0.000307
+lmY: 0.001878 +/- 0.000305
 
-Arima: 0.001896 +/- 0.000479
+Arima: 0.001878 +/- 0.000475
 
@@
 
-lmD: 0.001823 +/- 0.000299
+lmD: 0.001807 +/- 0.000297
 
-lmY: 0.001823 +/- 0.000299
+lmY: 0.001807 +/- 0.000297
 
-Arima: 0.001823 +/- 0.00046
+Arima: 0.001807 +/- 0.000456
 
@@
 
-lmD: 0.002414 +/- 0.000233
+lmD: 0.002392 +/- 0.000231
 
-lmY: 0.002414 +/- 0.000233
+lmY: 0.002392 +/- 0.000231
 
-Arima: 0.002414 +/- 0.000362
+Arima: 0.002392 +/- 0.000359
 
@@
 
-lmD: 0.002624 +/- 0.000228
+lmD: 0.0026 +/- 0.000226
 
-lmY: 0.002624 +/- 0.000228
+lmY: 0.0026 +/- 0.000226
 
-Arima: 0.002624 +/- 0.000339
+Arima: 0.0026 +/- 0.000336
 
@@
 
-lmD: 0.988112 +/- 0.144355
+lmD: 0.982152 +/- 0.142979
 
-lmY: 0.988134 +/- 0.144358
+lmY: 0.982174 +/- 0.142982
 
-Arima: 1.051184 +/- 0.218585
+Arima: 1.043911 +/- 0.216442
 
@@
 
-lmD: 0.816129 +/- 0.101923
+lmD: 0.76413 +/- 0.10147
 
-lmY: 0.816139 +/- 0.101925
+lmY: 0.764141 +/- 0.101472
 
-Arima: 0.816132 +/- 0.119665
+Arima: 0.764136 +/- 0.117502
 
@@
 
-lmD: 0.215792 +/- 0.037414
+lmD: 0.202029 +/- 0.037949
 
-lmY: 0.215795 +/- 0.037415
+lmY: 0.202033 +/- 0.03795
 
-Arima: 0.215796 +/- 0.040986
+Arima: 0.202033 +/- 0.041317
 
@@
 
-lmD: 0.181869 +/- 0.03711
+lmD: 0.164435 +/- 0.03794
 
-lmY: 0.181874 +/- 0.037111
+lmY: 0.164439 +/- 0.037941
 
-Arima: 0.181874 +/- 0.039209
+Arima: 0.164439 +/- 0.040154
 
@@
 
-lmD: 0.481659 +/- 0.045723
+lmD: 0.430568 +/- 0.042844
 
-lmY: 0.481664 +/- 0.045724
+lmY: 0.430573 +/- 0.042845
 
-Arima: 0.481665 +/- 0.054201
+Arima: 0.430575 +/- 0.050183
 
@@
 
-lmD: 0.001364 +/- 0.01878
+lmD: -0.009715 +/- 0.019808
 
-lmY: 0.001365 +/- 0.018781
+lmY: -0.009713 +/- 0.019809
 
-Arima: 0.001365 +/- 0.01932
+Arima: -0.009713 +/- 0.019969
 
@@
 
-lmD: -0.018679 +/- 0.017374
+lmD: -0.024545 +/- 0.018498
 
-lmY: -0.018679 +/- 0.017374
+lmY: -0.024544 +/- 0.018499
 
-Arima: -0.018679 +/- 0.017837
+Arima: -0.024544 +/- 0.018581
 
@@
 
-lmD: 0.496018 +/- 0.071855
+lmD: 0.467007 +/- 0.072175
 
-lmY: 0.496024 +/- 0.071857
+lmY: 0.467013 +/- 0.072176
 
-Arima: 0.496022 +/- 0.080622
+Arima: 0.467011 +/- 0.080184
 
@@
 
-lmD: 0.597354 +/- 0.08202
+lmD: 0.567078 +/- 0.082222
 
-lmY: 0.597361 +/- 0.082022
+lmY: 0.567087 +/- 0.082223
 
-Arima: 0.597357 +/- 0.094227
+Arima: 0.567084 +/- 0.093419
 
@@
 
-lmD: 1.432631 +/- 0.148944
+lmD: 1.246547 +/- 0.136785
 
-lmY: 1.432652 +/- 0.148947
+lmY: 1.246567 +/- 0.136788
 
-Arima: 1.432652 +/- 0.180994
+Arima: 1.246568 +/- 0.164233
 
@@
 
-lmD: 0.001383 +/- 0.000137
+lmD: 0.001291 +/- 0.000137
 
-lmY: 0.001383 +/- 0.000137
+lmY: 0.001291 +/- 0.000137
 
-Arima: 0.001383 +/- 0.00016
+Arima: 0.001291 +/- 0.000158
 
@@
 
-lmD: 0.00044 +/- 6.1e-05
+lmD: 0.000409 +/- 6.1e-05
 
-lmY: 0.00044 +/- 6.1e-05
+lmY: 0.000409 +/- 6.1e-05
 
-Arima: 0.00044 +/- 7e-05
+Arima: 0.000409 +/- 7e-05
 
@@
 
-lmD: 0.000363 +/- 6.4e-05
+lmD: 0.00033 +/- 6.4e-05
 
-lmY: 0.000363 +/- 6.4e-05
+lmY: 0.00033 +/- 6.4e-05
 
-Arima: 0.000363 +/- 7.2e-05
+Arima: 0.00033 +/- 7.2e-05
 
@@
 
-lmD: 4e-05 +/- 3.3e-05
+lmD: 1.8e-05 +/- 3.3e-05
 
-lmY: 4e-05 +/- 3.3e-05
+lmY: 1.8e-05 +/- 3.3e-05
 
-Arima: 4e-05 +/- 3.8e-05
+Arima: 1.8e-05 +/- 3.8e-05
 
@@
 
-lmD: 5e-06 +/- 2.9e-05
+lmD: -8e-06 +/- 3e-05
 
-lmY: 5e-06 +/- 2.9e-05
+lmY: -8e-06 +/- 3e-05
 
-Arima: 5e-06 +/- 3.4e-05
+Arima: -8e-06 +/- 3.5e-05
 
@@
 
-lmD: 0.000968 +/- 0.000108
+lmD: 0.00091 +/- 0.000108
 
-lmY: 0.000968 +/- 0.000108
+lmY: 0.00091 +/- 0.000108
 
-Arima: 0.000968 +/- 0.000125
+Arima: 0.00091 +/- 0.000124
 
@@
 
-lmD: 0.001126 +/- 0.000119
+lmD: 0.001059 +/- 0.000118
 
-lmY: 0.001126 +/- 0.000119
+lmY: 0.001059 +/- 0.000118
 
-Arima: 0.001126 +/- 0.000138
+Arima: 0.001059 +/- 0.000137
 
@@
 
-lmD: 0.036713 +/- 0.003659
+lmD: 0.031908 +/- 0.003379
 
-lmY: 0.036714 +/- 0.003659
+lmY: 0.031908 +/- 0.003379
 
-Arima: 0.036714 +/- 0.00425
+Arima: 0.031908 +/- 0.003889
 
@@
 
-lmD: 0.203753 +/- 0.246152
+lmD: 0.210914 +/- 0.239629
 
-lmY: 0.20379 +/- 0.246156
+lmY: 0.21095 +/- 0.239633
 
-Arima: 0.191314 +/- 0.355242
+Arima: 0.199623 +/- 0.33989
 
@@
 
-lmD: 0.066924 +/- 0.186933
+lmD: 0.075139 +/- 0.179414
 
-lmY: 0.066947 +/- 0.186936
+lmY: 0.075162 +/- 0.179417
 
-Arima: 0.031787 +/- 0.332858
+Arima: 0.041751 +/- 0.315453
 
@@
 
-lmD: 0.108038 +/- 0.185587
+lmD: 0.116601 +/- 0.178114
 
-lmY: 0.10806 +/- 0.18559
+lmY: 0.116622 +/- 0.178117
 
-Arima: 0.07227 +/- 0.320898
+Arima: 0.082858 +/- 0.303922
 
@@
 
-lmD: -0.047504 +/- 0.172428
+lmD: -0.039715 +/- 0.164546
 
-lmY: -0.047493 +/- 0.17243
+lmY: -0.039705 +/- 0.164548
 
-Arima: -0.093727 +/- 0.32618
+Arima: -0.084179 +/- 0.309433
 
@@
 
-lmD: -0.06805 +/- 0.171992
+lmD: -0.059533 +/- 0.164108
 
-lmY: -0.068039 +/- 0.171995
+lmY: -0.059523 +/- 0.164111
 
-Arima: -0.113836 +/- 0.324815
+Arima: -0.103637 +/- 0.308351
 
@@
 
-lmD: 0.1818 +/- 0.225799
+lmD: 0.190061 +/- 0.219003
 
-lmY: 0.181836 +/- 0.225802
+lmY: 0.190097 +/- 0.219007
 
-Arima: 0.164846 +/- 0.343081
+Arima: 0.174594 +/- 0.326917
 
@@
 
-lmD: 0.192758 +/- 0.234509
+lmD: 0.200402 +/- 0.22785
 
-lmY: 0.192794 +/- 0.234513
+lmY: 0.200437 +/- 0.227854
 
-Arima: 0.178049 +/- 0.348128
+Arima: 0.187023 +/- 0.332301
 
@@
 
-lmD: 0.372906 +/- 0.252445
+lmD: 0.360189 +/- 0.242668
 
-lmY: 0.372932 +/- 0.252449
+lmY: 0.360214 +/- 0.242672
 
-Arima: 0.373033 +/- 0.257109
+Arima: 0.36031 +/- 0.247054
 
@@
 
-lmD: 0.000567 +/- 0.000291
+lmD: 0.000562 +/- 0.000289
 
-lmY: 0.000567 +/- 0.000291
+lmY: 0.000562 +/- 0.000289
 
-Arima: 0.000567 +/- 0.000322
+Arima: 0.000562 +/- 0.000319
 
@@
 
-lmD: 0.000397 +/- 0.000226
+lmD: 0.000393 +/- 0.000224
 
-lmY: 0.000397 +/- 0.000226
+lmY: 0.000393 +/- 0.000224
 
-Arima: 0.000393 +/- 0.000269
+Arima: 0.00039 +/- 0.000267
 
@@
 
-lmD: 0.000416 +/- 0.000234
+lmD: 0.000413 +/- 0.000232
 
-lmY: 0.000416 +/- 0.000234
+lmY: 0.000413 +/- 0.000232
 
-Arima: 0.000413 +/- 0.000274
+Arima: 0.000409 +/- 0.000272
 
@@
 
-lmD: 0.000209 +/- 0.000208
+lmD: 0.000208 +/- 0.000207
 
-lmY: 0.000209 +/- 0.000208
+lmY: 0.000208 +/- 0.000207
 
-Arima: 0.000203 +/- 0.000261
+Arima: 0.000201 +/- 0.000259
 
@@
 
-lmD: 0.000194 +/- 0.000208
+lmD: 0.000192 +/- 0.000206
 
-lmY: 0.000194 +/- 0.000208
+lmY: 0.000192 +/- 0.000206
 
-Arima: 0.000187 +/- 0.000261
+Arima: 0.000185 +/- 0.000259
 
@@
 
-lmD: 0.000565 +/- 0.000272
+lmD: 0.00056 +/- 0.000269
 
-lmY: 0.000565 +/- 0.000272
+lmY: 0.00056 +/- 0.000269
 
-Arima: 0.000565 +/- 0.000304
+Arima: 0.00056 +/- 0.000301
 
@@
 
-lmD: 0.000571 +/- 0.00028
+lmD: 0.000566 +/- 0.000278
 
-lmY: 0.000571 +/- 0.00028
+lmY: 0.000566 +/- 0.000278
 
-Arima: 0.000571 +/- 0.000312
+Arima: 0.000566 +/- 0.000309
 
@@
 
-lmD: 0.008989 +/- 0.005522
+lmD: 0.008619 +/- 0.005275
 
-lmY: 0.008989 +/- 0.005522
+lmY: 0.00862 +/- 0.005275
 
-Arima: 0.009015 +/- 0.00575
+Arima: 0.008644 +/- 0.005494
 
@@
 
-Arima: 0.215796 +/- 0.040986
+Arima: 0.202033 +/- 0.041317
 
@@
 \begin{verbatim}
-Warning: Removed 25 rows containing missing values or values outside the scale
+Warning: Removed 26 rows containing missing values or values outside the scale
 range (`geom_bar()`).
@@
 \begin{verbatim}
-Warning: Removed 16 rows containing non-finite outside the scale range
+Warning: Removed 13 rows containing non-finite outside the scale range
 (`stat_bin2d()`).
@@
 \begin{verbatim}
-Warning: Removed 1 row containing missing values or values outside the scale
+Warning: Removed 2 rows containing missing values or values outside the scale
 range (`geom_tile()`).
@@
 
-lmY: 339.1753 +/- 35.87673
+lmY: 293.3335 +/- 31.54861
 
@@
 
-lmY: 123.4768 +/- 11.47021
+lmY: 110.0865 +/- 10.13369
 
@@
 
-lmY: 0.228163 +/- 0.054288
+lmY: 0.220182 +/- 0.057217
 
@@
 
-lmY: 0.174806 +/- 0.039192
+lmY: 0.168073 +/- 0.041495
 
@@
 \begin{verbatim}
-2024-04-19 10:28:33.6 athan@sagan GHI_enh_04_investigate.R 0.788870 mins
+2024-04-21 18:52:46.0 athan@tyler GHI_enh_04_investigate.R 1.292554 mins
 \end{verbatim}

### 2024-04-23 GHI_enh_Aeronet.tex
Commit 2024-04-23 17:12

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-16}
+\date{2024-04-22}
 
@@
 \begin{verbatim}
-Warning: Invalid .internal.selfref detected and fixed by taking a (shallow)
-copy of the data.table so that := can add this new column by reference. At an
-earlier point, this data.table has been copied by R (or was created manually
-using structure() or similar). Avoid names<- and attr<- which in R currently
-(and oddly) may copy the whole data.table. Use set* syntax instead to avoid
-copying: ?set, ?setnames and ?setattr. If this message doesn't help, please
-report your use case to the data.table issue tracker so the root cause can be
-fixed or this message improved.
-\end{verbatim}
-
-\begin{verbatim}
 Cross over point: 2014.75 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-6} \end{center}
+
 \begin{verbatim}
@@
 \begin{verbatim}
-2024-04-16 14:12:41.9 athan@tyler GHI_enh_Aeronet.R 0.120263 mins
+2024-04-22 07:36:33.0 athan@tyler GHI_enh_Aeronet.R 0.673847 mins
 \end{verbatim}

### 2024-04-23 GHI_enh_Aeronet.R

@@ -155,20 +155,19 @@ write.csv(
 
 
 
-plot(AE1[, exp(-AOD_500nm), tsy])
+plot(AE1[, exp(-AOD_500nm), tsy],
+     ylab = "exp(-AOD_500nm)")
 abline(lm_transp_trend)
 plot(1993:2024, trans_trend(1993:2024), col = "red")
 
 # rm(AE1)
 
 
-min(AE1$tsy):max(AE1$tsy)
+# min(AE1$tsy):max(AE1$tsy)
 
 
 plot(min(AE1$tsy):max(AE1$tsy), trans_AOD(min(AE1$tsy):max(AE1$tsy)), col = "red")
 
-trans_AOD(min(AE1$tsy))
-trans_AOD(max(AE1$tsy))
 
 
 CS <- readRDS("./data/Model_CS_2.Rds")
@@ -177,9 +176,9 @@ CS$ticTime  <- NULL
 CS$tacTime  <- NULL
 CS$ID       <- NULL
 
-CS[sza == 17 & type == "Low B.Low W",]
+# CS[sza == 17 & type == "Low B.Low W",]
 
-min(unique(CS$sza))
+# min(unique(CS$sza))
 
 
 # LT <- readRDS("./data/lookuptable_datatable.Rds")
@@ -203,7 +202,7 @@ plot(AE1[, AOD_500nm, tsy])
 abline(lm_AOD_trend)
 points(AEY$meantsy, AEY$Mean500,   col = "red", pch = 19 )
 points(AEY$meantsy, AEY$Median500, col = "green", pch = 19 )
-
+title("Yearly means and median")
 
 
 
@@ -281,7 +280,7 @@ legend("top", lty = 1, bty = "n", lwd = 2, cex = 1,
          )
 )
 
-100 * fit[2] / amean
+# 100 * fit[2] / amean
 
 # From Stelios' paper 2007:
 # AOD @340 from Brewer 086

### 2024-04-23 GHI_enh_Aeronet.tex
Commit 2024-04-23 19:30

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-22}
+\date{2024-04-23}
 
@@
 
+\begin{verbatim}
+[1] "Month Exact" "SZA min"     "SZA mean"    "SZA median" 
+\end{verbatim}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-8} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-9} \end{center}
 
@@
 \begin{verbatim}
-2024-04-22 07:36:33.0 athan@tyler GHI_enh_Aeronet.R 0.673847 mins
+2024-04-23 15:57:24.4 athan@tyler GHI_enh_Aeronet.R 0.931960 mins
 \end{verbatim}

### 2024-04-25 GHI_enh_Aeronet.tex
Commit 2024-04-23 20:25
Commit 2024-04-25 10:14
Commit 2024-04-25 16:14
Commit 2024-04-25 22:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-23}
+\date{2024-04-25}
 
@@
 \begin{verbatim}
-[1] "Month Exact" "SZA min"     "SZA mean"    "SZA median" 
+[1] 1997
 \end{verbatim}
@@
 \begin{verbatim}
+[1] 2005.667
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-10} \end{center}
+
+\begin{verbatim}
 pdf 
@@
 \begin{verbatim}
-2024-04-23 15:57:24.4 athan@tyler GHI_enh_Aeronet.R 0.931960 mins
+2024-04-25 17:03:02.2 athan@tyler GHI_enh_Aeronet.R 0.813675 mins
 \end{verbatim}

### 2024-04-26 GHI_enh_Aeronet.tex
Commit 2024-04-27 02:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-25}
+\date{2024-04-26}
 
@@
 
-\begin{verbatim}
-pdf 
-  3 
-\end{verbatim}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-11} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-12} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-13} \end{center}
+
+SZA min : 0.00133216113167738
+
+SZA mean : 0.00192971268218197
+
+SZA median : 0.00178690927379885
+
+\newpage
+
+\begin{longtable}[]{@{}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2222}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1389}}@{}}
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\centering
+year
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+typer
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+MeanGlo
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+1997 & BR SZA median & 449.5 \\
+2005 & SZA median & 392.1 \\
+2005 & BR SZA median & 459.3 \\
+2006 & SZA median & 493.1 \\
+2007 & SZA median & 470.8 \\
+2008 & SZA median & 326.2 \\
+2011 & SZA median & 505.1 \\
+2012 & SZA median & 500.8 \\
+2013 & SZA median & 498.6 \\
+2014 & SZA median & 477.7 \\
+2015 & SZA median & 504.8 \\
+2016 & SZA median & 510.9 \\
+2017 & SZA median & 551.4 \\
+2018 & SZA median & 499.7 \\
+2019 & SZA median & 476 \\
+2020 & SZA median & 483.7 \\
+2021 & SZA median & 506 \\
+2022 & SZA median & 554.9 \\
+2023 & SZA median & 522.8 \\
+\end{longtable}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-1} \end{center}
+
+\newpage
+
+\begin{longtable}[]{@{}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1806}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1389}}@{}}
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\centering
+year
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+typer
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+MeanGlo
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+1997 & BR SZA min & 1055 \\
+2005 & SZA min & 668.3 \\
+2005 & BR SZA min & 1064 \\
+2006 & SZA min & 817.1 \\
+2007 & SZA min & 785.1 \\
+2008 & SZA min & 557.2 \\
+2011 & SZA min & 831.1 \\
+2012 & SZA min & 824.3 \\
+2013 & SZA min & 814 \\
+2014 & SZA min & 822.1 \\
+2015 & SZA min & 828.6 \\
+2016 & SZA min & 832.3 \\
+2017 & SZA min & 899.3 \\
+2018 & SZA min & 822.3 \\
+2019 & SZA min & 789.7 \\
+2020 & SZA min & 820.3 \\
+2021 & SZA min & 829.7 \\
+2022 & SZA min & 902.4 \\
+2023 & SZA min & 859.5 \\
+\end{longtable}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-2} \end{center}
+
+\newpage
+
+\begin{longtable}[]{@{}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1944}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1389}}@{}}
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\centering
+year
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+typer
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+MeanGlo
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+1997 & BR SZA mean & 497.3 \\
+2005 & SZA mean & 353.9 \\
+2005 & BR SZA mean & 507.1 \\
+2006 & SZA mean & 460.7 \\
+2007 & SZA mean & 434.8 \\
+2008 & SZA mean & 288.6 \\
+2011 & SZA mean & 476.1 \\
+2012 & SZA mean & 468.4 \\
+2013 & SZA mean & 468.5 \\
+2014 & SZA mean & 444.8 \\
+2015 & SZA mean & 472.3 \\
+2016 & SZA mean & 480.3 \\
+2017 & SZA mean & 520.9 \\
+2018 & SZA mean & 467.3 \\
+2019 & SZA mean & 440.6 \\
+2020 & SZA mean & 450.8 \\
+2021 & SZA mean & 473.5 \\
+2022 & SZA mean & 525.5 \\
+2023 & SZA mean & 490.7 \\
+\end{longtable}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-3} \end{center}
+
+null device
+1
 
@@
 
-\begin{verbatim}
-2024-04-25 17:03:02.2 athan@tyler GHI_enh_Aeronet.R 0.813675 mins
-\end{verbatim}
-
 \end{document}

### 2024-04-27 GHI_enh_CSid.tex
Commit 2024-04-27 20:14

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  a4paper,oneside]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{placeins}
\captionsetup{font=small}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Enhancement of SDR in Thessaloniki},
  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-27}

\begin{document}
\maketitle
\begin{abstract}
Study of GHI enchantment.
\end{abstract}

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\texttt{Low\_B.Low\_W.glo} has compensation for sun distance, TSI variation and Kurudz difference

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# keep only clear}
\NormalTok{DATA }\OtherTok{\textless{}{-}}\NormalTok{ DATA[TYPE }\SpecialCharTok{==} \StringTok{"Clear"}\NormalTok{]}

\FunctionTok{table}\NormalTok{(DATA}\SpecialCharTok{$}\NormalTok{TYPE)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}

  Clear 
2577597 
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{DATA }\OtherTok{\textless{}{-}}\NormalTok{ DATA[}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wattGLB)]}

\FunctionTok{hist}\NormalTok{(DATA}\SpecialCharTok{$}\NormalTok{ClearnessIndex\_C\_4)}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-1} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# Hard limits}
\NormalTok{DATA }\OtherTok{\textless{}{-}}\NormalTok{ DATA[ClearnessIndex\_C\_4 }\SpecialCharTok{\textgreater{}} \FloatTok{0.8}\NormalTok{ ]}
\NormalTok{DATA }\OtherTok{\textless{}{-}}\NormalTok{ DATA[ClearnessIndex\_C\_4 }\SpecialCharTok{\textless{}} \FloatTok{1.3}\NormalTok{ ]}

\NormalTok{DTdaily }\OtherTok{\textless{}{-}}\NormalTok{ DATA[,}
\NormalTok{                .(}
                  \AttributeTok{glo\_Sum   =} \FunctionTok{sum}\NormalTok{(Low\_B.Low\_W.glo),}
                  \AttributeTok{GLB\_Sum   =} \FunctionTok{sum}\NormalTok{(wattGLB),}
                  \AttributeTok{GLB\_N     =} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wattGLB)),}
                  \AttributeTok{DayLength =} \FunctionTok{max}\NormalTok{(DayLength),}
\NormalTok{                  .N}
\NormalTok{                ),}
\NormalTok{                by }\OtherTok{=}\NormalTok{ Day]}

\NormalTok{Day\_points }\OtherTok{\textless{}{-}} \DecValTok{30}

\NormalTok{DATA }\OtherTok{\textless{}{-}}\NormalTok{ DATA[ Day }\SpecialCharTok{\%in\%}\NormalTok{ DTdaily[GLB\_N }\SpecialCharTok{\textgreater{}}\NormalTok{ Day\_points, Day]]}

\FunctionTok{hist}\NormalTok{(DTdaily}\SpecialCharTok{$}\NormalTok{GLB\_N)}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-2} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{hist}\NormalTok{(DTdaily[, GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength])}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-3} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# plot(DTdaily[, GLB\_N/DayLength, Day])}
\FunctionTok{summary}\NormalTok{(DTdaily[, GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength])}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.001152 0.181870 0.422018 0.420691 0.657944 0.838020 
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# remove days with few relative data}
\NormalTok{Daytime\_Ratio }\OtherTok{\textless{}{-}} \FloatTok{0.3}

\NormalTok{DTdaily[GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength }\SpecialCharTok{\textless{}}\NormalTok{ Daytime\_Ratio, .N]}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
[1] 2932
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{DATA }\OtherTok{\textless{}{-}}\NormalTok{ DATA[Day }\SpecialCharTok{\%in\%}\NormalTok{ DTdaily[GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength }\SpecialCharTok{\textgreater{}}\NormalTok{ Daytime\_Ratio, Day]]}

\NormalTok{DTdaily }\OtherTok{\textless{}{-}}\NormalTok{ DATA[,}
\NormalTok{                .(}
                  \AttributeTok{glo\_Sum   =} \FunctionTok{sum}\NormalTok{(Low\_B.Low\_W.glo),}
                  \AttributeTok{GLB\_Sum   =} \FunctionTok{sum}\NormalTok{(wattGLB),}
                  \AttributeTok{GLB\_N     =} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wattGLB)),}
                  \AttributeTok{DayLength =} \FunctionTok{max}\NormalTok{(DayLength),}
\NormalTok{                  .N}
\NormalTok{                ),}
\NormalTok{                by }\OtherTok{=}\NormalTok{ Day]}

\CommentTok{\# plot(DATA[, ClearnessIndex\_C\_4, Date ])}

\CommentTok{\# table(DATA$BAD\_h)}

\NormalTok{DTyear }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}\AttributeTok{glo =} \FunctionTok{mean}\NormalTok{(Low\_B.Low\_W.glo),}
                   \AttributeTok{GLB =} \FunctionTok{mean}\NormalTok{(wattGLB),}
\NormalTok{                   .N),}
\NormalTok{               by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date))]}

\NormalTok{ylim }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(DTyear[, glo, GLB])}

\CommentTok{\# plot(  DTyear[, glo, year],}
\CommentTok{\#        ylim = ylim)}
\CommentTok{\# points(DTyear[, GLB, year], col = "green")}

\FunctionTok{plot}\NormalTok{(DTyear[, N, year], }\AttributeTok{col =} \StringTok{"blue"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-4} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot}\NormalTok{(DTyear[, GLB}\SpecialCharTok{/}\NormalTok{glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\StringTok{"Clear GLB / CS libratran by year"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-5} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{DTmonth }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}\AttributeTok{glo =} \FunctionTok{mean}\NormalTok{(Low\_B.Low\_W.glo),}
                    \AttributeTok{GLB =} \FunctionTok{mean}\NormalTok{(wattGLB),}
\NormalTok{                    .N),}
\NormalTok{                by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date), }\FunctionTok{month}\NormalTok{(Date))]}
\NormalTok{DTmonth[, tsy }\SpecialCharTok{:=}\NormalTok{ year }\SpecialCharTok{+}\NormalTok{ (month }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)}\SpecialCharTok{/}\DecValTok{12}\NormalTok{ ]}

\NormalTok{ylim }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(DTmonth[, glo, GLB])}

\CommentTok{\# plot(  DTmonth[, glo, tsy],}
\CommentTok{\#        ylim = ylim)}
\CommentTok{\# points(DTmonth[, GLB, tsy], col = "green")}

\CommentTok{\# plot(  DTmonth[, .N, tsy], col = "blue")}
\FunctionTok{plot}\NormalTok{(  DTmonth[, GLB}\SpecialCharTok{/}\NormalTok{glo, tsy], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\StringTok{"Clear GLB / CS libratran by month"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-6} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{out.height =} \StringTok{"32\%"}\NormalTok{   )}

\NormalTok{Ratio\_lim }\OtherTok{\textless{}{-}} \FloatTok{0.85}

\NormalTok{DTdaily[GLB\_Sum}\SpecialCharTok{/}\NormalTok{glo\_Sum }\SpecialCharTok{\textless{}}\NormalTok{ Ratio\_lim, .N]}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
[1] 134
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{days }\OtherTok{\textless{}{-}} \FunctionTok{unique}\NormalTok{(}\FunctionTok{c}\NormalTok{(DTdaily[GLB\_Sum}\SpecialCharTok{/}\NormalTok{glo\_Sum }\SpecialCharTok{\textless{}}\NormalTok{ Ratio\_lim, Day]))}

\NormalTok{days }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(DTdaily[, Day], }\DecValTok{40}\NormalTok{)}

\ControlFlowTok{for}\NormalTok{ (ad }\ControlFlowTok{in} \FunctionTok{sort}\NormalTok{(days)) \{}
\NormalTok{  temp }\OtherTok{\textless{}{-}}\NormalTok{ DATA[Day }\SpecialCharTok{==}\NormalTok{ ad,]}

\NormalTok{  ylim }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(temp[, Low\_B.Low\_W.glo, wattGLB])}

  \FunctionTok{plot}\NormalTok{(  temp[, Low\_B.Low\_W.glo, Date],}
         \AttributeTok{col =} \StringTok{"blue"}\NormalTok{,}
         \AttributeTok{ylim =}\NormalTok{ ylim)}
  \FunctionTok{points}\NormalTok{(temp[, wattGLB, Date], }\AttributeTok{col =} \StringTok{"green"}\NormalTok{)}
  \FunctionTok{title}\NormalTok{(}\FunctionTok{as.Date}\NormalTok{(ad, }\AttributeTok{origin =} \StringTok{"1970{-}01{-}01"}\NormalTok{))}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-33} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-34} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-35} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-36} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-37} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-38} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-39} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-40} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-41} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-42} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-43} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-44} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-45} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-46} \end{center}

\textbf{END}

\end{document}

### 2024-05-01 GHI_enh_Aeronet.tex
Commit 2024-05-01 17:11

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-26}
+\date{2024-05-01}
 
@@
 \begin{verbatim}
-Cross over point: 2014.75 
+Cross over point: 2005 
 \end{verbatim}
@@
 
-SZA min : 0.00133216113167738
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-1} \end{center}
 
-SZA mean : 0.00192971268218197
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-2} \end{center}
 
-SZA median : 0.00178690927379885
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-3} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-8} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-9} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-10} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-11} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-12} \end{center}
+
+SZA min : 0.00137165912186399
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-13} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-14} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-15} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-16} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-17} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-18} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-19} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-20} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-21} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-22} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-23} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-24} \end{center}
+
+SZA mean : 0.0020024477410843
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-25} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-26} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-27} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-28} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-29} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-30} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-31} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-32} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-33} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-34} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-35} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-36} \end{center}
+
+SZA median : 0.00184853525463023
+
+\begin{longtable}[]{@{}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1184}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1053}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1316}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1711}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}@{}}
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\centering
+Intercept
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Slope
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Month
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+MeanGlo
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Type
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Zeropoint
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+SlopeRela
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+-1102 & 0.8309 & 1 & 565.8 & SZA min & 2014 & 0.001469 \\
+-810.5 & 0.7648 & 2 & 721.8 & SZA min & 2015 & 0.00106 \\
+-6892 & 3.872 & 3 & 888.2 & SZA min & 2015 & 0.00436 \\
+-1277 & 1.124 & 4 & 974.5 & SZA min & 2015 & 0.001153 \\
+-982.7 & 0.9904 & 5 & 1004 & SZA min & 2015 & 0.0009866 \\
+375.1 & 0.3116 & 6 & 993.2 & SZA min & 2015 & 0.0003138 \\
+-140.7 & 0.5624 & 7 & 984 & SZA min & 2015 & 0.0005715 \\
+444.2 & 0.2576 & 8 & 967.6 & SZA min & 2015 & 0.0002663 \\
+-3.347 & 0.4436 & 9 & 872.7 & SZA min & 2015 & 0.0005082 \\
+-1081 & 0.9159 & 10 & 758.3 & SZA min & 2015 & 0.001208 \\
+-2109 & 1.345 & 11 & 565.3 & SZA min & 2015 & 0.002379 \\
+-1598 & 1.044 & 12 & 477.6 & SZA min & 2014 & 0.002186 \\
+-1221 & 0.756 & 1 & 293.9 & SZA mean & 2014 & 0.002573 \\
+-1063 & 0.7194 & 2 & 377.8 & SZA mean & 2015 & 0.001904 \\
+-1776 & 1.125 & 3 & 485.6 & SZA mean & 2015 & 0.002317 \\
+-1680 & 1.118 & 4 & 561.4 & SZA mean & 2015 & 0.001992 \\
+-1628 & 1.111 & 5 & 599.9 & SZA mean & 2015 & 0.001852 \\
+-262.2 & 0.4374 & 6 & 606.9 & SZA mean & 2015 & 0.0007207 \\
+-745.5 & 0.6689 & 7 & 592.1 & SZA mean & 2015 & 0.00113 \\
+-122.7 & 0.3402 & 8 & 566.4 & SZA mean & 2015 & 0.0006007 \\
+-474.5 & 0.4816 & 9 & 477.8 & SZA mean & 2015 & 0.001008 \\
+-1443 & 0.9151 & 10 & 394.4 & SZA mean & 2015 & 0.00232 \\
+-2438 & 1.364 & 11 & 277.9 & SZA mean & 2015 & 0.004907 \\
+-1179 & 0.7187 & 12 & 265.7 & SZA mean & 2014 & 0.002705 \\
+-1216 & 0.772 & 1 & 331.6 & SZA median & 2014 & 0.002328 \\
+-1041 & 0.7293 & 2 & 419.7 & SZA median & 2015 & 0.001738 \\
+-1743 & 1.129 & 3 & 527.8 & SZA median & 2015 & 0.00214 \\
+-1654 & 1.123 & 4 & 595.7 & SZA median & 2015 & 0.001884 \\
+-1595 & 1.105 & 5 & 620.6 & SZA median & 2015 & 0.00178 \\
+-243.2 & 0.4343 & 6 & 619.6 & SZA median & 2015 & 0.0007009 \\
+-708.1 & 0.6584 & 7 & 608.4 & SZA median & 2015 & 0.001082 \\
+-109.2 & 0.3477 & 8 & 595.2 & SZA median & 2015 & 0.0005842 \\
+-441.5 & 0.4846 & 9 & 516.9 & SZA median & 2015 & 0.0009376 \\
+-1433 & 0.9306 & 10 & 435.1 & SZA median & 2015 & 0.002139 \\
+-2464 & 1.395 & 11 & 314.5 & SZA median & 2015 & 0.004436 \\
+-1176 & 0.7354 & 12 & 302.4 & SZA median & 2014 & 0.002432 \\
+\end{longtable}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-37} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-2} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-38} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-3} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-39} \end{center}
 

### 2024-05-01 GHI_enh_02_ID_CE.R

@@ -287,10 +287,10 @@ switch(csmodel,
 ## init flag
 DATA[, Enhanc_C_4 := FALSE]
 
-C4_test_cs_ref_ratio   <- 1.05;
+C4_test_cs_ref_ratio   <-  1.05
 C4_test_GLB_diff_THRES <-  0;
 C4_test_lowcut_sza     <- 90;  ## Disabled
-C4_test_lowcut_ratio   <- 1.18
+C4_test_lowcut_ratio   <-  1.18
 
 # DATA[, max(SZA)]
 
@@ -849,7 +849,6 @@ objects <- c(
     objects, "DATA"
 )
 
-stopifnot(any(objects %in% "DATA"))
 
 save(file = paste0("./data/", basename(sub("\\.R", ".Rda", Script.Name))),
      list = objects,

### 2024-05-08 GHI_enh_CSid.tex
Commit 2024-05-08 22:14

@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-27}
+\date{2024-05-08}
 
@@
 }
-\texttt{Low\_B.Low\_W.glo} has compensation for sun distance, TSI variation and Kurudz difference
+\texttt{Low\_B.Low\_W.glo} has compensation for sun distance, TSI variation and Kurudz difference only
 
@@
 
-\NormalTok{DTdaily }\OtherTok{\textless{}{-}}\NormalTok{ DATA[,}
-\NormalTok{                .(}
-                  \AttributeTok{glo\_Sum   =} \FunctionTok{sum}\NormalTok{(Low\_B.Low\_W.glo),}
-                  \AttributeTok{GLB\_Sum   =} \FunctionTok{sum}\NormalTok{(wattGLB),}
-                  \AttributeTok{GLB\_N     =} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wattGLB)),}
-                  \AttributeTok{DayLength =} \FunctionTok{max}\NormalTok{(DayLength),}
-\NormalTok{                  .N}
-\NormalTok{                ),}
-\NormalTok{                by }\OtherTok{=}\NormalTok{ Day]}
-
-\NormalTok{Day\_points }\OtherTok{\textless{}{-}} \DecValTok{30}
-
-\NormalTok{DATA }\OtherTok{\textless{}{-}}\NormalTok{ DATA[ Day }\SpecialCharTok{\%in\%}\NormalTok{ DTdaily[GLB\_N }\SpecialCharTok{\textgreater{}}\NormalTok{ Day\_points, Day]]}
-
-\FunctionTok{hist}\NormalTok{(DTdaily}\SpecialCharTok{$}\NormalTok{GLB\_N)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-2} \end{center}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{hist}\NormalTok{(DTdaily[, GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength])}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-3} \end{center}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# plot(DTdaily[, GLB\_N/DayLength, Day])}
-\FunctionTok{summary}\NormalTok{(DTdaily[, GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength])}
+\FunctionTok{source}\NormalTok{(}\StringTok{"./GHI\_enh\_Aeronet.R"}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{verbatim}
-    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
-0.001152 0.181870 0.422018 0.420691 0.657944 0.838020 
+Cross over point: 2005 
 \end{verbatim}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\DocumentationTok{\#\# remove days with few relative data}
-\NormalTok{Daytime\_Ratio }\OtherTok{\textless{}{-}} \FloatTok{0.3}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-2} \end{center}
 
-\NormalTok{DTdaily[GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength }\SpecialCharTok{\textless{}}\NormalTok{ Daytime\_Ratio, .N]}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-[1] 2932
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{DATA }\OtherTok{\textless{}{-}}\NormalTok{ DATA[Day }\SpecialCharTok{\%in\%}\NormalTok{ DTdaily[GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength }\SpecialCharTok{\textgreater{}}\NormalTok{ Daytime\_Ratio, Day]]}
-
-\NormalTok{DTdaily }\OtherTok{\textless{}{-}}\NormalTok{ DATA[,}
-\NormalTok{                .(}
-                  \AttributeTok{glo\_Sum   =} \FunctionTok{sum}\NormalTok{(Low\_B.Low\_W.glo),}
-                  \AttributeTok{GLB\_Sum   =} \FunctionTok{sum}\NormalTok{(wattGLB),}
-                  \AttributeTok{GLB\_N     =} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wattGLB)),}
-                  \AttributeTok{DayLength =} \FunctionTok{max}\NormalTok{(DayLength),}
-\NormalTok{                  .N}
-\NormalTok{                ),}
-\NormalTok{                by }\OtherTok{=}\NormalTok{ Day]}
-
-\CommentTok{\# plot(DATA[, ClearnessIndex\_C\_4, Date ])}
-
-\CommentTok{\# table(DATA$BAD\_h)}
-
-\NormalTok{DTyear }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}\AttributeTok{glo =} \FunctionTok{mean}\NormalTok{(Low\_B.Low\_W.glo),}
-                   \AttributeTok{GLB =} \FunctionTok{mean}\NormalTok{(wattGLB),}
-\NormalTok{                   .N),}
-\NormalTok{               by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date))]}
-
-\NormalTok{ylim }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(DTyear[, glo, GLB])}
-
-\CommentTok{\# plot(  DTyear[, glo, year],}
-\CommentTok{\#        ylim = ylim)}
-\CommentTok{\# points(DTyear[, GLB, year], col = "green")}
-
-\FunctionTok{plot}\NormalTok{(DTyear[, N, year], }\AttributeTok{col =} \StringTok{"blue"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-3} \end{center}
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{plot}\NormalTok{(DTyear[, GLB}\SpecialCharTok{/}\NormalTok{glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
-\FunctionTok{title}\NormalTok{(}\StringTok{"Clear GLB / CS libratran by year"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-5} \end{center}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{DTmonth }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}\AttributeTok{glo =} \FunctionTok{mean}\NormalTok{(Low\_B.Low\_W.glo),}
-                    \AttributeTok{GLB =} \FunctionTok{mean}\NormalTok{(wattGLB),}
-\NormalTok{                    .N),}
-\NormalTok{                by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date), }\FunctionTok{month}\NormalTok{(Date))]}
-\NormalTok{DTmonth[, tsy }\SpecialCharTok{:=}\NormalTok{ year }\SpecialCharTok{+}\NormalTok{ (month }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)}\SpecialCharTok{/}\DecValTok{12}\NormalTok{ ]}
-
-\NormalTok{ylim }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(DTmonth[, glo, GLB])}
-
-\CommentTok{\# plot(  DTmonth[, glo, tsy],}
-\CommentTok{\#        ylim = ylim)}
-\CommentTok{\# points(DTmonth[, GLB, tsy], col = "green")}
-
-\CommentTok{\# plot(  DTmonth[, .N, tsy], col = "blue")}
-\FunctionTok{plot}\NormalTok{(  DTmonth[, GLB}\SpecialCharTok{/}\NormalTok{glo, tsy], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
-\FunctionTok{title}\NormalTok{(}\StringTok{"Clear GLB / CS libratran by month"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-6} \end{center}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{out.height =} \StringTok{"32\%"}\NormalTok{   )}
-
-\NormalTok{Ratio\_lim }\OtherTok{\textless{}{-}} \FloatTok{0.85}
-
-\NormalTok{DTdaily[GLB\_Sum}\SpecialCharTok{/}\NormalTok{glo\_Sum }\SpecialCharTok{\textless{}}\NormalTok{ Ratio\_lim, .N]}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-[1] 134
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{days }\OtherTok{\textless{}{-}} \FunctionTok{unique}\NormalTok{(}\FunctionTok{c}\NormalTok{(DTdaily[GLB\_Sum}\SpecialCharTok{/}\NormalTok{glo\_Sum }\SpecialCharTok{\textless{}}\NormalTok{ Ratio\_lim, Day]))}
-
-\NormalTok{days }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(DTdaily[, Day], }\DecValTok{40}\NormalTok{)}
-
-\ControlFlowTok{for}\NormalTok{ (ad }\ControlFlowTok{in} \FunctionTok{sort}\NormalTok{(days)) \{}
-\NormalTok{  temp }\OtherTok{\textless{}{-}}\NormalTok{ DATA[Day }\SpecialCharTok{==}\NormalTok{ ad,]}
-
-\NormalTok{  ylim }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(temp[, Low\_B.Low\_W.glo, wattGLB])}
-
-  \FunctionTok{plot}\NormalTok{(  temp[, Low\_B.Low\_W.glo, Date],}
-         \AttributeTok{col =} \StringTok{"blue"}\NormalTok{,}
-         \AttributeTok{ylim =}\NormalTok{ ylim)}
-  \FunctionTok{points}\NormalTok{(temp[, wattGLB, Date], }\AttributeTok{col =} \StringTok{"green"}\NormalTok{)}
-  \FunctionTok{title}\NormalTok{(}\FunctionTok{as.Date}\NormalTok{(ad, }\AttributeTok{origin =} \StringTok{"1970{-}01{-}01"}\NormalTok{))}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
 
@@
 
+\begin{verbatim}
+SZA min : 0.00137165912186399 
+\end{verbatim}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-27} \end{center}
@@
 
+\begin{verbatim}
+SZA mean : 0.0020024477410843 
+\end{verbatim}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-39} \end{center}
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-47} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-48} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-49} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-50} \end{center}
+
+\begin{verbatim}
+SZA median : 0.00184853525463023
+
+\newpage
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-51} \end{center}
+
+\begin{verbatim}
+
+\newpage
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-52} \end{center}
+
+\begin{verbatim}
+
+\newpage
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{DATA[, tsy }\SpecialCharTok{:=} \FunctionTok{year}\NormalTok{(Date) }\SpecialCharTok{+}\NormalTok{ (}\FunctionTok{month}\NormalTok{(Date) }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)}\SpecialCharTok{/}\DecValTok{12}\NormalTok{ ]}
+
+\DocumentationTok{\#\# apply AOD trend}
+\NormalTok{trendsf }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(trend\_median, trend\_mean, trend\_min)}
+
+\NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_median}
+\NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_mean}
+
+\NormalTok{trend\_factor }\OtherTok{\textless{}{-}} \FloatTok{0.86}
+
+\NormalTok{DATA[, Thresh\_test }\SpecialCharTok{:=}\NormalTok{ Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{*}\NormalTok{ trend\_factor)]}
+
+\FunctionTok{rmserr}\NormalTok{(DATA}\SpecialCharTok{$}\NormalTok{Enhanc\_C\_4\_ref, DATA}\SpecialCharTok{$}\NormalTok{wattGLB)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+$mae
+[1] 94.57364
+
+$mse
+[1] 10035.43
+
+$rmse
+[1] 100.177
+
+$mape
+[1] 0.1485271
+
+$nmse
+[1] 0.1642926
+
+$rstd
+[1] 0.1495398
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{f }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x) \{}
+
+\NormalTok{  test }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}
+    \FunctionTok{mean}\NormalTok{(Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{*}\NormalTok{ x)),}
+    \FunctionTok{mean}\NormalTok{(wattGLB)),}
+\NormalTok{       by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date), }\FunctionTok{month}\NormalTok{(Date))]}
+
+  \CommentTok{\# DATA[, sum( abs((Enhanc\_C\_4\_ref * (1 + trend\_apply(tsy) * x)) {-} wattGLB)) ]}
+
+  \CommentTok{\# DATA[, sum(1 {-} (Enhanc\_C\_4\_ref * (1 + trend\_apply(tsy) * x) / wattGLB)) ]}
+
+  \FunctionTok{rmserr}\NormalTok{(test}\SpecialCharTok{$}\NormalTok{V1, test}\SpecialCharTok{$}\NormalTok{V2)}\SpecialCharTok{$}\NormalTok{mse}
+  \CommentTok{\# test[, sum(V1 {-} V2)]}
+\NormalTok{\}}
+
+\FunctionTok{optimise}\NormalTok{(f, }\AttributeTok{interval =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.2}\NormalTok{, }\FloatTok{1.8}\NormalTok{), }\AttributeTok{maximum =}\NormalTok{ F, }\AttributeTok{tol =} \FloatTok{0.0001}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+$minimum
+[1] 0.2000654
+
+$objective
+[1] 8644.06
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# optim(0.8, f, method = "Brent", lower = 0.2, upper = 1.5)}
+
+\CommentTok{\# plot(DATA[, .(tsy, (1 + trend\_apply(tsy) * trend\_factor))])}
+
+\NormalTok{DTdaily }\OtherTok{\textless{}{-}}\NormalTok{ DATA[,}
+\NormalTok{                .(}
+                  \AttributeTok{glo\_Sum    =} \FunctionTok{sum}\NormalTok{(Low\_B.Low\_W.glo),}
+                  \AttributeTok{GLB\_Sum    =} \FunctionTok{sum}\NormalTok{(wattGLB),}
+                  \AttributeTok{GLB\_N      =} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wattGLB)),}
+                  \AttributeTok{DayLength  =} \FunctionTok{max}\NormalTok{(DayLength),}
+                  \AttributeTok{En\_Ref\_sum =} \FunctionTok{sum}\NormalTok{(Enhanc\_C\_4\_ref),}
+                  \AttributeTok{Thresh\_sum =} \FunctionTok{sum}\NormalTok{(Thresh\_test),}
+\NormalTok{                  .N}
+\NormalTok{                ),}
+\NormalTok{                by }\OtherTok{=}\NormalTok{ Day]}
+
+\NormalTok{Day\_points }\OtherTok{\textless{}{-}} \DecValTok{30}
+
+\NormalTok{DATA }\OtherTok{\textless{}{-}}\NormalTok{ DATA[ Day }\SpecialCharTok{\%in\%}\NormalTok{ DTdaily[GLB\_N }\SpecialCharTok{\textgreater{}}\NormalTok{ Day\_points, Day]]}
+
+\FunctionTok{hist}\NormalTok{(DTdaily}\SpecialCharTok{$}\NormalTok{GLB\_N)}
+\FunctionTok{hist}\NormalTok{(DTdaily[, GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength])}
+\CommentTok{\# plot(DTdaily[, GLB\_N/DayLength, Day])}
+\FunctionTok{summary}\NormalTok{(DTdaily[, GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength])}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
+0.001152 0.181870 0.422018 0.420691 0.657944 0.838020 
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot}\NormalTok{(DTdaily[, En\_Ref\_sum, Day])}
+\FunctionTok{plot}\NormalTok{(DTdaily[, glo\_Sum, Day])}
+\FunctionTok{plot}\NormalTok{(DTdaily[, GLB\_Sum, Day])}
+
+\DocumentationTok{\#\# remove days with few relative data}
+\NormalTok{Daytime\_Ratio }\OtherTok{\textless{}{-}} \FloatTok{0.3}
+
+\NormalTok{DTdaily[GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength }\SpecialCharTok{\textless{}}\NormalTok{ Daytime\_Ratio, .N]}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+[1] 2932
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{DATA }\OtherTok{\textless{}{-}}\NormalTok{ DATA[Day }\SpecialCharTok{\%in\%}\NormalTok{ DTdaily[GLB\_N}\SpecialCharTok{/}\NormalTok{DayLength }\SpecialCharTok{\textgreater{}}\NormalTok{ Daytime\_Ratio, Day]]}
+
+\NormalTok{DTdaily }\OtherTok{\textless{}{-}}\NormalTok{ DATA[,}
+\NormalTok{                .(}
+                  \AttributeTok{glo\_Sum    =} \FunctionTok{sum}\NormalTok{(Low\_B.Low\_W.glo),}
+                  \AttributeTok{GLB\_Sum    =} \FunctionTok{sum}\NormalTok{(wattGLB),}
+                  \AttributeTok{GLB\_N      =} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wattGLB)),}
+                  \AttributeTok{DayLength  =} \FunctionTok{max}\NormalTok{(DayLength),}
+                  \AttributeTok{En\_Ref\_sum =} \FunctionTok{sum}\NormalTok{(Enhanc\_C\_4\_ref),}
+                  \AttributeTok{Thresh\_sum =} \FunctionTok{sum}\NormalTok{(Thresh\_test),}
+\NormalTok{                  .N}
+\NormalTok{                ),}
+\NormalTok{                by }\OtherTok{=}\NormalTok{ Day]}
+
+\CommentTok{\# plot(DATA[, ClearnessIndex\_C\_4, Date ])}
+
+\CommentTok{\# table(DATA$BAD\_h)}
+
+\NormalTok{DTyear }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}\AttributeTok{glo =} \FunctionTok{mean}\NormalTok{(Low\_B.Low\_W.glo),}
+                   \AttributeTok{GLB =} \FunctionTok{mean}\NormalTok{(wattGLB),}
+                   \AttributeTok{Ref =} \FunctionTok{mean}\NormalTok{(Enhanc\_C\_4\_ref),}
+                   \AttributeTok{Thr =} \FunctionTok{mean}\NormalTok{(Thresh\_test),}
+\NormalTok{                   .N),}
+\NormalTok{               by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date))]}
+
+\NormalTok{ylim }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(DTyear[, glo, GLB])}
+
+\CommentTok{\# plot(  DTyear[, glo, year],}
+\CommentTok{\#        ylim = ylim)}
+\CommentTok{\# points(DTyear[, GLB, year], col = "green")}
+
+\FunctionTok{plot}\NormalTok{(DTyear[, N, year], }\AttributeTok{col =} \StringTok{"blue"}\NormalTok{)}
+
+\FunctionTok{plot}\NormalTok{(DTyear[, GLB}\SpecialCharTok{/}\NormalTok{glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
+\FunctionTok{title}\NormalTok{(}\StringTok{"Clear GLB / CS libratran yearly means"}\NormalTok{)}
+
+\FunctionTok{plot}\NormalTok{(DTyear[, Ref}\SpecialCharTok{/}\NormalTok{GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
+\FunctionTok{title}\NormalTok{(}\StringTok{"Threshold ref / Clear Global yearly means"}\NormalTok{)}
+
+\FunctionTok{plot}\NormalTok{(DTyear[, Ref}\SpecialCharTok{/}\NormalTok{glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
+\FunctionTok{title}\NormalTok{(}\StringTok{"Threshold ref / CS libratran yearly means"}\NormalTok{)}
+
+\FunctionTok{plot}\NormalTok{(DTyear[, Thr}\SpecialCharTok{/}\NormalTok{GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
+\FunctionTok{title}\NormalTok{(}\FunctionTok{paste}\NormalTok{(}\StringTok{"Threshold / global yearly means"}\NormalTok{, trend\_factor))}
+
+\NormalTok{ff }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x) \{}
+    \FunctionTok{plot}\NormalTok{(DTyear[, }\DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ x }\SpecialCharTok{*}\NormalTok{ Thr}\SpecialCharTok{/}\NormalTok{GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{, }\AttributeTok{main =}\NormalTok{ x)}
+\NormalTok{    DTyear[, }\FunctionTok{sum}\NormalTok{(}\FunctionTok{abs}\NormalTok{(}\DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ x }\SpecialCharTok{*}\NormalTok{ Thr}\SpecialCharTok{/}\NormalTok{GLB))]}
+\NormalTok{\}}
+
+\FunctionTok{optimize}\NormalTok{(ff, }\FunctionTok{c}\NormalTok{(.}\DecValTok{5}\NormalTok{, }\FloatTok{1.5}\NormalTok{), }\AttributeTok{tol =} \FloatTok{0.001}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+$minimum
+[1] 0.8590668
+
+$objective
+[1] 0.6771877
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{ff}\NormalTok{(}\FloatTok{0.85}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+[1] 0.7037762
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot}\NormalTok{(DTyear[, GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
+\FunctionTok{plot}\NormalTok{(DTyear[, Thr, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
+\FunctionTok{plot}\NormalTok{(DTyear[, glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
+\FunctionTok{plot}\NormalTok{(DTyear[, Ref, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
+
+\FunctionTok{rmserr}\NormalTok{(DTyear}\SpecialCharTok{$}\NormalTok{GLB, DTyear}\SpecialCharTok{$}\NormalTok{Thr)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+$mae
+[1] 97.55895
+
+$mse
+[1] 9799.437
+
+$rmse
+[1] 98.9921
+
+$mape
+[1] 0.1680595
+
+$nmse
+[1] 46.16276
+
+$rstd
+[1] 0.1700543
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{DTmonth }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}\AttributeTok{glo =} \FunctionTok{mean}\NormalTok{(Low\_B.Low\_W.glo),}
+                    \AttributeTok{GLB =} \FunctionTok{mean}\NormalTok{(wattGLB),}
+                    \AttributeTok{Thr =} \FunctionTok{mean}\NormalTok{(Thresh\_test),}
+\NormalTok{                    .N),}
+\NormalTok{                by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date), }\FunctionTok{month}\NormalTok{(Date))]}
+\NormalTok{DTmonth[, tsy }\SpecialCharTok{:=}\NormalTok{ year }\SpecialCharTok{+}\NormalTok{ (month }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)}\SpecialCharTok{/}\DecValTok{12}\NormalTok{ ]}
+
+\NormalTok{ylim }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(DTmonth[, glo, GLB])}
+
+\CommentTok{\# plot(  DTmonth[, glo, tsy],}
+\CommentTok{\#        ylim = ylim)}
+\CommentTok{\# points(DTmonth[, GLB, tsy], col = "green")}
+
+\CommentTok{\# plot(  DTmonth[, .N, tsy], col = "blue")}
+\FunctionTok{plot}\NormalTok{(  DTmonth[, GLB}\SpecialCharTok{/}\NormalTok{glo, tsy], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
+\FunctionTok{title}\NormalTok{(}\StringTok{"Clear GLB / CS libratran by month"}\NormalTok{)}
+
+\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{out.height =} \StringTok{"32\%"}\NormalTok{   )}
+
+\NormalTok{Ratio\_lim }\OtherTok{\textless{}{-}} \FloatTok{0.85}
+
+\NormalTok{DTdaily[GLB\_Sum}\SpecialCharTok{/}\NormalTok{glo\_Sum }\SpecialCharTok{\textless{}}\NormalTok{ Ratio\_lim, .N]}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+[1] 134
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{days }\OtherTok{\textless{}{-}} \FunctionTok{unique}\NormalTok{(}\FunctionTok{c}\NormalTok{(DTdaily[GLB\_Sum}\SpecialCharTok{/}\NormalTok{glo\_Sum }\SpecialCharTok{\textless{}}\NormalTok{ Ratio\_lim, Day]))}
+
+\NormalTok{days }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(DTdaily[, Day], }\DecValTok{40}\NormalTok{)}
+
+\CommentTok{\# for (ad in sort(days)) \{}
+\CommentTok{\#   temp \textless{}{-} DATA[Day == ad,]}
+\CommentTok{\#}
+\CommentTok{\#   ylim \textless{}{-} range(temp[, Low\_B.Low\_W.glo, wattGLB])}
+\CommentTok{\#}
+\CommentTok{\#   plot(  temp[, Low\_B.Low\_W.glo, Date],}
+\CommentTok{\#          col = "blue",}
+\CommentTok{\#          ylim = ylim)}
+\CommentTok{\#   points(temp[, wattGLB, Date], col = "green")}
+\CommentTok{\#   title(as.Date(ad, origin = "1970{-}01{-}01"))}
+\CommentTok{\# \}}
+\end{Highlighting}
+\end{Shaded}
+
 \textbf{END}

### 2024-05-09 GHI_enh_CSid.tex
Commit 2024-05-09 12:14

@@
 \hypersetup{
-  pdftitle={Enhancement of SDR in Thessaloniki},
+  pdftitle={Enhancement of SDR in Thessaloniki Clear Sky},
   pdfauthor={Natsis Athanasios; Alkiviadis Bais},
@@
 
-\title{Enhancement of SDR in Thessaloniki}
+\title{Enhancement of SDR in Thessaloniki Clear Sky}
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-05-08}
+\date{2024-05-09}
 
@@
 $objective
-[1] 8644.06
+[1] 8619.603
 \end{verbatim}
@@
 \NormalTok{ylim }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(DTyear[, glo, GLB])}
-
-\CommentTok{\# plot(  DTyear[, glo, year],}
-\CommentTok{\#        ylim = ylim)}
-\CommentTok{\# points(DTyear[, GLB, year], col = "green")}
-
-\FunctionTok{plot}\NormalTok{(DTyear[, N, year], }\AttributeTok{col =} \StringTok{"blue"}\NormalTok{)}
-
-\FunctionTok{plot}\NormalTok{(DTyear[, GLB}\SpecialCharTok{/}\NormalTok{glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
-\FunctionTok{title}\NormalTok{(}\StringTok{"Clear GLB / CS libratran yearly means"}\NormalTok{)}
-
-\FunctionTok{plot}\NormalTok{(DTyear[, Ref}\SpecialCharTok{/}\NormalTok{GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
-\FunctionTok{title}\NormalTok{(}\StringTok{"Threshold ref / Clear Global yearly means"}\NormalTok{)}
-
-\FunctionTok{plot}\NormalTok{(DTyear[, Ref}\SpecialCharTok{/}\NormalTok{glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
-\FunctionTok{title}\NormalTok{(}\StringTok{"Threshold ref / CS libratran yearly means"}\NormalTok{)}
-
-\FunctionTok{plot}\NormalTok{(DTyear[, Thr}\SpecialCharTok{/}\NormalTok{GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
-\FunctionTok{title}\NormalTok{(}\FunctionTok{paste}\NormalTok{(}\StringTok{"Threshold / global yearly means"}\NormalTok{, trend\_factor))}
-
-\NormalTok{ff }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x) \{}
-    \FunctionTok{plot}\NormalTok{(DTyear[, }\DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ x }\SpecialCharTok{*}\NormalTok{ Thr}\SpecialCharTok{/}\NormalTok{GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{, }\AttributeTok{main =}\NormalTok{ x)}
-\NormalTok{    DTyear[, }\FunctionTok{sum}\NormalTok{(}\FunctionTok{abs}\NormalTok{(}\DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ x }\SpecialCharTok{*}\NormalTok{ Thr}\SpecialCharTok{/}\NormalTok{GLB))]}
-\NormalTok{\}}
-
-\FunctionTok{optimize}\NormalTok{(ff, }\FunctionTok{c}\NormalTok{(.}\DecValTok{5}\NormalTok{, }\FloatTok{1.5}\NormalTok{), }\AttributeTok{tol =} \FloatTok{0.001}\NormalTok{)}
 \end{Highlighting}
@@
 
+\subsection{Relations}\label{relations}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-3} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-4} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-5} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-6} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-7} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-8} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-9} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-10} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-11} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-12} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-13} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-14} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-15} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-16} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-17} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-18} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-19} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-20} \end{center}
+
 \begin{verbatim}
 $minimum
-[1] 0.8590668
+[1] 0.8593852
 
 $objective
-[1] 0.6771877
+[1] 0.6165028
 \end{verbatim}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{ff}\NormalTok{(}\FloatTok{0.85}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-21} \end{center}
 
 \begin{verbatim}
-[1] 0.7037762
+[1] 0.6615997
 \end{verbatim}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{plot}\NormalTok{(DTyear[, GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
-\FunctionTok{plot}\NormalTok{(DTyear[, Thr, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
-\FunctionTok{plot}\NormalTok{(DTyear[, glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
-\FunctionTok{plot}\NormalTok{(DTyear[, Ref, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
+\subsection{Yearly values}\label{yearly-values}
 
-\FunctionTok{rmserr}\NormalTok{(DTyear}\SpecialCharTok{$}\NormalTok{GLB, DTyear}\SpecialCharTok{$}\NormalTok{Thr)}
-\end{Highlighting}
-\end{Shaded}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-7-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-7-2} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-7-3} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-7-4} \end{center}
 
@@
 $mae
-[1] 97.55895
+[1] 97.0816
 
 $mse
-[1] 9799.437
+[1] 9657.575
 
 $rmse
-[1] 98.9921
+[1] 98.27296
 
 $mape
-[1] 0.1680595
+[1] 0.1672027
 
 $nmse
-[1] 46.16276
+[1] 45.49449
 
 $rstd
-[1] 0.1700543
+[1] 0.1688189
 \end{verbatim}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{DTmonth }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}\AttributeTok{glo =} \FunctionTok{mean}\NormalTok{(Low\_B.Low\_W.glo),}
-                    \AttributeTok{GLB =} \FunctionTok{mean}\NormalTok{(wattGLB),}
-                    \AttributeTok{Thr =} \FunctionTok{mean}\NormalTok{(Thresh\_test),}
-\NormalTok{                    .N),}
-\NormalTok{                by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date), }\FunctionTok{month}\NormalTok{(Date))]}
-\NormalTok{DTmonth[, tsy }\SpecialCharTok{:=}\NormalTok{ year }\SpecialCharTok{+}\NormalTok{ (month }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)}\SpecialCharTok{/}\DecValTok{12}\NormalTok{ ]}
-
-\NormalTok{ylim }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(DTmonth[, glo, GLB])}
-
-\CommentTok{\# plot(  DTmonth[, glo, tsy],}
-\CommentTok{\#        ylim = ylim)}
-\CommentTok{\# points(DTmonth[, GLB, tsy], col = "green")}
-
-\CommentTok{\# plot(  DTmonth[, .N, tsy], col = "blue")}
-\FunctionTok{plot}\NormalTok{(  DTmonth[, GLB}\SpecialCharTok{/}\NormalTok{glo, tsy], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
-\FunctionTok{title}\NormalTok{(}\StringTok{"Clear GLB / CS libratran by month"}\NormalTok{)}
-
-\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{out.height =} \StringTok{"32\%"}\NormalTok{   )}
-
-\NormalTok{Ratio\_lim }\OtherTok{\textless{}{-}} \FloatTok{0.85}
-
-\NormalTok{DTdaily[GLB\_Sum}\SpecialCharTok{/}\NormalTok{glo\_Sum }\SpecialCharTok{\textless{}}\NormalTok{ Ratio\_lim, .N]}
-\end{Highlighting}
-\end{Shaded}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-7-5} \end{center}
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{days }\OtherTok{\textless{}{-}} \FunctionTok{unique}\NormalTok{(}\FunctionTok{c}\NormalTok{(DTdaily[GLB\_Sum}\SpecialCharTok{/}\NormalTok{glo\_Sum }\SpecialCharTok{\textless{}}\NormalTok{ Ratio\_lim, Day]))}
-
-\NormalTok{days }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(DTdaily[, Day], }\DecValTok{40}\NormalTok{)}
-
-\CommentTok{\# for (ad in sort(days)) \{}
-\CommentTok{\#   temp \textless{}{-} DATA[Day == ad,]}
-\CommentTok{\#}
-\CommentTok{\#   ylim \textless{}{-} range(temp[, Low\_B.Low\_W.glo, wattGLB])}
-\CommentTok{\#}
-\CommentTok{\#   plot(  temp[, Low\_B.Low\_W.glo, Date],}
-\CommentTok{\#          col = "blue",}
-\CommentTok{\#          ylim = ylim)}
-\CommentTok{\#   points(temp[, wattGLB, Date], col = "green")}
-\CommentTok{\#   title(as.Date(ad, origin = "1970{-}01{-}01"))}
-\CommentTok{\# \}}
-\end{Highlighting}
-\end{Shaded}
-
 \textbf{END}

### 2024-05-09 GHI_enh_CSid.tex
Commit 2024-05-09 19:12

@@
 
+\DocumentationTok{\#\# for trend mean}
+\CommentTok{\# trend\_apply  \textless{}{-} trend\_mean}
+\CommentTok{\# trend\_factor \textless{}{-} {-}0.01995656}
+\DocumentationTok{\#\# for trend median}
 \NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_median}
-\NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_mean}
+\NormalTok{trend\_factor }\OtherTok{\textless{}{-}} \SpecialCharTok{{-}}\FloatTok{0.01995656}  \CommentTok{\# the same}
 
-\NormalTok{trend\_factor }\OtherTok{\textless{}{-}} \FloatTok{0.86}
-
-\NormalTok{DATA[, Thresh\_test }\SpecialCharTok{:=}\NormalTok{ Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{*}\NormalTok{ trend\_factor)]}
+\NormalTok{DATA[, Thresh\_test }\SpecialCharTok{:=}\NormalTok{ Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{+}\NormalTok{ trend\_factor)]}
 
@@
 \begin{Highlighting}[]
+\FunctionTok{rmserr}\NormalTok{(DATA}\SpecialCharTok{$}\NormalTok{Thresh\_test, DATA}\SpecialCharTok{$}\NormalTok{wattGLB)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+$mae
+[1] 85.55033
+
+$mse
+[1] 8567.15
+
+$rmse
+[1] 92.5589
+
+$mape
+[1] 0.1365803
+
+$nmse
+[1] 0.1436112
+
+$rstd
+[1] 0.1400624
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
 \NormalTok{f }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x) \{}
@@
 \NormalTok{  test }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}
-    \FunctionTok{mean}\NormalTok{(Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{*}\NormalTok{ x)),}
+    \FunctionTok{mean}\NormalTok{(Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{+}\NormalTok{ x)),}
     \FunctionTok{mean}\NormalTok{(wattGLB)),}
@@
 
-\FunctionTok{optimise}\NormalTok{(f, }\AttributeTok{interval =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.2}\NormalTok{, }\FloatTok{1.8}\NormalTok{), }\AttributeTok{maximum =}\NormalTok{ F, }\AttributeTok{tol =} \FloatTok{0.0001}\NormalTok{)}
+\FunctionTok{optimise}\NormalTok{(f, }\AttributeTok{interval =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\FloatTok{0.02}\NormalTok{, }\FloatTok{0.02}\NormalTok{), }\AttributeTok{maximum =}\NormalTok{ F, }\AttributeTok{tol =} \FloatTok{0.0001}\NormalTok{)}
 \end{Highlighting}
@@
 $minimum
-[1] 0.2000654
+[1] -0.01995656
 
 $objective
-[1] 8619.603
+[1] 7042.576
 \end{verbatim}
@@
 \FunctionTok{plot}\NormalTok{(DTdaily[, GLB\_Sum, Day])}
+\FunctionTok{plot}\NormalTok{(DTdaily[, Thresh\_sum, Day])}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-8} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-9} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-10} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-11} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-12} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-13} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-14} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-15} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-16} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-17} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-18} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-19} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-20} \end{center}
-
-\begin{verbatim}
-$minimum
-[1] 0.8593852
-
-$objective
-[1] 0.6165028
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-21} \end{center}
-
-\begin{verbatim}
-[1] 0.6615997
-\end{verbatim}
-
 \subsection{Yearly values}\label{yearly-values}
@@
 $mae
-[1] 97.0816
+[1] 83.65625
 
 $mse
-[1] 9657.575
+[1] 7337.38
 
 $rmse
-[1] 98.27296
+[1] 85.65851
 
 $mape
-[1] 0.1672027
+[1] 0.1442124
 
 $nmse
-[1] 45.49449
+[1] 34.56461
 
 $rstd
-[1] 0.1688189
+[1] 0.1471491
 \end{verbatim}

### 2024-05-09 GHI_enh_03_process.tex
Commit 2024-05-10 00:14

--- 2024-04-19 GHI_enh_03_process.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-19}
+\date{2024-05-09}
 
@@
     Min      1Q  Median      3Q     Max 
--384.81 -144.57  -53.50   96.68  768.76
+-327.56 -157.11  -65.36  116.74  760.36
 
@@
                   Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      -9.187e+01  4.952e+01  -1.855   0.0644 .  
-as.numeric(Date)  3.286e-07  3.958e-08   8.302 2.08e-15 ***
+(Intercept)      2.431e+02  4.880e+01   4.981  9.8e-07 ***
+as.numeric(Date) 6.397e-08  3.907e-08   1.637    0.102    
 ---
@@
 
-Residual standard error: 211.4 on 361 degrees of freedom
-Multiple R-squared:  0.1603,    Adjusted R-squared:  0.158 
-F-statistic: 68.92 on 1 and 361 DF,  p-value: 2.077e-15
+Residual standard error: 210.1 on 363 degrees of freedom
+Multiple R-squared:  0.007332,  Adjusted R-squared:  0.004597 
+F-statistic: 2.681 on 1 and 363 DF,  p-value: 0.1024
 \end{verbatim}
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       -9.187e+01  4.952e+01  -1.855   0.0644 .  
-ST_E_monthly$Date  3.286e-07  3.958e-08   8.302 2.08e-15 ***
+(Intercept)       2.431e+02  4.880e+01   4.981  9.8e-07 ***
+ST_E_monthly$Date 6.397e-08  3.907e-08   1.637    0.102    
 ---
@@
 aa
+aatm
 aday
+AEin1
 All_daily_ratio_lim
 alpha
+amean
 ampl
+asza
+atype
 avar
+b
 BIO_ELEVA
-C1_Clearness_Kt_THRES
-C1_GLB_diff_THRES
-C2_Clearness_Kt_THRES
-C3_cs_ref_ratio
 C4_cs_ref_ratio
@@
 Energy_Div
+fit
 I1_longterm
@@
 Kurudz_SC
+lm_mean
+lm_zeropoint
+mean_BR_mean
+mean_BR_median
+mean_BR_min
+mean_mean
+mean_median
+mean_min
+mid
 MIN_ELEVA
 MIN_N
+mm
 Monthly_aggegation_N_lim
@@
 SelEnhanc
+slope_mean
+slope_median
+slope_min
 SZA_aggregation_N_lim
@@
 SZA_confidence_limit
+t
+tsy
+units
 variables_fl
+xlim
 yearstodo
 ylim
+zeropoint
+zeropointA
 ST_daily
@@
 \begin{verbatim}
-2024-04-19 10:26:46.8 athan@sagan GHI_enh_03_process.R 3.634787 mins
+2024-05-09 20:10:12.1 athan@sagan GHI_enh_03_process.R 3.712139 mins
 \end{verbatim}

### 2024-05-09 GHI_enh_04_investigate.tex
Commit 2024-05-10 00:14

--- 2024-04-19 GHI_enh_04_investigate.tex
@@
 
-lmD: 1.552161 +/- 0.104876
+lmD: 0.56672 +/- 0.105912
 
-lmY: 1.552176 +/- 0.104878
+lmY: 0.566719 +/- 0.105914
 
-Arima: 1.552549 +/- 0.14034
+Arima: 0.567051 +/- 0.141823
 
@@
 
-lmD: 0.954836 +/- 0.154734
+lmD: -0.300529 +/- 0.154885
 
-lmY: 0.954859 +/- 0.154736
+lmY: -0.300528 +/- 0.154888
 
-Arima: 1.024507 +/- 0.23503
+Arima: -0.2336 +/- 0.235583
 
@@
 
-lmD: 1.088987 +/- 0.16743
+lmD: -0.247556 +/- 0.167713
 
-lmY: 1.089013 +/- 0.167433
+lmY: -0.247553 +/- 0.167716
 
-Arima: 1.160151 +/- 0.24838
+Arima: -0.179333 +/- 0.249282
 
@@
 
-lmD: 1.050842 +/- 0.240164
+lmD: -0.450424 +/- 0.239956
 
-lmY: 1.050851 +/- 0.240168
+lmY: -0.450441 +/- 0.23996
 
-Arima: 1.050895 +/- 0.364666
+Arima: -0.450398 +/- 0.364663
 
@@
 
-lmD: 0.958299 +/- 0.253655
+lmD: -0.558109 +/- 0.253332
 
-lmY: 0.958309 +/- 0.25366
+lmY: -0.558126 +/- 0.253337
 
-Arima: 0.958355 +/- 0.388216
+Arima: -0.55808 +/- 0.388026
 
@@
 
-lmD: 1.089066 +/- 0.07424
+lmD: 0.234369 +/- 0.074603
 
-lmY: 1.089079 +/- 0.074241
+lmY: 0.234366 +/- 0.074604
 
-Arima: 1.089082 +/- 0.109498
+Arima: 0.234368 +/- 0.110217
 
@@
 
-lmD: 1.136243 +/- 0.070602
+lmD: 0.302033 +/- 0.07107
 
-lmY: 1.136256 +/- 0.070603
+lmY: 0.302031 +/- 0.071072
 
-Arima: 1.136263 +/- 0.100583
+Arima: 0.302035 +/- 0.101344
 
@@
 
-lmD: 33.75698 +/- 5.702807
+lmD: -12.24511 +/- 5.698072
 
-lmY: 33.75752 +/- 5.702906
+lmY: -12.24538 +/- 5.698171
 
-Arima: 33.816428 +/- 8.918367
+Arima: -12.195036 +/- 8.900074
 
@@
 
-lmD: 0.003302 +/- 0.00027
+lmD: 0.00134 +/- 0.000272
 
-lmY: 0.003302 +/- 0.00027
+lmY: 0.00134 +/- 0.000272
 
-Arima: 0.003326 +/- 0.000357
+Arima: 0.001363 +/- 0.00036
 
@@
 
-lmD: 0.001743 +/- 0.000278
+lmD: 0.000403 +/- 0.000279
 
-lmY: 0.001743 +/- 0.000278
+lmY: 0.000403 +/- 0.000279
 
-Arima: 0.001906 +/- 0.000459
+Arima: 0.000564 +/- 0.000462
 
@@
 
-lmD: 0.001718 +/- 0.000312
+lmD: 0.000343 +/- 0.000314
 
-lmY: 0.001718 +/- 0.000312
+lmY: 0.000343 +/- 0.000314
 
-Arima: 0.001883 +/- 0.000503
+Arima: 0.000504 +/- 0.000507
 
@@
 
-lmD: 0.001896 +/- 0.000307
+lmD: 0.000941 +/- 0.000309
 
-lmY: 0.001896 +/- 0.000307
+lmY: 0.000941 +/- 0.000309
 
-Arima: 0.001896 +/- 0.000479
+Arima: 0.000941 +/- 0.000482
 
@@
 
-lmD: 0.001823 +/- 0.000299
+lmD: 0.000981 +/- 0.000301
 
-lmY: 0.001823 +/- 0.000299
+lmY: 0.000982 +/- 0.000301
 
-Arima: 0.001823 +/- 0.00046
+Arima: 0.000982 +/- 0.000462
 
@@
 
-lmD: 0.002414 +/- 0.000233
+lmD: 0.000734 +/- 0.000235
 
-lmY: 0.002414 +/- 0.000233
+lmY: 0.000734 +/- 0.000235
 
-Arima: 0.002414 +/- 0.000362
+Arima: 0.000734 +/- 0.000366
 
@@
 
-lmD: 0.002624 +/- 0.000228
+lmD: 0.000872 +/- 0.000229
 
-lmY: 0.002624 +/- 0.000228
+lmY: 0.000872 +/- 0.000229
 
-Arima: 0.002624 +/- 0.000339
+Arima: 0.000872 +/- 0.000342
 
@@
 
-lmD: 0.988112 +/- 0.144355
+lmD: 0.180964 +/- 0.145233
 
-lmY: 0.988134 +/- 0.144358
+lmY: 0.180972 +/- 0.145235
 
-Arima: 1.051184 +/- 0.218585
+Arima: 0.238782 +/- 0.22021
 
@@
 
-lmD: 0.816129 +/- 0.101923
+lmD: 0.127247 +/- 0.099723
 
-lmY: 0.816139 +/- 0.101925
+lmY: 0.127245 +/- 0.099725
 
-Arima: 0.816132 +/- 0.119665
+Arima: 0.127249 +/- 0.115059
 
@@
 
-lmD: 0.215792 +/- 0.037414
+lmD: 0.065571 +/- 0.036505
 
-lmY: 0.215795 +/- 0.037415
+lmY: 0.065571 +/- 0.036506
 
-Arima: 0.215796 +/- 0.040986
+Arima: 0.065573 +/- 0.04
 
@@
 
-lmD: 0.181869 +/- 0.03711
+lmD: 0.085245 +/- 0.036172
 
-lmY: 0.181874 +/- 0.037111
+lmY: 0.085246 +/- 0.036173
 
-Arima: 0.181874 +/- 0.039209
+Arima: 0.085247 +/- 0.038483
 
@@
 
-lmD: 0.481659 +/- 0.045723
+lmD: 0.015901 +/- 0.044784
 
-lmY: 0.481664 +/- 0.045724
+lmY: 0.015898 +/- 0.044784
 
-Arima: 0.481665 +/- 0.054201
+Arima: 0.015898 +/- 0.052937
 
@@
 
-lmD: 0.001364 +/- 0.01878
+lmD: 0.033836 +/- 0.018543
 
-lmY: 0.001365 +/- 0.018781
+lmY: 0.033837 +/- 0.018543
 
-Arima: 0.001365 +/- 0.01932
+Arima: 0.033838 +/- 0.01905
 
@@
 
-lmD: -0.018679 +/- 0.017374
+lmD: 0.03242 +/- 0.017152
 
-lmY: -0.018679 +/- 0.017374
+lmY: 0.032421 +/- 0.017152
 
-Arima: -0.018679 +/- 0.017837
+Arima: 0.032421 +/- 0.017569
 
@@
 
-lmD: 0.496018 +/- 0.071855
+lmD: 0.074226 +/- 0.070335
 
-lmY: 0.496024 +/- 0.071857
+lmY: 0.074225 +/- 0.070336
 
-Arima: 0.496022 +/- 0.080622
+Arima: 0.074226 +/- 0.077768
 
@@
 
-lmD: 0.597354 +/- 0.08202
+lmD: 0.087786 +/- 0.080412
 
-lmY: 0.597361 +/- 0.082022
+lmY: 0.087785 +/- 0.080413
 
-Arima: 0.597357 +/- 0.094227
+Arima: 0.087788 +/- 0.090783
 
@@
 
-lmD: 1.432631 +/- 0.148944
+lmD: 0.071192 +/- 0.144022
 
-lmY: 1.432652 +/- 0.148947
+lmY: 0.071187 +/- 0.144025
 
-Arima: 1.432652 +/- 0.180994
+Arima: 0.071193 +/- 0.173121
 
@@
 
-lmD: 0.001383 +/- 0.000137
+lmD: 0.000213 +/- 0.000135
 
-lmY: 0.001383 +/- 0.000137
+lmY: 0.000213 +/- 0.000135
 
-Arima: 0.001383 +/- 0.00016
+Arima: 0.000213 +/- 0.000155
 
@@
 
-lmD: 0.00044 +/- 6.1e-05
+lmD: 0.000117 +/- 5.9e-05
 
-lmY: 0.00044 +/- 6.1e-05
+lmY: 0.000117 +/- 5.9e-05
 
-Arima: 0.00044 +/- 7e-05
+Arima: 0.000117 +/- 6.8e-05
 
@@
 
-lmD: 0.000363 +/- 6.4e-05
+lmD: 0.000135 +/- 6.2e-05
 
-lmY: 0.000363 +/- 6.4e-05
+lmY: 0.000135 +/- 6.2e-05
 
-Arima: 0.000363 +/- 7.2e-05
+Arima: 0.000135 +/- 6.9e-05
 
@@
 
-lmD: 4e-05 +/- 3.3e-05
+lmD: 5.8e-05 +/- 3.1e-05
 
-lmY: 4e-05 +/- 3.3e-05
+lmY: 5.8e-05 +/- 3.1e-05
 
-Arima: 4e-05 +/- 3.8e-05
+Arima: 5.8e-05 +/- 3.6e-05
 
@@
 
-lmD: 5e-06 +/- 2.9e-05
+lmD: 5.3e-05 +/- 2.8e-05
 
-lmY: 5e-06 +/- 2.9e-05
+lmY: 5.3e-05 +/- 2.8e-05
 
-Arima: 5e-06 +/- 3.4e-05
+Arima: 5.3e-05 +/- 3.2e-05
 
@@
 
-lmD: 0.000968 +/- 0.000108
+lmD: 0.000174 +/- 0.000106
 
-lmY: 0.000968 +/- 0.000108
+lmY: 0.000174 +/- 0.000106
 
-Arima: 0.000968 +/- 0.000125
+Arima: 0.000174 +/- 0.000121
 
@@
 
-lmD: 0.001126 +/- 0.000119
+lmD: 0.000194 +/- 0.000116
 
-lmY: 0.001126 +/- 0.000119
+lmY: 0.000194 +/- 0.000116
 
-Arima: 0.001126 +/- 0.000138
+Arima: 0.000194 +/- 0.000134
 
@@
 
-lmD: 0.036713 +/- 0.003659
+lmD: 0.001754 +/- 0.003555
 
-lmY: 0.036714 +/- 0.003659
+lmY: 0.001754 +/- 0.003556
 
-Arima: 0.036714 +/- 0.00425
+Arima: 0.001754 +/- 0.00409
 
@@
 
-lmD: 0.203753 +/- 0.246152
+lmD: -1.406706 +/- 0.24506
 
-lmY: 0.20379 +/- 0.246156
+lmY: -1.406695 +/- 0.245065
 
-Arima: 0.191314 +/- 0.355242
+Arima: -1.417205 +/- 0.351582
 
@@
 
-lmD: 0.066924 +/- 0.186933
+lmD: -1.527566 +/- 0.186094
 
-lmY: 0.066947 +/- 0.186936
+lmY: -1.527568 +/- 0.186097
 
-Arima: 0.031787 +/- 0.332858
+Arima: -1.558334 +/- 0.32687
 
@@
 
-lmD: 0.108038 +/- 0.185587
+lmD: -1.488694 +/- 0.184965
 
-lmY: 0.10806 +/- 0.18559
+lmY: -1.488697 +/- 0.184968
 
-Arima: 0.07227 +/- 0.320898
+Arima: -1.520192 +/- 0.31545
 
@@
 
-lmD: -0.047504 +/- 0.172428
+lmD: -1.626611 +/- 0.17175
 
-lmY: -0.047493 +/- 0.17243
+lmY: -1.626625 +/- 0.171753
 
-Arima: -0.093727 +/- 0.32618
+Arima: -1.666679 +/- 0.318198
 
@@
 
-lmD: -0.06805 +/- 0.171992
+lmD: -1.642527 +/- 0.171263
 
-lmY: -0.068039 +/- 0.171995
+lmY: -1.642542 +/- 0.171266
 
-Arima: -0.113836 +/- 0.324815
+Arima: -1.682227 +/- 0.316737
 
@@
 
-lmD: 0.1818 +/- 0.225799
+lmD: -1.425903 +/- 0.224826
 
-lmY: 0.181836 +/- 0.225802
+lmY: -1.425893 +/- 0.22483
 
-Arima: 0.164846 +/- 0.343081
+Arima: -1.440441 +/- 0.339186
 
@@
 
-lmD: 0.192758 +/- 0.234509
+lmD: -1.416548 +/- 0.23349
 
-lmY: 0.192794 +/- 0.234513
+lmY: -1.416538 +/- 0.233494
 
-Arima: 0.178049 +/- 0.348128
+Arima: -1.429067 +/- 0.34436
 
@@
 
-lmD: 0.372906 +/- 0.252445
+lmD: 0.057623 +/- 0.247504
 
-lmY: 0.372932 +/- 0.252449
+lmY: 0.057642 +/- 0.247508
 
-Arima: 0.373033 +/- 0.257109
+Arima: 0.05775 +/- 0.252236
 
@@
 
-lmD: 0.000567 +/- 0.000291
+lmD: -0.001993 +/- 0.000291
 
-lmY: 0.000567 +/- 0.000291
+lmY: -0.001994 +/- 0.000291
 
-Arima: 0.000567 +/- 0.000322
+Arima: -0.001994 +/- 0.000321
 
@@
 
-lmD: 0.000397 +/- 0.000226
+lmD: -0.002127 +/- 0.000226
 
-lmY: 0.000397 +/- 0.000226
+lmY: -0.002127 +/- 0.000226
 
-Arima: 0.000393 +/- 0.000269
+Arima: -0.002131 +/- 0.000268
 
@@
 
-lmD: 0.000416 +/- 0.000234
+lmD: -0.002106 +/- 0.000234
 
-lmY: 0.000416 +/- 0.000234
+lmY: -0.002106 +/- 0.000234
 
-Arima: 0.000413 +/- 0.000274
+Arima: -0.00211 +/- 0.000274
 
@@
 
-lmD: 0.000209 +/- 0.000208
+lmD: -0.002288 +/- 0.000208
 
-lmY: 0.000209 +/- 0.000208
+lmY: -0.002288 +/- 0.000208
 
-Arima: 0.000203 +/- 0.000261
+Arima: -0.002296 +/- 0.000261
 
@@
 
-lmD: 0.000194 +/- 0.000208
+lmD: -0.0023 +/- 0.000208
 
-lmY: 0.000194 +/- 0.000208
+lmY: -0.0023 +/- 0.000208
 
-Arima: 0.000187 +/- 0.000261
+Arima: -0.002309 +/- 0.000261
 
@@
 
-lmD: 0.000565 +/- 0.000272
+lmD: -0.001986 +/- 0.000271
 
-lmY: 0.000565 +/- 0.000272
+lmY: -0.001986 +/- 0.000271
 
-Arima: 0.000565 +/- 0.000304
+Arima: -0.001986 +/- 0.000303
 
@@
 
-lmD: 0.000571 +/- 0.00028
+lmD: -0.001985 +/- 0.00028
 
-lmY: 0.000571 +/- 0.00028
+lmY: -0.001985 +/- 0.00028
 
-Arima: 0.000571 +/- 0.000312
+Arima: -0.001985 +/- 0.000311
 
@@
 
-lmD: 0.008989 +/- 0.005522
+lmD: 0.000428 +/- 0.005409
 
-lmY: 0.008989 +/- 0.005522
+lmY: 0.000428 +/- 0.005409
 
-Arima: 0.009015 +/- 0.00575
+Arima: 0.000453 +/- 0.005642
 
@@
 
-Arima: 0.215796 +/- 0.040986
+Arima: 0.065573 +/- 0.04
 
@@
 \begin{verbatim}
-Warning: Removed 25 rows containing missing values or values outside the scale
+Warning: Removed 23 rows containing missing values or values outside the scale
 range (`geom_bar()`).
@@
 \begin{verbatim}
-Warning: Removed 16 rows containing non-finite outside the scale range
+Warning: Removed 18 rows containing non-finite outside the scale range
 (`stat_bin2d()`).
@@
 
-lmY: 339.1753 +/- 35.87673
+lmY: 50.70791 +/- 35.58152
 
@@
 
-lmY: 123.4768 +/- 11.47021
+lmY: 20.14994 +/- 11.43911
 
@@
 
-lmY: 0.228163 +/- 0.054288
+lmY: 0.032227 +/- 0.053277
 
@@
 
-lmY: 0.174806 +/- 0.039192
+lmY: 0.036732 +/- 0.039744
 
@@
 \begin{verbatim}
-2024-04-19 10:28:33.6 athan@sagan GHI_enh_04_investigate.R 0.788870 mins
+2024-05-09 20:12:01.6 athan@sagan GHI_enh_04_investigate.R 0.834317 mins
 \end{verbatim}

### 2024-05-09 article/article.tex
Commit 2024-05-10 00:14

@@
 Our dataset, after the data selection processing, consists of 6144534
-records of GHI, of which \(1.592\,\%\) are CE and \(0.036\,\%\) are ECE
+records of GHI, of which \(1.906\,\%\) are CE and \(0.036\,\%\) are ECE
 events. The highest GHI recorder was \(1416.6\,W/m^2\) on 24~May 2007.
-The absolute stronger CE event had an OIR of \(335.28\,W/m^2\) on 24~May
-2007. The relative stronger CE event was \(50.2\,\%\) above the clear
-sky threshold, on 28~October 2016.
+The absolute stronger CE event had an OIR of \(353.46\,W/m^2\) on
+21~June 2001. The relative stronger CE event was \(49.9\,\%\) above the
+clear sky threshold, on 28~October 2016.
 
@@
 \citep{RCT2023}. The trends are reported together with the \(2\sigma\)
-error. We observe an increase of \(0.202\pm 0.083\,W/m^2/y\) on the mean
+error. We observe an increase of \(0.066\pm 0.08\,W/m^2/y\) on the mean
 OIR.
@@
 long term CE trends. Hence, we calculated the annual values from the
-one-minute measurements. The trend of OIR is \(0.22\pm 0.11\,W/m^2/y\)
+one-minute measurements. The trend of OIR is \(0.03\pm 0.11\,W/m^2/y\)
 (Figure\nobreakspace{}\ref{fig:P-energy-mean}), but this value alone is
@@
 The annual number of CE occurrences, shows a steady increase of
-\(110.1\pm 20.3\,\text{cases}/y\)
+\(20.1\pm 22.9\,\text{cases}/y\)
 (Figure\nobreakspace{}\ref{fig:P-energy-N}). We have to note that the
@@
 Subsequently, the mean annual increase of energy due to CE events is
-\(293.3\pm 63.1\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
+\(50.7\pm 71.2\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
 the trend of the number of occurrences.
@@
 Thus, a CEG consists of one or more successive CE cases, and can have a
-duration of multiple of minutes. We have identified 26042 groups, where
+duration of multiple of minutes. We have identified 30221 groups, where
 the group with the longest duration lasted 140 minutes on 07~July 2013.

### 2024-05-13 GHI_enh_03_process.tex
Commit 2024-05-13 12:21

@@
 \usepackage{amsmath,amssymb}
+\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
+  \usepackage{unicode-math}
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-\usepackage{lmodern}
-\ifPDFTeX\else
-  % xetex/luatex font selection
 \fi
@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Enhancement of SDR in Thessaloniki},
+  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
+  colorlinks=true,
+  linkcolor={Maroon},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
@@
 \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
 \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
@@
 \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
 \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
@@
 \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
 \newcommand{\ImportTok}[1]{#1}
@@
 \newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
 \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
-\hypersetup{
-  pdftitle={Enhancement of SDR in Thessaloniki},
-  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
-  colorlinks=true,
-  linkcolor={Maroon},
-  filecolor={Maroon},
-  citecolor={Blue},
-  urlcolor={Blue},
-  pdfcreator={LaTeX via pandoc}}
 
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-05-09}
+\date{2024-05-13}
 
@@
 \begin{verbatim}
-
 Call:
@@
 \begin{verbatim}
-2024-05-09 20:10:12.1 athan@sagan GHI_enh_03_process.R 3.712139 mins
+2024-05-13 09:11:34.5 athan@sagan GHI_enh_03_process.R 3.715344 mins
 \end{verbatim}

### 2024-05-13 GHI_enh_CSid.tex
Commit 2024-05-13 12:21

@@
 \NormalTok{trend\_factor }\OtherTok{\textless{}{-}} \SpecialCharTok{{-}}\FloatTok{0.01995656}  \CommentTok{\# the same}
+\NormalTok{trend\_apply\_adj }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(tsy) \{}
+  \FunctionTok{trend\_median}\NormalTok{(tsy) }\SpecialCharTok{{-}} \FloatTok{0.01995656}
+\NormalTok{\}}
 
-\NormalTok{DATA[, Thresh\_test }\SpecialCharTok{:=}\NormalTok{ Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{+}\NormalTok{ trend\_factor)]}
+\FunctionTok{trend\_apply}\NormalTok{(}\DecValTok{1999}\SpecialCharTok{:}\DecValTok{2000}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+[1] -0.01599489 -0.01332907
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{DATA[, Thresh\_test }\SpecialCharTok{:=}\NormalTok{ Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply\_adj}\NormalTok{(tsy))]}
 
@@
 \NormalTok{       by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date), }\FunctionTok{month}\NormalTok{(Date))]}
-
-  \CommentTok{\# DATA[, sum( abs((Enhanc\_C\_4\_ref * (1 + trend\_apply(tsy) * x)) {-} wattGLB)) ]}
-
-  \CommentTok{\# DATA[, sum(1 {-} (Enhanc\_C\_4\_ref * (1 + trend\_apply(tsy) * x) / wattGLB)) ]}
 
@@
                   \AttributeTok{En\_Ref\_sum =} \FunctionTok{sum}\NormalTok{(Enhanc\_C\_4\_ref),}
-                  \AttributeTok{Thresh\_sum =} \FunctionTok{sum}\NormalTok{(Thresh\_test),}
+                  \CommentTok{\# Thresh\_sum = sum(Thresh\_test),}
 \NormalTok{                  .N}
@@
                    \AttributeTok{Ref =} \FunctionTok{mean}\NormalTok{(Enhanc\_C\_4\_ref),}
-                   \AttributeTok{Thr =} \FunctionTok{mean}\NormalTok{(Thresh\_test),}
+                   \CommentTok{\# Thr = mean(Thresh\_test),}
 \NormalTok{                   .N),}
@@
 \end{Shaded}
+
+\newpage
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-5} \end{center}
+\newpage
 
@@
 \begin{verbatim}
-$mae
-[1] 83.65625
-
-$mse
-[1] 7337.38
-
-$rmse
-[1] 85.65851
-
-$mape
-[1] 0.1442124
-
-$nmse
-[1] 34.56461
-
-$rstd
-[1] 0.1471491
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-7-5} \end{center}
-
-\begin{verbatim}
 [1] 134

### 2024-05-14 GHI_enh_03_process.tex
Commit 2024-05-14 11:35

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-05-13}
+\date{2024-05-14}
 
@@
     Min      1Q  Median      3Q     Max 
--327.56 -157.11  -65.36  116.74  760.36
+-349.46 -163.23  -64.56  115.86  799.73
 
@@
                   Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      2.431e+02  4.880e+01   4.981  9.8e-07 ***
-as.numeric(Date) 6.397e-08  3.907e-08   1.637    0.102    
+(Intercept)      1.608e+02  5.029e+01   3.198 0.001507 ** 
+as.numeric(Date) 1.376e-07  4.026e-08   3.417 0.000704 ***
 ---
@@
 
-Residual standard error: 210.1 on 363 degrees of freedom
-Multiple R-squared:  0.007332,  Adjusted R-squared:  0.004597 
-F-statistic: 2.681 on 1 and 363 DF,  p-value: 0.1024
+Residual standard error: 216.5 on 363 degrees of freedom
+Multiple R-squared:  0.03117,   Adjusted R-squared:  0.0285 
+F-statistic: 11.68 on 1 and 363 DF,  p-value: 0.0007045
 \end{verbatim}
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       2.431e+02  4.880e+01   4.981  9.8e-07 ***
-ST_E_monthly$Date 6.397e-08  3.907e-08   1.637    0.102    
+(Intercept)       1.608e+02  5.029e+01   3.198 0.001507 ** 
+ST_E_monthly$Date 1.376e-07  4.026e-08   3.417 0.000704 ***
 ---
@@
 lm_zeropoint
+mean_55
+mean_BR_55
 mean_BR_mean
@@
 SelEnhanc
+slope_55
 slope_mean
@@
 \begin{verbatim}
-2024-05-13 09:11:34.5 athan@sagan GHI_enh_03_process.R 3.715344 mins
+2024-05-14 07:42:43.5 athan@tyler GHI_enh_03_process.R 11.010634 mins
 \end{verbatim}

### 2024-05-14 GHI_enh_04_investigate.tex
Commit 2024-05-13 12:21
Commit 2024-05-14 11:35

--- 2024-04-22 GHI_enh_04_investigate.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-21}
+\date{2024-05-14}
 
@@
 \begin{verbatim}
-
 Attaching package: 'zoo'
@@
 \begin{verbatim}
-
 Attaching package: 'ggpp'
@@
 
-lmD: 1.534136 +/- 0.10269
+lmD: 0.80888 +/- 0.10628
 
-lmY: 1.534151 +/- 0.102692
+lmY: 0.808883 +/- 0.106282
 
-Arima: 1.534524 +/- 0.137014
+Arima: 0.809228 +/- 0.142401
 
@@
 
-lmD: 0.957882 +/- 0.154677
+lmD: 0.002077 +/- 0.154863
 
-lmY: 0.957905 +/- 0.15468
+lmY: 0.002083 +/- 0.154866
 
-Arima: 1.026834 +/- 0.234823
+Arima: 0.069972 +/- 0.235505
 
@@
 
-lmD: 1.097965 +/- 0.167082
+lmD: 0.0726 +/- 0.167744
 
-lmY: 1.097991 +/- 0.167085
+lmY: 0.072609 +/- 0.167747
 
-Arima: 1.168104 +/- 0.247425
+Arima: 0.141941 +/- 0.249338
 
@@
 
-lmD: 1.054627 +/- 0.240574
+lmD: -0.087078 +/- 0.239888
 
-lmY: 1.054636 +/- 0.240578
+lmY: -0.087089 +/- 0.239892
 
-Arima: 1.054681 +/- 0.36529
+Arima: -0.087046 +/- 0.364497
 
@@
 
-lmD: 0.96011 +/- 0.254278
+lmD: -0.191061 +/- 0.253235
 
-lmY: 0.96012 +/- 0.254282
+lmY: -0.191072 +/- 0.253239
 
-Arima: 0.960167 +/- 0.389374
+Arima: -0.191026 +/- 0.387751
 
@@
 
-lmD: 1.084083 +/- 0.073658
+lmD: 0.442171 +/- 0.074674
 
-lmY: 1.084096 +/- 0.073659
+lmY: 0.442172 +/- 0.074676
 
-Arima: 1.0841 +/- 0.108761
+Arima: 0.442175 +/- 0.110249
 
@@
 
-lmD: 1.123441 +/- 0.069672
+lmD: 0.506855 +/- 0.071215
 
-lmY: 1.123454 +/- 0.069673
+lmY: 0.506856 +/- 0.071216
 
-Arima: 1.123462 +/- 0.099367
+Arima: 0.50686 +/- 0.101481
 
@@
 
-lmD: 33.98221 +/- 5.725078
+lmD: -1.191149 +/- 5.69247
 
-lmY: 33.98275 +/- 5.725178
+lmY: -1.191222 +/- 5.692569
 
-Arima: 34.039551 +/- 9.00373
+Arima: -1.138138 +/- 8.879593
 
@@
 
-lmD: 0.003272 +/- 0.000268
+lmD: 0.00182 +/- 0.000272
 
-lmY: 0.003272 +/- 0.000268
+lmY: 0.00182 +/- 0.000272
 
-Arima: 0.003296 +/- 0.000354
+Arima: 0.001843 +/- 0.000361
 
@@
 
-lmD: 0.001727 +/- 0.000275
+lmD: 0.000729 +/- 0.00028
 
-lmY: 0.001727 +/- 0.000275
+lmY: 0.00073 +/- 0.00028
 
-Arima: 0.001888 +/- 0.000454
+Arima: 0.000892 +/- 0.000462
 
@@
 
-lmD: 0.001702 +/- 0.000309
+lmD: 0.000678 +/- 0.000314
 
-lmY: 0.001702 +/- 0.000309
+lmY: 0.000678 +/- 0.000314
 
-Arima: 0.001865 +/- 0.000498
+Arima: 0.000841 +/- 0.000507
 
@@
 
-lmD: 0.001878 +/- 0.000305
+lmD: 0.001176 +/- 0.000309
 
-lmY: 0.001878 +/- 0.000305
+lmY: 0.001176 +/- 0.000309
 
-Arima: 0.001878 +/- 0.000475
+Arima: 0.001176 +/- 0.000483
 
@@
 
-lmD: 0.001807 +/- 0.000297
+lmD: 0.001189 +/- 0.000301
 
-lmY: 0.001807 +/- 0.000297
+lmY: 0.001189 +/- 0.000301
 
-Arima: 0.001807 +/- 0.000456
+Arima: 0.001189 +/- 0.000463
 
@@
 
-lmD: 0.002392 +/- 0.000231
+lmD: 0.001144 +/- 0.000235
 
-lmY: 0.002392 +/- 0.000231
+lmY: 0.001144 +/- 0.000235
 
-Arima: 0.002392 +/- 0.000359
+Arima: 0.001144 +/- 0.000366
 
@@
 
-lmD: 0.0026 +/- 0.000226
+lmD: 0.0013 +/- 0.00023
 
-lmY: 0.0026 +/- 0.000226
+lmY: 0.001301 +/- 0.00023
 
-Arima: 0.0026 +/- 0.000336
+Arima: 0.001301 +/- 0.000342
 
@@
 
-lmD: 0.982152 +/- 0.142979
+lmD: 0.376507 +/- 0.145413
 
-lmY: 0.982174 +/- 0.142982
+lmY: 0.376518 +/- 0.145415
 
-Arima: 1.043911 +/- 0.216442
+Arima: 0.436011 +/- 0.220423
 
@@
 
-lmD: 0.76413 +/- 0.10147
+lmD: 0.319795 +/- 0.10019
 
-lmY: 0.764141 +/- 0.101472
+lmY: 0.319795 +/- 0.100192
 
-Arima: 0.764136 +/- 0.117502
+Arima: 0.3198 +/- 0.116665
 
@@
 
-lmD: 0.202029 +/- 0.037949
+lmD: 0.10702 +/- 0.036516
 
-lmY: 0.202033 +/- 0.03795
+lmY: 0.107021 +/- 0.036517
 
-Arima: 0.202033 +/- 0.041317
+Arima: 0.107023 +/- 0.040195
 
@@
 
-lmD: 0.164435 +/- 0.03794
+lmD: 0.108459 +/- 0.036231
 
-lmY: 0.164439 +/- 0.037941
+lmY: 0.108461 +/- 0.036232
 
-Arima: 0.164439 +/- 0.040154
+Arima: 0.108462 +/- 0.03848
 
@@
 
-lmD: 0.430568 +/- 0.042844
+lmD: 0.144267 +/- 0.045486
 
-lmY: 0.430573 +/- 0.042845
+lmY: 0.144265 +/- 0.045487
 
-Arima: 0.430575 +/- 0.050183
+Arima: 0.144267 +/- 0.054102
 
@@
 
-lmD: -0.009715 +/- 0.019808
+lmD: 0.022726 +/- 0.0184
 
-lmY: -0.009713 +/- 0.019809
+lmY: 0.022726 +/- 0.0184
 
-Arima: -0.009713 +/- 0.019969
+Arima: 0.022726 +/- 0.018993
 
@@
 
-lmD: -0.024545 +/- 0.018498
+lmD: 0.018838 +/- 0.016889
 
-lmY: -0.024544 +/- 0.018499
+lmY: 0.018838 +/- 0.016889
 
-Arima: -0.024544 +/- 0.018581
+Arima: 0.018838 +/- 0.017339
 
@@
 
-lmD: 0.467007 +/- 0.072175
+lmD: 0.194707 +/- 0.070475
 
-lmY: 0.467013 +/- 0.072176
+lmY: 0.194706 +/- 0.070476
 
-Arima: 0.467011 +/- 0.080184
+Arima: 0.194713 +/- 0.07858
 
@@
 
-lmD: 0.567078 +/- 0.082222
+lmD: 0.227625 +/- 0.080608
 
-lmY: 0.567087 +/- 0.082223
+lmY: 0.227625 +/- 0.080609
 
-Arima: 0.567084 +/- 0.093419
+Arima: 0.22763 +/- 0.091764
 
@@
 
-lmD: 1.246547 +/- 0.136785
+lmD: 0.447759 +/- 0.147315
 
-lmY: 1.246567 +/- 0.136788
+lmY: 0.447759 +/- 0.147317
 
-Arima: 1.246568 +/- 0.164233
+Arima: 0.447766 +/- 0.177904
 
@@
 
-lmD: 0.001291 +/- 0.000137
+lmD: 0.000537 +/- 0.000135
 
-lmY: 0.001291 +/- 0.000137
+lmY: 0.000537 +/- 0.000135
 
-Arima: 0.001291 +/- 0.000158
+Arima: 0.000537 +/- 0.000157
 
@@
 
-lmD: 0.000409 +/- 6.1e-05
+lmD: 0.000206 +/- 6e-05
 
-lmY: 0.000409 +/- 6.1e-05
+lmY: 0.000206 +/- 6e-05
 
-Arima: 0.000409 +/- 7e-05
+Arima: 0.000206 +/- 6.8e-05
 
@@
 
-lmD: 0.00033 +/- 6.4e-05
+lmD: 0.000195 +/- 6.2e-05
 
-lmY: 0.00033 +/- 6.4e-05
+lmY: 0.000195 +/- 6.2e-05
 
-Arima: 0.00033 +/- 7.2e-05
+Arima: 0.000195 +/- 7e-05
 
@@
 
-lmD: 1.8e-05 +/- 3.3e-05
+lmD: 4.8e-05 +/- 3.1e-05
 
-lmY: 1.8e-05 +/- 3.3e-05
+lmY: 4.8e-05 +/- 3.1e-05
 
-Arima: 1.8e-05 +/- 3.8e-05
+Arima: 4.8e-05 +/- 3.6e-05
 
@@
 
-lmD: -8e-06 +/- 3e-05
+lmD: 3.7e-05 +/- 2.8e-05
 
-lmY: -8e-06 +/- 3e-05
+lmY: 3.7e-05 +/- 2.8e-05
 
-Arima: -8e-06 +/- 3.5e-05
+Arima: 3.7e-05 +/- 3.3e-05
 
@@
 
-lmD: 0.00091 +/- 0.000108
+lmD: 0.000394 +/- 0.000106
 
-lmY: 0.00091 +/- 0.000108
+lmY: 0.000394 +/- 0.000106
 
-Arima: 0.00091 +/- 0.000124
+Arima: 0.000394 +/- 0.000122
 
@@
 
-lmD: 0.001059 +/- 0.000118
+lmD: 0.00045 +/- 0.000117
 
-lmY: 0.001059 +/- 0.000118
+lmY: 0.00045 +/- 0.000117
 
-Arima: 0.001059 +/- 0.000137
+Arima: 0.00045 +/- 0.000135
 
@@
 
-lmD: 0.031908 +/- 0.003379
+lmD: 0.011422 +/- 0.003629
 
-lmY: 0.031908 +/- 0.003379
+lmY: 0.011422 +/- 0.003629
 
-Arima: 0.031908 +/- 0.003889
+Arima: 0.011422 +/- 0.004188
 
@@
 
-lmD: 0.210914 +/- 0.239629
+lmD: -1.014557 +/- 0.247144
 
-lmY: 0.21095 +/- 0.239633
+lmY: -1.014539 +/- 0.247148
 
-Arima: 0.199623 +/- 0.33989
+Arima: -1.025903 +/- 0.356761
 
@@
 
-lmD: 0.075139 +/- 0.179414
+lmD: -1.13974 +/- 0.188386
 
-lmY: 0.075162 +/- 0.179417
+lmY: -1.139735 +/- 0.188389
 
-Arima: 0.041751 +/- 0.315453
+Arima: -1.172188 +/- 0.333189
 
@@
 
-lmD: 0.116601 +/- 0.178114
+lmD: -1.100642 +/- 0.18719
 
-lmY: 0.116622 +/- 0.178117
+lmY: -1.100638 +/- 0.187194
 
-Arima: 0.082858 +/- 0.303922
+Arima: -1.133859 +/- 0.321558
 
@@
 
-lmD: -0.039715 +/- 0.164546
+lmD: -1.242646 +/- 0.174098
 
-lmY: -0.039705 +/- 0.164548
+lmY: -1.242654 +/- 0.174101
 
-Arima: -0.084179 +/- 0.309433
+Arima: -1.284884 +/- 0.324863
 
@@
 
-lmD: -0.059533 +/- 0.164108
+lmD: -1.259775 +/- 0.173629
 
-lmY: -0.059523 +/- 0.164111
+lmY: -1.259783 +/- 0.173632
 
-Arima: -0.103637 +/- 0.308351
+Arima: -1.301601 +/- 0.323343
 
@@
 
-lmD: 0.190061 +/- 0.219003
+lmD: -1.034796 +/- 0.226955
 
-lmY: 0.190097 +/- 0.219007
+lmY: -1.034779 +/- 0.226959
 
-Arima: 0.174594 +/- 0.326917
+Arima: -1.050406 +/- 0.344658
 
@@
 
-lmD: 0.200402 +/- 0.22785
+lmD: -1.02486 +/- 0.235592
 
-lmY: 0.200437 +/- 0.227854
+lmY: -1.024843 +/- 0.235596
 
-Arima: 0.187023 +/- 0.332301
+Arima: -1.038346 +/- 0.349707
 
@@
 
-lmD: 0.360189 +/- 0.242668
+lmD: 0.138738 +/- 0.251457
 
-lmY: 0.360214 +/- 0.242672
+lmY: 0.138759 +/- 0.251461
 
-Arima: 0.36031 +/- 0.247054
+Arima: 0.138867 +/- 0.256234
 
@@
 
-lmD: 0.000562 +/- 0.000289
+lmD: -0.001372 +/- 0.000292
 
-lmY: 0.000562 +/- 0.000289
+lmY: -0.001372 +/- 0.000292
 
-Arima: 0.000562 +/- 0.000319
+Arima: -0.001372 +/- 0.000322
 
@@
 
-lmD: 0.000393 +/- 0.000224
+lmD: -0.001515 +/- 0.000226
 
-lmY: 0.000393 +/- 0.000224
+lmY: -0.001515 +/- 0.000226
 
-Arima: 0.00039 +/- 0.000267
+Arima: -0.001519 +/- 0.000269
 
@@
 
-lmD: 0.000413 +/- 0.000232
+lmD: -0.001494 +/- 0.000234
 
-lmY: 0.000413 +/- 0.000232
+lmY: -0.001494 +/- 0.000234
 
-Arima: 0.000409 +/- 0.000272
+Arima: -0.001498 +/- 0.000275
 
@@
 
-lmD: 0.000208 +/- 0.000207
+lmD: -0.001682 +/- 0.000209
 
-lmY: 0.000208 +/- 0.000207
+lmY: -0.001683 +/- 0.000209
 
-Arima: 0.000201 +/- 0.000259
+Arima: -0.00169 +/- 0.000262
 
@@
 
-lmD: 0.000192 +/- 0.000206
+lmD: -0.001696 +/- 0.000208
 
-lmY: 0.000192 +/- 0.000206
+lmY: -0.001696 +/- 0.000208
 
-Arima: 0.000185 +/- 0.000259
+Arima: -0.001704 +/- 0.000262
 
@@
 
-lmD: 0.00056 +/- 0.000269
+lmD: -0.001367 +/- 0.000272
 
-lmY: 0.00056 +/- 0.000269
+lmY: -0.001367 +/- 0.000272
 
-Arima: 0.00056 +/- 0.000301
+Arima: -0.001367 +/- 0.000304
 
@@
 
-lmD: 0.000566 +/- 0.000278
+lmD: -0.001364 +/- 0.000281
 
-lmY: 0.000566 +/- 0.000278
+lmY: -0.001364 +/- 0.000281
 
-Arima: 0.000566 +/- 0.000309
+Arima: -0.001365 +/- 0.000312
 
@@
 
-lmD: 0.008619 +/- 0.005275
+lmD: 0.002612 +/- 0.005505
 
-lmY: 0.00862 +/- 0.005275
+lmY: 0.002612 +/- 0.005505
 
-Arima: 0.008644 +/- 0.005494
+Arima: 0.002638 +/- 0.005739
 
@@
 
-Arima: 0.202033 +/- 0.041317
+Arima: 0.107023 +/- 0.040196
 
@@
 \begin{verbatim}
-Warning: Removed 26 rows containing missing values or values outside the scale
+Warning: Removed 23 rows containing missing values or values outside the scale
 range (`geom_bar()`).
@@
 \begin{verbatim}
-Warning: Removed 13 rows containing non-finite outside the scale range
+Warning: Removed 19 rows containing non-finite outside the scale range
 (`stat_bin2d()`).
@@
 
-lmY: 293.3335 +/- 31.54861
+lmY: 129.677 +/- 37.08333
 
@@
 
-lmY: 110.0865 +/- 10.13369
+lmY: 48.08231 +/- 11.89152
 
@@
 
-lmY: 0.220182 +/- 0.057217
+lmY: 0.080779 +/- 0.053347
 
@@
 
-lmY: 0.168073 +/- 0.041495
+lmY: 0.065639 +/- 0.040043
 
@@
 \begin{verbatim}
-2024-04-21 18:52:46.0 athan@tyler GHI_enh_04_investigate.R 1.292554 mins
+2024-05-14 07:45:19.2 athan@tyler GHI_enh_04_investigate.R 2.165741 mins
 \end{verbatim}

### 2024-05-14 GHI_enh_Aeronet.tex
Commit 2024-05-02 09:10
Commit 2024-05-09 18:14
Commit 2024-05-14 11:35

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-05-01}
+\date{2024-05-14}
 
@@
 
-\begin{verbatim}
-[1] 2005.667
-\end{verbatim}
-
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-10} \end{center}
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-13} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-14} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-15} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-16} \end{center}
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-37} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-38} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-39} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-40} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-41} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-42} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-43} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-44} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-45} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-46} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-47} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-48} \end{center}
+
+SZA 55 : 0.00137369825595582
+
 \begin{longtable}[]{@{}
@@
 -1176 & 0.7354 & 12 & 302.4 & SZA median & 2014 & 0.002432 \\
+-847.8 & 0.7326 & 1 & 621.4 & SZA 55 & 2014 & 0.001179 \\
+-787.2 & 0.6968 & 2 & 608.5 & SZA 55 & 2015 & 0.001145 \\
+-1620 & 1.102 & 3 & 596.7 & SZA 55 & 2015 & 0.001848 \\
+-1575 & 1.071 & 4 & 570.5 & SZA 55 & 2015 & 0.001877 \\
+-1615 & 1.079 & 5 & 549.6 & SZA 55 & 2015 & 0.001964 \\
+-288.8 & 0.4157 & 6 & 536.3 & SZA 55 & 2015 & 0.000775 \\
+-483.7 & 0.5087 & 7 & 531.2 & SZA 55 & 2015 & 0.0009577 \\
+-140.4 & 0.3406 & 8 & 549.3 & SZA 55 & 2015 & 0.0006201 \\
+-415.5 & 0.4853 & 9 & 544.7 & SZA 55 & 2015 & 0.000891 \\
+-1327 & 0.9475 & 10 & 576 & SZA 55 & 2015 & 0.001645 \\
+-2204 & 1.393 & 11 & 567.8 & SZA 55 & 2015 & 0.002453 \\
+-785.3 & 0.6983 & 12 & 618.3 & SZA 55 & 2014 & 0.001129 \\
 \end{longtable}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-37} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-49} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-38} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-50} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-39} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-51} \end{center}
+
+\newpage
+
+\begin{longtable}[]{@{}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1667}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1667}}@{}}
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\centering
+year
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+typer
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+MeanGlo
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+1997 & BR SZA 55 & 578.9 \\
+2005 & SZA 55 & 576.4 \\
+2005 & BR SZA 55 & 588.6 \\
+2006 & SZA 55 & 574.9 \\
+2007 & SZA 55 & 584.7 \\
+2008 & SZA 55 & 615 \\
+2011 & SZA 55 & 562.4 \\
+2012 & SZA 55 & 582.9 \\
+2013 & SZA 55 & 582.1 \\
+2014 & SZA 55 & 594.3 \\
+2015 & SZA 55 & 586.7 \\
+2016 & SZA 55 & 583.9 \\
+2017 & SZA 55 & 581.3 \\
+2018 & SZA 55 & 581.2 \\
+2019 & SZA 55 & 584.4 \\
+2020 & SZA 55 & 600.3 \\
+2021 & SZA 55 & 587.5 \\
+2022 & SZA 55 & 587.4 \\
+2023 & SZA 55 & 583 \\
+\end{longtable}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-5-52} \end{center}
 

### 2024-05-14 GHI_enh_CSid.tex
Commit 2024-05-14 11:35

@@
 
-\begin{verbatim}
-SZA min : 0.00137165912186399 
-\end{verbatim}
-
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-27} \end{center}
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-29} \end{center}
+
+\begin{verbatim}
+SZA min : 0.00137165912186399 
+\end{verbatim}
 
@@
 
-\begin{verbatim}
-SZA mean : 0.0020024477410843 
-\end{verbatim}
-
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-39} \end{center}
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-41} \end{center}
+
+\begin{verbatim}
+SZA mean : 0.0020024477410843 
+\end{verbatim}
 
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-51} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-52} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-53} \end{center}
+
 \begin{verbatim}
 SZA median : 0.00184853525463023 
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-54} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-55} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-56} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-57} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-58} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-59} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-60} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-61} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-62} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-63} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-64} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-65} \end{center}
+
+\begin{verbatim}
+SZA 55 : 0.00137369825595582
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-51} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-66} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-52} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-67} \end{center}
+
+\begin{verbatim}
+
+\newpage
+\end{verbatim}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-5-68} \end{center}
 
@@
 \NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_median}
+\NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_55}
 \NormalTok{trend\_factor }\OtherTok{\textless{}{-}} \SpecialCharTok{{-}}\FloatTok{0.01995656}  \CommentTok{\# the same}
 \NormalTok{trend\_apply\_adj }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(tsy) \{}
-  \FunctionTok{trend\_median}\NormalTok{(tsy) }\SpecialCharTok{{-}} \FloatTok{0.01995656}
+  \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{{-}} \FloatTok{0.01995656}
 \NormalTok{\}}
@@
 \begin{verbatim}
-[1] -0.01599489 -0.01332907
+[1] -0.01247017 -0.01039180
 \end{verbatim}
@@
 $mae
-[1] 85.55033
+[1] 84.30937
 
 $mse
-[1] 8567.15
+[1] 8229.159
 
 $rmse
-[1] 92.5589
+[1] 90.71471
 
 $mape
-[1] 0.1365803
+[1] 0.1351012
 
 $nmse
-[1] 0.1436112
+[1] 0.1386586
 
 $rstd
-[1] 0.1400624
+[1] 0.1375293
 \end{verbatim}
@@
 $objective
-[1] 7042.576
+[1] 6810.44
 \end{verbatim}

### 2024-05-14 article/article.tex
Commit 2024-05-14 11:35

@@
 Our dataset, after the data selection processing, consists of 6144534
-records of GHI, of which \(1.906\,\%\) are CE and \(0.036\,\%\) are ECE
+records of GHI, of which \(1.95\,\%\) are CE and \(0.036\,\%\) are ECE
 events. The highest GHI recorder was \(1416.6\,W/m^2\) on 24~May 2007.
-The absolute stronger CE event had an OIR of \(353.46\,W/m^2\) on
-21~June 2001. The relative stronger CE event was \(49.9\,\%\) above the
-clear sky threshold, on 28~October 2016.
+The absolute stronger CE event had an OIR of \(353.05\,W/m^2\) on 24~May
+2007. The relative stronger CE event was \(50.7\,\%\) above the clear
+sky threshold, on 28~October 2016.
 
@@
 \citep{RCT2023}. The trends are reported together with the \(2\sigma\)
-error. We observe an increase of \(0.066\pm 0.08\,W/m^2/y\) on the mean
+error. We observe an increase of \(0.107\pm 0.08\,W/m^2/y\) on the mean
 OIR.
@@
 long term CE trends. Hence, we calculated the annual values from the
-one-minute measurements. The trend of OIR is \(0.03\pm 0.11\,W/m^2/y\)
+one-minute measurements. The trend of OIR is \(0.08\pm 0.11\,W/m^2/y\)
 (Figure\nobreakspace{}\ref{fig:P-energy-mean}), but this value alone is
@@
 The annual number of CE occurrences, shows a steady increase of
-\(20.1\pm 22.9\,\text{cases}/y\)
+\(48.1\pm 23.8\,\text{cases}/y\)
 (Figure\nobreakspace{}\ref{fig:P-energy-N}). We have to note that the
@@
 Subsequently, the mean annual increase of energy due to CE events is
-\(50.7\pm 71.2\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
+\(129.7\pm 74.2\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
 the trend of the number of occurrences.
@@
 Thus, a CEG consists of one or more successive CE cases, and can have a
-duration of multiple of minutes. We have identified 30221 groups, where
+duration of multiple of minutes. We have identified 30749 groups, where
 the group with the longest duration lasted 140 minutes on 07~July 2013.

### 2024-05-16 article/article.tex
Commit 2024-05-16 19:19

@@
 
+\hypertarget{climatology-of-clear-sky-irradiance}{%
+\subsubsection{Climatology of clear sky
+irradiance}\label{climatology-of-clear-sky-irradiance}}
+
 We approximated the expected clear sky GHI by using a radiation transfer
@@
 
-To create a look-up table that aligns with our dataset, we applied some
+To create a look-up table, that aligns with our dataset, we applied some
 adjustments. To account for the Sun's variability, in our one-minute GHI
-measurements, we adapted each modeled value by scaling the\\
-model's input spectrum integral, to the corresponding total solar
-irradiance (TSI) provided by NOAA \citep{Coddington2005}.\\
-Also, we applied the effect of the Earth -- Sun distance on the
-irradiance, by using the distance calculated by the Astropy
-\citep{AstropyCollaboration2022} software library. As needed, we
-interpolate the resulting irradiances to the exact SZA of our
-measurements. For each period of the year, we used the appropriate
-atmospheric profile (afglms or afglmw). Finally, we calculated the clear
-sky irradiance value at the horizontal plane. Thus, we were able to
-emulate different atmospheric condition and levels of atmospheric
-clearness for the climatological conditions of the site. With this
-method, the modeled clear sky irradiances can be directly compared to
-each measured one-minute value of GHI, for different conditions of
-atmospheric clearness.
+measurements, we adapted each modeled value by scaling the model's input
+spectrum integral, to the corresponding total solar irradiance (TSI)
+provided by NOAA \citep{Coddington2005}. Also, we account for the effect
+of the Earth -- Sun distance on the irradiance, by using the distance
+calculated by the Astropy \citep{AstropyCollaboration2022} software
+library. As needed, we interpolate the resulting irradiances to the
+exact SZA of our measurements. For each period of the year, we used the
+appropriate atmospheric profile (afglms or afglmw). Finally, we
+calculated the clear sky irradiance value at the horizontal plane. Thus,
+we were able to emulate different atmospheric condition and levels of
+atmospheric clearness for the climatological conditions of the site.
+With this method, the modeled clear sky irradiances can be directly
+compared to each measured one-minute value of GHI, for different
+conditions of atmospheric clearness.
+
+\hypertarget{long-term-change-of-clear-sky-irradiance}{%
+\subsubsection{Long term change of clear sky
+irradiance}\label{long-term-change-of-clear-sky-irradiance}}
+
+The above clear sky reference values are not enough to describe the long
+term variation due to the changes of the atmospheric constituents. As
+observed by \citet{Natsis2023}, there is long term brightening effect,
+over Thessaloniki for the studied period. In order to better describe
+this change, we used, estimations of AOD change derived from two
+sources. For 1993 -- 2005, \citet{Kazadzis2007} have found a change of
+\(-3.8\,\%\) per year at AOD on \(340\) nm, using a Brewer
+spectrophotometer. For 2005 to 2023, we derived the trend from the
+available AERONET data.
+
+To create a unified trend for the long term change of the clear sky
+irradiance, we sim simulated
 

### 2024-05-16 GHI_enh_Aeronet.R

@@ -223,6 +223,7 @@ LKU_month <- LKU[, .(sun_dist     = mean(sun_dist),
                      tsi_1au_comb = mean(tsi_1au_comb)),
                  by = .(year(Date), month(Date))]
 
+## Nine years of UV aerosol optical depth measurements at {T}hessaloniki, {G}reece
 LKU_year <- LKU[, .(sun_dist     = mean(sun_dist),
                     tsi_1au_comb = mean(tsi_1au_comb),
                     month        = NA),

### 2024-05-16 article/article.Rmd
Commit 2024-05-16 19:19

@@
 
+### Climatology of clear sky irradiance
+
 We approximated the expected clear sky GHI by using a radiation transfer model.  The
@@
 <!-- Lookup table -->
-To create a look-up table that aligns with our dataset, we applied some adjustments.
-To account for the Sun's variability, in our one-minute GHI measurements, 
-we adapted each modeled value by scaling the  
-model's input spectrum integral, to the corresponding total solar irradiance (TSI)
-provided by NOAA [@Coddington2005].  
-Also, we applied the effect of the Earth -- Sun
-distance on the irradiance, by using the distance calculated by the Astropy
-[@AstropyCollaboration2022] software library. As needed, we interpolate the resulting
-irradiances to the exact SZA of our measurements.  For each period of the year, we
-used the appropriate atmospheric profile (afglms or afglmw).  Finally, we calculated
-the clear sky irradiance value at the horizontal plane.  Thus, we were able to
-emulate different atmospheric condition and levels of atmospheric clearness for the
-climatological conditions of the site.  With this method, the modeled clear sky
-irradiances can be directly compared to each measured one-minute value of GHI, for
-different conditions of atmospheric clearness.
+To create a look-up table, that aligns with our dataset, we applied some adjustments.
+To account for the Sun's variability, in our one-minute GHI measurements, we adapted
+each modeled value by scaling the model's input spectrum integral, to the
+corresponding total solar irradiance (TSI) provided by NOAA [@Coddington2005].  Also,
+we account for the effect of the Earth -- Sun distance on the irradiance, by using
+the distance calculated by the Astropy [@AstropyCollaboration2022] software library.
+As needed, we interpolate the resulting irradiances to the exact SZA of our
+measurements.  For each period of the year, we used the appropriate atmospheric
+profile (afglms or afglmw).  Finally, we calculated the clear sky irradiance value at
+the horizontal plane.  Thus, we were able to emulate different atmospheric condition
+and levels of atmospheric clearness for the climatological conditions of the site.
+With this method, the modeled clear sky irradiances can be directly compared to each
+measured one-minute value of GHI, for different conditions of atmospheric clearness.
+
+### Long term change of clear sky irradiance
+
+<!-- Aerosol change -->
+The above clear sky reference values are not enough to describe the long term
+variation due to the changes of the atmospheric constituents. As observed
+by @Natsis2023, there is long term brightening effect, over Thessaloniki for the
+studied period. In order to better describe this change, we used, estimations of AOD
+change derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change
+of $-3.8\,\%$ per year at AOD on $340$ nm, using a Brewer spectrophotometer. For 2005
+to 2023, we derived the trend from the available AERONET data.
+
+To create a unified trend for the long term change of the clear sky irradiance, we
+sim simulated
 

### 2024-05-17 article/article.tex
Commit 2024-05-17 11:12

@@
 sources. For 1993 -- 2005, \citet{Kazadzis2007} have found a change of
-\(-3.8\,\%\) per year at AOD on \(340\) nm, using a Brewer
+\(-3.8\,\%\) per year at AOD on \(340\,\text{nm}\), using a Brewer
 spectrophotometer. For 2005 to 2023, we derived the trend from the
@@
 To create a unified trend for the long term change of the clear sky
-irradiance, we sim simulated
+irradiance, we simulated the values of AOD derived from those sources
+with Libradtran. For both, we use the AOD at \(500\,\text{nm}\), which
+was inferred by the available Ångström exponent, and we choose the SZA
+of \(55^\circ\) as a representative value for all runs.
+
+For the period 1993 -- 2005
+
+For the period 2005 -- 2005 we used
 

### 2024-05-17 article/article.Rmd
Commit 2024-05-17 11:12

@@
 change derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change
-of $-3.8\,\%$ per year at AOD on $340$ nm, using a Brewer spectrophotometer. For 2005
+of $-3.8\,\%$ per year at AOD on $340\,\text{nm}$, using a Brewer spectrophotometer. For 2005
 to 2023, we derived the trend from the available AERONET data.
@@
 To create a unified trend for the long term change of the clear sky irradiance, we
-sim simulated
+simulated the values of AOD derived from those sources with Libradtran. For both, we
+use the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
+exponent, and we choose the SZA of $55^\circ$ as a representative value for all runs.
+
+For the period 1993 -- 2005
+
+For the period 2005 -- 2005 we used
 

### 2024-05-17 article/article.Rmd
Commit 2024-05-17 12:14

@@
 simulated the values of AOD derived from those sources with Libradtran. For both, we
-use the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
-exponent, and we choose the SZA of $55^\circ$ as a representative value for all runs.
-
-For the period 1993 -- 2005
-
-For the period 2005 -- 2005 we used
+used the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
+coefficients, and we choose the SZA of $55^\circ$ as a representative value for all runs.
+For the first period, the alpha Ångström coefficient is $1.6$ and the beta
+coefficient $0.086$ and $0.059$, for 1997 and 2005 respectively. By interpolating the
+resulting clear sky irradiance, we have a trend of $+0.21\,\%$ per year.
+For the period 2005 -- 2005 we used the mean monthly values from AERONET, with a
+similar simulation scheme. We computed the trend of clear sky radiation for each
+month of the year, which gave us a mean clear sky radiation trend of $+0.14\,\%$ per year.
 

### 2024-05-17 article/article.tex
Commit 2024-05-17 12:14

@@
 irradiance, we simulated the values of AOD derived from those sources
-with Libradtran. For both, we use the AOD at \(500\,\text{nm}\), which
-was inferred by the available Ångström exponent, and we choose the SZA
-of \(55^\circ\) as a representative value for all runs.
-
-For the period 1993 -- 2005
-
-For the period 2005 -- 2005 we used
+with Libradtran. For both, we used the AOD at \(500\,\text{nm}\), which
+was inferred by the available Ångström coefficients, and we choose the
+SZA of \(55^\circ\) as a representative value for all runs. For the
+first period, the alpha Ångström coefficient is \(1.6\) and the beta
+coefficient \(0.086\) and \(0.059\), for 1997 and 2005 respectively. By
+interpolating the resulting clear sky irradiance, we have a trend of
+\(+0.21\,\%\) per year. For the period 2005 -- 2005 we used the mean
+monthly values from AERONET, with a similar simulation scheme. We
+computed the trend of clear sky radiation for each month of the year,
+which gave us a mean clear sky radiation trend of \(+0.14\,\%\) per
+year.
 

### 2024-05-17 GHI_enh_07_Aerosols.tex
Commit 2024-05-17 13:12

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  a4paper,oneside]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Enhancement of SDR in Thessaloniki},
  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{placeins}
\captionsetup{font=small}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-17}

\begin{document}
\maketitle
\begin{abstract}
Study of GHI enchantment.
\end{abstract}

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Cross over point: 2005 
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-5} \end{center}

\begin{verbatim}
[1] 1997
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-12} \end{center}

SZA min : 0.00137165912186399

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-24} \end{center}

SZA mean : 0.0020024477410843

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-33} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-34} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-35} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-36} \end{center}

SZA median : 0.00184853525463023

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-37} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-38} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-39} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-40} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-41} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-42} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-43} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-44} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-45} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-46} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-47} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-48} \end{center}

SZA 55 : 0.00137369825595582

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1184}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1053}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1316}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1711}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}
  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
Intercept
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Slope
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Month
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
MeanGlo
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Zeropoint
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
SlopeRela
\end{minipage} \\
\midrule
\endhead
-1102 & 0.8309 & 1 & 565.8 & SZA min & 2014 & 0.001469 \\
-810.5 & 0.7648 & 2 & 721.8 & SZA min & 2015 & 0.00106 \\
-6892 & 3.872 & 3 & 888.2 & SZA min & 2015 & 0.00436 \\
-1277 & 1.124 & 4 & 974.5 & SZA min & 2015 & 0.001153 \\
-982.7 & 0.9904 & 5 & 1004 & SZA min & 2015 & 0.0009866 \\
375.1 & 0.3116 & 6 & 993.2 & SZA min & 2015 & 0.0003138 \\
-140.7 & 0.5624 & 7 & 984 & SZA min & 2015 & 0.0005715 \\
444.2 & 0.2576 & 8 & 967.6 & SZA min & 2015 & 0.0002663 \\
-3.347 & 0.4436 & 9 & 872.7 & SZA min & 2015 & 0.0005082 \\
-1081 & 0.9159 & 10 & 758.3 & SZA min & 2015 & 0.001208 \\
-2109 & 1.345 & 11 & 565.3 & SZA min & 2015 & 0.002379 \\
-1598 & 1.044 & 12 & 477.6 & SZA min & 2014 & 0.002186 \\
-1221 & 0.756 & 1 & 293.9 & SZA mean & 2014 & 0.002573 \\
-1063 & 0.7194 & 2 & 377.8 & SZA mean & 2015 & 0.001904 \\
-1776 & 1.125 & 3 & 485.6 & SZA mean & 2015 & 0.002317 \\
-1680 & 1.118 & 4 & 561.4 & SZA mean & 2015 & 0.001992 \\
-1628 & 1.111 & 5 & 599.9 & SZA mean & 2015 & 0.001852 \\
-262.2 & 0.4374 & 6 & 606.9 & SZA mean & 2015 & 0.0007207 \\
-745.5 & 0.6689 & 7 & 592.1 & SZA mean & 2015 & 0.00113 \\
-122.7 & 0.3402 & 8 & 566.4 & SZA mean & 2015 & 0.0006007 \\
-474.5 & 0.4816 & 9 & 477.8 & SZA mean & 2015 & 0.001008 \\
-1443 & 0.9151 & 10 & 394.4 & SZA mean & 2015 & 0.00232 \\
-2438 & 1.364 & 11 & 277.9 & SZA mean & 2015 & 0.004907 \\
-1179 & 0.7187 & 12 & 265.7 & SZA mean & 2014 & 0.002705 \\
-1216 & 0.772 & 1 & 331.6 & SZA median & 2014 & 0.002328 \\
-1041 & 0.7293 & 2 & 419.7 & SZA median & 2015 & 0.001738 \\
-1743 & 1.129 & 3 & 527.8 & SZA median & 2015 & 0.00214 \\
-1654 & 1.123 & 4 & 595.7 & SZA median & 2015 & 0.001884 \\
-1595 & 1.105 & 5 & 620.6 & SZA median & 2015 & 0.00178 \\
-243.2 & 0.4343 & 6 & 619.6 & SZA median & 2015 & 0.0007009 \\
-708.1 & 0.6584 & 7 & 608.4 & SZA median & 2015 & 0.001082 \\
-109.2 & 0.3477 & 8 & 595.2 & SZA median & 2015 & 0.0005842 \\
-441.5 & 0.4846 & 9 & 516.9 & SZA median & 2015 & 0.0009376 \\
-1433 & 0.9306 & 10 & 435.1 & SZA median & 2015 & 0.002139 \\
-2464 & 1.395 & 11 & 314.5 & SZA median & 2015 & 0.004436 \\
-1176 & 0.7354 & 12 & 302.4 & SZA median & 2014 & 0.002432 \\
-847.8 & 0.7326 & 1 & 621.4 & SZA 55 & 2014 & 0.001179 \\
-787.2 & 0.6968 & 2 & 608.5 & SZA 55 & 2015 & 0.001145 \\
-1620 & 1.102 & 3 & 596.7 & SZA 55 & 2015 & 0.001848 \\
-1575 & 1.071 & 4 & 570.5 & SZA 55 & 2015 & 0.001877 \\
-1615 & 1.079 & 5 & 549.6 & SZA 55 & 2015 & 0.001964 \\
-288.8 & 0.4157 & 6 & 536.3 & SZA 55 & 2015 & 0.000775 \\
-483.7 & 0.5087 & 7 & 531.2 & SZA 55 & 2015 & 0.0009577 \\
-140.4 & 0.3406 & 8 & 549.3 & SZA 55 & 2015 & 0.0006201 \\
-415.5 & 0.4853 & 9 & 544.7 & SZA 55 & 2015 & 0.000891 \\
-1327 & 0.9475 & 10 & 576 & SZA 55 & 2015 & 0.001645 \\
-2204 & 1.393 & 11 & 567.8 & SZA 55 & 2015 & 0.002453 \\
-785.3 & 0.6983 & 12 & 618.3 & SZA 55 & 2014 & 0.001129 \\
\bottomrule
\end{longtable}

\newpage

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2222}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1389}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
year
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
typer
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
MeanGlo
\end{minipage} \\
\midrule
\endhead
1997 & BR SZA median & 449.5 \\
2005 & SZA median & 392.1 \\
2005 & BR SZA median & 459.3 \\
2006 & SZA median & 493.1 \\
2007 & SZA median & 470.8 \\
2008 & SZA median & 326.2 \\
2011 & SZA median & 505.1 \\
2012 & SZA median & 500.8 \\
2013 & SZA median & 498.6 \\
2014 & SZA median & 477.7 \\
2015 & SZA median & 504.8 \\
2016 & SZA median & 510.9 \\
2017 & SZA median & 551.4 \\
2018 & SZA median & 499.7 \\
2019 & SZA median & 476 \\
2020 & SZA median & 483.7 \\
2021 & SZA median & 506 \\
2022 & SZA median & 554.9 \\
2023 & SZA median & 522.8 \\
\bottomrule
\end{longtable}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-49} \end{center}

\newpage

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1806}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1389}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
year
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
typer
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
MeanGlo
\end{minipage} \\
\midrule
\endhead
1997 & BR SZA min & 1055 \\
2005 & SZA min & 668.3 \\
2005 & BR SZA min & 1064 \\
2006 & SZA min & 817.1 \\
2007 & SZA min & 785.1 \\
2008 & SZA min & 557.2 \\
2011 & SZA min & 831.1 \\
2012 & SZA min & 824.3 \\
2013 & SZA min & 814 \\
2014 & SZA min & 822.1 \\
2015 & SZA min & 828.6 \\
2016 & SZA min & 832.3 \\
2017 & SZA min & 899.3 \\
2018 & SZA min & 822.3 \\
2019 & SZA min & 789.7 \\
2020 & SZA min & 820.3 \\
2021 & SZA min & 829.7 \\
2022 & SZA min & 902.4 \\
2023 & SZA min & 859.5 \\
\bottomrule
\end{longtable}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-50} \end{center}

\newpage

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1944}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1389}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
year
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
typer
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
MeanGlo
\end{minipage} \\
\midrule
\endhead
1997 & BR SZA mean & 497.3 \\
2005 & SZA mean & 353.9 \\
2005 & BR SZA mean & 507.1 \\
2006 & SZA mean & 460.7 \\
2007 & SZA mean & 434.8 \\
2008 & SZA mean & 288.6 \\
2011 & SZA mean & 476.1 \\
2012 & SZA mean & 468.4 \\
2013 & SZA mean & 468.5 \\
2014 & SZA mean & 444.8 \\
2015 & SZA mean & 472.3 \\
2016 & SZA mean & 480.3 \\
2017 & SZA mean & 520.9 \\
2018 & SZA mean & 467.3 \\
2019 & SZA mean & 440.6 \\
2020 & SZA mean & 450.8 \\
2021 & SZA mean & 473.5 \\
2022 & SZA mean & 525.5 \\
2023 & SZA mean & 490.7 \\
\bottomrule
\end{longtable}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-51} \end{center}

\newpage

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1667}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1667}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
year
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
typer
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
MeanGlo
\end{minipage} \\
\midrule
\endhead
1997 & BR SZA 55 & 578.9 \\
2005 & SZA 55 & 576.4 \\
2005 & BR SZA 55 & 588.6 \\
2006 & SZA 55 & 574.9 \\
2007 & SZA 55 & 584.7 \\
2008 & SZA 55 & 615 \\
2011 & SZA 55 & 562.4 \\
2012 & SZA 55 & 582.9 \\
2013 & SZA 55 & 582.1 \\
2014 & SZA 55 & 594.3 \\
2015 & SZA 55 & 586.7 \\
2016 & SZA 55 & 583.9 \\
2017 & SZA 55 & 581.3 \\
2018 & SZA 55 & 581.2 \\
2019 & SZA 55 & 584.4 \\
2020 & SZA 55 & 600.3 \\
2021 & SZA 55 & 587.5 \\
2022 & SZA 55 & 587.4 \\
2023 & SZA 55 & 583 \\
\bottomrule
\end{longtable}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-52} \end{center}

\begin{verbatim}
Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
i Please use the `legend.position.inside` argument of `theme()` instead.
This warning is displayed once every 8 hours.
Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/P_CS_change-1} \end{center}

null device
1

\textbf{END}

\end{document}

### 2024-05-20 article/article.Rmd
Commit 2024-05-17 13:12
Commit 2024-05-17 14:14
Commit 2024-05-20 11:19

@@
 The above clear sky reference values are not enough to describe the long term
-variation due to the changes of the atmospheric constituents. As observed
-by @Natsis2023, there is long term brightening effect, over Thessaloniki for the
-studied period. In order to better describe this change, we used, estimations of AOD
-change derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change
-of $-3.8\,\%$ per year at AOD on $340\,\text{nm}$, using a Brewer spectrophotometer. For 2005
-to 2023, we derived the trend from the available AERONET data.
+variation due to the changes of the atmospheric constituents. As observed by
+@Natsis2023, there is long term brightening effect, over Thessaloniki for the studied
+period. In order to better describe this change, we used, estimations of AOD change
+derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change of
+$-3.8\,\%$ per year at AOD on $340\,\text{nm}$, using a Brewer spectrophotometer. For
+2005 to 2023, we derived the trend from the available AERONET data.
 
@@
 used the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
-coefficients, and we choose the SZA of $55^\circ$ as a representative value for all runs.
-For the first period, the alpha Ångström coefficient is $1.6$ and the beta
+coefficients, and we choose the SZA of $55^\circ$ as a representative value for all
+runs.  For the first period, the alpha Ångström coefficient is $1.6$ and the beta
 coefficient $0.086$ and $0.059$, for 1997 and 2005 respectively. By interpolating the
-resulting clear sky irradiance, we have a trend of $+0.21\,\%$ per year.
-For the period 2005 -- 2005 we used the mean monthly values from AERONET, with a
-similar simulation scheme. We computed the trend of clear sky radiation for each
-month of the year, which gave us a mean clear sky radiation trend of $+0.14\,\%$ per year.
+resulting clear sky irradiance, we have a trend of $+0.21\,\%$ per year.  For the
+period 2005 -- 2005 we used the mean monthly values from AERONET, with a similar
+simulation scheme. We computed the trend of clear sky radiation for each month of the
+year, which gave us a mean clear sky radiation trend of $+0.14\,\%$ per year.
+
+<!--
+# Kazadzis2007 - Nine years of UV aerosol optical depth measurements at Thessaloniki, Greece
+# From Stelios' paper 2007:
+# AOD @340 from Brewer 086
+# Period: 1997-2005
+# The mean AOD for this period was calculated to 0.403 for the Brewer and 0.422 for the CIMEL.
+# A linear regression on the Brewer deseasonalized data reveals a change of −3.8±0.93% per year.
+# From the above data AOD @340 changes by 0.0153 per year (or 0.138 for the 9 years).
+# Using Angstrom a= 1.6  this translates to a change in Angstrom β=0.00272 per year (or β=0.084 in 1997 and β=0.059 in 2005).
+-->
 

### 2024-05-21 GHI_enh_03_process.tex
Commit 2024-05-21 10:14

--- 2024-05-13 GHI_enh_03_process.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-05-13}
+\date{2024-05-20}
 
@@
     Min      1Q  Median      3Q     Max 
--327.56 -157.11  -65.36  116.74  760.36
+-319.48 -147.87  -56.18  101.04  719.45
 
@@
                   Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      2.431e+02  4.880e+01   4.981  9.8e-07 ***
-as.numeric(Date) 6.397e-08  3.907e-08   1.637    0.102    
+(Intercept)      1.379e+02  4.559e+01   3.025 0.002663 ** 
+as.numeric(Date) 1.306e-07  3.650e-08   3.579 0.000391 ***
 ---
@@
 
-Residual standard error: 210.1 on 363 degrees of freedom
-Multiple R-squared:  0.007332,  Adjusted R-squared:  0.004597 
-F-statistic: 2.681 on 1 and 363 DF,  p-value: 0.1024
+Residual standard error: 196.3 on 363 degrees of freedom
+Multiple R-squared:  0.03409,   Adjusted R-squared:  0.03143 
+F-statistic: 12.81 on 1 and 363 DF,  p-value: 0.0003913
 \end{verbatim}
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       2.431e+02  4.880e+01   4.981  9.8e-07 ***
-ST_E_monthly$Date 6.397e-08  3.907e-08   1.637    0.102    
+(Intercept)       1.379e+02  4.559e+01   3.025 0.002663 ** 
+ST_E_monthly$Date 1.306e-07  3.650e-08   3.579 0.000391 ***
 ---
@@
 aday
+adjpoint55
 AEin1
@@
 \begin{verbatim}
-2024-05-13 09:11:34.5 athan@sagan GHI_enh_03_process.R 3.715344 mins
+2024-05-20 16:54:33.3 athan@tyler GHI_enh_03_process.R 6.553817 mins
 \end{verbatim}

### 2024-05-21 GHI_enh_04_investigate.tex
Commit 2024-05-21 10:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-05-14}
+\date{2024-05-20}
 
@@
 
-lmD: 0.80888 +/- 0.10628
+lmD: 0.804776 +/- 0.104681
 
-lmY: 0.808883 +/- 0.106282
+lmY: 0.804779 +/- 0.104683
 
-Arima: 0.809228 +/- 0.142401
+Arima: 0.805121 +/- 0.139935
 
@@
 
-lmD: 0.002077 +/- 0.154863
+lmD: 0.002645 +/- 0.154816
 
-lmY: 0.002083 +/- 0.154866
+lmY: 0.002651 +/- 0.154818
 
-Arima: 0.069972 +/- 0.235505
+Arima: 0.069946 +/- 0.23533
 
@@
 
-lmD: 0.0726 +/- 0.167744
+lmD: 0.075523 +/- 0.167494
 
-lmY: 0.072609 +/- 0.167747
+lmY: 0.075532 +/- 0.167497
 
-Arima: 0.141941 +/- 0.249338
+Arima: 0.144037 +/- 0.248629
 
@@
 
-lmD: -0.087078 +/- 0.239888
+lmD: -0.093964 +/- 0.240209
 
-lmY: -0.087089 +/- 0.239892
+lmY: -0.093975 +/- 0.240213
 
-Arima: -0.087046 +/- 0.364497
+Arima: -0.093932 +/- 0.364937
 
@@
 
-lmD: -0.191061 +/- 0.253235
+lmD: -0.197599 +/- 0.2537
 
-lmY: -0.191072 +/- 0.253239
+lmY: -0.197611 +/- 0.253704
 
-Arima: -0.191026 +/- 0.387751
+Arima: -0.197564 +/- 0.388597
 
@@
 
-lmD: 0.442171 +/- 0.074674
+lmD: 0.446578 +/- 0.074214
 
-lmY: 0.442172 +/- 0.074676
+lmY: 0.446579 +/- 0.074216
 
-Arima: 0.442175 +/- 0.110249
+Arima: 0.446582 +/- 0.10962
 
@@
 
-lmD: 0.506855 +/- 0.071215
+lmD: 0.508145 +/- 0.070493
 
-lmY: 0.506856 +/- 0.071216
+lmY: 0.508147 +/- 0.070494
 
-Arima: 0.50686 +/- 0.101481
+Arima: 0.508152 +/- 0.100518
 
@@
 
-lmD: -1.191149 +/- 5.69247
+lmD: -1.087297 +/- 5.707626
 
-lmY: -1.191222 +/- 5.692569
+lmY: -1.087374 +/- 5.707725
 
-Arima: -1.138138 +/- 8.879593
+Arima: -1.035804 +/- 8.936135
 
@@
 
-lmD: 0.00182 +/- 0.000272
+lmD: 0.001815 +/- 0.00027
 
-lmY: 0.00182 +/- 0.000272
+lmY: 0.001815 +/- 0.00027
 
-Arima: 0.001843 +/- 0.000361
+Arima: 0.001839 +/- 0.000358
 
@@
 
-lmD: 0.000729 +/- 0.00028
+lmD: 0.00073 +/- 0.000278
 
-lmY: 0.00073 +/- 0.00028
+lmY: 0.00073 +/- 0.000278
 
-Arima: 0.000892 +/- 0.000462
+Arima: 0.000891 +/- 0.000459
 
@@
 
-lmD: 0.000678 +/- 0.000314
+lmD: 0.000679 +/- 0.000312
 
-lmY: 0.000678 +/- 0.000314
+lmY: 0.000679 +/- 0.000312
 
-Arima: 0.000841 +/- 0.000507
+Arima: 0.00084 +/- 0.000504
 
@@
 
-lmD: 0.001176 +/- 0.000309
+lmD: 0.001171 +/- 0.000307
 
-lmY: 0.001176 +/- 0.000309
+lmY: 0.001171 +/- 0.000307
 
-Arima: 0.001176 +/- 0.000483
+Arima: 0.001171 +/- 0.000479
 
@@
 
-lmD: 0.001189 +/- 0.000301
+lmD: 0.001184 +/- 0.000299
 
-lmY: 0.001189 +/- 0.000301
+lmY: 0.001184 +/- 0.000299
 
-Arima: 0.001189 +/- 0.000463
+Arima: 0.001184 +/- 0.00046
 
@@
 
-lmD: 0.001144 +/- 0.000235
+lmD: 0.001143 +/- 0.000233
 
-lmY: 0.001144 +/- 0.000235
+lmY: 0.001143 +/- 0.000233
 
-Arima: 0.001144 +/- 0.000366
+Arima: 0.001143 +/- 0.000363
 
@@
 
-lmD: 0.0013 +/- 0.00023
+lmD: 0.001299 +/- 0.000228
 
-lmY: 0.001301 +/- 0.00023
+lmY: 0.001299 +/- 0.000228
 
-Arima: 0.001301 +/- 0.000342
+Arima: 0.001299 +/- 0.00034
 
@@
 
-lmD: 0.376507 +/- 0.145413
+lmD: 0.379481 +/- 0.144397
 
-lmY: 0.376518 +/- 0.145415
+lmY: 0.379493 +/- 0.1444
 
-Arima: 0.436011 +/- 0.220423
+Arima: 0.438045 +/- 0.218822
 
@@
 
-lmD: 0.319795 +/- 0.10019
+lmD: 0.278784 +/- 0.099757
 
-lmY: 0.319795 +/- 0.100192
+lmY: 0.278785 +/- 0.099759
 
-Arima: 0.3198 +/- 0.116665
+Arima: 0.278791 +/- 0.11495
 
@@
 
-lmD: 0.10702 +/- 0.036516
+lmD: 0.086758 +/- 0.036893
 
-lmY: 0.107021 +/- 0.036517
+lmY: 0.086759 +/- 0.036894
 
-Arima: 0.107023 +/- 0.040195
+Arima: 0.086761 +/- 0.03998
 
@@
 
-lmD: 0.108459 +/- 0.036231
+lmD: 0.089859 +/- 0.036694
 
-lmY: 0.108461 +/- 0.036232
+lmY: 0.089861 +/- 0.036694
 
-Arima: 0.108462 +/- 0.03848
+Arima: 0.089862 +/- 0.038687
 
@@
 
-lmD: 0.144267 +/- 0.045486
+lmD: 0.134313 +/- 0.043256
 
-lmY: 0.144265 +/- 0.045487
+lmY: 0.134312 +/- 0.043256
 
-Arima: 0.144267 +/- 0.054102
+Arima: 0.134314 +/- 0.05079
 
@@
 
-lmD: 0.022726 +/- 0.0184
+lmD: 0.010492 +/- 0.018772
 
-lmY: 0.022726 +/- 0.0184
+lmY: 0.010493 +/- 0.018773
 
-Arima: 0.022726 +/- 0.018993
+Arima: 0.010494 +/- 0.019022
 
@@
 
-lmD: 0.018838 +/- 0.016889
+lmD: 0.006132 +/- 0.017414
 
-lmY: 0.018838 +/- 0.016889
+lmY: 0.006133 +/- 0.017414
 
-Arima: 0.018838 +/- 0.017339
+Arima: 0.006133 +/- 0.017662
 
@@
 
-lmD: 0.194707 +/- 0.070475
+lmD: 0.160601 +/- 0.070705
 
-lmY: 0.194706 +/- 0.070476
+lmY: 0.160602 +/- 0.070706
 
-Arima: 0.194713 +/- 0.07858
+Arima: 0.160604 +/- 0.07797
 
@@
 
-lmD: 0.227625 +/- 0.080608
+lmD: 0.198524 +/- 0.080714
 
-lmY: 0.227625 +/- 0.080609
+lmY: 0.198524 +/- 0.080715
 
-Arima: 0.22763 +/- 0.091764
+Arima: 0.198532 +/- 0.091006
 
@@
 
-lmD: 0.447759 +/- 0.147315
+lmD: 0.386176 +/- 0.138337
 
-lmY: 0.447759 +/- 0.147317
+lmY: 0.386177 +/- 0.13834
 
-Arima: 0.447766 +/- 0.177904
+Arima: 0.386184 +/- 0.16586
 
@@
 
-lmD: 0.000537 +/- 0.000135
+lmD: 0.000476 +/- 0.000135
 
-lmY: 0.000537 +/- 0.000135
+lmY: 0.000476 +/- 0.000135
 
-Arima: 0.000537 +/- 0.000157
+Arima: 0.000476 +/- 0.000155
 
@@
 
-lmD: 0.000206 +/- 6e-05
+lmD: 0.000172 +/- 6e-05
 
-lmY: 0.000206 +/- 6e-05
+lmY: 0.000172 +/- 6e-05
 
-Arima: 0.000206 +/- 6.8e-05
+Arima: 0.000172 +/- 6.8e-05
 
@@
 
-lmD: 0.000195 +/- 6.2e-05
+lmD: 0.00016 +/- 6.3e-05
 
-lmY: 0.000195 +/- 6.2e-05
+lmY: 0.00016 +/- 6.3e-05
 
-Arima: 0.000195 +/- 7e-05
+Arima: 0.00016 +/- 7e-05
 
@@
 
-lmD: 4.8e-05 +/- 3.1e-05
+lmD: 2.8e-05 +/- 3.2e-05
 
-lmY: 4.8e-05 +/- 3.1e-05
+lmY: 2.8e-05 +/- 3.2e-05
 
-Arima: 4.8e-05 +/- 3.6e-05
+Arima: 2.8e-05 +/- 3.6e-05
 
@@
 
-lmD: 3.7e-05 +/- 2.8e-05
+lmD: 1.7e-05 +/- 2.9e-05
 
-lmY: 3.7e-05 +/- 2.8e-05
+lmY: 1.7e-05 +/- 2.9e-05
 
-Arima: 3.7e-05 +/- 3.3e-05
+Arima: 1.7e-05 +/- 3.3e-05
 
@@
 
-lmD: 0.000394 +/- 0.000106
+lmD: 0.000347 +/- 0.000106
 
-lmY: 0.000394 +/- 0.000106
+lmY: 0.000347 +/- 0.000106
 
-Arima: 0.000394 +/- 0.000122
+Arima: 0.000347 +/- 0.000121
 
@@
 
-lmD: 0.00045 +/- 0.000117
+lmD: 0.000402 +/- 0.000116
 
-lmY: 0.00045 +/- 0.000117
+lmY: 0.000402 +/- 0.000116
 
-Arima: 0.00045 +/- 0.000135
+Arima: 0.000402 +/- 0.000134
 
@@
 
-lmD: 0.011422 +/- 0.003629
+lmD: 0.009848 +/- 0.003421
 
-lmY: 0.011422 +/- 0.003629
+lmY: 0.009848 +/- 0.003422
 
-Arima: 0.011422 +/- 0.004188
+Arima: 0.009849 +/- 0.003932
 
@@
 
-lmD: -1.014557 +/- 0.247144
+lmD: -1.014326 +/- 0.242383
 
-lmY: -1.014539 +/- 0.247148
+lmY: -1.01431 +/- 0.242387
 
-Arima: -1.025903 +/- 0.356761
+Arima: -1.024849 +/- 0.345654
 
@@
 
-lmD: -1.13974 +/- 0.188386
+lmD: -1.139227 +/- 0.182911
 
-lmY: -1.139735 +/- 0.188389
+lmY: -1.139223 +/- 0.182914
 
-Arima: -1.172188 +/- 0.333189
+Arima: -1.17037 +/- 0.320655
 
@@
 
-lmD: -1.100642 +/- 0.18719
+lmD: -1.099532 +/- 0.181744
 
-lmY: -1.100638 +/- 0.187194
+lmY: -1.09953 +/- 0.181747
 
-Arima: -1.133859 +/- 0.321558
+Arima: -1.131269 +/- 0.309288
 
@@
 
-lmD: -1.242646 +/- 0.174098
+lmD: -1.242636 +/- 0.168369
 
-lmY: -1.242654 +/- 0.174101
+lmY: -1.242644 +/- 0.168371
 
-Arima: -1.284884 +/- 0.324863
+Arima: -1.283474 +/- 0.312719
 
@@
 
-lmD: -1.259775 +/- 0.173629
+lmD: -1.259539 +/- 0.167895
 
-lmY: -1.259783 +/- 0.173632
+lmY: -1.259548 +/- 0.167897
 
-Arima: -1.301601 +/- 0.323343
+Arima: -1.300028 +/- 0.311399
 
@@
 
-lmD: -1.034796 +/- 0.226955
+lmD: -1.033796 +/- 0.221995
 
-lmY: -1.034779 +/- 0.226959
+lmY: -1.03378 +/- 0.221999
 
-Arima: -1.050406 +/- 0.344658
+Arima: -1.048334 +/- 0.332949
 
@@
 
-lmD: -1.02486 +/- 0.235592
+lmD: -1.02427 +/- 0.230733
 
-lmY: -1.024843 +/- 0.235596
+lmY: -1.024254 +/- 0.230737
 
-Arima: -1.038346 +/- 0.349707
+Arima: -1.036798 +/- 0.338243
 
@@
 
-lmD: 0.138738 +/- 0.251457
+lmD: 0.128338 +/- 0.244436
 
-lmY: 0.138759 +/- 0.251461
+lmY: 0.128359 +/- 0.24444
 
-Arima: 0.138867 +/- 0.256234
+Arima: 0.128462 +/- 0.249026
 
@@
 
-lmD: -0.001372 +/- 0.000292
+lmD: -0.001358 +/- 0.00029
 
-lmY: -0.001372 +/- 0.000292
+lmY: -0.001358 +/- 0.00029
 
-Arima: -0.001372 +/- 0.000322
+Arima: -0.001358 +/- 0.00032
 
@@
 
-lmD: -0.001515 +/- 0.000226
+lmD: -0.0015 +/- 0.000225
 
-lmY: -0.001515 +/- 0.000226
+lmY: -0.0015 +/- 0.000225
 
-Arima: -0.001519 +/- 0.000269
+Arima: -0.001504 +/- 0.000267
 
@@
 
-lmD: -0.001494 +/- 0.000234
+lmD: -0.001479 +/- 0.000233
 
-lmY: -0.001494 +/- 0.000234
+lmY: -0.001479 +/- 0.000233
 
-Arima: -0.001498 +/- 0.000275
+Arima: -0.001483 +/- 0.000273
 
@@
 
-lmD: -0.001682 +/- 0.000209
+lmD: -0.001666 +/- 0.000208
 
-lmY: -0.001683 +/- 0.000209
+lmY: -0.001666 +/- 0.000208
 
-Arima: -0.00169 +/- 0.000262
+Arima: -0.001674 +/- 0.00026
 
@@
 
-lmD: -0.001696 +/- 0.000208
+lmD: -0.00168 +/- 0.000207
 
-lmY: -0.001696 +/- 0.000208
+lmY: -0.00168 +/- 0.000207
 
-Arima: -0.001704 +/- 0.000262
+Arima: -0.001688 +/- 0.00026
 
@@
 
-lmD: -0.001367 +/- 0.000272
+lmD: -0.001352 +/- 0.00027
 
-lmY: -0.001367 +/- 0.000272
+lmY: -0.001352 +/- 0.00027
 
-Arima: -0.001367 +/- 0.000304
+Arima: -0.001353 +/- 0.000302
 
@@
 
-lmD: -0.001364 +/- 0.000281
+lmD: -0.00135 +/- 0.000279
 
-lmY: -0.001364 +/- 0.000281
+lmY: -0.00135 +/- 0.000279
 
-Arima: -0.001365 +/- 0.000312
+Arima: -0.001351 +/- 0.00031
 
@@
 
-lmD: 0.002612 +/- 0.005505
+lmD: 0.002398 +/- 0.005327
 
-lmY: 0.002612 +/- 0.005505
+lmY: 0.002399 +/- 0.005328
 
-Arima: 0.002638 +/- 0.005739
+Arima: 0.002424 +/- 0.005555
 
@@
 
-Arima: 0.107023 +/- 0.040196
+Arima: 0.086761 +/- 0.03998
 
@@
 \begin{verbatim}
-Warning: Removed 19 rows containing non-finite outside the scale range
+Warning: Removed 16 rows containing non-finite outside the scale range
 (`stat_bin2d()`).
@@
 \begin{verbatim}
-Warning: Removed 2 rows containing missing values or values outside the scale
+Warning: Removed 1 row containing missing values or values outside the scale
 range (`geom_tile()`).
@@
 
-lmY: 129.677 +/- 37.08333
+lmY: 116.8672 +/- 33.89196
 
@@
 
-lmY: 48.08231 +/- 11.89152
+lmY: 45.58799 +/- 10.96835
 
@@
 
-lmY: 0.080779 +/- 0.053347
+lmY: 0.062157 +/- 0.054182
 
@@
 
-lmY: 0.065639 +/- 0.040043
+lmY: 0.053059 +/- 0.041079
 
@@
 \begin{verbatim}
-2024-05-14 07:45:19.2 athan@tyler GHI_enh_04_investigate.R 2.165741 mins
+2024-05-20 16:56:07.0 athan@tyler GHI_enh_04_investigate.R 1.334659 mins
 \end{verbatim}

### 2024-05-21 GHI_enh_07_Aerosols.tex
Commit 2024-05-21 10:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-05-17}
+\date{2024-05-20}
 
@@
 
-SZA 55 : 0.00137369825595582
+SZA 55 : 0.00139576531267693
 
@@
 -288.8 & 0.4157 & 6 & 536.3 & SZA 55 & 2015 & 0.000775 \\
--483.7 & 0.5087 & 7 & 531.2 & SZA 55 & 2015 & 0.0009577 \\
+-766.8 & 0.6494 & 7 & 531.2 & SZA 55 & 2015 & 0.001223 \\
 -140.4 & 0.3406 & 8 & 549.3 & SZA 55 & 2015 & 0.0006201 \\
@@
 2005 & SZA 55 & 576.4 \\
-2005 & BR SZA 55 & 588.6 \\
+2005 & BR SZA 55 & 588.4 \\
 2006 & SZA 55 & 574.9 \\
@@
 2021 & SZA 55 & 587.5 \\
-2022 & SZA 55 & 587.4 \\
+2022 & SZA 55 & 585.2 \\
 2023 & SZA 55 & 583 \\

### 2024-05-21 article/article.tex
Commit 2024-05-17 14:14
Commit 2024-05-21 10:14

@@
 was inferred by the available Ångström coefficients, and we choose the
-SZA of \(55^\circ\) as a representative value for all runs. For the
-first period, the alpha Ångström coefficient is \(1.6\) and the beta
-coefficient \(0.086\) and \(0.059\), for 1997 and 2005 respectively. By
-interpolating the resulting clear sky irradiance, we have a trend of
-\(+0.21\,\%\) per year. For the period 2005 -- 2005 we used the mean
-monthly values from AERONET, with a similar simulation scheme. We
-computed the trend of clear sky radiation for each month of the year,
-which gave us a mean clear sky radiation trend of \(+0.14\,\%\) per
-year.
+SZA of \(55^\circ\) as a representative value for all runs.
+
+For the first period, the alpha Ångström coefficient is \(1.6\) and the
+beta coefficient \(0.086\) and \(0.059\), for 1997 and 2005
+respectively. By interpolating the resulting clear sky irradiance, we
+have a trend of \(+0.21\,\%\) per year. For the period 2005 -- 2005 we
+used the mean monthly values from AERONET, with a similar simulation
+scheme. We computed the trend of clear sky radiation for each month of
+the year, which gave us a mean clear sky radiation trend of
+\(+0.14\,\%\) per year.
+
+According to \citet{Kazadzis2007}, in the period 1997 -- 2005, the mean
+AOD of \(340\,\text{nm}\) was calculated to 0.403 by the Brewer
+spectrophotometer, with a linear trend of \(-3.8±0.93\,\%\) per year.
+This corresponds to a AOD \(340\,\text{nm}\) change of \(0.0153\) per
+year. Using the alpha Ångström coefficient of \(\alpha = 1.6\) this
+translates to a change in Ångström beta coefficient of \(\beta=0.00272\)
+per year (or \(\beta=0.084\) in 1997 and \(\beta=0.059\) in 2005).
 
@@
 Our dataset, after the data selection processing, consists of 6144534
-records of GHI, of which \(1.95\,\%\) are CE and \(0.036\,\%\) are ECE
+records of GHI, of which \(1.764\,\%\) are CE and \(0.036\,\%\) are ECE
 events. The highest GHI recorder was \(1416.6\,W/m^2\) on 24~May 2007.
-The absolute stronger CE event had an OIR of \(353.05\,W/m^2\) on 24~May
-2007. The relative stronger CE event was \(50.7\,\%\) above the clear
+The absolute stronger CE event had an OIR of \(345.86\,W/m^2\) on 24~May
+2007. The relative stronger CE event was \(49.7\,\%\) above the clear
 sky threshold, on 28~October 2016.
@@
 \citep{RCT2023}. The trends are reported together with the \(2\sigma\)
-error. We observe an increase of \(0.107\pm 0.08\,W/m^2/y\) on the mean
+error. We observe an increase of \(0.087\pm 0.08\,W/m^2/y\) on the mean
 OIR.
@@
 long term CE trends. Hence, we calculated the annual values from the
-one-minute measurements. The trend of OIR is \(0.08\pm 0.11\,W/m^2/y\)
+one-minute measurements. The trend of OIR is \(0.06\pm 0.11\,W/m^2/y\)
 (Figure\nobreakspace{}\ref{fig:P-energy-mean}), but this value alone is
@@
 The annual number of CE occurrences, shows a steady increase of
-\(48.1\pm 23.8\,\text{cases}/y\)
+\(45.6\pm 21.9\,\text{cases}/y\)
 (Figure\nobreakspace{}\ref{fig:P-energy-N}). We have to note that the
@@
 Subsequently, the mean annual increase of energy due to CE events is
-\(129.7\pm 74.2\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
+\(116.9\pm 67.8\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
 the trend of the number of occurrences.
@@
 Thus, a CEG consists of one or more successive CE cases, and can have a
-duration of multiple of minutes. We have identified 30749 groups, where
+duration of multiple of minutes. We have identified 28468 groups, where
 the group with the longest duration lasted 140 minutes on 07~July 2013.

### 2024-05-21 article/article.Rmd
Commit 2024-05-21 10:14

--- 2024-05-17 article/article.Rmd
@@
 used the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
-coefficients, and we choose the SZA of $55^\circ$ as a representative value for all runs.
+coefficients, and we choose the SZA of $55^\circ$ as a representative value for all
+runs.
+
 For the first period, the alpha Ångström coefficient is $1.6$ and the beta
 coefficient $0.086$ and $0.059$, for 1997 and 2005 respectively. By interpolating the
-resulting clear sky irradiance, we have a trend of $+0.21\,\%$ per year.
-For the period 2005 -- 2005 we used the mean monthly values from AERONET, with a
-similar simulation scheme. We computed the trend of clear sky radiation for each
-month of the year, which gave us a mean clear sky radiation trend of $+0.14\,\%$ per year.
+resulting clear sky irradiance, we have a trend of $+0.21\,\%$ per year.  For the
+period 2005 -- 2005 we used the mean monthly values from AERONET, with a similar
+simulation scheme. We computed the trend of clear sky radiation for each month of the
+year, which gave us a mean clear sky radiation trend of $+0.14\,\%$ per year.
+
+According to @Kazadzis2007, in the period 1997 -- 2005, the mean AOD of $340\,\text{nm}$ was calculated
+to 0.403 by the Brewer spectrophotometer, with a linear trend of $-3.8±0.93\,\%$ per year.
+This corresponds to a AOD $340\,\text{nm}$ change of $0.0153$ per year.
+Using the alpha Ångström coefficient of $\alpha = 1.6$ this translates to a change in Ångström beta coefficient of $\beta=0.00272$ per year (or $\beta=0.084$ in 1997 and $\beta=0.059$ in 2005).
+
+<!--
+1997 0.0839901
+2005 0.05496013
+# Kazadzis2007 - Nine years of UV aerosol optical depth measurements at Thessaloniki, Greece
+# From Stelios' paper 2007:
+# AOD @340 from Brewer 086
+# Period: 1997-2005
+# The mean AOD for this period was calculated to 0.403 for the Brewer and 0.422 for the CIMEL.
+# A linear regression on the Brewer deseasonalized data reveals a change of -3.8±0.93% per year.
+# From the above data AOD @340 changes by 0.0153 per year (or 0.138 for the 9 years).
+# Using Angstrom a= 1.6  this translates to a change in Angstrom β=0.00272 per year (or β=0.084 in 1997 and β=0.059 in 2005).
+-->
 

### 2024-05-21 GHI_enh_CSid.R

@@ -114,7 +114,7 @@ hist(DATA$ClearnessIndex_C_4)
 DATA <- DATA[ClearnessIndex_C_4 > 0.8 ]
 DATA <- DATA[ClearnessIndex_C_4 < 1.3 ]
 
-source("./GHI_enh_Aeronet.R")
+source("./GHI_enh_07_Aerosols.R")
 
 
 DATA[, tsy := year(Date) + (month(Date) - 1)/12 ]
@@ -130,7 +130,7 @@ trendsf <- c(trend_median, trend_mean, trend_min)
 # trend_apply  <- trend_mean
 # trend_factor <- -0.01995656
 ## for trend median
-trend_apply  <- trend_median
+# trend_apply  <- trend_median
 trend_apply  <- trend_55
 trend_factor <- -0.01995656  # the same
 trend_apply_adj <- function(tsy) {
@@ -156,7 +156,7 @@ f <- function(x) {
   # test[, sum(V1 - V2)]
 }
 
-optimise(f, interval = c(-0.02, 0.02), maximum = F, tol = 0.0001)
+optimise(f, interval = c(-0.03, 0.03), maximum = F, tol = 0.0001)
 
 
 # optim(0.8, f, method = "Brent", lower = 0.2, upper = 1.5)

### 2024-05-21 GHI_enh_02_ID_CE.R
Commit 2024-05-21 12:14

@@ -348,12 +348,11 @@ abline(v = C4_cs_ref_ratio, col = "red" )
 
 ## for most of the data
 DATA[SZA < C4_lowcut_sza,
-     Enhanc_C_4_ref := (1 + trans_trend(decimal_date(Date))) * (get(paste0(csmodel,".glo")) * C4_cs_ref_ratio) + C4_GLB_diff_THRES ]
+     Enhanc_C_4_ref :=
+       (1 + trans_trend(decimal_date(Date))) * (get(paste0(csmodel,".glo")) * C4_cs_ref_ratio) + C4_GLB_diff_THRES ]
 
-DATA[SZA < C4_lowcut_sza,
-     (1 + trans_trend(decimal_date(Date))) * (get(paste0(csmodel,".glo")) * C4_cs_ref_ratio) + C4_GLB_diff_THRES ]
-
-
+# DATA[SZA < C4_lowcut_sza,
+#       (1 + trans_trend(decimal_date(Date))) * (get(paste0(csmodel,".glo")) * C4_cs_ref_ratio) + C4_GLB_diff_THRES ]
 
 DATA[SZA < C4_lowcut_sza,
      Enhanc_C_4_ref_test :=                                    (get(paste0(csmodel,".glo")) * C4_test_cs_ref_ratio) ]
@@ -377,10 +376,9 @@ if (SelEnhanc == "Enhanc_C_4") {
   DATA[ , GLB_rati :=   wattGLB / Enhanc_C_4_ref                    ]
 }
 
-
-
-
-
+cat("C4_lowcut_sza",      C4_lowcut_sza    , "\n")
+cat("C4_cs_ref_ratio",    C4_cs_ref_ratio  , "\n")
+cat("C4_GLB_diff_THRES",  C4_GLB_diff_THRES, "\n")
 
 
 #+ echo=F, include=T
@@ -757,8 +755,11 @@ for (pyear in yearstodo) {
                               high     = "red",
                               na.value = NA) +
         labs(title = pyear) +
-        xlab(paste0(SelEnhanc, "_ref")) +
-        labs(color = "Over\nreference") +
+        ylab(bquote("SDR" ~ group("[", W/m^2,"]"))) +
+        xlab(bquote("Clear sky reference" ~ group("[", W/m^2,"]"))) +
+        # xlab(paste0(SelEnhanc, "_ref")) +
+        # labs(color = "Over\nIrradiance W/m^2") +
[…]

### 2024-05-21 GHI_enh_07_Aerosols.tex
Commit 2024-05-21 12:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-05-20}
+\date{2024-05-21}
 
@@
 }
+\begin{verbatim}
+Registered S3 methods overwritten by 'ggpp':
+  method                  from   
+  heightDetails.titleGrob ggplot2
+  widthDetails.titleGrob  ggplot2
+\end{verbatim}
+
+\begin{verbatim}
+Attaching package: 'ggpp'
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:ggplot2':
+
+    annotate
+\end{verbatim}
+
+\begin{verbatim}
+Registered S3 method overwritten by 'ggpmisc':
+  method                  from   
+  as.character.polynomial polynom
+\end{verbatim}
+
+\begin{verbatim}
+Attaching package: 'zoo'
+\end{verbatim}
+
+\begin{verbatim}
+The following objects are masked from 'package:data.table':
+
+    yearmon, yearqtr
+\end{verbatim}
+
+\begin{verbatim}
+The following objects are masked from 'package:base':
+
+    as.Date, as.Date.numeric
+\end{verbatim}
+
 \begin{verbatim}
@@
 
+\begin{verbatim}
+Warning: The S3 guide system was deprecated in ggplot2 3.5.0.
+i It has been replaced by a ggproto system that can be extended.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/P_CS_change-1} \end{center}

### 2024-05-21 article/article.Rmd
Commit 2024-05-21 15:10

--- 2024-05-17 article/article.Rmd
@@
 The above clear sky reference values are not enough to describe the long term
-variation due to the changes of the atmospheric constituents. As observed
-by @Natsis2023, there is long term brightening effect, over Thessaloniki for the
-studied period. In order to better describe this change, we used, estimations of AOD
-change derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change
-of $-3.8\,\%$ per year at AOD on $340\,\text{nm}$, using a Brewer spectrophotometer. For 2005
-to 2023, we derived the trend from the available AERONET data.
+variation, due to the changes of the atmospheric constituents. As observed by
+@Natsis2023, there is a long term brightening effect, over Thessaloniki for the studied
+period. In order to better describe this change, we used, estimations of AOD change
+derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change of
+$-3.8\,\%$ per year at AOD on $340\,\text{nm}$, using a Brewer spectrophotometer. For
+2005 to 2023, we derived the trend from the available AERONET data.
 
@@
 simulated the values of AOD derived from those sources with Libradtran. For both, we
-used the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
-coefficients, and we choose the SZA of $55^\circ$ as a representative value for all runs.
-For the first period, the alpha Ångström coefficient is $1.6$ and the beta
-coefficient $0.086$ and $0.059$, for 1997 and 2005 respectively. By interpolating the
-resulting clear sky irradiance, we have a trend of $+0.21\,\%$ per year.
-For the period 2005 -- 2005 we used the mean monthly values from AERONET, with a
-similar simulation scheme. We computed the trend of clear sky radiation for each
-month of the year, which gave us a mean clear sky radiation trend of $+0.14\,\%$ per year.
+have used the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
+coefficients, and we choose the SZA of $55^\circ$ as a representative value for all
+runs.
+
+According to @Kazadzis2007, in the period 1997 -- 2005, the mean AOD of
+$340\,\text{nm}$ was calculated to $0.403$ with the use of a Brewer
+spectrophotometer, with a linear trend of $-3.8±0.93\,\%$ per year.  This corresponds
+to a AOD $340\,\text{nm}$ change of $0.0153$ per year.  Using the alpha Ångström
+coefficient of $\alpha = 1.6$, this translates to a change in Ångström beta
+coefficient of $\beta=0.00272$ per year (or $\beta=0.084$ in 1997 and $\beta=0.059$
+in 2005).  By interpolating the resulting clear sky irradiance, we have a trend of
+$+0.21\,\%$ per year for the clear sky irradiance.  For the period 2005 -- 2005 we
+used the mean monthly values from AERONET, with a similar simulation scheme. We
+computed the trend of clear sky radiation for each month of the year, which gave us a
+mean clear sky radiation trend of $+0.14\,\%$ per year. We applied this long term
+change to the clear sky irradiance, in order to create a more realistic
+representation of the irradiance for the whole study period
+(Figure\nobreakspace{}\ref{fig:CS-change}).
+
+```{r CS-change, echo=FALSE, fig.cap="Simulated long term change of clear sky irradiance relevant to its climatological values."}
+knitr::include_graphics("../images/P_CS_change-1.png")
+```
+
+<!-- 1997 0.0839901
+<!-- 2005 0.05496013
+<!-- # Kazadzis2007 - Nine years of UV aerosol optical depth measurements at Thessaloniki, Greece
+<!-- # From Stelios' paper 2007:
+<!-- # AOD @340 from Brewer 086
+<!-- # Period: 1997-2005
+<!-- # The mean AOD for this period was calculated to 0.403 for the Brewer and 0.422 for the CIMEL.
+<!-- # A linear regression on the Brewer deseasonalized data reveals a change of -3.8±0.93% per year.
+<!-- # From the above data AOD @340 changes by 0.0153 per year (or 0.138 for the 9 years).
+<!-- # Using Angstrom a= 1.6  this translates to a change in Angstrom β=0.00272 per year (or β=0.084 in 1997 and β=0.059 in 2005).
+-->
 
@@
 
-The use of the actual modeled values of clear sky GHI alone, can not provide us with
+The use of the actual modeled values of clear sky GHI, described above , can not provide us with
 a robust method to distinguish the CE cases, due to the limited accuracy of the input
-data. Our main focus was to positively identify over irradiance events from CEs, thus
-we used a relative factor, to create an upper envelope of the clear sky irradiance,
+data. Our main focus was to positively identify over irradiance events from CEs, 
+so we created an upper envelope of the clear sky irradiance,
+
+.............................
+
 above which, any GHI value can safely attributed to CE.  We evaluated the performance
@@
 where: $\theta$ is the solar zenith angle, $\text{GHI}_\text{i}$ the measured
-irradiance, and $\text{GHI}_\text{mCSi}$ the selected modeled clear sky irradiance.
+irradiance, and $\text{GHI}_\text{mCSi}$ the selected modelled clear sky irradiance.
 -->
+<!-- \begin{equation} -->
+<!-- \text{CE} : \text{E}_\text{i} > \text{E}_\text{CSlim,i}, \text{where} \begin{cases} -->
+<!--  \text{E}_\text{CSlim,i} = `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\ -->
+<!-- \text{E}_\text{CSlim,i} = \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\ -->
+<!-- \text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ -->
+<!-- \end{cases}\label{eq:CE4} -->
+<!-- \end{equation} -->
+<!-- where: $\theta$ is the solar zenith angle, $\text{E}$ the measured -->
+<!-- irradiance, $\text{E}_\text{CSm}$ the selected modelled clear sky irradiance, and $i$ each of the one-minute observation. -->
+
 \begin{equation}
-\text{CE} : \text{E}_\text{i} > \text{E}_\text{CSlim,i}, \text{where} \begin{cases}
- \text{E}_\text{CSlim,i} = `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
-\text{E}_\text{CSlim,i} = \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
-\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
-\end{cases}\label{eq:CE4}
+\text{CE} : \text{E}_\text{i} > `r C4_GLB_diff_THRES` + `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i} \,\,[W/m^2] \label{eq:CE4}
 \end{equation}
 where: $\theta$ is the solar zenith angle, $\text{E}$ the measured
-irradiance, $\text{E}_\text{CSm}$ the selected modeled clear sky irradiance, and $i$ each of the one-minute observation.
+irradiance, $\text{E}_\text{CSm}$ the selected modelled clear sky irradiance, and $i$ each of the one-minute observation.
 

### 2024-05-21 article/article.tex
Commit 2024-05-21 15:10

@@
 The above clear sky reference values are not enough to describe the long
-term variation due to the changes of the atmospheric constituents. As
-observed by \citet{Natsis2023}, there is long term brightening effect,
+term variation, due to the changes of the atmospheric constituents. As
+observed by \citet{Natsis2023}, there is a long term brightening effect,
 over Thessaloniki for the studied period. In order to better describe
@@
 irradiance, we simulated the values of AOD derived from those sources
-with Libradtran. For both, we used the AOD at \(500\,\text{nm}\), which
-was inferred by the available Ångström coefficients, and we choose the
-SZA of \(55^\circ\) as a representative value for all runs.
-
-For the first period, the alpha Ångström coefficient is \(1.6\) and the
-beta coefficient \(0.086\) and \(0.059\), for 1997 and 2005
-respectively. By interpolating the resulting clear sky irradiance, we
-have a trend of \(+0.21\,\%\) per year. For the period 2005 -- 2005 we
-used the mean monthly values from AERONET, with a similar simulation
-scheme. We computed the trend of clear sky radiation for each month of
-the year, which gave us a mean clear sky radiation trend of
-\(+0.14\,\%\) per year.
+with Libradtran. For both, we have used the AOD at \(500\,\text{nm}\),
+which was inferred by the available Ångström coefficients, and we choose
+the SZA of \(55^\circ\) as a representative value for all runs.
 
 According to \citet{Kazadzis2007}, in the period 1997 -- 2005, the mean
-AOD of \(340\,\text{nm}\) was calculated to 0.403 by the Brewer
-spectrophotometer, with a linear trend of \(-3.8±0.93\,\%\) per year.
-This corresponds to a AOD \(340\,\text{nm}\) change of \(0.0153\) per
-year. Using the alpha Ångström coefficient of \(\alpha = 1.6\) this
+AOD of \(340\,\text{nm}\) was calculated to \(0.403\) with the use of a
+Brewer spectrophotometer, with a linear trend of \(-3.8±0.93\,\%\) per
+year. This corresponds to a AOD \(340\,\text{nm}\) change of \(0.0153\)
+per year. Using the alpha Ångström coefficient of \(\alpha = 1.6\), this
 translates to a change in Ångström beta coefficient of \(\beta=0.00272\)
-per year (or \(\beta=0.084\) in 1997 and \(\beta=0.059\) in 2005).
+per year (or \(\beta=0.084\) in 1997 and \(\beta=0.059\) in 2005). By
+interpolating the resulting clear sky irradiance, we have a trend of
+\(+0.21\,\%\) per year for the clear sky irradiance. For the period 2005
+-- 2005 we used the mean monthly values from AERONET, with a similar
+simulation scheme. We computed the trend of clear sky radiation for each
+month of the year, which gave us a mean clear sky radiation trend of
+\(+0.14\,\%\) per year. We applied this long term change to the clear
+sky irradiance, in order to create a more realistic representation of
+the irradiance for the whole study period
+(Figure\nobreakspace{}\ref{fig:CS-change}).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{../images/P_CS_change-1}
+
+}
+
+\caption{Simulated long term change of clear sky irradiance relevant to its climatological values.}\label{fig:CS-change}
+\end{figure}
 
@@
 
-The use of the actual modeled values of clear sky GHI alone, can not
-provide us with a robust method to distinguish the CE cases, due to the
-limited accuracy of the input data. Our main focus was to positively
-identify over irradiance events from CEs, thus we used a relative
-factor, to create an upper envelope of the clear sky irradiance, above
-which, any GHI value can safely attributed to CE. We evaluated the
+The use of the actual modeled values of clear sky GHI, described above ,
+can not provide us with a robust method to distinguish the CE cases, due
+to the limited accuracy of the input data. Our main focus was to
+positively identify over irradiance events from CEs, so we created an
+upper envelope of the clear sky irradiance,
+
+\ldots\ldots\ldots\ldots\ldots\ldots\ldots\ldots\ldots..
+
+above which, any GHI value can safely attributed to CE. We evaluated the
 performance of the modeled clear radiation for each of atmospheric level
@@
 (Equation\nobreakspace\ref{eq:CE4}). This is the criterion of our CE
-identification. \begin{equation}
-\text{CE} : \text{E}_\text{i} > \text{E}_\text{CSlim,i}, \text{where} \begin{cases}
- \text{E}_\text{CSlim,i} = 1.04 \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq 90^\circ$}\\
-\text{E}_\text{CSlim,i} = \left ({ 1.04 + \frac{1.04 - 1.04}{90 - 78} \cdot (\theta- 78) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ 78^\circ > \theta > 90^\circ$}\\
-\text{Excluded measurements}, & \theta > 78^\circ
-\end{cases}\label{eq:CE4}
+identification.
+
+\begin{equation}
+\text{CE} : \text{E}_\text{i} > 15 + 1.04 \cdot \text{E}_\text{CSm,i} \,\,[W/m^2] \label{eq:CE4}
 \end{equation} where: \(\theta\) is the solar zenith angle, \(\text{E}\)
-the measured irradiance, \(\text{E}_\text{CSm}\) the selected modeled
+the measured irradiance, \(\text{E}_\text{CSm}\) the selected modelled
 clear sky irradiance, and \(i\) each of the one-minute observation.

### 2024-05-21 article/article.Rmd
Commit 2024-05-21 18:10

@@
 
-The use of the actual modeled values of clear sky GHI, described above , can not provide us with
-a robust method to distinguish the CE cases, due to the limited accuracy of the input
-data. Our main focus was to positively identify over irradiance events from CEs, 
-so we created an upper envelope of the clear sky irradiance,
+The use of the actual modelled values of clear sky GHI, described above, can not
+provide us with a robust method to distinguish the CE cases, due to the limited
+accuracy of the input data, and the natural variability of the atmosphere. Our main
+focus was to positively identify over irradiance events related to CEs.  For this
+reason, we created an upper envelope of the clear sky irradiance, above which, any
+GHI value can safely be attributed to CE a event.
 
-.............................
-
-above which, any GHI value can safely attributed to CE.  We evaluated the performance
-of the modeled clear radiation for each of atmospheric level of clearness, as
-reference, in order to conclude which is the most appropriate.
+We had to select both, an appropriate set of atmospheric parameterization, in
+Libradtran, and the thresholds of CE identification.
+First we evaluated the performance of the modelled clear radiation, for each of
+atmospheric level of clearness we have created as reference, in order to conclude
+which is the most appropriate.
 

### 2024-05-21 article/article.tex
Commit 2024-05-21 18:10

@@
 
-The use of the actual modeled values of clear sky GHI, described above ,
+The use of the actual modelled values of clear sky GHI, described above,
 can not provide us with a robust method to distinguish the CE cases, due
-to the limited accuracy of the input data. Our main focus was to
-positively identify over irradiance events from CEs, so we created an
-upper envelope of the clear sky irradiance,
+to the limited accuracy of the input data, and the natural variability
+of the atmosphere. Our main focus was to positively identify over
+irradiance events related to CEs. For this reason, we created an upper
+envelope of the clear sky irradiance, above which, any GHI value can
+safely be attributed to CE a event.
 
-\ldots\ldots\ldots\ldots\ldots\ldots\ldots\ldots\ldots..
-
-above which, any GHI value can safely attributed to CE. We evaluated the
-performance of the modeled clear radiation for each of atmospheric level
-of clearness, as reference, in order to conclude which is the most
-appropriate.
+We had to select both, an appropriate set of atmospheric
+parameterization, in Libradtran, and the thresholds of CE
+identification. First we evaluated the performance of the modelled clear
+radiation, for each of atmospheric level of clearness we have created as
+reference, in order to conclude which is the most appropriate.
 

### 2024-05-21 article/article.Rmd
Commit 2024-05-21 19:13

--- 2024-05-21 article/article.Rmd
@@
 
-The use of the actual modeled values of clear sky GHI, described above , can not provide us with
-a robust method to distinguish the CE cases, due to the limited accuracy of the input
-data. Our main focus was to positively identify over irradiance events from CEs, 
-so we created an upper envelope of the clear sky irradiance,
+Our main focus was to positively identify over irradiance events related to CEs.  For
+this reason we had to select an appropriate set of atmospheric parameterization, in
+Libradtran, and define an relevant threshold for the CE identification.  The
+selection of the atmospheric parameterization will provide us with a reference, that
+has a good agreement with the clear sky conditions. Additional, with the
+implementation of the long term change, as described above, it will be able to align
+well with most of the natural variation of the physical quantity.  The selection of
+adequate threshold, will also allow us to have a robust method to distinguish the CE
+cases, which will compensate for the limited accuracy of the input data, and the
+natural variability of the atmosphere.
 
-.............................
+First, we evaluated the performance of the modelled clear radiation, for each of
+the atmospheric level of clearness we have created as reference, in relation to the
+measured GHI data, and choose as a representative of the clear sky radiation, the
+case where
+$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
+($\text{GHI}_\text{CSm}$).
+These values represent a typical atmosphere in Thessaloniki, with low load of
+aerosols and humidity, which are the main factor that attenuate the GHI, excluding
+clouds.  To create the upper limit of CE identification, we used a value relative to
+clear sky irradiance
+($`r 100*(C4_cs_ref_ratio-1)`\,\%$)
+with an additional constant offset of
+$`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$,
+as described in Equation\nobreakspace\ref{eq:CE4}).
+\begin{equation}
+\text{CE} : \text{E}_\text{i} > `r C4_GLB_diff_THRES` + `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
+\end{equation}
+where: $\text{E}$ the measured irradiance, $\text{E}_\text{CSm}$ the selected
+modelled clear sky irradiance, and $i$ each of the one-minute observation.  This is
+the criterion of our CE identification.
 
-above which, any GHI value can safely attributed to CE.  We evaluated the performance
-of the modeled clear radiation for each of atmospheric level of clearness, as
-reference, in order to conclude which is the most appropriate.
-
-To select the exact values of these thresholds factors (Equation \ref{eq:CE4}), we
-implemented an empirical method, by manual inspection of the CE identification, on
-specially selected days from the whole dataset.  We used seven sets of selected days,
-with characteristics relevant to the efficiency of the identification threshold.
-These sets were random groups of about 20 to 30 days with the following
+In the process of defining the above details, we implemented an empirical method, by
+manual inspection of the CE identification, on specially selected days from the whole
+dataset.  We used seven sets of selected days, with characteristics relevant to the
+efficiency of the identification threshold.  These sets were random groups of about
+20 to 30 days with the following
 characteristics:
@@
 
-After evaluating the modeled clear radiation for the different atmospheric
-conditions, in relation to the measured GHI data, we choose as a representative of
-the clear sky radiation, the case where
-$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
-($\text{GHI}_\text{CSm}$).
-These values represent a typical atmosphere in Thessaloniki with low load of aerosols
-and humidity, which are the main factor that attenuate the GHI, excluding clouds.  To
-create the limit of CE identification, we created a two branched threshold, as a
-function of SZA. A constant factor for low SZAs, and a higher ramped factor for
-higher SZAs (Equation\nobreakspace\ref{eq:CE4}).
-This is the criterion of our CE identification.
 <!--
@@
 
-\begin{equation}
-\text{CE} : \text{E}_\text{i} > `r C4_GLB_diff_THRES` + `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i} \,\,[W/m^2] \label{eq:CE4}
-\end{equation}
-where: $\theta$ is the solar zenith angle, $\text{E}$ the measured
-irradiance, $\text{E}_\text{CSm}$ the selected modelled clear sky irradiance, and $i$ each of the one-minute observation.
-
 <!-- reasoning for cretria -->
-We have to note, that the differentiation of the threshold factor was needed, because
-of the high irradiance values we observed, early in the morning and late in the
-afternoon. We have confirmed, by inspecting images from the sky cam, that we have
-duration of elevated irradiance, either due to the clearness of the atmosphere, or some
-interferences by reflections on nearby bright surfaces. Although, these cases may
-mask some of the CE events. The actual CE events, produce higher irradiance and thus
-are identified as such. As a side effect, the reported OIR will be slight
-underestimated for those SZAs, but the overall contribution of those cases to the
-total daily energy, is minimal due the low occurrences and the lower irradiances.
+<!-- We have to note, that the differentiation of the threshold factor was needed, because
+<!-- of the high irradiance values we observed, early in the morning and late in the
+<!-- afternoon. 
+<!-- We have confirmed, by inspecting images from the sky cam, that we have
+<!-- duration of elevated irradiance, either due to the clearness of the atmosphere, or some
+<!-- interferences by reflections on nearby bright surfaces. Although, these cases may
+<!-- mask some of the CE events. The actual CE events, produce higher irradiance and thus
+<!-- are identified as such. As a side effect, the reported OIR will be slight
+<!-- underestimated for those SZAs, but the overall contribution of those cases to the
+<!-- total daily energy, is minimal due the low occurrences and the lower irradiances.
+-->
 

### 2024-05-21 article/article.tex
Commit 2024-05-21 19:13

--- 2024-05-21 article/article.tex
@@
 
-The use of the actual modeled values of clear sky GHI, described above ,
-can not provide us with a robust method to distinguish the CE cases, due
-to the limited accuracy of the input data. Our main focus was to
-positively identify over irradiance events from CEs, so we created an
-upper envelope of the clear sky irradiance,
+Our main focus was to positively identify over irradiance events related
+to CEs. For this reason we had to select an appropriate set of
+atmospheric parameterization, in Libradtran, and define an relevant
+threshold for the CE identification. The selection of the atmospheric
+parameterization will provide us with a reference, that has a good
+agreement with the clear sky conditions. Additional, with the
+implementation of the long term change, as described above, it will be
+able to align well with most of the natural variation of the physical
+quantity. The selection of adequate threshold, will also allow us to
+have a robust method to distinguish the CE cases, which will compensate
+for the limited accuracy of the input data, and the natural variability
+of the atmosphere.
 
-\ldots\ldots\ldots\ldots\ldots\ldots\ldots\ldots\ldots..
-
-above which, any GHI value can safely attributed to CE. We evaluated the
-performance of the modeled clear radiation for each of atmospheric level
-of clearness, as reference, in order to conclude which is the most
-appropriate.
-
-To select the exact values of these thresholds factors (Equation
-\ref{eq:CE4}), we implemented an empirical method, by manual inspection
-of the CE identification, on specially selected days from the whole
-dataset. We used seven sets of selected days, with characteristics
-relevant to the efficiency of the identification threshold. These sets
-were random groups of about 20 to 30 days with the following
-characteristics: (a) the largest over irradiance CE events, (b) the
-largest daily total over irradiance, (c) without clouds (by implementing
-a clear sky identification algorithm as discussed in
-\citet{Natsis2023}), (d) without clouds and without EC events, (e) with
-at least \(60\,\%\) of the day length without clouds and some EC events,
-(h) random days and (i) some manual selected days that were included
-during the manual inspection. Where it was needed, for some of the edge
-cases, we also used images from a sky-cam, to further aid the decisions
-of the manual inspection.
-
-After evaluating the modeled clear radiation for the different
-atmospheric conditions, in relation to the measured GHI data, we choose
-as a representative of the clear sky radiation, the case where
+First, we evaluated the performance of the modelled clear radiation, for
+each of the atmospheric level of clearness we have created as reference,
+in relation to the measured GHI data, and choose as a representative of
+the clear sky radiation, the case where
 \(\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma\) and
 \(w_{h\text{cs}} = w_h - 1\sigma\) (\(\text{GHI}_\text{CSm}\)). These
-values represent a typical atmosphere in Thessaloniki with low load of
+values represent a typical atmosphere in Thessaloniki, with low load of
 aerosols and humidity, which are the main factor that attenuate the GHI,
-excluding clouds. To create the limit of CE identification, we created a
-two branched threshold, as a function of SZA. A constant factor for low
-SZAs, and a higher ramped factor for higher SZAs
-(Equation\nobreakspace\ref{eq:CE4}). This is the criterion of our CE
-identification.
+excluding clouds. To create the upper limit of CE identification, we
+used a value relative to clear sky irradiance (\(4\,\%\)) with an
+additional constant offset of \(15\,\text{W}/\text{m}^2\), as described
+in Equation\nobreakspace\ref{eq:CE4}). \begin{equation}
+\text{CE} : \text{E}_\text{i} > 15 + 1.04 \cdot \text{E}_\text{CSm,i} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
+\end{equation} where: \(\text{E}\) the measured irradiance,
+\(\text{E}_\text{CSm}\) the selected modelled clear sky irradiance, and
+\(i\) each of the one-minute observation. This is the criterion of our
+CE identification.
 
-\begin{equation}
-\text{CE} : \text{E}_\text{i} > 15 + 1.04 \cdot \text{E}_\text{CSm,i} \,\,[W/m^2] \label{eq:CE4}
-\end{equation} where: \(\theta\) is the solar zenith angle, \(\text{E}\)
-the measured irradiance, \(\text{E}_\text{CSm}\) the selected modelled
-clear sky irradiance, and \(i\) each of the one-minute observation.
-
-We have to note, that the differentiation of the threshold factor was
-needed, because of the high irradiance values we observed, early in the
-morning and late in the afternoon. We have confirmed, by inspecting
-images from the sky cam, that we have duration of elevated irradiance,
-either due to the clearness of the atmosphere, or some interferences by
-reflections on nearby bright surfaces. Although, these cases may mask
-some of the CE events. The actual CE events, produce higher irradiance
-and thus are identified as such. As a side effect, the reported OIR will
-be slight underestimated for those SZAs, but the overall contribution of
-those cases to the total daily energy, is minimal due the low
-occurrences and the lower irradiances.
+In the process of defining the above details, we implemented an
+empirical method, by manual inspection of the CE identification, on
+specially selected days from the whole dataset. We used seven sets of
+selected days, with characteristics relevant to the efficiency of the
+identification threshold. These sets were random groups of about 20 to
+30 days with the following characteristics: (a) the largest over
+irradiance CE events, (b) the largest daily total over irradiance, (c)
+without clouds (by implementing a clear sky identification algorithm as
+discussed in \citet{Natsis2023}), (d) without clouds and without EC
+events, (e) with at least \(60\,\%\) of the day length without clouds
+and some EC events, (h) random days and (i) some manual selected days
+that were included during the manual inspection. Where it was needed,
+for some of the edge cases, we also used images from a sky-cam, to
+further aid the decisions of the manual inspection.
 

### 2024-05-21 high_aod/article/test/test.Rmd
Commit 2024-05-22 00:15

--- 2024-05-21 article/article.Rmd
@@
 ---
-title: Downward shortwave solar irradiance enhancement by clouds.
-
+title: Short Paper
 author:
-  - name:        Athanasios N. Natsis
-    email:       natsisphysicist@gmail.com
-    affiliation: LAP
+  - name: Alice Anonymous
+    email: alice@example.com
+    affiliation: Some Institute of Technology
     correspondingauthor: true
     footnote: 1
-  - name:        Alkiviadis Bais
-    email:       abais@auth.gr
-    affiliation: LAP
-  - name:        Charikleia Meleti
-    email:       meleti@auth.gr
-    affiliation: LAP
+  - name: Bob Security
+    email: bob@example.com
+    affiliation: Another University
+  - name: Cat Memes
+    email: cat@example.com
+    affiliation: Another University
+    footnote: 2
+  - name: Derek Zoolander
+    email: derek@example.com
+    affiliation: Some Institute of Technology
     footnote: 2
 address:
-  - code:         LAP
-    organization: Laboratory of Atmospheric Physics, A.U.Th.
+  - code: Some Institute of Technology
+    organization: Big Wig University
     addressline: 1 main street
-    city:         Thessaloniki
+    city: Gotham
+    state: State
     postcode: 123456
-    country:      Greece
+    country: United States
   - code: Another University
@@
     city: Manchester,
-    state:        State
     country: The Netherlands
@@
 abstract: |
-  Here wii be the abstract.
+  This is the abstract.
 
   It consists of two paragraphs.
-
 keywords: 
@@
   - keyword2
-
 journal: "An awesome journal"
@@
 numbersections: true
-bibliography:   bibliography.bib
-
+bibliography: mybibfile.bib
 biblio-style: elsarticle-harv # author year style for natbib - use 'elsarticle-num' or 'elsarticle-num-names' for numbered scheme
-
 classoption: preprint, 3p, authoryear # remove authoryear is not using `elsarticle-harv`
@@
 # csl: https://www.zotero.org/styles/elsevier-harvard
-
 output: 
@@
     citation_package: natbib
-  bookdown::pdf_document2:
-    number_sections:  yes
-    fig_caption:      yes
-    keep_tex:         yes
-    latex_engine:     xelatex
-    toc:              yes
-    toc_depth:        4
-    fig_width:        7
-    fig_height:       4.5
-    documentclass:    article
-    classoption:      a4paper,oneside
-    fontsize:         12pt
-    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
-    link-citations:   yes
-    colorlinks:       yes
-    urlcolor:         blue
-    biblio-style:     apalike
-  bookdown::word_document2: default
 ---
-
-```{r setup, echo=F, include=FALSE}
-rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
-# renv::load("~/MANUSCRIPTS/02_enhancement/", quiet = TRUE)
-## document configurations
-knitr::opts_chunk$set(comment    = ""      )
-# knitr::opts_chunk$set(dev        = "pdf"   )
-knitr::opts_chunk$set(out.width  = "50%"   )
-knitr::opts_chunk$set(fig.align  = "center")
-# knitr::opts_chunk$set(fig.pos    = 'h!'    )
-options(knitr.graphics.auto_pdf = FALSE)
-library(pander)
-library(data.table)
-library(kableExtra)
-library(dplyr)
-## load data from trends analysis
-source("~/MANUSCRIPTS/02_enhancement/GHI_enh_00_variables.R")
-load("~/MANUSCRIPTS/02_enhancement/data/GHI_enh_03_process.Rda")
-TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/02_enhancement/figures/tbl_tsi_info.dat",
-                               strip.white = TRUE,
-                               sep = ";",
-                               header = TRUE))
-```
-
-# Abstract {.unnumbered}
-
-- Phenomenon
-- Effects
-- bibliography
-- our approach
-- our results
-
-CE: cloud enhancement cases one minute
-
-ECE: extreme cloud enhancement cases one minute over TSI on horizontal plane
-
-CEG: cloud enhancement groups, cases events with consecutive CE
-
-$\text{GHI}_\text{i}$: measured one minute global horizontal irradiance
-
-$\text{GHI}_\text{CSm}$: modeled clear sky one minute global horizontal irradiance
-
-# Intro
-
-The shortwave solar irradiance, reaching Earth's surface, is the main energy source
-of the atmosphere and biosphere and drives and governs the climate [@Gray2010].  It
-has direct practical application, in different industries, like energy production and
-agriculture method.  The variability of its intensity, can cause difficulties in
-predicting the yield, and designing the specifications of the appropriate equipment.
-A lot of research has been focused on predicting the renewable energy production in a
-fine timescale and in near real-time (for a review see @Inman2013; @Graabak2016).
-
-A big aspect of this variability is the interaction with the clouds. In general,
-clouds absorb part of the solar irradiance, but under certain conditions, can enhance
-the total shortwave irradiance reaching the ground. This effect, can locally increase
-the observed total shortwave irradiance higher than the expected clear sky irradiance
-[see references therein].
-
-Some of the proposed underling mechanisms of those events, have been summarized by
-@Gueymard2017, and include scattering on the edge of cumulus clouds or through thin
-cirrus.  Further investigation with radiation transfer modeling methods and
-observations have pointed as the prevailing mechanism, the forward Mie scattering
-[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015], through the clouds.
-The overall phenomenon depends on different interactive factors, that include cloud
-thickness, constitution and type; and the relative position of the sun, the clouds,
-and the observer [@Gueymard2017; @Veerman2022].  As such, there are multiple
-contributing mechanism that are responsible for the observed irradiance enhancements.
-
-Cloud enhancements have been reported, to be able to exceed in intensity even the
-value of the solar constant, resulting of clear indexes above unit. A summary of
-extreme enchantment cases have been compiled by @Martins2022. There are also some
-practical implication of the cloud enchantments.  The intensity and duration of
-enhancements can effect the efficiency and stability of photovoltaic power production
-[@Lappalainen2020; @Jaervelae2020], and extreme enhancements cases, have the
-potential to compromise the integrity of photovoltaic plants infrastructure
-[@DoNascimento2019].  It has also been demonstrated, that these events can interfere
-in the comparison of ground data and satellite observations [@Damiani2018]
-
-<!--
-Study of the mechanism has also been done with modeling of different cloud types and
-atmospheric conditions.  @Gueymard2017; @Veerman2022
--->
-
-<!--
-Instruments respose ....
-@Martins2022
--->
-
-Methods of identification cloud enchantment events in the literature, usually include
-the use of a simulated clear sky radiation as baseline, that is combined with an
-appropriate threshold or some other statistical characteristics, and in some cases,
-with visual methods with a sky cam [@Vamvakas2020; @Mol2023 and references therein].
-
-<!-- our work -->
-In this study, we evaluated the effects cloud enhancements on the total downward
-radiation by studding the occurrences, their intensity, and their duration in a
-thirty-year period at the city of Thessaloniki.  We used modeled clear sky
-irradiance, as a baseline to identify cloud enhancements.  We were able to determine
-some trends of the phenomenon, it's Climatology, and some of their  general
-characteristics. We weren't able to find a comparable study that provides trends for
-similar long term dataset, as ours.  The recording of the radiation signal is the
-mean of one-minute. Thus, the minimum resolution of cloud enhancement events (CE), in
-this study is one minute.
-
-<!-- Define CE and ECE -->
-In the relative bibliography different definition have been used for these events,
-some of the are summarized by @Gueymard2017.  Here, we defined as cloud enhancement
-events (CE) the cases when the measured global horizontal irradiance (GHI) at ground
-level, exceeds the expected value under clear-sky conditions.  Similar, we define as
-extreme cloud enhancement events (ECE), the cases when GHI, exceeds the Total Solar
-Irradiance on horizontal plane at ground level.  Although the duration of these
-bursts varies, from instantaneous to several minutes, here we are constrained by the
-recorded data, to one-minute steps.
-
-<!--
-Identification methods from bib
-
-- clearness index
-- modeled approaches
-- algorithmic id
-- AI
-- Visual
-
-Constrains of the site
-
-- data
-- instrument
-- location
--->
-
-# Data and methodology
-
-## GHI data
-
-The monitoring site is operating in the Laboratory of Atmospheric Physics of the
-Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
-\(22^\circ\,57'\,\)E, \(80\,\)m\ a.s.l.).
-In this study we present data from the period
-`r strftime(min(ST_daily$Date), "%d\\ %B %Y")` to
-`r strftime(max(ST_daily$Date), "%d\\ %B %Y")`.
-<!-- Instrument -->
-The GHI data were measured with a Kipp\ & Zonen CM-21 pyranometer.  During the study
-period, the pyranometer was independently calibrated three times at the
-Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of the
-instrument’s sensitivity was better than $0.7\,\%$ relative to the initial
-calibration by the manufacturer.
-<!-- Measurements -->
-For the acquisition of radiometric data, the signal of the pyranometer was sampled at
-a rate of $1\,\text{Hz}$.  The mean and the standard deviation of these samples were
-calculated and recorded for every minute.  The measurements were corrected for the
-zero offset ("dark signal" in volts), which was calculated by averaging all
-measurements recorded for a period of $3\,\text{h}$, before (morning) or after
-(evening) the Sun reaches an elevation angle of $-10^\circ$.  The signal was
-converted to irradiance using the ramped value of the instrument’s sensitivity
-between subsequent calibrations.
-
-<!-- Radiation data quality check -->
-To further improve the quality of the irradiance data, a manual screening was
-performed to remove inconsistent and erroneous recordings that can occur
-stochastically or systematically during the continuous operation of the instruments.
-The manual screening was aided by a radiation data quality assurance procedure,
-adjusted for the site, which was based on the methods of Long and Shi\ [@Long2006;
-@Long2008a].  Thus, problematic recordings have been excluded from further
-processing.  Although it is impossible to detect all false data, the large number of
-available data, and the aggregation scheme we used, ensures the quality of the
-radiation measurements used in this study.
-<!-- Data selection -->
-To preserve an unbiased representation of the data we applied a constraint, similar
-the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there must
-exist at least 45 minutes of valid measurements, including nighttime near sunrise and
-sunset. Days with less than 5 valid hours are rejected completely.
-<!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7),
-otherwise all data for this day is flagged as invalid. There must be at least This
-work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid,
-otherwise all minute data for this hour is flagged as invalid. -->
-Furthermore, due to the significant measurement uncertainty when the Sun is near the
-horizon, and due to some systematic obstructions by nearby buildings, we have
-excluded all measurements with solar zenith angle (SZA) greater than 
-$`r 90 - BIO_ELEVA`^\circ$.
-
-## Cloud enhancement detection
-
-To be able to detect the CE cases, we had to establish a baseline, above which we can
-characterize each data point as an enhancement event, by estimating the occurring
-over irradiance (OIR). The OIR, here is defined as the irradiance difference of the
-measured one-minute $\text{GHI}_i$ from the CE identification criterion in
-Equation\nobreakspace\ref{eq:CE4}
-($\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}$).
-To have an estimation, and a first insight on the phenomenon, we experimented with two
-simple approaches for the reference.  The Haurwitz's model [@Haurwitz1945], which is
-as simple clear sky model, and we had already adjusted and had good fit with our data
-[@Natsis2023], and the TSI at the top of the atmosphere.  We have tested both cases
-by using an appropriate relative threshold and/or an additional constant offset.  The
-initial results, showed that we can detect a big portion of the CE events. These
-results were helpful, and helped to establish some criteria to further improve the CE
-identification. It was evident, by inspecting the daily plot of irradiance, that
-changes on the atmospheric conditions introduced numerous false positive and false
-negative results.  To produce a more accurate reference, we had to take into account
-more factors that effect the clear sky radiation. So we used a radiation transfer
-model.
-
-## Modeled clear Sky Irradiance
-
-### Climatology of clear sky irradiance
-
-We approximated the expected clear sky GHI by using a radiation transfer model.  The
-simulations was performed by the well established model Libradtran [@Emde2016], a
-similar approach, was also used by @Vamvakas2020 for creating a clear sky reference.
-Because of the lack of observational data for the whole period, we used some long
-term climatological data for the main factors responsible for the attenuation of the
-broadband downward solar radiation in the atmosphere. Which are mainly, the aerosols
-and the water vapors.  Fortunately, our site participates in the Aerosol Robotic
-Network (AERONET) [@Giles2019; @Buis1998], as we operate a Cimel photometer since
-2003, collocated with the CM-21 pyranometer.  The mean monthly aerosol optical depth
-(AOD) on different wavelengths is provided by AERONET, along with the equivalent
-water column height in the atmosphere.
-
-<!-- Libradtran options -->
-For completeness, we will describe here the main points of the radiation simulation
-procedure. We used as input the spectrum of @Kurucz1994 in the range $280$ to
-$2500\,\text{nm}$, with the Libradtran radiation transfer solver "disort" on a
-"pseudospherical" geometry and the "LOWTRAN" gas parameterization. For each
-combination of conditions we use a SZA step of $0.2^\circ$.
-<!-- Atmospheric options -->
-For the atmospheric characteristics, we iterated for combinations of AOD at
-$500\,\text{nm}$ ($\tau_{500\text{nm}}$) with additional offsets of $\pm1$ and
-$\pm2\sigma$, and water column ($wc$), also with offsets of $\pm1$ and $\pm2\sigma$.
-We applied them on two atmospheric profiles, from the Air Force Geophysics
-Laboratory (AFGL). The "AFGL atmospheric constituent profile, midlatitude summer"
-(afglms) and the "AFGL atmospheric constituent profile, midlatitude winter" (afglmw)
-[@Anderson1986].
-
-<!-- Lookup table -->
-To create a look-up table, that aligns with our dataset, we applied some adjustments.
-To account for the Sun's variability, in our one-minute GHI measurements, we adapted
-each modeled value by scaling the model's input spectrum integral, to the
-corresponding total solar irradiance (TSI) provided by NOAA [@Coddington2005].  Also,
-we account for the effect of the Earth -- Sun distance on the irradiance, by using
-the distance calculated by the Astropy [@AstropyCollaboration2022] software library.
-As needed, we interpolate the resulting irradiances to the exact SZA of our
-measurements.  For each period of the year, we used the appropriate atmospheric
-profile (afglms or afglmw).  Finally, we calculated the clear sky irradiance value at
-the horizontal plane.  Thus, we were able to emulate different atmospheric condition
-and levels of atmospheric clearness for the climatological conditions of the site.
-With this method, the modeled clear sky irradiances can be directly compared to each
-measured one-minute value of GHI, for different conditions of atmospheric clearness.
-
-### Long term change of clear sky irradiance
-
-<!-- Aerosol change -->
-The above clear sky reference values are not enough to describe the long term
-variation, due to the changes of the atmospheric constituents. As observed by
-@Natsis2023, there is a long term brightening effect, over Thessaloniki for the studied
-period. In order to better describe this change, we used, estimations of AOD change
-derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change of
-$-3.8\,\%$ per year at AOD on $340\,\text{nm}$, using a Brewer spectrophotometer. For
-2005 to 2023, we derived the trend from the available AERONET data.
-
-To create a unified trend for the long term change of the clear sky irradiance, we
-simulated the values of AOD derived from those sources with Libradtran. For both, we
-have used the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
-coefficients, and we choose the SZA of $55^\circ$ as a representative value for all
-runs.
-
-According to @Kazadzis2007, in the period 1997 -- 2005, the mean AOD of
-$340\,\text{nm}$ was calculated to $0.403$ with the use of a Brewer
-spectrophotometer, with a linear trend of $-3.8±0.93\,\%$ per year.  This corresponds
-to a AOD $340\,\text{nm}$ change of $0.0153$ per year.  Using the alpha Ångström
-coefficient of $\alpha = 1.6$, this translates to a change in Ångström beta
-coefficient of $\beta=0.00272$ per year (or $\beta=0.084$ in 1997 and $\beta=0.059$
-in 2005).  By interpolating the resulting clear sky irradiance, we have a trend of
-$+0.21\,\%$ per year for the clear sky irradiance.  For the period 2005 -- 2005 we
-used the mean monthly values from AERONET, with a similar simulation scheme. We
-computed the trend of clear sky radiation for each month of the year, which gave us a
-mean clear sky radiation trend of $+0.14\,\%$ per year. We applied this long term
-change to the clear sky irradiance, in order to create a more realistic
-representation of the irradiance for the whole study period
-(Figure\nobreakspace{}\ref{fig:CS-change}).
-
-```{r CS-change, echo=FALSE, fig.cap="Simulated long term change of clear sky irradiance relevant to its climatological values."}
-knitr::include_graphics("../images/P_CS_change-1.png")
-```
-
-<!-- 1997 0.0839901
-<!-- 2005 0.05496013
-<!-- # Kazadzis2007 - Nine years of UV aerosol optical depth measurements at Thessaloniki, Greece
-<!-- # From Stelios' paper 2007:
-<!-- # AOD @340 from Brewer 086
-<!-- # Period: 1997-2005
-<!-- # The mean AOD for this period was calculated to 0.403 for the Brewer and 0.422 for the CIMEL.
-<!-- # A linear regression on the Brewer deseasonalized data reveals a change of -3.8±0.93% per year.
-<!-- # From the above data AOD @340 changes by 0.0153 per year (or 0.138 for the 9 years).
-<!-- # Using Angstrom a= 1.6  this translates to a change in Angstrom β=0.00272 per year (or β=0.084 in 1997 and β=0.059 in 2005).
--->
-
-## CE Criteria investigation
-
-The use of the actual modeled values of clear sky GHI, described above , can not provide us with
-a robust method to distinguish the CE cases, due to the limited accuracy of the input
-data. Our main focus was to positively identify over irradiance events from CEs, 
-so we created an upper envelope of the clear sky irradiance,
-
-.............................
-
-above which, any GHI value can safely attributed to CE.  We evaluated the performance
-of the modeled clear radiation for each of atmospheric level of clearness, as
-reference, in order to conclude which is the most appropriate.
-
-To select the exact values of these thresholds factors (Equation \ref{eq:CE4}), we
-implemented an empirical method, by manual inspection of the CE identification, on
-specially selected days from the whole dataset.  We used seven sets of selected days,
-with characteristics relevant to the efficiency of the identification threshold.
-These sets were random groups of about 20 to 30 days with the following
-characteristics:
-(a) the largest over irradiance CE events,
-(b) the largest daily total over irradiance,
-(c) without clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
-(d) without clouds and without EC events,
-(e) with at least $60\,\%$ of the day length without clouds and some EC events,
-(h) random days and
-(i) some manual selected days that were included during the manual inspection.
-Where it was needed, for some of the edge cases, we also used images from a sky-cam,
-to further aid the decisions of the manual inspection.
-
-After evaluating the modeled clear radiation for the different atmospheric
-conditions, in relation to the measured GHI data, we choose as a representative of
-the clear sky radiation, the case where
-$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
-($\text{GHI}_\text{CSm}$).
-These values represent a typical atmosphere in Thessaloniki with low load of aerosols
-and humidity, which are the main factor that attenuate the GHI, excluding clouds.  To
-create the limit of CE identification, we created a two branched threshold, as a
-function of SZA. A constant factor for low SZAs, and a higher ramped factor for
-higher SZAs (Equation\nobreakspace\ref{eq:CE4}).
-This is the criterion of our CE identification.
-<!--
-\begin{equation}
-\text{CE}_\text{Threshold} = \begin{cases}
-`r C4_cs_ref_ratio`, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
-\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
-\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
-\end{cases}\label{eq:CE4a}
-\end{equation}
-where: $\theta$ solar zenith angle.
--->
-<!--
-\begin{equation}
-\text{CE} : \begin{cases}
- \text{GHI}_\text{i} > `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
-\text{GHI}_\text{i} > \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
-\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
-\end{cases}\label{eq:CE4b}
-\end{equation}
-where: $\theta$ is the solar zenith angle, $\text{GHI}_\text{i}$ the measured
-irradiance, and $\text{GHI}_\text{mCSi}$ the selected modelled clear sky irradiance.
--->
-<!-- \begin{equation} -->
-<!-- \text{CE} : \text{E}_\text{i} > \text{E}_\text{CSlim,i}, \text{where} \begin{cases} -->
-<!--  \text{E}_\text{CSlim,i} = `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\ -->
-<!-- \text{E}_\text{CSlim,i} = \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\ -->
-<!-- \text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ -->
-<!-- \end{cases}\label{eq:CE4} -->
-<!-- \end{equation} -->
-<!-- where: $\theta$ is the solar zenith angle, $\text{E}$ the measured -->
-<!-- irradiance, $\text{E}_\text{CSm}$ the selected modelled clear sky irradiance, and $i$ each of the one-minute observation. -->
-
-\begin{equation}
-\text{CE} : \text{E}_\text{i} > `r C4_GLB_diff_THRES` + `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i} \,\,[W/m^2] \label{eq:CE4}
-\end{equation}
-where: $\theta$ is the solar zenith angle, $\text{E}$ the measured
-irradiance, $\text{E}_\text{CSm}$ the selected modelled clear sky irradiance, and $i$ each of the one-minute observation.
-
-<!-- reasoning for cretria -->
-We have to note, that the differentiation of the threshold factor was needed, because
-of the high irradiance values we observed, early in the morning and late in the
-afternoon. We have confirmed, by inspecting images from the sky cam, that we have
-duration of elevated irradiance, either due to the clearness of the atmosphere, or some
-interferences by reflections on nearby bright surfaces. Although, these cases may
-mask some of the CE events. The actual CE events, produce higher irradiance and thus
-are identified as such. As a side effect, the reported OIR will be slight
-underestimated for those SZAs, but the overall contribution of those cases to the
-total daily energy, is minimal due the low occurrences and the lower irradiances.
-
-<!--
-- can follow for clear days
-- this selection has some subjectivity
-- the most important are the thresholds
-- model have to be uniform on clear days
-- the level is adjusted by the threshold 
-- the effect of the sza uniform
--->
-
-.............
-
-These selections have some subjectivity, as the definition of clear sky, is depended
-on the intended usage. Our main focus is to be able to identify the OIR created by the
-clouds. Although, the aerosols and water vapor are always present and can not be
-completely removed. 
-The effect of the different clearness levels
-
-.............
-
-<!-- extreme cases criterion -->
-Another aspect of the CE events, that is often reported in the relative bibliography,
-are cases of extreme cloud enhancement (ECE). These are cases of CE where the
-measured intensity of the irradiance, exceeds the equivalent TSI on the top of the
-atmosphere, and satisfy the Equation\nobreakspace{}\ref{eq:ECE}.
-\begin{equation}
-\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
-\label{eq:ECE}
-\end{equation}
-where: $\theta$ the solar zenith angle, $E_{\odot}$ the solar constant, $r$ the Sun -- Earth distance, and $i$ each of the one-minute observation.
-
-.......
-
-- Include Example of days plot in the Appendix!
-... this is clearer to understand and describe ....
-
-.......
-
-<!-- ```{r echo=F, include=T, warning=FALSE, message=FALSE} -->
-<!-- ST_total -->
-<!-- cat("\n - - - \n") -->
-<!-- ST_daily[which.max(wattGLB.max), wattGLB.max] -->
-<!-- round(ST_E_daily[which.max(GLB_diff.max), GLB_diff.max], 2) -->
-<!-- round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1) -->
-<!-- plot(ST_daily$Date, ST_daily$GLB_diff.max) -->
-<!-- ``` -->
-
-<!-- \FloatBarrier -->
-
-# Results
-
-Our dataset, after the data selection processing, consists of
-`r ST_total$wattGLB.N` records of GHI, of which
-$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are CE and
-$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are ECE events.
-The highest GHI recorder was 
-$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,W/m^2$
-on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`.
-The absolute stronger CE event had an OIR of 
-$`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,W/m^2$ on
-`r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`.
-The relative stronger CE event was 
-$`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 
-clear sky threshold, on 
-`r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.
-
-## Trends
-
-```{r loadtrends, echo=F, include=T, warning=FALSE, message=FALSE}
-dailytrends <- data.table(
-  read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear.csv"))
-dailyCE <- dailytrends[DATA == "ST_E_daily"]
-yearlytrends <- data.table(
-  read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear_Proper.csv"))
-yearlyCE <- yearlytrends[DATA == "ST_E_yearly"]
-
-```
-
-We computed the daily trend of the mean OIR of CE
-(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order autoregressive
-model with lag of 1 day, using the 'maximum likelihood' fitting method [@Gardner1980;
-@Jones1980] by implementing the function 'arima' from the library 'stats' of the R
-programming language [@RCT2023]. The trends are reported together with the $2\sigma$
-error.  We observe an increase of
-$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
-`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2/y$
-on the mean OIR.
-
-```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."}
-knitr::include_graphics("../images/P_daily_trend-1.png")
-```
-
-Although, the previous result is closer to the raw data, we preferred to present the
-annual statistics, that give a more clear picture about the long term CE trends.
-Hence, we calculated the annual values from the one-minute measurements.  The trend of
-OIR is
-$`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2/y$
-(Figure\nobreakspace{}\ref{fig:P-energy-mean}),
-but this value alone is not very useful due the intrinsic high variability of this
-metric.
-
-<!-- ```{r CEmeanDaily2, echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"} -->
-<!-- knitr::include_graphics("../images/daily-12.png") -->
-<!-- ``` -->
-
-<!-- ```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"} -->
-<!-- knitr::include_graphics("../images/energy-3.png") -->
-<!-- ``` -->
-
-```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean OIR per CE."}
-knitr::include_graphics("../images/P_energy-7.png")
-```
-
-A better indicator of changes on the characteristic of CE would be the number of CE
-occurrences and the total energy of the CE over irradiance. The annual number of CE
-occurrences, shows a steady increase of
-$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/y$
-(Figure\nobreakspace{}\ref{fig:P-energy-N}).
-We have to note that the energy related to the CE events can not be directly linked
-with the total energy balance on the atmosphere. The net sun radiation of the region
-is not increased, but rather redistributed through the CE. Although, the
-instantaneous values, can exceed the equivalent clear sky irradiance to a
-considerable level.
-
-<!-- ```{r echo=FALSE, fig.cap="Trend of number of CE cases"} -->
-<!-- knitr::include_graphics("../images/energy-2.png") -->
-<!-- ``` -->
-
-```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly CE number of occurancies."}
-knitr::include_graphics("../images/P_energy-6.png")
-```
-
-Subsequently, the mean annual increase of energy due to CE events is
-$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
-(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
-occurrences.
-
-<!-- ```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"} -->
-<!-- knitr::include_graphics("../images/energy-1.png") -->
-<!-- ``` -->
-
-```{r P-energy-sum, echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
-knitr::include_graphics("../images/P_energy-5.png")
-```
-
-```{r P-energy-median, echo=FALSE, fig.cap="Trend of the yearly median over irradiance due to CE over irradiance"}
-knitr::include_graphics("../images/P_energy-8.png")
-```
-
-<!-- \FloatBarrier -->
-
-## Climatology
-
-Another interesting aspect of the CE cases, is their seasonal cycle. In
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the box plot
-(whisker plot), where the values have been normalized by the highest median value,
-that occurs in May.  Although the number of occurrences has a wide spread throughout
-the study period, the most active period of CE occurrences is during May and June.
-During the Winter (December -- February) the CE cases are about $25\,\%$ of the maximum.
-The rest of the months the occurrences ramp between the maximum and minimum.
-
-```{r relative-month-occurancies, echo=FALSE, fig.cap="Statistics of the number of CE occurancies for each month.
-The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
-knitr::include_graphics("../images/clim_CE_month_norm_MAX_median_N-2.png")
-```
-<!--
-```{r echo=FALSE, fig.cap="Distribution of the number of CE cases"}
-knitr::include_graphics("../images/climCEmonth-1.png")
-```
---->
-
-<!-- ```{r echo=FALSE, fig.cap="Distribution of CE above reference"} -->
-<!-- knitr::include_graphics("../images/relative_distributions-2.png") -->
-<!-- ``` -->
-<!--
-```{r echo=FALSE, fig.cap="Distribution of CE above reference"}
-knitr::include_graphics("../images/relative_distributions-4.png")
-```
--->
-
-The distribution of the CE over irradiance spreads uniformly
-Figure\nobreakspace{}\ref{fig:ovir-distribution}. Where there is an inverse relation
-between the events frequency and events intensity. This is expected as, the stronger
-the CE events become, the rarer the particular atmospheric and sun conditions
-occur.
-
-```{r ovir-distribution, echo=FALSE, fig.cap="Distribution of CE over irradiance"}
-knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
-```
-
-<!-- whisky plots relative to GLB -->
-
-<!-- set of yearly plots -->
-
-<!-- \FloatBarrier -->
-
-## Groups stats
-
-In order to further study the characteristics of the CE events, we grouped the single
-minute CE events, to continuous CE groups (CEG). Thus, a CEG consists of one or more
-successive CE cases, and can have a duration of multiple of minutes.  We have
-identified `r ST_G0[, .N]` groups, where the group with the longest duration lasted
-`r ST_G0[, max(GLB_diff.N)]` minutes on
-`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")`.
-By examining the frequency distribution of the CEG durations
-(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can conclude that
-longer durations are getting increasingly rare, with durations above 10 minutes very
-rare.
-
-```{r ceg-duration-distribution, echo=FALSE, fig.cap="Distribution of CE groups"}
-knitr::include_graphics("../images/groups-1.png")
-```
-
-... @Zhang2018 ....
-
-```{r echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"}
-knitr::include_graphics("../images/P-groups-bin2d-1.png")
-```
-
-<!-- ```{r echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"} -->
-<!-- knitr::include_graphics("../images/groups-4.png") -->
-<!-- ``` -->
-
-<!-- ```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"} -->
-<!-- knitr::include_graphics("../images/groups-8.png") -->
-<!-- ``` -->
-
-<!-- \FloatBarrier -->
-
-## Extreme CE above TSI
-
-Another aspect of the CE events are the cases when the irradiance is above the
-expected irradiance on top of the atmosphere, we have defined this as ECE
-(Equation\nobreakspace{}\ref{eq:ECE}).
-
--  max value ECE
-  relative to other works max values
-
-Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies} we have
-computed the distribution of the number of occurrences of ECE events by month in
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the most active
-period is in the spring (March -- May), followed by the months of June, September and
-October.
-
-.......
-
-```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Distribution of "}
-knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")
-```
-
-<!-- ```{r echo=FALSE, fig.cap="Distribution of the number of ECE cases"} -->
-<!-- knitr::include_graphics("../images/climECEmonth-1.png") -->
-<!-- ``` -->
-
-```{r echo=FALSE, fig.cap="Distribution of ECE above 'clear sky' reference"}
-knitr::include_graphics("../images/extremedistributions-2.png")
-```
-
-<!-- ```{r echo=FALSE, fig.cap="Distribution of ECE Irradiance above 'TSI'"} -->
-<!-- knitr::include_graphics("../images/extremedistributions-4.png") -->
-<!-- ``` -->
-
--   SZA
-
-<!-- ### Yearly plots relative to all GHI data. -->
-<!-- ```{r echo=FALSE, fig.cap=""} -->
-<!-- knitr::include_graphics("../images/rel_energy-1.png") -->
-<!-- ``` -->
-<!-- ```{r echo=FALSE, fig.cap=""} -->
-<!-- knitr::include_graphics("../images/rel_energy-2.png") -->
-<!-- ``` -->
-<!-- ```{r echo=FALSE, fig.cap=""} -->
-<!-- knitr::include_graphics("../images/rel_energy-3.png") -->
-<!-- ``` -->
-
-<!-- \FloatBarrier -->
-
-# Discussion and conclusions
-
-Compare to other location stats.
-max, ECE, distributions ....
-
-Climatology results
-
-# Appendix {.unnumbered}
-
-<!-- # References {.unnumbered} -->
-
-<!--
-Elsevier template
 
@@
 
--->
+# References {-}

### 2024-05-21 high_aod/GHI_enh_00_variables.R

@@ -1,0 +1,1 @@
+../GHI_enh_00_variables.R

### 2024-05-22 article/article.Rmd
Commit 2024-05-22 04:15

@@
 
-.............
-
-These selections have some subjectivity, as the definition of clear sky, is depended
-on the intended usage. Our main focus is to be able to identify the OIR created by the
-clouds. Although, the aerosols and water vapor are always present and can not be
-completely removed. 
-The effect of the different clearness levels
-
-.............
+The definition of the CE events with this method, has a level of subjectivity. The
+actual clear sky irradiance, is not known, and can only be approximated. Although,
+because our main focus is to be able to identify the OIR created by the clouds, we
+expect that we were able to detect all the major events of OIR due to CE.  Where,
+minor enhancements may be not detected, are less significant for most of our results.
 
@@
 Another aspect of the CE events, that is often reported in the relative bibliography,
-are cases of extreme cloud enhancement (ECE). These are cases of CE where the
+are cases of extreme cloud enhancement (ECE). These are cases of CE, where the
 measured intensity of the irradiance, exceeds the equivalent TSI on the top of the
@@
 where: $\theta$ the solar zenith angle, $E_{\odot}$ the solar constant, $r$ the Sun -- Earth distance, and $i$ each of the one-minute observation.
+
+To give a better understanding of the CE identification procedure, we included 
+an example of the CE identification for a selected day .... appendix....
+where the use of the reference and the threshold are shown, along with the relevant
+measurements.
+
+Similar we provide yearly plots
 

### 2024-05-22 article/article.tex
Commit 2024-05-22 04:15

@@
 
-\ldots\ldots\ldots\ldots.
-
-These selections have some subjectivity, as the definition of clear sky,
-is depended on the intended usage. Our main focus is to be able to
-identify the OIR created by the clouds. Although, the aerosols and water
-vapor are always present and can not be completely removed. The effect
-of the different clearness levels
-
-\ldots\ldots\ldots\ldots.
+The definition of the CE events with this method, has a level of
+subjectivity. The actual clear sky irradiance, is not known, and can
+only be approximated. Although, because our main focus is to be able to
+identify the OIR created by the clouds, we expect that we were able to
+detect all the major events of OIR due to CE. Where, minor enhancements
+may be not detected, are less significant for most of our results.
 
@@
 bibliography, are cases of extreme cloud enhancement (ECE). These are
-cases of CE where the measured intensity of the irradiance, exceeds the
+cases of CE, where the measured intensity of the irradiance, exceeds the
 equivalent TSI on the top of the atmosphere, and satisfy the
@@
 the one-minute observation.
+
+To give a better understanding of the CE identification procedure, we
+included an example of the CE identification for a selected day \ldots.
+appendix\ldots. where the use of the reference and the threshold are
+shown, along with the relevant measurements.
+
+Similar we provide yearly plots
 

### 2024-05-22 GHI_enh_03_process.tex
Commit 2024-05-22 20:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-05-20}
+\date{2024-05-22}
 
@@
 ST_G0
-ST_G1
 ST_monthly
@@
 \begin{verbatim}
-2024-05-20 16:54:33.3 athan@tyler GHI_enh_03_process.R 6.553817 mins
+2024-05-22 09:38:39.3 athan@tyler GHI_enh_03_process.R 5.198113 mins
 \end{verbatim}

### 2024-05-22 GHI_enh_02_ID_CE.R
Commit 2024-05-22 20:14

@@ -600,27 +600,29 @@ for (ii in 1:nrow(vec_days)) {
              ylab = expression(Watt/m^2), xlab = "Time (UTC)")
         ## Global
         lines(temp$Date, temp$wattGLB, col = "green")
+
         ## Direct
         # lines(temp$Date, temp$wattHOR, col = "blue")
+
         ## TSI on ground
         lines(temp$Date, temp$ETH)
 
         ## Active model reference
-        lines(temp[, get(paste0(SelEnhanc,"_ref")), Date], col = "red" )
+        lines(temp[, get(paste0(SelEnhanc, "_ref")), Date], col = "red" )
 
         ## A test reference
         # lines(temp[, Enhanc_C_4_ref_test, Date], col = "cyan" )
 
         ## CS libradtran reference
-        lines(temp[, get(paste0(csmodel, ".glo")), Date], col = "magenta" )
+        # lines(temp[, get(paste0(csmodel, ".glo")), Date], col = "magenta" )
 
         ## CS libradtran reference
         # lines(temp[, CS_low * TSI_Kurudz_factor , Date], col = "pink" )
 
-        ## add sza axis
-        aaa <- temp[Date %in% c(min(Date), (pretty(Date, 10) + 30), max(Date))  , ]
-        axis(1, at = aaa$Date, labels = round(aaa$SZA,1),
-             line = 1.2, lwd = 0, lwd.ticks = 0, cex.axis = 0.8)
+        # ## add sza axis
+        # aaa <- temp[Date %in% c(min(Date), (pretty(Date, 10) + 30), max(Date))  , ]
+        # axis(1, at = aaa$Date, labels = round(aaa$SZA,1),
+        #      line = 1.2, lwd = 0, lwd.ticks = 0, cex.axis = 0.8)
 
         ## Enchantment cases
         points(temp[get(SelEnhanc) == TRUE, wattGLB, Date], col = "red")
@@ -629,16 +631,25 @@ for (ii in 1:nrow(vec_days)) {
         points(temp[TYPE == "Cloud", wattGLB, Date], col = "blue", pch = 3, cex = 0.3)
 
         ## Decorations
-        title(main = paste(as.Date(aday, origin = "1970-01-01"), temp[get(SelEnhanc) == TRUE, .N], temp[TYPE == "Cloud", .N], vec_days$Descriprion[ii]))
[…]

### 2024-05-22 GHI_enh_03_process.R

@@ -345,19 +345,19 @@ ST_G0[, GLB_diff.sum  := GLB_diff.sum * 60 / Energy_Div]
 ST_G0[, wattGLB.sum   := wattGLB.sum  * 60 / Energy_Div]
 
 
-##  Groups with one gap  -------------------------------------------------------
-ST_G1 <- DATA[!is.na(C1Grp1),
-              unlist(c(lapply(.SD, enhanc.summary, na.rm = FALSE),
-                       Date = min(Date)),
-                     recursive = FALSE),
-              .SDcols = my.cols.gr,
-              by = .(Group1 = C1Grp1)]
-ST_G1$Date <- as.POSIXct(ST_G1$Date, origin = "1970-01-01")
-
-## convert sum Irradiance to energy
-## Σ(W/m^2) * 60 s = J/m^2
-ST_G1[, GLB_diff.sum  := GLB_diff.sum * 60 / Energy_Div]
-ST_G1[, wattGLB.sum   := wattGLB.sum  * 60 / Energy_Div]
+# ##  Groups with one gap  -------------------------------------------------------
+# ST_G1 <- DATA[!is.na(C1Grp1),
+#               unlist(c(lapply(.SD, enhanc.summary, na.rm = FALSE),
+#                        Date = min(Date)),
+#                      recursive = FALSE),
+#               .SDcols = my.cols.gr,
+#               by = .(Group1 = C1Grp1)]
+# ST_G1$Date <- as.POSIXct(ST_G1$Date, origin = "1970-01-01")
+#
+# ## convert sum Irradiance to energy
+# ## Σ(W/m^2) * 60 s = J/m^2
+# ST_G1[, GLB_diff.sum  := GLB_diff.sum * 60 / Energy_Div]
+# ST_G1[, wattGLB.sum   := wattGLB.sum  * 60 / Energy_Div]
 
 
 

### 2024-05-22 article/article.tex
Commit 2024-05-23 02:14

@@
 
+\usepackage{caption}
+\usepackage{placeins}
+\captionsetup{font=small}
 \usepackage{booktabs}
@@
 To give a better understanding of the CE identification procedure, we
-included an example of the CE identification for a selected day \ldots.
-appendix\ldots. where the use of the reference and the threshold are
-shown, along with the relevant measurements.
-
-Similar we provide yearly plots
-
-\ldots\ldots.
-
-\begin{itemize}
-\tightlist
-\item
-  Include Example of days plot in the Appendix! \ldots{} this is clearer
-  to understand and describe \ldots.
-\end{itemize}
-
-\ldots\ldots.
+provide an example of the CE identification for a selected day in the
+Appendix (Figure\nobreakspace{}\ref{fig:example-day}), where the use of
+the reference and the threshold are shown, along with the relevant
+measurements. Similar we provide an example plot of one year data, where
+the relation of the GHI and clear sky reference is shown, along with the
+OIR intensity also in the Appendix
+Figure\nobreakspace{}\ref{fig:example-year}.
 
@@
 Our dataset, after the data selection processing, consists of 6144534
-records of GHI, of which \(1.764\,\%\) are CE and \(0.036\,\%\) are ECE
-events. The highest GHI recorder was \(1416.6\,W/m^2\) on 24~May 2007.
-The absolute stronger CE event had an OIR of \(345.86\,W/m^2\) on 24~May
-2007. The relative stronger CE event was \(49.7\,\%\) above the clear
-sky threshold, on 28~October 2016.
+records of GHI, of which \(1.764\,\%\) are CE events and \(0.036\,\%\)
+are ECE events. The highest GHI recorder was \(1416.6\,W/m^2\) on 24~May
+2007. The absolute stronger CE event had an OIR of \(345.86\,W/m^2\) on
+24~May 2007. The relative stronger CE event was \(49.7\,\%\) above the
+clear sky threshold, on 28~October 2016.
 
@@
 
-We computed the daily trend of the mean OIR of CE
-(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order
-autoregressive model with lag of 1 day, using the `maximum likelihood'
+We computed the daily trend of the mean OIR of CE using a first-order
+autoregressive model with lag of 1 day, with the `maximum likelihood'
 fitting method \citep{Gardner1980, Jones1980} by implementing the
@@
 \citep{RCT2023}. The trends are reported together with the \(2\sigma\)
-error. We observe an increase of \(0.087\pm 0.08\,W/m^2/y\) on the mean
-OIR.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth]{../images/P_daily_trend-1}
-
-}
-
-\caption{Daily mean values and trend of the CE over irradiance.}\label{fig:CEmeanDaily}
-\end{figure}
+error. We observe an negligible change of \(0.087\pm 0.08\,W/m^2/y\) on
+the mean OIR.
 
@@
 long term CE trends. Hence, we calculated the annual values from the
-one-minute measurements. The trend of OIR is \(0.06\pm 0.11\,W/m^2/y\)
-(Figure\nobreakspace{}\ref{fig:P-energy-mean}), but this value alone is
-not very useful due the intrinsic high variability of this metric.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth]{../images/P_energy-7}
-
-}
-
-\caption{Trends of the mean OIR per CE.}\label{fig:P-energy-mean}
-\end{figure}
-
-A better indicator of changes on the characteristic of CE would be the
-number of CE occurrences and the total energy of the CE over irradiance.
-The annual number of CE occurrences, shows a steady increase of
-\(45.6\pm 21.9\,\text{cases}/y\)
+one-minute measurements. Although, the trend of the mean OIR has very
+weak statistical significance, the annual number of CE occurrences,
+shows a steady increase of \(45.6\pm 21.9\,\text{cases}/y\)
 (Figure\nobreakspace{}\ref{fig:P-energy-N}). We have to note that the
 energy related to the CE events can not be directly linked with the
-total energy balance on the atmosphere. The net sun radiation of the
-region is not increased, but rather redistributed through the CE.
-Although, the instantaneous values, can exceed the equivalent clear sky
-irradiance to a considerable level.
+total energy balance on the atmosphere. The net solar radiation of the
+region is not increased, but rather redistributed through the CE events.
+Resulting, instantaneous values, that can exceed the equivalent clear
+sky irradiance to a considerable level.
 
@@
 \caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:P-energy-sum}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth]{../images/P_energy-8}
-
-}
-
-\caption{Trend of the yearly median over irradiance due to CE over irradiance}\label{fig:P-energy-median}
 \end{figure}
@@
 
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{../images/example_days-18}
+
+}
+
+\caption{Example of cloud indentification data for 2019-07-11.
+Where are denoted with red circles all the detected CE events, the cloud intearaction with the GHI (blue crosses), and the thesholds of CE and the threshold of ECE events with red and black line respectively.}\label{fig:example-day}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{../images/example_years-13}
+
+}
+
+\caption{Example of the relation of the measured GHI versus the reference clear sky irradiance for the year 2005, where the intesity of the detected over irradianse (OIR) is color coded.}\label{fig:example-year}
+\end{figure}
+
+\FloatBarrier
+
 \bibliography{bibliography.bib}

### 2024-05-23 article/article.Rmd
Commit 2024-05-23 10:10

@@
   It consists of two paragraphs.
+
+header-includes:
+  - \usepackage{caption}
+  - \usepackage{placeins}
+  - \captionsetup{font=small}
 
@@
 
-To give a better understanding of the CE identification procedure, we included 
-an example of the CE identification for a selected day .... appendix....
-where the use of the reference and the threshold are shown, along with the relevant
-measurements.
-
-Similar we provide yearly plots
-
-.......
-
-- Include Example of days plot in the Appendix!
-... this is clearer to understand and describe ....
-
-.......
+To give a better understanding of the CE identification procedure, we provide an
+example of the CE identification for a selected day in the Appendix
+(Figure\nobreakspace{}\ref{fig:example-day}), where the use of the reference and the
+threshold are shown, along with the relevant measurements.  Similar we provide an
+example plot of one year data, where the relation of the GHI and clear sky reference
+is shown, along with the OIR intensity also in the Appendix
+Figure\nobreakspace{}\ref{fig:example-year}.
 
@@
 `r ST_total$wattGLB.N` records of GHI, of which
-$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are CE and
+$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are CE events and
 $`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are ECE events.
@@
 
-We computed the daily trend of the mean OIR of CE
-(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order autoregressive
-model with lag of 1 day, using the 'maximum likelihood' fitting method [@Gardner1980;
-@Jones1980] by implementing the function 'arima' from the library 'stats' of the R
-programming language [@RCT2023]. The trends are reported together with the $2\sigma$
-error.  We observe an increase of
+We computed the daily trend of the mean OIR of CE <!--
+(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), --> using a first-order autoregressive
+model with a lag of one day, with the 'maximum likelihood' fitting method
+[@Gardner1980; @Jones1980] by implementing the function 'arima' from the library
+'stats' of the R programming language [@RCT2023]. The trends are reported together
+with the $2\sigma$ error.  We observed a negligible change of
 $`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
@@
 on the mean OIR.
-
-```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."}
-knitr::include_graphics("../images/P_daily_trend-1.png")
-```
-
+<!-- ```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."} -->
+<!-- knitr::include_graphics("../images/P_daily_trend-1.png") -->
+<!-- ``` -->
 Although, the previous result is closer to the raw data, we preferred to present the
 annual statistics, that give a more clear picture about the long term CE trends.
-Hence, we calculated the annual values from the one-minute measurements.  The trend of
-OIR is
-$`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2/y$
-(Figure\nobreakspace{}\ref{fig:P-energy-mean}),
-but this value alone is not very useful due the intrinsic high variability of this
-metric.
+Hence, we calculated the annual values from the one-minute measurements.  Despite the
+very weak statistical significance of the mean OIR trend, the annual number of CE
+occurrences shows a steady increase of
+$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
+`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/y$
+(Figure\nobreakspace{}\ref{fig:P-energy-N}).
+Subsequently, the mean annual energy of the CE events is increasing with a rate of
+$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
+`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
+(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
+occurrences.  We have to note that the energy related to the CE events can not be
+directly linked with the total energy balance of the atmosphere. The net solar
+radiation of the region is not increased, but rather redistributed through the CE
+events.  This also is depicted by the "instantaneous" values of irradiance (average
+over one minute), that can exceed the equivalent clear sky irradiance to a
+considerable level.
+
+<!-- $`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm -->
+<!-- `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2/y$ -->
+<!-- (Figure\nobreakspace{}\ref{fig:P-energy-mean}), -->
+<!-- but this value alone is not very useful due the intrinsic high variability of this -->
+<!-- metric. -->
 
@@
 
-```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean OIR per CE."}
-knitr::include_graphics("../images/P_energy-7.png")
-```
-
-A better indicator of changes on the characteristic of CE would be the number of CE
-occurrences and the total energy of the CE over irradiance. The annual number of CE
-occurrences, shows a steady increase of
-$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/y$
-(Figure\nobreakspace{}\ref{fig:P-energy-N}).
-We have to note that the energy related to the CE events can not be directly linked
-with the total energy balance on the atmosphere. The net sun radiation of the region
-is not increased, but rather redistributed through the CE. Although, the
-instantaneous values, can exceed the equivalent clear sky irradiance to a
-considerable level.
+<!-- ```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean OIR per CE."} -->
+<!-- knitr::include_graphics("../images/P_energy-7.png") -->
+<!-- ``` -->
 
@@
 
-Subsequently, the mean annual increase of energy due to CE events is
-$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
-(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
-occurrences.
-
 <!-- ```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"} -->
@@
 
-```{r P-energy-median, echo=FALSE, fig.cap="Trend of the yearly median over irradiance due to CE over irradiance"}
-knitr::include_graphics("../images/P_energy-8.png")
-```
+<!-- ```{r P-energy-median, echo=FALSE, fig.cap="Trend of the yearly median over irradiance due to CE over irradiance"} -->
+<!-- knitr::include_graphics("../images/P_energy-8.png") -->
+<!-- ``` -->
 
@@
 
-## Climatology
+## CE Climatology
 
@@
 (whisker plot), where the values have been normalized by the highest median value,
-that occurs in May.  Although the number of occurrences has a wide spread throughout
+that occurs on June.  Although the number of occurrences has a wide spread throughout
 the study period, the most active period of CE occurrences is during May and June.
 During the Winter (December -- February) the CE cases are about $25\,\%$ of the maximum.
-The rest of the months the occurrences ramp between the maximum and minimum.
+For the rest months the occurrences gradually ramp between the maximum and minimum.
 
@@
 
+```{r example-day, echo=FALSE, fig.cap="Example of cloud indentification data for 2019-07-11.
+Where are denoted with red circles all the detected CE events, the cloud intearaction with the GHI (blue crosses), and the thesholds of CE and the threshold of ECE events with red and black line respectively."}
+knitr::include_graphics("../images/example_days-18.png")
+```
+
+```{r example-year, echo=FALSE, fig.cap="Example of the relation of the measured GHI versus the reference clear sky irradiance for the year 2005, where the intesity of the detected over irradianse (OIR) is color coded."}
+knitr::include_graphics("../images/example_years-13.png")
+```
+
 <!-- # References {.unnumbered} -->

### 2024-05-23 article/article.tex
Commit 2024-05-23 10:10

@@
 We computed the daily trend of the mean OIR of CE using a first-order
-autoregressive model with lag of 1 day, with the `maximum likelihood'
-fitting method \citep{Gardner1980, Jones1980} by implementing the
-function `arima' from the library `stats' of the R programming language
-\citep{RCT2023}. The trends are reported together with the \(2\sigma\)
-error. We observe an negligible change of \(0.087\pm 0.08\,W/m^2/y\) on
-the mean OIR.
-
-Although, the previous result is closer to the raw data, we preferred to
-present the annual statistics, that give a more clear picture about the
-long term CE trends. Hence, we calculated the annual values from the
-one-minute measurements. Although, the trend of the mean OIR has very
-weak statistical significance, the annual number of CE occurrences,
-shows a steady increase of \(45.6\pm 21.9\,\text{cases}/y\)
-(Figure\nobreakspace{}\ref{fig:P-energy-N}). We have to note that the
-energy related to the CE events can not be directly linked with the
-total energy balance on the atmosphere. The net solar radiation of the
-region is not increased, but rather redistributed through the CE events.
-Resulting, instantaneous values, that can exceed the equivalent clear
-sky irradiance to a considerable level.
+autoregressive model with a lag of one day, with the `maximum
+likelihood' fitting method \citep{Gardner1980, Jones1980} by
+implementing the function `arima' from the library `stats' of the R
+programming language \citep{RCT2023}. The trends are reported together
+with the \(2\sigma\) error. We observed a negligible change of
+\(0.087\pm 0.08\,W/m^2/y\) on the mean OIR. Although, the previous
+result is closer to the raw data, we preferred to present the annual
+statistics, that give a more clear picture about the long term CE
+trends. Hence, we calculated the annual values from the one-minute
+measurements. Despite the very weak statistical significance of the mean
+OIR trend, the annual number of CE occurrences shows a steady increase
+of \(45.6\pm 21.9\,\text{cases}/y\)
+(Figure\nobreakspace{}\ref{fig:P-energy-N}). Subsequently, the mean
+annual energy of the CE events is increasing with a rate of
+\(116.9\pm 67.8\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
+the trend of the number of occurrences. We have to note that the energy
+related to the CE events can not be directly linked with the total
+energy balance of the atmosphere. The net solar radiation of the region
+is not increased, but rather redistributed through the CE events. This
+also is depicted by the ``instantaneous'' values of irradiance (average
+over one minute), that can exceed the equivalent clear sky irradiance to
+a considerable level.
 
@@
 
-Subsequently, the mean annual increase of energy due to CE events is
-\(116.9\pm 67.8\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
-the trend of the number of occurrences.
-
 \begin{figure}
@@
 
-\hypertarget{climatology}{%
-\subsection{Climatology}\label{climatology}}
+\hypertarget{ce-climatology}{%
+\subsection{CE Climatology}\label{ce-climatology}}
 
@@
 box plot (whisker plot), where the values have been normalized by the
-highest median value, that occurs in May. Although the number of
+highest median value, that occurs on June. Although the number of
 occurrences has a wide spread throughout the study period, the most
@@
 Winter (December -- February) the CE cases are about \(25\,\%\) of the
-maximum. The rest of the months the occurrences ramp between the maximum
-and minimum.
+maximum. For the rest months the occurrences gradually ramp between the
+maximum and minimum.
 
@@
 
-\FloatBarrier
-
 \bibliography{bibliography.bib}

### 2024-05-23 article/article.Rmd
Commit 2024-05-23 12:14

@@
 
-We computed the daily trend of the mean OIR of CE <!--
-(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), --> using a first-order autoregressive
-model with a lag of one day, with the 'maximum likelihood' fitting method
-[@Gardner1980; @Jones1980] by implementing the function 'arima' from the library
-'stats' of the R programming language [@RCT2023]. The trends are reported together
-with the $2\sigma$ error.  We observed a negligible change of
+We computed the daily trend of the mean OIR of CE
+<!-- (Figure\nobreakspace{}\ref{fig:CEmeanDaily}), -->
+using a first-order autoregressive
+model with lag of 1 day, with the 'maximum likelihood' fitting method [@Gardner1980;
+@Jones1980] by implementing the function 'arima' from the library 'stats' of the R
+programming language [@RCT2023]. The trends are reported together with the $2\sigma$
+error.  We observe an negligible change of
 $`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
@@
 on the mean OIR.
+
 <!-- ```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."} -->
@@
 <!-- ``` -->
-Although, the previous result is closer to the raw data, we preferred to present the
-annual statistics, that give a more clear picture about the long term CE trends.
-Hence, we calculated the annual values from the one-minute measurements.  Despite the
-very weak statistical significance of the mean OIR trend, the annual number of CE
-occurrences shows a steady increase of
+
+Although, the previous result is closer to the raw data, we preferred to present
+the annual statistics, that give a more clear picture about the long term CE
+trends. Hence, we calculated the annual values from the one-minute measurements.
+Although, the trend of the mean OIR has very weak statistical significance, the
+annual number of CE occurrences, shows a steady increase of
 $`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
@@
 (Figure\nobreakspace{}\ref{fig:P-energy-N}).
-Subsequently, the mean annual energy of the CE events is increasing with a rate of
-$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
-(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
-occurrences.  We have to note that the energy related to the CE events can not be
-directly linked with the total energy balance of the atmosphere. The net solar
-radiation of the region is not increased, but rather redistributed through the CE
-events.  This also is depicted by the "instantaneous" values of irradiance (average
-over one minute), that can exceed the equivalent clear sky irradiance to a
+We have to note that the energy related to the CE events can not be directly
+linked with the total energy balance on the atmosphere. The net solar radiation of
+the region is not increased, but rather redistributed through the CE events. Resulting,
+instantaneous values, that can exceed the equivalent clear sky irradiance to a
 considerable level.
@@
 ```
+
+Subsequently, the mean annual increase of energy due to CE events is
+$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
+`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
+(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
+occurrences.
 

### 2024-05-23 article/article.Rmd
Commit 2024-05-23 16:10

--- 2024-05-23 article/article.Rmd
@@
 `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
-(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
+(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of CE
 occurrences.  We have to note that the energy related to the CE events can not be
@@
 
-Another interesting aspect of the CE cases, is their seasonal cycle. In
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the box plot
+Another interesting aspect of the CE cases occurrences, is their seasonal cycle. In
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have a monthly box plot
 (whisker plot), where the values have been normalized by the highest median value,
@@
 For the rest months the occurrences gradually ramp between the maximum and minimum.
+These seasonality is a combinations of the clouds occurrences, and the relevant
+position of the sun during the year. Unfortunately, the lack of detailed data of cloud
+formation, type and location is not allowing further analysis.
 
@@
 
-The distribution of the CE over irradiance spreads uniformly
-Figure\nobreakspace{}\ref{fig:ovir-distribution}. Where there is an inverse relation
+The distribution of the CE over irradiance intensity follows an exponential decline
+Figure\nobreakspace{}\ref{fig:ovir-distribution}, where there is an inverse relation
 between the events frequency and events intensity. This is expected as, the stronger
-the CE events become, the rarer the particular atmospheric and sun conditions
-occur.
+the CE events become, the rarer the particular atmospheric and sun conditions will
+occur. This is indicative to the magnitude and probability of the expected OIRs
+events over Thessaloniki.
 
-```{r ovir-distribution, echo=FALSE, fig.cap="Distribution of CE over irradiance"}
+```{r ovir-distribution, echo=FALSE, fig.cap="Distribution of CE over irradiance magnitude."}
 knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
@@
 In order to further study the characteristics of the CE events, we grouped the single
-minute CE events, to continuous CE groups (CEG). Thus, a CEG consists of one or more
-successive CE cases, and can have a duration of multiple of minutes.  We have
-identified `r ST_G0[, .N]` groups, where the group with the longest duration lasted
+minute CE events to continuous CE groups (CEG). Thus, a CEG consists of one or more
+successive CE cases, and can represent cloud enhancement conditions spanning a
+duration of multiple minutes.  We have identified `r ST_G0[, .N]` groups, where
+the group with the longest duration lasted
 `r ST_G0[, max(GLB_diff.N)]` minutes on
@@
 By examining the frequency distribution of the CEG durations
-(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can conclude that
-longer durations are getting increasingly rare, with durations above 10 minutes very
-rare.
+(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can conclude, that
+although we detected some CEG with durations longer than an hour, about $80\,\%$ of the CEG have a duration of less than 5 minutes.
 
-```{r ceg-duration-distribution, echo=FALSE, fig.cap="Distribution of CE groups"}
+```{r ceg-duration-distribution, echo=FALSE, fig.cap="Distribution of CE groups duration in minutes."}
 knitr::include_graphics("../images/groups-1.png")

### 2024-05-23 article/article.tex
Commit 2024-05-23 16:10

@@
 \(116.9\pm 67.8\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
-the trend of the number of occurrences. We have to note that the energy
-related to the CE events can not be directly linked with the total
-energy balance of the atmosphere. The net solar radiation of the region
-is not increased, but rather redistributed through the CE events. This
-also is depicted by the ``instantaneous'' values of irradiance (average
-over one minute), that can exceed the equivalent clear sky irradiance to
-a considerable level.
+the trend of the number of CE occurrences. We have to note that the
+energy related to the CE events can not be directly linked with the
+total energy balance of the atmosphere. The net solar radiation of the
+region is not increased, but rather redistributed through the CE events.
+This also is depicted by the ``instantaneous'' values of irradiance
+(average over one minute), that can exceed the equivalent clear sky
+irradiance to a considerable level.
 
@@
 
-Another interesting aspect of the CE cases, is their seasonal cycle. In
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the
-box plot (whisker plot), where the values have been normalized by the
-highest median value, that occurs on June. Although the number of
+Another interesting aspect of the CE cases occurrences, is their
+seasonal cycle. In
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have a
+monthly box plot (whisker plot), where the values have been normalized
+by the highest median value, that occurs on June. Although the number of
 occurrences has a wide spread throughout the study period, the most
@@
 maximum. For the rest months the occurrences gradually ramp between the
-maximum and minimum.
+maximum and minimum. These seasonality is a combinations of the clouds
+occurrences, and the relevant position of the sun during the year.
+Unfortunately, the lack of detailed data of cloud formation, type and
+location is not allowing further analysis.
 
@@
 
-The distribution of the CE over irradiance spreads uniformly
-Figure\nobreakspace{}\ref{fig:ovir-distribution}. Where there is an
-inverse relation between the events frequency and events intensity. This
-is expected as, the stronger the CE events become, the rarer the
-particular atmospheric and sun conditions occur.
+The distribution of the CE over irradiance intensity follows an
+exponential decline Figure\nobreakspace{}\ref{fig:ovir-distribution},
+where there is an inverse relation between the events frequency and
+events intensity. This is expected as, the stronger the CE events
+become, the rarer the particular atmospheric and sun conditions will
+occur. This is indicative to the magnitude and probability of the
+expected OIRs events over Thessaloniki.
 
@@
 
-\caption{Distribution of CE over irradiance}\label{fig:ovir-distribution}
+\caption{Distribution of CE over irradiance magnitude.}\label{fig:ovir-distribution}
 \end{figure}
@@
 In order to further study the characteristics of the CE events, we
-grouped the single minute CE events, to continuous CE groups (CEG).
-Thus, a CEG consists of one or more successive CE cases, and can have a
-duration of multiple of minutes. We have identified 28468 groups, where
-the group with the longest duration lasted 140 minutes on 07~July 2013.
-By examining the frequency distribution of the CEG durations
+grouped the single minute CE events to continuous CE groups (CEG). Thus,
+a CEG consists of one or more successive CE cases, and can represent
+cloud enhancement conditions spanning a duration of multiple minutes. We
+have identified 28468 groups, where the group with the longest duration
+lasted 140 minutes on 07~July 2013. By examining the frequency
+distribution of the CEG durations
 (Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can
-conclude that longer durations are getting increasingly rare, with
-durations above 10 minutes very rare.
+conclude, that although we detected some CEG with durations longer than
+an hour, about \(80\,\%\) of the CEG have a duration of less than 5
+minutes.
 
@@
 
-\caption{Distribution of CE groups}\label{fig:ceg-duration-distribution}
+\caption{Distribution of CE groups duration in minutes.}\label{fig:ceg-duration-distribution}
 \end{figure}

### 2024-05-23 article/article.tex
Commit 2024-05-23 19:10

@@
 
-\caption{Statistics of the number of CE occurancies for each month.
+\caption{Seasonal statistics of the number of CE occurancies for each month, normalized to the maximum occurancies on June.
 The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies}
@@
 
-\ldots{} \citet{Zhang2018} \ldots.
+The relation between the duration and the mean OIR intensity of the
+groups have been studied (Figure\nobreakspace{}\ref{fig:group-2d}). We
+observe that the GCE events tend to have either long duration, or large
+intensity, events with strong enhancement and long duration are very
+rare. A similar result on this relation, have been also reported by
+\citet{Zhang2018}, on a study using a far higher sampling rate than
+ours.
 
@@
 
-\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-3}
+\caption{Relation of mean over irradiance and CE group duration}\label{fig:group-2d}
 \end{figure}
@@
 
-Another aspect of the CE events are the cases when the irradiance is
-above the expected irradiance on top of the atmosphere, we have defined
-this as ECE (Equation\nobreakspace{}\ref{eq:ECE}).
+A characteristic of the CE events that is commonly reported and has some
+significance on the solar energy production infrastructure are the
+extreme CE events (ECE). Where solar irradiance exceeds the expected
+irradiance on top of the atmosphere, we have defined this as ECE
+(Equation\nobreakspace{}\ref{eq:ECE}).
 
@@
 Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the
-most active period is in the spring (March -- May), followed by the
-months of June, September and October.
+most active period is in the spring and the start of the summer (March
+-- June), followed by the late fall (Septemcer and October).
 
@@
 
-\caption{Distribution of }\label{fig:relative-month-occurancies-ECE}
+\caption{Seasonal statistics of the number of ECE occurancies for each month, normalized to the maximum occurancies on March.
+The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies-ECE}
 \end{figure}
@@
 
-\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-4}
+\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-3}
 \end{figure}

### 2024-05-23 article/article.Rmd
Commit 2024-05-23 19:10

@@
 
-```{r relative-month-occurancies, echo=FALSE, fig.cap="Statistics of the number of CE occurancies for each month.
+```{r relative-month-occurancies, echo=FALSE, fig.cap="Seasonal statistics of the number of CE occurancies for each month, normalized to the maximum occurancies on June.
 The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
@@
 successive CE cases, and can represent cloud enhancement conditions spanning a
-duration of multiple minutes.  We have identified `r ST_G0[, .N]` groups, where
-the group with the longest duration lasted
+duration of multiple minutes.  We have identified `r ST_G0[, .N]` groups, where the
+group with the longest duration lasted
 `r ST_G0[, max(GLB_diff.N)]` minutes on
@@
 (Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can conclude, that
-although we detected some CEG with durations longer than an hour, about $80\,\%$ of the CEG have a duration of less than 5 minutes.
+although we detected some CEG with durations longer than an hour, about $80\,\%$ of
+the CEG have a duration of less than 5 minutes.
 
@@
 
-... @Zhang2018 ....
+The relation between the duration and the mean OIR intensity of the groups have been
+studied (Figure\nobreakspace{}\ref{fig:group-2d}). We observe that the GCE events
+tend to have either long duration, or large intensity, events with strong enhancement
+and long duration are very rare. A similar result on this relation, have been also
+reported by @Zhang2018, on a study using a far higher sampling rate than ours.
 
-```{r echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"}
+```{r group-2d, echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"}
 knitr::include_graphics("../images/P-groups-bin2d-1.png")
@@
 
-Another aspect of the CE events are the cases when the irradiance is above the
-expected irradiance on top of the atmosphere, we have defined this as ECE
-(Equation\nobreakspace{}\ref{eq:ECE}).
+A characteristic of the CE events that is commonly reported and has some significance
+on the solar energy production infrastructure are the extreme CE events (ECE). Where
+solar irradiance exceeds the expected irradiance on top of the atmosphere, we have
+defined this as ECE (Equation\nobreakspace{}\ref{eq:ECE}).
 
@@
 Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the most active
-period is in the spring (March -- May), followed by the months of June, September and
-October.
+period is in the spring and the start of the summer (March -- June), followed by the
+late fall (Septemcer and October).
 
@@
 
-```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Distribution of "}
+```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal statistics of the number of ECE occurancies for each month, normalized to the maximum occurancies on March.
+The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
 knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")
@@
 # Discussion and conclusions
+
+Created a clear sky approximation and a long term change representation for a period of 30 years.
+
+Identify CE events and found a trend on .....
+The climatology of CE occurrences over the whole period and
+the magnitude of the CE events.
+We estabished the occurances of extreme CE events ...
 

### 2024-05-23 article/article.tex
Commit 2024-05-23 20:08

@@
 
+Created a clear sky approximation and a long term change representation
+for a period of 30 years.
+
+Identify CE events and found a trend on \ldots.. The climatology of CE
+occurrences over the whole period and the magnitude of the CE events. We
+estabished the occurances of extreme CE events \ldots{} The
+characteristic of the duration of ``continuous'' CE events. with their
+magnitude occurnacies and climatology
+
+Our find have similarities with other mediterranean / europe sites.
+
+The interaction of GHI with the clouds through this period shows a
+systematic change.
+
 Compare to other location stats. max, ECE, distributions \ldots.

### 2024-05-24 article/article.Rmd
Commit 2024-05-23 20:08
Commit 2024-05-24 11:10

@@
 
--  max value ECE
-  relative to other works max values
+<!-- -  max value ECE -->
+<!--   relative to other works max values -->
 
@@
 computed the distribution of the number of occurrences of ECE events by month in
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the most active
-period is in the spring and the start of the summer (March -- June), followed by the
-late fall (Septemcer and October).
-
-.......
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. The most active period
+for ECE events is in the spring and the start of the summer (March -- June), followed
+by a period in the late fall (September and October).  This is probably an effect of
+the weather characteristics of those periods where, there are continuous alternations
+between clear sky periods and clouds.
 
@@
 
-```{r echo=FALSE, fig.cap="Distribution of ECE above 'clear sky' reference"}
-knitr::include_graphics("../images/extremedistributions-2.png")
+```{r echo=FALSE, fig.cap="Distribution of ECE above clear sky threshold."}
+knitr::include_graphics("../images/P-extreme-distribution-1.png")
 ```
@@
 
--   SZA
+<!-- -   SZA -->
 
@@
 
-Created a clear sky approximation and a long term change representation for a period of 30 years.
+By creating a clear sky approximation of the GHI, which can represent the long- and
+short-term variation of the expected clear sky GHI, we were able to identify cases of 
+CE events.
+By analysing the CE cases we found
 
-Identify CE events and found a trend on .....
 The climatology of CE occurrences over the whole period and
+
 the magnitude of the CE events.
 We estabished the occurances of extreme CE events ...
+The characteristic of the duration of "continuous" CE events.
+with their magnitude occurnacies and climatology
+
+Our find have similarities with other mediterranean / europe sites.
+
+The interaction of GHI with the clouds through this period shows a systematic change.
 

### 2024-05-24 article/article.tex
Commit 2024-05-24 11:10

@@
 
-\begin{itemize}
-\tightlist
-\item
-  max value ECE relative to other works max values
-\end{itemize}
-
 Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies}
@@
 events by month in
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the
-most active period is in the spring and the start of the summer (March
--- June), followed by the late fall (Septemcer and October).
-
-\ldots\ldots.
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. The most
+active period for ECE events is in the spring and the start of the
+summer (March -- June), followed by a period in the late fall (September
+and October). This is probably an effect of the weather characteristics
+of those periods where, there are continuous alternations between clear
+sky periods and clouds.
 
@@
 
-{\centering \includegraphics[width=0.5\linewidth]{../images/extremedistributions-2}
+{\centering \includegraphics[width=0.5\linewidth]{../images/P-extreme-distribution-1}
 
@@
 
-\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-3}
+\caption{Distribution of ECE above clear sky threshold.}\label{fig:unnamed-chunk-3}
 \end{figure}
-
-\begin{itemize}
-\tightlist
-\item
-  SZA
-\end{itemize}
 
@@
 
-Created a clear sky approximation and a long term change representation
-for a period of 30 years.
+By creating a clear sky approximation of the GHI, which can represent
+the long- and short-term variation of the expected clear sky GHI, we
+were able to identify cases of CE events. By analysing the CE cases we
+found
 
-Identify CE events and found a trend on \ldots.. The climatology of CE
-occurrences over the whole period and the magnitude of the CE events. We
-estabished the occurances of extreme CE events \ldots{} The
-characteristic of the duration of ``continuous'' CE events. with their
-magnitude occurnacies and climatology
+The climatology of CE occurrences over the whole period and
+
+the magnitude of the CE events. We estabished the occurances of extreme
+CE events \ldots{} The characteristic of the duration of ``continuous''
+CE events. with their magnitude occurnacies and climatology
 

### 2024-05-24 article/article.tex
Commit 2024-05-24 12:16

@@
 OIR trend, the annual number of CE occurrences shows a steady increase
-of \(45.6\pm 21.9\,\text{cases}/y\)
+of \(45.6\pm 21.9\,\text{cases}/\text{year}\)
 (Figure\nobreakspace{}\ref{fig:P-energy-N}). Subsequently, the mean
 annual energy of the CE events is increasing with a rate of
-\(116.9\pm 67.8\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
-the trend of the number of CE occurrences. We have to note that the
-energy related to the CE events can not be directly linked with the
-total energy balance of the atmosphere. The net solar radiation of the
-region is not increased, but rather redistributed through the CE events.
-This also is depicted by the ``instantaneous'' values of irradiance
-(average over one minute), that can exceed the equivalent clear sky
-irradiance to a considerable level.
+\(116.9\pm 67.8\,\text{kj}/\text{year}\)
+(Figure~\ref{fig:P-energy-sum}), witch follows the trend of the number
+of CE occurrences. We have to note that the energy related to the CE
+events can not be directly linked with the total energy balance of the
+atmosphere. The net solar radiation of the region is not increased, but
+rather redistributed through the CE events. This also is depicted by the
+``instantaneous'' values of irradiance (average over one minute), that
+can exceed the equivalent clear sky irradiance to a considerable level.
 
@@
 the long- and short-term variation of the expected clear sky GHI, we
-were able to identify cases of CE events. By analysing the CE cases we
-found
+were able to identify cases of CE events. By analyzing the CE cases we
+found an increase of \(45.6\pm 21.9\,\text{cases}/\text{year}\), with
+the mean annual total energy of the CE events increasing with a rate of
+\(116.9\pm 67.8\,\text{kj}/\text{year}\). The most active season of CE
+events over Thessaloniki is concentrated on early summer, on May and
+June.
 
-The climatology of CE occurrences over the whole period and
+The magnitude of the ECE events doesn't exceeds the values reported from
+sites with more favorable conditions for the phenomenon. Although, the
+climatological characteristic of the ECE events, showed that the most
+active months are spread on half of the year (March -- June and
+September and October).
 
-the magnitude of the CE events. We estabished the occurances of extreme
-CE events \ldots{} The characteristic of the duration of ``continuous''
-CE events. with their magnitude occurnacies and climatology
+We find that CE conditions can have a duration of more than an hour in
+rare cases, with the bulk of the cases having a duration under 5
+minutes.
 
@@
 
-The interaction of GHI with the clouds through this period shows a
-systematic change.
+An interpretation of CE trends, shows that the interaction of GHI with
+the clouds through this 30 year period, is a dynamic phenomenon that's
+needs further investigation. Although, to approach it, we need more long
+term observations of AOD and clouds characteristics.
 
 Compare to other location stats. max, ECE, distributions \ldots.
-
-Climatology results
 

### 2024-05-24 article/article.Rmd
Commit 2024-05-24 12:16

@@
 $`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/y$
+`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$
 (Figure\nobreakspace{}\ref{fig:P-energy-N}).
@@
 $`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
+`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kj}/\text{year}$
 (Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of CE
@@
 CE events.
-By analysing the CE cases we found
+By analyzing the CE cases we found an increase of 
+$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
+`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$,
+with the
+mean annual total energy of the CE events increasing with a rate of
+$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
+`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kj}/\text{year}$.
+The most active season of CE events over Thessaloniki is concentrated on early
+summer, on May and June.
 
-The climatology of CE occurrences over the whole period and
+The magnitude of the ECE events doesn't exceeds the values reported from sites with
+more favorable conditions for the phenomenon. Although, the climatological
+characteristic of the ECE events, showed that the most active months are spread on
+half of the year (March -- June and September and October).
 
-the magnitude of the CE events.
-We estabished the occurances of extreme CE events ...
-The characteristic of the duration of "continuous" CE events.
-with their magnitude occurnacies and climatology
+We find that CE conditions can have a duration of more than an hour in rare
+cases, with the bulk of the cases having a duration under 5 minutes.
 
@@
 
-The interaction of GHI with the clouds through this period shows a systematic change.
+An interpretation of CE trends, shows that the interaction of GHI with the clouds
+through this 30 year period, is a dynamic phenomenon that's needs further investigation.
+Although, to approach it, we need more long term observations of AOD and clouds
+characteristics.
 
@@
 max, ECE, distributions ....
-
-Climatology results
 

### 2024-05-26 article/article.Rmd
Commit 2024-05-26 16:14

@@
   - code:         LAP
-    organization: Laboratory of Atmospheric Physics, A.U.Th.
-    addressline:  1 main street
+    organization: Laboratory of Atmospheric Physics, Physics Department, Aristotle University of Thessaloniki
+    # addressline:  1 main street
     city:         Thessaloniki
-    postcode:     123456
+    postcode:     54124
     country:      Greece
@@
 keywords: 
-  - keyword1
-  - keyword2
+  - cloud enhancement
+  - total solar radiation
+  - global horizonta irradiance
+  - over irradiance
 
@@
 $`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
-`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2/y$
+`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,\text{W}/\text{m}^2/\text{year}$
 on the mean OIR.
@@
 the CE events become, the rarer the particular atmospheric and sun conditions will
-occur. This is indicative to the magnitude and probability of the expected OIRs
-events over Thessaloniki.
+occur. This fact is indicative to the magnitude and probability of the expected OIRs
+events over Thessaloniki. Similar distribution of CE occurrences have been reported
+by @Vamvakas2020, where the magnitude of OIR is 
+higher due to the location of the the city of Patras, $2.5^\circ$ closer to the equator.
 
@@
 
-```{r echo=FALSE, fig.cap="Distribution of ECE above clear sky threshold."}
+The distribution of the ECE events (Figure\nobreakspace{}\ref{fig:P-extreme-distribution}), shows that there are rare cases where the OIR can exceed the 
+TSI even more than $400\,\text{W}/\text{m}^2$, with the $75\,\%$ of the cases to be below $200\,\text{W}/\text{m}^2$. Similar to CE cases, the  distribution of ECE have a similar pattern
+with the results of @Vamvakas2020, with the difference that the OIR values are lower fro Thessaloniki.
+
+```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE above clear sky threshold, for cases that are exceeding the TSI."}
 knitr::include_graphics("../images/P-extreme-distribution-1.png")
@@
 The magnitude of the ECE events doesn't exceeds the values reported from sites with
-more favorable conditions for the phenomenon. Although, the climatological
+more favourable conditions for the phenomenon. Although, the climatological
 characteristic of the ECE events, showed that the most active months are spread on
 half of the year (March -- June and September and October).
-
-We find that CE conditions can have a duration of more than an hour in rare
+We found that CE conditions, can have a duration of more than an hour in rare
 cases, with the bulk of the cases having a duration under 5 minutes.
-
-Our find have similarities with other mediterranean / europe sites.
+Some of the characteristics of CE and ECE events we analysed,
+have strong similarities with results
+by @Vamvakas2020, for a city southern of Thessaloniki, with analogues differences, due to the 
+ higher intensity of the solar radiation.
 
@@
 characteristics.
-
-Compare to other location stats.
-max, ECE, distributions ....
 

### 2024-05-26 article/article.tex
Commit 2024-05-26 16:14

@@
       \affiliation[LAP]{
-    organization={Laboratory of Atmospheric Physics,
-A.U.Th.},addressline={1 main
-street},city={Thessaloniki},postcode={123456},country={Greece},}
+    organization={Laboratory of Atmospheric Physics, Physics Department,
+Aristotle University of
+Thessaloniki},city={Thessaloniki},postcode={54124},country={Greece},}
     \affiliation[Another University]{
@@
     \begin{keyword}
-    keyword1 \sep 
-    keyword2
+    cloud enhancement \sep total solar radiation \sep global horizonta
+irradiance \sep 
+    over irradiance
   \end{keyword}
@@
 with the \(2\sigma\) error. We observed a negligible change of
-\(0.087\pm 0.08\,W/m^2/y\) on the mean OIR. Although, the previous
-result is closer to the raw data, we preferred to present the annual
-statistics, that give a more clear picture about the long term CE
-trends. Hence, we calculated the annual values from the one-minute
-measurements. Despite the very weak statistical significance of the mean
-OIR trend, the annual number of CE occurrences shows a steady increase
-of \(45.6\pm 21.9\,\text{cases}/\text{year}\)
+\(0.087\pm 0.08\,\text{W}/\text{m}^2/\text{year}\) on the mean OIR.
+Although, the previous result is closer to the raw data, we preferred to
+present the annual statistics, that give a more clear picture about the
+long term CE trends. Hence, we calculated the annual values from the
+one-minute measurements. Despite the very weak statistical significance
+of the mean OIR trend, the annual number of CE occurrences shows a
+steady increase of \(45.6\pm 21.9\,\text{cases}/\text{year}\)
 (Figure\nobreakspace{}\ref{fig:P-energy-N}). Subsequently, the mean
@@
 become, the rarer the particular atmospheric and sun conditions will
-occur. This is indicative to the magnitude and probability of the
-expected OIRs events over Thessaloniki.
+occur. This fact is indicative to the magnitude and probability of the
+expected OIRs events over Thessaloniki. Similar distribution of CE
+occurrences have been reported by \citet{Vamvakas2020}, where the
+magnitude of OIR is higher due to the location of the the city of
+Patras, \(2.5^\circ\) closer to the equator.
 
@@
 
+The distribution of the ECE events
+(Figure\nobreakspace{}\ref{fig:P-extreme-distribution}), shows that
+there are rare cases where the OIR can exceed the TSI even more than
+\(400\,\text{W}/\text{m}^2\), with the \(75\,\%\) of the cases to be
+below \(200\,\text{W}/\text{m}^2\). Similar to CE cases, the
+distribution of ECE have a similar pattern with the results of
+\citet{Vamvakas2020}, with the difference that the OIR values are lower
+fro Thessaloniki.
+
 \begin{figure}
@@
 
-\caption{Distribution of ECE above clear sky threshold.}\label{fig:unnamed-chunk-3}
+\caption{Distribution of ECE above clear sky threshold, for cases that are exceeding the TSI.}\label{fig:P-extreme-distribution}
 \end{figure}
@@
 The magnitude of the ECE events doesn't exceeds the values reported from
-sites with more favorable conditions for the phenomenon. Although, the
+sites with more favourable conditions for the phenomenon. Although, the
 climatological characteristic of the ECE events, showed that the most
 active months are spread on half of the year (March -- June and
-September and October).
-
-We find that CE conditions can have a duration of more than an hour in
-rare cases, with the bulk of the cases having a duration under 5
-minutes.
-
-Our find have similarities with other mediterranean / europe sites.
+September and October). We found that CE conditions, can have a duration
+of more than an hour in rare cases, with the bulk of the cases having a
+duration under 5 minutes. Some of the characteristics of CE and ECE
+events we analysed, have strong similarities with results by
+\citet{Vamvakas2020}, for a city southern of Thessaloniki, with
+analogues differences, due to the higher intensity of the solar
+radiation.
 
@@
 term observations of AOD and clouds characteristics.
-
-Compare to other location stats. max, ECE, distributions \ldots.
 

### 2024-05-26 article/article.Rmd
Commit 2024-05-26 22:14

@@
 ---
-title: Downward shortwave solar irradiance enhancement by clouds.
+title: Long term cloud enhancement events of global solar irradiance over Thessaloniki
 
@@
 
+```{r loadtrends, echo=F, include=T, warning=FALSE, message=FALSE}
+dailytrends <- data.table(
+  read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear.csv"))
+dailyCE <- dailytrends[DATA == "ST_E_daily"]
+yearlytrends <- data.table(
+  read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear_Proper.csv"))
+yearlyCE <- yearlytrends[DATA == "ST_E_yearly"]
+
+```
+
 # Abstract {.unnumbered}
 
-- Phenomenon
-- Effects
-- bibliography
-- our approach
-- our results
+We studied the enhancement of the global horizontal irradiance (GHI), over Thessaloniki, 
+for the period 1993 -- 2023, on one minute average records.
+We identify the cloud enhancement events (CE), by creating an appropriate clear sky
+irradiance reference with the use of a radiation transfer model, and aerosol optical 
+depth (AOD) data, from the AERONET, and a collocated Brewer photospectrometer.
+We found that there is a trend of CE cases of
+$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
+`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$,
+and a
+mean total energy change, of the CE events by
+$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
+`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kj}/\text{year}$
+with the peak of the CE events are observed during May and June.
+An analysis of the total duration of CE events, showed that durations longer than 
+5 minutes are very rare, with exceptions lasting over an hour.
+We have detected enhancements over the total solar irradiance, without exceeding the
+maximum values reported for other sites, with more favorable CE conditions.
 
+\  
+\  
 CE: cloud enhancement cases one minute
@@
 
-$\text{GHI}_\text{CSm}$: modeled clear sky one minute global horizontal irradiance
+$\text{GHI}_\text{CSm}$: modelled clear sky one minute global horizontal irradiance
 
@@
 The shortwave solar irradiance, reaching Earth's surface, is the main energy source
-of the atmosphere and biosphere and drives and governs the climate [@Gray2010].  It
-has direct practical application, in different industries, like energy production and
-agriculture method.  The variability of its intensity, can cause difficulties in
+of the atmosphere and the biosphere, and drives and governs the climate [@Gray2010].  It
+has direct practical application, in industries like energy and
+agricultural production. The variability of its intensity, can cause difficulties in
 predicting the yield, and designing the specifications of the appropriate equipment.
-A lot of research has been focused on predicting the renewable energy production in a
+Significant portion of research has been focused on predicting the renewable energy production in a
 fine timescale and in near real-time (for a review see @Inman2013; @Graabak2016).
 
-A big aspect of this variability is the interaction with the clouds. In general,
+A big aspect of this variability is the interaction of GHI with the clouds. In general,
 clouds absorb part of the solar irradiance, but under certain conditions, can enhance
 the total shortwave irradiance reaching the ground. This effect, can locally increase
-the observed total shortwave irradiance higher than the expected clear sky irradiance
+the observed GHI, even higher than the expected clear sky irradiance
 [see references therein].
@@
 
-```{r loadtrends, echo=F, include=T, warning=FALSE, message=FALSE}
-dailytrends <- data.table(
-  read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear.csv"))
-dailyCE <- dailytrends[DATA == "ST_E_daily"]
-yearlytrends <- data.table(
-  read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear_Proper.csv"))
-yearlyCE <- yearlytrends[DATA == "ST_E_yearly"]
-
-```
-
 We computed the daily trend of the mean OIR of CE <!--

### 2024-05-26 article/article.tex
Commit 2024-05-26 22:14

@@
             pdfauthor={},
-            pdftitle={Downward shortwave solar irradiance enhancement by clouds.},
+            pdftitle={Long term cloud enhancement events of global solar irradiance over Thessaloniki},
             colorlinks=false,
@@
 
-  \title{Downward shortwave solar irradiance enhancement by clouds.}
+  \title{Long term cloud enhancement events of global solar irradiance
+over Thessaloniki}
     \author[LAP]{Athanasios N. Natsis%
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Phenomenon
-\item
-  Effects
-\item
-  bibliography
-\item
-  our approach
-\item
-  our results
-\end{itemize}
+We studied the enhancement of the global horizontal irradiance (GHI),
+over Thessaloniki, for the period 1993 -- 2023, on one minute average
+records. We identify the cloud enhancement events (CE), by creating an
+appropriate clear sky irradiance reference with the use of a radiation
+transfer model, and aerosol optical depth (AOD) data, from the AERONET,
+and a collocated Brewer photospectrometer. We found that there is a
+trend of CE cases of \(45.6\pm 21.9\,\text{cases}/\text{year}\), and a
+mean total energy change, of the CE events by
+\(116.9\pm 67.8\,\text{kj}/\text{year}\) with the peak of the CE events
+are observed during May and June. An analysis of the total duration of
+CE events, showed that durations longer than 5 minutes are very rare,
+with exceptions lasting over an hour. We have detected enhancements over
+the total solar irradiance, without exceeding the maximum values
+reported for other sites, with more favorable CE conditions.
 
-CE: cloud enhancement cases one minute
+~ ~ CE: cloud enhancement cases one minute
 
@@
 
-\(\text{GHI}_\text{CSm}\): modeled clear sky one minute global
+\(\text{GHI}_\text{CSm}\): modelled clear sky one minute global
 horizontal irradiance
@@
 The shortwave solar irradiance, reaching Earth's surface, is the main
-energy source of the atmosphere and biosphere and drives and governs the
-climate \citep{Gray2010}. It has direct practical application, in
-different industries, like energy production and agriculture method. The
+energy source of the atmosphere and the biosphere, and drives and
+governs the climate \citep{Gray2010}. It has direct practical
+application, in industries like energy and agricultural production. The
 variability of its intensity, can cause difficulties in predicting the
-yield, and designing the specifications of the appropriate equipment. A
-lot of research has been focused on predicting the renewable energy
-production in a fine timescale and in near real-time (for a review see
-\citet{Inman2013}; \citet{Graabak2016}).
+yield, and designing the specifications of the appropriate equipment.
+Significant portion of research has been focused on predicting the
+renewable energy production in a fine timescale and in near real-time
+(for a review see \citet{Inman2013}; \citet{Graabak2016}).
 
-A big aspect of this variability is the interaction with the clouds. In
-general, clouds absorb part of the solar irradiance, but under certain
-conditions, can enhance the total shortwave irradiance reaching the
-ground. This effect, can locally increase the observed total shortwave
-irradiance higher than the expected clear sky irradiance {[}see
-references therein{]}.
+A big aspect of this variability is the interaction of GHI with the
+clouds. In general, clouds absorb part of the solar irradiance, but
+under certain conditions, can enhance the total shortwave irradiance
+reaching the ground. This effect, can locally increase the observed GHI,
+even higher than the expected clear sky irradiance {[}see references
+therein{]}.
 

### 2024-05-26 Article_B5/Article_B5.Rmd
Commit 2024-05-27 00:14

--- 2024-05-26 article/article.Rmd
@@
     affiliation: LAP
-    footnote: 2
+    footnote: 1
 address:
@@
     country:      Greece
-  - code:         Another University
-    organization: Department
-    addressline:  A street 29
-    postcode:     2054 NX
-    city:         Manchester,
-    state:        State
-    country:      The Netherlands
+  # - code:         Another University
+  #   organization: Department
+  #   addressline:  A street 29
+  #   postcode:     2054 NX
+  #   city:         Manchester,
+  #   state:        State
+  #   country:      The Netherlands
 footnote:
@@
 abstract: |
-  Here wii be the abstract.
-
-  It consists of two paragraphs.
+  Here will be the abstract.
 
@@
   - total solar radiation
-  - global horizonta irradiance
+  - global horizontal irradiance
   - over irradiance
@@
 
-Some of the proposed underling mechanisms of those events, have been summarized by
-@Gueymard2017, and include scattering on the edge of cumulus clouds or through thin
-cirrus.  Further investigation with radiation transfer modeling methods and
+Some of the proposed underling mechanisms of those enhancements, have been summarized
+by @Gueymard2017, and include scattering on the edge of cumulus clouds or through
+thin cirrus.  Further investigation with radiation transfer modeling methods and
 observations have pointed as the prevailing mechanism, the forward Mie scattering
 [@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015], through the clouds.
-The overall phenomenon depends on different interactive factors, that include cloud
-thickness, constitution and type; and the relative position of the sun, the clouds,
-and the observer [@Gueymard2017; @Veerman2022].  As such, there are multiple
-contributing mechanism that are responsible for the observed irradiance enhancements.
+The overall phenomenon depends on different interactive factors, which includes cloud
+thickness, constitution and type; and the relative position of the sun and the clouds
+[@Gueymard2017; @Veerman2022].  As such, there are multiple contributing mechanisms
+that are responsible for the observed irradiance enhancements.
 
-Cloud enhancements have been reported, to be able to exceed in intensity even the
+On multiple sites, cloud enhancements have been reported, to be able to briefly exceed the
 value of the solar constant, resulting of clear indexes above unit. A summary of
-extreme enchantment cases have been compiled by @Martins2022. There are also some
+extreme enchantment cases (ECE) have been compiled by @Martins2022. There are also, some
 practical implication of the cloud enchantments.  The intensity and duration of
@@
 -->
-
 <!--
@@
 <!-- our work -->
-In this study, we evaluated the effects cloud enhancements on the total downward
-radiation by studding the occurrences, their intensity, and their duration in a
+In this study, we evaluated the effects CE on the GHI by studding the occurrences, their intensity, and their duration in a
 thirty-year period at the city of Thessaloniki.  We used modeled clear sky
@@
 characteristics. We weren't able to find a comparable study that provides trends for
-similar long term dataset, as ours.  The recording of the radiation signal is the
-mean of one-minute. Thus, the minimum resolution of cloud enhancement events (CE), in
+similar long term dataset, as ours.  The recording of the GHI signal is the
+mean of one-minute. Thus, the minimum resolution of CE events, in
 this study is one minute.
@@
 In the relative bibliography different definition have been used for these events,
-some of the are summarized by @Gueymard2017.  Here, we defined as cloud enhancement
-events (CE) the cases when the measured global horizontal irradiance (GHI) at ground
+some of the are summarized by @Gueymard2017.  Here, we defined as CE
+events, the cases when the measured GHI at ground
 level, exceeds the expected value under clear-sky conditions.  Similar, we define as
 extreme cloud enhancement events (ECE), the cases when GHI, exceeds the Total Solar
-Irradiance on horizontal plane at ground level.  Although the duration of these
+Irradiance (TSI) on horizontal plane at ground level.  Although the duration of these
 bursts varies, from instantaneous to several minutes, here we are constrained by the
@@
 To further improve the quality of the irradiance data, a manual screening was
-performed to remove inconsistent and erroneous recordings that can occur
-stochastically or systematically during the continuous operation of the instruments.
+performed, in order to remove inconsistent and erroneous recordings that can occur
+stochastically or systematically during the long operation of the instrument.
 The manual screening was aided by a radiation data quality assurance procedure,
@@
 the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there must
-exist at least 45 minutes of valid measurements, including nighttime near sunrise and
-sunset. Days with less than 5 valid hours are rejected completely.
+exist at least 45 minutes of valid measurements, including nighttime, when near sunrise and
+sunset. Days with less than 5 valid hours were rejected completely.
 <!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7),
@@
 otherwise all minute data for this hour is flagged as invalid. -->
-Furthermore, due to the significant measurement uncertainty when the Sun is near the
+Furthermore, due to the significant measurement uncertainty, when the Sun is near the
 horizon, and due to some systematic obstructions by nearby buildings, we have
@@
 
-To be able to detect the CE cases, we had to establish a baseline, above which we can
-characterize each data point as an enhancement event, by estimating the occurring
-over irradiance (OIR). The OIR, here is defined as the irradiance difference of the
-measured one-minute $\text{GHI}_i$ from the CE identification criterion in
-Equation\nobreakspace\ref{eq:CE4}
-($\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}$).
-To have an estimation, and a first insight on the phenomenon, we experimented with two
-simple approaches for the reference.  The Haurwitz's model [@Haurwitz1945], which is
-as simple clear sky model, and we had already adjusted and had good fit with our data
-[@Natsis2023], and the TSI at the top of the atmosphere.  We have tested both cases
-by using an appropriate relative threshold and/or an additional constant offset.  The
-initial results, showed that we can detect a big portion of the CE events. These
-results were helpful, and helped to establish some criteria to further improve the CE
-identification. It was evident, by inspecting the daily plot of irradiance, that
-changes on the atmospheric conditions introduced numerous false positive and false
-negative results.  To produce a more accurate reference, we had to take into account
-more factors that effect the clear sky radiation. So we used a radiation transfer
-model.
+To be able to detect the CE cases, we had to establish a baseline, above which we 
+characterized each data point as an enhancement event, by estimating the occurring
+over irradiance (OIR). The OIR, is defined as the irradiance difference of the
+measured one-minute $\text{GHI}_i$ from the CE identification criterion
+($\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}$), as defined in
+Equation\nobreakspace\ref{eq:CE4}.
+To have an estimation, and a first insight on the phenomenon, we experimented with
+two simple approaches for the reference.  The Haurwitz's model [@Haurwitz1945], which
+is as simple clear sky model, and we had already adjusted and had good fit with our
+data [@Natsis2023], and the TSI at the top of the atmosphere.  We have tested both
+cases by using an appropriate relative threshold and/or an additional constant
+offset.  The initial results, showed that we can detect a big portion of the CE
+events. These results were helpful, as they are independent from unknown factors, and
+helped us to establish some criteria to further improve the CE identification. It was
+evident, by inspecting the daily plot of irradiance, that changes on the atmospheric
+conditions introduced numerous false positive and false negative results.  To produce
+a more accurate reference, we had to take into account more factors that effect the
+clear sky radiation. So we used a radiation transfer
+model in order to include the effects of ADO and the water vapors.
 
@@
 
-We approximated the expected clear sky GHI by using a radiation transfer model.  The
-simulations was performed by the well established model Libradtran [@Emde2016], a
-similar approach, was also used by @Vamvakas2020 for creating a clear sky reference.
-Because of the lack of observational data for the whole period, we used some long
-term climatological data for the main factors responsible for the attenuation of the
-broadband downward solar radiation in the atmosphere. Which are mainly, the aerosols
-and the water vapors.  Fortunately, our site participates in the Aerosol Robotic
-Network (AERONET) [@Giles2019; @Buis1998], as we operate a Cimel photometer since
-2003, collocated with the CM-21 pyranometer.  The mean monthly aerosol optical depth
-(AOD) on different wavelengths is provided by AERONET, along with the equivalent
-water column height in the atmosphere.
+We approximated the expected clear sky GHI by using the Libradtran radiation transfer
+model [@Emde2016], a similar approach, was also used by @Vamvakas2020 for creating a
+clear sky reference for studding cloud enhancement events.  Main factors responsible
+for the attenuation of the broadband downward solar radiation in the atmosphere are
+the aerosols and the water vapors.  Because of the lack of observational data for the
+whole period, we used some long term climatological data to recreate the whole
+period.  Fortunately, our site participates in the Aerosol Robotic Network (AERONET)
+[@Giles2019; @Buis1998], as there is in operation a Cimel photometer since 2003,
+collocated with the CM-21 pyranometer.  The mean monthly AOD on different wavelengths
+are provided by AERONET, along with the equivalent water column height in the
+atmosphere.
 
@@
 <!-- Atmospheric options -->
-For the atmospheric characteristics, we iterated for combinations of AOD at
+For the atmospheric characteristics, we iterated on combinations of AOD at
 $500\,\text{nm}$ ($\tau_{500\text{nm}}$) with additional offsets of $\pm1$ and
-$\pm2\sigma$, and water column ($wc$), also with offsets of $\pm1$ and $\pm2\sigma$.
+$\pm2\sigma$, and water column ($w$), also with offsets of $\pm1$ and $\pm2\sigma$.
 We applied them on two atmospheric profiles, from the Air Force Geophysics
@@
 each modeled value by scaling the model's input spectrum integral, to the
-corresponding total solar irradiance (TSI) provided by NOAA [@Coddington2005].  Also,
+corresponding TSI, provided by NOAA [@Coddington2005].  Also,
 we account for the effect of the Earth -- Sun distance on the irradiance, by using
 the distance calculated by the Astropy [@AstropyCollaboration2022] software library.
-As needed, we interpolate the resulting irradiances to the exact SZA of our
+As needed, we interpolate the resulting irradiances to the SZA of our
 measurements.  For each period of the year, we used the appropriate atmospheric
@@
 The above clear sky reference values are not enough to describe the long term
-variation, due to the changes of the atmospheric constituents. As observed by
+variation, due to the changes of the atmospheric constituents, mainly AOD. As observed by
 @Natsis2023, there is a long term brightening effect, over Thessaloniki for the studied
-period. In order to better describe this change, we used, estimations of AOD change
+period. In order to better incorporate this change, we used, estimations of AOD change
 derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change of
 $-3.8\,\%$ per year at AOD on $340\,\text{nm}$, using a Brewer spectrophotometer. For
-2005 to 2023, we derived the trend from the available AERONET data.
+2005 to 2023, we derived the trend from the available monthly climatological data of AERONET.
 
 To create a unified trend for the long term change of the clear sky irradiance, we
-simulated the values of AOD derived from those sources with Libradtran. For both, we
-have used the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
-coefficients, and we choose the SZA of $55^\circ$ as a representative value for all
+simulated the values of AOD derived from those sources with Libradtran. For both
+inputs, we
+used the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
+coefficients. We choose the SZA of $55^\circ$ as a representative value for all the
 runs.
@@
 spectrophotometer, with a linear trend of $-3.8±0.93\,\%$ per year.  This corresponds
-to a AOD $340\,\text{nm}$ change of $0.0153$ per year.  Using the alpha Ångström
+to a change of $0.0153$ per year for the AOD of $340\,\text{nm}$ .  Using the alpha Ångström
 coefficient of $\alpha = 1.6$, this translates to a change in Ångström beta
@@
 
-```{r CS-change, echo=FALSE, fig.cap="Simulated long term change of clear sky irradiance relevant to its climatological values."}
+```{r CS-change, echo=FALSE, fig.cap="Simulated long term change of the clear sky irradiance relevant to its climatological values, due to changed of AOD."}
 knitr::include_graphics("../images/P_CS_change-1.png")
@@
 has a good agreement with the clear sky conditions. Additional, with the
-implementation of the long term change, as described above, it will be able to align
+implementation of the long term change of AOD, as described above, it will be able to align
 well with most of the natural variation of the physical quantity.  The selection of
-adequate threshold, will also allow us to have a robust method to distinguish the CE
+adequate threshold, will allow us to have a robust method to distinguish the CE
 cases, which will compensate for the limited accuracy of the input data, and the
@@
 In the process of defining the above details, we implemented an empirical method, by
-manual inspection of the CE identification, on specially selected days from the whole
-dataset.  We used seven sets of selected days, with characteristics relevant to the
-efficiency of the identification threshold.  These sets were random groups of about
-20 to 30 days with the following
-characteristics:
-(a) the largest over irradiance CE events,
+manual inspection of the CE identification results, on selected days from the whole
+dataset.  We used seven sets of days, with characteristics relevant to the efficiency
+of the identification threshold.  These sets were random groups of about 20 to 30
+days with the following characteristics:
+(a) the strongest over irradiance CE events,
 (b) the largest daily total over irradiance,
-(c) without clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
-(d) without clouds and without EC events,
-(e) with at least $60\,\%$ of the day length without clouds and some EC events,
-(h) random days and
-(i) some manual selected days that were included during the manual inspection.
+(c) absence of clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
+(d) absence of clouds and absence of EC events,
+(e) with at least $60\,\%$ of the day length without clouds and presence of EC events,
+(h) random selected days and
+(i) some manual selected days that were included during the manual inspection process.
 Where it was needed, for some of the edge cases, we also used images from a sky-cam,
@@
 expect that we were able to detect all the major events of OIR due to CE.  Where,
-minor enhancements may be not detected, are less significant for most of our results.
+some CE events, with very low OIR, may be not detected, these are few and their magnitude
+will not effect our results.
 
@@
 measured intensity of the irradiance, exceeds the equivalent TSI on the top of the
-atmosphere, and satisfy the Equation\nobreakspace{}\ref{eq:ECE}.
+atmosphere, and detected according to the Equation\nobreakspace{}\ref{eq:ECE}.
 \begin{equation}
@@
 
-To give a better understanding of the CE identification procedure, we provide an
-example of the CE identification for a selected day in the Appendix
-(Figure\nobreakspace{}\ref{fig:example-day}), where the use of the reference and the
-threshold are shown, along with the relevant measurements.  Similar we provide an
-example plot of one year data, where the relation of the GHI and clear sky reference
-is shown, along with the OIR intensity also in the Appendix
-Figure\nobreakspace{}\ref{fig:example-year}.
+To give a better understanding of the CE identification procedure, we provided an
+example of the CE identification for a selected day, in the Appendix
+(Figure\nobreakspace{}\ref{fig:example-day}), where the use of the clear sky
+reference and the identification threshold are shown, along with the relevant
+measurements.  Similar, we provided an example plot of data for one year, where the
+relation of the GHI and clear sky reference is shown, along with the OIR intensity
+(Appendix Figure\nobreakspace{}\ref{fig:example-year}).
 
@@
 Our dataset, after the data selection processing, consists of
-`r ST_total$wattGLB.N` records of GHI, of which
-$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are CE events and
-$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are ECE events.
-The highest GHI recorder was 
+`r ST_total$wattGLB.N` records of GHI measurements, of which
+$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ were identified as CE events and
+$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ as ECE events.
+The highest recorded GHI due to CE was
 $`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,W/m^2$
-on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`.
-The absolute stronger CE event had an OIR of 
-$`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,W/m^2$ on
-`r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`.
+on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, and had
+the maximum value of OIR at $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,W/m^2$.
+<!-- The absolute strongest CE event had an OIR of 
+<!-- $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,W/m^2$ on
+<!-- `r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`. -->
 The relative stronger CE event was 
@@
 
-## Trends
+## Long term trends
 
@@
 
-## CE Climatology
+## Cloud enhancements climatology
 
 Another interesting aspect of the CE cases occurrences, is their seasonal cycle. In
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have a monthly box plot
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the monthly box plot
 (whisker plot), where the values have been normalized by the highest median value,
@@
 During the Winter (December -- February) the CE cases are about $25\,\%$ of the maximum.
-For the rest months the occurrences gradually ramp between the maximum and minimum.
-These seasonality is a combinations of the clouds occurrences, and the relevant
-position of the sun during the year. Unfortunately, the lack of detailed data of cloud
+For the rest months, the occurrences gradually ramp between the maximum and minimum.
+This seasonality is a combinations of the clouds occurrences, and the relevant
+position of the sun during each season of the year. Unfortunately, the lack of detailed data on cloud
 formation, type and location is not allowing further analysis.
@@
 
-The distribution of the CE over irradiance intensity follows an exponential decline
+The distribution of the OIR intensity, follows an exponential decline
 Figure\nobreakspace{}\ref{fig:ovir-distribution}, where there is an inverse relation
-between the events frequency and events intensity. This is expected as, the stronger
-the CE events become, the rarer the particular atmospheric and sun conditions will
-occur. This fact is indicative to the magnitude and probability of the expected OIRs
+between the CE events frequency and their intensity. This is expected, as the stronger
+the CE events become, the rarer the particular atmospheric and sun conditions can
+occur. This fact, is indicative to the magnitude and the probability of the expected OIRs
 events over Thessaloniki. Similar distribution of CE occurrences have been reported
-by @Vamvakas2020, where the magnitude of OIR is 
-higher due to the location of the the city of Patras, $2.5^\circ$ closer to the equator.
+by @Vamvakas2020, where the magnitude of OIR were
+higher due to the location of the city of Patras, $2.5^\circ$ closer to the equator.
 
@@
 
-## Groups stats
+## Groups of cloud enhancement
 
-In order to further study the characteristics of the CE events, we grouped the single
+In order to study the total duration of the CE events, we grouped the one
 minute CE events to continuous CE groups (CEG). Thus, a CEG consists of one or more
 successive CE cases, and can represent cloud enhancement conditions spanning a
-duration of multiple minutes.  We have identified `r ST_G0[, .N]` groups, where the
+duration of multiple minutes.  We have identified `r ST_G0[, .N]` groups of CE in the
+whole period of study, where the
 group with the longest duration lasted
@@
 
-The relation between the duration and the mean OIR intensity of the groups have been
-studied (Figure\nobreakspace{}\ref{fig:group-2d}). We observe that the GCE events
-tend to have either long duration, or large intensity, events with strong enhancement
-and long duration are very rare. A similar result on this relation, have been also
+The relation between the duration and the mean OIR intensity of the groups have also been
+studied (Figure\nobreakspace{}\ref{fig:group-2d}). We observed that the GCE events
+tend to have either long duration, or large intensity. Events with strong enhancement
+and long duration are very rare. Similar results on this relation, have been
 reported by @Zhang2018, on a study using a far higher sampling rate than ours.
 
-```{r group-2d, echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"}
+```{r group-2d, echo=FALSE, fig.cap="Relation of the mean over irradiance and duration of GCE, where the color scale donotes the frequency of the respected events."}
 knitr::include_graphics("../images/P-groups-bin2d-1.png")
@@
 
-## Extreme CE above TSI
+## Extreme cloud enhancement events
 
-A characteristic of the CE events that is commonly reported and has some significance
+An aspect of the CE events that is commonly reported and has some significance
 on the solar energy production infrastructure are the extreme CE events (ECE). Where
-solar irradiance exceeds the expected irradiance on top of the atmosphere, we have
-defined this as ECE (Equation\nobreakspace{}\ref{eq:ECE}).
-
-<!-- -  max value ECE -->
-<!--   relative to other works max values -->
-
+solar irradiance exceeds the expected irradiance on top of the atmosphere
+(Equation\nobreakspace{}\ref{eq:ECE}).
 Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies} we have
@@
 for ECE events is in the spring and the start of the summer (March -- June), followed
-by a period in the late fall (September and October).  This is probably an effect of
-the weather characteristics of those periods where, there are continuous alternations
+by a period in the late fall (September and October).  This is probably related to 
+the weather characteristics of these periods, where there are continuous alternations
 between clear sky periods and clouds.
@@
 
-The distribution of the ECE events (Figure\nobreakspace{}\ref{fig:P-extreme-distribution}), shows that there are rare cases where the OIR can exceed the 
-TSI even more than $400\,\text{W}/\text{m}^2$, with the $75\,\%$ of the cases to be below $200\,\text{W}/\text{m}^2$. Similar to CE cases, the  distribution of ECE have a similar pattern
-with the results of @Vamvakas2020, with the difference that the OIR values are lower fro Thessaloniki.
+The distribution of the ECE events (Figure\nobreakspace{}\ref{fig:P-extreme-distribution}),
+shows that there are rare cases where the OIR can exceed the TSI even more than
+$400\,\text{W}/\text{m}^2$, with the $75\,\%$ of the cases to be below
+$200\,\text{W}/\text{m}^2$. 
+Those finds are in accordance with results form @Vamvakas2020, 
+with the difference that the OIR values are lower for Thessaloniki.
 
@@
 
-By creating a clear sky approximation of the GHI, which can represent the long- and
+By creating a clear sky approximation of the GHI, which represents the long- and
 short-term variation of the expected clear sky GHI, we were able to identify cases of 
 CE events.
-By analyzing the CE cases we found an increase of 
+After analyzing the CE cases, we found an increase of 
 $`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
@@
 have strong similarities with results
-by @Vamvakas2020, for a city southern of Thessaloniki, with analogues differences, due to the 
- higher intensity of the solar radiation.
+by @Vamvakas2020, for a city southern of Thessaloniki, with the analogues differences on the
+ intensity of the solar radiation.
 
-An interpretation of CE trends, shows that the interaction of GHI with the clouds
+An interpretation of the CE trends, shows that the interaction of GHI with the
+clouds,
 through this 30 year period, is a dynamic phenomenon that's needs further investigation.

### 2024-05-26 Article_B5/Article_B5_plain.tex
Commit 2024-05-27 00:14

--- 2024-05-26 article/article.tex
@@
   %
-  \fnref{2}}
+  \fnref{1}}
    \ead{meleti@auth.gr} 
@@
 Thessaloniki},city={Thessaloniki},postcode={54124},country={Greece},}
-    \affiliation[Another University]{
-    organization={Department},addressline={A street
-29},city={Manchester,},postcode={2054 NX},state={State},country={The
-Netherlands},}
     \cortext[cor1]{Corresponding author}
@@
   \begin{abstract}
-  Here wii be the abstract.
-
-  It consists of two paragraphs.
+  Here will be the abstract.
   \end{abstract}
     \begin{keyword}
-    cloud enhancement \sep total solar radiation \sep global horizonta
+    cloud enhancement \sep total solar radiation \sep global horizontal
 irradiance \sep 
@@
 
-Some of the proposed underling mechanisms of those events, have been
-summarized by \citet{Gueymard2017}, and include scattering on the edge
-of cumulus clouds or through thin cirrus. Further investigation with
-radiation transfer modeling methods and observations have pointed as the
-prevailing mechanism, the forward Mie scattering
+Some of the proposed underling mechanisms of those enhancements, have
+been summarized by \citet{Gueymard2017}, and include scattering on the
+edge of cumulus clouds or through thin cirrus. Further investigation
+with radiation transfer modeling methods and observations have pointed
+as the prevailing mechanism, the forward Mie scattering
 \citep{Pecenak2016, Thuillier2013, Yordanov2013, Yordanov2015}, through
 the clouds. The overall phenomenon depends on different interactive
-factors, that include cloud thickness, constitution and type; and the
-relative position of the sun, the clouds, and the observer
+factors, which includes cloud thickness, constitution and type; and the
+relative position of the sun and the clouds
 \citep{Gueymard2017, Veerman2022}. As such, there are multiple
-contributing mechanism that are responsible for the observed irradiance
+contributing mechanisms that are responsible for the observed irradiance
 enhancements.
 
-Cloud enhancements have been reported, to be able to exceed in intensity
-even the value of the solar constant, resulting of clear indexes above
-unit. A summary of extreme enchantment cases have been compiled by
-\citet{Martins2022}. There are also some practical implication of the
-cloud enchantments. The intensity and duration of enhancements can
-effect the efficiency and stability of photovoltaic power production
-\citep{Lappalainen2020, Jaervelae2020}, and extreme enhancements cases,
-have the potential to compromise the integrity of photovoltaic plants
-infrastructure \citep{DoNascimento2019}. It has also been demonstrated,
-that these events can interfere in the comparison of ground data and
-satellite observations \citep{Damiani2018}
+On multiple sites, cloud enhancements have been reported, to be able to
+briefly exceed the value of the solar constant, resulting of clear
+indexes above unit. A summary of extreme enchantment cases (ECE) have
+been compiled by \citet{Martins2022}. There are also, some practical
+implication of the cloud enchantments. The intensity and duration of
+enhancements can effect the efficiency and stability of photovoltaic
+power production \citep{Lappalainen2020, Jaervelae2020}, and extreme
+enhancements cases, have the potential to compromise the integrity of
+photovoltaic plants infrastructure \citep{DoNascimento2019}. It has also
+been demonstrated, that these events can interfere in the comparison of
+ground data and satellite observations \citep{Damiani2018}
 
@@
 
-In this study, we evaluated the effects cloud enhancements on the total
-downward radiation by studding the occurrences, their intensity, and
-their duration in a thirty-year period at the city of Thessaloniki. We
-used modeled clear sky irradiance, as a baseline to identify cloud
-enhancements. We were able to determine some trends of the phenomenon,
-it's Climatology, and some of their general characteristics. We weren't
-able to find a comparable study that provides trends for similar long
-term dataset, as ours. The recording of the radiation signal is the mean
-of one-minute. Thus, the minimum resolution of cloud enhancement events
-(CE), in this study is one minute.
+In this study, we evaluated the effects CE on the GHI by studding the
+occurrences, their intensity, and their duration in a thirty-year period
+at the city of Thessaloniki. We used modeled clear sky irradiance, as a
+baseline to identify cloud enhancements. We were able to determine some
+trends of the phenomenon, it's Climatology, and some of their general
+characteristics. We weren't able to find a comparable study that
+provides trends for similar long term dataset, as ours. The recording of
+the GHI signal is the mean of one-minute. Thus, the minimum resolution
+of CE events, in this study is one minute.
 
@@
 these events, some of the are summarized by \citet{Gueymard2017}. Here,
-we defined as cloud enhancement events (CE) the cases when the measured
-global horizontal irradiance (GHI) at ground level, exceeds the expected
-value under clear-sky conditions. Similar, we define as extreme cloud
-enhancement events (ECE), the cases when GHI, exceeds the Total Solar
-Irradiance on horizontal plane at ground level. Although the duration of
-these bursts varies, from instantaneous to several minutes, here we are
-constrained by the recorded data, to one-minute steps.
+we defined as CE events, the cases when the measured GHI at ground
+level, exceeds the expected value under clear-sky conditions. Similar,
+we define as extreme cloud enhancement events (ECE), the cases when GHI,
+exceeds the Total Solar Irradiance (TSI) on horizontal plane at ground
+level. Although the duration of these bursts varies, from instantaneous
+to several minutes, here we are constrained by the recorded data, to
+one-minute steps.
 
@@
 To further improve the quality of the irradiance data, a manual
-screening was performed to remove inconsistent and erroneous recordings
-that can occur stochastically or systematically during the continuous
-operation of the instruments. The manual screening was aided by a
+screening was performed, in order to remove inconsistent and erroneous
+recordings that can occur stochastically or systematically during the
+long operation of the instrument. The manual screening was aided by a
 radiation data quality assurance procedure, adjusted for the site, which
@@
 day, there must exist at least 45 minutes of valid measurements,
-including nighttime near sunrise and sunset. Days with less than 5 valid
-hours are rejected completely. Furthermore, due to the significant
-measurement uncertainty when the Sun is near the horizon, and due to
-some systematic obstructions by nearby buildings, we have excluded all
-measurements with solar zenith angle (SZA) greater than \(78^\circ\).
+including nighttime, when near sunrise and sunset. Days with less than 5
+valid hours were rejected completely. Furthermore, due to the
+significant measurement uncertainty, when the Sun is near the horizon,
+and due to some systematic obstructions by nearby buildings, we have
+excluded all measurements with solar zenith angle (SZA) greater than
+\(78^\circ\).
 
@@
 To be able to detect the CE cases, we had to establish a baseline, above
-which we can characterize each data point as an enhancement event, by
-estimating the occurring over irradiance (OIR). The OIR, here is defined
-as the irradiance difference of the measured one-minute \(\text{GHI}_i\)
-from the CE identification criterion in
-Equation\nobreakspace\ref{eq:CE4}
-(\(\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}\)). To have an
-estimation, and a first insight on the phenomenon, we experimented with
-two simple approaches for the reference. The Haurwitz's model
-\citep{Haurwitz1945}, which is as simple clear sky model, and we had
-already adjusted and had good fit with our data \citep{Natsis2023}, and
-the TSI at the top of the atmosphere. We have tested both cases by using
-an appropriate relative threshold and/or an additional constant offset.
-The initial results, showed that we can detect a big portion of the CE
-events. These results were helpful, and helped to establish some
-criteria to further improve the CE identification. It was evident, by
-inspecting the daily plot of irradiance, that changes on the atmospheric
-conditions introduced numerous false positive and false negative
-results. To produce a more accurate reference, we had to take into
-account more factors that effect the clear sky radiation. So we used a
-radiation transfer model.
+which we characterized each data point as an enhancement event, by
+estimating the occurring over irradiance (OIR). The OIR, is defined as
+the irradiance difference of the measured one-minute \(\text{GHI}_i\)
+from the CE identification criterion
+(\(\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}\)), as defined
+in Equation\nobreakspace\ref{eq:CE4}. To have an estimation, and a first
+insight on the phenomenon, we experimented with two simple approaches
+for the reference. The Haurwitz's model \citep{Haurwitz1945}, which is
+as simple clear sky model, and we had already adjusted and had good fit
+with our data \citep{Natsis2023}, and the TSI at the top of the
+atmosphere. We have tested both cases by using an appropriate relative
+threshold and/or an additional constant offset. The initial results,
+showed that we can detect a big portion of the CE events. These results
+were helpful, as they are independent from unknown factors, and helped
+us to establish some criteria to further improve the CE identification.
+It was evident, by inspecting the daily plot of irradiance, that changes
+on the atmospheric conditions introduced numerous false positive and
+false negative results. To produce a more accurate reference, we had to
+take into account more factors that effect the clear sky radiation. So
+we used a radiation transfer model in order to include the effects of
+ADO and the water vapors.
 
@@
 
-We approximated the expected clear sky GHI by using a radiation transfer
-model. The simulations was performed by the well established model
-Libradtran \citep{Emde2016}, a similar approach, was also used by
-\citet{Vamvakas2020} for creating a clear sky reference. Because of the
-lack of observational data for the whole period, we used some long term
-climatological data for the main factors responsible for the attenuation
-of the broadband downward solar radiation in the atmosphere. Which are
-mainly, the aerosols and the water vapors. Fortunately, our site
+We approximated the expected clear sky GHI by using the Libradtran
+radiation transfer model \citep{Emde2016}, a similar approach, was also
+used by \citet{Vamvakas2020} for creating a clear sky reference for
+studding cloud enhancement events. Main factors responsible for the
+attenuation of the broadband downward solar radiation in the atmosphere
+are the aerosols and the water vapors. Because of the lack of
+observational data for the whole period, we used some long term
+climatological data to recreate the whole period. Fortunately, our site
 participates in the Aerosol Robotic Network (AERONET)
-\citep{Giles2019, Buis1998}, as we operate a Cimel photometer since
-2003, collocated with the CM-21 pyranometer. The mean monthly aerosol
-optical depth (AOD) on different wavelengths is provided by AERONET,
-along with the equivalent water column height in the atmosphere.
+\citep{Giles2019, Buis1998}, as there is in operation a Cimel photometer
+since 2003, collocated with the CM-21 pyranometer. The mean monthly AOD
+on different wavelengths are provided by AERONET, along with the
+equivalent water column height in the atmosphere.
 
@@
 of conditions we use a SZA step of \(0.2^\circ\). For the atmospheric
-characteristics, we iterated for combinations of AOD at
+characteristics, we iterated on combinations of AOD at
 \(500\,\text{nm}\) (\(\tau_{500\text{nm}}\)) with additional offsets of
-\(\pm1\) and \(\pm2\sigma\), and water column (\(wc\)), also with
-offsets of \(\pm1\) and \(\pm2\sigma\). We applied them on two
-atmospheric profiles, from the Air Force Geophysics Laboratory (AFGL).
-The ``AFGL atmospheric constituent profile, midlatitude summer''
-(afglms) and the ``AFGL atmospheric constituent profile, midlatitude
-winter'' (afglmw) \citep{Anderson1986}.
+\(\pm1\) and \(\pm2\sigma\), and water column (\(w\)), also with offsets
+of \(\pm1\) and \(\pm2\sigma\). We applied them on two atmospheric
+profiles, from the Air Force Geophysics Laboratory (AFGL). The ``AFGL
+atmospheric constituent profile, midlatitude summer'' (afglms) and the
+``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw)
+\citep{Anderson1986}.
 
@@
 measurements, we adapted each modeled value by scaling the model's input
-spectrum integral, to the corresponding total solar irradiance (TSI)
-provided by NOAA \citep{Coddington2005}. Also, we account for the effect
-of the Earth -- Sun distance on the irradiance, by using the distance
-calculated by the Astropy \citep{AstropyCollaboration2022} software
-library. As needed, we interpolate the resulting irradiances to the
-exact SZA of our measurements. For each period of the year, we used the
-appropriate atmospheric profile (afglms or afglmw). Finally, we
-calculated the clear sky irradiance value at the horizontal plane. Thus,
-we were able to emulate different atmospheric condition and levels of
-atmospheric clearness for the climatological conditions of the site.
-With this method, the modeled clear sky irradiances can be directly
-compared to each measured one-minute value of GHI, for different
-conditions of atmospheric clearness.
+spectrum integral, to the corresponding TSI, provided by NOAA
+\citep{Coddington2005}. Also, we account for the effect of the Earth --
+Sun distance on the irradiance, by using the distance calculated by the
+Astropy \citep{AstropyCollaboration2022} software library. As needed, we
+interpolate the resulting irradiances to the SZA of our measurements.
+For each period of the year, we used the appropriate atmospheric profile
+(afglms or afglmw). Finally, we calculated the clear sky irradiance
+value at the horizontal plane. Thus, we were able to emulate different
+atmospheric condition and levels of atmospheric clearness for the
+climatological conditions of the site. With this method, the modeled
+clear sky irradiances can be directly compared to each measured
+one-minute value of GHI, for different conditions of atmospheric
+clearness.
 
@@
 The above clear sky reference values are not enough to describe the long
-term variation, due to the changes of the atmospheric constituents. As
-observed by \citet{Natsis2023}, there is a long term brightening effect,
-over Thessaloniki for the studied period. In order to better describe
-this change, we used, estimations of AOD change derived from two
-sources. For 1993 -- 2005, \citet{Kazadzis2007} have found a change of
-\(-3.8\,\%\) per year at AOD on \(340\,\text{nm}\), using a Brewer
-spectrophotometer. For 2005 to 2023, we derived the trend from the
-available AERONET data.
+term variation, due to the changes of the atmospheric constituents,
+mainly AOD. As observed by \citet{Natsis2023}, there is a long term
+brightening effect, over Thessaloniki for the studied period. In order
+to better incorporate this change, we used, estimations of AOD change
+derived from two sources. For 1993 -- 2005, \citet{Kazadzis2007} have
+found a change of \(-3.8\,\%\) per year at AOD on \(340\,\text{nm}\),
+using a Brewer spectrophotometer. For 2005 to 2023, we derived the trend
+from the available monthly climatological data of AERONET.
 
@@
 irradiance, we simulated the values of AOD derived from those sources
-with Libradtran. For both, we have used the AOD at \(500\,\text{nm}\),
-which was inferred by the available Ångström coefficients, and we choose
-the SZA of \(55^\circ\) as a representative value for all runs.
+with Libradtran. For both inputs, we used the AOD at \(500\,\text{nm}\),
+which was inferred by the available Ångström coefficients. We choose the
+SZA of \(55^\circ\) as a representative value for all the runs.
 
@@
 Brewer spectrophotometer, with a linear trend of \(-3.8±0.93\,\%\) per
-year. This corresponds to a AOD \(340\,\text{nm}\) change of \(0.0153\)
-per year. Using the alpha Ångström coefficient of \(\alpha = 1.6\), this
-translates to a change in Ångström beta coefficient of \(\beta=0.00272\)
-per year (or \(\beta=0.084\) in 1997 and \(\beta=0.059\) in 2005). By
-interpolating the resulting clear sky irradiance, we have a trend of
-\(+0.21\,\%\) per year for the clear sky irradiance. For the period 2005
--- 2005 we used the mean monthly values from AERONET, with a similar
-simulation scheme. We computed the trend of clear sky radiation for each
-month of the year, which gave us a mean clear sky radiation trend of
-\(+0.14\,\%\) per year. We applied this long term change to the clear
-sky irradiance, in order to create a more realistic representation of
-the irradiance for the whole study period
+year. This corresponds to a change of \(0.0153\) per year for the AOD of
+\(340\,\text{nm}\) . Using the alpha Ångström coefficient of
+\(\alpha = 1.6\), this translates to a change in Ångström beta
+coefficient of \(\beta=0.00272\) per year (or \(\beta=0.084\) in 1997
+and \(\beta=0.059\) in 2005). By interpolating the resulting clear sky
+irradiance, we have a trend of \(+0.21\,\%\) per year for the clear sky
+irradiance. For the period 2005 -- 2005 we used the mean monthly values
+from AERONET, with a similar simulation scheme. We computed the trend of
+clear sky radiation for each month of the year, which gave us a mean
+clear sky radiation trend of \(+0.14\,\%\) per year. We applied this
+long term change to the clear sky irradiance, in order to create a more
+realistic representation of the irradiance for the whole study period
 (Figure\nobreakspace{}\ref{fig:CS-change}).
@@
 
-\caption{Simulated long term change of clear sky irradiance relevant to its climatological values.}\label{fig:CS-change}
+\caption{Simulated long term change of the clear sky irradiance relevant to its climatological values, due to changed of AOD.}\label{fig:CS-change}
 \end{figure}
@@
 agreement with the clear sky conditions. Additional, with the
-implementation of the long term change, as described above, it will be
-able to align well with most of the natural variation of the physical
-quantity. The selection of adequate threshold, will also allow us to
+implementation of the long term change of AOD, as described above, it
+will be able to align well with most of the natural variation of the
+physical quantity. The selection of adequate threshold, will allow us to
 have a robust method to distinguish the CE cases, which will compensate
@@
 In the process of defining the above details, we implemented an
-empirical method, by manual inspection of the CE identification, on
-specially selected days from the whole dataset. We used seven sets of
-selected days, with characteristics relevant to the efficiency of the
-identification threshold. These sets were random groups of about 20 to
-30 days with the following characteristics: (a) the largest over
-irradiance CE events, (b) the largest daily total over irradiance, (c)
-without clouds (by implementing a clear sky identification algorithm as
-discussed in \citet{Natsis2023}), (d) without clouds and without EC
-events, (e) with at least \(60\,\%\) of the day length without clouds
-and some EC events, (h) random days and (i) some manual selected days
-that were included during the manual inspection. Where it was needed,
-for some of the edge cases, we also used images from a sky-cam, to
-further aid the decisions of the manual inspection.
+empirical method, by manual inspection of the CE identification results,
+on selected days from the whole dataset. We used seven sets of days,
+with characteristics relevant to the efficiency of the identification
+threshold. These sets were random groups of about 20 to 30 days with the
+following characteristics: (a) the strongest over irradiance CE events,
+(b) the largest daily total over irradiance, (c) absence of clouds (by
+implementing a clear sky identification algorithm as discussed in
+\citet{Natsis2023}), (d) absence of clouds and absence of EC events, (e)
+with at least \(60\,\%\) of the day length without clouds and presence
+of EC events, (h) random selected days and (i) some manual selected days
+that were included during the manual inspection process. Where it was
+needed, for some of the edge cases, we also used images from a sky-cam,
+to further aid the decisions of the manual inspection.
 
@@
 identify the OIR created by the clouds, we expect that we were able to
-detect all the major events of OIR due to CE. Where, minor enhancements
-may be not detected, are less significant for most of our results.
+detect all the major events of OIR due to CE. Where, some CE events,
+with very low OIR, may be not detected, these are few and their
+magnitude will not effect our results.
 
@@
 cases of CE, where the measured intensity of the irradiance, exceeds the
-equivalent TSI on the top of the atmosphere, and satisfy the
-Equation\nobreakspace{}\ref{eq:ECE}. \begin{equation}
+equivalent TSI on the top of the atmosphere, and detected according to
+the Equation\nobreakspace{}\ref{eq:ECE}. \begin{equation}
 \text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
@@
 To give a better understanding of the CE identification procedure, we
-provide an example of the CE identification for a selected day in the
+provided an example of the CE identification for a selected day, in the
 Appendix (Figure\nobreakspace{}\ref{fig:example-day}), where the use of
-the reference and the threshold are shown, along with the relevant
-measurements. Similar we provide an example plot of one year data, where
-the relation of the GHI and clear sky reference is shown, along with the
-OIR intensity also in the Appendix
-Figure\nobreakspace{}\ref{fig:example-year}.
+the clear sky reference and the identification threshold are shown,
+along with the relevant measurements. Similar, we provided an example
+plot of data for one year, where the relation of the GHI and clear sky
+reference is shown, along with the OIR intensity (Appendix
+Figure\nobreakspace{}\ref{fig:example-year}).
 
@@
 Our dataset, after the data selection processing, consists of 6144534
-records of GHI, of which \(1.764\,\%\) are CE events and \(0.036\,\%\)
-are ECE events. The highest GHI recorder was \(1416.6\,W/m^2\) on 24~May
-2007. The absolute stronger CE event had an OIR of \(345.86\,W/m^2\) on
-24~May 2007. The relative stronger CE event was \(49.7\,\%\) above the
-clear sky threshold, on 28~October 2016.
+records of GHI measurements, of which \(1.764\,\%\) were identified as
+CE events and \(0.036\,\%\) as ECE events. The highest recorded GHI due
+to CE was \(1416.6\,W/m^2\) on 24~May 2007, and had the maximum value of
+OIR at \(345.9\,W/m^2\). The relative stronger CE event was \(49.7\,\%\)
+above the clear sky threshold, on 28~October 2016.
 
-\hypertarget{trends}{%
-\subsection{Trends}\label{trends}}
+\hypertarget{long-term-trends}{%
+\subsection{Long term trends}\label{long-term-trends}}
 
@@
 
-\hypertarget{ce-climatology}{%
-\subsection{CE Climatology}\label{ce-climatology}}
+\hypertarget{cloud-enhancements-climatology}{%
+\subsection{Cloud enhancements
+climatology}\label{cloud-enhancements-climatology}}
 
@@
 seasonal cycle. In
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have a
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the
 monthly box plot (whisker plot), where the values have been normalized
@@
 Winter (December -- February) the CE cases are about \(25\,\%\) of the
-maximum. For the rest months the occurrences gradually ramp between the
-maximum and minimum. These seasonality is a combinations of the clouds
-occurrences, and the relevant position of the sun during the year.
-Unfortunately, the lack of detailed data of cloud formation, type and
-location is not allowing further analysis.
+maximum. For the rest months, the occurrences gradually ramp between the
+maximum and minimum. This seasonality is a combinations of the clouds
+occurrences, and the relevant position of the sun during each season of
+the year. Unfortunately, the lack of detailed data on cloud formation,
+type and location is not allowing further analysis.
 
@@
 
-The distribution of the CE over irradiance intensity follows an
-exponential decline Figure\nobreakspace{}\ref{fig:ovir-distribution},
-where there is an inverse relation between the events frequency and
-events intensity. This is expected as, the stronger the CE events
-become, the rarer the particular atmospheric and sun conditions will
-occur. This fact is indicative to the magnitude and probability of the
-expected OIRs events over Thessaloniki. Similar distribution of CE
-occurrences have been reported by \citet{Vamvakas2020}, where the
-magnitude of OIR is higher due to the location of the the city of
-Patras, \(2.5^\circ\) closer to the equator.
+The distribution of the OIR intensity, follows an exponential decline
+Figure\nobreakspace{}\ref{fig:ovir-distribution}, where there is an
+inverse relation between the CE events frequency and their intensity.
+This is expected, as the stronger the CE events become, the rarer the
+particular atmospheric and sun conditions can occur. This fact, is
+indicative to the magnitude and the probability of the expected OIRs
+events over Thessaloniki. Similar distribution of CE occurrences have
+been reported by \citet{Vamvakas2020}, where the magnitude of OIR were
+higher due to the location of the city of Patras, \(2.5^\circ\) closer
+to the equator.
 
@@
 
-\hypertarget{groups-stats}{%
-\subsection{Groups stats}\label{groups-stats}}
+\hypertarget{groups-of-cloud-enhancement}{%
+\subsection{Groups of cloud
+enhancement}\label{groups-of-cloud-enhancement}}
 
-In order to further study the characteristics of the CE events, we
-grouped the single minute CE events to continuous CE groups (CEG). Thus,
-a CEG consists of one or more successive CE cases, and can represent
-cloud enhancement conditions spanning a duration of multiple minutes. We
-have identified 28468 groups, where the group with the longest duration
-lasted 140 minutes on 07~July 2013. By examining the frequency
-distribution of the CEG durations
+In order to study the total duration of the CE events, we grouped the
+one minute CE events to continuous CE groups (CEG). Thus, a CEG consists
+of one or more successive CE cases, and can represent cloud enhancement
+conditions spanning a duration of multiple minutes. We have identified
+28468 groups of CE in the whole period of study, where the group with
+the longest duration lasted 140 minutes on 07~July 2013. By examining
+the frequency distribution of the CEG durations
 (Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can
@@
 The relation between the duration and the mean OIR intensity of the
-groups have been studied (Figure\nobreakspace{}\ref{fig:group-2d}). We
-observe that the GCE events tend to have either long duration, or large
-intensity, events with strong enhancement and long duration are very
-rare. A similar result on this relation, have been also reported by
+groups have also been studied (Figure\nobreakspace{}\ref{fig:group-2d}).
+We observed that the GCE events tend to have either long duration, or
+large intensity. Events with strong enhancement and long duration are
+very rare. Similar results on this relation, have been reported by
 \citet{Zhang2018}, on a study using a far higher sampling rate than
@@
 
-\caption{Relation of mean over irradiance and CE group duration}\label{fig:group-2d}
+\caption{Relation of the mean over irradiance and duration of GCE, where the color scale donotes the frequency of the respected events.}\label{fig:group-2d}
 \end{figure}
 
-\hypertarget{extreme-ce-above-tsi}{%
-\subsection{Extreme CE above TSI}\label{extreme-ce-above-tsi}}
+\hypertarget{extreme-cloud-enhancement-events}{%
+\subsection{Extreme cloud enhancement
+events}\label{extreme-cloud-enhancement-events}}
 
-A characteristic of the CE events that is commonly reported and has some
+An aspect of the CE events that is commonly reported and has some
 significance on the solar energy production infrastructure are the
 extreme CE events (ECE). Where solar irradiance exceeds the expected
-irradiance on top of the atmosphere, we have defined this as ECE
-(Equation\nobreakspace{}\ref{eq:ECE}).
-
-Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies}
-we have computed the distribution of the number of occurrences of ECE
-events by month in
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. The most
-active period for ECE events is in the spring and the start of the
-summer (March -- June), followed by a period in the late fall (September
-and October). This is probably an effect of the weather characteristics
-of those periods where, there are continuous alternations between clear
-sky periods and clouds.
+irradiance on top of the atmosphere
+(Equation\nobreakspace{}\ref{eq:ECE}). Analogous to
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies} we have
+computed the distribution of the number of occurrences of ECE events by
+month in Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}.
+The most active period for ECE events is in the spring and the start of
+the summer (March -- June), followed by a period in the late fall
+(September and October). This is probably related to the weather
+characteristics of these periods, where there are continuous
+alternations between clear sky periods and clouds.
 
@@
 \(400\,\text{W}/\text{m}^2\), with the \(75\,\%\) of the cases to be
-below \(200\,\text{W}/\text{m}^2\). Similar to CE cases, the
-distribution of ECE have a similar pattern with the results of
-\citet{Vamvakas2020}, with the difference that the OIR values are lower
-fro Thessaloniki.
+below \(200\,\text{W}/\text{m}^2\). Those finds are in accordance with
+results form \citet{Vamvakas2020}, with the difference that the OIR
+values are lower for Thessaloniki.
 
@@
 
-By creating a clear sky approximation of the GHI, which can represent
-the long- and short-term variation of the expected clear sky GHI, we
-were able to identify cases of CE events. By analyzing the CE cases we
+By creating a clear sky approximation of the GHI, which represents the
+long- and short-term variation of the expected clear sky GHI, we were
+able to identify cases of CE events. After analyzing the CE cases, we
 found an increase of \(45.6\pm 21.9\,\text{cases}/\text{year}\), with
@@
 events we analysed, have strong similarities with results by
-\citet{Vamvakas2020}, for a city southern of Thessaloniki, with
-analogues differences, due to the higher intensity of the solar
-radiation.
+\citet{Vamvakas2020}, for a city southern of Thessaloniki, with the
+analogues differences on the intensity of the solar radiation.
 
-An interpretation of CE trends, shows that the interaction of GHI with
-the clouds through this 30 year period, is a dynamic phenomenon that's
-needs further investigation. Although, to approach it, we need more long
-term observations of AOD and clouds characteristics.
+An interpretation of the CE trends, shows that the interaction of GHI
+with the clouds, through this 30 year period, is a dynamic phenomenon
+that's needs further investigation. Although, to approach it, we need
+more long term observations of AOD and clouds characteristics.
 

### 2024-06-03 article/article.Rmd
Commit 2024-06-03 13:10

@@
     correspondingauthor: true
-    footnote: 1
+    # footnote: 1
   - name:        Alkiviadis Bais
@@
     affiliation: LAP
-    footnote: 2
+    # footnote: 1
 address:
@@
   - total solar radiation
-  - global horizonta irradiance
+  - global horizontal irradiance
   - over irradiance
 
-journal:        "An awesome journal"
+journal:        "Atmospheric Research"
 date:           "`r Sys.Date()`"
@@
 
-biblio-style:   elsarticle-harv # author year style for natbib - use 'elsarticle-num' or 'elsarticle-num-names' for numbered scheme
+biblio-style:   elsarticle-num-names # elsarticle-harv author year style for natbib - use 'elsarticle-num' or 'elsarticle-num-names' for numbered scheme
 
-classoption:    preprint, 3p, authoryear # remove authoryear is not using `elsarticle-harv`
+classoption:    preprint, 5p, authoryear # remove authoryear is not using `elsarticle-harv`
 # Use a CSL with `citation_package = "default"`
@@
 # knitr::opts_chunk$set(dev        = "pdf"   )
-knitr::opts_chunk$set(out.width  = "50%"   )
+knitr::opts_chunk$set(out.width  = "100%"   )
 knitr::opts_chunk$set(fig.align  = "center")
@@
 \
+
 CE: cloud enhancement cases one minute
@@
 Our dataset, after the data selection processing, consists of
-`r ST_total$wattGLB.N` records of GHI, of which
-$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are CE events and
-$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are ECE events.
-The highest GHI recorder was 
-$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,W/m^2$
-on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`.
-The absolute stronger CE event had an OIR of 
-$`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,W/m^2$ on
-`r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`.
+`r ST_total$wattGLB.N` records of GHI measurements, of which
+$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ were identified as CE events and
+$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ as ECE events.
+The highest recorded GHI due to CE was
+$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$
+on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, and had
+the maximum value of OIR at $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
+<!-- The absolute strongest CE event had an OIR of 
+<!-- $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,\text{W}/\text{m}^2$ on
+<!-- `r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`. -->
 The relative stronger CE event was 
@@
 
-```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly CE number of occurancies."}
+```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly cloud enhancement occurrences."}
 knitr::include_graphics("../images/P_energy-6.png")
@@
 
-## CE Climatology
+## Cloud enhancements climatology
 
 Another interesting aspect of the CE cases occurrences, is their seasonal cycle. In
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have a monthly box plot
+Figure\nobreakspace{}\ref{fig:relative-month-occurrences}, we have the monthly box plot
 (whisker plot), where the values have been normalized by the highest median value,
@@
 During the Winter (December -- February) the CE cases are about $25\,\%$ of the maximum.
-For the rest months the occurrences gradually ramp between the maximum and minimum.
-These seasonality is a combinations of the clouds occurrences, and the relevant
-position of the sun during the year. Unfortunately, the lack of detailed data of cloud
+For the rest months, the occurrences gradually ramp between the maximum and minimum.
+This seasonality is a combinations of the clouds occurrences, and the relevant
+position of the sun during each season of the year. Unfortunately, the lack of detailed data on cloud
 formation, type and location is not allowing further analysis.
 
-```{r relative-month-occurancies, echo=FALSE, fig.cap="Seasonal statistics of the number of CE occurancies for each month, normalized to the maximum occurancies on June.
-The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
+```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal statistics of the number of CE occurrences for each month, normalized to the maximum occurrences on June.
+The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the maximum and minimum values, the dots are outlier values, and the rhombus is the mean."}
 knitr::include_graphics("../images/clim_CE_month_norm_MAX_median_N-2.png")
@@
 
-The relation between the duration and the mean OIR intensity of the groups have been
-studied (Figure\nobreakspace{}\ref{fig:group-2d}). We observe that the GCE events
-tend to have either long duration, or large intensity, events with strong enhancement
-and long duration are very rare. A similar result on this relation, have been also
+The relation between the duration and the mean OIR intensity of the groups have also been
+studied (Figure\nobreakspace{}\ref{fig:group-2d}). We observed that the GCE events
+tend to have either long duration, or large intensity. Events with strong enhancement
+and long duration are very rare. Similar results on this relation, have been
 reported by @Zhang2018, on a study using a far higher sampling rate than ours.
 
-```{r group-2d, echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"}
+```{r group-2d, echo=FALSE, fig.cap="Relation of the mean over irradiance and duration of GCE, where the color scale denotes the frequency of the respected events."}
 knitr::include_graphics("../images/P-groups-bin2d-1.png")
@@
 ```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal statistics of the number of ECE occurancies for each month, normalized to the maximum occurancies on March.
-The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
+The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the maximum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
 knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")
@@
 
-```{r example-day, echo=FALSE, fig.cap="Example of cloud indentification data for 2019-07-11.
-Where are denoted with red circles all the detected CE events, the cloud intearaction with the GHI (blue crosses), and the thesholds of CE and the threshold of ECE events with red and black line respectively."}
+```{r example-day, echo=FALSE, fig.cap="Example of cloud identification data for 2019-07-11.
+Where are denoted with red circles all the detected CE events, the cloud interaction with the GHI (blue crosses), and the thresholds of CE and the threshold of ECE events with red and black line respectively.", fig.pos='H'}
 knitr::include_graphics("../images/example_days-18.png")
@@
 
-```{r example-year, echo=FALSE, fig.cap="Example of the relation of the measured GHI versus the reference clear sky irradiance for the year 2005, where the intesity of the detected over irradianse (OIR) is color coded."}
+```{r example-year, echo=FALSE, fig.cap="Example of the relation of the measured GHI versus the reference clear sky irradiance for the year 2005, where the intensity of the detected over irradiance (OIR) is color coded.", fig.pos='H'}
 knitr::include_graphics("../images/example_years-13.png")
@@
 <!-- # References {.unnumbered} -->
-
-<!--
-Elsevier template
-
-Please make sure that your manuscript follows the guidelines in the 
-Guide for Authors of the relevant journal. It is not necessary to 
-typeset your manuscript in exactly the same way as an article, 
-unless you are submitting to a camera-ready copy (CRC) journal.
-
-For detailed instructions regarding the elsevier article class, see   <https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions>
-
-# Bibliography styles
-
-Here are two sample references: @Feynman1963118 [@Dirac1953888].
-
-By default, natbib will be used with the `authoryear` style, set in `classoption` variable in YAML and with `elsearticle-harv.bst` which is among provided style by `elsarticle` documentclass.
-Other available style are `elsarticle-num.bst` and `elsarticle-num-names.bst` — the first one can be used for the numbered scheme, second one for numbered with new options of natbib.sty.
-
-You can sets extra options with `natbiboptions` variable in YAML header. Example 
-```yaml
-natbiboptions: longnamesfirst,angle,semicolon
-```
-
-There are various more specific bibliography styles available at
-<https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files>. 
-To use one of these, add it in the header using, for example, `biblio-style: model1-num-names`.
-
-## Using CSL
-
-If `citation_package` is set to `default` in `elsevier_article()`, then pandoc is used for citations instead of `natbib`.
-In this case, the `csl` option is used to format the references.
-Alternative `csl` files are available from <https://www.zotero.org/styles?q=elsevier>.
-These can be downloaded
-and stored locally, or the url can be used as in the example header.
-
-# Equations
-
-Here is an equation:
-$$ 
-  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
-  \left(\frac{x}{\beta}\right)^{\alpha-1}
-  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
-  \alpha,\beta,x > 0 .
-$$
-
-Here is another:
-\begin{align}
-  a^2+b^2=c^2.
-\end{align}
-
-Inline equations: $\sum_{i = 2}^\infty\{\alpha_i^\beta\}$
-
-# Figures and tables
-
-Figure \ref{fig2} is generated using an R chunk.
-
-```{r fig2, fig.width = 5, fig.height = 5, fig.align='center', out.width="50%", fig.cap = "\\label{fig2}A meaningless scatterplot.", echo = FALSE}
-plot(runif(25), runif(25))
-```
-
-# Tables coming from R
-
-Tables can also be generated using R chunks, as shown in Table \ref{tab1} for example.
-
-```{r tab1, echo = TRUE}
-knitr::kable(head(mtcars)[,1:4], 
-    caption = "\\label{tab1}Caption centered above table"
-)
-```
-
--->

### 2024-06-03 article/article.tex
Commit 2024-06-03 13:10

@@
-\documentclass[preprint, 3p,
+\documentclass[preprint, 5p,
 authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
@@
 
-  \journal{An awesome journal} % Sets Journal name
+  \journal{Atmospheric Research} % Sets Journal name
 
@@
 \usepackage[]{natbib}
-\bibliographystyle{elsarticle-harv}
+\bibliographystyle{elsarticle-num-names}
 
@@
   \corref{cor1}%
-  \fnref{1}}
+  }
    \ead{natsisphysicist@gmail.com} 
@@
   %
-  \fnref{2}}
+  }
    \ead{meleti@auth.gr} 
@@
 
-~ ~ CE: cloud enhancement cases one minute
+~ ~
+
+CE: cloud enhancement cases one minute
 
@@
 
-{\centering \includegraphics[width=0.5\linewidth]{../images/P_CS_change-1}
+{\centering \includegraphics[width=1\linewidth]{../images/P_CS_change-1}
 
@@
 Our dataset, after the data selection processing, consists of 6144534
-records of GHI, of which \(1.764\,\%\) are CE events and \(0.036\,\%\)
-are ECE events. The highest GHI recorder was \(1416.6\,W/m^2\) on 24~May
-2007. The absolute stronger CE event had an OIR of \(345.86\,W/m^2\) on
-24~May 2007. The relative stronger CE event was \(49.7\,\%\) above the
-clear sky threshold, on 28~October 2016.
+records of GHI measurements, of which \(1.764\,\%\) were identified as
+CE events and \(0.036\,\%\) as ECE events. The highest recorded GHI due
+to CE was \(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007, and had the
+maximum value of OIR at \(345.9\,\text{W}/\text{m}^2\). The relative
+stronger CE event was \(49.7\,\%\) above the clear sky threshold, on
+28~October 2016.
 
-\hypertarget{trends}{%
-\subsection{Trends}\label{trends}}
+\hypertarget{long-term-trends}{%
+\subsection{Long term trends}\label{long-term-trends}}
 
@@
 
-{\centering \includegraphics[width=0.5\linewidth]{../images/P_energy-6}
+{\centering \includegraphics[width=1\linewidth]{../images/P_energy-6}
 
@@
 
-\caption{Trend of yearly CE number of occurancies.}\label{fig:P-energy-N}
+\caption{Trend of yearly cloud enhancement occurrences.}\label{fig:P-energy-N}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.5\linewidth]{../images/P_energy-5}
+{\centering \includegraphics[width=1\linewidth]{../images/P_energy-5}
 
@@
 seasonal cycle. In
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have a
+Figure\nobreakspace{}\ref{fig:relative-month-occurrences}, we have the
 monthly box plot (whisker plot), where the values have been normalized
@@
 
-{\centering \includegraphics[width=0.5\linewidth]{../images/clim_CE_month_norm_MAX_median_N-2}
+{\centering \includegraphics[width=1\linewidth]{../images/clim_CE_month_norm_MAX_median_N-2}
 
@@
 
-\caption{Seasonal statistics of the number of CE occurancies for each month, normalized to the maximum occurancies on June.
-The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies}
+\caption{Seasonal statistics of the number of CE occurrences for each month, normalized to the maximum occurrences on June.
+The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the maximum and minimum values, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurrences}
 \end{figure}
 
-The distribution of the CE over irradiance intensity follows an
-exponential decline Figure\nobreakspace{}\ref{fig:ovir-distribution},
-where there is an inverse relation between the events frequency and
-events intensity. This is expected as, the stronger the CE events
-become, the rarer the particular atmospheric and sun conditions will
-occur. This fact is indicative to the magnitude and probability of the
-expected OIRs events over Thessaloniki. Similar distribution of CE
-occurrences have been reported by \citet{Vamvakas2020}, where the
-magnitude of OIR is higher due to the location of the the city of
-Patras, \(2.5^\circ\) closer to the equator.
+The distribution of the OIR intensity, follows an exponential decline
+Figure\nobreakspace{}\ref{fig:ovir-distribution}, where there is an
+inverse relation between the CE events frequency and their intensity.
+This is expected, as the stronger the CE events become, the rarer the
+particular atmospheric and sun conditions can occur. This fact, is
+indicative to the magnitude and the probability of the expected OIRs
+events over Thessaloniki. Similar distribution of CE occurrences have
+been reported by \citet{Vamvakas2020}, where the magnitude of OIR were
+higher due to the location of the city of Patras, \(2.5^\circ\) closer
+to the equator.
 
@@
 
-{\centering \includegraphics[width=0.5\linewidth]{../images/P-relative-distribution-diff-1}
+{\centering \includegraphics[width=1\linewidth]{../images/P-relative-distribution-diff-1}
 
@@
 
-{\centering \includegraphics[width=0.5\linewidth]{../images/groups-1}
+{\centering \includegraphics[width=1\linewidth]{../images/groups-1}
 
@@
 
-{\centering \includegraphics[width=0.5\linewidth]{../images/P-groups-bin2d-1}
+{\centering \includegraphics[width=1\linewidth]{../images/P-groups-bin2d-1}
 
@@
 
-\caption{Relation of mean over irradiance and CE group duration}\label{fig:group-2d}
+\caption{Relation of the mean over irradiance and duration of GCE, where the color scale denotes the frequency of the respected events.}\label{fig:group-2d}
 \end{figure}
 
-\hypertarget{extreme-ce-above-tsi}{%
-\subsection{Extreme CE above TSI}\label{extreme-ce-above-tsi}}
+\hypertarget{extreme-cloud-enhancement-events}{%
+\subsection{Extreme cloud enhancement
+events}\label{extreme-cloud-enhancement-events}}
 
-A characteristic of the CE events that is commonly reported and has some
+An aspect of the CE events that is commonly reported and has some
 significance on the solar energy production infrastructure are the
 extreme CE events (ECE). Where solar irradiance exceeds the expected
-irradiance on top of the atmosphere, we have defined this as ECE
-(Equation\nobreakspace{}\ref{eq:ECE}).
-
-Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies}
-we have computed the distribution of the number of occurrences of ECE
-events by month in
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. The most
-active period for ECE events is in the spring and the start of the
-summer (March -- June), followed by a period in the late fall (September
-and October). This is probably an effect of the weather characteristics
-of those periods where, there are continuous alternations between clear
-sky periods and clouds.
+irradiance on top of the atmosphere
+(Equation\nobreakspace{}\ref{eq:ECE}). Analogous to
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies} we have
+computed the distribution of the number of occurrences of ECE events by
+month in Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}.
+The most active period for ECE events is in the spring and the start of
+the summer (March -- June), followed by a period in the late fall
+(September and October). This is probably related to the weather
+characteristics of these periods, where there are continuous
+alternations between clear sky periods and clouds.
 
@@
 
-{\centering \includegraphics[width=0.5\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}
+{\centering \includegraphics[width=1\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}
 
@@
 \caption{Seasonal statistics of the number of ECE occurancies for each month, normalized to the maximum occurancies on March.
-The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies-ECE}
+The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the maximum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies-ECE}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.5\linewidth]{../images/P-extreme-distribution-1}
+{\centering \includegraphics[width=1\linewidth]{../images/P-extreme-distribution-1}
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 
-{\centering \includegraphics[width=0.5\linewidth]{../images/example_days-18}
+{\centering \includegraphics[width=1\linewidth]{../images/example_days-18}
 
@@
 
-\caption{Example of cloud indentification data for 2019-07-11.
-Where are denoted with red circles all the detected CE events, the cloud intearaction with the GHI (blue crosses), and the thesholds of CE and the threshold of ECE events with red and black line respectively.}\label{fig:example-day}
+\caption{Example of cloud identification data for 2019-07-11.
+Where are denoted with red circles all the detected CE events, the cloud interaction with the GHI (blue crosses), and the thresholds of CE and the threshold of ECE events with red and black line respectively.}\label{fig:example-day}
 \end{figure}
 
-\begin{figure}
+\begin{figure}[H]
 
-{\centering \includegraphics[width=0.5\linewidth]{../images/example_years-13}
+{\centering \includegraphics[width=1\linewidth]{../images/example_years-13}
 
@@
 
-\caption{Example of the relation of the measured GHI versus the reference clear sky irradiance for the year 2005, where the intesity of the detected over irradianse (OIR) is color coded.}\label{fig:example-year}
+\caption{Example of the relation of the measured GHI versus the reference clear sky irradiance for the year 2005, where the intensity of the detected over irradiance (OIR) is color coded.}\label{fig:example-year}
 \end{figure}

### 2024-06-03 article/article.Rmd
Commit 2024-06-03 15:11

@@
 ```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal statistics of the number of ECE occurancies for each month, normalized to the maximum occurancies on March.
-The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the maximum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
+The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the max imum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
 knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")

### 2024-06-04 GHI_enh_04_investigate.tex
Commit 2024-05-23 10:10
Commit 2024-05-23 12:14
Commit 2024-05-23 16:10
Commit 2024-05-24 12:16
Commit 2024-06-04 19:13

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-05-20}
+\date{2024-06-04}
 
@@
 
+{[}1{]} 0.8092946
+
 \begin{verbatim}
@@
 
+\textbf{@Martins2022}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-8} \end{center}
-
-@Martins2022
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-9} \end{center}
 
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-6} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-7} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-8} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_multi-1} \end{center}
 
@@
 \begin{verbatim}
-2024-05-20 16:56:07.0 athan@tyler GHI_enh_04_investigate.R 1.334659 mins
+2024-06-04 15:58:17.7 athan@tyler GHI_enh_04_investigate.R 2.098396 mins
 \end{verbatim}

### 2024-06-04 article/article.tex
Commit 2024-06-04 19:13

@@
 
+{\centering \includegraphics[width=1\linewidth]{../images/P_energy-7}
+
+}
+
+\caption{Trends of the mean OIR per CE.}\label{fig:P-energy-mean}
+\end{figure}
+
+\begin{figure}
+
 {\centering \includegraphics[width=1\linewidth]{../images/P_energy-6}
@@
 \caption{Seasonal statistics of the number of ECE occurancies for each month, normalized to the maximum occurancies on March.
-The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the maximum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies-ECE}
+The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the max imum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies-ECE}
 \end{figure}

### 2024-06-04 GHI_enh_04_investigate.R
Commit 2024-06-04 20:14

@@ -1258,7 +1258,7 @@ write.csv(yeartrends, "./figures/Daily_trends_byYear_Proper.csv")
   plot(ST_yearly[, 100 * GLB_diff.N_pos/wattGLB.N, year],
        col = varcol("GLB_diff.sumPOS"),
        ylab = "CE cases %")
-  title("CE cases % in all measurments")
+  title("CE cases % in all measurments GLB_diff.N_pos/wattGLB.N")
 
   lmD <- lm( ST_yearly[, year, 100 * GLB_diff.N_pos/wattGLB.N])
   abline(lmD)
@@ -1271,6 +1271,27 @@ write.csv(yeartrends, "./figures/Daily_trends_byYear_Proper.csv")
                signif(abs(fit[2]), 2) ,"%/y" )
   )
 }
+
+{
+  plot(ST_yearly[, 100 * GLB_diff.N_pos/All_N, year],
+       col = varcol("GLB_diff.sumPOS"),
+       ylab = "CE cases %")
+  title("CE cases % in all minutes GLB_diff.N_pos/All_N")
+
+  lmD <- lm( ST_yearly[, year, 100 * GLB_diff.N_pos/All_N])
+  abline(lmD)
+
+  ## display trend on graph
+  fit <- lmD[[1]]
+  legend("top", lty = 1, bty = "n", lwd = 2, cex = 1,
+         paste("Trend: ",
+               if (fit[2] > 0) "+" else "-",
+               signif(abs(fit[2]), 2) ,"%/y" )
+  )
+}
+
+
+
 
 
 
@@ -1292,6 +1313,11 @@ write.csv(yeartrends, "./figures/Daily_trends_byYear_Proper.csv")
                signif(abs(fit[2]), 2) ,"%/y" )
   )
 }
+
+
+
+
+
 
 
 

### 2024-06-05 GHI_enh_04_investigate.tex
Commit 2024-06-04 20:14
Commit 2024-06-05 19:11

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-06-04}
+\date{2024-06-05}
 
@@
 
+\begin{verbatim}
+GLB_diff.sumPOS wattGLB.N  All_N
+          <num>     <int>  <int>
+\end{verbatim}
+
+1: 3173.039 141910 199083
+2: 6310.134 205953 266252
+3: 6472.142 194258 266281
+4: 6358.752 196986 266833
+5: 7519.146 203571 266271
+6: 7303.386 199796 266242
+7: 6537.694 209089 266279
+8: 6666.833 204624 266836
+9: 8305.434 193973 266273
+10: 8407.637 205622 266249
+11: 6028.173 205861 266274
+12: 8499.016 202060 266836
+13: 10136.909 193257 266277
+14: 10177.418 190648 266260
+15: 8198.753 185166 266267
+16: 6885.184 207421 266837
+17: 8875.608 190199 266275
+18: 12048.958 158225 266263
+19: 8051.621 198105 266266
+20: 6440.105 199732 266829
+21: 9768.023 205393 266283
+22: 13165.957 202673 266272
+23: 9065.769 190944 266263
+24: 12366.395 211300 266771
+25: 10233.159 210016 266195
+26: 9323.758 209719 266182
+27: 8790.709 202142 266154
+28: 9263.675 199167 266734
+29: 9272.453 211799 266203
+30: 7097.597 209101 266156
+31: 10248.966 205824 265971
+GLB\_diff.sumPOS wattGLB.N All\_N
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-2} \end{center}
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-3} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-4} \end{center}
 
@@
 \begin{verbatim}
-2024-06-04 15:58:17.7 athan@tyler GHI_enh_04_investigate.R 2.098396 mins
+2024-06-05 15:58:36.8 athan@tyler GHI_enh_04_investigate.R 1.238620 mins
 \end{verbatim}

### 2024-06-05 GHI_enh_04_investigate.tex
Commit 2024-06-05 21:10

@@
 
-\begin{verbatim}
-Warning in ans * length(l) + if1: longer object length is not a multiple of
-shorter object length
-\end{verbatim}
-
-\newpage
-
-\begin{verbatim}
-Loading required package: stringr
-\end{verbatim}
-
-\hypertarget{trends-on-daily-observations-data}{%
-\paragraph{Trends on Daily Observations data}\label{trends-on-daily-observations-data}}
-
-Units for GLB\_diff.max : Watt/m\^{}2
-
-lmD: 0.804776 +/- 0.104681
-
-lmY: 0.804779 +/- 0.104683
-
-Arima: 0.805121 +/- 0.139935
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-1} \end{center}
-
-Units for GLB\_diff.mean : Watt/m\^{}2
-
-lmD: 0.002645 +/- 0.154816
-
-lmY: 0.002651 +/- 0.154818
-
-Arima: 0.069946 +/- 0.23533
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-2} \end{center}
-
-Units for GLB\_diff.median : Watt/m\^{}2
-
-lmD: 0.075523 +/- 0.167494
-
-lmY: 0.075532 +/- 0.167497
-
-Arima: 0.144037 +/- 0.248629
-
-Units for GLB\_diff.N :
-
-lmD: -0.012345 +/- 0.138879
-
-lmY: -0.01233 +/- 0.138882
-
-\begin{verbatim}
-Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
-possible convergence problem: optim gave code = 1
-\end{verbatim}
-
-\begin{verbatim}
-Warning in sqrt(diag(se)): NaNs produced
-Warning in sqrt(diag(se)): NaNs produced
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-3} \end{center}
-
-Arima: -0.013183 +/- 6.904159
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-4} \end{center}
-
-Units for GLB\_diff.p\_10 : Watt/m\^{}2
-
-lmD: -0.093964 +/- 0.240209
-
-lmY: -0.093975 +/- 0.240213
-
-Arima: -0.093932 +/- 0.364937
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-5} \end{center}
-
-Units for GLB\_diff.p\_5 : Watt/m\^{}2
-
-lmD: -0.197599 +/- 0.2537
-
-lmY: -0.197611 +/- 0.253704
-
-Arima: -0.197564 +/- 0.388597
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-6} \end{center}
-
-Units for GLB\_diff.p\_90 : Watt/m\^{}2
-
-lmD: 0.446578 +/- 0.074214
-
-lmY: 0.446579 +/- 0.074216
-
-Arima: 0.446582 +/- 0.10962
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-7} \end{center}
-
-Units for GLB\_diff.p\_95 : Watt/m\^{}2
-
-lmD: 0.508145 +/- 0.070493
-
-lmY: 0.508147 +/- 0.070494
-
-Arima: 0.508152 +/- 0.100518
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-8} \end{center}
-
-Units for GLB\_diff.sum : kJ/m\^{}2
-
-lmD: -1.087297 +/- 5.707626
-
-lmY: -1.087374 +/- 5.707725
-
-Arima: -1.035804 +/- 8.936135
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-9} \end{center}
-
-Units for GLB\_ench.max : Watt/m\^{}2
-
-lmD: 0.001815 +/- 0.00027
-
-lmY: 0.001815 +/- 0.00027
-
-Arima: 0.001839 +/- 0.000358
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-10} \end{center}
-
-Units for GLB\_ench.mean : Watt/m\^{}2
-
-lmD: 0.00073 +/- 0.000278
-
-lmY: 0.00073 +/- 0.000278
-
-Arima: 0.000891 +/- 0.000459
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-11} \end{center}
-
-Units for GLB\_ench.median : Watt/m\^{}2
-
-lmD: 0.000679 +/- 0.000312
-
-lmY: 0.000679 +/- 0.000312
-
-Arima: 0.00084 +/- 0.000504
-
-Units for GLB\_ench.N :
-
-lmD: -0.012345 +/- 0.138879
-
-lmY: -0.01233 +/- 0.138882
-
-\begin{verbatim}
-Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
-possible convergence problem: optim gave code = 1
-Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
-NaNs produced
-Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
-NaNs produced
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-12} \end{center}
-
-Arima: -0.013183 +/- 6.904159
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-13} \end{center}
-
-Units for GLB\_ench.p\_10 : Watt/m\^{}2
-
-lmD: 0.001171 +/- 0.000307
-
-lmY: 0.001171 +/- 0.000307
-
-Arima: 0.001171 +/- 0.000479
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-14} \end{center}
-
-Units for GLB\_ench.p\_5 : Watt/m\^{}2
-
-lmD: 0.001184 +/- 0.000299
-
-lmY: 0.001184 +/- 0.000299
-
-Arima: 0.001184 +/- 0.00046
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-15} \end{center}
-
-Units for GLB\_ench.p\_90 : Watt/m\^{}2
-
-lmD: 0.001143 +/- 0.000233
-
-lmY: 0.001143 +/- 0.000233
-
-Arima: 0.001143 +/- 0.000363
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-16} \end{center}
-
-Units for GLB\_ench.p\_95 : Watt/m\^{}2
-
-lmD: 0.001299 +/- 0.000228
-
-lmY: 0.001299 +/- 0.000228
-
-Arima: 0.001299 +/- 0.00034
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-17} \end{center}
-
-Units for GLB\_ench.sum : Watt/m\^{}2
-
-lmD: 0.379481 +/- 0.144397
-
-lmY: 0.379493 +/- 0.1444
-
-Arima: 0.438045 +/- 0.218822
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-18} \end{center}
-
-\newpage
-
-\hypertarget{trends-on-daily-enhancements-data}{%
-\paragraph{Trends on Daily Enhancements data}\label{trends-on-daily-enhancements-data}}
-
-Units for GLB\_diff.max : Watt/m\^{}2
-
-lmD: 0.278784 +/- 0.099757
-
-lmY: 0.278785 +/- 0.099759
-
-Arima: 0.278791 +/- 0.11495
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-19} \end{center}
-
-Units for GLB\_diff.mean : Watt/m\^{}2
-
-lmD: 0.086758 +/- 0.036893
-
-lmY: 0.086759 +/- 0.036894
-
-Arima: 0.086761 +/- 0.03998
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-20} \end{center}
-
-Units for GLB\_diff.median : Watt/m\^{}2
-
-lmD: 0.089859 +/- 0.036694
-
-lmY: 0.089861 +/- 0.036694
-
-Arima: 0.089862 +/- 0.038687
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-21} \end{center}
-
-Units for GLB\_diff.N :
-
-lmD: 0.134313 +/- 0.043256
-
-lmY: 0.134312 +/- 0.043256
-
-Arima: 0.134314 +/- 0.05079
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-22} \end{center}
-
-Units for GLB\_diff.p\_10 : Watt/m\^{}2
-
-lmD: 0.010492 +/- 0.018772
-
-lmY: 0.010493 +/- 0.018773
-
-Arima: 0.010494 +/- 0.019022
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-23} \end{center}
-
-Units for GLB\_diff.p\_5 : Watt/m\^{}2
-
-lmD: 0.006132 +/- 0.017414
-
-lmY: 0.006133 +/- 0.017414
-
-Arima: 0.006133 +/- 0.017662
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-24} \end{center}
-
-Units for GLB\_diff.p\_90 : Watt/m\^{}2
-
-lmD: 0.160601 +/- 0.070705
-
-lmY: 0.160602 +/- 0.070706
-
-Arima: 0.160604 +/- 0.07797
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-25} \end{center}
-
-Units for GLB\_diff.p\_95 : Watt/m\^{}2
-
-lmD: 0.198524 +/- 0.080714
-
-lmY: 0.198524 +/- 0.080715
-
-Arima: 0.198532 +/- 0.091006
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-26} \end{center}
-
-Units for GLB\_diff.sum : kJ/m\^{}2
-
-lmD: 0.386176 +/- 0.138337
-
-lmY: 0.386177 +/- 0.13834
-
-Arima: 0.386184 +/- 0.16586
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-27} \end{center}
-
-Units for GLB\_ench.max : Watt/m\^{}2
-
-lmD: 0.000476 +/- 0.000135
-
-lmY: 0.000476 +/- 0.000135
-
-Arima: 0.000476 +/- 0.000155
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-28} \end{center}
-
-Units for GLB\_ench.mean : Watt/m\^{}2
-
-lmD: 0.000172 +/- 6e-05
-
-lmY: 0.000172 +/- 6e-05
-
-Arima: 0.000172 +/- 6.8e-05
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-29} \end{center}
-
-Units for GLB\_ench.median : Watt/m\^{}2
-
-lmD: 0.00016 +/- 6.3e-05
-
-lmY: 0.00016 +/- 6.3e-05
-
-Arima: 0.00016 +/- 7e-05
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-30} \end{center}
-
-Units for GLB\_ench.N :
-
-lmD: 0.134313 +/- 0.043256
-
-lmY: 0.134312 +/- 0.043256
-
-Arima: 0.134314 +/- 0.05079
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-31} \end{center}
-
-Units for GLB\_ench.p\_10 : Watt/m\^{}2
-
-lmD: 2.8e-05 +/- 3.2e-05
-
-lmY: 2.8e-05 +/- 3.2e-05
-
-Arima: 2.8e-05 +/- 3.6e-05
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-32} \end{center}
-
-Units for GLB\_ench.p\_5 : Watt/m\^{}2
-
-lmD: 1.7e-05 +/- 2.9e-05
-
-lmY: 1.7e-05 +/- 2.9e-05
-
-Arima: 1.7e-05 +/- 3.3e-05
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-33} \end{center}
-
-Units for GLB\_ench.p\_90 : Watt/m\^{}2
-
-lmD: 0.000347 +/- 0.000106
-
-lmY: 0.000347 +/- 0.000106
-
-Arima: 0.000347 +/- 0.000121
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-34} \end{center}
-
-Units for GLB\_ench.p\_95 : Watt/m\^{}2
-
-lmD: 0.000402 +/- 0.000116
-
-lmY: 0.000402 +/- 0.000116
-
-Arima: 0.000402 +/- 0.000134
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-35} \end{center}
-
-Units for GLB\_ench.sum : Watt/m\^{}2
-
-lmD: 0.009848 +/- 0.003421
-
-lmY: 0.009848 +/- 0.003422
-
-Arima: 0.009849 +/- 0.003932
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-36} \end{center}
-
-\newpage
-
-\hypertarget{trends-on-daily-extreme-enhancements-data}{%
-\paragraph{Trends on Daily Extreme Enhancements data}\label{trends-on-daily-extreme-enhancements-data}}
-
-Units for GLB\_diff.max : Watt/m\^{}2
-
-lmD: -1.014326 +/- 0.242383
-
-lmY: -1.01431 +/- 0.242387
-
-Arima: -1.024849 +/- 0.345654
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-37} \end{center}
-
-Units for GLB\_diff.mean : Watt/m\^{}2
-
-lmD: -1.139227 +/- 0.182911
-
-lmY: -1.139223 +/- 0.182914
-
-Arima: -1.17037 +/- 0.320655
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-38} \end{center}
-
-Units for GLB\_diff.median : Watt/m\^{}2
-
-lmD: -1.099532 +/- 0.181744
-
-lmY: -1.09953 +/- 0.181747
-
-Arima: -1.131269 +/- 0.309288
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-39} \end{center}
-
-Units for GLB\_diff.N :
-
-lmD: 0.030347 +/- 0.021245
-
-lmY: 0.030349 +/- 0.021246
-
-Arima: 0.030378 +/- 0.022031
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-40} \end{center}
-
-Units for GLB\_diff.p\_10 : Watt/m\^{}2
-
-lmD: -1.242636 +/- 0.168369
-
-lmY: -1.242644 +/- 0.168371
-
-Arima: -1.283474 +/- 0.312719
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-41} \end{center}
-
-Units for GLB\_diff.p\_5 : Watt/m\^{}2
-
-lmD: -1.259539 +/- 0.167895
-
-lmY: -1.259548 +/- 0.167897
-
-Arima: -1.300028 +/- 0.311399
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-42} \end{center}
-
-Units for GLB\_diff.p\_90 : Watt/m\^{}2
-
-lmD: -1.033796 +/- 0.221995
-
-lmY: -1.03378 +/- 0.221999
-
-Arima: -1.048334 +/- 0.332949
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-43} \end{center}
-
-Units for GLB\_diff.p\_95 : Watt/m\^{}2
-
-lmD: -1.02427 +/- 0.230733
-
-lmY: -1.024254 +/- 0.230737
-
-Arima: -1.036798 +/- 0.338243
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-44} \end{center}
-
-Units for GLB\_diff.sum : kJ/m\^{}2
-
-lmD: 0.128338 +/- 0.244436
-
-lmY: 0.128359 +/- 0.24444
-
-Arima: 0.128462 +/- 0.249026
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-45} \end{center}
-
-Units for GLB\_ench.max : Watt/m\^{}2
-
-lmD: -0.001358 +/- 0.00029
-
-lmY: -0.001358 +/- 0.00029
-
-Arima: -0.001358 +/- 0.00032
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-46} \end{center}
-
-Units for GLB\_ench.mean : Watt/m\^{}2
-
-lmD: -0.0015 +/- 0.000225
-
-lmY: -0.0015 +/- 0.000225
-
-Arima: -0.001504 +/- 0.000267
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-47} \end{center}
-
-Units for GLB\_ench.median : Watt/m\^{}2
-
-lmD: -0.001479 +/- 0.000233
-
-lmY: -0.001479 +/- 0.000233
-
-Arima: -0.001483 +/- 0.000273
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-48} \end{center}
-
-Units for GLB\_ench.N :
-
-lmD: 0.030347 +/- 0.021245
-
-lmY: 0.030349 +/- 0.021246
-
-Arima: 0.030378 +/- 0.022031
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-49} \end{center}
-
-Units for GLB\_ench.p\_10 : Watt/m\^{}2
-
-lmD: -0.001666 +/- 0.000208
-
-lmY: -0.001666 +/- 0.000208
-
-Arima: -0.001674 +/- 0.00026
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-50} \end{center}
-
-Units for GLB\_ench.p\_5 : Watt/m\^{}2
-
-lmD: -0.00168 +/- 0.000207
-
-lmY: -0.00168 +/- 0.000207
-
-Arima: -0.001688 +/- 0.00026
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-51} \end{center}
-
-Units for GLB\_ench.p\_90 : Watt/m\^{}2
-
-lmD: -0.001352 +/- 0.00027
-
-lmY: -0.001352 +/- 0.00027
-
-Arima: -0.001353 +/- 0.000302
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-52} \end{center}
-
-Units for GLB\_ench.p\_95 : Watt/m\^{}2
-
-lmD: -0.00135 +/- 0.000279
-
-lmY: -0.00135 +/- 0.000279
-
-Arima: -0.001351 +/- 0.00031
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-53} \end{center}
-
-Units for GLB\_ench.sum : Watt/m\^{}2
-
-lmD: 0.002398 +/- 0.005327
-
-lmY: 0.002399 +/- 0.005328
-
-Arima: 0.002424 +/- 0.005555
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-54} \end{center}
-
-Arima: 0.086761 +/- 0.03998
-
-\begin{verbatim}
-Warning: The S3 guide system was deprecated in ggplot2 3.5.0.
-i It has been replaced by a ggproto system that can be extended.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_daily_trend-1} \end{center}
-
 \newpage
@@
 
+\newpage
+
+\hypertarget{yearly-trends}{%
+\subsection{yearly trends}\label{yearly-trends}}
+
 lmY: 116.8672 +/- 33.89196
@@
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-4} \end{center}
+
+\newpage
+
+\hypertarget{yearly-trends-month-weight}{%
+\subsection{yearly trends month weight}\label{yearly-trends-month-weight}}
+
+lmY: 95.37747 +/- 25.54612
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_MW_energy-1} \end{center}
+
+lmY: 37.11864 +/- 8.427722
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_MW_energy-2} \end{center}
 
@@
 
-\newpage
-\FloatBarrier
-
-\hypertarget{monthly-energy-contribution-of-enhancements}{%
-\subsubsection{Monthly Energy contribution of enhancements}\label{monthly-energy-contribution-of-enhancements}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-1} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-2} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-3} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-4} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-5} \end{center}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-6} \end{center}
-
 @Martins2022
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_monthly-7} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-5} \end{center}
 
@@
 \begin{verbatim}
-2024-06-05 15:58:36.8 athan@tyler GHI_enh_04_investigate.R 1.238620 mins
+2024-06-05 17:31:25.4 athan@tyler GHI_enh_04_investigate.R 1.589891 mins
 \end{verbatim}

### 2024-06-06 GHI_enh_04_investigate.tex
Commit 2024-06-06 11:11

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-06-05}
+\date{2024-06-06}
 
@@
 }
-\begin{verbatim}
-Attaching package: 'zoo'
-\end{verbatim}
-
-\begin{verbatim}
-The following objects are masked from 'package:data.table':
-
-    yearmon, yearqtr
-\end{verbatim}
-
-\begin{verbatim}
-The following objects are masked from 'package:base':
-
-    as.Date, as.Date.numeric
-\end{verbatim}
-
-\begin{verbatim}
-Registered S3 methods overwritten by 'ggpp':
-  method                  from   
-  heightDetails.titleGrob ggplot2
-  widthDetails.titleGrob  ggplot2
-\end{verbatim}
-
-\begin{verbatim}
-Attaching package: 'ggpp'
-\end{verbatim}
-
-\begin{verbatim}
-The following object is masked from 'package:ggh4x':
-
-    stat_centroid
-\end{verbatim}
-
-\begin{verbatim}
-The following object is masked from 'package:ggplot2':
-
-    annotate
-\end{verbatim}
-
-\begin{verbatim}
-Registered S3 method overwritten by 'ggpmisc':
-  method                  from   
-  as.character.polynomial polynom
-\end{verbatim}
-
 \begin{verbatim}
@@
 
+\hypertarget{climatolgy}{%
+\section{Climatolgy}\label{climatolgy}}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_N_doy-1} \end{center}
@@
 
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCEmonth-MW-1} \end{center}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_N-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_N_MW-1} \end{center}
+
+\hypertarget{monthly-ce}{%
+\subsection{Monthly CE}\label{monthly-ce}}
 
@@
 
+\hypertarget{monthly-weighted-ce}{%
+\subsection{Monthly weighted CE}\label{monthly-weighted-ce}}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N_MW-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N_MW-2} \end{center}
+
+\hypertarget{monthly-extreme-ce-raw}{%
+\subsection{Monthly extreme CE raw}\label{monthly-extreme-ce-raw}}
+
 \begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-MW-1} \end{center}
+
+\hypertarget{monthly-extreme-ce}{%
+\subsection{Monthly extreme CE}\label{monthly-extreme-ce}}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCE_daily-1} \end{center}
+\hypertarget{monthly-weighted-extreme-ce}{%
+\subsection{Monthly weighted extreme CE}\label{monthly-weighted-extreme-ce}}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCE_week-1} \end{center}
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N_MW-1} \end{center}
+
+\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N_MW-2} \end{center}
 
@@
 \begin{verbatim}
-2024-06-05 17:31:25.4 athan@tyler GHI_enh_04_investigate.R 1.589891 mins
+2024-06-06 08:05:21.1 athan@tyler GHI_enh_04_investigate.R 2.110215 mins
 \end{verbatim}

### 2024-06-06 GHI_enh_04_investigate.tex
Commit 2024-06-06 13:11

@@
 \usepackage{caption}
+\usepackage{float}
 \usepackage{placeins}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-1} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-1}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-2} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-2}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-2}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-5} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-6} \end{center}
+\caption{ - empty caption - }\label{fig:groups-3}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-4}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-5}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-5}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-6}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-6}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-7} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-7}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-7}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-8}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-1} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-groups-bin2d-1}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-2} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-2}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-groups-bin2d-2}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-3} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-3}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-groups-bin2d-3}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-4} \end{center}
+\begin{figure}[H]
 
-\hypertarget{climatolgy}{%
-\section{Climatolgy}\label{climatolgy}}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-4}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_N_doy-1} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCEmonth-1} \end{center}
+\caption{ - empty caption - }\label{fig:P-groups-bin2d-4}
+\end{figure}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCEmonth-MW-1} \end{center}
+\hypertarget{climatoogy}{%
+\section{Climatoogy}\label{climatoogy}}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_N-1} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_N_MW-1} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim-CE-N-doy-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:clim-CE-N-doy}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCEmonth-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:climCEmonth}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCEmonth-MW-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:climCEmonth-MW}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim-CE-month-norm-MAX-N-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:clim-CE-month-norm-MAX-N}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim-CE-month-norm-MAX-N-MW-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:clim-CE-month-norm-MAX-N-MW}
+\end{figure}
 
@@
 \subsection{Monthly CE}\label{monthly-ce}}
-
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N-2} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim-CE-month-norm-MAX-median-N-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:clim-CE-month-norm-MAX-median-N}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N_MW-1} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_month_norm_MAX_median_N_MW-2} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim-CE-month-norm-MAX-median-N-MW-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:clim-CE-month-norm-MAX-median-N-MW}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-1} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-MW-1} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:climECEmonth}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-MW-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:climECEmonth-MW}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N-1} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N-2} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim-ECE-month-norm-MAX-median-N-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:clim-ECE-month-norm-MAX-median-N-1}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim-ECE-month-norm-MAX-median-N-2}
+
+}
+
+\caption{ - empty caption - }\label{fig:clim-ECE-month-norm-MAX-median-N-2}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N_MW-1} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N_MW-2} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim-ECE-month-norm-MAX-median-N-MW-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:clim-ECE-month-norm-MAX-median-N-MW}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-1} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-2} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-1}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-3} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-4} \end{center}
+\caption{ - empty caption - }\label{fig:energy-1}
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-5} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-2}
+
+}
+
+\caption{ - empty caption - }\label{fig:energy-2}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-3}
+
+}
+
+\caption{ - empty caption - }\label{fig:energy-3}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-4}
+
+}
+
+\caption{ - empty caption - }\label{fig:energy-4}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-5}
+
+}
+
+\caption{ - empty caption - }\label{fig:energy-5}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-6} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-6}
+
+}
+
+\caption{ - empty caption - }\label{fig:energy-6}
+\end{figure}
 
@@
 \hypertarget{yearly-trends}{%
-\subsection{yearly trends}\label{yearly-trends}}
+\subsection{Yearly trends}\label{yearly-trends}}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-1} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-energy-1}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-2} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-2}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-energy-2}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-3} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-3}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-energy-3}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-4} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-4}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-energy-4}
+\end{figure}
 
@@
 
-\hypertarget{yearly-trends-month-weight}{%
-\subsection{yearly trends month weight}\label{yearly-trends-month-weight}}
+\hypertarget{yearly-trends-month-weighted}{%
+\subsection{Yearly trends month weighted}\label{yearly-trends-month-weighted}}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_MW_energy-1} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-MW-energy-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-MW-energy-1}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_MW_energy-2} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-1} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-MW-energy-2}
 
-\begin{verbatim}
-GLB_diff.sumPOS wattGLB.N  All_N
-          <num>     <int>  <int>
-\end{verbatim}
+}
 
-1: 3173.039 141910 199083
-2: 6310.134 205953 266252
-3: 6472.142 194258 266281
-4: 6358.752 196986 266833
-5: 7519.146 203571 266271
-6: 7303.386 199796 266242
-7: 6537.694 209089 266279
-8: 6666.833 204624 266836
-9: 8305.434 193973 266273
-10: 8407.637 205622 266249
-11: 6028.173 205861 266274
-12: 8499.016 202060 266836
-13: 10136.909 193257 266277
-14: 10177.418 190648 266260
-15: 8198.753 185166 266267
-16: 6885.184 207421 266837
-17: 8875.608 190199 266275
-18: 12048.958 158225 266263
-19: 8051.621 198105 266266
-20: 6440.105 199732 266829
-21: 9768.023 205393 266283
-22: 13165.957 202673 266272
-23: 9065.769 190944 266263
-24: 12366.395 211300 266771
-25: 10233.159 210016 266195
-26: 9323.758 209719 266182
-27: 8790.709 202142 266154
-28: 9263.675 199167 266734
-29: 9272.453 211799 266203
-30: 7097.597 209101 266156
-31: 10248.966 205824 265971
-GLB\_diff.sumPOS wattGLB.N All\_N
+\caption{ - empty caption - }\label{fig:P-MW-energy-2}
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-2} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-1}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-3} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-4} \end{center}
+\caption{ - empty caption - }\label{fig:rel-energy-1}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-2}
+
+}
+
+\caption{ - empty caption - }\label{fig:rel-energy-2}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-3}
+
+}
+
+\caption{ - empty caption - }\label{fig:rel-energy-3}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-4}
+
+}
+
+\caption{ - empty caption - }\label{fig:rel-energy-4}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel_energy-5} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-5}
+
+}
+
+\caption{ - empty caption - }\label{fig:rel-energy-5}
+\end{figure}
 
@@
 \begin{verbatim}
-2024-06-06 08:05:21.1 athan@tyler GHI_enh_04_investigate.R 2.110215 mins
+2024-06-06 09:19:49.0 athan@tyler GHI_enh_04_investigate.R 2.764330 mins
 \end{verbatim}

### 2024-06-06 GHI_enh_07_Aerosols.R
Commit 2024-06-06 13:11

@@ -17,13 +17,14 @@
 #'
 #' header-includes:
 #' - \usepackage{caption}
+#' - \usepackage{float}
 #' - \usepackage{placeins}
 #' - \captionsetup{font=small}
 #'
 #' output:
 #'   bookdown::pdf_document2:
 #'     number_sections: no
-#'     fig_caption:     no
+#'     fig_caption:     yes
 #'     keep_tex:        yes
 #'     latex_engine:    xelatex
 #'     toc:             yes
@@ -52,8 +53,9 @@ knitr::opts_chunk$set(dev        = c("pdf", "png")) ## expected option
 # knitr::opts_chunk$set(dev        = "png"    )       ## for too much data
 knitr::opts_chunk$set(out.width  = "100%"   )
 knitr::opts_chunk$set(fig.align  = "center" )
+knitr::opts_chunk$set(fig.cap    = " - empty caption - " )
 knitr::opts_chunk$set(cache      =  FALSE   )  ## !! breaks calculations
-knitr::opts_chunk$set(fig.pos    = '!h'     )
+knitr::opts_chunk$set(fig.pos    = 'H'    )
 
 #+ echo=FALSE, include=TRUE
 ## __ Set environment  ---------------------------------------------------------

### 2024-06-06 GHI_enh_03_process.tex
Commit 2024-06-04 19:13
Commit 2024-06-05 19:11
Commit 2024-06-05 21:10
Commit 2024-06-06 14:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-05-22}
+\date{2024-06-06}
 
@@
 }
+\begin{verbatim}
+   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
+    0.0    89.7   180.0   180.0   270.3   360.0 
+\end{verbatim}
+
+\begin{verbatim}
+    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
+-72.8133 -27.5835   0.6886   0.3233  28.1502  83.4876 
+\end{verbatim}
+
 Alpha * HAU is CS\_ref
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-1} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-1}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-2} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-2}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-2}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-3} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-3}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-3}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-4} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-4}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-4}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-5} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-5}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-5}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-6} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-6}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-6}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-7} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-7}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-7}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-8} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-8}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-8}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-9} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-9}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-9}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-10} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-10}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-10}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-11} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-11}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-11}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-12} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-12}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-12}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-13} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-13}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-13}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-14} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-14}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-14}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-15} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-15}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-15}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-16} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-16}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-16}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-17} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-17}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-17}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-18} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-18}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-18}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-19} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-19}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-19}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-20} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-20}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6-20}
+\end{figure}
 
@@
 \begin{verbatim}
-2024-05-22 09:38:39.3 athan@tyler GHI_enh_03_process.R 5.198113 mins
+2024-06-06 10:26:55.1 athan@tyler GHI_enh_03_process.R 5.853366 mins
 \end{verbatim}

### 2024-06-06 GHI_enh_02_ID_CE.R
Commit 2024-06-06 18:14

@@ -17,13 +17,14 @@
 #'
 #' header-includes:
 #' - \usepackage{caption}
+#' - \usepackage{float}
 #' - \usepackage{placeins}
 #' - \captionsetup{font=small}
 #'
 #' output:
 #'   bookdown::pdf_document2:
 #'     number_sections: no
-#'     fig_caption:     no
+#'     fig_caption:     yes
 #'     keep_tex:        yes
 #'     latex_engine:    xelatex
 #'     toc:             yes
@@ -50,8 +51,9 @@ knitr::opts_chunk$set(dev        = c("pdf", "png")) ## expected option
 # knitr::opts_chunk$set(dev        = "png"    )       ## for too much data
 knitr::opts_chunk$set(out.width  = "100%"   )
 knitr::opts_chunk$set(fig.align  = "center" )
+knitr::opts_chunk$set(fig.cap    = " - empty caption - " )
 knitr::opts_chunk$set(cache      =  FALSE   )  ## !! breaks calculations
-knitr::opts_chunk$set(fig.pos    = '!h'     )
+knitr::opts_chunk$set(fig.pos    = 'H'    )
 
 #+ echo=FALSE, include=TRUE
 ## __ Set environment  ---------------------------------------------------------
@@ -564,7 +566,7 @@ testdays <- data.table(Day = c(
 #'
 #' # Plot some days with strong enhancement cases
 #'
-#+ example_days, echo=F, include=T, results="asis"
+#+ example-days, echo=F, include=T, results="asis"
 
 vec_days <- matrix(
     ##   Data      Description
@@ -746,7 +748,7 @@ for (ii in 1:nrow(vec_days)) {
 #' \FloatBarrier
 #' # Plot years with enhancement cases
 #'
-#+ example_years, echo=F, include=T, results="asis"
+#+ example-years, echo=F, include=T, results="asis"
 
 ## TODO plot only enhancement cases
 ## DO it with base plot

### 2024-06-06 GHI_enh_06_sza.tex
Commit 2024-04-19 14:14
Commit 2024-04-22 06:14
Commit 2024-05-10 00:14
Commit 2024-05-13 12:21
Commit 2024-05-14 11:35
Commit 2024-05-21 10:14
Commit 2024-05-22 20:14
Commit 2024-06-06 18:14

--- 2024-04-14 GHI_enh_06_sza.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-04-14}
+\date{2024-06-06}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-1} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-2} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-1}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-3} \end{center}
+}
+
+\caption{ - empty caption - }(\#fig:sza-1)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-2}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza-2)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-3}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza-3)
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-1} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-2} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-1}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-3} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-4} \end{center}
+\caption{ - empty caption - }(\#fig:sza_month-1)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-5} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-2}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-6} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-7} \end{center}
+\caption{ - empty caption - }(\#fig:sza_month-2)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-8} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-3}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-9} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-10} \end{center}
+\caption{ - empty caption - }(\#fig:sza_month-3)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-11} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-4}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-12} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-13} \end{center}
+\caption{ - empty caption - }(\#fig:sza_month-4)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-14} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-5}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-15} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-16} \end{center}
+\caption{ - empty caption - }(\#fig:sza_month-5)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-17} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-6}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-18} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-19} \end{center}
+\caption{ - empty caption - }(\#fig:sza_month-6)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-20} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-7}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-21} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-22} \end{center}
+\caption{ - empty caption - }(\#fig:sza_month-7)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-23} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-8}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-24} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-25} \end{center}
+\caption{ - empty caption - }(\#fig:sza_month-8)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-26} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-9}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-27} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-28} \end{center}
+\caption{ - empty caption - }(\#fig:sza_month-9)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-29} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-10}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-30} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-31} \end{center}
+\caption{ - empty caption - }(\#fig:sza_month-10)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-32} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-11}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-33} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-34} \end{center}
+\caption{ - empty caption - }(\#fig:sza_month-11)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-35} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-12}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-36} \end{center}
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-12)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-13}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-13)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-14}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-14)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-15}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-15)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-16}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-16)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-17}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-17)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-18}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-18)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-19}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-19)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-20}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-20)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-21}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-21)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-22}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-22)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-23}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-23)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-24}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-24)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-25}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-25)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-26}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-26)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-27}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-27)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-28}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-28)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-29}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-29)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-30}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-30)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-31}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-31)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-32}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-32)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-33}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-33)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-34}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-34)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-35}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-35)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-36}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_month-36)
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-1} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-2} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-1}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-3} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-4} \end{center}
+\caption{ - empty caption - }(\#fig:sza_doy-1)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-2}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_doy-2)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-3}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_doy-3)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-4}
+
+}
+
+\caption{ - empty caption - }(\#fig:sza_doy-4)
+\end{figure}
 
@@
 \begin{verbatim}
-2024-04-14 00:55:04.2 athan@tyler GHI_enh_06_sza.R 0.288979 mins
+2024-06-06 10:30:43.6 athan@tyler GHI_enh_06_sza.R 0.359110 mins
 \end{verbatim}

### 2024-06-06 GHI_enh_07_Aerosols.tex
Commit 2024-05-22 20:14
Commit 2024-06-06 18:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-05-21}
+\date{2024-06-06}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-1} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-2} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-1}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-3} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-4} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-1)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-5} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-2}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-2)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-3}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-3)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-4}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-4)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-5}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-5)
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-6} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-7} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-6}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-8} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-9} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-6)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-10} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-7}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-11} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-12} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-7)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-13} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-8}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-14} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-15} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-8)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-16} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-9}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-1} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-2} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-9)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-3} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-10}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-4} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-5} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-10)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-6} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-11}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-7} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-8} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-11)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-9} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-12}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-10} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-11} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-12)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-12} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-13}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-13)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-14}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-14)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-15}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-15)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-16}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-4-16)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-1}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-1)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-2}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-2)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-3}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-3)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-4}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-4)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-5}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-5)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-6}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-6)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-7}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-7)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-8}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-8)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-9}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-9)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-10}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-10)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-11}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-11)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-12}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-12)
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-13} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-14} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-13}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-15} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-16} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-13)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-17} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-14}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-18} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-19} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-14)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-20} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-15}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-21} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-22} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-15)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-23} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-16}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-24} \end{center}
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-16)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-17}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-17)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-18}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-18)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-19}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-19)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-20}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-20)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-21}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-21)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-22}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-22)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-23}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-23)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-24}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-24)
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-25} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-26} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-25}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-27} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-28} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-25)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-29} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-26}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-30} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-31} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-26)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-32} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-27}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-33} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-34} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-27)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-35} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-28}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-36} \end{center}
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-28)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-29}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-29)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-30}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-30)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-31}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-31)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-32}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-32)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-33}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-33)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-34}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-34)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-35}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-35)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-36}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-36)
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-37} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-38} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-37}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-39} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-40} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-37)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-41} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-38}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-42} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-43} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-38)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-44} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-39}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-45} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-46} \end{center}
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-39)
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-47} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-40}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-48} \end{center}
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-40)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-41}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-41)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-42}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-42)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-43}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-43)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-44}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-44)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-45}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-45)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-46}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-46)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-47}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-47)
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-48}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-48)
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-49} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-49}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-49)
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-50} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-50}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-50)
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-51} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-51}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-51)
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-52} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-52}
+
+}
+
+\caption{ - empty caption - }(\#fig:unnamed-chunk-5-52)
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/P_CS_change-1} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/P_CS_change-1}
+
+}
+
+\caption{ - empty caption - }(\#fig:P_CS_change)
+\end{figure}
 

### 2024-06-06 GHI_enh_06_sza.tex
Commit 2024-06-06 20:17

--- 2024-04-14 GHI_enh_06_sza.tex
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-1} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-2} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-1}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-3} \end{center}
+}
+
+\caption{ - empty caption - }\label{fig:sza-1}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-2}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-2}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-3}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-3}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-1} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-2} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-1}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-3} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-4} \end{center}
+\caption{ - empty caption - }\label{fig:sza-month-1}
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-5} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-2}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-6} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-7} \end{center}
+\caption{ - empty caption - }\label{fig:sza-month-2}
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-8} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-3}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-9} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-10} \end{center}
+\caption{ - empty caption - }\label{fig:sza-month-3}
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-11} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-4}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-12} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-13} \end{center}
+\caption{ - empty caption - }\label{fig:sza-month-4}
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-14} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-5}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-15} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-16} \end{center}
+\caption{ - empty caption - }\label{fig:sza-month-5}
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-17} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-6}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-18} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-19} \end{center}
+\caption{ - empty caption - }\label{fig:sza-month-6}
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-20} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-7}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-21} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-22} \end{center}
+\caption{ - empty caption - }\label{fig:sza-month-7}
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-23} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-8}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-24} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-25} \end{center}
+\caption{ - empty caption - }\label{fig:sza-month-8}
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-26} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-9}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-27} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-28} \end{center}
+\caption{ - empty caption - }\label{fig:sza-month-9}
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-29} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-10}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-30} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-31} \end{center}
+\caption{ - empty caption - }\label{fig:sza-month-10}
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-32} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-11}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-33} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-34} \end{center}
+\caption{ - empty caption - }\label{fig:sza-month-11}
+\end{figure}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-35} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-12}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-36} \end{center}
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-12}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-13}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-13}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-14}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-14}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-15}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-15}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-16}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-16}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-17}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-17}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-18}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-18}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-19}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-19}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-20}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-20}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-21}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-21}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-22}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-22}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-23}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-23}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-24}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-24}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-25}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-25}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-26}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-26}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-27}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-27}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-28}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-28}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-29}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-29}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-30}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-30}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-31}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-31}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-32}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-32}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-33}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-33}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-34}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-34}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-35}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-35}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-month-36}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-month-36}
+\end{figure}
 
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-1} \end{center}
+\begin{figure}[H]
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-2} \end{center}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-doy-1}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-3} \end{center}
+}
 
-\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-4} \end{center}
+\caption{ - empty caption - }\label{fig:sza-doy-1}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-doy-2}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-doy-2}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-doy-3}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-doy-3}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-doy-4}
+
+}
+
+\caption{ - empty caption - }\label{fig:sza-doy-4}
+\end{figure}
 
@@
 \begin{verbatim}
-2024-04-14 00:55:04.2 athan@tyler GHI_enh_06_sza.R 0.288979 mins
+2024-06-06 15:04:39.7 athan@tyler GHI_enh_06_sza.R 0.661558 mins
 \end{verbatim}

### 2024-06-06 GHI_enh_07_Aerosols.R

@@ -1036,7 +1036,7 @@ dataset <- rbind(
 )
 
 
-#+ P_CS_change, echo=F, include=T, results="asis"
+#+ P-CS-change, echo=F, include=T, results="asis"
 # p2 <-
 ggplot(dataset,
        aes(x = year,

### 2024-06-06 article/article.Rmd
Commit 2024-06-04 18:17
Commit 2024-06-07 00:17

--- 2024-06-03 article/article.Rmd
@@
 ```{r CS-change, echo=FALSE, fig.cap="Simulated long term change of the clear sky irradiance relevant to its climatological values, due to changed of AOD."}
-knitr::include_graphics("../images/P_CS_change-1.png")
+knitr::include_graphics("../images/P-CS-change-1.png")
 ```
@@
 
-<!-- ```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean OIR per CE."} -->
-<!-- knitr::include_graphics("../images/P_energy-7.png") -->
-<!-- ``` -->
+```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean OIR per CE."}
+knitr::include_graphics("../images/P-energy-3.png")
+```
 
@@
 ```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly cloud enhancement occurrences."}
-knitr::include_graphics("../images/P_energy-6.png")
+knitr::include_graphics("../images/P-energy-2.png")
 ```
@@
 ```{r P-energy-sum, echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
-knitr::include_graphics("../images/P_energy-5.png")
+knitr::include_graphics("../images/P-energy-1.png")
 ```
@@
 The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the maximum and minimum values, the dots are outlier values, and the rhombus is the mean."}
-knitr::include_graphics("../images/clim_CE_month_norm_MAX_median_N-2.png")
+knitr::include_graphics("../images/clim-CE-month-norm-MAX-median-N-1.png")
 ```
@@
 ```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal statistics of the number of ECE occurancies for each month, normalized to the maximum occurancies on March.
-The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the maximum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
-knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")
+The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the max imum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
+knitr::include_graphics("../images/clim-ECE-month-norm-MAX-median-N-2.png")
 ```
@@
 Where are denoted with red circles all the detected CE events, the cloud interaction with the GHI (blue crosses), and the thresholds of CE and the threshold of ECE events with red and black line respectively.", fig.pos='H'}
-knitr::include_graphics("../images/example_days-18.png")
+knitr::include_graphics("../images/example-days-18.png")
 ```
@@
 ```{r example-year, echo=FALSE, fig.cap="Example of the relation of the measured GHI versus the reference clear sky irradiance for the year 2005, where the intensity of the detected over irradiance (OIR) is color coded.", fig.pos='H'}
-knitr::include_graphics("../images/example_years-13.png")
+knitr::include_graphics("../images/example-years-13.png")
 ```

### 2024-06-06 article/article.tex
Commit 2024-06-07 00:17

@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/P_CS_change-1}
+{\centering \includegraphics[width=1\linewidth]{../images/P-CS-change-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/P_energy-7}
+{\centering \includegraphics[width=1\linewidth]{../images/P-energy-3}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/P_energy-6}
+{\centering \includegraphics[width=1\linewidth]{../images/P-energy-2}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/P_energy-5}
+{\centering \includegraphics[width=1\linewidth]{../images/P-energy-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/clim_CE_month_norm_MAX_median_N-2}
+{\centering \includegraphics[width=1\linewidth]{../images/clim-CE-month-norm-MAX-median-N-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}
+{\centering \includegraphics[width=1\linewidth]{../images/clim-ECE-month-norm-MAX-median-N-2}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/example_days-18}
+{\centering \includegraphics[width=1\linewidth]{../images/example-days-18}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/example_years-13}
+{\centering \includegraphics[width=1\linewidth]{../images/example-years-13}
 

### 2024-06-07 GHI_enh_04_investigate.tex
Commit 2024-06-06 14:14
Commit 2024-06-07 00:17
Commit 2024-06-07 11:14
Commit 2024-06-07 12:24

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-06-06}
+\date{2024-06-07}
 
@@
 \end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-6}
+
+}
+
+\caption{ - empty caption - }\label{fig:rel-energy-6}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-7}
+
+}
+
+\caption{ - empty caption - }\label{fig:rel-energy-7}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-8}
+
+}
+
+\caption{ - empty caption - }\label{fig:rel-energy-8}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-9}
+
+}
+
+\caption{ - empty caption - }\label{fig:rel-energy-9}
+\end{figure}
 
@@
 \begin{verbatim}
-2024-06-06 09:19:49.0 athan@tyler GHI_enh_04_investigate.R 2.764330 mins
+2024-06-07 08:51:14.3 athan@tyler GHI_enh_04_investigate.R 1.824008 mins
 \end{verbatim}

### 2024-06-07 article/article.Rmd
Commit 2024-06-07 13:12

@@
 ---
-title: Long term cloud enhancement events of global solar irradiance over Thessaloniki
+title: Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece
 
@@
 
-# Intro
+# Introduction
 
-The shortwave solar irradiance, reaching Earth's surface, is the main energy source
-of the atmosphere and the biosphere, and drives and governs the climate [@Gray2010].  It
-has direct practical application, in industries like energy and
-agricultural production. The variability of its intensity, can cause difficulties in
-predicting the yield, and designing the specifications of the appropriate equipment.
-Significant portion of research has been focused on predicting the renewable energy production in a
-fine timescale and in near real-time (for a review see @Inman2013; @Graabak2016).
+The shortwave solar radiation, reaching Earth's surface, is the main energy source of
+the atmosphere and the biosphere, and drives and governs the climate [@Gray2010].  It
+has direct practical application; in industries like energy and agricultural
+production. The variability of its intensity; can impose difficulties in predicting
+the yield; and in designing the specifications of the appropriate equipment.
+Significant portion of research has been focused on predicting the renewable energy
+production in a fine timescale and in near real-time (for a review see @Inman2013;
+@Graabak2016).
 
-A big aspect of this variability is the interaction of GHI with the clouds. In general,
-clouds absorb part of the solar irradiance, but under certain conditions, can enhance
-the total shortwave irradiance reaching the ground. This effect, can locally increase
-the observed GHI, even higher than the expected clear sky irradiance
-[see references therein].
+An important aspect of the variability of solar radiation is its interaction with the
+clouds. In general, clouds can attenuate a fraction  of solar irradiance, but under
+certain conditions, can lead to  enhancement of the global horizontal irradiance
+(GHI) reaching the ground. This effect can locally increase the observed GHI to
+levels even higher than the expected clear-sky irradiance [@Cordero2023; @Vamvakas2020 see references therein].
 

### 2024-06-07 article/article.tex
Commit 2024-06-07 13:12

@@
             pdfauthor={},
-            pdftitle={Long term cloud enhancement events of global solar irradiance over Thessaloniki},
+            pdftitle={Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece},
             colorlinks=false,
@@
   \title{Long term cloud enhancement events of global solar irradiance
-over Thessaloniki}
+over Thessaloniki, Greece}
     \author[LAP]{Athanasios N. Natsis%
@@
 
-\hypertarget{intro}{%
-\section{Intro}\label{intro}}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-The shortwave solar irradiance, reaching Earth's surface, is the main
+The shortwave solar radiation, reaching Earth's surface, is the main
 energy source of the atmosphere and the biosphere, and drives and
 governs the climate \citep{Gray2010}. It has direct practical
-application, in industries like energy and agricultural production. The
-variability of its intensity, can cause difficulties in predicting the
-yield, and designing the specifications of the appropriate equipment.
+application; in industries like energy and agricultural production. The
+variability of its intensity; can impose difficulties in predicting the
+yield; and in designing the specifications of the appropriate equipment.
 Significant portion of research has been focused on predicting the
@@
 
-A big aspect of this variability is the interaction of GHI with the
-clouds. In general, clouds absorb part of the solar irradiance, but
-under certain conditions, can enhance the total shortwave irradiance
-reaching the ground. This effect, can locally increase the observed GHI,
-even higher than the expected clear sky irradiance {[}see references
-therein{]}.
+An important aspect of the variability of solar radiation is its
+interaction with the clouds. In general, clouds can attenuate a fraction
+of solar irradiance, but under certain conditions, can lead to
+enhancement of the global horizontal irradiance (GHI) reaching the
+ground. This effect can locally increase the observed GHI to levels even
+higher than the expected clear-sky irradiance \citep[ see references
+therein]{Cordero2023, Vamvakas2020}.
 

### 2024-06-07 article/article.Rmd
Commit 2024-06-07 14:14

@@
 (GHI) reaching the ground. This effect can locally increase the observed GHI to
-levels even higher than the expected clear-sky irradiance [@Cordero2023; @Vamvakas2020 see references therein].
+levels even higher than the expected clear-sky irradiance [see references therein].
 

### 2024-06-07 article/article.tex
Commit 2024-06-07 14:14

@@
 ground. This effect can locally increase the observed GHI to levels even
-higher than the expected clear-sky irradiance \citep[ see references
-therein]{Cordero2023, Vamvakas2020}.
+higher than the expected clear-sky irradiance {[}see references
+therein{]}.
 

### 2024-06-07 article/article.Rmd
Commit 2024-06-07 15:12

@@
 
-\  
-\
-
 CE: cloud enhancement cases one minute
@@
 (GHI) reaching the ground. This effect can locally increase the observed GHI to
-levels even higher than the expected clear-sky irradiance [see references therein].
+levels even higher than the expected clear-sky irradiance [@Cordero2023;
+@Vamvakas2020; @CastillejoCuberos2020; @Vamvakas2020 and references therein].
 
 Some of the proposed underling mechanisms of those enhancements, have been summarized
-by @Gueymard2017, and include scattering on the edge of cumulus clouds or through
-thin cirrus.  Further investigation with radiation transfer modeling methods and
-observations have pointed as the prevailing mechanism, the forward Mie scattering
-[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015], through the clouds.
-The overall phenomenon depends on different interactive factors, which includes cloud
-thickness, constitution and type; and the relative position of the sun and the clouds
-[@Gueymard2017; @Veerman2022].  As such, there are multiple contributing mechanisms
-that are responsible for the observed irradiance enhancements.
+by @Gueymard2017; the most important being the scattering of radiation on the edges
+of cumulus clouds.  It has been also suggested that enhancement of GHI can be
+produced by thin cirrus clouds though refraction and scattering [@Thuillier2013].
+Further investigation with radiative transfer modeling and observations pointed as
+the prevailing mechanism, the strong forward Mie scattering through clouds of low
+optical depth [@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015].  Overall,
+enhancement event depend on different interactive factors, which include cloud
+thickness, structure and type, and the relative position of the sun and the clouds
+[@Gueymard2017; @Veerman2022].
 
-On multiple sites, cloud enhancements have been reported, to be able to briefly exceed the
-value of the solar constant, resulting of clear indexes above unit. A summary of
-extreme enchantment cases (ECE) have been compiled by @Martins2022. There are also, some
-practical implication of the cloud enchantments.  The intensity and duration of
-enhancements can effect the efficiency and stability of photovoltaic power production
-[@Lappalainen2020; @Jaervelae2020], and extreme enhancements cases, have the
-potential to compromise the integrity of photovoltaic plants infrastructure
-[@DoNascimento2019].  It has also been demonstrated, that these events can interfere
-in the comparison of ground data and satellite observations [@Damiani2018]
+On multiple sites, cloud enhancements (CE) have been reported to be able to briefly
+exceed the value of the solar constant, resulting of clearness indices above unit. A
+summary of extreme enchantment cases (ECE) has been compiled by @Martins2022. There
+are also; some practical implications of the cloud enchantments.  The intensity and
+duration of enhancements can effect the efficiency and stability of photovoltaic
+power production [@Lappalainen2020; @Jaervelae2020]; while ECEs have the potential to
+compromise the integrity of photovoltaic plants infrastructure [@DoNascimento2019].
+It has also been demonstrated, that these events can interfere in the comparison of
+ground-based and satellite observations [@Damiani2018]
 
@@
 -->
-
-Methods of identification cloud enchantment events in the literature, usually include
-the use of a simulated clear sky radiation as baseline, that is combined with an
-appropriate threshold or some other statistical characteristics, and in some cases,
-with visual methods with a sky cam [@Vamvakas2020; @Mol2023 and references therein].
+Methods of identification of CE events usually include the use of simulated clear
+sky irradiance as baseline, that is combined with an appropriate threshold or some
+other statistical characteristics, and in some cases, with visual inspection of sky
+camera images [@Vamvakas2020; @Mol2023 and references therein].
 
 <!-- our work -->
-In this study, we evaluated the effects CE on the GHI by studding the occurrences, their intensity, and their duration in a
-thirty-year period at the city of Thessaloniki.  We used modeled clear sky
-irradiance, as a baseline to identify cloud enhancements.  We were able to determine
-some trends of the phenomenon, it's Climatology, and some of their  general
-characteristics. We weren't able to find a comparable study that provides trends for
-similar long term dataset, as ours.  The recording of the GHI signal is the
-mean of one-minute. Thus, the minimum resolution of CE events, in
-this study is one minute.
+In this study, we evaluate the effects CE on GHI by investigating their frequency of
+occurrence, intensity, and duration in a thirty-year period of GHI observations at
+Thessaloniki, Greece.  We used modeled clear sky irradiance, as a baseline to
+identify cloud enhancements.  We were able to determine some trends of the
+phenomenon, it's Climatology, and some of their  general characteristics. We weren't
+able to find a comparable study that provides trends for similar long term dataset,
+as ours.  The recording of the GHI signal is the mean of one-minute. Thus, the
+minimum resolution of CE events, in this study is one minute.
 

### 2024-06-07 article/article.tex
Commit 2024-06-07 15:12

@@
 
-~ ~
-
 CE: cloud enhancement cases one minute
@@
 ground. This effect can locally increase the observed GHI to levels even
-higher than the expected clear-sky irradiance {[}see references
-therein{]}.
+higher than the expected clear-sky irradiance \citep[ and references
+therein]{Cordero2023, Vamvakas2020, CastillejoCuberos2020, Vamvakas2020}.
 
 Some of the proposed underling mechanisms of those enhancements, have
-been summarized by \citet{Gueymard2017}, and include scattering on the
-edge of cumulus clouds or through thin cirrus. Further investigation
-with radiation transfer modeling methods and observations have pointed
-as the prevailing mechanism, the forward Mie scattering
-\citep{Pecenak2016, Thuillier2013, Yordanov2013, Yordanov2015}, through
-the clouds. The overall phenomenon depends on different interactive
-factors, which includes cloud thickness, constitution and type; and the
-relative position of the sun and the clouds
-\citep{Gueymard2017, Veerman2022}. As such, there are multiple
-contributing mechanisms that are responsible for the observed irradiance
-enhancements.
+been summarized by \citet{Gueymard2017}; the most important being the
+scattering of radiation on the edges of cumulus clouds. It has been also
+suggested that enhancement of GHI can be produced by thin cirrus clouds
+though refraction and scattering \citep{Thuillier2013}. Further
+investigation with radiative transfer modeling and observations pointed
+as the prevailing mechanism, the strong forward Mie scattering through
+clouds of low optical depth
+\citep{Pecenak2016, Thuillier2013, Yordanov2013, Yordanov2015}. Overall,
+enhancement event depend on different interactive factors, which include
+cloud thickness, structure and type, and the relative position of the
+sun and the clouds \citep{Gueymard2017, Veerman2022}.
 
-On multiple sites, cloud enhancements have been reported, to be able to
-briefly exceed the value of the solar constant, resulting of clear
-indexes above unit. A summary of extreme enchantment cases (ECE) have
-been compiled by \citet{Martins2022}. There are also, some practical
-implication of the cloud enchantments. The intensity and duration of
-enhancements can effect the efficiency and stability of photovoltaic
-power production \citep{Lappalainen2020, Jaervelae2020}, and extreme
-enhancements cases, have the potential to compromise the integrity of
+On multiple sites, cloud enhancements (CE) have been reported to be able
+to briefly exceed the value of the solar constant, resulting of
+clearness indices above unit. A summary of extreme enchantment cases
+(ECE) has been compiled by \citet{Martins2022}. There are also; some
+practical implications of the cloud enchantments. The intensity and
+duration of enhancements can effect the efficiency and stability of
+photovoltaic power production \citep{Lappalainen2020, Jaervelae2020};
+while ECEs have the potential to compromise the integrity of
 photovoltaic plants infrastructure \citep{DoNascimento2019}. It has also
 been demonstrated, that these events can interfere in the comparison of
-ground data and satellite observations \citep{Damiani2018}
+ground-based and satellite observations \citep{Damiani2018}
 
-Methods of identification cloud enchantment events in the literature,
-usually include the use of a simulated clear sky radiation as baseline,
-that is combined with an appropriate threshold or some other statistical
-characteristics, and in some cases, with visual methods with a sky cam
-\citep[ and references therein]{Vamvakas2020, Mol2023}.
+Methods of identification of CE events usually include the use of
+simulated clear sky irradiance as baseline, that is combined with an
+appropriate threshold or some other statistical characteristics, and in
+some cases, with visual inspection of sky camera images \citep[ and
+references therein]{Vamvakas2020, Mol2023}.
 
-In this study, we evaluated the effects CE on the GHI by studding the
-occurrences, their intensity, and their duration in a thirty-year period
-at the city of Thessaloniki. We used modeled clear sky irradiance, as a
-baseline to identify cloud enhancements. We were able to determine some
-trends of the phenomenon, it's Climatology, and some of their general
-characteristics. We weren't able to find a comparable study that
-provides trends for similar long term dataset, as ours. The recording of
-the GHI signal is the mean of one-minute. Thus, the minimum resolution
-of CE events, in this study is one minute.
+In this study, we evaluate the effects CE on GHI by investigating their
+frequency of occurrence, intensity, and duration in a thirty-year period
+of GHI observations at Thessaloniki, Greece. We used modeled clear sky
+irradiance, as a baseline to identify cloud enhancements. We were able
+to determine some trends of the phenomenon, it's Climatology, and some
+of their general characteristics. We weren't able to find a comparable
+study that provides trends for similar long term dataset, as ours. The
+recording of the GHI signal is the mean of one-minute. Thus, the minimum
+resolution of CE events, in this study is one minute.
 

### 2024-06-07 article/article.Rmd
Commit 2024-06-07 19:12

@@
 compromise the integrity of photovoltaic plants infrastructure [@DoNascimento2019].
-It has also been demonstrated, that these events can interfere in the comparison of
-ground-based and satellite observations [@Damiani2018]
+It has also been demonstrated that these events can interfere in the comparison of
+ground-based and satellite observations [@Damiani2018].  Global warming has likely
+affected cloud coverage in the last few decades. @Liu2023 reported increases in cloud
+cover over the tropical and subtropical oceans and decreases over most continents,
+while @Dong2022 reported decreases over North America and Europe. To our knowledge,
+there is no evidence on whether this trend has affected also the number and strength
+of CE events.
 

### 2024-06-07 article/article.tex
Commit 2024-06-07 19:12

@@
 photovoltaic plants infrastructure \citep{DoNascimento2019}. It has also
-been demonstrated, that these events can interfere in the comparison of
-ground-based and satellite observations \citep{Damiani2018}
+been demonstrated that these events can interfere in the comparison of
+ground-based and satellite observations \citep{Damiani2018}. Global
+warming has likely affected cloud coverage in the last few decades.
+\citet{Liu2023} reported increases in cloud cover over the tropical and
+subtropical oceans and decreases over most continents, while
+\citet{Dong2022} reported decreases over North America and Europe. To
+our knowledge, there is no evidence on whether this trend has affected
+also the number and strength of CE events.
 

### 2024-06-08 article/article.Rmd
Commit 2024-06-08 07:13

@@
 cover over the tropical and subtropical oceans and decreases over most continents,
-while @Dong2022 reported decreases over North America and Europe. To our knowledge,
+while @Dong2023 reported decreases over North America and Europe. To our knowledge,
 there is no evidence on whether this trend has affected also the number and strength

### 2024-06-08 article/article.Rmd
Commit 2024-06-08 08:12

@@
 the atmosphere and the biosphere, and drives and governs the climate [@Gray2010].  It
-has direct practical application; in industries like energy and agricultural
-production. The variability of its intensity; can impose difficulties in predicting
-the yield; and in designing the specifications of the appropriate equipment.
+has direct practical application in industries like energy and agricultural
+production. The variability of its intensity can impose difficulties in predicting
+the yield and in designing the specifications of the appropriate equipment.
 Significant portion of research has been focused on predicting the renewable energy
@@
 summary of extreme enchantment cases (ECE) has been compiled by @Martins2022. There
-are also; some practical implications of the cloud enchantments.  The intensity and
+are also some practical implications of the cloud enchantments.  The intensity and
 duration of enhancements can effect the efficiency and stability of photovoltaic
-power production [@Lappalainen2020; @Jaervelae2020]; while ECEs have the potential to
+power production [@Lappalainen2020; @Jaervelae2020] while ECEs have the potential to
 compromise the integrity of photovoltaic plants infrastructure [@DoNascimento2019].
@@
 atmospheric conditions.  @Gueymard2017; @Veerman2022
--->
-<!--
+
 Instruments respose ....
@@
 -->
+
 Methods of identification of CE events usually include the use of simulated clear
@@
 occurrence, intensity, and duration in a thirty-year period of GHI observations at
-Thessaloniki, Greece.  We used modeled clear sky irradiance, as a baseline to
-identify cloud enhancements.  We were able to determine some trends of the
-phenomenon, it's Climatology, and some of their  general characteristics. We weren't
-able to find a comparable study that provides trends for similar long term dataset,
-as ours.  The recording of the GHI signal is the mean of one-minute. Thus, the
-minimum resolution of CE events, in this study is one minute.
+Thessaloniki, Greece.  We used modeled clear sky irradiance as a baseline to identify
+cloud enhancements and we determined long term trends of the above mentioned metrics,
+their climatology and some general characteristics.  To our knowledge there are no
+other studies that provide trends from such  long dataset.
 
@@
 events, the cases when the measured GHI at ground
-level, exceeds the expected value under clear-sky conditions.  Similar, we define as
-extreme cloud enhancement events (ECE), the cases when GHI, exceeds the Total Solar
-Irradiance (TSI) on horizontal plane at ground level.  Although the duration of these
-bursts varies, from instantaneous to several minutes, here we are constrained by the
+level, exceeds the expected value under clear-sky conditions.  Similarly, we define as
+extreme cloud enhancement events (ECE), the cases when GHI at ground level exceeds the Total Solar
+Irradiance (TSI).  Although the duration of these
+bursts can vary, from seconds to several minutes, here we are constrained by the
 recorded data, to one-minute steps.
@@
 
-## GHI data
+## Instrumentation and data
 

### 2024-06-08 article/article.tex
Commit 2024-06-08 07:13
Commit 2024-06-08 08:12

@@
 governs the climate \citep{Gray2010}. It has direct practical
-application; in industries like energy and agricultural production. The
-variability of its intensity; can impose difficulties in predicting the
-yield; and in designing the specifications of the appropriate equipment.
+application in industries like energy and agricultural production. The
+variability of its intensity can impose difficulties in predicting the
+yield and in designing the specifications of the appropriate equipment.
 Significant portion of research has been focused on predicting the
@@
 clearness indices above unit. A summary of extreme enchantment cases
-(ECE) has been compiled by \citet{Martins2022}. There are also; some
+(ECE) has been compiled by \citet{Martins2022}. There are also some
 practical implications of the cloud enchantments. The intensity and
 duration of enhancements can effect the efficiency and stability of
-photovoltaic power production \citep{Lappalainen2020, Jaervelae2020};
+photovoltaic power production \citep{Lappalainen2020, Jaervelae2020}
 while ECEs have the potential to compromise the integrity of
@@
 subtropical oceans and decreases over most continents, while
-\citet{Dong2022} reported decreases over North America and Europe. To
+\citet{Dong2023} reported decreases over North America and Europe. To
 our knowledge, there is no evidence on whether this trend has affected
@@
 of GHI observations at Thessaloniki, Greece. We used modeled clear sky
-irradiance, as a baseline to identify cloud enhancements. We were able
-to determine some trends of the phenomenon, it's Climatology, and some
-of their general characteristics. We weren't able to find a comparable
-study that provides trends for similar long term dataset, as ours. The
-recording of the GHI signal is the mean of one-minute. Thus, the minimum
-resolution of CE events, in this study is one minute.
+irradiance as a baseline to identify cloud enhancements and we
+determined long term trends of the above mentioned metrics, their
+climatology and some general characteristics. To our knowledge there are
+no other studies that provide trends from such long dataset.
 
@@
 we defined as CE events, the cases when the measured GHI at ground
-level, exceeds the expected value under clear-sky conditions. Similar,
-we define as extreme cloud enhancement events (ECE), the cases when GHI,
-exceeds the Total Solar Irradiance (TSI) on horizontal plane at ground
-level. Although the duration of these bursts varies, from instantaneous
-to several minutes, here we are constrained by the recorded data, to
-one-minute steps.
+level, exceeds the expected value under clear-sky conditions. Similarly,
+we define as extreme cloud enhancement events (ECE), the cases when GHI
+at ground level exceeds the Total Solar Irradiance (TSI). Although the
+duration of these bursts can vary, from seconds to several minutes, here
+we are constrained by the recorded data, to one-minute steps.
 
@@
 
-\hypertarget{ghi-data}{%
-\subsection{GHI data}\label{ghi-data}}
+\hypertarget{instrumentation-and-data}{%
+\subsection{Instrumentation and data}\label{instrumentation-and-data}}
 

### 2024-06-08 article/article.tex
Commit 2024-06-08 09:12

@@
 
-In the relative bibliography different definition have been used for
-these events, some of the are summarized by \citet{Gueymard2017}. Here,
-we defined as CE events, the cases when the measured GHI at ground
+In this study, we define an event as CE when the measured GHI at ground
 level, exceeds the expected value under clear-sky conditions. Similarly,
@@
 at ground level exceeds the Total Solar Irradiance (TSI). Although the
-duration of these bursts can vary, from seconds to several minutes, here
-we are constrained by the recorded data, to one-minute steps.
+duration of these bursts can vary from seconds to several minutes, here
+we are constrained by the temporal resolution of our data to identify
+evens with duration of at minimum one-minute.
 
@@
 
-The monitoring site is operating in the Laboratory of Atmospheric
-Physics of the Aristotle University of Thessaloniki
-(\(40^\circ\,38'\,\)N, \(22^\circ\,57'\,\)E, \(80\,\)m~a.s.l.). In this
-study we present data from the period 13~April 1993 to 31~December 2023.
-The GHI data were measured with a Kipp~\& Zonen CM-21 pyranometer.
+The data used in this study were recorded at the monitoring site of the
+Laboratory of Atmospheric Physics, Aristotle University of Thessaloniki,
+in Thessaloniki, Greece (\(40^\circ\,38'\,\)N, \(22^\circ\,57'\,\)E,
+\(80\,\)m~a.s.l.). The GHI data were measured with a Kipp~\& Zonen CM-21
+pyranometer and cover the period 13~April 1993 to 31~December 2023.
 During the study period, the pyranometer was independently calibrated
@@
 manufacturer. For the acquisition of radiometric data, the signal of the
-pyranometer was sampled at a rate of \(1\,\text{Hz}\). The mean and the
-standard deviation of these samples were calculated and recorded for
-every minute. The measurements were corrected for the zero offset
-(``dark signal'' in volts), which was calculated by averaging all
-measurements recorded for a period of \(3\,\text{h}\), before (morning)
-or after (evening) the Sun reaches an elevation angle of \(-10^\circ\).
-The signal was converted to irradiance using the ramped value of the
+pyranometer was sampled at a rate of \(1\,\text{Hz}\) with the mean and
+standard deviation of these samples calculated and recorded every
+minute. The measurements were corrected for the zero offset (``dark
+signal'' in volts), which was calculated by averaging all measurements
+recorded for a period of \(3\,\text{h}\), before (morning) or after
+(evening) the Sun reaches an elevation angle of \(-10^\circ\). The
+signal was converted to irradiance using the ramped value of the
 instrument's sensitivity between subsequent calibrations.
@@
 unbiased representation of the data we applied a constraint, similar the
-one used by \citet{CastillejoCuberos2020}. Where, for each valid hour of
-day, there must exist at least 45 minutes of valid measurements,
-including nighttime, when near sunrise and sunset. Days with less than 5
-valid hours were rejected completely. Furthermore, due to the
-significant measurement uncertainty, when the Sun is near the horizon,
-and due to some systematic obstructions by nearby buildings, we have
-excluded all measurements with solar zenith angle (SZA) greater than
+one used by \citet{CastillejoCuberos2020}. For each valid hour of day,
+there must exist at least 45 minutes of valid measurements, including
+nighttime, when near sunrise and sunset. Days with less than 5 valid
+hours were rejected completely. Furthermore, due to the significant
+measurement uncertainty in GHI when the Sun is near the horizon, and due
+to some systematic obstructions by nearby buildings, we have excluded
+all measurements with solar zenith angle (SZA) greater than
 \(78^\circ\).
+
+Finally, images from a sky camera have been used in the manual
+inspection of the CE identification. The sky camera operates since 2012
+and stores images in 5 min time steps.
 
@@
 
-To be able to detect the CE cases, we had to establish a baseline, above
-which we characterized each data point as an enhancement event, by
-estimating the occurring over irradiance (OIR). The OIR, is defined as
-the irradiance difference of the measured one-minute \(\text{GHI}_i\)
-from the CE identification criterion
+For the detection of CE cases we established a baseline of irradiance
+above which we characterized each data point as an enhancement event and
+calculated the over irradiance (OIR). The OIR is defined as the
+irradiance difference of the measured one-minute \(\text{GHI}_i\) from
+the CE identification criterion
 (\(\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}\)), as defined
@@
 
-For completeness, we will describe here the main points of the radiation
-simulation procedure. We used as input the spectrum of
-\citet{Kurucz1994} in the range \(280\) to \(2500\,\text{nm}\), with the
-Libradtran radiation transfer solver ``disort'' on a ``pseudospherical''
-geometry and the ``LOWTRAN'' gas parameterization. For each combination
-of conditions we use a SZA step of \(0.2^\circ\). For the atmospheric
-characteristics, we iterated on combinations of AOD at
-\(500\,\text{nm}\) (\(\tau_{500\text{nm}}\)) with additional offsets of
-\(\pm1\) and \(\pm2\sigma\), and water column (\(w\)), also with offsets
-of \(\pm1\) and \(\pm2\sigma\). We applied them on two atmospheric
-profiles, from the Air Force Geophysics Laboratory (AFGL). The ``AFGL
-atmospheric constituent profile, midlatitude summer'' (afglms) and the
-``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw)
-\citep{Anderson1986}.
-
-To create a look-up table, that aligns with our dataset, we applied some
-adjustments. To account for the Sun's variability, in our one-minute GHI
-measurements, we adapted each modeled value by scaling the model's input
-spectrum integral, to the corresponding TSI, provided by NOAA
-\citep{Coddington2005}. Also, we account for the effect of the Earth --
-Sun distance on the irradiance, by using the distance calculated by the
-Astropy \citep{AstropyCollaboration2022} software library. As needed, we
-interpolate the resulting irradiances to the SZA of our measurements.
-For each period of the year, we used the appropriate atmospheric profile
-(afglms or afglmw). Finally, we calculated the clear sky irradiance
-value at the horizontal plane. Thus, we were able to emulate different
-atmospheric condition and levels of atmospheric clearness for the
-climatological conditions of the site. With this method, the modeled
-clear sky irradiances can be directly compared to each measured
-one-minute value of GHI, for different conditions of atmospheric
-clearness.
+For the atmospheric characteristics, we iterated on combinations of AOD
+at \(500\,\text{nm}\) (\(\tau_{500\text{nm}}\)) with additional offsets
+of \(\pm1\) and \(\pm2\sigma\), and water column (\(w\)), also with
+offsets of \(\pm1\) and \(\pm2\sigma\). We applied them on two
+atmospheric profiles, from the Air Force Geophysics Laboratory (AFGL).
+The ``AFGL atmospheric constituent profile, midlatitude summer''
+(afglms) and the ``AFGL atmospheric constituent profile, midlatitude
+winter'' (afglmw) \citep{Anderson1986}. --\textgreater{}
 

### 2024-06-08 article/article.Rmd
Commit 2024-06-08 09:12

@@
 
-<!-- Define CE and ECE -->
-In the relative bibliography different definition have been used for these events,
-some of the are summarized by @Gueymard2017.  Here, we defined as CE
-events, the cases when the measured GHI at ground
-level, exceeds the expected value under clear-sky conditions.  Similarly, we define as
-extreme cloud enhancement events (ECE), the cases when GHI at ground level exceeds the Total Solar
-Irradiance (TSI).  Although the duration of these
-bursts can vary, from seconds to several minutes, here we are constrained by the
-recorded data, to one-minute steps.
+<!-- Define CE and ECE tomove? -->
+In this study, we define an event as CE when the measured GHI at ground level,
+exceeds the expected value under clear-sky conditions. Similarly, we define as
+extreme cloud enhancement events (ECE), the cases when GHI at ground level exceeds
+the Total Solar Irradiance (TSI). Although the duration of these bursts can vary from
+seconds to several minutes, here we are constrained by the temporal resolution of our
+data to identify evens with duration of at minimum one-minute.
 
@@
 
-The monitoring site is operating in the Laboratory of Atmospheric Physics of the
-Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
-\(22^\circ\,57'\,\)E, \(80\,\)m\ a.s.l.).
-In this study we present data from the period
+The data used in this study were recorded at the monitoring site of the Laboratory of
+Atmospheric Physics, Aristotle University of Thessaloniki, in Thessaloniki, Greece
+(\(40^\circ\,38'\,\)N, \(22^\circ\,57'\,\)E, \(80\,\)m\ a.s.l.).  The GHI data were
+measured with a Kipp\ & Zonen CM-21 pyranometer and cover the period
 `r strftime(min(ST_daily$Date), "%d\\ %B %Y")` to
@@
 <!-- Instrument -->
-The GHI data were measured with a Kipp\ & Zonen CM-21 pyranometer.  During the study
+  During the study
 period, the pyranometer was independently calibrated three times at the
@@
 For the acquisition of radiometric data, the signal of the pyranometer was sampled at
-a rate of $1\,\text{Hz}$.  The mean and the standard deviation of these samples were
-calculated and recorded for every minute.  The measurements were corrected for the
-zero offset ("dark signal" in volts), which was calculated by averaging all
-measurements recorded for a period of $3\,\text{h}$, before (morning) or after
-(evening) the Sun reaches an elevation angle of $-10^\circ$.  The signal was
-converted to irradiance using the ramped value of the instrument’s sensitivity
-between subsequent calibrations.
+a rate of $1\,\text{Hz}$ with the mean and standard deviation of these samples
+calculated and recorded every minute.  The measurements were corrected for the zero
+offset ("dark signal" in volts), which was calculated by averaging all measurements
+recorded for a period of $3\,\text{h}$, before (morning) or after (evening) the Sun
+reaches an elevation angle of $-10^\circ$.  The signal was converted to irradiance
+using the ramped value of the instrument’s sensitivity between subsequent
+calibrations.
 
@@
 performed, in order to remove inconsistent and erroneous recordings that can occur
-stochastically or systematically during the long operation of the instrument.
-The manual screening was aided by a radiation data quality assurance procedure,
-adjusted for the site, which was based on the methods of Long and Shi\ [@Long2006;
+stochastically or systematically during the long operation of the instrument.  The
+manual screening was aided by a radiation data quality assurance procedure, adjusted
+for the site, which was based on the methods of Long and Shi\ [@Long2006;
 @Long2008a].  Thus, problematic recordings have been excluded from further
@@
 To preserve an unbiased representation of the data we applied a constraint, similar
-the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there must
-exist at least 45 minutes of valid measurements, including nighttime, when near sunrise and
+the one used by @CastillejoCuberos2020. For each valid hour of day, there must exist
+at least 45 minutes of valid measurements, including nighttime, when near sunrise and
 sunset. Days with less than 5 valid hours were rejected completely.
@@
 otherwise all minute data for this hour is flagged as invalid. -->
-Furthermore, due to the significant measurement uncertainty, when the Sun is near the
-horizon, and due to some systematic obstructions by nearby buildings, we have
-excluded all measurements with solar zenith angle (SZA) greater than 
-$`r 90 - BIO_ELEVA`^\circ$.
+Furthermore, due to the significant measurement uncertainty in GHI when the Sun is
+near the horizon, and due to some systematic obstructions by nearby buildings, we
+have excluded all measurements with solar zenith angle (SZA) greater than $`r 90 -
+BIO_ELEVA`^\circ$.
+
+Finally, images from a sky camera have been used in the manual inspection of the CE
+identification. The sky camera operates since 2012 and stores images in 5 min time
+steps.
 
@@
 
-To be able to detect the CE cases, we had to establish a baseline, above which we 
-characterized each data point as an enhancement event, by estimating the occurring
-over irradiance (OIR). The OIR, is defined as the irradiance difference of the
-measured one-minute $\text{GHI}_i$ from the CE identification criterion
-($\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}$), as defined in
+For the detection of CE cases we established a baseline of irradiance above which we
+characterized each data point as an enhancement event and calculated the over
+irradiance (OIR). The OIR is defined as the irradiance difference of the measured
+one-minute $\text{GHI}_i$ from the CE identification criterion ($\text{OIR}_i =
+\text{GHI}_i - \text{GHI}_\text{CSlim}$), as defined in
 Equation\nobreakspace\ref{eq:CE4}.
@@
 <!-- Libradtran options -->
+<!-- 
 For completeness, we will describe here the main points of the radiation simulation
@@
 [@Anderson1986].
+-->
 
 <!-- Lookup table -->
+<!-- 
 To create a look-up table, that aligns with our dataset, we applied some adjustments.
@@
 measured one-minute value of GHI, for different conditions of atmospheric clearness.
+-->
 

### 2024-06-09 article/article.Rmd
Commit 2024-06-09 17:12

@@
 irradiance (OIR). The OIR is defined as the irradiance difference of the measured
-one-minute $\text{GHI}_i$ from the CE identification criterion ($\text{OIR}_i =
+one-minute $\text{GHI}_i$ from the $\text{GHI}_\text{ref}$ corresponding to
+cloud-free atmosphere. 
+<!-- CE identification criterion ($\text{OIR}_i =
 \text{GHI}_i - \text{GHI}_\text{CSlim}$), as defined in
-Equation\nobreakspace\ref{eq:CE4}.
-To have an estimation, and a first insight on the phenomenon, we experimented with
-two simple approaches for the reference.  The Haurwitz's model [@Haurwitz1945], which
-is as simple clear sky model, and we had already adjusted and had good fit with our
-data [@Natsis2023], and the TSI at the top of the atmosphere.  We have tested both
-cases by using an appropriate relative threshold and/or an additional constant
-offset.  The initial results, showed that we can detect a big portion of the CE
-events. These results were helpful, as they are independent from unknown factors, and
-helped us to establish some criteria to further improve the CE identification. It was
-evident, by inspecting the daily plot of irradiance, that changes on the atmospheric
-conditions introduced numerous false positive and false negative results.  To produce
-a more accurate reference, we had to take into account more factors that effect the
-clear sky radiation. So we used a radiation transfer
-model in order to include the effects of ADO and the water vapors.
+Equation\nobreakspace\ref{eq:CE4}. -->
+First, we tested two simple approaches for the determination of
+$\text{GHI}_\text{ref}$: The Haurwitz's model [@Haurwitz1945], which is a simple
+clear sky model and was already adjusted and applied to our data [@Natsis2023], and
+the total solar irradiance (TSI) at the top of the atmosphere, adjusted for the
+Sun-Earth distance.  We have tested both methods by using an appropriate relative
+threshold and/or an additional constant offset.  The initial results showed that we
+can detect a big portion of the CE events. However, by inspecting the daily plots of
+irradiance it became evident that changes on the atmospheric conditions introduced
+numerous false positive and false negative results.  To produce a more accurate
+reference, we had to take into account more factors that effect the clear sky
+radiation. So we used a radiation transfer model in order to include the effects of
+ADO and the water vapors.
 

### 2024-06-09 article/article.tex
Commit 2024-06-09 17:12

@@
 irradiance difference of the measured one-minute \(\text{GHI}_i\) from
-the CE identification criterion
-(\(\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}\)), as defined
-in Equation\nobreakspace\ref{eq:CE4}. To have an estimation, and a first
-insight on the phenomenon, we experimented with two simple approaches
-for the reference. The Haurwitz's model \citep{Haurwitz1945}, which is
-as simple clear sky model, and we had already adjusted and had good fit
-with our data \citep{Natsis2023}, and the TSI at the top of the
-atmosphere. We have tested both cases by using an appropriate relative
-threshold and/or an additional constant offset. The initial results,
-showed that we can detect a big portion of the CE events. These results
-were helpful, as they are independent from unknown factors, and helped
-us to establish some criteria to further improve the CE identification.
-It was evident, by inspecting the daily plot of irradiance, that changes
-on the atmospheric conditions introduced numerous false positive and
-false negative results. To produce a more accurate reference, we had to
-take into account more factors that effect the clear sky radiation. So
-we used a radiation transfer model in order to include the effects of
-ADO and the water vapors.
+the \(\text{GHI}_\text{ref}\) corresponding to cloud-free atmosphere.
+First, we tested two simple approaches for the determination of
+\(\text{GHI}_\text{ref}\): The Haurwitz's model \citep{Haurwitz1945},
+which is a simple clear sky model and was already adjusted and applied
+to our data \citep{Natsis2023}, and the total solar irradiance (TSI) at
+the top of the atmosphere, adjusted for the Sun-Earth distance. We have
+tested both cases by using an appropriate relative threshold and/or an
+additional constant offset. The initial results, showed that we can
+detect a big portion of the CE events. These results were helpful, as
+they are independent from unknown factors, and helped us to establish
+some criteria to further improve the CE identification. It was evident,
+by inspecting the daily plot of irradiance, that changes on the
+atmospheric conditions introduced numerous false positive and false
+negative results. To produce a more accurate reference, we had to take
+into account more factors that effect the clear sky radiation. So we
+used a radiation transfer model in order to include the effects of ADO
+and the water vapors.
 

### 2024-06-09 article/article.Rmd
Commit 2024-06-09 18:17

@@
 can detect a big portion of the CE events. However, by inspecting the daily plots of
-irradiance it became evident that changes on the atmospheric conditions introduced
-numerous false positive and false negative results.  To produce a more accurate
-reference, we had to take into account more factors that effect the clear sky
-radiation. So we used a radiation transfer model in order to include the effects of
-ADO and the water vapors.
+irradiance it became evident that changes in atmospheric conditions introduced
+numerous false positive and false negative results.  The main reason for these
+discrepancies is the variability of the effects of aerosols and water vapor which
+were not taken into account in the two simple methods.  To produce a more
+representative reference  we included the effects of these factors through variables
+using a radiative transfer model (RTM).  The applied methodology is discussed in
+section\nobreakspace{}\ref{rtmcs}
 
-## Modeled clear Sky Irradiance
+## Modeled clear Sky Irradiance {#rtmcs}
 
@@
 
-We approximated the expected clear sky GHI by using the Libradtran radiation transfer
-model [@Emde2016], a similar approach, was also used by @Vamvakas2020 for creating a
-clear sky reference for studding cloud enhancement events.  Main factors responsible
-for the attenuation of the broadband downward solar radiation in the atmosphere are
-the aerosols and the water vapors.  Because of the lack of observational data for the
-whole period, we used some long term climatological data to recreate the whole
-period.  Fortunately, our site participates in the Aerosol Robotic Network (AERONET)
-[@Giles2019; @Buis1998], as there is in operation a Cimel photometer since 2003,
-collocated with the CM-21 pyranometer.  The mean monthly AOD on different wavelengths
-are provided by AERONET, along with the equivalent water column height in the
-atmosphere.
+<!-- Libradtran options -->
+We approximated the expected clear sky $\text{GHI}_\text{ref}$ with the radiative
+transfer model uvspec, part of libRadtran [@Emde2016], similarly to the approach used
+by @Vamvakas2020.  In uvspec we used the solar spectrum of @Kurucz1994 in the range
+$280$ to $2500\,\text{nm}$, the radiative trasfer solver "disort" in
+"pseudospherical" geometry and the "LOWTRAN" gas parameterization.  The model was run
+for a range of variables in order to create a look up table (LUT) for the estimation
+of the cloud-free reference irradiance for each individual observation of our
+dataset. In this context, the model was run for SZAs in the range $10$ -- $90^\circ$
+with a step of $0.2^\circ$ and for the atmospheric profiles of the Air Force
+Geophysics Laboratory [@Anderson1986] midlatitude summer and midlatitude winter,
+representative of the warm and cold seasons.
 
-<!-- Libradtran options -->
-<!-- 
-For completeness, we will describe here the main points of the radiation simulation
-procedure. We used as input the spectrum of @Kurucz1994 in the range $280$ to
-$2500\,\text{nm}$, with the Libradtran radiation transfer solver "disort" on a
-"pseudospherical" geometry and the "LOWTRAN" gas parameterization. For each
-combination of conditions we use a SZA step of $0.2^\circ$.
+Main factors responsible for the attenuation of the broadband downward solar
+radiation under cloud free atmospheres are aerosols and water vapor.  At
+Thessaloniki, such measurements are available since 2003 from the Cimel sun
+photometer that belongs to the Aerosol Robotic Network (AERONET) [@Giles2019;
+@Buis1998].  The mean monthly AOD on different wavelengths are provided by
+AERONET, along with the equivalent water column height in the atmosphere.
+
 <!-- Atmospheric options -->
@@
 $\pm2\sigma$, and water column ($w$), also with offsets of $\pm1$ and $\pm2\sigma$.
-We applied them on two atmospheric profiles, from the Air Force Geophysics
-Laboratory (AFGL). The "AFGL atmospheric constituent profile, midlatitude summer"
-(afglms) and the "AFGL atmospheric constituent profile, midlatitude winter" (afglmw)
-[@Anderson1986].
--->
 

### 2024-06-09 article/article.tex
Commit 2024-06-09 18:17

@@
 the top of the atmosphere, adjusted for the Sun-Earth distance. We have
-tested both cases by using an appropriate relative threshold and/or an
-additional constant offset. The initial results, showed that we can
-detect a big portion of the CE events. These results were helpful, as
-they are independent from unknown factors, and helped us to establish
-some criteria to further improve the CE identification. It was evident,
-by inspecting the daily plot of irradiance, that changes on the
-atmospheric conditions introduced numerous false positive and false
-negative results. To produce a more accurate reference, we had to take
-into account more factors that effect the clear sky radiation. So we
-used a radiation transfer model in order to include the effects of ADO
-and the water vapors.
+tested both methods by using an appropriate relative threshold and/or an
+additional constant offset. The initial results showed that we can
+detect a big portion of the CE events. However, by inspecting the daily
+plots of irradiance it became evident that changes in atmospheric
+conditions introduced numerous false positive and false negative
+results. The main reason for these discrepancies is the variability of
+the effects of aerosols and water vapor which were not taken into
+account in the two simple methods. To produce a more representative
+reference we included the effects of these factors through variables
+using a radiative transfer model (RTM). The applied methodology is
+discussed in section\nobreakspace{}\ref{rtmcs}
 
-\hypertarget{modeled-clear-sky-irradiance}{%
-\subsection{Modeled clear Sky
-Irradiance}\label{modeled-clear-sky-irradiance}}
+\hypertarget{rtmcs}{%
+\subsection{Modeled clear Sky Irradiance}\label{rtmcs}}
 
@@
 
-We approximated the expected clear sky GHI by using the Libradtran
-radiation transfer model \citep{Emde2016}, a similar approach, was also
-used by \citet{Vamvakas2020} for creating a clear sky reference for
-studding cloud enhancement events. Main factors responsible for the
-attenuation of the broadband downward solar radiation in the atmosphere
-are the aerosols and the water vapors. Because of the lack of
-observational data for the whole period, we used some long term
-climatological data to recreate the whole period. Fortunately, our site
-participates in the Aerosol Robotic Network (AERONET)
-\citep{Giles2019, Buis1998}, as there is in operation a Cimel photometer
-since 2003, collocated with the CM-21 pyranometer. The mean monthly AOD
-on different wavelengths are provided by AERONET, along with the
-equivalent water column height in the atmosphere.
+We approximated the expected clear sky \(\text{GHI}_\text{ref}\) with
+the radiative transfer model uvspec, part of libRadtran
+\citep{Emde2016}, similarly to the approach used by
+\citet{Vamvakas2020}. In uvspec we used the solar spectrum of
+\citet{Kurucz1994} in the range \(280\) to \(2500\,\text{nm}\), the
+radiative trasfer solver ``disort'' in ``pseudospherical'' geometry and
+the ``LOWTRAN'' gas parameterization. The model was run for a range of
+variables in order to create a look up table (LUT) for the estimation of
+the cloud-free reference irradiance for each individual observation of
+our dataset. In this context, the model was run for SZAs in the range
+\(10\) -- \(90^\circ\) with a step of \(0.2^\circ\) and for the
+atmospheric profiles of the Air Force Geophysics Laboratory
+\citep{Anderson1986} midlatitude summer and midlatitude winter,
+representative of the warm and cold seasons.
+
+Main factors responsible for the attenuation of the broadband downward
+solar radiation under cloud free atmospheres are aerosols and water
+vapor. At Thessaloniki, such measurements are available since 2003 from
+the Cimel sun photometer that belongs to the Aerosol Robotic Network
+(AERONET) \citep{Giles2019, Buis1998}. The mean monthly AOD on different
+wavelengths are provided by AERONET, along with the equivalent water
+column height in the atmosphere.
 
@@
 of \(\pm1\) and \(\pm2\sigma\), and water column (\(w\)), also with
-offsets of \(\pm1\) and \(\pm2\sigma\). We applied them on two
-atmospheric profiles, from the Air Force Geophysics Laboratory (AFGL).
-The ``AFGL atmospheric constituent profile, midlatitude summer''
-(afglms) and the ``AFGL atmospheric constituent profile, midlatitude
-winter'' (afglmw) \citep{Anderson1986}. --\textgreater{}
+offsets of \(\pm1\) and \(\pm2\sigma\).
 

### 2024-06-09 article/article.Rmd
Commit 2024-06-09 19:11

@@
 photometer that belongs to the Aerosol Robotic Network (AERONET) [@Giles2019;
-@Buis1998].  The mean monthly AOD on different wavelengths are provided by
-AERONET, along with the equivalent water column height in the atmosphere.
+@Buis1998].  From the observations in the period 2003 -- 2023 we calculated the
+monthly climatological means and standard deviation ($\sigma$) for the aerosol
+optical depth (AOD) at $500\,\text{nm}$ and the equivalent height of the water column
+(WC).  The monthly climatological values of AOD and water column, as well as
+combinations with additional offsets of $\pm1\sigma$ and $\pm2\sigma$ , were used as
+inputs to the RTM in the construction of the LUT.
 
-<!-- Atmospheric options -->
-For the atmospheric characteristics, we iterated on combinations of AOD at
-$500\,\text{nm}$ ($\tau_{500\text{nm}}$) with additional offsets of $\pm1$ and
-$\pm2\sigma$, and water column ($w$), also with offsets of $\pm1$ and $\pm2\sigma$.
+For each measurement of the dataset, we calculated from the LUT a
+$\text{GHI}_\text{ref}$ value for the respective season and SZA (by linear
+interpolation), and for the climatological values of AOD and WC of the respective
+month. The same procedure was followed for the estimation of the
+$\text{GHI}_\text{ref}$ for all combinations of the AOD and WC with the above
+mentioned standard deviation offsets.  Finally, each $\text{GHI}_\text{ref}$ value
+was adjusted to the actual Sun-Earth distance derived by the Astropy software library
+[@AstropyCollaboration2022].
 
@@
 <!-- Aerosol change -->
-The above clear sky reference values are not enough to describe the long term
-variation, due to the changes of the atmospheric constituents, mainly AOD. As observed by
-@Natsis2023, there is a long term brightening effect, over Thessaloniki for the studied
-period. In order to better incorporate this change, we used, estimations of AOD change
+The above clear sky reference values are based on the climatological AOD and WC,
+hence they cannot describe accurately the long term variation of
+$\text{GHI}_\text{ref}$ due to changes in the two atmospheric constituents, mainly
+AOD.  As reported by @Natsis2023, there is a long term brightening effect in the GHI
+data of Thessaloniki for the period 1993 -- 2023, which for clear-sky data was
+attributed to long-term changes in aerosol effects.
+
+In order to better incorporate this change, we used, estimations of AOD change
 derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change of

### 2024-06-09 article/article.tex
Commit 2024-06-09 19:11

@@
 the Cimel sun photometer that belongs to the Aerosol Robotic Network
-(AERONET) \citep{Giles2019, Buis1998}. The mean monthly AOD on different
-wavelengths are provided by AERONET, along with the equivalent water
-column height in the atmosphere.
+(AERONET) \citep{Giles2019, Buis1998}. From the observations in the
+period 2003 -- 2023 we calculated the monthly climatological means and
+standard deviation (\(\sigma\)) for the aerosol optical depth (AOD) at
+\(500\,\text{nm}\) and the equivalent height of the water column (WC).
+The monthly climatological values of AOD and water column, as well as
+combinations with additional offsets of \(\pm1\sigma\) and
+\(\pm2\sigma\) , were used as inputs to the RTM in the construction of
+the LUT.
 
-For the atmospheric characteristics, we iterated on combinations of AOD
-at \(500\,\text{nm}\) (\(\tau_{500\text{nm}}\)) with additional offsets
-of \(\pm1\) and \(\pm2\sigma\), and water column (\(w\)), also with
-offsets of \(\pm1\) and \(\pm2\sigma\).
+For each measurement of the dataset, we calculated from the LUT a
+\(\text{GHI}_\text{ref}\) value for the respective season and SZA (by
+linear interpolation), and for the climatological values of AOD and WC
+of the respective month. The same procedure was followed for the
+estimation of the \(\text{GHI}_\text{ref}\) for all combinations of the
+AOD and WC with the above mentioned standard deviation offsets. Finally,
+each \(\text{GHI}_\text{ref}\) value was adjusted to the actual
+Sun-Earth distance derived by the Astropy software library
+\citep{AstropyCollaboration2022}.
 
@@
 
-The above clear sky reference values are not enough to describe the long
-term variation, due to the changes of the atmospheric constituents,
-mainly AOD. As observed by \citet{Natsis2023}, there is a long term
-brightening effect, over Thessaloniki for the studied period. In order
-to better incorporate this change, we used, estimations of AOD change
-derived from two sources. For 1993 -- 2005, \citet{Kazadzis2007} have
-found a change of \(-3.8\,\%\) per year at AOD on \(340\,\text{nm}\),
-using a Brewer spectrophotometer. For 2005 to 2023, we derived the trend
-from the available monthly climatological data of AERONET.
+The above clear sky reference values are based on the climatological AOD
+and WC, hence they cannot describe accurately the long term variation of
+\(\text{GHI}_\text{ref}\) due to changes in the two atmospheric
+constituents, mainly AOD. As reported by \citet{Natsis2023}, there is a
+long term brightening effect in the GHI data of Thessaloniki for the
+period 1993 -- 2023, which for clear-sky data was attributed to
+long-term changes in aerosol effects. In order to better incorporate
+this change, we used, estimations of AOD change derived from two
+sources. For 1993 -- 2005, \citet{Kazadzis2007} have found a change of
+\(-3.8\,\%\) per year at AOD on \(340\,\text{nm}\), using a Brewer
+spectrophotometer. For 2005 to 2023, we derived the trend from the
+available monthly climatological data of AERONET.
 

### 2024-06-09 article/article.Rmd
Commit 2024-06-09 20:15

@@
 <!-- Aerosol change -->
-The above clear sky reference values are based on the climatological AOD and WC,
-hence they cannot describe accurately the long term variation of
-$\text{GHI}_\text{ref}$ due to changes in the two atmospheric constituents, mainly
-AOD.  As reported by @Natsis2023, there is a long term brightening effect in the GHI
-data of Thessaloniki for the period 1993 -- 2023, which for clear-sky data was
-attributed to long-term changes in aerosol effects.
-
-In order to better incorporate this change, we used, estimations of AOD change
+The above clear sky reference values are not enough to describe the long term
+variation, due to the changes of the atmospheric constituents, mainly AOD. As observed by
+@Natsis2023, there is a long term brightening effect, over Thessaloniki for the studied
+period. In order to better incorporate this change, we used, estimations of AOD change
 derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change of

### 2024-06-09 article/article.tex
Commit 2024-06-09 20:15

@@
 
-The above clear sky reference values are based on the climatological AOD
-and WC, hence they cannot describe accurately the long term variation of
-\(\text{GHI}_\text{ref}\) due to changes in the two atmospheric
-constituents, mainly AOD. As reported by \citet{Natsis2023}, there is a
-long term brightening effect in the GHI data of Thessaloniki for the
-period 1993 -- 2023, which for clear-sky data was attributed to
-long-term changes in aerosol effects. In order to better incorporate
-this change, we used, estimations of AOD change derived from two
-sources. For 1993 -- 2005, \citet{Kazadzis2007} have found a change of
-\(-3.8\,\%\) per year at AOD on \(340\,\text{nm}\), using a Brewer
-spectrophotometer. For 2005 to 2023, we derived the trend from the
-available monthly climatological data of AERONET.
+The above clear sky reference values are not enough to describe the long
+term variation, due to the changes of the atmospheric constituents,
+mainly AOD. As observed by \citet{Natsis2023}, there is a long term
+brightening effect, over Thessaloniki for the studied period. In order
+to better incorporate this change, we used, estimations of AOD change
+derived from two sources. For 1993 -- 2005, \citet{Kazadzis2007} have
+found a change of \(-3.8\,\%\) per year at AOD on \(340\,\text{nm}\),
+using a Brewer spectrophotometer. For 2005 to 2023, we derived the trend
+from the available monthly climatological data of AERONET.
 

### 2024-06-09 article/article.Rmd
Commit 2024-06-09 21:11

--- 2024-06-09 article/article.Rmd
@@
 
+BR <- readRDS("~/MANUSCRIPTS/02_enhancement/data/Model_CS_trend.Rds")
+BR <-  unique(BR[typer == "BR SZA 55", .(year, pw_avg_mm, b, a)])
 ```
@@
 data of Thessaloniki for the period 1993 -- 2023, which for clear-sky data was
-attributed to long-term changes in aerosol effects.
+attributed to long-term changes in aerosol effects.  Therefore, an adjustment of the
+$\text{GHI}_\text{ref}$ used in this study is necessary. As AERONET data start only
+in 2003, we used for the period 1993 -– 2005 estimates of changes in AOD at
+$340\,\text{nm}$ derived from a collocated Brewer spectrophotometer derived from two
+sources. For 1993 -- 2005 [@Kazadzis2007] to calculate the trend in
+$\text{GHI}_\text{ref}$ during this period.
 
-In order to better incorporate this change, we used, estimations of AOD change
-derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change of
+<!--
 $-3.8\,\%$ per year at AOD on $340\,\text{nm}$, using a Brewer spectrophotometer. For
-2005 to 2023, we derived the trend from the available monthly climatological data of AERONET.
+-->
 
@@
 simulated the values of AOD derived from those sources with Libradtran. For both
-inputs, we
-used the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
-coefficients. We choose the SZA of $55^\circ$ as a representative value for all the
-runs.
+inputs, we used the AOD at $500\,\text{nm}$, which was inferred by the available
+Ångström coefficients. We choose the SZA of $55^\circ$ as a representative value for
+all the runs.
 
-According to @Kazadzis2007, in the period 1997 -- 2005, the mean AOD of
-$340\,\text{nm}$ was calculated to $0.403$ with the use of a Brewer
-spectrophotometer, with a linear trend of $-3.8±0.93\,\%$ per year.  This corresponds
-to a change of $0.0153$ per year for the AOD of $340\,\text{nm}$ .  Using the alpha Ångström
-coefficient of $\alpha = 1.6$, this translates to a change in Ångström beta
-coefficient of $\beta=0.00272$ per year (or $\beta=0.084$ in 1997 and $\beta=0.059$
-in 2005).  By interpolating the resulting clear sky irradiance, we have a trend of
+According to this study, in the period 1997 -- 2005, the mean AOD at $340\,\text{nm}$
+$0.403$ with a trend of $-3.8±0.93\,\%$ per year, corresponding to a change of
+$0.0153$ per year.  Using an Ångström coefficient $\alpha = 1.6$, this translates to
+a change in the Ångström coefficient $\beta=0.00272$ per year (or $\beta=0.084$ in
+1997 and $\beta=0.059$
+in 2005).
+
+Simulations with uvspec for the above Ångström coefficients, with WC of $`r
+round(BR[year==1997, pw_avg_mm],1)`\,\text{mm}$ and $`r round(BR[year==2005,
+pw_avg_mm],1)`\,\text{mm}$ for 1997 and 2005 respectively and for a SZA of $55^\circ$
+
+By interpolating the resulting clear sky irradiance, we have a trend of
 $+0.21\,\%$ per year for the clear sky irradiance.  For the period 2005 -- 2005 we

### 2024-06-09 article/article.tex
Commit 2024-06-09 21:11

--- 2024-06-09 article/article.tex
@@
 period 1993 -- 2023, which for clear-sky data was attributed to
-long-term changes in aerosol effects. In order to better incorporate
-this change, we used, estimations of AOD change derived from two
-sources. For 1993 -- 2005, \citet{Kazadzis2007} have found a change of
-\(-3.8\,\%\) per year at AOD on \(340\,\text{nm}\), using a Brewer
-spectrophotometer. For 2005 to 2023, we derived the trend from the
-available monthly climatological data of AERONET.
+long-term changes in aerosol effects. Therefore, an adjustment of the
+\(\text{GHI}_\text{ref}\) used in this study is necessary. As AERONET
+data start only in 2003, we used for the period 1993 -\/-- 2005
+estimates of changes in AOD at \(340\,\text{nm}\) derived from a
+collocated Brewer spectrophotometer derived from two sources. For 1993
+-- 2005 \citep{Kazadzis2007} to calculate the trend in
+\(\text{GHI}_\text{ref}\) during this period.
 
@@
 
-According to \citet{Kazadzis2007}, in the period 1997 -- 2005, the mean
-AOD of \(340\,\text{nm}\) was calculated to \(0.403\) with the use of a
-Brewer spectrophotometer, with a linear trend of \(-3.8±0.93\,\%\) per
-year. This corresponds to a change of \(0.0153\) per year for the AOD of
-\(340\,\text{nm}\) . Using the alpha Ångström coefficient of
-\(\alpha = 1.6\), this translates to a change in Ångström beta
-coefficient of \(\beta=0.00272\) per year (or \(\beta=0.084\) in 1997
-and \(\beta=0.059\) in 2005). By interpolating the resulting clear sky
-irradiance, we have a trend of \(+0.21\,\%\) per year for the clear sky
-irradiance. For the period 2005 -- 2005 we used the mean monthly values
-from AERONET, with a similar simulation scheme. We computed the trend of
-clear sky radiation for each month of the year, which gave us a mean
-clear sky radiation trend of \(+0.14\,\%\) per year. We applied this
-long term change to the clear sky irradiance, in order to create a more
-realistic representation of the irradiance for the whole study period
+According to this study, in the period 1997 -- 2005, the mean AOD at
+\(340\,\text{nm}\) \(0.403\) with a trend of \(-3.8±0.93\,\%\) per year,
+corresponding to a change of \(0.0153\) per year. Using an Ångström
+coefficient \(\alpha = 1.6\), this translates to a change in the
+Ångström coefficient \(\beta=0.00272\) per year (or \(\beta=0.084\) in
+1997 and \(\beta=0.059\) in 2005).
+
+Simulations with uvspec for the above Ångström coefficients, with WC of
+\(`r round(BR[year==1997, pw_avg_mm],1)`\,\text{mm}\) and
+\(15.4\,\text{mm}\) for 1997 and 2005 respectively and for a SZA of
+\(55^\circ\)
+
+By interpolating the resulting clear sky irradiance, we have a trend of
+\(+0.21\,\%\) per year for the clear sky irradiance. For the period 2005
+-- 2005 we used the mean monthly values from AERONET, with a similar
+simulation scheme. We computed the trend of clear sky radiation for each
+month of the year, which gave us a mean clear sky radiation trend of
+\(+0.14\,\%\) per year. We applied this long term change to the clear
+sky irradiance, in order to create a more realistic representation of
+the irradiance for the whole study period
 (Figure\nobreakspace{}\ref{fig:CS-change}).

### 2024-06-09 article/article.tex
Commit 2024-06-09 22:17

@@
 According to this study, in the period 1997 -- 2005, the mean AOD at
-\(340\,\text{nm}\) \(0.403\) with a trend of \(-3.8±0.93\,\%\) per year,
-corresponding to a change of \(0.0153\) per year. Using an Ångström
-coefficient \(\alpha = 1.6\), this translates to a change in the
-Ångström coefficient \(\beta=0.00272\) per year (or \(\beta=0.084\) in
-1997 and \(\beta=0.059\) in 2005).
-
-Simulations with uvspec for the above Ångström coefficients, with WC of
-\(`r round(BR[year==1997, pw_avg_mm],1)`\,\text{mm}\) and
+\(340\,\text{nm}\) \(0.403\) with a trend of \(-3.8\pm0.93\,\%\) per
+year, corresponding to a change of \(0.0153\) per year. Using an
+Ångström coefficient \(\alpha = 1.6\), this translates to a change in
+the Ångström coefficient \(\beta=0.00272\) per year (or \(\beta=0.084\)
+in 1997 and \(\beta=0.059\) in 2005). Simulations with uvspec for the
+above Ångström coefficients, with WC of \(15.7\,\text{mm}\) and
 \(15.4\,\text{mm}\) for 1997 and 2005 respectively and for a SZA of
-\(55^\circ\)
-
-By interpolating the resulting clear sky irradiance, we have a trend of
-\(+0.21\,\%\) per year for the clear sky irradiance. For the period 2005
--- 2005 we used the mean monthly values from AERONET, with a similar
-simulation scheme. We computed the trend of clear sky radiation for each
-month of the year, which gave us a mean clear sky radiation trend of
-\(+0.14\,\%\) per year. We applied this long term change to the clear
-sky irradiance, in order to create a more realistic representation of
-the irradiance for the whole study period
-(Figure\nobreakspace{}\ref{fig:CS-change}).
+\(55^\circ\) reveal trend of \(+0.21\,\%\) per year in
+\(\text{GHI}_\text{ref}\). The SZA of \(55^\circ\) was chosen as
+representative of all days in the year in order to get a rough estimate
+of the annually averaged change in clear sky irradiance. For the period
+2005 -- 2023 we used the mean monthly values of AOD and WC from AERONET
+in a similar simulation scheme to calculate the monthly mean of clear
+sky irradiance, and finally the trend of \(+0.14\,\%\) per year. We
+applied these two long term changes (see
+Figure\nobreakspace{}\ref{fig:CS-change}) to the climatological
+\(\text{GHI}_\text{ref}\), in order to create a more realistic
+representation of the clear-sky irradiance for the whole period of
+study.
 
@@
 
-\caption{Simulated long term change of the clear sky irradiance relevant to its climatological values, due to changed of AOD.}\label{fig:CS-change}
+\caption{Simulated long term change in clear sky irradiance relative to the climatological values due to changes in AOD.}\label{fig:CS-change}
 \end{figure}
 
-\hypertarget{ce-criteria-investigation}{%
-\subsection{CE Criteria investigation}\label{ce-criteria-investigation}}
+\hypertarget{criteria-for-the-identification-of-ce-events}{%
+\subsection{Criteria for the identification of CE
+events}\label{criteria-for-the-identification-of-ce-events}}
 
-Our main focus was to positively identify over irradiance events related
-to CEs. For this reason we had to select an appropriate set of
-atmospheric parameterization, in Libradtran, and define an relevant
-threshold for the CE identification. The selection of the atmospheric
-parameterization will provide us with a reference, that has a good
-agreement with the clear sky conditions. Additional, with the
-implementation of the long term change of AOD, as described above, it
-will be able to align well with most of the natural variation of the
-physical quantity. The selection of adequate threshold, will allow us to
-have a robust method to distinguish the CE cases, which will compensate
-for the limited accuracy of the input data, and the natural variability
-of the atmosphere.
+In this study our main focus was to quantify over irradiance events
+related to CEs. A key issue for achieving this goal is to define a
+threshold for the CE identification, representative of the clear-sky
+irradiance at the time of each GHI measurement. This depends on the
+selection of the appropriate atmospheric parameterization for the RTM
+simulations. The implementation of the long term change of AOD,
+discussed in section\nobreakspace{}\ref{rtmcs}, allows capturing a large
+part of the natural variability of clear-sky GHI. However, the
+short-term variability of AOD cannot be taken adequately into account
+when using monthly values for the model simulations. We tried different
+approaches to increase the robustness of the methodology and compensate
+for the limited accuracy of the RTM input data and the unpredictable
+natural variability of the atmosphere.
 
-First, we evaluated the performance of the modelled clear radiation, for
-each of the atmospheric level of clearness we have created as reference,
-in relation to the measured GHI data, and choose as a representative of
-the clear sky radiation, the case where
+First, we evaluated the performance of the modelled
+\(\text{GHI}_\text{ref}\) in relation to the measured GHI for different
+levels of atmospheric clearness, by using in the RTM the monthly
+climatological AOD and WC, less their respective standard deviations.
+the atmospheric level of clearness we have created as reference, in
+relation to the measured GHI data, and choose as a representative of the
+clear sky radiation, the case where
 \(\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma\) and

### 2024-06-09 article/article.Rmd
Commit 2024-06-09 22:17

@@
 According to this study, in the period 1997 -- 2005, the mean AOD at $340\,\text{nm}$
-$0.403$ with a trend of $-3.8±0.93\,\%$ per year, corresponding to a change of
+$0.403$ with a trend of $-3.8\pm0.93\,\%$ per year, corresponding to a change of
 $0.0153$ per year.  Using an Ångström coefficient $\alpha = 1.6$, this translates to
 a change in the Ångström coefficient $\beta=0.00272$ per year (or $\beta=0.084$ in
-1997 and $\beta=0.059$
-in 2005).
+1997 and $\beta=0.059$ in 2005).  Simulations with uvspec for the above Ångström
+coefficients, with WC of
+$`r round(BR[year==1997,pw_avg_mm],1)`\,\text{mm}$ and 
+$`r round(BR[year==2005,pw_avg_mm],1)`\,\text{mm}$
+for 1997 and 2005 respectively and for a SZA of $55^\circ$ reveal trend of
+$+0.21\,\%$ per year in $\text{GHI}_\text{ref}$. 
+The SZA of $55^\circ$ was chosen as representative of all days in the year in order
+to get a rough estimate of the annually averaged change in clear sky irradiance.  For
+the period 2005 -- 2023 we used the mean monthly values of AOD and WC from AERONET in
+a similar simulation scheme to calculate the monthly mean of clear sky irradiance,
+and finally the trend of $+0.14\,\%$ per year. We applied these two long term changes
+(see Figure\nobreakspace{}\ref{fig:CS-change}) to the climatological
+$\text{GHI}_\text{ref}$, in order to create a more realistic representation of the
+clear-sky irradiance for the whole period of study.
 
-Simulations with uvspec for the above Ångström coefficients, with WC of $`r
-round(BR[year==1997, pw_avg_mm],1)`\,\text{mm}$ and $`r round(BR[year==2005,
-pw_avg_mm],1)`\,\text{mm}$ for 1997 and 2005 respectively and for a SZA of $55^\circ$
-
-By interpolating the resulting clear sky irradiance, we have a trend of
-$+0.21\,\%$ per year for the clear sky irradiance.  For the period 2005 -- 2005 we
-used the mean monthly values from AERONET, with a similar simulation scheme. We
-computed the trend of clear sky radiation for each month of the year, which gave us a
-mean clear sky radiation trend of $+0.14\,\%$ per year. We applied this long term
-change to the clear sky irradiance, in order to create a more realistic
-representation of the irradiance for the whole study period
-(Figure\nobreakspace{}\ref{fig:CS-change}).
-
-```{r CS-change, echo=FALSE, fig.cap="Simulated long term change of the clear sky irradiance relevant to its climatological values, due to changed of AOD."}
-knitr::include_graphics("../images/P-CS-change-1.png")
+```{r CS-change, echo=FALSE, fig.cap="Simulated long term change in clear sky irradiance relative to the climatological values due to changes in AOD."}
+knitr::include_graphics("../images/P-CS-change-1.pdf")
 ```
@@
 
-## CE Criteria investigation
+## Criteria for the identification of CE events
 
-Our main focus was to positively identify over irradiance events related to CEs.  For
-this reason we had to select an appropriate set of atmospheric parameterization, in
-Libradtran, and define an relevant threshold for the CE identification.  The
-selection of the atmospheric parameterization will provide us with a reference, that
-has a good agreement with the clear sky conditions. Additional, with the
-implementation of the long term change of AOD, as described above, it will be able to align
-well with most of the natural variation of the physical quantity.  The selection of
-adequate threshold, will allow us to have a robust method to distinguish the CE
-cases, which will compensate for the limited accuracy of the input data, and the
-natural variability of the atmosphere.
+In this study our main focus was to quantify over irradiance events related to CEs. A
+key issue for achieving this goal is to  define a threshold for the CE
+identification, representative of the clear-sky irradiance at the time of each GHI
+measurement. This depends on the selection of the appropriate atmospheric
+parameterization for the RTM simulations. The implementation of the long term change
+of AOD, discussed in section\nobreakspace{}\ref{rtmcs}, allows capturing a large part
+of the natural variability of clear-sky GHI. However, the short-term variability of
+AOD cannot be taken adequately into account when using monthly values for the model
+simulations. We tried different approaches to increase the robustness of the
+methodology and compensate for the limited accuracy of the RTM input data and the
+unpredictable natural variability of the atmosphere.
 
-First, we evaluated the performance of the modelled clear radiation, for each of
+First, we evaluated the performance of the modelled $\text{GHI}_\text{ref}$ in
+relation to the measured GHI for different levels of atmospheric clearness, by using
+in the RTM the monthly climatological AOD and WC, less their respective standard
+deviations.
 the atmospheric level of clearness we have created as reference, in relation to the

### 2024-06-09 article/article.Rmd
Commit 2024-06-09 23:11

@@
 deviations.
-the atmospheric level of clearness we have created as reference, in relation to the
-measured GHI data, and choose as a representative of the clear sky radiation, the
-case where
-$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
-($\text{GHI}_\text{CSm}$).
-These values represent a typical atmosphere in Thessaloniki, with low load of
+<!-- $\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
+($\text{GHI}_\text{CSm}$). -->
+These values represent typical atmosphere in Thessaloniki, with lower than average load of
 aerosols and humidity, which are the main factor that attenuate the GHI, excluding
-clouds.  To create the upper limit of CE identification, we used a value relative to
+clouds. 
+To create the upper limit of CE identification, we used a value relative to
 clear sky irradiance

### 2024-06-09 article/article.tex
Commit 2024-06-09 23:11

@@
 climatological AOD and WC, less their respective standard deviations.
-the atmospheric level of clearness we have created as reference, in
-relation to the measured GHI data, and choose as a representative of the
-clear sky radiation, the case where
-\(\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma\) and
-\(w_{h\text{cs}} = w_h - 1\sigma\) (\(\text{GHI}_\text{CSm}\)). These
-values represent a typical atmosphere in Thessaloniki, with low load of
-aerosols and humidity, which are the main factor that attenuate the GHI,
-excluding clouds. To create the upper limit of CE identification, we
-used a value relative to clear sky irradiance (\(4\,\%\)) with an
-additional constant offset of \(15\,\text{W}/\text{m}^2\), as described
-in Equation\nobreakspace\ref{eq:CE4}). \begin{equation}
+These values represent typical atmosphere in Thessaloniki, with lower
+than average load of aerosols and humidity, which are the main factor
+that attenuate the GHI, excluding clouds. To create the upper limit of
+CE identification, we used a value relative to clear sky irradiance
+(\(4\,\%\)) with an additional constant offset of
+\(15\,\text{W}/\text{m}^2\), as described in
+Equation\nobreakspace\ref{eq:CE4}). \begin{equation}
 \text{CE} : \text{E}_\text{i} > 15 + 1.04 \cdot \text{E}_\text{CSm,i} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}

### 2024-06-10 GHI_enh_04_investigate.tex
Commit 2024-06-07 15:12
Commit 2024-06-10 11:11

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Enhancement of SDR in Thessaloniki},
-  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
-  colorlinks=true,
-  linkcolor={Maroon},
-  filecolor={Maroon},
-  citecolor={Blue},
-  urlcolor={Blue},
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
@@
 \fi
+\usepackage{bookmark}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same}
+\hypersetup{
+  pdftitle={Enhancement of SDR in Thessaloniki},
+  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
+  colorlinks=true,
+  linkcolor={Maroon},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
 
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-06-07}
+\date{2024-06-10}
 
@@
 
-\hypertarget{daily-trends}{%
-\subsubsection{Daily Trends}\label{daily-trends}}
+\subsubsection{Daily Trends}\label{daily-trends}
 
@@
 
-\hypertarget{group-stats}{%
-\subsubsection{Group stats}\label{group-stats}}
+\subsubsection{Group stats}\label{group-stats}
 
@@
 \begin{verbatim}
-Warning: Removed 23 rows containing missing values or values outside the scale
-range (`geom_bar()`).
+Warning: Removed 23 rows containing missing values or values outside the scale range
+(`geom_bar()`).
 \end{verbatim}
@@
 
-\hypertarget{zhang2018}{%
-\subsection{@Zhang2018}\label{zhang2018}}
+\subsection{@Zhang2018}\label{zhang2018}
 
@@
 \begin{verbatim}
-Warning: Removed 1 row containing missing values or values outside the scale
-range (`geom_tile()`).
+Warning: Removed 1 row containing missing values or values outside the scale range
+(`geom_tile()`).
 \end{verbatim}
@@
 
-\hypertarget{climatoogy}{%
-\section{Climatoogy}\label{climatoogy}}
+\section{Climatoogy}\label{climatoogy}
 
@@
 
-\hypertarget{monthly-ce}{%
-\subsection{Monthly CE}\label{monthly-ce}}
+\subsection{Monthly CE}\label{monthly-ce}
 
@@
 
-\hypertarget{monthly-weighted-ce}{%
-\subsection{Monthly weighted CE}\label{monthly-weighted-ce}}
+\subsection{Monthly weighted CE}\label{monthly-weighted-ce}
 
@@
 
-\hypertarget{monthly-extreme-ce-raw}{%
-\subsection{Monthly extreme CE raw}\label{monthly-extreme-ce-raw}}
+\subsection{Monthly extreme CE raw}\label{monthly-extreme-ce-raw}
 
@@
 
-\hypertarget{monthly-extreme-ce}{%
-\subsection{Monthly extreme CE}\label{monthly-extreme-ce}}
+\subsection{Monthly extreme CE}\label{monthly-extreme-ce}
 
@@
 
-\hypertarget{monthly-weighted-extreme-ce}{%
-\subsection{Monthly weighted extreme CE}\label{monthly-weighted-extreme-ce}}
+\subsection{Monthly weighted extreme CE}\label{monthly-weighted-extreme-ce}
 
@@
 
-\hypertarget{energy-contribution-of-enhancements}{%
-\subsubsection{Energy contribution of enhancements}\label{energy-contribution-of-enhancements}}
+\subsubsection{Energy contribution of enhancements}\label{energy-contribution-of-enhancements}
 
@@
 
-\hypertarget{yearly-trends}{%
-\subsection{Yearly trends}\label{yearly-trends}}
+\subsection{Yearly trends}\label{yearly-trends}
 
@@
 
-\hypertarget{yearly-trends-month-weighted}{%
-\subsection{Yearly trends month weighted}\label{yearly-trends-month-weighted}}
+\subsection{Yearly trends month weighted}\label{yearly-trends-month-weighted}
 
@@
 \end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-10}
+
+}
+
+\caption{ - empty caption - }\label{fig:rel-energy-10}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-11}
+
+}
+
+\caption{ - empty caption - }\label{fig:rel-energy-11}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-12}
+
+}
+
+\caption{ - empty caption - }\label{fig:rel-energy-12}
+\end{figure}
 
@@
 \begin{verbatim}
-2024-06-07 08:51:14.3 athan@tyler GHI_enh_04_investigate.R 1.824008 mins
+2024-06-10 07:18:04.5 athan@tyler GHI_enh_04_investigate.R 1.775136 mins
 \end{verbatim}

### 2024-06-10 GHI_enh_04_investigate.R
Commit 2024-06-10 11:11

@@ -1738,7 +1738,11 @@ plot(ST_monthly[, All_N,          month], main = "All data")
 
 plot(ST_monthly[, GLB_ench.N_pos, month], main = "CE N")
 
+plot(ST_monthly[, All_NBIO,       month], main = "All data above elevation 12")
 
+plot(ST_monthly[, wattGLB.N, month], main = "GHI Observations")
+
+plot(ST_monthly[, wattGLB.N/All_NBIO,       month], main = "MW above elevation 12")
 
 
 #' **END**

### 2024-06-10 GHI_enh_04_investigate.tex
Commit 2024-06-10 13:11

--- 2024-06-07 GHI_enh_04_investigate.tex
@@
 
-lmY: 95.37747 +/- 25.54612
+lmY: 116.3147 +/- 30.85223
 
@@
 
-lmY: 37.11864 +/- 8.427722
+lmY: 45.55073 +/- 10.16657
 
@@
 \begin{verbatim}
-2024-06-07 08:51:14.3 athan@tyler GHI_enh_04_investigate.R 1.824008 mins
+2024-06-10 09:43:05.7 athan@tyler GHI_enh_04_investigate.R 3.417696 mins
 \end{verbatim}

### 2024-06-11 article/article.tex
Commit 2024-06-11 09:11

@@
 
-According to this study, in the period 1997 -- 2005, the mean AOD at
+According to this study, in the period 1997 -- 2005 the mean AOD at
 \(340\,\text{nm}\) \(0.403\) with a trend of \(-3.8\pm0.93\,\%\) per
@@
 than average load of aerosols and humidity, which are the main factor
-that attenuate the GHI, excluding clouds. To create the upper limit of
-CE identification, we used a value relative to clear sky irradiance
-(\(4\,\%\)) with an additional constant offset of
-\(15\,\text{W}/\text{m}^2\), as described in
-Equation\nobreakspace\ref{eq:CE4}). \begin{equation}
+that attenuate the GHI, excluding clouds. With this approach the
+simulated \(\text{GHI}_\text{ref}\) should be generally greater than the
+measured GHI when aerosols are more abundant. To compensate for this, we
+increased the \(\text{GHI}_\text{ref}\) by (\(4\,\%\)) with an
+additional constant offset of \(15\,\text{W}/\text{m}^2\), as described
+in Equation\nobreakspace\ref{eq:CE4}. \begin{equation}
 \text{CE} : \text{E}_\text{i} > 15 + 1.04 \cdot \text{E}_\text{CSm,i} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
@@
 
-In the process of defining the above details, we implemented an
-empirical method, by manual inspection of the CE identification results,
-on selected days from the whole dataset. We used seven sets of days,
-with characteristics relevant to the efficiency of the identification
-threshold. These sets were random groups of about 20 to 30 days with the
+These values were determined through the implementation of an empirical
+method with manual inspection of the CE identification results on
+selected days of the whole dataset. We used seven sets of days with
+characteristics relevant to the efficiency of the identification
+threshold. These sets were random groups of about 20 -- 30 days with the
 following characteristics: (a) the strongest over irradiance CE events,
@@
 with at least \(60\,\%\) of the day length without clouds and presence
-of EC events, (h) random selected days and (i) some manual selected days
-that were included during the manual inspection process. Where it was
-needed, for some of the edge cases, we also used images from a sky-cam,
-to further aid the decisions of the manual inspection.
+of EC events, (h) randomly selected days and (i) manually selected days.
+Where needed in some of the edge cases, we also used images from a
+sky-camera to further aid the decision of the manual inspection.
 
-The definition of the CE events with this method, has a level of
-subjectivity. The actual clear sky irradiance, is not known, and can
-only be approximated. Although, because our main focus is to be able to
-identify the OIR created by the clouds, we expect that we were able to
-detect all the major events of OIR due to CE. Where, some CE events,
-with very low OIR, may be not detected, these are few and their
-magnitude will not effect our results.
+The definition of the CE events with this method has a degree of
+subjectivity, since the actual clear sky irradiance, is not known, and
+can only be approximated. However, this method is capable in detecting
+all major CE events. Where, some CE events, with very low OIR may be not
+detected, these are few with small over-irradiance and it is unlikely
+that will effect significantly our results.
 
-Another aspect of the CE events, that is often reported in the relative
+A sub-category of the CE events that is often discussed in the relevant
 bibliography, are cases of extreme cloud enhancement (ECE). These are

### 2024-06-11 article/article.Rmd
Commit 2024-06-11 09:11

@@
 
-According to this study, in the period 1997 -- 2005, the mean AOD at $340\,\text{nm}$
+According to this study, in the period 1997 -- 2005 the mean AOD at $340\,\text{nm}$
 $0.403$ with a trend of $-3.8\pm0.93\,\%$ per year, corresponding to a change of
@@
 ($\text{GHI}_\text{CSm}$). -->
-These values represent typical atmosphere in Thessaloniki, with lower than average load of
-aerosols and humidity, which are the main factor that attenuate the GHI, excluding
-clouds. 
-To create the upper limit of CE identification, we used a value relative to
-clear sky irradiance
+These values represent typical atmosphere in Thessaloniki, with lower than average
+load of aerosols and humidity, which are the main factor that attenuate the GHI,
+excluding clouds.  With this approach the simulated $\text{GHI}_\text{ref}$ should be
+generally greater than the measured GHI when aerosols are more abundant.  To
+compensate for this, we increased the $\text{GHI}_\text{ref}$ by 
 ($`r 100*(C4_cs_ref_ratio-1)`\,\%$)
@@
 $`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$,
-as described in Equation\nobreakspace\ref{eq:CE4}).
+as described in Equation\nobreakspace\ref{eq:CE4}.
 \begin{equation}
@@
 
-In the process of defining the above details, we implemented an empirical method, by
-manual inspection of the CE identification results, on selected days from the whole
-dataset.  We used seven sets of days, with characteristics relevant to the efficiency
-of the identification threshold.  These sets were random groups of about 20 to 30
+These values were determined through the implementation of an empirical method with
+manual inspection of the CE identification results  on selected days of the whole
+dataset.  We used seven sets of days with characteristics relevant to the efficiency
+of the identification threshold.  These sets were random groups of about 20 -- 30
 days with the following characteristics:
@@
 (e) with at least $60\,\%$ of the day length without clouds and presence of EC events,
-(h) random selected days and
-(i) some manual selected days that were included during the manual inspection process.
-Where it was needed, for some of the edge cases, we also used images from a sky-cam,
-to further aid the decisions of the manual inspection.
+(h) randomly selected days and
+(i) manually selected days.
+Where needed in some of the edge cases, we also used images from a sky-camera
+to further aid the decision of the manual inspection.
 
@@
 
-The definition of the CE events with this method, has a level of subjectivity. The
-actual clear sky irradiance, is not known, and can only be approximated. Although,
-because our main focus is to be able to identify the OIR created by the clouds, we
-expect that we were able to detect all the major events of OIR due to CE.  Where,
-some CE events, with very low OIR, may be not detected, these are few and their magnitude
-will not effect our results.
+The definition of the CE events with this method has a degree of subjectivity, since
+the actual clear sky irradiance, is not known, and can only be approximated.
+However, this method is capable in detecting all major CE events.  Where, some CE
+events, with very low OIR may be not detected, these are few with small
+over-irradiance and it is unlikely that will effect significantly our results.
 
 <!-- extreme cases criterion -->
-Another aspect of the CE events, that is often reported in the relative bibliography,
+A sub-category  of the CE events that is often discussed in the relevant bibliography,
 are cases of extreme cloud enhancement (ECE). These are cases of CE, where the

### 2024-06-11 article/article.Rmd
Commit 2024-06-11 10:14

@@
 (e) with at least $60\,\%$ of the day length without clouds and presence of EC events,
-(h) randomly selected days and
+(h) randomly selected days, and
 (i) manually selected days.
@@
 The definition of the CE events with this method has a degree of subjectivity, since
-the actual clear sky irradiance, is not known, and can only be approximated.
+the actual clear sky irradiance, is not known and can only be approximated.
 However, this method is capable in detecting all major CE events.  Where, some CE
@@
 <!-- extreme cases criterion -->
-A sub-category  of the CE events that is often discussed in the relevant bibliography,
-are cases of extreme cloud enhancement (ECE). These are cases of CE, where the
-measured intensity of the irradiance, exceeds the equivalent TSI on the top of the
-atmosphere, and detected according to the Equation\nobreakspace{}\ref{eq:ECE}.
+A sub-category  of the CE events that is often discussed in the relevant bibliography
+[@Cordero2023; @Martins2022; @Yordanov2015], are the extreme cloud enhancement (ECE)
+events. These are cases of CE where the measured intensity of the irradiance, exceeds
+the TSI at the top of the atmosphere:
+<!--and detected according to the Equation\nobreakspace{}\ref{eq:ECE}.-->
 \begin{equation}
@@
 \end{equation}
-where: $\theta$ the solar zenith angle, $E_{\odot}$ the solar constant, $r$ the Sun -- Earth distance, and $i$ each of the one-minute observation.
+where: $\theta$ the solar zenith angle, $E_{\odot}$ the solar constant adjusted for the actual Sun -- Earth distance, and $i$ each of the one-minute observation.
 
-To give a better understanding of the CE identification procedure, we provided an
-example of the CE identification for a selected day, in the Appendix
-(Figure\nobreakspace{}\ref{fig:example-day}), where the use of the clear sky
-reference and the identification threshold are shown, along with the relevant
-measurements.  Similar, we provided an example plot of data for one year, where the
-relation of the GHI and clear sky reference is shown, along with the OIR intensity
-(Appendix Figure\nobreakspace{}\ref{fig:example-year}).
+An example of CE identification for a selected day is given, in the Appendix
+(Figure\nobreakspace{}\ref{fig:example-day}), where the clear sky reference
+irradiance and the CE and ECE identification thresholds are shown along with the
+actual GHI measurements.  Similar, we provided an example plot of data for one year,
+where the relation of the GHI and clear sky reference is shown, along with the OIR
+intensity (Appendix Figure\nobreakspace{}\ref{fig:example-year}).
+
+```{r example-day, echo=FALSE, fig.cap="Example of cloud identification for 2019-07-11.
+The green line with blue symbols depicts the measured GHI in one minute steps.
+The red line shows the modelled threshold for the detection of CE events, which are denoted with red circles.
+The black curve represents the TSI at the top of the atmosphere, adjusted for the actual Sun-Earth distance and multiplied by the cosine of the cosine of SZA.", fig.pos='H'}
+knitr::include_graphics("../images/example-days-18.png")
+```
+
+```{r example-year, echo=FALSE, fig.cap="Example of the relation of the measured GHI versus the reference clear sky irradiance for the year 2005, where the intensity of the detected over irradiance (OIR) is color coded.", fig.pos='H'}
+knitr::include_graphics("../images/example-years-13.png")
+```
 
@@
 
-```{r example-day, echo=FALSE, fig.cap="Example of cloud identification data for 2019-07-11.
-Where are denoted with red circles all the detected CE events, the cloud interaction with the GHI (blue crosses), and the thresholds of CE and the threshold of ECE events with red and black line respectively.", fig.pos='H'}
-knitr::include_graphics("../images/example-days-18.png")
-```
-
-```{r example-year, echo=FALSE, fig.cap="Example of the relation of the measured GHI versus the reference clear sky irradiance for the year 2005, where the intensity of the detected over irradiance (OIR) is color coded.", fig.pos='H'}
-knitr::include_graphics("../images/example-years-13.png")
-```
-
 <!-- # References {.unnumbered} -->

### 2024-06-11 article/article.tex
Commit 2024-06-11 10:14

@@
 with at least \(60\,\%\) of the day length without clouds and presence
-of EC events, (h) randomly selected days and (i) manually selected days.
-Where needed in some of the edge cases, we also used images from a
+of EC events, (h) randomly selected days, and (i) manually selected
+days. Where needed in some of the edge cases, we also used images from a
 sky-camera to further aid the decision of the manual inspection.
@@
 The definition of the CE events with this method has a degree of
-subjectivity, since the actual clear sky irradiance, is not known, and
+subjectivity, since the actual clear sky irradiance, is not known and
 can only be approximated. However, this method is capable in detecting
@@
 A sub-category of the CE events that is often discussed in the relevant
-bibliography, are cases of extreme cloud enhancement (ECE). These are
-cases of CE, where the measured intensity of the irradiance, exceeds the
-equivalent TSI on the top of the atmosphere, and detected according to
-the Equation\nobreakspace{}\ref{eq:ECE}. \begin{equation}
+bibliography \citep{Cordero2023, Martins2022, Yordanov2015}, are the
+extreme cloud enhancement (ECE) events. These are cases of CE where the
+measured intensity of the irradiance, exceeds the TSI at the top of the
+atmosphere: \begin{equation}
 \text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
@@
 \end{equation} where: \(\theta\) the solar zenith angle, \(E_{\odot}\)
-the solar constant, \(r\) the Sun -- Earth distance, and \(i\) each of
-the one-minute observation.
+the solar constant adjusted for the actual Sun -- Earth distance, and
+\(i\) each of the one-minute observation.
 
-To give a better understanding of the CE identification procedure, we
-provided an example of the CE identification for a selected day, in the
-Appendix (Figure\nobreakspace{}\ref{fig:example-day}), where the use of
-the clear sky reference and the identification threshold are shown,
-along with the relevant measurements. Similar, we provided an example
-plot of data for one year, where the relation of the GHI and clear sky
-reference is shown, along with the OIR intensity (Appendix
+An example of CE identification for a selected day is given, in the
+Appendix (Figure\nobreakspace{}\ref{fig:example-day}), where the clear
+sky reference irradiance and the CE and ECE identification thresholds
+are shown along with the actual GHI measurements. Similar, we provided
+an example plot of data for one year, where the relation of the GHI and
+clear sky reference is shown, along with the OIR intensity (Appendix
 Figure\nobreakspace{}\ref{fig:example-year}).
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{../images/example-days-18}
+
+}
+
+\caption{Example of cloud identification for 2019-07-11.
+The green line with blue symbols depicts the measured GHI in one minute steps.
+The red line shows the modelled threshold for the detection of CE events, which are denoted with red circles.
+The black curve represents the TSI at the top of the atmosphere, adjusted for the actual Sun-Earth distance and multiplied by the cosine of the cosine of SZA.}\label{fig:example-day}
+\end{figure}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{../images/example-years-13}
+
+}
+
+\caption{Example of the relation of the measured GHI versus the reference clear sky irradiance for the year 2005, where the intensity of the detected over irradiance (OIR) is color coded.}\label{fig:example-year}
+\end{figure}
 
@@
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{../images/example-days-18}
-
-}
-
-\caption{Example of cloud identification data for 2019-07-11.
-Where are denoted with red circles all the detected CE events, the cloud interaction with the GHI (blue crosses), and the thresholds of CE and the threshold of ECE events with red and black line respectively.}\label{fig:example-day}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{../images/example-years-13}
-
-}
-
-\caption{Example of the relation of the measured GHI versus the reference clear sky irradiance for the year 2005, where the intensity of the detected over irradiance (OIR) is color coded.}\label{fig:example-year}
-\end{figure}
-
 \bibliography{bibliography.bib}

### 2024-06-11 GHI_enh_02_ID_CE.R

@@ -748,7 +748,7 @@ for (ii in 1:nrow(vec_days)) {
 #' \FloatBarrier
 #' # Plot years with enhancement cases
 #'
-#+ example-years, echo=F, include=T, results="asis"
+#+ P-example-years, echo=F, include=T, results="asis"
 
 ## TODO plot only enhancement cases
 ## DO it with base plot
@@ -759,7 +759,9 @@ if (TEST) {
     yearstodo <- sample(yearstodo, 3)
 }
 
-pyear <- 2018
+stop()
+
+pyear <- 2005
 for (pyear in yearstodo) {
     p <-
         ggplot(DATA[year(Date) == pyear],

### 2024-06-11 article/article.Rmd
Commit 2024-06-11 11:11

@@
 
-```{r example-year, echo=FALSE, fig.cap="Example of the relation of the measured GHI versus the reference clear sky irradiance for the year 2005, where the intensity of the detected over irradiance (OIR) is color coded.", fig.pos='H'}
+```{r example-year, echo=FALSE, fig.cap="Example scatter plot of the measured GHI and the reference clear sky irradiance for the year 2005.
+The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.", fig.pos='H'}
 knitr::include_graphics("../images/example-years-13.png")

### 2024-06-11 article/article.tex
Commit 2024-06-11 11:11

@@
 
-\caption{Example of the relation of the measured GHI versus the reference clear sky irradiance for the year 2005, where the intensity of the detected over irradiance (OIR) is color coded.}\label{fig:example-year}
+\caption{Example scatter plot of the measured GHI and the reference clear sky irradiance for the year 2005.
+The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.}\label{fig:example-year}
 \end{figure}

### 2024-06-11 GHI_enh_02_ID_CE.R
Commit 2024-06-11 11:11

@@ -759,7 +759,6 @@ if (TEST) {
     yearstodo <- sample(yearstodo, 3)
 }
 
-stop()
 
 pyear <- 2005
 for (pyear in yearstodo) {
@@ -768,6 +767,7 @@ for (pyear in yearstodo) {
                aes(get(paste0(SelEnhanc,"_ref")), wattGLB)) +
         geom_point(data   = DATA[year(Date) == pyear & get(SelEnhanc) == FALSE,],
                    colour = "black",
+                   alpha  = .1,
                    na.rm  = TRUE,
                    size   = 0.2) +
         geom_point(data   = DATA[year(Date) == pyear & get(SelEnhanc) == TRUE,],

### 2024-06-11 article/article.Rmd
Commit 2024-06-11 12:14

@@
   - \captionsetup{font=small}
+  - \usepackage{subcaption}
 
@@
 
-An example of CE identification for a selected day is given, in the Appendix
-(Figure\nobreakspace{}\ref{fig:example-day}), where the clear sky reference
-irradiance and the CE and ECE identification thresholds are shown along with the
-actual GHI measurements.  Similar, we provided an example plot of data for one year,
-where the relation of the GHI and clear sky reference is shown, along with the OIR
-intensity (Appendix Figure\nobreakspace{}\ref{fig:example-year}).
+An example of CE identification for a selected day is given, in the
+Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of the clear sky
+reference irradiance and the CE and ECE identification thresholds are shown along
+with the actual GHI measurements.  In addition, we provide an example scatter plot
+between the measured and the modeled clear-sky irradiance for one year, where the CE
+and ECE events are clearly grouped above the threshold of irradiance
+(Figure\nobreakspace{}\ref{fig:example-year}).
 
@@
 The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.", fig.pos='H'}
-knitr::include_graphics("../images/example-years-13.png")
+knitr::include_graphics("../images/P-example-years-13.png")
 ```
@@
 
-Our dataset, after the data selection processing, consists of
-`r ST_total$wattGLB.N` records of GHI measurements, of which
+Following the application of the above discussed methodology to the entire dataset 
+(`r round(ST_total$wattGLB.N / 10^6,1)` million one-minute GHI measurements),
 $`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ were identified as CE events and
@@
 $`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$
-on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, and had
-the maximum value of OIR at $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
+on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, corresponding
+to OIR of $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
 <!-- The absolute strongest CE event had an OIR of 
@@
 <!-- `r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`. -->
-The relative stronger CE event was 
+The stronger CE event of
 $`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 
-clear sky threshold, on 
+clear sky threshold was observed on 
 `r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.
+In the following sections we are discussing the long-term trends and variability of the CE events as well as of the corresponding OIR and excess irradiation .
 
-## Long term trends
+## Long-term trends
 
@@
 
-```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean OIR per CE."}
-knitr::include_graphics("../images/P-energy-3.png")
-```
+<!-- ```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean OIR per CE."} -->
+<!-- knitr::include_graphics("../images/P-energy-3.png") -->
+<!-- ``` -->
 
@@
 
-```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly cloud enhancement occurrences."}
-knitr::include_graphics("../images/P-energy-2.png")
-```
+<!-- ```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly cloud enhancement occurrences."} -->
+<!-- knitr::include_graphics("../images/P-energy-2.png") -->
+<!-- ``` -->
 
@@
 
-```{r P-energy-sum, echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
-knitr::include_graphics("../images/P-energy-1.png")
-```
+<!-- ```{r P-energy-sum, echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"} -->
+<!-- knitr::include_graphics("../images/P-energy-1.png") -->
+<!-- ``` -->
 
@@
 <!-- \FloatBarrier -->
+
+\begin{figure}[h!]
+        {\centering 
+            \subfloat[All skies.\label{fig:cusumnotrendmonthly-1}]
+                {\includegraphics[width=\linewidth]{../images/P-energy-3} }\\
+            \subfloat[Clear skies.\label{fig:cusumnotrendmonthly-2}]
+                {\includegraphics[width=\linewidth]{../images/P-energy-2} }\\
+            \subfloat[Cloudy skies.\label{fig:cusumnotrendmonthly-3}]
+                {\includegraphics[width=\linewidth]{../images/P-energy-1} }
+        }
+    \caption{Time series for the period 1992 -- 2023 of (a) the yearly CE number of occurrences, (b) the yearly mean OIR and (c) the yearly excess irradiation.
+The black lines represent the linear trends on the yearly data.}\label{fig:cusumnotrendmonthly}
+\end{figure}
 

### 2024-06-11 article/article.tex
Commit 2024-06-11 12:14

@@
 \captionsetup{font=small}
+\usepackage{subcaption}
 \usepackage{booktabs}
@@
 An example of CE identification for a selected day is given, in the
-Appendix (Figure\nobreakspace{}\ref{fig:example-day}), where the clear
-sky reference irradiance and the CE and ECE identification thresholds
-are shown along with the actual GHI measurements. Similar, we provided
-an example plot of data for one year, where the relation of the GHI and
-clear sky reference is shown, along with the OIR intensity (Appendix
-Figure\nobreakspace{}\ref{fig:example-year}).
+Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of
+the clear sky reference irradiance and the CE and ECE identification
+thresholds are shown along with the actual GHI measurements. In
+addition, we provide an example scatter plot between the measured and
+the modeled clear-sky irradiance for one year, where the CE and ECE
+events are clearly grouped above the threshold of irradiance
+(Figure\nobreakspace{}\ref{fig:example-year}).
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/example-years-13}
+{\centering \includegraphics[width=1\linewidth]{../images/P-example-years-13}
 
@@
 
-Our dataset, after the data selection processing, consists of 6144534
-records of GHI measurements, of which \(1.764\,\%\) were identified as
-CE events and \(0.036\,\%\) as ECE events. The highest recorded GHI due
-to CE was \(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007, and had the
-maximum value of OIR at \(345.9\,\text{W}/\text{m}^2\). The relative
-stronger CE event was \(49.7\,\%\) above the clear sky threshold, on
-28~October 2016.
+Following the application of the above discussed methodology to the
+entire dataset (6.1 million one-minute GHI measurements), \(1.764\,\%\)
+were identified as CE events and \(0.036\,\%\) as ECE events. The
+highest recorded GHI due to CE was \(1416.6\,\text{W}/\text{m}^2\) on
+24~May 2007, corresponding to OIR of \(345.9\,\text{W}/\text{m}^2\). The
+stronger CE event of \(49.7\,\%\) above the clear sky threshold was
+observed on 28~October 2016. In the following sections we are discussing
+the long-term trends and variability of the CE events as well as of the
+corresponding OIR and excess irradiation .
 
 \hypertarget{long-term-trends}{%
-\subsection{Long term trends}\label{long-term-trends}}
+\subsection{Long-term trends}\label{long-term-trends}}
 
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../images/P-energy-3}
-
+\begin{figure}[h!]
+        {\centering 
+            \subfloat[All skies.\label{fig:cusumnotrendmonthly-1}]
+                {\includegraphics[width=\linewidth]{../images/P-energy-3} }\\
+            \subfloat[Clear skies.\label{fig:cusumnotrendmonthly-2}]
+                {\includegraphics[width=\linewidth]{../images/P-energy-2} }\\
+            \subfloat[Cloudy skies.\label{fig:cusumnotrendmonthly-3}]
+                {\includegraphics[width=\linewidth]{../images/P-energy-1} }
         }
-
-\caption{Trends of the mean OIR per CE.}\label{fig:P-energy-mean}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../images/P-energy-2}
-
-}
-
-\caption{Trend of yearly cloud enhancement occurrences.}\label{fig:P-energy-N}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../images/P-energy-1}
-
-}
-
-\caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:P-energy-sum}
+    \caption{Time series for the period 1992 -- 2023 of (a) the yearly CE number of occurrences, (b) the yearly mean OIR and (c) the yearly excess irradiation.
+The black lines represent the linear trends on the yearly data.}\label{fig:cusumnotrendmonthly}
 \end{figure}

### 2024-06-11 article/article.Rmd
Commit 2024-06-11 13:11

@@
 $`r round(BR[year==2005,pw_avg_mm],1)`\,\text{mm}$
-for 1997 and 2005 respectively and for a SZA of $55^\circ$ reveal trend of
+for 1997 and 2005 respectively and for a SZA of $55^\circ$ reveal a trend of
 $+0.21\,\%$ per year in $\text{GHI}_\text{ref}$. 
@@
 ($\text{GHI}_\text{CSm}$). -->
-These values represent typical atmosphere in Thessaloniki, with lower than average
+These values represent typical atmosphere in Thessaloniki with lower than average
 load of aerosols and humidity, which are the main factor that attenuate the GHI,
@@
 - can follow for clear days
-- this selection has some subjectivity
 - the most important are the thresholds
@@
 The definition of the CE events with this method has a degree of subjectivity, since
-the actual clear sky irradiance, is not known and can only be approximated.
-However, this method is capable in detecting all major CE events.  Where, some CE
-events, with very low OIR may be not detected, these are few with small
-over-irradiance and it is unlikely that will effect significantly our results.
+the actual clear sky irradiance is not known and can only be approximated.  However,
+this method is capable in detecting all major CE events.  Where some CE events with
+very low OIR may be not detected, these are few with small over-irradiance and it is
+unlikely that will effect significantly our results.
 
@@
 [@Cordero2023; @Martins2022; @Yordanov2015], are the extreme cloud enhancement (ECE)
-events. These are cases of CE where the measured intensity of the irradiance, exceeds
+events. These are cases of CE where the measured intensity of the irradiance exceeds
 the TSI at the top of the atmosphere:
@@
 
-An example of CE identification for a selected day is given, in the
+An example of CE identification for a selected day is given in the
 Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of the clear sky
@@
 Following the application of the above discussed methodology to the entire dataset 
-(`r round(ST_total$wattGLB.N / 10^6,1)` million one-minute GHI measurements),
+(`r round(ST_total$wattGLB.N / 10^6,1)` million of one-minute GHI measurements),
 $`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ were identified as CE events and
@@
 
-We computed the daily trend of the mean OIR of CE <!--
-(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), --> using a first-order autoregressive
-model with a lag of one day, with the 'maximum likelihood' fitting method
-[@Gardner1980; @Jones1980] by implementing the function 'arima' from the library
-'stats' of the R programming language [@RCT2023]. The trends are reported together
-with the $2\sigma$ error.  We observed a negligible change of
+The main focus of this study is to investigate the time evolution of the CE events by
+analyzing the GHI measurements at Thessaloniki. Cloud enhancements can be influenced
+by different factors, such as the geometry, size and optical thickness of clouds,
+their height in the atmosphere and on local weather regimes **!!!(ref)!!!**.  Some of
+these factors are related to changes in climate; hence it would be reasonable to
+expect capturing their contributions to the frequency of occurrence of CE events over
+Thessaloniki, as well as to the average OIR and excess irradiation. 
+The long-term trends were calculated using a first-order autoregressive model with the
+'maximum likelihood' fitting method
+[@Gardner1980; @Jones1980], by implementing the function 'arima' from the library
+'stats' of the R programming language [@RCT2023]. All trends are reported together
+with their $2\sigma$ error.
+
+We observed a negligible change of
 $`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
@@
 <!-- ``` -->
-
 <!-- ```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"} -->
@@
 <!-- ``` -->
-
 <!-- ```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean OIR per CE."} -->
@@
 <!-- ``` -->
-
 <!-- ```{r echo=FALSE, fig.cap="Trend of number of CE cases"} -->
@@
 <!-- ``` -->
-
 <!-- ```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly cloud enhancement occurrences."} -->
@@
 <!-- ``` -->
-
 <!-- ```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"} -->
@@
 <!-- ``` -->
-
 <!-- ```{r P-energy-sum, echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"} -->
@@
 <!-- ``` -->
-
 <!-- ```{r P-energy-median, echo=FALSE, fig.cap="Trend of the yearly median over irradiance due to CE over irradiance"} -->
@@
 
-\begin{figure}[h!]
+\begin{figure}% [h!]
         {\centering 
-            \subfloat[All skies.\label{fig:cusumnotrendmonthly-1}]
+            \subfloat[\label{fig:cusumnotrendmonthly-1}]
                 {\includegraphics[width=\linewidth]{../images/P-energy-3} }\\
-            \subfloat[Clear skies.\label{fig:cusumnotrendmonthly-2}]
+            \subfloat[\label{fig:P-energy-N}]
                 {\includegraphics[width=\linewidth]{../images/P-energy-2} }\\
-            \subfloat[Cloudy skies.\label{fig:cusumnotrendmonthly-3}]
+            \subfloat[\label{fig:cusumnotrendmonthly-3}]
                 {\includegraphics[width=\linewidth]{../images/P-energy-1} }
@@
 characteristics.
-
-# Appendix {.unnumbered}
-
-<!-- # References {.unnumbered} -->

### 2024-06-11 article/article.tex
Commit 2024-06-11 13:11

@@
 \(15.4\,\text{mm}\) for 1997 and 2005 respectively and for a SZA of
-\(55^\circ\) reveal trend of \(+0.21\,\%\) per year in
+\(55^\circ\) reveal a trend of \(+0.21\,\%\) per year in
 \(\text{GHI}_\text{ref}\). The SZA of \(55^\circ\) was chosen as
@@
 climatological AOD and WC, less their respective standard deviations.
-These values represent typical atmosphere in Thessaloniki, with lower
+These values represent typical atmosphere in Thessaloniki with lower
 than average load of aerosols and humidity, which are the main factor
@@
 The definition of the CE events with this method has a degree of
-subjectivity, since the actual clear sky irradiance, is not known and
-can only be approximated. However, this method is capable in detecting
-all major CE events. Where, some CE events, with very low OIR may be not
+subjectivity, since the actual clear sky irradiance is not known and can
+only be approximated. However, this method is capable in detecting all
+major CE events. Where some CE events with very low OIR may be not
 detected, these are few with small over-irradiance and it is unlikely
@@
 extreme cloud enhancement (ECE) events. These are cases of CE where the
-measured intensity of the irradiance, exceeds the TSI at the top of the
+measured intensity of the irradiance exceeds the TSI at the top of the
 atmosphere: \begin{equation}
@@
 
-An example of CE identification for a selected day is given, in the
+An example of CE identification for a selected day is given in the
 Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of
@@
 Following the application of the above discussed methodology to the
-entire dataset (6.1 million one-minute GHI measurements), \(1.764\,\%\)
-were identified as CE events and \(0.036\,\%\) as ECE events. The
-highest recorded GHI due to CE was \(1416.6\,\text{W}/\text{m}^2\) on
-24~May 2007, corresponding to OIR of \(345.9\,\text{W}/\text{m}^2\). The
-stronger CE event of \(49.7\,\%\) above the clear sky threshold was
-observed on 28~October 2016. In the following sections we are discussing
-the long-term trends and variability of the CE events as well as of the
-corresponding OIR and excess irradiation .
+entire dataset (6.1 million of one-minute GHI measurements),
+\(1.764\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
+events. The highest recorded GHI due to CE was
+\(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007, corresponding to OIR of
+\(345.9\,\text{W}/\text{m}^2\). The stronger CE event of \(49.7\,\%\)
+above the clear sky threshold was observed on 28~October 2016. In the
+following sections we are discussing the long-term trends and
+variability of the CE events as well as of the corresponding OIR and
+excess irradiation .
 
@@
 
-We computed the daily trend of the mean OIR of CE using a first-order
-autoregressive model with a lag of one day, with the `maximum
-likelihood' fitting method \citep{Gardner1980, Jones1980} by
-implementing the function `arima' from the library `stats' of the R
-programming language \citep{RCT2023}. The trends are reported together
-with the \(2\sigma\) error. We observed a negligible change of
+The main focus of this study is to investigate the time evolution of the
+CE events by analyzing the GHI measurements at Thessaloniki. Cloud
+enhancements can be influenced by different factors, such as the
+geometry, size and optical thickness of clouds, their height in the
+atmosphere and on local weather regimes \textbf{!!!(ref)!!!}. Some of
+these factors are related to changes in climate; hence it would be
+reasonable to expect capturing their contributions to the frequency of
+occurrence of CE events over Thessaloniki, as well as to the average OIR
+and excess irradiation. The long-term trends were calculated using a
+first-order autoregressive model with the `maximum likelihood' fitting
+method \citep{Gardner1980, Jones1980}, by implementing the function
+`arima' from the library `stats' of the R programming language
+\citep{RCT2023}. All trends are reported together with their \(2\sigma\)
+error.
+
+We observed a negligible change of
 \(0.087\pm 0.08\,\text{W}/\text{m}^2/\text{year}\) on the mean OIR.
@@
 
-\hypertarget{appendix}{%
-\section*{Appendix}\label{appendix}}
-\addcontentsline{toc}{section}{Appendix}
-
 \bibliography{bibliography.bib}

### 2024-06-11 article/article.Rmd
Commit 2024-06-11 19:11

@@
 
-We observed a negligible change of
-$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
-`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,\text{W}/\text{m}^2/\text{year}$
-on the mean OIR.
-<!-- ```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."} -->
-<!-- knitr::include_graphics("../images/P_daily_trend-1.png") -->
-<!-- ``` -->
+Figure\nobreakspace{}\ref{fig:P-energy} shows the time series of the yearly number of
+CE cases (each with duration of one minute), the yearly mean OIR and the yearly
+excess irradiation  for the period 1993 -- 2023, together with corresponding linear
+trends. All three quantities show increasing trends, most pronounced for the
+frequency of occurrence 
+($`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
+`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$)
+and the excess irradiation 
+($`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
+`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$),
+which are also statistically significant.
+In contrast the trend of the yearly mean OIR is negligible 
+($`r round(yearlyCE[var == "GLB_diff.mean", slope], 1)`\pm
+`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\,\text{W}/\text{m}^2/\text{year}$)
+and of no statistical significance.
+
 Although, the previous result is closer to the raw data, we preferred to present the
@@
 $`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kj}/\text{year}$
+`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$
 (Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of CE
@@
 
-<!-- \FloatBarrier -->
-
 \begin{figure}% [h!]
         {\centering 
-            \subfloat[\label{fig:cusumnotrendmonthly-1}]
+            \subfloat[\label{fig:P-energy-mean}]
                 {\includegraphics[width=\linewidth]{../images/P-energy-3} }\\
@@
                 {\includegraphics[width=\linewidth]{../images/P-energy-2} }\\
-            \subfloat[\label{fig:cusumnotrendmonthly-3}]
+            \subfloat[\label{fig:P-energy-sum}]
                 {\includegraphics[width=\linewidth]{../images/P-energy-1} }
@@
     \caption{Time series for the period 1992 -- 2023 of (a) the yearly CE number of occurrences, (b) the yearly mean OIR and (c) the yearly excess irradiation.
-The black lines represent the linear trends on the yearly data.}\label{fig:cusumnotrendmonthly}
+The black lines represent the linear trends on the yearly data.}\label{fig:P-energy}
 \end{figure}

### 2024-06-11 article/article.tex
Commit 2024-06-11 19:11

@@
 
-We observed a negligible change of
-\(0.087\pm 0.08\,\text{W}/\text{m}^2/\text{year}\) on the mean OIR.
+Figure\nobreakspace{}\ref{fig:P-energy} shows the time series of the
+yearly number of CE cases (each with duration of one minute), the yearly
+mean OIR and the yearly excess irradiation for the period 1993 -- 2023,
+together with corresponding linear trends. All three quantities show
+increasing trends, most pronounced for the frequency of occurrence
+(\(45.6\pm 21.9\,\text{cases}/\text{year}\)) and the excess irradiation
+(\(116.9\pm 67.8\,\text{kJ}/\text{year}\)), which are also statistically
+significant. In contrast the trend of the yearly mean OIR is negligible
+(\(0.1\pm 0.1\,\,\text{W}/\text{m}^2/\text{year}\)) and of no
+statistical significance.
+
 Although, the previous result is closer to the raw data, we preferred to
@@
 annual energy of the CE events is increasing with a rate of
-\(116.9\pm 67.8\,\text{kj}/\text{year}\)
+\(116.9\pm 67.8\,\text{kJ}/\text{year}\)
 (Figure~\ref{fig:P-energy-sum}), witch follows the trend of the number
@@
         {\centering 
-            \subfloat[\label{fig:cusumnotrendmonthly-1}]
+            \subfloat[\label{fig:P-energy-mean}]
                 {\includegraphics[width=\linewidth]{../images/P-energy-3} }\\

### 2024-06-11 article/article.Rmd
Commit 2024-06-11 20:14

@@
 ($`r round(yearlyCE[var == "GLB_diff.mean", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\,\text{W}/\text{m}^2/\text{year}$)
+`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\text{W}/\text{m}^2/\text{year}$)
 and of no statistical significance.
+The average OIR for the entire period is about
+$`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$ with standard
+deviation of
+$`r round(sd(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$.
+The interannual variability of the data about the trend lines is quite large.
+Furthermore, it tends to increase with time (at least for the quantities of panels b
+and c), suggesting a significant variability in cloud patterns over the area,
+possibly associated to changes in climate.
 
-Although, the previous result is closer to the raw data, we preferred to present the
-annual statistics, that give a more clear picture about the long term CE trends.
-Hence, we calculated the annual values from the one-minute measurements.  Despite the
-very weak statistical significance of the mean OIR trend, the annual number of CE
-occurrences shows a steady increase of
-$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$
-(Figure\nobreakspace{}\ref{fig:P-energy-N}).
-Subsequently, the mean annual energy of the CE events is increasing with a rate of
-$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$
-(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of CE
-occurrences.  We have to note that the energy related to the CE events can not be
-directly linked with the total energy balance of the atmosphere. The net solar
-radiation of the region is not increased, but rather redistributed through the CE
-events.  This also is depicted by the "instantaneous" values of irradiance (average
-over one minute), that can exceed the equivalent clear sky irradiance to a
-considerable level.
+We have to note that the excess irradiation related to the CE events can not be
+directly linked to the total energy balance of the atmosphere. The net solar
+radiation of the region is not increased, but is rather redistributed through the CE
+events.  This is also depicted by the ECE irradiance values, which can exceed the
+equivalent clear sky irradiance by a significant amount.
 
@@
 
-## Cloud enhancements climatology
+## Climatology of cloud enhancement events
 
-Another interesting aspect of the CE cases occurrences, is their seasonal cycle. In
+Another interesting aspect of the CE events, is their distribution within the year. In
 Figure\nobreakspace{}\ref{fig:relative-month-occurrences}, we have the monthly box plot

### 2024-06-11 article/article.tex
Commit 2024-06-11 20:14

@@
 significant. In contrast the trend of the yearly mean OIR is negligible
-(\(0.1\pm 0.1\,\,\text{W}/\text{m}^2/\text{year}\)) and of no
-statistical significance.
+(\(0.1\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of no statistical
+significance. The average OIR for the entire period is about
+\(39.9\,\text{W}/\text{m}^2\) with standard deviation of
+\(2.7\,\text{W}/\text{m}^2\). The interannual variability of the data
+about the trend lines is quite large. Furthermore, it tends to increase
+with time (at least for the quantities of panels b and c), suggesting a
+significant variability in cloud patterns over the area, possibly
+associated to changes in climate.
 
-Although, the previous result is closer to the raw data, we preferred to
-present the annual statistics, that give a more clear picture about the
-long term CE trends. Hence, we calculated the annual values from the
-one-minute measurements. Despite the very weak statistical significance
-of the mean OIR trend, the annual number of CE occurrences shows a
-steady increase of \(45.6\pm 21.9\,\text{cases}/\text{year}\)
-(Figure\nobreakspace{}\ref{fig:P-energy-N}). Subsequently, the mean
-annual energy of the CE events is increasing with a rate of
-\(116.9\pm 67.8\,\text{kJ}/\text{year}\)
-(Figure~\ref{fig:P-energy-sum}), witch follows the trend of the number
-of CE occurrences. We have to note that the energy related to the CE
-events can not be directly linked with the total energy balance of the
-atmosphere. The net solar radiation of the region is not increased, but
-rather redistributed through the CE events. This also is depicted by the
-``instantaneous'' values of irradiance (average over one minute), that
-can exceed the equivalent clear sky irradiance to a considerable level.
+We have to note that the excess irradiation related to the CE events can
+not be directly linked to the total energy balance of the atmosphere.
+The net solar radiation of the region is not increased, but is rather
+redistributed through the CE events. This is also depicted by the ECE
+irradiance values, which can exceed the equivalent clear sky irradiance
+by a significant amount.
 
@@
 
-\hypertarget{cloud-enhancements-climatology}{%
-\subsection{Cloud enhancements
-climatology}\label{cloud-enhancements-climatology}}
+\hypertarget{climatology-of-cloud-enhancement-events}{%
+\subsection{Climatology of cloud enhancement
+events}\label{climatology-of-cloud-enhancement-events}}
 
-Another interesting aspect of the CE cases occurrences, is their
-seasonal cycle. In
+Another interesting aspect of the CE events, is their distribution
+within the year. In
 Figure\nobreakspace{}\ref{fig:relative-month-occurrences}, we have the

### 2024-06-11 article/article.Rmd
Commit 2024-06-11 21:11

@@
 `r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.
-In the following sections we are discussing the long-term trends and variability of the CE events as well as of the corresponding OIR and excess irradiation .
+In the following sections we are discussing the long-term trends and variability of the CE events as well as of the corresponding OIR and excess irradiation.
 
@@
 
-Another interesting aspect of the CE events, is their distribution within the year. In
-Figure\nobreakspace{}\ref{fig:relative-month-occurrences}, we have the monthly box plot
-(whisker plot), where the values have been normalized by the highest median value,
+!!! monthly weithe !!!
+
+Another interesting aspect of the CE events is their distribution within the year.
+Figure\nobreakspace{}\ref{fig:relative-month-occurrences} shows the monthly box 
+and whisker plot of the CE number of occurrence normalized with the highest median value,
 that occurs on June.  Although the number of occurrences has a wide spread throughout

### 2024-06-11 article/article.tex
Commit 2024-06-11 21:11

@@
 variability of the CE events as well as of the corresponding OIR and
-excess irradiation .
+excess irradiation.
 
@@
 
-Another interesting aspect of the CE events, is their distribution
-within the year. In
-Figure\nobreakspace{}\ref{fig:relative-month-occurrences}, we have the
-monthly box plot (whisker plot), where the values have been normalized
-by the highest median value, that occurs on June. Although the number of
-occurrences has a wide spread throughout the study period, the most
-active period of CE occurrences is during May and June. During the
-Winter (December -- February) the CE cases are about \(25\,\%\) of the
-maximum. For the rest months, the occurrences gradually ramp between the
-maximum and minimum. This seasonality is a combinations of the clouds
-occurrences, and the relevant position of the sun during each season of
-the year. Unfortunately, the lack of detailed data on cloud formation,
-type and location is not allowing further analysis.
+!!! monthly weithe !!!
+
+Another interesting aspect of the CE events is their distribution within
+the year. Figure\nobreakspace{}\ref{fig:relative-month-occurrences}
+shows the monthly box and whisker plot of the CE number of occurrence
+normalized with the highest median value, that occurs on June. Although
+the number of occurrences has a wide spread throughout the study period,
+the most active period of CE occurrences is during May and June. During
+the Winter (December -- February) the CE cases are about \(25\,\%\) of
+the maximum. For the rest months, the occurrences gradually ramp between
+the maximum and minimum. This seasonality is a combinations of the
+clouds occurrences, and the relevant position of the sun during each
+season of the year. Unfortunately, the lack of detailed data on cloud
+formation, type and location is not allowing further analysis.
 

### 2024-06-11 article/article.Rmd
Commit 2024-06-11 22:14

@@
 
-!!! monthly weithe !!!
+!!! monthly weigth !!!
 
 Another interesting aspect of the CE events is their distribution within the year.
-Figure\nobreakspace{}\ref{fig:relative-month-occurrences} shows the monthly box 
-and whisker plot of the CE number of occurrence normalized with the highest median value,
-that occurs on June.  Although the number of occurrences has a wide spread throughout
-the study period, the most active period of CE occurrences is during May and June.
-During the Winter (December -- February) the CE cases are about $25\,\%$ of the maximum.
-For the rest months, the occurrences gradually ramp between the maximum and minimum.
-This seasonality is a combinations of the clouds occurrences, and the relevant
-position of the sun during each season of the year. Unfortunately, the lack of detailed data on cloud
-formation, type and location is not allowing further analysis.
+Figure\nobreakspace{}\ref{fig:relative-month-occurrences} shows the monthly box and
+whisker plot of the CE number of occurrence normalized with the highest median value,
+that occurs on June.  Although CE events are present  throughout the year, the most
+active period  is during May and June.  During the winter (December -- February) the
+number of CE cases is about $25\,\%$ of the maximum.  For the rest months, the
+occurrences gradually ramp between the maximum and minimum.  This seasonality is a
+combinations of the clouds occurrences, and the relevant position of the sun during
+each season of the year. Unfortunately, the lack of detailed data on cloud formation,
+type and location is not allowing further analysis.
 

### 2024-06-11 article/article.tex
Commit 2024-06-11 22:14

@@
 
-!!! monthly weithe !!!
+!!! monthly weigth !!!
 
@@
 normalized with the highest median value, that occurs on June. Although
-the number of occurrences has a wide spread throughout the study period,
-the most active period of CE occurrences is during May and June. During
-the Winter (December -- February) the CE cases are about \(25\,\%\) of
-the maximum. For the rest months, the occurrences gradually ramp between
-the maximum and minimum. This seasonality is a combinations of the
-clouds occurrences, and the relevant position of the sun during each
-season of the year. Unfortunately, the lack of detailed data on cloud
-formation, type and location is not allowing further analysis.
+CE events are present throughout the year, the most active period is
+during May and June. During the winter (December -- February) the number
+of CE cases is about \(25\,\%\) of the maximum. For the rest months, the
+occurrences gradually ramp between the maximum and minimum. This
+seasonality is a combinations of the clouds occurrences, and the
+relevant position of the sun during each season of the year.
+Unfortunately, the lack of detailed data on cloud formation, type and
+location is not allowing further analysis.
 

### 2024-06-11 article/article.Rmd
Commit 2024-06-11 23:11

@@
 whisker plot of the CE number of occurrence normalized with the highest median value,
-that occurs on June.  Although CE events are present  throughout the year, the most
-active period  is during May and June.  During the winter (December -- February) the
-number of CE cases is about $25\,\%$ of the maximum.  For the rest months, the
-occurrences gradually ramp between the maximum and minimum.  This seasonality is a
-combinations of the clouds occurrences, and the relevant position of the sun during
-each season of the year. Unfortunately, the lack of detailed data on cloud formation,
-type and location is not allowing further analysis.
+that occurs in June, depicting a clear seasonal cycle.  Although CE events are
+present  throughout the year, the most active period  is during May and June.  During
+the winter (December -- February), the number of CE cases is about $25\,\%$ of the
+maximum, while in the intermediate months, the number of occurrences gradually ramps
+between the maximum and minimum.  This seasonality is a combined effect of different
+factors, among them the types of clouds, their frequency of occurrence the seasonally
+varying relative position of the sun, as well as the local landscape characteristics
+that may influence the formation of clouds.  Unfortunately, lack of detailed data on
+cloud formation, type and location is not allowing further analysis. The interannual
+variability of the monthly CE events is quite high as manifested by the large monthly
+extremes, especially in the summer.
 
-```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal statistics of the number of CE occurrences for each month, normalized to the maximum occurrences on June.
-The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the maximum and minimum values, the dots are outlier values, and the rhombus is the mean."}
-knitr::include_graphics("../images/clim-CE-month-norm-MAX-median-N-1.png")
+```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal variability of the number of CE events normalized to the maximum occurring in June, in the form of a box and whisker plot.
+The monthly values have been also normalized to the relative abundance of valid GHI observations.
+The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles,The thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
+The vertical lines (whiskers) extend between the maximum and minimum monthly values and the solid circles are outliers."}
+knitr::include_graphics("../images/clim-CE-month-norm-MAX-median-N-MW-1.png")
 ```
@@
 
-The distribution of the OIR intensity, follows an exponential decline
-Figure\nobreakspace{}\ref{fig:ovir-distribution}, where there is an inverse relation
-between the CE events frequency and their intensity. This is expected, as the stronger
-the CE events become, the rarer the particular atmospheric and sun conditions can
+The distribution of the number of CE events as a function of OIR is shown in
+Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently, there is an inverse
+relation between the frequency of CE events  and OIR with an exponential-like
+decline. This is expected, as the stronger the CE events become, the rarer are the
+conditions favoring the occurrence of CE events. For the majority (over $60\%$) of
+the CE events the OIR is below the long term average of $40\,\text{W}/\text{m}^2$,
+while about $10\%$ of the events correspond to OIR larger than
+$100\,\text{W}/\text{m}^2$ and up to highest value of 300 W/m^2^ .
+particular atmospheric and sun conditions can
 occur. This fact, is indicative to the magnitude and the probability of the expected OIRs

### 2024-06-11 article/article.tex
Commit 2024-06-11 23:11

@@
 shows the monthly box and whisker plot of the CE number of occurrence
-normalized with the highest median value, that occurs on June. Although
-CE events are present throughout the year, the most active period is
-during May and June. During the winter (December -- February) the number
-of CE cases is about \(25\,\%\) of the maximum. For the rest months, the
-occurrences gradually ramp between the maximum and minimum. This
-seasonality is a combinations of the clouds occurrences, and the
-relevant position of the sun during each season of the year.
-Unfortunately, the lack of detailed data on cloud formation, type and
-location is not allowing further analysis.
+normalized with the highest median value, that occurs in June, depicting
+a clear seasonal cycle. Although CE events are present throughout the
+year, the most active period is during May and June. During the winter
+(December -- February), the number of CE cases is about \(25\,\%\) of
+the maximum, while in the intermediate months, the number of occurrences
+gradually ramps between the maximum and minimum. This seasonality is a
+combined effect of different factors, among them the types of clouds,
+their frequency of occurrence the seasonally varying relative position
+of the sun, as well as the local landscape characteristics that may
+influence the formation of clouds. Unfortunately, lack of detailed data
+on cloud formation, type and location is not allowing further analysis.
+The interannual variability of the monthly CE events is quite high as
+manifested by the large monthly extremes, especially in the summer.
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/clim-CE-month-norm-MAX-median-N-1}
+{\centering \includegraphics[width=1\linewidth]{../images/clim-CE-month-norm-MAX-median-N-MW-1}
 
@@
 
-\caption{Seasonal statistics of the number of CE occurrences for each month, normalized to the maximum occurrences on June.
-The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the maximum and minimum values, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurrences}
+\caption{Seasonal variability of the number of CE events normalized to the maximum occurring in June, in the form of a box and whisker plot.
+The monthly values have been also normalized to the relative abundance of valid GHI observations.
+The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles,The thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
+The vertical lines (whiskers) extend between the maximum and minimum monthly values and the solid circles are outliers.}\label{fig:relative-month-occurrences}
 \end{figure}
 
-The distribution of the OIR intensity, follows an exponential decline
-Figure\nobreakspace{}\ref{fig:ovir-distribution}, where there is an
-inverse relation between the CE events frequency and their intensity.
-This is expected, as the stronger the CE events become, the rarer the
-particular atmospheric and sun conditions can occur. This fact, is
-indicative to the magnitude and the probability of the expected OIRs
-events over Thessaloniki. Similar distribution of CE occurrences have
-been reported by \citet{Vamvakas2020}, where the magnitude of OIR were
-higher due to the location of the city of Patras, \(2.5^\circ\) closer
-to the equator.
+The distribution of the number of CE events as a function of OIR is
+shown in Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently,
+there is an inverse relation between the frequency of CE events and OIR
+with an exponential-like decline. This is expected, as the stronger the
+CE events become, the rarer are the conditions favoring the occurrence
+of CE events. For the majority (over \(60\%\)) of the CE events the OIR
+is below the long term average of \(40\,\text{W}/\text{m}^2\), while
+about \(10\%\) of the events correspond to OIR larger than
+\(100\,\text{W}/\text{m}^2\) and up to highest value of 300
+W/m\textsuperscript{2} . particular atmospheric and sun conditions can
+occur. This fact, is indicative to the magnitude and the probability of
+the expected OIRs events over Thessaloniki. Similar distribution of CE
+occurrences have been reported by \citet{Vamvakas2020}, where the
+magnitude of OIR were higher due to the location of the city of Patras,
+\(2.5^\circ\) closer to the equator.
 

### 2024-06-12 article/article.Rmd
Commit 2024-06-12 09:12

@@
 conditions favoring the occurrence of CE events. For the majority (over $60\%$) of
-the CE events the OIR is below the long term average of $40\,\text{W}/\text{m}^2$,
+the CE events the OIR is below the long term average of
+$`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$,
 while about $10\%$ of the events correspond to OIR larger than
-$100\,\text{W}/\text{m}^2$ and up to highest value of 300 W/m^2^ .
-particular atmospheric and sun conditions can
-occur. This fact, is indicative to the magnitude and the probability of the expected OIRs
-events over Thessaloniki. Similar distribution of CE occurrences have been reported
+$100\,\text{W}/\text{m}^2$ and up to highest value of 300 W/m^2^.
+This distribution is indicative of the magnitude and the probability of the expected
+CE
+events over Thessaloniki. Similar distribution of CE events, occurrences have been reported
 by @Vamvakas2020, where the magnitude of OIR were

### 2024-06-12 article/article.tex
Commit 2024-06-12 09:12

@@
 of CE events. For the majority (over \(60\%\)) of the CE events the OIR
-is below the long term average of \(40\,\text{W}/\text{m}^2\), while
+is below the long term average of \(39.9\,\text{W}/\text{m}^2\), while
 about \(10\%\) of the events correspond to OIR larger than
 \(100\,\text{W}/\text{m}^2\) and up to highest value of 300
-W/m\textsuperscript{2} . particular atmospheric and sun conditions can
-occur. This fact, is indicative to the magnitude and the probability of
-the expected OIRs events over Thessaloniki. Similar distribution of CE
-occurrences have been reported by \citet{Vamvakas2020}, where the
-magnitude of OIR were higher due to the location of the city of Patras,
-\(2.5^\circ\) closer to the equator.
+W/m\textsuperscript{2}. This distribution is indicative of the magnitude
+and the probability of the expected CE events over Thessaloniki. Similar
+distribution of CE events, occurrences have been reported by
+\citet{Vamvakas2020}, where the magnitude of OIR were higher due to the
+location of the city of Patras, \(2.5^\circ\) closer to the equator.
 

### 2024-06-12 GHI_enh_05_distributions.R
Commit 2024-06-12 09:12

@@ -114,6 +114,7 @@ if (
 ##  Load Enhancement data  -----------------------------------------------------
 
 ## load statistics
+load("./data/GHI_enh_03_process.Rda")
 load("./data/GHI_enh_02_ID_CE.Rda")
 tic  <- Sys.time()
 
@@ -363,6 +364,23 @@ ggplot(data = DATA[GLB_diff > 0], aes(x = GLB_diff)) +
   labs(caption = bquote(paste("Bin width: ", .(binwidth)) ~ group("[", W/m^2,"]"))) #  +
   # inset_element(p1, left = 0.4, bottom = 0.4, right = 1, top = 1,
   #               align_to = "plot")
+
+
+cat(pander(summary(DATA[GLB_diff > 0, GLB_diff])),"\n")
+
+cat(pander(quantile(DATA[GLB_diff > 0, GLB_diff])),"\n")
+
+above <- 100
+per   <- 100 * DATA[GLB_diff > 0 & GLB_diff > above, .N] / DATA[GLB_diff > 0, .N]
+
+cat(paste("\n", per, "% of the values are above", above, "W/m^2\n\n" ))
+
+
+below <- mean(ST_E_yearly$GLB_diff.mean)
+per   <- 100 * DATA[GLB_diff > 0 & GLB_diff < below, .N] / DATA[GLB_diff > 0, .N]
+
+cat(paste("\n", per, "% of the values are below", below, "W/m^2\n\n" ))
+
 
 
 

### 2024-06-12 article/article.tex
Commit 2024-06-12 10:14

@@
 CE events become, the rarer are the conditions favoring the occurrence
-of CE events. For the majority (over \(60\%\)) of the CE events the OIR
+of CE events. For the majority (over \(62\%\)) of the CE events the OIR
 is below the long term average of \(39.9\,\text{W}/\text{m}^2\), while
-about \(10\%\) of the events correspond to OIR larger than
-\(100\,\text{W}/\text{m}^2\) and up to highest value of 300
-W/m\textsuperscript{2}. This distribution is indicative of the magnitude
-and the probability of the expected CE events over Thessaloniki. Similar
-distribution of CE events, occurrences have been reported by
-\citet{Vamvakas2020}, where the magnitude of OIR were higher due to the
-location of the city of Patras, \(2.5^\circ\) closer to the equator.
+about \(8.1\%\) of the events correspond to OIR larger than
+\(100\,\text{W}/\text{m}^2\) and up to highest value of
+\(412.4\,\text{W}/\text{m}^2\). This distribution is indicative of the
+magnitude and the probability of the expected CE events over
+Thessaloniki. Similar distribution of CE events, albeit with larger OIR
+values, has been reported by \citet{Vamvakas2020}, fot the city of
+Patras.This site is located \(2.5^\circ\) closer to the equator. south
+of Thessaloniki and is exposed to air masses coming mainly from the
+eastern Mediterranean resulting in different cloud patterns, that may
+affect the characteristics and magnitude of the CE events.
 
@@
 
-\caption{Distribution of CE over irradiance magnitude.}\label{fig:ovir-distribution}
+\caption{Relative frequency distribution of CE events as a function of OIR.}\label{fig:ovir-distribution}
 \end{figure}
 
-\hypertarget{groups-of-cloud-enhancement}{%
-\subsection{Groups of cloud
-enhancement}\label{groups-of-cloud-enhancement}}
+\hypertarget{duration-of-cloud-enhancement-events}{%
+\subsection{Duration of cloud enhancement
+events}\label{duration-of-cloud-enhancement-events}}
 
-In order to study the total duration of the CE events, we grouped the
-one minute CE events to continuous CE groups (CEG). Thus, a CEG consists
-of one or more successive CE cases, and can represent cloud enhancement
-conditions spanning a duration of multiple minutes. We have identified
-28468 groups of CE in the whole period of study, where the group with
-the longest duration lasted 140 minutes on 07~July 2013. By examining
-the frequency distribution of the CEG durations
+The duration of the CE events is variable and can last for several
+minutes or even more than an hour. In order to study the characteristics
+of these consecutive events, we grouped them into bins of increasing
+duration in steps of one minute.
+
+We have identified 28468 groups of CE in the whole period of study,
+where the group with the longest duration lasted 140 minutes on 07~July
+2013. By examining the frequency distribution of the CEG durations
 (Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can

### 2024-06-12 article/article.Rmd
Commit 2024-06-12 10:14

@@
 decline. This is expected, as the stronger the CE events become, the rarer are the
-conditions favoring the occurrence of CE events. For the majority (over $60\%$) of
+conditions favoring the occurrence of CE events. For the majority (over $62\%$) of
 the CE events the OIR is below the long term average of
 $`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$,
-while about $10\%$ of the events correspond to OIR larger than
-$100\,\text{W}/\text{m}^2$ and up to highest value of 300 W/m^2^.
+while about $8.1\%$ of the events correspond to OIR larger than
+$100\,\text{W}/\text{m}^2$ and up to highest value of $412.4\,\text{W}/\text{m}^2$.
 This distribution is indicative of the magnitude and the probability of the expected
-CE
-events over Thessaloniki. Similar distribution of CE events, occurrences have been reported
-by @Vamvakas2020, where the magnitude of OIR were
-higher due to the location of the city of Patras, $2.5^\circ$ closer to the equator.
+CE events over Thessaloniki.  Similar distribution of CE events, albeit with larger
+OIR values, has been reported by @Vamvakas2020, fot the city of Patras.This site is
+located $2.5^\circ$ closer to the equator.  south of Thessaloniki and is exposed to
+air masses coming mainly from the eastern Mediterranean resulting in different cloud
+patterns, that may affect the characteristics and magnitude of the CE events.
 
-```{r ovir-distribution, echo=FALSE, fig.cap="Distribution of CE over irradiance magnitude."}
+```{r ovir-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE events as a function of OIR."}
 knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
@@
 
-<!-- whisky plots relative to GLB -->
+## Duration of cloud enhancement events
 
-<!-- set of yearly plots -->
+The duration of the CE events is variable and can last for several minutes or even
+more than an hour. In order to study the characteristics of these consecutive events,
+we grouped them into bins of increasing duration in steps of one minute.
 
-<!-- \FloatBarrier -->
-
-## Groups of cloud enhancement
-
-In order to study the total duration of the CE events, we grouped the one
-minute CE events to continuous CE groups (CEG). Thus, a CEG consists of one or more
-successive CE cases, and can represent cloud enhancement conditions spanning a
-duration of multiple minutes.  We have identified `r ST_G0[, .N]` groups of CE in the
+We have identified `r ST_G0[, .N]` groups of CE in the
 whole period of study, where the

### 2024-06-12 article/article.Rmd
Commit 2024-06-12 11:11

@@
 decline. This is expected, as the stronger the CE events become, the rarer are the
-conditions favoring the occurrence of CE events. For the majority (over $62\%$) of
+conditions favoring the occurrence of CE events. For the majority (over $62\,\%$) of
 the CE events the OIR is below the long term average of
 $`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$,
-while about $8.1\%$ of the events correspond to OIR larger than
+while about $8.1\,\%$ of the events correspond to OIR larger than
 $100\,\text{W}/\text{m}^2$ and up to highest value of $412.4\,\text{W}/\text{m}^2$.
@@
 CE events over Thessaloniki.  Similar distribution of CE events, albeit with larger
-OIR values, has been reported by @Vamvakas2020, fot the city of Patras.This site is
-located $2.5^\circ$ closer to the equator.  south of Thessaloniki and is exposed to
-air masses coming mainly from the eastern Mediterranean resulting in different cloud
-patterns, that may affect the characteristics and magnitude of the CE events.
+OIR values, has been reported by @Vamvakas2020, for the city of Patras.This site is
+located $2.5^\circ$ south of Thessaloniki and is exposed to air masses coming mainly
+from the eastern Mediterranean resulting in different cloud patterns, that may affect
+the characteristics and magnitude of the CE events.
 
@@
 `r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")`.
-By examining the frequency distribution of the CEG durations
-(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can conclude, that
-although we detected some CEG with durations longer than an hour, about $80\,\%$ of
-the CEG have a duration of less than 5 minutes.
 
-```{r ceg-duration-distribution, echo=FALSE, fig.cap="Distribution of CE groups duration in minutes."}
+Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}) shows the frequency
+distribution of the CE events according to their duration.  We conclude that although
+some groups of events last for more than an hour about $80\,\%$ have duration of less
+than 5 minutes.
+
+```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration."}
 knitr::include_graphics("../images/groups-1.png")
@@
 
-```{r group-2d, echo=FALSE, fig.cap="Relation of the mean over irradiance and duration of GCE, where the color scale denotes the frequency of the respected events."}
+```{r group-2d, echo=FALSE, fig.cap="Relation of excess irradiation of CE groups with their duration. The logarithmic color scale denotes the frequency of the respective groups of events."}
 knitr::include_graphics("../images/P-groups-bin2d-1.png")

### 2024-06-12 article/article.tex
Commit 2024-06-12 11:11

@@
 CE events become, the rarer are the conditions favoring the occurrence
-of CE events. For the majority (over \(62\%\)) of the CE events the OIR
-is below the long term average of \(39.9\,\text{W}/\text{m}^2\), while
-about \(8.1\%\) of the events correspond to OIR larger than
+of CE events. For the majority (over \(62\,\%\)) of the CE events the
+OIR is below the long term average of \(39.9\,\text{W}/\text{m}^2\),
+while about \(8.1\,\%\) of the events correspond to OIR larger than
 \(100\,\text{W}/\text{m}^2\) and up to highest value of
@@
 Thessaloniki. Similar distribution of CE events, albeit with larger OIR
-values, has been reported by \citet{Vamvakas2020}, fot the city of
-Patras.This site is located \(2.5^\circ\) closer to the equator. south
-of Thessaloniki and is exposed to air masses coming mainly from the
-eastern Mediterranean resulting in different cloud patterns, that may
-affect the characteristics and magnitude of the CE events.
+values, has been reported by \citet{Vamvakas2020}, for the city of
+Patras.This site is located \(2.5^\circ\) south of Thessaloniki and is
+exposed to air masses coming mainly from the eastern Mediterranean
+resulting in different cloud patterns, that may affect the
+characteristics and magnitude of the CE events.
 
@@
 where the group with the longest duration lasted 140 minutes on 07~July
-2013. By examining the frequency distribution of the CEG durations
-(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can
-conclude, that although we detected some CEG with durations longer than
-an hour, about \(80\,\%\) of the CEG have a duration of less than 5
-minutes.
+2013.
+
+Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}) shows the
+frequency distribution of the CE events according to their duration. We
+conclude that although some groups of events last for more than an hour
+about \(80\,\%\) have duration of less than 5 minutes.
 
@@
 
-\caption{Distribution of CE groups duration in minutes.}\label{fig:ceg-duration-distribution}
+\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration.}\label{fig:ceg-duration-distribution}
 \end{figure}
@@
 
-\caption{Relation of the mean over irradiance and duration of GCE, where the color scale denotes the frequency of the respected events.}\label{fig:group-2d}
+\caption{Relation of excess irradiation of CE groups with their duration. The logarithmic color scale denotes the frequency of the respective groups of events.}\label{fig:group-2d}
 \end{figure}

### 2024-06-12 GHI_enh_04_investigate.tex
Commit 2024-06-11 13:11
Commit 2024-06-11 20:14
Commit 2024-06-11 23:11
Commit 2024-06-12 11:11
Commit 2024-06-12 12:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-06-10}
+\date{2024-06-12}
 
@@
 \end{figure}
+\begin{figure}[H]
 
-{[}1{]} 0.8092946
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-2}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-2}
+\end{figure}
+
+\begin{verbatim}
+Attaching package: 'scales'
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:viridis':
+
+    viridis_pal
+\end{verbatim}
+
+\begin{verbatim}
+Warning: The dot-dot notation (`..count..`) was deprecated in ggplot2 3.4.0.
+i Please use `after_stat(count)` instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-3}
+\end{figure}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-2}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4}
 
@@
 
-\caption{ - empty caption - }\label{fig:groups-2}
+\caption{ - empty caption - }\label{fig:groups-4}
 \end{figure}
@@
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-3}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-4}
-\end{figure}
 \begin{figure}[H]
@@
 \end{figure}
-
-\hypertarget{zhang2018}{%
-\subsection{@Zhang2018}\label{zhang2018}}
-
 \begin{figure}[H]
@@
 \caption{ - empty caption - }\label{fig:groups-8}
+\end{figure}
+
+\hypertarget{zhang2018}{%
+\subsection{@Zhang2018}\label{zhang2018}}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-9}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-10}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-10}
 \end{figure}
@@
 \begin{verbatim}
-2024-06-10 09:43:05.7 athan@tyler GHI_enh_04_investigate.R 3.417696 mins
+2024-06-12 08:50:47.4 athan@tyler GHI_enh_04_investigate.R 1.594768 mins
 \end{verbatim}

### 2024-06-12 GHI_enh_04_investigate.R

@@ -427,7 +427,29 @@ ggplot(data = ST_G0, aes(x = GLB_ench.N)) +
 #   inset_element(p1, left = 0.3, bottom = 0.3, right = 1, top = 1,
 #                 align_to = "plot")
 
-ST_G0[GLB_ench.N <= 5, .N] / ST_G0[, .N]
+ggplot(data = ST_G0, aes(x = GLB_ench.N)) +
+  geom_histogram(aes(y = (after_stat(count))/sum(after_stat(count)) * 100),
+                 binwidth = 0.16,
+                 boundary = 0,
+                 color    = "black") +
+  # xlab(bquote(.(varname("GLB_diff")) ~ group("[", W/m^2,"]"))) +
+  xlab("Duration of enhancement group [min]") +
+  ylab("Relative frequency [%]") +
+  scale_x_log10()
+
+
+
+library(scales)
+
+ggplot(data = ST_G0, aes(x = GLB_ench.N)) +
+  stat_density(aes(y=..count..), color="black", fill="blue", alpha=0.3) +
+  xlab("Duration of enhancement group [min]") +
+  ylab("Relative frequency [%]") +
+  scale_x_continuous( trans="log1p" ) +
+  scale_y_continuous(breaks=c(0,125,250,375,500,625,750), expand=c(0,0))
+
+
+
 
 
 ggplot(data = ST_G0, aes(x = GLB_ench.N)) +

### 2024-06-12 article/article.Rmd
Commit 2024-06-12 19:11

@@
 $`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kj}/\text{year}$
+`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$
 with the peak of the CE events are observed during May and June.
@@
 using a radiative transfer model (RTM).  The applied methodology is discussed in
-section\nobreakspace{}\ref{rtmcs}
+section\nobreakspace{}\ref{rtmcs}..
 
@@
 $\text{GHI}_\text{ref}$ used in this study is necessary. As AERONET data start only
-in 2003, we used for the period 1993 -– 2005 estimates of changes in AOD at
-$340\,\text{nm}$ derived from a collocated Brewer spectrophotometer derived from two
-sources. For 1993 -- 2005 [@Kazadzis2007] to calculate the trend in
-$\text{GHI}_\text{ref}$ during this period.
+in 2003, we used for the period 1993 -- 2005 estimates of changes in AOD at
+$340\,\text{nm}$ derived from a collocated Brewer spectrophotometer [@Kazadzis2007]
+to calculate the trend in $\text{GHI}_\text{ref}$ during this period.
 
@@
 (`r round(ST_total$wattGLB.N / 10^6,1)` million of one-minute GHI measurements),
-$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ were identified as CE events and
+$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 2)`\,\%$ were identified as CE events and
 $`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ as ECE events.
@@
 Figure\nobreakspace{}\ref{fig:relative-month-occurrences} shows the monthly box and
-whisker plot of the CE number of occurrence normalized with the highest median value,
+whisker plot of the CE number of occurrence normalized with the highest median value
 that occurs in June, depicting a clear seasonal cycle.  Although CE events are
 present  throughout the year, the most active period  is during May and June.  During
-the winter (December -- February), the number of CE cases is about $25\,\%$ of the
-maximum, while in the intermediate months, the number of occurrences gradually ramps
+winter (December -- February), the number of CE cases is about $25\,\%$ of the
+maximum, while in the intermediate months the number of occurrences gradually ramps
 between the maximum and minimum.  This seasonality is a combined effect of different
@@
 The monthly values have been also normalized to the relative abundance of valid GHI observations.
-The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles,The thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
+The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles.
+The thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
 The vertical lines (whiskers) extend between the maximum and minimum monthly values and the solid circles are outliers."}
@@
 CE events over Thessaloniki.  Similar distribution of CE events, albeit with larger
-OIR values, has been reported by @Vamvakas2020, for the city of Patras.This site is
+OIR values, has been reported by @Vamvakas2020 for the city of Patras. This site is
 located $2.5^\circ$ south of Thessaloniki and is exposed to air masses coming mainly
@@
 
-The relation between the duration and the mean OIR intensity of the groups have also been
-studied (Figure\nobreakspace{}\ref{fig:group-2d}). We observed that the GCE events
-tend to have either long duration, or large intensity. Events with strong enhancement
-and long duration are very rare. Similar results on this relation, have been
-reported by @Zhang2018, on a study using a far higher sampling rate than ours.
+The relation between the duration of the CE groups and the excess irradiation of the
+groups has also been investigated (Figure\nobreakspace{}\ref{fig:group-2d}).
+Evidently, evens of high excess irradiation have small duration and vice versa. The
+vast majority of grouped events are associated with small excess irradiation (e.g.
+$<5\,\text{kJ}/\text{m}^2$) and small duration (e.g. $<5\,\text{min}$) while groups
+with strong excess irradiation and long duration are rare.  Similar results on this
+relation, have been reported by @Zhang2018, on a study using a far higher sampling
+rate than ours.
 
@@
 <!-- ``` -->
-
 <!-- ```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"} -->
@@
 (Equation\nobreakspace{}\ref{eq:ECE}).
-Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies} we have
+Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurrences} we have
 computed the distribution of the number of occurrences of ECE events by month in
@@
 $`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kj}/\text{year}$.
+`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$.
 The most active season of CE events over Thessaloniki is concentrated on early

### 2024-06-12 article/article.tex
Commit 2024-06-12 19:11

@@
 mean total energy change, of the CE events by
-\(116.9\pm 67.8\,\text{kj}/\text{year}\) with the peak of the CE events
+\(116.9\pm 67.8\,\text{kJ}/\text{year}\) with the peak of the CE events
 are observed during May and June. An analysis of the total duration of
@@
 using a radiative transfer model (RTM). The applied methodology is
-discussed in section\nobreakspace{}\ref{rtmcs}
+discussed in section\nobreakspace{}\ref{rtmcs}..
 
@@
 \(\text{GHI}_\text{ref}\) used in this study is necessary. As AERONET
-data start only in 2003, we used for the period 1993 -\/-- 2005
-estimates of changes in AOD at \(340\,\text{nm}\) derived from a
-collocated Brewer spectrophotometer derived from two sources. For 1993
--- 2005 \citep{Kazadzis2007} to calculate the trend in
+data start only in 2003, we used for the period 1993 -- 2005 estimates
+of changes in AOD at \(340\,\text{nm}\) derived from a collocated Brewer
+spectrophotometer \citep{Kazadzis2007} to calculate the trend in
 \(\text{GHI}_\text{ref}\) during this period.
@@
 entire dataset (6.1 million of one-minute GHI measurements),
-\(1.764\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
+\(1.76\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
 events. The highest recorded GHI due to CE was
@@
 shows the monthly box and whisker plot of the CE number of occurrence
-normalized with the highest median value, that occurs in June, depicting
+normalized with the highest median value that occurs in June, depicting
 a clear seasonal cycle. Although CE events are present throughout the
-year, the most active period is during May and June. During the winter
+year, the most active period is during May and June. During winter
 (December -- February), the number of CE cases is about \(25\,\%\) of
-the maximum, while in the intermediate months, the number of occurrences
+the maximum, while in the intermediate months the number of occurrences
 gradually ramps between the maximum and minimum. This seasonality is a
@@
 The monthly values have been also normalized to the relative abundance of valid GHI observations.
-The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles,The thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
+The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles.
+The thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
 The vertical lines (whiskers) extend between the maximum and minimum monthly values and the solid circles are outliers.}\label{fig:relative-month-occurrences}
@@
 Thessaloniki. Similar distribution of CE events, albeit with larger OIR
-values, has been reported by \citet{Vamvakas2020}, for the city of
-Patras.This site is located \(2.5^\circ\) south of Thessaloniki and is
+values, has been reported by \citet{Vamvakas2020} for the city of
+Patras. This site is located \(2.5^\circ\) south of Thessaloniki and is
 exposed to air masses coming mainly from the eastern Mediterranean
@@
 
-The relation between the duration and the mean OIR intensity of the
-groups have also been studied (Figure\nobreakspace{}\ref{fig:group-2d}).
-We observed that the GCE events tend to have either long duration, or
-large intensity. Events with strong enhancement and long duration are
-very rare. Similar results on this relation, have been reported by
-\citet{Zhang2018}, on a study using a far higher sampling rate than
-ours.
+The relation between the duration of the CE groups and the excess
+irradiation of the groups has also been investigated
+(Figure\nobreakspace{}\ref{fig:group-2d}). Evidently, evens of high
+excess irradiation have small duration and vice versa. The vast majority
+of grouped events are associated with small excess irradiation (e.g.
+\(<5\,\text{kJ}/\text{m}^2\)) and small duration
+(e.g.~\(<5\,\text{min}\)) while groups with strong excess irradiation
+and long duration are rare. Similar results on this relation, have been
+reported by \citet{Zhang2018}, on a study using a far higher sampling
+rate than ours.
 
@@
 (Equation\nobreakspace{}\ref{eq:ECE}). Analogous to
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies} we have
+Figure\nobreakspace{}\ref{fig:relative-month-occurrences} we have
 computed the distribution of the number of occurrences of ECE events by
@@
 the mean annual total energy of the CE events increasing with a rate of
-\(116.9\pm 67.8\,\text{kj}/\text{year}\). The most active season of CE
+\(116.9\pm 67.8\,\text{kJ}/\text{year}\). The most active season of CE
 events over Thessaloniki is concentrated on early summer, on May and

### 2024-06-13 article/article.Rmd
Commit 2024-06-13 19:11

@@
 by different factors, such as the geometry, size and optical thickness of clouds,
-their height in the atmosphere and on local weather regimes **!!!(ref)!!!**.  Some of
-these factors are related to changes in climate; hence it would be reasonable to
-expect capturing their contributions to the frequency of occurrence of CE events over
-Thessaloniki, as well as to the average OIR and excess irradiation. 
-The long-term trends were calculated using a first-order autoregressive model with the
-'maximum likelihood' fitting method
-[@Gardner1980; @Jones1980], by implementing the function 'arima' from the library
-'stats' of the R programming language [@RCT2023]. All trends are reported together
-with their $2\sigma$ error.
+their height in the atmosphere and on local weather regimes [@Mol2023; @Veerman2022;
+@Gristey2022; @Tzoumanikas2016].  Some of these factors are related to changes in
+climate; hence it would be reasonable to expect capturing their contributions to the
+frequency of occurrence of CE events over Thessaloniki, as well as to the average OIR
+and excess irradiation.  The long-term trends were calculated using a first-order
+autoregressive model with the 'maximum likelihood' fitting method [@Gardner1980;
+@Jones1980], by implementing the function 'arima' from the library 'stats' of the R
+programming language [@RCT2023]. All trends are reported together with their
+$2\sigma$ error.
 

### 2024-06-13 article/article.tex
Commit 2024-06-13 19:11

@@
 geometry, size and optical thickness of clouds, their height in the
-atmosphere and on local weather regimes \textbf{!!!(ref)!!!}. Some of
+atmosphere and on local weather regimes
+\citep{Mol2023, Veerman2022, Gristey2022, Tzoumanikas2016}. Some of
 these factors are related to changes in climate; hence it would be

### 2024-06-20 article/article.tex
Commit 2024-06-20 10:15

@@
 
-We studied the enhancement of the global horizontal irradiance (GHI),
-over Thessaloniki, for the period 1993 -- 2023, on one minute average
-records. We identify the cloud enhancement events (CE), by creating an
-appropriate clear sky irradiance reference with the use of a radiation
-transfer model, and aerosol optical depth (AOD) data, from the AERONET,
-and a collocated Brewer photospectrometer. We found that there is a
-trend of CE cases of \(45.6\pm 21.9\,\text{cases}/\text{year}\), and a
-mean total energy change, of the CE events by
-\(116.9\pm 67.8\,\text{kJ}/\text{year}\) with the peak of the CE events
-are observed during May and June. An analysis of the total duration of
-CE events, showed that durations longer than 5 minutes are very rare,
-with exceptions lasting over an hour. We have detected enhancements over
-the total solar irradiance, without exceeding the maximum values
-reported for other sites, with more favorable CE conditions.
+We studied the enhancement of the global horizontal irradiance induced
+by clouds over Thessaloniki for the period 1993 -- 2023 using data
+recorded every one minute. We identified the cloud enhancement events
+(CE) by creating an appropriate clear sky irradiance reference with the
+use of a radiative transfer model and aerosol optical depth data from a
+collocated Cimel sun photometer and a Brewer spectrophotometer. We found
+a trend in CE events of \(45.6\pm 21.9\,\text{cases}/\text{year}\), and
+a trend in the CE events irradiation of
+\(116.9\pm 67.8\,\text{kJ}/\text{year}\). The peak of the CE events was
+observed during May and June. An analysis of the total duration of CE
+events, showed that durations longer than 5 minutes are very rare, with
+exceptions lasting over an hour. Finally we have detected enhancements
+above the total solar irradiance at the top of the atmosphere of up to
+\(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the cases below
+\(200\,\text{W}/\text{m}^{2}\).
 
@@
 enhancement of the global horizontal irradiance (GHI) reaching the
-ground. This effect can locally increase the observed GHI to levels even
-higher than the expected clear-sky irradiance \citep[ and references
+ground. This cloud enhancement (CE) effect can locally increase the
+observed GHI to levels even higher than the expected clear-sky
+irradiance \citep[ and references
 therein]{Cordero2023, Vamvakas2020, CastillejoCuberos2020, Vamvakas2020}.
@@
 \citep{Pecenak2016, Thuillier2013, Yordanov2013, Yordanov2015}. Overall,
-enhancement event depend on different interactive factors, which include
-cloud thickness, structure and type, and the relative position of the
-sun and the clouds \citep{Gueymard2017, Veerman2022}.
+enhancement events depend on different interactive factors, which
+include cloud thickness, structure and type, and the relative position
+of the sun and the clouds \citep{Gueymard2017, Veerman2022}.
 
-On multiple sites, cloud enhancements (CE) have been reported to be able
-to briefly exceed the value of the solar constant, resulting of
-clearness indices above unit. A summary of extreme enchantment cases
-(ECE) has been compiled by \citet{Martins2022}. There are also some
-practical implications of the cloud enchantments. The intensity and
-duration of enhancements can effect the efficiency and stability of
-photovoltaic power production \citep{Lappalainen2020, Jaervelae2020}
-while ECEs have the potential to compromise the integrity of
-photovoltaic plants infrastructure \citep{DoNascimento2019}. It has also
-been demonstrated that these events can interfere in the comparison of
-ground-based and satellite observations \citep{Damiani2018}. Global
-warming has likely affected cloud coverage in the last few decades.
-\citet{Liu2023} reported increases in cloud cover over the tropical and
-subtropical oceans and decreases over most continents, while
-\citet{Dong2023} reported decreases over North America and Europe. To
-our knowledge, there is no evidence on whether this trend has affected
-also the number and strength of CE events.
+On multiple sites, cloud enhancements have been reported that exceed
+momentarily the solar constant, resulting in clearness indices above
+unit. A summary of extreme cloud enchantment (ECE) cases has been
+compiled by \citet{Martins2022}. Cloud enhancements can have also some
+practical implications. The intensity and duration of enhancements can
+effect the efficiency and stability of photovoltaic power production
+\citep{Lappalainen2020, Jaervelae2020} while ECEs have the potential to
+compromise the integrity of photovoltaic plants infrastructure
+\citep{DoNascimento2019}. It has also been demonstrated that these
+events can interfere in the comparison of ground-based and satellite
+observations \citep{Damiani2018}. Global warming has likely affected
+cloud coverage in the last few decades. \citet{Liu2023} reported
+increases in cloud cover over the tropical and subtropical oceans and
+decreases over most continents, while \citet{Dong2023} reported
+decreases over North America and Europe. To our knowledge, there is no
+evidence on whether this trend has affected also the number and strength
+of CE events.
 

### 2024-06-20 article/article.Rmd
Commit 2024-06-20 10:15

@@
 
-We studied the enhancement of the global horizontal irradiance (GHI), over Thessaloniki, 
-for the period 1993 -- 2023, on one minute average records.
-We identify the cloud enhancement events (CE), by creating an appropriate clear sky
-irradiance reference with the use of a radiation transfer model, and aerosol optical 
-depth (AOD) data, from the AERONET, and a collocated Brewer photospectrometer.
-We found that there is a trend of CE cases of
+We studied the enhancement of the global horizontal irradiance induced by clouds over
+Thessaloniki for the period 1993 -- 2023 using data recorded every one minute.  We
+identified the cloud enhancement events (CE) by creating an appropriate clear sky
+irradiance reference with the use of a radiative transfer model and aerosol optical
+depth data from a collocated Cimel sun photometer and a Brewer spectrophotometer. We
+found a trend in CE events of
 $`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
 `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$,
-and a
-mean total energy change, of the CE events by
+and a trend in the CE events irradiation of 
 $`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$
-with the peak of the CE events are observed during May and June.
-An analysis of the total duration of CE events, showed that durations longer than 
-5 minutes are very rare, with exceptions lasting over an hour.
-We have detected enhancements over the total solar irradiance, without exceeding the
-maximum values reported for other sites, with more favorable CE conditions.
+`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$.
+The peak of the CE events was observed during May and June.  An analysis of the total
+duration of CE events, showed that durations longer than 5 minutes are very rare,
+with exceptions lasting over an hour.  Finally we have detected enhancements above
+the total solar irradiance at the top of the atmosphere of up to
+$400\,\text{W}/\text{m}^{2}$, with the $75\,\%$ of the cases below
+$200\,\text{W}/\text{m}^{2}$.
 
@@
 certain conditions, can lead to  enhancement of the global horizontal irradiance
-(GHI) reaching the ground. This effect can locally increase the observed GHI to
-levels even higher than the expected clear-sky irradiance [@Cordero2023;
-@Vamvakas2020; @CastillejoCuberos2020; @Vamvakas2020 and references therein].
+(GHI) reaching the ground. This cloud enhancement (CE) effect can locally increase
+the observed GHI to levels even higher than the expected clear-sky irradiance
+[@Cordero2023; @Vamvakas2020; @CastillejoCuberos2020; @Vamvakas2020 and references
+therein].
 
@@
 optical depth [@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015].  Overall,
-enhancement event depend on different interactive factors, which include cloud
+enhancement events depend on different interactive factors, which include cloud
 thickness, structure and type, and the relative position of the sun and the clouds
@@
 
-On multiple sites, cloud enhancements (CE) have been reported to be able to briefly
-exceed the value of the solar constant, resulting of clearness indices above unit. A
-summary of extreme enchantment cases (ECE) has been compiled by @Martins2022. There
-are also some practical implications of the cloud enchantments.  The intensity and
-duration of enhancements can effect the efficiency and stability of photovoltaic
-power production [@Lappalainen2020; @Jaervelae2020] while ECEs have the potential to
-compromise the integrity of photovoltaic plants infrastructure [@DoNascimento2019].
-It has also been demonstrated that these events can interfere in the comparison of
-ground-based and satellite observations [@Damiani2018].  Global warming has likely
-affected cloud coverage in the last few decades. @Liu2023 reported increases in cloud
-cover over the tropical and subtropical oceans and decreases over most continents,
-while @Dong2023 reported decreases over North America and Europe. To our knowledge,
-there is no evidence on whether this trend has affected also the number and strength
-of CE events.
+On multiple sites, cloud enhancements have been reported that exceed momentarily the
+solar constant, resulting in clearness indices above unit. A summary of extreme cloud
+enchantment (ECE) cases has been compiled by @Martins2022. Cloud enhancements can
+have  also some practical implications.  The intensity and duration of enhancements
+can effect the efficiency and stability of photovoltaic power production
+[@Lappalainen2020; @Jaervelae2020] while ECEs have the potential to compromise the
+integrity of photovoltaic plants infrastructure [@DoNascimento2019].  It has also
+been demonstrated that these events can interfere in the comparison of ground-based
+and satellite observations [@Damiani2018].  Global warming has likely affected cloud
+coverage in the last few decades. @Liu2023 reported increases in cloud cover over the
+tropical and subtropical oceans and decreases over most continents, while @Dong2023
+reported decreases over North America and Europe. To our knowledge, there is no
+evidence on whether this trend has affected also the number and strength of CE
+events.
 
@@
 `r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.
-In the following sections we are discussing the long-term trends and variability of the CE events as well as of the corresponding OIR and excess irradiation.
+In the following sections we are discussing the long-term trends and variability of
+the CE events as well as of the corresponding OIR and excess irradiation.
 

### 2024-06-20 article/article.Rmd
Commit 2024-06-20 17:13
Commit 2024-06-20 20:14

@@
 
-<!-- Define CE and ECE tomove? -->
-In this study, we define an event as CE when the measured GHI at ground level,
-exceeds the expected value under clear-sky conditions. Similarly, we define as
-extreme cloud enhancement events (ECE), the cases when GHI at ground level exceeds
-the Total Solar Irradiance (TSI). Although the duration of these bursts can vary from
-seconds to several minutes, here we are constrained by the temporal resolution of our
-data to identify evens with duration of at minimum one-minute.
-
 <!--
@@
 @Long2008a].  Thus, problematic recordings have been excluded from further
-processing.  Although it is impossible to detect all false data, the large number of
+processing.
+<!--
+Although it is impossible to detect all false data, the large number of
 available data, and the aggregation scheme we used, ensures the quality of the
 radiation measurements used in this study.
+-->
 <!-- Data selection -->
+<!--
 To preserve an unbiased representation of the data we applied a constraint, similar
@@
 sunset. Days with less than 5 valid hours were rejected completely.
-<!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7),
+-->
+<!--
+# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7),
 otherwise all data for this day is flagged as invalid. There must be at least This
 work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid,
-otherwise all minute data for this hour is flagged as invalid. -->
+otherwise all minute data for this hour is flagged as invalid.
+-->
 Furthermore, due to the significant measurement uncertainty in GHI when the Sun is
@@
 
+<!-- Define CE and ECE tomove? -->
+In this study, we define an event as CE when the measured GHI at ground level,
+exceeds the expected value under clear-sky conditions. Similarly, we define as
+extreme cloud enhancement events (ECE), the cases when GHI at ground level exceeds
+the Total Solar Irradiance (TSI). Although the duration of these bursts can vary from
+seconds to several minutes, here we are constrained by the temporal resolution of our
+data to identify evens with duration of at minimum one-minute.
+
 For the detection of CE cases we established a baseline of irradiance above which we
@@
 irradiance (OIR). The OIR is defined as the irradiance difference of the measured
-one-minute $\text{GHI}_i$ from the $\text{GHI}_\text{ref}$ corresponding to
+one-minute GHI from the $\text{GHI}_\text{ref}$ corresponding to
 cloud-free atmosphere.
@@
 attributed to long-term changes in aerosol effects.  Therefore, an adjustment of the
-$\text{GHI}_\text{ref}$ used in this study is necessary. As AERONET data start only
-in 2003, we used for the period 1993 -- 2005 estimates of changes in AOD at
-$340\,\text{nm}$ derived from a collocated Brewer spectrophotometer [@Kazadzis2007]
-to calculate the trend in $\text{GHI}_\text{ref}$ during this period.
+$\text{GHI}_\text{ref}$ during the period of study was made using simulation with the
+RTM based on the long-term variations of the AOD. As AERONET data start only in 2003,
+we used for the period 1993 -- 2005 estimates of changes in AOD at $340\,\text{nm}$
+derived from a collocated Brewer spectrophotometer [@Kazadzis2007] to calculate the
+trend in $\text{GHI}_\text{ref}$ during this period.
 
@@
 
+<!--
 To create a unified trend for the long term change of the clear sky irradiance, we
@@
 all the runs.
+-->
 
 According to this study, in the period 1997 -- 2005 the mean AOD at $340\,\text{nm}$
-$0.403$ with a trend of $-3.8\pm0.93\,\%$ per year, corresponding to a change of
+is $0.403$ with a trend of $-3.8\pm0.93\,\%$ per year, corresponding to a change of
 $0.0153$ per year.  Using an Ångström coefficient $\alpha = 1.6$, this translates to
@@
 ($\text{GHI}_\text{CSm}$). -->
-These values represent typical atmosphere in Thessaloniki with lower than average
-load of aerosols and humidity, which are the main factor that attenuate the GHI,
+These values represent typical atmospheres in Thessaloniki with lower than average
+load of aerosols and humidity, which are the main factors that attenuate the GHI,
 excluding clouds.  With this approach the simulated $\text{GHI}_\text{ref}$ should be
@@
 (i) manually selected days.
-Where needed in some of the edge cases, we also used images from a sky-camera
-to further aid the decision of the manual inspection.
+For the latter case and where needed in some of the edge cases, we also used images
+from a sky-camera to further aid the decision of the manual inspection.
 
@@
 <!-- extreme cases criterion -->
-A sub-category  of the CE events that is often discussed in the relevant bibliography
+A sub-category  of the CE events that is often discussed in the relevant literature
 [@Cordero2023; @Martins2022; @Yordanov2015], are the extreme cloud enhancement (ECE)
 events. These are cases of CE where the measured intensity of the irradiance exceeds
-the TSI at the top of the atmosphere:
+the TSI at the top of the atmosphere. In this case the threshold EEEEEEEEEE:
 <!--and detected according to the Equation\nobreakspace{}\ref{eq:ECE}.-->

### 2024-06-20 article/article.tex
Commit 2024-06-20 17:13
Commit 2024-06-20 20:14

@@
 
-In this study, we define an event as CE when the measured GHI at ground
-level, exceeds the expected value under clear-sky conditions. Similarly,
-we define as extreme cloud enhancement events (ECE), the cases when GHI
-at ground level exceeds the Total Solar Irradiance (TSI). Although the
-duration of these bursts can vary from seconds to several minutes, here
-we are constrained by the temporal resolution of our data to identify
-evens with duration of at minimum one-minute.
-
 \hypertarget{data-and-methodology}{%
@@
 Thus, problematic recordings have been excluded from further processing.
-Although it is impossible to detect all false data, the large number of
-available data, and the aggregation scheme we used, ensures the quality
-of the radiation measurements used in this study. To preserve an
-unbiased representation of the data we applied a constraint, similar the
-one used by \citet{CastillejoCuberos2020}. For each valid hour of day,
-there must exist at least 45 minutes of valid measurements, including
-nighttime, when near sunrise and sunset. Days with less than 5 valid
-hours were rejected completely. Furthermore, due to the significant
-measurement uncertainty in GHI when the Sun is near the horizon, and due
-to some systematic obstructions by nearby buildings, we have excluded
-all measurements with solar zenith angle (SZA) greater than
-\(78^\circ\).
+Furthermore, due to the significant measurement uncertainty in GHI when
+the Sun is near the horizon, and due to some systematic obstructions by
+nearby buildings, we have excluded all measurements with solar zenith
+angle (SZA) greater than \(78^\circ\).
 
@@
 
+In this study, we define an event as CE when the measured GHI at ground
+level, exceeds the expected value under clear-sky conditions. Similarly,
+we define as extreme cloud enhancement events (ECE), the cases when GHI
+at ground level exceeds the Total Solar Irradiance (TSI). Although the
+duration of these bursts can vary from seconds to several minutes, here
+we are constrained by the temporal resolution of our data to identify
+evens with duration of at minimum one-minute.
+
 For the detection of CE cases we established a baseline of irradiance
@@
 calculated the over irradiance (OIR). The OIR is defined as the
-irradiance difference of the measured one-minute \(\text{GHI}_i\) from
-the \(\text{GHI}_\text{ref}\) corresponding to cloud-free atmosphere.
-First, we tested two simple approaches for the determination of
+irradiance difference of the measured one-minute GHI from the
+\(\text{GHI}_\text{ref}\) corresponding to cloud-free atmosphere. First,
+we tested two simple approaches for the determination of
 \(\text{GHI}_\text{ref}\): The Haurwitz's model \citep{Haurwitz1945},
@@
 long-term changes in aerosol effects. Therefore, an adjustment of the
-\(\text{GHI}_\text{ref}\) used in this study is necessary. As AERONET
-data start only in 2003, we used for the period 1993 -- 2005 estimates
-of changes in AOD at \(340\,\text{nm}\) derived from a collocated Brewer
-spectrophotometer \citep{Kazadzis2007} to calculate the trend in
-\(\text{GHI}_\text{ref}\) during this period.
-
-To create a unified trend for the long term change of the clear sky
-irradiance, we simulated the values of AOD derived from those sources
-with Libradtran. For both inputs, we used the AOD at \(500\,\text{nm}\),
-which was inferred by the available Ångström coefficients. We choose the
-SZA of \(55^\circ\) as a representative value for all the runs.
+\(\text{GHI}_\text{ref}\) during the period of study was made using
+simulation with the RTM based on the long-term variations of the AOD. As
+AERONET data start only in 2003, we used for the period 1993 -- 2005
+estimates of changes in AOD at \(340\,\text{nm}\) derived from a
+collocated Brewer spectrophotometer \citep{Kazadzis2007} to calculate
+the trend in \(\text{GHI}_\text{ref}\) during this period.
 
 According to this study, in the period 1997 -- 2005 the mean AOD at
-\(340\,\text{nm}\) \(0.403\) with a trend of \(-3.8\pm0.93\,\%\) per
+\(340\,\text{nm}\) is \(0.403\) with a trend of \(-3.8\pm0.93\,\%\) per
 year, corresponding to a change of \(0.0153\) per year. Using an
@@
 climatological AOD and WC, less their respective standard deviations.
-These values represent typical atmosphere in Thessaloniki with lower
-than average load of aerosols and humidity, which are the main factor
+These values represent typical atmospheres in Thessaloniki with lower
+than average load of aerosols and humidity, which are the main factors
 that attenuate the GHI, excluding clouds. With this approach the
@@
 of EC events, (h) randomly selected days, and (i) manually selected
-days. Where needed in some of the edge cases, we also used images from a
-sky-camera to further aid the decision of the manual inspection.
+days. For the latter case and where needed in some of the edge cases, we
+also used images from a sky-camera to further aid the decision of the
+manual inspection.
 
@@
 A sub-category of the CE events that is often discussed in the relevant
-bibliography \citep{Cordero2023, Martins2022, Yordanov2015}, are the
+literature \citep{Cordero2023, Martins2022, Yordanov2015}, are the
 extreme cloud enhancement (ECE) events. These are cases of CE where the
 measured intensity of the irradiance exceeds the TSI at the top of the
-atmosphere: \begin{equation}
+atmosphere. In this case the threshold EEEEEEEEEE: \begin{equation}
 \text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2

### 2024-06-22 article/article.tex
Commit 2024-06-22 19:11

@@
             pdfauthor={},
-            pdftitle={Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece},
+            pdftitle={Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece},
             colorlinks=false,
@@
 
-  \title{Long term cloud enhancement events of global solar irradiance
+  \title{Long-term cloud enhancement events of global solar irradiance
 over Thessaloniki, Greece}
@@
 irradiance as a baseline to identify cloud enhancements and we
-determined long term trends of the above mentioned metrics, their
+determined long-term trends of the above mentioned metrics, their
 climatology and some general characteristics. To our knowledge there are
@@
 \hypertarget{long-term-change-of-clear-sky-irradiance}{%
-\subsubsection{Long term change of clear sky
+\subsubsection{Long-term change of clear sky
 irradiance}\label{long-term-change-of-clear-sky-irradiance}}
@@
 The above clear sky reference values are based on the climatological AOD
-and WC, hence they cannot describe accurately the long term variation of
+and WC, hence they cannot describe accurately the long-term variation of
 \(\text{GHI}_\text{ref}\) due to changes in the two atmospheric
 constituents, mainly AOD. As reported by \citet{Natsis2023}, there is a
-long term brightening effect in the GHI data of Thessaloniki for the
+long-term brightening effect in the GHI data of Thessaloniki for the
 period 1993 -- 2023, which for clear-sky data was attributed to
@@
 above Ångström coefficients, with WC of \(15.7\,\text{mm}\) and
-\(15.4\,\text{mm}\) for 1997 and 2005 respectively and for a SZA of
-\(55^\circ\) reveal a trend of \(+0.21\,\%\) per year in
-\(\text{GHI}_\text{ref}\). The SZA of \(55^\circ\) was chosen as
-representative of all days in the year in order to get a rough estimate
-of the annually averaged change in clear sky irradiance. For the period
-2005 -- 2023 we used the mean monthly values of AOD and WC from AERONET
-in a similar simulation scheme to calculate the monthly mean of clear
-sky irradiance, and finally the trend of \(+0.14\,\%\) per year. We
-applied these two long term changes (see
+\(15.4\,\text{mm}\) for 1997 and 2005 respectively, also taken from
+AERONET, and for a SZA of \(55^\circ\) reveal a trend of \(+0.21\,\%\)
+per year in \(\text{GHI}_\text{ref}\). The SZA of \(55^\circ\) was
+chosen as representative of all days in the year in order to get a rough
+estimate of the annually averaged change in clear sky irradiance. For
+the period 2005 -- 2023 we used the mean monthly values of AOD and WC
+from AERONET in a similar simulation scheme to calculate the monthly
+mean of clear sky irradiance, and finally the trend of \(+0.14\,\%\) per
+year. We applied these two long-term changes (see
 Figure\nobreakspace{}\ref{fig:CS-change}) to the climatological
@@
 
-\caption{Simulated long term change in clear sky irradiance relative to the climatological values due to changes in AOD.}\label{fig:CS-change}
+\caption{Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD.}\label{fig:CS-change}
 \end{figure}
@@
 selection of the appropriate atmospheric parameterization for the RTM
-simulations. The implementation of the long term change of AOD,
+simulations. The implementation of the long-term change of AOD,
 discussed in section\nobreakspace{}\ref{rtmcs}, allows capturing a large
@@
 short-term variability of AOD cannot be taken adequately into account
-when using monthly values for the model simulations. We tried different
-approaches to increase the robustness of the methodology and compensate
-for the limited accuracy of the RTM input data and the unpredictable
-natural variability of the atmosphere.
+when using monthly values in the model simulations. We tried different
+approaches in order to strengthen the robustness of the methodology and
+compensate for the limited accuracy of the RTM input data and the
+unpredictable natural variability of the atmosphere.
 
@@
 measured GHI when aerosols are more abundant. To compensate for this, we
-increased the \(\text{GHI}_\text{ref}\) by (\(4\,\%\)) with an
-additional constant offset of \(15\,\text{W}/\text{m}^2\), as described
-in Equation\nobreakspace\ref{eq:CE4}. \begin{equation}
-\text{CE} : \text{E}_\text{i} > 15 + 1.04 \cdot \text{E}_\text{CSm,i} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
-\end{equation} where: \(\text{E}\) the measured irradiance,
-\(\text{E}_\text{CSm}\) the selected modelled clear sky irradiance, and
-\(i\) each of the one-minute observation. This is the criterion of our
-CE identification.
+defined the following threshold \(\text{E}\) to compare the measured
+\(\text{GHI}\): \begin{equation}
+\text{CE} : \text{E} > 15 + 1.04 \cdot \text{GHI}_\text{ref} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
+\end{equation} This is the criterion of our CE identification.
 
@@
 of EC events, (h) randomly selected days, and (i) manually selected
-days. For the latter case and where needed in some of the edge cases, we
-also used images from a sky-camera to further aid the decision of the
-manual inspection.
+days. For the latter case and where needed, we also used images from a
+sky-camera to further aid the decision of the manual inspection.
 
@@
 of CE events. For the majority (over \(62\,\%\)) of the CE events the
-OIR is below the long term average of \(39.9\,\text{W}/\text{m}^2\),
+OIR is below the longnterm average of \(39.9\,\text{W}/\text{m}^2\),
 while about \(8.1\,\%\) of the events correspond to OIR larger than
@@
 that's needs further investigation. Although, to approach it, we need
-more long term observations of AOD and clouds characteristics.
+more long-term observations of AOD and clouds characteristics.
 

### 2024-06-22 article/article.Rmd
Commit 2024-06-22 19:11

@@
 ---
-title: Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece
+title: Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece
 
@@
 
-Instruments respose ....
+Instruments response ....
 @Martins2022
@@
 Thessaloniki, Greece.  We used modeled clear sky irradiance as a baseline to identify
-cloud enhancements and we determined long term trends of the above mentioned metrics,
+cloud enhancements and we determined long-term trends of the above mentioned metrics,
 their climatology and some general characteristics.  To our knowledge there are no
@@
 
-### Long term change of clear sky irradiance
+### Long-term change of clear sky irradiance
 
@@
 The above clear sky reference values are based on the climatological AOD and WC,
-hence they cannot describe accurately the long term variation of
+hence they cannot describe accurately the long-term variation of
 $\text{GHI}_\text{ref}$ due to changes in the two atmospheric constituents, mainly
-AOD.  As reported by @Natsis2023, there is a long term brightening effect in the GHI
+AOD.  As reported by @Natsis2023, there is a long-term brightening effect in the GHI
 data of Thessaloniki for the period 1993 -- 2023, which for clear-sky data was
@@
 <!--
-To create a unified trend for the long term change of the clear sky irradiance, we
+To create a unified trend for the long-term change of the clear sky irradiance, we
 simulated the values of AOD derived from those sources with Libradtran. For both
@@
 $`r round(BR[year==2005,pw_avg_mm],1)`\,\text{mm}$
-for 1997 and 2005 respectively and for a SZA of $55^\circ$ reveal a trend of
+for 1997 and 2005 respectively, also taken from AERONET, and for a SZA of $55^\circ$
+reveal a trend of
 $+0.21\,\%$ per year in $\text{GHI}_\text{ref}$. 
@@
 a similar simulation scheme to calculate the monthly mean of clear sky irradiance,
-and finally the trend of $+0.14\,\%$ per year. We applied these two long term changes
+and finally the trend of $+0.14\,\%$ per year. We applied these two long-term changes
 (see Figure\nobreakspace{}\ref{fig:CS-change}) to the climatological
@@
 
-```{r CS-change, echo=FALSE, fig.cap="Simulated long term change in clear sky irradiance relative to the climatological values due to changes in AOD."}
+```{r CS-change, echo=FALSE, fig.cap="Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD."}
 knitr::include_graphics("../images/P-CS-change-1.pdf")
@@
 measurement. This depends on the selection of the appropriate atmospheric
-parameterization for the RTM simulations. The implementation of the long term change
+parameterization for the RTM simulations. The implementation of the long-term change
 of AOD, discussed in section\nobreakspace{}\ref{rtmcs}, allows capturing a large part
 of the natural variability of clear-sky GHI. However, the short-term variability of
-AOD cannot be taken adequately into account when using monthly values for the model
-simulations. We tried different approaches to increase the robustness of the
-methodology and compensate for the limited accuracy of the RTM input data and the
+AOD cannot be taken adequately into account when using monthly values in the model
+simulations. We tried different approaches in order to strengthen the robustness of
+the methodology and compensate for the limited accuracy of the RTM input data and the
 unpredictable natural variability of the atmosphere.
@@
 deviations.
-<!-- $\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
-($\text{GHI}_\text{CSm}$). -->
+<!--
+$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
+($\text{GHI}_\text{CSm}$).
+-->
 These values represent typical atmospheres in Thessaloniki with lower than average
@@
 generally greater than the measured GHI when aerosols are more abundant.  To
-compensate for this, we increased the $\text{GHI}_\text{ref}$ by 
+compensate for this, we defined the following threshold $\text{E}$ to compare the
+measured $\text{GHI}$: 
+<!--
 ($`r 100*(C4_cs_ref_ratio-1)`\,\%$)
@@
 as described in Equation\nobreakspace\ref{eq:CE4}.
+-->
 \begin{equation}
-\text{CE} : \text{E}_\text{i} > `r C4_GLB_diff_THRES` + `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
+\text{CE} : \text{E} > `r C4_GLB_diff_THRES` + `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{ref} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
 \end{equation}
+<!--
 where: $\text{E}$ the measured irradiance, $\text{E}_\text{CSm}$ the selected
@@
 the criterion of our CE identification.
+-->
+This is the criterion of our CE identification.
 
@@
 (i) manually selected days.
-For the latter case and where needed in some of the edge cases, we also used images
-from a sky-camera to further aid the decision of the manual inspection.
+For the latter case and where needed, we also used images from a sky-camera to
+further aid the decision of the manual inspection.
 
@@
 conditions favoring the occurrence of CE events. For the majority (over $62\,\%$) of
-the CE events the OIR is below the long term average of
+the CE events the OIR is below the longnterm average of
 $`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$,
@@
 through this 30 year period, is a dynamic phenomenon that's needs further investigation.
-Although, to approach it, we need more long term observations of AOD and clouds
+Although, to approach it, we need more long-term observations of AOD and clouds
 characteristics.

### 2024-06-22 article/article.tex
Commit 2024-06-22 20:14

@@
 measured GHI when aerosols are more abundant. To compensate for this, we
-defined the following threshold \(\text{E}\) to compare the measured
+defined the following threshold \(E\) to compare the measured
 \(\text{GHI}\): \begin{equation}
-\text{CE} : \text{E} > 15 + 1.04 \cdot \text{GHI}_\text{ref} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
+\text{CE} : E > 15 + 1.04 \cdot \text{GHI}_\text{ref} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
 \end{equation} This is the criterion of our CE identification.
@@
 measured intensity of the irradiance exceeds the TSI at the top of the
-atmosphere. In this case the threshold EEEEEEEEEE: \begin{equation}
-\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
+atmosphere. In this case the threshold \(E\) is given by:
+\begin{equation}
+\text{ECE}: E > \cos(\theta) \cdot E_{\odot} \frac{r^2_\text{m}} {r^2}
 \label{eq:ECE}
 \end{equation} where: \(\theta\) the solar zenith angle, \(E_{\odot}\)
-the solar constant adjusted for the actual Sun -- Earth distance, and
-\(i\) each of the one-minute observation.
+the solar constant adjusted for the actual Sun -- Earth distance \(r\)
+and \(r_\text{m}\) is the mean Sun -- Earth distance of
+\(1.496\times10^8\,\text{km}\).
 
@@
 
-\caption{Example of cloud identification for 2019-07-11.
+\caption{Example of CE identification for 2019-07-11.
 The green line with blue symbols depicts the measured GHI in one minute steps.
-The red line shows the modelled threshold for the detection of CE events, which are denoted with red circles.
+The red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles.
 The black curve represents the TSI at the top of the atmosphere, adjusted for the actual Sun-Earth distance and multiplied by the cosine of the cosine of SZA.}\label{fig:example-day}

### 2024-06-22 GHI_enh_02_ID_CE.R

@@ -759,8 +759,9 @@ if (TEST) {
     yearstodo <- sample(yearstodo, 3)
 }
 
+stop("d")
 
-pyear <- 2005
+yearstodo <- 2005
 for (pyear in yearstodo) {
     p <-
         ggplot(DATA[year(Date) == pyear],
@@ -778,7 +779,7 @@ for (pyear in yearstodo) {
                               high     = "red",
                               na.value = NA) +
         labs(title = pyear) +
-        ylab(bquote("SDR" ~ group("[", W/m^2,"]"))) +
+        ylab(bquote("GHI" ~ group("[", W/m^2,"]"))) +
         xlab(bquote("Clear sky reference" ~ group("[", W/m^2,"]"))) +
         # xlab(paste0(SelEnhanc, "_ref")) +
         # labs(color = "Over\nIrradiance W/m^2") +
@@ -792,7 +793,8 @@ for (pyear in yearstodo) {
             legend.background    = element_rect(fill = "transparent"),
             legend.margin        = margin(6, 6, 6, 6) ) +
         scale_x_continuous(expand = expansion(mult = c(0.03, 0.03))) +
-        scale_y_continuous(breaks = scales::breaks_extended(n = 6),
+        scale_y_continuous(#breaks = scales::breaks_extended(n = 6),
+                           breaks = pretty(),
                            expand = expansion(mult = c(0.03, 0.03)))
     print(p)
 
@@ -805,7 +807,6 @@ for (pyear in yearstodo) {
     #     geom_point(data = DATA[year(Date) == 2018 & GLB_diff < 0], colour = "black", size = 0.5) +
     #     geom_point(data = DATA[year(Date) == 2018 & GLB_diff > 0], size = 0.5, aes(color = GLB_diff)) +
     #     scale_colour_gradient2(low = "black", mid = "yellow", high = "red", na.value = NA)
-
 }
 
 

### 2024-06-22 article/article.Rmd
Commit 2024-06-22 20:14

@@
 generally greater than the measured GHI when aerosols are more abundant.  To
-compensate for this, we defined the following threshold $\text{E}$ to compare the
+compensate for this, we defined the following threshold $E$ to compare the
 measured $\text{GHI}$: 
@@
 \begin{equation}
-\text{CE} : \text{E} > `r C4_GLB_diff_THRES` + `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{ref} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
+\text{CE} : E > `r C4_GLB_diff_THRES` + `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{ref} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
 \end{equation}
@@
 
-<!-- reasoning for cretria -->
+<!-- reasoning for criteria -->
 <!-- We have to note, that the differentiation of the threshold factor was needed, because
@@
 events. These are cases of CE where the measured intensity of the irradiance exceeds
-the TSI at the top of the atmosphere. In this case the threshold EEEEEEEEEE:
+the TSI at the top of the atmosphere. In this case the threshold $E$ is given by:
 <!--and detected according to the Equation\nobreakspace{}\ref{eq:ECE}.-->
 \begin{equation}
-\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
+\text{ECE}: E > \cos(\theta) \cdot E_{\odot} \frac{r^2_\text{m}} {r^2}
 \label{eq:ECE}
 \end{equation}
-where: $\theta$ the solar zenith angle, $E_{\odot}$ the solar constant adjusted for the actual Sun -- Earth distance, and $i$ each of the one-minute observation.
+where: $\theta$ the solar zenith angle, $E_{\odot}$ the solar constant adjusted for
+the actual Sun -- Earth distance $r$ and $r_\text{m}$ is the mean Sun -- Earth
+distance of $1.496\times10^8\,\text{km}$.
 
@@
 
-```{r example-day, echo=FALSE, fig.cap="Example of cloud identification for 2019-07-11.
+```{r example-day, echo=FALSE, fig.cap="Example of CE identification for 2019-07-11.
 The green line with blue symbols depicts the measured GHI in one minute steps.
-The red line shows the modelled threshold for the detection of CE events, which are denoted with red circles.
+The red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles.
 The black curve represents the TSI at the top of the atmosphere, adjusted for the actual Sun-Earth distance and multiplied by the cosine of the cosine of SZA.", fig.pos='H'}

### 2024-06-23 article/article.Rmd
Commit 2024-06-23 16:14

@@
 and of no statistical significance.
-The average OIR for the entire period is about
-$`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$ with standard
-deviation of
-$`r round(sd(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$.
+The average OIR for the entire period is
+$`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2 
+\pm `r round(sd(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$.
 The interannual variability of the data about the trend lines is quite large.
-Furthermore, it tends to increase with time (at least for the quantities of panels b
-and c), suggesting a significant variability in cloud patterns over the area,
-possibly associated to changes in climate.
+Furthermore, the spread tends to increase with time (at least for the quantities of
+panels b and c), suggesting a significant variability in cloud patterns over the
+area, possibly associated to changes in climate.
 
@@
 
-!!! monthly weigth !!!
-
 Another interesting aspect of the CE events is their distribution within the year.
 Figure\nobreakspace{}\ref{fig:relative-month-occurrences} shows the monthly box and
-whisker plot of the CE number of occurrence normalized with the highest median value
+whisker plot of the CE number of occurrence normalized with the highest median value,
 that occurs in June, depicting a clear seasonal cycle.  Although CE events are
-present  throughout the year, the most active period  is during May and June.  During
+present  throughout the year, the most active months are May and June. During the
 winter (December -- February), the number of CE cases is about $25\,\%$ of the
-maximum, while in the intermediate months the number of occurrences gradually ramps
+maximum, while in the intermediate months, the number of occurrences gradually ramps
 between the maximum and minimum.  This seasonality is a combined effect of different
-factors, among them the types of clouds, their frequency of occurrence the seasonally
-varying relative position of the sun, as well as the local landscape characteristics
-that may influence the formation of clouds.  Unfortunately, lack of detailed data on
-cloud formation, type and location is not allowing further analysis. The interannual
-variability of the monthly CE events is quite high as manifested by the large monthly
-extremes, especially in the summer.
+factors, among them the types of clouds, their frequency of occurrence, the
+seasonally varying relative position of the sun, as well as the local landscape
+characteristics that may influence the formation of the clouds.  Unfortunately, lack
+of detailed data on cloud formation, type and location is not allowing further
+analysis. The interannual variability of the monthly CE events is quite high as
+manifested by the large monthly extremes, especially in the summer.
 
@@
 The monthly values have been also normalized to the relative abundance of valid GHI observations.
-The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles.
-The thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
+The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles, the thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
 The vertical lines (whiskers) extend between the maximum and minimum monthly values and the solid circles are outliers."}
@@
 Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently, there is an inverse
-relation between the frequency of CE events  and OIR with an exponential-like
-decline. This is expected, as the stronger the CE events become, the rarer are the
+relationship between the frequency of CE events and OIR with an exponential-like
+decline. This is expected, as the stronger the CE events are, the rarer the
 conditions favoring the occurrence of CE events. For the majority (over $62\,\%$) of
-the CE events the OIR is below the longnterm average of
+the CE events the OIR is below the long-term average of
 $`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$,
 while about $8.1\,\%$ of the events correspond to OIR larger than
-$100\,\text{W}/\text{m}^2$ and up to highest value of $412.4\,\text{W}/\text{m}^2$.
+$100\,\text{W}/\text{m}^2$ and up to the highest value of $412.4\,\text{W}/\text{m}^2$.
 This distribution is indicative of the magnitude and the probability of the expected
 CE events over Thessaloniki.  Similar distribution of CE events, albeit with larger
-OIR values, has been reported by @Vamvakas2020 for the city of Patras. This site is
+OIR values, has been reported by @Vamvakas2020, for the city of Patras. This site is
 located $2.5^\circ$ south of Thessaloniki and is exposed to air masses coming mainly

### 2024-06-23 article/article.tex
Commit 2024-06-23 16:14

@@
 (\(0.1\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of no statistical
-significance. The average OIR for the entire period is about
-\(39.9\,\text{W}/\text{m}^2\) with standard deviation of
-\(2.7\,\text{W}/\text{m}^2\). The interannual variability of the data
-about the trend lines is quite large. Furthermore, it tends to increase
-with time (at least for the quantities of panels b and c), suggesting a
-significant variability in cloud patterns over the area, possibly
-associated to changes in climate.
+significance. The average OIR for the entire period is
+\(39.9\,\text{W}/\text{m}^2 \pm 2.7\,\text{W}/\text{m}^2\). The
+interannual variability of the data about the trend lines is quite
+large. Furthermore, the spread tends to increase with time (at least for
+the quantities of panels b and c), suggesting a significant variability
+in cloud patterns over the area, possibly associated to changes in
+climate.
 
@@
 
-!!! monthly weigth !!!
-
 Another interesting aspect of the CE events is their distribution within
@@
 shows the monthly box and whisker plot of the CE number of occurrence
-normalized with the highest median value that occurs in June, depicting
+normalized with the highest median value, that occurs in June, depicting
 a clear seasonal cycle. Although CE events are present throughout the
-year, the most active period is during May and June. During winter
+year, the most active months are May and June. During the winter
 (December -- February), the number of CE cases is about \(25\,\%\) of
-the maximum, while in the intermediate months the number of occurrences
+the maximum, while in the intermediate months, the number of occurrences
 gradually ramps between the maximum and minimum. This seasonality is a
 combined effect of different factors, among them the types of clouds,
-their frequency of occurrence the seasonally varying relative position
+their frequency of occurrence, the seasonally varying relative position
 of the sun, as well as the local landscape characteristics that may
-influence the formation of clouds. Unfortunately, lack of detailed data
-on cloud formation, type and location is not allowing further analysis.
-The interannual variability of the monthly CE events is quite high as
-manifested by the large monthly extremes, especially in the summer.
+influence the formation of the clouds. Unfortunately, lack of detailed
+data on cloud formation, type and location is not allowing further
+analysis. The interannual variability of the monthly CE events is quite
+high as manifested by the large monthly extremes, especially in the
+summer.
 
@@
 The monthly values have been also normalized to the relative abundance of valid GHI observations.
-The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles.
-The thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
+The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles, the thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
 The vertical lines (whiskers) extend between the maximum and minimum monthly values and the solid circles are outliers.}\label{fig:relative-month-occurrences}
@@
 shown in Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently,
-there is an inverse relation between the frequency of CE events and OIR
-with an exponential-like decline. This is expected, as the stronger the
-CE events become, the rarer are the conditions favoring the occurrence
-of CE events. For the majority (over \(62\,\%\)) of the CE events the
-OIR is below the longnterm average of \(39.9\,\text{W}/\text{m}^2\),
-while about \(8.1\,\%\) of the events correspond to OIR larger than
-\(100\,\text{W}/\text{m}^2\) and up to highest value of
+there is an inverse relationship between the frequency of CE events and
+OIR with an exponential-like decline. This is expected, as the stronger
+the CE events are, the rarer the conditions favoring the occurrence of
+CE events. For the majority (over \(62\,\%\)) of the CE events the OIR
+is below the long-term average of \(39.9\,\text{W}/\text{m}^2\), while
+about \(8.1\,\%\) of the events correspond to OIR larger than
+\(100\,\text{W}/\text{m}^2\) and up to the highest value of
 \(412.4\,\text{W}/\text{m}^2\). This distribution is indicative of the
@@
 Thessaloniki. Similar distribution of CE events, albeit with larger OIR
-values, has been reported by \citet{Vamvakas2020} for the city of
+values, has been reported by \citet{Vamvakas2020}, for the city of
 Patras. This site is located \(2.5^\circ\) south of Thessaloniki and is

### 2024-06-23 article/article.tex
Commit 2024-06-23 17:12

@@
 CE events. For the majority (over \(62\,\%\)) of the CE events the OIR
-is below the long-term average of \(39.9\,\text{W}/\text{m}^2\), while
-about \(8.1\,\%\) of the events correspond to OIR larger than
+is below the long-term average of \(39.9 \, \text{W} / \text{m}^2\),
+while about \(8.1\,\%\) of the events correspond to OIR larger than
 \(100\,\text{W}/\text{m}^2\) and up to the highest value of
@@
 of these consecutive events, we grouped them into bins of increasing
-duration in steps of one minute.
-
-We have identified 28468 groups of CE in the whole period of study,
-where the group with the longest duration lasted 140 minutes on 07~July
-2013.
-
-Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}) shows the
+duration in steps of one minute. We have identified 28468 groups of CE
+in the whole period of study, where the group of the longest duration of
+140 minutes occurred on 07~July 2013.
+Figure\nobreakspace{}\ref{fig:ceg-duration-distribution} shows the
 frequency distribution of the CE events according to their duration. We
@@
 
-The relation between the duration of the CE groups and the excess
-irradiation of the groups has also been investigated
-(Figure\nobreakspace{}\ref{fig:group-2d}). Evidently, evens of high
-excess irradiation have small duration and vice versa. The vast majority
-of grouped events are associated with small excess irradiation (e.g.
-\(<5\,\text{kJ}/\text{m}^2\)) and small duration
+The relation between the duration and the mean OIR of the groups has
+also been studied (Figure\nobreakspace{}\ref{fig:group-2d}). Evidently,
+evens of high excess irradiation have small duration and vice versa. The
+vast majority of grouped events are associated with small excess
+irradiation (e.g.~\(<5\,\text{kJ}/\text{m}^2\)) and small duration
 (e.g.~\(<5\,\text{min}\)) while groups with strong excess irradiation
-and long duration are rare. Similar results on this relation, have been
-reported by \citet{Zhang2018}, on a study using a far higher sampling
-rate than ours.
+and long duration are very rare. Similar results of this relation have
+been reported by \citet{Zhang2018}, on a study using a far higher
+sampling rate than ours.
 
@@
 
-\caption{Seasonal statistics of the number of ECE occurancies for each month, normalized to the maximum occurancies on March.
-The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the max imum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies-ECE}
+\caption{Seasonal variability of the number of ECE events normalized to the maximum occurring in March, in the form of a box and whisker plot.
+The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles.
+The thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
+The vertical lines (whiskers) extend between the maximum and minimum monthly values.}\label{fig:relative-month-occurancies-ECE}
 \end{figure}
@@
 
-\hypertarget{discussion-and-conclusions}{%
-\section{Discussion and conclusions}\label{discussion-and-conclusions}}
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
 
@@
 
-The magnitude of the ECE events doesn't exceeds the values reported from
-sites with more favourable conditions for the phenomenon. Although, the
+The magnitude of the ECE events does not exceeds the values reported for
+sites with more favourable conditions for the phenomenon. The
 climatological characteristic of the ECE events, showed that the most

### 2024-06-23 article/article.Rmd
Commit 2024-06-23 17:12

@@
 ```
+
 <!--
@@
 <!-- ``` -->
+
 <!--
@@
 the CE events the OIR is below the long-term average of
-$`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$,
+$`r round(mean(ST_E_yearly$GLB_diff.mean), 1)` \, \text{W} / \text{m}^2$, 
 while about $8.1\,\%$ of the events correspond to OIR larger than
@@
 more than an hour. In order to study the characteristics of these consecutive events,
-we grouped them into bins of increasing duration in steps of one minute.
-
-We have identified `r ST_G0[, .N]` groups of CE in the
-whole period of study, where the
-group with the longest duration lasted
-`r ST_G0[, max(GLB_diff.N)]` minutes on
+we grouped them into bins of increasing duration in steps of one minute.  We have
+identified `r ST_G0[, .N]` groups of CE in the whole period of study, where the group
+of the longest duration of
+`r ST_G0[, max(GLB_diff.N)]` minutes occurred on
 `r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")`.
-
-Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}) shows the frequency
+Figure\nobreakspace{}\ref{fig:ceg-duration-distribution} shows the frequency
 distribution of the CE events according to their duration.  We conclude that although
@@
 
-The relation between the duration of the CE groups and the excess irradiation of the
-groups has also been investigated (Figure\nobreakspace{}\ref{fig:group-2d}).
-Evidently, evens of high excess irradiation have small duration and vice versa. The
-vast majority of grouped events are associated with small excess irradiation (e.g.
-$<5\,\text{kJ}/\text{m}^2$) and small duration (e.g. $<5\,\text{min}$) while groups
-with strong excess irradiation and long duration are rare.  Similar results on this
-relation, have been reported by @Zhang2018, on a study using a far higher sampling
-rate than ours.
+The relation between the duration and the mean OIR of the groups has also been
+studied (Figure\nobreakspace{}\ref{fig:group-2d}).  Evidently, evens of high excess
+irradiation have small duration and vice versa. The vast majority of grouped events
+are associated with small excess irradiation (e.g. $<5\,\text{kJ}/\text{m}^2$) and
+small duration (e.g. $<5\,\text{min}$) while groups with strong excess irradiation
+and long duration are very rare.  Similar results of this relation have been
+reported by @Zhang2018, on a study using a far higher sampling rate than ours.
 
@@
 <!-- ``` -->
+
 <!-- ```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"} -->
@@
 <!-- ``` -->
-
-<!-- \FloatBarrier -->
 
@@
 
-```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal statistics of the number of ECE occurancies for each month, normalized to the maximum occurancies on March.
-The box represents the values of the low $25\\,\\%$ percentile to $75\\,\\%$ percentile, where the thick horizontal line inside is the mean, the vertical lines extend to the max imum and minimum vales, the dots are outlier values, and the rhombus is the mean."}
+```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal variability of the number of ECE events normalized to the maximum occurring in March, in the form of a box and whisker plot.
+The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles.
+The thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
+The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
 knitr::include_graphics("../images/clim-ECE-month-norm-MAX-median-N-2.png")
@@
 
-<!-- -   SZA -->
+<!--  SZA -->
 
@@
 <!-- ``` -->
+
 <!-- ```{r echo=FALSE, fig.cap=""} -->
@@
 
-# Discussion and conclusions
+# Conclusions
 
@@
 
-The magnitude of the ECE events doesn't exceeds the values reported from sites with
-more favourable conditions for the phenomenon. Although, the climatological
-characteristic of the ECE events, showed that the most active months are spread on
-half of the year (March -- June and September and October).
-We found that CE conditions, can have a duration of more than an hour in rare
-cases, with the bulk of the cases having a duration under 5 minutes.
-Some of the characteristics of CE and ECE events we analysed,
+The magnitude of the ECE events does not exceeds the values reported for sites with
+more favourable conditions for the phenomenon. The climatological characteristic of
+the ECE events, showed that the most active months are spread on half of the year
+(March -- June and September and October).  We found that CE conditions, can have a
+duration of more than an hour in rare cases, with the bulk of the cases having a
+duration under 5 minutes.  Some of the characteristics of CE and ECE events we
+analysed,
 have strong similarities with results

### 2024-06-23 article/article.tex
Commit 2024-06-23 18:14

@@
 
-The magnitude of the ECE events does not exceeds the values reported for
+The magnitude of the ECE events does not exceed the values reported for
 sites with more favourable conditions for the phenomenon. The
 climatological characteristic of the ECE events, showed that the most
-active months are spread on half of the year (March -- June and
-September and October). We found that CE conditions, can have a duration
-of more than an hour in rare cases, with the bulk of the cases having a
-duration under 5 minutes. Some of the characteristics of CE and ECE
-events we analysed, have strong similarities with results by
-\citet{Vamvakas2020}, for a city southern of Thessaloniki, with the
-analogues differences on the intensity of the solar radiation.
+active months are spread in half of the year (March -- June, September
+and October). We found that CE conditions, can have a duration of more
+than an hour in rare cases, with the bulk of the cases having a duration
+under 5 minutes. Some of the characteristics of CE and ECE events we
+analysed have strong similarities with results by \citet{Vamvakas2020}
+for the city of Patras, south of Thessaloniki, with analog differences
+on the intensity of the solar radiation.
 
-An interpretation of the CE trends, shows that the interaction of GHI
+An interpretation of the CE trends shows that the interaction of GHI
 with the clouds, through this 30 year period, is a dynamic phenomenon
-that's needs further investigation. Although, to approach it, we need
-more long-term observations of AOD and clouds characteristics.
+that needs further investigation. Although, to approach it, we need more
+long-term observations of AOD and clouds characteristics.
 

### 2024-06-23 article/article.Rmd
Commit 2024-06-23 18:14

@@
 
-The magnitude of the ECE events does not exceeds the values reported for sites with
+The magnitude of the ECE events does not exceed the values reported for sites with
 more favourable conditions for the phenomenon. The climatological characteristic of
-the ECE events, showed that the most active months are spread on half of the year
-(March -- June and September and October).  We found that CE conditions, can have a
+the ECE events, showed that the most active months are spread in half of the year
+(March -- June, September and October). We found that CE conditions, can have a
 duration of more than an hour in rare cases, with the bulk of the cases having a
 duration under 5 minutes.  Some of the characteristics of CE and ECE events we
-analysed,
-have strong similarities with results
-by @Vamvakas2020, for a city southern of Thessaloniki, with the analogues differences on the
- intensity of the solar radiation.
+analysed have strong similarities with results by @Vamvakas2020 for the city of
+Patras, south of Thessaloniki, with analog differences on the intensity of the
+solar radiation.
 
-An interpretation of the CE trends, shows that the interaction of GHI with the
-clouds,
-through this 30 year period, is a dynamic phenomenon that's needs further investigation.
-Although, to approach it, we need more long-term observations of AOD and clouds
-characteristics.
+An interpretation of the CE trends shows that the interaction of GHI with the clouds,
+through this 30 year period, is a dynamic phenomenon that needs further
+investigation.  Although, to approach it, we need more long-term observations of AOD
+and clouds characteristics.
+
+<!-- END -->

### 2024-06-24 article/article.Rmd
Commit 2024-06-24 06:14

@@
 simulations. We tried different approaches in order to strengthen the robustness of
-the methodology and compensate for the limited accuracy of the RTM input data and the
-unpredictable natural variability of the atmosphere.
+the methodology and to compensate for the limited accuracy of the RTM input data and
+the unpredictable natural variability of the atmosphere.
 
@@
 <!-- `r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`. -->
-The stronger CE event of
+The strongest CE event of
 $`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 

### 2024-06-24 article/article.tex
Commit 2024-06-24 06:14

@@
 approaches in order to strengthen the robustness of the methodology and
-compensate for the limited accuracy of the RTM input data and the
+to compensate for the limited accuracy of the RTM input data and the
 unpredictable natural variability of the atmosphere.
@@
 \(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007, corresponding to OIR of
-\(345.9\,\text{W}/\text{m}^2\). The stronger CE event of \(49.7\,\%\)
+\(345.9\,\text{W}/\text{m}^2\). The strongest CE event of \(49.7\,\%\)
 above the clear sky threshold was observed on 28~October 2016. In the

### 2024-06-25 article/article.tex
Commit 2024-06-25 21:11

@@
 
-\hypertarget{abstract}{%
-\section*{Abstract}\label{abstract}}
+\section*{Abstract}\label{abstract}
 \addcontentsline{toc}{section}{Abstract}
@@
 collocated Cimel sun photometer and a Brewer spectrophotometer. We found
-a trend in CE events of \(45.6\pm 21.9\,\text{cases}/\text{year}\), and
-a trend in the CE events irradiation of
-\(116.9\pm 67.8\,\text{kJ}/\text{year}\). The peak of the CE events was
-observed during May and June. An analysis of the total duration of CE
-events, showed that durations longer than 5 minutes are very rare, with
-exceptions lasting over an hour. Finally we have detected enhancements
-above the total solar irradiance at the top of the atmosphere of up to
-\(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the cases below
-\(200\,\text{W}/\text{m}^{2}\).
+a trend in CE events of \(45.6\pm
+21.9\,\text{cases}/\text{year}\), and a trend in the CE events
+irradiation of \(116.9\pm
+67.8\,\text{kJ}/\text{year}\). The peak of the CE events was observed
+during May and June. An analysis of the total duration of CE events,
+showed that durations longer than 5 minutes are very rare, with
+exceptions lasting over an hour and up to 140 minutes. Finally, we have
+detected enhancements above the total solar irradiance at the top of the
+atmosphere of up to \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\)
+of the cases below \(200\,\text{W}/\text{m}^{2}\). The most active
+season of these extreme events is spring until early summer and autumn.
 
-CE: cloud enhancement cases one minute
-
-ECE: extreme cloud enhancement cases one minute over TSI on horizontal
-plane
-
-CEG: cloud enhancement groups, cases events with consecutive CE
-
-\(\text{GHI}_\text{i}\): measured one minute global horizontal
-irradiance
-
-\(\text{GHI}_\text{CSm}\): modelled clear sky one minute global
-horizontal irradiance
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}
 
@@
 of GHI observations at Thessaloniki, Greece. We used modeled clear sky
-irradiance as a baseline to identify cloud enhancements and we
-determined long-term trends of the above mentioned metrics, their
+irradiance as a baseline to identify cloud enhancements, and we
+determined long-term trends of the above-mentioned metrics, their
 climatology and some general characteristics. To our knowledge there are
@@
 
-\hypertarget{data-and-methodology}{%
-\section{Data and methodology}\label{data-and-methodology}}
+\section{Data and methodology}\label{data-and-methodology}
 
-\hypertarget{instrumentation-and-data}{%
-\subsection{Instrumentation and data}\label{instrumentation-and-data}}
+\subsection{Instrumentation and data}\label{instrumentation-and-data}
 
@@
 
-\hypertarget{cloud-enhancement-detection}{%
 \subsection{Cloud enhancement
-detection}\label{cloud-enhancement-detection}}
+detection}\label{cloud-enhancement-detection}
 
@@
 using a radiative transfer model (RTM). The applied methodology is
-discussed in section\nobreakspace{}\ref{rtmcs}..
+discussed in section\nobreakspace{}\ref{rtmcs}.
 
-\hypertarget{rtmcs}{%
-\subsection{Modeled clear Sky Irradiance}\label{rtmcs}}
+\subsection{Modeled clear Sky Irradiance}\label{rtmcs}
 
-\hypertarget{climatology-of-clear-sky-irradiance}{%
 \subsubsection{Climatology of clear sky
-irradiance}\label{climatology-of-clear-sky-irradiance}}
+irradiance}\label{climatology-of-clear-sky-irradiance}
 
@@
 \citet{Kurucz1994} in the range \(280\) to \(2500\,\text{nm}\), the
-radiative trasfer solver ``disort'' in ``pseudospherical'' geometry and
+radiative transfer solver ``disort'' in ``pseudospherical'' geometry and
 the ``LOWTRAN'' gas parameterization. The model was run for a range of
-variables in order to create a look up table (LUT) for the estimation of
+variables in order to create a look-up table (LUT) for the estimation of
 the cloud-free reference irradiance for each individual observation of
@@
 combinations with additional offsets of \(\pm1\sigma\) and
-\(\pm2\sigma\) , were used as inputs to the RTM in the construction of
+\(\pm2\sigma\), were used as inputs to the RTM in the construction of
 the LUT.
@@
 estimation of the \(\text{GHI}_\text{ref}\) for all combinations of the
-AOD and WC with the above mentioned standard deviation offsets. Finally,
+AOD and WC with the above-mentioned standard deviation offsets. Finally,
 each \(\text{GHI}_\text{ref}\) value was adjusted to the actual
@@
 
-\hypertarget{long-term-change-of-clear-sky-irradiance}{%
 \subsubsection{Long-term change of clear sky
-irradiance}\label{long-term-change-of-clear-sky-irradiance}}
+irradiance}\label{long-term-change-of-clear-sky-irradiance}
 
@@
 
-\hypertarget{criteria-for-the-identification-of-ce-events}{%
 \subsection{Criteria for the identification of CE
-events}\label{criteria-for-the-identification-of-ce-events}}
+events}\label{criteria-for-the-identification-of-ce-events}
 
@@
 major CE events. Where some CE events with very low OIR may be not
-detected, these are few with small over-irradiance and it is unlikely
-that will effect significantly our results.
+detected, these are few with small over-irradiance, and it is unlikely
+that will affect significantly our results.
 
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\section{Results}\label{results}
 
 Following the application of the above discussed methodology to the
-entire dataset (6.1 million of one-minute GHI measurements),
+entire dataset (\(6.1\) million of one-minute GHI measurements),
 \(1.76\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
@@
 
-\hypertarget{long-term-trends}{%
-\subsection{Long-term trends}\label{long-term-trends}}
+\subsection{Long-term trends}\label{long-term-trends}
 
@@
 (\(45.6\pm 21.9\,\text{cases}/\text{year}\)) and the excess irradiation
-(\(116.9\pm 67.8\,\text{kJ}/\text{year}\)), which are also statistically
-significant. In contrast the trend of the yearly mean OIR is negligible
-(\(0.1\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of no statistical
-significance. The average OIR for the entire period is
-\(39.9\,\text{W}/\text{m}^2 \pm 2.7\,\text{W}/\text{m}^2\). The
-interannual variability of the data about the trend lines is quite
-large. Furthermore, the spread tends to increase with time (at least for
-the quantities of panels b and c), suggesting a significant variability
-in cloud patterns over the area, possibly associated to changes in
-climate.
+(\(116.9 \pm 67.8\,\text{kJ}/\text{year}\)), which are also
+statistically significant. In contrast the trend of the yearly mean OIR
+is negligible (\(0.1\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of
+no statistical significance. The average OIR for the entire period is
+\(39.9\pm 2.7\,\text{W}/\text{m}^2\). The interannual variability of the
+data about the trend lines is quite large. Furthermore, the spread tends
+to increase with time (at least for the quantities of panels b and c),
+suggesting a significant variability in cloud patterns over the area,
+possibly associated to changes in climate.
 
@@
 
-\hypertarget{climatology-of-cloud-enhancement-events}{%
 \subsection{Climatology of cloud enhancement
-events}\label{climatology-of-cloud-enhancement-events}}
+events}\label{climatology-of-cloud-enhancement-events}
 
@@
 
-\hypertarget{duration-of-cloud-enhancement-events}{%
 \subsection{Duration of cloud enhancement
-events}\label{duration-of-cloud-enhancement-events}}
+events}\label{duration-of-cloud-enhancement-events}
 
@@
 
-\hypertarget{extreme-cloud-enhancement-events}{%
 \subsection{Extreme cloud enhancement
-events}\label{extreme-cloud-enhancement-events}}
+events}\label{extreme-cloud-enhancement-events}
 
@@
 
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
+\section{Conclusions}\label{conclusions}
 
@@
 events over Thessaloniki is concentrated on early summer, on May and
-June.
+June. We found that continuous CE events can last up to \(140\) minutes,
+and \(80\,\\%\) of them bellow \(5\) minutes.
 
 The magnitude of the ECE events does not exceed the values reported for
-sites with more favourable conditions for the phenomenon. The
+sites with more favourable conditions for the phenomenon. We have
+observed cases exceeding the TSI by \(400\,\text{W}/\text{m}^{2}\) with
+\(75\,\%\) of the cases under \(200\,\text{W}/\text{m}^{2}\). The
 climatological characteristic of the ECE events, showed that the most
@@
 An interpretation of the CE trends shows that the interaction of GHI
-with the clouds, through this 30 year period, is a dynamic phenomenon
+with the clouds, through this 30-year period, is a dynamic phenomenon
 that needs further investigation. Although, to approach it, we need more

### 2024-06-25 article/article.Rmd
Commit 2024-06-25 21:11

@@
 duration of CE events, showed that durations longer than 5 minutes are very rare,
-with exceptions lasting over an hour.  Finally we have detected enhancements above
+with exceptions lasting over an hour and up to 140 minutes.  Finally, we have detected enhancements above
 the total solar irradiance at the top of the atmosphere of up to
 $400\,\text{W}/\text{m}^{2}$, with the $75\,\%$ of the cases below
-$200\,\text{W}/\text{m}^{2}$.
+$200\,\text{W}/\text{m}^{2}$. The most active season of these extreme events is
+spring until early summer and autumn.
 
+<!--
 CE: cloud enhancement cases one minute
@@
 $\text{GHI}_\text{CSm}$: modelled clear sky one minute global horizontal irradiance 
+-->
 
@@
 clouds. In general, clouds can attenuate a fraction of solar irradiance, but under
-certain conditions, can lead to  enhancement of the global horizontal irradiance
-(GHI) reaching the ground. This cloud enhancement (CE) effect can locally increase
-the observed GHI to levels even higher than the expected clear-sky irradiance
+certain conditions, can lead to enhancement of the global horizontal irradiance (GHI)
+reaching the ground. This cloud enhancement (CE) effect can locally increase the
+observed GHI to levels even higher than the expected clear-sky irradiance
 [@Cordero2023; @Vamvakas2020; @CastillejoCuberos2020; @Vamvakas2020 and references
@@
 Thessaloniki, Greece.  We used modeled clear sky irradiance as a baseline to identify
-cloud enhancements and we determined long-term trends of the above mentioned metrics,
+cloud enhancements, and we determined long-term trends of the above-mentioned metrics,
 their climatology and some general characteristics.  To our knowledge there are no
@@
 using a radiative transfer model (RTM).  The applied methodology is discussed in
-section\nobreakspace{}\ref{rtmcs}..
+section\nobreakspace{}\ref{rtmcs}.
 
@@
 by @Vamvakas2020.  In uvspec we used the solar spectrum of @Kurucz1994 in the range
-$280$ to $2500\,\text{nm}$, the radiative trasfer solver "disort" in
+$280$ to $2500\,\text{nm}$, the radiative transfer solver "disort" in
 "pseudospherical" geometry and the "LOWTRAN" gas parameterization.  The model was run
-for a range of variables in order to create a look up table (LUT) for the estimation
+for a range of variables in order to create a look-up table (LUT) for the estimation
 of the cloud-free reference irradiance for each individual observation of our
@@
 (WC).  The monthly climatological values of AOD and water column, as well as
-combinations with additional offsets of $\pm1\sigma$ and $\pm2\sigma$ , were used as
+combinations with additional offsets of $\pm1\sigma$ and $\pm2\sigma$, were used as
 inputs to the RTM in the construction of the LUT.
@@
 month. The same procedure was followed for the estimation of the
-$\text{GHI}_\text{ref}$ for all combinations of the AOD and WC with the above
-mentioned standard deviation offsets.  Finally, each $\text{GHI}_\text{ref}$ value
-was adjusted to the actual Sun-Earth distance derived by the Astropy software library
-[@AstropyCollaboration2022].
+$\text{GHI}_\text{ref}$ for all combinations of the AOD and WC with the
+above-mentioned standard deviation offsets.  Finally, each $\text{GHI}_\text{ref}$
+value was adjusted to the actual Sun-Earth distance derived by the Astropy software
+library [@AstropyCollaboration2022].
 
@@
 this method is capable in detecting all major CE events.  Where some CE events with
-very low OIR may be not detected, these are few with small over-irradiance and it is
-unlikely that will effect significantly our results.
+very low OIR may be not detected, these are few with small over-irradiance, and it is
+unlikely that will affect significantly our results.
 
-<!-- extreme cases criterion -->
+<!-- extreme caces criterion -->
 A sub-category of the CE events that is often discussed in the relevant literature
@@
 Following the application of the above discussed methodology to the entire dataset 
-(`r round(ST_total$wattGLB.N / 10^6,1)` million of one-minute GHI measurements),
+($`r round(ST_total$wattGLB.N / 10^6,1)`$ million of one-minute GHI measurements),
 $`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 2)`\,\%$ were identified as CE events and
@@
 frequency of occurrence 
-($`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$)
+($`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$)
 and the excess irradiation 
-($`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$),
+($`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)` \pm `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$),
 which are also statistically significant.
 In contrast the trend of the yearly mean OIR is negligible 
-($`r round(yearlyCE[var == "GLB_diff.mean", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\text{W}/\text{m}^2/\text{year}$)
+($`r round(yearlyCE[var == "GLB_diff.mean", slope], 1)`\pm `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\text{W}/\text{m}^2/\text{year}$)
 and of no statistical significance.
 The average OIR for the entire period is
-$`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2 
-\pm `r round(sd(ST_E_yearly$GLB_diff.mean), 1)`\,\text{W}/\text{m}^2$.
+$`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\pm `r round(sd(ST_E_yearly$GLB_diff.mean),1)`\,\text{W}/\text{m}^2$.
 The interannual variability of the data about the trend lines is quite large.
@@
 equivalent clear sky irradiance by a significant amount.
-
-<!-- $`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm -->
-<!-- `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2/y$ -->
-<!-- (Figure\nobreakspace{}\ref{fig:P-energy-mean}), -->
-<!-- but this value alone is not very useful due the intrinsic high variability of this -->
-<!-- metric. -->
-
-<!-- ```{r CEmeanDaily2, echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"} -->
-<!-- knitr::include_graphics("../images/daily-12.png") -->
-<!-- ``` -->
-<!-- ```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"} -->
-<!-- knitr::include_graphics("../images/energy-3.png") -->
-<!-- ``` -->
-<!-- ```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean OIR per CE."} -->
-<!-- knitr::include_graphics("../images/P-energy-3.png") -->
-<!-- ``` -->
-<!-- ```{r echo=FALSE, fig.cap="Trend of number of CE cases"} -->
-<!-- knitr::include_graphics("../images/energy-2.png") -->
-<!-- ``` -->
-<!-- ```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly cloud enhancement occurrences."} -->
-<!-- knitr::include_graphics("../images/P-energy-2.png") -->
-<!-- ``` -->
-<!-- ```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"} -->
-<!-- knitr::include_graphics("../images/energy-1.png") -->
-<!-- ``` -->
-<!-- ```{r P-energy-sum, echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"} -->
-<!-- knitr::include_graphics("../images/P-energy-1.png") -->
-<!-- ``` -->
-<!-- ```{r P-energy-median, echo=FALSE, fig.cap="Trend of the yearly median over irradiance due to CE over irradiance"} -->
-<!-- knitr::include_graphics("../images/P_energy-8.png") -->
-<!-- ``` -->
 
@@
 ```
-
-<!--
-```{r echo=FALSE, fig.cap="Distribution of the number of CE cases"}
-knitr::include_graphics("../images/climCEmonth-1.png")
-```
---->
-
-<!-- ```{r echo=FALSE, fig.cap="Distribution of CE above reference"} -->
-<!-- knitr::include_graphics("../images/relative_distributions-2.png") -->
-<!-- ``` -->
-
-<!--
-```{r echo=FALSE, fig.cap="Distribution of CE above reference"}
-knitr::include_graphics("../images/relative_distributions-4.png")
-```
--->
 
@@
 
-<!-- \FloatBarrier -->
-
 # Conclusions
@@
 After analyzing the CE cases, we found an increase of 
-$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$,
+$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$,
 with the
 mean annual total energy of the CE events increasing with a rate of
-$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$.
+$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$.
 The most active season of CE events over Thessaloniki is concentrated on early
 summer, on May and June.
+We found that continuous CE events can last up to $140$ minutes, and $80\,\\%$ of
+them bellow $5$ minutes.
 
 The magnitude of the ECE events does not exceed the values reported for sites with
-more favourable conditions for the phenomenon. The climatological characteristic of
-the ECE events, showed that the most active months are spread in half of the year
-(March -- June, September and October). We found that CE conditions, can have a
-duration of more than an hour in rare cases, with the bulk of the cases having a
-duration under 5 minutes.  Some of the characteristics of CE and ECE events we
-analysed have strong similarities with results by @Vamvakas2020 for the city of
-Patras, south of Thessaloniki, with analog differences on the intensity of the
-solar radiation.
+more favourable conditions for the phenomenon. We have observed cases exceeding the
+TSI by $400\,\text{W}/\text{m}^{2}$ with $75\,\%$ of the cases under
+$200\,\text{W}/\text{m}^{2}$. The climatological characteristic of the ECE events,
+showed that the most active months are spread in half of the year (March -- June,
+September and October). We found that CE conditions, can have a duration of more than
+an hour in rare cases, with the bulk of the cases having a duration under 5 minutes.
+Some of the characteristics of CE and ECE events we analysed have strong similarities
+with results by @Vamvakas2020 for the city of Patras, south of Thessaloniki, with
+analog differences on the intensity of the solar radiation.
 
 An interpretation of the CE trends shows that the interaction of GHI with the clouds,
-through this 30 year period, is a dynamic phenomenon that needs further
+through this 30-year period, is a dynamic phenomenon that needs further
 investigation.  Although, to approach it, we need more long-term observations of AOD

### 2024-06-26 Article_B7/Article_B7_plain.tex
Commit 2024-06-26 09:15

--- 2024-06-25 article/article.tex
@@
     \cortext[cor1]{Corresponding author}
-    \fntext[1]{This is the first author footnote.}
-    \fntext[2]{Another author footnote.}
 
   \begin{abstract}
-  Here will be the abstract.
+  We studied the enhancement of the global horizontal irradiance induced
+  by clouds over Thessaloniki for the period 1993 -- 2023 using data
+  recorded every one minute. We identified the cloud enhancement events
+  (CE) by creating an appropriate clear sky irradiance reference with
+  the use of a radiative transfer model and aerosol optical depth data
+  from a collocated Cimel sun photometer and a Brewer spectrophotometer.
+  We found a trend in CE events of
+  \(45.6\pm 21.9\,\text{cases}/\text{year}\), and a trend in the CE
+  events irradiation of \(116.9\pm 67.8\,\text{kJ}/\text{year}\). The
+  peak of the CE events was observed during May and June. An analysis of
+  the total duration of CE events, showed that durations longer than 5
+  minutes are very rare, with exceptions lasting over an hour and up to
+  140 minutes. Finally, we have detected enhancements above the total
+  solar irradiance at the top of the atmosphere of up to
+  \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the cases below
+  \(200\,\text{W}/\text{m}^{2}\). The most active season of these
+  extreme events is spring until early summer and autumn.
   \end{abstract}
@@
 
-\section*{Abstract}\label{abstract}
-\addcontentsline{toc}{section}{Abstract}
-
-We studied the enhancement of the global horizontal irradiance induced
-by clouds over Thessaloniki for the period 1993 -- 2023 using data
-recorded every one minute. We identified the cloud enhancement events
-(CE) by creating an appropriate clear sky irradiance reference with the
-use of a radiative transfer model and aerosol optical depth data from a
-collocated Cimel sun photometer and a Brewer spectrophotometer. We found
-a trend in CE events of \(45.6\pm
-21.9\,\text{cases}/\text{year}\), and a trend in the CE events
-irradiation of \(116.9\pm
-67.8\,\text{kJ}/\text{year}\). The peak of the CE events was observed
-during May and June. An analysis of the total duration of CE events,
-showed that durations longer than 5 minutes are very rare, with
-exceptions lasting over an hour and up to 140 minutes. Finally, we have
-detected enhancements above the total solar irradiance at the top of the
-atmosphere of up to \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\)
-of the cases below \(200\,\text{W}/\text{m}^{2}\). The most active
-season of these extreme events is spring until early summer and autumn.
-
-\section{Introduction}\label{introduction}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 
-\section{Data and methodology}\label{data-and-methodology}
+\hypertarget{data-and-methodology}{%
+\section{Data and methodology}\label{data-and-methodology}}
 
-\subsection{Instrumentation and data}\label{instrumentation-and-data}
+\hypertarget{instrumentation-and-data}{%
+\subsection{Instrumentation and data}\label{instrumentation-and-data}}
 
@@
 
+\hypertarget{cloud-enhancement-detection}{%
 \subsection{Cloud enhancement
-detection}\label{cloud-enhancement-detection}
+detection}\label{cloud-enhancement-detection}}
 
@@
 
-\subsection{Modeled clear Sky Irradiance}\label{rtmcs}
+\hypertarget{rtmcs}{%
+\subsection{Modeled clear Sky Irradiance}\label{rtmcs}}
 
+\hypertarget{climatology-of-clear-sky-irradiance}{%
 \subsubsection{Climatology of clear sky
-irradiance}\label{climatology-of-clear-sky-irradiance}
+irradiance}\label{climatology-of-clear-sky-irradiance}}
 
@@
 
+\hypertarget{long-term-change-of-clear-sky-irradiance}{%
 \subsubsection{Long-term change of clear sky
-irradiance}\label{long-term-change-of-clear-sky-irradiance}
+irradiance}\label{long-term-change-of-clear-sky-irradiance}}
 
@@
 
+\hypertarget{criteria-for-the-identification-of-ce-events}{%
 \subsection{Criteria for the identification of CE
-events}\label{criteria-for-the-identification-of-ce-events}
+events}\label{criteria-for-the-identification-of-ce-events}}
 
@@
 
-\section{Results}\label{results}
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
@@
 
-\subsection{Long-term trends}\label{long-term-trends}
+\hypertarget{long-term-trends}{%
+\subsection{Long-term trends}\label{long-term-trends}}
 
@@
 
+\hypertarget{climatology-of-cloud-enhancement-events}{%
 \subsection{Climatology of cloud enhancement
-events}\label{climatology-of-cloud-enhancement-events}
+events}\label{climatology-of-cloud-enhancement-events}}
 
@@
 
+\hypertarget{duration-of-cloud-enhancement-events}{%
 \subsection{Duration of cloud enhancement
-events}\label{duration-of-cloud-enhancement-events}
+events}\label{duration-of-cloud-enhancement-events}}
 
@@
 
+\hypertarget{extreme-cloud-enhancement-events}{%
 \subsection{Extreme cloud enhancement
-events}\label{extreme-cloud-enhancement-events}
+events}\label{extreme-cloud-enhancement-events}}
 
@@
 
-\section{Conclusions}\label{conclusions}
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
 
@@
 June. We found that continuous CE events can last up to \(140\) minutes,
-and \(80\,\\%\) of them bellow \(5\) minutes.
+and \(80\,\%\) of them bellow \(5\) minutes.
 

### 2024-06-26 Article_B7/Article_B7.Rmd
Commit 2024-06-26 09:15

--- 2024-06-25 article/article.Rmd
@@
   #   country:      The Netherlands
-footnote:
-  - code: 1
-    text: "This is the first author footnote."
-  - code: 2
-    text: "Another author footnote."
+# footnote:
+#   - code: 1
+#     text: "This is the first author footnote."
+#   - code: 2
+#     text: "Another author footnote."
 abstract: |
-  Here will be the abstract.
+  We studied the enhancement of the global horizontal irradiance induced
+  by clouds over Thessaloniki for the period 1993 -- 2023 using data
+  recorded every one minute. We identified the cloud enhancement events
+  (CE) by creating an appropriate clear sky irradiance reference with the
+  use of a radiative transfer model and aerosol optical depth data from a
+  collocated Cimel sun photometer and a Brewer spectrophotometer. We found
+  a trend in CE events of \(45.6\pm 21.9\,\text{cases}/\text{year}\), and
+  a trend in the CE events irradiation of
+  \(116.9\pm 67.8\,\text{kJ}/\text{year}\). The peak of the CE events was
+  observed during May and June. An analysis of the total duration of CE
+  events, showed that durations longer than 5 minutes are very rare, with
+  exceptions lasting over an hour and up to 140 minutes. Finally, we have
+  detected enhancements above the total solar irradiance at the top of the
+  atmosphere of up to \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\)
+  of the cases below \(200\,\text{W}/\text{m}^{2}\). The most active
+  season of these extreme events is spring until early summer and autumn.
 
@@
 
-# Abstract {.unnumbered}
+<!-- # Abstract {.unnumbered} -->
 
+<!--
 We studied the enhancement of the global horizontal irradiance induced by clouds over
@@
 spring until early summer and autumn. 
+-->
 
@@
 summer, on May and June.
-We found that continuous CE events can last up to $140$ minutes, and $80\,\\%$ of
+We found that continuous CE events can last up to $140$ minutes, and $80\,\%$ of
 them bellow $5$ minutes.

### 2024-06-27 GHI_enh_04_investigate.tex
Commit 2024-06-27 16:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-06-12}
+\date{2024-06-27}
 
@@
 \end{figure}
-
-\begin{verbatim}
-Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
-i Please use the `legend.position.inside` argument of `theme()` instead.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
-
 \begin{figure}[H]
@@
 
-\hypertarget{zhang2018}{%
-\subsection{@Zhang2018}\label{zhang2018}}
+\begin{verbatim}
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
+i Please use the `legend.position.inside` argument of `theme()` instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
 
@@
 \caption{ - empty caption - }\label{fig:groups-10}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-11}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-11}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-12}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-12}
+\end{figure}
+
+\hypertarget{zhang2018}{%
+\subsection{@Zhang2018}\label{zhang2018}}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-13}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-13}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-14}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-14}
 \end{figure}
@@
 \begin{verbatim}
-2024-06-12 08:50:47.4 athan@tyler GHI_enh_04_investigate.R 1.594768 mins
+2024-06-27 02:44:09.1 athan@tyler GHI_enh_04_investigate.R 2.523809 mins
 \end{verbatim}

### 2024-07-04 article/article.Rmd
Commit 2024-07-04 21:13

@@
   #   country:      The Netherlands
-footnote:
-  - code: 1
-    text: "This is the first author footnote."
-  - code: 2
-    text: "Another author footnote."
+# footnote:
+#   - code: 1
+#     text: "This is the first author footnote."
+#   - code: 2
+#     text: "Another author footnote."
 abstract: |
-  Here will be the abstract.
+  In this study we investigate the characteristics of global horizontal irradiance
+  enhancement events induced by clouds over Thessaloniki for the period 1993 -- 2023
+  using data recorded every one minute. We identified the cloud enhancement (CE)
+  events by creating an appropriate clear-sky irradiance reference with the use of a
+  radiative transfer model and aerosol optical depth data from a collocated Cimel sun
+  photometer and a Brewer spectrophotometer. We found a trend in CE events of
+  \(45.6\pm 21.9\,\text{cases}/\text{year}\), and a trend in the CE events
+  irradiation of \(116.9\pm 67.8\,\text{kJ}/\text{year}\). The peak of the CE events
+  was observed during May and June. The analysis of the total duration of CE events
+  showed that durations longer than 5 minutes are very rare, with exceptions lasting
+  over an hour and up to 140 minutes. Finally, we have detected enhancements above
+  the total solar irradiance at the top of the atmosphere of up to
+  \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the cases below
+  \(200\,\text{W}/\text{m}^{2}\). The most active period of these extreme events is
+  spring -- early summer with a secondary peak in autumn.
 
@@
 
-The shortwave solar radiation, reaching Earth's surface, is the main energy source of
-the atmosphere and the biosphere, and drives and governs the climate [@Gray2010].  It
-has direct practical application in industries like energy and agricultural
+The shortwave solar radiation, reaching Earth's surface, is the main energy source
+for the atmosphere and the biosphere, and drives and governs the climate [@Gray2010].
+It has direct practical application in industries related to energy and agricultural
 production. The variability of its intensity can impose difficulties in predicting
@@
 Significant portion of research has been focused on predicting the renewable energy
-production in a fine timescale and in near real-time (for a review see @Inman2013;
-@Graabak2016).
+production in a fine timescale and in near real-time [for a review see @Inman2013;
+@Graabak2016].
 
@@
 have also some practical implications.  The intensity and duration of enhancements
-can effect the efficiency and stability of photovoltaic power production
-[@Lappalainen2020; @Jaervelae2020] while ECEs have the potential to compromise the
+can affect the efficiency and stability of photovoltaic power production
+[@Lappalainen2020; @Jaervelae2020], while ECEs have the potential to compromise the
 integrity of photovoltaic plants infrastructure [@DoNascimento2019].  It has also
 been demonstrated that these events can interfere in the comparison of ground-based
-and satellite observations [@Damiani2018].  Global warming has likely affected cloud
-coverage in the last few decades. @Liu2023 reported increases in cloud cover over the
-tropical and subtropical oceans and decreases over most continents, while @Dong2023
-reported decreases over North America and Europe. To our knowledge, there is no
-evidence on whether this trend has affected also the number and strength of CE
-events.
+and satellite observations of radiation [@Damiani2018].  Global warming has likely
+affected cloud coverage in the last few decades. @Liu2023 reported increases in cloud
+cover over the tropical and subtropical oceans and decreases over most continents,
+while @Dong2023 reported decreases over North America and Europe. To our knowledge,
+there is no evidence on whether this trend has affected also the number and strength
+of CE events.
 
@@
 Methods of identification of CE events usually include the use of simulated clear
-sky irradiance as baseline, that is combined with an appropriate threshold or some
+sky irradiance as baseline, combined with an appropriate threshold or some
 other statistical characteristics, and in some cases, with visual inspection of sky
@@
 @Long2008a].  Thus, problematic recordings have been excluded from further
-processing.
+processing.  Furthermore, due to the significant measurement uncertainty in GHI when
+the Sun is near the horizon, and due to some systematic obstructions by nearby
+buildings, we have excluded all measurements with solar zenith angle (SZA) greater
+than $`r 90 - BIO_ELEVA`^\circ$.  Finally, images from a sky camera have been used in
+the manual inspection of the CE identification. The sky camera operates since 2012
+and stores images in 5 min time steps.
 <!--
@@
 -->
-Furthermore, due to the significant measurement uncertainty in GHI when the Sun is
-near the horizon, and due to some systematic obstructions by nearby buildings, we
-have excluded all measurements with solar zenith angle (SZA) greater than $`r 90 -
-BIO_ELEVA`^\circ$.
-
-Finally, images from a sky camera have been used in the manual inspection of the CE
-identification. The sky camera operates since 2012 and stores images in 5 min time
-steps.
 
@@
 irradiance (OIR). The OIR is defined as the irradiance difference of the measured
-one-minute GHI from the $\text{GHI}_\text{ref}$ corresponding to
-cloud-free atmosphere.
+one-minute GHI from the $\text{GHI}_\text{ref}$ corresponding to cloud-free
+atmosphere.
 <!-- CE identification criterion ($\text{OIR}_i =
@@
 threshold and/or an additional constant offset.  The initial results showed that we
-can detect a big portion of the CE events. However, by inspecting the daily plots of
-irradiance it became evident that changes in atmospheric conditions introduced
-numerous false positive and false negative results.  The main reason for these
-discrepancies is the variability of the effects of aerosols and water vapor which
-were not taken into account in the two simple methods.  To produce a more
-representative reference we included the effects of these factors through variables
-using a radiative transfer model (RTM).  The applied methodology is discussed in
+can detect a big portion of the actual CE events.  However, by inspecting the daily
+plots of irradiance it became evident that changes in atmospheric conditions
+introduced numerous false positive or false negative results. The main reason for
+these discrepancies is the variability of the effects of aerosols and water vapor
+which were not taken into account in the two simple methods.  To produce a more
+representative reference we included the effects of these factors using a radiative
+transfer model (RTM).  The applied methodology is discussed in
 section\nobreakspace{}\ref{rtmcs}.
@@
 optical depth (AOD) at $500\,\text{nm}$ and the equivalent height of the water column
-(WC).  The monthly climatological values of AOD and water column, as well as
-combinations with additional offsets of $\pm1\sigma$ and $\pm2\sigma$, were used as
-inputs to the RTM in the construction of the LUT.
+(WC).  The monthly climatological values of AOD and WC, as well as combinations with
+additional offsets of $\pm1\sigma$ and $\pm2\sigma$, were used as inputs to the RTM
+in the construction of the LUT.
 
@@
 <!-- Aerosol change -->
-The above clear sky reference values are based on the climatological AOD and WC,
-hence they cannot describe accurately the long-term variation of
-$\text{GHI}_\text{ref}$ due to changes in the two atmospheric constituents, mainly
-AOD.  As reported by @Natsis2023, there is a long-term brightening effect in the GHI
-data of Thessaloniki for the period 1993 -- 2023, which for clear-sky data was
-attributed to long-term changes in aerosol effects.  Therefore, an adjustment of the
-$\text{GHI}_\text{ref}$ during the period of study was made using simulation with the
-RTM based on the long-term variations of the AOD. As AERONET data start only in 2003,
-we used for the period 1993 -- 2005 estimates of changes in AOD at $340\,\text{nm}$
-derived from a collocated Brewer spectrophotometer [@Kazadzis2007] to calculate the
-trend in $\text{GHI}_\text{ref}$ during this period.
+The clear-sky reference values discussed above are based on the climatological AOD
+and WC; hence they cannot describe accurately the long-term variation of
+$\text{GHI}_\text{ref}$ due to long-term changes in the two atmospheric constituents,
+mainly AOD.  As reported by @Natsis2023, there is a long-term brightening effect in
+the GHI data of Thessaloniki for the period 1993 -- 2023, which for clear-sky data
+was attributed to long-term changes in aerosol effects.  Therefore, an adjustment of
+the $\text{GHI}_\text{ref}$ during the period of study was made using simulation with
+the RTM based on the long-term variations of the AOD. As AERONET data start only in
+2003, we used for the period 1993 -- 2005 estimates of changes in AOD at
+$340\,\text{nm}$ derived from a collocated Brewer spectrophotometer [@Kazadzis2007]
+to calculate the trend in $\text{GHI}_\text{ref}$ during this period.
 

### 2024-07-04 article/article.tex
Commit 2024-07-04 21:13

@@
     \cortext[cor1]{Corresponding author}
-    \fntext[1]{This is the first author footnote.}
-    \fntext[2]{Another author footnote.}
 
   \begin{abstract}
-  Here will be the abstract.
+  In this study we investigate the characteristics of global horizontal
+  irradiance enhancement events induced by clouds over Thessaloniki for
+  the period 1993 -- 2023 using data recorded every one minute. We
+  identified the cloud enhancement (CE) events by creating an
+  appropriate clear-sky irradiance reference with the use of a radiative
+  transfer model and aerosol optical depth data from a collocated Cimel
+  sun photometer and a Brewer spectrophotometer. We found a trend in CE
+  events of \(45.6\pm 21.9\,\text{cases}/\text{year}\), and a trend in
+  the CE events irradiation of \(116.9\pm 67.8\,\text{kJ}/\text{year}\).
+  The peak of the CE events was observed during May and June. The
+  analysis of the total duration of CE events showed that durations
+  longer than 5 minutes are very rare, with exceptions lasting over an
+  hour and up to 140 minutes. Finally, we have detected enhancements
+  above the total solar irradiance at the top of the atmosphere of up to
+  \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the cases below
+  \(200\,\text{W}/\text{m}^{2}\). The most active period of these
+  extreme events is spring -- early summer with a secondary peak in
+  autumn.
   \end{abstract}
@@
 
-\section*{Abstract}\label{abstract}
-\addcontentsline{toc}{section}{Abstract}
-
-We studied the enhancement of the global horizontal irradiance induced
-by clouds over Thessaloniki for the period 1993 -- 2023 using data
-recorded every one minute. We identified the cloud enhancement events
-(CE) by creating an appropriate clear sky irradiance reference with the
-use of a radiative transfer model and aerosol optical depth data from a
-collocated Cimel sun photometer and a Brewer spectrophotometer. We found
-a trend in CE events of \(45.6\pm
-21.9\,\text{cases}/\text{year}\), and a trend in the CE events
-irradiation of \(116.9\pm
-67.8\,\text{kJ}/\text{year}\). The peak of the CE events was observed
-during May and June. An analysis of the total duration of CE events,
-showed that durations longer than 5 minutes are very rare, with
-exceptions lasting over an hour and up to 140 minutes. Finally, we have
-detected enhancements above the total solar irradiance at the top of the
-atmosphere of up to \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\)
-of the cases below \(200\,\text{W}/\text{m}^{2}\). The most active
-season of these extreme events is spring until early summer and autumn.
-
-\section{Introduction}\label{introduction}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
 The shortwave solar radiation, reaching Earth's surface, is the main
-energy source of the atmosphere and the biosphere, and drives and
+energy source for the atmosphere and the biosphere, and drives and
 governs the climate \citep{Gray2010}. It has direct practical
-application in industries like energy and agricultural production. The
-variability of its intensity can impose difficulties in predicting the
-yield and in designing the specifications of the appropriate equipment.
-Significant portion of research has been focused on predicting the
-renewable energy production in a fine timescale and in near real-time
-(for a review see \citet{Inman2013}; \citet{Graabak2016}).
+application in industries related to energy and agricultural production.
+The variability of its intensity can impose difficulties in predicting
+the yield and in designing the specifications of the appropriate
+equipment. Significant portion of research has been focused on
+predicting the renewable energy production in a fine timescale and in
+near real-time \citep[for a review see][]{Inman2013, Graabak2016}.
 
@@
 practical implications. The intensity and duration of enhancements can
-effect the efficiency and stability of photovoltaic power production
-\citep{Lappalainen2020, Jaervelae2020} while ECEs have the potential to
+affect the efficiency and stability of photovoltaic power production
+\citep{Lappalainen2020, Jaervelae2020}, while ECEs have the potential to
 compromise the integrity of photovoltaic plants infrastructure
@@
 events can interfere in the comparison of ground-based and satellite
-observations \citep{Damiani2018}. Global warming has likely affected
-cloud coverage in the last few decades. \citet{Liu2023} reported
-increases in cloud cover over the tropical and subtropical oceans and
-decreases over most continents, while \citet{Dong2023} reported
-decreases over North America and Europe. To our knowledge, there is no
-evidence on whether this trend has affected also the number and strength
-of CE events.
+observations of radiation \citep{Damiani2018}. Global warming has likely
+affected cloud coverage in the last few decades. \citet{Liu2023}
+reported increases in cloud cover over the tropical and subtropical
+oceans and decreases over most continents, while \citet{Dong2023}
+reported decreases over North America and Europe. To our knowledge,
+there is no evidence on whether this trend has affected also the number
+and strength of CE events.
 
 Methods of identification of CE events usually include the use of
-simulated clear sky irradiance as baseline, that is combined with an
-appropriate threshold or some other statistical characteristics, and in
-some cases, with visual inspection of sky camera images \citep[ and
-references therein]{Vamvakas2020, Mol2023}.
+simulated clear sky irradiance as baseline, combined with an appropriate
+threshold or some other statistical characteristics, and in some cases,
+with visual inspection of sky camera images \citep[ and references
+therein]{Vamvakas2020, Mol2023}.
 
@@
 nearby buildings, we have excluded all measurements with solar zenith
-angle (SZA) greater than \(78^\circ\).
+angle (SZA) greater than \(78^\circ\). Finally, images from a sky camera
+have been used in the manual inspection of the CE identification. The
+sky camera operates since 2012 and stores images in 5 min time steps.
 
-Finally, images from a sky camera have been used in the manual
-inspection of the CE identification. The sky camera operates since 2012
-and stores images in 5 min time steps.
-
+\hypertarget{cloud-enhancement-detection}{%
 \subsection{Cloud enhancement
-detection}\label{cloud-enhancement-detection}
+detection}\label{cloud-enhancement-detection}}
 
@@
 additional constant offset. The initial results showed that we can
-detect a big portion of the CE events. However, by inspecting the daily
-plots of irradiance it became evident that changes in atmospheric
-conditions introduced numerous false positive and false negative
-results. The main reason for these discrepancies is the variability of
-the effects of aerosols and water vapor which were not taken into
-account in the two simple methods. To produce a more representative
-reference we included the effects of these factors through variables
-using a radiative transfer model (RTM). The applied methodology is
-discussed in section\nobreakspace{}\ref{rtmcs}.
+detect a big portion of the actual CE events. However, by inspecting the
+daily plots of irradiance it became evident that changes in atmospheric
+conditions introduced numerous false positive or false negative results.
+The main reason for these discrepancies is the variability of the
+effects of aerosols and water vapor which were not taken into account in
+the two simple methods. To produce a more representative reference we
+included the effects of these factors using a radiative transfer model
+(RTM). The applied methodology is discussed in
+section\nobreakspace{}\ref{rtmcs}.
 
-\subsection{Modeled clear Sky Irradiance}\label{rtmcs}
+\hypertarget{rtmcs}{%
+\subsection{Modeled clear Sky Irradiance}\label{rtmcs}}
 
+\hypertarget{climatology-of-clear-sky-irradiance}{%
 \subsubsection{Climatology of clear sky
-irradiance}\label{climatology-of-clear-sky-irradiance}
+irradiance}\label{climatology-of-clear-sky-irradiance}}
 
@@
 \(500\,\text{nm}\) and the equivalent height of the water column (WC).
-The monthly climatological values of AOD and water column, as well as
-combinations with additional offsets of \(\pm1\sigma\) and
-\(\pm2\sigma\), were used as inputs to the RTM in the construction of
-the LUT.
+The monthly climatological values of AOD and WC, as well as combinations
+with additional offsets of \(\pm1\sigma\) and \(\pm2\sigma\), were used
+as inputs to the RTM in the construction of the LUT.
 
@@
 
+\hypertarget{long-term-change-of-clear-sky-irradiance}{%
 \subsubsection{Long-term change of clear sky
-irradiance}\label{long-term-change-of-clear-sky-irradiance}
+irradiance}\label{long-term-change-of-clear-sky-irradiance}}
 
-The above clear sky reference values are based on the climatological AOD
-and WC, hence they cannot describe accurately the long-term variation of
-\(\text{GHI}_\text{ref}\) due to changes in the two atmospheric
-constituents, mainly AOD. As reported by \citet{Natsis2023}, there is a
-long-term brightening effect in the GHI data of Thessaloniki for the
-period 1993 -- 2023, which for clear-sky data was attributed to
-long-term changes in aerosol effects. Therefore, an adjustment of the
-\(\text{GHI}_\text{ref}\) during the period of study was made using
-simulation with the RTM based on the long-term variations of the AOD. As
-AERONET data start only in 2003, we used for the period 1993 -- 2005
-estimates of changes in AOD at \(340\,\text{nm}\) derived from a
-collocated Brewer spectrophotometer \citep{Kazadzis2007} to calculate
-the trend in \(\text{GHI}_\text{ref}\) during this period.
+The clear-sky reference values discussed above are based on the
+climatological AOD and WC; hence they cannot describe accurately the
+long-term variation of \(\text{GHI}_\text{ref}\) due to long-term
+changes in the two atmospheric constituents, mainly AOD. As reported by
+\citet{Natsis2023}, there is a long-term brightening effect in the GHI
+data of Thessaloniki for the period 1993 -- 2023, which for clear-sky
+data was attributed to long-term changes in aerosol effects. Therefore,
+an adjustment of the \(\text{GHI}_\text{ref}\) during the period of
+study was made using simulation with the RTM based on the long-term
+variations of the AOD. As AERONET data start only in 2003, we used for
+the period 1993 -- 2005 estimates of changes in AOD at
+\(340\,\text{nm}\) derived from a collocated Brewer spectrophotometer
+\citep{Kazadzis2007} to calculate the trend in \(\text{GHI}_\text{ref}\)
+during this period.
 

### 2024-07-04 article/article.Rmd
Commit 2024-07-04 22:14

@@
 was attributed to long-term changes in aerosol effects.  Therefore, an adjustment of
-the $\text{GHI}_\text{ref}$ during the period of study was made using simulation with
-the RTM based on the long-term variations of the AOD. As AERONET data start only in
-2003, we used for the period 1993 -- 2005 estimates of changes in AOD at
+the $\text{GHI}_\text{ref}$ during the period of study was made using simulations
+with the RTM based on the long-term variations of the AOD. As AERONET data start only
+in 2003, we used for the period 1993 -- 2005 estimates of changes in AOD at
 $340\,\text{nm}$ derived from a collocated Brewer spectrophotometer [@Kazadzis2007]
-to calculate the trend in $\text{GHI}_\text{ref}$ during this period.
+to calculate the trend in $\text{GHI}_\text{ref}$ due to aerosols during this period.
 
@@
 
-According to this study, in the period 1997 -- 2005 the mean AOD at $340\,\text{nm}$
+According to @Kazadzis2007, in the period 1997 -- 2005 the mean AOD at $340\,\text{nm}$
 is $0.403$ with a trend of $-3.8\pm0.93\,\%$ per year, corresponding to a change of
 $0.0153$ per year.  Using an Ångström coefficient $\alpha = 1.6$, this translates to
-a change in the Ångström coefficient $\beta=0.00272$ per year (or $\beta=0.084$ in
+a change in the Ångström coefficient $\beta$ of $0.00272$ per year (or $\beta=0.084$ in
 1997 and $\beta=0.059$ in 2005).  Simulations with uvspec for the above Ångström
@@
 the period 2005 -- 2023 we used the mean monthly values of AOD and WC from AERONET in
-a similar simulation scheme to calculate the monthly mean of clear sky irradiance,
+a similar simulation scheme to calculate the monthly mean clear-sky irradiance,
 and finally the trend of $+0.14\,\%$ per year. We applied these two long-term changes
@@
 
-```{r CS-change, echo=FALSE, fig.cap="Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD."}
+```{r CS-change, echo=FALSE, fig.cap="Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1992 -- 2023."}
 knitr::include_graphics("../images/P-CS-change-1.pdf")
@@
 
-In this study our main focus was to quantify over irradiance events related to CEs. A
+In this study our main focus was to quantify the over irradiance related to CEs. A
 key issue for achieving this goal is to define a threshold for the CE
@@
 parameterization for the RTM simulations. The implementation of the long-term change
-of AOD, discussed in section\nobreakspace{}\ref{rtmcs}, allows capturing a large part
+in AOD, discussed in section\nobreakspace{}\ref{rtmcs}, allows capturing a large part
 of the natural variability of clear-sky GHI. However, the short-term variability of
@@
 \end{equation}
+This is the criterion of our CE identification.
+
 <!--
@@
 -->
-This is the criterion of our CE identification.
 

### 2024-07-04 article/article.tex
Commit 2024-07-04 22:14

@@
 an adjustment of the \(\text{GHI}_\text{ref}\) during the period of
-study was made using simulation with the RTM based on the long-term
+study was made using simulations with the RTM based on the long-term
 variations of the AOD. As AERONET data start only in 2003, we used for
@@
 \citep{Kazadzis2007} to calculate the trend in \(\text{GHI}_\text{ref}\)
-during this period.
+due to aerosols during this period.
 
-According to this study, in the period 1997 -- 2005 the mean AOD at
-\(340\,\text{nm}\) is \(0.403\) with a trend of \(-3.8\pm0.93\,\%\) per
-year, corresponding to a change of \(0.0153\) per year. Using an
-Ångström coefficient \(\alpha = 1.6\), this translates to a change in
-the Ångström coefficient \(\beta=0.00272\) per year (or \(\beta=0.084\)
-in 1997 and \(\beta=0.059\) in 2005). Simulations with uvspec for the
-above Ångström coefficients, with WC of \(15.7\,\text{mm}\) and
-\(15.4\,\text{mm}\) for 1997 and 2005 respectively, also taken from
-AERONET, and for a SZA of \(55^\circ\) reveal a trend of \(+0.21\,\%\)
-per year in \(\text{GHI}_\text{ref}\). The SZA of \(55^\circ\) was
-chosen as representative of all days in the year in order to get a rough
-estimate of the annually averaged change in clear sky irradiance. For
-the period 2005 -- 2023 we used the mean monthly values of AOD and WC
-from AERONET in a similar simulation scheme to calculate the monthly
-mean of clear sky irradiance, and finally the trend of \(+0.14\,\%\) per
-year. We applied these two long-term changes (see
-Figure\nobreakspace{}\ref{fig:CS-change}) to the climatological
+According to \citet{Kazadzis2007}, in the period 1997 -- 2005 the mean
+AOD at \(340\,\text{nm}\) is \(0.403\) with a trend of
+\(-3.8\pm0.93\,\%\) per year, corresponding to a change of \(0.0153\)
+per year. Using an Ångström coefficient \(\alpha = 1.6\), this
+translates to a change in the Ångström coefficient \(\beta\) of
+\(0.00272\) per year (or \(\beta=0.084\) in 1997 and \(\beta=0.059\) in
+2005). Simulations with uvspec for the above Ångström coefficients, with
+WC of \(15.7\,\text{mm}\) and \(15.4\,\text{mm}\) for 1997 and 2005
+respectively, also taken from AERONET, and for a SZA of \(55^\circ\)
+reveal a trend of \(+0.21\,\%\) per year in \(\text{GHI}_\text{ref}\).
+The SZA of \(55^\circ\) was chosen as representative of all days in the
+year in order to get a rough estimate of the annually averaged change in
+clear sky irradiance. For the period 2005 -- 2023 we used the mean
+monthly values of AOD and WC from AERONET in a similar simulation scheme
+to calculate the monthly mean clear-sky irradiance, and finally the
+trend of \(+0.14\,\%\) per year. We applied these two long-term changes
+(see Figure\nobreakspace{}\ref{fig:CS-change}) to the climatological
 \(\text{GHI}_\text{ref}\), in order to create a more realistic
@@
 
-\caption{Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD.}\label{fig:CS-change}
+\caption{Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1992 -- 2023.}\label{fig:CS-change}
 \end{figure}
@@
 
-In this study our main focus was to quantify over irradiance events
-related to CEs. A key issue for achieving this goal is to define a
-threshold for the CE identification, representative of the clear-sky
-irradiance at the time of each GHI measurement. This depends on the
-selection of the appropriate atmospheric parameterization for the RTM
-simulations. The implementation of the long-term change of AOD,
-discussed in section\nobreakspace{}\ref{rtmcs}, allows capturing a large
-part of the natural variability of clear-sky GHI. However, the
-short-term variability of AOD cannot be taken adequately into account
-when using monthly values in the model simulations. We tried different
-approaches in order to strengthen the robustness of the methodology and
-to compensate for the limited accuracy of the RTM input data and the
+In this study our main focus was to quantify the over irradiance related
+to CEs. A key issue for achieving this goal is to define a threshold for
+the CE identification, representative of the clear-sky irradiance at the
+time of each GHI measurement. This depends on the selection of the
+appropriate atmospheric parameterization for the RTM simulations. The
+implementation of the long-term change in AOD, discussed in
+section\nobreakspace{}\ref{rtmcs}, allows capturing a large part of the
+natural variability of clear-sky GHI. However, the short-term
+variability of AOD cannot be taken adequately into account when using
+monthly values in the model simulations. We tried different approaches
+in order to strengthen the robustness of the methodology and to
+compensate for the limited accuracy of the RTM input data and the
 unpredictable natural variability of the atmosphere.

### 2024-07-04 article/article.Rmd
Commit 2024-07-05 00:14

@@
 \end{equation}
-This is the criterion of our CE identification.
 
@@
 
-These values were determined through the implementation of an empirical method with
-manual inspection of the CE identification results on selected days of the whole
-dataset.  We used seven sets of days with characteristics relevant to the efficiency
-of the identification threshold.  These sets were random groups of about 20 -- 30
-days with the following characteristics:
+This is the criterion of our CE identification.  The constant terms were determined
+through the implementation of an empirical method with manual inspection of the CE
+identification results on selected days of the whole dataset.  We tested seven sets
+of days with different characteristics relevant to the efficiency of the
+identification threshold.  These sets were random groups of about 20 -- 30 days with
+the following characteristics:
 (a) the strongest over irradiance CE events,
@@
 (i) manually selected days.
-For the latter case and where needed, we also used images from a sky-camera to
+For the latter case and where needed, we also used images from the sky-camera to
 further aid the decision of the manual inspection.
@@
 the actual clear sky irradiance is not known and can only be approximated.  However,
-this method is capable in detecting all major CE events.  Where some CE events with
-very low OIR may be not detected, these are few with small over-irradiance, and it is
-unlikely that will affect significantly our results.
+this method was proven capable in detecting all major CE events.  Where some CE
+events with very low OIR may be not detected, these are few with small
+over-irradiance, and it is unlikely that will affect significantly our results.
 
@@
 
-```{r example-day, echo=FALSE, fig.cap="Example of CE identification for 2019-07-11.
+```{r example-day, echo=FALSE, fig.cap="Example of CE identification in Thessaloniki for 2019-07-11.
 The green line with blue symbols depicts the measured GHI in one minute steps.
 The red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles.
-The black curve represents the TSI at the top of the atmosphere, adjusted for the actual Sun-Earth distance and multiplied by the cosine of the cosine of SZA.", fig.pos='H'}
+The black curve represents the TSI at the top of the atmosphere, adjusted for the actual Sun-Earth distance and multiplied by the cosine of SZA.", fig.pos='H'}
 knitr::include_graphics("../images/example-days-18.png")
@@
 
-```{r example-year, echo=FALSE, fig.cap="Example scatter plot of the measured GHI and the reference clear sky irradiance for the year 2005.
+```{r example-year, echo=FALSE, fig.cap="Example scatter plot of the measured GHI and the reference clear sky irradiance in Thessaloniki for the year 2005.
 The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.", fig.pos='H'}
@@
 
-The main focus of this study is to investigate the time evolution of the CE events by
+One aspect of this study is to investigate the time evolution of the CE events by
 analyzing the GHI measurements at Thessaloniki. Cloud enhancements can be influenced
 by different factors, such as the geometry, size and optical thickness of clouds,
-their height in the atmosphere and on local weather regimes [@Mol2023; @Veerman2022;
+their height in the atmosphere and local weather regimes [@Mol2023; @Veerman2022;
 @Gristey2022; @Tzoumanikas2016].  Some of these factors are related to changes in
-climate; hence it would be reasonable to expect capturing their contributions to the
-frequency of occurrence of CE events over Thessaloniki, as well as to the average OIR
-and excess irradiation.  The long-term trends were calculated using a first-order
-autoregressive model with the 'maximum likelihood' fitting method [@Gardner1980;
-@Jones1980], by implementing the function 'arima' from the library 'stats' of the R
-programming language [@RCT2023]. All trends are reported together with their
-$2\sigma$ error.
+climate; hence it would be reasonable to expect contributing to the frequency of
+occurrence of CE events over Thessaloniki, as well as to the average OIR and excess
+irradiation.  The long-term trends were calculated using a first-order autoregressive
+model with the 'maximum likelihood' fitting method [@Gardner1980; @Jones1980], by
+implementing the function 'arima' from the library 'stats' of the R programming
+language [@RCT2023]. All trends are reported together with their $2\sigma$ error.
 
@@
 
-We have to note that the excess irradiation related to the CE events can not be
+We have to note that the excess irradiation related to the CE events cannot be
 directly linked to the total energy balance of the atmosphere. The net solar
@@
 
-Another interesting aspect of the CE events is their distribution within the year.
+Next we investigated the distribution of the CE events within the year.
 Figure\nobreakspace{}\ref{fig:relative-month-occurrences} shows the monthly box and
-whisker plot of the CE number of occurrence normalized with the highest median value,
-that occurs in June, depicting a clear seasonal cycle.  Although CE events are
-present throughout the year, the most active months are May and June. During the
+whisker plot of the CE number of occurrences normalized with the highest median
+value, which occurs in June, depicting a clear seasonal cycle.  Although CE events
+are present throughout the year, the most active months are May and June. During the
 winter (December -- February), the number of CE cases is about $25\,\%$ of the
@@
 
-```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal variability of the number of CE events normalized to the maximum occurring in June, in the form of a box and whisker plot.
-The monthly values have been also normalized to the relative abundance of valid GHI observations.
+```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal variability of the number of CE events in Thessaloniki for the period 1992 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot.
+The monthly values have also been normalized to the relative abundance of valid GHI observations.
 The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles, the thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
-The vertical lines (whiskers) extend between the maximum and minimum monthly values and the solid circles are outliers."}
+The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
 knitr::include_graphics("../images/clim-CE-month-norm-MAX-median-N-MW-1.png")
@@
 
-```{r ovir-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE events as a function of OIR."}
+```{r ovir-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE events in Thessaloniki for the period 1992 -- 2023 as a function of OIR."}
 knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
@@
 distribution of the CE events according to their duration.  We conclude that although
-some groups of events last for more than an hour about $80\,\%$ have duration of less
-than 5 minutes.
+some groups of events last for more than an hour, about $80\,\%$ have duration of
+less than 5 minutes.
 
-```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration."}
+```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1992 -- 2023."}
 knitr::include_graphics("../images/groups-1.png")
@@
 irradiation have small duration and vice versa. The vast majority of grouped events
-are associated with small excess irradiation (e.g. $<5\,\text{kJ}/\text{m}^2$) and
-small duration (e.g. $<5\,\text{min}$) while groups with strong excess irradiation
-and long duration are very rare.  Similar results of this relation have been
-reported by @Zhang2018, on a study using a far higher sampling rate than ours.
+are associated with small excess irradiation (e.g., $<5\,\text{kJ}/\text{m}^2$) and
+small duration (e.g., $<5\,\text{min}$) while groups with strong excess irradiation
+and long duration are very rare.  Similar results of this relation have been reported
+by @Zhang2018 in a study using a far higher sampling rate ($100\,\text{Hz}$) than
+ours.
 
-```{r group-2d, echo=FALSE, fig.cap="Relation of excess irradiation of CE groups with their duration. The logarithmic color scale denotes the frequency of the respective groups of events."}
+```{r group-2d, echo=FALSE, fig.cap="Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1992 -- 2023.
+The logarithmic color scale denotes the frequency of the respective groups of events."}
 knitr::include_graphics("../images/P-groups-bin2d-1.png")
@@
 
-An aspect of the CE events that is commonly reported and has some significance
-on the solar energy production infrastructure are the extreme CE events (ECE). Where
-solar irradiance exceeds the expected irradiance on top of the atmosphere
-(Equation\nobreakspace{}\ref{eq:ECE}).
-Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurrences} we have
-computed the distribution of the number of occurrences of ECE events by month in
+An aspect of the CE events that is commonly reported and has some significance on the
+solar energy production infrastructure are the extreme CE events (ECE), where solar
+irradiance exceeds the expected irradiance on top of the atmosphere
+(Equation\nobreakspace{}\ref{eq:ECE}).  Analogous to
+Figure\nobreakspace{}\ref{fig:relative-month-occurrences} we have computed the
+distribution of the number of occurrences of ECE events by month in
 Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. The most active period
-for ECE events is in the spring and the start of the summer (March -- June), followed
-by a period in the late fall (September and October).  This is probably related to 
-the weather characteristics of these periods, where there are continuous alternations
-between clear sky periods and clouds.
+for ECE events is in spring and early summer (March -- June), followed by a
+period in late autumn (September and October).  This is probably related to the
+weather characteristics in these periods, with frequent alternations between clear
+sky periods and clouds.
 
-```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal variability of the number of ECE events normalized to the maximum occurring in March, in the form of a box and whisker plot.
+```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal variability of the number of ECE events in Thessaloniki for the period 1993 -- 2023 normalized to the maximum occurring in March, in the form of a box and whisker plot.
 The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles.
@@
 
-The distribution of the ECE events (Figure\nobreakspace{}\ref{fig:P-extreme-distribution}),
-shows that there are rare cases where the OIR can exceed the TSI even more than
-$400\,\text{W}/\text{m}^2$, with the $75\,\%$ of the cases to be below
-$200\,\text{W}/\text{m}^2$. 
-Those finds are in accordance with results form @Vamvakas2020, 
-with the difference that the OIR values are lower for Thessaloniki.
+The distribution of the ECE events
+(Figure\nobreakspace{}\ref{fig:P-extreme-distribution}) shows that in rare cases the
+OIR can exceed the TSI even by more than $400\,\text{W}/\text{m}^2$, while in
+$75\,\%$ of the cases the OIR is below $200\,\text{W}/\text{m}^2$. The OIR for the
+most frequent ECEs ranges between $140$ and $180\,\text{W}/\text{m}^2$.  These
+findings are in accordance with the results of @Vamvakas2020, the only difference
+being that the OIR values reported for are higher than those for Thessaloniki.
 
-```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE above clear sky threshold, for cases that are exceeding the TSI."}
+```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE events in Thessaloniki for the period 1992 -- 2023."}
 knitr::include_graphics("../images/P-extreme-distribution-1.png")
@@
 
-By creating a clear sky approximation of the GHI, which represents the long- and
-short-term variation of the expected clear sky GHI, we were able to identify cases of 
-CE events.
-After analyzing the CE cases, we found an increase of 
+By creating a clear sky approximation representing the long- and short-term
+variability of the expected clear sky GHI, we were able to identify cases of CE
+events in Thessaloniki for the period 1993 -- 2023.  After analyzing the CE cases, we
+found an increase of
 $`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$,
-with the
-mean annual total energy of the CE events increasing with a rate of
+with the mean annual irradiation of the CE events increasing with a rate of
 $`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$.
-The most active season of CE events over Thessaloniki is concentrated on early
-summer, on May and June.
-We found that continuous CE events can last up to $140$ minutes, and $80\,\%$ of
-them bellow $5$ minutes.
+The most active months of CE events are May and June.  We found that continuous CE
+events can last up to $140$ minutes, while the duration of $80\,\%$ of them is bellow
+$5$ minutes.
 
-The magnitude of the ECE events does not exceed the values reported for sites with
-more favourable conditions for the phenomenon. We have observed cases exceeding the
-TSI by $400\,\text{W}/\text{m}^{2}$ with $75\,\%$ of the cases under
-$200\,\text{W}/\text{m}^{2}$. The climatological characteristic of the ECE events,
-showed that the most active months are spread in half of the year (March -- June,
-September and October). We found that CE conditions, can have a duration of more than
-an hour in rare cases, with the bulk of the cases having a duration under 5 minutes.
-Some of the characteristics of CE and ECE events we analysed have strong similarities
-with results by @Vamvakas2020 for the city of Patras, south of Thessaloniki, with
-analog differences on the intensity of the solar radiation.
+We have observed ECE cases exceeding the TSI by $400\,\text{W}/\text{m}^{2}$ with
+$75\,\%$ of the cases under $200\,\text{W}/\text{m}^{2}$. The climatological
+characteristics of the ECE events showed that the most active months are spread in
+half of the year and particularly in the periods March -- June, September and
+October.  The magnitude of the ECE events identified in Thessaloniki events does not
+exceed the values reported for sites with more favourable conditions for the
+phenomenon [e.g. @Cordero2023]. Some of the characteristics of CE and ECE events we
+analyzed have strong similarities with the results of @Vamvakas2020 for the city of
+Patras, south of Thessaloniki, albeit with differences in the magnitude of OIR.
 
@@
 through this 30-year period, is a dynamic phenomenon that needs further
-investigation.  Although, to approach it, we need more long-term observations of AOD
-and clouds characteristics.
+investigation. For such studies it would be essential to have more detailed
+information on cloud characteristics, especially in order to investigate possible
+associations of the observed trends with changes in climate.
 

### 2024-07-04 article/article.tex
Commit 2024-07-05 00:14

@@
 \text{CE} : E > 15 + 1.04 \cdot \text{GHI}_\text{ref} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
-\end{equation} This is the criterion of our CE identification.
+\end{equation}
 
-These values were determined through the implementation of an empirical
-method with manual inspection of the CE identification results on
-selected days of the whole dataset. We used seven sets of days with
+This is the criterion of our CE identification. The constant terms were
+determined through the implementation of an empirical method with manual
+inspection of the CE identification results on selected days of the
+whole dataset. We tested seven sets of days with different
 characteristics relevant to the efficiency of the identification
@@
 of EC events, (h) randomly selected days, and (i) manually selected
-days. For the latter case and where needed, we also used images from a
+days. For the latter case and where needed, we also used images from the
 sky-camera to further aid the decision of the manual inspection.
@@
 subjectivity, since the actual clear sky irradiance is not known and can
-only be approximated. However, this method is capable in detecting all
-major CE events. Where some CE events with very low OIR may be not
-detected, these are few with small over-irradiance, and it is unlikely
-that will affect significantly our results.
+only be approximated. However, this method was proven capable in
+detecting all major CE events. Where some CE events with very low OIR
+may be not detected, these are few with small over-irradiance, and it is
+unlikely that will affect significantly our results.
 
@@
 
-\caption{Example of CE identification for 2019-07-11.
+\caption{Example of CE identification in Thessaloniki for 2019-07-11.
 The green line with blue symbols depicts the measured GHI in one minute steps.
 The red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles.
-The black curve represents the TSI at the top of the atmosphere, adjusted for the actual Sun-Earth distance and multiplied by the cosine of the cosine of SZA.}\label{fig:example-day}
+The black curve represents the TSI at the top of the atmosphere, adjusted for the actual Sun-Earth distance and multiplied by the cosine of SZA.}\label{fig:example-day}
 \end{figure}
@@
 
-\caption{Example scatter plot of the measured GHI and the reference clear sky irradiance for the year 2005.
+\caption{Example scatter plot of the measured GHI and the reference clear sky irradiance in Thessaloniki for the year 2005.
 The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.}\label{fig:example-year}
@@
 
-The main focus of this study is to investigate the time evolution of the
-CE events by analyzing the GHI measurements at Thessaloniki. Cloud
+One aspect of this study is to investigate the time evolution of the CE
+events by analyzing the GHI measurements at Thessaloniki. Cloud
 enhancements can be influenced by different factors, such as the
 geometry, size and optical thickness of clouds, their height in the
-atmosphere and on local weather regimes
+atmosphere and local weather regimes
 \citep{Mol2023, Veerman2022, Gristey2022, Tzoumanikas2016}. Some of
 these factors are related to changes in climate; hence it would be
-reasonable to expect capturing their contributions to the frequency of
-occurrence of CE events over Thessaloniki, as well as to the average OIR
-and excess irradiation. The long-term trends were calculated using a
-first-order autoregressive model with the `maximum likelihood' fitting
-method \citep{Gardner1980, Jones1980}, by implementing the function
-`arima' from the library `stats' of the R programming language
-\citep{RCT2023}. All trends are reported together with their \(2\sigma\)
-error.
+reasonable to expect contributing to the frequency of occurrence of CE
+events over Thessaloniki, as well as to the average OIR and excess
+irradiation. The long-term trends were calculated using a first-order
+autoregressive model with the `maximum likelihood' fitting method
+\citep{Gardner1980, Jones1980}, by implementing the function `arima'
+from the library `stats' of the R programming language \citep{RCT2023}.
+All trends are reported together with their \(2\sigma\) error.
 
@@
 
-We have to note that the excess irradiation related to the CE events can
-not be directly linked to the total energy balance of the atmosphere.
+We have to note that the excess irradiation related to the CE events
+cannot be directly linked to the total energy balance of the atmosphere.
 The net solar radiation of the region is not increased, but is rather
@@
 
-Another interesting aspect of the CE events is their distribution within
-the year. Figure\nobreakspace{}\ref{fig:relative-month-occurrences}
-shows the monthly box and whisker plot of the CE number of occurrence
-normalized with the highest median value, that occurs in June, depicting
-a clear seasonal cycle. Although CE events are present throughout the
-year, the most active months are May and June. During the winter
-(December -- February), the number of CE cases is about \(25\,\%\) of
-the maximum, while in the intermediate months, the number of occurrences
-gradually ramps between the maximum and minimum. This seasonality is a
-combined effect of different factors, among them the types of clouds,
-their frequency of occurrence, the seasonally varying relative position
-of the sun, as well as the local landscape characteristics that may
-influence the formation of the clouds. Unfortunately, lack of detailed
-data on cloud formation, type and location is not allowing further
-analysis. The interannual variability of the monthly CE events is quite
-high as manifested by the large monthly extremes, especially in the
-summer.
+Next we investigated the distribution of the CE events within the year.
+Figure\nobreakspace{}\ref{fig:relative-month-occurrences} shows the
+monthly box and whisker plot of the CE number of occurrences normalized
+with the highest median value, which occurs in June, depicting a clear
+seasonal cycle. Although CE events are present throughout the year, the
+most active months are May and June. During the winter (December --
+February), the number of CE cases is about \(25\,\%\) of the maximum,
+while in the intermediate months, the number of occurrences gradually
+ramps between the maximum and minimum. This seasonality is a combined
+effect of different factors, among them the types of clouds, their
+frequency of occurrence, the seasonally varying relative position of the
+sun, as well as the local landscape characteristics that may influence
+the formation of the clouds. Unfortunately, lack of detailed data on
+cloud formation, type and location is not allowing further analysis. The
+interannual variability of the monthly CE events is quite high as
+manifested by the large monthly extremes, especially in the summer.
 
@@
 
-\caption{Seasonal variability of the number of CE events normalized to the maximum occurring in June, in the form of a box and whisker plot.
-The monthly values have been also normalized to the relative abundance of valid GHI observations.
+\caption{Seasonal variability of the number of CE events in Thessaloniki for the period 1992 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot.
+The monthly values have also been normalized to the relative abundance of valid GHI observations.
 The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles, the thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
-The vertical lines (whiskers) extend between the maximum and minimum monthly values and the solid circles are outliers.}\label{fig:relative-month-occurrences}
+The vertical lines (whiskers) extend between the maximum and minimum monthly values.}\label{fig:relative-month-occurrences}
 \end{figure}
@@
 
-\caption{Relative frequency distribution of CE events as a function of OIR.}\label{fig:ovir-distribution}
+\caption{Relative frequency distribution of CE events in Thessaloniki for the period 1992 -- 2023 as a function of OIR.}\label{fig:ovir-distribution}
 \end{figure}
@@
 frequency distribution of the CE events according to their duration. We
-conclude that although some groups of events last for more than an hour
+conclude that although some groups of events last for more than an hour,
 about \(80\,\%\) have duration of less than 5 minutes.
@@
 
-\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration.}\label{fig:ceg-duration-distribution}
+\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1992 -- 2023.}\label{fig:ceg-duration-distribution}
 \end{figure}
@@
 vast majority of grouped events are associated with small excess
-irradiation (e.g.~\(<5\,\text{kJ}/\text{m}^2\)) and small duration
-(e.g.~\(<5\,\text{min}\)) while groups with strong excess irradiation
+irradiation (e.g., \(<5\,\text{kJ}/\text{m}^2\)) and small duration
+(e.g., \(<5\,\text{min}\)) while groups with strong excess irradiation
 and long duration are very rare. Similar results of this relation have
-been reported by \citet{Zhang2018}, on a study using a far higher
-sampling rate than ours.
+been reported by \citet{Zhang2018} in a study using a far higher
+sampling rate (\(100\,\text{Hz}\)) than ours.
 
@@
 
-\caption{Relation of excess irradiation of CE groups with their duration. The logarithmic color scale denotes the frequency of the respective groups of events.}\label{fig:group-2d}
+\caption{Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1992 -- 2023.
+The logarithmic color scale denotes the frequency of the respective groups of events.}\label{fig:group-2d}
 \end{figure}
@@
 significance on the solar energy production infrastructure are the
-extreme CE events (ECE). Where solar irradiance exceeds the expected
+extreme CE events (ECE), where solar irradiance exceeds the expected
 irradiance on top of the atmosphere
@@
 month in Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}.
-The most active period for ECE events is in the spring and the start of
-the summer (March -- June), followed by a period in the late fall
-(September and October). This is probably related to the weather
-characteristics of these periods, where there are continuous
-alternations between clear sky periods and clouds.
+The most active period for ECE events is in spring and early summer
+(March -- June), followed by a period in late autumn (September and
+October). This is probably related to the weather characteristics in
+these periods, with frequent alternations between clear sky periods and
+clouds.
 
@@
 
-\caption{Seasonal variability of the number of ECE events normalized to the maximum occurring in March, in the form of a box and whisker plot.
+\caption{Seasonal variability of the number of ECE events in Thessaloniki for the period 1993 -- 2023 normalized to the maximum occurring in March, in the form of a box and whisker plot.
 The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles.
@@
 The distribution of the ECE events
-(Figure\nobreakspace{}\ref{fig:P-extreme-distribution}), shows that
-there are rare cases where the OIR can exceed the TSI even more than
-\(400\,\text{W}/\text{m}^2\), with the \(75\,\%\) of the cases to be
-below \(200\,\text{W}/\text{m}^2\). Those finds are in accordance with
-results form \citet{Vamvakas2020}, with the difference that the OIR
-values are lower for Thessaloniki.
+(Figure\nobreakspace{}\ref{fig:P-extreme-distribution}) shows that in
+rare cases the OIR can exceed the TSI even by more than
+\(400\,\text{W}/\text{m}^2\), while in \(75\,\%\) of the cases the OIR
+is below \(200\,\text{W}/\text{m}^2\). The OIR for the most frequent
+ECEs ranges between \(140\) and \(180\,\text{W}/\text{m}^2\). These
+findings are in accordance with the results of \citet{Vamvakas2020}, the
+only difference being that the OIR values reported for are higher than
+those for Thessaloniki.
 
@@
 
-\caption{Distribution of ECE above clear sky threshold, for cases that are exceeding the TSI.}\label{fig:P-extreme-distribution}
+\caption{Distribution of ECE events in Thessaloniki for the period 1992 -- 2023.}\label{fig:P-extreme-distribution}
 \end{figure}
@@
 
-By creating a clear sky approximation of the GHI, which represents the
-long- and short-term variation of the expected clear sky GHI, we were
-able to identify cases of CE events. After analyzing the CE cases, we
-found an increase of \(45.6\pm 21.9\,\text{cases}/\text{year}\), with
-the mean annual total energy of the CE events increasing with a rate of
-\(116.9\pm 67.8\,\text{kJ}/\text{year}\). The most active season of CE
-events over Thessaloniki is concentrated on early summer, on May and
-June. We found that continuous CE events can last up to \(140\) minutes,
-and \(80\,\%\) of them bellow \(5\) minutes.
+By creating a clear sky approximation representing the long- and
+short-term variability of the expected clear sky GHI, we were able to
+identify cases of CE events in Thessaloniki for the period 1993 -- 2023.
+After analyzing the CE cases, we found an increase of
+\(45.6\pm 21.9\,\text{cases}/\text{year}\), with the mean annual
+irradiation of the CE events increasing with a rate of
+\(116.9\pm 67.8\,\text{kJ}/\text{year}\). The most active months of CE
+events are May and June. We found that continuous CE events can last up
+to \(140\) minutes, while the duration of \(80\,\%\) of them is bellow
+\(5\) minutes.
 
-The magnitude of the ECE events does not exceed the values reported for
-sites with more favourable conditions for the phenomenon. We have
-observed cases exceeding the TSI by \(400\,\text{W}/\text{m}^{2}\) with
-\(75\,\%\) of the cases under \(200\,\text{W}/\text{m}^{2}\). The
-climatological characteristic of the ECE events, showed that the most
-active months are spread in half of the year (March -- June, September
-and October). We found that CE conditions, can have a duration of more
-than an hour in rare cases, with the bulk of the cases having a duration
-under 5 minutes. Some of the characteristics of CE and ECE events we
-analysed have strong similarities with results by \citet{Vamvakas2020}
-for the city of Patras, south of Thessaloniki, with analog differences
-on the intensity of the solar radiation.
+We have observed ECE cases exceeding the TSI by
+\(400\,\text{W}/\text{m}^{2}\) with \(75\,\%\) of the cases under
+\(200\,\text{W}/\text{m}^{2}\). The climatological characteristics of
+the ECE events showed that the most active months are spread in half of
+the year and particularly in the periods March -- June, September and
+October. The magnitude of the ECE events identified in Thessaloniki
+events does not exceed the values reported for sites with more
+favourable conditions for the phenomenon \citep[e.g.][]{Cordero2023}.
+Some of the characteristics of CE and ECE events we analyzed have strong
+similarities with the results of \citet{Vamvakas2020} for the city of
+Patras, south of Thessaloniki, albeit with differences in the magnitude
+of OIR.
 
@@
 with the clouds, through this 30-year period, is a dynamic phenomenon
-that needs further investigation. Although, to approach it, we need more
-long-term observations of AOD and clouds characteristics.
+that needs further investigation. For such studies it would be essential
+to have more detailed information on cloud characteristics, especially
+in order to investigate possible associations of the observed trends
+with changes in climate.
 

### 2024-07-05 article/article.Rmd
Commit 2024-07-05 06:14

@@
 variability of the expected clear sky GHI, we were able to identify cases of CE
-events in Thessaloniki for the period 1993 -- 2023.  After analyzing the CE cases, we
+events in Thessaloniki for the period 1992 -- 2023.  After analyzing the CE cases, we
 found an increase of
@@
 characteristics of the ECE events showed that the most active months are spread in
-half of the year and particularly in the periods March -- June, September and
+half of the year and particularly in the periods March -- June and September --
 October.  The magnitude of the ECE events identified in Thessaloniki events does not
 exceed the values reported for sites with more favourable conditions for the
-phenomenon [e.g. @Cordero2023]. Some of the characteristics of CE and ECE events we
+phenomenon [e.g., @Cordero2023]. Some of the characteristics of CE and ECE events we
 analyzed have strong similarities with the results of @Vamvakas2020 for the city of

### 2024-07-05 article/article.tex
Commit 2024-07-05 06:14

@@
 short-term variability of the expected clear sky GHI, we were able to
-identify cases of CE events in Thessaloniki for the period 1993 -- 2023.
+identify cases of CE events in Thessaloniki for the period 1992 -- 2023.
 After analyzing the CE cases, we found an increase of
@@
 the ECE events showed that the most active months are spread in half of
-the year and particularly in the periods March -- June, September and
+the year and particularly in the periods March -- June and September --
 October. The magnitude of the ECE events identified in Thessaloniki
 events does not exceed the values reported for sites with more
-favourable conditions for the phenomenon \citep[e.g.][]{Cordero2023}.
+favourable conditions for the phenomenon \citep[e.g.,][]{Cordero2023}.
 Some of the characteristics of CE and ECE events we analyzed have strong

### 2024-07-05 article/article.Rmd
Commit 2024-07-05 09:12

@@
 $\text{GHI}_\text{ref}$: The Haurwitz's model [@Haurwitz1945], which is a simple
-clear sky model and was already adjusted and applied to our data [@Natsis2023], and
-the total solar irradiance (TSI) at the top of the atmosphere, adjusted for the
-Sun-Earth distance.  We have tested both methods by using an appropriate relative
+clear sky model and was already adjusted and applied to our data [@Natsis2023].
+<!--
+, and the total solar irradiance (TSI) at the top of the atmosphere, adjusted for the
+Sun-Earth distance.
+-->
+We have tested both methods by using an appropriate relative
 threshold and/or an additional constant offset.  The initial results showed that we
@@
 $`r round(BR[year==2005,pw_avg_mm],1)`\,\text{mm}$
-for 1997 and 2005 respectively, also taken from AERONET, and for a SZA of $55^\circ$
-reveal a trend of
+for 1997 and 2005 respectively, where for 1997 we used the first available WC data
+(i.e. 2003) as a proxy, also taken from AERONET, and for a SZA of $55^\circ$ reveal a
+trend of
 $+0.21\,\%$ per year in $\text{GHI}_\text{ref}$.
@@
 
-```{r CS-change, echo=FALSE, fig.cap="Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1992 -- 2023."}
+```{r CS-change, echo=FALSE, fig.cap="Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1993 -- 2023."}
 knitr::include_graphics("../images/P-CS-change-1.pdf")
@@
         }
-    \caption{Time series for the period 1992 -- 2023 of (a) the yearly CE number of occurrences, (b) the yearly mean OIR and (c) the yearly excess irradiation.
+    \caption{Time series for the period 1993 -- 2023 of (a) the yearly CE number of occurrences, (b) the yearly mean OIR and (c) the yearly excess irradiation.
 The black lines represent the linear trends on the yearly data.}\label{fig:P-energy}
@@
 
-```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal variability of the number of CE events in Thessaloniki for the period 1992 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot.
+```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal variability of the number of CE events in Thessaloniki for the period 1993 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot.
 The monthly values have also been normalized to the relative abundance of valid GHI observations.
@@
 
-```{r ovir-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE events in Thessaloniki for the period 1992 -- 2023 as a function of OIR."}
+```{r ovir-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE events in Thessaloniki for the period 1993 -- 2023 as a function of OIR."}
 knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
@@
 
-```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1992 -- 2023."}
+```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023."}
 knitr::include_graphics("../images/groups-1.png")
@@
 
-```{r group-2d, echo=FALSE, fig.cap="Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1992 -- 2023.
+```{r group-2d, echo=FALSE, fig.cap="Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1993 -- 2023.
 The logarithmic color scale denotes the frequency of the respective groups of events."}
@@
 
-```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE events in Thessaloniki for the period 1992 -- 2023."}
+```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE events in Thessaloniki for the period 1993 -- 2023."}
 knitr::include_graphics("../images/P-extreme-distribution-1.png")
@@
 variability of the expected clear sky GHI, we were able to identify cases of CE
-events in Thessaloniki for the period 1992 -- 2023.  After analyzing the CE cases, we
+events in Thessaloniki for the period 1993 -- 2023.  After analyzing the CE cases, we
 found an increase of

### 2024-07-05 article/article.tex
Commit 2024-07-05 09:12

@@
 which is a simple clear sky model and was already adjusted and applied
-to our data \citep{Natsis2023}, and the total solar irradiance (TSI) at
-the top of the atmosphere, adjusted for the Sun-Earth distance. We have
-tested both methods by using an appropriate relative threshold and/or an
-additional constant offset. The initial results showed that we can
-detect a big portion of the actual CE events. However, by inspecting the
-daily plots of irradiance it became evident that changes in atmospheric
-conditions introduced numerous false positive or false negative results.
-The main reason for these discrepancies is the variability of the
-effects of aerosols and water vapor which were not taken into account in
-the two simple methods. To produce a more representative reference we
-included the effects of these factors using a radiative transfer model
-(RTM). The applied methodology is discussed in
-section\nobreakspace{}\ref{rtmcs}.
+to our data \citep{Natsis2023}. We have tested both methods by using an
+appropriate relative threshold and/or an additional constant offset. The
+initial results showed that we can detect a big portion of the actual CE
+events. However, by inspecting the daily plots of irradiance it became
+evident that changes in atmospheric conditions introduced numerous false
+positive or false negative results. The main reason for these
+discrepancies is the variability of the effects of aerosols and water
+vapor which were not taken into account in the two simple methods. To
+produce a more representative reference we included the effects of these
+factors using a radiative transfer model (RTM). The applied methodology
+is discussed in section\nobreakspace{}\ref{rtmcs}.
 
@@
 WC of \(15.7\,\text{mm}\) and \(15.4\,\text{mm}\) for 1997 and 2005
-respectively, also taken from AERONET, and for a SZA of \(55^\circ\)
-reveal a trend of \(+0.21\,\%\) per year in \(\text{GHI}_\text{ref}\).
-The SZA of \(55^\circ\) was chosen as representative of all days in the
-year in order to get a rough estimate of the annually averaged change in
-clear sky irradiance. For the period 2005 -- 2023 we used the mean
-monthly values of AOD and WC from AERONET in a similar simulation scheme
-to calculate the monthly mean clear-sky irradiance, and finally the
-trend of \(+0.14\,\%\) per year. We applied these two long-term changes
-(see Figure\nobreakspace{}\ref{fig:CS-change}) to the climatological
+respectively, where for 1997 we used the first available WC data
+(i.e.~2003) as a proxy, also taken from AERONET, and for a SZA of
+\(55^\circ\) reveal a trend of \(+0.21\,\%\) per year in
+\(\text{GHI}_\text{ref}\). The SZA of \(55^\circ\) was chosen as
+representative of all days in the year in order to get a rough estimate
+of the annually averaged change in clear sky irradiance. For the period
+2005 -- 2023 we used the mean monthly values of AOD and WC from AERONET
+in a similar simulation scheme to calculate the monthly mean clear-sky
+irradiance, and finally the trend of \(+0.14\,\%\) per year. We applied
+these two long-term changes (see
+Figure\nobreakspace{}\ref{fig:CS-change}) to the climatological
 \(\text{GHI}_\text{ref}\), in order to create a more realistic
@@
 
-\caption{Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1992 -- 2023.}\label{fig:CS-change}
+\caption{Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1993 -- 2023.}\label{fig:CS-change}
 \end{figure}
@@
 
-\caption{Seasonal variability of the number of CE events in Thessaloniki for the period 1992 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot.
+\caption{Seasonal variability of the number of CE events in Thessaloniki for the period 1993 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot.
 The monthly values have also been normalized to the relative abundance of valid GHI observations.
@@
 
-\caption{Relative frequency distribution of CE events in Thessaloniki for the period 1992 -- 2023 as a function of OIR.}\label{fig:ovir-distribution}
+\caption{Relative frequency distribution of CE events in Thessaloniki for the period 1993 -- 2023 as a function of OIR.}\label{fig:ovir-distribution}
 \end{figure}
@@
 
-\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1992 -- 2023.}\label{fig:ceg-duration-distribution}
+\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023.}\label{fig:ceg-duration-distribution}
 \end{figure}
@@
 
-\caption{Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1992 -- 2023.
+\caption{Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1993 -- 2023.
 The logarithmic color scale denotes the frequency of the respective groups of events.}\label{fig:group-2d}
@@
 
-\caption{Distribution of ECE events in Thessaloniki for the period 1992 -- 2023.}\label{fig:P-extreme-distribution}
+\caption{Distribution of ECE events in Thessaloniki for the period 1993 -- 2023.}\label{fig:P-extreme-distribution}
 \end{figure}
@@
 short-term variability of the expected clear sky GHI, we were able to
-identify cases of CE events in Thessaloniki for the period 1992 -- 2023.
+identify cases of CE events in Thessaloniki for the period 1993 -- 2023.
 After analyzing the CE cases, we found an increase of

### 2024-07-05 GHI_enh_04_investigate.tex
Commit 2024-07-05 11:10

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-06-27}
+\date{2024-07-05}
 
@@
 \end{figure}
+
+\begin{verbatim}
+Warning in annotate("segment", x = 25, xend = 50, y = 3, yend = 15, colour =
+"pink", : Ignoring unknown parameters: `line`
+\end{verbatim}
+
 \begin{figure}[H]
@@
 \caption{ - empty caption - }\label{fig:groups-2}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-3}
 \end{figure}
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4}
 
@@
 
-\caption{ - empty caption - }\label{fig:groups-3}
+\caption{ - empty caption - }\label{fig:groups-4}
 \end{figure}
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-4}
-\end{figure}
-\begin{figure}[H]
-
 {\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-5}
@@
 \end{figure}
+
+\begin{verbatim}
+Warning: Removed 229 rows containing non-finite outside the scale range
+(`stat_bin()`).
+\end{verbatim}
+
+\begin{verbatim}
+Warning: Removed 28216 rows containing non-finite outside the scale range
+(`stat_bin()`).
+\end{verbatim}
+
 \begin{figure}[H]
@@
 \end{figure}
+
+\begin{verbatim}
+Warning: Removed 229 rows containing non-finite outside the scale range (`stat_bin()`).
+Removed 28216 rows containing non-finite outside the scale range (`stat_bin()`).
+\end{verbatim}
+
 \begin{figure}[H]
@@
 \caption{ - empty caption - }\label{fig:groups-7}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-8}
 \end{figure}
@@
 
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-8}
+\end{figure}
 \begin{figure}[H]
@@
 \end{figure}
+
+\hypertarget{zhang2018}{%
+\subsection{@Zhang2018}\label{zhang2018}}
+
 \begin{figure}[H]
@@
 \caption{ - empty caption - }\label{fig:groups-13}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-14}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-14}
 \end{figure}
@@
 \begin{verbatim}
-2024-06-27 02:44:09.1 athan@tyler GHI_enh_04_investigate.R 2.523809 mins
+2024-07-05 07:51:29.9 athan@tyler GHI_enh_04_investigate.R 2.549931 mins
 \end{verbatim}

### 2024-07-05 GHI_enh_04_investigate.tex
Commit 2024-07-05 12:14

@@
 \begin{verbatim}
+The following object is masked from 'package:purrr':
+
+    discard
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:readr':
+
+    col_factor
+\end{verbatim}
+
+\begin{verbatim}
 The following object is masked from 'package:viridis':
@@
 \begin{verbatim}
-Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
-i Please use the `legend.position.inside` argument of `theme()` instead.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+Warning: Removed 229 rows containing non-finite outside the scale range (`stat_bin()`).
+Removed 28216 rows containing non-finite outside the scale range (`stat_bin()`).
 \end{verbatim}
@@
 \end{figure}
+
+\begin{verbatim}
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
+i Please use the `legend.position.inside` argument of `theme()` instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
 \begin{figure}[H]
@@
 \caption{ - empty caption - }\label{fig:groups-13}
+\end{figure}
+
+\hypertarget{zhang2018}{%
+\subsection{@Zhang2018}\label{zhang2018}}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-14}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-14}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-15}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-15}
 \end{figure}
@@
 \begin{verbatim}
-2024-07-05 07:51:29.9 athan@tyler GHI_enh_04_investigate.R 2.549931 mins
+2024-07-05 08:41:25.9 athan@tyler GHI_enh_04_investigate.R 1.700820 mins
 \end{verbatim}

### 2024-07-05 GHI_enh_04_investigate.tex
Commit 2024-07-05 13:12

@@
 \begin{verbatim}
+Attaching package: 'ggpubr'
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:cowplot':
+
+    get_legend
+\end{verbatim}
+
+\begin{verbatim}
+The following objects are masked from 'package:ggpp':
+
+    as_npc, as_npcx, as_npcy
+\end{verbatim}
+
+\begin{verbatim}
 Warning: Removed 229 rows containing non-finite outside the scale range (`stat_bin()`).
@@
 \begin{verbatim}
-Warning: Removed 229 rows containing non-finite outside the scale range (`stat_bin()`).
-Removed 28216 rows containing non-finite outside the scale range (`stat_bin()`).
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
+i Please use the `legend.position.inside` argument of `theme()` instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
 \end{verbatim}
@@
 \caption{ - empty caption - }\label{fig:groups-14}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-15}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-15}
 \end{figure}
@@
 \begin{verbatim}
-2024-07-05 08:41:25.9 athan@tyler GHI_enh_04_investigate.R 1.700820 mins
+2024-07-05 09:30:57.8 athan@tyler GHI_enh_04_investigate.R 2.177551 mins
 \end{verbatim}

### 2024-07-09 article/article.tex
Commit 2024-07-09 21:13

@@
 \(0.00272\) per year (or \(\beta=0.084\) in 1997 and \(\beta=0.059\) in
-2005). Simulations with uvspec for the above Ångström coefficients, with
-WC of \(15.7\,\text{mm}\) and \(15.4\,\text{mm}\) for 1997 and 2005
-respectively, where for 1997 we used the first available WC data
-(i.e.~2003) as a proxy, also taken from AERONET, and for a SZA of
-\(55^\circ\) reveal a trend of \(+0.21\,\%\) per year in
+2005). Simulations with uvspec for the above Ångström coefficients,
+assuming constant WC of \(15.6\,\text{mm}\) taken from the Cimel, and
+for a SZA of \(55^\circ\) reveal a trend of \(+0.21\,\%\) per year in
 \(\text{GHI}_\text{ref}\). The SZA of \(55^\circ\) was chosen as

### 2024-07-09 article/article.Rmd
Commit 2024-07-09 21:13

@@
 a change in the Ångström coefficient $\beta$ of $0.00272$ per year (or $\beta=0.084$ in
-1997 and $\beta=0.059$ in 2005).  Simulations with uvspec for the above Ångström
+1997 and $\beta=0.059$ in 2005).
+<!--
+Simulations with uvspec for the above Ångström
 coefficients, with WC of
@@
 $+0.21\,\%$ per year in $\text{GHI}_\text{ref}$. 
-The SZA of $55^\circ$ was chosen as representative of all days in the year in order
+-->
+Simulations with uvspec for the above Ångström coefficients, assuming constant WC of
+$15.6\,\text{mm}$ taken from the Cimel, and for a SZA of $55^\circ$ reveal a trend of
+$+0.21\,\%$ per year in $\text{GHI}_\text{ref}$.  The SZA of $55^\circ$ was chosen as
+representative of all days in the year in order
 to get a rough estimate of the annually averaged change in clear sky irradiance.  For

### 2024-07-09 Article_B8/Article_B8.Rmd
Commit 2024-07-09 22:18

--- 2024-07-09 article/article.Rmd
@@
 
-```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023."}
-knitr::include_graphics("../images/groups-1.png")
+```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023.
+The histogram was splited in two plots with differnt y-axis limits for better readability."}
+# knitr::include_graphics("../images/groups-1.png")
+knitr::include_graphics("../images/groups-7.png")
 ```

### 2024-07-09 Article_B8/Article_B8_plain.tex
Commit 2024-07-09 22:18

--- 2024-07-09 article/article.tex
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/groups-1}
+{\centering \includegraphics[width=1\linewidth]{../images/groups-7}
 
@@
 
-\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023.}\label{fig:ceg-duration-distribution}
+\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023.
+The histogram was splited in two plots with differnt y-axis limits for better readability.}\label{fig:ceg-duration-distribution}
 \end{figure}

### 2024-07-10 article/article.Rmd
Commit 2024-07-10 10:14

@@
 the CE events the OIR is below the long-term average of
-$`r round(mean(ST_E_yearly$GLB_diff.mean), 1)` \, \text{W} / \text{m}^2$,
-while about $8.1\,\%$ of the events correspond to OIR larger than
-$100\,\text{W}/\text{m}^2$ and up to the highest value of $412.4\,\text{W}/\text{m}^2$.
-This distribution is indicative of the magnitude and the probability of the expected
-CE events over Thessaloniki.  Similar distribution of CE events, albeit with larger
-OIR values, has been reported by @Vamvakas2020, for the city of Patras. This site is
-located $2.5^\circ$ south of Thessaloniki and is exposed to air masses coming mainly
-from the eastern Mediterranean resulting in different cloud patterns, that may affect
-the characteristics and magnitude of the CE events.
+$`r round(mean(ST_E_yearly$GLB_diff.mean),1)`\,\text{W}/\text{m}^2$, while about
+$8.1\,\%$ of the events correspond to OIR larger than $100\,\text{W}/\text{m}^2$ and
+up to the highest value of $412.4\,\text{W}/\text{m}^2$.  This distribution is
+indicative of the magnitude and the probability of the expected CE events over
+Thessaloniki.  Similar distribution of CE events, albeit with larger OIR values, has
+been reported by @Vamvakas2020, for the city of Patras. This site is located
+$2.5^\circ$ south of Thessaloniki and is exposed to air masses coming mainly from the
+eastern Mediterranean resulting in different cloud patterns, that may affect the
+characteristics and magnitude of the CE events.
 
@@
 
-```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023."}
-knitr::include_graphics("../images/groups-1.png")
+```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023.
+The histogram was split in two plots with different y-axis scales for better readability."}
+# knitr::include_graphics("../images/groups-1.png")
+knitr::include_graphics("../images/groups-7.png")
 ```

### 2024-07-10 SUBMISSION/article/article.tex
Commit 2024-07-10 11:13

--- 2024-07-09 Article_B8/Article_B8_plain.tex
@@
 CE events. For the majority (over \(62\,\%\)) of the CE events the OIR
-is below the long-term average of \(39.9 \, \text{W} / \text{m}^2\),
-while about \(8.1\,\%\) of the events correspond to OIR larger than
+is below the long-term average of \(39.9\,\text{W}/\text{m}^2\), while
+about \(8.1\,\%\) of the events correspond to OIR larger than
 \(100\,\text{W}/\text{m}^2\) and up to the highest value of
@@
 \caption{Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023.
-The histogram was splited in two plots with differnt y-axis limits for better readability.}\label{fig:ceg-duration-distribution}
+The histogram was split in two plots with different y-axis scales for better readability.}\label{fig:ceg-duration-distribution}
 \end{figure}

### 2024-08-23 article/article.Rmd
Commit 2024-08-23 14:14

@@
     keep_tex:         true
+    keep_md:          true
     citation_package: natbib
@@
                                header = TRUE))
+plus_sign <- function(x) ifelse(x >= 0, paste0("+", x), x)
 ```
@@
 observed GHI to levels even higher than the expected clear-sky irradiance
-[@Cordero2023; @Vamvakas2020; @CastillejoCuberos2020; @Vamvakas2020 and references
+[@Cordero2023; @Vamvakas2020; @CastillejoCuberos2020;  and references
 therein].
@@
 solar constant, resulting in clearness indices above unit. A summary of extreme cloud
-enchantment (ECE) cases has been compiled by @Martins2022. Cloud enhancements can
+enhancement (ECE) cases has been compiled by @Martins2022. Cloud enhancements can
 have also some practical implications.  The intensity and duration of enhancements
@@
 <!-- our work -->
-In this study, we evaluate the effects CE on GHI by investigating their frequency of
-occurrence, intensity, and duration in a thirty-year period of GHI observations at
+In this study, we evaluate the effects of CE on GHI by investigating their frequency
+of occurrence, intensity, and duration in a thirty-year period of GHI observations at
 Thessaloniki, Greece.  We used modeled clear sky irradiance as a baseline to identify
-cloud enhancements, and we determined long-term trends of the above-mentioned metrics,
-their climatology and some general characteristics.  To our knowledge there are no
-other studies that provide trends from such long dataset.
+cloud enhancements, and we determined long-term trends of the above-mentioned
+metrics, their climatology and some general characteristics.  To our knowledge there
+are no other studies that provide trends from such long dataset.
 
@@
 seconds to several minutes, here we are constrained by the temporal resolution of our
-data to identify evens with duration of at minimum one-minute.
+data to identify events with duration of at minimum one-minute.
 
@@
 (c) absence of clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
-(d) absence of clouds and absence of EC events,
-(e) with at least $60\,\%$ of the day length without clouds and presence of EC events,
+(d) absence of clouds and absence of CE events,
+(e) with at least $60\,\%$ of the day length without clouds and presence of CE events,
 (h) randomly selected days, and
@@
 frequency of occurrence 
-($`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$)
+($`r plus_sign(round(yearlyCE[var == "GLB_diff.N", slope], 1))`\pm `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$)
 and the excess irradiation 
-($`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)` \pm `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$),
+($`r plus_sign(round(yearlyCE[var == "GLB_diff.sum", slope], 1))` \pm `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$),
 which are also statistically significant.
 In contrast the trend of the yearly mean OIR is negligible 
-($`r round(yearlyCE[var == "GLB_diff.mean", slope], 1)`\pm `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\text{W}/\text{m}^2/\text{year}$)
+($`r plus_sign(round(yearlyCE[var == "GLB_diff.mean", slope], 1))`\pm `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\text{W}/\text{m}^2/\text{year}$)
 and of no statistical significance.
 The average OIR for the entire period is
-$`r round(mean(ST_E_yearly$GLB_diff.mean), 1)`\pm `r round(sd(ST_E_yearly$GLB_diff.mean),1)`\,\text{W}/\text{m}^2$.
+$`r plus_sign(round(mean(ST_E_yearly$GLB_diff.mean), 1))`\pm `r round(sd(ST_E_yearly$GLB_diff.mean),1)`\,\text{W}/\text{m}^2$.
 The interannual variability of the data about the trend lines is quite large.
@@
 The relation between the duration and the mean OIR of the groups has also been
-studied (Figure\nobreakspace{}\ref{fig:group-2d}).  Evidently, evens of high excess
+studied (Figure\nobreakspace{}\ref{fig:group-2d}).  Evidently, events of high excess
 irradiation have small duration and vice versa. The vast majority of grouped events
@@
 found an increase of
-$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$,
+$`r plus_sign(round(yearlyCE[var == "GLB_diff.N", slope], 1))`\pm `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$,
 with the mean annual irradiation of the CE events increasing with a rate of
-$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$.
+$`r plus_sign(round(yearlyCE[var == "GLB_diff.sum", slope], 1))`\pm `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$.
 The most active months of CE events are May and June.  We found that continuous CE

### 2024-08-23 article/article.tex
Commit 2024-08-23 14:14

@@
 observed GHI to levels even higher than the expected clear-sky
-irradiance \citep[ and references
-therein]{Cordero2023, Vamvakas2020, CastillejoCuberos2020, Vamvakas2020}.
+irradiance {[}\citet{Cordero2023}; \citet{Vamvakas2020};
+\citet{CastillejoCuberos2020}; and references therein{]}.
 
@@
 momentarily the solar constant, resulting in clearness indices above
-unit. A summary of extreme cloud enchantment (ECE) cases has been
+unit. A summary of extreme cloud enhancement (ECE) cases has been
 compiled by \citet{Martins2022}. Cloud enhancements can have also some
@@
 
-In this study, we evaluate the effects CE on GHI by investigating their
-frequency of occurrence, intensity, and duration in a thirty-year period
-of GHI observations at Thessaloniki, Greece. We used modeled clear sky
-irradiance as a baseline to identify cloud enhancements, and we
-determined long-term trends of the above-mentioned metrics, their
+In this study, we evaluate the effects of CE on GHI by investigating
+their frequency of occurrence, intensity, and duration in a thirty-year
+period of GHI observations at Thessaloniki, Greece. We used modeled
+clear sky irradiance as a baseline to identify cloud enhancements, and
+we determined long-term trends of the above-mentioned metrics, their
 climatology and some general characteristics. To our knowledge there are
@@
 we are constrained by the temporal resolution of our data to identify
-evens with duration of at minimum one-minute.
+events with duration of at minimum one-minute.
 
@@
 implementing a clear sky identification algorithm as discussed in
-\citet{Natsis2023}), (d) absence of clouds and absence of EC events, (e)
+\citet{Natsis2023}), (d) absence of clouds and absence of CE events, (e)
 with at least \(60\,\%\) of the day length without clouds and presence
-of EC events, (h) randomly selected days, and (i) manually selected
+of CE events, (h) randomly selected days, and (i) manually selected
 days. For the latter case and where needed, we also used images from the
@@
 increasing trends, most pronounced for the frequency of occurrence
-(\(45.6\pm 21.9\,\text{cases}/\text{year}\)) and the excess irradiation
-(\(116.9 \pm 67.8\,\text{kJ}/\text{year}\)), which are also
+(\(+45.6\pm 21.9\,\text{cases}/\text{year}\)) and the excess irradiation
+(\(+116.9 \pm 67.8\,\text{kJ}/\text{year}\)), which are also
 statistically significant. In contrast the trend of the yearly mean OIR
-is negligible (\(0.1\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of
+is negligible (\(+0.1\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of
 no statistical significance. The average OIR for the entire period is
-\(39.9\pm 2.7\,\text{W}/\text{m}^2\). The interannual variability of the
-data about the trend lines is quite large. Furthermore, the spread tends
-to increase with time (at least for the quantities of panels b and c),
-suggesting a significant variability in cloud patterns over the area,
-possibly associated to changes in climate.
+\(+39.9\pm 2.7\,\text{W}/\text{m}^2\). The interannual variability of
+the data about the trend lines is quite large. Furthermore, the spread
+tends to increase with time (at least for the quantities of panels b and
+c), suggesting a significant variability in cloud patterns over the
+area, possibly associated to changes in climate.
 
@@
 
-\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023.}\label{fig:ceg-duration-distribution}
+\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023.
+The histogram was split in two plots with different y-axis scales for better readability.}\label{fig:ceg-duration-distribution}
 \end{figure}
@@
 also been studied (Figure\nobreakspace{}\ref{fig:group-2d}). Evidently,
-evens of high excess irradiation have small duration and vice versa. The
-vast majority of grouped events are associated with small excess
+events of high excess irradiation have small duration and vice versa.
+The vast majority of grouped events are associated with small excess
 irradiation (e.g., \(<5\,\text{kJ}/\text{m}^2\)) and small duration
@@
 After analyzing the CE cases, we found an increase of
-\(45.6\pm 21.9\,\text{cases}/\text{year}\), with the mean annual
+\(+45.6\pm 21.9\,\text{cases}/\text{year}\), with the mean annual
 irradiation of the CE events increasing with a rate of
-\(116.9\pm 67.8\,\text{kJ}/\text{year}\). The most active months of CE
+\(+116.9\pm 67.8\,\text{kJ}/\text{year}\). The most active months of CE
 events are May and June. We found that continuous CE events can last up

### 2024-08-23 article/article.tex
Commit 2024-08-23 15:09

@@
 redistributed through the CE events. This is also depicted by the ECE
-irradiance values, which can exceed the equivalent clear sky irradiance
-by a significant amount.
+irradiance values, which exceed the equivalent clear sky irradiance by a
+significant amount.
 
@@
 The distribution of the number of CE events as a function of OIR is
-shown in Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently,
-there is an inverse relationship between the frequency of CE events and
-OIR with an exponential-like decline. This is expected, as the stronger
-the CE events are, the rarer the conditions favoring the occurrence of
-CE events. For the majority (over \(62\,\%\)) of the CE events the OIR
-is below the long-term average of \(39.9\,\text{W}/\text{m}^2\), while
+shown in Figure\nobreakspace{}\ref{fig:ovir-distribution}. There is an
+inverse relationship between the frequency of CE events and OIR with an
+exponential-like decline. This is expected, as the stronger the CE
+events are, the rarer the conditions favoring the occurrence of CE
+events. For the majority (over \(62\,\%\)) of the CE events the OIR is
+below the long-term average of \(39.9\,\text{W}/\text{m}^2\), while
 about \(8.1\,\%\) of the events correspond to OIR larger than

### 2024-08-23 article/article.Rmd
Commit 2024-08-23 15:09

@@
 radiation of the region is not increased, but is rather redistributed through the CE
-events.  This is also depicted by the ECE irradiance values, which can exceed the
+events.  This is also depicted by the ECE irradiance values, which exceed the
 equivalent clear sky irradiance by a significant amount.
@@
 The distribution of the number of CE events as a function of OIR is shown in
-Figure\nobreakspace{}\ref{fig:ovir-distribution}.  Apparently, there is an inverse
+Figure\nobreakspace{}\ref{fig:ovir-distribution}.  There is an inverse
 relationship between the frequency of CE events and OIR with an exponential-like

### 2024-08-23 article/article.Rmd
Commit 2024-08-23 20:14

@@
 characterized each data point as an enhancement event and calculated the over
-irradiance (OIR). The OIR is defined as the irradiance difference of the measured
+irradiance (OI). The OI is defined as the irradiance difference of the measured
 one-minute GHI from the $\text{GHI}_\text{ref}$ corresponding to cloud-free
 atmosphere.
-<!-- CE identification criterion ($\text{OIR}_i =
+<!-- CE identification criterion ($\text{OI}_i =
 \text{GHI}_i - \text{GHI}_\text{CSlim}$), as defined in
@@
 
-In this study our main focus was to quantify the over irradiance related to CEs. A
+In this study our main focus was to quantify the OI related to CEs. A
 key issue for achieving this goal is to define a threshold for the CE
@@
 the following characteristics:
-(a) the strongest over irradiance CE events,
-(b) the largest daily total over irradiance,
+(a) the strongest OI CE events,
+(b) the largest daily total OI,
 (c) absence of clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
@@
 <!-- mask some of the CE events. The actual CE events, produce higher irradiance and thus
-<!-- are identified as such. As a side effect, the reported OIR will be slight
+<!-- are identified as such. As a side effect, the reported OI will be slight
 <!-- underestimated for those SZAs, but the overall contribution of those cases to the
@@
 this method was proven capable in detecting all major CE events.  Where some CE
-events with very low OIR may be not detected, these are few with small
+events with very low OI may be not detected, these are few with small
 over-irradiance, and it is unlikely that will affect significantly our results.
@@
 <!-- extreme caces criterion -->
-A sub-category of the CE events that is often discussed in the relevant literature
+A sub-category of the CE events that is often discussed in the literature
 [@Cordero2023; @Martins2022; @Yordanov2015], are the extreme cloud enhancement (ECE)
@@
 on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, corresponding
-to OIR of $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
-<!-- The absolute strongest CE event had an OIR of 
+to OI of $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
+<!-- The absolute strongest CE event had an OI of 
 <!-- $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,\text{W}/\text{m}^2$ on
@@
 In the following sections we are discussing the long-term trends and variability of
-the CE events as well as of the corresponding OIR and excess irradiation.
+the CE events as well as of the corresponding OI and excess irradiation.
 
@@
 climate; hence it would be reasonable to expect contributing to the frequency of
-occurrence of CE events over Thessaloniki, as well as to the average OIR and excess
+occurrence of CE events over Thessaloniki, as well as to the average OI and excess
 irradiation.  The long-term trends were calculated using a first-order autoregressive
@@
 Figure\nobreakspace{}\ref{fig:P-energy} shows the time series of the yearly number of
-CE cases (each with duration of one minute), the yearly mean OIR and the yearly
+CE cases (each with duration of one minute), the yearly mean OI and the yearly
 excess irradiation for the period 1993 -- 2023, together with corresponding linear
@@
 which are also statistically significant.
-In contrast the trend of the yearly mean OIR is negligible 
+In contrast the trend of the yearly mean OI is negligible 
 ($`r plus_sign(round(yearlyCE[var == "GLB_diff.mean", slope], 1))`\pm `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\text{W}/\text{m}^2/\text{year}$)
 and of no statistical significance.
-The average OIR for the entire period is
+The average OI for the entire period is
 $`r plus_sign(round(mean(ST_E_yearly$GLB_diff.mean), 1))`\pm `r round(sd(ST_E_yearly$GLB_diff.mean),1)`\,\text{W}/\text{m}^2$.
@@
         }
-    \caption{Time series for the period 1993 -- 2023 of (a) the yearly CE number of occurrences, (b) the yearly mean OIR and (c) the yearly excess irradiation.
+    \caption{Time series for the period 1993 -- 2023 of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation.
 The black lines represent the linear trends on the yearly data.}\label{fig:P-energy}
@@
 
-The distribution of the number of CE events as a function of OIR is shown in
+The distribution of the number of CE events as a function of OI is shown in
 Figure\nobreakspace{}\ref{fig:ovir-distribution}.  There is an inverse
-relationship between the frequency of CE events and OIR with an exponential-like
+relationship between the frequency of CE events and OI with an exponential-like
 decline. This is expected, as the stronger the CE events are, the rarer the
 conditions favoring the occurrence of CE events.  For the majority (over $62\,\%$) of
-the CE events the OIR is below the long-term average of
+the CE events the OI is below the long-term average of
 $`r round(mean(ST_E_yearly$GLB_diff.mean),1)`\,\text{W}/\text{m}^2$, while about
-$8.1\,\%$ of the events correspond to OIR larger than $100\,\text{W}/\text{m}^2$ and
+$8.1\,\%$ of the events correspond to OI larger than $100\,\text{W}/\text{m}^2$ and
 up to the highest value of $412.4\,\text{W}/\text{m}^2$.  This distribution is
 indicative of the magnitude and the probability of the expected CE events over
-Thessaloniki.  Similar distribution of CE events, albeit with larger OIR values, has
+Thessaloniki.  Similar distribution of CE events, albeit with larger OI values, has
 been reported by @Vamvakas2020, for the city of Patras. This site is located
@@
 
-```{r ovir-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE events in Thessaloniki for the period 1993 -- 2023 as a function of OIR."}
+```{r ovir-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE events in Thessaloniki for the period 1993 -- 2023 as a function of OI."}
 knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
@@
 
-The relation between the duration and the mean OIR of the groups has also been
+The relation between the duration and the mean OI of the groups has also been
 studied (Figure\nobreakspace{}\ref{fig:group-2d}).  Evidently, events of high excess
@@
 
-<!-- ```{r echo=FALSE, fig.cap="Relation of mean over irradiance and CE group duration"} -->
+<!-- ```{r echo=FALSE, fig.cap="Relation of mean OI and CE group duration"} -->
 <!-- knitr::include_graphics("../images/groups-4.png") -->
@@
 
-<!-- ```{r echo=FALSE, fig.cap="Relation of maximun over irradiance and CE group duration"} -->
+<!-- ```{r echo=FALSE, fig.cap="Relation of maximun OI and CE group duration"} -->
 <!-- knitr::include_graphics("../images/groups-8.png") -->
@@
 solar energy production infrastructure are the extreme CE events (ECE), where solar
-irradiance exceeds the expected irradiance on top of the atmosphere
+irradiance exceeds the expected irradiance on top of the atmosphere at the same SZA
 (Equation\nobreakspace{}\ref{eq:ECE}).  Analogous to
@@
 (Figure\nobreakspace{}\ref{fig:P-extreme-distribution}) shows that in rare cases the
-OIR can exceed the TSI even by more than $400\,\text{W}/\text{m}^2$, while in
-$75\,\%$ of the cases the OIR is below $200\,\text{W}/\text{m}^2$. The OIR for the
+OI can exceed the TSI even by more than $400\,\text{W}/\text{m}^2$, while in
+$75\,\%$ of the cases the OI is below $200\,\text{W}/\text{m}^2$. The OI for the
 most frequent ECEs ranges between $140$ and $180\,\text{W}/\text{m}^2$.  These
 findings are in accordance with the results of @Vamvakas2020, the only difference
-being that the OIR values reported for are higher than those for Thessaloniki.
+being that the OI values reported for are higher than those for Thessaloniki.
 
@@
 analyzed have strong similarities with the results of @Vamvakas2020 for the city of
-Patras, south of Thessaloniki, albeit with differences in the magnitude of OIR.
+Patras, south of Thessaloniki, albeit with differences in the magnitude of OI.
 

### 2024-08-23 GHI_enh_07_Aerosols.R

@@ -318,7 +318,7 @@ abline(lm1, col = "red")
 
 ## display trend on graph
 fit <- lm1[[1]]
-units <- "Watt/m^2"
+units <- "W/m^2"
 legend("top", lty = 1, bty = "n", lwd = 2, cex = 1,
        c(paste("Trend: ",
              if (fit[2] > 0) "+" else "-",
@@ -355,7 +355,7 @@ abline(lm_55, col = "red")
 
 ## display trend on graph
 fit <- lm_55[[1]]
-units <- "Watt/m^2"
+units <- "W/m^2"
 legend("top", lty = 1, bty = "n", lwd = 2, cex = 1,
        c(paste("Trend: ",
                if (fit[2] > 0) "+" else "-",
@@ -387,7 +387,7 @@ abline(lm_BR_55, col = "red")
 
 ## display trend on graph
 fit <- lm_BR_55[[1]]
-units <- "Watt/m^2"
+units <- "W/m^2"
 legend("top", lty = 1, bty = "n", lwd = 2, cex = 1,
        c(paste("Trend: ",
                if (fit[2] > 0) "+" else "-",
@@ -457,7 +457,7 @@ abline(lm_min, col = "red")
 
 ## display trend on graph
 fit <- lm_min[[1]]
-units <- "Watt/m^2"
+units <- "W/m^2"
 legend("top", lty = 1, bty = "n", lwd = 2, cex = 1,
        c(paste("Trend: ",
              if (fit[2] > 0) "+" else "-",
@@ -488,7 +488,7 @@ abline(lm_BR_min, col = "red")
 
 ## display trend on graph
 fit <- lm_BR_min[[1]]
-units <- "Watt/m^2"
+units <- "W/m^2"
 legend("top", lty = 1, bty = "n", lwd = 2, cex = 1,
        c(paste("Trend: ",
                if (fit[2] > 0) "+" else "-",
@@ -557,7 +557,7 @@ abline(lm_mean, col = "red")
 
 ## display trend on graph
 fit   <- lm_mean[[1]]
-units <- "Watt/m^2"
+units <- "W/m^2"
 legend("top", lty = 1, bty = "n", lwd = 2, cex = 1,
        c(paste("Trend: ",
                if (fit[2] > 0) "+" else "-",
@@ -594,7 +594,7 @@ abline(lm_BR_mean, col = "red")
 
 ## display trend on graph
 fit <- lm_BR_mean[[1]]
-units <- "Watt/m^2"
+units <- "W/m^2"
[…]

### 2024-08-23 article/article.tex
Commit 2024-08-23 20:14

@@
 
-A sub-category of the CE events that is often discussed in the relevant
+A sub-category of the CE events that is often discussed in the
 literature \citep{Cordero2023, Martins2022, Yordanov2015}, are the
@@
 extreme CE events (ECE), where solar irradiance exceeds the expected
-irradiance on top of the atmosphere
+irradiance on top of the atmosphere at the same SZA
 (Equation\nobreakspace{}\ref{eq:ECE}). Analogous to

### 2024-08-23 GHI_enh_03_process.R

@@ -876,7 +876,7 @@ ST_monthly[season_Yqrt %% 1 == 0.75, Season := "Autumn"]
 # #+ excess, include=F, echo=F, fig.cap="Trend and mean radiation enhancement radiation, above threshold, per case."
 # plot( Enh_yearly$year, Enh_yearly$Ench_intesit,
 #       xlab = "Year",
-#       ylab = bquote("Mean enhancement intensity ["~ Watt~m^-2~N^-1~"]")
+#       ylab = bquote("Mean enhancement intensity ["~ W~m^-2~N^-1~"]")
 # )
 # abline( h = mean(Enh_yearly$Ench_intesit, na.rm = TRUE), lty = 2 )
 # lm1        <- lm( Enh_yearly$Ench_intesit ~ Enh_yearly$year )
@@ -889,7 +889,7 @@ ST_monthly[season_Yqrt %% 1 == 0.75, Season := "Autumn"]
 # #+ include=F, echo=F
 # plot( Enh_yearly$year, Enh_yearly$avg_Ench,
 #       xlab = "Year",
-#       ylab = bquote("Average enchantment intensity ["~ Watt~m^-2~"]")
+#       ylab = bquote("Average enchantment intensity ["~ W~m^-2~"]")
 # )
 #
 # plot(Enh_daily$Day, Enh_daily$sum_Diff)

### 2024-08-24 GHI_enh_07_Aerosols.tex
Commit 2024-06-06 20:17
Commit 2024-06-09 22:17
Commit 2024-08-24 06:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-06-06}
+\date{2024-08-23}
 
@@
 \begin{verbatim}
-Registered S3 method overwritten by 'ggpmisc':
-  method                  from   
-  as.character.polynomial polynom
-\end{verbatim}
-
-\begin{verbatim}
 Attaching package: 'zoo'
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-1)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-1}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-2)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-2}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-3)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-3}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-4)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-4}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-5)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-5}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-6)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-6}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-7)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-7}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-8)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-8}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-9)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-9}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-10)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-10}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-11)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-11}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-12)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-12}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-13)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-13}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-14)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-14}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-15)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-15}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-4-16)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-16}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-1)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-1}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-2)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-2}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-3)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-3}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-4)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-4}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-5)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-5}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-6)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-6}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-7)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-7}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-8)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-8}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-9)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-9}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-10)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-10}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-11)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-11}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-12)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-12}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-13)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-13}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-14)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-14}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-15)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-15}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-16)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-16}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-17)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-17}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-18)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-18}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-19)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-19}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-20)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-20}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-21)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-21}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-22)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-22}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-23)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-23}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-24)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-24}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-25)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-25}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-26)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-26}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-27)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-27}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-28)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-28}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-29)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-29}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-30)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-30}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-31)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-31}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-32)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-32}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-33)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-33}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-34)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-34}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-35)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-35}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-36)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-36}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-37)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-37}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-38)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-38}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-39)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-39}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-40)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-40}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-41)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-41}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-42)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-42}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-43)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-43}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-44)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-44}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-45)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-45}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-46)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-46}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-47)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-47}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-48)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-48}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-49)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-49}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-50)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-50}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-51)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-51}
 \end{figure}
@@
 
-\caption{ - empty caption - }(\#fig:unnamed-chunk-5-52)
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-52}
 \end{figure}
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/P_CS_change-1}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/P-CS-change-1}
 
@@
 
-\caption{ - empty caption - }(\#fig:P_CS_change)
+\caption{ - empty caption - }\label{fig:P-CS-change}
 \end{figure}

### 2024-08-24 article/article.tex
Commit 2024-08-24 06:14

@@
 above which we characterized each data point as an enhancement event and
-calculated the over irradiance (OIR). The OIR is defined as the
-irradiance difference of the measured one-minute GHI from the
+calculated the over irradiance (OI). The OI is defined as the irradiance
+difference of the measured one-minute GHI from the
 \(\text{GHI}_\text{ref}\) corresponding to cloud-free atmosphere. First,
@@
 
-In this study our main focus was to quantify the over irradiance related
-to CEs. A key issue for achieving this goal is to define a threshold for
-the CE identification, representative of the clear-sky irradiance at the
-time of each GHI measurement. This depends on the selection of the
+In this study our main focus was to quantify the OI related to CEs. A
+key issue for achieving this goal is to define a threshold for the CE
+identification, representative of the clear-sky irradiance at the time
+of each GHI measurement. This depends on the selection of the
 appropriate atmospheric parameterization for the RTM simulations. The
@@
 threshold. These sets were random groups of about 20 -- 30 days with the
-following characteristics: (a) the strongest over irradiance CE events,
-(b) the largest daily total over irradiance, (c) absence of clouds (by
-implementing a clear sky identification algorithm as discussed in
-\citet{Natsis2023}), (d) absence of clouds and absence of CE events, (e)
-with at least \(60\,\%\) of the day length without clouds and presence
-of CE events, (h) randomly selected days, and (i) manually selected
-days. For the latter case and where needed, we also used images from the
-sky-camera to further aid the decision of the manual inspection.
+following characteristics: (a) the strongest OI CE events, (b) the
+largest daily total OI, (c) absence of clouds (by implementing a clear
+sky identification algorithm as discussed in \citet{Natsis2023}), (d)
+absence of clouds and absence of CE events, (e) with at least \(60\,\%\)
+of the day length without clouds and presence of CE events, (h) randomly
+selected days, and (i) manually selected days. For the latter case and
+where needed, we also used images from the sky-camera to further aid the
+decision of the manual inspection.
 
@@
 only be approximated. However, this method was proven capable in
-detecting all major CE events. Where some CE events with very low OIR
-may be not detected, these are few with small over-irradiance, and it is
+detecting all major CE events. Where some CE events with very low OI may
+be not detected, these are few with small over-irradiance, and it is
 unlikely that will affect significantly our results.
@@
 events. The highest recorded GHI due to CE was
-\(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007, corresponding to OIR of
+\(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007, corresponding to OI of
 \(345.9\,\text{W}/\text{m}^2\). The strongest CE event of \(49.7\,\%\)
@@
 following sections we are discussing the long-term trends and
-variability of the CE events as well as of the corresponding OIR and
+variability of the CE events as well as of the corresponding OI and
 excess irradiation.
@@
 reasonable to expect contributing to the frequency of occurrence of CE
-events over Thessaloniki, as well as to the average OIR and excess
+events over Thessaloniki, as well as to the average OI and excess
 irradiation. The long-term trends were calculated using a first-order
@@
 yearly number of CE cases (each with duration of one minute), the yearly
-mean OIR and the yearly excess irradiation for the period 1993 -- 2023,
+mean OI and the yearly excess irradiation for the period 1993 -- 2023,
 together with corresponding linear trends. All three quantities show
@@
 (\(+116.9 \pm 67.8\,\text{kJ}/\text{year}\)), which are also
-statistically significant. In contrast the trend of the yearly mean OIR
+statistically significant. In contrast the trend of the yearly mean OI
 is negligible (\(+0.1\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of
-no statistical significance. The average OIR for the entire period is
+no statistical significance. The average OI for the entire period is
 \(+39.9\pm 2.7\,\text{W}/\text{m}^2\). The interannual variability of
@@
 
-The distribution of the number of CE events as a function of OIR is
-shown in Figure\nobreakspace{}\ref{fig:ovir-distribution}. There is an
-inverse relationship between the frequency of CE events and OIR with an
+The distribution of the number of CE events as a function of OI is shown
+in Figure\nobreakspace{}\ref{fig:ovir-distribution}. There is an inverse
+relationship between the frequency of CE events and OI with an
 exponential-like decline. This is expected, as the stronger the CE
 events are, the rarer the conditions favoring the occurrence of CE
-events. For the majority (over \(62\,\%\)) of the CE events the OIR is
+events. For the majority (over \(62\,\%\)) of the CE events the OI is
 below the long-term average of \(39.9\,\text{W}/\text{m}^2\), while
-about \(8.1\,\%\) of the events correspond to OIR larger than
+about \(8.1\,\%\) of the events correspond to OI larger than
 \(100\,\text{W}/\text{m}^2\) and up to the highest value of
@@
 magnitude and the probability of the expected CE events over
-Thessaloniki. Similar distribution of CE events, albeit with larger OIR
+Thessaloniki. Similar distribution of CE events, albeit with larger OI
 values, has been reported by \citet{Vamvakas2020}, for the city of
@@
 
-\caption{Relative frequency distribution of CE events in Thessaloniki for the period 1993 -- 2023 as a function of OIR.}\label{fig:ovir-distribution}
+\caption{Relative frequency distribution of CE events in Thessaloniki for the period 1993 -- 2023 as a function of OI.}\label{fig:ovir-distribution}
 \end{figure}
@@
 
-The relation between the duration and the mean OIR of the groups has
-also been studied (Figure\nobreakspace{}\ref{fig:group-2d}). Evidently,
+The relation between the duration and the mean OI of the groups has also
+been studied (Figure\nobreakspace{}\ref{fig:group-2d}). Evidently,
 events of high excess irradiation have small duration and vice versa.
@@
 (Figure\nobreakspace{}\ref{fig:P-extreme-distribution}) shows that in
-rare cases the OIR can exceed the TSI even by more than
-\(400\,\text{W}/\text{m}^2\), while in \(75\,\%\) of the cases the OIR
-is below \(200\,\text{W}/\text{m}^2\). The OIR for the most frequent
-ECEs ranges between \(140\) and \(180\,\text{W}/\text{m}^2\). These
-findings are in accordance with the results of \citet{Vamvakas2020}, the
-only difference being that the OIR values reported for are higher than
-those for Thessaloniki.
+rare cases the OI can exceed the TSI even by more than
+\(400\,\text{W}/\text{m}^2\), while in \(75\,\%\) of the cases the OI is
+below \(200\,\text{W}/\text{m}^2\). The OI for the most frequent ECEs
+ranges between \(140\) and \(180\,\text{W}/\text{m}^2\). These findings
+are in accordance with the results of \citet{Vamvakas2020}, the only
+difference being that the OI values reported for are higher than those
+for Thessaloniki.
 
@@
 Patras, south of Thessaloniki, albeit with differences in the magnitude
-of OIR.
+of OI.
 

### 2024-08-24 GHI_enh_00_dictionary.R
Commit 2024-08-24 11:08

@@ -66,7 +66,7 @@ varcol <- function(avar) {
 ## Name for each variable
 varname <- function(avar) {
   switch(gsub("\\..*$", "", gsub(".*_", "", avar)),
-         diff    = "Over Irradiance",
+         diff    = "OI",
          ench    = "Relative Enchancement",
          rati    = "Enchancement ratio",
          wattGLB = "GHI",

### 2024-08-24 GHI_enh_04_investigate.tex
Commit 2024-08-24 06:14
Commit 2024-08-24 11:08
Commit 2024-08-24 19:11

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-07-05}
+\date{2024-08-24}
 
@@
 \begin{verbatim}
-Warning: Removed 23 rows containing missing values or values outside the scale
-range (`geom_bar()`).
+Warning: Removed 32 rows containing missing values or values outside the scale range
+(`geom_bar()`).
 \end{verbatim}
@@
 \end{figure}
-
-\begin{verbatim}
-Warning: Removed 229 rows containing non-finite outside the scale range
-(`stat_bin()`).
-\end{verbatim}
-
-\begin{verbatim}
-Warning: Removed 28216 rows containing non-finite outside the scale range
-(`stat_bin()`).
-\end{verbatim}
-
 \begin{figure}[H]
@@
 \caption{ - empty caption - }\label{fig:groups-6}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-7}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-7}
+\end{figure}
+
+\begin{verbatim}
+Warning: Removed 252 rows containing non-finite outside the scale range
+(`stat_bin()`).
+\end{verbatim}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-8}
+\end{figure}
+
+\begin{verbatim}
+Warning: Removed 28187 rows containing non-finite outside the scale range
+(`stat_bin()`).
+\end{verbatim}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-9}
+\end{figure}
+
+\begin{verbatim}
+Warning: Removed 252 rows containing non-finite outside the scale range
+(`stat_bin()`).
+\end{verbatim}
+
+\begin{verbatim}
+Warning: Removed 28187 rows containing non-finite outside the scale range
+(`stat_bin()`).
+\end{verbatim}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-10}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-10}
 \end{figure}
@@
 \begin{verbatim}
-Warning: Removed 229 rows containing non-finite outside the scale range (`stat_bin()`).
-Removed 28216 rows containing non-finite outside the scale range (`stat_bin()`).
+Warning: Removed 252 rows containing non-finite outside the scale range (`stat_bin()`).
+Removed 28187 rows containing non-finite outside the scale range (`stat_bin()`).
 \end{verbatim}
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-7}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-7}
-\end{figure}
-
-\begin{verbatim}
-Warning: Removed 229 rows containing non-finite outside the scale range (`stat_bin()`).
-Removed 28216 rows containing non-finite outside the scale range (`stat_bin()`).
-\end{verbatim}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-8}
-\end{figure}
-
-\begin{verbatim}
-Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
-i Please use the `legend.position.inside` argument of `theme()` instead.
-This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-9}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-10}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-10}
-\end{figure}
 \begin{figure}[H]
@@
 \end{figure}
+
+\begin{verbatim}
+Warning: Removed 252 rows containing non-finite outside the scale range (`stat_bin()`).
+Removed 28187 rows containing non-finite outside the scale range (`stat_bin()`).
+\end{verbatim}
+
 \begin{figure}[H]
@@
 \caption{ - empty caption - }\label{fig:groups-14}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-15}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-15}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-16}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-16}
+\end{figure}
+
+\hypertarget{zhang2018}{%
+\subsection{@Zhang2018}\label{zhang2018}}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-17}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-17}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-18}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-18}
 \end{figure}
@@
 
-lmY: 0.062157 +/- 0.054182
+lmY: 0.029427 +/- 0.054286
 
@@
 
-lmY: 0.053059 +/- 0.041079
+lmY: 0.03518 +/- 0.042507
 
@@
 \begin{verbatim}
-2024-07-05 09:30:57.8 athan@tyler GHI_enh_04_investigate.R 2.177551 mins
+2024-08-24 16:09:38.1 athan@tyler GHI_enh_04_investigate.R 1.792265 mins
 \end{verbatim}

### 2024-08-24 article/article.Rmd
Commit 2024-08-23 22:14
Commit 2024-08-24 20:10

@@
 <!--
-CE: cloud enhancement cases one minute
-
-ECE: extreme cloud enhancement cases one minute over TSI on horizontal plane
-
-CEG: cloud enhancement groups, cases events with consecutive CE
 
@@
 The green line with blue symbols depicts the measured GHI in one minute steps.
-The red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles.
-The black curve represents the TSI at the top of the atmosphere, adjusted for the actual Sun-Earth distance and multiplied by the cosine of SZA.", fig.pos='H'}
+Red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles.Black curve represents the TOA TSI on horizontal plane.", fig.pos='H'}
 knitr::include_graphics("../images/example-days-18.png")
@@
 # knitr::include_graphics("../images/groups-1.png")
-knitr::include_graphics("../images/groups-7.png")
+knitr::include_graphics("../images/groups-8.png")
 ```

### 2024-08-24 article/article.tex
Commit 2024-08-24 11:08
Commit 2024-08-24 20:10

@@
 The green line with blue symbols depicts the measured GHI in one minute steps.
-The red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles.
-The black curve represents the TSI at the top of the atmosphere, adjusted for the actual Sun-Earth distance and multiplied by the cosine of SZA.}\label{fig:example-day}
+Red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles.Black curve represents the TOA TSI on horizontal plane.}\label{fig:example-day}
 \end{figure}
@@
 statistically significant. In contrast the trend of the yearly mean OI
-is negligible (\(+0.1\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of
-no statistical significance. The average OI for the entire period is
+is negligible (\(+0\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of no
+statistical significance. The average OI for the entire period is
 \(+39.9\pm 2.7\,\text{W}/\text{m}^2\). The interannual variability of
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/groups-7}
+{\centering \includegraphics[width=1\linewidth]{../images/groups-8}
 

### 2024-08-24 GHI_enh_04_investigate.tex
Commit 2024-08-24 20:10

@@
 \end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-7}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-7}
-\end{figure}
-
-\begin{verbatim}
-Warning: Removed 252 rows containing non-finite outside the scale range
-(`stat_bin()`).
-\end{verbatim}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-8}
-\end{figure}
-
-\begin{verbatim}
-Warning: Removed 28187 rows containing non-finite outside the scale range
-(`stat_bin()`).
-\end{verbatim}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-9}
-\end{figure}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-10}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-7}
 
@@
 
-\caption{ - empty caption - }\label{fig:groups-10}
+\caption{ - empty caption - }\label{fig:groups-7}
 \end{figure}
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-11}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8}
 
@@
 
-\caption{ - empty caption - }\label{fig:groups-11}
+\caption{ - empty caption - }\label{fig:groups-8}
 \end{figure}
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-12}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9}
 
@@
 
-\caption{ - empty caption - }\label{fig:groups-12}
+\caption{ - empty caption - }\label{fig:groups-9}
 \end{figure}
@@
 
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-10}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-10}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-11}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-11}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-12}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-12}
+\end{figure}
+\begin{figure}[H]
+
 {\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-13}
@@
 \caption{ - empty caption - }\label{fig:groups-15}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-16}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-16}
-\end{figure}
-
-\hypertarget{zhang2018}{%
-\subsection{@Zhang2018}\label{zhang2018}}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-17}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-17}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-18}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-18}
 \end{figure}
@@
 \begin{verbatim}
-2024-08-24 16:09:38.1 athan@tyler GHI_enh_04_investigate.R 1.792265 mins
+2024-08-24 16:34:51.8 athan@tyler GHI_enh_04_investigate.R 2.043213 mins
 \end{verbatim}

### 2024-08-24 article/article.Rmd
Commit 2024-08-25 00:10

@@
 # knitr::include_graphics("../images/groups-1.png")
-knitr::include_graphics("../images/groups-8.png")
+knitr::include_graphics("../images/groups-7.png")
 ```

### 2024-08-25 article/article.Rmd
Commit 2024-08-25 13:09

@@
 
-```{r ovir-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE events in Thessaloniki for the period 1993 -- 2023 as a function of OI."}
-knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
+```{r ovir-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE events in Thessaloniki for the period 1993 -- 2023 as a function of OI.
+The histogram was split in two plots with different y-axis scales for better readability."}
+knitr::include_graphics("../images/P-relative-distribution-diff-2.png")
 ```

### 2024-08-25 article/article.Rmd
Commit 2024-08-25 17:12

@@
 duration of CE events, showed that durations longer than 5 minutes are very rare,
-with exceptions lasting over an hour and up to 140 minutes.  Finally, we have detected enhancements above
-the total solar irradiance at the top of the atmosphere of up to
+with exceptions lasting over an hour and up to 140 minutes.  Finally, we have
+detected enhancements above the total solar irradiance at the top of the atmosphere
+for the same solar zenith angle of up to
 $400\,\text{W}/\text{m}^{2}$, with the $75\,\%$ of the cases below
@@
 Equation\nobreakspace\ref{eq:CE4}. -->
-First, we tested two simple approaches for the determination of
+First, we used a simple approach for the determination of
 $\text{GHI}_\text{ref}$: The Haurwitz's model [@Haurwitz1945], which is a simple
@@
 -->
-We have tested both methods by using an appropriate relative
-threshold and/or an additional constant offset.  The initial results showed that we
-can detect a big portion of the actual CE events.  However, by inspecting the daily
-plots of irradiance it became evident that changes in atmospheric conditions
-introduced numerous false positive or false negative results. The main reason for
-these discrepancies is the variability of the effects of aerosols and water vapor
-which were not taken into account in the two simple methods.  To produce a more
-representative reference we included the effects of these factors using a radiative
-transfer model (RTM).  The applied methodology is discussed in
-section\nobreakspace{}\ref{rtmcs}.
+We created a threshold by using an appropriate relative and/or an additional constant
+offset.  The initial results showed that we can detect a big portion of the actual CE
+events.  However, by inspecting the daily plots of irradiance it became evident that
+changes in atmospheric conditions introduced numerous false positive or false
+negative results. The main reason for these discrepancies is the variability of the
+effects of aerosols and water vapor which were not taken into account in the two
+simple methods.  To produce a more representative reference we included the effects
+of these factors using a radiative transfer model (RTM).  The applied methodology is
+discussed in section\nobreakspace{}\ref{rtmcs}.
 

### 2024-08-25 article/article.tex
Commit 2024-08-25 00:10
Commit 2024-08-25 17:12

@@
 \(\text{GHI}_\text{ref}\) corresponding to cloud-free atmosphere. First,
-we tested two simple approaches for the determination of
+we used a simple approach for the determination of
 \(\text{GHI}_\text{ref}\): The Haurwitz's model \citep{Haurwitz1945},
 which is a simple clear sky model and was already adjusted and applied
-to our data \citep{Natsis2023}. We have tested both methods by using an
-appropriate relative threshold and/or an additional constant offset. The
-initial results showed that we can detect a big portion of the actual CE
-events. However, by inspecting the daily plots of irradiance it became
-evident that changes in atmospheric conditions introduced numerous false
+to our data \citep{Natsis2023}. We created a threshold by using an
+appropriate relative and/or an additional constant offset. The initial
+results showed that we can detect a big portion of the actual CE events.
+However, by inspecting the daily plots of irradiance it became evident
+that changes in atmospheric conditions introduced numerous false
 positive or false negative results. The main reason for these
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/P-relative-distribution-diff-1}
+{\centering \includegraphics[width=1\linewidth]{../images/P-relative-distribution-diff-2}
 
@@
 
-\caption{Relative frequency distribution of CE events in Thessaloniki for the period 1993 -- 2023 as a function of OI.}\label{fig:ovir-distribution}
+\caption{Relative frequency distribution of CE events in Thessaloniki for the period 1993 -- 2023 as a function of OI.
+The histogram was split in two plots with different y-axis scales for better readability.}\label{fig:ovir-distribution}
 \end{figure}
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/groups-8}
+{\centering \includegraphics[width=1\linewidth]{../images/groups-7}
 

### 2024-08-25 GHI_enh_03_process.tex
Commit 2024-06-06 20:17
Commit 2024-06-10 10:14
Commit 2024-08-24 06:14
Commit 2024-08-25 19:11

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-06-06}
+\date{2024-08-25}
 
@@
    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
-    0.0    89.7   180.0   180.0   270.3   360.0 
+   0.00   89.59  180.00  180.00  270.41  360.00 
 \end{verbatim}
@@
     Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
--72.8133 -27.5835   0.6886   0.3233  28.1502  83.4876 
+-72.8133 -27.4719   0.7629   0.4279  28.2416  83.4876 
 \end{verbatim}
@@
 slope_min
+solar_constant
 SZA_aggregation_N_lim
@@
 \begin{verbatim}
-2024-06-06 10:26:55.1 athan@tyler GHI_enh_03_process.R 5.853366 mins
+2024-08-25 15:41:24.7 athan@tyler GHI_enh_03_process.R 7.859937 mins
 \end{verbatim}

### 2024-08-25 article/article.Rmd
Commit 2024-08-25 19:11

@@
 BR <-  unique(BR[typer == "BR SZA 55", .(year, pw_avg_mm, b, a)])
+MC <- readRDS("~/MANUSCRIPTS/02_enhancement/data/Max_cases.Rds")
 ```
@@
 
+$`r round(MC[Typ == "Max Glob", wattGLB],1)`\,\text{W}/\text{m}^2$
+$`r strftime(MC[Typ == "Max Glob", Date], "%d\\ %B %Y")`\,\text{W}/\text{m}^2$
+$`r round(MC[Typ == "Max Glob", GLB_diff],1)`\,\text{W}/\text{m}^2$
+$`r round(100*MC[Typ == "Max Glob", GLB_ench],1)`\,\%$
+
+$`r round(MC[Typ == "Max Enha", wattGLB],1)`\,\text{W}/\text{m}^2$
+$`r strftime(MC[Typ == "Max Enha", Date], "%d\\ %B %Y")`\,\text{W}/\text{m}^2$
+$`r round(MC[Typ == "Max Enha", GLB_diff],1)`\,\text{W}/\text{m}^2$
+$`r round(100*MC[Typ == "Max Enha", GLB_ench],1)`\,\%$
+
 Following the application of the above discussed methodology to the entire dataset 
@@
 The highest recorded GHI due to CE was
-$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$
-on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, corresponding
-to OI of $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
+$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$ on
+ `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, corresponding to OI of 
+$`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
+!!!!$`r round(100*ST_daily[which.max(GLB_diff.max), GLB_ench.max], 1)`\,\%$.!!!!!
 <!-- The absolute strongest CE event had an OI of 
@@
 `r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.
+!!!$`r round(ST_daily[which.max(GLB_ench.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$!!!!
 In the following sections we are discussing the long-term trends and variability of

### 2024-08-25 GHI_enh_05_distributions.R

@@ -497,16 +497,13 @@ quantile(DATA[wattGLB > ETH, GLB_diff])
 
 
 
-
-
-
-
-
-
-
-
-
-
+saveRDS(
+  rbind(
+    DATA[which.max(wattGLB),  .(Typ = "Max Glob", wattGLB, SZA, GLB_ench, GLB_diff, Date, CE = Enhanc_C_4, ECE = wattGLB > ETH)],
+    DATA[which.max(GLB_ench), .(Typ = "Max Enha", wattGLB, SZA, GLB_ench, GLB_diff, Date, CE = Enhanc_C_4, ECE = wattGLB > ETH)]
+  ),
+  "data/Max_cases.Rds"
+)
 
 
 

### 2024-08-26 article/article.tex
Commit 2024-08-25 19:11
Commit 2024-08-26 09:08

@@
 events. The highest recorded GHI due to CE was
-\(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007, corresponding to OI of
-\(345.9\,\text{W}/\text{m}^2\). The strongest CE event of \(49.7\,\%\)
-above the clear sky threshold was observed on 28~October 2016. In the
-following sections we are discussing the long-term trends and
-variability of the CE events as well as of the corresponding OI and
-excess irradiation.
+\(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007 at a SZA of
+\(19.9^\circ\) corresponding to OI of \(345.9\,\text{W}/\text{m}^2\) or
+\(32.3\,\%\) above the threshold. The strongest CE event of \(49.7\,\%\)
+above the clear sky threshold was observed on 28~October 2016 at a SZA
+of \(59.2^\circ\) with a GHI value of \(861.8\,\text{W}/\text{m}^2\) and
+a OI of \(286.1\,\text{W}/\text{m}^2\). Both cases are ECE events with
+\(168.7\,\text{W}/\text{m}^2\) and \(155.4\,\text{W}/\text{m}^2\) above
+the TSI at TSI for the same SZA, respectively. In the following sections
+we are discussing the long-term trends and variability of the CE events
+as well as of the corresponding OI and excess irradiation.
 

### 2024-08-26 article/article.Rmd
Commit 2024-08-26 09:08

--- 2024-08-25 article/article.Rmd
@@
 The highest recorded GHI due to CE was
-$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$
-on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, corresponding
-to OI of $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
-<!-- The absolute strongest CE event had an OI of 
-<!-- $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,\text{W}/\text{m}^2$ on
-<!-- `r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`. -->
+$`r round(MC[Typ == "Max Glob", wattGLB],1)`\,\text{W}/\text{m}^2$ on
+ `r strftime(MC[Typ == "Max Glob", Date], "%d\\ %B %Y")` at a SZA of
+$`r round(MC[Typ == "Max Glob", SZA],1)`^\circ$ corresponding to OI of
+$`r round(MC[Typ == "Max Glob", GLB_diff],1)`\,\text{W}/\text{m}^2$ or
+$`r round(100*MC[Typ == "Max Glob", GLB_ench],1)`\,\%$ above the threshold.
 The strongest CE event of
-$`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 
+$`r round(100*MC[Typ == "Max Enha", GLB_ench],1)`\,\%$ above the 
 clear sky threshold was observed on 
-`r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.
+`r strftime(MC[Typ == "Max Enha", Date], "%d\\ %B %Y")` at a SZA of
+$`r round(MC[Typ == "Max Enha", SZA],1)`^\circ$ with a GHI value of 
+$`r round(MC[Typ == "Max Enha", wattGLB],1)`\,\text{W}/\text{m}^2$ and a OI of
+$`r round(MC[Typ == "Max Enha", GLB_diff],1)`\,\text{W}/\text{m}^2$.
+Both cases are ECE events with
+$`r round(MC[Typ == "Max Glob", wattGLB - ETH],1)`\,\text{W}/\text{m}^2$ and
+$`r round(MC[Typ == "Max Enha", wattGLB - ETH],1)`\,\text{W}/\text{m}^2$ above the
+TSI at TSI for the same SZA, respectively.
 In the following sections we are discussing the long-term trends and variability of

### 2024-08-26 GHI_enh_02_ID_CE.R
Commit 2024-08-26 17:10

@@ -607,7 +607,7 @@ for (ii in 1:nrow(vec_days)) {
              ylim = ylim,
              ylab = expression(W/m^2), xlab = "Time (UTC)")
 
-        abline(h = solar_constant, col = "orange", lty = 3)
+        abline(h = solar_constant, col = "orange2", lty = 3)
 
         ## Global
         lines(temp$Date, temp$wattGLB, col = "green")
@@ -636,8 +636,8 @@ for (ii in 1:nrow(vec_days)) {
         #      line = 1.2, lwd = 0, lwd.ticks = 0, cex.axis = 0.8)
 
         ## Enchantment cases
-        points(temp[get(SelEnhanc) == TRUE & wattGLB <  ETH, wattGLB, Date], col = "red")
-        points(temp[get(SelEnhanc) == TRUE & wattGLB >= ETH, wattGLB, Date], col = "magenta")
+        points(temp[get(SelEnhanc) == TRUE & wattGLB <  ETH, wattGLB, Date], col = "palevioletred3")
+        points(temp[get(SelEnhanc) == TRUE & wattGLB >= ETH, wattGLB, Date], col = "red")
 
 
         ## Cloud cases
@@ -649,14 +649,14 @@ for (ii in 1:nrow(vec_days)) {
 
         legend("bottomright", ncol = 2,
                      c(  "GHI","CE threshold","TSI on horizontal plane","Solar Constant", "CE events","ECE events","Clouds IDs"),
-               col = c("green",         "red",                  "black",        "orange",       "red",   "magenta",      "blue"),
+               col = c("green",         "red",                  "black",       "orange2",       "palevioletred3",       "red",      "blue"),
                pch = c(     NA,            NA,                       NA,              NA,          1 ,          1 ,           3),
                lty = c(      1,             1,                        1,               3,          NA,          NA,          NA),
                bty = "n",
                cex = 0.8
         )
 
-
+stop()
         ## ggplot
 
         # cols <- brewer.pal(n = 9, name = 'Set1')

### 2024-08-26 GHI_enh_03_process.R
Commit 2024-08-26 19:11

@@ -363,6 +363,10 @@ ST_G0 <- DATA[!is.na(C1Grp0),
 ST_G0$Date <- as.POSIXct(ST_G0$Date, origin = "1970-01-01")
 
 
+stop()
+# min max SZA
+# first last SZA
+
 ## convert sum Irradiance to energy
 ## Σ(W/m^2) * 60 s = J/m^2
 ST_G0[, GLB_diff.sum  := GLB_diff.sum * 60 / Energy_Div]

### 2024-08-26 article/article.tex
Commit 2024-08-26 23:11

@@
 \(80\,\)m~a.s.l.). The GHI data were measured with a Kipp~\& Zonen CM-21
-pyranometer and cover the period 13~April 1993 to 31~December 2023.
+pyranometer and cover the period 01~January 1994 to 31~December 2023.
 During the study period, the pyranometer was independently calibrated
@@
 Following the application of the above discussed methodology to the
-entire dataset (\(6.1\) million of one-minute GHI measurements),
-\(1.76\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
+entire dataset (\(6\) million of one-minute GHI measurements),
+\(1.78\,\%\) were identified as CE events and \(0.037\,\%\) as ECE
 events. The highest recorded GHI due to CE was
@@
 statistical significance. The average OI for the entire period is
-\(+39.9\pm 2.7\,\text{W}/\text{m}^2\). The interannual variability of
+\(+40.1\pm 2.5\,\text{W}/\text{m}^2\). The interannual variability of
 the data about the trend lines is quite large. Furthermore, the spread
@@
 events. For the majority (over \(62\,\%\)) of the CE events the OI is
-below the long-term average of \(39.9\,\text{W}/\text{m}^2\), while
+below the long-term average of \(40.1\,\text{W}/\text{m}^2\), while
 about \(8.1\,\%\) of the events correspond to OI larger than
@@
 of these consecutive events, we grouped them into bins of increasing
-duration in steps of one minute. We have identified 28468 groups of CE
+duration in steps of one minute. We have identified 28062 groups of CE
 in the whole period of study, where the group of the longest duration of

### 2024-08-26 GHI_enh_03_process.tex
Commit 2024-08-26 23:11

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-08-25}
+\date{2024-08-26}
 
@@
    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
-   0.00   89.59  180.00  180.00  270.41  360.00 
+   0.00   89.59  180.00  180.00  270.42  360.00 
 \end{verbatim}
@@
     Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
--72.8133 -27.4719   0.7629   0.4279  28.2416  83.4876 
+-72.8133 -27.4717   0.7634   0.4285  28.2424  83.4876 
 \end{verbatim}
@@
 \end{Shaded}
-
-\begin{verbatim}
-Warning: Removed 2 rows containing missing values or values outside the scale range (`geom_line()`).
-Removed 2 rows containing missing values or values outside the scale range (`geom_line()`).
-\end{verbatim}
 
@@
 
-\begin{verbatim}
-Warning: Removed 2 rows containing missing values or values outside the scale range (`geom_line()`).
-Removed 2 rows containing missing values or values outside the scale range (`geom_line()`).
-\end{verbatim}
-
 \begin{figure}[H]
@@
     Min      1Q  Median      3Q     Max 
--319.48 -147.87  -56.18  101.04  719.45
+-316.47 -148.10  -55.61  103.32  718.33
 
@@
                   Estimate Std. Error t value Pr(>|t|)   
-(Intercept)      1.379e+02  4.559e+01   3.025 0.002663 ** 
-as.numeric(Date) 1.306e-07  3.650e-08   3.579 0.000391 ***
+(Intercept)      1.520e+02  4.805e+01   3.164  0.00169 **
+as.numeric(Date) 1.205e-07  3.816e-08   3.157  0.00173 **
 ---
@@
 
-Residual standard error: 196.3 on 363 degrees of freedom
-Multiple R-squared:  0.03409,   Adjusted R-squared:  0.03143 
-F-statistic: 12.81 on 1 and 363 DF,  p-value: 0.0003913
+Residual standard error: 197.8 on 354 degrees of freedom
+Multiple R-squared:  0.02738,   Adjusted R-squared:  0.02463 
+F-statistic: 9.966 on 1 and 354 DF,  p-value: 0.001732
 \end{verbatim}
@@
                    Estimate Std. Error t value Pr(>|t|)   
-(Intercept)       1.379e+02  4.559e+01   3.025 0.002663 ** 
-ST_E_monthly$Date 1.306e-07  3.650e-08   3.579 0.000391 ***
+(Intercept)       1.520e+02  4.805e+01   3.164  0.00169 **
+ST_E_monthly$Date 1.205e-07  3.816e-08   3.157  0.00173 **
 ---
@@
 \begin{verbatim}
-2024-08-25 15:41:24.7 athan@tyler GHI_enh_03_process.R 7.859937 mins
+2024-08-26 19:50:18.2 athan@sagan GHI_enh_03_process.R 3.387402 mins
 \end{verbatim}

### 2024-08-26 GHI_enh_04_investigate.tex
Commit 2024-08-25 00:10
Commit 2024-08-26 23:11

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-08-24}
+\date{2024-08-26}
 
@@
 This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+Call `lifecycle::last_lifecycle_warnings()` to see where this
+warning was generated.
 \end{verbatim}
@@
 \begin{verbatim}
-Warning: Removed 32 rows containing missing values or values outside the scale range
-(`geom_bar()`).
+Warning: Removed 32 rows containing missing values or values outside the
+scale range (`geom_bar()`).
 \end{verbatim}
@@
 \end{figure}
+
+\begin{verbatim}
+Warning: Removed 246 rows containing non-finite outside the scale range
+(`stat_bin()`).
+\end{verbatim}
+
+\begin{verbatim}
+Warning: Removed 27787 rows containing non-finite outside the scale range
+(`stat_bin()`).
+\end{verbatim}
+
 \begin{figure}[H]
@@
 \caption{ - empty caption - }\label{fig:groups-6}
-\end{figure}
-
-\begin{verbatim}
-Warning: Removed 252 rows containing non-finite outside the scale range
-(`stat_bin()`).
-\end{verbatim}
-
-\begin{verbatim}
-Warning: Removed 28187 rows containing non-finite outside the scale range
-(`stat_bin()`).
-\end{verbatim}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-7}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-7}
 \end{figure}
@@
 \begin{verbatim}
-Warning: Removed 252 rows containing non-finite outside the scale range (`stat_bin()`).
-Removed 28187 rows containing non-finite outside the scale range (`stat_bin()`).
+Warning: Removed 246 rows containing non-finite outside the scale range
+(`stat_bin()`).
+Removed 27787 rows containing non-finite outside the scale range
+(`stat_bin()`).
+\end{verbatim}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-7}
+
+}
+
+\caption{ - empty caption - }\label{fig:groups-7}
+\end{figure}
+
+\begin{verbatim}
+Warning: Removed 246 rows containing non-finite outside the scale range
+(`stat_bin()`).
+Removed 27787 rows containing non-finite outside the scale range
+(`stat_bin()`).
 \end{verbatim}
@@
 \begin{verbatim}
-Warning: Removed 252 rows containing non-finite outside the scale range (`stat_bin()`).
-Removed 28187 rows containing non-finite outside the scale range (`stat_bin()`).
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in
+ggplot2 3.5.0.
+i Please use the `legend.position.inside` argument of `theme()`
+  instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this
+warning was generated.
 \end{verbatim}
@@
 \end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-15}
-
-}
-
-\caption{ - empty caption - }\label{fig:groups-15}
-\end{figure}
 
@@
 \begin{verbatim}
-Warning: Removed 16 rows containing non-finite outside the scale range
+Warning: Removed 15 rows containing non-finite outside the scale range
 (`stat_bin2d()`).
@@
 \begin{verbatim}
-Warning: The `fun.y` argument of `stat_summary()` is deprecated as of ggplot2 3.3.0.
+Warning: The `fun.y` argument of `stat_summary()` is deprecated as of ggplot2
+3.3.0.
 i Please use the `fun` argument instead.
 This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+Call `lifecycle::last_lifecycle_warnings()` to see where this
+warning was generated.
 \end{verbatim}
@@
 \begin{verbatim}
-2024-08-24 16:34:51.8 athan@tyler GHI_enh_04_investigate.R 2.043213 mins
+2024-08-26 19:52:09.6 athan@sagan GHI_enh_04_investigate.R 0.838254 mins
 \end{verbatim}

### 2024-08-27 high_aod/upload.sh
Commit 2024-08-27 06:14

@@ -1,33 +1,0 @@
-#!/bin/bash
-## created on 2023-02-21
-
-#### enter description here
-
-bwlim=500
-rclone="$HOME/PROGRAMS/rclone"
-config="$HOME/Documents/rclone.conf"
-otheropt=" --checkers=20 --delete-before --stats=30s"
-bwlimit="  --bwlimit=${bwlim}k"
-
-
-if [[ "$(hostname)" = "sagan" ]]; then 
-    bwlim=500000
-    bwlimit="  --bwlimit=${bwlim}k"
-    echo "$(hostname)"
-fi
-# if [[ "$(hostname)" = "sagan" ]]; then 
-#     echo "Upload all pdfs"
-#     "${rclone}" ${otheropt} ${bwlimit} --config "$config" --include "*.pdf"  sync "$HOME/MANUSCRIPTS/2022_sdr_trends/" "lapauththanasis:/Trends"
-# else
-#     echo "This runs only on sagan"
-# fi
-
-echo "Upload all pdfs"
-"${rclone}" ${otheropt} ${bwlimit} --verbose --config "$config" --max-depth 1 --include "*.{pdf}"                      copy "/home/athan/MANUSCRIPTS/02_enhancement/"        "lapauththanasis:/Enhance"
-"${rclone}" ${otheropt} ${bwlimit} --verbose --config "$config" --max-depth 1 --include "*.{pdf,odt,docx}"             copy "/home/athan/MANUSCRIPTS/02_enhancement/article" "lapauththanasis:/Enhance"
-"${rclone}" ${otheropt} ${bwlimit} --verbose --config "$config" --max-depth 2 --include "[Aa]rticle*/*.{pdf,odt,docx}" copy "/home/athan/MANUSCRIPTS/02_enhancement/"        "lapauththanasis:/Enhance"
-
-#
-#"${rclone}" ${otheropt} ${bwlimit} --verbose --config "$config" --max-depth 2 --include "Article*/*.{pdf,odt,docx}"    copy "/home/athan/MANUSCRIPTS/02_enhancement/"        "lapauththanasis:/Enhance"
-
-exit 0 

### 2024-08-27 high_aod/GHI_enh_04_investigate.R
Commit 2024-08-27 06:14

@@ -1,1417 +1,0 @@
-# /* #!/usr/bin/env Rscript */
-# /* Copyright (C) 2022 Athanasios Natsis <natsisphysicist@gmail.com> */
-#' ---
-#' title:         "Enhancement of SDR in Thessaloniki "
-#' author:
-#'   - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisphysicist@gmail.com]
-#'   - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
-#' abstract:
-#'   "Study of GHI enchantment."
-#'
-#' documentclass:  article
-#' classoption:    a4paper,oneside
-#' fontsize:       10pt
-#' geometry:       "left=0.5in,right=0.5in,top=0.5in,bottom=0.5in"
-#' link-citations: yes
-#' colorlinks:     yes
-#'
-#' header-includes:
-#' - \usepackage{caption}
-#' - \usepackage{placeins}
-#' - \captionsetup{font=small}
-#'
-#' output:
-#'   bookdown::pdf_document2:
-#'     number_sections: no
-#'     fig_caption:     no
-#'     keep_tex:        yes
-#'     latex_engine:    xelatex
-#'     toc:             yes
-#'     toc_depth:       4
-#'     fig_width:       7
-#'     fig_height:      4.5
-#'   html_document:
-#'     toc:             true
-#'     keep_md:         yes
-#'     fig_width:       7
-#'     fig_height:      4.5
-#'
-#' date: "`r format(Sys.time(), '%F')`"
-#'
-#' ---
-
-#+ echo=F, include=T
-
-## __ Document options  --------------------------------------------------------
-
-#+ echo=FALSE, include=TRUE
-knitr::opts_chunk$set(comment    = ""       )
-knitr::opts_chunk$set(dev        = c("pdf", "png"))
-# knitr::opts_chunk$set(dev        = "png"    )
-knitr::opts_chunk$set(out.width  = "100%"   )
-knitr::opts_chunk$set(fig.align  = "center" )
-knitr::opts_chunk$set(cache      =  FALSE   )  ## !! breaks calculations
-# knitr::opts_chunk$set(fig.pos    = '!h'    )
-
-#+ echo=FALSE, include=TRUE
-## __ Set environment  ---------------------------------------------------------
-Sys.setenv(TZ = "UTC")
[…]

### 2024-08-27 Article_B11/Article_B11_plain.tex
Commit 2024-08-27 07:11

--- 2024-08-26 article/article.tex
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/P-example-years-13}
+{\centering \includegraphics[width=1\linewidth]{../images/P-example-years-12}
 
@@
 \caption{Example scatter plot of the measured GHI and the reference clear sky irradiance in Thessaloniki for the year 2005.
-The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.}\label{fig:example-year}
+The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.
+The reference green line goes through the origin with a slope of one.}\label{fig:example-year}
 \end{figure}

### 2024-08-27 Article_B11/Article_B11.Rmd
Commit 2024-08-27 07:11

--- 2024-08-26 article/article.Rmd
@@
 ```{r example-year, echo=FALSE, fig.cap="Example scatter plot of the measured GHI and the reference clear sky irradiance in Thessaloniki for the year 2005.
-The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.", fig.pos='H'}
-knitr::include_graphics("../images/P-example-years-13.png")
+The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.
+The reference green line goes through the origin with a slope of one.", fig.pos='H'}
+knitr::include_graphics("../images/P-example-years-12.png")
 ```

### 2024-08-27 article/article.Rmd
Commit 2024-08-27 10:14

@@
 $340\,\text{nm}$ derived from a collocated Brewer spectrophotometer [@Kazadzis2007]
-to calculate the trend in $\text{GHI}_\text{ref}$ due to aerosols during this period.
+to calculate the change in $\text{GHI}_\text{ref}$ due to aerosols during this period.
 
@@
 According to @Kazadzis2007, in the period 1997 -- 2005 the mean AOD at $340\,\text{nm}$
-is $0.403$ with a trend of $-3.8\pm0.93\,\%$ per year, corresponding to a change of
+is $0.403$ with a change of $-3.8\pm0.93\,\%$ per year, corresponding to a change of
 $0.0153$ per year.  Using an Ångström coefficient $\alpha = 1.6$, this translates to
@@
 (i.e. 2003) as a proxy, also taken from AERONET, and for a SZA of $55^\circ$ reveal a
-trend of
+change of
 $+0.21\,\%$ per year in $\text{GHI}_\text{ref}$. 
@@
 Simulations with uvspec for the above Ångström coefficients, assuming constant WC of
-$15.6\,\text{mm}$ taken from the Cimel, and for a SZA of $55^\circ$ reveal a trend of
+$15.6\,\text{mm}$ taken from the Cimel, and for a SZA of $55^\circ$ reveal a change of
 $+0.21\,\%$ per year in $\text{GHI}_\text{ref}$.  The SZA of $55^\circ$ was chosen as
@@
 a similar simulation scheme to calculate the monthly mean clear-sky irradiance,
-and finally the trend of $+0.14\,\%$ per year. We applied these two long-term changes
+and finally the change of $+0.14\,\%$ per year. We applied these two long-term changes
 (see Figure\nobreakspace{}\ref{fig:CS-change}) to the climatological

### 2024-08-27 article/article.tex
Commit 2024-08-27 06:14
Commit 2024-08-27 10:14

@@
 \(340\,\text{nm}\) derived from a collocated Brewer spectrophotometer
-\citep{Kazadzis2007} to calculate the trend in \(\text{GHI}_\text{ref}\)
-due to aerosols during this period.
+\citep{Kazadzis2007} to calculate the change in
+\(\text{GHI}_\text{ref}\) due to aerosols during this period.
 
 According to \citet{Kazadzis2007}, in the period 1997 -- 2005 the mean
-AOD at \(340\,\text{nm}\) is \(0.403\) with a trend of
+AOD at \(340\,\text{nm}\) is \(0.403\) with a change of
 \(-3.8\pm0.93\,\%\) per year, corresponding to a change of \(0.0153\)
@@
 assuming constant WC of \(15.6\,\text{mm}\) taken from the Cimel, and
-for a SZA of \(55^\circ\) reveal a trend of \(+0.21\,\%\) per year in
+for a SZA of \(55^\circ\) reveal a change of \(+0.21\,\%\) per year in
 \(\text{GHI}_\text{ref}\). The SZA of \(55^\circ\) was chosen as
@@
 in a similar simulation scheme to calculate the monthly mean clear-sky
-irradiance, and finally the trend of \(+0.14\,\%\) per year. We applied
+irradiance, and finally the change of \(+0.14\,\%\) per year. We applied
 these two long-term changes (see

### 2024-08-27 article/article.Rmd
Commit 2024-08-27 11:10

@@
 `r ST_G0[, max(GLB_diff.N)]` minutes occurred on
-`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")`.
+`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")` in a SZA range of 
+$`r round(ST_G0[which.max(GLB_diff.N), SZA.min],1)`^\circ$ -- 
+$`r round(ST_G0[which.max(GLB_diff.N), SZA.max],1)`^\circ$.
 Figure\nobreakspace{}\ref{fig:ceg-duration-distribution} shows the frequency
@@
 for ECE events is in spring and early summer (March -- June), followed by a
-period in late autumn (September and October).  This is probably related to the
+period in early autumn (September and October).  This is probably related to the
 weather characteristics in these periods, with frequent alternations between clear

### 2024-08-27 article/article.tex
Commit 2024-08-27 11:10

@@
 in the whole period of study, where the group of the longest duration of
-140 minutes occurred on 07~July 2013.
-Figure\nobreakspace{}\ref{fig:ceg-duration-distribution} shows the
-frequency distribution of the CE events according to their duration. We
-conclude that although some groups of events last for more than an hour,
-about \(80\,\%\) have duration of less than 5 minutes.
+140 minutes occurred on 07~July 2013 in a SZA range of \(52.1^\circ\) --
+\(77.9^\circ\). Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}
+shows the frequency distribution of the CE events according to their
+duration. We conclude that although some groups of events last for more
+than an hour, about \(80\,\%\) have duration of less than 5 minutes.
 
@@
 The most active period for ECE events is in spring and early summer
-(March -- June), followed by a period in late autumn (September and
+(March -- June), followed by a period in early autumn (September and
 October). This is probably related to the weather characteristics in

### 2024-08-27 GHI_enh_05_distributions.R
Commit 2024-08-27 12:14

@@ -494,8 +494,7 @@ quantile(DATA[wattGLB > ETH, GLB_diff])
 
 
 
-
-
+## stopre some date for max cases
 
 saveRDS(
   rbind(
@@ -504,6 +503,24 @@ saveRDS(
   ),
   "data/Max_cases.Rds"
 )
+
+
+
+
+
+## Test missing data  -------
+
+
+#+  echo=F, include=T, results="asis"
+
+length(seq.Date(min(DATA$Day), max(DATA$Day), by = "day")) - DATA[, length(unique(Day))]
+
+
+DATA[, sum(is.na(wattGLB))]
+
+
+
+
 
 
 

### 2024-08-28 GHI_enh_07_Aerosols.tex
Commit 2024-08-26 20:14
Commit 2024-08-27 12:14
Commit 2024-08-27 14:14
Commit 2024-08-28 08:14
Commit 2024-08-28 19:23
Commit 2024-08-28 21:11

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-08-23}
+\date{2024-08-28}
 
@@
 \begin{verbatim}
-Registered S3 methods overwritten by 'ggpp':
-  method                  from   
-  heightDetails.titleGrob ggplot2
-  widthDetails.titleGrob  ggplot2
-\end{verbatim}
 
-\begin{verbatim}
-Attaching package: 'ggpp'
-\end{verbatim}
-
-\begin{verbatim}
-The following object is masked from 'package:ggplot2':
-
-    annotate
-\end{verbatim}
-
-\begin{verbatim}
 Attaching package: 'zoo'
@@
   >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}@{}}
-\toprule
+\toprule\noalign{}
 \begin{minipage}[b]{\linewidth}\centering
@@
 \end{minipage} \\
-\midrule
+\midrule\noalign{}
 \endhead
+\bottomrule\noalign{}
+\endlastfoot
 -1102 & 0.8309 & 1 & 565.8 & SZA min & 2014 & 0.001469 \\
@@
 -785.3 & 0.6983 & 12 & 618.3 & SZA 55 & 2014 & 0.001129 \\
-\bottomrule
 \end{longtable}
@@
   >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1389}}@{}}
-\toprule
+\toprule\noalign{}
 \begin{minipage}[b]{\linewidth}\centering
@@
 \end{minipage} \\
-\midrule
+\midrule\noalign{}
 \endhead
+\bottomrule\noalign{}
+\endlastfoot
 1997 & BR SZA median & 449.5 \\
@@
 2023 & SZA median & 522.8 \\
-\bottomrule
 \end{longtable}
@@
 \end{minipage} \\
-\midrule
+\midrule\noalign{}
 \endhead
+\bottomrule\noalign{}
+\endlastfoot
 1997 & BR SZA min & 1055 \\
@@
 2023 & SZA min & 859.5 \\
-\bottomrule
 \end{longtable}
@@
 \end{minipage} \\
-\midrule
+\midrule\noalign{}
 \endhead
+\bottomrule\noalign{}
+\endlastfoot
 1997 & BR SZA mean & 497.3 \\
@@
 2023 & SZA mean & 490.7 \\
-\bottomrule
 \end{longtable}
@@
   >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1667}}@{}}
-\toprule
+\toprule\noalign{}
 \begin{minipage}[b]{\linewidth}\centering
@@
 \end{minipage} \\
-\midrule
+\midrule\noalign{}
 \endhead
+\bottomrule\noalign{}
+\endlastfoot
 1997 & BR SZA 55 & 578.9 \\
@@
 2023 & SZA 55 & 583 \\
-\bottomrule
 \end{longtable}

### 2024-08-28 GHI_enh_07_Aerosols_yearly.tex
Commit 2024-08-28 22:11

--- 2024-08-28 GHI_enh_07_Aerosols.tex
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-1}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-4-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-2}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-4-2}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-3}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-4-3}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-4}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-4-4}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-5}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-4-5}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-6}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-4-6}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-7}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-4-7}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-8}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-4-8}
 
@@
 \end{figure}
+
+{[}1{]} ``SZA 55'' ``BR SZA 55'' ``Year BR SZA 55''
+
 \begin{figure}[H]
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-9}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-9}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-10}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-10}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-11}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-11}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-12}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-12}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-13}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-13}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-14}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-14}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-15}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-15}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-16}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-16}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-1}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-5-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-2}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-5-2}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-3}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-5-3}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-4}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-5-4}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-5}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-5-5}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-6}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-5-6}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-7}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-5-7}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-8}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-5-8}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-9}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-5-9}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-10}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-5-10}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-11}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-5-11}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-12}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-5-12}
 
@@
 
-SZA min : 0.00137165912186399
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-13}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-13}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-14}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-14}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-15}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-15}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-16}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-16}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-17}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-17}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-18}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-18}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-19}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-19}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-20}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-20}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-21}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-21}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-22}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-22}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-23}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-23}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-24}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-24}
-\end{figure}
-
-SZA mean : 0.0020024477410843
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-25}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-25}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-26}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-26}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-27}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-27}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-28}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-28}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-29}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-29}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-30}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-30}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-31}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-31}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-32}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-32}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-33}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-33}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-34}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-34}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-35}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-35}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-36}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-36}
-\end{figure}
-
-SZA median : 0.00184853525463023
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-37}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-37}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-38}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-38}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-39}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-39}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-40}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-40}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-41}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-41}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-42}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-42}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-43}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-43}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-44}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-44}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-45}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-45}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-46}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-46}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-47}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-47}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-48}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-48}
-\end{figure}
-
 SZA 55 : 0.00139576531267693
@@
 \begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}
-  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1184}}
-  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1053}}
-  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1316}}
-  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1711}}
-  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}
-  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}@{}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1667}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1111}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1389}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1667}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1667}}@{}}
 \toprule\noalign{}
@@
 \endlastfoot
--1102 & 0.8309 & 1 & 565.8 & SZA min & 2014 & 0.001469 \\
--810.5 & 0.7648 & 2 & 721.8 & SZA min & 2015 & 0.00106 \\
--6892 & 3.872 & 3 & 888.2 & SZA min & 2015 & 0.00436 \\
--1277 & 1.124 & 4 & 974.5 & SZA min & 2015 & 0.001153 \\
--982.7 & 0.9904 & 5 & 1004 & SZA min & 2015 & 0.0009866 \\
-375.1 & 0.3116 & 6 & 993.2 & SZA min & 2015 & 0.0003138 \\
--140.7 & 0.5624 & 7 & 984 & SZA min & 2015 & 0.0005715 \\
-444.2 & 0.2576 & 8 & 967.6 & SZA min & 2015 & 0.0002663 \\
--3.347 & 0.4436 & 9 & 872.7 & SZA min & 2015 & 0.0005082 \\
--1081 & 0.9159 & 10 & 758.3 & SZA min & 2015 & 0.001208 \\
--2109 & 1.345 & 11 & 565.3 & SZA min & 2015 & 0.002379 \\
--1598 & 1.044 & 12 & 477.6 & SZA min & 2014 & 0.002186 \\
--1221 & 0.756 & 1 & 293.9 & SZA mean & 2014 & 0.002573 \\
--1063 & 0.7194 & 2 & 377.8 & SZA mean & 2015 & 0.001904 \\
--1776 & 1.125 & 3 & 485.6 & SZA mean & 2015 & 0.002317 \\
--1680 & 1.118 & 4 & 561.4 & SZA mean & 2015 & 0.001992 \\
--1628 & 1.111 & 5 & 599.9 & SZA mean & 2015 & 0.001852 \\
--262.2 & 0.4374 & 6 & 606.9 & SZA mean & 2015 & 0.0007207 \\
--745.5 & 0.6689 & 7 & 592.1 & SZA mean & 2015 & 0.00113 \\
--122.7 & 0.3402 & 8 & 566.4 & SZA mean & 2015 & 0.0006007 \\
--474.5 & 0.4816 & 9 & 477.8 & SZA mean & 2015 & 0.001008 \\
--1443 & 0.9151 & 10 & 394.4 & SZA mean & 2015 & 0.00232 \\
--2438 & 1.364 & 11 & 277.9 & SZA mean & 2015 & 0.004907 \\
--1179 & 0.7187 & 12 & 265.7 & SZA mean & 2014 & 0.002705 \\
--1216 & 0.772 & 1 & 331.6 & SZA median & 2014 & 0.002328 \\
--1041 & 0.7293 & 2 & 419.7 & SZA median & 2015 & 0.001738 \\
--1743 & 1.129 & 3 & 527.8 & SZA median & 2015 & 0.00214 \\
--1654 & 1.123 & 4 & 595.7 & SZA median & 2015 & 0.001884 \\
--1595 & 1.105 & 5 & 620.6 & SZA median & 2015 & 0.00178 \\
--243.2 & 0.4343 & 6 & 619.6 & SZA median & 2015 & 0.0007009 \\
--708.1 & 0.6584 & 7 & 608.4 & SZA median & 2015 & 0.001082 \\
--109.2 & 0.3477 & 8 & 595.2 & SZA median & 2015 & 0.0005842 \\
--441.5 & 0.4846 & 9 & 516.9 & SZA median & 2015 & 0.0009376 \\
--1433 & 0.9306 & 10 & 435.1 & SZA median & 2015 & 0.002139 \\
--2464 & 1.395 & 11 & 314.5 & SZA median & 2015 & 0.004436 \\
--1176 & 0.7354 & 12 & 302.4 & SZA median & 2014 & 0.002432 \\
 -847.8 & 0.7326 & 1 & 621.4 & SZA 55 & 2014 & 0.001179 \\
@@
 
+\newpage
+
 \begin{longtable}[]{@{}
   >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2222}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2361}}
   >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1389}}@{}}
@@
 \endlastfoot
-1997 & BR SZA median & 449.5 \\
-2005 & SZA median & 392.1 \\
-2005 & BR SZA median & 459.3 \\
-2006 & SZA median & 493.1 \\
-2007 & SZA median & 470.8 \\
-2008 & SZA median & 326.2 \\
-2011 & SZA median & 505.1 \\
-2012 & SZA median & 500.8 \\
-2013 & SZA median & 498.6 \\
-2014 & SZA median & 477.7 \\
-2015 & SZA median & 504.8 \\
-2016 & SZA median & 510.9 \\
-2017 & SZA median & 551.4 \\
-2018 & SZA median & 499.7 \\
-2019 & SZA median & 476 \\
-2020 & SZA median & 483.7 \\
-2021 & SZA median & 506 \\
-2022 & SZA median & 554.9 \\
-2023 & SZA median & 522.8 \\
-\end{longtable}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-49}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-49}
-\end{figure}
-
-\newpage
-
-\begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1806}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1389}}@{}}
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\centering
-year
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-typer
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-MeanGlo
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-1997 & BR SZA min & 1055 \\
-2005 & SZA min & 668.3 \\
-2005 & BR SZA min & 1064 \\
-2006 & SZA min & 817.1 \\
-2007 & SZA min & 785.1 \\
-2008 & SZA min & 557.2 \\
-2011 & SZA min & 831.1 \\
-2012 & SZA min & 824.3 \\
-2013 & SZA min & 814 \\
-2014 & SZA min & 822.1 \\
-2015 & SZA min & 828.6 \\
-2016 & SZA min & 832.3 \\
-2017 & SZA min & 899.3 \\
-2018 & SZA min & 822.3 \\
-2019 & SZA min & 789.7 \\
-2020 & SZA min & 820.3 \\
-2021 & SZA min & 829.7 \\
-2022 & SZA min & 902.4 \\
-2023 & SZA min & 859.5 \\
-\end{longtable}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-50}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-50}
-\end{figure}
-
-\newpage
-
-\begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1944}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1389}}@{}}
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\centering
-year
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-typer
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-MeanGlo
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-1997 & BR SZA mean & 497.3 \\
-2005 & SZA mean & 353.9 \\
-2005 & BR SZA mean & 507.1 \\
-2006 & SZA mean & 460.7 \\
-2007 & SZA mean & 434.8 \\
-2008 & SZA mean & 288.6 \\
-2011 & SZA mean & 476.1 \\
-2012 & SZA mean & 468.4 \\
-2013 & SZA mean & 468.5 \\
-2014 & SZA mean & 444.8 \\
-2015 & SZA mean & 472.3 \\
-2016 & SZA mean & 480.3 \\
-2017 & SZA mean & 520.9 \\
-2018 & SZA mean & 467.3 \\
-2019 & SZA mean & 440.6 \\
-2020 & SZA mean & 450.8 \\
-2021 & SZA mean & 473.5 \\
-2022 & SZA mean & 525.5 \\
-2023 & SZA mean & 490.7 \\
-\end{longtable}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-51}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-51}
-\end{figure}
-
-\newpage
-
-\begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1667}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1667}}@{}}
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\centering
-year
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-typer
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-MeanGlo
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-1997 & BR SZA 55 & 578.9 \\
+1997 & Year BR SZA 55 & 604.3 \\
+1998 & Year BR SZA 55 & 601.7 \\
+1999 & Year BR SZA 55 & 602.1 \\
+2000 & Year BR SZA 55 & 603.9 \\
+2001 & Year BR SZA 55 & 604.5 \\
+2002 & Year BR SZA 55 & 604.8 \\
+2003 & Year BR SZA 55 & 603.5 \\
+2004 & Year BR SZA 55 & 605 \\
 2005 & SZA 55 & 576.4 \\
-2005 & BR SZA 55 & 588.4 \\
+2005 & Year BR SZA 55 & 603.7 \\
 2006 & SZA 55 & 574.9 \\
+2006 & Year BR SZA 55 & 603.9 \\
 2007 & SZA 55 & 584.7 \\
+2007 & Year BR SZA 55 & 604.2 \\
 2008 & SZA 55 & 615 \\
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-52}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/unnamed-chunk-5-13}
 
@@
 
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-52}
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-13}
 \end{figure}
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/P-CS-change-1}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_yearly_files/figure-latex/P-CS-change-1}
 

### 2024-08-29 GHI_enh_05_distributions.R
Commit 2024-08-29 11:07

@@ -544,6 +544,47 @@ hist(COMPLETE_monthly[, Complete])
 
 
 
+monthly <- DATA[, .(Relative_enha_GLB = sum(Enhanc_C_4)/sum(!is.na(wattGLB)),
+                    Relative_enha_N   = sum(Enhanc_C_4)/.N),
+                by = .(year(Date), month(Date)) ]
+
+
+boxplot(monthly$Relative_enha_GLB ~ monthly$month)
+boxplot(monthly$Relative_enha_N ~ monthly$month)
+
+
+
+
+ggplot(monthly, aes(y = Relative_enha_GLB,
+                         x = factor(month,
+                                    levels = 1:12,
+                                    labels = month.abb[1:12]))) +
+  geom_boxplot(fill = varcol("GLB_diff"), outliers = FALSE) +
+  xlab("") +
+  ylab("CE relative to GLB") +
+  stat_summary(fun.y = mean, geom = "point", shape = 23, size = 3) +
+  theme(
+    panel.grid.major.x = element_blank(),
+    panel.grid.minor.x = element_blank()
+  )
+
+
+
+ggplot(monthly, aes(y = Relative_enha_N,
+                    x = factor(month,
+                               levels = 1:12,
+                               labels = month.abb[1:12]))) +
+  geom_boxplot(fill = varcol("GLB_diff"), outliers = FALSE) +
+  xlab("") +
+  ylab("CE relative to all minutes") +
+  stat_summary(fun.y = mean, geom = "point", shape = 23, size = 3) +
+  theme(
+    panel.grid.major.x = element_blank(),
+    panel.grid.minor.x = element_blank()
+  )
+
+
+
 
 #' **END**
 #+ include=T, echo=F

### 2024-08-29 GHI_enh_07_Aerosols_yearly.R

@@ -1044,7 +1044,7 @@ ggplot(dataset,
   ylab(bquote("Difference %" )) +
   xlab("Date") +
   annotate("text", x = 2000, y = dataset[year==2000, change],
-           label = "paste(\"+0.21 %/y\")", parse = TRUE,
+           label = "paste(\"+0.022 %/y\")", parse = TRUE,
            fontface = 2,
            size     = 5,
            hjust    = 1.1,

### 2024-08-29 article/article.Rmd
Commit 2024-08-29 18:14

@@
 \begin{equation}
-\text{ECE}: E > \cos(\theta) \cdot E_{\odot} \frac{r^2_\text{m}} {r^2}
+\text{ECE}: E > \cos(\text{SZA}) \cdot E_{\odot} \frac{r^2_\text{m}} {r^2}
 \label{eq:ECE}
 \end{equation}
-where: $\theta$ the solar zenith angle, $E_{\odot}$ the solar constant adjusted for
+where: $\text{SZA}$ the solar zenith angle, $E_{\odot}$ the solar constant adjusted for
 the actual Sun -- Earth distance $r$ and $r_\text{m}$ is the mean Sun -- Earth

### 2024-08-29 article/article.tex
Commit 2024-08-29 18:14

@@
 \begin{equation}
-\text{ECE}: E > \cos(\theta) \cdot E_{\odot} \frac{r^2_\text{m}} {r^2}
+\text{ECE}: E > \cos(\text{SZA}) \cdot E_{\odot} \frac{r^2_\text{m}} {r^2}
 \label{eq:ECE}
-\end{equation} where: \(\theta\) the solar zenith angle, \(E_{\odot}\)
-the solar constant adjusted for the actual Sun -- Earth distance \(r\)
-and \(r_\text{m}\) is the mean Sun -- Earth distance of
+\end{equation} where: \(\text{SZA}\) the solar zenith angle,
+\(E_{\odot}\) the solar constant adjusted for the actual Sun -- Earth
+distance \(r\) and \(r_\text{m}\) is the mean Sun -- Earth distance of
 \(1.496\times10^8\,\text{km}\).
@@
 entire dataset (\(6\) million of one-minute GHI measurements),
-\(1.78\,\%\) were identified as CE events and \(0.037\,\%\) as ECE
+\(1.78\,\%\) were identified as CE events and \(0.04\,\%\) as ECE
 events. The highest recorded GHI due to CE was
@@
 a OI of \(286.1\,\text{W}/\text{m}^2\). Both cases are ECE events with
-\(168.7\,\text{W}/\text{m}^2\) and \(155.4\,\text{W}/\text{m}^2\) above
+\(136.8\,\text{W}/\text{m}^2\) and \(164.5\,\text{W}/\text{m}^2\) above
 the TSI at TSI for the same SZA, respectively. In the following sections
@@
 increasing trends, most pronounced for the frequency of occurrence
-(\(+45.6\pm 21.9\,\text{cases}/\text{year}\)) and the excess irradiation
-(\(+116.9 \pm 67.8\,\text{kJ}/\text{year}\)), which are also
+(\(+45.6\pm 22\,\text{cases}/\text{year}\)) and the excess irradiation
+(\(+116.3 \pm 68.2\,\text{kJ}/\text{year}\)), which are also
 statistically significant. In contrast the trend of the yearly mean OI
@@
 of these consecutive events, we grouped them into bins of increasing
-duration in steps of one minute. We have identified 28062 groups of CE
+duration in steps of one minute. We have identified 28182 groups of CE
 in the whole period of study, where the group of the longest duration of
@@
 After analyzing the CE cases, we found an increase of
-\(+45.6\pm 21.9\,\text{cases}/\text{year}\), with the mean annual
+\(+45.6\pm 22\,\text{cases}/\text{year}\), with the mean annual
 irradiation of the CE events increasing with a rate of
-\(+116.9\pm 67.8\,\text{kJ}/\text{year}\). The most active months of CE
+\(+116.3\pm 68.2\,\text{kJ}/\text{year}\). The most active months of CE
 events are May and June. We found that continuous CE events can last up

### 2024-08-29 GHI_enh_05_distributions.R

@@ -494,7 +494,34 @@ quantile(DATA[wattGLB > ETH, GLB_diff])
 
 
 
-## stopre some date for max cases
+binwidth = 10
+ggplot(data = DATA[wattGLB > ETH], aes(x = wattGLB - ETH)) +
+  geom_histogram(aes(y = (after_stat(count))/sum(after_stat(count)) * 100),
+                 binwidth = binwidth,
+                 boundary = 0,
+                 fill = "lightblue",
+                 color    = "black") +
+  xlab(bquote("Irradiance above TSI for the same SZA" ~ group("[", W/m^2,"]"))) +
+  ylab("Relative frequency [%]") # +
+  # labs(caption = bquote(paste("Bin width: ", .(binwidth)) ~ group("[", W/m^2,"]"))) #  +
+# inset_element(p1, left = 0.4, bottom = 0.4, right = 1, top = 1,
+#               align_to = "plot")
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+##  Store some date for max cases  ------------------------
 
 saveRDS(
   rbind(
@@ -583,6 +610,45 @@ ggplot(monthly, aes(y = Relative_enha_N,
     panel.grid.minor.x = element_blank()
   )
 
+
+
+
+## Check days for reviers
+
+
+
+keep_ratio <- 0.6
+
+
+Keep <- DATA[, sum(!is.na(wattGLB))/.N > keep_ratio, by = .(Day = as.Date(Date))]
+
+Keep[V1 == F, .N]/Keep[V1 == T, .N]
+
+cat("Keeping", keep_ratio, "of each day, removes", Keep[V1 == F, .N], "days of", Keep[V1 == T, .N], "total days or", 100*Keep[V1 == F, .N]/Keep[V1 == T, .N],"%\n")
+
+
+## Doys with data
+Keep[, doy := yday(Day)]
+
+cnt_doy <- Keep[, sum(V1 == T), by = doy]
+
+cnt_missing_doy <- Keep[, sum(V1 == F), by = doy]
+
+
+plot(cnt_missing_doy$doy, cnt_missing_doy$V1)
+
+
+
+cnt_missing_doy[V1 == 0, ]
+
[…]

### 2024-08-29 GHI_enh_03_process.tex
Commit 2024-08-27 00:14
Commit 2024-08-27 14:14
Commit 2024-08-28 13:11
Commit 2024-08-28 19:23
Commit 2024-08-29 18:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-08-26}
+\date{2024-08-29}
 
@@
     Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
--72.8133 -27.4717   0.7634   0.4285  28.2424  83.4876 
+-72.8133 -27.4712   0.7647   0.4304  28.2448  83.4876 
 \end{verbatim}
@@
     Min      1Q  Median      3Q     Max 
--316.47 -148.10  -55.61  103.32  718.33
+-317.54 -148.95  -56.71  107.07  717.24
 
@@
                   Estimate Std. Error t value Pr(>|t|)   
-(Intercept)      1.520e+02  4.805e+01   3.164  0.00169 **
-as.numeric(Date) 1.205e-07  3.816e-08   3.157  0.00173 **
+(Intercept)      1.533e+02  4.805e+01   3.190  0.00155 **
+as.numeric(Date) 1.203e-07  3.816e-08   3.153  0.00175 **
 ---
@@
 Residual standard error: 197.8 on 354 degrees of freedom
-Multiple R-squared:  0.02738,   Adjusted R-squared:  0.02463 
-F-statistic: 9.966 on 1 and 354 DF,  p-value: 0.001732
+Multiple R-squared:  0.02732,   Adjusted R-squared:  0.02457 
+F-statistic: 9.943 on 1 and 354 DF,  p-value: 0.001752
 \end{verbatim}
@@
                    Estimate Std. Error t value Pr(>|t|)   
-(Intercept)       1.520e+02  4.805e+01   3.164  0.00169 **
-ST_E_monthly$Date 1.205e-07  3.816e-08   3.157  0.00173 **
+(Intercept)       1.533e+02  4.805e+01   3.190  0.00155 **
+ST_E_monthly$Date 1.203e-07  3.816e-08   3.153  0.00175 **
 ---
@@
 \begin{verbatim}
-2024-08-26 19:50:18.2 athan@sagan GHI_enh_03_process.R 3.387402 mins
+2024-08-29 10:26:26.0 athan@sagan GHI_enh_03_process.R 3.652528 mins
 \end{verbatim}

### 2024-08-29 GHI_enh_04_investigate.tex
Commit 2024-08-27 00:14
Commit 2024-08-27 14:14
Commit 2024-08-28 13:11
Commit 2024-08-28 19:23
Commit 2024-08-29 18:14

@@
 This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this
-warning was generated.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
 \end{verbatim}
@@
 \begin{verbatim}
-Warning: Removed 32 rows containing missing values or values outside the
-scale range (`geom_bar()`).
+Warning: Removed 32 rows containing missing values or values outside the scale
+range (`geom_bar()`).
 \end{verbatim}
@@
 \begin{verbatim}
-Warning: Removed 27787 rows containing non-finite outside the scale range
+Warning: Removed 27907 rows containing non-finite outside the scale range
 (`stat_bin()`).
@@
 \begin{verbatim}
-Warning: Removed 246 rows containing non-finite outside the scale range
-(`stat_bin()`).
-Removed 27787 rows containing non-finite outside the scale range
-(`stat_bin()`).
+Warning: Removed 246 rows containing non-finite outside the scale range (`stat_bin()`).
+Removed 27907 rows containing non-finite outside the scale range (`stat_bin()`).
 \end{verbatim}
@@
 \begin{verbatim}
-Warning: A numeric `legend.position` argument in `theme()` was deprecated in
-ggplot2 3.5.0.
-i Please use the `legend.position.inside` argument of `theme()`
-  instead.
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
+i Please use the `legend.position.inside` argument of `theme()` instead.
 This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this
-warning was generated.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
 \end{verbatim}
@@
 \begin{verbatim}
-Warning: The `fun.y` argument of `stat_summary()` is deprecated as of ggplot2
-3.3.0.
+Warning: The `fun.y` argument of `stat_summary()` is deprecated as of ggplot2 3.3.0.
 i Please use the `fun` argument instead.
 This warning is displayed once every 8 hours.
-Call `lifecycle::last_lifecycle_warnings()` to see where this
-warning was generated.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
 \end{verbatim}
@@
 
-lmY: 116.8672 +/- 33.89196
+lmY: 116.2574 +/- 34.09971
 
@@
 
-lmY: 45.58799 +/- 10.96835
+lmY: 45.56418 +/- 10.97738
 
@@
 
-lmY: 0.029427 +/- 0.054286
+lmY: 0.025809 +/- 0.054193
 
@@
 
-lmY: 0.03518 +/- 0.042507
+lmY: 0.034753 +/- 0.043154
 
@@
 
-lmY: 116.3147 +/- 30.85223
+lmY: 115.7198 +/- 31.03115
 
@@
 
-lmY: 45.55073 +/- 10.16657
+lmY: 45.48822 +/- 10.14071
 
@@
 \begin{verbatim}
-2024-08-26 19:52:09.6 athan@sagan GHI_enh_04_investigate.R 0.838254 mins
+2024-08-29 10:27:28.5 athan@sagan GHI_enh_04_investigate.R 0.869041 mins
 \end{verbatim}

### 2024-08-29 article/article.Rmd
Commit 2024-08-29 20:14

@@
 \end{equation}
-where: $\text{SZA}$ the solar zenith angle, $E_{\odot}$ the solar constant adjusted for
-the actual Sun -- Earth distance $r$ and $r_\text{m}$ is the mean Sun -- Earth
-distance of $1.496\times10^8\,\text{km}$.
+where: $\text{SZA}$ the solar zenith angle, $E_{\odot}$ is the solar constant at the
+mean Sun - Earth distance ($`r round(solar_constant)`\,\text{W}/\text{m}^2$), $r$ is
+the actual Sun - Earth distance and $r_\text{m}$ is the mean Sun -- Earth distance of
+$1.496\times10^8\,\text{km}$.
 
@@
 In contrast the trend of the yearly mean OI is negligible 
-($`r plus_sign(round(yearlyCE[var == "GLB_diff.mean", slope], 1))`\pm `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\text{W}/\text{m}^2/\text{year}$)
+($`r plus_sign(round(yearlyCE[var == "GLB_diff.mean", slope], 2))`\pm `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\text{W}/\text{m}^2/\text{year}$)
 and of no statistical significance.
@@
 
-```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE events in Thessaloniki for the period 1993 -- 2023."}
-knitr::include_graphics("../images/P-extreme-distribution-1.png")
+```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE events in Thessaloniki for the period 1993 -- 2023. Measured as extra irradiance over TSI at TOA for the same SZA."}
+knitr::include_graphics("../images/P-extreme-distribution-2.png")
 ```
+
+<!-- ```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE events in Thessaloniki for the period 1993 -- 2023."} -->
+<!-- knitr::include_graphics("../images/P-extreme-distribution-1.png") -->
+<!-- ``` -->
 

### 2024-08-29 article/article.tex
Commit 2024-08-29 20:14

@@
 \end{equation} where: \(\text{SZA}\) the solar zenith angle,
-\(E_{\odot}\) the solar constant adjusted for the actual Sun -- Earth
-distance \(r\) and \(r_\text{m}\) is the mean Sun -- Earth distance of
+\(E_{\odot}\) is the solar constant at the mean Sun - Earth distance
+(\(1361\,\text{W}/\text{m}^2\)), \(r\) is the actual Sun - Earth
+distance and \(r_\text{m}\) is the mean Sun -- Earth distance of
 \(1.496\times10^8\,\text{km}\).
@@
 statistically significant. In contrast the trend of the yearly mean OI
-is negligible (\(+0\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of no
-statistical significance. The average OI for the entire period is
+is negligible (\(+0.03\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of
+no statistical significance. The average OI for the entire period is
 \(+40.1\pm 2.5\,\text{W}/\text{m}^2\). The interannual variability of
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/P-extreme-distribution-1}
+{\centering \includegraphics[width=1\linewidth]{../images/P-extreme-distribution-2}
 
@@
 
-\caption{Distribution of ECE events in Thessaloniki for the period 1993 -- 2023.}\label{fig:P-extreme-distribution}
+\caption{Distribution of ECE events in Thessaloniki for the period 1993 -- 2023. Measured as extra irradiance over TSI at TOA for the same SZA.}\label{fig:P-extreme-distribution}
 \end{figure}

### 2024-08-29 GHI_enh_05_distributions.R
Commit 2024-08-29 22:14

@@ -631,7 +631,7 @@ ggplot(monthlyE, aes(y = Relative_enha_GLB,
                          x = factor(month,
                                     levels = 1:12,
                                     labels = month.abb[1:12]))) +
-  geom_boxplot(fill = varcol("GLB_diff"), outliers = FALSE) +
+  geom_boxplot(fill = "lightblue", outliers = FALSE) +
   xlab("") +
   ylab("CE relative to GLB") +
   stat_summary(fun.y = mean, geom = "point", shape = 23, size = 3) +
@@ -646,7 +646,7 @@ ggplot(monthlyE, aes(y = Relative_enha_N,
                     x = factor(month,
                                levels = 1:12,
                                labels = month.abb[1:12]))) +
-  geom_boxplot(fill = varcol("GLB_diff"), outliers = FALSE) +
+  geom_boxplot(fill = "lightblue", outliers = FALSE) +
   xlab("") +
   ylab("CE relative to all minutes") +
   stat_summary(fun.y = mean, geom = "point", shape = 23, size = 3) +
@@ -665,10 +665,7 @@ ggplot(monthlyE, aes(y = Relative_enha_N,
 
 keep_ratio <- 0.6
 
-
 Keep <- DATA[, sum(!is.na(wattGLB))/.N > keep_ratio, by = .(Day = as.Date(Date))]
-
-Keep[V1 == F, .N]/Keep[V1 == T, .N]
 
 cat("Keeping", keep_ratio, "of each day, removes", Keep[V1 == F, .N], "days of", Keep[V1 == T, .N], "total days or", 100*Keep[V1 == F, .N]/Keep[V1 == T, .N],"%\n")
 
@@ -680,18 +677,15 @@ cnt_doy <- Keep[, sum(V1 == T), by = doy]
 
 cnt_missing_doy <- Keep[, sum(V1 == F), by = doy]
 
-
 plot(cnt_missing_doy$doy, cnt_missing_doy$V1)
-
-
-
-cnt_missing_doy[V1 == 0, ]
 
 pander(cnt_missing_doy[V1 == 0, ], caption = paste("There are", nrow(cnt_missing_doy[V1 == 0, ]), "doys with all days no missing more than", 100*keep_ratio, "% data"))
 
 
 
 
+cat("Solar constant at 1au from NOAA TSI for the same data:",
+    mean(DATA$tsi_1au_comb, na.rm = T), "\n\n")
 
[…]

### 2024-08-31 GHI_enh_read_aod_brewer.tex
Commit 2024-08-31 12:14

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  a4paper,oneside]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{float}
\usepackage{placeins}
\captionsetup{font=small}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Enhancement of SDR in Thessaloniki},
  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-08-31}

\begin{document}
\maketitle
\begin{abstract}
Study of GHI enchantment.
\end{abstract}

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
dinfo
στήλες: Year, DOY, cloudiness flag (0: no clouds), total ozone flag (1: measured, 3: climatological)

daod
AOD at wavelengths 290 - 363 nm with a step of 0.5 nm (each row corresponds to a row from dinfo)

dmin
Minute corresponding to each AOD values

dsza
SZA corresponding to each AOD values

dqflg
Εδώ έχω ένα quality flag που έβγαλα από το schic και τελικά δε χρησιμοποίησα

\begin{verbatim}
Ignore time of day
\end{verbatim}

\begin{verbatim}
Ignore SZA
\end{verbatim}

\begin{verbatim}
Drop empy columns
\end{verbatim}

\begin{verbatim}
Ignore negative AOD
\end{verbatim}

\begin{verbatim}
Ignore infinite AOD
\end{verbatim}

\begin{verbatim}
Drop 1997
\end{verbatim}

\begin{verbatim}
AOD_292 
      1 
\end{verbatim}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-1}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-1}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-2}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-2}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-3}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-3}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-4}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-4}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-5}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-5}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-6}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-6}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-7}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-7}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-8}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-8}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-9}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-9}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-10}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-10}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-11}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-11}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-12}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-12}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-13}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-13}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-14}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-14}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-15}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-15}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-16}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-16}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-17}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-17}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-18}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-18}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-19}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-19}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-20}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-20}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-21}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-21}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-22}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-22}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-23}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-23}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-24}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-24}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-25}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-25}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-26}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-26}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-27}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-27}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-28}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-28}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-29}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-29}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-30}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-30}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-31}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-31}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-32}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-32}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-33}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-33}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-34}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-34}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-35}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-35}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-36}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-36}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-37}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-37}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-38}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-38}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-39}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-39}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-40}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-40}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-41}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-41}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-42}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-42}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-43}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-43}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-44}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-44}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-45}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-45}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-46}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-46}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-47}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-47}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-48}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-48}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-49}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-49}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-50}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-50}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-51}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-51}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-52}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-52}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-53}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-53}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-54}

}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4-54}
\end{figure}

\textbf{END}

\end{document}

### 2024-08-31 article/article.Rmd
Commit 2024-08-31 12:14

@@
 ---
-title: Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece
+title: Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece
 
@@
 
-<!-- # Abstract {.unnumbered} -->
+# Abstract {.unnumbered}
 
-<!--
+**Abstract temporary placed here for technical reasons**
+
 We studied the enhancement of the global horizontal irradiance induced by clouds over
@@
 found a trend in CE events of
-$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$,
+$`r round(yearlyCE[var == "GLB_diff.N", slope], 0)`\pm
+`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd],0)`\,\text{cases}/\text{year}$,
 and a trend in the CE events irradiation of 
@@
 spring until early summer and autumn.
--->
 
@@
 frequency of occurrence 
-($`r plus_sign(round(yearlyCE[var == "GLB_diff.N", slope], 1))`\pm `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$)
+($`r plus_sign(round(yearlyCE[var == "GLB_diff.N", slope], 0))`\pm `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 0)`\,\text{cases}/\text{year}$)
 and the excess irradiation 

### 2024-08-31 article/article.tex
Commit 2024-08-31 12:14

@@
             pdfauthor={},
-            pdftitle={Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece},
+            pdftitle={Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece},
             colorlinks=false,
@@
 
-  \title{Long-term cloud enhancement events of global solar irradiance
-over Thessaloniki, Greece}
+  \title{Analysis of cloud enhancement events in a 30-year record of
+global solar irradiance at Thessaloniki, Greece}
     \author[LAP]{Athanasios N. Natsis%
@@
  \end{frontmatter}
+
+\hypertarget{abstract}{%
+\section*{Abstract}\label{abstract}}
+\addcontentsline{toc}{section}{Abstract}
+
+\textbf{Abstract temporary placed here for technical reasons}
+
+We studied the enhancement of the global horizontal irradiance induced
+by clouds over Thessaloniki for the period 1993 -- 2023 using data
+recorded every one minute. We identified the cloud enhancement events
+(CE) by creating an appropriate clear sky irradiance reference with the
+use of a radiative transfer model and aerosol optical depth data from a
+collocated Cimel sun photometer and a Brewer spectrophotometer. We found
+a trend in CE events of \(46\pm 22\,\text{cases}/\text{year}\), and a
+trend in the CE events irradiation of
+\(116.3\pm 68.2\,\text{kJ}/\text{year}\). The peak of the CE events was
+observed during May and June. An analysis of the total duration of CE
+events, showed that durations longer than 5 minutes are very rare, with
+exceptions lasting over an hour and up to 140 minutes. Finally, we have
+detected enhancements above the total solar irradiance at the top of the
+atmosphere for the same solar zenith angle of up to
+\(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the cases below
+\(200\,\text{W}/\text{m}^{2}\). The most active season of these extreme
+events is spring until early summer and autumn.
 
@@
 increasing trends, most pronounced for the frequency of occurrence
-(\(+45.6\pm 22\,\text{cases}/\text{year}\)) and the excess irradiation
+(\(+46\pm 22\,\text{cases}/\text{year}\)) and the excess irradiation
 (\(+116.3 \pm 68.2\,\text{kJ}/\text{year}\)), which are also

### 2024-08-31 article/article.Rmd
Commit 2024-08-31 13:12

@@
   In this study we investigate the characteristics of global horizontal irradiance
-  enhancement events induced by clouds over Thessaloniki for the period 1993 -- 2023
+  enhancement events induced by clouds over Thessaloniki for the period 1994 -- 2023
   using data recorded every one minute. We identified the cloud enhancement (CE)
@@
 We studied the enhancement of the global horizontal irradiance induced by clouds over
-Thessaloniki for the period 1993 -- 2023 using data recorded every one minute.  We
+Thessaloniki for the period 1994 -- 2023 using data recorded every one minute.  We
 identified the cloud enhancement events (CE) by creating an appropriate clear sky
@@
 found a trend in CE events of
-$`r round(yearlyCE[var == "GLB_diff.N", slope], 0)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd],0)`\,\text{cases}/\text{year}$,
+$`r plus_sign(round(yearlyCE[var=="GLB_diff.N",slope],0))`\pm
+`r round(2*yearlyCE[var=="GLB_diff.N",slope.sd],0)`\,\text{cases}/\text{year}$,
 and a trend in the CE events irradiation of 
-$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
-`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$.
+$`r plus_sign(round(yearlyCE[var=="GLB_diff.sum",slope],1))`\pm
+`r round(2*yearlyCE[var=="GLB_diff.sum",slope.sd],1)`\,\text{kJ}/\text{year}$.
 The peak of the CE events was observed during May and June.  An analysis of the total
@@
 -->
+An overview of the data analyzed for the study of the CE and ECE events is given in
+Figure\nobreakspace{}\ref{fig:CLB-daily}, as the daily mean of the measured GHI.
+
+```{r CLB-daily, echo=FALSE, fig.cap="Daily mean values of GHI in Thessaloniki for the period 1994 -- 2023."}
+knitr::include_graphics("../images/P_daily_trend-3.png")
+```
 
@@
 with the RTM based on the long-term variations of the AOD. As AERONET data start only
-in 2003, we used for the period 1993 -- 2005 estimates of changes in AOD at
+in 2003, we used for the period 1994 -- 2005 estimates of changes in AOD at
 $340\,\text{nm}$ derived from a collocated Brewer spectrophotometer [@Kazadzis2007]
@@
 
-```{r CS-change, echo=FALSE, fig.cap="Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1993 -- 2023."}
-knitr::include_graphics("../images/P-CS-change-1.pdf")
+```{r CS-change, echo=FALSE, fig.cap="Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1994 -- 2023."}
+knitr::include_graphics("../images/P-CS-change-1.png")
 ```
@@
 CE cases (each with duration of one minute), the yearly mean OI and the yearly
-excess irradiation for the period 1993 -- 2023, together with corresponding linear
+excess irradiation for the period 1994 -- 2023, together with corresponding linear
 trends. All three quantities show increasing trends, most pronounced for the
@@
         }
-    \caption{Time series for the period 1993 -- 2023 of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation.
+    \caption{Time series for the period 1994 -- 2023 of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation.
 The black lines represent the linear trends on the yearly data.}\label{fig:P-energy}
@@
 
-```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal variability of the number of CE events in Thessaloniki for the period 1993 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot.
+```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal variability of the number of CE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot.
 The monthly values have also been normalized to the relative abundance of valid GHI observations.
@@
 
-```{r ovir-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE events in Thessaloniki for the period 1993 -- 2023 as a function of OI.
+```{r ovir-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE events in Thessaloniki for the period 1994 -- 2023 as a function of OI.
 The histogram was split in two plots with different y-axis scales for better readability."}
@@
 
-```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023.
+```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1994 -- 2023.
 The histogram was split in two plots with different y-axis scales for better readability."}
@@
 
-```{r group-2d, echo=FALSE, fig.cap="Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1993 -- 2023.
+```{r group-2d, echo=FALSE, fig.cap="Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1994 -- 2023.
 The logarithmic color scale denotes the frequency of the respective groups of events."}
@@
 
-```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal variability of the number of ECE events in Thessaloniki for the period 1993 -- 2023 normalized to the maximum occurring in March, in the form of a box and whisker plot.
+```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal variability of the number of ECE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in March, in the form of a box and whisker plot.
 The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles.
@@
 
-```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE events in Thessaloniki for the period 1993 -- 2023. Measured as extra irradiance over TSI at TOA for the same SZA."}
+```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE events in Thessaloniki for the period 1994 -- 2023. Measured as extra irradiance over TSI at TOA for the same SZA."}
 knitr::include_graphics("../images/P-extreme-distribution-2.png")
@@
 
-<!-- ```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE events in Thessaloniki for the period 1993 -- 2023."} -->
+<!-- ```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE events in Thessaloniki for the period 1994 -- 2023."} -->
 <!-- knitr::include_graphics("../images/P-extreme-distribution-1.png") -->
@@
 variability of the expected clear sky GHI, we were able to identify cases of CE
-events in Thessaloniki for the period 1993 -- 2023.  After analyzing the CE cases, we
+events in Thessaloniki for the period 1994 -- 2023.  After analyzing the CE cases, we
 found an increase of

### 2024-08-31 article/article.tex
Commit 2024-08-31 13:12

@@
   irradiance enhancement events induced by clouds over Thessaloniki for
-  the period 1993 -- 2023 using data recorded every one minute. We
+  the period 1994 -- 2023 using data recorded every one minute. We
   identified the cloud enhancement (CE) events by creating an
@@
 We studied the enhancement of the global horizontal irradiance induced
-by clouds over Thessaloniki for the period 1993 -- 2023 using data
+by clouds over Thessaloniki for the period 1994 -- 2023 using data
 recorded every one minute. We identified the cloud enhancement events
@@
 collocated Cimel sun photometer and a Brewer spectrophotometer. We found
-a trend in CE events of \(46\pm 22\,\text{cases}/\text{year}\), and a
+a trend in CE events of \(+46\pm 22\,\text{cases}/\text{year}\), and a
 trend in the CE events irradiation of
-\(116.3\pm 68.2\,\text{kJ}/\text{year}\). The peak of the CE events was
+\(+116.3\pm 68.2\,\text{kJ}/\text{year}\). The peak of the CE events was
 observed during May and June. An analysis of the total duration of CE
@@
 have been used in the manual inspection of the CE identification. The
-sky camera operates since 2012 and stores images in 5 min time steps.
+sky camera operates since 2012 and stores images in 5 min time steps. An
+overview of the data analyzed for the study of the CE and ECE events is
+given in Figure\nobreakspace{}\ref{fig:CLB-daily}, as the daily mean of
+the measured GHI.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../images/P_daily_trend-3}
+
+}
+
+\caption{Daily mean values of GHI in Thessaloniki for the period 1994 -- 2023.}\label{fig:CLB-daily}
+\end{figure}
 
@@
 variations of the AOD. As AERONET data start only in 2003, we used for
-the period 1993 -- 2005 estimates of changes in AOD at
+the period 1994 -- 2005 estimates of changes in AOD at
 \(340\,\text{nm}\) derived from a collocated Brewer spectrophotometer
@@
 
-\caption{Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1993 -- 2023.}\label{fig:CS-change}
+\caption{Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1994 -- 2023.}\label{fig:CS-change}
 \end{figure}
@@
 yearly number of CE cases (each with duration of one minute), the yearly
-mean OI and the yearly excess irradiation for the period 1993 -- 2023,
+mean OI and the yearly excess irradiation for the period 1994 -- 2023,
 together with corresponding linear trends. All three quantities show
@@
 
-\caption{Seasonal variability of the number of CE events in Thessaloniki for the period 1993 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot.
+\caption{Seasonal variability of the number of CE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot.
 The monthly values have also been normalized to the relative abundance of valid GHI observations.
@@
 
-\caption{Relative frequency distribution of CE events in Thessaloniki for the period 1993 -- 2023 as a function of OI.
+\caption{Relative frequency distribution of CE events in Thessaloniki for the period 1994 -- 2023 as a function of OI.
 The histogram was split in two plots with different y-axis scales for better readability.}\label{fig:ovir-distribution}
@@
 
-\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023.
+\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1994 -- 2023.
 The histogram was split in two plots with different y-axis scales for better readability.}\label{fig:ceg-duration-distribution}
@@
 
-\caption{Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1993 -- 2023.
+\caption{Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1994 -- 2023.
 The logarithmic color scale denotes the frequency of the respective groups of events.}\label{fig:group-2d}
@@
 
-\caption{Seasonal variability of the number of ECE events in Thessaloniki for the period 1993 -- 2023 normalized to the maximum occurring in March, in the form of a box and whisker plot.
+\caption{Seasonal variability of the number of ECE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in March, in the form of a box and whisker plot.
 The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles.
@@
 
-\caption{Distribution of ECE events in Thessaloniki for the period 1993 -- 2023. Measured as extra irradiance over TSI at TOA for the same SZA.}\label{fig:P-extreme-distribution}
+\caption{Distribution of ECE events in Thessaloniki for the period 1994 -- 2023. Measured as extra irradiance over TSI at TOA for the same SZA.}\label{fig:P-extreme-distribution}
 \end{figure}
@@
 short-term variability of the expected clear sky GHI, we were able to
-identify cases of CE events in Thessaloniki for the period 1993 -- 2023.
+identify cases of CE events in Thessaloniki for the period 1994 -- 2023.
 After analyzing the CE cases, we found an increase of

### 2024-08-31 article/article.Rmd
Commit 2024-08-31 14:11

@@
 
-```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal variability of the number of CE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot.
+```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal variability of the number of CE events relative to the corresponding number of GHI measurements in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot.
+The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles, the thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
+The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
+knitr::include_graphics("../images/P-CE-climatology-normlz-1.png")
+```
+
+<!--
+```{r relative-month-occurrence, echo=FALSE, fig.cap="Seasonal variability of the number of CE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot.
 The monthly values have also been normalized to the relative abundance of valid GHI observations.
@@
 ```
+-->
 
@@
 
-```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal variability of the number of ECE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in March, in the form of a box and whisker plot.
+```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal variability of the number of ECE events relative to the the corresponding number of GHI measurements in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot.
+The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles.
+The thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
+The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
+knitr::include_graphics("../images/P-ECE-climatology-normlz-1.png")
+```
+
+<!--
+```{r relative-month-occurancies-ECEs, echo=FALSE, fig.cap="Seasonal variability of the number of ECE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in March, in the form of a box and whisker plot.
 The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles.

### 2024-08-31 article/article.tex
Commit 2024-08-31 14:11

@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/clim-CE-month-norm-MAX-median-N-MW-1}
+{\centering \includegraphics[width=1\linewidth]{../images/P-CE-climatology-normlz-1}
 
@@
 
-\caption{Seasonal variability of the number of CE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in June, in the form of a box and whisker plot.
-The monthly values have also been normalized to the relative abundance of valid GHI observations.
+\caption{Seasonal variability of the number of CE events relative to the corresponding number of GHI measurements in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot.
 The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles, the thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/clim-ECE-month-norm-MAX-median-N-2}
+{\centering \includegraphics[width=1\linewidth]{../images/P-ECE-climatology-normlz-1}
 
@@
 
-\caption{Seasonal variability of the number of ECE events in Thessaloniki for the period 1994 -- 2023 normalized to the maximum occurring in March, in the form of a box and whisker plot.
+\caption{Seasonal variability of the number of ECE events relative to the the corresponding number of GHI measurements in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot.
 The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles.

### 2024-08-31 GHI_enh_05_distributions.R
Commit 2024-08-31 15:11

@@ -721,12 +721,8 @@ for (ay in unique(year(LUK$Date))) {
 pander(solstis, caption = "Solstices from Libratran")
 
 
-cat("Max for all period", max(solstis$Enerhy_Kj/1000, na.rm = T), "MJ", "\n\n")
-cat("Meas for all period", mean(solstis$Enerhy_Kj/1000, na.rm = T), "MJ", "\n\n")
-
-
-
-source("./GHI_enh_00_variables.R")
+cat("Solstice max for all period", max(solstis$Enerhy_Kj/1000, na.rm = T), "MJ", "\n\n")
+cat("Solstice mean for all period", mean(solstis$Enerhy_Kj/1000, na.rm = T), "MJ", "\n\n")
 
 
 

### 2024-09-01 GHI_enh_read_aod_brewer.tex
Commit 2024-09-01 13:10

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-08-31}
+\date{2024-09-01}
 
@@
 \begin{verbatim}
-Drop empy columns
+Drop empty columns
 \end{verbatim}
@@
 \begin{verbatim}
-Drop 1997
+Drop year 1997
 \end{verbatim}
@@
 \begin{verbatim}
-AOD_292 
-      1 
+Max N data for 1 
 \end{verbatim}
@@
 
+\begin{longtable}[]{@{}
+  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1806}}
+  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1806}}@{}}
+\caption{AOD change \%/y}\tabularnewline
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\centering
+slope\_pCpY
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+AOD
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\centering
+slope\_pCpY
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+AOD
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+0.2558 & AOD\_292 \\
+0.0385 & AOD\_292.5 \\
+0.04534 & AOD\_293 \\
+0.06775 & AOD\_293.5 \\
+0.05734 & AOD\_294 \\
+0.0763 & AOD\_294.5 \\
+0.0831 & AOD\_295 \\
+0.08266 & AOD\_295.5 \\
+0.1019 & AOD\_296 \\
+0.09853 & AOD\_296.5 \\
+0.09384 & AOD\_297 \\
+0.08095 & AOD\_297.5 \\
+0.09393 & AOD\_298 \\
+0.08817 & AOD\_298.5 \\
+0.0804 & AOD\_299 \\
+0.07093 & AOD\_299.5 \\
+0.06308 & AOD\_300 \\
+0.05071 & AOD\_300.5 \\
+0.05359 & AOD\_301 \\
+0.04396 & AOD\_301.5 \\
+0.03347 & AOD\_302 \\
+0.02571 & AOD\_302.5 \\
+0.02131 & AOD\_303 \\
+0.01803 & AOD\_303.5 \\
+0.01171 & AOD\_304 \\
+0.01022 & AOD\_304.5 \\
+0.005416 & AOD\_305 \\
+0.0005074 & AOD\_305.5 \\
+0.002836 & AOD\_306 \\
+0.0001914 & AOD\_306.5 \\
+0.001028 & AOD\_307 \\
+0.0002915 & AOD\_307.5 \\
+0.01176 & AOD\_308 \\
+0.02345 & AOD\_308.5 \\
+0.02512 & AOD\_309 \\
+0.02872 & AOD\_309.5 \\
+0.03807 & AOD\_310 \\
+0.04033 & AOD\_310.5 \\
+0.04404 & AOD\_311 \\
+0.04732 & AOD\_311.5 \\
+0.04988 & AOD\_312 \\
+0.05461 & AOD\_312.5 \\
+0.05661 & AOD\_313 \\
+0.06141 & AOD\_313.5 \\
+0.05901 & AOD\_314 \\
+0.05361 & AOD\_314.5 \\
+0.0447 & AOD\_315 \\
+0.03122 & AOD\_315.5 \\
+0.02879 & AOD\_316 \\
+0.02784 & AOD\_316.5 \\
+0.02667 & AOD\_317 \\
+0.02556 & AOD\_317.5 \\
+0.02617 & AOD\_318 \\
+0.02414 & AOD\_318.5 \\
+0.01576 & AOD\_319 \\
+0.007456 & AOD\_319.5 \\
+0.002617 & AOD\_320 \\
+0.00727 & AOD\_320.5 \\
+0.0097 & AOD\_321 \\
+0.01868 & AOD\_321.5 \\
+0.02508 & AOD\_322 \\
+0.02554 & AOD\_322.5 \\
+0.02652 & AOD\_323 \\
+0.02711 & AOD\_323.5 \\
+0.03271 & AOD\_324 \\
+0.03674 & AOD\_324.5 \\
+0.03564 & AOD\_325 \\
+0.04207 & AOD\_325.5 \\
+0.04356 & AOD\_326 \\
+0.04334 & AOD\_326.5 \\
+0.04177 & AOD\_327 \\
+0.04679 & AOD\_327.5 \\
+0.04267 & AOD\_328 \\
+0.03719 & AOD\_328.5 \\
+0.03491 & AOD\_329 \\
+0.03328 & AOD\_329.5 \\
+0.03067 & AOD\_330 \\
+0.03602 & AOD\_330.5 \\
+0.03564 & AOD\_331 \\
+0.03208 & AOD\_331.5 \\
+0.02064 & AOD\_332 \\
+0.01897 & AOD\_332.5 \\
+0.02294 & AOD\_333 \\
+0.02197 & AOD\_333.5 \\
+0.02225 & AOD\_334 \\
+0.02282 & AOD\_334.5 \\
+0.02284 & AOD\_335 \\
+0.02381 & AOD\_335.5 \\
+0.02606 & AOD\_336 \\
+0.02517 & AOD\_336.5 \\
+0.02722 & AOD\_337 \\
+0.02877 & AOD\_337.5 \\
+0.03161 & AOD\_338 \\
+0.03294 & AOD\_338.5 \\
+0.03393 & AOD\_339 \\
+0.03063 & AOD\_339.5 \\
+0.02624 & AOD\_340 \\
+0.02005 & AOD\_340.5 \\
+0.02407 & AOD\_341 \\
+0.02232 & AOD\_341.5 \\
+0.02444 & AOD\_342 \\
+0.02502 & AOD\_342.5 \\
+0.02645 & AOD\_343 \\
+0.0247 & AOD\_343.5 \\
+0.02531 & AOD\_344 \\
+0.02526 & AOD\_344.5 \\
+0.02374 & AOD\_345 \\
+0.02159 & AOD\_345.5 \\
+0.02034 & AOD\_346 \\
+0.02048 & AOD\_346.5 \\
+0.01923 & AOD\_347 \\
+0.01956 & AOD\_347.5 \\
+0.0214 & AOD\_348 \\
+0.01945 & AOD\_348.5 \\
+0.01227 & AOD\_349 \\
+0.01165 & AOD\_349.5 \\
+0.01124 & AOD\_350 \\
+0.009548 & AOD\_350.5 \\
+0.008288 & AOD\_351 \\
+0.006796 & AOD\_351.5 \\
+0.004561 & AOD\_352 \\
+0.004843 & AOD\_352.5 \\
+0.003653 & AOD\_353 \\
+0.0007953 & AOD\_353.5 \\
+0.001056 & AOD\_354 \\
+0.004497 & AOD\_354.5 \\
+0.003201 & AOD\_355 \\
+0.009072 & AOD\_355.5 \\
+0.00913 & AOD\_356 \\
+0.00913 & AOD\_356.5 \\
+0.009986 & AOD\_357 \\
+0.01327 & AOD\_357.5 \\
+0.01149 & AOD\_358 \\
+0.008446 & AOD\_358.5 \\
+0.004012 & AOD\_359 \\
+0.00145 & AOD\_359.5 \\
+0.001221 & AOD\_360 \\
+0.00208 & AOD\_360.5 \\
+0.003965 & AOD\_361 \\
+0.01953 & AOD\_361.5 \\
+0.06372 & AOD\_362 \\
+0.066 & AOD\_362.5 \\
+0.05968 & AOD\_363 \\
+\end{longtable}
+
 \textbf{END}

### 2024-09-02 article/article.Rmd
Commit 2024-09-02 09:09

@@
 #     text: "Another author footnote."
-abstract: |
-  In this study we investigate the characteristics of global horizontal irradiance
-  enhancement events induced by clouds over Thessaloniki for the period 1994 -- 2023
-  using data recorded every one minute. We identified the cloud enhancement (CE)
-  events by creating an appropriate clear-sky irradiance reference with the use of a
-  radiative transfer model and aerosol optical depth data from a collocated Cimel sun
-  photometer and a Brewer spectrophotometer. We found a trend in CE events of
-  \(45.6\pm 21.9\,\text{cases}/\text{year}\), and a trend in the CE events
-  irradiation of \(116.9\pm 67.8\,\text{kJ}/\text{year}\). The peak of the CE events
-  was observed during May and June. The analysis of the total duration of CE events
-  showed that durations longer than 5 minutes are very rare, with exceptions lasting
-  over an hour and up to 140 minutes. Finally, we have detected enhancements above
-  the total solar irradiance at the top of the atmosphere of up to
-  \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the cases below
-  \(200\,\text{W}/\text{m}^{2}\). The most active period of these extreme events is
-  spring -- early summer with a secondary peak in autumn.
+# abstract: |
+#   In this study we investigate the characteristics of global horizontal irradiance
+#   enhancement events induced by clouds over Thessaloniki for the period 1994 -- 2023
+#   using data recorded every one minute. We identified the cloud enhancement (CE)
+#   events by creating an appropriate clear-sky irradiance reference with the use of a
+#   radiative transfer model and aerosol optical depth data from a collocated Cimel sun
+#   photometer and a Brewer spectrophotometer. We found a trend in CE events of
+#   \(45.6\pm 21.9\,\text{cases}/\text{year}\), and a trend in the CE events
+#   irradiation of \(116.9\pm 67.8\,\text{kJ}/\text{year}\). The peak of the CE events
+#   was observed during May and June. The analysis of the total duration of CE events
+#   showed that durations longer than 5 minutes are very rare, with exceptions lasting
+#   over an hour and up to 140 minutes. Finally, we have detected enhancements above
+#   the total solar irradiance at the top of the atmosphere of up to
+#   \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the cases below
+#   \(200\,\text{W}/\text{m}^{2}\). The most active period of these extreme events is
+#   spring -- early summer with a secondary peak in autumn.
 
@@
 extreme cloud enhancement events (ECE), the cases when GHI at ground level exceeds
-the Total Solar Irradiance (TSI). Although the duration of these bursts can vary from
-seconds to several minutes, here we are constrained by the temporal resolution of our
-data to identify events with duration of at minimum one-minute.
+the Total Solar Irradiance (TSI) at the top of the atmosphere (TOA) for the same SZA.
+Although the duration of these bursts can vary from seconds to several minutes, here
+we are constrained by the temporal resolution of our data to identify events with
+duration of at minimum one-minute.
 
@@
 $`r round(MC[Typ == "Max Enha", wattGLB - ETH],1)`\,\text{W}/\text{m}^2$ above the
-TSI at TSI for the same SZA, respectively.
+TSI at TOA for the same SZA, respectively.
 In the following sections we are discussing the long-term trends and variability of
@@
 
-The relation between the duration and the mean OI of the groups has also been
-studied (Figure\nobreakspace{}\ref{fig:group-2d}).  Evidently, events of high excess
+The relation between the duration and the mean OI of the groups has also been studied
+(Figure\nobreakspace{}\ref{fig:group-2d}).  Evidently, events of high excess
 irradiation have small duration and vice versa. The vast majority of grouped events
-are associated with small excess irradiation (e.g., $<5\,\text{kJ}/\text{m}^2$) and
-small duration (e.g., $<5\,\text{min}$) while groups with strong excess irradiation
-and long duration are very rare.  Similar results of this relation have been reported
-by @Zhang2018 in a study using a far higher sampling rate ($100\,\text{Hz}$) than
+are associated with small excess irradiation ($<5\,\text{kJ}/\text{m}^2$) and small
+duration ($<5\,\text{min}$). For example the extra energy flux of
+$5\,\text{kJ}/\text{m}^2$ for $5\,\text{min}$ is equivalent to OI of
+$\sim17\,\text{W}/\text{m}^2$ for the same duration. While groups with strong excess
+irradiation and long duration are very rare.  Similar results of this relation have
+been reported by @Zhang2018 in a study using a far higher sampling rate
+($100\,\text{Hz}$) than
 ours.
@@
 ```
-
-<!-- ```{r echo=FALSE, fig.cap="Relation of mean OI and CE group duration"} -->
-<!-- knitr::include_graphics("../images/groups-4.png") -->
-<!-- ``` -->
-
-<!-- ```{r echo=FALSE, fig.cap="Relation of maximun OI and CE group duration"} -->
-<!-- knitr::include_graphics("../images/groups-8.png") -->
-<!-- ``` -->
 
@@
 
-<!-- ```{r echo=FALSE, fig.cap="Distribution of the number of ECE cases"} -->
-<!-- knitr::include_graphics("../images/climECEmonth-1.png") -->
-<!-- ``` -->
-
 The distribution of the ECE events
 (Figure\nobreakspace{}\ref{fig:P-extreme-distribution}) shows that in rare cases the
-OI can exceed the TSI even by more than $400\,\text{W}/\text{m}^2$, while in
-$75\,\%$ of the cases the OI is below $200\,\text{W}/\text{m}^2$. The OI for the
-most frequent ECEs ranges between $140$ and $180\,\text{W}/\text{m}^2$.  These
-findings are in accordance with the results of @Vamvakas2020, the only difference
-being that the OI values reported for are higher than those for Thessaloniki.
+OI can exceed the TSI at TOA for the same SZA even by more than
+$400\,\text{W}/\text{m}^2$, while in $75\,\%$ of the cases the OI is below
+$200\,\text{W}/\text{m}^2$. The OI for the most frequent ECEs ranges between $140$
+and $180\,\text{W}/\text{m}^2$.  These findings are in accordance with the results of
+@Vamvakas2020, the only difference being that the OI values reported for are higher
+than those for Thessaloniki.
 
@@
 ```
-
-<!-- ```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE events in Thessaloniki for the period 1994 -- 2023."} -->
-<!-- knitr::include_graphics("../images/P-extreme-distribution-1.png") -->
-<!-- ``` -->
-
-<!-- ```{r echo=FALSE, fig.cap="Distribution of ECE Irradiance above 'TSI'"} -->
-<!-- knitr::include_graphics("../images/extremedistributions-4.png") -->
-<!-- ``` -->
-
-<!--  SZA -->
-
-<!-- ### Yearly plots relative to all GHI data. -->
-<!-- ```{r echo=FALSE, fig.cap=""} -->
-<!-- knitr::include_graphics("../images/rel_energy-1.png") -->
-<!-- ``` -->
-
-<!-- ```{r echo=FALSE, fig.cap=""} -->
-<!-- knitr::include_graphics("../images/rel_energy-2.png") -->
-<!-- ``` -->
-
-<!-- ```{r echo=FALSE, fig.cap=""} -->
-<!-- knitr::include_graphics("../images/rel_energy-3.png") -->
-<!-- ``` -->
 

### 2024-09-02 article/article.tex
Commit 2024-09-02 09:09

@@
   \begin{abstract}
-  In this study we investigate the characteristics of global horizontal
-  irradiance enhancement events induced by clouds over Thessaloniki for
-  the period 1994 -- 2023 using data recorded every one minute. We
-  identified the cloud enhancement (CE) events by creating an
-  appropriate clear-sky irradiance reference with the use of a radiative
-  transfer model and aerosol optical depth data from a collocated Cimel
-  sun photometer and a Brewer spectrophotometer. We found a trend in CE
-  events of \(45.6\pm 21.9\,\text{cases}/\text{year}\), and a trend in
-  the CE events irradiation of \(116.9\pm 67.8\,\text{kJ}/\text{year}\).
-  The peak of the CE events was observed during May and June. The
-  analysis of the total duration of CE events showed that durations
-  longer than 5 minutes are very rare, with exceptions lasting over an
-  hour and up to 140 minutes. Finally, we have detected enhancements
-  above the total solar irradiance at the top of the atmosphere of up to
-  \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the cases below
-  \(200\,\text{W}/\text{m}^{2}\). The most active period of these
-  extreme events is spring -- early summer with a secondary peak in
-  autumn.
+
   \end{abstract}
@@
 we define as extreme cloud enhancement events (ECE), the cases when GHI
-at ground level exceeds the Total Solar Irradiance (TSI). Although the
-duration of these bursts can vary from seconds to several minutes, here
-we are constrained by the temporal resolution of our data to identify
-events with duration of at minimum one-minute.
+at ground level exceeds the Total Solar Irradiance (TSI) at the top of
+the atmosphere (TOA) for the same SZA. Although the duration of these
+bursts can vary from seconds to several minutes, here we are constrained
+by the temporal resolution of our data to identify events with duration
+of at minimum one-minute.
 
@@
 \(136.8\,\text{W}/\text{m}^2\) and \(164.5\,\text{W}/\text{m}^2\) above
-the TSI at TSI for the same SZA, respectively. In the following sections
+the TSI at TOA for the same SZA, respectively. In the following sections
 we are discussing the long-term trends and variability of the CE events
@@
 The vast majority of grouped events are associated with small excess
-irradiation (e.g., \(<5\,\text{kJ}/\text{m}^2\)) and small duration
-(e.g., \(<5\,\text{min}\)) while groups with strong excess irradiation
-and long duration are very rare. Similar results of this relation have
-been reported by \citet{Zhang2018} in a study using a far higher
-sampling rate (\(100\,\text{Hz}\)) than ours.
+irradiation (\(<5\,\text{kJ}/\text{m}^2\)) and small duration
+(\(<5\,\text{min}\)). For example the extra energy flux of
+\(5\,\text{kJ}/\text{m}^2\) for \(5\,\text{min}\) is equivalent to OI of
+\(\sim17\,\text{W}/\text{m}^2\) for the same duration. While groups with
+strong excess irradiation and long duration are very rare. Similar
+results of this relation have been reported by \citet{Zhang2018} in a
+study using a far higher sampling rate (\(100\,\text{Hz}\)) than ours.
 
@@
 (Figure\nobreakspace{}\ref{fig:P-extreme-distribution}) shows that in
-rare cases the OI can exceed the TSI even by more than
-\(400\,\text{W}/\text{m}^2\), while in \(75\,\%\) of the cases the OI is
-below \(200\,\text{W}/\text{m}^2\). The OI for the most frequent ECEs
-ranges between \(140\) and \(180\,\text{W}/\text{m}^2\). These findings
-are in accordance with the results of \citet{Vamvakas2020}, the only
-difference being that the OI values reported for are higher than those
-for Thessaloniki.
+rare cases the OI can exceed the TSI at TOA for the same SZA even by
+more than \(400\,\text{W}/\text{m}^2\), while in \(75\,\%\) of the cases
+the OI is below \(200\,\text{W}/\text{m}^2\). The OI for the most
+frequent ECEs ranges between \(140\) and \(180\,\text{W}/\text{m}^2\).
+These findings are in accordance with the results of
+\citet{Vamvakas2020}, the only difference being that the OI values
+reported for are higher than those for Thessaloniki.
 

### 2024-09-02 GHI_enh_read_aod_brewer.tex
Commit 2024-09-01 14:14
Commit 2024-09-02 21:09

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-09-01}
+\date{2024-09-02}
 
@@
 \caption{ - empty caption - }\label{fig:unnamed-chunk-4-54}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-55}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-55}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-56}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-56}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-57}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-57}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-58}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-58}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-59}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-59}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-60}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-60}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-61}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-61}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-62}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-62}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-63}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-63}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-64}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-64}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-65}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-65}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-66}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-66}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-67}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-67}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-68}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-68}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-69}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-69}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-70}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-70}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-71}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-71}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-72}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-72}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-73}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-73}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-74}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-74}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-75}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-75}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-76}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-76}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-77}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-77}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-78}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-78}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-79}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-79}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-80}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-80}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-81}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-81}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-82}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-82}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-83}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-83}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-84}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-84}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-85}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-85}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-86}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-86}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-87}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-87}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-88}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-88}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-89}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-89}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-90}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-90}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-91}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-91}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-92}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-92}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-93}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-93}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-94}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-94}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-95}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-95}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-96}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-96}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-97}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-97}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-98}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-98}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-99}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-99}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-100}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-100}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-101}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-101}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-102}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-102}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-103}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-103}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-104}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-104}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-105}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-105}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-106}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-106}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-107}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-107}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-108}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-108}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-109}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-109}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-110}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-110}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-111}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-111}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-112}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-112}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-113}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-113}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-114}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-114}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-115}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-115}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-116}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-116}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-117}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-117}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-118}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-118}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-119}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-119}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-120}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-120}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-121}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-121}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-122}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-122}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-123}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-123}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-124}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-124}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-125}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-125}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-126}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-126}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-127}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-127}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-128}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-128}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-129}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-129}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-130}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-130}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-131}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-131}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-132}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-132}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-133}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-133}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-134}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-134}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-135}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-135}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-136}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-136}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-137}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-137}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-138}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-138}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-139}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-139}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-140}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-140}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-141}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-141}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-142}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-142}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-143}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-143}
 \end{figure}
@@
 
+\begin{verbatim}
+range 0.0001914191 0.2557606 
+\end{verbatim}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-144}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-144}
+\end{figure}
+
 \textbf{END}

### 2024-09-03 GHI_enh_read_aod_brewer.tex
Commit 2024-09-03 09:09

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-09-02}
+\date{2024-09-03}
 
@@
 Max N data for 1 
+\end{verbatim}
+
+\begin{verbatim}
+Drop data with clouds
 \end{verbatim}
@@
 \endlastfoot
-0.2558 & AOD\_292 \\
-0.0385 & AOD\_292.5 \\
-0.04534 & AOD\_293 \\
-0.06775 & AOD\_293.5 \\
-0.05734 & AOD\_294 \\
-0.0763 & AOD\_294.5 \\
-0.0831 & AOD\_295 \\
-0.08266 & AOD\_295.5 \\
-0.1019 & AOD\_296 \\
-0.09853 & AOD\_296.5 \\
-0.09384 & AOD\_297 \\
-0.08095 & AOD\_297.5 \\
-0.09393 & AOD\_298 \\
-0.08817 & AOD\_298.5 \\
-0.0804 & AOD\_299 \\
-0.07093 & AOD\_299.5 \\
-0.06308 & AOD\_300 \\
-0.05071 & AOD\_300.5 \\
-0.05359 & AOD\_301 \\
-0.04396 & AOD\_301.5 \\
-0.03347 & AOD\_302 \\
-0.02571 & AOD\_302.5 \\
-0.02131 & AOD\_303 \\
-0.01803 & AOD\_303.5 \\
-0.01171 & AOD\_304 \\
-0.01022 & AOD\_304.5 \\
-0.005416 & AOD\_305 \\
-0.0005074 & AOD\_305.5 \\
-0.002836 & AOD\_306 \\
-0.0001914 & AOD\_306.5 \\
-0.001028 & AOD\_307 \\
-0.0002915 & AOD\_307.5 \\
-0.01176 & AOD\_308 \\
-0.02345 & AOD\_308.5 \\
-0.02512 & AOD\_309 \\
-0.02872 & AOD\_309.5 \\
-0.03807 & AOD\_310 \\
-0.04033 & AOD\_310.5 \\
-0.04404 & AOD\_311 \\
-0.04732 & AOD\_311.5 \\
-0.04988 & AOD\_312 \\
-0.05461 & AOD\_312.5 \\
-0.05661 & AOD\_313 \\
-0.06141 & AOD\_313.5 \\
-0.05901 & AOD\_314 \\
-0.05361 & AOD\_314.5 \\
-0.0447 & AOD\_315 \\
-0.03122 & AOD\_315.5 \\
-0.02879 & AOD\_316 \\
-0.02784 & AOD\_316.5 \\
-0.02667 & AOD\_317 \\
-0.02556 & AOD\_317.5 \\
-0.02617 & AOD\_318 \\
-0.02414 & AOD\_318.5 \\
-0.01576 & AOD\_319 \\
-0.007456 & AOD\_319.5 \\
-0.002617 & AOD\_320 \\
-0.00727 & AOD\_320.5 \\
-0.0097 & AOD\_321 \\
-0.01868 & AOD\_321.5 \\
-0.02508 & AOD\_322 \\
-0.02554 & AOD\_322.5 \\
-0.02652 & AOD\_323 \\
-0.02711 & AOD\_323.5 \\
-0.03271 & AOD\_324 \\
-0.03674 & AOD\_324.5 \\
-0.03564 & AOD\_325 \\
-0.04207 & AOD\_325.5 \\
-0.04356 & AOD\_326 \\
-0.04334 & AOD\_326.5 \\
-0.04177 & AOD\_327 \\
-0.04679 & AOD\_327.5 \\
-0.04267 & AOD\_328 \\
-0.03719 & AOD\_328.5 \\
-0.03491 & AOD\_329 \\
-0.03328 & AOD\_329.5 \\
-0.03067 & AOD\_330 \\
-0.03602 & AOD\_330.5 \\
-0.03564 & AOD\_331 \\
-0.03208 & AOD\_331.5 \\
-0.02064 & AOD\_332 \\
-0.01897 & AOD\_332.5 \\
-0.02294 & AOD\_333 \\
-0.02197 & AOD\_333.5 \\
-0.02225 & AOD\_334 \\
-0.02282 & AOD\_334.5 \\
-0.02284 & AOD\_335 \\
-0.02381 & AOD\_335.5 \\
-0.02606 & AOD\_336 \\
-0.02517 & AOD\_336.5 \\
-0.02722 & AOD\_337 \\
-0.02877 & AOD\_337.5 \\
-0.03161 & AOD\_338 \\
-0.03294 & AOD\_338.5 \\
-0.03393 & AOD\_339 \\
-0.03063 & AOD\_339.5 \\
-0.02624 & AOD\_340 \\
-0.02005 & AOD\_340.5 \\
-0.02407 & AOD\_341 \\
-0.02232 & AOD\_341.5 \\
-0.02444 & AOD\_342 \\
-0.02502 & AOD\_342.5 \\
-0.02645 & AOD\_343 \\
-0.0247 & AOD\_343.5 \\
-0.02531 & AOD\_344 \\
-0.02526 & AOD\_344.5 \\
-0.02374 & AOD\_345 \\
-0.02159 & AOD\_345.5 \\
-0.02034 & AOD\_346 \\
-0.02048 & AOD\_346.5 \\
-0.01923 & AOD\_347 \\
-0.01956 & AOD\_347.5 \\
-0.0214 & AOD\_348 \\
-0.01945 & AOD\_348.5 \\
-0.01227 & AOD\_349 \\
-0.01165 & AOD\_349.5 \\
-0.01124 & AOD\_350 \\
-0.009548 & AOD\_350.5 \\
-0.008288 & AOD\_351 \\
-0.006796 & AOD\_351.5 \\
-0.004561 & AOD\_352 \\
-0.004843 & AOD\_352.5 \\
-0.003653 & AOD\_353 \\
-0.0007953 & AOD\_353.5 \\
-0.001056 & AOD\_354 \\
-0.004497 & AOD\_354.5 \\
-0.003201 & AOD\_355 \\
-0.009072 & AOD\_355.5 \\
-0.00913 & AOD\_356 \\
-0.00913 & AOD\_356.5 \\
-0.009986 & AOD\_357 \\
-0.01327 & AOD\_357.5 \\
-0.01149 & AOD\_358 \\
-0.008446 & AOD\_358.5 \\
-0.004012 & AOD\_359 \\
-0.00145 & AOD\_359.5 \\
-0.001221 & AOD\_360 \\
-0.00208 & AOD\_360.5 \\
-0.003965 & AOD\_361 \\
-0.01953 & AOD\_361.5 \\
-0.06372 & AOD\_362 \\
-0.066 & AOD\_362.5 \\
-0.05968 & AOD\_363 \\
+0.07593 & AOD\_292 \\
+0.1666 & AOD\_292.5 \\
+0.09945 & AOD\_293 \\
+0.09468 & AOD\_293.5 \\
+0.05937 & AOD\_294 \\
+0.06021 & AOD\_294.5 \\
+0.07722 & AOD\_295 \\
+0.08395 & AOD\_295.5 \\
+0.09015 & AOD\_296 \\
+0.0975 & AOD\_296.5 \\
+0.09944 & AOD\_297 \\
+0.08816 & AOD\_297.5 \\
+0.09295 & AOD\_298 \\
+0.09489 & AOD\_298.5 \\
+0.09257 & AOD\_299 \\
+0.09279 & AOD\_299.5 \\
+0.09115 & AOD\_300 \\
+0.09293 & AOD\_300.5 \\
+0.09517 & AOD\_301 \\
+0.1004 & AOD\_301.5 \\
+0.1001 & AOD\_302 \\
+0.09831 & AOD\_302.5 \\
+0.1008 & AOD\_303 \\
+0.1019 & AOD\_303.5 \\
+0.1023 & AOD\_304 \\
+0.1034 & AOD\_304.5 \\
+0.102 & AOD\_305 \\
+0.1014 & AOD\_305.5 \\
+0.1026 & AOD\_306 \\
+0.09934 & AOD\_306.5 \\
+0.09853 & AOD\_307 \\
+0.1004 & AOD\_307.5 \\
+0.1002 & AOD\_308 \\
+0.1001 & AOD\_308.5 \\
+0.1017 & AOD\_309 \\
+0.1028 & AOD\_309.5 \\
+0.1056 & AOD\_310 \\
+0.1059 & AOD\_310.5 \\
+0.1063 & AOD\_311 \\
+0.1058 & AOD\_311.5 \\
+0.1036 & AOD\_312 \\
+0.1066 & AOD\_312.5 \\
+0.1056 & AOD\_313 \\
+0.1056 & AOD\_313.5 \\
+0.1067 & AOD\_314 \\
+0.1065 & AOD\_314.5 \\
+0.1072 & AOD\_315 \\
+0.108 & AOD\_315.5 \\
+0.1068 & AOD\_316 \\
+0.1073 & AOD\_316.5 \\
+0.1079 & AOD\_317 \\
+0.108 & AOD\_317.5 \\
+0.1068 & AOD\_318 \\
+0.1052 & AOD\_318.5 \\
+0.1059 & AOD\_319 \\
+0.1054 & AOD\_319.5 \\
+0.106 & AOD\_320 \\
+0.1062 & AOD\_320.5 \\
+0.1071 & AOD\_321 \\
+0.1034 & AOD\_321.5 \\
+0.1031 & AOD\_322 \\
+0.1036 & AOD\_322.5 \\
+0.104 & AOD\_323 \\
+0.1036 & AOD\_323.5 \\
+0.1044 & AOD\_324 \\
+0.104 & AOD\_324.5 \\
+0.1036 & AOD\_325 \\
+0.1024 & AOD\_325.5 \\
+0.1032 & AOD\_326 \\
+0.1016 & AOD\_326.5 \\
+0.1008 & AOD\_327 \\
+0.1025 & AOD\_327.5 \\
+0.1036 & AOD\_328 \\
+0.1041 & AOD\_328.5 \\
+0.1047 & AOD\_329 \\
+0.1042 & AOD\_329.5 \\
+0.1059 & AOD\_330 \\
+0.1055 & AOD\_330.5 \\
+0.1041 & AOD\_331 \\
+0.1045 & AOD\_331.5 \\
+0.1038 & AOD\_332 \\
+0.1074 & AOD\_332.5 \\
+0.1079 & AOD\_333 \\
+0.1083 & AOD\_333.5 \\
+0.1089 & AOD\_334 \\
+0.1102 & AOD\_334.5 \\
+0.1103 & AOD\_335 \\
+0.1098 & AOD\_335.5 \\
+0.11 & AOD\_336 \\
+0.1103 & AOD\_336.5 \\
+0.11 & AOD\_337 \\
+0.1108 & AOD\_337.5 \\
+0.1092 & AOD\_338 \\
+0.1103 & AOD\_338.5 \\
+0.1097 & AOD\_339 \\
+0.109 & AOD\_339.5 \\
+0.1087 & AOD\_340 \\
+0.1091 & AOD\_340.5 \\
+0.1094 & AOD\_341 \\
+0.1097 & AOD\_341.5 \\
+0.1098 & AOD\_342 \\
+0.1114 & AOD\_342.5 \\
+0.1088 & AOD\_343 \\
+0.1086 & AOD\_343.5 \\
+0.1088 & AOD\_344 \\
+0.1082 & AOD\_344.5 \\
+0.1083 & AOD\_345 \\
+0.1104 & AOD\_345.5 \\
+0.1104 & AOD\_346 \\
+0.1103 & AOD\_346.5 \\
+0.1091 & AOD\_347 \\
+0.109 & AOD\_347.5 \\
+0.1085 & AOD\_348 \\
+0.1082 & AOD\_348.5 \\
+0.1093 & AOD\_349 \\
+0.1079 & AOD\_349.5 \\
+0.1062 & AOD\_350 \\
+0.1042 & AOD\_350.5 \\
+0.1049 & AOD\_351 \\
+0.104 & AOD\_351.5 \\
+0.1034 & AOD\_352 \\
+0.1042 & AOD\_352.5 \\
+0.1075 & AOD\_353 \\
+0.1079 & AOD\_353.5 \\
+0.1085 & AOD\_354 \\
+0.1135 & AOD\_354.5 \\
+0.1145 & AOD\_355 \\
+0.1137 & AOD\_355.5 \\
+0.1135 & AOD\_356 \\
+0.1151 & AOD\_356.5 \\
+0.1154 & AOD\_357 \\
+0.1148 & AOD\_357.5 \\
+0.1163 & AOD\_358 \\
+0.1174 & AOD\_358.5 \\
+0.1179 & AOD\_359 \\
+0.1181 & AOD\_359.5 \\
+0.1197 & AOD\_360 \\
+0.1188 & AOD\_360.5 \\
+0.1179 & AOD\_361 \\
+0.1155 & AOD\_361.5 \\
+0.1236 & AOD\_362 \\
+0.1082 & AOD\_362.5 \\
+0.08471 & AOD\_363 \\
 \end{longtable}
@@
 \begin{verbatim}
-range 0.0001914191 0.2557606 
+range 0.0593665 0.1665588 
 \end{verbatim}

### 2024-09-03 GHI_enh_05_distributions.R
Commit 2024-09-03 10:14

@@ -575,6 +575,8 @@ monthly <- DATA[, .(Relative_enha_GLB = sum(Enhanc_C_4, na.rm = T)/sum(!is.na(wa
                 by = .(year(Date), month(Date)) ]
 
 
+
+
 boxplot(monthly$Relative_enha_GLB ~ monthly$month)
 boxplot(monthly$Relative_enha_N ~ monthly$month)
 
@@ -610,7 +612,6 @@ ggplot(monthly, aes(y = 100 * Relative_enha_N,
     panel.grid.minor.x = element_blank()
   )
 #+ echo=F, include=T
-
 
 
 
@@ -661,6 +662,19 @@ ggplot(monthlyE, aes(y = Relative_enha_N,
   )
 
 #+ echo=F, include=T
+
+
+mont <- DATA[Enhanc_C_4 == T,
+             .(CE_OI = sum(GLB_diff, na.rm = F),
+               OI_N  = length(GLB_diff>0)),
+             by = .(year(Date), month(Date)) ]
+
+boxplot(DATA[Enhanc_C_4 == T, GLB_diff] ~  DATA[Enhanc_C_4 == T, month])
+title("Mean OI")
+
+
+boxplot(mont[, CE_OI/OI_N] ~ mont$month)
+title("Mean monthly OI")
 
 
 

### 2024-09-03 article/article.tex
Commit 2024-09-03 22:14

@@
 the yield and in designing the specifications of the appropriate
-equipment. Significant portion of research has been focused on
-predicting the renewable energy production in a fine timescale and in
-near real-time \citep[for a review see][]{Inman2013, Graabak2016}.
+equipment. A significant portion of the relevant research has been
+focused on predicting the renewable energy production in a fine
+timescale and in near real-time \citep[for a review
+see][]{Inman2013, Graabak2016}.
 
@@
 
-Some of the proposed underling mechanisms of those enhancements, have
+Some of the proposed underling mechanisms of those enhancements have
 been summarized by \citet{Gueymard2017}; the most important being the
@@
 \citep{Pecenak2016, Thuillier2013, Yordanov2013, Yordanov2015}. Overall,
-enhancement events depend on different interactive factors, which
-include cloud thickness, structure and type, and the relative position
-of the sun and the clouds \citep{Gueymard2017, Veerman2022}.
+the appearance of CE events depend on different interactive factors,
+which include cloud thickness, structure and type, and the relative
+position of the sun and the clouds \citep{Gueymard2017, Veerman2022}.
 
@@
 reported decreases over North America and Europe. To our knowledge,
-there is no evidence on whether this trend has affected also the number
+there is no evidence of whether this trend has affected also the number
 and strength of CE events.
@@
 
-In this study, we evaluate the effects of CE on GHI by investigating
-their frequency of occurrence, intensity, and duration in a thirty-year
-period of GHI observations at Thessaloniki, Greece. We used modeled
-clear sky irradiance as a baseline to identify cloud enhancements, and
-we determined long-term trends of the above-mentioned metrics, their
-climatology and some general characteristics. To our knowledge there are
-no other studies that provide trends from such long dataset.
+In this study, we evaluate the effects of CE events on GHI by
+investigating their frequency of occurrence, intensity, and duration in
+a thirty-year record of GHI observations at Thessaloniki, Greece. We
+used modeled clear sky irradiance as a baseline to identify cloud
+enhancements, and we determined long-term trends of the above-mentioned
+metrics, their climatology and some general characteristics. To our
+knowledge there are no other studies that provide trends from such a
+long dataset.
 
@@
 signal was converted to irradiance using the ramped value of the
-instrument's sensitivity between subsequent calibrations.
+instrument's sensitivity between subsequent calibrations. We note that
+the specific model of the pyranometer is not capable in recording the
+instrument's temperature, therefore any temperature changes that may
+occur during the day (including those due to sudden increases or
+decreases in incidence irradiance) were not considered in the data
+reduction procedure. However, the sensitivity of the instrument to
+temperature is less than \(\pm1\,\%\) for its operational range
+(\(-20^\circ\) -- \(50^\circ\)C).
 
 To further improve the quality of the irradiance data, a manual
-screening was performed, in order to remove inconsistent and erroneous
-recordings that can occur stochastically or systematically during the
-long operation of the instrument. The manual screening was aided by a
+screening was performed, to remove inconsistent and erroneous recordings
+that can occur stochastically or systematically during the long
+operation of the instrument. The manual screening was aided by a
 radiation data quality assurance procedure, adjusted for the site, which
@@
 In this study, we define an event as CE when the measured GHI at ground
-level, exceeds the expected value under clear-sky conditions. Similarly,
+level exceeds the expected value under clear-sky conditions. Similarly,
 we define as extreme cloud enhancement events (ECE), the cases when GHI
@@
 
-For the detection of CE cases we established a baseline of irradiance
+For the detection of CE cases, we established a baseline of irradiance
 above which we characterized each data point as an enhancement event and
@@
 discrepancies is the variability of the effects of aerosols and water
-vapor which were not taken into account in the two simple methods. To
-produce a more representative reference we included the effects of these
-factors using a radiative transfer model (RTM). The applied methodology
-is discussed in section\nobreakspace{}\ref{rtmcs}.
+vapor which were not considered in the simple method. To produce a more
+representative reference we included the effects of these factors using
+a radiative transfer model (RTM). The applied methodology is discussed
+in section\nobreakspace{}\ref{rtmcs}.
 
@@
 the ``LOWTRAN'' gas parameterization. The model was run for a range of
-variables in order to create a look-up table (LUT) for the estimation of
-the cloud-free reference irradiance for each individual observation of
-our dataset. In this context, the model was run for SZAs in the range
-\(10\) -- \(90^\circ\) with a step of \(0.2^\circ\) and for the
-atmospheric profiles of the Air Force Geophysics Laboratory
-\citep{Anderson1986} midlatitude summer and midlatitude winter,
-representative of the warm and cold seasons.
+variables to create a look-up table (LUT) for the estimation of the
+cloud-free reference irradiance for each individual observation of our
+dataset. In this context, the model was run for SZAs in the range \(10\)
+-- \(90^\circ\) with a step of \(0.2^\circ\) and for the atmospheric
+profiles of the Air Force Geophysics Laboratory \citep{Anderson1986}
+midlatitude summer and midlatitude winter, representative of the warm
+and cold seasons.
 
@@
 vapor. At Thessaloniki, such measurements are available since 2003 from
-the Cimel sun photometer that belongs to the Aerosol Robotic Network
+a Cimel sun photometer which is part of the Aerosol Robotic Network
 (AERONET) \citep{Giles2019, Buis1998}. From the observations in the
@@
 an adjustment of the \(\text{GHI}_\text{ref}\) during the period of
-study was made using simulations with the RTM based on the long-term
-variations of the AOD. As AERONET data start only in 2003, we used for
-the period 1994 -- 2005 estimates of changes in AOD at
+study was made using simulations with the RTM to account for the
+long-term variations of the AOD. As AERONET data start only in 2003, we
+used for the period 1994 -- 2005 estimates of changes in AOD at
 \(340\,\text{nm}\) derived from a collocated Brewer spectrophotometer

### 2024-09-03 article/article.Rmd
Commit 2024-09-03 22:14

@@
 
-<!--
-
-$\text{GHI}_\text{i}$: measured one minute global horizontal irradiance
-
-$\text{GHI}_\text{CSm}$: modelled clear sky one minute global horizontal irradiance 
--->
-
 # Introduction
@@
 production. The variability of its intensity can impose difficulties in predicting
-the yield and in designing the specifications of the appropriate equipment.
-Significant portion of research has been focused on predicting the renewable energy
-production in a fine timescale and in near real-time [for a review see @Inman2013;
-@Graabak2016].
+the yield and in designing the specifications of the appropriate equipment.  A
+significant portion of the relevant research has been focused on predicting the
+renewable energy production in a fine timescale and in near real-time [for a review
+see @Inman2013; @Graabak2016].
 
@@
 
-Some of the proposed underling mechanisms of those enhancements, have been summarized
+Some of the proposed underling mechanisms of those enhancements have been summarized
 by @Gueymard2017; the most important being the scattering of radiation on the edges
@@
 optical depth [@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015].  Overall,
-enhancement events depend on different interactive factors, which include cloud
-thickness, structure and type, and the relative position of the sun and the clouds
-[@Gueymard2017; @Veerman2022].
+the appearance of CE events depend on different interactive factors, which include
+cloud thickness, structure and type, and the relative position of the sun and the
+clouds [@Gueymard2017; @Veerman2022].
 
@@
 while @Dong2023 reported decreases over North America and Europe. To our knowledge,
-there is no evidence on whether this trend has affected also the number and strength
+there is no evidence of whether this trend has affected also the number and strength
 of CE events.
@@
 <!-- our work -->
-In this study, we evaluate the effects of CE on GHI by investigating their frequency
-of occurrence, intensity, and duration in a thirty-year period of GHI observations at
-Thessaloniki, Greece.  We used modeled clear sky irradiance as a baseline to identify
-cloud enhancements, and we determined long-term trends of the above-mentioned
-metrics, their climatology and some general characteristics.  To our knowledge there
-are no other studies that provide trends from such long dataset.
-
-<!--
-Identification methods from bib
-
-- clearness index
-- modeled approaches
-- algorithmic id
-- AI
-- Visual
-
-Constrains of the site
-
-- data
-- instrument
-- location
--->
+In this study, we evaluate the effects of CE events on GHI by investigating their
+frequency of occurrence, intensity, and duration in a thirty-year record of GHI
+observations at Thessaloniki, Greece.  We used modeled clear sky irradiance as a
+baseline to identify cloud enhancements, and we determined long-term trends of the
+above-mentioned metrics, their climatology and some general characteristics.  To our
+knowledge there are no other studies that provide trends from such a long dataset.
 
@@
 using the ramped value of the instrument’s sensitivity between subsequent
-calibrations.
+calibrations.  We note that the specific model of the pyranometer is not capable in
+recording the instrument's temperature, therefore any temperature changes that may
+occur during the day (including those due to sudden increases or decreases in
+incidence irradiance) were not considered in the data reduction procedure. However,
+the sensitivity of the instrument to temperature is less than $\pm1\,\%$ for its
+operational range ($-20^\circ$ -- $50^\circ$C).
 
@@
 To further improve the quality of the irradiance data, a manual screening was
-performed, in order to remove inconsistent and erroneous recordings that can occur
+performed, to remove inconsistent and erroneous recordings that can occur
 stochastically or systematically during the long operation of the instrument.  The
@@
 <!-- Define CE and ECE tomove? -->
-In this study, we define an event as CE when the measured GHI at ground level,
+In this study, we define an event as CE when the measured GHI at ground level
 exceeds the expected value under clear-sky conditions. Similarly, we define as
@@
 
-For the detection of CE cases we established a baseline of irradiance above which we
+For the detection of CE cases, we established a baseline of irradiance above which we
 characterized each data point as an enhancement event and calculated the over
@@
 negative results. The main reason for these discrepancies is the variability of the
-effects of aerosols and water vapor which were not taken into account in the two
-simple methods.  To produce a more representative reference we included the effects
-of these factors using a radiative transfer model (RTM).  The applied methodology is
-discussed in section\nobreakspace{}\ref{rtmcs}.
+effects of aerosols and water vapor which were not considered in the simple method.
+To produce a more representative reference we included the effects of these factors
+using a radiative transfer model (RTM).  The applied methodology is discussed in
+section\nobreakspace{}\ref{rtmcs}.
 
@@
 "pseudospherical" geometry and the "LOWTRAN" gas parameterization.  The model was run
-for a range of variables in order to create a look-up table (LUT) for the estimation
-of the cloud-free reference irradiance for each individual observation of our
-dataset. In this context, the model was run for SZAs in the range $10$ -- $90^\circ$
-with a step of $0.2^\circ$ and for the atmospheric profiles of the Air Force
-Geophysics Laboratory [@Anderson1986] midlatitude summer and midlatitude winter,
-representative of the warm and cold seasons.
+for a range of variables to create a look-up table (LUT) for the estimation of the
+cloud-free reference irradiance for each individual observation of our dataset. In
+this context, the model was run for SZAs in the range $10$ -- $90^\circ$ with a step
+of $0.2^\circ$ and for the atmospheric profiles of the Air Force Geophysics
+Laboratory [@Anderson1986] midlatitude summer and midlatitude winter, representative
+of the warm and cold seasons.
 
@@
 radiation under cloud free atmospheres are aerosols and water vapor.  At
-Thessaloniki, such measurements are available since 2003 from the Cimel sun
-photometer that belongs to the Aerosol Robotic Network (AERONET) [@Giles2019;
-@Buis1998].  From the observations in the period 2003 -- 2023 we calculated the
-monthly climatological means and standard deviation ($\sigma$) for the aerosol
-optical depth (AOD) at $500\,\text{nm}$ and the equivalent height of the water column
-(WC).  The monthly climatological values of AOD and WC, as well as combinations with
-additional offsets of $\pm1\sigma$ and $\pm2\sigma$, were used as inputs to the RTM
-in the construction of the LUT.
+Thessaloniki, such measurements are available since 2003 from a Cimel sun photometer
+which is part of the Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998].  From
+the observations in the period 2003 -- 2023 we calculated the monthly climatological
+means and standard deviation ($\sigma$) for the aerosol optical depth (AOD) at
+$500\,\text{nm}$ and the equivalent height of the water column (WC).  The monthly
+climatological values of AOD and WC, as well as combinations with additional offsets
+of $\pm1\sigma$ and $\pm2\sigma$, were used as inputs to the RTM in the construction
+of the LUT.
 
@@
 the $\text{GHI}_\text{ref}$ during the period of study was made using simulations
-with the RTM based on the long-term variations of the AOD. As AERONET data start only
-in 2003, we used for the period 1994 -- 2005 estimates of changes in AOD at
-$340\,\text{nm}$ derived from a collocated Brewer spectrophotometer [@Kazadzis2007]
-to calculate the change in $\text{GHI}_\text{ref}$ due to aerosols during this period.
+with the RTM to account for the long-term variations of the AOD. As AERONET data
+start only in 2003, we used for the period 1994 -- 2005 estimates of changes in AOD
+at $340\,\text{nm}$ derived from a collocated Brewer spectrophotometer
+[@Kazadzis2007] to calculate the change in $\text{GHI}_\text{ref}$ due to aerosols
+during this period.
 
@@
 
-<!--
-\begin{equation}
-\text{CE}_\text{Threshold} = \begin{cases}
-`r C4_cs_ref_ratio`, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
-\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
-\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
-\end{cases}\label{eq:CE4a}
-\end{equation}
-where: $\theta$ solar zenith angle.
--->
-<!--
-\begin{equation}
-\text{CE} : \begin{cases}
- \text{GHI}_\text{i} > `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
-\text{GHI}_\text{i} > \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
-\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
-\end{cases}\label{eq:CE4b}
-\end{equation}
-where: $\theta$ is the solar zenith angle, $\text{GHI}_\text{i}$ the measured
-irradiance, and $\text{GHI}_\text{mCSi}$ the selected modelled clear sky irradiance.
--->
-<!-- \begin{equation} -->
-<!-- \text{CE} : \text{E}_\text{i} > \text{E}_\text{CSlim,i}, \text{where} \begin{cases} -->
-<!--  \text{E}_\text{CSlim,i} = `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\ -->
-<!-- \text{E}_\text{CSlim,i} = \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{E}_\text{CSm,i}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\ -->
-<!-- \text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ -->
-<!-- \end{cases}\label{eq:CE4} -->
-<!-- \end{equation} -->
-<!-- where: $\theta$ is the solar zenith angle, $\text{E}$ the measured -->
-<!-- irradiance, $\text{E}_\text{CSm}$ the selected modelled clear sky irradiance, and $i$ each of the one-minute observation. -->
-
 <!-- reasoning for criteria -->
@@
 the TSI at the top of the atmosphere. In this case the threshold $E$ is given by:
-<!--and detected according to the Equation\nobreakspace{}\ref{eq:ECE}.-->
 \begin{equation}

### 2024-09-03 article/article.tex
Commit 2024-09-03 23:04

@@
 \(340\,\text{nm}\) derived from a collocated Brewer spectrophotometer
-\citep{Kazadzis2007} to calculate the change in
-\(\text{GHI}_\text{ref}\) due to aerosols during this period.
+\citep{Kazadzis2007} to calculate the trend in \(\text{GHI}_\text{ref}\)
+due to aerosols during this period.
 
@@
 Figure\nobreakspace{}\ref{fig:CS-change}) to the climatological
-\(\text{GHI}_\text{ref}\), in order to create a more realistic
-representation of the clear-sky irradiance for the whole period of
-study.
+\(\text{GHI}_\text{ref}\), to create a more realistic representation of
+the clear-sky irradiance for the whole period of study. The rate of
+changes in the two subperiods are different, but reasonable, since the
+effect of the enforced air pollution abatement measures in the area in
+the 1990s had greater effects in the first years of application.
 
@@
 monthly values in the model simulations. We tried different approaches
-in order to strengthen the robustness of the methodology and to
-compensate for the limited accuracy of the RTM input data and the
-unpredictable natural variability of the atmosphere.
+to strengthen the robustness of the methodology and to compensate for
+the limited accuracy of the RTM input data and the unpredictable natural
+variability of the atmosphere.
 

### 2024-09-03 article/article.Rmd
Commit 2024-09-03 23:04

@@
 at $340\,\text{nm}$ derived from a collocated Brewer spectrophotometer
-[@Kazadzis2007] to calculate the change in $\text{GHI}_\text{ref}$ due to aerosols
+[@Kazadzis2007] to calculate the trend in $\text{GHI}_\text{ref}$ due to aerosols
 during this period.
@@
 (see Figure\nobreakspace{}\ref{fig:CS-change}) to the climatological
-$\text{GHI}_\text{ref}$, in order to create a more realistic representation of the
-clear-sky irradiance for the whole period of study.
+$\text{GHI}_\text{ref}$, to create a more realistic representation of the clear-sky
+irradiance for the whole period of study.  The rate of changes in the two subperiods
+are different, but reasonable, since the effect of the enforced air pollution
+abatement measures in the area in the 1990s had greater effects in the first years of
+application.
 
@@
 AOD cannot be taken adequately into account when using monthly values in the model
-simulations. We tried different approaches in order to strengthen the robustness of
+simulations. We tried different approaches to strengthen the robustness of
 the methodology and to compensate for the limited accuracy of the RTM input data and

### 2024-09-04 GHI_enh_07_Aerosols.tex
Commit 2024-08-29 11:07
Commit 2024-09-04 09:09
Commit 2024-09-04 10:14

--- 2024-08-24 GHI_enh_07_Aerosols.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-08-23}
+\date{2024-09-04}
 
@@
 }
-\begin{verbatim}
-Registered S3 methods overwritten by 'ggpp':
-  method                  from   
-  heightDetails.titleGrob ggplot2
-  widthDetails.titleGrob  ggplot2
-\end{verbatim}
-
-\begin{verbatim}
-Attaching package: 'ggpp'
-\end{verbatim}
-
-\begin{verbatim}
-The following object is masked from 'package:ggplot2':
-
-    annotate
-\end{verbatim}
-
 \begin{verbatim}
@@
 \caption{ - empty caption - }\label{fig:unnamed-chunk-4-8}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-9}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-9}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-10}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-10}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-11}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-11}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-12}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-12}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-13}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-13}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-14}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-14}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-15}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-15}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-4-16}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-4-16}
 \end{figure}
@@
 \begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}
-  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1184}}
-  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1053}}
-  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1316}}
-  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1711}}
-  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}
-  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1579}}@{}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1667}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1111}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1389}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1667}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1667}}@{}}
 \toprule
@@
 \endhead
--1102 & 0.8309 & 1 & 565.8 & SZA min & 2014 & 0.001469 \\
--810.5 & 0.7648 & 2 & 721.8 & SZA min & 2015 & 0.00106 \\
--6892 & 3.872 & 3 & 888.2 & SZA min & 2015 & 0.00436 \\
--1277 & 1.124 & 4 & 974.5 & SZA min & 2015 & 0.001153 \\
--982.7 & 0.9904 & 5 & 1004 & SZA min & 2015 & 0.0009866 \\
-375.1 & 0.3116 & 6 & 993.2 & SZA min & 2015 & 0.0003138 \\
--140.7 & 0.5624 & 7 & 984 & SZA min & 2015 & 0.0005715 \\
-444.2 & 0.2576 & 8 & 967.6 & SZA min & 2015 & 0.0002663 \\
--3.347 & 0.4436 & 9 & 872.7 & SZA min & 2015 & 0.0005082 \\
--1081 & 0.9159 & 10 & 758.3 & SZA min & 2015 & 0.001208 \\
--2109 & 1.345 & 11 & 565.3 & SZA min & 2015 & 0.002379 \\
--1598 & 1.044 & 12 & 477.6 & SZA min & 2014 & 0.002186 \\
--1221 & 0.756 & 1 & 293.9 & SZA mean & 2014 & 0.002573 \\
--1063 & 0.7194 & 2 & 377.8 & SZA mean & 2015 & 0.001904 \\
--1776 & 1.125 & 3 & 485.6 & SZA mean & 2015 & 0.002317 \\
--1680 & 1.118 & 4 & 561.4 & SZA mean & 2015 & 0.001992 \\
--1628 & 1.111 & 5 & 599.9 & SZA mean & 2015 & 0.001852 \\
--262.2 & 0.4374 & 6 & 606.9 & SZA mean & 2015 & 0.0007207 \\
--745.5 & 0.6689 & 7 & 592.1 & SZA mean & 2015 & 0.00113 \\
--122.7 & 0.3402 & 8 & 566.4 & SZA mean & 2015 & 0.0006007 \\
--474.5 & 0.4816 & 9 & 477.8 & SZA mean & 2015 & 0.001008 \\
--1443 & 0.9151 & 10 & 394.4 & SZA mean & 2015 & 0.00232 \\
--2438 & 1.364 & 11 & 277.9 & SZA mean & 2015 & 0.004907 \\
--1179 & 0.7187 & 12 & 265.7 & SZA mean & 2014 & 0.002705 \\
--1216 & 0.772 & 1 & 331.6 & SZA median & 2014 & 0.002328 \\
--1041 & 0.7293 & 2 & 419.7 & SZA median & 2015 & 0.001738 \\
--1743 & 1.129 & 3 & 527.8 & SZA median & 2015 & 0.00214 \\
--1654 & 1.123 & 4 & 595.7 & SZA median & 2015 & 0.001884 \\
--1595 & 1.105 & 5 & 620.6 & SZA median & 2015 & 0.00178 \\
--243.2 & 0.4343 & 6 & 619.6 & SZA median & 2015 & 0.0007009 \\
--708.1 & 0.6584 & 7 & 608.4 & SZA median & 2015 & 0.001082 \\
--109.2 & 0.3477 & 8 & 595.2 & SZA median & 2015 & 0.0005842 \\
--441.5 & 0.4846 & 9 & 516.9 & SZA median & 2015 & 0.0009376 \\
--1433 & 0.9306 & 10 & 435.1 & SZA median & 2015 & 0.002139 \\
--2464 & 1.395 & 11 & 314.5 & SZA median & 2015 & 0.004436 \\
--1176 & 0.7354 & 12 & 302.4 & SZA median & 2014 & 0.002432 \\
 -847.8 & 0.7326 & 1 & 621.4 & SZA 55 & 2014 & 0.001179 \\
@@
 
-\begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2222}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1389}}@{}}
-\toprule
-\begin{minipage}[b]{\linewidth}\centering
-year
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-typer
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-MeanGlo
-\end{minipage} \\
-\midrule
-\endhead
-1997 & BR SZA median & 449.5 \\
-2005 & SZA median & 392.1 \\
-2005 & BR SZA median & 459.3 \\
-2006 & SZA median & 493.1 \\
-2007 & SZA median & 470.8 \\
-2008 & SZA median & 326.2 \\
-2011 & SZA median & 505.1 \\
-2012 & SZA median & 500.8 \\
-2013 & SZA median & 498.6 \\
-2014 & SZA median & 477.7 \\
-2015 & SZA median & 504.8 \\
-2016 & SZA median & 510.9 \\
-2017 & SZA median & 551.4 \\
-2018 & SZA median & 499.7 \\
-2019 & SZA median & 476 \\
-2020 & SZA median & 483.7 \\
-2021 & SZA median & 506 \\
-2022 & SZA median & 554.9 \\
-2023 & SZA median & 522.8 \\
-\bottomrule
-\end{longtable}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-49}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-49}
-\end{figure}
-
-\newpage
-
-\begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1806}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1389}}@{}}
-\toprule
-\begin{minipage}[b]{\linewidth}\centering
-year
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-typer
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-MeanGlo
-\end{minipage} \\
-\midrule
-\endhead
-1997 & BR SZA min & 1055 \\
-2005 & SZA min & 668.3 \\
-2005 & BR SZA min & 1064 \\
-2006 & SZA min & 817.1 \\
-2007 & SZA min & 785.1 \\
-2008 & SZA min & 557.2 \\
-2011 & SZA min & 831.1 \\
-2012 & SZA min & 824.3 \\
-2013 & SZA min & 814 \\
-2014 & SZA min & 822.1 \\
-2015 & SZA min & 828.6 \\
-2016 & SZA min & 832.3 \\
-2017 & SZA min & 899.3 \\
-2018 & SZA min & 822.3 \\
-2019 & SZA min & 789.7 \\
-2020 & SZA min & 820.3 \\
-2021 & SZA min & 829.7 \\
-2022 & SZA min & 902.4 \\
-2023 & SZA min & 859.5 \\
-\bottomrule
-\end{longtable}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-50}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-50}
-\end{figure}
-
-\newpage
-
-\begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0972}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1944}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1389}}@{}}
-\toprule
-\begin{minipage}[b]{\linewidth}\centering
-year
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-typer
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-MeanGlo
-\end{minipage} \\
-\midrule
-\endhead
-1997 & BR SZA mean & 497.3 \\
-2005 & SZA mean & 353.9 \\
-2005 & BR SZA mean & 507.1 \\
-2006 & SZA mean & 460.7 \\
-2007 & SZA mean & 434.8 \\
-2008 & SZA mean & 288.6 \\
-2011 & SZA mean & 476.1 \\
-2012 & SZA mean & 468.4 \\
-2013 & SZA mean & 468.5 \\
-2014 & SZA mean & 444.8 \\
-2015 & SZA mean & 472.3 \\
-2016 & SZA mean & 480.3 \\
-2017 & SZA mean & 520.9 \\
-2018 & SZA mean & 467.3 \\
-2019 & SZA mean & 440.6 \\
-2020 & SZA mean & 450.8 \\
-2021 & SZA mean & 473.5 \\
-2022 & SZA mean & 525.5 \\
-2023 & SZA mean & 490.7 \\
-\bottomrule
-\end{longtable}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-51}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-51}
-\end{figure}
-
 \newpage
@@
 \endhead
-1997 & BR SZA 55 & 578.9 \\
+1997 & BR SZA 55 & 579.5 \\
 2005 & SZA 55 & 576.4 \\
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-52}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_07_Aerosols_files/figure-latex/unnamed-chunk-5-13}
 

### 2024-09-04 article/article.Rmd
Commit 2024-09-04 10:14

@@
 According to @Kazadzis2007, in the period 1997 -- 2005 the mean AOD at $340\,\text{nm}$
-is $0.403$ with a change of $-3.8\pm0.93\,\%$ per year, corresponding to a change of
+is $0.4$ with a change of $-3.8\pm0.93\,\%$ per year, corresponding to a change of
 $0.0153$ per year.  Using an Ångström coefficient $\alpha = 1.6$, this translates to

### 2024-09-04 GHI_enh_read_aod_brewer.tex
Commit 2024-09-04 14:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-09-03}
+\date{2024-09-04}
 
@@
 Drop data with clouds
+\end{verbatim}
+
+\begin{verbatim}
+Limit max AOD to  0.8 
 \end{verbatim}
@@
 0.07593 & AOD\_292 \\
-0.1666 & AOD\_292.5 \\
-0.09945 & AOD\_293 \\
-0.09468 & AOD\_293.5 \\
-0.05937 & AOD\_294 \\
-0.06021 & AOD\_294.5 \\
-0.07722 & AOD\_295 \\
-0.08395 & AOD\_295.5 \\
-0.09015 & AOD\_296 \\
-0.0975 & AOD\_296.5 \\
-0.09944 & AOD\_297 \\
-0.08816 & AOD\_297.5 \\
-0.09295 & AOD\_298 \\
-0.09489 & AOD\_298.5 \\
-0.09257 & AOD\_299 \\
-0.09279 & AOD\_299.5 \\
-0.09115 & AOD\_300 \\
-0.09293 & AOD\_300.5 \\
-0.09517 & AOD\_301 \\
-0.1004 & AOD\_301.5 \\
-0.1001 & AOD\_302 \\
-0.09831 & AOD\_302.5 \\
-0.1008 & AOD\_303 \\
-0.1019 & AOD\_303.5 \\
-0.1023 & AOD\_304 \\
-0.1034 & AOD\_304.5 \\
-0.102 & AOD\_305 \\
-0.1014 & AOD\_305.5 \\
-0.1026 & AOD\_306 \\
-0.09934 & AOD\_306.5 \\
-0.09853 & AOD\_307 \\
-0.1004 & AOD\_307.5 \\
-0.1002 & AOD\_308 \\
-0.1001 & AOD\_308.5 \\
-0.1017 & AOD\_309 \\
-0.1028 & AOD\_309.5 \\
-0.1056 & AOD\_310 \\
-0.1059 & AOD\_310.5 \\
-0.1063 & AOD\_311 \\
-0.1058 & AOD\_311.5 \\
-0.1036 & AOD\_312 \\
-0.1066 & AOD\_312.5 \\
-0.1056 & AOD\_313 \\
-0.1056 & AOD\_313.5 \\
-0.1067 & AOD\_314 \\
-0.1065 & AOD\_314.5 \\
-0.1072 & AOD\_315 \\
-0.108 & AOD\_315.5 \\
-0.1068 & AOD\_316 \\
-0.1073 & AOD\_316.5 \\
-0.1079 & AOD\_317 \\
-0.108 & AOD\_317.5 \\
-0.1068 & AOD\_318 \\
-0.1052 & AOD\_318.5 \\
-0.1059 & AOD\_319 \\
-0.1054 & AOD\_319.5 \\
-0.106 & AOD\_320 \\
-0.1062 & AOD\_320.5 \\
-0.1071 & AOD\_321 \\
-0.1034 & AOD\_321.5 \\
-0.1031 & AOD\_322 \\
-0.1036 & AOD\_322.5 \\
-0.104 & AOD\_323 \\
-0.1036 & AOD\_323.5 \\
-0.1044 & AOD\_324 \\
-0.104 & AOD\_324.5 \\
-0.1036 & AOD\_325 \\
-0.1024 & AOD\_325.5 \\
-0.1032 & AOD\_326 \\
-0.1016 & AOD\_326.5 \\
-0.1008 & AOD\_327 \\
-0.1025 & AOD\_327.5 \\
-0.1036 & AOD\_328 \\
-0.1041 & AOD\_328.5 \\
-0.1047 & AOD\_329 \\
-0.1042 & AOD\_329.5 \\
-0.1059 & AOD\_330 \\
-0.1055 & AOD\_330.5 \\
-0.1041 & AOD\_331 \\
-0.1045 & AOD\_331.5 \\
-0.1038 & AOD\_332 \\
-0.1074 & AOD\_332.5 \\
-0.1079 & AOD\_333 \\
-0.1083 & AOD\_333.5 \\
-0.1089 & AOD\_334 \\
-0.1102 & AOD\_334.5 \\
-0.1103 & AOD\_335 \\
-0.1098 & AOD\_335.5 \\
-0.11 & AOD\_336 \\
-0.1103 & AOD\_336.5 \\
-0.11 & AOD\_337 \\
-0.1108 & AOD\_337.5 \\
-0.1092 & AOD\_338 \\
-0.1103 & AOD\_338.5 \\
-0.1097 & AOD\_339 \\
-0.109 & AOD\_339.5 \\
-0.1087 & AOD\_340 \\
-0.1091 & AOD\_340.5 \\
-0.1094 & AOD\_341 \\
-0.1097 & AOD\_341.5 \\
-0.1098 & AOD\_342 \\
-0.1114 & AOD\_342.5 \\
-0.1088 & AOD\_343 \\
-0.1086 & AOD\_343.5 \\
-0.1088 & AOD\_344 \\
-0.1082 & AOD\_344.5 \\
-0.1083 & AOD\_345 \\
-0.1104 & AOD\_345.5 \\
-0.1104 & AOD\_346 \\
-0.1103 & AOD\_346.5 \\
-0.1091 & AOD\_347 \\
-0.109 & AOD\_347.5 \\
-0.1085 & AOD\_348 \\
-0.1082 & AOD\_348.5 \\
-0.1093 & AOD\_349 \\
-0.1079 & AOD\_349.5 \\
-0.1062 & AOD\_350 \\
-0.1042 & AOD\_350.5 \\
-0.1049 & AOD\_351 \\
-0.104 & AOD\_351.5 \\
-0.1034 & AOD\_352 \\
-0.1042 & AOD\_352.5 \\
-0.1075 & AOD\_353 \\
-0.1079 & AOD\_353.5 \\
-0.1085 & AOD\_354 \\
-0.1135 & AOD\_354.5 \\
-0.1145 & AOD\_355 \\
-0.1137 & AOD\_355.5 \\
-0.1135 & AOD\_356 \\
-0.1151 & AOD\_356.5 \\
-0.1154 & AOD\_357 \\
-0.1148 & AOD\_357.5 \\
-0.1163 & AOD\_358 \\
-0.1174 & AOD\_358.5 \\
-0.1179 & AOD\_359 \\
-0.1181 & AOD\_359.5 \\
-0.1197 & AOD\_360 \\
-0.1188 & AOD\_360.5 \\
-0.1179 & AOD\_361 \\
-0.1155 & AOD\_361.5 \\
-0.1236 & AOD\_362 \\
-0.1082 & AOD\_362.5 \\
-0.08471 & AOD\_363 \\
+0.07434 & AOD\_292.5 \\
+0.06485 & AOD\_293 \\
+0.03045 & AOD\_293.5 \\
+0.003635 & AOD\_294 \\
+0.003565 & AOD\_294.5 \\
+0.01818 & AOD\_295 \\
+0.02132 & AOD\_295.5 \\
+0.03856 & AOD\_296 \\
+0.05433 & AOD\_296.5 \\
+0.05082 & AOD\_297 \\
+0.04256 & AOD\_297.5 \\
+0.04915 & AOD\_298 \\
+0.05339 & AOD\_298.5 \\
+0.0521 & AOD\_299 \\
+0.0563 & AOD\_299.5 \\
+0.05211 & AOD\_300 \\
+0.05446 & AOD\_300.5 \\
+0.05641 & AOD\_301 \\
+0.05911 & AOD\_301.5 \\
+0.05837 & AOD\_302 \\
+0.05654 & AOD\_302.5 \\
+0.05637 & AOD\_303 \\
+0.05911 & AOD\_303.5 \\
+0.06221 & AOD\_304 \\
+0.0617 & AOD\_304.5 \\
+0.06055 & AOD\_305 \\
+0.05969 & AOD\_305.5 \\
+0.06106 & AOD\_306 \\
+0.06151 & AOD\_306.5 \\
+0.06109 & AOD\_307 \\
+0.06102 & AOD\_307.5 \\
+0.06112 & AOD\_308 \\
+0.05896 & AOD\_308.5 \\
+0.05981 & AOD\_309 \\
+0.06092 & AOD\_309.5 \\
+0.06128 & AOD\_310 \\
+0.06248 & AOD\_310.5 \\
+0.06266 & AOD\_311 \\
+0.06244 & AOD\_311.5 \\
+0.06146 & AOD\_312 \\
+0.06306 & AOD\_312.5 \\
+0.06236 & AOD\_313 \\
+0.06216 & AOD\_313.5 \\
+0.06163 & AOD\_314 \\
+0.06109 & AOD\_314.5 \\
+0.06058 & AOD\_315 \\
+0.06143 & AOD\_315.5 \\
+0.06154 & AOD\_316 \\
+0.06132 & AOD\_316.5 \\
+0.06198 & AOD\_317 \\
+0.06208 & AOD\_317.5 \\
+0.06153 & AOD\_318 \\
+0.06167 & AOD\_318.5 \\
+0.06209 & AOD\_319 \\
+0.06263 & AOD\_319.5 \\
+0.06239 & AOD\_320 \\
+0.06294 & AOD\_320.5 \\
+0.06408 & AOD\_321 \\
+0.06103 & AOD\_321.5 \\
+0.06081 & AOD\_322 \\
+0.06198 & AOD\_322.5 \\
+0.06209 & AOD\_323 \\
+0.06283 & AOD\_323.5 \\
+0.06396 & AOD\_324 \\
+0.06505 & AOD\_324.5 \\
+0.06508 & AOD\_325 \\
+0.06573 & AOD\_325.5 \\
+0.06572 & AOD\_326 \\
+0.06501 & AOD\_326.5 \\
+0.06474 & AOD\_327 \\
+0.0639 & AOD\_327.5 \\
+0.0644 & AOD\_328 \\
+0.06489 & AOD\_328.5 \\
+0.06504 & AOD\_329 \\
+0.0651 & AOD\_329.5 \\
+0.06543 & AOD\_330 \\
+0.06558 & AOD\_330.5 \\
+0.06525 & AOD\_331 \\
+0.06546 & AOD\_331.5 \\
+0.06584 & AOD\_332 \\
+0.06598 & AOD\_332.5 \\
+0.06566 & AOD\_333 \\
+0.06592 & AOD\_333.5 \\
+0.06643 & AOD\_334 \\
+0.06669 & AOD\_334.5 \\
+0.06659 & AOD\_335 \\
+0.06676 & AOD\_335.5 \\
+0.06725 & AOD\_336 \\
+0.06766 & AOD\_336.5 \\
+0.06754 & AOD\_337 \\
+0.06775 & AOD\_337.5 \\
+0.06769 & AOD\_338 \\
+0.06857 & AOD\_338.5 \\
+0.06795 & AOD\_339 \\
+0.06759 & AOD\_339.5 \\
+0.06771 & AOD\_340 \\
+0.06853 & AOD\_340.5 \\
+0.06766 & AOD\_341 \\
+0.06773 & AOD\_341.5 \\
+0.06835 & AOD\_342 \\
+0.06879 & AOD\_342.5 \\
+0.06639 & AOD\_343 \\
+0.06634 & AOD\_343.5 \\
+0.06638 & AOD\_344 \\
+0.06642 & AOD\_344.5 \\
+0.06593 & AOD\_345 \\
+0.06787 & AOD\_345.5 \\
+0.06794 & AOD\_346 \\
+0.06754 & AOD\_346.5 \\
+0.06782 & AOD\_347 \\
+0.06901 & AOD\_347.5 \\
+0.06837 & AOD\_348 \\
+0.06846 & AOD\_348.5 \\
+0.06928 & AOD\_349 \\
+0.06937 & AOD\_349.5 \\
+0.06896 & AOD\_350 \\
+0.07022 & AOD\_350.5 \\
+0.07031 & AOD\_351 \\
+0.06975 & AOD\_351.5 \\
+0.06989 & AOD\_352 \\
+0.07064 & AOD\_352.5 \\
+0.07133 & AOD\_353 \\
+0.07209 & AOD\_353.5 \\
+0.07342 & AOD\_354 \\
+0.07431 & AOD\_354.5 \\
+0.07486 & AOD\_355 \\
+0.07434 & AOD\_355.5 \\
+0.07405 & AOD\_356 \\
+0.07435 & AOD\_356.5 \\
+0.07383 & AOD\_357 \\
+0.07229 & AOD\_357.5 \\
+0.07375 & AOD\_358 \\
+0.07471 & AOD\_358.5 \\
+0.07492 & AOD\_359 \\
+0.07484 & AOD\_359.5 \\
+0.07569 & AOD\_360 \\
+0.07545 & AOD\_360.5 \\
+0.07436 & AOD\_361 \\
+0.07164 & AOD\_361.5 \\
+0.07609 & AOD\_362 \\
+0.05581 & AOD\_362.5 \\
+0.0216 & AOD\_363 \\
 \end{longtable}
@@
 \begin{verbatim}
-range 0.0593665 0.1665588 
+range 0.00356534 0.0760932 
 \end{verbatim}
@@
 
+\begin{verbatim}
+
+Call:
+lm(formula = export$Brewer_AOD340 ~ export$Cimel_AOD340)
+
+Residuals:
+      Min        1Q    Median        3Q       Max 
+-0.107947 -0.035666  0.002093  0.019482  0.312855
+
+Coefficients:
+                    Estimate Std. Error t value Pr(>|t|)    
+(Intercept)          0.09636    0.01866   5.163 1.37e-06 ***
+export$Cimel_AOD340  0.69840    0.04813  14.511  < 2e-16 ***
+---
+Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+
+Residual standard error: 0.05916 on 93 degrees of freedom
+  (195 observations deleted due to missingness)
+Multiple R-squared:  0.6936,    Adjusted R-squared:  0.6904 
+F-statistic: 210.6 on 1 and 93 DF,  p-value: < 2.2e-16
+\end{verbatim}
+
+\begin{verbatim}
+
+Call:
+lm(formula = export$Brewer_AOD340 ~ 0 + export$Cimel_AOD340)
+
+Residuals:
+     Min       1Q   Median       3Q      Max 
+-0.17265 -0.02907  0.00868  0.03643  0.31808
+
+Coefficients:
+                    Estimate Std. Error t value Pr(>|t|)    
+export$Cimel_AOD340  0.93340    0.01766   52.85   <2e-16 ***
+---
+Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+
+Residual standard error: 0.06675 on 94 degrees of freedom
+  (195 observations deleted due to missingness)
+Multiple R-squared:  0.9674,    Adjusted R-squared:  0.9671 
+F-statistic:  2793 on 1 and 94 DF,  p-value: < 2.2e-16
+\end{verbatim}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-145}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-145}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_read_aod_brewer_files/figure-latex/unnamed-chunk-4-146}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4-146}
+\end{figure}
+
 \textbf{END}

### 2024-09-05 GHI_enh_07_Aerosols_BR_CIM.R
Commit 2024-09-05 10:14

@@ -85,6 +85,7 @@ library(ggh4x         , quietly = TRUE, warn.conflicts = FALSE)
 library(grid          , quietly = TRUE, warn.conflicts = FALSE)
 library(latex2exp     , quietly = TRUE, warn.conflicts = FALSE)
 library(cowplot       , quietly = TRUE, warn.conflicts = FALSE)
+library(lubridate     , quietly = TRUE, warn.conflicts = FALSE)
 
 source("./GHI_enh_00_variables.R")
 source("./GHI_enh_00_dictionary.R")
@@ -97,7 +98,7 @@ CS <- readRDS("~/LibRadTranG/Clear_sky_model_AERONET_monthly/Model_CS_trend_fix_
 
 CS <- CS[, .(year, month, sza, edir, edn, typer, atmosphere_file)]
 CS[, glo := (edir + edn) / 1000 ]
-CS[, tsy := year + (month - 1) / 12]
+CS[, tsy := decimal_date(Date)]
 
 CS[, Date := as.POSIXct(as.Date(paste(year, month, 1), "%Y %m %d")) ]
 
@@ -144,7 +145,8 @@ legend("topleft", pch = 1, lty = NA, bty = "n", lwd = 2, cex = 1,
 ## create mean of each month for continuity
 
 COM <- CS[, .(glo = mean(glo)), by = Date]
-COM[, tsy := year(Date) + (month(Date) - 1) / 12]
+# COM[, tsy := year(Date) + (month(Date) - 1) / 12]
+COM[, tsy := decimal_date(Date)]
 
 
 
@@ -153,10 +155,36 @@ ggplot(data = COM, aes(x = tsy, y = glo)) +
   geom_point()
 
 
-plot(COM[, glo, tsy])
-lmm <- lm(COM[, glo] ~ COM[, tsy])
+xlim <- range(1994, COM[, tsy])
+plot(COM[, glo, tsy],
+     xlim = xlim)
+
+lmm  <- lm(    COM[, glo]  ~ COM[, tsy])
+logm <- lm(log(COM[, glo]) ~ COM[, tsy])
+polm <- lm(COM[, glo] ~ poly(COM[, tsy], 2, raw=TRUE))
+
+logm_C <- coef(logm)
+polym_C <- coef(polm)
+
+summary(polm)
 
 abline(lmm, col = "green")
+
+
+## create range to plot
+t <- (tsy = seq(1994, 2024, 0.1))
+
+
[…]

### 2024-09-05 GHI_enh_02_ID_CE.R
Commit 2024-09-05 11:09

@@ -263,24 +263,19 @@ csmodel <- "Low_B.Low_W"
 
 
 if (APPLY_TRANS) {
-  source("./GHI_enh_07_Aerosols.R")
   cat("USING TRASPARENCY TREND\n")
+
+  # source("./GHI_enh_07_Aerosols.R")
   ## choose function
   # trans_trend <- trend_median
   # trans_trend <- trend_median_adj
-  trans_trend <- trend_55_adj
-
-
-  trans_trend(1995)
-  trend_55_adj(c(1995,1996))
-
+  # trans_trend <- trend_55_adj
 
   source("./GHI_enh_07_Aerosols_BR_CIM.R")
+  # trend_polyf(1994:2024)
+  # plot(trend_polyf(1994:2024), trend_55_adj(1994:2024))
+  trans_trend <- trend_polyf
 
-  polyf_rel(c(1995,1996))
-  polyf_rel(1995)
-
-  stop()
 } else {
   trans_trend <- function(x) {x * 0}
 }

### 2024-09-05 GHI_enh_05_distributions.R

@@ -566,6 +566,12 @@ plot(COMPLETE_monthly[, Complete, Date])
 
 hist(COMPLETE_monthly[, Complete])
 
+COMPLETE_yearly      <- DATA[, .(Complete = sum(!is.na(wattGLB))/.N) , by = .(year(Date))]
+# COMPLETE_monthly$Date <- as.POSIXct(strptime(paste(COMPLETE_monthly$year, COMPLETE_monthly$month, "1"),"%Y %m %d"))
+
+
+
+
 
 
 ##  Climatology of CE   ----------------------------------------------

### 2024-09-05 article/article.Rmd
Commit 2024-09-05 12:14

@@
 
-In this study our main focus was to quantify the OI related to CEs. A
-key issue for achieving this goal is to define a threshold for the CE
-identification, representative of the clear-sky irradiance at the time of each GHI
-measurement. This depends on the selection of the appropriate atmospheric
-parameterization for the RTM simulations. The implementation of the long-term change
-in AOD, discussed in section\nobreakspace{}\ref{rtmcs}, allows capturing a large part
-of the natural variability of clear-sky GHI. However, the short-term variability of
-AOD cannot be taken adequately into account when using monthly values in the model
-simulations. We tried different approaches to strengthen the robustness of
-the methodology and to compensate for the limited accuracy of the RTM input data and
-the unpredictable natural variability of the atmosphere.
+One of the goals of this study was to quantify the OI related to CEs. A key issue for
+achieving this goal is to define a threshold for the CE identification,
+representative of the clear-sky irradiance at the time of each GHI measurement. This
+depends on the selection of the appropriate atmospheric parameterization for the RTM
+simulations. The implementation of the long-term change in AOD, discussed in
+section\nobreakspace{}\ref{rtmcs}, allows capturing a large part of the natural
+variability of clear-sky GHI. However, the short-term variability of AOD cannot be
+taken adequately into account when using monthly values in the model simulations. We
+tried different approaches to strengthen the robustness of the methodology and to
+compensate for the limited accuracy of the RTM input data and the unpredictable
+natural variability of the atmosphere.
 
@@
 events. These are cases of CE where the measured intensity of the irradiance exceeds
-the TSI at the top of the atmosphere. In this case the threshold $E$ is given by:
+the TSI on horizontal plane at TOA. In this case the threshold $E$ is given by:
 \begin{equation}

### 2024-09-05 article/article.tex
Commit 2024-09-04 10:14
Commit 2024-09-05 12:14

@@
 collocated Cimel sun photometer and a Brewer spectrophotometer. We found
-a trend in CE events of \(+46\pm 22\,\text{cases}/\text{year}\), and a
+a trend in CE events of \(+85\pm 20\,\text{cases}/\text{year}\), and a
 trend in the CE events irradiation of
-\(+116.3\pm 68.2\,\text{kJ}/\text{year}\). The peak of the CE events was
+\(+226.4\pm 62.6\,\text{kJ}/\text{year}\). The peak of the CE events was
 observed during May and June. An analysis of the total duration of CE
@@
 According to \citet{Kazadzis2007}, in the period 1997 -- 2005 the mean
-AOD at \(340\,\text{nm}\) is \(0.403\) with a change of
+AOD at \(340\,\text{nm}\) is \(0.4\) with a change of
 \(-3.8\pm0.93\,\%\) per year, corresponding to a change of \(0.0153\)
@@
 
-In this study our main focus was to quantify the OI related to CEs. A
+One of the goals of this study was to quantify the OI related to CEs. A
 key issue for achieving this goal is to define a threshold for the CE
@@
 extreme cloud enhancement (ECE) events. These are cases of CE where the
-measured intensity of the irradiance exceeds the TSI at the top of the
-atmosphere. In this case the threshold \(E\) is given by:
-\begin{equation}
+measured intensity of the irradiance exceeds the TSI on horizontal plane
+at TOA. In this case the threshold \(E\) is given by: \begin{equation}
 \text{ECE}: E > \cos(\text{SZA}) \cdot E_{\odot} \frac{r^2_\text{m}} {r^2}
@@
 entire dataset (\(6\) million of one-minute GHI measurements),
-\(1.78\,\%\) were identified as CE events and \(0.04\,\%\) as ECE
+\(1.68\,\%\) were identified as CE events and \(0.04\,\%\) as ECE
 events. The highest recorded GHI due to CE was
 \(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007 at a SZA of
-\(19.9^\circ\) corresponding to OI of \(345.9\,\text{W}/\text{m}^2\) or
-\(32.3\,\%\) above the threshold. The strongest CE event of \(49.7\,\%\)
+\(19.9^\circ\) corresponding to OI of \(338.4\,\text{W}/\text{m}^2\) or
+\(31.4\,\%\) above the threshold. The strongest CE event of \(49.9\,\%\)
 above the clear sky threshold was observed on 28~October 2016 at a SZA
 of \(59.2^\circ\) with a GHI value of \(861.8\,\text{W}/\text{m}^2\) and
-a OI of \(286.1\,\text{W}/\text{m}^2\). Both cases are ECE events with
+a OI of \(286.9\,\text{W}/\text{m}^2\). Both cases are ECE events with
 \(136.8\,\text{W}/\text{m}^2\) and \(164.5\,\text{W}/\text{m}^2\) above
@@
 increasing trends, most pronounced for the frequency of occurrence
-(\(+46\pm 22\,\text{cases}/\text{year}\)) and the excess irradiation
-(\(+116.3 \pm 68.2\,\text{kJ}/\text{year}\)), which are also
+(\(+85\pm 20\,\text{cases}/\text{year}\)) and the excess irradiation
+(\(+226.4 \pm 62.6\,\text{kJ}/\text{year}\)), which are also
 statistically significant. In contrast the trend of the yearly mean OI
-is negligible (\(+0.03\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of
+is negligible (\(+0.12\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of
 no statistical significance. The average OI for the entire period is
-\(+40.1\pm 2.5\,\text{W}/\text{m}^2\). The interannual variability of
+\(+39.7\pm 2.8\,\text{W}/\text{m}^2\). The interannual variability of
 the data about the trend lines is quite large. Furthermore, the spread
@@
 events. For the majority (over \(62\,\%\)) of the CE events the OI is
-below the long-term average of \(40.1\,\text{W}/\text{m}^2\), while
+below the long-term average of \(39.7\,\text{W}/\text{m}^2\), while
 about \(8.1\,\%\) of the events correspond to OI larger than
@@
 of these consecutive events, we grouped them into bins of increasing
-duration in steps of one minute. We have identified 28182 groups of CE
+duration in steps of one minute. We have identified 26837 groups of CE
 in the whole period of study, where the group of the longest duration of
@@
 After analyzing the CE cases, we found an increase of
-\(+45.6\pm 22\,\text{cases}/\text{year}\), with the mean annual
+\(+85.3\pm 20\,\text{cases}/\text{year}\), with the mean annual
 irradiation of the CE events increasing with a rate of
-\(+116.3\pm 68.2\,\text{kJ}/\text{year}\). The most active months of CE
+\(+226.4\pm 62.6\,\text{kJ}/\text{year}\). The most active months of CE
 events are May and June. We found that continuous CE events can last up

### 2024-09-05 GHI_enh_03_process.tex
Commit 2024-09-05 12:14

@@
 \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
 \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
@@
 \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
 \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
@@
 \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
 \newcommand{\ImportTok}[1]{#1}
@@
 \newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
 \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-08-29}
+\date{2024-09-05}
 
@@
    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
-   0.00   89.59  180.00  180.00  270.42  360.00 
+   0.00   89.58  180.00  180.00  270.42  360.00 
 \end{verbatim}
@@
     Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
--72.8133 -27.4712   0.7647   0.4304  28.2448  83.4876 
+-72.8133 -27.4706   0.7672   0.4338  28.2495  83.4876 
 \end{verbatim}
@@
 
-\hypertarget{time-series-decomposition-tests}{%
-\subsection{Time series decomposition tests}\label{time-series-decomposition-tests}}
+\subsection{Time series decomposition tests}\label{time-series-decomposition-tests}
 
@@
 \begin{verbatim}
+
 Call:
@@
     Min      1Q  Median      3Q     Max 
--317.54 -148.95  -56.71  107.07  717.24
+-333.34 -132.29  -52.26   96.74  664.64
 
@@
                   Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      1.533e+02  4.805e+01   3.190  0.00155 **
-as.numeric(Date) 1.203e-07  3.816e-08   3.153  0.00175 **
+(Intercept)      7.113e+00  4.604e+01   0.155    0.877    
+as.numeric(Date) 2.252e-07  3.656e-08   6.160 1.98e-09 ***
 ---
@@
 
-Residual standard error: 197.8 on 354 degrees of freedom
-Multiple R-squared:  0.02732,   Adjusted R-squared:  0.02457 
-F-statistic: 9.943 on 1 and 354 DF,  p-value: 0.001752
+Residual standard error: 189.5 on 354 degrees of freedom
+Multiple R-squared:  0.09681,   Adjusted R-squared:  0.09426 
+F-statistic: 37.94 on 1 and 354 DF,  p-value: 1.979e-09
 \end{verbatim}
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       1.533e+02  4.805e+01   3.190  0.00155 **
-ST_E_monthly$Date 1.203e-07  3.816e-08   3.153  0.00175 **
+(Intercept)       7.113e+00  4.604e+01   0.155    0.877    
+ST_E_monthly$Date 2.252e-07  3.656e-08   6.160 1.98e-09 ***
 ---
@@
 aa
-aatm
 aday
-adjpoint55
-AEin1
 All_daily_ratio_lim
 alpha
-amean
 ampl
-asza
-atype
 avar
-b
 BIO_ELEVA
@@
 Energy_Div
-fit
 I1_longterm
@@
 Kurudz_SC
-lm_mean
-lm_zeropoint
-mean_55
-mean_BR_55
-mean_BR_mean
-mean_BR_median
-mean_BR_min
-mean_mean
-mean_median
-mean_min
-mid
+logm_C
 MIN_ELEVA
 MIN_N
-mm
 Monthly_aggegation_N_lim
@@
 my.cols.gr
+polyf_zero
+polym_C
 pyear
@@
 SelEnhanc
-slope_55
-slope_mean
-slope_median
-slope_min
 solar_constant
@@
 tsy
-units
+tzero
 variables_fl
@@
 ylim
-zeropoint
-zeropointA
 ST_daily
@@
 \begin{verbatim}
-2024-08-29 10:26:26.0 athan@sagan GHI_enh_03_process.R 3.652528 mins
+2024-09-05 08:08:34.0 athan@sagan GHI_enh_03_process.R 5.165189 mins
 \end{verbatim}

### 2024-09-05 GHI_enh_04_investigate.tex
Commit 2024-08-29 20:14
Commit 2024-08-30 20:14
Commit 2024-08-30 21:12
Commit 2024-08-31 13:12
Commit 2024-09-05 12:14

--- 2024-08-26 GHI_enh_04_investigate.tex
@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-08-26}
+\date{2024-09-05}
 
@@
 \begin{verbatim}
-Warning: Removed 246 rows containing non-finite outside the scale range
+Warning: Removed 220 rows containing non-finite outside the scale range
 (`stat_bin()`).
@@
 \begin{verbatim}
-Warning: Removed 27787 rows containing non-finite outside the scale range
+Warning: Removed 26591 rows containing non-finite outside the scale range
 (`stat_bin()`).
@@
 \begin{verbatim}
-Warning: Removed 246 rows containing non-finite outside the scale range
-(`stat_bin()`).
-Removed 27787 rows containing non-finite outside the scale range
-(`stat_bin()`).
+Warning: Removed 220 rows containing non-finite outside the scale range (`stat_bin()`).
+Removed 26591 rows containing non-finite outside the scale range (`stat_bin()`).
 \end{verbatim}
@@
 \begin{verbatim}
-Warning: Removed 15 rows containing non-finite outside the scale range
+Warning: Removed 14 rows containing non-finite outside the scale range
 (`stat_bin2d()`).
@@
 
-lmY: 116.8672 +/- 33.89196
+lmY: 226.3963 +/- 31.30176
 
@@
 
-lmY: 45.58799 +/- 10.96835
+lmY: 85.26719 +/- 10.01748
 
@@
 
-lmY: 0.029427 +/- 0.054286
+lmY: 0.116043 +/- 0.055572
 
@@
 
-lmY: 0.03518 +/- 0.042507
+lmY: 0.107931 +/- 0.044598
 
@@
 
-lmY: 116.3147 +/- 30.85223
+lmY: 222.2785 +/- 28.96957
 
@@
 
-lmY: 45.55073 +/- 10.16657
+lmY: 83.81382 +/- 9.456821
 
@@
 \caption{ - empty caption - }\label{fig:P-MW-energy-2}
+\end{figure}
+
+\newpage
+
+\hypertarget{yearly-trends-with-data-completeness}{%
+\subsection{Yearly trends with data completeness}\label{yearly-trends-with-data-completeness}}
+
+lmY: 229.8063 +/- 39.56838
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-energy-complete-1}
+\end{figure}
+
+lmY: 86.21667 +/- 12.87325
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-2}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-energy-complete-2}
+\end{figure}
+
+lmY: 0.085425 +/- 0.09766
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-3}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-energy-complete-3}
+\end{figure}
+
+lmY: 0.086495 +/- 0.070955
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-4}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-energy-complete-4}
 \end{figure}
@@
 \begin{verbatim}
-2024-08-26 19:52:09.6 athan@sagan GHI_enh_04_investigate.R 0.838254 mins
+2024-09-05 08:56:04.2 athan@sagan GHI_enh_04_investigate.R 13.014418 mins
 \end{verbatim}

### 2024-09-05 GHI_enh_05_distributions.R
Commit 2024-09-05 13:11

@@ -522,14 +522,16 @@ ggplot(data = DATA[wattGLB > ETH], aes(x = wattGLB - ETH)) +
 
 ##  Store some date for max cases  ------------------------
 
-saveRDS(
-  rbind(
-    DATA[which.max(wattGLB),  .(Typ = "Max Glob", wattGLB, SZA, GLB_ench, GLB_diff, Date, ETH, CE = Enhanc_C_4, ECE = wattGLB > ETH)],
-    DATA[which.max(GLB_ench), .(Typ = "Max Enha", wattGLB, SZA, GLB_ench, GLB_diff, Date, ETH, CE = Enhanc_C_4, ECE = wattGLB > ETH)]
-  ),
-  "data/Max_cases.Rds"
+MC <-   rbind(
+  DATA[which.max(wattGLB),  .(Typ = "Max Glob", wattGLB, SZA, GLB_ench, GLB_diff, Date, ETH, CE = Enhanc_C_4, ECE = wattGLB > ETH)],
+  DATA[which.max(GLB_ench), .(Typ = "Max Enha", wattGLB, SZA, GLB_ench, GLB_diff, Date, ETH, CE = Enhanc_C_4, ECE = wattGLB > ETH)]
 )
+MC[ , DOY := yday(Date)]
+MC[ , Localtime := paste(as.POSIXlt(Date, tz = "Europe/Athens"))]
 
+pander::pander(MC)
+
+saveRDS(MC, "data/Max_cases.Rds")
 
 
 

### 2024-09-05 GHI_enh_05_distributions.R
Commit 2024-09-05 14:14

@@ -529,11 +529,20 @@ MC <-   rbind(
 MC[ , DOY := yday(Date)]
 MC[ , Localtime := paste(as.POSIXlt(Date, tz = "Europe/Athens"))]
 
-pander::pander(MC)
 
 saveRDS(MC, "data/Max_cases.Rds")
 
 
+pander::pander(MC, caption = "Max enhancements")
+
+MC2 <- ST_G0[which.max(GLB_diff.N), .(Date, GLB_diff.N)]
+MC2[ , DOY := yday(Date)]
+MC2[ , Localtime := paste(as.POSIXlt(Date, tz = "Europe/Athens"))]
+
+pander::pander(
+  MC2,
+  caption = "Max duration"
+)
 
 
 ## Test missing data  -------

### 2024-09-05 GHI_enh_03_process.tex
Commit 2024-09-05 23:10

@@
 \fi
-\usepackage{bookmark}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
-\hypersetup{
-  pdftitle={Enhancement of SDR in Thessaloniki},
-  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
-  colorlinks=true,
-  linkcolor={Maroon},
-  filecolor={Maroon},
-  citecolor={Blue},
-  urlcolor={Blue},
-  pdfcreator={LaTeX via pandoc}}
 
@@
 
-\subsection{Time series decomposition tests}\label{time-series-decomposition-tests}
+\hypertarget{time-series-decomposition-tests}{%
+\subsection{Time series decomposition tests}\label{time-series-decomposition-tests}}
 
@@
 \begin{verbatim}
-2024-09-05 08:08:34.0 athan@sagan GHI_enh_03_process.R 5.165189 mins
+2024-09-05 19:30:15.8 athan@sagan GHI_enh_03_process.R 3.894151 mins
 \end{verbatim}

### 2024-09-06 GHI_enh_daily_test_plots.tex
Commit 2024-09-06 10:14

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  a4paper,oneside]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{float}
\usepackage{placeins}
\captionsetup{font=small}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Enhancement of SDR in Thessaloniki},
  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-06}

\begin{document}
\maketitle
\begin{abstract}
Study of GHI enchantment.
\end{abstract}

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Warning:

 ** Test is active!! ** 
\end{verbatim}

\FloatBarrier

\section{Plot some days with strong enhancement cases}\label{plot-some-days-with-strong-enhancement-cases}

\FloatBarrier

\subsection{Days with extreme cases day}\label{days-with-extreme-cases-day}

\FloatBarrier

\subsection{Days with strong enhancement day}\label{days-with-strong-enhancement-day}

\FloatBarrier

\subsection{Days with sunny day}\label{days-with-sunny-day}

\FloatBarrier

\subsection{Days with sunny enhancement day}\label{days-with-sunny-enhancement-day}

\FloatBarrier

\subsection{Days with cloudy day}\label{days-with-cloudy-day}

\FloatBarrier

\subsection{Days with manual test days}\label{days-with-manual-test-days}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-1}

}

\caption{ - empty caption - }\label{fig:example-days-1}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-2}

}

\caption{ - empty caption - }\label{fig:example-days-2}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-3}

}

\caption{ - empty caption - }\label{fig:example-days-3}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-4}

}

\caption{ - empty caption - }\label{fig:example-days-4}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-5}

}

\caption{ - empty caption - }\label{fig:example-days-5}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-6}

}

\caption{ - empty caption - }\label{fig:example-days-6}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-7}

}

\caption{ - empty caption - }\label{fig:example-days-7}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-8}

}

\caption{ - empty caption - }\label{fig:example-days-8}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-9}

}

\caption{ - empty caption - }\label{fig:example-days-9}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-10}

}

\caption{ - empty caption - }\label{fig:example-days-10}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-11}

}

\caption{ - empty caption - }\label{fig:example-days-11}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-12}

}

\caption{ - empty caption - }\label{fig:example-days-12}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-13}

}

\caption{ - empty caption - }\label{fig:example-days-13}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-14}

}

\caption{ - empty caption - }\label{fig:example-days-14}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-15}

}

\caption{ - empty caption - }\label{fig:example-days-15}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-16}

}

\caption{ - empty caption - }\label{fig:example-days-16}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-17}

}

\caption{ - empty caption - }\label{fig:example-days-17}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-18}

}

\caption{ - empty caption - }\label{fig:example-days-18}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-19}

}

\caption{ - empty caption - }\label{fig:example-days-19}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-20}

}

\caption{ - empty caption - }\label{fig:example-days-20}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-21}

}

\caption{ - empty caption - }\label{fig:example-days-21}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-22}

}

\caption{ - empty caption - }\label{fig:example-days-22}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-23}

}

\caption{ - empty caption - }\label{fig:example-days-23}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-24}

}

\caption{ - empty caption - }\label{fig:example-days-24}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-25}

}

\caption{ - empty caption - }\label{fig:example-days-25}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-26}

}

\caption{ - empty caption - }\label{fig:example-days-26}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-27}

}

\caption{ - empty caption - }\label{fig:example-days-27}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-28}

}

\caption{ - empty caption - }\label{fig:example-days-28}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-29}

}

\caption{ - empty caption - }\label{fig:example-days-29}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-30}

}

\caption{ - empty caption - }\label{fig:example-days-30}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-31}

}

\caption{ - empty caption - }\label{fig:example-days-31}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-32}

}

\caption{ - empty caption - }\label{fig:example-days-32}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-33}

}

\caption{ - empty caption - }\label{fig:example-days-33}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-34}

}

\caption{ - empty caption - }\label{fig:example-days-34}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-35}

}

\caption{ - empty caption - }\label{fig:example-days-35}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-36}

}

\caption{ - empty caption - }\label{fig:example-days-36}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-37}

}

\caption{ - empty caption - }\label{fig:example-days-37}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-38}

}

\caption{ - empty caption - }\label{fig:example-days-38}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-39}

}

\caption{ - empty caption - }\label{fig:example-days-39}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-40}

}

\caption{ - empty caption - }\label{fig:example-days-40}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-41}

}

\caption{ - empty caption - }\label{fig:example-days-41}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-42}

}

\caption{ - empty caption - }\label{fig:example-days-42}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-43}

}

\caption{ - empty caption - }\label{fig:example-days-43}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-44}

}

\caption{ - empty caption - }\label{fig:example-days-44}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-45}

}

\caption{ - empty caption - }\label{fig:example-days-45}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-46}

}

\caption{ - empty caption - }\label{fig:example-days-46}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-47}

}

\caption{ - empty caption - }\label{fig:example-days-47}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-48}

}

\caption{ - empty caption - }\label{fig:example-days-48}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-49}

}

\caption{ - empty caption - }\label{fig:example-days-49}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-50}

}

\caption{ - empty caption - }\label{fig:example-days-50}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-51}

}

\caption{ - empty caption - }\label{fig:example-days-51}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-52}

}

\caption{ - empty caption - }\label{fig:example-days-52}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-53}

}

\caption{ - empty caption - }\label{fig:example-days-53}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-54}

}

\caption{ - empty caption - }\label{fig:example-days-54}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-55}

}

\caption{ - empty caption - }\label{fig:example-days-55}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-56}

}

\caption{ - empty caption - }\label{fig:example-days-56}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-57}

}

\caption{ - empty caption - }\label{fig:example-days-57}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-58}

}

\caption{ - empty caption - }\label{fig:example-days-58}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-59}

}

\caption{ - empty caption - }\label{fig:example-days-59}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-60}

}

\caption{ - empty caption - }\label{fig:example-days-60}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-61}

}

\caption{ - empty caption - }\label{fig:example-days-61}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-62}

}

\caption{ - empty caption - }\label{fig:example-days-62}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-63}

}

\caption{ - empty caption - }\label{fig:example-days-63}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-64}

}

\caption{ - empty caption - }\label{fig:example-days-64}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-65}

}

\caption{ - empty caption - }\label{fig:example-days-65}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-66}

}

\caption{ - empty caption - }\label{fig:example-days-66}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-67}

}

\caption{ - empty caption - }\label{fig:example-days-67}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-68}

}

\caption{ - empty caption - }\label{fig:example-days-68}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-69}

}

\caption{ - empty caption - }\label{fig:example-days-69}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-70}

}

\caption{ - empty caption - }\label{fig:example-days-70}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-71}

}

\caption{ - empty caption - }\label{fig:example-days-71}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-72}

}

\caption{ - empty caption - }\label{fig:example-days-72}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-73}

}

\caption{ - empty caption - }\label{fig:example-days-73}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-74}

}

\caption{ - empty caption - }\label{fig:example-days-74}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-75}

}

\caption{ - empty caption - }\label{fig:example-days-75}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-76}

}

\caption{ - empty caption - }\label{fig:example-days-76}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-77}

}

\caption{ - empty caption - }\label{fig:example-days-77}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-78}

}

\caption{ - empty caption - }\label{fig:example-days-78}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-79}

}

\caption{ - empty caption - }\label{fig:example-days-79}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-80}

}

\caption{ - empty caption - }\label{fig:example-days-80}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-81}

}

\caption{ - empty caption - }\label{fig:example-days-81}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-82}

}

\caption{ - empty caption - }\label{fig:example-days-82}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-83}

}

\caption{ - empty caption - }\label{fig:example-days-83}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-84}

}

\caption{ - empty caption - }\label{fig:example-days-84}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-85}

}

\caption{ - empty caption - }\label{fig:example-days-85}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-86}

}

\caption{ - empty caption - }\label{fig:example-days-86}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-87}

}

\caption{ - empty caption - }\label{fig:example-days-87}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-88}

}

\caption{ - empty caption - }\label{fig:example-days-88}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-89}

}

\caption{ - empty caption - }\label{fig:example-days-89}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-90}

}

\caption{ - empty caption - }\label{fig:example-days-90}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-91}

}

\caption{ - empty caption - }\label{fig:example-days-91}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-92}

}

\caption{ - empty caption - }\label{fig:example-days-92}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-93}

}

\caption{ - empty caption - }\label{fig:example-days-93}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-94}

}

\caption{ - empty caption - }\label{fig:example-days-94}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-95}

}

\caption{ - empty caption - }\label{fig:example-days-95}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-96}

}

\caption{ - empty caption - }\label{fig:example-days-96}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-97}

}

\caption{ - empty caption - }\label{fig:example-days-97}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-98}

}

\caption{ - empty caption - }\label{fig:example-days-98}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-99}

}

\caption{ - empty caption - }\label{fig:example-days-99}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-100}

}

\caption{ - empty caption - }\label{fig:example-days-100}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-101}

}

\caption{ - empty caption - }\label{fig:example-days-101}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-102}

}

\caption{ - empty caption - }\label{fig:example-days-102}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-103}

}

\caption{ - empty caption - }\label{fig:example-days-103}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-104}

}

\caption{ - empty caption - }\label{fig:example-days-104}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-105}

}

\caption{ - empty caption - }\label{fig:example-days-105}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-106}

}

\caption{ - empty caption - }\label{fig:example-days-106}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-107}

}

\caption{ - empty caption - }\label{fig:example-days-107}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-108}

}

\caption{ - empty caption - }\label{fig:example-days-108}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-109}

}

\caption{ - empty caption - }\label{fig:example-days-109}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-110}

}

\caption{ - empty caption - }\label{fig:example-days-110}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-111}

}

\caption{ - empty caption - }\label{fig:example-days-111}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-112}

}

\caption{ - empty caption - }\label{fig:example-days-112}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-113}

}

\caption{ - empty caption - }\label{fig:example-days-113}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-114}

}

\caption{ - empty caption - }\label{fig:example-days-114}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-115}

}

\caption{ - empty caption - }\label{fig:example-days-115}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-116}

}

\caption{ - empty caption - }\label{fig:example-days-116}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-117}

}

\caption{ - empty caption - }\label{fig:example-days-117}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-118}

}

\caption{ - empty caption - }\label{fig:example-days-118}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-119}

}

\caption{ - empty caption - }\label{fig:example-days-119}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-120}

}

\caption{ - empty caption - }\label{fig:example-days-120}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-121}

}

\caption{ - empty caption - }\label{fig:example-days-121}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-122}

}

\caption{ - empty caption - }\label{fig:example-days-122}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-123}

}

\caption{ - empty caption - }\label{fig:example-days-123}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-124}

}

\caption{ - empty caption - }\label{fig:example-days-124}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-125}

}

\caption{ - empty caption - }\label{fig:example-days-125}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-126}

}

\caption{ - empty caption - }\label{fig:example-days-126}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-127}

}

\caption{ - empty caption - }\label{fig:example-days-127}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-128}

}

\caption{ - empty caption - }\label{fig:example-days-128}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-129}

}

\caption{ - empty caption - }\label{fig:example-days-129}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-130}

}

\caption{ - empty caption - }\label{fig:example-days-130}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-131}

}

\caption{ - empty caption - }\label{fig:example-days-131}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-132}

}

\caption{ - empty caption - }\label{fig:example-days-132}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-133}

}

\caption{ - empty caption - }\label{fig:example-days-133}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-134}

}

\caption{ - empty caption - }\label{fig:example-days-134}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-135}

}

\caption{ - empty caption - }\label{fig:example-days-135}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-136}

}

\caption{ - empty caption - }\label{fig:example-days-136}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-137}

}

\caption{ - empty caption - }\label{fig:example-days-137}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-138}

}

\caption{ - empty caption - }\label{fig:example-days-138}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-139}

}

\caption{ - empty caption - }\label{fig:example-days-139}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-140}

}

\caption{ - empty caption - }\label{fig:example-days-140}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-141}

}

\caption{ - empty caption - }\label{fig:example-days-141}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-142}

}

\caption{ - empty caption - }\label{fig:example-days-142}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-143}

}

\caption{ - empty caption - }\label{fig:example-days-143}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-144}

}

\caption{ - empty caption - }\label{fig:example-days-144}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-145}

}

\caption{ - empty caption - }\label{fig:example-days-145}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-146}

}

\caption{ - empty caption - }\label{fig:example-days-146}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-147}

}

\caption{ - empty caption - }\label{fig:example-days-147}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-148}

}

\caption{ - empty caption - }\label{fig:example-days-148}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-149}

}

\caption{ - empty caption - }\label{fig:example-days-149}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-150}

}

\caption{ - empty caption - }\label{fig:example-days-150}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-151}

}

\caption{ - empty caption - }\label{fig:example-days-151}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-152}

}

\caption{ - empty caption - }\label{fig:example-days-152}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-153}

}

\caption{ - empty caption - }\label{fig:example-days-153}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-154}

}

\caption{ - empty caption - }\label{fig:example-days-154}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-155}

}

\caption{ - empty caption - }\label{fig:example-days-155}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-156}

}

\caption{ - empty caption - }\label{fig:example-days-156}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-157}

}

\caption{ - empty caption - }\label{fig:example-days-157}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-158}

}

\caption{ - empty caption - }\label{fig:example-days-158}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-159}

}

\caption{ - empty caption - }\label{fig:example-days-159}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-160}

}

\caption{ - empty caption - }\label{fig:example-days-160}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-161}

}

\caption{ - empty caption - }\label{fig:example-days-161}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-162}

}

\caption{ - empty caption - }\label{fig:example-days-162}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-163}

}

\caption{ - empty caption - }\label{fig:example-days-163}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-164}

}

\caption{ - empty caption - }\label{fig:example-days-164}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-165}

}

\caption{ - empty caption - }\label{fig:example-days-165}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-166}

}

\caption{ - empty caption - }\label{fig:example-days-166}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-167}

}

\caption{ - empty caption - }\label{fig:example-days-167}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-168}

}

\caption{ - empty caption - }\label{fig:example-days-168}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-169}

}

\caption{ - empty caption - }\label{fig:example-days-169}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-170}

}

\caption{ - empty caption - }\label{fig:example-days-170}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-171}

}

\caption{ - empty caption - }\label{fig:example-days-171}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-172}

}

\caption{ - empty caption - }\label{fig:example-days-172}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-173}

}

\caption{ - empty caption - }\label{fig:example-days-173}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-174}

}

\caption{ - empty caption - }\label{fig:example-days-174}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-175}

}

\caption{ - empty caption - }\label{fig:example-days-175}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-176}

}

\caption{ - empty caption - }\label{fig:example-days-176}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-177}

}

\caption{ - empty caption - }\label{fig:example-days-177}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-178}

}

\caption{ - empty caption - }\label{fig:example-days-178}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-179}

}

\caption{ - empty caption - }\label{fig:example-days-179}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-180}

}

\caption{ - empty caption - }\label{fig:example-days-180}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-181}

}

\caption{ - empty caption - }\label{fig:example-days-181}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-182}

}

\caption{ - empty caption - }\label{fig:example-days-182}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-183}

}

\caption{ - empty caption - }\label{fig:example-days-183}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-184}

}

\caption{ - empty caption - }\label{fig:example-days-184}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-185}

}

\caption{ - empty caption - }\label{fig:example-days-185}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-186}

}

\caption{ - empty caption - }\label{fig:example-days-186}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-187}

}

\caption{ - empty caption - }\label{fig:example-days-187}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-188}

}

\caption{ - empty caption - }\label{fig:example-days-188}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-189}

}

\caption{ - empty caption - }\label{fig:example-days-189}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-190}

}

\caption{ - empty caption - }\label{fig:example-days-190}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-191}

}

\caption{ - empty caption - }\label{fig:example-days-191}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-192}

}

\caption{ - empty caption - }\label{fig:example-days-192}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-193}

}

\caption{ - empty caption - }\label{fig:example-days-193}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-194}

}

\caption{ - empty caption - }\label{fig:example-days-194}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-195}

}

\caption{ - empty caption - }\label{fig:example-days-195}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-196}

}

\caption{ - empty caption - }\label{fig:example-days-196}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-197}

}

\caption{ - empty caption - }\label{fig:example-days-197}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-198}

}

\caption{ - empty caption - }\label{fig:example-days-198}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-199}

}

\caption{ - empty caption - }\label{fig:example-days-199}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-200}

}

\caption{ - empty caption - }\label{fig:example-days-200}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-201}

}

\caption{ - empty caption - }\label{fig:example-days-201}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-202}

}

\caption{ - empty caption - }\label{fig:example-days-202}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-203}

}

\caption{ - empty caption - }\label{fig:example-days-203}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-204}

}

\caption{ - empty caption - }\label{fig:example-days-204}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-205}

}

\caption{ - empty caption - }\label{fig:example-days-205}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-206}

}

\caption{ - empty caption - }\label{fig:example-days-206}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-207}

}

\caption{ - empty caption - }\label{fig:example-days-207}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-208}

}

\caption{ - empty caption - }\label{fig:example-days-208}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-209}

}

\caption{ - empty caption - }\label{fig:example-days-209}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-210}

}

\caption{ - empty caption - }\label{fig:example-days-210}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-211}

}

\caption{ - empty caption - }\label{fig:example-days-211}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-212}

}

\caption{ - empty caption - }\label{fig:example-days-212}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-213}

}

\caption{ - empty caption - }\label{fig:example-days-213}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-214}

}

\caption{ - empty caption - }\label{fig:example-days-214}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-215}

}

\caption{ - empty caption - }\label{fig:example-days-215}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-216}

}

\caption{ - empty caption - }\label{fig:example-days-216}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-217}

}

\caption{ - empty caption - }\label{fig:example-days-217}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-218}

}

\caption{ - empty caption - }\label{fig:example-days-218}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-219}

}

\caption{ - empty caption - }\label{fig:example-days-219}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-220}

}

\caption{ - empty caption - }\label{fig:example-days-220}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-221}

}

\caption{ - empty caption - }\label{fig:example-days-221}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-222}

}

\caption{ - empty caption - }\label{fig:example-days-222}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-223}

}

\caption{ - empty caption - }\label{fig:example-days-223}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-224}

}

\caption{ - empty caption - }\label{fig:example-days-224}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-225}

}

\caption{ - empty caption - }\label{fig:example-days-225}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-226}

}

\caption{ - empty caption - }\label{fig:example-days-226}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-227}

}

\caption{ - empty caption - }\label{fig:example-days-227}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-228}

}

\caption{ - empty caption - }\label{fig:example-days-228}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-229}

}

\caption{ - empty caption - }\label{fig:example-days-229}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-230}

}

\caption{ - empty caption - }\label{fig:example-days-230}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-231}

}

\caption{ - empty caption - }\label{fig:example-days-231}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-232}

}

\caption{ - empty caption - }\label{fig:example-days-232}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-233}

}

\caption{ - empty caption - }\label{fig:example-days-233}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-234}

}

\caption{ - empty caption - }\label{fig:example-days-234}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-235}

}

\caption{ - empty caption - }\label{fig:example-days-235}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-236}

}

\caption{ - empty caption - }\label{fig:example-days-236}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-237}

}

\caption{ - empty caption - }\label{fig:example-days-237}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-238}

}

\caption{ - empty caption - }\label{fig:example-days-238}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-239}

}

\caption{ - empty caption - }\label{fig:example-days-239}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-240}

}

\caption{ - empty caption - }\label{fig:example-days-240}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-241}

}

\caption{ - empty caption - }\label{fig:example-days-241}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-242}

}

\caption{ - empty caption - }\label{fig:example-days-242}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-243}

}

\caption{ - empty caption - }\label{fig:example-days-243}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-244}

}

\caption{ - empty caption - }\label{fig:example-days-244}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-245}

}

\caption{ - empty caption - }\label{fig:example-days-245}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-246}

}

\caption{ - empty caption - }\label{fig:example-days-246}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-247}

}

\caption{ - empty caption - }\label{fig:example-days-247}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-248}

}

\caption{ - empty caption - }\label{fig:example-days-248}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-249}

}

\caption{ - empty caption - }\label{fig:example-days-249}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-250}

}

\caption{ - empty caption - }\label{fig:example-days-250}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-251}

}

\caption{ - empty caption - }\label{fig:example-days-251}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-252}

}

\caption{ - empty caption - }\label{fig:example-days-252}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-253}

}

\caption{ - empty caption - }\label{fig:example-days-253}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-254}

}

\caption{ - empty caption - }\label{fig:example-days-254}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-255}

}

\caption{ - empty caption - }\label{fig:example-days-255}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-256}

}

\caption{ - empty caption - }\label{fig:example-days-256}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-257}

}

\caption{ - empty caption - }\label{fig:example-days-257}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-258}

}

\caption{ - empty caption - }\label{fig:example-days-258}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-259}

}

\caption{ - empty caption - }\label{fig:example-days-259}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-260}

}

\caption{ - empty caption - }\label{fig:example-days-260}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-261}

}

\caption{ - empty caption - }\label{fig:example-days-261}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-262}

}

\caption{ - empty caption - }\label{fig:example-days-262}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-263}

}

\caption{ - empty caption - }\label{fig:example-days-263}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-264}

}

\caption{ - empty caption - }\label{fig:example-days-264}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-265}

}

\caption{ - empty caption - }\label{fig:example-days-265}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-266}

}

\caption{ - empty caption - }\label{fig:example-days-266}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-267}

}

\caption{ - empty caption - }\label{fig:example-days-267}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-268}

}

\caption{ - empty caption - }\label{fig:example-days-268}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-269}

}

\caption{ - empty caption - }\label{fig:example-days-269}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-270}

}

\caption{ - empty caption - }\label{fig:example-days-270}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-271}

}

\caption{ - empty caption - }\label{fig:example-days-271}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-272}

}

\caption{ - empty caption - }\label{fig:example-days-272}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-273}

}

\caption{ - empty caption - }\label{fig:example-days-273}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-274}

}

\caption{ - empty caption - }\label{fig:example-days-274}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-275}

}

\caption{ - empty caption - }\label{fig:example-days-275}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-276}

}

\caption{ - empty caption - }\label{fig:example-days-276}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-277}

}

\caption{ - empty caption - }\label{fig:example-days-277}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-278}

}

\caption{ - empty caption - }\label{fig:example-days-278}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-279}

}

\caption{ - empty caption - }\label{fig:example-days-279}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-280}

}

\caption{ - empty caption - }\label{fig:example-days-280}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-281}

}

\caption{ - empty caption - }\label{fig:example-days-281}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-282}

}

\caption{ - empty caption - }\label{fig:example-days-282}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-283}

}

\caption{ - empty caption - }\label{fig:example-days-283}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-284}

}

\caption{ - empty caption - }\label{fig:example-days-284}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-285}

}

\caption{ - empty caption - }\label{fig:example-days-285}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-286}

}

\caption{ - empty caption - }\label{fig:example-days-286}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-287}

}

\caption{ - empty caption - }\label{fig:example-days-287}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-288}

}

\caption{ - empty caption - }\label{fig:example-days-288}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-289}

}

\caption{ - empty caption - }\label{fig:example-days-289}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-290}

}

\caption{ - empty caption - }\label{fig:example-days-290}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-291}

}

\caption{ - empty caption - }\label{fig:example-days-291}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-292}

}

\caption{ - empty caption - }\label{fig:example-days-292}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-293}

}

\caption{ - empty caption - }\label{fig:example-days-293}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-294}

}

\caption{ - empty caption - }\label{fig:example-days-294}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-295}

}

\caption{ - empty caption - }\label{fig:example-days-295}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-296}

}

\caption{ - empty caption - }\label{fig:example-days-296}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-297}

}

\caption{ - empty caption - }\label{fig:example-days-297}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-298}

}

\caption{ - empty caption - }\label{fig:example-days-298}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-299}

}

\caption{ - empty caption - }\label{fig:example-days-299}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-300}

}

\caption{ - empty caption - }\label{fig:example-days-300}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-301}

}

\caption{ - empty caption - }\label{fig:example-days-301}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-302}

}

\caption{ - empty caption - }\label{fig:example-days-302}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-303}

}

\caption{ - empty caption - }\label{fig:example-days-303}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-304}

}

\caption{ - empty caption - }\label{fig:example-days-304}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-305}

}

\caption{ - empty caption - }\label{fig:example-days-305}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-306}

}

\caption{ - empty caption - }\label{fig:example-days-306}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-307}

}

\caption{ - empty caption - }\label{fig:example-days-307}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-308}

}

\caption{ - empty caption - }\label{fig:example-days-308}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-309}

}

\caption{ - empty caption - }\label{fig:example-days-309}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-310}

}

\caption{ - empty caption - }\label{fig:example-days-310}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-311}

}

\caption{ - empty caption - }\label{fig:example-days-311}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-312}

}

\caption{ - empty caption - }\label{fig:example-days-312}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-313}

}

\caption{ - empty caption - }\label{fig:example-days-313}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-314}

}

\caption{ - empty caption - }\label{fig:example-days-314}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-315}

}

\caption{ - empty caption - }\label{fig:example-days-315}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-316}

}

\caption{ - empty caption - }\label{fig:example-days-316}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-317}

}

\caption{ - empty caption - }\label{fig:example-days-317}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-318}

}

\caption{ - empty caption - }\label{fig:example-days-318}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-319}

}

\caption{ - empty caption - }\label{fig:example-days-319}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-320}

}

\caption{ - empty caption - }\label{fig:example-days-320}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-321}

}

\caption{ - empty caption - }\label{fig:example-days-321}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-322}

}

\caption{ - empty caption - }\label{fig:example-days-322}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-323}

}

\caption{ - empty caption - }\label{fig:example-days-323}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-324}

}

\caption{ - empty caption - }\label{fig:example-days-324}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-325}

}

\caption{ - empty caption - }\label{fig:example-days-325}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-326}

}

\caption{ - empty caption - }\label{fig:example-days-326}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-327}

}

\caption{ - empty caption - }\label{fig:example-days-327}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-328}

}

\caption{ - empty caption - }\label{fig:example-days-328}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-329}

}

\caption{ - empty caption - }\label{fig:example-days-329}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-330}

}

\caption{ - empty caption - }\label{fig:example-days-330}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-331}

}

\caption{ - empty caption - }\label{fig:example-days-331}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-332}

}

\caption{ - empty caption - }\label{fig:example-days-332}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-333}

}

\caption{ - empty caption - }\label{fig:example-days-333}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-334}

}

\caption{ - empty caption - }\label{fig:example-days-334}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-335}

}

\caption{ - empty caption - }\label{fig:example-days-335}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-336}

}

\caption{ - empty caption - }\label{fig:example-days-336}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-337}

}

\caption{ - empty caption - }\label{fig:example-days-337}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-338}

}

\caption{ - empty caption - }\label{fig:example-days-338}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-339}

}

\caption{ - empty caption - }\label{fig:example-days-339}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-340}

}

\caption{ - empty caption - }\label{fig:example-days-340}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-341}

}

\caption{ - empty caption - }\label{fig:example-days-341}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-342}

}

\caption{ - empty caption - }\label{fig:example-days-342}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-343}

}

\caption{ - empty caption - }\label{fig:example-days-343}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-344}

}

\caption{ - empty caption - }\label{fig:example-days-344}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-345}

}

\caption{ - empty caption - }\label{fig:example-days-345}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-346}

}

\caption{ - empty caption - }\label{fig:example-days-346}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-347}

}

\caption{ - empty caption - }\label{fig:example-days-347}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-348}

}

\caption{ - empty caption - }\label{fig:example-days-348}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-349}

}

\caption{ - empty caption - }\label{fig:example-days-349}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-350}

}

\caption{ - empty caption - }\label{fig:example-days-350}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-351}

}

\caption{ - empty caption - }\label{fig:example-days-351}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-352}

}

\caption{ - empty caption - }\label{fig:example-days-352}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-353}

}

\caption{ - empty caption - }\label{fig:example-days-353}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-354}

}

\caption{ - empty caption - }\label{fig:example-days-354}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-355}

}

\caption{ - empty caption - }\label{fig:example-days-355}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-356}

}

\caption{ - empty caption - }\label{fig:example-days-356}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-357}

}

\caption{ - empty caption - }\label{fig:example-days-357}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-358}

}

\caption{ - empty caption - }\label{fig:example-days-358}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-359}

}

\caption{ - empty caption - }\label{fig:example-days-359}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-360}

}

\caption{ - empty caption - }\label{fig:example-days-360}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-361}

}

\caption{ - empty caption - }\label{fig:example-days-361}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-362}

}

\caption{ - empty caption - }\label{fig:example-days-362}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-363}

}

\caption{ - empty caption - }\label{fig:example-days-363}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-364}

}

\caption{ - empty caption - }\label{fig:example-days-364}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-365}

}

\caption{ - empty caption - }\label{fig:example-days-365}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-366}

}

\caption{ - empty caption - }\label{fig:example-days-366}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-367}

}

\caption{ - empty caption - }\label{fig:example-days-367}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-368}

}

\caption{ - empty caption - }\label{fig:example-days-368}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-369}

}

\caption{ - empty caption - }\label{fig:example-days-369}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-370}

}

\caption{ - empty caption - }\label{fig:example-days-370}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-371}

}

\caption{ - empty caption - }\label{fig:example-days-371}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-372}

}

\caption{ - empty caption - }\label{fig:example-days-372}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-373}

}

\caption{ - empty caption - }\label{fig:example-days-373}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-374}

}

\caption{ - empty caption - }\label{fig:example-days-374}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-375}

}

\caption{ - empty caption - }\label{fig:example-days-375}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-376}

}

\caption{ - empty caption - }\label{fig:example-days-376}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-377}

}

\caption{ - empty caption - }\label{fig:example-days-377}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-378}

}

\caption{ - empty caption - }\label{fig:example-days-378}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-379}

}

\caption{ - empty caption - }\label{fig:example-days-379}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-380}

}

\caption{ - empty caption - }\label{fig:example-days-380}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-381}

}

\caption{ - empty caption - }\label{fig:example-days-381}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-382}

}

\caption{ - empty caption - }\label{fig:example-days-382}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-383}

}

\caption{ - empty caption - }\label{fig:example-days-383}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-384}

}

\caption{ - empty caption - }\label{fig:example-days-384}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-385}

}

\caption{ - empty caption - }\label{fig:example-days-385}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-386}

}

\caption{ - empty caption - }\label{fig:example-days-386}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-387}

}

\caption{ - empty caption - }\label{fig:example-days-387}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-388}

}

\caption{ - empty caption - }\label{fig:example-days-388}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-389}

}

\caption{ - empty caption - }\label{fig:example-days-389}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-390}

}

\caption{ - empty caption - }\label{fig:example-days-390}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-391}

}

\caption{ - empty caption - }\label{fig:example-days-391}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-392}

}

\caption{ - empty caption - }\label{fig:example-days-392}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-393}

}

\caption{ - empty caption - }\label{fig:example-days-393}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-394}

}

\caption{ - empty caption - }\label{fig:example-days-394}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-395}

}

\caption{ - empty caption - }\label{fig:example-days-395}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-396}

}

\caption{ - empty caption - }\label{fig:example-days-396}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-397}

}

\caption{ - empty caption - }\label{fig:example-days-397}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-398}

}

\caption{ - empty caption - }\label{fig:example-days-398}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-399}

}

\caption{ - empty caption - }\label{fig:example-days-399}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-400}

}

\caption{ - empty caption - }\label{fig:example-days-400}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-401}

}

\caption{ - empty caption - }\label{fig:example-days-401}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-402}

}

\caption{ - empty caption - }\label{fig:example-days-402}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-403}

}

\caption{ - empty caption - }\label{fig:example-days-403}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-404}

}

\caption{ - empty caption - }\label{fig:example-days-404}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-405}

}

\caption{ - empty caption - }\label{fig:example-days-405}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-406}

}

\caption{ - empty caption - }\label{fig:example-days-406}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-407}

}

\caption{ - empty caption - }\label{fig:example-days-407}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-408}

}

\caption{ - empty caption - }\label{fig:example-days-408}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-409}

}

\caption{ - empty caption - }\label{fig:example-days-409}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-410}

}

\caption{ - empty caption - }\label{fig:example-days-410}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-411}

}

\caption{ - empty caption - }\label{fig:example-days-411}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-412}

}

\caption{ - empty caption - }\label{fig:example-days-412}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-413}

}

\caption{ - empty caption - }\label{fig:example-days-413}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-414}

}

\caption{ - empty caption - }\label{fig:example-days-414}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-415}

}

\caption{ - empty caption - }\label{fig:example-days-415}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-416}

}

\caption{ - empty caption - }\label{fig:example-days-416}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-417}

}

\caption{ - empty caption - }\label{fig:example-days-417}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-418}

}

\caption{ - empty caption - }\label{fig:example-days-418}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-419}

}

\caption{ - empty caption - }\label{fig:example-days-419}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-420}

}

\caption{ - empty caption - }\label{fig:example-days-420}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-421}

}

\caption{ - empty caption - }\label{fig:example-days-421}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-422}

}

\caption{ - empty caption - }\label{fig:example-days-422}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-423}

}

\caption{ - empty caption - }\label{fig:example-days-423}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-424}

}

\caption{ - empty caption - }\label{fig:example-days-424}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-425}

}

\caption{ - empty caption - }\label{fig:example-days-425}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-426}

}

\caption{ - empty caption - }\label{fig:example-days-426}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-427}

}

\caption{ - empty caption - }\label{fig:example-days-427}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-428}

}

\caption{ - empty caption - }\label{fig:example-days-428}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-429}

}

\caption{ - empty caption - }\label{fig:example-days-429}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-430}

}

\caption{ - empty caption - }\label{fig:example-days-430}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-431}

}

\caption{ - empty caption - }\label{fig:example-days-431}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-432}

}

\caption{ - empty caption - }\label{fig:example-days-432}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-433}

}

\caption{ - empty caption - }\label{fig:example-days-433}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-434}

}

\caption{ - empty caption - }\label{fig:example-days-434}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-435}

}

\caption{ - empty caption - }\label{fig:example-days-435}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-436}

}

\caption{ - empty caption - }\label{fig:example-days-436}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-437}

}

\caption{ - empty caption - }\label{fig:example-days-437}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-438}

}

\caption{ - empty caption - }\label{fig:example-days-438}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-439}

}

\caption{ - empty caption - }\label{fig:example-days-439}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-440}

}

\caption{ - empty caption - }\label{fig:example-days-440}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-441}

}

\caption{ - empty caption - }\label{fig:example-days-441}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-442}

}

\caption{ - empty caption - }\label{fig:example-days-442}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-443}

}

\caption{ - empty caption - }\label{fig:example-days-443}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-444}

}

\caption{ - empty caption - }\label{fig:example-days-444}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-445}

}

\caption{ - empty caption - }\label{fig:example-days-445}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-446}

}

\caption{ - empty caption - }\label{fig:example-days-446}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-447}

}

\caption{ - empty caption - }\label{fig:example-days-447}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-448}

}

\caption{ - empty caption - }\label{fig:example-days-448}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-449}

}

\caption{ - empty caption - }\label{fig:example-days-449}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-450}

}

\caption{ - empty caption - }\label{fig:example-days-450}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-451}

}

\caption{ - empty caption - }\label{fig:example-days-451}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-452}

}

\caption{ - empty caption - }\label{fig:example-days-452}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-453}

}

\caption{ - empty caption - }\label{fig:example-days-453}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-454}

}

\caption{ - empty caption - }\label{fig:example-days-454}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-455}

}

\caption{ - empty caption - }\label{fig:example-days-455}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-456}

}

\caption{ - empty caption - }\label{fig:example-days-456}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-457}

}

\caption{ - empty caption - }\label{fig:example-days-457}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-458}

}

\caption{ - empty caption - }\label{fig:example-days-458}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-459}

}

\caption{ - empty caption - }\label{fig:example-days-459}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-460}

}

\caption{ - empty caption - }\label{fig:example-days-460}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-461}

}

\caption{ - empty caption - }\label{fig:example-days-461}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-462}

}

\caption{ - empty caption - }\label{fig:example-days-462}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-463}

}

\caption{ - empty caption - }\label{fig:example-days-463}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-464}

}

\caption{ - empty caption - }\label{fig:example-days-464}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-465}

}

\caption{ - empty caption - }\label{fig:example-days-465}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-466}

}

\caption{ - empty caption - }\label{fig:example-days-466}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-467}

}

\caption{ - empty caption - }\label{fig:example-days-467}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-468}

}

\caption{ - empty caption - }\label{fig:example-days-468}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-469}

}

\caption{ - empty caption - }\label{fig:example-days-469}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-470}

}

\caption{ - empty caption - }\label{fig:example-days-470}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-471}

}

\caption{ - empty caption - }\label{fig:example-days-471}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-472}

}

\caption{ - empty caption - }\label{fig:example-days-472}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-473}

}

\caption{ - empty caption - }\label{fig:example-days-473}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-474}

}

\caption{ - empty caption - }\label{fig:example-days-474}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-475}

}

\caption{ - empty caption - }\label{fig:example-days-475}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-476}

}

\caption{ - empty caption - }\label{fig:example-days-476}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-477}

}

\caption{ - empty caption - }\label{fig:example-days-477}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-478}

}

\caption{ - empty caption - }\label{fig:example-days-478}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-479}

}

\caption{ - empty caption - }\label{fig:example-days-479}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-480}

}

\caption{ - empty caption - }\label{fig:example-days-480}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-481}

}

\caption{ - empty caption - }\label{fig:example-days-481}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-482}

}

\caption{ - empty caption - }\label{fig:example-days-482}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-483}

}

\caption{ - empty caption - }\label{fig:example-days-483}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-484}

}

\caption{ - empty caption - }\label{fig:example-days-484}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-485}

}

\caption{ - empty caption - }\label{fig:example-days-485}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-486}

}

\caption{ - empty caption - }\label{fig:example-days-486}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-487}

}

\caption{ - empty caption - }\label{fig:example-days-487}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-488}

}

\caption{ - empty caption - }\label{fig:example-days-488}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-489}

}

\caption{ - empty caption - }\label{fig:example-days-489}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-490}

}

\caption{ - empty caption - }\label{fig:example-days-490}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-491}

}

\caption{ - empty caption - }\label{fig:example-days-491}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-492}

}

\caption{ - empty caption - }\label{fig:example-days-492}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-493}

}

\caption{ - empty caption - }\label{fig:example-days-493}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-494}

}

\caption{ - empty caption - }\label{fig:example-days-494}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-495}

}

\caption{ - empty caption - }\label{fig:example-days-495}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-496}

}

\caption{ - empty caption - }\label{fig:example-days-496}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-497}

}

\caption{ - empty caption - }\label{fig:example-days-497}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-498}

}

\caption{ - empty caption - }\label{fig:example-days-498}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-499}

}

\caption{ - empty caption - }\label{fig:example-days-499}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-500}

}

\caption{ - empty caption - }\label{fig:example-days-500}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-501}

}

\caption{ - empty caption - }\label{fig:example-days-501}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-502}

}

\caption{ - empty caption - }\label{fig:example-days-502}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-503}

}

\caption{ - empty caption - }\label{fig:example-days-503}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-504}

}

\caption{ - empty caption - }\label{fig:example-days-504}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-505}

}

\caption{ - empty caption - }\label{fig:example-days-505}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-506}

}

\caption{ - empty caption - }\label{fig:example-days-506}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-507}

}

\caption{ - empty caption - }\label{fig:example-days-507}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-508}

}

\caption{ - empty caption - }\label{fig:example-days-508}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-509}

}

\caption{ - empty caption - }\label{fig:example-days-509}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-510}

}

\caption{ - empty caption - }\label{fig:example-days-510}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-511}

}

\caption{ - empty caption - }\label{fig:example-days-511}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-512}

}

\caption{ - empty caption - }\label{fig:example-days-512}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-513}

}

\caption{ - empty caption - }\label{fig:example-days-513}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-514}

}

\caption{ - empty caption - }\label{fig:example-days-514}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-515}

}

\caption{ - empty caption - }\label{fig:example-days-515}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-516}

}

\caption{ - empty caption - }\label{fig:example-days-516}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-517}

}

\caption{ - empty caption - }\label{fig:example-days-517}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-518}

}

\caption{ - empty caption - }\label{fig:example-days-518}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-519}

}

\caption{ - empty caption - }\label{fig:example-days-519}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-520}

}

\caption{ - empty caption - }\label{fig:example-days-520}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-521}

}

\caption{ - empty caption - }\label{fig:example-days-521}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-522}

}

\caption{ - empty caption - }\label{fig:example-days-522}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-523}

}

\caption{ - empty caption - }\label{fig:example-days-523}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-524}

}

\caption{ - empty caption - }\label{fig:example-days-524}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-525}

}

\caption{ - empty caption - }\label{fig:example-days-525}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-526}

}

\caption{ - empty caption - }\label{fig:example-days-526}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-527}

}

\caption{ - empty caption - }\label{fig:example-days-527}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-528}

}

\caption{ - empty caption - }\label{fig:example-days-528}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-529}

}

\caption{ - empty caption - }\label{fig:example-days-529}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-530}

}

\caption{ - empty caption - }\label{fig:example-days-530}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-531}

}

\caption{ - empty caption - }\label{fig:example-days-531}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-532}

}

\caption{ - empty caption - }\label{fig:example-days-532}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-533}

}

\caption{ - empty caption - }\label{fig:example-days-533}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-534}

}

\caption{ - empty caption - }\label{fig:example-days-534}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-535}

}

\caption{ - empty caption - }\label{fig:example-days-535}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-536}

}

\caption{ - empty caption - }\label{fig:example-days-536}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-537}

}

\caption{ - empty caption - }\label{fig:example-days-537}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-538}

}

\caption{ - empty caption - }\label{fig:example-days-538}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-539}

}

\caption{ - empty caption - }\label{fig:example-days-539}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-540}

}

\caption{ - empty caption - }\label{fig:example-days-540}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-541}

}

\caption{ - empty caption - }\label{fig:example-days-541}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-542}

}

\caption{ - empty caption - }\label{fig:example-days-542}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-543}

}

\caption{ - empty caption - }\label{fig:example-days-543}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-544}

}

\caption{ - empty caption - }\label{fig:example-days-544}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-545}

}

\caption{ - empty caption - }\label{fig:example-days-545}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-546}

}

\caption{ - empty caption - }\label{fig:example-days-546}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-547}

}

\caption{ - empty caption - }\label{fig:example-days-547}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-548}

}

\caption{ - empty caption - }\label{fig:example-days-548}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-549}

}

\caption{ - empty caption - }\label{fig:example-days-549}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-550}

}

\caption{ - empty caption - }\label{fig:example-days-550}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-551}

}

\caption{ - empty caption - }\label{fig:example-days-551}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-552}

}

\caption{ - empty caption - }\label{fig:example-days-552}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-553}

}

\caption{ - empty caption - }\label{fig:example-days-553}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-554}

}

\caption{ - empty caption - }\label{fig:example-days-554}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-555}

}

\caption{ - empty caption - }\label{fig:example-days-555}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-556}

}

\caption{ - empty caption - }\label{fig:example-days-556}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-557}

}

\caption{ - empty caption - }\label{fig:example-days-557}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-558}

}

\caption{ - empty caption - }\label{fig:example-days-558}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-559}

}

\caption{ - empty caption - }\label{fig:example-days-559}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-560}

}

\caption{ - empty caption - }\label{fig:example-days-560}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-561}

}

\caption{ - empty caption - }\label{fig:example-days-561}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-562}

}

\caption{ - empty caption - }\label{fig:example-days-562}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-563}

}

\caption{ - empty caption - }\label{fig:example-days-563}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-564}

}

\caption{ - empty caption - }\label{fig:example-days-564}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-565}

}

\caption{ - empty caption - }\label{fig:example-days-565}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-566}

}

\caption{ - empty caption - }\label{fig:example-days-566}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-567}

}

\caption{ - empty caption - }\label{fig:example-days-567}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-568}

}

\caption{ - empty caption - }\label{fig:example-days-568}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-569}

}

\caption{ - empty caption - }\label{fig:example-days-569}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-570}

}

\caption{ - empty caption - }\label{fig:example-days-570}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-571}

}

\caption{ - empty caption - }\label{fig:example-days-571}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-572}

}

\caption{ - empty caption - }\label{fig:example-days-572}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-573}

}

\caption{ - empty caption - }\label{fig:example-days-573}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-574}

}

\caption{ - empty caption - }\label{fig:example-days-574}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-575}

}

\caption{ - empty caption - }\label{fig:example-days-575}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-576}

}

\caption{ - empty caption - }\label{fig:example-days-576}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-577}

}

\caption{ - empty caption - }\label{fig:example-days-577}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-578}

}

\caption{ - empty caption - }\label{fig:example-days-578}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-579}

}

\caption{ - empty caption - }\label{fig:example-days-579}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-580}

}

\caption{ - empty caption - }\label{fig:example-days-580}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-581}

}

\caption{ - empty caption - }\label{fig:example-days-581}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-582}

}

\caption{ - empty caption - }\label{fig:example-days-582}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-583}

}

\caption{ - empty caption - }\label{fig:example-days-583}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-584}

}

\caption{ - empty caption - }\label{fig:example-days-584}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-585}

}

\caption{ - empty caption - }\label{fig:example-days-585}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-586}

}

\caption{ - empty caption - }\label{fig:example-days-586}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-587}

}

\caption{ - empty caption - }\label{fig:example-days-587}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-588}

}

\caption{ - empty caption - }\label{fig:example-days-588}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-589}

}

\caption{ - empty caption - }\label{fig:example-days-589}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-590}

}

\caption{ - empty caption - }\label{fig:example-days-590}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-591}

}

\caption{ - empty caption - }\label{fig:example-days-591}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-592}

}

\caption{ - empty caption - }\label{fig:example-days-592}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-593}

}

\caption{ - empty caption - }\label{fig:example-days-593}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-594}

}

\caption{ - empty caption - }\label{fig:example-days-594}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-595}

}

\caption{ - empty caption - }\label{fig:example-days-595}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-596}

}

\caption{ - empty caption - }\label{fig:example-days-596}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-597}

}

\caption{ - empty caption - }\label{fig:example-days-597}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-598}

}

\caption{ - empty caption - }\label{fig:example-days-598}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-599}

}

\caption{ - empty caption - }\label{fig:example-days-599}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-600}

}

\caption{ - empty caption - }\label{fig:example-days-600}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-601}

}

\caption{ - empty caption - }\label{fig:example-days-601}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-602}

}

\caption{ - empty caption - }\label{fig:example-days-602}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-603}

}

\caption{ - empty caption - }\label{fig:example-days-603}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-604}

}

\caption{ - empty caption - }\label{fig:example-days-604}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-605}

}

\caption{ - empty caption - }\label{fig:example-days-605}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-606}

}

\caption{ - empty caption - }\label{fig:example-days-606}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-607}

}

\caption{ - empty caption - }\label{fig:example-days-607}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-608}

}

\caption{ - empty caption - }\label{fig:example-days-608}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-609}

}

\caption{ - empty caption - }\label{fig:example-days-609}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-610}

}

\caption{ - empty caption - }\label{fig:example-days-610}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-611}

}

\caption{ - empty caption - }\label{fig:example-days-611}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-612}

}

\caption{ - empty caption - }\label{fig:example-days-612}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-613}

}

\caption{ - empty caption - }\label{fig:example-days-613}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-614}

}

\caption{ - empty caption - }\label{fig:example-days-614}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-615}

}

\caption{ - empty caption - }\label{fig:example-days-615}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-616}

}

\caption{ - empty caption - }\label{fig:example-days-616}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-617}

}

\caption{ - empty caption - }\label{fig:example-days-617}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-618}

}

\caption{ - empty caption - }\label{fig:example-days-618}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-619}

}

\caption{ - empty caption - }\label{fig:example-days-619}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-620}

}

\caption{ - empty caption - }\label{fig:example-days-620}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-621}

}

\caption{ - empty caption - }\label{fig:example-days-621}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-622}

}

\caption{ - empty caption - }\label{fig:example-days-622}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-623}

}

\caption{ - empty caption - }\label{fig:example-days-623}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-624}

}

\caption{ - empty caption - }\label{fig:example-days-624}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-625}

}

\caption{ - empty caption - }\label{fig:example-days-625}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-626}

}

\caption{ - empty caption - }\label{fig:example-days-626}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-627}

}

\caption{ - empty caption - }\label{fig:example-days-627}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-628}

}

\caption{ - empty caption - }\label{fig:example-days-628}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-629}

}

\caption{ - empty caption - }\label{fig:example-days-629}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-630}

}

\caption{ - empty caption - }\label{fig:example-days-630}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-631}

}

\caption{ - empty caption - }\label{fig:example-days-631}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-632}

}

\caption{ - empty caption - }\label{fig:example-days-632}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-633}

}

\caption{ - empty caption - }\label{fig:example-days-633}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-634}

}

\caption{ - empty caption - }\label{fig:example-days-634}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-635}

}

\caption{ - empty caption - }\label{fig:example-days-635}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-636}

}

\caption{ - empty caption - }\label{fig:example-days-636}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-637}

}

\caption{ - empty caption - }\label{fig:example-days-637}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-638}

}

\caption{ - empty caption - }\label{fig:example-days-638}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-639}

}

\caption{ - empty caption - }\label{fig:example-days-639}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-640}

}

\caption{ - empty caption - }\label{fig:example-days-640}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-641}

}

\caption{ - empty caption - }\label{fig:example-days-641}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-642}

}

\caption{ - empty caption - }\label{fig:example-days-642}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-643}

}

\caption{ - empty caption - }\label{fig:example-days-643}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-644}

}

\caption{ - empty caption - }\label{fig:example-days-644}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-645}

}

\caption{ - empty caption - }\label{fig:example-days-645}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-646}

}

\caption{ - empty caption - }\label{fig:example-days-646}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-647}

}

\caption{ - empty caption - }\label{fig:example-days-647}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-648}

}

\caption{ - empty caption - }\label{fig:example-days-648}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-649}

}

\caption{ - empty caption - }\label{fig:example-days-649}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-650}

}

\caption{ - empty caption - }\label{fig:example-days-650}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-651}

}

\caption{ - empty caption - }\label{fig:example-days-651}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-652}

}

\caption{ - empty caption - }\label{fig:example-days-652}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-653}

}

\caption{ - empty caption - }\label{fig:example-days-653}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-654}

}

\caption{ - empty caption - }\label{fig:example-days-654}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-655}

}

\caption{ - empty caption - }\label{fig:example-days-655}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-656}

}

\caption{ - empty caption - }\label{fig:example-days-656}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-657}

}

\caption{ - empty caption - }\label{fig:example-days-657}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-658}

}

\caption{ - empty caption - }\label{fig:example-days-658}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-659}

}

\caption{ - empty caption - }\label{fig:example-days-659}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-660}

}

\caption{ - empty caption - }\label{fig:example-days-660}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-661}

}

\caption{ - empty caption - }\label{fig:example-days-661}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-662}

}

\caption{ - empty caption - }\label{fig:example-days-662}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-663}

}

\caption{ - empty caption - }\label{fig:example-days-663}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-664}

}

\caption{ - empty caption - }\label{fig:example-days-664}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-665}

}

\caption{ - empty caption - }\label{fig:example-days-665}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-666}

}

\caption{ - empty caption - }\label{fig:example-days-666}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-667}

}

\caption{ - empty caption - }\label{fig:example-days-667}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-668}

}

\caption{ - empty caption - }\label{fig:example-days-668}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-669}

}

\caption{ - empty caption - }\label{fig:example-days-669}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-670}

}

\caption{ - empty caption - }\label{fig:example-days-670}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-671}

}

\caption{ - empty caption - }\label{fig:example-days-671}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-672}

}

\caption{ - empty caption - }\label{fig:example-days-672}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-673}

}

\caption{ - empty caption - }\label{fig:example-days-673}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-674}

}

\caption{ - empty caption - }\label{fig:example-days-674}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-675}

}

\caption{ - empty caption - }\label{fig:example-days-675}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-676}

}

\caption{ - empty caption - }\label{fig:example-days-676}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-677}

}

\caption{ - empty caption - }\label{fig:example-days-677}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-678}

}

\caption{ - empty caption - }\label{fig:example-days-678}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-679}

}

\caption{ - empty caption - }\label{fig:example-days-679}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-680}

}

\caption{ - empty caption - }\label{fig:example-days-680}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-681}

}

\caption{ - empty caption - }\label{fig:example-days-681}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-682}

}

\caption{ - empty caption - }\label{fig:example-days-682}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-683}

}

\caption{ - empty caption - }\label{fig:example-days-683}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-684}

}

\caption{ - empty caption - }\label{fig:example-days-684}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-685}

}

\caption{ - empty caption - }\label{fig:example-days-685}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-686}

}

\caption{ - empty caption - }\label{fig:example-days-686}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-687}

}

\caption{ - empty caption - }\label{fig:example-days-687}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-688}

}

\caption{ - empty caption - }\label{fig:example-days-688}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-689}

}

\caption{ - empty caption - }\label{fig:example-days-689}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-690}

}

\caption{ - empty caption - }\label{fig:example-days-690}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-691}

}

\caption{ - empty caption - }\label{fig:example-days-691}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-692}

}

\caption{ - empty caption - }\label{fig:example-days-692}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-693}

}

\caption{ - empty caption - }\label{fig:example-days-693}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-694}

}

\caption{ - empty caption - }\label{fig:example-days-694}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-695}

}

\caption{ - empty caption - }\label{fig:example-days-695}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-696}

}

\caption{ - empty caption - }\label{fig:example-days-696}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-697}

}

\caption{ - empty caption - }\label{fig:example-days-697}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-698}

}

\caption{ - empty caption - }\label{fig:example-days-698}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-699}

}

\caption{ - empty caption - }\label{fig:example-days-699}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-700}

}

\caption{ - empty caption - }\label{fig:example-days-700}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-701}

}

\caption{ - empty caption - }\label{fig:example-days-701}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-702}

}

\caption{ - empty caption - }\label{fig:example-days-702}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-703}

}

\caption{ - empty caption - }\label{fig:example-days-703}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-704}

}

\caption{ - empty caption - }\label{fig:example-days-704}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-705}

}

\caption{ - empty caption - }\label{fig:example-days-705}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-706}

}

\caption{ - empty caption - }\label{fig:example-days-706}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-707}

}

\caption{ - empty caption - }\label{fig:example-days-707}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-708}

}

\caption{ - empty caption - }\label{fig:example-days-708}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-709}

}

\caption{ - empty caption - }\label{fig:example-days-709}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-710}

}

\caption{ - empty caption - }\label{fig:example-days-710}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-711}

}

\caption{ - empty caption - }\label{fig:example-days-711}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-712}

}

\caption{ - empty caption - }\label{fig:example-days-712}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-713}

}

\caption{ - empty caption - }\label{fig:example-days-713}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-714}

}

\caption{ - empty caption - }\label{fig:example-days-714}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-715}

}

\caption{ - empty caption - }\label{fig:example-days-715}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-716}

}

\caption{ - empty caption - }\label{fig:example-days-716}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-717}

}

\caption{ - empty caption - }\label{fig:example-days-717}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-718}

}

\caption{ - empty caption - }\label{fig:example-days-718}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-719}

}

\caption{ - empty caption - }\label{fig:example-days-719}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-720}

}

\caption{ - empty caption - }\label{fig:example-days-720}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-721}

}

\caption{ - empty caption - }\label{fig:example-days-721}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-722}

}

\caption{ - empty caption - }\label{fig:example-days-722}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-723}

}

\caption{ - empty caption - }\label{fig:example-days-723}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-724}

}

\caption{ - empty caption - }\label{fig:example-days-724}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-725}

}

\caption{ - empty caption - }\label{fig:example-days-725}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-726}

}

\caption{ - empty caption - }\label{fig:example-days-726}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-727}

}

\caption{ - empty caption - }\label{fig:example-days-727}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-728}

}

\caption{ - empty caption - }\label{fig:example-days-728}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-729}

}

\caption{ - empty caption - }\label{fig:example-days-729}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-730}

}

\caption{ - empty caption - }\label{fig:example-days-730}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-731}

}

\caption{ - empty caption - }\label{fig:example-days-731}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-732}

}

\caption{ - empty caption - }\label{fig:example-days-732}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-733}

}

\caption{ - empty caption - }\label{fig:example-days-733}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-734}

}

\caption{ - empty caption - }\label{fig:example-days-734}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-735}

}

\caption{ - empty caption - }\label{fig:example-days-735}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-736}

}

\caption{ - empty caption - }\label{fig:example-days-736}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-737}

}

\caption{ - empty caption - }\label{fig:example-days-737}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-738}

}

\caption{ - empty caption - }\label{fig:example-days-738}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-739}

}

\caption{ - empty caption - }\label{fig:example-days-739}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-740}

}

\caption{ - empty caption - }\label{fig:example-days-740}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-741}

}

\caption{ - empty caption - }\label{fig:example-days-741}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-742}

}

\caption{ - empty caption - }\label{fig:example-days-742}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-743}

}

\caption{ - empty caption - }\label{fig:example-days-743}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-744}

}

\caption{ - empty caption - }\label{fig:example-days-744}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-745}

}

\caption{ - empty caption - }\label{fig:example-days-745}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-746}

}

\caption{ - empty caption - }\label{fig:example-days-746}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-747}

}

\caption{ - empty caption - }\label{fig:example-days-747}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-748}

}

\caption{ - empty caption - }\label{fig:example-days-748}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-749}

}

\caption{ - empty caption - }\label{fig:example-days-749}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-750}

}

\caption{ - empty caption - }\label{fig:example-days-750}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-751}

}

\caption{ - empty caption - }\label{fig:example-days-751}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-752}

}

\caption{ - empty caption - }\label{fig:example-days-752}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-753}

}

\caption{ - empty caption - }\label{fig:example-days-753}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-754}

}

\caption{ - empty caption - }\label{fig:example-days-754}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-755}

}

\caption{ - empty caption - }\label{fig:example-days-755}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-756}

}

\caption{ - empty caption - }\label{fig:example-days-756}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-757}

}

\caption{ - empty caption - }\label{fig:example-days-757}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-758}

}

\caption{ - empty caption - }\label{fig:example-days-758}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-759}

}

\caption{ - empty caption - }\label{fig:example-days-759}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-760}

}

\caption{ - empty caption - }\label{fig:example-days-760}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-761}

}

\caption{ - empty caption - }\label{fig:example-days-761}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-762}

}

\caption{ - empty caption - }\label{fig:example-days-762}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-763}

}

\caption{ - empty caption - }\label{fig:example-days-763}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-764}

}

\caption{ - empty caption - }\label{fig:example-days-764}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-765}

}

\caption{ - empty caption - }\label{fig:example-days-765}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-766}

}

\caption{ - empty caption - }\label{fig:example-days-766}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-767}

}

\caption{ - empty caption - }\label{fig:example-days-767}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-768}

}

\caption{ - empty caption - }\label{fig:example-days-768}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-769}

}

\caption{ - empty caption - }\label{fig:example-days-769}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-770}

}

\caption{ - empty caption - }\label{fig:example-days-770}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-771}

}

\caption{ - empty caption - }\label{fig:example-days-771}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-772}

}

\caption{ - empty caption - }\label{fig:example-days-772}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-773}

}

\caption{ - empty caption - }\label{fig:example-days-773}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-774}

}

\caption{ - empty caption - }\label{fig:example-days-774}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-775}

}

\caption{ - empty caption - }\label{fig:example-days-775}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-776}

}

\caption{ - empty caption - }\label{fig:example-days-776}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-777}

}

\caption{ - empty caption - }\label{fig:example-days-777}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-778}

}

\caption{ - empty caption - }\label{fig:example-days-778}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-779}

}

\caption{ - empty caption - }\label{fig:example-days-779}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-780}

}

\caption{ - empty caption - }\label{fig:example-days-780}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-781}

}

\caption{ - empty caption - }\label{fig:example-days-781}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-782}

}

\caption{ - empty caption - }\label{fig:example-days-782}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-783}

}

\caption{ - empty caption - }\label{fig:example-days-783}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-784}

}

\caption{ - empty caption - }\label{fig:example-days-784}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-785}

}

\caption{ - empty caption - }\label{fig:example-days-785}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-786}

}

\caption{ - empty caption - }\label{fig:example-days-786}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-787}

}

\caption{ - empty caption - }\label{fig:example-days-787}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-788}

}

\caption{ - empty caption - }\label{fig:example-days-788}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-789}

}

\caption{ - empty caption - }\label{fig:example-days-789}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-790}

}

\caption{ - empty caption - }\label{fig:example-days-790}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-791}

}

\caption{ - empty caption - }\label{fig:example-days-791}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-792}

}

\caption{ - empty caption - }\label{fig:example-days-792}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-793}

}

\caption{ - empty caption - }\label{fig:example-days-793}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-794}

}

\caption{ - empty caption - }\label{fig:example-days-794}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-795}

}

\caption{ - empty caption - }\label{fig:example-days-795}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-796}

}

\caption{ - empty caption - }\label{fig:example-days-796}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-797}

}

\caption{ - empty caption - }\label{fig:example-days-797}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-798}

}

\caption{ - empty caption - }\label{fig:example-days-798}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-799}

}

\caption{ - empty caption - }\label{fig:example-days-799}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-800}

}

\caption{ - empty caption - }\label{fig:example-days-800}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-801}

}

\caption{ - empty caption - }\label{fig:example-days-801}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-802}

}

\caption{ - empty caption - }\label{fig:example-days-802}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-803}

}

\caption{ - empty caption - }\label{fig:example-days-803}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-804}

}

\caption{ - empty caption - }\label{fig:example-days-804}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-805}

}

\caption{ - empty caption - }\label{fig:example-days-805}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-806}

}

\caption{ - empty caption - }\label{fig:example-days-806}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-807}

}

\caption{ - empty caption - }\label{fig:example-days-807}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-808}

}

\caption{ - empty caption - }\label{fig:example-days-808}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-809}

}

\caption{ - empty caption - }\label{fig:example-days-809}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-810}

}

\caption{ - empty caption - }\label{fig:example-days-810}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-811}

}

\caption{ - empty caption - }\label{fig:example-days-811}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-812}

}

\caption{ - empty caption - }\label{fig:example-days-812}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-813}

}

\caption{ - empty caption - }\label{fig:example-days-813}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-814}

}

\caption{ - empty caption - }\label{fig:example-days-814}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-815}

}

\caption{ - empty caption - }\label{fig:example-days-815}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-816}

}

\caption{ - empty caption - }\label{fig:example-days-816}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-817}

}

\caption{ - empty caption - }\label{fig:example-days-817}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-818}

}

\caption{ - empty caption - }\label{fig:example-days-818}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-819}

}

\caption{ - empty caption - }\label{fig:example-days-819}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-820}

}

\caption{ - empty caption - }\label{fig:example-days-820}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-821}

}

\caption{ - empty caption - }\label{fig:example-days-821}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-822}

}

\caption{ - empty caption - }\label{fig:example-days-822}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-823}

}

\caption{ - empty caption - }\label{fig:example-days-823}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-824}

}

\caption{ - empty caption - }\label{fig:example-days-824}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-825}

}

\caption{ - empty caption - }\label{fig:example-days-825}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-826}

}

\caption{ - empty caption - }\label{fig:example-days-826}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-827}

}

\caption{ - empty caption - }\label{fig:example-days-827}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-828}

}

\caption{ - empty caption - }\label{fig:example-days-828}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-829}

}

\caption{ - empty caption - }\label{fig:example-days-829}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-830}

}

\caption{ - empty caption - }\label{fig:example-days-830}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-831}

}

\caption{ - empty caption - }\label{fig:example-days-831}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-832}

}

\caption{ - empty caption - }\label{fig:example-days-832}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-833}

}

\caption{ - empty caption - }\label{fig:example-days-833}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-834}

}

\caption{ - empty caption - }\label{fig:example-days-834}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-835}

}

\caption{ - empty caption - }\label{fig:example-days-835}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-836}

}

\caption{ - empty caption - }\label{fig:example-days-836}
\end{figure}

\textbf{END}

\begin{verbatim}
2024-09-06 06:08:04.9 athan@sagan GHI_enh_02_ID_CE.R 2.698150 mins
\end{verbatim}

\end{document}

### 2024-09-06 GHI_enh_08_validation.tex
Commit 2024-09-06 12:14

--- 2024-09-06 GHI_enh_daily_test_plots.tex
@@
 \begin{verbatim}
-Warning:
-
- ** Test is active!! ** 
-\end{verbatim}
-
-\FloatBarrier
-
-\section{Plot some days with strong enhancement cases}\label{plot-some-days-with-strong-enhancement-cases}
-
-\FloatBarrier
-
-\subsection{Days with extreme cases day}\label{days-with-extreme-cases-day}
-
-\FloatBarrier
-
-\subsection{Days with strong enhancement day}\label{days-with-strong-enhancement-day}
-
-\FloatBarrier
-
-\subsection{Days with sunny day}\label{days-with-sunny-day}
-
-\FloatBarrier
-
-\subsection{Days with sunny enhancement day}\label{days-with-sunny-enhancement-day}
-
-\FloatBarrier
-
-\subsection{Days with cloudy day}\label{days-with-cloudy-day}
-
-\FloatBarrier
-
-\subsection{Days with manual test days}\label{days-with-manual-test-days}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-1}
+Drop all enhacement cases
+\end{verbatim}
+
+\begin{verbatim}
+Drop all clouds
+\end{verbatim}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-4-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-4}
+\end{figure}
+
+\FloatBarrier
+
+\hypertarget{plot-some-days-with-strong-enhancement-cases}{%
+\section{Plot some days with strong enhancement cases}\label{plot-some-days-with-strong-enhancement-cases}}
+
+\FloatBarrier
+
+\hypertarget{days-with-sunny-day}{%
+\subsection{Days with sunny day}\label{days-with-sunny-day}}
+
+\FloatBarrier
+
+\hypertarget{days-with-sunny-enhancement-day}{%
+\subsection{Days with sunny enhancement day}\label{days-with-sunny-enhancement-day}}
+
+\FloatBarrier
+
+\hypertarget{days-with-cloudy-day}{%
+\subsection{Days with cloudy day}\label{days-with-cloudy-day}}
+
+\FloatBarrier
+
+\hypertarget{days-with-random-day}{%
+\subsection{Days with random day}\label{days-with-random-day}}
+
+\FloatBarrier
+
+\hypertarget{days-with-manual-test-days}{%
+\subsection{Days with manual test days}\label{days-with-manual-test-days}}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-2}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-2}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-3}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-3}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-4}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-4}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-5}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-5}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-6}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-6}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-7}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-7}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-8}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-8}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-9}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-9}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-10}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-10}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-11}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-11}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-12}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-12}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-13}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-13}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-14}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-14}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-15}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-15}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-16}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-16}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-17}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-17}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-18}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-18}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-19}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-19}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-20}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-20}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-21}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-21}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-22}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-22}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-23}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-23}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-24}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-24}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-25}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-25}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-26}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-26}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-27}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-27}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-28}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-28}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-29}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-29}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-30}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-30}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-31}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-31}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-32}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-32}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-33}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-33}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-34}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-34}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-35}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-35}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-36}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-36}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-37}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-37}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-38}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-38}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-39}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-39}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-40}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-40}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-41}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-41}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-42}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-42}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-43}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-43}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-44}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-44}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-45}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-45}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-46}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-46}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-47}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-47}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-48}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-48}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-49}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-49}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-50}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-50}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-51}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-51}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-52}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-52}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-53}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-53}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-54}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-54}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-55}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-55}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-56}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-56}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-57}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-57}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-58}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-58}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-59}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-59}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-60}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-60}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-61}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-61}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-62}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-62}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-63}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-63}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-64}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-64}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-65}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-65}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-66}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-66}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-67}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-67}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-68}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-68}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-69}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-69}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-70}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-70}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-71}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-71}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-72}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-72}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-73}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-73}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-74}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-74}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-75}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-75}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-76}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-76}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-77}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-77}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-78}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-78}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-79}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-79}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-80}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-80}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-81}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-81}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-82}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-82}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-83}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-83}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-84}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-84}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-85}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-85}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-86}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-86}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-87}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-87}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-88}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-88}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-89}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-89}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-90}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-90}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-91}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-91}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-92}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-92}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-93}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-93}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-94}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-94}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-95}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-95}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-96}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-96}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-97}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-97}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-98}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-98}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-99}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-99}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-100}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-100}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-101}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-101}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-102}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-102}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-103}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-103}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-104}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-104}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-105}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-105}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-106}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-106}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-107}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-107}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-108}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-108}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-109}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-109}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-110}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-110}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-111}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-111}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-112}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-112}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-113}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-113}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-114}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-114}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-115}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-115}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-116}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-116}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-117}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-117}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-118}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-118}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-119}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-119}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-120}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-120}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-121}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-121}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-122}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-122}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-123}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-123}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-124}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-124}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-125}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-125}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-126}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-126}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-127}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-127}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-128}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-128}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-129}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-129}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-130}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-130}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-131}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-131}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-132}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-132}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-133}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-133}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-134}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-134}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-135}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-135}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-136}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-136}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-137}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-137}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-138}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-138}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-139}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-139}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-140}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-140}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-141}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-141}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-142}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-142}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-143}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-143}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-144}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-144}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-145}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-145}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-146}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-146}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-147}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-147}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-148}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-148}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-149}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-149}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-150}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-150}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-151}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-151}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-152}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-152}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-153}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-153}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-154}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-154}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-155}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-155}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-156}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-156}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-157}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-157}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-158}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-158}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-159}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-159}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-160}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-160}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-161}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-161}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-162}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-162}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-163}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-163}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-164}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-164}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-165}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-165}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-166}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-166}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-167}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-167}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-168}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-168}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-169}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-169}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-170}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-170}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-171}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-171}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-172}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-172}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-173}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-173}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-174}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-174}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-175}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-175}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-176}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-176}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-177}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-177}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-178}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-178}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-179}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-179}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-180}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-180}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-181}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-181}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-182}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-182}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-183}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-183}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-184}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-184}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-185}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-185}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-186}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-186}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-187}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-187}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-188}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-188}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-189}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-189}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-190}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-190}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-191}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-191}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-192}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-192}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-193}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-193}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-194}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-194}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-195}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-195}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-196}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-196}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-197}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-197}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-198}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-198}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-199}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-199}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-200}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-200}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-201}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-201}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-202}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-202}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-203}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-203}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-204}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-204}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-205}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-205}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-206}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-206}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-207}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-207}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-208}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-208}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-209}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-209}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-210}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-210}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-211}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-211}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-212}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-212}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-213}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-213}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-214}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-214}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-215}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-215}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-216}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-216}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-217}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-217}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-218}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-218}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-219}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-219}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-220}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-220}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-221}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-221}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-222}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-222}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-223}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-223}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-224}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-224}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-225}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-225}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-226}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-226}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-227}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-227}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-228}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-228}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-229}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-229}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-230}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-230}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-231}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-231}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-232}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-232}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-233}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-233}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-234}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-234}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-235}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-235}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-236}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-236}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-237}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-237}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-238}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-238}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-239}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-239}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-240}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-240}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-241}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-241}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-242}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-242}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-243}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-243}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-244}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-244}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-245}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-245}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-246}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-246}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-247}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-247}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-248}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-248}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-249}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-249}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-250}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-250}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-251}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-251}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-252}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-252}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-253}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-253}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-254}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-254}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-255}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-255}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-256}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-256}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-257}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-257}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-258}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-258}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-259}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-259}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-260}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-260}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-261}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-261}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-262}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-262}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-263}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-263}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-264}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-264}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-265}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-265}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-266}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-266}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-267}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-267}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-268}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-268}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-269}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-269}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-270}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-270}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-271}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-271}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-272}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-272}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-273}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-273}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-274}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-274}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-275}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-275}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-276}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-276}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-277}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-277}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-278}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-278}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-279}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-279}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-280}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-280}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-281}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-281}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-282}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-282}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-283}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-283}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-284}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-284}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-285}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-285}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-286}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-286}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-287}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-287}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-288}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-288}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-289}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-289}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-290}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-290}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-291}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-291}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-292}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-292}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-293}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-293}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-294}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-294}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-295}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-295}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-296}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-296}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-297}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-297}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-298}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-298}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-299}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-299}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-300}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-300}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-301}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-301}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-302}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-302}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-303}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-303}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-304}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-304}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-305}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-305}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-306}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-306}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-307}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-307}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-308}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-308}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-309}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-309}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-310}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-310}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-311}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-311}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-312}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-312}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-313}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-313}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-314}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-314}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-315}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-315}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-316}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-316}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-317}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-317}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-318}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-318}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-319}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-319}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-320}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-320}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-321}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-321}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-322}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-322}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-323}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-323}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-324}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-324}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-325}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-325}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-326}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-326}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-327}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-327}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-328}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-328}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-329}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-329}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-330}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-330}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-331}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-331}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-332}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-332}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-333}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-333}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-334}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-334}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-335}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-335}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-336}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-336}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-337}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-337}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-338}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-338}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-339}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-339}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-340}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-340}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-341}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-341}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-342}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-342}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-343}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-343}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-344}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-344}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-345}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-345}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-346}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-346}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-347}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-347}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-348}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-348}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-349}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-349}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-350}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-350}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-351}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-351}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-352}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-352}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-353}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-353}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-354}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-354}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-355}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-355}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-356}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-356}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-357}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-357}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-358}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-358}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-359}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-359}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-360}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-360}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-361}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-361}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-362}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-362}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-363}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-363}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-364}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-364}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-365}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-365}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-366}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-366}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-367}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-367}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-368}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-368}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-369}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-369}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-370}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-370}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-371}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-371}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-372}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-372}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-373}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-373}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-374}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-374}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-375}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-375}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-376}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-376}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-377}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-377}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-378}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-378}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-379}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-379}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-380}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-380}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-381}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-381}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-382}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-382}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-383}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-383}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-384}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-384}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-385}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-385}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-386}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-386}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-387}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-387}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-388}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-388}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-389}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-389}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-390}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-390}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-391}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-391}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-392}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-392}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-393}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-393}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-394}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-394}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-395}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-395}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-396}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-396}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-397}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-397}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-398}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-398}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-399}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-399}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-400}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-400}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-401}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-401}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-402}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-402}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-403}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-403}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-404}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-404}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-405}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-405}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-406}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-406}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-407}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-407}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-408}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-408}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-409}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-409}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-410}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-410}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-411}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-411}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-412}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-412}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-413}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-413}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-414}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-414}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-415}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-415}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-416}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-416}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-417}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-417}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-418}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-418}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-419}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-419}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-420}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-420}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-421}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-421}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-422}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-422}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-423}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-423}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-424}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-424}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-425}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-425}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-426}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-426}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-427}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-427}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-428}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-428}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-429}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-429}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-430}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-430}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-431}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-431}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-432}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-432}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-433}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-433}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-434}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-434}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-435}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-435}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-436}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-436}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-437}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-437}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-438}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-438}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-439}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-439}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-440}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-440}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-441}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-441}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-442}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-442}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-443}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-443}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-444}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-444}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-445}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-445}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-446}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-446}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-447}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-447}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-448}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-448}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-449}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-449}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-450}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-450}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-451}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-451}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-452}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-452}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-453}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-453}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-454}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-454}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-455}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-455}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-456}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-456}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-457}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-457}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-458}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-458}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-459}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-459}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-460}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-460}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-461}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-461}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-462}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-462}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-463}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-463}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-464}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-464}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-465}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-465}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-466}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-466}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-467}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-467}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-468}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-468}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-469}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-469}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-470}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-470}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-471}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-471}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-472}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-472}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-473}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-473}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-474}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-474}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-475}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-475}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-476}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-476}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-477}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-477}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-478}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-478}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-479}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-479}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-480}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-480}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-481}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-481}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-482}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-482}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-483}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-483}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-484}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-484}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-485}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-485}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-486}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-486}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-487}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-487}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-488}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-488}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-489}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-489}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-490}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-490}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-491}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-491}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-492}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-492}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-493}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-493}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-494}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-494}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-495}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-495}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-496}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-496}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-497}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-497}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-498}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-498}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-499}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-499}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-500}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-500}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-501}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-501}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-502}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-502}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-503}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-503}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-504}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-504}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-505}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-505}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-506}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-506}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-507}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-507}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-508}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-508}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-509}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-509}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-510}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-510}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-511}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-511}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-512}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-512}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-513}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-513}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-514}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-514}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-515}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-515}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-516}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-516}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-517}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-517}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-518}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-518}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-519}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-519}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-520}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-520}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-521}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-521}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-522}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-522}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-523}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-523}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-524}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-524}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-525}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-525}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-526}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-526}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-527}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-527}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-528}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-528}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-529}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-529}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-530}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-530}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-531}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-531}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-532}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-532}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-533}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-533}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-534}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-534}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-535}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-535}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-536}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-536}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-537}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-537}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-538}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-538}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-539}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-539}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-540}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-540}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-541}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-541}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-542}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-542}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-543}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-543}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-544}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-544}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-545}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-545}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-546}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-546}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-547}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-547}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-548}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-548}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-549}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-549}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-550}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-550}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-551}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-551}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-552}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-552}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-553}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-553}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-554}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-554}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-555}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-555}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-556}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-556}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-557}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-557}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-558}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-558}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-559}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-559}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-560}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-560}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-561}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-561}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-562}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-562}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-563}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-563}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-564}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-564}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-565}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-565}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-566}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-566}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-567}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-567}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-568}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-568}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-569}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-569}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-570}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-570}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-571}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-571}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-572}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-572}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-573}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-573}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-574}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-574}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-575}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-575}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-576}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-576}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-577}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-577}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-578}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-578}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-579}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-579}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-580}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-580}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-581}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-581}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-582}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-582}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-583}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-583}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-584}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-584}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-585}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-585}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-586}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-586}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-587}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-587}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-588}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-588}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-589}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-589}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-590}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-590}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-591}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-591}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-592}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-592}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-593}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-593}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-594}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-594}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-595}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-595}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-596}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-596}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-597}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-597}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-598}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-598}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-599}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-599}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-600}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-600}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-601}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-601}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-602}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-602}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-603}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-603}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-604}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-604}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-605}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-605}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-606}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-606}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-607}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-607}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-608}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-608}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-609}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-609}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-610}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-610}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-611}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-611}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-612}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-612}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-613}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-613}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-614}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-614}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-615}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-615}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-616}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-616}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-617}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-617}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-618}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-618}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-619}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-619}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-620}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-620}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-621}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-621}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-622}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-622}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-623}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-623}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-624}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-624}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-625}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-625}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-626}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-626}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-627}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-627}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-628}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-628}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-629}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-629}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-630}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-630}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-631}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-631}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-632}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-632}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-633}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-633}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-634}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-634}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-635}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-635}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-636}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-636}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-637}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-637}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-638}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-638}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-639}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-639}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-640}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-640}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-641}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-641}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-642}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-642}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-643}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-643}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-644}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-644}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-645}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-645}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-646}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-646}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-647}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-647}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-648}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-648}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-649}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-649}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-650}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-650}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-651}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-651}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-652}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-652}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-653}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-653}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-654}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-654}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-655}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-655}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-656}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-656}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-657}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-657}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-658}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-658}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-659}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-659}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-660}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-660}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-661}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-661}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-662}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-662}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-663}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-663}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-664}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-664}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-665}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-665}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-666}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-666}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-667}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-667}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-668}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-668}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-669}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-669}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-670}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-670}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-671}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-671}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-672}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-672}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-673}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-673}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-674}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-674}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-675}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-675}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-676}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-676}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-677}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-677}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-678}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-678}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-679}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-679}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-680}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-680}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-681}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-681}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-682}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-682}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-683}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-683}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-684}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-684}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-685}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-685}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-686}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-686}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-687}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-687}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-688}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-688}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-689}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-689}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-690}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-690}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-691}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-691}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-692}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-692}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-693}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-693}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-694}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-694}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-695}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-695}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-696}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-696}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-697}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-697}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-698}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-698}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-699}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-699}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-700}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-700}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-701}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-701}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-702}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-702}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-703}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-703}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-704}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-704}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-705}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-705}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-706}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-706}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-707}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-707}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-708}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-708}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-709}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-709}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-710}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-710}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-711}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-711}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-712}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-712}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-713}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-713}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-714}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-714}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-715}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-715}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-716}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-716}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-717}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-717}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-718}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-718}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-719}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-719}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-720}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-720}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-721}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-721}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-722}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-722}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-723}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-723}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-724}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-724}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-725}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-725}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-726}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-726}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-727}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-727}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-728}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-728}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-729}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-729}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-730}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-730}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-731}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-731}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-732}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-732}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-733}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-733}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-734}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-734}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-735}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-735}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-736}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-736}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-737}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-737}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-738}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-738}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-739}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-739}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-740}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-740}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-741}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-741}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-742}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-742}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-743}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-743}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-744}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-744}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-745}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-745}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-746}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-746}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-747}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-747}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-748}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-748}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-749}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-749}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-750}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-750}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-751}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-751}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-752}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-752}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-753}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-753}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-754}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-754}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-755}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-755}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-756}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-756}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-757}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-757}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-758}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-758}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-759}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-759}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-760}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-760}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-761}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-761}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-762}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-762}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-763}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-763}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-764}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-764}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-765}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-765}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-766}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-766}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-767}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-767}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-768}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-768}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-769}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-769}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-770}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-770}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-771}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-771}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-772}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-772}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-773}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-773}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-774}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-774}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-775}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-775}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-776}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-776}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-777}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-777}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-778}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-778}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-779}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-779}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-780}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-780}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-781}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-781}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-782}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-782}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-783}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-783}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-784}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-784}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-785}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-785}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-786}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-786}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-787}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-787}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-788}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-788}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-789}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-789}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-790}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-790}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-791}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-791}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-792}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-792}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-793}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-793}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-794}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-794}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-795}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-795}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-796}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-796}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-797}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-797}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-798}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-798}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-799}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-799}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-800}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-800}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-801}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-801}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-802}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-802}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-803}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-803}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-804}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-804}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-805}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-805}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-806}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-806}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-807}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-807}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-808}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-808}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-809}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-809}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-810}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-810}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-811}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-811}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-812}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-812}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-813}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-813}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-814}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-814}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-815}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-815}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-816}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-816}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-817}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-817}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-818}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-818}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-819}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-819}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-820}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-820}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-821}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-821}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-822}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-822}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-823}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-823}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-824}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-824}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-825}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-825}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-826}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-826}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-827}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-827}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-828}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-828}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-829}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-829}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-830}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-830}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-831}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-831}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-832}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-832}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-833}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-833}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-834}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-834}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-835}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-835}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-836}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-836}
-\end{figure}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-1}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-2}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-2}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-3}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-5-3}
+\end{figure}
+
+\begin{verbatim}
+[1] 0.9972485
+\end{verbatim}
+
+\begin{verbatim}
+    Pearson's product-moment correlation
+
+data:  KEEP$wattGLB and KEEP$Low_B.Low_W.glo
+t = 7903.5, df = 345175, p-value < 2.2e-16
+alternative hypothesis: true correlation is not equal to 0
+95 percent confidence interval:
+ 0.9972301 0.9972667
+sample estimates:
+      cor 
+0.9972485 
+\end{verbatim}
 
@@
 \begin{verbatim}
-2024-09-06 06:08:04.9 athan@sagan GHI_enh_02_ID_CE.R 2.698150 mins
+2024-09-06 09:06:13.6 athan@sagan GHI_enh_08_validation.R 2.489076 mins
 \end{verbatim}

### 2024-09-06 GHI_enh_08_validation.R
Commit 2024-09-06 12:14

@@ -91,10 +91,10 @@ source("./GHI_enh_00_dictionary.R")
 
 ## Override notification function
 options(error = function() {
-    if (interactive()) {
-        system("mplayer /usr/share/sounds/freedesktop/stereo/dialog-warning.oga", ignore.stdout = T, ignore.stderr = T)
-        system(paste("notify-send -u normal -t 30000 ", Script.Name, " 'An error occurred!'"))
-    }
+  if (interactive()) {
+    system("mplayer /usr/share/sounds/freedesktop/stereo/dialog-warning.oga", ignore.stdout = T, ignore.stderr = T)
+    system(paste("notify-send -u normal -t 30000 ", Script.Name, " 'An error occurred!'"))
+  }
 })
 
 
@@ -111,10 +111,10 @@ set.seed(RANDOM_SEED)
 
 
 
-cat("Drop all enhacement cases")
+cat("Drop all enhacement cases\n\n")
 DATA <- DATA[Enhanc_C_4 == F]
 
-cat("Drop all clouds")
+cat("Drop all clouds\n\n")
 DATA <- DATA[TYPE == "Clear"]
 
 
@@ -123,15 +123,18 @@ DATA <- janitor::remove_empty(DATA, which = "cols")
 
 COMPLETE <- DATA[, .(Completeness = sum(!is.na(wattGLB)) / DayLength) , by = Day ]
 
+## ??
+# DATA[, Completeness := sum(!is.na(wattGLB)) / DayLength , by = Day ]
 
-day_fill <- 0.7
+
+day_fill <- 0.8
 
 KEEP <- DATA[Day %in% COMPLETE[Completeness > day_fill, Day], ]
+# KEEP <- DATA[Completeness > day_fill, ]
+
+
 
 hist(COMPLETE$Completeness)
-
-
-
 
 
 
@@ -144,41 +147,41 @@ sunny_days <- KEEP[, .(Sunshine = sum(TYPE == "Clear") / max(DayLength, na.rm = 
 
 
 ## days with maximum values
-setorder(enh_days, -Enh_diff_max)
-maxenhd <- enh_days[1:400]
+# setorder(enh_days, -Enh_diff_max)
+# maxenhd <- enh_days[1:400]
 
 ## strong total enhancement days
-setorder(enh_days, -Enh_sum)
-daylist <- enh_days[1:400]
[…]

### 2024-09-06 GHI_enh_08_validation.tex
Commit 2024-09-06 13:09

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Enhancement of SDR in Thessaloniki},
-  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
-  colorlinks=true,
-  linkcolor={Maroon},
-  filecolor={Maroon},
-  citecolor={Blue},
-  urlcolor={Blue},
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{longtable,booktabs,array}
@@
 
-\hypertarget{plot-some-days-with-strong-enhancement-cases}{%
-\section{Plot some days with strong enhancement cases}\label{plot-some-days-with-strong-enhancement-cases}}
+\section{Plot some days with strong enhancement cases}\label{plot-some-days-with-strong-enhancement-cases}
 
@@
 
-\hypertarget{days-with-sunny-day}{%
-\subsection{Days with sunny day}\label{days-with-sunny-day}}
+\subsection{Days with sunny day}\label{days-with-sunny-day}
 
@@
 
-\hypertarget{days-with-sunny-enhancement-day}{%
-\subsection{Days with sunny enhancement day}\label{days-with-sunny-enhancement-day}}
+\subsection{Days with sunny enhancement day}\label{days-with-sunny-enhancement-day}
 
@@
 
-\hypertarget{days-with-cloudy-day}{%
-\subsection{Days with cloudy day}\label{days-with-cloudy-day}}
+\subsection{Days with cloudy day}\label{days-with-cloudy-day}
 
@@
 
-\hypertarget{days-with-random-day}{%
-\subsection{Days with random day}\label{days-with-random-day}}
+\subsection{Days with random day}\label{days-with-random-day}
 
@@
 
-\hypertarget{days-with-manual-test-days}{%
-\subsection{Days with manual test days}\label{days-with-manual-test-days}}
+\subsection{Days with manual test days}\label{days-with-manual-test-days}
 
@@
 
+\newpage
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot}\NormalTok{(KEEP[, Low\_B.Low\_W.glo, wattGLB], }\AttributeTok{xlab =} \StringTok{"Low\_B.Low\_W.glo Clear Sky"}\NormalTok{)}
+\FunctionTok{title}\NormalTok{(}\FunctionTok{paste}\NormalTok{(}\StringTok{"Days:"}\NormalTok{, }\FunctionTok{length}\NormalTok{(}\FunctionTok{unique}\NormalTok{(KEEP[, Day])), }\StringTok{"Day fill:"}\NormalTok{, day\_fill, }\StringTok{"Points:"}\NormalTok{, KEEP[, }\FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wattGLB))]))}
+\FunctionTok{abline}\NormalTok{(}\AttributeTok{a =} \DecValTok{0}\NormalTok{, }\AttributeTok{b =} \DecValTok{1}\NormalTok{, }\AttributeTok{col =} \StringTok{"green"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
 \begin{figure}[H]
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-6}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-6-1}
 
@@
 
-\caption{ - empty caption - }\label{fig:example-days-6}
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6}
 \end{figure}
 
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-7}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-7}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-8}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-8}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-9}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-9}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-10}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-10}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-1}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-1}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-2}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-2}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-3}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-3}
-\end{figure}
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{print}\NormalTok{(}\FunctionTok{cor.test}\NormalTok{(KEEP}\SpecialCharTok{$}\NormalTok{wattGLB, KEEP}\SpecialCharTok{$}\NormalTok{Low\_B.Low\_W.glo, }\AttributeTok{method =} \FunctionTok{c}\NormalTok{(}\StringTok{"pearson"}\NormalTok{)))}
+\end{Highlighting}
+\end{Shaded}
 
 \begin{verbatim}
-[1] 0.9972485
-\end{verbatim}
 
-\begin{verbatim}
     Pearson's product-moment correlation
@@
 
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{print}\NormalTok{(}\FunctionTok{lm}\NormalTok{(KEEP[, wattGLB, Low\_B.Low\_W.glo]))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+
+Call:
+lm(formula = KEEP[, wattGLB, Low_B.Low_W.glo])
+
+Coefficients:
+(Intercept)      wattGLB  
+     18.357        1.038  
+\end{verbatim}
+
+\newpage
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plot}\NormalTok{(KEEP[, Enhanc\_C\_4\_ref, wattGLB], }\AttributeTok{xlab =} \StringTok{"CE threshold"}\NormalTok{)}
+\FunctionTok{title}\NormalTok{(}\FunctionTok{paste}\NormalTok{(}\StringTok{"Days:"}\NormalTok{, }\FunctionTok{length}\NormalTok{(}\FunctionTok{unique}\NormalTok{(KEEP[, Day])), }\StringTok{"Day fill:"}\NormalTok{, day\_fill, }\StringTok{"Points:"}\NormalTok{, KEEP[, }\FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wattGLB))]))}
+\FunctionTok{abline}\NormalTok{(}\AttributeTok{a =} \DecValTok{0}\NormalTok{, }\AttributeTok{b =} \DecValTok{1}\NormalTok{, }\AttributeTok{col =} \StringTok{"green"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-7-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-7}
+\end{figure}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{print}\NormalTok{(}\FunctionTok{cor.test}\NormalTok{(KEEP}\SpecialCharTok{$}\NormalTok{wattGLB, KEEP}\SpecialCharTok{$}\NormalTok{Enhanc\_C\_4\_ref, }\AttributeTok{method =} \FunctionTok{c}\NormalTok{(}\StringTok{"pearson"}\NormalTok{)))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+
+    Pearson's product-moment correlation
+
+data:  KEEP$wattGLB and KEEP$Enhanc_C_4_ref
+t = 7938, df = 345175, p-value < 2.2e-16
+alternative hypothesis: true correlation is not equal to 0
+95 percent confidence interval:
+ 0.9972540 0.9972904
+sample estimates:
+      cor 
+0.9972722 
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{print}\NormalTok{(}\FunctionTok{lm}\NormalTok{(KEEP[, wattGLB, Enhanc\_C\_4\_ref]))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+
+Call:
+lm(formula = KEEP[, wattGLB, Enhanc_C_4_ref])
+
+Coefficients:
+(Intercept)      wattGLB  
+     34.056        1.078  
+\end{verbatim}
+
 \textbf{END}
@@
 \begin{verbatim}
-2024-09-06 09:06:13.6 athan@sagan GHI_enh_08_validation.R 2.489076 mins
+2024-09-06 09:43:14.1 athan@sagan GHI_enh_08_validation.R 2.207945 mins
 \end{verbatim}

### 2024-09-06 GHI_enh_02_ID_CE.R

@@ -293,9 +293,8 @@ switch(csmodel,
        Low_2_B.Low_2_W = { C4_cs_ref_ratio <- 1.03; C4_GLB_diff_THRES <-  5; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
        Low_B.Exact_W   = { C4_cs_ref_ratio <- 1.04; C4_GLB_diff_THRES <- 20; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
        Low_B.High_W    = { C4_cs_ref_ratio <- 1.05; C4_GLB_diff_THRES <- 20; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.12},
-       # Low_B.Low_W     = { C4_cs_ref_ratio <- 1.05; C4_GLB_diff_THRES <-  0; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.18}, ## without transparency
-       # Low_B.Low_W     = { C4_cs_ref_ratio <- 1.09; C4_GLB_diff_THRES <-  0; C4_lowcut_sza <- 60; C4_lowcut_ratio <- 1.18}, ## without transparency
-       Low_B.Low_W     = { C4_cs_ref_ratio <- 1.04; C4_GLB_diff_THRES <- 15; C4_lowcut_sza <- 90; C4_lowcut_ratio <- 1.04},
+       # Low_B.Low_W     = { C4_cs_ref_ratio <- 1.04; C4_GLB_diff_THRES <- 15; C4_lowcut_sza <- 90; C4_lowcut_ratio <- 1.04}, ## Submitted pater
+       Low_B.Low_W     = { C4_cs_ref_ratio <- 1.00; C4_GLB_diff_THRES <- 25; C4_lowcut_sza <- 90; C4_lowcut_ratio <- 1.00},   ## Values from validation
                          { C4_cs_ref_ratio <- 1   ; C4_GLB_diff_THRES <-  0; C4_lowcut_sza <- 90; C4_lowcut_ratio <- 1   })
 
 

### 2024-09-06 article/article.tex
Commit 2024-09-06 14:14

@@
 collocated Cimel sun photometer and a Brewer spectrophotometer. We found
-a trend in CE events of \(+85\pm 20\,\text{cases}/\text{year}\), and a
+a trend in CE events of \(+111\pm 27\,\text{cases}/\text{year}\), and a
 trend in the CE events irradiation of
-\(+226.4\pm 62.6\,\text{kJ}/\text{year}\). The peak of the CE events was
+\(+325.2\pm 88\,\text{kJ}/\text{year}\). The peak of the CE events was
 observed during May and June. An analysis of the total duration of CE
@@
 \(\text{GHI}\): \begin{equation}
-\text{CE} : E > 15 + 1.04 \cdot \text{GHI}_\text{ref} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
+\text{CE} : E > 25 + 1 \cdot \text{GHI}_\text{ref} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
 \end{equation}
@@
 entire dataset (\(6\) million of one-minute GHI measurements),
-\(1.68\,\%\) were identified as CE events and \(0.04\,\%\) as ECE
+\(2.32\,\%\) were identified as CE events and \(0.04\,\%\) as ECE
 events. The highest recorded GHI due to CE was
 \(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007 at a SZA of
-\(19.9^\circ\) corresponding to OI of \(338.4\,\text{W}/\text{m}^2\) or
-\(31.4\,\%\) above the threshold. The strongest CE event of \(49.9\,\%\)
+\(19.9^\circ\) corresponding to OI of \(369.3\,\text{W}/\text{m}^2\) or
+\(35.3\,\%\) above the threshold. The strongest CE event of \(53\,\%\)
 above the clear sky threshold was observed on 28~October 2016 at a SZA
 of \(59.2^\circ\) with a GHI value of \(861.8\,\text{W}/\text{m}^2\) and
-a OI of \(286.9\,\text{W}/\text{m}^2\). Both cases are ECE events with
+a OI of \(298.4\,\text{W}/\text{m}^2\). Both cases are ECE events with
 \(136.8\,\text{W}/\text{m}^2\) and \(164.5\,\text{W}/\text{m}^2\) above
@@
 increasing trends, most pronounced for the frequency of occurrence
-(\(+85\pm 20\,\text{cases}/\text{year}\)) and the excess irradiation
-(\(+226.4 \pm 62.6\,\text{kJ}/\text{year}\)), which are also
-statistically significant. In contrast the trend of the yearly mean OI
-is negligible (\(+0.12\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of
-no statistical significance. The average OI for the entire period is
-\(+39.7\pm 2.8\,\text{W}/\text{m}^2\). The interannual variability of
+(\(+111\pm 27\,\text{cases}/\text{year}\)) and the excess irradiation
+(\(+325.2 \pm 88\,\text{kJ}/\text{year}\)), which are also statistically
+significant. In contrast the trend of the yearly mean OI is negligible
+(\(+0.14\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of no
+statistical significance. The average OI for the entire period is
+\(+42.6\pm 2.8\,\text{W}/\text{m}^2\). The interannual variability of
 the data about the trend lines is quite large. Furthermore, the spread
@@
 events. For the majority (over \(62\,\%\)) of the CE events the OI is
-below the long-term average of \(39.7\,\text{W}/\text{m}^2\), while
+below the long-term average of \(42.6\,\text{W}/\text{m}^2\), while
 about \(8.1\,\%\) of the events correspond to OI larger than
@@
 of these consecutive events, we grouped them into bins of increasing
-duration in steps of one minute. We have identified 26837 groups of CE
+duration in steps of one minute. We have identified 34849 groups of CE
 in the whole period of study, where the group of the longest duration of
@@
 After analyzing the CE cases, we found an increase of
-\(+85.3\pm 20\,\text{cases}/\text{year}\), with the mean annual
+\(+111\pm 26.9\,\text{cases}/\text{year}\), with the mean annual
 irradiation of the CE events increasing with a rate of
-\(+226.4\pm 62.6\,\text{kJ}/\text{year}\). The most active months of CE
+\(+325.2\pm 88\,\text{kJ}/\text{year}\). The most active months of CE
 events are May and June. We found that continuous CE events can last up

### 2024-09-06 GHI_enh_03_process.tex
Commit 2024-09-06 14:14

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-09-05}
+\date{2024-09-06}
 
@@
     Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
--72.8133 -27.4706   0.7672   0.4338  28.2495  83.4876 
+-72.8133 -27.4706   0.7675   0.4342  28.2501  83.4876 
 \end{verbatim}
@@
     Min      1Q  Median      3Q     Max 
--333.34 -132.29  -52.26   96.74  664.64
+-440.00 -199.37  -79.04  137.06  963.22
 
@@
                   Estimate Std. Error t value Pr(>|t|)    
-(Intercept)      7.113e+00  4.604e+01   0.155    0.877    
-as.numeric(Date) 2.252e-07  3.656e-08   6.160 1.98e-09 ***
+(Intercept)      3.300e+01  6.644e+01   0.497     0.62    
+as.numeric(Date) 2.926e-07  5.276e-08   5.546 5.73e-08 ***
 ---
@@
 
-Residual standard error: 189.5 on 354 degrees of freedom
-Multiple R-squared:  0.09681,   Adjusted R-squared:  0.09426 
-F-statistic: 37.94 on 1 and 354 DF,  p-value: 1.979e-09
+Residual standard error: 273.5 on 354 degrees of freedom
+Multiple R-squared:  0.07994,   Adjusted R-squared:  0.07734 
+F-statistic: 30.76 on 1 and 354 DF,  p-value: 5.728e-08
 \end{verbatim}
@@
                    Estimate Std. Error t value Pr(>|t|)    
-(Intercept)       7.113e+00  4.604e+01   0.155    0.877    
-ST_E_monthly$Date 2.252e-07  3.656e-08   6.160 1.98e-09 ***
+(Intercept)       3.300e+01  6.644e+01   0.497     0.62    
+ST_E_monthly$Date 2.926e-07  5.276e-08   5.546 5.73e-08 ***
 ---
@@
 \begin{verbatim}
-2024-09-05 19:30:15.8 athan@sagan GHI_enh_03_process.R 3.894151 mins
+2024-09-06 10:16:28.4 athan@sagan GHI_enh_03_process.R 3.892410 mins
 \end{verbatim}

### 2024-09-06 GHI_enh_04_investigate.tex
Commit 2024-09-05 13:11
Commit 2024-09-06 00:14
Commit 2024-09-06 14:14

@@
 \begin{verbatim}
-Warning: Removed 32 rows containing missing values or values outside the scale
+Warning: Removed 29 rows containing missing values or values outside the scale
 range (`geom_bar()`).
@@
 \begin{verbatim}
-Warning: Removed 220 rows containing non-finite outside the scale range
+Warning: Removed 364 rows containing non-finite outside the scale range
 (`stat_bin()`).
@@
 \begin{verbatim}
-Warning: Removed 26591 rows containing non-finite outside the scale range
+Warning: Removed 34442 rows containing non-finite outside the scale range
 (`stat_bin()`).
@@
 \begin{verbatim}
-Warning: Removed 220 rows containing non-finite outside the scale range (`stat_bin()`).
-Removed 26591 rows containing non-finite outside the scale range (`stat_bin()`).
+Warning: Removed 364 rows containing non-finite outside the scale range (`stat_bin()`).
+Removed 34442 rows containing non-finite outside the scale range (`stat_bin()`).
 \end{verbatim}
@@
 \begin{verbatim}
-Warning: Removed 14 rows containing non-finite outside the scale range
+Warning: Removed 19 rows containing non-finite outside the scale range
 (`stat_bin2d()`).
@@
 
-lmY: 226.3963 +/- 31.30176
+lmY: 325.2046 +/- 44.00396
 
@@
 
-lmY: 85.26719 +/- 10.01748
+lmY: 110.9722 +/- 13.43944
 
@@
 
-lmY: 0.116043 +/- 0.055572
+lmY: 0.14418 +/- 0.052969
 
@@
 
-lmY: 0.107931 +/- 0.044598
+lmY: 0.125986 +/- 0.041509
 
@@
 
-lmY: 222.2785 +/- 28.96957
+lmY: 320.1081 +/- 40.93156
 
@@
 
-lmY: 83.81382 +/- 9.456821
+lmY: 109.4004 +/- 12.63018
 
@@
 
-lmY: 229.8063 +/- 39.56838
+lmY: 329.8573 +/- 56.0224
 
@@
 
-lmY: 86.21667 +/- 12.87325
+lmY: 112.1073 +/- 17.43077
 
@@
 
-lmY: 0.085425 +/- 0.09766
+lmY: 0.111567 +/- 0.096855
 
@@
 
-lmY: 0.086495 +/- 0.070955
+lmY: 0.10318 +/- 0.067313
 
@@
 \begin{verbatim}
-2024-09-05 08:56:04.2 athan@sagan GHI_enh_04_investigate.R 13.014418 mins
+2024-09-06 10:26:49.9 athan@sagan GHI_enh_04_investigate.R 10.084896 mins
 \end{verbatim}

### 2024-09-06 GHI_enh_08_validation.tex
Commit 2024-09-06 14:14

--- 2024-09-06 GHI_enh_08_validation.tex
@@
 
+\newpage
+
 \begin{figure}[H]
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-6}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-6-1}
 
@@
 
-\caption{ - empty caption - }\label{fig:example-days-6}
+\caption{ - empty caption - }\label{fig:unnamed-chunk-6}
 \end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-7}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-7}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-8}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-8}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-9}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-9}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-10}
-
-}
-
-\caption{ - empty caption - }\label{fig:example-days-10}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-1}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-1}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-2}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-2}
-\end{figure}
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-3}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-5-3}
-\end{figure}
-
-\begin{verbatim}
-[1] 0.9972485
-\end{verbatim}
 
@@
 
+\begin{verbatim}
+Call:
+lm(formula = KEEP[, wattGLB, Low_B.Low_W.glo])
+
+Coefficients:
+(Intercept)      wattGLB  
+     18.357        1.038  
+\end{verbatim}
+
+\newpage
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-7-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-7}
+\end{figure}
+
+\begin{verbatim}
+    Pearson's product-moment correlation
+
+data:  KEEP$wattGLB and KEEP$Enhanc_C_4_ref
+t = 7938, df = 345175, p-value < 2.2e-16
+alternative hypothesis: true correlation is not equal to 0
+95 percent confidence interval:
+ 0.9972540 0.9972904
+sample estimates:
+      cor 
+0.9972722 
+\end{verbatim}
+
+\begin{verbatim}
+Call:
+lm(formula = KEEP[, wattGLB, Enhanc_C_4_ref])
+
+Coefficients:
+(Intercept)      wattGLB  
+     43.323        1.036  
+\end{verbatim}
+
 \textbf{END}
@@
 \begin{verbatim}
-2024-09-06 09:06:13.6 athan@sagan GHI_enh_08_validation.R 2.489076 mins
+2024-09-06 10:32:08.3 athan@sagan GHI_enh_08_validation.R 1.913171 mins
 \end{verbatim}

### 2024-09-06 article/article.Rmd
Commit 2024-09-06 17:10

@@
 #   using data recorded every one minute. We identified the cloud enhancement (CE)
-#   events by creating an appropriate clear-sky irradiance reference with the use of a
+#   events by creating an appropriate cloud-free irradiance reference with the use of a
 #   radiative transfer model and aerosol optical depth data from a collocated Cimel sun
@@
 Thessaloniki for the period 1994 -- 2023 using data recorded every one minute.  We
-identified the cloud enhancement events (CE) by creating an appropriate clear sky
+identified the cloud enhancement events (CE) by creating an appropriate cloud-free
 irradiance reference with the use of a radiative transfer model and aerosol optical
@@
 reaching the ground. This cloud enhancement (CE) effect can locally increase the
-observed GHI to levels even higher than the expected clear-sky irradiance
+observed GHI to levels even higher than the expected cloud-free irradiance
 [@Cordero2023; @Vamvakas2020; @CastillejoCuberos2020;  and references
@@
 
-Methods of identification of CE events usually include the use of simulated clear
-sky irradiance as baseline, combined with an appropriate threshold or some
+Methods of identification of CE events usually include the use of simulated cloud-free irradiance as baseline, combined with an appropriate threshold or some
 other statistical characteristics, and in some cases, with visual inspection of sky
@@
 frequency of occurrence, intensity, and duration in a thirty-year record of GHI
-observations at Thessaloniki, Greece.  We used modeled clear sky irradiance as a
+observations at Thessaloniki, Greece.  We used modeled cloud-free irradiance as a
 baseline to identify cloud enhancements, and we determined long-term trends of the
@@
 In this study, we define an event as CE when the measured GHI at ground level
-exceeds the expected value under clear-sky conditions. Similarly, we define as
+exceeds the expected value under cloud-free conditions. Similarly, we define as
 extreme cloud enhancement events (ECE), the cases when GHI at ground level exceeds
@@
 $\text{GHI}_\text{ref}$: The Haurwitz's model [@Haurwitz1945], which is a simple
-clear sky model and was already adjusted and applied to our data [@Natsis2023].
+cloud-free model and was already adjusted and applied to our data [@Natsis2023].
 <!--
@@
 
-## Modeled clear Sky Irradiance {#rtmcs}
+## Modeled cloud-free Irradiance {#rtmcs}
 
-### Climatology of clear sky irradiance
+### Climatology of cloud-free irradiance
 
 <!-- Libradtran options -->
-We approximated the expected clear sky $\text{GHI}_\text{ref}$ with the radiative
+We approximated the expected cloud-free $\text{GHI}_\text{ref}$ with the radiative
 transfer model uvspec, part of libRadtran [@Emde2016], similarly to the approach used
@@
 measurements.  For each period of the year, we used the appropriate atmospheric
-profile (afglms or afglmw).  Finally, we calculated the clear sky irradiance value at
+profile (afglms or afglmw).  Finally, we calculated the cloud-free irradiance value at
 the horizontal plane.  Thus, we were able to emulate different atmospheric condition
 and levels of atmospheric clearness for the climatological conditions of the site.
-With this method, the modeled clear sky irradiances can be directly compared to each
+With this method, the modeled cloud-free irradiances can be directly compared to each
 measured one-minute value of GHI, for different conditions of atmospheric clearness.
@@
 
-### Long-term change of clear sky irradiance
+### Long-term change of cloud-free irradiance
 
 <!-- Aerosol change -->
-The clear-sky reference values discussed above are based on the climatological AOD
+The cloud-free reference values discussed above are based on the climatological AOD
 and WC; hence they cannot describe accurately the long-term variation of
@@
 mainly AOD.  As reported by @Natsis2023, there is a long-term brightening effect in
-the GHI data of Thessaloniki for the period 1993 -- 2023, which for clear-sky data
+the GHI data of Thessaloniki for the period 1993 -- 2023, which for cloud-free data
 was attributed to long-term changes in aerosol effects.  Therefore, an adjustment of
@@
 <!--
-To create a unified trend for the long-term change of the clear sky irradiance, we
+To create a unified trend for the long-term change of the cloud-free irradiance, we
 simulated the values of AOD derived from those sources with Libradtran. For both
@@
 representative of all days in the year in order
-to get a rough estimate of the annually averaged change in clear sky irradiance.  For
+to get a rough estimate of the annually averaged change in cloud-free irradiance.  For
 the period 2005 -- 2023 we used the mean monthly values of AOD and WC from AERONET in
-a similar simulation scheme to calculate the monthly mean clear-sky irradiance,
+a similar simulation scheme to calculate the monthly mean cloud-free irradiance,
 and finally the change of $+0.14\,\%$ per year. We applied these two long-term changes
 (see Figure\nobreakspace{}\ref{fig:CS-change}) to the climatological
-$\text{GHI}_\text{ref}$, to create a more realistic representation of the clear-sky
+$\text{GHI}_\text{ref}$, to create a more realistic representation of the cloud-free
 irradiance for the whole period of study.  The rate of changes in the two subperiods
@@
 
-```{r CS-change, echo=FALSE, fig.cap="Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1994 -- 2023."}
+```{r CS-change, echo=FALSE, fig.cap="Simulated long-term change in cloud-free irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1994 -- 2023."}
 knitr::include_graphics("../images/P-CS-change-1.png")
@@
 achieving this goal is to define a threshold for the CE identification,
-representative of the clear-sky irradiance at the time of each GHI measurement. This
+representative of the cloud-free irradiance at the time of each GHI measurement. This
 depends on the selection of the appropriate atmospheric parameterization for the RTM
@@
 section\nobreakspace{}\ref{rtmcs}, allows capturing a large part of the natural
-variability of clear-sky GHI. However, the short-term variability of AOD cannot be
+variability of cloud-free GHI. However, the short-term variability of AOD cannot be
 taken adequately into account when using monthly values in the model simulations. We
@@
 where: $\text{E}$ the measured irradiance, $\text{E}_\text{CSm}$ the selected
-modelled clear sky irradiance, and $i$ each of the one-minute observation.  This is
+modelled cloud-free irradiance, and $i$ each of the one-minute observation.  This is
 the criterion of our CE identification.
@@
 (b) the largest daily total OI,
-(c) absence of clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
+(c) absence of clouds (by implementing a cloud-free identification algorithm as discussed in @Natsis2023),
 (d) absence of clouds and absence of CE events,
@@
 The definition of the CE events with this method has a degree of subjectivity, since
-the actual clear sky irradiance is not known and can only be approximated.  However,
+the actual cloud-free irradiance is not known and can only be approximated.  However,
 this method was proven capable in detecting all major CE events.  Where some CE
@@
 An example of CE identification for a selected day is given in the
-Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of the clear sky
+Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of the cloud-free
 reference irradiance and the CE and ECE identification thresholds are shown along
 with the actual GHI measurements.  In addition, we provide an example scatter plot
-between the measured and the modeled clear-sky irradiance for one year, where the CE
+between the measured and the modeled cloud-free irradiance for one year, where the CE
 and ECE events are clearly grouped above the threshold of irradiance
@@
 
-```{r example-year, echo=FALSE, fig.cap="Example scatter plot of the measured GHI and the reference clear sky irradiance in Thessaloniki for the year 2005.
+```{r example-year, echo=FALSE, fig.cap="Example scatter plot of the measured GHI and the reference cloud-free irradiance in Thessaloniki for the year 2005.
 The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.
@@
 $`r round(100*MC[Typ == "Max Enha", GLB_ench],1)`\,\%$ above the 
-clear sky threshold was observed on 
+cloud-free threshold was observed on 
 `r strftime(MC[Typ == "Max Enha", Date], "%d\\ %B %Y")` at a SZA of
@@
 events.  This is also depicted by the ECE irradiance values, which exceed the
-equivalent clear sky irradiance by a significant amount.
+equivalent cloud-free irradiance by a significant amount.
 
@@
 period in early autumn (September and October).  This is probably related to the
-weather characteristics in these periods, with frequent alternations between clear
-sky periods and clouds.
+weather characteristics in these periods, with frequent alternations between cloud-free periods and clouds.
 
@@
 
-By creating a clear sky approximation representing the long- and short-term
-variability of the expected clear sky GHI, we were able to identify cases of CE
+By creating a cloud-free approximation representing the long- and short-term
+variability of the expected cloud-free GHI, we were able to identify cases of CE
 events in Thessaloniki for the period 1994 -- 2023.  After analyzing the CE cases, we

### 2024-09-06 GHI_enh_daily_test_plots.R
Commit 2024-09-06 17:10

@@ -264,7 +264,7 @@ for (ii in 1:nrow(gather_days)) {
   ## Active model reference
   lines(temp[, get(paste0(SelEnhanc, "_ref")), Date], col = "red" )
 
-  ## Clear sky ref
+  ## Cloud-free ref
   lines(temp[, get(paste0(csmodel,".glo")), Date], col = "darkorchid" )
 
   # ## add sza axis
@@ -285,7 +285,7 @@ for (ii in 1:nrow(gather_days)) {
   title(main = paste(as.Date(aday, origin = "1970-01-01"), doy , type))
 
   legend("bottomright", ncol = 2,
-         c(  "GHI","CE threshold","TSI at TOA on horizontal plane","Solar Constant", "CE events","ECE events","Identified clouds",  "Clear sky"),
+         c(  "GHI","CE threshold","TSI at TOA on horizontal plane","Solar Constant", "CE events","ECE events","Identified clouds",  "Cloud-free")
          col = c("green",         "red",                  "black",       "orange2","burlywood4",       "red",             "blue","darkorchid"),
          pch = c(     NA,            NA,                       NA,              NA,          1 ,          1 ,                  3,           NA),
          lty = c(      1,             1,                        1,               1,          NA,          NA,                 NA,            1),

### 2024-09-06 article/article.tex
Commit 2024-09-06 19:12

@@
 recorded every one minute. We identified the cloud enhancement events
-(CE) by creating an appropriate clear sky irradiance reference with the
+(CE) by creating an appropriate cloud-free irradiance reference with the
 use of a radiative transfer model and aerosol optical depth data from a
@@
 ground. This cloud enhancement (CE) effect can locally increase the
-observed GHI to levels even higher than the expected clear-sky
+observed GHI to levels even higher than the expected cloud-free
 irradiance {[}\citet{Cordero2023}; \citet{Vamvakas2020};
@@
 Methods of identification of CE events usually include the use of
-simulated clear sky irradiance as baseline, combined with an appropriate
-threshold or some other statistical characteristics, and in some cases,
-with visual inspection of sky camera images \citep[ and references
-therein]{Vamvakas2020, Mol2023}.
+simulated cloud-free irradiance as baseline, combined with an
+appropriate threshold or some other statistical characteristics, and in
+some cases, with visual inspection of sky camera images \citep[ and
+references therein]{Vamvakas2020, Mol2023}.
 
@@
 a thirty-year record of GHI observations at Thessaloniki, Greece. We
-used modeled clear sky irradiance as a baseline to identify cloud
+used modeled cloud-free irradiance as a baseline to identify cloud
 enhancements, and we determined long-term trends of the above-mentioned
@@
 In this study, we define an event as CE when the measured GHI at ground
-level exceeds the expected value under clear-sky conditions. Similarly,
+level exceeds the expected value under cloud-free conditions. Similarly,
 we define as extreme cloud enhancement events (ECE), the cases when GHI
@@
 \(\text{GHI}_\text{ref}\): The Haurwitz's model \citep{Haurwitz1945},
-which is a simple clear sky model and was already adjusted and applied
+which is a simple cloud-free model and was already adjusted and applied
 to our data \citep{Natsis2023}. We created a threshold by using an
@@
 \hypertarget{rtmcs}{%
-\subsection{Modeled clear Sky Irradiance}\label{rtmcs}}
+\subsection{Modeled cloud-free Irradiance}\label{rtmcs}}
 
-\hypertarget{climatology-of-clear-sky-irradiance}{%
-\subsubsection{Climatology of clear sky
-irradiance}\label{climatology-of-clear-sky-irradiance}}
+\hypertarget{climatology-of-cloud-free-irradiance}{%
+\subsubsection{Climatology of cloud-free
+irradiance}\label{climatology-of-cloud-free-irradiance}}
 
-We approximated the expected clear sky \(\text{GHI}_\text{ref}\) with
+We approximated the expected cloud-free \(\text{GHI}_\text{ref}\) with
 the radiative transfer model uvspec, part of libRadtran
@@
 
-\hypertarget{long-term-change-of-clear-sky-irradiance}{%
-\subsubsection{Long-term change of clear sky
-irradiance}\label{long-term-change-of-clear-sky-irradiance}}
+\hypertarget{long-term-change-of-cloud-free-irradiance}{%
+\subsubsection{Long-term change of cloud-free
+irradiance}\label{long-term-change-of-cloud-free-irradiance}}
 
-The clear-sky reference values discussed above are based on the
+The cloud-free reference values discussed above are based on the
 climatological AOD and WC; hence they cannot describe accurately the
@@
 \citet{Natsis2023}, there is a long-term brightening effect in the GHI
-data of Thessaloniki for the period 1993 -- 2023, which for clear-sky
+data of Thessaloniki for the period 1993 -- 2023, which for cloud-free
 data was attributed to long-term changes in aerosol effects. Therefore,
@@
 representative of all days in the year in order to get a rough estimate
-of the annually averaged change in clear sky irradiance. For the period
+of the annually averaged change in cloud-free irradiance. For the period
 2005 -- 2023 we used the mean monthly values of AOD and WC from AERONET
-in a similar simulation scheme to calculate the monthly mean clear-sky
+in a similar simulation scheme to calculate the monthly mean cloud-free
 irradiance, and finally the change of \(+0.14\,\%\) per year. We applied
@@
 \(\text{GHI}_\text{ref}\), to create a more realistic representation of
-the clear-sky irradiance for the whole period of study. The rate of
+the cloud-free irradiance for the whole period of study. The rate of
 changes in the two subperiods are different, but reasonable, since the
@@
 
-\caption{Simulated long-term change in clear sky irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1994 -- 2023.}\label{fig:CS-change}
+\caption{Simulated long-term change in cloud-free irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1994 -- 2023.}\label{fig:CS-change}
 \end{figure}
@@
 key issue for achieving this goal is to define a threshold for the CE
-identification, representative of the clear-sky irradiance at the time
+identification, representative of the cloud-free irradiance at the time
 of each GHI measurement. This depends on the selection of the
@@
 section\nobreakspace{}\ref{rtmcs}, allows capturing a large part of the
-natural variability of clear-sky GHI. However, the short-term
+natural variability of cloud-free GHI. However, the short-term
 variability of AOD cannot be taken adequately into account when using
@@
 following characteristics: (a) the strongest OI CE events, (b) the
-largest daily total OI, (c) absence of clouds (by implementing a clear
-sky identification algorithm as discussed in \citet{Natsis2023}), (d)
-absence of clouds and absence of CE events, (e) with at least \(60\,\%\)
-of the day length without clouds and presence of CE events, (h) randomly
-selected days, and (i) manually selected days. For the latter case and
-where needed, we also used images from the sky-camera to further aid the
-decision of the manual inspection.
+largest daily total OI, (c) absence of clouds (by implementing a
+cloud-free identification algorithm as discussed in \citet{Natsis2023}),
+(d) absence of clouds and absence of CE events, (e) with at least
+\(60\,\%\) of the day length without clouds and presence of CE events,
+(h) randomly selected days, and (i) manually selected days. For the
+latter case and where needed, we also used images from the sky-camera to
+further aid the decision of the manual inspection.
 
 The definition of the CE events with this method has a degree of
-subjectivity, since the actual clear sky irradiance is not known and can
-only be approximated. However, this method was proven capable in
+subjectivity, since the actual cloud-free irradiance is not known and
+can only be approximated. However, this method was proven capable in
 detecting all major CE events. Where some CE events with very low OI may
@@
 Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of
-the clear sky reference irradiance and the CE and ECE identification
+the cloud-free reference irradiance and the CE and ECE identification
 thresholds are shown along with the actual GHI measurements. In
 addition, we provide an example scatter plot between the measured and
-the modeled clear-sky irradiance for one year, where the CE and ECE
+the modeled cloud-free irradiance for one year, where the CE and ECE
 events are clearly grouped above the threshold of irradiance
@@
 
-\caption{Example scatter plot of the measured GHI and the reference clear sky irradiance in Thessaloniki for the year 2005.
+\caption{Example scatter plot of the measured GHI and the reference cloud-free irradiance in Thessaloniki for the year 2005.
 The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.
@@
 \(35.3\,\%\) above the threshold. The strongest CE event of \(53\,\%\)
-above the clear sky threshold was observed on 28~October 2016 at a SZA
+above the cloud-free threshold was observed on 28~October 2016 at a SZA
 of \(59.2^\circ\) with a GHI value of \(861.8\,\text{W}/\text{m}^2\) and
@@
 redistributed through the CE events. This is also depicted by the ECE
-irradiance values, which exceed the equivalent clear sky irradiance by a
-significant amount.
+irradiance values, which exceed the equivalent cloud-free irradiance by
+a significant amount.
 
@@
 October). This is probably related to the weather characteristics in
-these periods, with frequent alternations between clear sky periods and
+these periods, with frequent alternations between cloud-free periods and
 clouds.
@@
 
-By creating a clear sky approximation representing the long- and
-short-term variability of the expected clear sky GHI, we were able to
+By creating a cloud-free approximation representing the long- and
+short-term variability of the expected cloud-free GHI, we were able to
 identify cases of CE events in Thessaloniki for the period 1994 -- 2023.

### 2024-09-06 article/article.Rmd
Commit 2024-09-06 19:12

@@
 #   In this study we investigate the characteristics of global horizontal irradiance
-#   enhancement events induced by clouds over Thessaloniki for the period 1994 -- 2023
-#   using data recorded every one minute. We identified the cloud enhancement (CE)
-#   events by creating an appropriate cloud-free irradiance reference with the use of a
-#   radiative transfer model and aerosol optical depth data from a collocated Cimel sun
-#   photometer and a Brewer spectrophotometer. We found a trend in CE events of
-#   \(45.6\pm 21.9\,\text{cases}/\text{year}\), and a trend in the CE events
-#   irradiation of \(116.9\pm 67.8\,\text{kJ}/\text{year}\). The peak of the CE events
-#   was observed during May and June. The analysis of the total duration of CE events
-#   showed that durations longer than 5 minutes are very rare, with exceptions lasting
-#   over an hour and up to 140 minutes. Finally, we have detected enhancements above
-#   the total solar irradiance at the top of the atmosphere of up to
-#   \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the cases below
 #   \(200\,\text{W}/\text{m}^{2}\). The most active period of these extreme events is
@@
 
-We studied the enhancement of the global horizontal irradiance induced by clouds over
-Thessaloniki for the period 1994 -- 2023 using data recorded every one minute.  We
-identified the cloud enhancement events (CE) by creating an appropriate cloud-free
-irradiance reference with the use of a radiative transfer model and aerosol optical
-depth data from a collocated Cimel sun photometer and a Brewer spectrophotometer. We
-found a trend in CE events of
+In this study, we investigate the characteristics of global horizontal irradiance
+enhancement events induced by clouds over Thessaloniki for the period 1994 -- 2023
+using data recorded every one minute.  We identified the cloud enhancement (CE)
+events by creating an appropriate cloud-free irradiance reference using a radiative
+transfer model and aerosol optical depth data from a collocated Cimel sun photometer
+and a Brewer spectrophotometer. We found a trend in CE events of
 $`r plus_sign(round(yearlyCE[var=="GLB_diff.N",slope],0))`\pm
 `r round(2*yearlyCE[var=="GLB_diff.N",slope.sd],0)`\,\text{cases}/\text{year}$,
-and a trend in the CE events irradiation of
+and a trend in the corresponding irradiation of
 $`r plus_sign(round(yearlyCE[var=="GLB_diff.sum",slope],1))`\pm
@@
 The peak of the CE events was observed during May and June.  An analysis of the total
-duration of CE events, showed that durations longer than 5 minutes are very rare,
+duration of CE events, showed that with durations longer than 5 minutes are very rare,
 with exceptions lasting over an hour and up to 140 minutes.  Finally, we have
@@
 $400\,\text{W}/\text{m}^{2}$, with the $75\,\%$ of the cases below
-$200\,\text{W}/\text{m}^{2}$. The most active season of these extreme events is
-spring until early summer and autumn.
+$200\,\text{W}/\text{m}^{2}$. Most of these  extreme events occur in
+spring -- early summer, with a secondary peak in autumn.
 
@@
 than $`r 90 - BIO_ELEVA`^\circ$.  Finally, images from a sky camera have been used in
-the manual inspection of the CE identification. The sky camera operates since 2012
-and stores images in 5 min time steps.
-<!--
-Although it is impossible to detect all false data, the large number of
-available data, and the aggregation scheme we used, ensures the quality of the
-radiation measurements used in this study.
--->
-<!-- Data selection -->
-<!--
-To preserve an unbiased representation of the data we applied a constraint, similar
-the one used by @CastillejoCuberos2020. For each valid hour of day, there must exist
-at least 45 minutes of valid measurements, including nighttime, when near sunrise and
-sunset. Days with less than 5 valid hours were rejected completely.
--->
-<!--
-# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7),
-otherwise all data for this day is flagged as invalid. There must be at least This
-work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid,
-otherwise all minute data for this hour is flagged as invalid.
--->
-An overview of the data analyzed for the study of the CE and ECE events is given in
-Figure\nobreakspace{}\ref{fig:CLB-daily}, as the daily mean of the measured GHI.
+the manual inspection of the CE identification. The sky camera has been operating
+since 2012 and stores images in 5 min time steps.  An overview of the GHI data used
+in this study is given in
+Figure\nobreakspace{}\ref{fig:CLB-daily}, as the daily means.
 
-```{r CLB-daily, echo=FALSE, fig.cap="Daily mean values of GHI in Thessaloniki for the period 1994 -- 2023."}
+```{r CLB-daily, echo=FALSE, fig.cap="Timeseries of daily mean GHI measured at Thessaloniki for the period 1994 -- 2023."}
 knitr::include_graphics("../images/P_daily_trend-3.png")
@@
 
-Next we investigated the distribution of the CE events within the year.
+Next, we investigated the distribution of the CE events within the year.
 Figure\nobreakspace{}\ref{fig:relative-month-occurrences} shows the monthly box and

### 2024-09-06 GHI_enh_05_distributions.R
Commit 2024-09-06 20:14

@@ -525,8 +525,9 @@ ggplot(data = DATA[wattGLB > ETH], aes(x = wattGLB - ETH)) +
 DATA[, GL]
 
 MC <-   rbind(
-  DATA[which.max(wattGLB),  .(Typ = "Max Glob", wattGLB, SZA, GLB_ench, GLB_diff, Date, TSI_ref = ETH, TSI_OI = wattGLB - ETH)],
-  DATA[which.max(GLB_ench), .(Typ = "Max Enha", wattGLB, SZA, GLB_ench, GLB_diff, Date, TSI_ref = ETH, TSI_OI = wattGLB - ETH)]
+  DATA[which.max(wattGLB),  .(Typ = "Max Global",  wattGLB, SZA, GLB_ench, GLB_diff, GLB_rati, Date, TSI_ref = ETH, TSI_OI = wattGLB - ETH)],
+  DATA[which.max(GLB_ench), .(Typ = "Max Enh abs", wattGLB, SZA, GLB_ench, GLB_diff, GLB_rati, Date, TSI_ref = ETH, TSI_OI = wattGLB - ETH)],
+  DATA[which.max(GLB_ench), .(Typ = "Max Enh rat", wattGLB, SZA, GLB_ench, GLB_diff, GLB_rati, Date, TSI_ref = ETH, TSI_OI = wattGLB - ETH)]
 )
 MC[, DOY := yday(Date)]
 MC[, Localtime := paste(as.POSIXlt(Date, tz = "Europe/Athens"))]
@@ -537,7 +538,7 @@ saveRDS(MC, "data/Max_cases.Rds")
 
 pander::pander(MC, caption = "Max enhancements")
 
-MC2 <- ST_G0[which.max(GLB_diff.N), .(Date, GLB_diff.N)]
+MC2 <- ST_G0[which.max(GLB_diff.N), .(Date, GLB_diff.N, SZA.first, SZA.last, SZA.min, SZA.max)]
 MC2[ , DOY := yday(Date)]
 MC2[ , Localtime := paste(as.POSIXlt(Date, tz = "Europe/Athens"))]
 

### 2024-09-06 article/article.Rmd
Commit 2024-09-06 20:14

@@
 measured $\text{GHI}$:
-<!--
-($`r 100*(C4_cs_ref_ratio-1)`\,\%$)
-with an additional constant offset of
-$`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$,
-as described in Equation\nobreakspace\ref{eq:CE4}.
--->
 \begin{equation}
@@
 
-<!--
-- can follow for clear days
-- the most important are the thresholds
-- model have to be uniform on clear days
-- the level is adjusted by the threshold 
-- the effect of the sza uniform
--->
-
 The definition of the CE events with this method has a degree of subjectivity, since
@@
 
-An example of CE identification for a selected day is given in the
+An example of the identification of CE events for a selected day is given in the
 Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of the cloud-free

### 2024-09-06 GHI_enh_07_Aerosols_BR_CIM.R
Commit 2024-09-06 21:11

@@ -199,7 +199,9 @@ polyf_zero <- dataset[tsy == tzero, expon]
 
 ## function to apply to GHI
 trend_polyf <- function(tsy) {
-  ((polym_C[1] + polym_C[2] * tsy + polym_C[3] * tsy^2) / polyf_zero) - 1
+  (polym_C[1] / polyf_zero) - 1 +
+  (polym_C[2] / polyf_zero) * tsy  +
+  (polym_C[3] / polyf_zero) * tsy^2
 }
 
 
@@ -207,10 +209,21 @@ cat("GHI_model (abs) =", polym_C[1], "+",
                          polym_C[2], "* year_frac +",
                          polym_C[3], "* year_frac^2", "\n\n")
 
-cat("GHI_model (rat) =", polym_C[1] / polyf_zero, "+",
-                         polym_C[2] / polyf_zero, "* year_frac +",
-                         polym_C[3] / polyf_zero, "* year_frac^2", "\n\n")
+cat("GHI_model (rat) =",
+     signif((polym_C[1] / polyf_zero) - 1, digits = 4), "+",
+     signif(polym_C[2] / polyf_zero,       digits = 4), "* year_frac +",
+     signif(polym_C[3] / polyf_zero,       digits = 4), "* year_frac^2", "\n\n")
 
+cat("GHI_model (%)   =",
+    signif(100 * ((polym_C[1] / polyf_zero) - 1), digits = 4), "+",
+    signif(100 * polym_C[2] / polyf_zero,         digits = 4), "* year_frac +",
+    signif(100 * polym_C[3] / polyf_zero,         digits = 4), "* year_frac^2", "\n\n")
+
+
+cat("GHI_model (%)   =",
+    round(100 * ((polym_C[1] / polyf_zero) - 1), digits = 4), "+",
+    round(100 * polym_C[2] / polyf_zero,         digits = 4), "* year_frac +",
+    round(100 * polym_C[3] / polyf_zero,         digits = 4), "* year_frac^2", "\n\n")
 
 
 

### 2024-09-06 GHI_enh_08_validation.tex
Commit 2024-09-06 19:12
Commit 2024-09-06 23:11

@@
 
-\caption{ - empty caption - }\label{fig:unnamed-chunk-7}
+\caption{ - empty caption - }\label{fig:unnamed-chunk-7-1}
 \end{figure}
@@
 
+\begin{verbatim}
+Loading required package: ggpp
+\end{verbatim}
+
+\begin{verbatim}
+Registered S3 methods overwritten by 'ggpp':
+  method                  from   
+  heightDetails.titleGrob ggplot2
+  widthDetails.titleGrob  ggplot2
+\end{verbatim}
+
+\begin{verbatim}
+Attaching package: 'ggpp'
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:ggplot2':
+
+    annotate
+\end{verbatim}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-7-2}
+
+}
+
+\caption{ - empty caption - }\label{fig:unnamed-chunk-7-2}
+\end{figure}
+
 \textbf{END}
@@
 \begin{verbatim}
-2024-09-06 10:32:08.3 athan@sagan GHI_enh_08_validation.R 1.913171 mins
+2024-09-06 19:52:22.8 athan@tyler GHI_enh_08_validation.R 21.715553 mins
 \end{verbatim}

### 2024-09-07 GHI_enh_08_validation.tex
Commit 2024-09-07 09:10

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-09-06}
+\date{2024-09-07}
 
@@
 }
+\begin{verbatim}
+Registered S3 methods overwritten by 'ggpp':
+  method                  from   
+  heightDetails.titleGrob ggplot2
+  widthDetails.titleGrob  ggplot2
+\end{verbatim}
+
+\begin{verbatim}
+Attaching package: 'ggpp'
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:ggplot2':
+
+    annotate
+\end{verbatim}
+
 \begin{verbatim}
@@
 
+\begin{verbatim}
+Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
+i Please use the `legend.position.inside` argument of `theme()` instead.
+This warning is displayed once every 8 hours.
+Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
 \begin{figure}[H]
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-6-1}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/P-validation-cloudfree-GHI-1}
 
@@
 
-\caption{ - empty caption - }\label{fig:unnamed-chunk-6}
+\caption{ - empty caption - }\label{fig:P-validation-cloudfree-GHI}
 \end{figure}
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-7-1}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/P-validation-threshold-GHI-1}
 
@@
 
-\caption{ - empty caption - }\label{fig:unnamed-chunk-7-1}
+\caption{ - empty caption - }\label{fig:P-validation-threshold-GHI}
 \end{figure}
@@
 
-\begin{verbatim}
-Loading required package: ggpp
-\end{verbatim}
-
-\begin{verbatim}
-Registered S3 methods overwritten by 'ggpp':
-  method                  from   
-  heightDetails.titleGrob ggplot2
-  widthDetails.titleGrob  ggplot2
-\end{verbatim}
-
-\begin{verbatim}
-Attaching package: 'ggpp'
-\end{verbatim}
-
-\begin{verbatim}
-The following object is masked from 'package:ggplot2':
-
-    annotate
-\end{verbatim}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-7-2}
-
-}
-
-\caption{ - empty caption - }\label{fig:unnamed-chunk-7-2}
-\end{figure}
-
 \textbf{END}
@@
 \begin{verbatim}
-2024-09-06 19:52:22.8 athan@tyler GHI_enh_08_validation.R 21.715553 mins
+2024-09-07 05:12:02.5 athan@tyler GHI_enh_08_validation.R 5.397558 mins
 \end{verbatim}

### 2024-09-07 article/article.Rmd
Commit 2024-09-06 23:11
Commit 2024-09-07 10:14

@@
 `r round(2*yearlyCE[var=="GLB_diff.sum",slope.sd],1)`\,\text{kJ}/\text{year}$.
-The peak of the CE events was observed during May and June.  An analysis of the total
-duration of CE events, showed that with durations longer than 5 minutes are very rare,
-with exceptions lasting over an hour and up to 140 minutes.  Finally, we have
-detected enhancements above the total solar irradiance at the top of the atmosphere
-for the same solar zenith angle of up to
+The peak of the CE events was observed during May and June. CE events with duration
+longer than 5\nobreakspace{}min are very rare, with exceptions lasting over an hour and up to
+140 minutes.  Finally, we have detected enhancements above the total solar irradiance
+at the top of the atmosphere for the same solar zenith angle of up to
 $400\,\text{W}/\text{m}^{2}$, with the $75\,\%$ of the cases below
-$200\,\text{W}/\text{m}^{2}$. Most of these  extreme events occur in
-spring -- early summer, with a secondary peak in autumn.
+$200\,\text{W}/\text{m}^{2}$. Most of these  extreme events occur in spring -- early
+summer, with a secondary peak in autumn.
 
@@
 The highest recorded GHI due to CE was
-$`r round(MC[Typ == "Max Glob", wattGLB],1)`\,\text{W}/\text{m}^2$ on
- `r strftime(MC[Typ == "Max Glob", Date], "%d\\ %B %Y")` at a SZA of
-$`r round(MC[Typ == "Max Glob", SZA],1)`^\circ$ corresponding to OI of
-$`r round(MC[Typ == "Max Glob", GLB_diff],1)`\,\text{W}/\text{m}^2$ or
-$`r round(100*MC[Typ == "Max Glob", GLB_ench],1)`\,\%$ above the threshold.
+$`r round(MC[Typ == "Max Global", wattGLB],1)`\,\text{W}/\text{m}^2$ on
+ `r strftime(MC[Typ == "Max Global", Date], "%d\\ %B %Y")` at a SZA of
+$`r round(MC[Typ == "Max Global", SZA],1)`^\circ$ corresponding to OI of
+$`r round(MC[Typ == "Max Global", GLB_diff],1)`\,\text{W}/\text{m}^2$ or
+$`r round(100*MC[Typ == "Max Global", GLB_ench],1)`\,\%$ above the threshold.
 The strongest CE event of
@@
 cloud-free threshold was observed on 
-`r strftime(MC[Typ == "Max Enha", Date], "%d\\ %B %Y")` at a SZA of
-$`r round(MC[Typ == "Max Enha", SZA],1)`^\circ$ with a GHI value of 
-$`r round(MC[Typ == "Max Enha", wattGLB],1)`\,\text{W}/\text{m}^2$ and a OI of
-$`r round(MC[Typ == "Max Enha", GLB_diff],1)`\,\text{W}/\text{m}^2$.
+`r strftime(MC[Typ == "Max Enh abs", Date], "%d\\ %B %Y")` at a SZA of
+$`r round(MC[Typ == "Max Enh abs", SZA],1)`^\circ$ with a GHI value of 
+$`r round(MC[Typ == "Max Enh abs", wattGLB],1)`\,\text{W}/\text{m}^2$ and a OI of
+$`r round(MC[Typ == "Max Enh abs", GLB_diff],1)`\,\text{W}/\text{m}^2$.
 Both cases are ECE events with
-$`r round(MC[Typ == "Max Glob", wattGLB - ETH],1)`\,\text{W}/\text{m}^2$ and
-$`r round(MC[Typ == "Max Enha", wattGLB - ETH],1)`\,\text{W}/\text{m}^2$ above the
+$`r round(MC[Typ == "Max Global", TSI_OI],1)`\,\text{W}/\text{m}^2$ and
+$`r round(MC[Typ == "Max Enh abs", TSI_OI],1)`\,\text{W}/\text{m}^2$ above the
 TSI at TOA for the same SZA, respectively.

### 2024-09-07 article/article.tex
Commit 2024-09-07 10:14

@@
 
-We studied the enhancement of the global horizontal irradiance induced
-by clouds over Thessaloniki for the period 1994 -- 2023 using data
-recorded every one minute. We identified the cloud enhancement events
-(CE) by creating an appropriate cloud-free irradiance reference with the
-use of a radiative transfer model and aerosol optical depth data from a
-collocated Cimel sun photometer and a Brewer spectrophotometer. We found
-a trend in CE events of \(+111\pm 27\,\text{cases}/\text{year}\), and a
-trend in the CE events irradiation of
-\(+325.2\pm 88\,\text{kJ}/\text{year}\). The peak of the CE events was
-observed during May and June. An analysis of the total duration of CE
-events, showed that durations longer than 5 minutes are very rare, with
+In this study, we investigate the characteristics of global horizontal
+irradiance enhancement events induced by clouds over Thessaloniki for
+the period 1994 -- 2023 using data recorded every one minute. We
+identified the cloud enhancement (CE) events by creating an appropriate
+cloud-free irradiance reference using a radiative transfer model and
+aerosol optical depth data from a collocated Cimel sun photometer and a
+Brewer spectrophotometer. We found a trend in CE events of
+\(+111\pm 27\,\text{cases}/\text{year}\), and a trend in the
+corresponding irradiation of \(+325.2\pm 88\,\text{kJ}/\text{year}\).
+The peak of the CE events was observed during May and June. CE events
+with duration longer than 5\nobreakspace{}min are very rare, with
 exceptions lasting over an hour and up to 140 minutes. Finally, we have
@@
 \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the cases below
-\(200\,\text{W}/\text{m}^{2}\). The most active season of these extreme
-events is spring until early summer and autumn.
+\(200\,\text{W}/\text{m}^{2}\). Most of these extreme events occur in
+spring -- early summer, with a secondary peak in autumn.
 
@@
 have been used in the manual inspection of the CE identification. The
-sky camera operates since 2012 and stores images in 5 min time steps. An
-overview of the data analyzed for the study of the CE and ECE events is
-given in Figure\nobreakspace{}\ref{fig:CLB-daily}, as the daily mean of
-the measured GHI.
+sky camera has been operating since 2012 and stores images in 5 min time
+steps. An overview of the GHI data used in this study is given in
+Figure\nobreakspace{}\ref{fig:CLB-daily}, as the daily means.
 
@@
 
-\caption{Daily mean values of GHI in Thessaloniki for the period 1994 -- 2023.}\label{fig:CLB-daily}
+\caption{Timeseries of daily mean GHI measured at Thessaloniki for the period 1994 -- 2023.}\label{fig:CLB-daily}
 \end{figure}
@@
 
-An example of CE identification for a selected day is given in the
-Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of
-the cloud-free reference irradiance and the CE and ECE identification
-thresholds are shown along with the actual GHI measurements. In
-addition, we provide an example scatter plot between the measured and
-the modeled cloud-free irradiance for one year, where the CE and ECE
-events are clearly grouped above the threshold of irradiance
-(Figure\nobreakspace{}\ref{fig:example-year}).
+An example of the identification of CE events for a selected day is
+given in the Figure\nobreakspace{}\ref{fig:example-day}, where the daily
+course of the cloud-free reference irradiance and the CE and ECE
+identification thresholds are shown along with the actual GHI
+measurements. In addition, we provide an example scatter plot between
+the measured and the modeled cloud-free irradiance for one year, where
+the CE and ECE events are clearly grouped above the threshold of
+irradiance (Figure\nobreakspace{}\ref{fig:example-year}).
 
@@
 \(19.9^\circ\) corresponding to OI of \(369.3\,\text{W}/\text{m}^2\) or
-\(35.3\,\%\) above the threshold. The strongest CE event of \(53\,\%\)
+\(35.3\,\%\) above the threshold. The strongest CE event of \(\,\%\)
 above the cloud-free threshold was observed on 28~October 2016 at a SZA
@@
 
-Next we investigated the distribution of the CE events within the year.
+Next, we investigated the distribution of the CE events within the year.
 Figure\nobreakspace{}\ref{fig:relative-month-occurrences} shows the

### 2024-09-07 article/article.Rmd
Commit 2024-09-07 18:14
Commit 2024-09-07 19:12

@@
 by @Gueymard2017; the most important being the scattering of radiation on the edges
-of cumulus clouds.  It has been also suggested that enhancement of GHI can be
+of cumulus clouds.  It has also been suggested that enhancement of GHI can be
 produced by thin cirrus clouds though refraction and scattering [@Thuillier2013].
@@
 above-mentioned metrics, their climatology and some general characteristics.  To our
-knowledge there are no other studies that provide trends from such a long dataset.
+knowledge, there are no other studies that provide trends from such a long dataset.
 
@@
 in this study is given in
-Figure\nobreakspace{}\ref{fig:CLB-daily}, as the daily means.
+Figure\nobreakspace{}\ref{fig:CLB-daily}, as the daily means.  Daily means were
+calculated only for days with at least $60\,\%$ of data availability; however, all
+available one-minute measurements have been used for the detection of CE events.
 
 ```{r CLB-daily, echo=FALSE, fig.cap="Timeseries of daily mean GHI measured at Thessaloniki for the period 1994 -- 2023."}
-knitr::include_graphics("../images/P_daily_trend-3.png")
+knitr::include_graphics("../images/P_daily_trend-5.png")
 ```
@@
 Although the duration of these bursts can vary from seconds to several minutes, here
-we are constrained by the temporal resolution of our data to identify events with
+we are constrained by the temporal resolution of our data to identify events with a
 duration of at minimum one-minute.
@@
 one-minute GHI from the $\text{GHI}_\text{ref}$ corresponding to cloud-free
-atmosphere.
-<!-- CE identification criterion ($\text{OI}_i =
-\text{GHI}_i - \text{GHI}_\text{CSlim}$), as defined in
-Equation\nobreakspace\ref{eq:CE4}. -->
-First, we used a simple approach for the determination of
+atmosphere.  First, we used a simple approach for the determination of
 $\text{GHI}_\text{ref}$: The Haurwitz's model [@Haurwitz1945], which is a simple
-cloud-free model and was already adjusted and applied to our data [@Natsis2023].
-<!--
-, and the total solar irradiance (TSI) at the top of the atmosphere, adjusted for the
-Sun-Earth distance.
--->
-We created a threshold by using an appropriate relative and/or an additional constant
-offset.  The initial results showed that we can detect a big portion of the actual CE
-events.  However, by inspecting the daily plots of irradiance it became evident that
-changes in atmospheric conditions introduced numerous false positive or false
-negative results. The main reason for these discrepancies is the variability of the
-effects of aerosols and water vapor which were not considered in the simple method.
-To produce a more representative reference we included the effects of these factors
-using a radiative transfer model (RTM).  The applied methodology is discussed in
-section\nobreakspace{}\ref{rtmcs}.
+clear sky radiation model and was already adjusted and applied to our data
+[@Natsis2023].  We created a threshold by using an appropriate relative and/or an
+additional constant offset.  The initial results showed that we can detect a big
+portion of the actual CE events.  However, by inspecting the daily plots of
+irradiance it became evident that changes in atmospheric conditions introduced
+numerous false positive or false negative results. The main reason for these
+discrepancies is the variability of the effects of aerosols and water vapor which
+were not considered in the simple method.  To produce a more representative reference
+we included the effects of these factors using a radiative transfer model (RTM).  The
+applied methodology is discussed in section\nobreakspace{}\ref{rtmcs}.
 
@@
 radiation under cloud free atmospheres are aerosols and water vapor.  At
-Thessaloniki, such measurements are available since 2003 from a Cimel sun photometer
+Thessaloniki, such measurements are available since 2003 from a Cimel sun photometer,
 which is part of the Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998].  From
@@
 
-<!-- Aerosol change -->
 The cloud-free reference values discussed above are based on the climatological AOD
@@
 was attributed to long-term changes in aerosol effects.  Therefore, an adjustment of
-the $\text{GHI}_\text{ref}$ during the period of study was made using simulations
-with the RTM to account for the long-term variations of the AOD. As AERONET data
+the $\text{GHI}_\text{ref}$ during the period of study was made using RTM simulations
+to account for the long-term variations of the AOD.  High quality AOD data with a
+Cimel sun-photometer (part of AERONET) at Thessaloniki start only in 2003, while
+spectral AOD measurements using direct-sun observations with a MKIII Brewer
+spectrophotometer are available for the period 1997 -- 2017. These data are taken
+sporadically during each day and are less dense compared to the AERONET data. By
+comparing monthly AOD data at $340\,\text{nm}$ of the two instruments for the common
+periods of operation we adjusted the Brewer data and filled the missing months of the
+Cimel record data with Brewer data.  Using the monthly time series of AOD at
+$340\,\text{nm}$, as well as monthly climatological values of the Angstrom exponent
+and constant WC of $15.6\,\text{mm}$ derived from the Cimel record, we simulated with
+the RTM the cloud-free GHI at SZA of $55^\circ$ for each month in the period 1997 --
+2023. The SZA of $55^\circ$ was chosen as representative of all days in the year to
+get a rough estimate of the annually averaged change in cloud-free GHI. A
+second-degree polynomial fit was applied to the simulated yearly averaged GHI
+to derive the long-term change in GHI due to aerosols.
+
+As AERONET data
 start only in 2003, we used for the period 1994 -- 2005 estimates of changes in AOD
@@
 during this period.
-
-<!--
-$-3.8\,\%$ per year at AOD on $340\,\text{nm}$, using a Brewer spectrophotometer. For
--->
 
@@
 
-<!-- 1997 0.0839901
-<!-- 2005 0.05496013
-<!-- # Kazadzis2007 - Nine years of UV aerosol optical depth measurements at Thessaloniki, Greece
-<!-- # From Stelios' paper 2007:
-<!-- # AOD @340 from Brewer 086
-<!-- # Period: 1997-2005
-<!-- # The mean AOD for this period was calculated to 0.403 for the Brewer and 0.422 for the CIMEL.
-<!-- # A linear regression on the Brewer deseasonalized data reveals a change of -3.8±0.93% per year.
-<!-- # From the above data AOD @340 changes by 0.0153 per year (or 0.138 for the 9 years).
-<!-- # Using Angstrom a= 1.6 this translates to a change in Angstrom β=0.00272 per year (or β=0.084 in 1997 and β=0.059 in 2005).
+<!--
+GHI_model (%)
+ = -12170 + 12.05 * year_frac + -0.002981 * year_frac^2
 -->
+
+\begin{equation}
+\text{AOD change} [\Delta\%] :  -12170 + 12.05 \cdot y + -0.002981 \cdot y^2  \label{eq:AODchange}
+\end{equation}
+where $y$ the date as a decimal fraction of the year
 

### 2024-09-07 GHI_enh_05_distributions.R

@@ -782,7 +782,8 @@ pander::pander(DT_example)
 library(magick)
 
 
-left  <- image_read("/home/folder/LAP_skycam/skycam/2019/1922019/ 1922019100002.JPEG")
+# left  <- image_read("/home/folder/LAP_skycam/skycam/2019/1922019/ 1922019100002.JPEG")
+left  <- image_read("/home/folder/LAP_skycam/skycam/2019/1922019/ 1922019101501.JPEG")
 right <- image_read("/home/folder/LAP_skycam/skycam/2019/1922019/ 1922019103001.JPEG")
 
 # print(left)
@@ -803,8 +804,8 @@ rr <- image_scale(
 
 A <- image_ggplot(ll) +
   annotate(geom = "text", x = 10, y = 15,  label = "(a)",       hjust = 0, vjust = 0, size =  7, colour = "orange") +
-  annotate(geom = "text", x = 15, y = 585, label = "10:00 UTC", hjust = 0, vjust = 1, size =  7, colour = "orange")
-date_A <- as.POSIXct(strptime(paste(example_day,   "10:00"), "%F %H:%M"))
+  annotate(geom = "text", x = 15, y = 585, label = "10:15 UTC", hjust = 0, vjust = 1, size =  7, colour = "orange")
+date_A <- as.POSIXct(strptime(paste(example_day,   "10:15"), "%F %H:%M"))
 
 B <- image_ggplot(rr) +
   annotate(geom = "text", x = 10, y = 15,  label = "(b)",       hjust = 0, vjust = 0, size =  7, colour = "orange") +
@@ -847,8 +848,8 @@ plot(temp$Date, temp$wattGLB, col = "green",
 abline(v = date_A, col = "grey", lwd = 2, lty = 2)
 abline(v = date_B, col = "grey", lwd = 2, lty = 2)
 
-text(x = date_A, y = 200, "(a)", col = "gray")
-text(x = date_B, y = 200, "(b)", col = "gray")
+text(x = date_A, y = 200, "(a)", pos = 2, offset = 1, col = "gray")
+text(x = date_B, y = 200, "(b)", pos = 4, offset = 1, col = "gray")
 
 
 abline(h = solar_constant, col = "orange2", lty = 1, lwd = 2)

### 2024-09-07 article/article.tex
Commit 2024-09-07 19:12

@@
 been summarized by \citet{Gueymard2017}; the most important being the
-scattering of radiation on the edges of cumulus clouds. It has been also
+scattering of radiation on the edges of cumulus clouds. It has also been
 suggested that enhancement of GHI can be produced by thin cirrus clouds
@@
 metrics, their climatology and some general characteristics. To our
-knowledge there are no other studies that provide trends from such a
+knowledge, there are no other studies that provide trends from such a
 long dataset.
@@
 steps. An overview of the GHI data used in this study is given in
-Figure\nobreakspace{}\ref{fig:CLB-daily}, as the daily means.
+Figure\nobreakspace{}\ref{fig:CLB-daily}, as the daily means. Daily
+means were calculated only for days with at least \(60\,\%\) of data
+availability; however, all available one-minute measurements have been
+used for the detection of CE events.
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/P_daily_trend-3}
+{\centering \includegraphics[width=1\linewidth]{../images/P_daily_trend-5}
 
@@
 bursts can vary from seconds to several minutes, here we are constrained
-by the temporal resolution of our data to identify events with duration
-of at minimum one-minute.
+by the temporal resolution of our data to identify events with a
+duration of at minimum one-minute.
 
@@
 \(\text{GHI}_\text{ref}\): The Haurwitz's model \citep{Haurwitz1945},
-which is a simple cloud-free model and was already adjusted and applied
-to our data \citep{Natsis2023}. We created a threshold by using an
-appropriate relative and/or an additional constant offset. The initial
-results showed that we can detect a big portion of the actual CE events.
-However, by inspecting the daily plots of irradiance it became evident
-that changes in atmospheric conditions introduced numerous false
+which is a simple clear sky radiation model and was already adjusted and
+applied to our data \citep{Natsis2023}. We created a threshold by using
+an appropriate relative and/or an additional constant offset. The
+initial results showed that we can detect a big portion of the actual CE
+events. However, by inspecting the daily plots of irradiance it became
+evident that changes in atmospheric conditions introduced numerous false
 positive or false negative results. The main reason for these
@@
 vapor. At Thessaloniki, such measurements are available since 2003 from
-a Cimel sun photometer which is part of the Aerosol Robotic Network
+a Cimel sun photometer, which is part of the Aerosol Robotic Network
 (AERONET) \citep{Giles2019, Buis1998}. From the observations in the
@@
 an adjustment of the \(\text{GHI}_\text{ref}\) during the period of
-study was made using simulations with the RTM to account for the
-long-term variations of the AOD. As AERONET data start only in 2003, we
-used for the period 1994 -- 2005 estimates of changes in AOD at
-\(340\,\text{nm}\) derived from a collocated Brewer spectrophotometer
-\citep{Kazadzis2007} to calculate the trend in \(\text{GHI}_\text{ref}\)
-due to aerosols during this period.
+study was made using RTM simulations to account for the long-term
+variations of the AOD. High quality AOD data with a Cimel sun-photometer
+(part of AERONET) at Thessaloniki start only in 2003, while spectral AOD
+measurements using direct-sun observations with a MKIII Brewer
+spectrophotometer are available for the period 1997 -- 2017. These data
+are taken sporadically during each day and are less dense compared to
+the AERONET data. By comparing monthly AOD data at \(340\,\text{nm}\) of
+the two instruments for the common periods of operation we adjusted the
+Brewer data and filled the missing months of the Cimel record data with
+Brewer data. Using the monthly time series of AOD at \(340\,\text{nm}\),
+as well as monthly climatological values of the Angstrom exponent and
+constant WC of \(15.6\,\text{mm}\) derived from the Cimel record, we
+simulated with the RTM the cloud-free GHI at SZA of \(55^\circ\) for
+each month in the period 1997 -- 2023. The SZA of \(55^\circ\) was
+chosen as representative of all days in the year to get a rough estimate
+of the annually averaged change in cloud-free GHI. A second-degree
+polynomial fit was applied to the simulated yearly averaged GHI to
+derive the long-term change in GHI due to aerosols.
+
+As AERONET data start only in 2003, we used for the period 1994 -- 2005
+estimates of changes in AOD at \(340\,\text{nm}\) derived from a
+collocated Brewer spectrophotometer \citep{Kazadzis2007} to calculate
+the trend in \(\text{GHI}_\text{ref}\) due to aerosols during this
+period.
 
@@
 \end{figure}
+
+\begin{equation}
+\text{AOD change} [\Delta\%] :  -12170 + 12.05 \cdot y + -0.002981 \cdot y^2  \label{eq:AODchange}
+\end{equation} where \(y\) the date as a decimal fraction of the year
 

### 2024-09-07 article/article.Rmd
Commit 2024-09-07 20:12

@@
 second-degree polynomial fit was applied to the simulated yearly averaged GHI
-to derive the long-term change in GHI due to aerosols.
+to derive the long-term change in GHI due to aerosols (Equation\nobreakspace{}\ref{eq:AODchange}).
 
@@
 1997 and $\beta=0.059$ in 2005).
-<!--
-Simulations with uvspec for the above Ångström
-coefficients, with WC of
-$`r round(BR[year==1997,pw_avg_mm],1)`\,\text{mm}$ and
-$`r round(BR[year==2005,pw_avg_mm],1)`\,\text{mm}$
-for 1997 and 2005 respectively, where for 1997 we used the first available WC data
-(i.e. 2003) as a proxy, also taken from AERONET, and for a SZA of $55^\circ$ reveal a
-change of
-$+0.21\,\%$ per year in $\text{GHI}_\text{ref}$. 
--->
 Simulations with uvspec for the above Ångström coefficients, assuming constant WC of
@@
 \begin{equation}
-\text{AOD change} [\Delta\%] :  -12170 + 12.05 \cdot y + -0.002981 \cdot y^2  \label{eq:AODchange}
+\Delta(\text{AOD}) = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 [\%] \label{eq:AODchange}
 \end{equation}
@@
 
-<!--
-where: $\text{E}$ the measured irradiance, $\text{E}_\text{CSm}$ the selected
-modelled cloud-free irradiance, and $i$ each of the one-minute observation.  This is
-the criterion of our CE identification.
--->
+To assess the validity of the threshold, we tested the correlation of the measured
+GHI with those of the cloud-free irradiance
+(Figure\nobreakspace{}\ref{fig:validation-GHI}), for only cloud-free measurements of
+days with data availability of greater than 80%. Due to the selection of the
+simulations with lower AOD and WC, these values have a positive bias of more than
+$18\,\text{W}/\text{m}^2$. This bias was desired, so that together with the CE
+criterion, could achieve a clear distinction of CE cases.
+
+```{r validation-GHI, echo=FALSE, fig.cap="The reference green line goes through the origin with a slope of one.", fig.pos='H'}
+knitr::include_graphics("../images/P-validation-cloudfree-GHI-1.png")
+```
 
@@
 Red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles.Black curve represents the TOA TSI on horizontal plane.", fig.pos='H'}
-knitr::include_graphics("../images/example-days-18.png")
+knitr::include_graphics("../images/P-example-day-2.png")
 ```
@@
 Figure\nobreakspace{}\ref{fig:P-energy} shows the time series of the yearly number of
-CE cases (each with duration of one minute), the yearly mean OI and the yearly
-excess irradiation for the period 1994 -- 2023, together with corresponding linear
-trends. All three quantities show increasing trends, most pronounced for the
+CE cases (each with duration of one minute), the yearly mean OI and the yearly excess
+irradiation for the period 1994 -- 2023, together with corresponding linear trends.
+To account for missing data all three quantities have been divided with the fraction
+of the valid GHI observations in each month.
+All three quantities show increasing trends, most pronounced for the
 frequency of occurrence 

### 2024-09-07 article/article.tex
Commit 2024-09-07 20:12

@@
 polynomial fit was applied to the simulated yearly averaged GHI to
-derive the long-term change in GHI due to aerosols.
+derive the long-term change in GHI due to aerosols
+(Equation\nobreakspace{}\ref{eq:AODchange}).
 
@@
 \begin{equation}
-\text{AOD change} [\Delta\%] :  -12170 + 12.05 \cdot y + -0.002981 \cdot y^2  \label{eq:AODchange}
+\Delta(\text{AOD}) = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 [\%] \label{eq:AODchange}
 \end{equation} where \(y\) the date as a decimal fraction of the year
@@
 \end{equation}
+
+To assess the validity of the threshold, we tested the correlation of
+the measured GHI with those of the cloud-free irradiance (Figure), for
+only cloud-free measurements of days with data availability of greater
+than 80\%. Due to the selection of the simulations with lower AOD and
+WC, these values have a positive bias of more than (Correlation). This
+was desired so that together with the PSE criterion, we could achieve a
+clear distinction of PSE cases.
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/example-days-18}
+{\centering \includegraphics[width=1\linewidth]{../images/P-example-day-2}
 
@@
 mean OI and the yearly excess irradiation for the period 1994 -- 2023,
-together with corresponding linear trends. All three quantities show
-increasing trends, most pronounced for the frequency of occurrence
+together with corresponding linear trends. To account for missing data
+all three quantities have been divided with the fraction of the valid
+GHI observations in each month. All three quantities show increasing
+trends, most pronounced for the frequency of occurrence
 (\(+111\pm 27\,\text{cases}/\text{year}\)) and the excess irradiation

### 2024-09-07 GHI_enh_05_distributions.R
Commit 2024-09-07 20:12

@@ -848,8 +848,8 @@ plot(temp$Date, temp$wattGLB, col = "green",
 abline(v = date_A, col = "grey", lwd = 2, lty = 2)
 abline(v = date_B, col = "grey", lwd = 2, lty = 2)
 
-text(x = date_A, y = 200, "(a)", pos = 2, offset = 1, col = "gray")
-text(x = date_B, y = 200, "(b)", pos = 4, offset = 1, col = "gray")
+text(x = date_A, y = 200, "(a)", pos = 2, offset = 0.4, col = "gray")
+text(x = date_B, y = 200, "(b)", pos = 4, offset = 0.4, col = "gray")
 
 
 abline(h = solar_constant, col = "orange2", lty = 1, lwd = 2)

### 2024-09-07 article/article.Rmd
Commit 2024-09-07 21:12

@@
 
+<!--
 ```{r CS-change, echo=FALSE, fig.cap="Simulated long-term change in cloud-free irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1994 -- 2023."}
@@
 \begin{equation}
-\Delta(\text{AOD}) = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 [\%] \label{eq:AODchange}
+\Delta(\text{AOD}) [\%] = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 \label{eq:AODchange}
 \end{equation}
-where $y$ the date as a decimal fraction of the year
+where $y$ the date as a decimal fraction of the year. For the period of the study the
+relative change of AOD ranges between $-1.88$ and $-0.23\,\%$.
 
@@
 Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of the cloud-free
-reference irradiance and the CE and ECE identification thresholds are shown along
-with the actual GHI measurements.  In addition, we provide an example scatter plot
-between the measured and the modeled cloud-free irradiance for one year, where the CE
-and ECE events are clearly grouped above the threshold of irradiance
-(Figure\nobreakspace{}\ref{fig:example-year}).
+reference irradiance and the CE and ECE thresholds are shown along with the actual
+GHI measurements.  The GHI data in the periods 7:30 -- 8:30 and after 14:00 are very
+close to the modeled cloud-free GHI (light blue line) thus were identified as
+cloud-free instances. There is some ambiguity for the data points laying between the
+CE threshold and the cloud-free irradiance, which are not identified as CE events.
+These data points correspond to cases either with AOD below the one assumed in the
+model, or with very small OI.
+
+In addition, we provide in Figure\nobreakspace{}\ref{fig:example-year} an example
+scatter plot between the measured GHI and the modeled cloud-free irradiance for one
+year (2005), where the CE and ECE events are clearly grouped above the cloud-free
+irradiance (approximated with the green line).
 

### 2024-09-07 article/article.tex
Commit 2024-09-07 21:12

@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../images/P-CS-change-1}
-
-}
-
-\caption{Simulated long-term change in cloud-free irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1994 -- 2023.}\label{fig:CS-change}
-\end{figure}
-
 \begin{equation}
-\Delta(\text{AOD}) = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 [\%] \label{eq:AODchange}
-\end{equation} where \(y\) the date as a decimal fraction of the year
+\Delta(\text{AOD}) [\%] = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 \label{eq:AODchange}
+\end{equation} where \(y\) the date as a decimal fraction of the year.
+For the period of the study the relative change of AOD ranges between
+\(-1.88\) and \(-0.23\,\%\).
 
@@
 To assess the validity of the threshold, we tested the correlation of
-the measured GHI with those of the cloud-free irradiance (Figure), for
-only cloud-free measurements of days with data availability of greater
-than 80\%. Due to the selection of the simulations with lower AOD and
-WC, these values have a positive bias of more than (Correlation). This
-was desired so that together with the PSE criterion, we could achieve a
-clear distinction of PSE cases.
+the measured GHI with those of the cloud-free irradiance
+(Figure\nobreakspace{}\ref{fig:validation-GHI}), for only cloud-free
+measurements of days with data availability of greater than 80\%. Due to
+the selection of the simulations with lower AOD and WC, these values
+have a positive bias of more than \(18\,\text{W}/\text{m}^2\). This bias
+was desired, so that together with the CE criterion, could achieve a
+clear distinction of CE cases.
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{../images/P-validation-cloudfree-GHI-1}
+
+}
+
+\caption{The reference green line goes through the origin with a slope of one.}\label{fig:validation-GHI}
+\end{figure}
 
@@
 course of the cloud-free reference irradiance and the CE and ECE
-identification thresholds are shown along with the actual GHI
-measurements. In addition, we provide an example scatter plot between
-the measured and the modeled cloud-free irradiance for one year, where
-the CE and ECE events are clearly grouped above the threshold of
-irradiance (Figure\nobreakspace{}\ref{fig:example-year}).
+thresholds are shown along with the actual GHI measurements. The GHI
+data in the periods 7:30 -- 8:30 and after 14:00 are very close to the
+modeled cloud-free GHI (light blue line) thus were identified as
+cloud-free instances. There is some ambiguity for the data points laying
+between the CE threshold and the cloud-free irradiance, which are not
+identified as CE events. These data points correspond to cases either
+with AOD below the one assumed in the model, or with very small OI.
+
+In addition, we provide in Figure\nobreakspace{}\ref{fig:example-year}
+an example scatter plot between the measured GHI and the modeled
+cloud-free irradiance for one year (2005), where the CE and ECE events
+are clearly grouped above the cloud-free irradiance (approximated with
+the green line). (Figure\nobreakspace{}\ref{fig:example-year}).
 

### 2024-09-08 article/article.Rmd
Commit 2024-09-08 08:14

@@
 irradiation for the period 1994 -- 2023, together with corresponding linear trends.
-To account for missing data all three quantities have been divided with the fraction
-of the valid GHI observations in each month.
-All three quantities show increasing trends, most pronounced for the
-frequency of occurrence 
+To account for missing data, all three quantities have been divided with the fraction
+of the valid GHI observations in each month.  Statistically significant (at the
+$95\,\%$ confidence level) increasing trends appear for the yearly number of CE
+events
 ($`r plus_sign(round(yearlyCE[var == "GLB_diff.N", slope], 0))`\pm `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 0)`\,\text{cases}/\text{year}$)
@@
 ($`r plus_sign(round(yearlyCE[var == "GLB_diff.sum", slope], 1))` \pm `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$),
-which are also statistically significant.
-In contrast the trend of the yearly mean OI is negligible 
+while the the trend in the yearly mean OI is negligible
 ($`r plus_sign(round(yearlyCE[var == "GLB_diff.mean", slope], 2))`\pm `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\text{W}/\text{m}^2/\text{year}$)

### 2024-09-08 article/article.tex
Commit 2024-09-08 08:14

@@
 are clearly grouped above the cloud-free irradiance (approximated with
-the green line). (Figure\nobreakspace{}\ref{fig:example-year}).
+the green line).
 
@@
 mean OI and the yearly excess irradiation for the period 1994 -- 2023,
-together with corresponding linear trends. To account for missing data
+together with corresponding linear trends. To account for missing data,
 all three quantities have been divided with the fraction of the valid
-GHI observations in each month. All three quantities show increasing
-trends, most pronounced for the frequency of occurrence
-(\(+111\pm 27\,\text{cases}/\text{year}\)) and the excess irradiation
-(\(+325.2 \pm 88\,\text{kJ}/\text{year}\)), which are also statistically
-significant. In contrast the trend of the yearly mean OI is negligible
+GHI observations in each month. Statistically significant (at the
+\(95\,\%\) confidence level) increasing trends appear for the yearly
+number of CE events (\(+111\pm 27\,\text{cases}/\text{year}\)) and the
+excess irradiation (\(+325.2 \pm 88\,\text{kJ}/\text{year}\)), while the
+the trend in the yearly mean OI is negligible
 (\(+0.14\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of no

### 2024-09-08 article/article.Rmd
Commit 2024-09-08 10:14

@@
 Red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles.Black curve represents the TOA TSI on horizontal plane.", fig.pos='H'}
-knitr::include_graphics("../images/P-example-day-2.png")
+knitr::include_graphics("../images/P-example-day-5.png")
 ```

### 2024-09-08 article/article.Rmd
Commit 2024-09-08 11:09

@@
 The peak of the CE events was observed during May and June. CE events with duration
-longer than 5\nobreakspace{}min are very rare, with exceptions lasting over an hour and up to
-140 minutes.  Finally, we have detected enhancements above the total solar irradiance
-at the top of the atmosphere for the same solar zenith angle of up to
+longer than 10\nobreakspace{}min are very rare
+($<`r ceiling(100*ST_G0[,sum(GLB_ench.N>10)/.N])`\,\%$), with exceptions lasting
+over an hour and up to 140 minutes.  Finally, we have detected enhancements above the
+total solar irradiance at the top of the atmosphere for the same solar zenith angle
+of up to
 $400\,\text{W}/\text{m}^{2}$, with the $75\,\%$ of the cases below

### 2024-09-08 article/article.tex
Commit 2024-09-08 10:14
Commit 2024-09-08 11:09

@@
 The peak of the CE events was observed during May and June. CE events
-with duration longer than 5\nobreakspace{}min are very rare, with
-exceptions lasting over an hour and up to 140 minutes. Finally, we have
-detected enhancements above the total solar irradiance at the top of the
-atmosphere for the same solar zenith angle of up to
-\(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the cases below
-\(200\,\text{W}/\text{m}^{2}\). Most of these extreme events occur in
-spring -- early summer, with a secondary peak in autumn.
+with duration longer than 10\nobreakspace{}min are very rare
+(\(<8\,\%\)), with exceptions lasting over an hour and up to 140
+minutes. Finally, we have detected enhancements above the total solar
+irradiance at the top of the atmosphere for the same solar zenith angle
+of up to \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the
+cases below \(200\,\text{W}/\text{m}^{2}\). Most of these extreme events
+occur in spring -- early summer, with a secondary peak in autumn.
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/P-example-day-2}
+{\centering \includegraphics[width=1\linewidth]{../images/P-example-day-5}
 

### 2024-09-08 article/article.tex
Commit 2024-09-08 12:14

@@
 irradiance at the top of the atmosphere for the same solar zenith angle
-of up to \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the
-cases below \(200\,\text{W}/\text{m}^{2}\). Most of these extreme events
+of up to \(209\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the
+cases below \(40\,\text{W}/\text{m}^{2}\). Most of these extreme events
 occur in spring -- early summer, with a secondary peak in autumn.

### 2024-09-08 article/article.Rmd
Commit 2024-09-08 12:14

@@
 of up to
-$400\,\text{W}/\text{m}^{2}$, with the $75\,\%$ of the cases below
-$200\,\text{W}/\text{m}^{2}$. Most of these  extreme events occur in spring -- early
+$209\,\text{W}/\text{m}^{2}$, with the $75\,\%$ of the cases below
+$40\,\text{W}/\text{m}^{2}$. Most of these extreme events occur in spring -- early
 summer, with a secondary peak in autumn.
@@
 
-Methods of identification of CE events usually include the use of simulated cloud-free irradiance as baseline, combined with an appropriate threshold or some
+Methods of identification of CE events usually include the use of simulated
+cloud-free irradiance as baseline, combined with an appropriate threshold or some
 other statistical characteristics, and in some cases, with visual inspection of sky
@@
 portion of the actual CE events.  However, by inspecting the daily plots of
-irradiance it became evident that changes in atmospheric conditions introduced
+irradiance, it became evident that changes in atmospheric conditions introduced
 numerous false positive or false negative results. The main reason for these
@@
 of the warm and cold seasons.
+
+The variable parameters of LUT consists of the month along with the relevant seasonal atmospheric profile,
+the climatological values of the alpha, beta parameters of the Ångström
+equation for 500nm derived from the 340nm, the WC and the SZA of the simulation.
 

### 2024-09-08 article/article.Rmd
Commit 2024-09-08 13:09

@@
 
-The variable parameters of LUT consists of the month along with the relevant seasonal atmospheric profile,
-the climatological values of the alpha, beta parameters of the Ångström
-equation for 500nm derived from the 340nm, the WC and the SZA of the simulation.
-
 Main factors responsible for the attenuation of the broadband downward solar
@@
 <!-- Lookup table -->
-<!-- 
-To create a look-up table, that aligns with our dataset, we applied some adjustments.
-To account for the Sun's variability, in our one-minute GHI measurements, we adapted
-each modeled value by scaling the model's input spectrum integral, to the
-corresponding TSI, provided by NOAA [@Coddington2005].  Also,
-we account for the effect of the Earth -- Sun distance on the irradiance, by using
-the distance calculated by the Astropy [@AstropyCollaboration2022] software library.
-As needed, we interpolate the resulting irradiances to the SZA of our
-measurements.  For each period of the year, we used the appropriate atmospheric
-profile (afglms or afglmw).  Finally, we calculated the cloud-free irradiance value at
-the horizontal plane.  Thus, we were able to emulate different atmospheric condition
-and levels of atmospheric clearness for the climatological conditions of the site.
-With this method, the modeled cloud-free irradiances can be directly compared to each
-measured one-minute value of GHI, for different conditions of atmospheric clearness.
--->
+**to edit**
+
+The variable parameters of LUT consists of the month along with the relevant seasonal
+atmospheric profile, the climatological values of the alpha, beta parameters of the
+Ångström equation for 500nm derived from the 340nm, the WC, with the perturbation as
+described above, and the SZA of the simulation.
+
+For the application of  the LUT, to account for the Sun's variability, in our
+one-minute GHI measurements, we adapted each modeled value by scaling the model's
+input spectrum integral, to the corresponding TSI, provided by NOAA
+[@Coddington2005].  Also, we account for the effect of the Earth -- Sun distance on
+the irradiance, by using the distance calculated by the Astropy
+[@AstropyCollaboration2022] software library.  As needed, we interpolate the
+resulting irradiances to the SZA of our measurements.  For each period of the year,
+we used the appropriate atmospheric profile (afglms or afglmw).  Finally, we
+calculated the cloud-free irradiance value at the horizontal plane.  With this
+method, the modeled cloud-free irradiances schemes can be directly compared to each
+measured one-minute value of GHI.
 

### 2024-09-08 article/article.tex
Commit 2024-09-08 13:09

@@
 initial results showed that we can detect a big portion of the actual CE
-events. However, by inspecting the daily plots of irradiance it became
+events. However, by inspecting the daily plots of irradiance, it became
 evident that changes in atmospheric conditions introduced numerous false
@@
 \citep{AstropyCollaboration2022}.
+
+\textbf{to edit}
+
+The variable parameters of LUT consists of the month along with the
+relevant seasonal atmospheric profile, the climatological values of the
+alpha, beta parameters of the Ångström equation for 500nm derived from
+the 340nm, the WC, with the perturbation as described above, and the SZA
+of the simulation.
+
+For the application of the LUT, to account for the Sun's variability, in
+our one-minute GHI measurements, we adapted each modeled value by
+scaling the model's input spectrum integral, to the corresponding TSI,
+provided by NOAA \citep{Coddington2005}. Also, we account for the effect
+of the Earth -- Sun distance on the irradiance, by using the distance
+calculated by the Astropy \citep{AstropyCollaboration2022} software
+library. As needed, we interpolate the resulting irradiances to the SZA
+of our measurements. For each period of the year, we used the
+appropriate atmospheric profile (afglms or afglmw). Finally, we
+calculated the cloud-free irradiance value at the horizontal plane. With
+this method, the modeled cloud-free irradiances schemes can be directly
+compared to each measured one-minute value of GHI.
 

### 2024-09-08 article/article.Rmd
Commit 2024-09-08 19:10

@@
 "pseudospherical" geometry and the "LOWTRAN" gas parameterization.  The model was run
-for a range of variables to create a look-up table (LUT) for the estimation of the
-cloud-free reference irradiance for each individual observation of our dataset. In
-this context, the model was run for SZAs in the range $10$ -- $90^\circ$ with a step
-of $0.2^\circ$ and for the atmospheric profiles of the Air Force Geophysics
-Laboratory [@Anderson1986] midlatitude summer and midlatitude winter, representative
-of the warm and cold seasons.
+for climatological values of the Angstrom coefficients, water column (WC), SZA and
+the appropriate seasonal atmospheric profile to create a look-up table (LUT) for the
+estimation of the cloud-free reference irradiance for each individual observation of
+our dataset. In this context, the model was run for SZAs in the range $10$ --
+$90^\circ$ with a step of $0.2^\circ$ and for the atmospheric profiles of the Air
+Force Geophysics Laboratory [@Anderson1986] midlatitude summer and midlatitude
+winter, representative of the warm and cold seasons.
 
@@
 <!-- Lookup table -->
-**to edit**
-
+<!-- 
 The variable parameters of LUT consists of the month along with the relevant seasonal
@@
 measured one-minute value of GHI.
+-->
 
@@
 Cimel record data with Brewer data.  Using the monthly time series of AOD at
-$340\,\text{nm}$, as well as monthly climatological values of the Angstrom exponent
+$340\,\text{nm}$, as well as monthly climatological values of the Ångström exponent
 and constant WC of $15.6\,\text{mm}$ derived from the Cimel record, we simulated with
@@
 second-degree polynomial fit was applied to the simulated yearly averaged GHI
-to derive the long-term change in GHI due to aerosols (Equation\nobreakspace{}\ref{eq:AODchange}).
+to derive the long-term change in GHI due to aerosols:
+\begin{equation}
+\Delta(\text{AOD}) [\%] = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 \label{eq:AODchange}
+\end{equation}
+where $y$ is the date as a decimal fraction of the year. For the period of the study
+the relative change of AOD ranges between $-1.88$ and $-0.23\,\%$.  Finally, we
+applied these long-term changes of Equation\nobreakspace{}\ref{eq:AODchange} to the
+climatological $\text{GHI}_\text{ref}$, to create a more realistic representation of
+the cloud-free irradiance for the entire period of study. For the period 1994 -- 1996
+where no AOD data are available, we assumed that the changes in GHI follow the same
+polynomial fit.
 
+<!--
 As AERONET data
@@
 
-<!--
 To create a unified trend for the long-term change of the cloud-free irradiance, we
@@
 
+<!--
 According to @Kazadzis2007, in the period 1997 -- 2005 the mean AOD at $340\,\text{nm}$
@@
 application.
+-->
 
@@
 -->
-
-\begin{equation}
-\Delta(\text{AOD}) [\%] = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 \label{eq:AODchange}
-\end{equation}
-where $y$ the date as a decimal fraction of the year. For the period of the study the
-relative change of AOD ranges between $-1.88$ and $-0.23\,\%$.
 

### 2024-09-08 article/article.tex
Commit 2024-09-08 19:10

--- 2024-09-08 article/article.tex
@@
 radiative transfer solver ``disort'' in ``pseudospherical'' geometry and
-the ``LOWTRAN'' gas parameterization. The model was run for a range of
-variables to create a look-up table (LUT) for the estimation of the
-cloud-free reference irradiance for each individual observation of our
-dataset. In this context, the model was run for SZAs in the range \(10\)
--- \(90^\circ\) with a step of \(0.2^\circ\) and for the atmospheric
-profiles of the Air Force Geophysics Laboratory \citep{Anderson1986}
-midlatitude summer and midlatitude winter, representative of the warm
-and cold seasons.
+the ``LOWTRAN'' gas parameterization. The model was run for
+climatological values of the Angstrom coefficients, water column (WC),
+SZA and the appropriate seasonal atmospheric profile to create a look-up
+table (LUT) for the estimation of the cloud-free reference irradiance
+for each individual observation of our dataset. In this context, the
+model was run for SZAs in the range \(10\) -- \(90^\circ\) with a step
+of \(0.2^\circ\) and for the atmospheric profiles of the Air Force
+Geophysics Laboratory \citep{Anderson1986} midlatitude summer and
+midlatitude winter, representative of the warm and cold seasons.
 
@@
 Brewer data. Using the monthly time series of AOD at \(340\,\text{nm}\),
-as well as monthly climatological values of the Angstrom exponent and
+as well as monthly climatological values of the Ångström exponent and
 constant WC of \(15.6\,\text{mm}\) derived from the Cimel record, we
@@
 polynomial fit was applied to the simulated yearly averaged GHI to
-derive the long-term change in GHI due to aerosols
-(Equation\nobreakspace{}\ref{eq:AODchange}).
-
-As AERONET data start only in 2003, we used for the period 1994 -- 2005
-estimates of changes in AOD at \(340\,\text{nm}\) derived from a
-collocated Brewer spectrophotometer \citep{Kazadzis2007} to calculate
-the trend in \(\text{GHI}_\text{ref}\) due to aerosols during this
-period.
-
-According to \citet{Kazadzis2007}, in the period 1997 -- 2005 the mean
-AOD at \(340\,\text{nm}\) is \(0.4\) with a change of
-\(-3.8\pm0.93\,\%\) per year, corresponding to a change of \(0.0153\)
-per year. Using an Ångström coefficient \(\alpha = 1.6\), this
-translates to a change in the Ångström coefficient \(\beta\) of
-\(0.00272\) per year (or \(\beta=0.084\) in 1997 and \(\beta=0.059\) in
-2005). Simulations with uvspec for the above Ångström coefficients,
-assuming constant WC of \(15.6\,\text{mm}\) taken from the Cimel, and
-for a SZA of \(55^\circ\) reveal a change of \(+0.21\,\%\) per year in
-\(\text{GHI}_\text{ref}\). The SZA of \(55^\circ\) was chosen as
-representative of all days in the year in order to get a rough estimate
-of the annually averaged change in cloud-free irradiance. For the period
-2005 -- 2023 we used the mean monthly values of AOD and WC from AERONET
-in a similar simulation scheme to calculate the monthly mean cloud-free
-irradiance, and finally the change of \(+0.14\,\%\) per year. We applied
-these two long-term changes (see
-Figure\nobreakspace{}\ref{fig:CS-change}) to the climatological
-\(\text{GHI}_\text{ref}\), to create a more realistic representation of
-the cloud-free irradiance for the whole period of study. The rate of
-changes in the two subperiods are different, but reasonable, since the
-effect of the enforced air pollution abatement measures in the area in
-the 1990s had greater effects in the first years of application.
-
-\begin{equation}
+derive the long-term change in GHI due to aerosols: \begin{equation}
 \Delta(\text{AOD}) [\%] = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 \label{eq:AODchange}
-\end{equation} where \(y\) the date as a decimal fraction of the year.
-For the period of the study the relative change of AOD ranges between
-\(-1.88\) and \(-0.23\,\%\).
+\end{equation} where \(y\) is the date as a decimal fraction of the
+year. For the period of the study the relative change of AOD ranges
+between \(-1.88\) and \(-0.23\,\%\). Finally, we applied these long-term
+changes of Equation\nobreakspace{}\ref{eq:AODchange} to the
+climatological \(\text{GHI}_\text{ref}\), to create a more realistic
+representation of the cloud-free irradiance for the entire period of
+study. For the period 1994 -- 1996 where no AOD data are available, we
+assumed that the changes in GHI follow the same polynomial fit.
 

### 2024-09-08 article/article.tex
Commit 2024-09-08 20:14

@@
 than average load of aerosols and humidity, which are the main factors
-that attenuate the GHI, excluding clouds. With this approach the
+that attenuate the GHI, excluding clouds. With this approach, the
 simulated \(\text{GHI}_\text{ref}\) should be generally greater than the
-measured GHI when aerosols are more abundant. To compensate for this, we
-defined the following threshold \(E\) to compare the measured
-\(\text{GHI}\): \begin{equation}
-\text{CE} : E > 25 + 1 \cdot \text{GHI}_\text{ref} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
-\end{equation}
-
-To assess the validity of the threshold, we tested the correlation of
-the measured GHI with those of the cloud-free irradiance
-(Figure\nobreakspace{}\ref{fig:validation-GHI}), for only cloud-free
-measurements of days with data availability of greater than 80\%. Due to
-the selection of the simulations with lower AOD and WC, these values
-have a positive bias of more than \(18\,\text{W}/\text{m}^2\). This bias
-was desired, so that together with the CE criterion, could achieve a
-clear distinction of CE cases.
+measured GHI when aerosols are more abundant. The correlation of the
+\(\text{GHI}_\text{ref}\) with the GHI was tested for a subset of
+cloud-free days with more than \(80\,\%\) data availability
+(Figure\nobreakspace{}\ref{fig:validation-GHI}) and found to have a
+positive bias of more than \(18\,\text{W}/\text{m}^2\) across all levels
+of radiation. To achieve a robust and clear distinction of CE cases, we
+set the criteria of CE detection \(25\,\text{W}/\text{m}^2\) above the
+\(\text{GHI}_\text{ref}\).
 
@@
 
-\caption{The reference green line goes through the origin with a slope of one.}\label{fig:validation-GHI}
+\caption{The corelation GHI with $\text{GHI}_\text{ref}$, for cloud-free data of days with data availability more than $80\,\%$.}\label{fig:validation-GHI}
 \end{figure}
 
-This is the criterion of our CE identification. The constant terms were
-determined through the implementation of an empirical method with manual
-inspection of the CE identification results on selected days of the
-whole dataset. We tested seven sets of days with different
+To further ensure the effectiveness of this CE criterion, we implement a
+manual inspection of the CE identification results on selected days of
+the whole dataset. We tested seven sets of days with different
 characteristics relevant to the efficiency of the identification
@@
 following characteristics: (a) the strongest OI CE events, (b) the
-largest daily total OI, (c) absence of clouds (by implementing a
-cloud-free identification algorithm as discussed in \citet{Natsis2023}),
-(d) absence of clouds and absence of CE events, (e) with at least
-\(60\,\%\) of the day length without clouds and presence of CE events,
-(h) randomly selected days, and (i) manually selected days. For the
-latter case and where needed, we also used images from the sky-camera to
-further aid the decision of the manual inspection.
+largest daily total OI, (c) absence of clouds (by implementing a cloud
+identification algorithm as discussed in \citet{Natsis2023}), (d)
+absence of clouds and absence of CE events, (e) with at least \(60\,\%\)
+of the day length without clouds and presence of CE events, (h) randomly
+selected days, and (i) manually selected days. For the latter case and
+where needed, we also used images from the sky-camera to further aid the
+decision of the manual inspection.
 
@@
 \end{equation} where: \(\text{SZA}\) the solar zenith angle,
-\(E_{\odot}\) is the solar constant at the mean Sun - Earth distance
-(\(1361\,\text{W}/\text{m}^2\)), \(r\) is the actual Sun - Earth
+\(E_{\odot}\) is the solar constant at the mean Sun -- Earth distance
+(\(1367\,\text{W}/\text{m}^2\)), \(r\) is the actual Sun - Earth
 distance and \(r_\text{m}\) is the mean Sun -- Earth distance of
@@
 are clearly grouped above the cloud-free irradiance (approximated with
-the green line).
+the green line). The grey colored data points above this line correspond
+to the ambiguous data points discussed above. Finally, the black belt
+just below the green line is formed from data measured mainly under
+cloud-free conditions,conditions with the spread likely caused by the
+short-term variability of AOD. A small fraction of these data
+corresponds also to cases with thin cirrus clouds causing weak
+attenuation of GHI, often indistinguishable from the attenuation by
+aerosols.
 
@@
 \caption{Example of CE identification in Thessaloniki for 2019-07-11.
-The green line with blue symbols depicts the measured GHI in one minute steps.
-Red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles.Black curve represents the TOA TSI on horizontal plane.}\label{fig:example-day}
+The green line with blue symbols depicts the measured GHI in one-minute steps.
+The red line shows the modelled threshold for the detection of CE events, which are denoted with red circles.
+The black line represents the TOA TSI on a horizontal plane, equivalent to the threshold for the identification of ECE events, shown with red circles.
+The purple line is the modeled cloud-free irradiance.
+The dark yellow line is the solar constant of $1367\,\text{W}/\text{m}^{2}$}\label{fig:example-day}
 \end{figure}
@@
 \caption{Example scatter plot of the measured GHI and the reference cloud-free irradiance in Thessaloniki for the year 2005.
-The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.
+The over-irradiance for CE and ECE events is colour coded, while the remaining data points are shown in black.
 The reference green line goes through the origin with a slope of one.}\label{fig:example-year}
@@
 entire dataset (\(6\) million of one-minute GHI measurements),
-\(2.32\,\%\) were identified as CE events and \(0.04\,\%\) as ECE
+\(2.32\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
 events. The highest recorded GHI due to CE was
@@
 a OI of \(298.4\,\text{W}/\text{m}^2\). Both cases are ECE events with
-\(136.8\,\text{W}/\text{m}^2\) and \(164.5\,\text{W}/\text{m}^2\) above
+\(131.2\,\text{W}/\text{m}^2\) and \(161.5\,\text{W}/\text{m}^2\) above
 the TSI at TOA for the same SZA, respectively. In the following sections

### 2024-09-08 article/article.Rmd
Commit 2024-09-08 20:14

@@
 load of aerosols and humidity, which are the main factors that attenuate the GHI,
-excluding clouds.  With this approach the simulated $\text{GHI}_\text{ref}$ should be
-generally greater than the measured GHI when aerosols are more abundant.  To
+excluding clouds.  With this approach, the simulated $\text{GHI}_\text{ref}$ should be
+generally greater than the measured GHI when aerosols are more abundant. The
+correlation of the $\text{GHI}_\text{ref}$ with the GHI was tested for a subset of
+cloud-free days with more than $80\,\%$ data availability
+(Figure\nobreakspace{}\ref{fig:validation-GHI}) and found to have a positive bias of
+more than $18\,\text{W}/\text{m}^2$ across all levels of radiation.  To achieve a
+robust and clear distinction of CE cases, we set the criteria of CE detection
+$`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$ above the $\text{GHI}_\text{ref}$.
+
+```{r validation-GHI, echo=FALSE, fig.cap="The corelation GHI with $\\text{GHI}_\\text{ref}$, for cloud-free data of days with data availability more than $80\\,\\%$.", fig.pos='H'}
+knitr::include_graphics("../images/P-validation-cloudfree-GHI-1.png")
+```
+
+<!--
+To
 compensate for this, we defined the following threshold $E$ to compare the
@@
 \end{equation}
+-->
+<!--
+This is the criterion of our CE identification.  The constant terms were determined
+through the implementation of an empirical method
+-->
 
-To assess the validity of the threshold, we tested the correlation of the measured
-GHI with those of the cloud-free irradiance
-(Figure\nobreakspace{}\ref{fig:validation-GHI}), for only cloud-free measurements of
-days with data availability of greater than 80%. Due to the selection of the
-simulations with lower AOD and WC, these values have a positive bias of more than
-$18\,\text{W}/\text{m}^2$. This bias was desired, so that together with the CE
-criterion, could achieve a clear distinction of CE cases.
-
-```{r validation-GHI, echo=FALSE, fig.cap="The reference green line goes through the origin with a slope of one.", fig.pos='H'}
-knitr::include_graphics("../images/P-validation-cloudfree-GHI-1.png")
-```
-
-This is the criterion of our CE identification.  The constant terms were determined
-through the implementation of an empirical method with manual inspection of the CE
-identification results on selected days of the whole dataset.  We tested seven sets
-of days with different characteristics relevant to the efficiency of the
-identification threshold.  These sets were random groups of about 20 -- 30 days with
-the following characteristics:
+To further ensure the effectiveness of this CE criterion, we implement a manual
+inspection of the CE identification results on selected days of the whole dataset.
+We tested seven sets of days with different characteristics relevant to the
+efficiency of the identification threshold.  These sets were random groups of about
+20 -- 30 days with the following characteristics:
 (a) the strongest OI CE events,
 (b) the largest daily total OI,
-(c) absence of clouds (by implementing a cloud-free identification algorithm as discussed in @Natsis2023),
+(c) absence of clouds (by implementing a cloud identification algorithm as discussed in @Natsis2023),
 (d) absence of clouds and absence of CE events,
@@
 <!-- reasoning for criteria -->
-<!-- We have to note, that the differentiation of the threshold factor was needed, because
-<!-- of the high irradiance values we observed, early in the morning and late in the
-<!-- afternoon. 
 <!-- We have confirmed, by inspecting images from the sky cam, that we have
@@
 where: $\text{SZA}$ the solar zenith angle, $E_{\odot}$ is the solar constant at the
-mean Sun - Earth distance ($`r round(solar_constant)`\,\text{W}/\text{m}^2$), $r$ is
+mean Sun -- Earth distance ($`r round(solar_constant)`\,\text{W}/\text{m}^2$), $r$ is
 the actual Sun - Earth distance and $r_\text{m}$ is the mean Sun -- Earth distance of
@@
 year (2005), where the CE and ECE events are clearly grouped above the cloud-free
-irradiance (approximated with the green line).
+irradiance (approximated with the green line).  The grey colored data points above
+this line correspond to the ambiguous data points discussed above. Finally, the black
+belt just below the green line is formed from data measured mainly under cloud-free
+conditions,conditions with the spread likely caused by the short-term variability of
+AOD. A small fraction of these data corresponds also to cases with thin cirrus clouds
+causing weak attenuation of GHI, often indistinguishable from the attenuation by
+aerosols.
 
 ```{r example-day, echo=FALSE, fig.cap="Example of CE identification in Thessaloniki for 2019-07-11.
-The green line with blue symbols depicts the measured GHI in one minute steps.
-Red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles.Black curve represents the TOA TSI on horizontal plane.", fig.pos='H'}
+The green line with blue symbols depicts the measured GHI in one-minute steps.
+The red line shows the modelled threshold for the detection of CE events, which are denoted with red circles.
+The black line represents the TOA TSI on a horizontal plane, equivalent to the threshold for the identification of ECE events, shown with red circles.
+The purple line is the modeled cloud-free irradiance.
+The dark yellow line is the solar constant of $1367\\,\\text{W}/\\text{m}^{2}$", fig.pos='H'}
 knitr::include_graphics("../images/P-example-day-5.png")
@@
 ```{r example-year, echo=FALSE, fig.cap="Example scatter plot of the measured GHI and the reference cloud-free irradiance in Thessaloniki for the year 2005.
-The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.
+The over-irradiance for CE and ECE events is colour coded, while the remaining data points are shown in black.
 The reference green line goes through the origin with a slope of one.", fig.pos='H'}

### 2024-09-08 article/article.tex
Commit 2024-09-08 21:12

@@
 Brewer spectrophotometer. We found a trend in CE events of
-\(+111\pm 27\,\text{cases}/\text{year}\), and a trend in the
-corresponding irradiation of \(+325.2\pm 88\,\text{kJ}/\text{year}\).
+\(+112\pm 35\,\text{cases}/\text{year}\), and a trend in the
+corresponding irradiation of \(+329.9\pm 112\,\text{kJ}/\text{year}\).
 The peak of the CE events was observed during May and June. CE events
@@
 irradiance at the top of the atmosphere for the same solar zenith angle
-of up to \(209\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the
+of up to \(204\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the
 cases below \(40\,\text{W}/\text{m}^{2}\). Most of these extreme events
@@
 \(19.9^\circ\) corresponding to OI of \(369.3\,\text{W}/\text{m}^2\) or
-\(35.3\,\%\) above the threshold. The strongest CE event of \(\,\%\)
+\(35.3\,\%\) above the threshold. The strongest CE event of \(53\,\%\)
 above the cloud-free threshold was observed on 28~October 2016 at a SZA
 of \(59.2^\circ\) with a GHI value of \(861.8\,\text{W}/\text{m}^2\) and
-a OI of \(298.4\,\text{W}/\text{m}^2\). Both cases are ECE events with
-\(131.2\,\text{W}/\text{m}^2\) and \(161.5\,\text{W}/\text{m}^2\) above
-the TSI at TOA for the same SZA, respectively. In the following sections
-we are discussing the long-term trends and variability of the CE events
-as well as of the corresponding OI and excess irradiation.
+a OI of \(298.4\,\text{W}/\text{m}^2\). Both cases are also ECE events
+with \(131.2\,\text{W}/\text{m}^2\) and \(161.5\,\text{W}/\text{m}^2\)
+above the TSI at TOA for the same SZA, respectively. In the following
+sections we are discussing the long-term trends and variability of the
+CE events as well as of the corresponding OI and excess irradiation.
 
@@
 \(95\,\%\) confidence level) increasing trends appear for the yearly
-number of CE events (\(+111\pm 27\,\text{cases}/\text{year}\)) and the
-excess irradiation (\(+325.2 \pm 88\,\text{kJ}/\text{year}\)), while the
-the trend in the yearly mean OI is negligible
-(\(+0.14\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of no
+number of CE events (\(+112\pm 35\,\text{cases}/\text{year}\)) and the
+excess irradiation (\(+329.9 \pm 112\,\text{kJ}/\text{year}\)), while
+the the trend in the yearly mean OI is negligible
+(\(+0.11\pm 0.2\,\text{W}/\text{m}^2/\text{year}\)) and of no
 statistical significance. The average OI for the entire period is
-\(+42.6\pm 2.8\,\text{W}/\text{m}^2\). The interannual variability of
-the data about the trend lines is quite large. Furthermore, the spread
-tends to increase with time (at least for the quantities of panels b and
-c), suggesting a significant variability in cloud patterns over the
-area, possibly associated to changes in climate.
+\(+42.6\pm 2.8\,\text{W}/\text{m}^2\).
+
+!!!! The yearly excess irradiation due to CE events ranges between about
+\(6\) and 13 MJ/m\textsuperscript{2}. On average, it is about one fourth
+of the highest daily irradiation of \textasciitilde31
+MJ/m\textsuperscript{2} under cloud-free conditions recorded at the
+summer solstice in Thessaloniki. Therefore, from solar energy
+perspective the yearly excess irradiation is only a tiny fraction of the
+available solar energy. Although the interannual variability of the mean
+OI is rather weak, the variability about the trend lines is quite large
+for the number of CE cases and the excess irradiation (panels b and c).
+For these two quantities the spread tends to increase with time,
+suggesting a significant variability in cloud patterns over the area,
+possibly associated to changes in climate.
+
+The interannual variability of the data about the trend lines is quite
+large. Furthermore, the spread tends to increase with time (at least for
+the quantities of panels b and c), suggesting a significant variability
+in cloud patterns over the area, possibly associated to changes in
+climate.
 
@@
             \subfloat[\label{fig:P-energy-mean}]
-                {\includegraphics[width=\linewidth]{../images/P-energy-3} }\\
+                {\includegraphics[width=\linewidth]{../images/P-energy-complete-3} }\\
             \subfloat[\label{fig:P-energy-N}]
-                {\includegraphics[width=\linewidth]{../images/P-energy-2} }\\
+                {\includegraphics[width=\linewidth]{../images/P-energy-complete-2} }\\
             \subfloat[\label{fig:P-energy-sum}]
-                {\includegraphics[width=\linewidth]{../images/P-energy-1} }
+                {\includegraphics[width=\linewidth]{../images/P-energy-complete-1} }
         }
@@
 After analyzing the CE cases, we found an increase of
-\(+111\pm 26.9\,\text{cases}/\text{year}\), with the mean annual
+\(+112.1\pm 34.9\,\text{cases}/\text{year}\), with the mean annual
 irradiation of the CE events increasing with a rate of
-\(+325.2\pm 88\,\text{kJ}/\text{year}\). The most active months of CE
+\(+329.9\pm 112\,\text{kJ}/\text{year}\). The most active months of CE
 events are May and June. We found that continuous CE events can last up

### 2024-09-08 article/article.Rmd
Commit 2024-09-08 21:12

@@
   read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear_Proper.csv"))
+## regular trends
 yearlyCE <- yearlytrends[DATA == "ST_E_yearly"]
+
+## trends with "complete data" !!!!!
+yearlyCE <- yearlytrends[DATA == "ST_E_yearly_Complete"]
 
@@
 of up to
-$209\,\text{W}/\text{m}^{2}$, with the $75\,\%$ of the cases below
+$204\,\text{W}/\text{m}^{2}$, with the $75\,\%$ of the cases below
 $40\,\text{W}/\text{m}^{2}$. Most of these extreme events occur in spring -- early
@@
 The strongest CE event of
-$`r round(100*MC[Typ == "Max Enha", GLB_ench],1)`\,\%$ above the 
+$`r round(100*MC[Typ == "Max Enh abs", GLB_ench],1)`\,\%$ above the 
 cloud-free threshold was observed on 
@@
 $`r round(MC[Typ == "Max Enh abs", GLB_diff],1)`\,\text{W}/\text{m}^2$.
-Both cases are ECE events with
+Both cases are also ECE events with
 $`r round(MC[Typ == "Max Global", TSI_OI],1)`\,\text{W}/\text{m}^2$ and
@@
 $`r plus_sign(round(mean(ST_E_yearly$GLB_diff.mean), 1))`\pm `r round(sd(ST_E_yearly$GLB_diff.mean),1)`\,\text{W}/\text{m}^2$.
+The yearly excess irradiation due to CE events ranges between about $8$ and
+$24\,\text{MJ}/\text{m}^2$. On average, it is about one half of the highest daily
+irradiation of \~31 MJ/m^2^ under cloud-free conditions recorded at the summer
+solstice in Thessaloniki.  Therefore, from solar energy perspective the yearly excess
+irradiation is only a tiny fraction of the available solar energy. Although the
+interannual variability of the mean OI is rather weak, the variability about the
+trend lines is quite large for the number of CE cases and the excess irradiation
+(panels b and c). For these two quantities the spread tends to increase with time,
+suggesting a significant variability in cloud patterns over the area, possibly
+associated to changes in climate.
+
 The interannual variability of the data about the trend lines is quite large.

### 2024-09-08 article/article.tex
Commit 2024-09-08 22:14

@@
 The purple line is the modeled cloud-free irradiance.
-The dark yellow line is the solar constant of $1367\,\text{W}/\text{m}^{2}$}\label{fig:example-day}
+The dark yellow line is the solar constant of $1367\,\text{W}/\text{m}^{2}$.}\label{fig:example-day}
 \end{figure}
@@
 statistical significance. The average OI for the entire period is
-\(+42.6\pm 2.8\,\text{W}/\text{m}^2\).
+\(+42.6\pm 2.8\,\text{W}/\text{m}^2\). The yearly excess irradiation due
+to CE events ranges between about \(8\) and
+\(24\,\text{MJ}/\text{m}^2\). On average, it is about one half of the
+highest daily irradiation of \textasciitilde31 MJ/m\textsuperscript{2}
+under cloud-free conditions recorded at the summer solstice in
+Thessaloniki. Therefore, from solar energy perspective the yearly excess
+irradiation is only a tiny fraction of the available solar energy.
+Although the interannual variability of the mean OI is rather weak, the
+variability about the trend lines is quite large for the number of CE
+cases and the excess irradiation (panels b and c). For these two
+quantities the spread tends to increase with time, suggesting a
+significant variability in cloud patterns over the area, possibly
+associated to changes in climate.
 
-!!!! The yearly excess irradiation due to CE events ranges between about
-\(6\) and 13 MJ/m\textsuperscript{2}. On average, it is about one fourth
-of the highest daily irradiation of \textasciitilde31
-MJ/m\textsuperscript{2} under cloud-free conditions recorded at the
-summer solstice in Thessaloniki. Therefore, from solar energy
-perspective the yearly excess irradiation is only a tiny fraction of the
-available solar energy. Although the interannual variability of the mean
-OI is rather weak, the variability about the trend lines is quite large
-for the number of CE cases and the excess irradiation (panels b and c).
-For these two quantities the spread tends to increase with time,
-suggesting a significant variability in cloud patterns over the area,
-possibly associated to changes in climate.
-
-The interannual variability of the data about the trend lines is quite
-large. Furthermore, the spread tends to increase with time (at least for
-the quantities of panels b and c), suggesting a significant variability
-in cloud patterns over the area, possibly associated to changes in
-climate.
-
-We have to note that the excess irradiation related to the CE events
-cannot be directly linked to the total energy balance of the atmosphere.
-The net solar radiation of the region is not increased, but is rather
-redistributed through the CE events. This is also depicted by the ECE
-irradiance values, which exceed the equivalent cloud-free irradiance by
-a significant amount.
+We must note that the excess irradiation from the CE events that is
+received at the surface does not affect the balance of the energy budget
+in the atmosphere. The incoming solar radiation in the region is not
+increased by the OI but is rather redistributed through the CE events.
+This is also depicted by the ECE irradiance values, which exceed the
+equivalent cloud-free irradiance by a significant amount.
 
@@
         {\centering
+            \subfloat[\label{fig:P-energy-N}]
+                {\includegraphics[width=\linewidth]{../images/P-energy-complete-2} }\\
             \subfloat[\label{fig:P-energy-mean}]
                 {\includegraphics[width=\linewidth]{../images/P-energy-complete-3} }\\
-            \subfloat[\label{fig:P-energy-N}]
-                {\includegraphics[width=\linewidth]{../images/P-energy-complete-2} }\\
             \subfloat[\label{fig:P-energy-sum}]
@@
         }
-    \caption{Time series for the period 1994 -- 2023 of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation.
+    \caption{Time series of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation at Thessaloniki for the period 1994 – 2023.
 The black lines represent the linear trends on the yearly data.}\label{fig:P-energy}
@@
 Figure\nobreakspace{}\ref{fig:relative-month-occurrences} shows the
-monthly box and whisker plot of the CE number of occurrences normalized
-with the highest median value, which occurs in June, depicting a clear
-seasonal cycle. Although CE events are present throughout the year, the
-most active months are May and June. During the winter (December --
-February), the number of CE cases is about \(25\,\%\) of the maximum,
-while in the intermediate months, the number of occurrences gradually
-ramps between the maximum and minimum. This seasonality is a combined
-effect of different factors, among them the types of clouds, their
-frequency of occurrence, the seasonally varying relative position of the
-sun, as well as the local landscape characteristics that may influence
-the formation of the clouds. Unfortunately, lack of detailed data on
-cloud formation, type and location is not allowing further analysis. The
+monthly box and whisker plot of the number of occurrences of the CE
+events in percent, calculated relative to the available one-minute data
+in each month. Although CE events are present throughout the year,
+showing a clear seasonal cycle, the most active months are May and June,
+with their median representing about \(3\,\%\) of the data. The least
+frequent events (about \(1\,\%\)) occur in August and during winter
+(December -- February). This seasonality is a combined effect of
+different factors, among them the types of clouds, their frequency of
+occurrence, the seasonally varying relative position of the sun, as well
+as the local landscape characteristics that may influence the formation
+of the clouds. For example, during May and June the frequent formation
+of cumulus clouds in the area leads to a significant increase in the CE
+events. However, the lack of detailed data in the area on cloud
+characteristics does not allow further analysis. Finally, the
 interannual variability of the monthly CE events is quite high as
-manifested by the large monthly extremes, especially in the summer.
+manifested by the size of the boxes and the large monthly extremes,
+especially in the summer. Investigation of the causes of this
+variability is beyond the scope of this study. It could possibly be
+related to the cloud cover variability in winter and autumn over
+southern Europe, associated with the North Atlantic Oscillation (NAO)
+circulation
 

### 2024-09-08 article/article.Rmd
Commit 2024-09-08 22:14

@@
 The purple line is the modeled cloud-free irradiance.
-The dark yellow line is the solar constant of $1367\\,\\text{W}/\\text{m}^{2}$", fig.pos='H'}
+The dark yellow line is the solar constant of $1367\\,\\text{W}/\\text{m}^{2}$.", fig.pos='H'}
 knitr::include_graphics("../images/P-example-day-5.png")
@@
 
-The interannual variability of the data about the trend lines is quite large.
-Furthermore, the spread tends to increase with time (at least for the quantities of
-panels b and c), suggesting a significant variability in cloud patterns over the
-area, possibly associated to changes in climate.
-
-We have to note that the excess irradiation related to the CE events cannot be
-directly linked to the total energy balance of the atmosphere. The net solar
-radiation of the region is not increased, but is rather redistributed through the CE
-events.  This is also depicted by the ECE irradiance values, which exceed the
-equivalent cloud-free irradiance by a significant amount.
+We must note that the excess irradiation from the CE events that is received at the
+surface does not affect the balance of the energy budget in the atmosphere. The
+incoming solar radiation in the region is not increased by the OI but is rather
+redistributed through the CE events.  This is also depicted by the ECE irradiance
+values, which exceed the equivalent cloud-free irradiance by a significant amount.
 
@@
 Figure\nobreakspace{}\ref{fig:relative-month-occurrences} shows the monthly box and
-whisker plot of the CE number of occurrences normalized with the highest median
-value, which occurs in June, depicting a clear seasonal cycle.  Although CE events
-are present throughout the year, the most active months are May and June. During the
-winter (December -- February), the number of CE cases is about $25\,\%$ of the
-maximum, while in the intermediate months, the number of occurrences gradually ramps
-between the maximum and minimum.  This seasonality is a combined effect of different
-factors, among them the types of clouds, their frequency of occurrence, the
-seasonally varying relative position of the sun, as well as the local landscape
-characteristics that may influence the formation of the clouds.  Unfortunately, lack
-of detailed data on cloud formation, type and location is not allowing further
-analysis. The interannual variability of the monthly CE events is quite high as
-manifested by the large monthly extremes, especially in the summer.
+whisker plot of the number of occurrences of the CE events in percent, calculated
+relative to the available one-minute data in each month.  Although CE events are
+present throughout the year, showing a clear seasonal cycle, the most active months
+are May and June, with their median representing about $3\,\%$ of the data.  The
+least frequent events (about $1\,\%$) occur in August and during winter (December --
+February).  This seasonality is a combined effect of different factors, among them
+the types of clouds, their frequency of occurrence, the seasonally varying relative
+position of the sun, as well as the local landscape characteristics that may
+influence the formation of the clouds.  For example, during May and June the frequent
+formation of cumulus clouds in the area leads to a significant increase in the CE
+events.  However, the lack of detailed data in the area on cloud characteristics does
+not allow further analysis. Finally, the interannual variability of the monthly CE
+events is quite high as manifested by the size of the boxes and the large monthly
+extremes, especially in the summer. Investigation of the causes of this variability
+is beyond the scope of this study. It could possibly be related to the cloud cover
+variability in winter and autumn over southern Europe, associated with the North
+Atlantic Oscillation (NAO)
+circulation
 

### 2024-09-08 article/article.tex
Commit 2024-09-08 23:11

@@
 of cumulus clouds in the area leads to a significant increase in the CE
-events. However, the lack of detailed data in the area on cloud
+events. However, the lack of detailed data in the area of cloud
 characteristics does not allow further analysis. Finally, the
@@
 southern Europe, associated with the North Atlantic Oscillation (NAO)
-circulation
+circulation \citep{Chiacchio2010}, or to the observed decreasing trend
+in cloud cover as a result of global warming
+\citep[e.g.,][]{SanchezLorenzo2017}.
 
@@
 
-\caption{Seasonal variability of the number of CE events relative to the corresponding number of GHI measurements in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot.
-The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles, the thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
+\caption{Seasonal variability of the relative occurrence of CE events in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot.
+The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles, with the thick horizontal line representing the median.
 The vertical lines (whiskers) extend between the maximum and minimum monthly values.}\label{fig:relative-month-occurrences}
@@
 events are, the rarer the conditions favoring the occurrence of CE
-events. For the majority (over \(62\,\%\)) of the CE events the OI is
-below the long-term average of \(42.6\,\text{W}/\text{m}^2\), while
-about \(8.1\,\%\) of the events correspond to OI larger than
+events.
+
+!!!!
+
+For the majority (over \(62\,\%\)) of the CE events the OI is below the
+long-term average of \(42.6\,\text{W}/\text{m}^2\), while about
+\(8.1\,\%\) of the events correspond to OI larger than
 \(100\,\text{W}/\text{m}^2\) and up to the highest value of

### 2024-09-08 article/article.Rmd
Commit 2024-09-08 23:11

@@
 formation of cumulus clouds in the area leads to a significant increase in the CE
-events.  However, the lack of detailed data in the area on cloud characteristics does
+events.  However, the lack of detailed data in the area of cloud characteristics does
 not allow further analysis. Finally, the interannual variability of the monthly CE
@@
 variability in winter and autumn over southern Europe, associated with the North
-Atlantic Oscillation (NAO)
-circulation
+Atlantic Oscillation (NAO) circulation [@Chiacchio2010], or to the observed
+decreasing trend in cloud cover as a result of global warming [e.g.,
+@SanchezLorenzo2017].
 
-```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal variability of the number of CE events relative to the corresponding number of GHI measurements in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot.
-The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles, the thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
+```{r relative-month-occurrences, echo=FALSE, fig.cap="Seasonal variability of the relative occurrence of CE events in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot.
+The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles, with the thick horizontal line representing the median.
 The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
@@
 decline. This is expected, as the stronger the CE events are, the rarer the
-conditions favoring the occurrence of CE events.  For the majority (over $62\,\%$) of
+conditions favoring the occurrence of CE events.
+
+!!!!
+
+For the majority (over $62\,\%$) of
 the CE events the OI is below the long-term average of
 $`r round(mean(ST_E_yearly$GLB_diff.mean),1)`\,\text{W}/\text{m}^2$, while about
-$8.1\,\%$ of the events correspond to OI larger than $100\,\text{W}/\text{m}^2$ and
+$8.1\,\%$ of the events correspond to OI larger than
+$100\,\text{W}/\text{m}^2$ and
 up to the highest value of $412.4\,\text{W}/\text{m}^2$.  This distribution is

### 2024-09-09 article/article.Rmd
Commit 2024-09-09 09:11

@@
 ## regular trends
-yearlyCE <- yearlytrends[DATA == "ST_E_yearly"]
+# yearlyCE <- yearlytrends[DATA == "ST_E_yearly"]
 
@@
 yearlyCE <- yearlytrends[DATA == "ST_E_yearly_Complete"]
+
+## some values
+some01 <- readRDS("~/MANUSCRIPTS/02_enhancement/data/some_values_01.Rds")
 
@@
 The distribution of the number of CE events as a function of OI is shown in
-Figure\nobreakspace{}\ref{fig:ovir-distribution}.  There is an inverse
-relationship between the frequency of CE events and OI with an exponential-like
-decline. This is expected, as the stronger the CE events are, the rarer the
-conditions favoring the occurrence of CE events.
-
-!!!!
-
-For the majority (over $62\,\%$) of
+Figure\nobreakspace{}\ref{fig:ovir-distribution}.  There is an inverse relationship
+between the frequency of CE events and OI with an exponential-like decline. This is
+expected, as the stronger the CE events are, the rarer the conditions favouring the
+occurrence of CE events.
+For the majority (over $`r round(some01$Enh_pc_below_mean,0)`\,\%$) of
 the CE events the OI is below the long-term average of
-$`r round(mean(ST_E_yearly$GLB_diff.mean),1)`\,\text{W}/\text{m}^2$, while about
-$8.1\,\%$ of the events correspond to OI larger than
-$100\,\text{W}/\text{m}^2$ and
-up to the highest value of $412.4\,\text{W}/\text{m}^2$.  This distribution is
-indicative of the magnitude and the probability of the expected CE events over
-Thessaloniki.  Similar distribution of CE events, albeit with larger OI values, has
-been reported by @Vamvakas2020, for the city of Patras. This site is located
-$2.5^\circ$ south of Thessaloniki and is exposed to air masses coming mainly from the
-eastern Mediterranean resulting in different cloud patterns, that may affect the
-characteristics and magnitude of the CE events.
+$`r round(some01$Enh_OI_AVG,1)`\,\text{W}/\text{m}^2$, while
+$`r round(some01$Enh_pc_below_100,1)`\,\%$ of the events correspond to OI larger than
+$100\,\text{W}/\text{m}^2$ and up to the highest value of
+$`r round(some01$Max_OI,1)`\,\text{W}/\text{m}^2$.
+This distribution is indicative of the magnitude and the probability of the expected
+CE events over Thessaloniki.  Similar distribution of CE events, albeit with larger
+OI values, has been reported by @Vamvakas2020, for the city of Patras. This site is
+located $2.5^\circ$ south of Thessaloniki and is exposed to air masses coming mainly
+from the eastern Mediterranean, resulting in different cloud patterns, that may
+affect the characteristics and magnitude of the CE events.
 
@@
 The duration of the CE events is variable and can last for several minutes or even
-more than an hour. In order to study the characteristics of these consecutive events,
-we grouped them into bins of increasing duration in steps of one minute.  We have
-identified `r ST_G0[, .N]` groups of CE in the whole period of study, where the group
-of the longest duration of
+more than an hour. To study the characteristics of these consecutive events, we
+grouped them into bins of increasing duration in steps of one minute.  We have
+identified `r ST_G0[, .N]` groups of CE events in the whole period of study, where
+the group with the longest duration of
 `r ST_G0[, max(GLB_diff.N)]` minutes occurred on
-`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")` in a SZA range of 
-$`r round(ST_G0[which.max(GLB_diff.N), SZA.min],1)`^\circ$ -- 
+`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")`
+with SZA ranging between
+$`r round(ST_G0[which.max(GLB_diff.N), SZA.min],1)`^\circ$ and
 $`r round(ST_G0[which.max(GLB_diff.N), SZA.max],1)`^\circ$.
@@
 distribution of the CE events according to their duration.  We conclude that although
-some groups of events last for more than an hour, about $80\,\%$ have duration of
+some groups of events last for more than an hour, about $80\,\%$ have a duration of
 less than 5 minutes.
+
+($`r ceiling(100*ST_G0[,sum(GLB_ench.N>5)/.N])`\,\%$)
 

### 2024-09-09 article/article.tex
Commit 2024-09-09 09:11

@@
 exponential-like decline. This is expected, as the stronger the CE
-events are, the rarer the conditions favoring the occurrence of CE
-events.
-
-!!!!
-
-For the majority (over \(62\,\%\)) of the CE events the OI is below the
-long-term average of \(42.6\,\text{W}/\text{m}^2\), while about
-\(8.1\,\%\) of the events correspond to OI larger than
+events are, the rarer the conditions favouring the occurrence of CE
+events. For the majority (over \(62\,\%\)) of the CE events the OI is
+below the long-term average of \(42.6\,\text{W}/\text{m}^2\), while
+\(9.6\,\%\) of the events correspond to OI larger than
 \(100\,\text{W}/\text{m}^2\) and up to the highest value of
-\(412.4\,\text{W}/\text{m}^2\). This distribution is indicative of the
+\(437\,\text{W}/\text{m}^2\). This distribution is indicative of the
 magnitude and the probability of the expected CE events over
@@
 Patras. This site is located \(2.5^\circ\) south of Thessaloniki and is
-exposed to air masses coming mainly from the eastern Mediterranean
+exposed to air masses coming mainly from the eastern Mediterranean,
 resulting in different cloud patterns, that may affect the
@@
 The duration of the CE events is variable and can last for several
-minutes or even more than an hour. In order to study the characteristics
-of these consecutive events, we grouped them into bins of increasing
-duration in steps of one minute. We have identified 34849 groups of CE
-in the whole period of study, where the group of the longest duration of
-140 minutes occurred on 07~July 2013 in a SZA range of \(52.1^\circ\) --
-\(77.9^\circ\). Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}
-shows the frequency distribution of the CE events according to their
-duration. We conclude that although some groups of events last for more
-than an hour, about \(80\,\%\) have duration of less than 5 minutes.
+minutes or even more than an hour. To study the characteristics of these
+consecutive events, we grouped them into bins of increasing duration in
+steps of one minute. We have identified 34849 groups of CE events in the
+whole period of study, where the group with the longest duration of 140
+minutes occurred on 07~July 2013 with SZA ranging between \(52.1^\circ\)
+and \(77.9^\circ\).
+Figure\nobreakspace{}\ref{fig:ceg-duration-distribution} shows the
+frequency distribution of the CE events according to their duration. We
+conclude that although some groups of events last for more than an hour,
+about \(80\,\%\) have a duration of less than 5 minutes.
+
+(\(21\,\%\))
 

### 2024-09-09 article/article.Rmd
Commit 2024-09-09 11:11

@@
 distribution of the CE events according to their duration.  We conclude that although
-some groups of events last for more than an hour, about $80\,\%$ have a duration of
-less than 5 minutes.
-
-($`r ceiling(100*ST_G0[,sum(GLB_ench.N>5)/.N])`\,\%$)
+some groups of events last for more than an hour, about
+$`r round(100*ST_G0[,sum(GLB_ench.N<=5)/.N],0)`\,\%$ have a duration of
+equal or less than 5 minutes.
 
@@
 
-The relation between the duration and the mean OI of the groups has also been studied
-(Figure\nobreakspace{}\ref{fig:group-2d}).  Evidently, events of high excess
-irradiation have small duration and vice versa. The vast majority of grouped events
-are associated with small excess irradiation ($<5\,\text{kJ}/\text{m}^2$) and small
-duration ($<5\,\text{min}$). For example the extra energy flux of
-$5\,\text{kJ}/\text{m}^2$ for $5\,\text{min}$ is equivalent to OI of
-$\sim17\,\text{W}/\text{m}^2$ for the same duration. While groups with strong excess
-irradiation and long duration are very rare.  Similar results of this relation have
-been reported by @Zhang2018 in a study using a far higher sampling rate
-($100\,\text{Hz}$) than
-ours.
+The relation between the duration and the mean OI of the CE groups is shown in
+Figure\nobreakspace{}\ref{fig:group-2d}.  As expected, events with small duration and
+low OI are accumulated close to the origin of the plot.  Events of high excess
+irradiation have a short duration and vice versa. The vast majority of grouped events
+are associated with small excess irradiation ($<5\,\text{kJ}/\text{m}^2$) and short
+duration ($<5\,\text{min}$). For example, the excess irradiation of
+$5\,\text{kJ}/\text{m}^2$ for $5\,\text{min}$ is equivalent to an OI of
+$16.7\,\text{W}/\text{m}^2$ with duration of $5\,\text{min}$. On the contrary, groups
+with strong excess irradiation and long duration are very rare.  Similar results of
+this relation have been reported by @Zhang2018 in a study using a far higher sampling
+rate ($100\,\text{Hz}$) than ours.
 
 ```{r group-2d, echo=FALSE, fig.cap="Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1994 -- 2023.
-The logarithmic color scale denotes the frequency of the respective groups of events."}
+The logarithmic color scale denotes the frequency of the respective groups."}
 knitr::include_graphics("../images/P-groups-bin2d-1.png")
@@
 An aspect of the CE events that is commonly reported and has some significance on the
-solar energy production infrastructure are the extreme CE events (ECE), where solar
-irradiance exceeds the expected irradiance on top of the atmosphere at the same SZA
-(Equation\nobreakspace{}\ref{eq:ECE}).  Analogous to
-Figure\nobreakspace{}\ref{fig:relative-month-occurrences} we have computed the
-distribution of the number of occurrences of ECE events by month in
-Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. The most active period
-for ECE events is in spring and early summer (March -- June), followed by a
-period in early autumn (September and October).  This is probably related to the
-weather characteristics in these periods, with frequent alternations between cloud-free periods and clouds.
+solar energy production infrastructure are the extreme CE (ECE) events, where the
+measured GHI exceeds the expected irradiance at the TOA at the same SZA
+(Equation\nobreakspace{}\ref{eq:ECE}).  In analogy to
+Figure\nobreakspace{}\ref{fig:relative-month-occurrences}, we show in 
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE} the number of ECE
+events relative to the total number of one-min observations in each month. Judging by
+the distribution of the monthly medians, the most active months in ECE events are
+January -- March and November and the least active are July and August. The highest
+interannual variability in the 30-year record occurs from October to April. In the
+summer period, the fraction of ECE events is very small, with almost zero variability
+in July and August.  Although the most active months for CE events are May and June
+(Figure\nobreakspace{}\ref{fig:relative-month-occurrences}), these months behave
+differently for the ECE events, suggesting that the cumulus clouds that usually cause
+enhancements of irradiance are incapable to produce extreme events, possibly because
+of their size and structure, in conjunction with the smaller SZAs in the summer.
 
-```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal variability of the number of ECE events relative to the the corresponding number of GHI measurements in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot.
-The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles.
-The thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
+In general, the fraction of ECE events during the year is very small, well below
+$0.1\,\%$ of the data, therefore on average it would not affect the production of
+solar energy. However, during short, isolated periods extreme enhancements of GHI can
+be of concern.
+
+```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Seasonal variability of the relative occurrence of ECE events in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot.
+The box contains the data between the lower $25\\,\\%$ and the upper $75\\,\\%$ percentiles, with the thick horizontal line representing the median.
 The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
@@
 ```
-
 <!--
@@
 (Figure\nobreakspace{}\ref{fig:P-extreme-distribution}) shows that in rare cases the
-OI can exceed the TSI at TOA for the same SZA even by more than
-$400\,\text{W}/\text{m}^2$, while in $75\,\%$ of the cases the OI is below
-$200\,\text{W}/\text{m}^2$. The OI for the most frequent ECEs ranges between $140$
-and $180\,\text{W}/\text{m}^2$.  These findings are in accordance with the results of
-@Vamvakas2020, the only difference being that the OI values reported for are higher
-than those for Thessaloniki.
+measured GHI exceeds the TOA TSI at the same SZA even by more than
+$200\,\text{W}/\text{m}^2$, while in $75\,\%$ of the cases the OI is below
+$40\,\text{W}/\text{m}^2$. The $50\,\%$ OI of the most frequent ECEs cases ranges
+between $127$ and $211\,\text{W}/\text{m}^2$.  These findings are in accordance with
+the results of @Vamvakas2020, the only difference being that the OI values reported
+are higher than those for Thessaloniki.
 
-```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE events in Thessaloniki for the period 1994 -- 2023. Measured as extra irradiance over TSI at TOA for the same SZA."}
+```{r P-extreme-distribution, echo=FALSE, fig.cap="Relative frequency distribution of ECE events, in Thessaloniki for the period 1994 -- 2023, as a function of the extra irradiance over TSI at TOA for the same SZA."}
 knitr::include_graphics("../images/P-extreme-distribution-2.png")

### 2024-09-09 article/article.tex
Commit 2024-09-09 11:11

@@
 conclude that although some groups of events last for more than an hour,
-about \(80\,\%\) have a duration of less than 5 minutes.
-
-(\(21\,\%\))
+about \(79\,\%\) have a duration of equal or less than 5 minutes.
 
@@
 
-The relation between the duration and the mean OI of the groups has also
-been studied (Figure\nobreakspace{}\ref{fig:group-2d}). Evidently,
-events of high excess irradiation have small duration and vice versa.
-The vast majority of grouped events are associated with small excess
-irradiation (\(<5\,\text{kJ}/\text{m}^2\)) and small duration
-(\(<5\,\text{min}\)). For example the extra energy flux of
-\(5\,\text{kJ}/\text{m}^2\) for \(5\,\text{min}\) is equivalent to OI of
-\(\sim17\,\text{W}/\text{m}^2\) for the same duration. While groups with
-strong excess irradiation and long duration are very rare. Similar
-results of this relation have been reported by \citet{Zhang2018} in a
-study using a far higher sampling rate (\(100\,\text{Hz}\)) than ours.
+The relation between the duration and the mean OI of the CE groups is
+shown in Figure\nobreakspace{}\ref{fig:group-2d}. As expected, events
+with small duration and low OI are accumulated close to the origin of
+the plot. Events of high excess irradiation have a short duration and
+vice versa. The vast majority of grouped events are associated with
+small excess irradiation (\(<5\,\text{kJ}/\text{m}^2\)) and short
+duration (\(<5\,\text{min}\)). For example, the excess irradiation of
+\(5\,\text{kJ}/\text{m}^2\) for \(5\,\text{min}\) is equivalent to an OI
+of \(16.7\,\text{W}/\text{m}^2\) with duration of \(5\,\text{min}\). On
+the contrary, groups with strong excess irradiation and long duration
+are very rare. Similar results of this relation have been reported by
+\citet{Zhang2018} in a study using a far higher sampling rate
+(\(100\,\text{Hz}\)) than ours.
 
@@
 \caption{Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1994 -- 2023.
-The logarithmic color scale denotes the frequency of the respective groups of events.}\label{fig:group-2d}
+The logarithmic color scale denotes the frequency of the respective groups.}\label{fig:group-2d}
 \end{figure}
@@
 significance on the solar energy production infrastructure are the
-extreme CE events (ECE), where solar irradiance exceeds the expected
-irradiance on top of the atmosphere at the same SZA
-(Equation\nobreakspace{}\ref{eq:ECE}). Analogous to
-Figure\nobreakspace{}\ref{fig:relative-month-occurrences} we have
-computed the distribution of the number of occurrences of ECE events by
-month in Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}.
-The most active period for ECE events is in spring and early summer
-(March -- June), followed by a period in early autumn (September and
-October). This is probably related to the weather characteristics in
-these periods, with frequent alternations between cloud-free periods and
-clouds.
+extreme CE (ECE) events, where the measured GHI exceeds the expected
+irradiance at the TOA at the same SZA
+(Equation\nobreakspace{}\ref{eq:ECE}). In analogy to
+Figure\nobreakspace{}\ref{fig:relative-month-occurrences}, we show in
+Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE} the number
+of ECE events relative to the total number of one-min observations in
+each month. Judging by the distribution of the monthly medians, the most
+active months in ECE events are January -- March and November and the
+least active are July and August. The highest interannual variability in
+the 30-year record occurs from October to April. In the summer period,
+the fraction of ECE events is very small, with almost zero variability
+in July and August. Although the most active months for CE events are
+May and June
+(Figure\nobreakspace{}\ref{fig:relative-month-occurrences}), these
+months behave differently for the ECE events, suggesting that the
+cumulus clouds that usually cause enhancements of irradiance are
+incapable to produce extreme events, possibly because of their size and
+structure, in conjunction with the smaller SZAs in the summer.
+
+In general, the fraction of ECE events during the year is very small,
+well below \(0.1\,\%\) of the data, therefore on average it would not
+affect the production of solar energy. However, during short, isolated
+periods extreme enhancements of GHI can be of concern.
 
@@
 
-\caption{Seasonal variability of the number of ECE events relative to the the corresponding number of GHI measurements in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot.
-The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles.
-The thick horizontal line and the diamond symbol represent the median and the mean values, respectively.
+\caption{Seasonal variability of the relative occurrence of ECE events in Thessaloniki for the period 1994 -- 2023, in the form of a box and whisker plot.
+The box contains the data between the lower $25\,\%$ and the upper $75\,\%$ percentiles, with the thick horizontal line representing the median.
 The vertical lines (whiskers) extend between the maximum and minimum monthly values.}\label{fig:relative-month-occurancies-ECE}
@@
 (Figure\nobreakspace{}\ref{fig:P-extreme-distribution}) shows that in
-rare cases the OI can exceed the TSI at TOA for the same SZA even by
-more than \(400\,\text{W}/\text{m}^2\), while in \(75\,\%\) of the cases
-the OI is below \(200\,\text{W}/\text{m}^2\). The OI for the most
-frequent ECEs ranges between \(140\) and \(180\,\text{W}/\text{m}^2\).
-These findings are in accordance with the results of
-\citet{Vamvakas2020}, the only difference being that the OI values
-reported for are higher than those for Thessaloniki.
+rare cases the measured GHI exceeds the TOA TSI at the same SZA even by
+more than \(200\,\text{W}/\text{m}^2\), while in \(75\,\%\) of the cases
+the OI is below \(40\,\text{W}/\text{m}^2\). The \(50\,\%\) OI of the
+most frequent ECEs cases ranges between \(127\) and
+\(211\,\text{W}/\text{m}^2\). These findings are in accordance with the
+results of \citet{Vamvakas2020}, the only difference being that the OI
+values reported are higher than those for Thessaloniki.
 
@@
 
-\caption{Distribution of ECE events in Thessaloniki for the period 1994 -- 2023. Measured as extra irradiance over TSI at TOA for the same SZA.}\label{fig:P-extreme-distribution}
+\caption{Relative frequency distribution of ECE events, in Thessaloniki for the period 1994 -- 2023, as a function of the extra irradiance over TSI at TOA for the same SZA.}\label{fig:P-extreme-distribution}
 \end{figure}

### 2024-09-09 Article_B12/Article_B12_plain.tex
Commit 2024-09-09 12:14

--- 2024-09-09 article/article.tex
@@
 irradiance enhancement events induced by clouds over Thessaloniki for
-the period 1994 -- 2023 using data recorded every one minute. We
+the period 1994 -- 2023 using data recorded every one minute. To our
+knowledge, there isn't a similar study with such a long time series. We
 identified the cloud enhancement (CE) events by creating an appropriate
@@
 events are May and June. We found that continuous CE events can last up
-to \(140\) minutes, while the duration of \(80\,\%\) of them is bellow
-\(5\) minutes.
+to \(140\) minutes, while the duration of \(79\,\%\) of them is equal or
+bellow \(5\) minutes.
 
-We have observed ECE cases exceeding the TSI by
-\(400\,\text{W}/\text{m}^{2}\) with \(75\,\%\) of the cases under
-\(200\,\text{W}/\text{m}^{2}\). The climatological characteristics of
-the ECE events showed that the most active months are spread in half of
-the year and particularly in the periods March -- June and September --
-October. The magnitude of the ECE events identified in Thessaloniki
-events does not exceed the values reported for sites with more
-favourable conditions for the phenomenon \citep[e.g.,][]{Cordero2023}.
-Some of the characteristics of CE and ECE events we analyzed have strong
-similarities with the results of \citet{Vamvakas2020} for the city of
-Patras, south of Thessaloniki, albeit with differences in the magnitude
-of OI.
+We have observed ECE cases with GHI exceeding the TOA TSI on horizontal
+plane by more than \(200\,\text{W}/\text{m}^{2}\) while for \(75\,\%\)
+of the cases the excess irradiance (relative to TOA TSI on horizontal
+plane) is below \(40\,\text{W}/\text{m}^{2}\). The climatological
+characteristics of the ECE events showed that the most active months are
+spread over half of the year, and particularly in the periods March --
+June and September -- October. The magnitude of the ECE events
+identified in Thessaloniki events does not exceed the values reported
+for sites with more favourable conditions for the phenomenon
+\citep[e.g.,][]{Cordero2023}. Some of the characteristics of CE and ECE
+events we analyzed have strong similarities with the results of
+\citet{Vamvakas2020} for the city of Patras, south of Thessaloniki,
+albeit with differences in the magnitude of OI.
 
@@
 with the clouds, through this 30-year period, is a dynamic phenomenon
-that needs further investigation. For such studies it would be essential
-to have more detailed information on cloud characteristics, especially
-in order to investigate possible associations of the observed trends
-with changes in climate.
+that needs further investigation. For such studies, it would be
+essential to have more detailed information on cloud characteristics,
+especially in order to investigate possible associations of the observed
+trends with changes in climate.
 

### 2024-09-09 Article_B12/Article_B12.Rmd
Commit 2024-09-09 12:14

--- 2024-09-09 article/article.Rmd
@@
 enhancement events induced by clouds over Thessaloniki for the period 1994 -- 2023
-using data recorded every one minute.  We identified the cloud enhancement (CE)
-events by creating an appropriate cloud-free irradiance reference using a radiative
-transfer model and aerosol optical depth data from a collocated Cimel sun photometer
-and a Brewer spectrophotometer. We found a trend in CE events of
+using data recorded every one minute.  To our knowledge, there isn't a similar study
+with such a long time series.  We identified the cloud enhancement (CE) events by
+creating an appropriate cloud-free irradiance reference using a radiative transfer
+model and aerosol optical depth data from a collocated Cimel sun photometer and a
+Brewer spectrophotometer. We found a trend in CE events of
 $`r plus_sign(round(yearlyCE[var=="GLB_diff.N",slope],0))`\pm
@@
 The most active months of CE events are May and June.  We found that continuous CE
-events can last up to $140$ minutes, while the duration of $80\,\%$ of them is bellow
-$5$ minutes.
+events can last up to $140$ minutes, while the duration of $79\,\%$ of them is equal
+or bellow $5$ minutes.
 
-We have observed ECE cases exceeding the TSI by $400\,\text{W}/\text{m}^{2}$ with
-$75\,\%$ of the cases under $200\,\text{W}/\text{m}^{2}$. The climatological
-characteristics of the ECE events showed that the most active months are spread in
-half of the year and particularly in the periods March -- June and September --
-October.  The magnitude of the ECE events identified in Thessaloniki events does not
-exceed the values reported for sites with more favourable conditions for the
-phenomenon [e.g., @Cordero2023]. Some of the characteristics of CE and ECE events we
-analyzed have strong similarities with the results of @Vamvakas2020 for the city of
-Patras, south of Thessaloniki, albeit with differences in the magnitude of OI.
+We have observed ECE cases with GHI exceeding the TOA TSI on horizontal plane by more
+than $200\,\text{W}/\text{m}^{2}$ while for $75\,\%$ of the cases the excess
+irradiance (relative to TOA TSI on horizontal plane) is below
+$40\,\text{W}/\text{m}^{2}$. The climatological characteristics of the ECE events
+showed that the most active months are spread over half of the year, and particularly in
+the periods March -- June and September -- October.  The magnitude of the ECE events
+identified in Thessaloniki events does not exceed the values reported for sites with
+more favourable conditions for the phenomenon [e.g., @Cordero2023]. Some of the
+characteristics of CE and ECE events we analyzed have strong similarities with the
+results of @Vamvakas2020 for the city of Patras, south of Thessaloniki, albeit with
+differences in the magnitude of OI.
 
@@
 through this 30-year period, is a dynamic phenomenon that needs further
-investigation. For such studies it would be essential to have more detailed
+investigation. For such studies, it would be essential to have more detailed
 information on cloud characteristics, especially in order to investigate possible

### 2024-09-09 article/article.tex
Commit 2024-09-09 14:14

@@
 derive the long-term change in GHI due to aerosols: \begin{equation}
-\Delta(\text{AOD}) [\%] = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 \label{eq:AODchange}
+\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 \label{eq:AODchange}
 \end{equation} where \(y\) is the date as a decimal fraction of the

### 2024-09-09 article/article.Rmd
Commit 2024-09-09 14:14

@@
 \begin{equation}
-\Delta(\text{AOD}) [\%] = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 \label{eq:AODchange}
+\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 \label{eq:AODchange}
 \end{equation}

### 2024-09-09 article/article.Rmd
Commit 2024-09-09 19:11

@@
 the yield and in designing the specifications of the appropriate equipment.  A
-significant portion of the relevant research has been focused on predicting the
+significant portion of the relevant research has been focused on predicting
 renewable energy production in a fine timescale and in near real-time [for a review
@@
 
-Some of the proposed underling mechanisms of those enhancements have been summarized
+Some of the proposed underlying mechanisms of those enhancements have been summarized
 by @Gueymard2017; the most important being the scattering of radiation on the edges
 of cumulus clouds.  It has also been suggested that enhancement of GHI can be
-produced by thin cirrus clouds though refraction and scattering [@Thuillier2013].
+produced by thin cirrus clouds through refraction and scattering [@Thuillier2013].
 Further investigation with radiative transfer modeling and observations pointed as
@@
 optical depth [@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015].  Overall,
-the appearance of CE events depend on different interactive factors, which include
+the appearance of CE events depends on different interactive factors, which include
 cloud thickness, structure and type, and the relative position of the sun and the
@@
 while @Dong2023 reported decreases over North America and Europe. To our knowledge,
-there is no evidence of whether this trend has affected also the number and strength
+there is no evidence of whether this trend has also affected the number and strength
 of CE events.
@@
 using the ramped value of the instrument’s sensitivity between subsequent
-calibrations.  We note that the specific model of the pyranometer is not capable in
+calibrations.  We note that the specific model of the pyranometer is not capable of
 recording the instrument's temperature, therefore any temperature changes that may
@@
 than $`r 90 - BIO_ELEVA`^\circ$.  Finally, images from a sky camera have been used in
-the manual inspection of the CE identification. The sky camera has been operating
-since 2012 and stores images in 5 min time steps.  An overview of the GHI data used
-in this study is given in
-Figure\nobreakspace{}\ref{fig:CLB-daily}, as the daily means.  Daily means were
-calculated only for days with at least $60\,\%$ of data availability; however, all
-available one-minute measurements have been used for the detection of CE events.
+the manual inspection of the CE events identification. The sky camera has been
+operating since 2012 and stores images in 15 min time steps.  An overview of the GHI
+data used in this study is given in Figure\nobreakspace{}\ref{fig:CLB-daily}, as the
+daily means.  Daily means were calculated only for days with at least $60\,\%$ of
+data availability; however, all available one-minute measurements have been used for
+the detection of CE events.
 
-```{r CLB-daily, echo=FALSE, fig.cap="Timeseries of daily mean GHI measured at Thessaloniki for the period 1994 -- 2023."}
+```{r CLB-daily, echo=FALSE, fig.cap="Time-series of daily mean GHI measured at Thessaloniki for the period 1994 -- 2023."}
 knitr::include_graphics("../images/P_daily_trend-5.png")
@@
 
-## Cloud enhancement detection
+## Detection of cloud enhancements
 
-<!-- Define CE and ECE tomove? -->
 In this study, we define an event as CE when the measured GHI at ground level
-exceeds the expected value under cloud-free conditions. Similarly, we define as
-extreme cloud enhancement events (ECE), the cases when GHI at ground level exceeds
+exceeds the expected GHI under cloud-free conditions. Similarly, we define as
+extreme cloud enhancement (ECE) events the cases when GHI at ground level exceeds
 the Total Solar Irradiance (TSI) at the top of the atmosphere (TOA) for the same SZA.
@@
 For the detection of CE cases, we established a baseline of irradiance above which we
-characterized each data point as an enhancement event and calculated the over
+characterized each data point as a CE event and calculated the over
 irradiance (OI). The OI is defined as the irradiance difference of the measured
@@
 $\text{GHI}_\text{ref}$: The Haurwitz's model [@Haurwitz1945], which is a simple
-clear sky radiation model and was already adjusted and applied to our data
-[@Natsis2023].  We created a threshold by using an appropriate relative and/or an
+clear sky radiation model and was already adjusted and applied to our data in
+@Natsis2023.  We created a threshold by using an appropriate relative and/or an
 additional constant offset.  The initial results showed that we can detect a big
@@
 
-## Modeled cloud-free Irradiance {#rtmcs}
+## Modeled cloud-free irradiance {#rtmcs}
 
@@
 "pseudospherical" geometry and the "LOWTRAN" gas parameterization.  The model was run
-for climatological values of the Angstrom coefficients, water column (WC), SZA and
-the appropriate seasonal atmospheric profile to create a look-up table (LUT) for the
-estimation of the cloud-free reference irradiance for each individual observation of
-our dataset. In this context, the model was run for SZAs in the range $10$ --
-$90^\circ$ with a step of $0.2^\circ$ and for the atmospheric profiles of the Air
-Force Geophysics Laboratory [@Anderson1986] midlatitude summer and midlatitude
+for climatological values of the aerosol Ångström coefficients, water column (WC),
+SZA and the appropriate seasonal atmospheric profile to create a look-up table (LUT)
+for the estimation of the cloud-free reference irradiance for each individual
+observation of our dataset. In this context, the model was run for SZAs in the range
+$10$ -- $90^\circ$ with a step of $0.2^\circ$ and for the atmospheric profiles of the
+Air Force Geophysics Laboratory [@Anderson1986] midlatitude summer and midlatitude
 winter, representative of the warm and cold seasons.
@@
 Main factors responsible for the attenuation of the broadband downward solar
-radiation under cloud free atmospheres are aerosols and water vapor.  At
-Thessaloniki, such measurements are available since 2003 from a Cimel sun photometer,
-which is part of the Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998].  From
-the observations in the period 2003 -- 2023 we calculated the monthly climatological
-means and standard deviation ($\sigma$) for the aerosol optical depth (AOD) at
-$500\,\text{nm}$ and the equivalent height of the water column (WC).  The monthly
-climatological values of AOD and WC, as well as combinations with additional offsets
-of $\pm1\sigma$ and $\pm2\sigma$, were used as inputs to the RTM in the construction
-of the LUT.
+radiation under cloud-free atmospheres are aerosols and water vapor.  At
+Thessaloniki, such measurements have been available since 2003 from a Cimel sun
+photometer, which is part of the Aerosol Robotic Network (AERONET) [@Giles2019;
+@Buis1998].  From the observations in the period 2003 -- 2023 we calculated the
+monthly climatological means and standard deviations ($\sigma$) for the aerosol
+optical depth (AOD) at $500\,\text{nm}$ and the equivalent height of the water column
+(WC).  The monthly climatological values of AOD and WC, as well as combinations with
+additional offsets of $\pm1\sigma$ and $\pm2\sigma$, were used as inputs to the RTM
+in the construction of the LUT.
 
@@
 
-### Long-term change of cloud-free irradiance
+### Long-term changes in cloud-free irradiance
 
@@
 to account for the long-term variations of the AOD.  High quality AOD data with a
-Cimel sun-photometer (part of AERONET) at Thessaloniki start only in 2003, while
-spectral AOD measurements using direct-sun observations with a MKIII Brewer
-spectrophotometer are available for the period 1997 -- 2017. These data are taken
-sporadically during each day and are less dense compared to the AERONET data. By
-comparing monthly AOD data at $340\,\text{nm}$ of the two instruments for the common
-periods of operation we adjusted the Brewer data and filled the missing months of the
-Cimel record data with Brewer data.  Using the monthly time series of AOD at
+Cimel sun-photometer at Thessaloniki start only in 2003, while spectral AOD
+measurements using direct-sun observations with a MKIII Brewer spectrophotometer are
+available for the period 1997 -- 2017. The Brewer AOD data are taken sporadically
+during each day and are less dense compared to the AERONET data. By comparing monthly
+AOD data at $340\,\text{nm}$ of the two instruments for the common periods of
+operation we adjusted the Brewer data and filled the missing months of the Cimel
+record with Brewer data.  Using the extended monthly time series of AOD at
 $340\,\text{nm}$, as well as monthly climatological values of the Ångström exponent
@@
 get a rough estimate of the annually averaged change in cloud-free GHI. A
-second-degree polynomial fit was applied to the simulated yearly averaged GHI
-to derive the long-term change in GHI due to aerosols:
+second-degree polynomial fit was applied to the simulated yearly averaged GHI to
+derive the long-term change in GHI due to aerosols:
 \begin{equation}
-\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 \label{eq:AODchange}
+\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot x + -0.002981 \cdot x^2 \label{eq:AODchange}
 \end{equation}
-where $y$ is the date as a decimal fraction of the year. For the period of the study
-the relative change of AOD ranges between $-1.88$ and $-0.23\,\%$.  Finally, we
+where $y$ is the date as a decimal fraction of the year.
+The resulting change in $\text{GHI}_\text{ref}$ ranges between $-1.88$ in 1994, a
+peak of $0.23\,\%$ in mid-2020 and $-0.19\,\%$ in the end of 2023. Finally, we
 applied these long-term changes of Equation\nobreakspace{}\ref{eq:AODchange} to the
-climatological $\text{GHI}_\text{ref}$, to create a more realistic representation of
+$\text{GHI}_\text{ref}$, to create a more realistic representation of
 the cloud-free irradiance for the entire period of study. For the period 1994 -- 1996
@@
 
+<!--
+GHI_model (%)
+ = -12170 + 12.05 * year_frac + -0.002981 * year_frac^2
+-->
 <!--
@@
 
-<!--
-GHI_model (%)
- = -12170 + 12.05 * year_frac + -0.002981 * year_frac^2
--->
-
 ## Criteria for the identification of CE events
@@
 depends on the selection of the appropriate atmospheric parameterization for the RTM
-simulations. The implementation of the long-term change in AOD, discussed in
-section\nobreakspace{}\ref{rtmcs}, allows capturing a large part of the natural
+simulations. The implementation of the long-term changes in GHI due to AOD, discussed
+in section\nobreakspace{}\ref{rtmcs}, allows capturing a large part of the natural
 variability of cloud-free GHI. However, the short-term variability of AOD cannot be
@@
 
-First, we evaluated the performance of the modelled $\text{GHI}_\text{ref}$ in
+First, we evaluated the performance of the modeled $\text{GHI}_\text{ref}$ in
 relation to the measured GHI for different levels of atmospheric clearness, by using
 in the RTM the monthly climatological AOD and WC, less their respective standard
-deviations.
-<!--
-$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
-($\text{GHI}_\text{CSm}$).
--->
-These values represent typical atmospheres in Thessaloniki with lower than average
-load of aerosols and humidity, which are the main factors that attenuate the GHI,
-excluding clouds.  With this approach, the simulated $\text{GHI}_\text{ref}$ should be
-generally greater than the measured GHI when aerosols are more abundant. The
-correlation of the $\text{GHI}_\text{ref}$ with the GHI was tested for a subset of
-cloud-free days with more than $80\,\%$ data availability
-(Figure\nobreakspace{}\ref{fig:validation-GHI}) and found to have a positive bias of
-more than $18\,\text{W}/\text{m}^2$ across all levels of radiation.  To achieve a
-robust and clear distinction of CE cases, we set the criteria of CE detection
-$`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$ above the $\text{GHI}_\text{ref}$.
+deviations.  These values represent typical atmospheres in Thessaloniki with
+lower-than-average load of aerosols and humidity, which are the main factors that
+attenuate the GHI, excluding clouds.  With this approach, the simulated
+$\text{GHI}_\text{ref}$ should be generally greater than the measured GHI when
+aerosols are more abundant.  The correlation of the $\text{GHI}_\text{ref}$ with the
+GHI was tested for a subset of cloud-free days with more than $80\,\%$ data
+availability (Figure\nobreakspace{}\ref{fig:validation-GHI}) and found to have a
+positive bias of more than $18\,\text{W}/\text{m}^2$ across all levels of radiation.
+To achieve a robust and clear distinction of CE cases, we set the criteria of CE
+detection $`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$ above the
+$\text{GHI}_\text{ref}$.
 
@@
 
+<!--
+$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
+($\text{GHI}_\text{CSm}$).
+-->
 <!--

### 2024-09-09 GHI_enh_05_distributions.R

@@ -636,7 +636,7 @@ ggplot(monthly, aes(y = 100 * Relative_enha_GLB,
                                     labels = month.abb[1:12]))) +
   geom_boxplot(fill = varcol("GLB_diff"), outliers = FALSE) +
   xlab("") +
-  ylab("CE occurence frequency relative to GHI [%]") +
+  ylab("Relative frequency [%]") +
   # stat_summary(fun.y = mean, geom = "point", shape = 23, size = 3) +
   theme(
     panel.grid.major.x = element_blank(),
@@ -685,7 +685,7 @@ ggplot(monthlyE, aes(y = 100 * Relative_enha_GLB,
                                     labels = month.abb[1:12]))) +
   geom_boxplot(fill = "lightblue", outliers = FALSE) +
   xlab("") +
-  ylab("ECE occurence frequency relative to GHI [%]") +
+  ylab("ECE occurrence frequency relative to GHI [%]") +
   # stat_summary(fun.y = mean, geom = "point", shape = 23, size = 3) +
   theme(
     panel.grid.major.x = element_blank(),
@@ -723,7 +723,7 @@ boxplot(mont[, CE_OI/OI_N] ~ mont$month)
 title("Mean monthly OI")
 
 
-## Check days for reviers
+## Check days for reviews
 
 
 
@@ -760,7 +760,6 @@ mean(DATA$TSIextEARTH_comb, na.rm = T)
 
 ## Solstice --------------------
 LUK <- readRDS("./data/lookuptable_datatable.Rds")
-# LUK <- LUK[SZA > 17]
 
 solstis <- data.table()
 for (ay in unique(year(LUK$Date))) {
@@ -777,7 +776,7 @@ for (ay in unique(year(LUK$Date))) {
 
 }
 
-pander(solstis, caption = "Solstices from Libratran")
+pander(solstis, caption = "Solstices from Libradtran")
 
 
 cat("Solstice max for all period", max(solstis$Enerhy_Kj/1000, na.rm = T), "MJ", "\n\n")

### 2024-09-09 GHI_enh_07_Aerosols_BR_CIM.R

@@ -204,6 +204,15 @@ trend_polyf <- function(tsy) {
   (polym_C[3] / polyf_zero) * tsy^2
 }
 
+
+
+x    <- (seq(1994, 2024, 0.01))
+test <- data.table(x = x, y = 100 * trend_polyf(x)  )
+
+first(test)
+last(test)
+test[which.max(y),]
+
 cat("Range of delta(AOD):", signif(100 * range(trend_polyf(seq(1994, 2024, 0.01))), 2), "\n\n")
 
 cat("Range of delta(AOD):", round(100 * range(trend_polyf(seq(1994, 2024, 0.01))), 2), "\n\n")

### 2024-09-09 article/article.tex
Commit 2024-09-09 19:11

@@
 equipment. A significant portion of the relevant research has been
-focused on predicting the renewable energy production in a fine
-timescale and in near real-time \citep[for a review
+focused on predicting renewable energy production in a fine timescale
+and in near real-time \citep[for a review
 see][]{Inman2013, Graabak2016}.
@@
 
-Some of the proposed underling mechanisms of those enhancements have
+Some of the proposed underlying mechanisms of those enhancements have
 been summarized by \citet{Gueymard2017}; the most important being the
@@
 suggested that enhancement of GHI can be produced by thin cirrus clouds
-though refraction and scattering \citep{Thuillier2013}. Further
+through refraction and scattering \citep{Thuillier2013}. Further
 investigation with radiative transfer modeling and observations pointed
@@
 \citep{Pecenak2016, Thuillier2013, Yordanov2013, Yordanov2015}. Overall,
-the appearance of CE events depend on different interactive factors,
+the appearance of CE events depends on different interactive factors,
 which include cloud thickness, structure and type, and the relative
@@
 reported decreases over North America and Europe. To our knowledge,
-there is no evidence of whether this trend has affected also the number
+there is no evidence of whether this trend has also affected the number
 and strength of CE events.
@@
 instrument's sensitivity between subsequent calibrations. We note that
-the specific model of the pyranometer is not capable in recording the
+the specific model of the pyranometer is not capable of recording the
 instrument's temperature, therefore any temperature changes that may
@@
 angle (SZA) greater than \(78^\circ\). Finally, images from a sky camera
-have been used in the manual inspection of the CE identification. The
-sky camera has been operating since 2012 and stores images in 5 min time
-steps. An overview of the GHI data used in this study is given in
+have been used in the manual inspection of the CE events identification.
+The sky camera has been operating since 2012 and stores images in 15 min
+time steps. An overview of the GHI data used in this study is given in
 Figure\nobreakspace{}\ref{fig:CLB-daily}, as the daily means. Daily
@@
 
-\caption{Timeseries of daily mean GHI measured at Thessaloniki for the period 1994 -- 2023.}\label{fig:CLB-daily}
+\caption{Time-series of daily mean GHI measured at Thessaloniki for the period 1994 -- 2023.}\label{fig:CLB-daily}
 \end{figure}
 
-\hypertarget{cloud-enhancement-detection}{%
-\subsection{Cloud enhancement
-detection}\label{cloud-enhancement-detection}}
+\hypertarget{detection-of-cloud-enhancements}{%
+\subsection{Detection of cloud
+enhancements}\label{detection-of-cloud-enhancements}}
 
 In this study, we define an event as CE when the measured GHI at ground
-level exceeds the expected value under cloud-free conditions. Similarly,
-we define as extreme cloud enhancement events (ECE), the cases when GHI
+level exceeds the expected GHI under cloud-free conditions. Similarly,
+we define as extreme cloud enhancement (ECE) events the cases when GHI
 at ground level exceeds the Total Solar Irradiance (TSI) at the top of
@@
 For the detection of CE cases, we established a baseline of irradiance
-above which we characterized each data point as an enhancement event and
+above which we characterized each data point as a CE event and
 calculated the over irradiance (OI). The OI is defined as the irradiance
@@
 which is a simple clear sky radiation model and was already adjusted and
-applied to our data \citep{Natsis2023}. We created a threshold by using
-an appropriate relative and/or an additional constant offset. The
+applied to our data in \citet{Natsis2023}. We created a threshold by
+using an appropriate relative and/or an additional constant offset. The
 initial results showed that we can detect a big portion of the actual CE
@@
 \hypertarget{rtmcs}{%
-\subsection{Modeled cloud-free Irradiance}\label{rtmcs}}
+\subsection{Modeled cloud-free irradiance}\label{rtmcs}}
 
@@
 the ``LOWTRAN'' gas parameterization. The model was run for
-climatological values of the Angstrom coefficients, water column (WC),
-SZA and the appropriate seasonal atmospheric profile to create a look-up
-table (LUT) for the estimation of the cloud-free reference irradiance
-for each individual observation of our dataset. In this context, the
-model was run for SZAs in the range \(10\) -- \(90^\circ\) with a step
-of \(0.2^\circ\) and for the atmospheric profiles of the Air Force
-Geophysics Laboratory \citep{Anderson1986} midlatitude summer and
+climatological values of the aerosol Ångström coefficients, water column
+(WC), SZA and the appropriate seasonal atmospheric profile to create a
+look-up table (LUT) for the estimation of the cloud-free reference
+irradiance for each individual observation of our dataset. In this
+context, the model was run for SZAs in the range \(10\) -- \(90^\circ\)
+with a step of \(0.2^\circ\) and for the atmospheric profiles of the Air
+Force Geophysics Laboratory \citep{Anderson1986} midlatitude summer and
 midlatitude winter, representative of the warm and cold seasons.
@@
 Main factors responsible for the attenuation of the broadband downward
-solar radiation under cloud free atmospheres are aerosols and water
-vapor. At Thessaloniki, such measurements are available since 2003 from
-a Cimel sun photometer, which is part of the Aerosol Robotic Network
-(AERONET) \citep{Giles2019, Buis1998}. From the observations in the
-period 2003 -- 2023 we calculated the monthly climatological means and
-standard deviation (\(\sigma\)) for the aerosol optical depth (AOD) at
-\(500\,\text{nm}\) and the equivalent height of the water column (WC).
-The monthly climatological values of AOD and WC, as well as combinations
-with additional offsets of \(\pm1\sigma\) and \(\pm2\sigma\), were used
-as inputs to the RTM in the construction of the LUT.
+solar radiation under cloud-free atmospheres are aerosols and water
+vapor. At Thessaloniki, such measurements have been available since 2003
+from a Cimel sun photometer, which is part of the Aerosol Robotic
+Network (AERONET) \citep{Giles2019, Buis1998}. From the observations in
+the period 2003 -- 2023 we calculated the monthly climatological means
+and standard deviations (\(\sigma\)) for the aerosol optical depth (AOD)
+at \(500\,\text{nm}\) and the equivalent height of the water column
+(WC). The monthly climatological values of AOD and WC, as well as
+combinations with additional offsets of \(\pm1\sigma\) and
+\(\pm2\sigma\), were used as inputs to the RTM in the construction of
+the LUT.
 
@@
 
-\hypertarget{long-term-change-of-cloud-free-irradiance}{%
-\subsubsection{Long-term change of cloud-free
-irradiance}\label{long-term-change-of-cloud-free-irradiance}}
+\hypertarget{long-term-changes-in-cloud-free-irradiance}{%
+\subsubsection{Long-term changes in cloud-free
+irradiance}\label{long-term-changes-in-cloud-free-irradiance}}
 
@@
 variations of the AOD. High quality AOD data with a Cimel sun-photometer
-(part of AERONET) at Thessaloniki start only in 2003, while spectral AOD
-measurements using direct-sun observations with a MKIII Brewer
-spectrophotometer are available for the period 1997 -- 2017. These data
-are taken sporadically during each day and are less dense compared to
-the AERONET data. By comparing monthly AOD data at \(340\,\text{nm}\) of
-the two instruments for the common periods of operation we adjusted the
-Brewer data and filled the missing months of the Cimel record data with
-Brewer data. Using the monthly time series of AOD at \(340\,\text{nm}\),
-as well as monthly climatological values of the Ångström exponent and
+at Thessaloniki start only in 2003, while spectral AOD measurements
+using direct-sun observations with a MKIII Brewer spectrophotometer are
+available for the period 1997 -- 2017. The Brewer AOD data are taken
+sporadically during each day and are less dense compared to the AERONET
+data. By comparing monthly AOD data at \(340\,\text{nm}\) of the two
+instruments for the common periods of operation we adjusted the Brewer
+data and filled the missing months of the Cimel record with Brewer data.
+Using the extended monthly time series of AOD at \(340\,\text{nm}\), as
+well as monthly climatological values of the Ångström exponent and
 constant WC of \(15.6\,\text{mm}\) derived from the Cimel record, we

### 2024-09-09 article/article.Rmd
Commit 2024-09-09 20:11

@@
 lower-than-average load of aerosols and humidity, which are the main factors that
-attenuate the GHI, excluding clouds.  With this approach, the simulated
-$\text{GHI}_\text{ref}$ should be generally greater than the measured GHI when
+attenuate the GHI, in the absence of clouds.  With this approach, the simulated
+$\text{GHI}_\text{ref}$ should generally be greater than the measured GHI when
 aerosols are more abundant.  The correlation of the $\text{GHI}_\text{ref}$ with the
-GHI was tested for a subset of cloud-free days with more than $80\,\%$ data
-availability (Figure\nobreakspace{}\ref{fig:validation-GHI}) and found to have a
-positive bias of more than $18\,\text{W}/\text{m}^2$ across all levels of radiation.
-To achieve a robust and clear distinction of CE cases, we set the criteria of CE
-detection $`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$ above the
-$\text{GHI}_\text{ref}$.
+GHI was tested for a subset of 513 cloud-free days with more than $80\,\%$ data
+availability (Figure\nobreakspace{}\ref{fig:validation-GHI}).
+The scatter plot shows a good agreement between the modeled and the measured GHI with
+a spread that arises mainly from the short-term variability of AOD and WC.  The
+linear regression reveals a positive bias of $18.4\,\text{W}/\text{m}^2$ and a slope
+very close to unity.  To achieve a robust and clear distinction of the CE cases, we
+applied on the $\text{GHI}_\text{ref}$ an additional offset of
+$`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$.
 
-```{r validation-GHI, echo=FALSE, fig.cap="The corelation GHI with $\\text{GHI}_\\text{ref}$, for cloud-free data of days with data availability more than $80\\,\\%$.", fig.pos='H'}
+```{r validation-GHI, echo=FALSE, fig.cap="Scatter plot of the measured GHI and the $\\text{GHI}_\\text{ref}$, for cloud-free days with data availability of more than $80\\,\\%$.
+The linear regression on the data is also shown on the figure with the blue line.", fig.pos='H'}
 knitr::include_graphics("../images/P-validation-cloudfree-GHI-1.png")
@@
 
-To further ensure the effectiveness of this CE criterion, we implement a manual
-inspection of the CE identification results on selected days of the whole dataset.
-We tested seven sets of days with different characteristics relevant to the
-efficiency of the identification threshold.  These sets were random groups of about
-20 -- 30 days with the following characteristics:
+To further ensure the effectiveness of this CE criterion, we inspected manually the
+CE identification results on selected days of the whole dataset.  We tested seven
+random groups of about 20 -- 30 days with the following characteristics:
 (a) the strongest OI CE events,
@@
 For the latter case and where needed, we also used images from the sky-camera to
-further aid the decision of the manual inspection.
+further aid the inspection.
 
@@
 this method was proven capable in detecting all major CE events.  Where some CE
-events with very low OI may be not detected, these are few with small
-over-irradiance, and it is unlikely that will affect significantly our results.
+events with very low OI may be not detected, these were few with small
+over-irradiance, and it is unlikely that will significantly affect our results.
 
 <!-- extreme caces criterion -->
-A sub-category of the CE events that is often discussed in the literature
-[@Cordero2023; @Martins2022; @Yordanov2015], are the extreme cloud enhancement (ECE)
+A subcategory of the CE events that is often discussed in the literature
+[@Cordero2023; @Martins2022; @Yordanov2015], are the extreme cloud enhancement
 events. These are cases of CE where the measured intensity of the irradiance exceeds
-the TSI on horizontal plane at TOA. In this case the threshold $E$ is given by:
+the TSI on a horizontal plane at TOA. In this case the threshold $E$ is given by:
 \begin{equation}
@@
 reference irradiance and the CE and ECE thresholds are shown along with the actual
-GHI measurements.  The GHI data in the periods 7:30 -- 8:30 and after 14:00 are very
-close to the modeled cloud-free GHI (light blue line) thus were identified as
-cloud-free instances. There is some ambiguity for the data points laying between the
-CE threshold and the cloud-free irradiance, which are not identified as CE events.
-These data points correspond to cases either with AOD below the one assumed in the
-model, or with very small OI.
+GHI measurements.  Three sky-camera images at the bottom illustrate the cloud
+conditions during the highest ECE events (a and c), while (b) shows the conditions
+where clouds caused a substantial reduction in GHI.  The GHI data in the periods 7:30
+-- 8:30 and after 14:00 are very close to the modeled cloud-free GHI (purple line)
+thus were identified as cloud-free instances. There is some ambiguity for the data
+points lying between the CE threshold and the cloud-free irradiance, which are not
+identified as CE events.  These data points correspond to cases either with AOD below
+the one assumed in the model, or with very small OI.
 
 In addition, we provide in Figure\nobreakspace{}\ref{fig:example-year} an example
-scatter plot between the measured GHI and the modeled cloud-free irradiance for one
-year (2005), where the CE and ECE events are clearly grouped above the cloud-free
-irradiance (approximated with the green line).  The grey colored data points above
-this line correspond to the ambiguous data points discussed above. Finally, the black
-belt just below the green line is formed from data measured mainly under cloud-free
-conditions,conditions with the spread likely caused by the short-term variability of
+scatter plot between the measured GHI and the modeled cloud-free irradiance for year
+2005, where the CE and ECE events are clearly grouped above the cloud-free irradiance
+(approximated with the green line).  The gray colored data points above this line
+correspond to the ambiguous data points discussed above. Finally, the black belt just
+below the green line is formed from data measured mainly under cloud-free
+conditions, with the spread likely caused by the short-term variability of
 AOD. A small fraction of these data corresponds also to cases with thin cirrus clouds
@@
 The green line with blue symbols depicts the measured GHI in one-minute steps.
-The red line shows the modelled threshold for the detection of CE events, which are denoted with red circles.
+The red line shows the modeled threshold for the detection of CE events, which are denoted with gray circles.
 The black line represents the TOA TSI on a horizontal plane, equivalent to the threshold for the identification of ECE events, shown with red circles.
 The purple line is the modeled cloud-free irradiance.
-The dark yellow line is the solar constant of $1367\\,\\text{W}/\\text{m}^{2}$.", fig.pos='H'}
+The dark yellow line is the solar constant of $1367\\,\\text{W}/\\text{m}^{2}$.
+The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.", fig.pos='H'}
 knitr::include_graphics("../images/P-example-day-5.png")
@@
 ```{r example-year, echo=FALSE, fig.cap="Example scatter plot of the measured GHI and the reference cloud-free irradiance in Thessaloniki for the year 2005.
-The over-irradiance for CE and ECE events is colour coded, while the remaining data points are shown in black.
-The reference green line goes through the origin with a slope of one.", fig.pos='H'}
+The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.
+The reference green line goes through the origin with a slope of unity.", fig.pos='H'}
 knitr::include_graphics("../images/P-example-years-12.png")
 ```
-
-<!-- ```{r echo=F, include=T, warning=FALSE, message=FALSE} -->
-<!-- ST_total -->
-<!-- cat("\n - - - \n") -->
-<!-- ST_daily[which.max(wattGLB.max), wattGLB.max] -->
-<!-- round(ST_E_daily[which.max(GLB_diff.max), GLB_diff.max], 2) -->
-<!-- round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1) -->
-<!-- plot(ST_daily$Date, ST_daily$GLB_diff.max) -->
-<!-- ``` -->
 
@@
 Following the application of the above discussed methodology to the entire dataset
-($`r round(ST_total$wattGLB.N / 10^6,1)`$ million of one-minute GHI measurements),
+($>`r round(ST_total$wattGLB.N / 10^6,1)`$ million of one-minute GHI measurements),
 $`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 2)`\,\%$ were identified as CE events and
@@
 `r strftime(MC[Typ == "Max Enh abs", Date], "%d\\ %B %Y")` at a SZA of
-$`r round(MC[Typ == "Max Enh abs", SZA],1)`^\circ$ with a GHI value of 
+$`r round(MC[Typ == "Max Enh abs", SZA],1)`^\circ$ with a GHI of
 $`r round(MC[Typ == "Max Enh abs", wattGLB],1)`\,\text{W}/\text{m}^2$ and a OI of
@@
 ($`r plus_sign(round(yearlyCE[var == "GLB_diff.sum", slope], 1))` \pm `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$),
-while the the trend in the yearly mean OI is negligible
-($`r plus_sign(round(yearlyCE[var == "GLB_diff.mean", slope], 2))`\pm `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\text{W}/\text{m}^2/\text{year}$)
+while the trend in the yearly mean OI is negligible
+($`r plus_sign(round(yearlyCE[var == "GLB_diff.mean", slope], 1))`\pm `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\text{W}/\text{m}^2/\text{year}$)
 and of no statistical significance.
@@
 suggesting a significant variability in cloud patterns over the area, possibly
-associated to changes in climate.
+associated with changes in climate.
 
@@
 incoming solar radiation in the region is not increased by the OI but is rather
-redistributed through the CE events.  This is also depicted by the ECE irradiance
-values, which exceed the equivalent cloud-free irradiance by a significant amount.
+redistributed at the specific location as asdditional scattered radiation.  This is
+also depicted by the ECE irradiance values, which exceed the equivalent cloud-free
+irradiance by a significant amount.
 

### 2024-09-09 article/article.tex
Commit 2024-09-09 20:11

@@
 derive the long-term change in GHI due to aerosols: \begin{equation}
-\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 \label{eq:AODchange}
+\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot x + -0.002981 \cdot x^2 \label{eq:AODchange}
 \end{equation} where \(y\) is the date as a decimal fraction of the
-year. For the period of the study the relative change of AOD ranges
-between \(-1.88\) and \(-0.23\,\%\). Finally, we applied these long-term
-changes of Equation\nobreakspace{}\ref{eq:AODchange} to the
-climatological \(\text{GHI}_\text{ref}\), to create a more realistic
-representation of the cloud-free irradiance for the entire period of
-study. For the period 1994 -- 1996 where no AOD data are available, we
-assumed that the changes in GHI follow the same polynomial fit.
+year. The resulting change in \(\text{GHI}_\text{ref}\) ranges between
+\(-1.88\) in 1994, a peak of \(0.23\,\%\) in mid-2020 and \(-0.19\,\%\)
+in the end of 2023. Finally, we applied these long-term changes of
+Equation\nobreakspace{}\ref{eq:AODchange} to the
+\(\text{GHI}_\text{ref}\), to create a more realistic representation of
+the cloud-free irradiance for the entire period of study. For the period
+1994 -- 1996 where no AOD data are available, we assumed that the
+changes in GHI follow the same polynomial fit.
 
@@
 appropriate atmospheric parameterization for the RTM simulations. The
-implementation of the long-term change in AOD, discussed in
+implementation of the long-term changes in GHI due to AOD, discussed in
 section\nobreakspace{}\ref{rtmcs}, allows capturing a large part of the
@@
 
-First, we evaluated the performance of the modelled
+First, we evaluated the performance of the modeled
 \(\text{GHI}_\text{ref}\) in relation to the measured GHI for different
@@
 climatological AOD and WC, less their respective standard deviations.
-These values represent typical atmospheres in Thessaloniki with lower
-than average load of aerosols and humidity, which are the main factors
-that attenuate the GHI, excluding clouds. With this approach, the
-simulated \(\text{GHI}_\text{ref}\) should be generally greater than the
-measured GHI when aerosols are more abundant. The correlation of the
-\(\text{GHI}_\text{ref}\) with the GHI was tested for a subset of
-cloud-free days with more than \(80\,\%\) data availability
-(Figure\nobreakspace{}\ref{fig:validation-GHI}) and found to have a
-positive bias of more than \(18\,\text{W}/\text{m}^2\) across all levels
-of radiation. To achieve a robust and clear distinction of CE cases, we
-set the criteria of CE detection \(25\,\text{W}/\text{m}^2\) above the
-\(\text{GHI}_\text{ref}\).
+These values represent typical atmospheres in Thessaloniki with
+lower-than-average load of aerosols and humidity, which are the main
+factors that attenuate the GHI, in the absence of clouds. With this
+approach, the simulated \(\text{GHI}_\text{ref}\) should generally be
+greater than the measured GHI when aerosols are more abundant. The
+correlation of the \(\text{GHI}_\text{ref}\) with the GHI was tested for
+a subset of 513 cloud-free days with more than \(80\,\%\) data
+availability (Figure\nobreakspace{}\ref{fig:validation-GHI}). The
+scatter plot shows a good agreement between the modeled and the measured
+GHI with a spread that arises mainly from the short-term variability of
+AOD and WC. The linear regression reveals a positive bias of
+\(18.4\,\text{W}/\text{m}^2\) and a slope very close to unity. To
+achieve a robust and clear distinction of the CE cases, we applied on
+the \(\text{GHI}_\text{ref}\) an additional offset of
+\(25\,\text{W}/\text{m}^2\).
 
@@
 
-\caption{The corelation GHI with $\text{GHI}_\text{ref}$, for cloud-free data of days with data availability more than $80\,\%$.}\label{fig:validation-GHI}
+\caption{Scatter plot of the measured GHI and the $\text{GHI}_\text{ref}$, for cloud-free days with data availability of more than $80\,\%$.
+The linear regression on the data is also shown on the figure with the blue line.}\label{fig:validation-GHI}
 \end{figure}
 
-To further ensure the effectiveness of this CE criterion, we implement a
-manual inspection of the CE identification results on selected days of
-the whole dataset. We tested seven sets of days with different
-characteristics relevant to the efficiency of the identification
-threshold. These sets were random groups of about 20 -- 30 days with the
+To further ensure the effectiveness of this CE criterion, we inspected
+manually the CE identification results on selected days of the whole
+dataset. We tested seven random groups of about 20 -- 30 days with the
 following characteristics: (a) the strongest OI CE events, (b) the
@@
 where needed, we also used images from the sky-camera to further aid the
-decision of the manual inspection.
+inspection.
 
@@
 detecting all major CE events. Where some CE events with very low OI may
-be not detected, these are few with small over-irradiance, and it is
-unlikely that will affect significantly our results.
+be not detected, these were few with small over-irradiance, and it is
+unlikely that will significantly affect our results.
 
-A sub-category of the CE events that is often discussed in the
-literature \citep{Cordero2023, Martins2022, Yordanov2015}, are the
-extreme cloud enhancement (ECE) events. These are cases of CE where the
-measured intensity of the irradiance exceeds the TSI on horizontal plane
-at TOA. In this case the threshold \(E\) is given by: \begin{equation}
+A subcategory of the CE events that is often discussed in the literature
+\citep{Cordero2023, Martins2022, Yordanov2015}, are the extreme cloud
+enhancement events. These are cases of CE where the measured intensity
+of the irradiance exceeds the TSI on a horizontal plane at TOA. In this
+case the threshold \(E\) is given by: \begin{equation}
 \text{ECE}: E > \cos(\text{SZA}) \cdot E_{\odot} \frac{r^2_\text{m}} {r^2}
@@
 course of the cloud-free reference irradiance and the CE and ECE
-thresholds are shown along with the actual GHI measurements. The GHI
-data in the periods 7:30 -- 8:30 and after 14:00 are very close to the
-modeled cloud-free GHI (light blue line) thus were identified as
-cloud-free instances. There is some ambiguity for the data points laying
-between the CE threshold and the cloud-free irradiance, which are not
-identified as CE events. These data points correspond to cases either
-with AOD below the one assumed in the model, or with very small OI.
+thresholds are shown along with the actual GHI measurements. Three
+sky-camera images at the bottom illustrate the cloud conditions during
+the highest ECE events (a and c), while (b) shows the conditions where
+clouds caused a substantial reduction in GHI. The GHI data in the
+periods 7:30 -- 8:30 and after 14:00 are very close to the modeled
+cloud-free GHI (purple line) thus were identified as cloud-free
+instances. There is some ambiguity for the data points lying between the
+CE threshold and the cloud-free irradiance, which are not identified as
+CE events. These data points correspond to cases either with AOD below
+the one assumed in the model, or with very small OI.
 

### 2024-09-09 GHI_enh_02_ID_CE.R

@@ -775,7 +775,7 @@ for (pyear in yearstodo) {
                           high     = "red",
                           limits   = c(0, NA),  ## always display zero
                           na.value = NA) +
-    labs(title = pyear) +
+    # labs(title = pyear) +
     ylab(bquote("Measured GHI" ~ group("[", W/m^2,"]"))) +
     xlab(bquote("GHI reference" ~ group("[", W/m^2,"]"))) +
     labs(color = bquote("OI" ~ group("[", W/m^2,"]"))) +

### 2024-09-09 article/article.Rmd
Commit 2024-09-09 21:18

@@
 #     text: "Another author footnote."
-# abstract: |
-#   In this study we investigate the characteristics of global horizontal irradiance
-#   \(200\,\text{W}/\text{m}^{2}\). The most active period of these extreme events is
-#   spring -- early summer with a secondary peak in autumn.
+abstract: |
+  In this study, we investigate the characteristics of global horizontal
+  irradiance enhancement events induced by clouds over Thessaloniki for
+  the period 1994 -- 2023 using data recorded every one minute. To our
+  knowledge, there isn't a similar study with such a long time series. We
+  identified the cloud enhancement (CE) events by creating an appropriate
+  cloud-free irradiance reference using a radiative transfer model and
+  aerosol optical depth data from a collocated Cimel sun photometer and a
+  Brewer spectrophotometer. We found a trend in CE events of
+  \(+112\pm 35\,\text{cases}/\text{year}\), and a trend in the
+  corresponding irradiation of \(+329.9\pm 112\,\text{kJ}/\text{year}\).
+  The peak of the CE events was observed during May and June. CE events
+  with duration longer than 10\nobreakspace{}min are very rare
+  (\(<8\,\%\)), with exceptions lasting over an hour and up to 140
+  minutes. Finally, we have detected enhancements above the total solar
+  irradiance at the top of the atmosphere for the same solar zenith angle
+  of up to \(204\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the
+  cases below \(40\,\text{W}/\text{m}^{2}\). Most of these extreme events
+  occur in spring -- early summer, with a secondary peak in autumn.
 
@@
 
+<!--
 # Abstract {.unnumbered}
@@
 summer, with a secondary peak in autumn.
+-->
 
@@
 <!-- Instrument -->
-  During the study
-period, the pyranometer was independently calibrated three times at the
-Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of the
-instrument’s sensitivity was better than $0.7\,\%$ relative to the initial
+During the study period, the pyranometer was independently calibrated three times at
+the Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of
+the instrument’s sensitivity was better than $0.7\,\%$ relative to the initial
 calibration by the manufacturer.
@@
 incoming solar radiation in the region is not increased by the OI but is rather
-redistributed at the specific location as asdditional scattered radiation.  This is
+redistributed at the specific location as additional scattered radiation.  This is
 also depicted by the ECE irradiance values, which exceed the equivalent cloud-free
@@
 formation of cumulus clouds in the area leads to a significant increase in the CE
-events.  However, the lack of detailed data in the area of cloud characteristics does
+events.  However, the lack of detailed data on cloud characteristics in the area does
 not allow further analysis. Finally, the interannual variability of the monthly CE
@@
 between the frequency of CE events and OI with an exponential-like decline. This is
-expected, as the stronger the CE events are, the rarer the conditions favouring the
+expected, as the stronger the CE events are, the rarer the conditions favoring the
 occurrence of CE events.
@@
 located $2.5^\circ$ south of Thessaloniki and is exposed to air masses coming mainly
-from the eastern Mediterranean, resulting in different cloud patterns, that may
+from the eastern Mediterranean, resulting in different cloud patterns that may
 affect the characteristics and magnitude of the CE events.
@@
 $`r round(100*ST_G0[,sum(GLB_ench.N<=5)/.N],0)`\,\%$ have a duration of
-equal or less than 5 minutes.
+equal or less than 5 minutes, likely due to the movements of clouds causing frequent
+blocking of the direct irradiance, which reduce the duration of the CE events.
 
@@
 Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE} the number of ECE
-events relative to the total number of one-min observations in each month. Judging by
+events relative to the available number of one-min observations in each month. Judging by
 the distribution of the monthly medians, the most active months in ECE events are
@@
 enhancements of irradiance are incapable to produce extreme events, possibly because
-of their size and structure, in conjunction with the smaller SZAs in the summer.
+of their size and structure, in conjunction with the smaller SZAs in the summer.  In
+contrast, during winter the Sun is lower in the sky and clouds are frequently less
+dense allowing a large fraction of radiation to be scattered forward and enhance the
+irradiance at the surface. These conclusions are based on manual inspection of many
+sky-camera images during the summer and winter periods. An automated procedure of
+checking the sky-camera images for such events would greatly improve our ability to
+classify the CE and ECE events and help in the attribution of the causes of the
+events.
 
@@
 By creating a cloud-free approximation representing the long- and short-term
-variability of the expected cloud-free GHI, we were able to identify cases of CE
-events in Thessaloniki for the period 1994 -- 2023.  After analyzing the CE cases, we
-found an increase of
+variability of the expected cloud-free GHI, we were able to identify cases of CE and
+ECE events in Thessaloniki for the period 1994 -- 2023.  After analyzing the CE
+cases, we found an increasing tendency of
 $`r plus_sign(round(yearlyCE[var == "GLB_diff.N", slope], 1))`\pm `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$,
@@
 
-We have observed ECE cases with GHI exceeding the TOA TSI on horizontal plane by more
-than $200\,\text{W}/\text{m}^{2}$ while for $75\,\%$ of the cases the excess
-irradiance (relative to TOA TSI on horizontal plane) is below
+We have observed ECE cases with GHI exceeding the TOA TSI on a horizontal plane by
+more than $200\,\text{W}/\text{m}^{2}$ while for $75\,\%$ of the cases the excess
+irradiance (relative to TOA TSI on a horizontal plane) is below
 $40\,\text{W}/\text{m}^{2}$. The climatological characteristics of the ECE events
-showed that the most active months are spread over half of the year, and particularly in
-the periods March -- June and September -- October.  The magnitude of the ECE events
-identified in Thessaloniki events does not exceed the values reported for sites with
-more favourable conditions for the phenomenon [e.g., @Cordero2023]. Some of the
-characteristics of CE and ECE events we analyzed have strong similarities with the
-results of @Vamvakas2020 for the city of Patras, south of Thessaloniki, albeit with
-differences in the magnitude of OI.
+showed that the most active months are spread over half of the year, and particularly
+in the months January -- March and November, while ECE events are practically absent
+in July and August.  The magnitude of the ECE events identified in Thessaloniki does
+not exceed the values reported for sites with more favorable conditions for the
+phenomenon [e.g., @Cordero2023]. Some of the characteristics of CE and ECE events we
+analyzed have strong similarities with the results of @Vamvakas2020 for the city of
+Patras, south of Thessaloniki, albeit with differences in the magnitude of OI.
 
-An interpretation of the CE trends shows that the interaction of GHI with the clouds,
-through this 30-year period, is a dynamic phenomenon that needs further
-investigation. For such studies, it would be essential to have more detailed
-information on cloud characteristics, especially in order to investigate possible
-associations of the observed trends with changes in climate.
+The investigation of the CE trends in Thessaloniki through this 30-year period shows
+that the interaction of GHI with clouds is a complex phenomenon that merits further
+attention. For such studies, it would be essential to have more detailed information
+on cloud characteristics, especially in order to investigate possible associations of
+the observed trends with changes in climate.  Finally, automated procedures to
+analyze the sky-camera images would greatly improve our knowledge about the
+generation of these events.
 

### 2024-09-09 article/article.tex
Commit 2024-09-09 21:18

@@
   \begin{abstract}
-
+  In this study, we investigate the characteristics of global horizontal
+  irradiance enhancement events induced by clouds over Thessaloniki for
+  the period 1994 -- 2023 using data recorded every one minute. To our
+  knowledge, there isn't a similar study with such a long time series.
+  We identified the cloud enhancement (CE) events by creating an
+  appropriate cloud-free irradiance reference using a radiative transfer
+  model and aerosol optical depth data from a collocated Cimel sun
+  photometer and a Brewer spectrophotometer. We found a trend in CE
+  events of \(+112\pm 35\,\text{cases}/\text{year}\), and a trend in the
+  corresponding irradiation of \(+329.9\pm 112\,\text{kJ}/\text{year}\).
+  The peak of the CE events was observed during May and June. CE events
+  with duration longer than 10\nobreakspace{}min are very rare
+  (\(<8\,\%\)), with exceptions lasting over an hour and up to 140
+  minutes. Finally, we have detected enhancements above the total solar
+  irradiance at the top of the atmosphere for the same solar zenith
+  angle of up to \(204\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of
+  the cases below \(40\,\text{W}/\text{m}^{2}\). Most of these extreme
+  events occur in spring -- early summer, with a secondary peak in
+  autumn.
   \end{abstract}
@@
  \end{frontmatter}
-
-\hypertarget{abstract}{%
-\section*{Abstract}\label{abstract}}
-\addcontentsline{toc}{section}{Abstract}
-
-\textbf{Abstract temporary placed here for technical reasons}
-
-In this study, we investigate the characteristics of global horizontal
-irradiance enhancement events induced by clouds over Thessaloniki for
-the period 1994 -- 2023 using data recorded every one minute. To our
-knowledge, there isn't a similar study with such a long time series. We
-identified the cloud enhancement (CE) events by creating an appropriate
-cloud-free irradiance reference using a radiative transfer model and
-aerosol optical depth data from a collocated Cimel sun photometer and a
-Brewer spectrophotometer. We found a trend in CE events of
-\(+112\pm 35\,\text{cases}/\text{year}\), and a trend in the
-corresponding irradiation of \(+329.9\pm 112\,\text{kJ}/\text{year}\).
-The peak of the CE events was observed during May and June. CE events
-with duration longer than 10\nobreakspace{}min are very rare
-(\(<8\,\%\)), with exceptions lasting over an hour and up to 140
-minutes. Finally, we have detected enhancements above the total solar
-irradiance at the top of the atmosphere for the same solar zenith angle
-of up to \(204\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the
-cases below \(40\,\text{W}/\text{m}^{2}\). Most of these extreme events
-occur in spring -- early summer, with a secondary peak in autumn.
 
@@
 an example scatter plot between the measured GHI and the modeled
-cloud-free irradiance for one year (2005), where the CE and ECE events
-are clearly grouped above the cloud-free irradiance (approximated with
-the green line). The grey colored data points above this line correspond
-to the ambiguous data points discussed above. Finally, the black belt
-just below the green line is formed from data measured mainly under
-cloud-free conditions,conditions with the spread likely caused by the
-short-term variability of AOD. A small fraction of these data
-corresponds also to cases with thin cirrus clouds causing weak
-attenuation of GHI, often indistinguishable from the attenuation by
-aerosols.
+cloud-free irradiance for year 2005, where the CE and ECE events are
+clearly grouped above the cloud-free irradiance (approximated with the
+green line). The gray colored data points above this line correspond to
+the ambiguous data points discussed above. Finally, the black belt just
+below the green line is formed from data measured mainly under
+cloud-free conditions, with the spread likely caused by the short-term
+variability of AOD. A small fraction of these data corresponds also to
+cases with thin cirrus clouds causing weak attenuation of GHI, often
+indistinguishable from the attenuation by aerosols.
 
@@
 The green line with blue symbols depicts the measured GHI in one-minute steps.
-The red line shows the modelled threshold for the detection of CE events, which are denoted with red circles.
+The red line shows the modeled threshold for the detection of CE events, which are denoted with gray circles.
 The black line represents the TOA TSI on a horizontal plane, equivalent to the threshold for the identification of ECE events, shown with red circles.
 The purple line is the modeled cloud-free irradiance.
-The dark yellow line is the solar constant of $1367\,\text{W}/\text{m}^{2}$.}\label{fig:example-day}
+The dark yellow line is the solar constant of $1367\,\text{W}/\text{m}^{2}$.
+The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.}\label{fig:example-day}
 \end{figure}
@@
 \caption{Example scatter plot of the measured GHI and the reference cloud-free irradiance in Thessaloniki for the year 2005.
-The over-irradiance for CE and ECE events is colour coded, while the remaining data points are shown in black.
-The reference green line goes through the origin with a slope of one.}\label{fig:example-year}
+The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.
+The reference green line goes through the origin with a slope of unity.}\label{fig:example-year}
 \end{figure}
@@
 Following the application of the above discussed methodology to the
-entire dataset (\(6\) million of one-minute GHI measurements),
+entire dataset (\(>6\) million of one-minute GHI measurements),
 \(2.32\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
@@
 above the cloud-free threshold was observed on 28~October 2016 at a SZA
-of \(59.2^\circ\) with a GHI value of \(861.8\,\text{W}/\text{m}^2\) and
-a OI of \(298.4\,\text{W}/\text{m}^2\). Both cases are also ECE events
-with \(131.2\,\text{W}/\text{m}^2\) and \(161.5\,\text{W}/\text{m}^2\)
-above the TSI at TOA for the same SZA, respectively. In the following
-sections we are discussing the long-term trends and variability of the
-CE events as well as of the corresponding OI and excess irradiation.
+of \(59.2^\circ\) with a GHI of \(861.8\,\text{W}/\text{m}^2\) and a OI
+of \(298.4\,\text{W}/\text{m}^2\). Both cases are also ECE events with
+\(131.2\,\text{W}/\text{m}^2\) and \(161.5\,\text{W}/\text{m}^2\) above
+the TSI at TOA for the same SZA, respectively. In the following sections
+we are discussing the long-term trends and variability of the CE events
+as well as of the corresponding OI and excess irradiation.
 
@@
 excess irradiation (\(+329.9 \pm 112\,\text{kJ}/\text{year}\)), while
-the the trend in the yearly mean OI is negligible
-(\(+0.11\pm 0.2\,\text{W}/\text{m}^2/\text{year}\)) and of no
-statistical significance. The average OI for the entire period is
+the trend in the yearly mean OI is negligible
+(\(+0.1\pm 0.2\,\text{W}/\text{m}^2/\text{year}\)) and of no statistical
+significance. The average OI for the entire period is
 \(+42.6\pm 2.8\,\text{W}/\text{m}^2\). The yearly excess irradiation due
@@
 significant variability in cloud patterns over the area, possibly
-associated to changes in climate.
+associated with changes in climate.
 
@@
 in the atmosphere. The incoming solar radiation in the region is not
-increased by the OI but is rather redistributed through the CE events.
-This is also depicted by the ECE irradiance values, which exceed the
-equivalent cloud-free irradiance by a significant amount.
+increased by the OI but is rather redistributed at the specific location
+as additional scattered radiation. This is also depicted by the ECE
+irradiance values, which exceed the equivalent cloud-free irradiance by
+a significant amount.
 
@@
 of cumulus clouds in the area leads to a significant increase in the CE
-events. However, the lack of detailed data in the area of cloud
-characteristics does not allow further analysis. Finally, the
-interannual variability of the monthly CE events is quite high as
-manifested by the size of the boxes and the large monthly extremes,
-especially in the summer. Investigation of the causes of this
-variability is beyond the scope of this study. It could possibly be
-related to the cloud cover variability in winter and autumn over
-southern Europe, associated with the North Atlantic Oscillation (NAO)
-circulation \citep{Chiacchio2010}, or to the observed decreasing trend
-in cloud cover as a result of global warming
-\citep[e.g.,][]{SanchezLorenzo2017}.
+events. However, the lack of detailed data on cloud characteristics in
+the area does not allow further analysis. Finally, the interannual
+variability of the monthly CE events is quite high as manifested by the
+size of the boxes and the large monthly extremes, especially in the
+summer. Investigation of the causes of this variability is beyond the
+scope of this study. It could possibly be related to the cloud cover
+variability in winter and autumn over southern Europe, associated with
+the North Atlantic Oscillation (NAO) circulation \citep{Chiacchio2010},
+or to the observed decreasing trend in cloud cover as a result of global
+warming \citep[e.g.,][]{SanchezLorenzo2017}.
 
@@
 exponential-like decline. This is expected, as the stronger the CE
-events are, the rarer the conditions favouring the occurrence of CE
+events are, the rarer the conditions favoring the occurrence of CE
 events. For the majority (over \(62\,\%\)) of the CE events the OI is
@@
 exposed to air masses coming mainly from the eastern Mediterranean,
-resulting in different cloud patterns, that may affect the
+resulting in different cloud patterns that may affect the
 characteristics and magnitude of the CE events.
@@
 conclude that although some groups of events last for more than an hour,
-about \(79\,\%\) have a duration of equal or less than 5 minutes.
+about \(79\,\%\) have a duration of equal or less than 5 minutes, likely
+due to the movements of clouds causing frequent blocking of the direct
+irradiance, which reduce the duration of the CE events.
 
@@
 Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE} the number
-of ECE events relative to the total number of one-min observations in
-each month. Judging by the distribution of the monthly medians, the most
-active months in ECE events are January -- March and November and the
-least active are July and August. The highest interannual variability in
-the 30-year record occurs from October to April. In the summer period,
-the fraction of ECE events is very small, with almost zero variability
-in July and August. Although the most active months for CE events are
-May and June
+of ECE events relative to the available number of one-min observations
+in each month. Judging by the distribution of the monthly medians, the
+most active months in ECE events are January -- March and November and
+the least active are July and August. The highest interannual
+variability in the 30-year record occurs from October to April. In the
+summer period, the fraction of ECE events is very small, with almost
+zero variability in July and August. Although the most active months for
+CE events are May and June
 (Figure\nobreakspace{}\ref{fig:relative-month-occurrences}), these
@@
 incapable to produce extreme events, possibly because of their size and
-structure, in conjunction with the smaller SZAs in the summer.
+structure, in conjunction with the smaller SZAs in the summer. In
+contrast, during winter the Sun is lower in the sky and clouds are
+frequently less dense allowing a large fraction of radiation to be
+scattered forward and enhance the irradiance at the surface. These
+conclusions are based on manual inspection of many sky-camera images
+during the summer and winter periods. An automated procedure of checking
+the sky-camera images for such events would greatly improve our ability
+to classify the CE and ECE events and help in the attribution of the
+causes of the events.
 
@@
 short-term variability of the expected cloud-free GHI, we were able to
-identify cases of CE events in Thessaloniki for the period 1994 -- 2023.
-After analyzing the CE cases, we found an increase of
-\(+112.1\pm 34.9\,\text{cases}/\text{year}\), with the mean annual
+identify cases of CE and ECE events in Thessaloniki for the period 1994
+-- 2023. After analyzing the CE cases, we found an increasing tendency
+of \(+112.1\pm 34.9\,\text{cases}/\text{year}\), with the mean annual
 irradiation of the CE events increasing with a rate of
@@
 
-We have observed ECE cases with GHI exceeding the TOA TSI on horizontal
-plane by more than \(200\,\text{W}/\text{m}^{2}\) while for \(75\,\%\)
-of the cases the excess irradiance (relative to TOA TSI on horizontal
-plane) is below \(40\,\text{W}/\text{m}^{2}\). The climatological
-characteristics of the ECE events showed that the most active months are
-spread over half of the year, and particularly in the periods March --
-June and September -- October. The magnitude of the ECE events
-identified in Thessaloniki events does not exceed the values reported
-for sites with more favourable conditions for the phenomenon
-\citep[e.g.,][]{Cordero2023}. Some of the characteristics of CE and ECE
-events we analyzed have strong similarities with the results of
-\citet{Vamvakas2020} for the city of Patras, south of Thessaloniki,
-albeit with differences in the magnitude of OI.
+We have observed ECE cases with GHI exceeding the TOA TSI on a
+horizontal plane by more than \(200\,\text{W}/\text{m}^{2}\) while for
+\(75\,\%\) of the cases the excess irradiance (relative to TOA TSI on a
+horizontal plane) is below \(40\,\text{W}/\text{m}^{2}\). The
+climatological characteristics of the ECE events showed that the most
+active months are spread over half of the year, and particularly in the
+months January -- March and November, while ECE events are practically
+absent in July and August. The magnitude of the ECE events identified in
+Thessaloniki does not exceed the values reported for sites with more
+favorable conditions for the phenomenon \citep[e.g.,][]{Cordero2023}.
+Some of the characteristics of CE and ECE events we analyzed have strong
+similarities with the results of \citet{Vamvakas2020} for the city of
+Patras, south of Thessaloniki, albeit with differences in the magnitude
+of OI.
 
-An interpretation of the CE trends shows that the interaction of GHI
-with the clouds, through this 30-year period, is a dynamic phenomenon
-that needs further investigation. For such studies, it would be
+The investigation of the CE trends in Thessaloniki through this 30-year
+period shows that the interaction of GHI with clouds is a complex
+phenomenon that merits further attention. For such studies, it would be
 essential to have more detailed information on cloud characteristics,
 especially in order to investigate possible associations of the observed
-trends with changes in climate.
+trends with changes in climate. Finally, automated procedures to analyze
+the sky-camera images would greatly improve our knowledge about the
+generation of these events.
 

### 2024-09-09 GHI_enh_05_distributions.R
Commit 2024-09-09 21:18

@@ -894,11 +894,9 @@ abline(v = date_A, col = "grey", lwd = 2, lty = 2)
 abline(v = date_B, col = "grey", lwd = 2, lty = 2)
 abline(v = date_C, col = "grey", lwd = 2, lty = 2)
 
-
 text(x = date_A, y = 250, "(a)", pos = 2, offset = 0.2, col = "gray", cex = 0.8)
 text(x = date_B, y = 250, "(b)", pos = 2, offset = 0.2, col = "gray", cex = 0.8)
 text(x = date_C, y = 250, "(c)", pos = 4, offset = 0.2, col = "gray", cex = 0.8)
-
 
 abline(h = solar_constant, col = "orange2", lty = 1, lwd = 2)
 
@@ -938,68 +936,8 @@ legend("bottom", ncol = 2,
 )
 
 
-
+## store base plot
 p1 <- recordPlot()
-
-
-
-# par(mar = c(4, 4, 1, 1))
-# # ylim <- range(0, temp$ETH, temp$wattGLB, na.rm = TRUE)
-# ylim <- range(0, temp$ETH, temp$wattGLB, solar_constant, na.rm = TRUE)
-#
-# plot(temp$Date, temp$wattGLB, col = "green",
-#      pch  = ".", cex = 2,
-#      ylim = ylim,
-#      ylab = bquote("GHI" ~ group("[", W/m^2,"]")),
-#      xlab = "Time (UTC)")
-#
-# ## mark photos
-# abline(v = date_A, col = "grey", lwd = 2, lty = 2)
-# abline(v = date_B, col = "grey", lwd = 2, lty = 2)
-#
-# text(x = date_A, y = 200, "(a)", pos = 2, offset = 0.4, col = "gray")
-# text(x = date_B, y = 200, "(b)", pos = 4, offset = 0.4, col = "gray")
-#
-#
-# abline(h = solar_constant, col = "orange2", lty = 1, lwd = 2)
-#
-# ## Global
-# lines(temp$Date, temp$wattGLB, col = "green")
-#
-# ## TSI on ground
-# lines(temp$Date, temp$ETH)
-#
-# ## Active model reference
-# lines(temp[, get(paste0(SelEnhanc, "_ref")), Date], col = "red" )
-#
-# ## Cloud-free ref
-# lines(temp[, get(paste0(csmodel,".glo")), Date], col = "darkorchid" )
-#
-#
-# ## Enchantment cases
[…]

### 2024-09-10 article/article.Rmd
Commit 2024-09-10 10:15

@@
 \end{equation}
-where $y$ is the date as a decimal fraction of the year.
-The resulting change in $\text{GHI}_\text{ref}$ ranges between $-1.88$ in 1994, a
-peak of $0.23\,\%$ in mid-2020 and $-0.19\,\%$ in the end of 2023. Finally, we
-applied these long-term changes of Equation\nobreakspace{}\ref{eq:AODchange} to the
-$\text{GHI}_\text{ref}$, to create a more realistic representation of
-the cloud-free irradiance for the entire period of study. For the period 1994 -- 1996
-where no AOD data are available, we assumed that the changes in GHI follow the same
-polynomial fit.
+where $y$ is the date as a decimal fraction of the year.  The resulting change in
+$\text{GHI}_\text{ref}$ ranges between $-1.88$ in 1994 and $-0.19\,\%$ in the end of
+2023, peaking at $0.23\,\%$ in the mid-2020. Finally, we applied these long-term
+changes of Equation\nobreakspace{}\ref{eq:AODchange} to the $\text{GHI}_\text{ref}$,
+to create a more realistic representation of the cloud-free irradiance for the entire
+period of study. For the period 1994 -- 1996 where no AOD data are available, we
+assumed that the changes in GHI follow the same polynomial fit.
 
@@
 very close to unity.  To achieve a robust and clear distinction of the CE cases, we
-applied on the $\text{GHI}_\text{ref}$ an additional offset of
+applied to the $\text{GHI}_\text{ref}$ an additional offset of
 $`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$.
@@
 equal or less than 5 minutes, likely due to the movements of clouds causing frequent
-blocking of the direct irradiance, which reduce the duration of the CE events.
+blockings of the direct irradiance, which reduce the duration of the CE events.
 

### 2024-09-10 article/article.tex
Commit 2024-09-10 10:15

@@
 year. The resulting change in \(\text{GHI}_\text{ref}\) ranges between
-\(-1.88\) in 1994, a peak of \(0.23\,\%\) in mid-2020 and \(-0.19\,\%\)
-in the end of 2023. Finally, we applied these long-term changes of
-Equation\nobreakspace{}\ref{eq:AODchange} to the
+\(-1.88\) in 1994 and \(-0.19\,\%\) in the end of 2023, peaking at
+\(0.23\,\%\) in the mid-2020. Finally, we applied these long-term
+changes of Equation\nobreakspace{}\ref{eq:AODchange} to the
 \(\text{GHI}_\text{ref}\), to create a more realistic representation of
@@
 \(18.4\,\text{W}/\text{m}^2\) and a slope very close to unity. To
-achieve a robust and clear distinction of the CE cases, we applied on
+achieve a robust and clear distinction of the CE cases, we applied to
 the \(\text{GHI}_\text{ref}\) an additional offset of
@@
 about \(79\,\%\) have a duration of equal or less than 5 minutes, likely
-due to the movements of clouds causing frequent blocking of the direct
+due to the movements of clouds causing frequent blockings of the direct
 irradiance, which reduce the duration of the CE events.

### 2024-09-10 GHI_enh_03_process.tex
Commit 2024-09-06 19:12
Commit 2024-09-08 20:14
Commit 2024-09-10 10:15

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-09-06}
+\date{2024-09-10}
 
@@
     Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
--72.8133 -27.4706   0.7675   0.4342  28.2501  83.4876 
+-72.8133 -27.4709   0.7683   0.4355  28.2523  83.4876 
 \end{verbatim}
@@
 variables_fl
+x
 xlim
@@
 \begin{verbatim}
-2024-09-06 10:16:28.4 athan@sagan GHI_enh_03_process.R 3.892410 mins
+2024-09-10 06:21:12.3 athan@sagan GHI_enh_03_process.R 4.336426 mins
 \end{verbatim}

### 2024-09-10 GHI_enh_04_investigate.tex
Commit 2024-09-07 19:12
Commit 2024-09-08 12:14
Commit 2024-09-08 20:14
Commit 2024-09-08 21:12
Commit 2024-09-08 22:14
Commit 2024-09-10 10:15
Commit 2024-09-10 11:09

@@
 \subsubsection{Group stats}\label{group-stats}}
+
+{[}1{]} 0
+Duration \textless{} 5 minutes 73.5 \%
+
+Duration \textless=5 minutes 79.3 \%
+
+Duration \textgreater{} 10 minutes 7.7 \%
+
+{[}1{]} 8
 
@@
 \begin{verbatim}
+The following object is masked from 'package:viridis':
+
+    viridis_pal
+\end{verbatim}
+
+\begin{verbatim}
 The following object is masked from 'package:purrr':
@@
     col_factor
-\end{verbatim}
-
-\begin{verbatim}
-The following object is masked from 'package:viridis':
-
-    viridis_pal
 \end{verbatim}
@@
 \begin{verbatim}
-Attaching package: 'ggpubr'
-\end{verbatim}
-
-\begin{verbatim}
-The following object is masked from 'package:cowplot':
-
-    get_legend
-\end{verbatim}
-
-\begin{verbatim}
-The following objects are masked from 'package:ggpp':
-
-    as_npc, as_npcx, as_npcy
-\end{verbatim}
-
-\begin{verbatim}
 Warning: Removed 364 rows containing non-finite outside the scale range (`stat_bin()`).
@@
 \end{figure}
+
+TableGrob (2 x 3) ``arrange'': 4 grobs
+z cells name grob
+1 1 (1-1,2-2) arrange gtable{[}layout{]}
+2 2 (1-1,3-3) arrange gtable{[}layout{]}
+3 3 (2-2,2-3) arrange text{[}GRID.text.696{]}
+4 4 (1-2,1-1) arrange text{[}GRID.text.694{]}
+TableGrob (2 x 3) ``arrange'': 4 grobs
+z cells name grob
+1 1 (1-1,2-2) arrange gtable{[}layout{]}
+2 2 (1-1,3-3) arrange gtable{[}layout{]}
+3 3 (2-2,2-3) arrange text{[}GRID.text.696{]}
+4 4 (1-2,1-1) arrange text{[}GRID.text.694{]}
 
@@
 \begin{verbatim}
-2024-09-06 10:26:49.9 athan@sagan GHI_enh_04_investigate.R 10.084896 mins
+2024-09-10 07:46:40.3 athan@sagan GHI_enh_04_investigate.R 1.579120 mins
 \end{verbatim}

### 2024-09-10 GHI_enh_03_process.tex
Commit 2024-09-10 12:14

@@
 Energy_Div
+gg_text_size
 I1_longterm
@@
 \begin{verbatim}
-2024-09-10 06:21:12.3 athan@sagan GHI_enh_03_process.R 4.336426 mins
+2024-09-10 08:57:18.4 athan@sagan GHI_enh_03_process.R 5.001571 mins
 \end{verbatim}

### 2024-09-10 GHI_enh_05_distributions.R

@@ -993,7 +993,7 @@ pp1 <- ggplot(data = temp, aes(x = Date)) +
              aes(y =  wattGLB, colour = "ECE events"),        shape = 1, size = 1.6          ) +
   ## legend
   scale_colour_manual("",
-                      guide = guide_legend(ncol = 2),
+                      guide = guide_legend(ncol = 1),
                       breaks = c("GHI",
                                  "Cloud-free",
                                  "CE Threshold",
@@ -1018,8 +1018,8 @@ pp1 <- ggplot(data = temp, aes(x = Date)) +
     legend.justification  = c("right", "bottom"),
     # legend.box.just       = "right",
     legend.background     = element_blank(),
-    legend.spacing.y = unit(0, 'cm'),
-    legend.spacing.x = unit(.005, 'cm'),
+    # legend.spacing.y = unit(0, 'cm'),
+    # legend.spacing.x = unit(.005, 'cm'),
     legend.box.background = element_rect(color = NA, fill = NA),
     legend.key            = element_blank(),
     legend.margin         = margin(1, 1, 1, 1) ) +
@@ -1032,9 +1032,19 @@ pp1 <- ggplot(data = temp, aes(x = Date)) +
 pp1
 
 
+pp1 + theme(legend.key.size = unit(.9, "lines"))
+
+pp1 + theme(legend.title = element_text(size = 10),
+            legend.text  = element_text(size = 10),
+            legend.key.size = unit(.9, "lines"))
+
+
+pp2 <- pp1 + theme(legend.position = "bottom",
+                   legend.key.size = unit(.5, "lines"))
+
 
 merg <- plot_grid(
-  pp1, bt,
+  pp2, bt,
   nrow = 2,
   rel_heights = c(3,1)
 )
@@ -1043,24 +1053,39 @@ print(merg)
 
 merg + theme(aspect.ratio = 1)
 
-
-
-calc_element(
-  "axis.text.x.bottom",
-  ggplot2:::plot_theme(ggplot_build(pp1)$plot)
-)$size
-
-calc_element(
-  "text",
-  ggplot2:::plot_theme(ggplot_build(pp1)$plot)
-)$size
+merg + theme(aspect.ratio = 0.8)
 
 
 
+## seperate legend
+
+
+legend <- get_legend(pp1)
[…]

### 2024-09-10 article/article.Rmd
Commit 2024-09-10 12:14

@@
   irradiance enhancement events induced by clouds over Thessaloniki for
-  the period 1994 -- 2023 using data recorded every one minute. To our
-  knowledge, there isn't a similar study with such a long time series. We
+  the period 1994 -- 2023 using data recorded every one minute. We
   identified the cloud enhancement (CE) events by creating an appropriate
@@
   corresponding irradiation of \(+329.9\pm 112\,\text{kJ}/\text{year}\).
+  To our knowledge, such long-term changes in CE events have not been presented in the past.
   The peak of the CE events was observed during May and June. CE events
@@
 
-biblio-style:   elsarticle-num-names # elsarticle-harv author year style for natbib - use 'elsarticle-num' or 'elsarticle-num-names' for numbered scheme
+biblio-style:   elsarticle-harv # elsarticle-harv author year style for natbib - use 'elsarticle-num' or 'elsarticle-num-names' for numbered scheme
+# biblio-style:   elsarticle-num-names # elsarticle-harv author year style for natbib - use 'elsarticle-num' or 'elsarticle-num-names' for numbered scheme
 
@@
 enhancement events induced by clouds over Thessaloniki for the period 1994 -- 2023
-using data recorded every one minute.  To our knowledge, there isn't a similar study
-with such a long time series.  We identified the cloud enhancement (CE) events by
+using data recorded every one minute. We identified the cloud enhancement (CE) events by
 creating an appropriate cloud-free irradiance reference using a radiative transfer
@@
 `r round(2*yearlyCE[var=="GLB_diff.sum",slope.sd],1)`\,\text{kJ}/\text{year}$.
+To our knowledge, such long-term changes in CE events have not been presented in the past.
 The peak of the CE events was observed during May and June. CE events with duration

### 2024-09-10 article/article.tex
Commit 2024-09-10 12:14

@@
 \usepackage[]{natbib}
-\bibliographystyle{elsarticle-num-names}
+\bibliographystyle{elsarticle-harv}
 
@@
   irradiance enhancement events induced by clouds over Thessaloniki for
-  the period 1994 -- 2023 using data recorded every one minute. To our
-  knowledge, there isn't a similar study with such a long time series.
-  We identified the cloud enhancement (CE) events by creating an
+  the period 1994 -- 2023 using data recorded every one minute. We
+  identified the cloud enhancement (CE) events by creating an
   appropriate cloud-free irradiance reference using a radiative transfer
@@
   corresponding irradiation of \(+329.9\pm 112\,\text{kJ}/\text{year}\).
-  The peak of the CE events was observed during May and June. CE events
-  with duration longer than 10\nobreakspace{}min are very rare
-  (\(<8\,\%\)), with exceptions lasting over an hour and up to 140
-  minutes. Finally, we have detected enhancements above the total solar
-  irradiance at the top of the atmosphere for the same solar zenith
-  angle of up to \(204\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of
-  the cases below \(40\,\text{W}/\text{m}^{2}\). Most of these extreme
-  events occur in spring -- early summer, with a secondary peak in
-  autumn.
+  To our knowledge, such long-term changes in CE events have not been
+  presented in the past. The peak of the CE events was observed during
+  May and June. CE events with duration longer than 10\nobreakspace{}min
+  are very rare (\(<8\,\%\)), with exceptions lasting over an hour and
+  up to 140 minutes. Finally, we have detected enhancements above the
+  total solar irradiance at the top of the atmosphere for the same solar
+  zenith angle of up to \(204\,\text{W}/\text{m}^{2}\), with the
+  \(75\,\%\) of the cases below \(40\,\text{W}/\text{m}^{2}\). Most of
+  these extreme events occur in spring -- early summer, with a secondary
+  peak in autumn.
   \end{abstract}

### 2024-09-10 article/article.Rmd
Commit 2024-09-10 13:11

@@
 
+```{r  echo=FALSE, fig.cap="Example of Colar constant of $1367\\,\\text{W}/\\text{m}^{2}$.
+The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.", fig.pos='H'}
+knitr::include_graphics("../images/P-example-day-12.png")
+```
 <!-- END -->

### 2024-09-10 GHI_enh_05_distributions.R

@@ -1042,6 +1042,12 @@ pp1 + theme(legend.title = element_text(size = 10),
 pp2 <- pp1 + theme(legend.position = "bottom",
                    legend.key.size = unit(.5, "lines"))
 
+pp2 <- pp1 + theme(legend.position       = c(1, .5),
+                   legend.title          = element_blank(),
+                   legend.text           = element_text(size = 14),
+                   legend.justification  = c("right", "center"),
+                   legend.key.size       = unit(.5, "lines"))
+
 
 merg <- plot_grid(
   pp2, bt,
@@ -1058,21 +1064,37 @@ merg + theme(aspect.ratio = 0.8)
 
 
 ## seperate legend
+# theme(legend.box.margin = margin(0, 0, 0, 12))
+
+legend <- get_legend(pp2)
+# legend <- legend + theme(guide = guide_legend(ncol = 1))
 
 
-legend <- get_legend(pp1)
-legend <- legend + theme(guide = guide_legend(ncol = 1))
+
+prow <- plot_grid(
+  A,
+  B,
+  C,
+  legend,
+  nrow = 1,
+  rel_widths = c(1,1,1, 1.5)
+)
+# prow
 
 
 
-bt     <- grid.arrange(A, B, C, legend, nrow = 1)
 mergln <- plot_grid(
   pp2 + theme(legend.position="none"),
-  bt,
+  prow,
   nrow = 2,
-  rel_heights = c(3,1)
+  rel_heights = c(3,1.5)
 )
+show(mergln)
 
+
+mergln + theme(aspect.ratio = 1)
+
+mergln + theme(aspect.ratio = 0.8)
 
 
 

### 2024-09-10 article/article.tex
Commit 2024-09-10 13:11
Commit 2024-09-10 18:14

@@
 
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{../images/P-example-day-3}
+
+}
+
+\caption{Example of Colar constant of $1367\,\text{W}/\text{m}^{2}$.
+The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.}\label{fig:unnamed-chunk-1}
+\end{figure}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{../images/P-example-day-4}
+
+}
+
+\caption{Example of Colar constant of $1367\,\text{W}/\text{m}^{2}$.
+The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.}\label{fig:unnamed-chunk-2}
+\end{figure}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{../images/P-example-day-5}
+
+}
+
+\caption{Example of Colar constant of $1367\,\text{W}/\text{m}^{2}$.
+The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.}\label{fig:unnamed-chunk-3}
+\end{figure}
+
 \bibliography{bibliography.bib}

### 2024-09-10 article/article.Rmd
Commit 2024-09-10 18:14

--- 2024-09-10 article/article.Rmd
@@
 
+```{r  echo=FALSE, fig.cap="Example of Colar constant of $1367\\,\\text{W}/\\text{m}^{2}$.
+The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.", fig.pos='H'}
+knitr::include_graphics("../images/P-example-day-3.png")
+```
+
+```{r  echo=FALSE, fig.cap="Example of Colar constant of $1367\\,\\text{W}/\\text{m}^{2}$.
+The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.", fig.pos='H'}
+knitr::include_graphics("../images/P-example-day-4.png")
+```
+
+```{r  echo=FALSE, fig.cap="Example of Colar constant of $1367\\,\\text{W}/\\text{m}^{2}$.
+The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.", fig.pos='H'}
+knitr::include_graphics("../images/P-example-day-5.png")
+```
 <!-- END -->

### 2024-09-10 article/article.tex
Commit 2024-09-10 19:11

--- 2024-09-10 article/article.tex
@@
 
-{\centering \includegraphics[width=1\linewidth]{../images/P-example-day-5}
+{\centering \includegraphics[width=1\linewidth]{../images/P-example-day-3}
 
@@
 The green line with blue symbols depicts the measured GHI in one-minute steps.
-The red line shows the modeled threshold for the detection of CE events, which are denoted with gray circles.
-The black line represents the TOA TSI on a horizontal plane, equivalent to the threshold for the identification of ECE events, shown with red circles.
+The red line shows the modeled threshold for the detection of CE events, which are denoted with red circles.
+The black line represents the TOA TSI on a horizontal plane, equivalent to the threshold for the identification of ECE events, shown with magenta circles.
 The purple line is the modeled cloud-free irradiance.
 The dark yellow line is the solar constant of $1367\,\text{W}/\text{m}^{2}$.
-The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.}\label{fig:example-day}
+The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical orange dashed lines.}\label{fig:example-day}
 \end{figure}

### 2024-09-10 article/article.Rmd
Commit 2024-09-10 19:11

--- 2024-09-10 article/article.Rmd
@@
 The green line with blue symbols depicts the measured GHI in one-minute steps.
-The red line shows the modeled threshold for the detection of CE events, which are denoted with gray circles.
-The black line represents the TOA TSI on a horizontal plane, equivalent to the threshold for the identification of ECE events, shown with red circles.
+The red line shows the modeled threshold for the detection of CE events, which are denoted with red circles.
+The black line represents the TOA TSI on a horizontal plane, equivalent to the threshold for the identification of ECE events, shown with magenta circles.
 The purple line is the modeled cloud-free irradiance.
 The dark yellow line is the solar constant of $1367\\,\\text{W}/\\text{m}^{2}$.
-The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.", fig.pos='H'}
-knitr::include_graphics("../images/P-example-day-5.png")
+The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical orange dashed lines.", fig.pos='H'}
+knitr::include_graphics("../images/P-example-day-3.png")
 ```

### 2024-09-10 GHI_enh_05_distributions.R

@@ -25,7 +25,7 @@
 #'   bookdown::pdf_document2:
 #'     number_sections: no
 #'     fig_caption:     yes
-#'     keep_tex:        yes
+#'     keep_tex:        no
 #'     latex_engine:    xelatex
 #'     toc:             yes
 #'     toc_depth:       4
@@ -970,7 +970,7 @@ pp1 <- ggplot(data = temp, aes(x = Date)) +
   annotate(geom = "text", x = date_A - 300, y = 100, label = "(a)", hjust = 1, color = "#ff652d") +
   geom_vline(aes(xintercept = date_B), linetype = "longdash", linewidth = .6, color = "#ff652d") +
   annotate(geom = "text", x = date_B - 300, y = 100, label = "(b)", hjust = 1, color = "#ff652d") +
-  geom_vline(aes(xintercept = date_C, color = "Sky camera photo"), linetype = "longdash", linewidth = .6) +
+  geom_vline(aes(xintercept = date_C, color = "Sky camera photos"), linetype = "longdash", linewidth = .6) +
   annotate(geom = "text", x = date_C + 300, y = 100, label = "(c)", hjust = 0, color = "#ff652d") +
   ## data points
   geom_point(data = temp[TYPE == "Cloud"],
@@ -990,7 +990,7 @@ pp1 <- ggplot(data = temp, aes(x = Date)) +
                                  "CE events",
                                  "ECE events",
                                  "Identified clouds",
-                                 "Sky camera photo"),
+                                 "Sky camera photos"),
                       values = c("GHI"                     = "#317529",
                                  "CE Threshold"            = "#b00821" ,
                                  "TOA TSI on horiz. plane" = "black",
@@ -999,7 +999,7 @@ pp1 <- ggplot(data = temp, aes(x = Date)) +
                                  "ECE events"              = "#ff00ff",
                                  "Solar Constant"          = "orange2",
                                  "Cloud-free"              = "darkorchid",
-                                 "Sky camera photo"        = "#ff652d")) +
+                                 "Sky camera photos"       = "#ff652d")) +
   # guides(fill = guide_legend(ncol = 2)) +
 
   labs(title = paste(as.Date(example_day, origin = "1970-01-01"))) +
@@ -1076,15 +1076,14 @@ mergln <- plot_grid(
   pp2 + theme(legend.position = "none"),
[…]

### 2024-09-11 GHI_enh_04_investigate.tex
Commit 2024-09-10 12:14
Commit 2024-09-10 22:14
Commit 2024-09-11 09:08

@@
 \author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
-\date{2024-09-10}
+\date{2024-09-11}
 
@@
 \end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-multi-1}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-energy-complete-multi-1}
+\end{figure}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-4}
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-multi-2}
 
@@
 
-\caption{ - empty caption - }\label{fig:P-energy-complete-4}
+\caption{ - empty caption - }\label{fig:P-energy-complete-multi-2}
 \end{figure}
@@
 \begin{verbatim}
-2024-09-10 07:46:40.3 athan@sagan GHI_enh_04_investigate.R 1.579120 mins
+2024-09-11 05:57:13.1 athan@sagan GHI_enh_04_investigate.R 1.539943 mins
 \end{verbatim}

### 2024-09-11 article/article.tex
Commit 2024-09-11 09:08

@@
         }
-    \caption{Time series of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation at Thessaloniki for the period 1994 – 2023.
+    \caption{Time-series of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation at Thessaloniki for the period 1994 – 2023.
 The black lines represent the linear trends on the yearly data.}\label{fig:P-energy}

### 2024-09-11 article/article.Rmd
Commit 2024-09-11 10:14

@@
 
+<!--
 \begin{figure}% [h!]
@@
         }
-    \caption{Time series of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation at Thessaloniki for the period 1994 – 2023.
+    \caption{Time-series of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation at Thessaloniki for the period 1994 – 2023.
 The black lines represent the linear trends on the yearly data.}\label{fig:P-energy}
 \end{figure}
+-->
+
+```{r P-energy, echo=FALSE, fig.cap="Time-series of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation at Thessaloniki for the period 1994 – 2023.
+The black lines represent the linear trends on the yearly data."}
+knitr::include_graphics("../images/P-energy-complete-multi-3.png")
+```
 
@@
 ```{r group-2d, echo=FALSE, fig.cap="Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1994 -- 2023.
-The logarithmic color scale denotes the frequency of the respective groups."}
+The logarithmic color scale denotes the frequency of the respective groups.
+Note that 19 pints with duration higher than 60 min are not shown."}
 knitr::include_graphics("../images/P-groups-bin2d-1.png")
@@
 
+# Data availability {.unnumbered}
+
 <!-- END -->

### 2024-09-11 article/article.tex
Commit 2024-09-11 10:14

@@
 
-\begin{figure}% [h!]
-        {\centering
-            \subfloat[\label{fig:P-energy-N}]
-                {\includegraphics[width=\linewidth]{../images/P-energy-complete-2} }\\
-            \subfloat[\label{fig:P-energy-mean}]
-                {\includegraphics[width=\linewidth]{../images/P-energy-complete-3} }\\
-            \subfloat[\label{fig:P-energy-sum}]
-                {\includegraphics[width=\linewidth]{../images/P-energy-complete-1} }
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../images/P-energy-complete-multi-3}
+
 }
+
 \caption{Time-series of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation at Thessaloniki for the period 1994 – 2023.
@@
 \caption{Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1994 -- 2023.
-The logarithmic color scale denotes the frequency of the respective groups.}\label{fig:group-2d}
+The logarithmic color scale denotes the frequency of the respective groups.
+Note that 19 pints with duration higher than 60 min are not shown.}\label{fig:group-2d}
 \end{figure}
@@
 
+\hypertarget{data-availability}{%
+\section*{Data availability}\label{data-availability}}
+\addcontentsline{toc}{section}{Data availability}
+
 \bibliography{bibliography.bib}

### 2024-09-11 GHI_enh_04_investigate.tex
Commit 2024-09-11 10:14

@@
 
-lmY: 109.4004 +/- 12.63018
+lmY: 108.9825 +/- 13.53098
 
@@
 \end{figure}
-
-lmY: 0.10318 +/- 0.067313
-
 \begin{figure}[H]
@@
 \caption{ - empty caption - }\label{fig:P-energy-complete-multi-2}
+\end{figure}
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-multi-3}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-energy-complete-multi-3}
+\end{figure}
+
+lmY: 0.10318 +/- 0.067313
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-multi-4}
+
+}
+
+\caption{ - empty caption - }\label{fig:P-energy-complete-multi-4}
 \end{figure}
@@
 \begin{verbatim}
-2024-09-11 05:57:13.1 athan@sagan GHI_enh_04_investigate.R 1.539943 mins
+2024-09-11 07:08:04.1 athan@sagan GHI_enh_04_investigate.R 1.522287 mins
 \end{verbatim}

### 2024-09-11 GHI_enh_04_investigate.R

@@ -969,8 +969,8 @@ ggplot(data    = ST_G0,
                      minor_breaks = seq(0, 500, by = 25)) +
   scale_x_continuous(guide        = "axis_minor",
                      minor_breaks = seq(0, 500, by = 10)) +
-  labs(caption = paste("Removed", ST_G0[GLB_ench.N > lim_dur, .N],
-                       "points with duration >", lim_dur, "minutes.")) +
+  # labs(caption = paste("Removed", ST_G0[GLB_ench.N > lim_dur, .N],
+  #                      "points with duration >", lim_dur, "minutes.")) +
   xlim(-1, lim_dur)
 
 
@@ -990,8 +990,8 @@ ggplot(data    = ST_G0,
                      minor_breaks = seq(0, 500, by = 25)) +
   scale_x_continuous(guide        = "axis_minor",
                      minor_breaks = seq(0, 500, by = 10)) +
-  labs(caption = paste("Removed", ST_G0[GLB_ench.N > lim_dur, .N],
-                       "points with duration >", lim_dur, "minutes.")) +
+  # labs(caption = paste("Removed", ST_G0[GLB_ench.N > lim_dur, .N],
+  #                      "points with duration >", lim_dur, "minutes.")) +
   xlim(-1, lim_dur)
 
 
@@ -1013,8 +1013,8 @@ ggplot(data    = ST_G0,
                      minor_breaks = seq(0, 500, by = 25)) +
   scale_x_continuous(guide        = "axis_minor",
                      minor_breaks = seq(0, 500, by = 10)) +
-  labs(caption = paste("Removed", ST_G0[GLB_ench.N > lim_dur, .N],
-                       "points with duration >", lim_dur, "minutes.")) +
+  # labs(caption = paste("Removed", ST_G0[GLB_ench.N > lim_dur, .N],
+  #                      "points with duration >", lim_dur, "minutes.")) +
   xlim(-1, lim_dur)
 
 
@@ -1036,8 +1036,8 @@ ggplot(data    = ST_G0[GLB_ench.N > 1,],
                      minor_breaks = seq(0, 500, by = 25)) +
   scale_x_continuous(guide        = "axis_minor",
                      minor_breaks = seq(0, 500, by = 10)) +
-  labs(caption = paste("Removed", ST_G0[GLB_ench.N > lim_dur, .N],
[…]

### 2024-09-11 SUBMISSION_02/article/article.tex
Commit 2024-09-11 12:14

--- 2024-09-11 article/article.tex
@@
 
-\hypertarget{data-availability}{%
-\section*{Data availability}\label{data-availability}}
-\addcontentsline{toc}{section}{Data availability}
+\hypertarget{reproducibility}{%
+\section*{Reproducibility}\label{reproducibility}}
+\addcontentsline{toc}{section}{Reproducibility}
+
+The GHI data are available as hourly values in the WMO World Radiation
+Data Center\footnote{\url{http://wrdc.mgo.rssi.ru}}.The relevant source
+code is available in three repositories for (a) the preparation of GHI
+data \citep{natsis_2024_13744467} (b) the detection of clouds
+\citep{thanasis_n_2024_13744460} and (c) the processes for this
+manuscript \citep{thanasis_n_2024_13744472}.
 

### 2024-09-11 article/article.Rmd
Commit 2024-09-11 11:08
Commit 2024-09-11 12:14

@@
 
-# Data availability {.unnumbered}
+# Reproducibility {.unnumbered}
+
+The GHI data are available as hourly values in the WMO World Radiation Data Center[^1].The relevant source code is available in three repositories for
+(a) the preparation of GHI data [@natsis_2024_13744467]
+(b) the detection of clouds [@thanasis_n_2024_13744460] and
+(c) the processes for this manuscript [@thanasis_n_2024_13744472].
+
+[^1]: [http://wrdc.mgo.rssi.ru](http://wrdc.mgo.rssi.ru)
 

### 2024-09-12 article/article.Rmd
Commit 2024-09-12 13:11

@@
 ```{r CLB-daily, echo=FALSE, fig.cap="Time-series of daily mean GHI measured at Thessaloniki for the period 1994 -- 2023."}
-knitr::include_graphics("../images/P_daily_trend-5.png")
+knitr::include_graphics("../images/P_daily_trend-5.pdf")
 ```
@@
 ```{r CS-change, echo=FALSE, fig.cap="Simulated long-term change in cloud-free irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1994 -- 2023."}
-knitr::include_graphics("../images/P-CS-change-1.png")
+knitr::include_graphics("../images/P-CS-change-1.pdf")
 ```
@@
 The linear regression on the data is also shown on the figure with the blue line.", fig.pos='H'}
-knitr::include_graphics("../images/P-validation-cloudfree-GHI-1.png")
+knitr::include_graphics("../images/P-validation-cloudfree-GHI-1.pdf")
 ```
@@
 The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical orange dashed lines.", fig.pos='H'}
-knitr::include_graphics("../images/P-example-day-3.png")
+knitr::include_graphics("../images/P-example-day-3.pdf")
 ```
@@
 The reference green line goes through the origin with a slope of unity.", fig.pos='H'}
-knitr::include_graphics("../images/P-example-years-12.png")
+knitr::include_graphics("../images/P-example-years-12.pdf")
 ```
@@
 The black lines represent the linear trends on the yearly data."}
-knitr::include_graphics("../images/P-energy-complete-multi-3.png")
+knitr::include_graphics("../images/P-energy-complete-multi-3.pdf")
 ```
@@
 The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
-knitr::include_graphics("../images/P-CE-climatology-normlz-1.png")
+knitr::include_graphics("../images/P-CE-climatology-normlz-1.pdf")
 ```
@@
 The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
-knitr::include_graphics("../images/clim-CE-month-norm-MAX-median-N-MW-1.png")
+knitr::include_graphics("../images/clim-CE-month-norm-MAX-median-N-MW-1.pdf")
 ```
@@
 The histogram was split in two plots with different y-axis scales for better readability."}
-knitr::include_graphics("../images/P-relative-distribution-diff-2.png")
+knitr::include_graphics("../images/P-relative-distribution-diff-2.pdf")
 ```
@@
 The histogram was split in two plots with different y-axis scales for better readability."}
-# knitr::include_graphics("../images/groups-1.png")
-knitr::include_graphics("../images/groups-7.png")
+# knitr::include_graphics("../images/groups-1.pdf")
+knitr::include_graphics("../images/groups-7.pdf")
 ```
@@
 Note that 19 pints with duration higher than 60 min are not shown."}
-knitr::include_graphics("../images/P-groups-bin2d-1.png")
+knitr::include_graphics("../images/P-groups-bin2d-1.pdf")
 ```
@@
 The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
-knitr::include_graphics("../images/P-ECE-climatology-normlz-1.png")
+knitr::include_graphics("../images/P-ECE-climatology-normlz-1.pdf")
 ```
@@
 The vertical lines (whiskers) extend between the maximum and minimum monthly values."}
-knitr::include_graphics("../images/clim-ECE-month-norm-MAX-median-N-2.png")
+knitr::include_graphics("../images/clim-ECE-month-norm-MAX-median-N-2.pdf")
 ```
@@
 ```{r P-extreme-distribution, echo=FALSE, fig.cap="Relative frequency distribution of ECE events, in Thessaloniki for the period 1994 -- 2023, as a function of the extra irradiance over TSI at TOA for the same SZA."}
-knitr::include_graphics("../images/P-extreme-distribution-2.png")
+knitr::include_graphics("../images/P-extreme-distribution-2.pdf")
 ```

### 2024-09-19 article/article.Rmd
Commit 2024-09-19 11:10

@@
 manual screening was aided by a radiation data quality assurance procedure, adjusted
-for the site, which was based on the methods of Long and Shi\ [@Long2006;
-@Long2008a].  Thus, problematic recordings have been excluded from further
+for the site, which was based on the methods of Long and Shi\ [-@Long2006;
+-@Long2008a].  Thus, problematic recordings have been excluded from further
 processing.  Furthermore, due to the significant measurement uncertainty in GHI when

### 2024-09-19 article/article.Rmd
Commit 2024-09-19 12:14
Commit 2024-09-19 19:08

@@
 \end{equation}
-where $y$ is the date as a decimal fraction of the year.  The resulting change in
+where $x$ is the date as a decimal fraction of the year.  The resulting change in
 $\text{GHI}_\text{ref}$ ranges between $-1.88$ in 1994 and $-0.19\,\%$ in the end of
@@
 The logarithmic color scale denotes the frequency of the respective groups.
-Note that 19 pints with duration higher than 60 min are not shown."}
+Note that 19 points of groups with duration higher than 60 min are not shown."}
 knitr::include_graphics("../images/P-groups-bin2d-1.pdf")

### 2024-10-07 article/article.Rmd
Commit 2024-10-07 09:12

@@
 \begin{equation}
-\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot x + -0.002981 \cdot x^2 \label{eq:AODchange}
+\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot x -0.002981 \cdot x^2 \label{eq:AODchange}
 \end{equation}
 where $x$ is the date as a decimal fraction of the year.  The resulting change in
-$\text{GHI}_\text{ref}$ ranges between $-1.88$ in 1994 and $-0.19\,\%$ in the end of
+$\text{GHI}_\text{ref}$ ranges between $-1.88\,\%$ in 1994 and $-0.19\,\%$ in the end of
 2023, peaking at $0.23\,\%$ in the mid-2020. Finally, we applied these long-term
@@
 achieving this goal is to define a threshold for the CE identification,
-representative of the cloud-free irradiance at the time of each GHI measurement. This
-depends on the selection of the appropriate atmospheric parameterization for the RTM
-simulations. The implementation of the long-term changes in GHI due to AOD, discussed
-in section\nobreakspace{}\ref{rtmcs}, allows capturing a large part of the natural
-variability of cloud-free GHI. However, the short-term variability of AOD cannot be
-taken adequately into account when using monthly values in the model simulations. We
-tried different approaches to strengthen the robustness of the methodology and to
-compensate for the limited accuracy of the RTM input data and the unpredictable
-natural variability of the atmosphere.
+representative of the cloud-free irradiance at the time of each GHI measurement.
+This depends on the selection of the appropriate values of the input parameters for
+the RTM simulations.  The implementation of the long-term changes in GHI due to AOD,
+discussed in section\nobreakspace{}\ref{rtmcs}, allows capturing a large part of the
+natural variability of cloud-free GHI. However, the short-term variability of AOD
+cannot be taken adequately into account when using monthly values in the model
+simulations. We tried different approaches to strengthen the robustness of the
+methodology and to compensate for the limited accuracy of the RTM input data and the
+unpredictable natural variability of the atmosphere.
 

### 2024-10-07 article/article.tex
Commit 2024-09-11 11:08
Commit 2024-10-07 09:12

@@
 radiation data quality assurance procedure, adjusted for the site, which
-was based on the methods of Long and Shi~\citep{Long2006, Long2008a}.
-Thus, problematic recordings have been excluded from further processing.
+was based on the methods of Long and
+Shi~\citetext{\citeyear{Long2006}; \citeyear{Long2008a}}. Thus,
+problematic recordings have been excluded from further processing.
 Furthermore, due to the significant measurement uncertainty in GHI when
@@
 derive the long-term change in GHI due to aerosols: \begin{equation}
-\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot x + -0.002981 \cdot x^2 \label{eq:AODchange}
-\end{equation} where \(y\) is the date as a decimal fraction of the
+\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot x -0.002981 \cdot x^2 \label{eq:AODchange}
+\end{equation} where \(x\) is the date as a decimal fraction of the
 year. The resulting change in \(\text{GHI}_\text{ref}\) ranges between
-\(-1.88\) in 1994 and \(-0.19\,\%\) in the end of 2023, peaking at
+\(-1.88\,\%\) in 1994 and \(-0.19\,\%\) in the end of 2023, peaking at
 \(0.23\,\%\) in the mid-2020. Finally, we applied these long-term
@@
 of each GHI measurement. This depends on the selection of the
-appropriate atmospheric parameterization for the RTM simulations. The
+appropriate values of the input parameters for the RTM simulations. The
 implementation of the long-term changes in GHI due to AOD, discussed in
@@
 The logarithmic color scale denotes the frequency of the respective groups.
-Note that 19 pints with duration higher than 60 min are not shown.}\label{fig:group-2d}
+Note that 19 points of groups with duration higher than 60 min are not shown.}\label{fig:group-2d}
 \end{figure}

### 2024-10-07 article/article.Rmd
Commit 2024-10-07 11:09

@@
   \(+112\pm 35\,\text{cases}/\text{year}\), and a trend in the
-  corresponding irradiation of \(+329.9\pm 112\,\text{kJ}/\text{year}\).
+  corresponding irradiation of \(+329.9\pm 112.0\,\text{kJ}/\text{year}\).
   To our knowledge, such long-term changes in CE events have not been presented in the past.
@@
 and a trend in the corresponding irradiation of
-$`r plus_sign(round(yearlyCE[var=="GLB_diff.sum",slope],1))`\pm
-`r round(2*yearlyCE[var=="GLB_diff.sum",slope.sd],1)`\,\text{kJ}/\text{year}$.
+$`r plus_sign(format(round(yearlyCE[var=="GLB_diff.sum",slope],1),nsmall=1))`\pm `r format(round(2*yearlyCE[var=="GLB_diff.sum",slope.sd],1),nsmall=1)`\,\text{kJ}/\text{year}$.
 To our knowledge, such long-term changes in CE events have not been presented in the past.
@@
 and the excess irradiation
-($`r plus_sign(round(yearlyCE[var == "GLB_diff.sum", slope], 1))` \pm `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$),
+($`r plus_sign(format(round(yearlyCE[var=="GLB_diff.sum",slope],1),nsmall=1))`\pm `r format(round(2*yearlyCE[var=="GLB_diff.sum",slope.sd],1),nsmall=1)`\,\text{kJ}/\text{year}$),
 while the trend in the yearly mean OI is negligible
@@
 with the mean annual irradiation of the CE events increasing with a rate of
-$`r plus_sign(round(yearlyCE[var == "GLB_diff.sum", slope], 1))`\pm `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$.
+$`r plus_sign(format(round(yearlyCE[var=="GLB_diff.sum",slope],1),nsmall=1))`\pm `r format(round(2*yearlyCE[var=="GLB_diff.sum",slope.sd],1),nsmall=1)`\,\text{kJ}/\text{year}$.
 The most active months of CE events are May and June.  We found that continuous CE

### 2024-10-07 article/article.tex
Commit 2024-10-07 11:09

@@
   events of \(+112\pm 35\,\text{cases}/\text{year}\), and a trend in the
-  corresponding irradiation of \(+329.9\pm 112\,\text{kJ}/\text{year}\).
-  To our knowledge, such long-term changes in CE events have not been
-  presented in the past. The peak of the CE events was observed during
-  May and June. CE events with duration longer than 10\nobreakspace{}min
-  are very rare (\(<8\,\%\)), with exceptions lasting over an hour and
-  up to 140 minutes. Finally, we have detected enhancements above the
-  total solar irradiance at the top of the atmosphere for the same solar
-  zenith angle of up to \(204\,\text{W}/\text{m}^{2}\), with the
-  \(75\,\%\) of the cases below \(40\,\text{W}/\text{m}^{2}\). Most of
-  these extreme events occur in spring -- early summer, with a secondary
-  peak in autumn.
+  corresponding irradiation of
+  \(+329.9\pm 112.0\,\text{kJ}/\text{year}\). To our knowledge, such
+  long-term changes in CE events have not been presented in the past.
+  The peak of the CE events was observed during May and June. CE events
+  with duration longer than 10\nobreakspace{}min are very rare
+  (\(<8\,\%\)), with exceptions lasting over an hour and up to 140
+  minutes. Finally, we have detected enhancements above the total solar
+  irradiance at the top of the atmosphere for the same solar zenith
+  angle of up to \(204\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of
+  the cases below \(40\,\text{W}/\text{m}^{2}\). Most of these extreme
+  events occur in spring -- early summer, with a secondary peak in
+  autumn.
   \end{abstract}
@@
 number of CE events (\(+112\pm 35\,\text{cases}/\text{year}\)) and the
-excess irradiation (\(+329.9 \pm 112\,\text{kJ}/\text{year}\)), while
+excess irradiation (\(+329.9\pm 112.0\,\text{kJ}/\text{year}\)), while
 the trend in the yearly mean OI is negligible
@@
 irradiation of the CE events increasing with a rate of
-\(+329.9\pm 112\,\text{kJ}/\text{year}\). The most active months of CE
+\(+329.9\pm 112.0\,\text{kJ}/\text{year}\). The most active months of CE
 events are May and June. We found that continuous CE events can last up

### 2024-10-09 article/article.Rmd
Commit 2024-10-09 12:14
Commit 2024-10-09 21:12

@@
 $340\,\text{nm}$, as well as monthly climatological values of the Ångström exponent
-and constant WC of $15.6\,\text{mm}$ derived from the Cimel record, we simulated with
+and constant WC of $15.5\,\text{mm}$ derived from the Cimel record, we simulated with
 the RTM the cloud-free GHI at SZA of $55^\circ$ for each month in the period 1997 --
@@
 \begin{equation}
-\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot x -0.002981 \cdot x^2 \label{eq:AODchange}
+\Delta(\text{GHI}) [\%] = -12154 + 12.03 \cdot x -0.002977 \cdot x^2 \label{eq:AODchange}
 \end{equation}
-where $x$ is the date as a decimal fraction of the year.  The resulting change in
+where $x$ the year as a continuous variable.  The resulting change in
 $\text{GHI}_\text{ref}$ ranges between $-1.88\,\%$ in 1994 and $-0.19\,\%$ in the end of
@@
 GHI_model (%)
- = -12170 + 12.05 * year_frac + -0.002981 * year_frac^2
+ = -12153.97 + 12.0304 \cdot x -0.002977 * year_frac^2
 -->
@@
 $`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$.
+We also calculated the trend of the relative difference of the measured GHI versus the
+$\text{GHI}_\text{ref}$ for the same cloud-free days, and found a change of
+$0.03\,\%$ with a strong statistical significance. This further assures that the
+produced reference can adequate describe the long term variability of the observed
+GHI.
 

### 2024-10-09 article/article.tex
Commit 2024-10-09 20:14
Commit 2024-10-09 21:12

@@
 well as monthly climatological values of the Ångström exponent and
-constant WC of \(15.6\,\text{mm}\) derived from the Cimel record, we
+constant WC of \(15.5\,\text{mm}\) derived from the Cimel record, we
 simulated with the RTM the cloud-free GHI at SZA of \(55^\circ\) for
@@
 derive the long-term change in GHI due to aerosols: \begin{equation}
-\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot x -0.002981 \cdot x^2 \label{eq:AODchange}
-\end{equation} where \(x\) is the date as a decimal fraction of the
-year. The resulting change in \(\text{GHI}_\text{ref}\) ranges between
+\Delta(\text{GHI}) [\%] = -12154 + 12.03 \cdot x -0.002977 \cdot x^2 \label{eq:AODchange}
+\end{equation} where \(x\) the year as a continuous variable. The
+resulting change in \(\text{GHI}_\text{ref}\) ranges between
 \(-1.88\,\%\) in 1994 and \(-0.19\,\%\) in the end of 2023, peaking at
@@
 the \(\text{GHI}_\text{ref}\) an additional offset of
-\(25\,\text{W}/\text{m}^2\).
+\(25\,\text{W}/\text{m}^2\). We also calculated the trend of the
+relative different of the measured GHI over the
+\(\text{GHI}_\text{ref}\) for the same cloud-free days, and found a
+change of \(0.03\,\%\) with a strong statistical significance. This
+further assures that the produced reference can adequate describe the
+long term variability of the observed GHI.
 

### 2024-10-09 article/article.Rmd
Commit 2024-10-09 22:22

--- 2024-10-07 article/article.Rmd
@@
 \begin{equation}
-\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot x -0.002981 \cdot x^2 \label{eq:AODchange}
+\Delta(\text{GHI}) [\%] = -12153.97 + 12.0304 \cdot x -0.002977 \cdot x^2 \label{eq:AODchange}
 \end{equation}
-where $x$ is the date as a decimal fraction of the year.  The resulting change in
+where $x$ the year as a continuous variable.  The resulting change in
 $\text{GHI}_\text{ref}$ ranges between $-1.88\,\%$ in 1994 and $-0.19\,\%$ in the end of
@@
 Simulations with uvspec for the above Ångström coefficients, assuming constant WC of
-$15.6\,\text{mm}$ taken from the Cimel, and for a SZA of $55^\circ$ reveal a change of
+$15.5\,\text{mm}$ taken from the Cimel, and for a SZA of $55^\circ$ reveal a change of
 $+0.21\,\%$ per year in $\text{GHI}_\text{ref}$.  The SZA of $55^\circ$ was chosen as

### 2024-10-10 article/article.tex
Commit 2024-10-10 11:10

--- 2024-10-07 article/article.tex
@@
 derive the long-term change in GHI due to aerosols: \begin{equation}
-\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot x -0.002981 \cdot x^2 \label{eq:AODchange}
-\end{equation} where \(x\) is the date as a decimal fraction of the
-year. The resulting change in \(\text{GHI}_\text{ref}\) ranges between
+\Delta(\text{GHI}) [\%] = -12153.97 + 12.0304 \cdot x -0.002977 \cdot x^2 \label{eq:AODchange}
+\end{equation} where \(x\) the year as a continuous variable. The
+resulting change in \(\text{GHI}_\text{ref}\) ranges between
 \(-1.88\,\%\) in 1994 and \(-0.19\,\%\) in the end of 2023, peaking at
@@
 entire dataset (\(>6\) million of one-minute GHI measurements),
-\(2.32\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
+\(2.23\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
 events. The highest recorded GHI due to CE was
 \(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007 at a SZA of
-\(19.9^\circ\) corresponding to OI of \(369.3\,\text{W}/\text{m}^2\) or
-\(35.3\,\%\) above the threshold. The strongest CE event of \(53\,\%\)
+\(19.9^\circ\) corresponding to OI of \(366.3\,\text{W}/\text{m}^2\) or
+\(34.9\,\%\) above the threshold. The strongest CE event of \(53.2\,\%\)
 above the cloud-free threshold was observed on 28~October 2016 at a SZA
 of \(59.2^\circ\) with a GHI of \(861.8\,\text{W}/\text{m}^2\) and a OI
-of \(298.4\,\text{W}/\text{m}^2\). Both cases are also ECE events with
+of \(299.4\,\text{W}/\text{m}^2\). Both cases are also ECE events with
 \(131.2\,\text{W}/\text{m}^2\) and \(161.5\,\text{W}/\text{m}^2\) above
@@
 \(95\,\%\) confidence level) increasing trends appear for the yearly
-number of CE events (\(+112\pm 35\,\text{cases}/\text{year}\)) and the
-excess irradiation (\(+329.9\pm 112.0\,\text{kJ}/\text{year}\)), while
+number of CE events (\(+148\pm 35\,\text{cases}/\text{year}\)) and the
+excess irradiation (\(+430.8\pm 113.2\,\text{kJ}/\text{year}\)), while
 the trend in the yearly mean OI is negligible
-(\(+0.1\pm 0.2\,\text{W}/\text{m}^2/\text{year}\)) and of no statistical
+(\(+0.2\pm 0.2\,\text{W}/\text{m}^2/\text{year}\)) and of no statistical
 significance. The average OI for the entire period is
-\(+42.6\pm 2.8\,\text{W}/\text{m}^2\). The yearly excess irradiation due
+\(+42.4\pm 3.1\,\text{W}/\text{m}^2\). The yearly excess irradiation due
 to CE events ranges between about \(8\) and
@@
 events. For the majority (over \(62\,\%\)) of the CE events the OI is
-below the long-term average of \(42.6\,\text{W}/\text{m}^2\), while
+below the long-term average of \(42.4\,\text{W}/\text{m}^2\), while
 \(9.6\,\%\) of the events correspond to OI larger than
 \(100\,\text{W}/\text{m}^2\) and up to the highest value of
-\(437\,\text{W}/\text{m}^2\). This distribution is indicative of the
+\(438.3\,\text{W}/\text{m}^2\). This distribution is indicative of the
 magnitude and the probability of the expected CE events over
@@
 consecutive events, we grouped them into bins of increasing duration in
-steps of one minute. We have identified 34849 groups of CE events in the
+steps of one minute. We have identified 33663 groups of CE events in the
 whole period of study, where the group with the longest duration of 140
@@
 -- 2023. After analyzing the CE cases, we found an increasing tendency
-of \(+112.1\pm 34.9\,\text{cases}/\text{year}\), with the mean annual
+of \(+148.3\pm 35.3\,\text{cases}/\text{year}\), with the mean annual
 irradiation of the CE events increasing with a rate of
-\(+329.9\pm 112.0\,\text{kJ}/\text{year}\). The most active months of CE
+\(+430.8\pm 113.2\,\text{kJ}/\text{year}\). The most active months of CE
 events are May and June. We found that continuous CE events can last up

### 2024-10-10 article/article.tex
Commit 2024-10-10 12:14

@@
 entire dataset (\(>6\) million of one-minute GHI measurements),
-\(2.23\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
+\(2.36\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
 events. The highest recorded GHI due to CE was
 \(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007 at a SZA of
-\(19.9^\circ\) corresponding to OI of \(366.3\,\text{W}/\text{m}^2\) or
-\(34.9\,\%\) above the threshold. The strongest CE event of \(53.2\,\%\)
+\(19.9^\circ\) corresponding to OI of \(370.6\,\text{W}/\text{m}^2\) or
+\(35.4\,\%\) above the threshold. The strongest CE event of \(53.2\,\%\)
 above the cloud-free threshold was observed on 28~October 2016 at a SZA
 of \(59.2^\circ\) with a GHI of \(861.8\,\text{W}/\text{m}^2\) and a OI
-of \(299.4\,\text{W}/\text{m}^2\). Both cases are also ECE events with
+of \(299.1\,\text{W}/\text{m}^2\). Both cases are also ECE events with
 \(131.2\,\text{W}/\text{m}^2\) and \(161.5\,\text{W}/\text{m}^2\) above
@@
 \(95\,\%\) confidence level) increasing trends appear for the yearly
-number of CE events (\(+148\pm 35\,\text{cases}/\text{year}\)) and the
-excess irradiation (\(+430.8\pm 113.2\,\text{kJ}/\text{year}\)), while
+number of CE events (\(+113\pm 35\,\text{cases}/\text{year}\)) and the
+excess irradiation (\(+336.2\pm 114.1\,\text{kJ}/\text{year}\)), while
 the trend in the yearly mean OI is negligible
-(\(+0.2\pm 0.2\,\text{W}/\text{m}^2/\text{year}\)) and of no statistical
+(\(+0.1\pm 0.2\,\text{W}/\text{m}^2/\text{year}\)) and of no statistical
 significance. The average OI for the entire period is
-\(+42.4\pm 3.1\,\text{W}/\text{m}^2\). The yearly excess irradiation due
+\(+42.7\pm 2.8\,\text{W}/\text{m}^2\). The yearly excess irradiation due
 to CE events ranges between about \(8\) and
@@
 events. For the majority (over \(62\,\%\)) of the CE events the OI is
-below the long-term average of \(42.4\,\text{W}/\text{m}^2\), while
-\(9.6\,\%\) of the events correspond to OI larger than
+below the long-term average of \(42.7\,\text{W}/\text{m}^2\), while
+\(9.7\,\%\) of the events correspond to OI larger than
 \(100\,\text{W}/\text{m}^2\) and up to the highest value of
-\(438.3\,\text{W}/\text{m}^2\). This distribution is indicative of the
+\(438.2\,\text{W}/\text{m}^2\). This distribution is indicative of the
 magnitude and the probability of the expected CE events over
@@
 consecutive events, we grouped them into bins of increasing duration in
-steps of one minute. We have identified 33663 groups of CE events in the
+steps of one minute. We have identified 35342 groups of CE events in the
 whole period of study, where the group with the longest duration of 140
@@
 -- 2023. After analyzing the CE cases, we found an increasing tendency
-of \(+148.3\pm 35.3\,\text{cases}/\text{year}\), with the mean annual
+of \(+113.4\pm 35.5\,\text{cases}/\text{year}\), with the mean annual
 irradiation of the CE events increasing with a rate of
-\(+430.8\pm 113.2\,\text{kJ}/\text{year}\). The most active months of CE
+\(+336.2\pm 114.1\,\text{kJ}/\text{year}\). The most active months of CE
 events are May and June. We found that continuous CE events can last up

### 2024-10-10 article/article.tex
Commit 2024-10-10 13:12
Commit 2024-10-10 18:14

@@
 unit. A summary of extreme cloud enhancement (ECE) cases has been
-compiled by \citet{Martins2022}. Cloud enhancements can have also some
+compiled by \citet{Martins2022}. Cloud enhancements can also have some
 practical implications. The intensity and duration of enhancements can
@@
 combinations with additional offsets of \(\pm1\sigma\) and
-\(\pm2\sigma\), were used as inputs to the RTM in the construction of
-the LUT.
+\(\pm2\sigma\), were used as inputs to the RTM for the construction of
+the LUT. Of note, the total ozone column plays a minor role in GHI as it
+affects mainly the UV wavelengths. However, it is entered in the RTM
+simulations via the seasonal atmospheric profiles. The long-term
+variability of total ozone in Thessaloniki for the period of study is
+very small thus cannot affect the long-term \(\text{GHI}_\text{ref}\).
 
@@
 the \(\text{GHI}_\text{ref}\) an additional offset of
-\(25\,\text{W}/\text{m}^2\).
+\(`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2\). The long-term difference
+between the measured GHI and the \(\text{GHI}_{\text{ref}}\) for the
+same cloud-free days has a trend of \(0.2\,\text{W}/\text{m}^2\) per
+year which further supports the validity of the produced long-term
+\(\text{GHI}_\text{ref}\).
 

### 2024-10-10 article/article.Rmd
Commit 2024-10-10 13:12
Commit 2024-10-10 19:13

@@
     country:      Greece
-  # - code:         Another University
-  #   organization: Department
-  #   addressline:  A street 29
-  #   postcode:     2054 NX
-  #   city:         Manchester,
-  #   state:        State
-  #   country:      The Netherlands
 # footnote:
@@
   Brewer spectrophotometer. We found a trend in CE events of
-  \(+112\pm 35\,\text{cases}/\text{year}\), and a trend in the
-  corresponding irradiation of \(+329.9\pm 112.0\,\text{kJ}/\text{year}\).
-  To our knowledge, such long-term changes in CE events have not been presented in the past.
-  The peak of the CE events was observed during May and June. CE events
-  with duration longer than 10\nobreakspace{}min are very rare
-  (\(<8\,\%\)), with exceptions lasting over an hour and up to 140
-  minutes. Finally, we have detected enhancements above the total solar
-  irradiance at the top of the atmosphere for the same solar zenith angle
-  of up to \(204\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the
-  cases below \(40\,\text{W}/\text{m}^{2}\). Most of these extreme events
-  occur in spring -- early summer, with a secondary peak in autumn.
+  \(+113\pm 35\,\text{cases}/\text{year}\), and a trend in the
+  corresponding irradiation of \(+336.2\pm 114.1\,\text{kJ}/\text{year}\).
+  To our knowledge, such long-term changes in CE events have not been
+  presented in the past. The peak of the CE events was observed during May
+  and June. CE events with duration longer than 10\nobreakspace{}min are
+  very rare (\(<8\,\%\)), with exceptions lasting over an hour and up to
+  140 minutes. Finally, we have detected enhancements above the total
+  solar irradiance at the top of the atmosphere for the same solar zenith
+  angle of up to \(204\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of
+  the cases below \(40\,\text{W}/\text{m}^{2}\). Most of these extreme
+  events occur in spring -- early summer, with a secondary peak in autumn.
+
+#  In this study, we investigate the characteristics of global horizontal
+#  irradiance enhancement events induced by clouds over Thessaloniki for
+#  the period 1994 -- 2023 using data recorded every one minute. We
+#  identified the cloud enhancement (CE) events by creating an appropriate
+#  cloud-free irradiance reference using a radiative transfer model and
+#  aerosol optical depth data from a collocated Cimel sun photometer and a
+#  Brewer spectrophotometer. We found a trend in CE events of
+#  \(+112\pm 35\,\text{cases}/\text{year}\), and a trend in the
+#  corresponding irradiation of \(+329.9\pm 112.0\,\text{kJ}/\text{year}\).
+#  To our knowledge, such long-term changes in CE events have not been presented in the past.
+#  The peak of the CE events was observed during May and June. CE events
+#  with duration longer than 10\nobreakspace{}min are very rare
+#  (\(<8\,\%\)), with exceptions lasting over an hour and up to 140
+#  minutes. Finally, we have detected enhancements above the total solar
+#  irradiance at the top of the atmosphere for the same solar zenith angle
+#  of up to \(204\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the
+#  cases below \(40\,\text{W}/\text{m}^{2}\). Most of these extreme events
+#  occur in spring -- early summer, with a secondary peak in autumn.
 
@@
 enhancement (ECE) cases has been compiled by @Martins2022. Cloud enhancements can
-have also some practical implications.  The intensity and duration of enhancements
+also have some practical implications.  The intensity and duration of enhancements
 can affect the efficiency and stability of photovoltaic power production
@@
 additional offsets of $\pm1\sigma$ and $\pm2\sigma$, were used as inputs to the RTM
-in the construction of the LUT.
+for the construction of the LUT.  Of note, the total ozone column plays a minor role
+in GHI as it affects mainly the UV wavelengths. However, it is entered in the RTM
+simulations via the seasonal atmospheric profiles. The long-term variability of total
+ozone in Thessaloniki for the period of study is very small thus cannot affect the
+long-term $\text{GHI}_\text{ref}$.
 
@@
 \begin{equation}
-\Delta(\text{GHI}) [\%] = -12153.97 + 12.0304 \cdot x -0.002977 \cdot x^2 \label{eq:AODchange}
+\Delta(\text{GHI}) [\%] = -12153.97 + 12.0304 \cdot y -0.002977 \cdot y^2 \label{eq:AODchange}
 \end{equation}
-where $x$ the year as a continuous variable.  The resulting change in
-$\text{GHI}_\text{ref}$ ranges between $-1.88\,\%$ in 1994 and $-0.19\,\%$ in the end of
-2023, peaking at $0.23\,\%$ in the mid-2020. Finally, we applied these long-term
+where $y$ is the year in decimal form.  The resulting change in
+$\text{GHI}_\text{ref}$ ranges between $-2\,\%$ in 1994 and $0.05\,\%$ in the end of
+2023, peaking at $0.09\,\%$ in the mid-2020. Finally, we applied these long-term
 changes of Equation\nobreakspace{}\ref{eq:AODchange} to the $\text{GHI}_\text{ref}$,
@@
 GHI_model (%)
- = -12170 + 12.05 * year_frac + -0.002981 * year_frac^2
+  -12153.97 + 12.0304 * x + -0.002977 * x^2
 -->
@@
 applied to the $\text{GHI}_\text{ref}$ an additional offset of
-$`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$.
+$`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$.  The long-term difference between the
+measured GHI and the $\text{GHI}_{\text{ref}}$ for the same cloud-free days has a
+trend of $0.2\,\text{W}/\text{m}^2$ per year which further supports the validity of
+the produced long-term $\text{GHI}_\text{ref}$.
 
@@
 conditions, with the spread likely caused by the short-term variability of
-AOD. A small fraction of these data corresponds also to cases with thin cirrus clouds
+AOD. A small fraction of these data corresponds to cases with thin cirrus clouds
 causing weak attenuation of GHI, often indistinguishable from the attenuation by
@@
 The logarithmic color scale denotes the frequency of the respective groups.
-Note that 19 points of groups with duration higher than 60 min are not shown."}
+Note that 19 points for groups with duration higher than 60 min are not shown."}
 knitr::include_graphics("../images/P-groups-bin2d-1.pdf")

### 2024-10-10 article/article.tex
Commit 2024-10-10 19:13

@@
   photometer and a Brewer spectrophotometer. We found a trend in CE
-  events of \(+112\pm 35\,\text{cases}/\text{year}\), and a trend in the
+  events of \(+113\pm 35\,\text{cases}/\text{year}\), and a trend in the
   corresponding irradiation of
-  \(+329.9\pm 112.0\,\text{kJ}/\text{year}\). To our knowledge, such
+  \(+336.2\pm 114.1\,\text{kJ}/\text{year}\). To our knowledge, such
   long-term changes in CE events have not been presented in the past.
@@
 derive the long-term change in GHI due to aerosols: \begin{equation}
-\Delta(\text{GHI}) [\%] = -12153.97 + 12.0304 \cdot x -0.002977 \cdot x^2 \label{eq:AODchange}
-\end{equation} where \(x\) the year as a continuous variable. The
-resulting change in \(\text{GHI}_\text{ref}\) ranges between
-\(-1.88\,\%\) in 1994 and \(-0.19\,\%\) in the end of 2023, peaking at
-\(0.23\,\%\) in the mid-2020. Finally, we applied these long-term
-changes of Equation\nobreakspace{}\ref{eq:AODchange} to the
+\Delta(\text{GHI}) [\%] = -12153.97 + 12.0304 \cdot y -0.002977 \cdot y^2 \label{eq:AODchange}
+\end{equation} where \(y\) is the year in decimal form. The resulting
+change in \(\text{GHI}_\text{ref}\) ranges between \(-2\,\%\) in 1994
+and \(0.05\,\%\) in the end of 2023, peaking at \(0.09\,\%\) in the
+mid-2020. Finally, we applied these long-term changes of
+Equation\nobreakspace{}\ref{eq:AODchange} to the
 \(\text{GHI}_\text{ref}\), to create a more realistic representation of
@@
 the \(\text{GHI}_\text{ref}\) an additional offset of
-\(`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2\). The long-term difference
-between the measured GHI and the \(\text{GHI}_{\text{ref}}\) for the
-same cloud-free days has a trend of \(0.2\,\text{W}/\text{m}^2\) per
-year which further supports the validity of the produced long-term
+\(25\,\text{W}/\text{m}^2\). The long-term difference between the
+measured GHI and the \(\text{GHI}_{\text{ref}}\) for the same cloud-free
+days has a trend of \(0.2\,\text{W}/\text{m}^2\) per year which further
+supports the validity of the produced long-term
 \(\text{GHI}_\text{ref}\).
@@
 cloud-free conditions, with the spread likely caused by the short-term
-variability of AOD. A small fraction of these data corresponds also to
-cases with thin cirrus clouds causing weak attenuation of GHI, often
+variability of AOD. A small fraction of these data corresponds to cases
+with thin cirrus clouds causing weak attenuation of GHI, often
 indistinguishable from the attenuation by aerosols.
@@
 The logarithmic color scale denotes the frequency of the respective groups.
-Note that 19 points of groups with duration higher than 60 min are not shown.}\label{fig:group-2d}
+Note that 19 points for groups with duration higher than 60 min are not shown.}\label{fig:group-2d}
 \end{figure}

### 2024-10-11 SUBMISSION_03/article/article.tex
Commit 2024-10-12 01:08

--- 2024-09-11 SUBMISSION_02/article/article.tex
@@
   events of \(+112\pm 35\,\text{cases}/\text{year}\), and a trend in the
-  corresponding irradiation of \(+329.9\pm 112\,\text{kJ}/\text{year}\).
+  corresponding irradiation of \(+329.9\pm 112.0\,\text{kJ}/\text{year}\).
   To our knowledge, such long-term changes in CE events have not been
@@
 derive the long-term change in GHI due to aerosols: \begin{equation}
-\Delta(\text{GHI}) [\%] = -12170 + 12.05 \cdot x + -0.002981 \cdot x^2 \label{eq:AODchange}
-\end{equation} where \(y\) is the date as a decimal fraction of the
-year. The resulting change in \(\text{GHI}_\text{ref}\) ranges between
-\(-1.88\) in 1994 and \(-0.19\,\%\) in the end of 2023, peaking at
-\(0.23\,\%\) in the mid-2020. Finally, we applied these long-term
-changes of Equation\nobreakspace{}\ref{eq:AODchange} to the
+\Delta(\text{GHI}) [\%] = -12153.97 + 12.0304 \cdot y -0.002977 \cdot y^2 \label{eq:AODchange}
+\end{equation} where \(y\) is the year in decimal form. The resulting 
+change in \(\text{GHI}_\text{ref}\) ranges between \(-2\,\%\) in 1994
+and \(0.05\,\%\) in the end of 2023, peaking at \(0.09\,\%\) in the
+mid-2020. Finally, we applied these long-term changes of
+Equation\nobreakspace{}\ref{eq:AODchange} to the
 \(\text{GHI}_\text{ref}\), to create a more realistic representation of
@@
 the \(\text{GHI}_\text{ref}\) an additional offset of
-\(25\,\text{W}/\text{m}^2\).
+\(25\,\text{W}/\text{m}^2\). The long-term difference between the
+measured GHI and the \(\text{GHI}_{\text{ref}}\) for the same cloud-free
+days has a trend of \(0.2\,\text{W}/\text{m}^2\) per year which further
+supports the validity of the produced long-term
+\(\text{GHI}_\text{ref}\).
 
@@
 The logarithmic color scale denotes the frequency of the respective groups.
-Note that 19 pints with duration higher than 60 min are not shown.}\label{fig:group-2d}
+Note that 19 points for groups with duration higher than 60 min are not shown.}\label{fig:group-2d}
 \end{figure}
